```{r data generation, echo = FALSE, results = "hide"}
B = sample(2:3,1)
while(T){
    x1 = sort(sample(-10:10,4))
    x2 = x1
    y1 = sample(-3:3,4)
    y2 = y1*B
    if(min(x1)<0 && max(x1)>0 && min(y1)<0 && max(y1)>0){break}
}

CA = paste0("g(x)=\\frac{f(x)}{",B,"}")

sol3 = paste0(1*(2:4==B),collapse="")

```

Question
========

Let function $g$ be defined as a transformation of function $f$.

$$`r CA`$$

The blue curve represents $y=f(x)$. The red curve represents $y=g(x)$.

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 10
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
lines(x2,y2,col="blue",lwd=1.4)
points(x2,y2,col="blue",pch=19,cex=0.5)
lines(x1,y1,col="red",lwd=1.4)
points(x1,y1,col="red",pch=19,cex=0.5)


plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=f(x)$"),TeX("$y=g(x)$")),col=c("blue","red"),lwd=c(1.4,1.4))
```
\

What kind of transformation do we see from $y=f(x)$ to $y=g(x)$?

* ##ANSWER1## ##ANSWER2## by factor ##ANSWER3##


Answerlist
--------

* Horizontal
* Vertical
* Stretch
* Shrink
* 2
* 3
* 4


Solution
========

Notice the red dots are squeezed closer to the horizontal axis by a factor of `r B`. Or, as a coordinate transformation:

$$(a,b) \to \left(a~,~\frac{b}{`r B`}\right)$$

The correct description is that we see a vertical shrink by factor `r B`.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: 01|01|`r sol3`
exname: ver_squeeze_desc