```{r data generation, echo = FALSE, results = "hide"}
np = 4
VH = sample(2:3)
V = VH[1]
H = VH[2]
a = sort(6*sample(c(-5:-1,1:5),np))
b = 6*sample(c(-5:-1,1:5),np)

qt = sample(1:4,1)
if(qt==1){
    CA = paste0("y~=~",V,"\\cdot f(",H,"\\cdot x)",collapse="")
    x = a/H
    y = b*V
    hss = "shrink"
    vss = "stretch"
    ex1 = paste0(H,"\\cdot x",collapse="")
    ex2 = paste0("\\frac{a}{",H,"}",collapse="")
    ex3 = paste0(V,"\\cdot b",collapse="")
}
if(qt==2){
    CA = paste0("y~=~",V,"\\cdot f{\\left(\\frac{x}{",H,"}\\right)}",collapse="")
    x = a*H
    y = b*V
    hss = "stretch"
    vss = "stretch"
    ex1 = paste0("\\frac{x}{",H,"}",collapse="")
    ex2 = paste0(H,"\\cdot a",collapse="")
    ex3 = paste0(V,"\\cdot b",collapse="")
}
if(qt==3){
    CA = paste0("y~=~ \\frac{f(",H,"\\cdot x)}{",V,"}",collapse="")
    x = a/H
    y = b/V
    hss = "shrink"
    vss = "shrink"
    ex1 = paste0(H,"\\cdot x",collapse="")
    ex2 = paste0("\\frac{a}{",H,"}",collapse="")
    ex3 = paste0("\\frac{b}{",V,"}",collapse="")
}
if(qt==4){
    CA = paste0("y~=~\\frac{f{\\left(\\frac{x}{",H,"}\\right)}}{",V,"}",collapse="")
    x = a*H
    y = b/V
    hss = "stretch"
    vss = "shrink"
    ex1 = paste0("\\frac{x}{",H,"}",collapse="")
    ex2 = paste0(H,"\\cdot a",collapse="")
    ex3 = paste0("\\frac{b}{",V,"}",collapse="")
}

al = numeric()

aches = list()
sols = character()
for(i in 1:length(a)){
    aches[[i]] = c(a[i]/3,a[i]/2,a[i]*2,a[i]*3)
    sols = c(sols,paste0(1*(x[i]==aches[[i]]),collapse=""))
    al = c(al,a[i]/3,a[i]/2,a[i]*2,a[i]*3)
}
for(i in 1:length(a)){
    aches[[np+i]] = c(b[i]/3,b[i]/2,b[i]*2,b[i]*3)
    sols = c(sols,paste0(1*(y[i]==aches[[np+i]]),collapse=""))
    al = c(al,b[i]/3,b[i]/2,b[i]*2,b[i]*3)
}



```

Question
========

Let $f$ be a function. Solutions to $b=f[a]$ are shown as rows in the table:

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(a,b)
colnames(df) = c("$a$","$b$")
kable(df) %>%
    kable_styling("bordered",full_width = F)
```


Each $(a,b)$ solution has a corresponding $(x,y)$ solution to the equation below.

$$`r CA`$$

Express the corresponding solutions in the same order.

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(paste0("##ANSWER",1:np,"##"),paste0("##ANSWER",(np+1):(2*np),"##"))
colnames(df) = c("$x$","$y$")
kable(df) %>%
    kable_styling("bordered",full_width = F)
```

Answerlist
--------

`r paste0("* ",al,collapse="\n")`


Solution
========

The transformations are a horizontal `r hss` by factor `r H` and a vertical `r vss` by factor `r V`.

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(x,y)
colnames(df) = c("$x$","$y$")
kable(df) %>%
    kable_styling("bordered",full_width = F)

```

We could approach this by finding the coordinate transformations. First, we set the argument to $a$.

$$`r ex1`=a$$
$$x=`r ex2`$$

Then, replace $f(\ldots)$ with $b$.

$$y=`r ex3`$$

This gives the coordinate transformation:

$$(a,b)~\to~ \left(`r ex2`~,~`r ex3`\right)$$



Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",2*np),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: ab_to_xy_stretch