---
output: slidy_presentation
title: "Stretching and Shrinking Functions"
---


# Agenda

* Entrance Ticket: [ET_1001](https://bart.instructure.com/courses/2110/quizzes/3209)
    * When function transformation given as an equation like $y=\ldots f(x\ldots)\ldots$:
        * To get new $x$ values, set argument=$a$, where $a$ is an old $x$ value.
        * To get new $y$ values, replace $f(\ldots)$ with $b$, where $b$ is an old $y$ value.
* [OCW_1001_scaling_descriptions](https://bart.instructure.com/courses/2110/quizzes/3210)
    * Describe the stretching/shrinking shown with equation and graph.
* [OCW_1001_B_stretch_eqs](https://bart.instructure.com/courses/2110/quizzes/3211)
    * From graph, determine the function-stretch equation.


# Stretching/shrinking

Transformations are described relative to $y=f(x)$.

* $y=f(2x)$ causes points to shrink horizontally towards the $y$ axis.
$$(a,b)\to \left(\frac{a}{2}~,~b\right)$$
* $y=f{\left(\frac{x}{2}\right)}$ causes points to stretch horizontally away from the $y$ axis.
$$(a,b)\to \left(2a~,~b\right)$$
* $y=2\cdot f(x)$ causes points to stretch vertically away from the $x$ axis.
$$(a,b)\to \left(a~,~2b\right)$$
* $y=\frac{f(x)}{2}$ causes points to shrink vertically toward the $x$ axis.
$$(a,b)\to \left(a~,~\frac{b}{2}\right)$$

Of course, I'm just using 2 as an example. This generalizes with any scale factor.

* The horizontal transformations are "backwards" and indicated by operations inside the argument. 
* The vertical transformations are "normal" and indicated by operations outside the function.


# Examples of horizontal shrinking

Notice $y=\sqrt{2x}$ is shrunk towards the $y$ axis. (Unfortunately we see this could also be visualized as a stretch vertically. A lot of the parent functions have an equivalent vertical stretch for any horiztonal shrink.)

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 10
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
x = seq(0,10,0.01)
xp = c(1,2,4,9)
lines(x,sqrt(x),col="grey",lwd=1.4)
points(xp,sqrt(xp),col="grey",pch=19,cex=0.5)
lines(x,sqrt(2*x),col="blue",lwd=1.4)
points(xp/2,sqrt(xp),col="blue",pch=19,cex=0.5)

plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=\\sqrt{x}$"),TeX("$y=\\sqrt{2x}$")),col=c("grey","blue"),lwd=c(1.4,1.4))
```
\

Notice $y=\cos(2x)$ is shrunk towards the $y$ axis. The trigonometric wave functions are excellent examples of functions with clearly distinct horizontal shrink and vertical stretch.

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 10
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
x = seq(-10,10,0.01)
xp = pi*(-5:5)
lines(x,cos(x),col="grey",lwd=1.4)
points(xp,cos(xp),col="grey",pch=19,cex=0.5)
lines(x,cos(2*x),col="blue",lwd=1.4)
points(xp/2,cos(xp),col="blue",pch=19,cex=0.5)

plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=\\cos{x}$"),TeX("$y=\\cos(2x)$")),col=c("grey","blue"),lwd=c(1.4,1.4))
```
\


# Example of horizontal stretch

Notice $y=\cos{\left(\frac{x}{2}\right)}$ is stretched away from the $x$ axis.

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 10
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
x = seq(-10,10,0.01)
lines(x,cos(x),col="grey",lwd=1.4)
lines(x,cos(x/2),col="blue",lwd=1.4)

plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=\\cos{x}$"),TeX("$y=\\cos{\\left(\\frac{x}{2}\\right)}$")),col=c("grey","blue"),lwd=c(1.4,1.4))
```
\



# Example of vertical stretch

Notice $y=2\cos(x)$ is stretched away from the $x$ axis.

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 10
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
x = seq(-10,10,0.01)
lines(x,cos(x),col="grey",lwd=1.4)
lines(x,2*cos(x),col="blue",lwd=1.4)

plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=\\cos{x}$"),TeX("$y=2\\cos(x)$")),col=c("grey","blue"),lwd=c(1.4,1.4))
```
\


# Example of vertical shrink

Notice $y=\frac{\cos(x)}{2}$ is shrunk toward the $x$ axis.

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 10
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
x = seq(-10,10,0.01)
lines(x,cos(x),col="grey",lwd=1.4)
lines(x,cos(x)/2,col="blue",lwd=1.4)

plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=\\cos{x}$"),TeX("$y=\\frac{\\cos(x)}{2}$"),""),col=c("grey","blue",NA),lwd=c(1.4,1.4,0))
```
\




