```{r data generation, echo = FALSE, results = "hide"}
g1 = list("A",
          list("A"="B-A-B",
               "B"="A+B+A"),
          6,
          60)
g2 = list("A",
          list("A"="A[+A][-A]B",
               "B"="[--B][++B]A"),
          5,
          30)
g3 = list("A",
          list("A"="-B+B+B+B+B+B",
               "B"="B[--CCA][-CCA]B",
               "C"="CC"),
          5,
          60)
g4 = list("A",
          list("A"="[----AAB][--AAB][++AAB]AAB",
               "B"="[-C][+C][--C][++C][---C][+++C]",
               "C"="CAB"),
          3,
          45)

g5 = list("A",
          list("A"="[-AAB][--AAB][+AAB][++AAB]AAB",
               "B"="[-C][+C][--C][++C]CA",
               "C"="CC"),
          3,
          72)

g6 = list("A",
          list("A"="-B+B+B+B+B+B",
               "B"="BB[-CCA]",
               "C"="CC"),
          5,
          60)

g7 = list("A",
          list("A"="B+B+B+B+B",
               "B"="[-CCA]BB",
               "C"="CC"),
          5,
          72)

g8 = list("A++++A",
          list("A"="+A-B-B[B]",
               "B"="-B+A+A[A]"),
          5,
          45)

g9 = list("A++A",
          list("A"="AB[-A][+A]",
               "B"="A"),
          6,
          90)

g10 = list("A+++A+++A+++A",
          list("A"="B--B",
               "B"="AA+++AA"),
          7,
          30)

g11 = list("A",
           list("A"="AB",
                "B"="A[++C][--C]",
                "C"="C[+C][-C]A"),
           7,
           45)

g12 = list("A",
           list("A"="X[-A][+A]AA",
                "X"="XX"),
           5,
           60)

g13 = list("A",
           list("A"="X[-A][+A]A",
                "X"="XX"),
           6,
           60)

g14 = list("A++++++.A",
           list("A"="B+B+B+B+B+B+B",
                "B"="B[-CCA][+CCA]",
                "C"="CC"),
           5,
           30)

g15 = list("A",
           list("A"="ABA",
                "B"="[-BAB][+BAB]"),
           6,
           90)

g16 = list("AA",
           list("A"="ABA",
                "B"="C[-BAB][+BAB]",
                "C"="CC"),
           5,
           90)

g17 = list("AA",
           list("A"="B-AA-B",
                "B"="A+B+A"),
                6,
                45)

g18 = list("AA",
           list("A"="B-AA-B",
                "B"="AB+B+A"),
                5,
                90)

g19 = list("AA",
           list("A"="B-AA-B",
                "B"="AB+B+AB"),
                5,
                90)

g20 = list("A++A++A++A",
           list("A"="B-CAC-B",
                "B"="AB-BA",
                "C"="CC"),
                5,
                135)

g21 = list("A.A",
           list("A"="BC",
                "B"="B[+C][-C]",
                "C"="CAD",
                "D"="DD[+D+D][-D-D]"),
                5,
                60)

g22 = list("A",
           list("A"="B-ABA-B",
                "B"="A+B+A"),
           6,
           72)

g23 = list("A",
           list("A"="B-ABA-B",
                "B"="A+B+A"),
           6,
           90)

g24 = list("A",
           list("A"="B-ABA-B",
                "B"="A+B+A"),
           6,
           120)

g25 = list("A",
           list("A"="B-ABA-B",
                "B"="A+B+A"),
           6,
           108)

g26 = list("A",
           list("A"="B-ABA-B",
                "B"="A+B+A"),
           4,
           135)

g27 = list("A++A++A++A",
           list("A"="B-ABA-B",
                "B"="A+BB+A"),
           4,
           135)

g28 = list("A",
           list("A"="A[+A][-A]B",
                "B"="A[--B][++B]B"),
           6,
           108)

g29 = list("A",
           list("A"="A[+A][-A]A[+B][-B]",
                "B"="A[--B][++B]B"),
           5,
           60)

g30 = list("A",
           list("A"="A[+A][-A]A[+B][-B]",
                "B"="A[--B][++B]B"),
           5,
           20)

g31 = list("A",
           list("A"="A[+A][-A]A[+B][-B]",
                "B"="A[----B][++++B]B"),
           5,
           45)

g32 = list("A",
           list("A"="A[++A][--A]A[+B][-B]",
                "B"="A[----B][++++B]B"),
           5,
           45)

g33 = list("A",
           list("A"="B++B++B++B++B",
                "B"="B[-CCC-CC-CCA][----CC-CCB]B",
                "C"="CC"),
           5,
           36)

g34 = list("A",
           list("A"="B++A++A++B",
                "B"="AB[A-CC-CC-CCA]BA",
                "C"="CC"),
           5,
           90)

g35 = list("A++++XA",
           list("A"="AA[-B][+B]B",
                "B"="[---ABC][+++ABC]",
                "C"="A[-CB][+CB]",
                "X"="XX"),
           5,
           45)

g36 = list("A+++XA",
           list("A"="AA[-B][+B]B",
                "B"="[--ABC][++ABC]",
                "C"="A[-CB][+CB]",
                "X"="XX"),
           5,
           60)

g37 = list("[A]+[A]+[A]+[A]+[A]+[A]",
           list("A"="AA[-B][+B]B",
                "B"="[-ABC][+ABC]",
                "C"="A[-CB][+CB]"),
           4,
           60)

g38 = list("[A]+[A]+[A]+[A]+[A]",
           list("A"="AA[-B][+B]B",
                "B"="[-ABC][+ABC]",
                "C"="A[-CB][+CB]"),
           4,
           72)

g39 = list("[A]+[A]+[A]+[A]",
           list("A"="AA[-B][+B]B",
                "B"="[-ABC][+ABC]",
                "C"="A[-CB][+CB]"),
           4,
           90)

g40 = list("[A]+[A]+[A]",
           list("A"="AA[-B][+B]B",
                "B"="[-ABC][+ABC]",
                "C"="A[-CB][+CB]"),
           4,
           120)

g41 = list("A",
           list("A"="C[+CA][CCCA][-CA]",
                "C"="CC"),
           6,
           45)

g42 = list("A",
           list("A"="C[+CA][CCCCB][-CA]",
                "B"="[++A][--A]",
                "C"="CC"),
           6,
           45)

g43 = list("[A]--[A]--[A]--[A]",
           list("A"="C[+CB][CCA][-CB]",
                "B"="CCC[+++A][---A]",
                "C"="CA"),
           4,
           45)

g44 = list("A",
           list("A"="A[-DB][+DB]C",
                "B"="DC[++DA][--DA]B",
                "C"="[+++D][---D]A",
                "D"="DD"),
           6,
           40)

g45 = list("[A]+++[A]+++[A]",
           list("A"="A[---XB][-XB][+XB][+++XB]",
                "B"="XB[++XA][--XA]XA",
                "X"="XX"),
           4,
           40)

g46 = list("[A]+++[A]+++[A]",
           list("A"="A[---XB][-XB][+XB][+++XB]",
                "B"="XB[++XA][--XA]A",
                "X"="XX"),
           4,
           40)

g47 = list("A",
           list("A"="[---B][-B][+B][+++B]",
                "B"="BD[++DA][--DA]B",
                "D"="DD"),
           5,
           45)

g48 = list("A------A",
           list("A"="[---B][-B][+B][+++B]",
                "B"="BD[++DA][--DA]B",
                "D"="DD"),
           5,
           30)

g49 = list("A+A++++++A+A",
           list("A"="[---B][-B][+B][+++B]",
                "B"="BD[++DA][--DA]B",
                "D"="DD"),
           4,
           30)

g50 = list("A--A--A",
           list("A"="A[-A]A"),
           6,
           60)

g51 = list("B---A",
           list("A"="A[-AB]A",
                "B"="B[+BA]B"),
           5,
           60)

g52 = list("[A][B]",
           list("A"="[-XBA]A",
                "B"="[+XAB]B",
                "X"="XX"),
           6,
           30)

g53 = list("[A][B]",
           list("A"="C[-A-B]A",
                "B"="C[+B+A]B",
                "C"="CC"),
           5,
           30)

g54 = list("[+A][-B]",
           list("A"="[-CA-CB]A",
                "B"="[+CB+CA]B",
                "C"="CC"),
           7,
           30)

g55 = list("[+A][-B]",
           list("A"="[-CA-CB]A",
                "B"="[+CB+CA]B",
                "C"="CC"),
           6,
           90)

g56 = list("[+A][-B]",
           list("A"="[-CA-CB]A",
                "B"="[+CB+CA]B",
                "C"="CC"),
           6,
           120)

g57 = list("[+A][-B]",
           list("A"="[-CA-CB]A",
                "B"="[+CB+CA]B",
                "C"="CC"),
           6,
           150)

g58 = list("[+A][-B]",
           list("A"="[-CA-CB]CA",
                "B"="[+CB+CA]CB",
                "C"="CC"),
           6,
           150)

g59 = list("A",
           list("A"="XXX-B+BB+BB+BB+B",
                "X"="XX",
                "B"="B[-XXA]B"),
           4,
           90)

g60 = list("A",
           list("A"="XX[BBB+BB+B]A",
                "X"="XX",
                "B"="B[-XA][+XA]B"),
           4,
           30)

g61 = list("A",
           list("A"="XX[B+BB+BB+BB+B]",
                "X"="XX",
                "B"="BA"),
           6,
           90)

g62 = list("A",
           list("A"="XXX[B+BB+BB+B]",
                "X"="XX",
                "B"="BA"),
           6,
           120)

g63 = list("A",
           list("A"="X[-B+BB+BB+BB+BB+BB+B]",
                "X"="XX",
                "B"="X[+A-AA-AA-AA-AA-AA-A]"),
           3,
           10)

g64 = list("A",
           list("A"="B[-A][+A]",
                "B"="[DA][--DA][++DA]",
                "D"="DD"),
           7,
           60)

g65 = list("X",
           list("F"="FF",
                "X"="F[+XXF+F][-XXF-F]FXX"),
           4,
           30)

g66 = list("X",
           list("F"="FF",
                "X"="FF[+XFF+XF][-XFF-XF]FXX"),
           4,
           30)

g67 = list("X",
           list("F"="FF",
                "X"="FF[+XFFX+XF][-XFFX-XF]FXXFX"),
           3,
           30)

g68 = list("A",
           list("A"="AA[-B][+B]B",
                "B"="B[-ABC][+ABC]",
                "C"="C[-CBA][+CBA]"),
           4,
           60)

g69 = list("A",
           list("A"="A[-BC][+BC]BC",
                "B"="BB[-ABC][+ABC]",
                "C"="CCC[-CBA][+CBA]"),
           4,
           60)

g70 = list("GA",
           list("A"="[---BC][+++BC]",
                "B"="F[--AC][++AC]",
                "C"="FF[-BA][+BA]",
                "F"="FF",
                "G"="F"),
           5,
           15)

g71 = list("GA",
           list("A"="[---BC][+++BC]",
                "B"="[--AC][++AC]",
                "C"="FF[-BA][+BA]",
                "F"="FF",
                "G"="F"),
           5,
           15)

g72 = list("[A]------------[A]",
           list("A"="[---BC][+++BC]",
                "B"="[--AC][++AC]",
                "C"="F[-BA][+BA]",
                "F"="FF"),
           5,
           15)

g73 = list("C",
           list("A"="F[---BC][+++BC]",
                "B"="F[-CA][+CA]",
                "C"="[-AB][+AB]",
                "F"="FF"),
           6,
           15)

goodies = list(g1,g2,g3,g4,g5,g6,g7,g8,g9,g10,g11,g12,g13,g14,g15,g16,g17,g18,g19,g20,g21,g22,g23,g24,g25,g26,g27,g28,g29,g30,g31,g32,g33,g34,g35,g36,g37,g38,g39,g40,g41,g42,g43,g44,g45,g46,g47,g48,g49,g50,g51,g52,g53,g54,g55,g56,g57,g58,g59,g60,g61,g62,g63,g64,g65,g66,g67,g68,g69,g70,g71,g72,g73)


showrules = function(g){
    rules = g[[2]]
    pr = paste0("`",names(rules)," > ",rules,"`",collapse="\\\n")
    return(pr)
}

initial_angle = 90  
line_color = "black"
line_width = 1
bg_color = "white"

getstr = function(start,rules,n){
    st = start
    for(jj in 1:n){
        st2 = ""
        for(i in 1:nchar(st)){
            ch = substr(st,i,i)
            if(!is.null(rules[[ch]])){
                st2 = paste0(st2,rules[[ch]],collapse="")
            } else {
                st2 = paste0(st2,ch,collapse="")
            }
        }
        st = st2
    }
    return(st)
}
getxyc = function(string="AA+AA+AA+A+A",angle=pi/2,angle_initial=pi/2,col="blue"){
    switch = 1
    d = angle_initial
    x = 0
    y = 0
    xl = c(x)
    yl = c(y)
    cols = numeric()
    dsave = numeric()
    xsave = numeric()
    ysave = numeric()
    for(i in 1:nchar(string)){
        ch = substr(string,i,i)
        cn = as.integer(charToRaw(ch))
        if(cn>=as.integer(charToRaw("A")) && cn<=as.integer(charToRaw("L"))){
            cols = c(cols,col)
            x = x+cos(d)
            y = y+sin(d)
            xl = c(xl,x)
            yl = c(yl,y)
        }
        if(cn>=as.integer(charToRaw("M")) && cn<=as.integer(charToRaw("Z"))){
            cols = c(cols,"NA")
            x = x+cos(d)
            y = y+sin(d)
            xl = c(xl,x)
            yl = c(yl,y)
        }
        if(cn==as.integer(charToRaw("["))){
            dsave = c(dsave,d)
            xsave = c(xsave,x)
            ysave = c(ysave,y)
        }
        if(cn==as.integer(charToRaw("]"))){
            cols = c(cols,"NA")
            x = xsave[length(xsave)]
            y = ysave[length(ysave)]
            d = dsave[length(dsave)]
            if(length(xsave)>1){
                xsave = xsave[1:(length(xsave)-1)]
                ysave = ysave[1:(length(ysave)-1)]
                dsave = dsave[1:(length(dsave)-1)]
            } else {
                xsave = numeric()
                ysave = numeric()
                dsave = numeric()
            }
            xl = c(xl,x)
            yl = c(yl,y)
        }
        if(cn==as.integer(charToRaw("-"))){
            d = d+angle*switch
        }
        if(cn==as.integer(charToRaw("+"))){
            d = d-angle*switch
        }
        if(cn==as.integer(charToRaw("."))){
            switch = switch*(-1)
        }
    }
    xwid = max(xl)-min(xl)
    ywid = max(yl)-min(yl)
    xmid = (max(xl)+min(xl))/2
    ymid = (max(yl)+min(yl))/2
    wid = max(c(xwid,ywid))
    x2 = (xl-xmid)/wid*2
    y2 = (yl-ymid)/wid*2
    return(list(x2,y2,cols))
}
makeplot = function(xyc,lwd=1){
    x = xyc[[1]]
    y = xyc[[2]]
    c = xyc[[3]]
    plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
    for(i in 2:length(x)){
        lines(c(x[i-1],x[i]),c(y[i-1],y[i]),col=c[i-1],lwd=lwd)
    }
}

ng = length(goodies)
gs = sample(1:length(goodies),8)
gc = sample(gs,1)
sol = paste0(1*(gs==gc),collapse="")

```

Question
========

Consider the $L$-system (and angle) defined below:

* Start:
``r goodies[[gc]][[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(goodies[[gc]]))
```
\
* Number of recursions (number of iterations):
    * `r goodies[[gc]][[3]]`
* Angle
    * `r goodies[[gc]][[4]]`°

When we use the resulting string (and angle) to drive turtle graphics, using [https://draemm.li/various/fractals/l-systems/](https://draemm.li/various/fractals/l-systems/), what image is produced?

You can also use [this L-system string generator](https://chadworley.github.io/Lsys_string_gen.html) along with [Turbo Turtle](https://scratch.mit.edu/projects/1225522722/editor/) to generate the pattern.

(You will need to adjust other parameters to get image rotated, centered, and scaled.)

```{r,echo=F,fig.dim=c(4,8)}
par(mfrow=c(4,2),pty="s",mar=c(1,1.5,2,1.5))
jj = 0
for(i in gs){
    jj = jj+1
    s = getstr(goodies[[i]][[1]],goodies[[i]][[2]],goodies[[i]][[3]])
    angle = goodies[[i]][[4]]
    xyc = getxyc(s,angle/180*pi,angle_initial=initial_angle/180*pi,col=line_color)
    makeplot(xyc,lwd=0.7)
    mtext(LETTERS[jj],3)
}
```
\



Answerlist
--------

* A
* B
* C
* D
* E
* F
* G
* H



Solution
========

The correct pattern is pattern `r LETTERS[which(gs==gc)]`.

1. Use the link: [https://draemm.li/various/fractals/l-systems/](https://draemm.li/various/fractals/l-systems/)
2. Copy in the starting string, replacement rules, number of recursions, and angle.
3. Adjust the center and scale to clearly see the pattern. You might also need to rotate the pattern.
4. Select the correct pattern.


In case you're interested in the parameters of the other patterns shown:

## Pattern A

```{r,echo=F}
GG = goodies[[gs[1]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`

## Pattern B

```{r,echo=F}
GG = goodies[[gs[2]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`

## Pattern C

```{r,echo=F}
GG = goodies[[gs[3]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`
    
## Pattern D

```{r,echo=F}
GG = goodies[[gs[4]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`
    
## Pattern E

```{r,echo=F}
GG = goodies[[gs[5]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`

## Pattern F

```{r,echo=F}
GG = goodies[[gs[6]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`

## Pattern G

```{r,echo=F}
GG = goodies[[gs[7]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`
    
## Pattern H

```{r,echo=F}
GG = goodies[[gs[8]]]
```

* Start:
``r GG[[1]]``
* Rules:\
```{r,echo=F,results='asis'}
cat(showrules(GG))
```
\
* Number of recursions (number of iterations):
    * `r GG[[3]]`
* Angle
    * `r GG[[4]]`



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: lsys_pattern