```{r,echo=F}
while(T){
  x = round(runif(1,380,360*4)*sample(c(-1,1),1))
  t = x
  if(abs(x)%%360>10 && abs(x)%%360<350){break}
}
s = ""
if(t<0){
  while(t<0){
    t = t+360
    wrd1 = "less than 0"
    wrd2 = "add"
    s = paste0(s,"$$",t-360,"+360=",t,"$$\n")
  }
} else {
  while(t>360){
    t = t-360
    wrd1 = "more than 360"
    wrd2 = "subtract"
    s = paste0(s,"$$",t+360,"-360=",t,"$$\n")
  }
}
t= round(t)
shuch = list(c(0,x/180*pi),c(0,t/180*pi))
```

Question
========

Find an angle measure (in degrees) between 0$^\circ$ and 360$^\circ$ that is coterminal to an angle of `r x`$^\circ$.


Solution
========

The given angle, `r x`$^\circ$, is `r wrd1`$^\circ$, so `r wrd2` 360$^\circ$ until you get an angle between 0$^\circ$ and 360$^\circ$.

`r s`

Thus, the answer is `r t`$^\circ$. We can graph both angles: `r x`$^\circ$ and `r t`$^\circ$.

```{r,echo=F,fig.dim=c(4,8)}
par(mfrow = c(2, 1))
for(i in 1:length(shuch)){
  par(mar=c(1,1,1,1),pty="s")
  plot(0,0,type="n",ann=F,axes=F,xlim=c(-1,1),ylim=c(-1,1))
  abline(h=0)
  abline(v=0)
  a1 = shuch[[i]][1]
  a2 = shuch[[i]][2]
  lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
  lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
  len = 500
  th = seq(a1,a2,(a2-a1)/len)
  len = length(th)-1
  if(abs(a2-a1)>2*pi){
    r = seq(0.4,0.8,0.4/len)
  } else {
    r = 0.8
  }
  lines(r*cos(th),r*sin(th),lwd=2,col="red")
  arrows(0.8*cos(th[len]),0.8*sin(th[len]),0.8*cos(th[len+1]),0.8*sin(th[len+1]),lwd=2,col="red",length=0.1)
  for(theta in 1:360){
    thet = theta/180*pi
    if(theta%%10==0){
      lines(c(0.9*cos(thet),cos(thet)),c(0.9*sin(thet),sin(thet)),lwd=2)
    } else {
      lines(c(0.95*cos(thet),cos(thet)),c(0.95*sin(thet),sin(thet)))
    }
  }
}

```
\

Notice both terminal sides are in the same spot, even though the rotations to get there are different.


Meta-information
============
extype: num
exsolution: `r t`
exname: coterminal_angles