```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  den = sample(c(5,10,7,14,9,18,11,12,22,24),1)
  num = sample(1:den,1)
  div = gcd(den,num)
  num = round(num/div)
  den = round(den/div)
  radnum = num*2
  radden = den
  raddiv = gcd(radnum,radden)
  radnum = round(radnum/raddiv)
  radden = round(radden/raddiv)
  deg = den*360/num
  ang = radnum*pi/radden
  ref = ang%%(pi/2)
  ref = min(ref,pi/2-ref)
  if(radden>2 && radden<13 && radden!=4 && abs(pi/4-ref)>pi/17){break}
}

correct = c(0,ang)

ch1 = c(0,ref)
ch2 = c(0,pi/2-ref)
ch3 = c(0,pi/2+ref)
ch4 = c(0,pi-ref)
ch5 = c(0,pi+ref)
ch6 = c(0,3*pi/2-ref)
ch7 = c(0,3*pi/2+ref)
ch8 = c(0,2*pi-ref)

allchoices = list(ch1,ch2,ch3,ch4,ch5,ch6,ch7,ch8)
shuch = allchoices
sol = ""
for(i in 1:length(shuch)){
  if(shuch[[i]][1]==correct[1] && abs(shuch[[i]][2]-correct[2])<0.01){
    sol = paste0(sol,"1",collapse="")
    sollet = LETTERS[i]
  } else {
    sol = paste0(sol,"0",collapse="")
  }
}


rn = paste0(radnum)
if(radnum==1){rn=""}
offby = sample(c(-3,-2,-1,1,2,3),1)

rn3 = radnum+offby*2*radden
rn2 = radnum+offby*2*radden
if(rn2 == -1){rn2="-"} else {rn2=paste0(rn2)}

t = rn3
s = ""
if(t<0){
  while(t<0){
    t = t+2*radden
    wrd1 = "less than 0"
    wrd2 = "add"
    s = paste0(s,"$$\\frac{",t-2*radden,"\\pi}{",radden,
               "}+\\frac{",2*radden,"\\pi}{",radden,"}=\\frac{",t,"\\pi}{",radden,"}$$\n")
  }
} else {
  while(t>2*radden){
    t = t-2*radden
    wrd1 = "more than $2\\pi$"
    wrd2 = "subtract"
    s = paste0(s,"$$\\frac{",t+2*radden,"\\pi}{",radden,
               "}-\\frac{",2*radden,"\\pi}{",radden,"}=\\frac{",t,"\\pi}{",radden,"}$$\n")
  }
}

```

Question
========

An angle measure, $\theta$, equals $\frac{`r rn2`\pi}{`r radden`}$ radians. A second angle measure, $\phi$, is coterminal to $\theta$, and $0\le\phi<2\pi$. Which graph shows $\phi$ in standard position?

```{r,echo=F,fig.dim=c(6,12)}
par(mfrow = c(4, 2))
for(i in 1:length(shuch)){
  par(mar=c(0,3,3,3),pty="s")
  plot(0,0,type="n",axes=F,xlim=c(-1,1),ylim=c(-1,1),main=LETTERS[i])
  abline(h=0)
  abline(v=0)
  a1 = shuch[[i]][1]
  a2 = shuch[[i]][2]
  lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
  lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
  len = 100
  th = seq(a1,a2,length.out = len+1)
  r = 0.8 #seq(0.4,0.8,0.4/len)
  lines(r*cos(th),r*sin(th),lwd=2,col="red")
  arrows(0.8*cos(th[len]),0.8*sin(th[len]),0.8*cos(th[len+1]),0.8*sin(th[len+1]),lwd=2,col="red",length=0.1)
}

```
\

Answerlist
--------

* A
* B
* C
* D
* E
* F
* G
* H



Solution
========

The given angle measure is $\theta=\frac{`r rn2`\pi}{`r radden`}$ radians. Because the given angle is `r wrd1`, repeatedly `r wrd2` $2\pi$ until getting a coterminal angle between 0 and $2\pi$. It should be mentioned that $2\pi = \frac{`r 2*radden`\pi}{`r radden`}$, so we can add fractions with common denominators.

`r s`


We found the coterminal angle $\phi=\frac{`r rn`\pi}{`r radden`}$. I prefer to think of this as $`r radnum`$ times $\frac{\pi}{`r radden`}$, so then I imagine the top semicircle (and bottom semicircle) broken up into `r radden` equally-spaced wedges.


```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,3,3,3),pty="s")
plot(0,0,type="n",axes=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
abline(h=0,col=rgb(0,0,0,0.2))
abline(v=0,col=rgb(0,0,0,0.2))
a1 = correct[1]
a2 = correct[2]
lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
len = 100
mi = 0.4
ma = 0.8
th = seq(a1,a2,length.out = len+1)
r = 0.8 #seq(mi,ma,(ma-mi)/len)
lines(r*cos(th),r*sin(th),lwd=2,col="red")
arrows(0.8*cos(th[len]),0.8*sin(th[len]),0.8*cos(th[len+1]),0.8*sin(th[len+1]),lwd=2,col="red",length=0.2)

for(i in 1:(2*radden-1)){
  chi = i*pi/radden
  ni = i
  if(i==1){
    ni = ""
  }
  lines(c(1.1*cos(chi),0),c(1.1*sin(chi),0),col="purple",lwd=1,lty=2)
  text(1.25*cos(chi),1.25*sin(chi),TeX(paste0("$\\frac{",i,"\\pi}{",radden,"}$")))
}

```
\



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: plot_angle_standard_position