```{r,echo=F}
# 360 = 36*10 = 6*6*2*5 = 2^3*3^2*5
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  r = sample(3:9,1)
  den = sample(c(5,10,7,14,9,18,11,12,22,24),1)
  num = sample(1:den,1)
  div = gcd(den,num)
  num = round(num/div)
  den = round(den/div)
  radnum = num*2
  radden = den
  raddiv = gcd(radnum,radden)
  radnum = round(radnum/raddiv)
  radden = round(radden/raddiv)
  ang = radnum*pi/radden
  deg = ang/pi*180
  anum = radnum*r
  aden = radden
  div2 = gcd(anum,aden)
  anum = round(anum/div2)
  aden = round(aden/div2)
  shuch = list(c(0,deg/180*pi))
  if(radden>2 && radden<13 && radden!=4 && ang>pi/4){break}
}
if(radnum==1){
  rn = ""
} else {
  rn = paste0(radnum)
}
choices = 1:20
al = paste0("* ",choices,"\n",collapse="")

sol1 = paste0(1*(choices==radnum),collapse="")
sol2 = paste0(1*(choices==radden),collapse="")

```

Question
========

An arc is drawn along the circumference of a circle with a radius of `r r` meters. The arc's length is $\frac{`r anum`\pi}{`r aden`}$ radians. What is the arc's angle measure in radians?

```{r,echo=F,fig.dim=c(4,4)}
library(latex2exp)
par(pty="s")
for(i in 1:length(shuch)){
  par(mar=c(1,1,1,1),pty="s")
  plot(0,0,type="n",ann=F,axes=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
  for(j in 0:(r+4)){
    abline(h=j/r,col=rgb(0,0,0,0.2),lty=2)
    abline(h=-j/r,col=rgb(0,0,0,0.2),lty=2)
    abline(v=j/r,col=rgb(0,0,0,0.2),lty=2)
    abline(v=-j/r,col=rgb(0,0,0,0.2),lty=2)
  }
  th = seq(0,2*pi,pi/100)
  lines(cos(th),sin(th))
  a1 = shuch[[i]][1]
  a2 = shuch[[i]][2]
  lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=2)
  text(0.5,-0.07,paste0(r," m"),col="blue")
  lines(c(0,cos(a2)),c(0,sin(a2)))
  len = 100
  th = seq(a1,a2,(a2-a1)/len)
  len = length(th)-1
  lines(cos(th),sin(th),col="purple",lwd=2)
  ra = 1/r
  lines(cos(th)*ra,sin(th)*ra,col="red",lwd=2)
  arrows(ra*cos(th[len]),ra*sin(th[len]),
         ra*cos(th[len+1]),ra*sin(th[len+1]),length=0.05,
         col="red",lwd=2)
  text((ra+0.1)*cos(th[len%/%2]),(ra+0.1)*sin(th[len%/%2]),
       TeX("$x$"),col="red")
  text(1.2*cos(th[len%/%2]),1.2*sin(th[len%/%2]),
       TeX(paste0("\\frac{",anum,"\\pi}{",aden,"}")),col="purple")
}
```
\

The angle measure, $x$, can be expressed as $\frac{a\pi}{b}$, where $a$ and $b$ are both whole numbers with no shared factors other than 1. Find $a$ and $b$.

* $a=$ ##ANSWER1##
* $b=$ ##ANSWER2##

Answerlist
--------

`r al`
`r al`


Solution
========

Divide the arc length by the radius to get the angle measure (in radians).

$$x = \frac{\frac{`r anum`\pi}{`r aden`}}{`r r`}$$

$$x = \frac{`r anum`\pi}{`r aden`} \cdot \frac{1}{`r r`}$$

$$x = \frac{`r anum`\pi}{`r aden` \cdot `r r`}$$

$$x = \frac{`r rn`\pi}{`r radden`}$$



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: rads_from_arc_length