```{r data generation, echo = FALSE, results = "hide"}
# We ask: if A is function of B (50% chance yes)
#         if B is function of A (50% chance yes)
#         if relation is one-to-one (if prior both yes then yes)
# versions: 1=nono, 2=yesno, 3=noyes, 4=yesyes

shouldAafoB = sample(c(F,T),1)
shouldBafoA = sample(c(F,T),1)

while(T){
  n = sample(6:8,1)
  A = sample(0:9,n,T)
  B = sample(0:9,n,T)
  afa = character()
  afb = character()
  bfa = character()
  bfb = character()
  ifAafoB = T
  ifBafoA = T
  afbads = ""
  bfbads = ""
  for(i in 1:n){
    a = as.character(A[i])
    b = as.character(B[i])
    if(!(a %in% afa)){
      afa = c(afa,a)
      afb = c(afb,b)
    } else {
      pos = which(afa==a)
      if(afb[pos]!=b){
        ifBafoA = F
        afbads = paste0("(",c(a,a),", ",c(afb[pos],b),")",collapse=" and ")
      }
    }
    if(!(b %in% bfb)){
      bfb = c(bfb,b)
      bfa = c(bfa,a)
    } else {
      pos = which(bfb==b)
      if(bfa[pos]!=a){
        ifAafoB = F
        bfbads = paste0("(",c(bfa[pos],a),", ",c(b,b),")",collapse=" and ")
      }
    }
  }
  mystr = paste("(",A,", ",B,")\n\n",collapse="")
  if(ifAafoB==shouldAafoB && 
     ifBafoA==shouldBafoA && 
     length(unique(A)) >= length(A)-2 &&
     length(unique(A)) < length(A) && 
     length(unique(B)) >= length(B)-2 && 
     length(unique(B)) < length(B) ){
    break
  }
}

if(!ifBafoA && !ifAafoB){
  ans1 = "01"
  ans2 = "01"
  ans3 = "01"
  sol = paste0("An $x$ value has two different connections, so $y$ is not a function of $x$. For example: ",afbads,"\n\n Also, a $y$ value has two different connections, so $x$ is not a function of $y$. For example: ",bfbads,"\n\n We would need both to be function of the other to have a one-to-one function. Neither is, so we don't even have a function in either direction.")
}
if(ifBafoA && !ifAafoB){
  ans1 = "10"
  ans2 = "01"
  ans3 = "01"
  sol = paste0("Every $x$ value has only one connection, so $y$ is a function of $x$. \n\n A $y$ value has two connections, so $x$ is not a function of $y$. For example: ",bfbads," \n\n Because $x$ is not a function of $y$, these connections are inconsistent with a one-to-one function.")
}
if(!ifBafoA && ifAafoB){
  ans1 = "01"
  ans2 = "10"
  ans3 = "01"
  sol = paste0("An $x$ value has two connections, so $y$ is not a function of $x$. For example: ",afbads,"\n\n Every $y$ value has only one connection, so $x$ is a function of $y$. \n\n Because $y$ is not a function of $x$, these connections are inconsistent with a one-to-one function.")
}
if(ifBafoA && ifAafoB){
  ans1 = "10"
  ans2 = "10"
  ans3 = "10"
  sol = "Every $x$ value has only one connection, and vice versa. This means $y$ is a function of $x$ and $x$ is a function of $y$, and the connections are consistent with a one-to-one function."
}
```

Question
========

```{r,echo=FALSE,fig.dim=c(5,5)}
par(pty="s")
plot(0,0,type="n",axes = F,asp=1,xlim=c(0,10),ylim=c(0,10),ann=FALSE)
for(i in 0:9){
  text(0,i,i)
  text(10,i,i)
}
text(0,10,"x",cex=2)
text(10,10,"y",cex=2)
for(i in 1:n){
  lines(c(0.5,9.5),c(A[i],B[i]))
}
```
\

Are these connections consistent with $y$ being a function of $x$? ##ANSWER1##

Are these connections consistent with $x$ being a function of $y$? ##ANSWER2##

Are these connections consistent with a one-to-one function? ##ANSWER3##


Answerlist
--------

* Yes
* No
* Yes
* No
* Yes
* No


Solution
========

If any value of $x$ has two different connections, then $y$ is not a function of $x$. If any value of $y$ has two different connections, then $x$ is not a function of $y$.

`r sol`

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`
exname: are_connections_a_function