```{r data generation, echo = FALSE, results = "hide"}
x = 1:9

f = sample(1:9,9,T)
g = sample(1:9,9,T)
h = sample(1:9,9,T)

xa = sample(1:9,3)
fa = f[xa[1]]
gb = g[xa[2]]
hc = h[xa[3]]

ac = 1:9
al = paste0("* ",ac,collapse="\n")

sol1 = paste0(1*(fa==ac),collapse="")
sol2 = paste0(1*(gb==ac),collapse="")
sol3 = paste0(1*(hc==ac),collapse="")

```

Question
========

Consider the functions $f$, $g$, and $h$ shown below.

```{r,echo=F,warning=FALSE}
library(kableExtra)
data <- data.frame(
  x,
  f,
  g,
  h
)
colnames(data) = c("x","f(x)","g(x)","h(x)")
kable(data, "html") %>%
  kable_styling(bootstrap_options = "bordered",full_width=F)
```
\

Evaluate the function expressions below.

* $f(`r xa[1]`)~=$ ##ANSWER1##
* $g(`r xa[2]`)~=$ ##ANSWER2##
* $h(`r xa[3]`)~=$ ##ANSWER3##

Answerlist
--------

`r al`
`r al`
`r al`


Solution
========

To evaluate $f(`r xa[1]`)$, start in the FIRST COLUMN, and go down to the row where $x=`r xa[1]`$. Then, move to the SECOND COLUMN in the same row, to see that $f(`r xa[1]`)~=~`r fa`$.

To evaluate $g(`r xa[2]`)$, start in the FIRST COLUMN, and go down to the row where $x=`r xa[2]`$. Then, move to the THIRD COLUMN in the same row, to see that $g(`r xa[2]`)~=~`r gb`$.

To evaluate $h(`r xa[3]`)$, start in the FIRST COLUMN, and go down to the row where $x=`r xa[3]`$. Then, move to the FOURTH COLUMN in the same row, to see that $h(`r xa[3]`)~=~`r hc`$.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: eval_functions_tab