```{r,echo=FALSE}
options(scipen=999)

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

while(T){
    xy = sample(3:12,2)
    x = xy[1]*sample(c(-1,1),1)
    y = (xy[2]-0.5)*sample(c(-1,1),1)
    area = x^2+2*x*y
    x1 = sqrt(area+y^2)-y
    x2 = -sqrt(area+y^2)-y
    if(abs(x+y)>2 && abs(area)>0 && abs(x1)<=30 && abs(x2)<=30 && abs(x1)>0 && abs(x2)>0){break}
}

ach = -30:30
al = paste0("* ",ach,collapse="\n")

sol1 = ach==x1
sol2 = ach==x2

sol = sol1+sol2
sol = sol!=0
sol = paste0(1*sol,collapse="")

```

Question
========

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$

Answerlist
--------

`r al`


Solution
========

The given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$

In order to make the left side of the equation a [perfect square](https://www.khanacademy.org/math/math2/xe2ae2386aa2e13d6:quad-1/xe2ae2386aa2e13d6:perfect-sq/a/factoring-quadratics-perfect-squares), we can add $\left(\frac{`r 2*y`}{2}\right)^2=\frac{`r (2*y)^2`}{4}$ to both sides.

$$`r pn(c(1,2*y),2:1)`+\frac{`r (2*y)^2`}{4}~=~`r area`+\frac{`r (2*y)^2`}{4}$$

On the right side of the equation, we need common denominators.

$$`r pn(c(1,2*y),2:1)`+\frac{`r (2*y)^2`}{4}~=~\frac{`r 4*area`}{4}+\frac{`r (2*y)^2`}{4}$$


$$`r pn(c(1,2*y),2:1)`+\frac{`r (2*y)^2`}{4}~=~\frac{`r 4*area`+`r (2*y)^2`}{4}$$


$$`r pn(c(1,2*y),2:1)`+\frac{`r (2*y)^2`}{4}~=~\frac{`r 4*area+(2*y)^2`}{4}$$

Factor the left side of the equation.

```{r,echo=F}
if(y<0){
    eq1 = paste0("\\left(x-\\frac{",-y*2,"}{2}\\right)^2~=~\\frac{",4*area+(2*y)^2,"}{4}")
    eq2 = paste0("x-\\frac{",-y*2,"}{2}~=~\\pm\\frac{",sqrt(4*area+(2*y)^2),"}{2}")
    eq3 = paste0("x~=~\\frac{",-y*2,"}{2}\\pm\\frac{",sqrt(4*area+(2*y)^2),"}{2}")
    eq4 = paste0("x~=~\\frac{",-y*2,"\\pm ",sqrt(4*area+(2*y)^2),"}{2}")
} else {
    eq1 = paste0("\\left(x+\\frac{",y*2,"}{2}\\right)^2~=~\\frac{",4*area+(2*y)^2,"}{4}")
    eq2 = paste0("x+\\frac{",y*2,"}{2}~=~\\pm\\frac{",sqrt(4*area+(2*y)^2),"}{2}")
    eq3 = paste0("x~=~\\frac{",-y*2,"}{2}\\pm\\frac{",sqrt(4*area+(2*y)^2),"}{2}")
    eq4 = paste0("x~=~\\frac{",-y*2,"\\pm ",sqrt(4*area+(2*y)^2),"}{2}")

}
```

$$`r eq1`$$

Because the squaring function is not one-to-one, when we "undo" it in algebra, we need to consider the possibility of multiple solutions. In this case, squaring either $\frac{`r sqrt(4*area+(2*y)^2)`}{2}$ or $\frac{`r -sqrt(4*area+(2*y)^2)`}{2}$  produces $\frac{`r 4*area+(2*y)^2`}{4}$.

$$`r eq2`$$


$$`r eq3`$$


$$`r eq4`$$



$$x~=~`r x1`~~~~~~~~\text{or}~~~~~~~~x~=~`r x2`$$


Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: complete_the_square_E