```{r,echo=FALSE}

while(T){
    quotient = sample(3:9,1)
    divisor = sample(3:9,1)
    remainder = sample(1:(divisor-1),1)
    dividend = quotient*divisor+remainder
    nums = c(quotient,divisor,remainder,dividend)
    if(length(unique(nums))==4){break}
}


```

Question
========

Acquaint yourself with the terminology and process of [Euclidean division](https://en.wikipedia.org/wiki/Euclidean_division).

If the dividend is `r dividend` and the divisor is `r divisor`, then what is the **quotient**?


Solution
========

If `r dividend` beads are grouped into piles of `r divisor` beads, there will be `r quotient` complete piles and `r remainder` beads left over. In the terminology to Euclidean division:

* The dividend = `r dividend`
* The divisor = `r divisor`
* The quotient = `r quotient`
* The remainder = `r remainder`

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,1),ylim=c(0,1))

npiles = quotient
npc = floor(sqrt(npiles))
nbc = floor(sqrt(divisor))
wid = 1/(npc+2)/2


polygon(c(0,0,1,1),c(0,1,1,0))

x1s = numeric()
y1s = numeric()

for(i in 0:(npiles-1)){
    xmid = (i %% npc+1) / (npc+2) 
    ymid = (i %/% npc+0.5) / (npc+2)
    # points(xmid,ymid,pch=20)
    for(j in 0:(divisor-1)){
        xshi = (-0.5+(j %% nbc) / (nbc+2)) * wid
        yshi = (-0.5+(j %/% nbc) / (nbc+2)) * wid
        # points(xmid+xshi,ymid+yshi,pch=19)
        x1s = c(x1s,xmid+xshi)
        y1s = c(y1s,ymid+yshi)
    }
}

x2s = numeric()
y2s = numeric()

for(i in 1:remainder){
    xmid = 1-1/(npc+2)
    ymid = 0.5
    for(j in 0:(remainder-1)){
        xshi = (-0.5+(j %% nbc) / (nbc+2)) * wid
        yshi = (-0.5+(j %/% nbc) / (nbc+2)) * wid
        # points(xmid+xshi,ymid+yshi,pch=19,col="red")
        x2s = c(x2s,xmid+xshi)
        y2s = c(y2s,ymid+yshi)
    }
}

xmin = min(c(x1s,x2s))
xmax = max(c(x1s,x2s))
ymin = min(c(y1s,y2s))
ymax = max(c(y1s,y2s))

xwid = xmax-xmin
ywid = ymax-ymin
xmid = mean(c(xmax,xmin))
ymid = mean(c(ymax,ymin))

xa = (x1s-xmid)/xwid*0.8
ya = (y1s-ymid)/ywid*0.8
xb = (x2s-xmid)/xwid*0.8
yb = (y2s-ymid)/ywid*0.8

points(xa+0.5,ya+0.5,pch=19)
points(xb+0.5,yb+0.5,pch=19,col="red")

```
\

It might also help to express this with math notation:

$$\frac{`r dividend`}{`r divisor`}~=~`r quotient`+\frac{`r remainder`}{`r divisor`}$$


Meta-information
============
extype: num
exsolution: `r quotient`
exname: euclidean_division_quotient