```{r,echo=F,warning=F}
library(reticulate)
while(T){
  x = sample(-9:9,4)
  A = matrix(sample(1:6,16,T)*sample(c(-1,1),16,T),nrow=4)
  B = A%*%x
  if(max(abs(B))<100 && det(A)!=0){break}
}
fixexp = function(exp){ #This only works if 11x or 31x is not poss
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("-1w","-w",exp,fixed=T)
  exp = gsub("1w","w",exp,fixed=T)
  exp = gsub("-1x","-x",exp,fixed=T)
  exp = gsub("+1x","+x",exp,fixed=T)
  exp = gsub("-1y","-y",exp,fixed=T)
  exp = gsub("+1y","+y",exp,fixed=T)
  exp = gsub("-1z","-z",exp,fixed=T)
  exp = gsub("+1z","+z",exp,fixed=T)
  exp = gsub("-0w","",exp,fixed=T)
  exp = gsub("0w","",exp,fixed=T)
  exp = gsub("-0x","",exp,fixed=T)
  exp = gsub("+0x","",exp,fixed=T)
  exp = gsub("-0y","",exp,fixed=T)
  exp = gsub("+0y","",exp,fixed=T)
  exp = gsub("-0z","",exp,fixed=T)
  exp = gsub("+0z","",exp,fixed=T)
  return(exp)
}
eq1 = paste0(A[1,1],"w+",A[1,2],"x+",A[1,3],"y+",A[1,4],"z=",B[1])
eq2 = paste0(A[2,1],"w+",A[2,2],"x+",A[2,3],"y+",A[2,4],"z=",B[2])
eq3 = paste0(A[3,1],"w+",A[3,2],"x+",A[3,3],"y+",A[3,4],"z=",B[3])
eq4 = paste0(A[4,1],"w+",A[4,2],"x+",A[4,3],"y+",A[4,4],"z=",B[4])
eq1 = fixexp(eq1)
eq2 = fixexp(eq2)
eq3 = fixexp(eq3)
eq4 = fixexp(eq4)

ex1 = paste0(A[1,1],"w+",A[1,2],"x+",A[1,3],"y+",A[1,4],"z+",-B[1])
ex2 = paste0(A[2,1],"w+",A[2,2],"x+",A[2,3],"y+",A[2,4],"z+",-B[2])
ex3 = paste0(A[3,1],"w+",A[3,2],"x+",A[3,3],"y+",A[3,4],"z+",-B[3])
ex4 = paste0(A[4,1],"w+",A[4,2],"x+",A[4,3],"y+",A[4,4],"z+",-B[4])
ex1 = fixexp(ex1)
ex2 = fixexp(ex2)
ex3 = fixexp(ex3)
ex4 = fixexp(ex4)

ac = -9:9
sol1 = paste0(1*(ac==x[1]),collapse="")
sol2 = paste0(1*(ac==x[2]),collapse="")
sol3 = paste0(1*(ac==x[3]),collapse="")
sol4 = paste0(1*(ac==x[4]),collapse="")

al = paste0("* ",ac,collapse="\n")

```

Question
========

Solve the system of linear equations.

$$\begin{align}
`r gsub("=","&=",eq1)` \\
`r gsub("=","&=",eq2)` \\
`r gsub("=","&=",eq3)` \\
`r gsub("=","&=",eq4)` 
\end{align}$$

* $w=$ ##ANSWER1##
* $x=$ ##ANSWER2##
* $y=$ ##ANSWER3##
* $z=$ ##ANSWER4##

Answerlist
--------

`r al`
`r al`
`r al`
`r al`



Solution
========

Don't do this by hand. Let's use SageMath, which is based on Python.

You can run SageMath code [here](https://chadworley.github.io/sage.html) or [here](https://sagecell.sagemath.org/).


```{r,echo=F,results='asis'}
s = '```python\n'
s = paste0(s,'var("w x y z")  #these will be our algebraic variables\n')
s = paste0(s,"eq1 = ",A[1,1],"*w+",A[1,2],"*x+",A[1,3],"*y+",A[1,4],"*z==",B[1],"\n")
s = paste0(s,"eq2 = ",A[2,1],"*w+",A[2,2],"*x+",A[2,3],"*y+",A[2,4],"*z==",B[2],"\n")
s = paste0(s,"eq3 = ",A[3,1],"*w+",A[3,2],"*x+",A[3,3],"*y+",A[3,4],"*z==",B[3],"\n")
s = paste0(s,"eq4 = ",A[4,1],"*w+",A[4,2],"*x+",A[4,3],"*y+",A[4,4],"*z==",B[4],"\n")
s = paste0(s,"solve([eq1,eq2,eq3,eq4],[w,x,y,z])\n```")
s = gsub("+-","-",s,fixed=T)
cat(s)
```

Notice the equations (`eq1`, `eq2`, `eq3`, and `eq4`) are stored as expressions that equal 0. Every equation can be written with one side equal to 0. In programming, the `=` symbol is already used for [assignment](https://cs.stanford.edu/people/nick/py/python-var.html) and the `==` symbol is used to test for equivalence. In a Computer Algebra System (CAS), the default way to store an equation is as an expression that equals 0. Basically, you should start by rewriting the system:

$$\begin{align}
`r ex1`&=0 \\
`r ex2`&=0 \\
`r ex3`&=0 \\
`r ex4`&=0
\end{align}$$

Anyway, your Python code should tell you the answer:


$$w=`r x[1]`$$

$$x=`r x[2]`$$

$$y=`r x[3]`$$

$$z=`r x[4]`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: 4x4_lin_sys