```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  ABC = sample(2:9,3)*sample(c(-1,1),3,T)
  A = ABC[1]
  B = ABC[2]
  C = ABC[3]
  abc = sample(2:9,3)*sample(c(-1,1),3,T)
  a = abc[1]
  b = abc[2]
  c = abc[3]
  p = A+B+C
  q = A*b+A*c+B*a+B*c+C*a+C*b
  r = A*b*c+B*a*c+C*a*b
  nums = c(a+b,a+c,b+c,a*b,a*c,b*c)
  if(abs(p)>1 && abs(q)>1 && abs(r)>1 &&
     abs(p)<20 && abs(q)<20 && abs(r)<20 &&
     gcd(p,q,r)==1 && max(abs(nums))<20){break}
}

ac = -9:9
al = paste0("* ",ac,collapse="\n")
sol1 = paste0(1*(ac==A),collapse="")
sol2 = paste0(1*(ac==B),collapse="")
sol3 = paste0(1*(ac==C),collapse="")

numer = paste0(p,"x^2+",q,"x+",r,collapse="")
numer = gsub("+-","-",numer,fixed=T)
denom = paste0("(x+",c(a,b,c),")",collapse="")
denom = gsub("+-","-",denom,fixed=T)

numer2 = paste0(p,"*x^2+",q,"*x+",r,collapse="")
numer2 = gsub("+-","-",numer2,fixed=T)
denom2 = paste0("(x+",c(a,b,c),")",collapse="*")
denom2 = gsub("+-","-",denom2,fixed=T)

bot1 = paste0("x+",a,collapse="")
bot1 = gsub("+-","-",bot1,fixed=T)
bot2 = paste0("x+",b,collapse="")
bot2 = gsub("+-","-",bot2,fixed=T)
bot3 = paste0("x+",c,collapse="")
bot3 = gsub("+-","-",bot3,fixed=T)

fixit = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("-1A","-A",exp,fixed=T)
  exp = gsub("+1B","+B",exp,fixed=T)
  exp = gsub("-1B","-B",exp,fixed=T)
  exp = gsub("+1C","+C",exp,fixed=T)
  exp = gsub("-1C","-C",exp,fixed=T)
  exp = gsub("+1*","+",exp,fixed=T)
  exp = gsub("-1*","-",exp,fixed=T)
  return(exp)
}

exp1 = paste0("Ax^2+",b+c,"Ax+",b*c,"A+",
              "Bx^2+",a+c,"Bx+",a*c,"B+",
              "Cx^2+",a+b,"Cx+",a*b,"C",collapse="")
exp1 = fixit(exp1)

exp2 = paste0("(A+B+C)x^2+(",
              b+c,"A+",a+c,"B+",a+b,"C)x+(",
              b*c,"A+",a*c,"B+",a*b,"C)",
              collapse="")
exp2 = fixit(exp2)

peq = "A+B+C"
qeq = paste0(b+c,"A+",a+c,"B+",a+b,"C",collapse="")
qeq = fixit(qeq)
req = paste0(b*c,"A+",a*c,"B+",a*b,"C",collapse="")
req = fixit(req)

qeq2 = paste0(b+c,"*A+",a+c,"*B+",a+b,"*C",collapse="")
qeq2 = fixit(qeq2)
req2 = paste0(b*c,"*A+",a*c,"*B+",a*b,"*C",collapse="")
req2 = fixit(req2)

```

Question
========

In Calculus, when [integrating](https://en.wikipedia.org/wiki/Integral) [rational expressions](https://en.wikipedia.org/wiki/Algebraic_fraction#Rational_fractions), it is often helpful to perform [partial-fraction decomposition](https://openstax.org/books/precalculus-2e/pages/9-4-partial-fractions). 

The procedure can be exemplified by trying to determine constants $A$, $B$, and $C$ to satisfy the equation below **for all** values of $x$.

$$\frac{`r numer`}{`r denom`} = \frac{A}{`r bot1`}+\frac{B}{`r bot2`}+\frac{C}{`r bot3`}$$

* $A=$ ##ANSWER1##
* $B=$ ##ANSWER2##
* $C=$ ##ANSWER3##


Answerlist
--------

`r al`
`r al`
`r al`

Solution
========

We start with the given equivalence:
$$\frac{`r numer`}{`r denom`} = \frac{A}{`r bot1`}+\frac{B}{`r bot2`}+\frac{C}{`r bot3`}$$

Multiply both sides by $`r denom`$.

$$`r numer` ~~=~~ A(`r bot2`)(`r bot3`)+B(`r bot1`)(`r bot3`)+C(`r bot1`)(`r bot2`)$$

Expand (by [FOIL](https://en.wikipedia.org/wiki/FOIL_method) and [distributing](https://en.wikipedia.org/wiki/Distributive_property)).

$$`r numer` ~~=~~ `r exp1`$$

Gather similar terms (with same degree of $x$) to identify the coefficients.

$$(`r p`)x^2+(`r q`)x+(`r r`) ~~=~~ `r exp2`$$
Corresponding coefficients must be equal for the above equivalence to hold for all $x$.

$$\begin{align}
`r p`&=A+B+C\\
`r q`&=`r qeq`\\
`r r`&=`r req`
\end{align}$$

Solve the 3x3 system. You can use elimination, or you can use [SageMath](https://chadworley.github.io/sage.html).

```{r,echo=F,results='asis'}
s = '```python\n'
s = paste0(s,'var("A B C")\n')
s = paste0(s,"eq1 = ",p,"==A+B+C\n")
s = paste0(s,"eq2 = ",q,"==",qeq2,"\n")
s = paste0(s,"eq3 = ",r,"==",req2,"\n")
s = paste0(s,"solve([eq1,eq2,eq3],[A,B,C])\n```")
s = gsub("+-","-",s,fixed=T)
cat(s)
```

$$\begin{align}
A&=`r A`\\
B&=`r B`\\
C&=`r C`
\end{align}$$

And, really, [SageMath](https://chadworley.github.io/sage.html) can do the entire partial-fraction decomposition by using the  [`partial_fraction()`](https://doc.sagemath.org/html/en/reference/calculus/sage/symbolic/expression.html#sage.symbolic.expression.Expression.partial_fraction) method available to [expression](https://doc.sagemath.org/html/en/reference/calculus/sage/symbolic/expression.html#) objects.

```{r,echo=F,results='asis'}
s = '```python\n'
s = paste0(s,'var("x")\n')
s = paste0(s,"nmrtr = ",numer2,"\n")
s = paste0(s,"dnmntr = ",denom2,"\n")
s = paste0(s,"exp = nmrtr/dnmntr\n")
s = paste0(s,"exp.partial_fraction()\n```")
s = gsub("+-","-",s,fixed=T)
cat(s)
```


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: pfd_3_linear