```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

while(T){
  u1 = rnorm(3)
  u1[2] = abs(u1[2])
  u1 = u1/sqrt(sum(u1^2))
  u2 = rnorm(3)
  u2[2] = abs(u2[2])
  u2 = u2/sqrt(sum(u2^2))
  u3 = rnorm(3)
  u3[2] = abs(u3[2])
  u3 = u3/sqrt(sum(u3^2))
  u4 = rnorm(3)
  u4[2] = abs(u4[2])
  u4 = u4/sqrt(sum(u4^2))
  us = list(u1,u2,u3,u4)
  phi12 = acos(abs(sum(u1*u2)))
  phi13 = acos(abs(sum(u1*u3)))
  phi14 = acos(abs(sum(u1*u4)))
  phi23 = acos(abs(sum(u2*u3)))
  phi24 = acos(abs(sum(u2*u4)))
  phi34 = acos(abs(sum(u3*u4)))
  phis = c(phi12,phi13,phi14,phi23,phi24,phi34)
  if(min(phis)>pi/6){break}
}

getR = function(u,t){
  ux = u[1]
  uy = u[2]
  uz = u[3]
  f = cos(t)+ux^2*(1-cos(t))
  g = ux*uy*(1-cos(t))-uz*sin(t)
  h = ux*uz*(1-cos(t))+uy*sin(t)
  i = uy*ux*(1-cos(t))+uz*sin(t)
  j = cos(t)+uy^2*(1-cos(t))
  k = uy*uz*(1-cos(t))-ux*sin(t)
  l = uz*ux*(1-cos(t))-uy*sin(t)
  m = uz*uy*(1-cos(t))+ux*sin(t)
  n = cos(t)+uz^2*(1-cos(t))
  R = matrix(c(f,g,h,i,j,k,l,m,n),3,byrow=T)
  return(R)
}

n = 50
#X = matrix(round(runif(n*3,-1,1),2),nrow=3)

X = matrix(c(1,-1,-1,
      -1,-1,-1,
      -1,1,-1,
      1,1,-1,
      1,-1,-1,
      0,0,1,
      1,1,-1,
      -1,1,-1,
      0,0,1,
      -1,-1,-1),3)

ord = sample(1:4)
sol = paste0(1*(1==ord),collapse="")
P = matrix(c(1,0,0,0,0,1),2,byrow = T)
```

Question
========

Your goal is to make an animation (with 20 frames) of square pyramid spinning around a given axis. In 3D space, direction can be indicated with a unit vector $\vec{u}$:

$$\vec{u} = \begin{bmatrix}u_x \\ u_y \\ u_z \end{bmatrix}$$
A unit vector has a length of 1, so $u_x^2+u_y^2+u_z^2=1$.

In order to rotate points around the axis $\vec{u}$ by an angle $\theta$, we can use the [general 3D rotation matrix](https://en.wikipedia.org/wiki/Rotation_matrix#Rotation_matrix_from_axis_and_angle):

$$R = \begin{bmatrix} \cos(\theta)+u_x^2(1-\cos(\theta)) & u_xu_y(1-\cos(\theta))-u_z\sin(\theta) & u_xu_z(1-\cos(\theta))+u_y\sin(\theta) \\ u_yu_x(1-\cos(\theta))+u_z\sin(\theta) & \cos(\theta)+u_y^2(1-\cos(\theta)) & u_yu_z(1-\cos(\theta))-u_x\sin(\theta) \\ u_zu_x(1-\cos(\theta))-u_y\sin(\theta) & u_zu_y(1-\cos(\theta))+u_x\sin(\theta) & \cos(\theta)+u_z^2(1-\cos(\theta)) \end{bmatrix}$$
Because our animation has 20 frames, the angle should be $\theta=\frac{2\pi}{20}$.

We will use the basic [orthographic projection](https://en.wikipedia.org/wiki/Orthographic_projection#Geometry) matrix below to flatten 3D points into a 2D plane:

$$P = \begin{bmatrix}1 & 0 & 0 \\ 0 & 0 & 1\end{bmatrix}$$

The axis of rotation should be:

$$u_x=`r u1[1]`$$
$$u_y=`r u1[2]`$$
$$u_z=`r u1[3]`$$

Finish the code below to graph the animation.

```
n = 20 #The number of frames
X = matrix([[ 1,-1,-1, 1, 1, 0, 1,-1, 0,-1],
            [-1,-1, 1, 1,-1, 0, 1, 1, 0,-1],
            [-1,-1,-1,-1,-1, 1,-1,-1, 1,-1]])
P = matrix([[1,0,0],
            [0,0,1]])
R = ######### ENTER YOUR CODE HERE ##############
plots = []
for i in range(n):
    XP = P*R^i*X
    nextplot = line(XP.transpose(),xmin=-2,xmax=2,ymin=-2,ymax=2,axes=False,aspect_ratio=1)
    plots.append(nextplot)
a = animate(plots)
show(a)
```

## A

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(3,3)}
n = 20
par(pty="s",mar=c(0,0,0,0))
wo = ord[1]
u = us[[wo]]
t = 2*pi/n
R = getR(u,t)
Xc = X
for(i in 1:n){
  plot(0,0,type="n",axes=F,ann=F,xlim=c(-2,2),ylim=c(-2,2))
  Xc_flat = P%*%Xc
  lines(Xc_flat[1,],Xc_flat[2,])
  Xc = R%*%Xc
}
```
\

## B

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(3,3)}
n = 20
par(pty="s",mar=c(0,0,0,0))
wo = ord[2]
u = us[[wo]]
t = 2*pi/n
R = getR(u,t)
Xc = X
for(i in 1:n){
  plot(0,0,type="n",axes=F,ann=F,xlim=c(-2,2),ylim=c(-2,2))
  Xc_flat = P%*%Xc
  lines(Xc_flat[1,],Xc_flat[2,])
  Xc = R%*%Xc
}
```
\

## C

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(3,3)}
n = 20
par(pty="s",mar=c(0,0,0,0))
wo = ord[3]
u = us[[wo]]
t = 2*pi/n
R = getR(u,t)
Xc = X
for(i in 1:n){
  plot(0,0,type="n",axes=F,ann=F,xlim=c(-2,2),ylim=c(-2,2))
  Xc_flat = P%*%Xc
  lines(Xc_flat[1,],Xc_flat[2,])
  Xc = R%*%Xc
}
```
\

## D

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(3,3)}
n = 20
par(pty="s",mar=c(0,0,0,0))
wo = ord[4]
u = us[[wo]]
t = 2*pi/n
R = getR(u,t)
Xc = X
for(i in 1:n){
  plot(0,0,type="n",axes=F,ann=F,xlim=c(-2,2),ylim=c(-2,2))
  Xc_flat = P%*%Xc
  lines(Xc_flat[1,],Xc_flat[2,])
  Xc = R%*%Xc
}
```
\

Answerlist
--------

* A
* B
* C
* D



Solution
========

The answer is `r c("A","B","C","D")[ord==1]`.

[SageMath](https://sagecell.sagemath.org/)
```
n = 20 #The number of frames
X = matrix([[ 1,-1,-1, 1, 1, 0, 1,-1, 0,-1],
            [-1,-1, 1, 1,-1, 0, 1, 1, 0,-1],
            [-1,-1,-1,-1,-1, 1,-1,-1, 1,-1]])
P = matrix([[1,0,0],
            [0,0,1]])
R = matrix(`r matcc(getR(u1,2*pi/20))`)
plots = []
for i in range(n):
    XP = P*R^i*X
    nextplot = line(XP.transpose(),xmin=-2,xmax=2,ymin=-2,ymax=2,axes=False,aspect_ratio=1)
    plots.append(nextplot)
a = animate(plots)
show(a)
```

Instead of calculating each element of the rotation matrix (R), I would recommend putting in the formulas in terms of $u_x$, $u_y$, $u_z$, and $\theta$. You would need to define those variables before they were referenced:

```
ux = `r u1[1]`
uy = `r u1[2]`
uz = `r u1[3]`
th = 2*pi/20
```



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: spinning_pyramid