```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
while(T){
  xs = sample(c(-10:-1,1:10),3)
  ys = sample(c(-10:-1,1:10),2)
  x1 = sort(xs[1:2])[1]
  x2 = sort(xs[1:2])[2]
  y1 = ys[1]
  y2 = ys[2]
  x3 = xs[3]
  m = (y2-y1)/(x2-x1)
  b = y1-m*x1
  y3 = m*(x3-x1)+y1
  if(abs(y3)<20){break}
}
```


Question
========

A line goes through two points: (`r x1`, `r y1`) and (`r x2`, `r y2`).

On the same line, if $x=`r x3`$, then what is $y$? In other words, a third point on the line is (`r x3`, $y_3$), and your goal is to find $y_3$.

The tolerance is $\pm 0.01$.

Solution
========

Find the slope.

$$m = \frac{y_2-y_1}{x_2-x_1}$$
$$m = \frac{(`r y2`)-(`r y1`)}{(`r x2`)-(`r x1`)}$$

$$m=`r m`$$

Find the $y$-intercept of the line ($b$) by using slope-intercept form and the first point.

$$y = mx+b$$

$$`r y1` = (`r m`)(`r x1`)+b $$

$$`r y1` = `r m*x1`+b $$

Subtract `r m*x1` from both sides.

$$`r y1-m*x1` = b$$

So the $y$-intercept equals $b=`r b`$.

Now, plug in the third $x$ value.

$$y = mx+b$$

$$y_3 = (`r m`)(`r x3`)+(`r b`)$$

$$y_3 = `r y3`$$

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s")
xx = seq(-20,20,1)
yy = m*xx+b
plot(xx,yy,type="l",xlim=c(-20,20),ylim=c(-20,20),lwd=2,ylab="y",xlab="x")
abline(h=0,lwd=2)
abline(v=0,lwd=2)
points(c(x1,x2,x3),c(y1,y2,y3))
```
\


Meta-information
============
extype: num
exsolution: `r y3`
exname: find_third_point
extol: 0.01