```{r,echo=FALSE}
library(reticulate)
nxc = sample(3:6,1)
xc = sort(sample(-9:9,nxc))
#types: VA, zero, hole
while(T){
  xct = sample(1:3,nxc,TRUE)
  if(length(unique(xct))==3){break}
}
na = numeric()
da = numeric()
fs = sample(c(2,3,5,7,11),2)
nf = fs[1]*sample(c(-1,1),1)
df = fs[2]
sols = character()
vas = numeric()
zrs = numeric()
hls = numeric()
for(i in 1:nxc){
  if(xct[i]==1){
    da = c(da,xc[i])
    sols = c(sols,"100")
    vas = c(vas,xc[i])
  }
  if(xct[i]==2){
    na = c(na,xc[i])
    sols = c(sols,"010")
    zrs = c(zrs,xc[i])
  }
  if(xct[i]==3){
    da = c(da,xc[i])
    na = c(na,xc[i])
    sols = c(sols,"001")
    hls = c(hls,xc[i])
  }
}
if(length(na)>length(da)){
  sols = c(sols,"001")
  haex = "So, there is no HA."
}
if(length(na)<length(da)){
  sols = c(sols,"100")
  haex = "So, the HA is at $y=0$."
}
if(length(na)==length(da)){
  sols = c(sols,"010")
  haex = paste0("So, the HA is at $y=\\frac{",nf,"}{",df,"}$.",collapse="")
}

numstr = gsub("--","+",paste0("(x-",na,")",collapse="*"),fixed=TRUE)
denstr = gsub("--","+",paste0("(x-",da,")",collapse="*"),fixed=TRUE)
numstr = gsub("(x-0)","x",numstr,fixed=TRUE)
denstr = gsub("(x-0)","x",denstr,fixed=TRUE)

ansblock = paste0("* At $x=",xc,"$, there is a ##ANSWER",1:nxc,"##\n",collapse="")

anslis = c("vertical asymptote","zero","removable discontinuity")
anli = paste0("* ",anslis,"\n",collapse="")
fanli = paste0(rep(anli,nxc),collapse="")
sols = paste0(sols,collapse="|")
schoices = paste0(rep("schoice",nxc+1),collapse="|")
```


Question
========

```{python,echo=FALSE}
from sympy import *
x = symbols("x")
nstr = sympify(r.numstr)
dstr = sympify(r.denstr)
lnstr = latex(nstr)
ldstr = latex(dstr)
```



Consider the rational function $f$ defined below in factored form.

$$f(x) = \frac{`r nf` `r py$lnstr`}{`r df` `r py$ldstr`}$$

Identify the [vertical asymptotes](https://en.wikipedia.org/wiki/Asymptote#Vertical_asymptotes), [zeros](https://en.wikipedia.org/wiki/Zero_of_a_function), and [removable discontinuities](https://en.wikipedia.org/wiki/Classification_of_discontinuities#Removable_discontinuity) (holes).

`r ansblock`



* Also, is there a horizontal asymptote? `r paste0("##ANSWER",nxc+1,"##",collapse="")`



Answerlist
--------
`r fanli`
* Yes, at y=0
* Yes, at y=`r nf`/`r df`
* No. The end behavior heads toward infinity or negative infinity.

Solution
========

I've attempted to graph the rational function below, but I'd recommend investigating with a graphing calculator.

```{r,echo=FALSE,fig.dim=c(6,6)}
eval(parse(text=paste0("f = function(x){",numstr,"/(",denstr,")}",collapse="")))
x = seq(-10,10,0.0001)
plot(x,f(x),xlim=c(-10,10),ylim=c(-30,30),type="l",lwd=3)
points(zrs,f(zrs),pch=19)
for(i in -10:10){
  abline(v=i,lty=2)
}
abline(h=0)
abline(v=0)
points(hls,f(hls+0.00001),pch=19,cex=1.5)
points(hls,f(hls+0.00001),pch=19,cex=0.9,col="white")
abline(v=vas,lty=4,col="red",lwd=2)
```
\

Each factor exerts a strong influence when it's equal to 0.

* Vertical asymptotes correspond to factors in the denominator but not in the numerator. This is because $\lim\limits_{x\to0}\frac{1}{x}=\pm\infty$. There are vertical asymptotes at $x=\{`r vas`\}$.
* Zeros correspond to factors in the numerator but not the denominator. Zero times anything is zero, and zero divided by a nonzero number is zero. There are zeros at $x=\{`r zrs`\}$.
* Removable discontinuities correspond to a factor showing in the numerator and denominator. For any nonzero $b$, $\frac{b}{b}=1$. However, $\frac{0}{0}$ is undefined.  There are holes at $x=\{`r hls`\}$.

For the horizontal asymptote, you need to consider the degree of the numerator and the degree of the denominator. Since each factor is linear (with [multiplicity](https://en.wikipedia.org/wiki/Multiplicity_(mathematics)) of 1), the degree matches the number of factors.

* If the degree of the denominator is larger, then HA at $y=0$.
* If the degrees are equal, then HA at a nonzero value.
* If the degree of the numerator is larger, then no HA.

The degree of the numerator is `r length(na)`, and the degree of the denominator is `r length(da)`. `r haex`


Meta-information
============
extype: cloze
exclozetype: `r schoices`
exsolution: `r sols`
exname: VA_zero_hole_HA