```{r data generation, echo = FALSE, results = "hide"}
while(T){
    h = sample(-4:4,1)
    k = sample(1:8,1)
    if(h!=k){break}
}
isup = sample(c(T,F),1)
mult = -1+2*isup
k = k*(-mult)
dis = sample(2:5,1)
roots = c(h-dis,h+dis)
p = roots[1]
q = roots[2]
k2 = (h-p)*(h-q)
a = k/k2
adom = "(-∞,∞)"
if(isup){
  ainc = paste0("(",h,",∞)")
  adec = paste0("(-∞,",h,")")
  apos = paste0("(-∞,",p,")U(",q,",∞)")
  aneg = paste0("(",p,",",q,")")
  aran = paste0("[",k,",∞)")
} else {
  adec = paste0("(",h,",∞)")
  ainc = paste0("(-∞,",h,")")
  aneg = paste0("(-∞,",p,")U(",q,",∞)")
  apos = paste0("(",p,",",q,")")
  aran = paste0("(-∞,",k,"]")
}
fun = function(x){a*(x-p)*(x-q)}
achos = sample(c(ainc,adec,apos,aneg,adom,aran))
schos = paste0("* ",achos,"\n",collapse="")

ans1 = paste0(1*(achos==apos),collapse="")
ans2 = paste0(1*(achos==aneg),collapse="")
ans3 = paste0(1*(achos==ainc),collapse="")
ans4 = paste0(1*(achos==adec),collapse="")
ans5 = paste0(1*(achos==adom),collapse="")
ans6 = paste0(1*(achos==aran),collapse="")
```

Question
========

Consider the quadratic function graphed below:

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s",mar=c(5,5,0,0))
x = seq(-11,11,0.001)
plot(x,fun(x),type="n",xlim=c(-10,10),ylim=c(-10,10),lwd=2,ylab="y",xlab="x")
for(j in seq(-10,10,1)){
  abline(h=j,lwd=0.6,col="grey")
  abline(v=j,lwd=0.6,col="grey")
}
for(j in seq(-10,10,5)){
  abline(h=j,lwd=1.2,col="darkgrey")
  abline(v=j,lty=1.2,col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,fun(x),type="l",lwd=3,col="blue")
```
\



* What is the interval(s) over which the function is positive? ##ANSWER1##
* What is the interval(s) over which the function is negative? ##ANSWER2##
* What is the interval(s) over which the function is increasing? ##ANSWER3##
* What is the interval(s) over which the function is decreasing? ##ANSWER4##
* What is the domain (in interval notation)? ##ANSWER5##
* What is the range (in interval notation)? ##ANSWER6##


Answerlist
--------
`r schos`
`r schos`
`r schos`
`r schos`
`r schos`
`r schos`


Solution
========

* Positive: `r apos`
* Negative: `r aneg`
* Increasing: `r ainc`
* Decreasing: `r adec`
* Domain: `r adom`
* Range: `r aran`


* The function "is positive" when $f(x)>0$. The interval refers to the $x$ values (inputs) that produce a positive output. Determine where the curve is above the $x$ axis. Indicate "where" with the $x$ values at the endpoints: `r apos`
* The function "is negative" when $f(x)<0$. The interval refers to the $x$ values (inputs) that produce a negative output. Determine where the curve is below the $x$ axis. Indicate "where" with the $x$ values at the endpoints: `r aneg`
* The function is increasing when an ant going left-to-right is walking up hill: `r ainc`
* The function is decreasing when an ant going left-to-right is walking down hill: `r adec`



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`|`r ans5`|`r ans6`
exname: intervals_quadratic
exshuffle: false