```{r data generation, echo = FALSE, results = "hide"}
B = sample(2:3,1)
while(T){
    x1 = sort(sample(-3:3,4))
    x2 = x1*B
    y1 = sample(-10:10,4)
    y2 = y1
    if(min(x1)<0 && max(x1)>0 && min(y1)<0 && max(y1)>0){break}
}

ach = paste0("g(x)=",2:3,"\\cdot f(x)")
ach = c(ach,paste0("g(x)= \\frac{f(x)}{",2:3,"}"))
ach = c(ach,paste0("g(x)= f{\\left(",2:3,"\\cdot x\\right)}"))
ach = c(ach,paste0("g(x)= f{\\left(\\frac{x}{",2:3,"}\\right)}"))

ach = sample(ach)

al = paste0("* $",ach,"$",collapse="\n")

CA = paste0("g(x)= f{\\left(",B,"\\cdot x\\right)}")

sol = paste0(1*(ach==CA),collapse="")

```

Question
========

The blue curve represents $y=f(x)$. The red curve represents $y=g(x)$.

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 10
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
lines(x2,y2,col="blue",lwd=1.4)
points(x2,y2,col="blue",pch=19,cex=0.5)
lines(x1,y1,col="red",lwd=1.4)
points(x1,y1,col="red",pch=19,cex=0.5)


plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=f(x)$"),TeX("$y=g(x)$")),col=c("blue","red"),lwd=c(1.4,1.4))
```
\

What equation expresses the function transformation?

Answerlist
--------

`r al`


Solution
========

We see the points are transformed horizontally, so we are expecting the operation **inside the argument**. We also remember that horizontal transformations are "backwards".

In this case, we see from blue to red, the points have shrunk towards the vertical axis by a factor of `r B`. In other words, the coordinate transformation is:

$$(a,b)\to \left(\frac{a}{`r B`}~,~b\right)$$

Unfortunately, when we express the transformation as an equation in function notation, we see the inverse operation. So, instead of division, we see multiplication. So, the correct answer is:

$$`r CA`$$

For example, in the graph we see $g(`r x1[length(x1)]`) = f(`r x2[length(x1)]`) = `r y2[length(x1)]`$. We see this because the red curve has a point at $(`r x1[length(x1)]`,`r y2[length(x1)]`)$ and the blue curve has a corresponding point at $(`r x2[length(x1)]`,`r y2[length(x1)]`)$. It might help to visually check all the following:

$$g(`r x1[1]`) = f(`r x2[1]`)$$
$$g(`r x1[2]`) = f(`r x2[2]`)$$
$$g(`r x1[3]`) = f(`r x2[3]`)$$
$$g(`r x1[4]`) = f(`r x2[4]`)$$


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: hor_squeeze