---
output: slidy_presentation
---

# Factor when $a=$ prime

You are given a quadratic expression in standard form:

$$5x^2+17x+6$$

Factor the expression into factored form using the **BOX** method.


# Factor with box method

Given standard form, factor into factored form.

$$5x^2+17x+6$$

Use box to organize your guess-and-check. 

* Fill boxes you know for certain.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)

lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,"5x")
# text(5,7,-2)
text(1,5,"x")
# text(1,3,5)
text(1,7,"*")

text(3,5,TeX("$5x^2$"))
text(5,3,"6")

# text(5,5,"-12x",col="red")
# text(3,3,"35x",col="red")


# text(7.2,6,TeX("$42x^2-12x+35x-10$"),col="red")

# text(7.2,4.6,"Combine",col="red")
# text(7.2,4,"like",col="red")
# text(7.2,3.4,"terms.",col="red")

# text(7.2,2,TeX("$42x^2+23x-10$"),col="red")
```


# Factor with box method

Given standard form, factor into factored form.

$$5x^2+17x+6$$

Use box to organize your guess-and-check. 

* Guess $(5x+1)$ and $(x+6)$ because $1\cdot 6 = 6$.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)

lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,"5x")
text(5,7,"1",col="red")
text(1,5,"x")
text(1,3,"6",col="red")
text(1,7,"*")

text(3,5,TeX("$5x^2$"))
text(5,3,"6")

text(5,5,"x",col="red")
text(3,3,"30x",col="red")

text(7.2,6,TeX("$5x^2+x+30x+6$"),col="red")

text(7.2,4.6,"Combine",col="red")
text(7.2,4,"like",col="red")
text(7.2,3.4,"terms.",col="red")

text(7.2,2,TeX("$5x^2+31x+6$"),col="red")
```

The guess was NOT correct! Make a new guess.


# Factor with box method

Given standard form, factor into factored form.

$$5x^2+17x+6$$

Use box to organize your guess-and-check. 

* Guess $(5x+2)$ and $(x+3)$ because $2\cdot 3 = 6$.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)

lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,"5x")
text(5,7,"2",col="red")
text(1,5,"x")
text(1,3,"3",col="red")
text(1,7,"*")

text(3,5,TeX("$5x^2$"))
text(5,3,"6")

text(5,5,"2x",col="red")
text(3,3,"15x",col="red")

text(7.2,6,TeX("$5x^2+2x+15x+6$"),col="red")

text(7.2,4.6,"Combine",col="red")
text(7.2,4,"like",col="red")
text(7.2,3.4,"terms.",col="red")

text(7.2,2,TeX("$5x^2+17x+6$"),col="red")
```

The guess was correct! We have factored the expression.

$$(5x+2)(x+3)$$






