```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
l1 = 1:9 #possible values for a
a = sort(sample(l1,2,F))
s = a[1]+a[2]
p = a[1]*a[2]
ans1 = paste0((l1==a[1])*1,collapse="")
ans2 = paste0((l1==a[2])*1,collapse="")
```

Question
========


Find two integers whose sum is `r s` and whose product is `r p`.

What is the smaller found integer? ##ANSWER1##

What is the larger found integer? ##ANSWER2##

*Reminder, the smaller integer is further left on the number line. The choices should be listed smallest to largest.*

Answerlist
--------

```{r,echo=F,results="asis"}
cat(paste0("* ",l1,"\n",collapse=""))
cat(paste0("* ",l1,"\n",collapse=""))
```

Solution
========

By guess and check, we find the two integers are $`r a[1]`$ and $`r a[2]`$.

The sum:
$$(`r a[1]`)+(`r a[2]`) = `r s`$$

The product:
$$(`r a[1]`)(`r a[2]`) = `r p`$$

## Fancy method

Set up a system of equations:

$$x+y=`r s`$$
$$xy=`r p`$$

Solve the first equation for $y$, to get $y=`r s`-x$. Substitute this expression into second equation.
$$x(`r s`-x)=`r p` $$
Distribute
$$(`r s`)x-x^2=`r p`$$
Put this quadratic equation into standard form.
```{python,echo=F}
from sympy import *
x = symbols("x")
exp = x**2-r.s*x+r.p
lexp = latex(exp)
```
$$0 = `r py$lexp`$$

Remember the quadratic formula: if $ax^2+bx+c=0$, then $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$. In our case, $a=1$ and $b=`r -s`$ and $c=`r p`$.

$$x = \frac{`r s`\pm\sqrt{(`r -s`)^2-4(1)(`r p`)}}{2(1)} $$

Simplify.

$$x = \frac{`r s`\pm \sqrt{`r s^2-4*1*p`}}{2} = \frac{`r s` \pm `r sqrt(s^2-4*1*p)`}{2}$$

If you simply the fraction, you'll get `r a[1]` and `r a[2]`.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r ans1`|`r ans2`
exname: guess_pair_from_sum_and_product_MC