```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
while(T){
  ps = numeric()
  qs = numeric()
  mults = numeric()
  wrds = character()
  funs = list()
  ys = list()
  exps = character()
  x = seq(-10,10,0.1)
  for(i in 1:4){
    while(T){
      r = sample(-8:8,2)
      p = r[1]
      q = r[2]
      k1 = -((q-p)/2)^2
      t = sample(1:5,1)
      b = sample(1:100,1)
      a = t/b
      if(abs(k1*a)<10 && round(k1*a)==round(k1*a,8)){break}
    }
    mult = sample(c(-1,1),1)
    if(mult==-1){
      wrd = 'downward, and the expression has a negative multiplicative coefficient.'
    } else {
      wrd = 'upward, and the expression has a positive multiplicative coefficient.'
    }
    exp = paste0(mult*t,"/",b,"*(x-(",p,"))*(x-(",q,"))")
    y = mult*a*(x-p)*(x-q)
    ys = append(ys,list(y))
    exps = append(exps,exp)
    ps = c(ps,p)
    qs = c(qs,q)
    mults = c(mults,mult)
    wrds = c(wrds,wrd)
  }
  rexps = sample(exps)
  ans1 = paste0(1*(rexps[1]==exps),collapse="")
  ans2 = paste0(1*(rexps[2]==exps),collapse="")
  ans3 = paste0(1*(rexps[3]==exps),collapse="")
  ans4 = paste0(1*(rexps[4]==exps),collapse="")
  canbreak = TRUE
  for(i in 1:(length(ps)-1)){
    for(j in (i+1):length(ps)){
      pq1 = sort(c(ps[i],qs[i]))
      pq2 = sort(c(ps[j],qs[j]))
      if(sum(pq1==pq2)==2){canbreak==FALSE}
    }
  }
  if(canbreak){break}
}
```

Question
========

```{python,echo=FALSE}
from sympy import *
x = symbols("x")
rex1 = latex(factor(parse_expr(r.rexps[0])))
rex2 = latex(factor(parse_expr(r.rexps[1])))
rex3 = latex(factor(parse_expr(r.rexps[2])))
rex4 = latex(factor(parse_expr(r.rexps[3])))
aex1 = latex(factor(parse_expr(r.exps[0])))
aex2 = latex(factor(parse_expr(r.exps[1])))
aex3 = latex(factor(parse_expr(r.exps[2])))
aex4 = latex(factor(parse_expr(r.exps[3])))
pex = ["y="+str(factor(parse_expr(r.rexps[0]))).replace("*","\\*"),"y="+str(factor(parse_expr(r.rexps[1]))).replace("*","\\*"),"y="+str(factor(parse_expr(r.rexps[2]))).replace("*","\\*"),"y="+str(factor(parse_expr(r.rexps[3]))).replace("*","\\*")]
```

Match the following equations to their graphs.

a. $y=`r py$rex1`$
b. $y=`r py$rex2`$
c. $y=`r py$rex3`$
d. $y=`r py$rex4`$


```{r, echo=FALSE,fig.dim=c(5,5),results='asis'}
for(i in 1:length(ys)){
  cat(paste0(i,". \n\n"))
  y = unlist(ys[[i]])
  par(pty="s")
  plot(x,y,type="n",xlim=c(-10,10),ylim=c(-10,10))
  for(j in -10:10){
      abline(h=j,lty=3,lwd=0.5)
      abline(v=j,lty=3,lwd=0.5)
    }
  abline(h=0,lwd=2)
  abline(v=0,lwd=2)
  lines(x,y,type="l",xlim=c(-10,10),ylim=c(-10,10),lwd=3,col="blue")
  cat(paste0("\n##ANSWER",i,"##\n\n"))
}
anli = paste0("* ",py$pex,"\n",collapse="")
```


Answerlist
--------
`r anli`
`r anli`
`r anli`
`r anli`

Solution
========

1. The first graph has roots at `r ps[1]` and `r qs[1]`. Notice the equation $`r py$aex1`$ has factors that match those roots. Also, notice the parabola faces `r wrds[1]`
2. The second graph has roots at `r ps[2]` and `r qs[2]`. Notice the equation $`r py$aex2`$ has factors that match those roots. Also, notice the parabola faces `r wrds[2]`
3. The third graph has roots at `r ps[3]` and `r qs[3]`. Notice the equation $`r py$aex3`$ has factors that match those roots. Also, notice the parabola faces `r wrds[3]`
4. The fourth graph has roots at `r ps[4]` and `r qs[4]`. Notice the equation $`r py$aex4`$ has factors that match those roots. Also, notice the parabola faces `r wrds[4]`


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`
exname: factored_quad_graphs