```{r,echo=F}
abcd = sample(1:9,4,T)*sample(c(-1,1),4,T)

p1 = prod(abcd[1:2])
p2 = prod(abcd[3:4])

OI = p1+p2

s1 = paste0(p1)
s2 = paste0(p2)
if(p1<0){
    s1 = paste0("(",p1,")")
}
if(p2<0){
    s2 = paste0("(",p2,")")
}

nums = c(p1,p2,OI)

```




Question
========

Find the sum of the two integers.

$$`r s1`+`r s2`$$


Solution
========

I like to imagine 1-dimensional vectors on a [number line](https://en.wikipedia.org/wiki/Number_line#Comparing_numbers).

First, let's picture $`r s1`$ and $`r s2`$ as 1-dimensional vectors over a number line.

```{r,echo=F,fig.dim=c(6,2)}
xmin = floor(min(c(nums-10,-10))/10)*10
xmax = ceiling(max(c(nums+10,+10))/10)*10
par(mar=c(4,0,0,0))
plot(0,0,"n",xlim=c(xmin,xmax),ylim=c(0,1),axes=F,ann=F)
axis(1)
abline(v=0)
arrows(0,0.66,p1,0.66,0.1,15,2,col="red",lwd=2)
arrows(0,0.33,p2,0.33,0.1,15,2,col="blue",lwd=2)

```
\

Then, move the second vector so its tail sits at the head of the first vector. Our answer is represented by the purple vector, pointing from 0 to the sum of `r s1` plus `r s2`, which is `r OI`.

```{r,echo=F,fig.dim=c(6,2)}
xmin = floor(min(c(nums-10,-10))/10)*10
xmax = ceiling(max(c(nums+10,10))/10)*10
par(mar=c(4,0,0,0))
plot(0,0,"n",xlim=c(xmin,xmax),ylim=c(0,1),axes=F,ann=F)
axis(1)
abline(v=0)
lines(c(p1,p1),c(0.75,0.5),lty=3)
arrows(0,0.75,p1,0.75,0.1,15,2,col="red",lwd=2)
arrows(p1,0.50,p1+p2,0.50,0.1,15,2,col="blue",lwd=2)
arrows(0,0.25,p1+p2,0.25,0.1,15,2,col="purple",lwd=3)

```
\



```{r,echo=F}
lr1 = c("left","right")[round(sign(p1)/2+1.5)]
lr2 = c("left","right")[round(sign(p2)/2+1.5)]
lr3 = c("left","right")[round(sign(OI)/2+1.5)]
```

More simply, I think of negative addends as representing leftward movement and positive addends representing rightward movement.

* An addend of $`r s1`$ represents moving **`r lr1`** by `r abs(p1)`.
* An addend of $`r s2`$ represents moving **`r lr2`** by `r abs(p2)`.

When we combine those two movements, we get a net movement of **`r lr3`** by `r abs(OI)`. Thus our answer is $`r OI`$.



Meta-information
============
extype: num
exsolution: `r OI`
exname: sum_OI
