```{r data generation, echo = FALSE, results = "hide"}
# We ask: if A is function of B (50% chance yes)
#         if B is function of A (50% chance yes)
#         if relation is one-to-one (if prior both yes then yes)
# versions: 1=nono, 2=yesno, 3=noyes, 4=yesyes

shouldAafoB = sample(c(F,T),1)
shouldBafoA = sample(c(F,T),1)

while(T){
  n = sample(6:8,1)
  A = sample(0:10,n,T)
  B = sample(0:10,n,T)
  afa = character()
  afb = character()
  bfa = character()
  bfb = character()
  ifAafoB = T
  ifBafoA = T
  afbads = ""
  bfbads = ""
  for(i in 1:n){
    a = as.character(A[i])
    b = as.character(B[i])
    if(!(a %in% afa)){
      afa = c(afa,a)
      afb = c(afb,b)
    } else {
      pos = which(afa==a)
      if(afb[pos]!=b){
        ifBafoA = F
        afbads = paste0("(",c(a,a),", ",c(afb[pos],b),")",collapse=" and ")
      }
    }
    if(!(b %in% bfb)){
      bfb = c(bfb,b)
      bfa = c(bfa,a)
    } else {
      pos = which(bfb==b)
      if(bfa[pos]!=a){
        ifAafoB = F
        bfbads = paste0("(",c(bfa[pos],a),", ",c(b,b),")",collapse=" and ")
      }
    }
  }
  mystr = paste("(",A,", ",B,")\n\n",collapse="")
  if(ifAafoB==shouldAafoB && 
     ifBafoA==shouldBafoA && 
     length(unique(A)) >= length(A)-2 &&
     length(unique(A)) < length(A) && 
     length(unique(B)) >= length(B)-2 && 
     length(unique(B)) < length(B) ){
    break
  }
}

if(!ifBafoA && !ifAafoB){
  ans1 = "01"
  ans2 = "01"
  ans3 = "01"
  sol = paste0("An $x$ value repeats with different $y$ values, so $y$ is not a function of $x$. The graph fails the vertical line test. For example: ",afbads,"\n\n Also, a $y$ value repeates with different $x$ values, so $x$ is not a function of $y$. The graph fails the horizontal line test. For example: ",bfbads,"\n\n We would need both to be function of the other to have a one-to-one function. Neither is, so we don't even have a function in either direction.")
}
if(ifBafoA && !ifAafoB){
  ans1 = "10"
  ans2 = "01"
  ans3 = "01"
  sol = paste0("Every $x$ value has only one $y$ value, so $y$ is a function of $x$. The graph passes the vertical line test. \n\n A $y$ value repeates with different $x$ values, so $x$ is not a function of $y$. The graph fails the horizontal line test. For example: ",bfbads," \n\n Because $x$ is not a function of $y$, these points are inconsistent with a one-to-one function.")
}
if(!ifBafoA && ifAafoB){
  ans1 = "01"
  ans2 = "10"
  ans3 = "01"
  sol = paste0("An $x$ value repeats with different $y$ values, so $y$ is not a function of $x$. The graph fails the vertical-line test. For example: ",afbads,"\n\n Every $y$ value has only one $x$ value, so $x$ is a function of $y$. The graph passes the horizontal line test. \n\n Because $y$ is not a function of $x$, these points are inconsistent with a one-to-one function.")
}
if(ifBafoA && ifAafoB){
  ans1 = "10"
  ans2 = "10"
  ans3 = "10"
  sol = "Every $x$ value has only one $y$ value, and vice versa. The graph passes both the vertical-line and horizontal-line tests. This means $y$ is a function of $x$ and $x$ is a function of $y$, and the points are consistent with a one-to-one function."
}
```

Question
========

```{r,echo=FALSE,fig.dim=c(5,5)}
par(pty="s")
plot(A,B,xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="y",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
```
\

Are these points consistent with $y$ being a function of $x$? ##ANSWER1##

Are these points consistent with $x$ being a function of $y$? ##ANSWER2##

Are these points consistent with a one-to-one function? ##ANSWER3##


Answerlist
--------

* Yes
* No
* Yes
* No
* Yes
* No


Solution
========

It is best to visualize the vertical line test and the horizontal line test. If you can draw a vertical line through 2 (or more) points, then $y$ is not a function of $x$. If you can draw a horizontal line through 2 (or more) points, then $x$ is not a function of $y$.

`r sol`

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`
exname: are_points_a_function