# Problem statement

Each day a student is given 3 multiple-choice questions with 4 possible choices but only 1 correct choice. Students are given 3 attempts; after each attempt they are told how many questions they got right, but not which questions were correct.

On each attempt, the questions and choices remain constant, and students remember their past guesses and results.

Also, in this class, only the highest score (of the 3 attempts) counts. So, we are not "simply" maximizing the expected points of the third attempt. I'm not sure if this matters yet, but I think it will.

If we assume the students do not read the questions, but use an optimal strategy, then what is the expected number of correct questions?


# Possible strategies

We can always start by guessing AAA.

* AAA
    * AAB
        * ABA BBA ABB BBB AAC ABC BBC
    * ABB
        * AAB ABC ACC AAC BAA BAB BAC BBB BBC BCC
    * BBB
        * ABB AAB BBC BCC CCC AAC ACC ABC


# Summary of optimal stategy

* AAA
    * 1/64 chance of 3: aaa
        * done with 3 points
    * 9/64 chance of 2: aab aba baa aac aca caa aad ada daa
        * Guess AAB for EV = 7/3
            * 1/9 chance of 2,3 done with 3 points
            * 2/9 chance of 2,2 $\to$ guess AAC to get EV=(3+2)/2=5/2
            * 6/9 chance of 2,1 $\to$ guess ABA to get EV=(1+6*2)/6=13/6
    * 27/64 chance of 1: abb abc abd acb acc acd adb adc add bab bac bad bba bca bda cab cac cad cba cca cda dab dac dad dba dca dda
        * Guess AAB for EV=49/27
            * 6/27 chance of 1,2 $\to$ guess ABB for EV=13/6
            * 12/27 chance of 1,1 $\to$ guess AAC for EV=18/12
            * 9/27 chance of 1,0 $\to$ guess BBA for EV=15/9
    * 27/63 chance of 0: bbb ccc ccd cdc cdd dcc dcd ddc ddd bcc bcd bdc bdd cbc cbd ccb cdb dbc dbd dcb ddb bbc bbd bcd bdb cbb dbb
        * Guess BBB for EV=44/27
            * 1/27 chance of 0,3 $\to$ done with 3
            * 6/27 chance of 0,2 $\to$ guess BBC for EV=13/6
            * 12/27 chance of 0,1 $\to$ guess BBC for EV=16/12
            * 8/27 chance of 0,0 $\to$ guess CCC for EV=12/8


```{r,echo=F}
cnt = function(str1,str2){
    pp1 = strsplit(str1,"")
    pp2 = strsplit(str2,"")
    return(sum(pp1[[1]]==pp2[[1]]))
}


s1 <- list('AAA',
            list("BBB",list("CCC"),list("BBC"),list("BBC")),
            list("AAB",list("BBA"),list("ABC"),list("ABB")),
            list("AAB",list("CCC"),list("ABA"),list("AAC"))
            )

# st0 = c("g"="AAA",
#        "g0"="BBB","g00"="CCC","g01"="BBC","g02"="BBC",
#        "g1"="AAB","g10"="BBA","g11"="ABC","g12"="ABB",
#        "g2"="AAB","g20"="CCC","g21"="ABA","g22"="AAC")

st0 = c("g"="AAA",
       "g0"="BBB","g00"="CCC","g01"="BBC","g02"="BBC",
       "g1"="AAB","g10"="BBA","g11"="AAC","g12"="ABB",
       "g2"="AAB","g20"="CCC","g21"="ABA","g22"="AAC")

gposs = c("AAA")
gxposs = c("AAB","ABB","BBB")
gyposs = unique(c("ABA","BBA","ABB","BBB","AAC","ABC","BBC",
                  "AAB","ABC","ACC","BAA","BAB","BAC","BBB",
                  "BBC","BCC","ABB","AAB","BBC","BCC","CCC","AAC","ACC","ABC"))

sols = character()
for(i in LETTERS[1:4]){
    for(j in LETTERS[1:4]){
        for(k in LETTERS[1:4]){
            sols = c(sols,paste0(i,j,k,collapse=""))
        }
    }
}

st=st0
```



```{r,echo=F}
runstrat = function(st){
    pnts = numeric()
    for(sol in sols){
        gx = st[[1]]
        cx = cnt(sol,gx)
        if(cx==3){
            cy=3
            cz=3
        } else if(cx==2){
            gy = st[["g2"]]
            cy = cnt(sol,gy)
            if(cy==3){
                cz=3
            } else if(cy==2){
                gz = st[["g22"]]
                cz = cnt(sol,gz)
            } else if(cy==1){
                gz = st[["g21"]]
                cz = cnt(sol,gz)
            } else if(cy==0){
                gz = st[["g20"]]
                cz = cnt(sol,gz)
            }
        } else if(cx==1){
            gy = st[["g1"]]
            cy = cnt(sol,gy)
            if(cy==3){
                cz=3
            } else if(cy==2){
                gz = st[["g12"]]
                cz = cnt(sol,gz)
            } else if(cy==1){
                gz = st[["g11"]]
                cz = cnt(sol,gz)
            } else if(cy==0){
                gz = st[["g10"]]
                cz = cnt(sol,gz)
            }
        } else if(cx==0){
            gy = st[["g0"]]
            cy = cnt(sol,gy)
            if(cy==3){
                cz=3
            } else if(cy==2){
                gz = st[["g02"]]
                cz = cnt(sol,gz)
            } else if(cy==1){
                gz = st[["g01"]]
                cz = cnt(sol,gz)
            } else if(cy==0){
                gz = st[["g00"]]
                cz = cnt(sol,gz)
            }
        }
        pnts = c(pnts,max(c(cx,cy,cz)))
    }
    return(pnts)
}

bestmean = 0
# for(i in 1:10^5){
#     st = st0
#     nspots = sample(0:(length(st)-1),1)
#     spots = sample(2:length(st),nspots)
#     # for(spot in spots){
#     #     if(nchar(names(st[spot]))==2){
#     #         st[spot] = sample(gxposs,1)
#     #     } else {
#     #         st[spot] = sample(gyposs,1)
#     #     }
#     # }
#     for(spot in spots){
#         st[spot] = paste0(LETTERS[sample(1:3,3,T)],collapse="")
#     }
#     pnts = runstrat(st)
#     mpnts = mean(pnts)
#     if(mpnts>bestmean){
#         print(st)
#         print(mpnts)
#         bestmean=mpnts
#     }
# }

```









```{r,echo=F}
library(data.tree)
g = Node$new("initial")
g$guess = strsplit("AAA","")
g0 = g$AddChild("X=0")
g0$guess = strsplit("BBB","")
g00 = g0$AddChild("Y=0")
g00$guess =  strsplit("CCC","")
g01 = g0$AddChild("Y=1")
g01$guess = strsplit("BBC","")
g02 = g0$AddChild("Y=2")
g02$guess = strsplit("BBC","")
g1 = g$AddChild("X=1")
g1$guess = strsplit("AAB","")
g10 = g1$AddChild("Y=0")
g10$guess =  strsplit("BBA","")
g11 = g1$AddChild("Y=1")
g11$guess = strsplit("ABC","")
g12 = g1$AddChild("Y=2")
g12$guess = strsplit("ABB","")
g2 = g$AddChild("X=2")
g2$guess = strsplit("AAB","")
g20 = g2$AddChild("Y=0")
g20$guess =  strsplit("CCC","") #Shouldn't happen
g21 = g2$AddChild("Y=1")
g21$guess = strsplit("ABA","")
g22 = g2$AddChild("Y=2")
g22$guess = strsplit("AAC","")

```
            
```{r}

tots = numeric()
g = c("A","A","A")
g2 = c("A","A","B")
g22 = c("A","A","C")
g21 = c("A","B","A")
g20 = c("X","X","X") #Shouldn't happen
g1 = c("A","A","B") 
g12 = c("A","B","B")
g11 = c("A","B","C")
g10 = c("B","B","A")
g0 = c("B","B","B")
g02 = c("B","B","C")
g01 = c("B","B","C")
g00 = c("C","C","C")



for(i in 1:10^3){
    sol = LETTERS[sample(1:4,3,T)]
    g1 = c("A","A","A")
    m1 = sum(sol==g1)
    if(m1==3){
        m2=3
        m3=3
    } else if(m1==2){
        g2 = c("A","A","B")
        m2 = sum(sol==g2)
        if(m2==3){
            m3 = 3
        } else if(m2==2){
            g3 = c("A","A","C")
            m3 = sum(sol==g3)
        } else if(m2==1){
            g3 = c("A","B","A")
            m3 = sum(sol==g3)
        } else if(m2==0){
            print("I don't think you should end up here!")
        }
    } else if(m1==1){
        g2 = c("A","A","B")
        m2 = sum(sol==g2)
        if(m2==3){
            m3 = 3
        } else if(m2==2){
            g3 = c("A","B","B")
            m3 = sum(sol==g3)
        } else if(m2==1){
            g3 = c("A","B","C")
            m3 = sum(sol==g3)
        } else if(m2==0){
            g3 = c("B","B","A")
            m3 = sum(sol==g3)
        }
    } else if(m1==0){
        g2 = c("B","B","B")
        m2 = sum(sol==g2)
        if(m2==3){
            m3 = 3
        } else if(m2==2){
            g3 = c("B","B","C")
            m3 = sum(sol==g3)
        } else if(m2==1){
            g3 = c("B","B","C")
            m3 = sum(sol==g3)
        } else if(m2==0){
            g3 = c("C","C","C")
            m3 = sum(sol==g3)
        }
    }
    tot = max(c(m1,m2,m3))
    tots = c(tots,tot)
}
table(tots)
```



