---
output: pdf_document
params:
    rseed: 1
    showsol: false
    titex: ""
urlcolor: blue
---

```{r,echo=F}
set.seed(params$rseed)
sols = numeric()
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
pfull = function(c,d){
    p = paste0("(",c,")x^{",d,"}",collapse="+")
    return(p)
}
if(params$showsol){
    solstart = ""
    solend = "\\vfill"
} else {
    solstart = "<!---"
    solend = "-->"
}

```

Name: \hspace{4in} Date: \hfill \hrule

# Polynomial Operations `r params$titex` (version `r params$rseed`)

```{r,echo=F}
missings = sample(2:5,2)
cfp = sample(1:10,6)*sample(c(-1,1),6,T)
cfq = sample(1:10,6)*sample(c(-1,1),6,T)
cfp[missings[1]] = 0
cfq[missings[2]] = 0
p = pfix(cfp,5:0)
q = pfix(cfq,5:0)
pf = pfull(cfp,5:0)
qf = pfull(cfq,5:0)
asb = sample(1:3,1)
if(asb==1){
    wrd = "Express the sum of $p(x)+ q(x)$ in standard form."
    wrd2 = "p(x)+q(x)"
    cfr = cfp+cfq
} else if(asb==2){
    wrd = paste0("Express the difference $p(x)-q(x)$ in standard form.")
    wrd2 = "p(x)-q(x)"
    cfr = cfp-cfq
} else if(asb==3){
    wrd = paste0("Express the difference $q(x)-p(x)$ in standard form.")
    wrd2 = "q(x)-p(x)"
    cfr = cfq-cfp
}
rf = pfull(cfr,5:0)
r = pfix(cfr,5:0)
```

**1. Let polynomials $p(x)$ and $q(x)$ be defined below.
$$p(x)~=~`r p`$$
$$q(x)~=~`r q`$$
`r wrd`**

\vfill

`r solstart`
Get "unsimplified" forms. Then find $`r wrd2`$ with addition/subtraction.
$$
\begin{aligned}
p(x) &= `r pf`\\
q(x) &= `r qf`\\
`r wrd2` &= `r rf` \\
`r wrd2` &= `r r` 
\end{aligned}
$$
`r solend`



```{r,echo=F}
while(T){
    cfa = sample(2:9,3)*sample(c(-1,1),3,T)
    cfb = sample(2:9,2)*sample(c(-1,1),2,T)
    A = cfa[1]
    B = cfa[2]
    C = cfa[3]
    m = cfb[1]
    i = cfb[2]
    cfcraw = c(A*m,B*m,A*i,C*m,B*i,C*i)
    cfc = c(A*m,B*m+A*i,C*m+B*i,C*i)
    pa = pfix(cfa,2:0)
    pb = pfix(cfb,1:0)
    pc = pfix(cfc,3:0)
    pcraw = pfix(cfcraw,c(3,2,2,1,1,0))
    if(max(abs(c(cfc,B*m,A*i,C*m,B*i)))<70){break}
}


```

**2. Let polynomials $a(x)$ and $b(x)$ be defined below.
$$a(x)~=~`r pa`$$
$$b(x)~=~`r pb`$$
Express the product $a(x)\cdot b(x)$ in standard form.**

\vfill

`r solstart`
You can use a table for multiplication.
\begin{center}
\begin{tabular}{|c| c c c |} \hline
*        & $`r A`x^2$   &  $`r B`x$    & $`r C`$    \\ \hline
$`r m`x$ & $`r A*m`x^3$ & $`r B*m`x^2$ & $`r m*C`x$ \\
$`r i`$  & $`r A*i`x^2$ & $`r B*i`x$ & $`r i*C`$ \\ \hline
\end{tabular}
\end{center}
$$a(x)\cdot b(x) ~=~ `r pcraw`$$
Combine like terms.
$$a(x)\cdot b(x) ~=~ `r pc`$$
`r solend`

```{r,echo=F}
n = sample(4:6,1)
ccc = choose(n,0:n)
ddd = n:0
pbt = pfix(ccc,ddd)
```

**3. Express $(x+1)^{`r n`}$ in standard (expanded) form.**

\vfill

`r solstart`
Remember [the binomial theorem](https://en.wikipedia.org/wiki/Binomial_theorem). It tells us to use Pascal's triangle.
$$`r pbt`$$
`r solend`

\newpage

# Polynomial Operations `r params$titex` (version `r params$rseed`)

```{r,echo=F}
cg = c(1,sample(4:9,1)*sample(c(-1,1),1))
while(T){
    cz = sample(-9:9,3)*sample(c(-1,1),3,T)
    cf = c(cg[1]*cz[1],cg[1]*cz[2]+cg[2]*cz[1],cg[1]*cz[3]+cg[2]*cz[2],cg[2]*cz[3]+sample(1:10,1)*sample(c(-1,1),1))
    pf = pfix(cf,3:0)
    pg = pfix(cg,1:0)
    aa = -cg[2]
    b1 = cf[1]
    m2 = b1*aa
    b2 = cf[2]+m2
    m3 = b2*aa
    b3 = cf[3]+m3
    m4 = b3*aa
    b4 = cf[4]+m4
    ch = c(b1,b2,b3)
    ph = pfix(ch,2:0)
    R = b4
    if(cf[1]!=0 && max(abs(cf))<30 && abs(aa)!=abs(R)){break}
}
```

**4. Let polynomials $f(x)$ and $g(x)$ be defined below.
$$
\begin{aligned}
f(x)~&=~`r pf`\\
g(x) ~&=~ `r pg`
\end{aligned}
$$
The quotient of $\frac{f(x)}{g(x)}$ can be expressed as a polynomial, $h(x)$, and a remainder, $R$ (a real number).
$$\frac{f(x)}{g(x)}~~=~~ h(x) + \frac{R}{`r pg`}$$
By using synthetic division or long division, express $h(x)$ in standard form, and find the remainder $R$.**

\vfill

`r solstart`
I prefer using synthetic division.
\begin{center}
\begin{tabular}{c|c c c c}
       & `r cf[1]` & `r cf[2]` & `r cf[3]` & `r cf[4]` \\
`r aa` &           & `r m2`    & `r m3`    & `r m4` \\ \hline
       &  `r b1`   & `r b2`    & `r b3`    & `r b4`  
\end{tabular}
\end{center}
So,
$$\frac{f(x)}{g(x)} ~=~ `r ph`+\frac{`r R`}{`r pg`}$$
In other words, $h(x)=`r ph`$ and the remainder is $R=`r R`$.
`r solend`




**5. Let polynomial $f(x)$ still be defined as $f(x)=`r pf`$. Evaluate $f(`r aa`)$.**

\vfill

`r solstart`
You could do this the hard way.
$$
\begin{aligned}
f(`r aa`) ~~&=~~ (`r cf[1]`)\cdot(`r aa`)^3 ~+~ (`r cf[2]`)\cdot(`r aa`)^2 ~+~ (`r cf[3]`)\cdot(`r aa`)~+~(`r cf[4]`) \\
&=~~ (`r cf[1]`)\cdot(`r aa^3`) ~+~ (`r cf[2]`)\cdot(`r aa^2`) ~+~ (`r cf[3]`)\cdot(`r aa`)~+~(`r cf[4]`) \\
&=~~ (`r cf[1]*aa^3`) ~+~ (`r cf[2]*aa^2`) ~+~ (`r cf[3]*aa`)~+~(`r cf[4]`) \\
&=~~ `r cf[1]*aa^3+cf[2]*aa^2+cf[3]*aa+cf[4]`
\end{aligned}
$$
Or, if you reference the [polynomial remainder theorem](https://en.wikipedia.org/wiki/Polynomial_remainder_theorem), you can state that you know $f(`r aa`)$ equals the remainder when $f(x)$ is divided by $`r pg`$. Thus, $f(`r aa`)=`r R`$.
`r solend`
