---
output: pdf_document
params:
    rseed: 1
    showsol: true
    titex: "Practice"
urlcolor: blue
---

```{r,echo=F}
set.seed(params$rseed)
sols = numeric()
if(params$showsol){
    solstart = "### Solution"
    solend = "\\vfill"
    hidesolstart = "<!---"
    hidesolend = "-->"
} else {
    solstart = "<!---"
    solend = "-->"
    hidesolstart = ""
    hidesolend = ""
}
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
```

Name: \hspace{4in} Date: \hfill \hrule

## Polynomial Factoring `r params$titex` (version `r params$rseed`)

```{r,echo=F}
pfsq = (1:20)^2
bbb = c(2,3,5,6,7,8,9)
while(T){
    R1 = sample(c(-6:-1,1:6),1)
    R2infr = sample(1:3,1,F,c(1,3,5))
    R2inrad = sample(c(2,3,5,6,7,10,11,13,14,15),1)
    R2sq = R2inrad*R2infr^2 #sample(2:25,1) # 2*3^2*5^3 #sample(6:99,1)
    R2 = sqrt(R2sq)
    a = 1
    b = -2*R1
    c = R1^2+R2sq
    radi = b^2-4*a*c
    if(abs(c)<100 && abs(radi)<=150){break}
}
ex = pfix(c(a,b,c),2:0)

```



1. **The quadratic formula says if $ax^2+bx+c=0$ then $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$. Use the quadratic formula to solve the following equation.**
$$`r ex`=0$$
**Simplify your answer(s) as much as possible.**

\vfill
\vfill

`r solstart`

$$x = \frac{-(`r b`)\pm\sqrt{(`r b`)^2-4(`r a`)(`r c`)}}{2(`r a`)} $$
$$x = \frac{-(`r b`)\pm\sqrt{`r b^2`-`r 4*a*c`}}{2(`r a`)} $$

$$x = \frac{`r -b` \pm \sqrt{`r b^2-4*a*c`}}{`r 2*a`}$$

$$x = \frac{`r -b` \pm \sqrt{-`r R2infr^2*4`\cdot`r R2inrad`}}{`r 2*a`}$$

$$x = \frac{`r -b` \pm `r R2infr*2`\sqrt{`r R2inrad`}\,i}{`r 2*a`}$$

```{r,echo=F}
ex = paste0(round(-b/2),"\\pm",R2infr,"\\sqrt{",R2inrad,"}\\,i",collapse="")
ex = gsub("\\pm1\\sqrt","\\pm\\sqrt",ex,fixed=T)
```

$$x = `r ex`$$

Notice that $i$ in NOT under the square-root radical symbol!!

`r solend`

\vfill

```{r,echo=F}
while(T){
    nums = sample(2:9,4)*sample(c(-1,1),4,T)
    m = nums[1]
    n = nums[2]
    p = nums[3]
    q = nums[4]
    c1 = paste0("{",m,"}+{",n,"}i",collapse="")
    c1 = gsub("+{-","-{",c1,fixed=T)
    c2 = paste0("{",p,"}+{",q,"}i",collapse="")
    c2 = gsub("+{-","-{",c2,fixed=T)
    
    A = m*p
    B = m*q
    C = n*p
    D = n*q
    
    rp = A-D
    ip = B+C
    if(abs(rp)>1 && abs(ip)>1 && max(abs(c(A,B,C,D,rp,ip)))<80 && abs(rp)!=abs(ip)){break}
}

exp1 = paste0("{",A,"}+{",B,"}i+{",C,"}i+{",D,"}i^2",collapse="")
exp1 = gsub("+{-","-{",exp1,fixed=T)
exp2 = paste0("{",A,"}+{",B,"}i+{",C,"}i+{",-D,"}",collapse="")
exp2 = gsub("+{-","-{",exp2,fixed=T)
exp3 = paste0("{",A,"}+{",-D,"}+{",B,"}i+{",C,"}i",collapse="")
exp3 = gsub("+{-","-{",exp3,fixed=T)
exp4 = paste0("{",A-D,"}+{",B+C,"}i",collapse="")
exp4 = gsub("+{-","-{",exp4,fixed=T)

```

2. **Express the product of $`r c1`$ and $`r c2`$ in standard form ($a+bi$).**

\vfill

`r solstart`
$$(`r c1`)\cdot(`r c2`)$$
$$`r exp1`$$
$$`r exp2`$$
$$`r exp3`$$
$$`r exp4`$$
`r solend`

\newpage

## Polynomial Factoring `r params$titex` (version `r params$rseed`)

```{r,echo=F}
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
while(T){
    r = sample(c(-6:-1,1:6),3)
    a = 1
    b = -sum(r)
    c = r[1]*r[2]+r[2]*r[3]+r[1]*r[3]
    d = -r[1]*r[2]*r[3]
    A = a
    B = b+r[1]*a
    C = c+r[1]*(b+r[1]*a)
    if(min(abs(c(a,b,c,d,A,B,C)))>0){break}
}



```

3. **Write function $f(x)=`r pfix(c(a,b,c,d),3:0)`$ in factored form. I'll give you a hint: one factor is $(`r pfix(c(1,-r[1]),1:0)`)$.**

\vfill

`r solstart`

\begin{center}
\begin{tabular}{c|c c c c}
          & `r a` & `r b`       & `r c`                 & `r d` \\
`r r[1]` &       & `r r[1]*a` & `r r[1]*(b+r[1]*a)`  & `r r[1]*(c+r[1]*(b+r[1]*a))` \\ \hline
          & `r a` & `r b+r[1]*a`& `r c+r[1]*(b+r[1]*a)` & `r d+r[1]*(c+r[1]*(b+r[1]*a))`
\end{tabular}
\end{center}

$$f(x)~=~(`r pfix(c(1,-r[1]),1:0)`)(`r pfix(c(a,b+r[1]*a,c+r[1]*(b+r[1]*a)),2:0)`)$$

$$f(x)~=~(`r pfix(c(1,-r[1]),1:0)`)(`r pfix(c(1,-r[2]),1:0)`)(`r pfix(c(1,-r[3]),1:0)`)$$


`r solend`


```{r,echo=F}
ffix = function(roots,degs,A=1,x="x"){
    rr = roots[degs!=0]
    dd = degs[degs!=0]
    if(A==1){
        p = paste0("",paste0("(",x,"-",rr,")^{",dd,"}",collapse="\\cdot "))
    } else if(A==-1){
        p = paste0("-",paste0("(",x,"-",rr,")^{",dd,"}",collapse="\\cdot "))
    } else {
        p = paste0(A,paste0("(",x,"-",rr,")^{",dd,"}",collapse="\\cdot "))
    }
    p = gsub("--","+",p,fixed=T)
    p = gsub(paste0("(",x,"-0)",collapse=""),x,p,fixed=T)
    p = gsub("^{1}","",p,fixed=T)
    return(p)
}
nr = sample(3:4,1)
while(T){
    rs = sort(sample(c(-8:-1,1:8),nr))
    if(min(diff(rs))>2 && max(diff(rs))<6){break}
}

degs = sample(c(1,2,sample(c(1,2),nr-2,T)))
A = sample(c(-1,1),1)

```

4. **Polynomial $p$ is defined below in factored form.
$$p(x)~=~`r ffix(rs,degs,A)`$$
Sketch a graph of polynomial $y=p(x)$.**


```{r,echo=F,fig.dim=c(7,3),include = !params$showsol}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-12,12),ylim=c(-1,1))
arrows(-11,0,11,0,0.1,10,3,lwd=2)
arrows(0,-1,0,1,0.1,10,3,lwd=2)
for(i in 1:10){
    if(i==10){
        lines(c(i,i),c(0.1,-0.1),lwd=2)
        lines(c(-i,-i),c(0.1,-0.1),lwd=2)
    }else if(i==5){
        lines(c(i,i),c(0.08,-0.08),lwd=1.5)
        lines(c(-i,-i),c(0.08,-0.08),lwd=1.5)
    } else {
        lines(c(i,i),c(0.05,-0.05),lwd=1)
        lines(c(-i,-i),c(0.05,-0.05),lwd=1)
    }
}
text(11,-0.1,"x",cex=0.7)
text(-0.3,0.99,"y",cex=0.7)
```
\

```{r,echo=F,fig.dim=c(7,3),include = params$showsol}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-12,12),ylim=c(-1,1))
arrows(-11,0,11,0,0.1,10,3,lwd=2)
arrows(0,-1,0,1,0.1,10,3,lwd=2)
for(i in 1:10){
    if(i==10){
        lines(c(i,i),c(0.1,-0.1),lwd=2)
        lines(c(-i,-i),c(0.1,-0.1),lwd=2)
    }else if(i==5){
        lines(c(i,i),c(0.08,-0.08),lwd=1.5)
        lines(c(-i,-i),c(0.08,-0.08),lwd=1.5)
    } else {
        lines(c(i,i),c(0.05,-0.05),lwd=1)
        lines(c(-i,-i),c(0.05,-0.05),lwd=1)
    }
}
xx = seq(-12,12,0.01)
yy = rep(A,length(xx))
for(i in 1:nr){
    yy = yy*(xx-rs[i])^degs[i]
}
xxlo = seq(-12,min(rs),0.01)
yylo = rep(A,length(xxlo))
for(i in 1:nr){
    yylo = yylo*((xxlo-rs[i])^degs[i])
}
xxhi = seq(max(rs),12,0.01)
yyhi = rep(A,length(xxhi))
for(i in 1:nr){
    yyhi = yyhi*((xxhi-rs[i])^degs[i])
}
xx2 = seq(min(rs),max(rs),0.01)
yy2 = rep(A,length(xx2))
for(i in 1:nr){
    yy2 = yy2*((xx2-rs[i])^degs[i])
}
mama = max(abs(yy2))
lines(xxlo,yylo/mama*4/(pi/2),col="blue",lwd=2)
lines(xxhi,yyhi/mama*4/(pi/2),col="blue",lwd=2)
lines(xx2,atan(yy2/mama*10)/(pi/2),col="blue",lwd=2)
for(rr in rs){
    points(rr,0,pch=20,cex=2)
}
text(11,-0.1,"x",cex=0.7)
text(-0.3,0.99,"y",cex=0.7)

```
\


