---
output: slidy_presentation
---

# Agenda

* Entrance Ticket: [ET_0925](https://bart.instructure.com/courses/2110/quizzes/3201)
* Parent functions and shifting (translations)
    * [OCW_0925_ID_parent_and_shift](https://bart.instructure.com/courses/2110/quizzes/3202)

# How to shift...

* Parent function curve is $y=f(x)$.

* To shift **right** by $5$ and **down** by $3$:
$$y=f(x-5)-3$$
* To shift **right** by $4$ and **up** by $8$:
$$y=f(x-4)+8$$
* To shift **left** by $2$ and **down** by $7$:
$$y=f(x+2)-7$$
* To shift **left** by $6$ and **up** by $1$:
$$y=f(x+6)+1$$
* Notice the horizontal-coordinate transformation is "backwards".
    * This goes back to "set argument to value and solve equation"
    * When solving, you apply INVERSE operations in REVERSE order
    * Those inverses are applied to the old $x$ to get new $x$
* Notice the vertical-coordinate transformation is "normal".
    * We simply replace the $f(\ldots)$ with old $y$ and evaluate expression to get new $y$.


# Some Parent Functions

```{r,echo=F}
fdim = 2
```

### Absolute-value function

$$y=|x|$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit = function(){
    par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
    for(i in -5:5){
        lines(c(-5,5),c(i,i),col="grey",lwd=0.5)
        lines(c(i,i),c(-5,5),col="grey",lwd=0.5)
    }
    for(i in seq(-5,5,10)){
        lines(c(-5,5),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-5,5),col="darkgrey",lwd=0.8)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    text(5,-0.5,"5",cex=0.7)
    text(-0.5,5,"5",cex=0.7)
    text(5,0.5,"x",cex=0.7)
    text(0.5,5,"y",cex=0.7)
}
startit()
x = seq(-5,5,0.1)
y = abs(x)
lines(x,y,lwd=3,col="blue")
xp = 0
yp = 0
points(yp,xp,pch=19,col="blue",cex=0.8)
```

### Squaring function

$$y=x^2$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-sqrt(5),sqrt(5),0.01)
y = x^2
lines(x,y,lwd=3,col="blue")
xp = -2:2
yp = xp^2
points(xp,yp,pch=19,col="blue",cex=0.8)
```


### Square-root function

$$y=\sqrt{x}~~~~\text{or}~~~~y=x^{1/2}$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(0,sqrt(5),0.01)
y = x^2
lines(y,x,lwd=3,col="blue")
xp = 0:2
yp = xp^2
points(yp,xp,pch=19,col="blue",cex=0.8)
```


\newpage

### Reciprocal function

$$y=\frac{1}{x}~~~~\text{or}~~~~y=x^{-1}$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x1 = seq(-5,-1/5,0.01)
y1 = 1/x1
lines(x1,y1,lwd=3,col="blue")
x2 = seq(1/5,5,0.01)
y2 = 1/x2
lines(x2,y2,lwd=3,col="blue")
xp = c(-1,1)
yp = 1/xp
points(yp,xp,pch=19,col="blue",cex=0.8)
```

### Cubing function

$$y=x^3$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-5^(1/3),5^(1/3),0.01)
y = x^3
lines(x,y,lwd=3,col="blue")
xp = -2:2
yp = xp^3
points(xp,yp,pch=19,col="blue",cex=0.8)
```


### Cube-root function

$$y=\sqrt[3]{x}~~~~\text{or}~~~~y=x^{1/3}$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-5,5,0.01)
y = sign(x)*abs(x)^(1/3)
lines(x,y,lwd=3,col="blue")
xp = c(-8,-1,0,1,8)
yp = sign(xp)*abs(xp)^(1/3)
points(xp,yp,pch=19,col="blue",cex=0.8)
```

\newpage

### Exponential (base 2)

$$y=2^x$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-5,log(5)/log(2),0.001)
y = 2^x
lines(x,y,lwd=3,col="blue")
xp = c(0,1,2)
yp = 2^xp
points(xp,yp,pch=19,col="blue",cex=0.8)
```


### Logarithm (base 2)

$$y=\log_2(x)$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-5,log(5)/log(2),0.001)
y = 2^x
lines(y,x,lwd=3,col="blue")
xp = c(0,1,2)
yp = 2^xp
points(yp,xp,pch=19,col="blue",cex=0.8)
```

### Squared reciprocal

$$y=\frac{1}{x^2}~~~~\text{or}~~~~y=x^{-2}$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-5,-sqrt(1/5),0.001)
y = 1/x^2
lines(x,y,lwd=3,col="blue")
x = seq(sqrt(1/5),5,0.001)
y = 1/x^2
lines(x,y,lwd=3,col="blue")
xp = c(-1,1)
yp = 1/xp^2
points(xp,yp,pch=19,col="blue",cex=0.8)
```

\newpage

### Sine 

$$y=\sin(x)$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-5,5,0.001)
y = sin(x)
lines(x,y,lwd=3,col="blue")
xp = 0
yp = 0
points(xp,yp,pch=19,col="blue",cex=0.8)
```


### Cosine 

$$y=\cos(x)$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-5,5,0.001)
y = cos(x)
lines(x,y,lwd=3,col="blue")
xp = 0
yp = 1
points(xp,yp,pch=19,col="blue",cex=0.8)
```


### Tangent 

$$y=\tan(x)$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-atan(5),atan(5),0.001)
y = tan(x)
lines(x,y,lwd=3,col="blue")
x = seq(-pi-atan(5),-pi+atan(5),0.001)
y = tan(x)
lines(x,y,lwd=3,col="blue")
x = seq(pi-atan(5),pi+atan(5),0.001)
y = tan(x)
lines(x,y,lwd=3,col="blue")
xp = 0
yp = 0
points(xp,yp,pch=19,col="blue",cex=0.9)
```


