```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+{-","-{",exp,fixed=T)
  exp = gsub("{1}x^{0}","1",exp,fixed=T)
  exp = gsub("{1}","{}",exp,fixed=T)
  exp = gsub("x^{0}","{}",exp,fixed=T)
  return(exp)
}
fixer2 = function(exp){
  exp = gsub("+{-","-{",exp,fixed=T)
  return(exp)
}

while(T){
  pows = sort(sample(1:9,2))
  xs = round(sort(sample(11:89,2))/100,2)
  ys = xs^pows[1]-xs^pows[2]
  nt1 = xs[2]^(pows[1]+1)/(pows[1]+1)
  nt2 = xs[2]^(pows[2]+1)/(pows[2]+1)
  nt3 = xs[1]^(pows[1]+1)/(pows[1]+1)
  nt4 = xs[1]^(pows[2]+1)/(pows[2]+1)
  A = nt1-nt2-nt3+nt4
  if(min(ys)>0.05 && abs(diff(xs))>0.1 && A>0.01){break}
}

f = fixer(paste0("x^{",pows[1],"}-x^{",pows[2],"}"))
g = paste0("\\frac{1}{",pows[1]+1,"}x^{",pows[1]+1,"}-\\frac{1}{",pows[2]+1,"}x^{",pows[2]+1,"}")

t1 = paste0("\\frac{1}{",pows[1]+1,"}(",xs[2],")^{",pows[1]+1,"}")
t2 = paste0("\\frac{1}{",pows[2]+1,"}(",xs[2],")^{",pows[2]+1,"}")
t3 = paste0("\\frac{1}{",pows[1]+1,"}(",xs[1],")^{",pows[1]+1,"}")
t4 = paste0("\\frac{1}{",pows[2]+1,"}(",xs[1],")^{",pows[2]+1,"}")



```

Question
========

A [definite integral](https://en.wikipedia.org/wiki/Integral) can be used to express the area under a curve. For example, say we wanted to find the area under $f(x)=`r f`$ between $x=`r xs[1]`$ and $x=`r xs[2]`$. Let's draw a picture.

```{r,fig.dim=c(7,7),echo=F}
par(pty="s")
plot(0,0,type="n",xlim=c(0,1),ylim=c(0,1),xlab="x",ylab="y")
for(i in seq(0.1,1,0.1)){
  abline(h=i,col="grey")
  abline(v=i,col="grey")
}
arrows(-0.03,0,1.03,0,code=3,lwd=2,length=0.05)
arrows(0,-0.03,0,1.03,code=3,lwd=2,length=0.05)
x = seq(0,1,0.01)
y = x^pows[1]-x^pows[2]
legend(0,1,"y = f(x)",col="blue",lwd=3)

polygon(c(xs[1],x[(x>=xs[1])&(x<=xs[2])],xs[2]),c(0,y[(x>=xs[1])&(x<=xs[2])],0),col=rgb(1,0.3,0.3,0.5),border="red")
text(mean(xs),0.05,"A",col="red")
lines(x,y,col="blue",lwd=3)

```
\


The area equals the definite integral of the function on interval [`r xs[1]`, `r xs[2]`].

$$A ~=~ \int_{`r xs[1]`}^{`r xs[2]`} \left(`r f` \right)~dx$$

This definite integral can be evaluated from an antiderivative of $f(x)$. Let $g(x)$ be an antiderivative of $f(x)$ such that $g'(x)=f(x)$. 

$$A~=~g(`r xs[2]`)-g(`r xs[1]`)$$

Find the area. The tolerance is $\pm 0.001$.


Solution
========

We were given the curve's function.

$$f(x)=`r f`$$


Remember how to find an antiderivative of a polynomial.

$$g(x)=`r g`+C$$

In this case, we can't determine $C$, but we do not need to because the area is a difference of two instances of $g$.

$$g(`r xs[2]`)-g(`r xs[1]`)=\left(\frac{1}{`r pows[1]+1`}(`r xs[2]`)^{`r pows[1]+1`}-\frac{1}{`r pows[2]+1`}(`r xs[2]`)^{`r pows[2]+1`}+C\right)-\left(\frac{1}{`r pows[1]+1`}(`r xs[1]`)^{`r pows[1]+1`}-\frac{1}{`r pows[2]+1`}(`r xs[1]`)^{`r pows[2]+1`}+C\right)$$

Simplify.

$$A=\frac{1}{`r pows[1]+1`}(`r xs[2]`)^{`r pows[1]+1`}-\frac{1}{`r pows[2]+1`}(`r xs[2]`)^{`r pows[2]+1`}-\frac{1}{`r pows[1]+1`}(`r xs[1]`)^{`r pows[1]+1`}+\frac{1}{`r pows[2]+1`}(`r xs[1]`)^{`r pows[2]+1`}$$

Evaluate.

$$A=(`r nt1`)-(`r nt2`)-(`r nt3`)+(`r nt4`)$$

So,

$$A = `r A`$$



Meta-information
============
extype: num
exsolution: `r A`
exname: definite_integral
extol: 0.001