```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+{-","-{",exp,fixed=T)
  exp = gsub("{1}x^{0}","1",exp,fixed=T)
  exp = gsub("{1}","{}",exp,fixed=T)
  exp = gsub("x^{0}","{}",exp,fixed=T)
  return(exp)
}

while(T){
  ps = round(10^runif(2,-0.5,0.5),2)
  a = ps[1]
  b = ps[2]
  V = pi/(a+b+1)
  if(abs(diff(c(a,b)))>0.2 && V>0.2){break}
}

xs = seq(0,1,0.01)
ys = xs^a
zs = xs^b

zero = rep(0,length(xs))

X1 = matrix(c(rev(xs),xs,zero,zero,rev(zs),-zs),3,byrow=T)
X2 = matrix(c(rev(xs),xs,rev(ys),-ys,zero,zero),3,byrow=T)
X = list(X1,X2)
n = 180
t = seq(0,2*pi,length.out=n)
for(x in seq(0.1,1,0.1)){
  xs = rep(x,length(t))
  ry = x^a
  rz = x^b
  ys = ry*cos(t)
  zs = rz*sin(t)
  cl = length(X)
  X[[cl+1]] = matrix(c(xs,ys,zs),nrow=3,byrow=T)
}

Y = list()
for(x in seq(0.01,1,0.01)){
  xs = rep(x,length(t))
  ry = x^a
  rz = x^b
  ys = ry*cos(t)
  zs = rz*sin(t)
  cl = length(Y)
  Y[[cl+1]] = matrix(c(xs,ys,zs),nrow=3,byrow=T)
}

```

Question
========

A 3D shape is produced with elliptical cross sections. As $x$ progresses from along the interval $[0,1]$, the cross section perpendicular to the $x$ axis will be an ellipse with axes (and radii) parallel to the $y$ and $z$ axes. The (maximum and minimum) radii are power functions with respect to $x$.

$$r_1(x) ~=~ x^{`r a`}$$
$$r_2(x) ~=~ x^{`r b`}$$

```{r,echo=F,fig.dim=c(6,6)}
getR = function(u,t){
  ux = u[1]
  uy = u[2]
  uz = u[3]
  f = cos(t)+ux^2*(1-cos(t))
  g = ux*uy*(1-cos(t))-uz*sin(t)
  h = ux*uz*(1-cos(t))+uy*sin(t)
  i = uy*ux*(1-cos(t))+uz*sin(t)
  j = cos(t)+uy^2*(1-cos(t))
  k = uy*uz*(1-cos(t))-ux*sin(t)
  l = uz*ux*(1-cos(t))-uy*sin(t)
  m = uz*uy*(1-cos(t))+ux*sin(t)
  n = cos(t)+uz^2*(1-cos(t))
  R = matrix(c(f,g,h,i,j,k,l,m,n),3,byrow=T)
  return(R)
}
tp = pi/4
r = 0.05
P = matrix(c(1,r*cos(tp),0,
             0,r*sin(tp),1),2,byrow=T)
par(pty="s")
u = c(0,0,1)
Xc = X
Yc = Y
plot(0,0,type="n",xlim=c(-0.5,1.5),ylim=c(-1,1),xlab="x",ylab="z")
for(j in 1:length(Yc)){
  Yc_flat = P%*%Yc[[j]]
  polygon(Yc_flat[1,],Yc_flat[2,],col="red",border="red",lwd=3)
}
abline(h=0)
abline(v=0)
lines(c(-sqrt(2)/4,sqrt(2)/4),c(-sqrt(2)/4,sqrt(2)/4))
for(j in 1:length(Xc)){
  Xc_flat = P%*%Xc[[j]]
  lines(Xc_flat[1,],Xc_flat[2,],lwd=2)
}
```
\


```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(6,6)}
getR = function(u,t){
  ux = u[1]
  uy = u[2]
  uz = u[3]
  f = cos(t)+ux^2*(1-cos(t))
  g = ux*uy*(1-cos(t))-uz*sin(t)
  h = ux*uz*(1-cos(t))+uy*sin(t)
  i = uy*ux*(1-cos(t))+uz*sin(t)
  j = cos(t)+uy^2*(1-cos(t))
  k = uy*uz*(1-cos(t))-ux*sin(t)
  l = uz*ux*(1-cos(t))-uy*sin(t)
  m = uz*uy*(1-cos(t))+ux*sin(t)
  n = cos(t)+uz^2*(1-cos(t))
  R = matrix(c(f,g,h,i,j,k,l,m,n),3,byrow=T)
  return(R)
}
tp = pi/4
r = 0.2
P = matrix(c(1,r*cos(tp),0,
             0,r*sin(tp),1),2,byrow=T)
n = 20
par(pty="s",mar=c(0,0,0,0))
u = c(0,0,1)
t = 2*pi/n
R = getR(u,t)
Xc = X
Yc = Y
for(i in 1:n){
  plot(0,0,type="n",axes=F,ann=F,xlim=c(-1.5,1.5),ylim=c(-1.5,1.5))
  for(j in 1:length(Yc)){
    Yc_flat = P%*%Yc[[j]]
    polygon(Yc_flat[1,],Yc_flat[2,],col="red",border="red",lwd=3)
    Yc[[j]] = R%*%Yc[[j]]
  }
  for(j in 1:length(Xc)){
    Xc_flat = P%*%Xc[[j]]
    lines(Xc_flat[1,],Xc_flat[2,])
    Xc[[j]] = R%*%Xc[[j]]
  }
}
```
\

Find the volume of the shape. The tolerance is $\pm 0.01$ cubic units. 

As a hint, I'll remind you that the area of an ellipse is found by multiplying the radii by each other and pi: $A=\pi\cdot r_1 \cdot r_2$.


Solution
========

Imagine breaking the 3D shape into a bunch of elliptical slices with infinitesimal thickness $dx$.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s",mar=c(0,0,0,0))
tp = -pi/6
r = 0.3
P = matrix(c(1,r*cos(tp),0,
             0,r*sin(tp),1),2,byrow=T)
plot(0,0,type="n",xlim=c(-0.5,1.5),ylim=c(-1,1))
dx = 0.05
nd = 100
th = seq(0,2*pi,length.out=nd)
for(x in rev(seq(0,1-dx,dx))){
  y = x^a
  z = x^b
  sq = matrix(c(rep(x+dx,nd),y*cos(th),z*sin(th)),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)
  for(i in 1:(length(th)-1)){
    xs = c(x,x,x+dx,x+dx)
    ys = c(y*cos(th[i]),y*cos(th[i+1]),y*cos(th[i+1]),y*cos(th[i]))
    zs = c(z*sin(th[i]),z*sin(th[i+1]),z*sin(th[i+1]),z*sin(th[i]))
    sq = matrix(c(xs,ys,zs),nrow=3,byrow=T)
    flsq = P%*%sq
    polygon(flsq[1,],flsq[2,],col="red",border=NA,lwd=1)
  }
  sq = matrix(c(rep(x,nd),y*cos(th),z*sin(th)),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)
}
abline(h=0)
abline(v=0)
xs = seq(0,1,0.001)
ys = xs^a
zs = xs^b
sq = matrix(c(xs,rep(0,length(xs)),zs),nrow=3,byrow=T)
flsq = P%*%sq
lines(flsq[1,],flsq[2,],col="black",lwd=2)
sq = matrix(c(xs,rep(0,length(xs)),-zs),nrow=3,byrow=T)
flsq = P%*%sq
lines(flsq[1,],flsq[2,],col="black",lwd=2)
sq = matrix(c(xs,ys,rep(0,length(xs))),nrow=3,byrow=T)
flsq = P%*%sq
lines(flsq[1,],flsq[2,],col="black",lwd=2)
sq = matrix(c(xs,-ys,rep(0,length(xs))),nrow=3,byrow=T)
flsq = P%*%sq
lines(flsq[1,],flsq[2,],col="black",lwd=1,lty=3)

```
\

Each elliptical slab has an infinitesimal volume.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-0.5,1.5),ylim=c(-1,1))
abline(h=0)
abline(v=0)
dx = 0.1
x = 0.5
y = x^a
z = x^b
if(y>z){
  y=1.3
  z=0.95
} else {
  y=0.7
  z=0.95
}
th = seq(0,2*pi,length.out=300)
xs = rep(x,length(th))
ys = y*cos(th)
zs = z*sin(th)
sq = matrix(c(xs+dx,ys,zs),nrow=3,byrow=T)
flsq = P%*%sq
polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)
for(i in 1:(length(th)-1)){
  xs1 = c(x,x,x+dx,x+dx)
  ys1 = c(y*cos(th[i]),y*cos(th[i+1]),y*cos(th[i+1]),y*cos(th[i]))
  zs1 = c(z*sin(th[i]),z*sin(th[i+1]),z*sin(th[i+1]),z*sin(th[i]))
  sq = matrix(c(xs1,ys1,zs1),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],col="red",border=NA,lwd=1)
}
sq = matrix(c(xs,ys,zs),nrow=3,byrow=T)
flsq = P%*%sq
polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=3)

xs = c(x,x)
ys = c(0,y)
zs = c(0,0)
sq = matrix(c(xs,ys,zs),nrow=3,byrow=T)
flsq = P%*%sq
lines(flsq[1,],flsq[2,],col="black",lwd=3)

xs = c(x,x)
ys = c(0,0)
zs = c(0,z)
sq = matrix(c(xs,ys,zs),nrow=3,byrow=T)
flsq = P%*%sq
lines(flsq[1,],flsq[2,],col="black",lwd=3)

lines(c(0,x),c(0,0))
library(latex2exp)
text(x-0.05,z/2,TeX("$r_2$"))

sq = P%*%matrix(c(x-0.07,2*y/3,0))
text(sq[1,],sq[2,],TeX("$r_1$"))

text(x+dx/2,z+0.05,"dx")
```
\

$$dV = \pi r_1 r_2 \, dx$$

$$dV = \pi x^{`r a`} x^{`r b`} \, dx$$

$$dV = \pi x^{`r a+b`} \, dx$$

To get the total volume, we need to **S**um up all the infinitesimal volumes as $x$ varies from 0 to 1.

$$V = \int_{x=0}^{x=1} dV$$

$$V = \int_{0}^{1} \pi x^{`r a+b`} \, dx$$

Find antiderivitive $g(x)$ so that $g'(x)=\pi x^{`r a+b`}$ and $g(0)=0$ (so the constant of integration is 0).

$$g(x) = \frac{\pi}{`r a+b+1`} x^{`r a+b+1`}$$

The total volume can be expressed in terms of function $g$.

$$V = g(1)-g(0)$$

Evaluate.

$$V = \frac{\pi}{`r a+b+1`} (1)^{`r a+b+1`}-\frac{\pi}{`r a+b+1`} (0)^{`r a+b+1`}$$


$$V = \frac{\pi}{`r a+b+1`}$$

$$V\approx `r V`$$


Meta-information
============
extype: num
exsolution: `r V`
exname: vol_ellipse_cs
extol: 0.01