```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+{-","-{",exp,fixed=T)
  exp = gsub("{1}x^{0}","1",exp,fixed=T)
  exp = gsub("{1}","{}",exp,fixed=T)
  exp = gsub("x^{0}","{}",exp,fixed=T)
  return(exp)
}

hk = rev(sort(sample(4:13,2)))
h = hk[1]
k = hk[2]
m = sample(2:5,1)
b = k-m*h
a = k/h^2

xint = -b/m

```

Question
========

A bowl is designed as the [revolution](https://en.wikipedia.org/wiki/Solid_of_revolution) of the region between $z=`r m`x-`r abs(b)`$ and $z=\frac{`r k`}{`r h^2`}x^2$. The revolution occurs around the $z$ axis. The bowl will be made of wood. 

```{r,echo=F,fig.dim=c(7,7)}
par(pty="s")
plot(0,0,type="n",xlim=c(0,h),ylim=c(0,h),xlab="x",ylab="z")
for(i in 0:h){
  abline(h=i,col="grey")
  abline(v=i,col="grey")
}
arrows(0,0,0,h+0.2,length=0.05)
arrows(0,0,h+0.2,0,length=0.05)
x = seq(0,h,length.out=100)
x2 = seq(-b/m,h,length.out=100)
y1 = a*x^2
y2 = m*x2+b
lines(x,y1)
lines(x2,y2)
points(h,k,pch=19)
polygon(c(x,rev(x2)),c(y1,rev(y2)),col=rgb(0.9,0.2,0.2,0.8))
```
\

Notice the point of intersection is $(`r h`, `r k`)$. Below is a wireframe animation of the bowl.

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(6,6)}
curves = list()
n = 12
nframes = 10
for(y in 0:k){
  th = seq(0,2*pi,length.out=360)
  x1 = (y-b)/m
  nc = length(curves)
  pnts = matrix(c(x1*cos(th),x1*sin(th),rep(y,length(th))),nrow=3,byrow=T)
  curves[[nc+1]] = pnts
  x2 = sqrt(y/a)
  pnts = matrix(c(x2*cos(th),x2*sin(th),rep(y,length(th))),nrow=3,byrow=T)
  curves[[nc+2]] = pnts
}
for(th in seq(0,2*pi,length.out=n)){
  x = seq(0,h,length.out=100)
  x2 = seq(xint,h,length.out=100)
  z1 = m*x2+b
  z2 = a*x^2
  nc = length(curves)
  pnts = matrix(c(x2*cos(th),x2*sin(th),z1),nrow=3,byrow=T)
  curves[[nc+1]] = pnts
  pnts = matrix(c(x*cos(th),x*sin(th),z2),nrow=3,byrow=T)
  curves[[nc+2]] = pnts
}

getR = function(u,t){
  ux = u[1]
  uy = u[2]
  uz = u[3]
  f = cos(t)+ux^2*(1-cos(t))
  g = ux*uy*(1-cos(t))-uz*sin(t)
  h = ux*uz*(1-cos(t))+uy*sin(t)
  i = uy*ux*(1-cos(t))+uz*sin(t)
  j = cos(t)+uy^2*(1-cos(t))
  k = uy*uz*(1-cos(t))-ux*sin(t)
  l = uz*ux*(1-cos(t))-uy*sin(t)
  m = uz*uy*(1-cos(t))+ux*sin(t)
  n = cos(t)+uz^2*(1-cos(t))
  R = matrix(c(f,g,h,i,j,k,l,m,n),3,byrow=T)
  return(R)
}
u = c(0,0,1)
t = 2*pi/n/nframes
R = getR(u,t)
tp = pi/2
r = 0.4
P = matrix(c(1,r*cos(tp),0,
             0,r*sin(tp),1),2,byrow=T)
X = curves
for(i in 1:nframes){
  par(pty="s")
  plot(0,0,type="n",xlim=c(-h,h),ylim=c(-h/2,3*h/2),ann=F,axes=F)
  for(j in 1:length(X)){
    Xf = P%*%X[[j]]
    lines(Xf[1,],Xf[2,],col="black",lwd=2)
    X[[j]] = R%*%X[[j]]
  }
}
```
\

Find the volume of the wood composing the bowl. I'd recommend using the [washer method](https://en.wikipedia.org/wiki/Disc_integration#Washer_method).


Solution
========

We will use the [washer method](https://en.wikipedia.org/wiki/Disc_integration#Washer_method). Notice we can approximate the shape with a bunch of thin washers.

```{r,echo=F,fig.dim=c(6,6)}
dz = k/30
zs = seq(dz,k-dz,dz)
r1 = sqrt(zs/a)
r2 = (zs-b)/m
f = 0.4

par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-h,h),ylim=c(-h/2,3*h/2),ann=F,axes=F)

draw_washer = function(z,r1,r2,dz,perspective_ratio=0.5,col="red"){
  N = 360
  pr = perspective_ratio
  th = seq(0,pi,length.out=N/2)
  lines(r1*cos(th),z-dz+r1*pr*sin(th),lwd=2)
  t = seq(0,pi,length.out=N/2)
  for(i in 1:(length(t)-1)){
    polygon(c(r1*cos(t[i]),r1*cos(t[i]),r1*cos(t[i+1]),r1*cos(t[i+1])),
            c(z-dz+r1*pr*sin(t[i]),z+r1*pr*sin(t[i]),z+r1*pr*sin(t[i+1]),z-dz+r1*pr*sin(t[i+1])),
            col=col,border=col)
  }
  t = seq(pi,2*pi,length.out=N/2)
  for(i in 1:(length(t)-1)){
    polygon(c(r2*cos(t[i]),r2*cos(t[i]),r2*cos(t[i+1]),r2*cos(t[i+1])),
            c(z-dz+r2*pr*sin(t[i]),z+r2*pr*sin(t[i]),z+r2*pr*sin(t[i+1]),z-dz+r2*pr*sin(t[i+1])),
            col=col,border=col)
  }
  th = seq(pi,2*pi,length.out=N/2)
  lines(r2*cos(th),z-dz+r2*pr*sin(th))
  t = seq(0,2*pi,length.out=N)
  for(i in 1:(length(t)-1)){
    polygon(c(r2*cos(t[i]),r2*cos(t[i+1]),r1*cos(t[i+1]),r1*cos(t[i])),
            c(z+r2*pr*sin(t[i]),z+r2*pr*sin(t[i+1]),z+r1*pr*sin(t[i+1]),z+r1*pr*sin(t[i])),
            col=col,border=col)
  }
  th = seq(0,2*pi,length.out=N)
  lines(r1*cos(th),z+r1*pr*sin(th))
  lines(r2*cos(th),z+r2*pr*sin(th))
}

for(i in 1:length(zs)){
  draw_washer(zs[i],r1[i],r2[i],dz,f,col=hsv(i/length(zs),0.7,0.5+0.1*i%%5))
}

```
\

Each washer has two radii (inner and outer) and an infinitesimal thickness.

```{r,echo=F,fig.dim=c(6,3)}
draw_washer = function(z,r1,r2,dz,perspective_ratio=0.5,col="red"){
  N = 360
  pr = perspective_ratio
  th = seq(0,pi,length.out=N/2)
  lines(r1*cos(th),z-dz+r1*pr*sin(th),lwd=2)
  t = seq(0,pi,length.out=N/2)
  for(i in 1:(length(t)-1)){
    polygon(c(r1*cos(t[i]),r1*cos(t[i]),r1*cos(t[i+1]),r1*cos(t[i+1])),
            c(z-dz+r1*pr*sin(t[i]),z+r1*pr*sin(t[i]),z+r1*pr*sin(t[i+1]),z-dz+r1*pr*sin(t[i+1])),
            col=col,border=col)
  }
  t = seq(pi,2*pi,length.out=N/2)
  for(i in 1:(length(t)-1)){
    polygon(c(r2*cos(t[i]),r2*cos(t[i]),r2*cos(t[i+1]),r2*cos(t[i+1])),
            c(z-dz+r2*pr*sin(t[i]),z+r2*pr*sin(t[i]),z+r2*pr*sin(t[i+1]),z-dz+r2*pr*sin(t[i+1])),
            col=col,border=col)
  }
  th = seq(pi,2*pi,length.out=N/2)
  lines(r2*cos(th),z-dz+r2*pr*sin(th))
  t = seq(0,2*pi,length.out=N)
  for(i in 1:(length(t)-1)){
    polygon(c(r2*cos(t[i]),r2*cos(t[i+1]),r1*cos(t[i+1]),r1*cos(t[i])),
            c(z+r2*pr*sin(t[i]),z+r2*pr*sin(t[i+1]),z+r1*pr*sin(t[i+1]),z+r1*pr*sin(t[i])),
            col=col,border=col)
  }
  th = seq(0,2*pi,length.out=N)
  lines(r1*cos(th),z+r1*pr*sin(th))
  lines(r2*cos(th),z+r2*pr*sin(th))
}

par(mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-1,1),ylim=c(-0.5,0.5),ann=F,axes=F)

draw_washer(0.05,0.5,0.9,0.1,col=rgb(0.9,0.9,0.9))
text(1,0,"dz",cex=1.3)
bmp = 0.01
x0 = 0.93
lines(c(x0-bmp,x0+bmp,x0,x0,x0+bmp,x0-bmp),
      c(-0.05,-0.05,-0.05,0.05,0.05,0.05))
lines(c(0,0.5),c(0.05,0.05),col="blue",lwd=3)
text(0.25,0,"r",col="blue",cex=1.3)
lines(c(0,0.9*cos(5*pi/6)),c(0.05,0.05+0.9*0.5*sin(5*pi/6)),col="red",lwd=3)
text(-0.27,0.2,"R",col="red",cex=1.3)
```
\

The infinitesimal volume for each washer can be expressed in terms of $r$, $R$, and $dz$.

$$dV ~=~ \pi \left(R^2 - r^2\right) \, dz$$

We need to express $R$ and $r$ as functions of $z$. Notice, that $R$ is equivalent to $x$ in the linear equation and $r$ is equivalent to $x$ in the quadratic equation. Let's start by finding $R$ in terms of $z$.

$$z = `r m`R-`r abs(b)`$$

Solve for $R$.

$$R = \frac{z+`r abs(b)`}{`r m`}$$

Now, let's get $r$ in terms of $z$.

$$z = \frac{`r k`}{`r h^2`}r^2$$

Solve for $r$.

$$r = \sqrt{\frac{`r h^2`z}{`r k`}}$$

To get the volume, we need to sum up a bunch of washer volumes as $z$ progresses from 0 to `r k`.

$$V = \int_{z=0}^{z=`r k`} dV$$

$$V = \int_{0}^{`r k`} \pi\left(R^2-r^2\right)\,dz$$


$$V = \int_{0}^{`r k`} \pi\left(\left(\frac{z+`r abs(b)`}{`r m`}\right)^2-\left(\sqrt{\frac{`r h^2`z}{`r k`}}\right)^2\right)\,dz$$

Remember [binomial expansion](https://en.wikipedia.org/wiki/Binomial_theorem).

$$V = \int_{0}^{`r k`} \pi\left(\left(\frac{z+`r abs(b)`}{`r m`}\right)^2-\left(\sqrt{\frac{`r h^2`z}{`r k`}}\right)^2\right)\,dz$$




Meta-information
============
extype: num
exsolution: 1
exname: vol_by_washers
extol: 0.01