```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+{-","-{",exp,fixed=T)
  exp = gsub("{1}x^{0}","1",exp,fixed=T)
  exp = gsub("{1}","{}",exp,fixed=T)
  exp = gsub("x^{0}","{}",exp,fixed=T)
  return(exp)
}

while(T){
  dy = sample(c(-1,0,1),10,T)
  y0 = sample((-2):2,1)
  y = c(y0,y0+cumsum(dy))
  ab = sort(sample(1:9,2))
  a = ab[1]
  b = ab[2]
  S = sum(c(y[(a+1):(b)],y[(a+2):(b+1)]))/2
  if(sum(sign(abs(diff(dy))))<6 && sum(sign(abs(diff(dy))))>2 &&
     min(y)>-5 && max(y)<5 && length(unique(dy[a:b]))==3 &&
     min(y[(a+1):(b+1)])<0 && max(y[(a+1):(b+1)])>0 && S!=0 &&
     sum(y==0)<3){break}
}


```

Question
========

A function $f(x)$ is graphed below.

```{r,echo=F,fig.dim=c(8,8)}
par(pty="s")
plot(0:10,y,"l",xlim=c(0,10),ylim=c(-5,5),xlab="x",ylab="y")

for(i in 0:10){
  abline(h=i,col="grey")
  abline(h=-i,col="grey")
  abline(v=i,col="grey")
}
arrows(-0.2,0,10.2,0,length=0.05,lwd=2,code=3)
arrows(0,-5.2,0,5.2,length=0.05,lwd=2,code=3)


lines(0:10,y,lwd=3,col="purple")
legend(4,10,"y=f(x)",col="purple",lwd=3)

```
\

Evaluate the following integral.
$$\int_{`r a`}^{`r b`}f(x)\,dx$$


Solution
========

The definite integral represents total of the [signed area](https://en.wikipedia.org/wiki/Signed_area) between the $x$-axis and $y=f(x)$ between $x=`r a`$ and $x=`r b`$. Find the area by counting boxes.

```{r,echo=F,fig.dim=c(8,8)}
par(pty="s")
plot(0:10,y,"l",xlim=c(0,10),ylim=c(-5,5),xlab="x",ylab="y")

for(i in 0:10){
  abline(h=i,col="grey")
  abline(h=-i,col="grey")
  abline(v=i,col="grey")
}
arrows(-0.2,0,10.2,0,length=0.05,lwd=2,code=3)
arrows(0,-5.2,0,5.2,length=0.05,lwd=2,code=3)

lines(0:10,y,lwd=3,col="purple")


pn = sign(y)

su = 0

for(i in a:(b-1)){
  y1 = y[i+1]
  y2 = y[i+2]
  if(y1==0 && y2==0){
    next
  }
  if(y1>=0 && y2 >=0){
    polygon(c(i,i,i+1,i+1),c(0,y1,y2,0),col=rgb(0,0,1,0.5),border=NA)
    text(i+0.5,max(c(y1,y2))+0.5,paste0("+",mean(c(y1,y2))),col="blue")
  } else {
    polygon(c(i,i,i+1,i+1),c(0,y1,y2,0),col=rgb(1,0,0,0.5),border=NA)
    text(i+0.5,min(c(y1,y2))-0.5,paste0("-",abs(mean(c(y1,y2)))),col="red")
  }
}


```
\

The definite integral represents the total signed area of $y=f(x)$ between $x=`r a`$ and $x=`r b`$.

$$\int_{`r a`}^{`r b`}f(x)\,dx = `r S`$$


Meta-information
============
extype: num
exsolution: `r S`
exname: graph_integ_net