```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)

x = sort(c(sample(seq(2,8,2),3),10))
x = sort(c(-x,0,x))
y = sample(seq(-8,8,2),4)

ans = sample(1:3,1)
if(ans==1){
  eon = "even"
  degs = c(0,2)
  ans1 = "100"
  explain = "The graph has reflective symmetry over the $y$ axis."
  y = c(y[4:1],sample(c(-5:5,0,0,0,0,0,0),1),y)
}
if(ans==2){
  eon = "odd"
  degs = c(1,3)
  ans1 = "010"
  explain = "The graph has rotational symmetry around the origin."
  y = c(-y[4:1],0,y)
}
if(ans==3){
  eon = "neither"
  degs = sample(list(c(0,1),c(1,2),c(0,3)),1)[[1]]
  ans1 = "001"
  explain = "The graph has neither reflective nor rotational symmetry."
  y = c(y,0,y)
}
```



Question
========


This question is in regards to [even and odd functions](https://en.wikipedia.org/wiki/Even_and_odd_functions){target="_blank"}.

* A function $f$ is **even** if and only if $f(-x)=f(x)$ for all $x$. In an even function, *opposite inputs give equal outputs*. An even function has reflective symmetry over the vertical axis.
* A function $f$ is **odd** if and only if $f(-x)=-f(x)$ for all $x$. In an odd function, *opposite inputs give opposite outputs*. An odd function has rotational symmetry around the origin.
* A function can also be neither even nor odd.

A function $f$ is graphed below.

```{r,fig.dim=c(5,5),echo=FALSE}
par(pty="s")
plot(x,y,type="n",xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="f(x)",asp=1,pch=20,cex=2)
for(i in seq(-10,10,2)){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
abline(v=0,lwd=2)
abline(h=0,lwd=2)
xspline(x,y,shape=c(0,rep(-0.4,length(x)-2),0),border="blue",lwd=4)
```
\

Is the function's graph consistent with the function being even, odd, or neither?



Answerlist
--------

* Even
* Odd
* Neither


Solution
========

`r explain`

The function is `r eon`.


Meta-information
============
extype: schoice
exsolution: `r ans1`
exname: even_odd_neither_graph