```{r data generation, echo = FALSE, results = "hide"}
cf = sample(2:9,8,T)*sample(c(-1,1),8,T)
dg = 7:0
mkp = function(cf,dg){
    f = paste0("{",cf,"}x^{",dg,"}",collapse="+")
    f = gsub("+{-","-{",f,fixed=T)
    f = gsub("x^{1}","x",f,fixed=T)
    f = gsub("x^{0}","",f,fixed=T)
    return(f)
}

wo = sample(1:3,1)

m1 = rep(c(-1,1),4) #f(-x)
m2 = rep(-1,8) #-f(x)
m3 = rep(c(1,-1),4) #-f(-x)

f = mkp(cf,dg)
fn = mkp(cf*m1,dg)
nf = mkp(cf*m2,dg)
nfn = mkp(cf*m3,dg)

fs = c(fn,nf,nfn)

cor = paste0("g(x)~=~",fs[wo],collapse="")

ach = paste0("g(x)~=~",sample(fs))
sol = paste0(1*(cor==ach),collapse="")

g = fs[wo]

descs = c("horizontal reflections over the $y$ axis","vertical reflections over the $x$ axis","180° rotations around the origin")
desc = descs[wo]

eqs = c("f(-x)","-f(x)","-f(-x)")
cor_fx = eqs[wo]

wrd1 = c("the ODD powered","ALL","the EVEN powered")[wo]

```



Question
========

Let function $f$ be defined by the polynomial below.

$$f(x)=`r f`$$

Another function, $g$, is another polynomial. The two functions are `r desc`. Which equation describes function $g$?


Answerlist
--------

* $`r ach[1]`$
* $`r ach[2]`$
* $`r ach[3]`$


Solution
========

The two functions are `r desc`, this tells us that, for all values of $x$:

$$g(x)~=~`r cor_fx`$$

And thus, between $f(x)$ and $g(x)$, the sign changed on `r wrd1` terms.

$$`r cor`$$

```{r,echo=F,fig.dim=c(8,4)}
par(mfrow=c(1,2),mar=c(2,2,0,0))
x = seq(-1,1,0.01)
f = rep(0,length(x))
for(i in 1:length(cf)){
    f = f+cf[i]*x^dg[i]
}

nf = -f
fn = rev(f)
nfn = -fn

fys = list(fn,nf,nfn)
f2 = fys[[wo]]

exy = max(abs(f))

plot(x,f,"l",ylim=c(-exy,exy),col="blue",xlab="",ylab="")
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,f,col="blue",lwd=2)
lines(x,f2,col="red",lwd=2)
text(1,0,"x",adj=c(1.1,1.1))
text(0,exy,"y",adj=c(1.1,1.1))

plot(0,0,"n",axes=F,ann=F)
legend("left",c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=2)

```


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: poly_which_reflection