```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
cf = sample(c(-5,-4,-3,-2,2,3,4,5),4)
a = round(cf[1])
b = round(cf[2])
c = round(cf[3])
d = round(cf[4])
```



Question
========

```{python, echo = FALSE, results = "hide"}
from sympy import *
x,a = symbols("x a")
exp = int(r.a)*x**3+int(r.b)*x**2+int(r.c)*x+int(r.d)
lexp = latex(exp)
wexp2 = latex( -int(r.a)*a**3-int(r.b)*a**2-int(r.c)*a-int(r.d) )
wexp1 = latex( exp.subs(x,a) )
cexp = latex( int(r.a)*a**3-int(r.b)*a**2+int(r.c)*a-int(r.d) )
wexp3 = latex( exp.subs(x,-a) )
exps = [cexp,wexp1,wexp2,wexp3]
```

```{r,echo=FALSE}
exps = py$exps
rexps = sample(exps)
ans1 = paste0(1*(rexps==exps[1]),collapse="")
```

Let function $f$ be defined as follows:
$$f(x) ~=~ `r py$lexp`$$
Which of the following expressions is equivalent to $-f(-a)$?

Answerlist
--------

* $`r rexps[1]`$
* $`r rexps[2]`$
* $`r rexps[3]`$
* $`r rexps[4]`$


Solution
========

Substitute $-a$ for $x$ and multiply the whole expression by $(-1)$.

$$-f(-a) ~=~ `r py$cexp`$$

The shortcut is to recognize that only the quadratic (with $x^2$) and constant (the two EVEN powered terms) switch signs between $f(x)$ and $-f(-a)$.


Meta-information
============
extype: schoice
exsolution: `r ans1`
exname: neg_of_f_neg_a