---
output: pdf_document
params:
    rseed: 1
    showsol: true
    titex: "Practice"
urlcolor: blue
---

```{r,echo=F}
set.seed(params$rseed)
sols = numeric()
if(params$showsol){
    solstart = ""
    solend = "\\vfill"
    hidesolstart = "<!---"
    hidesolend = "-->"
} else {
    solstart = "<!---"
    solend = "-->"
    hidesolstart = ""
    hidesolend = ""
}
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

while(T){
    q1 = paste0("You've been given a graph of $y=f(x)$, with a few key points indicated. Please sketch $y=f^{-1}(x)$, where $f^{-1}$ is the **inverse** of $f$.")
    x1 = sort(sample(-9:9,4))
    y1 = sort(sample(-9:9,4),decreasing = sample(c(T,F),1))
    x1a = y1
    y1a = x1
    minabsslope = min(abs(diff(y1)/diff(x1)))
    maxabsslope = max(abs(diff(y1)/diff(x1)))
    
    if(max(x1)-min(x1)>7 && length(unique(diff(y1)/diff(x1)))>=3 && maxabsslope/minabsslope>4 && sum(x1==y1)==0 && sum(abs(diff(y1)/diff(x1))==1)==0){break}
}

while(T){
    q2 = paste0("You've been given part of $y=f(x)$. Sketch the other half to make $f$ **even**.")
    x2 = sort(c(0,sample(1:9,3)))
    y2 = sample(-9:9,4)
    x2a = -x2
    y2a = y2
    if(max(x2)>6 && length(unique(diff(y2)/diff(x2)))>=3){break}
}

while(T){
    q3 = paste0("You've been given part of $y=f(x)$. Sketch the other half to make $f$ **odd**.")
    x3 = sort(c(0,sample(1:9,3)))
    y3 = c(0,sample(-9:9,3))
    x3a = -x3
    y3a = -y3
    if(max(x3)>6 && length(unique(diff(y3)/diff(x3)))>=3){break}
}

qs = c(q1,q2,q3)
xs = list(x1,x2,x3)
ys = list(y1,y2,y3)
xas = list(x1a,x2a,x3a)
yas = list(y1a,y2a,y3a)

myord = sample(1:3)


makeit = function(xx,yy){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in -10:10){
        if(i%%5==0){
            abline(h=i,col="darkgrey",lwd=1.2)
            abline(v=i,col="darkgrey",lwd=1.2)
        } else {
            abline(h=i,col="lightgrey")
            abline(v=i,col="lightgrey")
        }
    }
    arrows(-10.3,0,10.3,0,0.1,10,3,lwd=2)
    arrows(0,-10.3,0,10.3,0.1,10,3,lwd=2)
    text(10,-0.5,"10",cex=0.6)
    text(-10,-0.5,"-10",cex=0.6)
    text(10,0.5,"x",cex=0.6)
    text(-0.3,10,"10",cex=0.6,adj=1)
    text(-0.3,-10,"-10",cex=0.6,adj=1)
    text(0.3,10,"y",cex=0.6,adj=0)
    lines(xx,yy,col="blue",lwd=3)
    points(xx,yy,col="blue",pch=20,cex=1.5)
}

```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## Inverse, Even, Odd, Domain, Range `r params$titex` (version `r params$rseed`)



```{r,echo=F}
iii = myord[1]
```

1. `r qs[iii]`


```{r, echo=F, fig.dim=c(3.5,3.5)}
makeit(xs[[iii]],ys[[iii]])
if(params$showsol){
    lines(xas[[iii]],yas[[iii]],col="red",lwd=3)
    points(xas[[iii]],yas[[iii]],col="red",pch=20,cex=1.5)
}
```

\vfill


```{r,echo=F}
iii = myord[2]
```

2. `r qs[iii]`


```{r, echo=F, fig.dim=c(3.5,3.5)}
makeit(xs[[iii]],ys[[iii]])
if(params$showsol){
    lines(xas[[iii]],yas[[iii]],col="red",lwd=3)
    points(xas[[iii]],yas[[iii]],col="red",pch=20,cex=1.5)
}
```

\vfill

\newpage

## Inverse, Even, Odd, Domain, Range `r params$titex` (version `r params$rseed`)

```{r,echo=F}
iii = myord[3]
```

3. `r qs[iii]`

```{r, echo=F, fig.dim=c(3.5,3.5)}
makeit(xs[[iii]],ys[[iii]])
if(params$showsol){
    lines(xas[[iii]],yas[[iii]],col="red",lwd=3)
    points(xas[[iii]],yas[[iii]],col="red",pch=20,cex=1.5)
}
```

\vfill

4. Find the domain and range of the function shown below.

```{r,echo=F,fig.dim=c(3.5,3.5)}
while(T){
    x4 = sort(sample(-9:9,5))
    y4 = sample(-9:9,5)
    dlo = min(x4)
    dhi = max(x4)
    rlo = min(y4)
    rhi = max(y4)
    if(length(unique(c(dlo,dhi,rlo,rhi)))==4){break}
}
makeit(x4,y4)
if(params$showsol){
    polygon(c(dlo,dlo,dhi,dhi),c(rlo,rhi,rhi,rlo),border="red",lty = 3,lwd=3)
    lines(c(dlo,dlo,dlo,dhi,dhi,dhi),c(-0.5,0.5,0,0,-0.5,0.5),col="red",lwd=3)
    lines(c(-0.5,0.5,0,0,-0.5,0.5),c(rlo,rlo,rlo,rhi,rhi,rhi),col="red",lwd=3)
}
```
`r solstart`Domain= $[`r dlo`, `r dhi`]$ \hfill Range= $[`r rlo`, `r rhi`]$\newline Note: you do NOT need to draw lines on this last graph. You can just give domain and range.
`r solend`


