```{r,echo=F}

mu = sample(4:16,1)*50
sig = sample(c(2,5,10,15,20,25,30,40,50),1) #round(runif(1,10,120),-1)/2

zs = sort(sample(-3:3,2))
vals = mu+zs*sig

sol = round(pnorm(zs[2])-pnorm(zs[1]),2)
solex = pnorm(zs[2])-pnorm(zs[1])
```



Question
========

The figure below summarizes the [empirical rule](https://en.wikipedia.org/wiki/68%E2%80%9395%E2%80%9399.7_rule). If a normally-distributed population has a mean length of $\mu=`r mu`$ cm and a standard deviation of $\sigma=`r sig`$ cm, then what is the probability an individual has a length between `r vals[1]` cm and `r vals[2]` cm?

The tolerance is $\pm 0.01$ cm.

```{r echo=F,fig.width=8,fig.height=4}
z = seq(-3,3,0.01)
yl = seq(0,0.4,0.05)
zl = seq(-3,3,0.2)
plot(z,dnorm(z),type="l",axes=F,ylab="density",xlab="measurement",lwd=4,ylim=c(0,0.5))
axis(1,at=(-3):3,labels=c(expression(mu-3*sigma),expression(mu-2*sigma),expression(mu-sigma),
                          expression(mu),expression(mu+sigma),expression(mu+2*sigma),
                          expression(mu+3*sigma)))
abline(h=0)
for(z in (-3):3){
  lines(c(z,z),c(0,dnorm(z)))
}
for(z in zl){
  lines(c(z,z),c(0,0.4),lty=3,col=rgb(0.5,0.5,0.5))
}
for(y in yl){
  lines(c(-3,3),c(y,y),lty=3,col=rgb(0.5,0.5,0.5))
}
cols = c(rgb(0,0,0.5,0.4),rgb(0,0.5,0,0.4),rgb(0.5,0,0,0.4),rgb(0,0.5,0.5,0.4),rgb(0.5,0.5,0,0.4),rgb(0.5,0,0.5,0.4))
col2 = c(rgb(0,0,0.3),rgb(0,0.3,0),rgb(0.3,0,0),rgb(0,0.3,0.3),rgb(0.3,0.3,0),rgb(0.3,0,0.3))

for(i in (-3):2){
  zz = seq(i,i+1,0.01)
  polygon(c(i,zz,i+1),c(0,dnorm(zz),0),col=cols[i+4])
  text(i+0.5,0.225,round(pnorm(i+1)-pnorm(i),3),col=col2[i+4],cex=1.6)
}

lines(z,dnorm(z),lwd=4)

lines(c(-1,-1,1,1),c(0.42,0.43,0.43,0.42))
text(0,0.45,round(pnorm(1),3)-round(pnorm(-1),3))
lines(c(-2,-2,2,2),c(0.47,0.48,0.48,0.47))
text(0,0.50,round(pnorm(2),3)-round(pnorm(-2),3))
```
\

Solution
========

Fill in the values in the diagram.

```{r echo=F,fig.width=8,fig.height=4}
z = seq(-3,3,0.01)
yl = seq(0,0.4,0.05)
zl = seq(-3,3,0.2)
plot(z,dnorm(z),type="l",axes=F,ylab="density",xlab="length (cm)",lwd=4,ylim=c(0,0.5))
axis(1,at=(-3):3,labels=mu+(-3:3)*sig)
abline(h=0)
for(z in (-3):3){
  lines(c(z,z),c(0,dnorm(z)))
}
for(z in zl){
  lines(c(z,z),c(0,0.4),lty=3,col=rgb(0.5,0.5,0.5))
}
for(y in yl){
  lines(c(-3,3),c(y,y),lty=3,col=rgb(0.5,0.5,0.5))
}
cols = c(rgb(0,0,0.5,0.4),rgb(0,0.5,0,0.4),rgb(0.5,0,0,0.4),rgb(0,0.5,0.5,0.4),rgb(0.5,0.5,0,0.4),rgb(0.5,0,0.5,0.4))
col2 = c(rgb(0,0,0.3),rgb(0,0.3,0),rgb(0.3,0,0),rgb(0,0.3,0.3),rgb(0.3,0.3,0),rgb(0.3,0,0.3))

for(i in zs[1]:(zs[2]-1)){
  zz = seq(i,i+1,0.01)
  polygon(c(i,zz,i+1),c(0,dnorm(zz),0),col=cols[i+4])
  text(i+0.5,0.225,round(pnorm(i+1)-pnorm(i),3),col=col2[i+4],cex=1.6)
}

lines(z,dnorm(z),lwd=4)

lines(c(-1,-1,1,1),c(0.42,0.43,0.43,0.42))
text(0,0.45,round(pnorm(1),3)-round(pnorm(-1),3))
lines(c(-2,-2,2,2),c(0.47,0.48,0.48,0.47))
text(0,0.50,round(pnorm(2),3)-round(pnorm(-2),3))
```
\

You can find the $z$ scores if that is helpful.

$$z_1 ~=~ \frac{`r vals[1]`-`r mu`}{`r sig`} ~=~ `r zs[1]`$$
$$z_2 ~=~ \frac{`r vals[2]`-`r mu`}{`r sig`} ~=~ `r zs[2]`$$


Add up the areas.

$$P(`r vals[1]`\le X \le `r vals[2]`) ~=~ P(`r zs[1]`\le Z \le `r zs[2]`) ~\approx~ `r sol`$$



Meta-information
============
extype: num
exsolution: `r solex`
exname: empirical_rule
extol: 0.01