```{r,echo=F}
roundnum = 3
a = sample(2:9,1)
b = sample(-1:-13,1)
A = round(log10(a),roundnum)
```

Question
========

In Chemistry, the pH is used to measure the acidity of a solution. The pH is calculated from the concentration of hydrogen ions (in moles per liter).

$$\mathrm{pH} = -\log_{10}\big(\left[\mathrm{H^{+}}\right]\big)$$

The table below lists the (rounded) base-10 logarithm of integers between 1 and 9.

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab2, results="asis", echo=F}
mydf2 = data.frame(1:9,round(log10(1:9),roundnum))
colnames(mydf2) = c("$x$","$\\log_{10}(x)$")
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

If the concentration of hydrogen ions is $\left[\mathrm{H^{+}}\right]=`r a`\cdot 10^{`r b`}$ moles per liter, what is the pH? Please use the table, and do not round your answer any more than the table already has.


Solution
========

Plug that concentration into the pH formula.

$$\mathrm{pH} = -\log_{10}\left(`r a`\cdot 10^{`r b`}\right)$$

Remember that a log of a product equals a sum of logs.

$$\mathrm{pH} = -\left(\log_{10}(`r a`)+\log_{10}\left(10^{`r b`}\right)\right)$$

Use that table. Also, $\log_{10}(10^p)\equiv p$ for all $p$. So,

$$\mathrm{pH} = -\left(`r A`+(`r b`)\right)$$

Distribute the negative.

$$\mathrm{pH} = -`r A`+`r -b`$$

Evaluate $`r -b`-`r A`$.

$$\mathrm{pH} = `r -A-b`$$



Meta-information
============
extype: num
exsolution: `r -A-b`
exname: pH