```{r,echo=F}
isind = sample(c(T,F),1)

while(T){
  x = sample(3:50,4)
  anb = x[1]
  nab = x[2]
  ab = x[3]
  nanb = x[4]
  N = sum(x)
  PA = (anb+ab)/N
  PB = (nab+ab)/N
  PAnB = ab/N
  PAuB = (anb+nab+ab)/N
  PAgB = (ab)/(ab+nab)
  PBgA = (ab)/(ab+anb)
  answers = c(PA,PB,PAnB,PAuB,PAgB,PBgA)
  aln = sort(unique(answers))
  if(length(aln)<6){
    others = c(min(c(anb,nab))/max(c(anb,nab)),
               nanb/N,
               anb/N,
               nab/N)
    aln = sort(c(aln,sample(others,6-length(aln))))
  }
  ii = (ab/(anb+ab) == (nab+ab)/sum(x))
  if(ii == isind && min(diff(aln))>0.02){
    break
  }
}
qs = c("$P(B)=$",
       "$P(C)=$",
       "$P(B\\cap C)=$",
       "$P(B\\cup C)=$",
       "$P(B|C)=$",
       "$P(C|B)=$")
ord = sample(1:6)

ql = paste0("* ",qs[ord]," ##ANSWER",1:6,"##\n",collapse="")
al = paste0("* ",aln,collapse="\n")

sol1 = paste0(1*(answers[ord[1]]==aln),collapse="")
sol2 = paste0(1*(answers[ord[2]]==aln),collapse="")
sol3 = paste0(1*(answers[ord[3]]==aln),collapse="")
sol4 = paste0(1*(answers[ord[4]]==aln),collapse="")
sol5 = paste0(1*(answers[ord[5]]==aln),collapse="")
sol6 = paste0(1*(answers[ord[6]]==aln),collapse="")

if(isind){
  sol7 = "10"
  statement = "So, yes, they are independent."
} else {
  sol7 = "01"
  statement = "So, no, they are not independent."
}


```

Question
========

In a school, there are `r sum(x)` students. Each student can be in bike club, crochet club, both, or neither. The amounts are represented in the Venn diagram below.

```{r,echo=F,fig.dim=c(8,4)}
par(mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-1,1),ylim=c(0,1),axes=F,ann=F)
th = seq(0,2*pi,pi/100)
polygon(0.4*cos(th)-0.2,0.4*sin(th)+0.5,col=rgb(1,0,0,0.5),border="red")
polygon(0.4*cos(th)+0.2,0.4*sin(th)+0.5,col=rgb(0,0,1,0.5),border="blue")
lines(c(-1,-1,1,1,-1),c(0,1,1,0,0))
text(-0.2,0.95,"bike",col="red",cex=2)
text(0.2,0.95,"crochet",col="blue",cex=2)
text(-0.4,0.5,anb,col="red",cex=2)
text(0,0.5,ab,col="black",cex=2)
text(0.4,0.5,nab,col="blue",cex=2)
text(0.8,0.5,nanb,cex=2)
```
\

Let $B$ represent the event that a randomly selected student is in bike club, and let $C$ represent the event that a random student is in crochet club.

`r ql`
* Are events $B$ and $C$ independent? ##ANSWER7##


Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
* Yes, B and C are independent.
* No, B and C are not independent.

Solution
========

The three symbols (and related concepts) we are learning are:

* [Intersection](https://en.wikipedia.org/wiki/Intersection_(set_theory)), [and](https://en.wikipedia.org/wiki/Logical_conjunction), $\cap$
* [Union](https://en.wikipedia.org/wiki/Union_(set_theory)), [or](https://en.wikipedia.org/wiki/Logical_disjunction), $\cup$
* [Conditional](https://en.wikipedia.org/wiki/Conditional_probability), given, $|$

To calculate the probabilities (in a more organized order):

* $P(B) = \frac{`r anb`+`r ab`}{`r N`} = `r PA`$
* $P(C) = \frac{`r nab`+`r ab`}{`r N`} = `r PB`$
* $P(B\cap C) = \frac{`r ab`}{`r N`} = `r PAnB`$
* $P(B\cup C) = \frac{`r anb`+`r ab`+`r nab`}{`r N`} = `r PAuB`$
* $P(B|C) = \frac{`r ab`}{`r ab`+`r nab`} = `r PAgB`$
* $P(C|B) = \frac{`r ab`}{`r ab`+`r anb`} = `r PBgA`$

The events are independent if and only if $P(B|C)~=~P(B)$. `r statement`



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`|`r sol6`|`r sol7`
exname: Venn_probs