```{r data generation, echo = FALSE, results = "hide"}
mu = runif(1,200,800)
sig = runif(1,10,70)
n = sample(8:12,1)
x = round(rnorm(n,mu,sig),1)
correct_val_1 = round(mean(x),1)
correct_val_2 = round(sd(x),1)
num_under_1 = sample(0:3,1)
num_under_2 = sample(0:3,1)
mults_1 = c(0,sample(-1:-5,num_under_1),sample(1:5,3-num_under_1))
mults_2 = c(0,sample(-1:-5,num_under_2),sample(1:5,3-num_under_2))
choices_1 = sort(correct_val_1+0.2*mults_1)
choices_2 = sort(correct_val_2+0.2*mults_2)
ans1 = paste0((choices_1==correct_val_1)*1,collapse="")
ans2 = paste0((choices_2==correct_val_2)*1,collapse="")
```


Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

A biologist investigated a population of turtles. They weighed turtles from a simple-random sample; those weights are shown below in grams.

```{r tab_data, echo=FALSE, results="asis"}
opts <- options(knitr.kable.NA = "")
mydf = data.frame(x)
colnames(mydf) = c("Turtle weights (g)")
knitr::kable(mydf,format="html", align = "c",row.names=F,table.attr='class="bordered-table"')
```
\

Find the sample mean, $\bar{x}$, and the sample standard deviation, $s$ (using Bessel's correction).

$\bar{x} =$ ##ANSWER1##

$s =$ ##ANSWER2##

Answerlist
--------
* `r choices_1[1]`
* `r choices_1[2]`
* `r choices_1[3]`
* `r choices_1[4]`
* `r choices_2[1]`
* `r choices_2[2]`
* `r choices_2[3]`
* `r choices_2[4]`

Solution
========

The correct answers were $\bar{x} = `r correct_val_1`$ and $s = `r correct_val_2`$

`r sd(x)`

Meta-information
================
extype: cloze
exclozetype: schoice|schoice
exsolution: `r ans1`|`r ans2`
exname: find sample mean and sample standard deviation
exshuffle: FALSE