```{r,echo=FALSE}
k = round(runif(1,0.001,0.05),3)
h0 = sample(3:7,1)*100
dt = 0.1
g = 9.81

t = c(0)
v = c(0)
h = c(h0)

for(i in 1:103){
  t = c(t,t[i]+dt)
  v = c(v,v[i]+(-g+k*v[i]^2)*dt)
  h = c(h,h[i]+v[i]*dt)
}
```


Question
========

When a object falls downward, its acceleration is influenced by two competing terms: gravity ($g$) and air resistance ($kv^2$). Notice air resistance is proportional to the square of velocity.

$$\frac{\Delta v}{\Delta t} = -g+kv^2$$

The coefficient $k$ depends on the shape of the object, the orientation of the object, the density of the object, and the density of the air.

Because the object is falling straight down, velocity is how fast the height is changing.

$$\frac{\Delta h}{\Delta t} = v$$

Let's set the parameters and initial values.

* Parameters:
  * $k = `r k`$ $\text{m}^{-1}$
  * $g = 9.81$ $\text{m/s}^2$
* Initial values:
  * $h(0) = `r h0`$ m
  * $v(0) = 0$ m/s
* Step size for Euler's method:
  * $\Delta t=0.1$ s

Using Euler's method, we can produce the first few rounds of the simulation.

<style>
table.brd td{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
}
table.brd th{
  border: 2px solid black;
  padding: 5px;
  text-align: center;
}
table.brd {
  border: 3px solid black;
}
</style>

<table class="brd">
  <tr>
    <th>$t$</th>
    <th>$v$</th>
    <th>$h$</th>
    <th>$\Delta t$</th>
    <th>$\Delta v ~=~ (-9.81+`r k`v^2)\cdot\Delta t$</th>
    <th>$\Delta h ~=~ v \cdot \Delta t$</th>
  </tr>
  <tr>
    <td>0</td>
    <td>0</td>
    <td>`r h0`</td>
    <td>0.1</td>
    <td>`r v[2]-v[1]`</td>
    <td>`r h[2]-h[1]`</td>
  </tr>
  <tr>
    <td>`r t[2]`</td>
    <td>`r v[2]`</td>
    <td>`r h[2]`</td>
    <td>0.1</td>
    <td>`r v[3]-v[2]`</td>
    <td>`r h[3]-h[2]`</td>
  </tr>
  <tr>
    <td>`r t[3]`</td>
    <td>`r v[3]`</td>
    <td>`r h[3]`</td>
    <td>0.1</td>
    <td>`r v[4]-v[3]`</td>
    <td>`r h[4]-h[3]`</td>
  </tr>
  <tr>
    <td>`r t[4]`</td>
    <td>`r v[4]`</td>
    <td>`r h[4]`</td>
    <td>0.1</td>
    <td>`r v[5]-v[4]`</td>
    <td>`r h[5]-h[4]`</td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
  </tr>
</table>

* Continue the simulation to estimate the height after 10 seconds. In other words, use Euler's method to find $h(10)$.

The tolerance is $\pm 0.01$ m.


Solution
========


```{r,fig.dim=c(6,6),echo=FALSE}
plot(t,h,type="l",ylab="height (m)",xlab="time (s)",main="Object falling with air resistance")
points(t[101],h[101])
text(t[101]-1.5,h[101],paste0("(10, ",round(h[101],4),")"))
```
\

<style>
table.sol td{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
}
table.sol td.fc{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
  background-color: #aaaaaa;
}
table.sol th{
  border: 2px solid black;
  padding: 5px;
  text-align: center;
  background-color: #aaaaaa;
}
table.sol {
  border: 3px solid black;
}

</style>

Formula view:

<table class="sol">
  <tr>
    <th> </th>
    <th>A</th> 
    <th>B</th>
    <th>C</th>
    <th>D</th>
    <th>E</th>
    <th>F</th>
  </tr>
  <tr>
    <td class="fc">1</td>
    <td> t </td>
    <td> v </td>
    <td> h </td>
    <td> dt </td>
    <td> dv </td>
    <td> dh </td>
  </tr>
  <tr>
    <td class="fc">2</td>
    <td> 0 </td>
    <td> 0 </td>
    <td> `r h0` </td>
    <td> 0.1 </td>
    <td> = (-9.81 + `r k` * B2^2) * D2</td>
    <td> = B2*D2</td>
  </tr>
  <tr>
    <td class="fc">3</td>
    <td> =A2+D2 </td>
    <td> =B2+E2 </td>
    <td> =C2+F2 </td>
    <td> 0.1 </td>
    <td> = (-9.81 + `r k` * B3^2) * D3</td>
    <td> = B3*D3</td>
  </tr>
  <tr>
    <td class="fc">4</td>
    <td> =A3+D3 </td>
    <td> =B3+E3 </td>
    <td> =C3+F3 </td>
    <td> 0.1 </td>
    <td> = (-9.81 + `r k` * B4^2) * D4</td>
    <td> = B4*D4</td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
  </tr>
  <tr>
    <td class="fc">101</td>
    <td> =A100+D100 </td>
    <td> =B100+E100 </td>
    <td> =C100+F100 </td>
    <td> 0.1 </td>
    <td> = (-9.81 + `r k` * B101^2) * D101</td>
    <td> = B101*C101</td>
  </tr>
  <tr>
    <td class="fc">102</td>
    <td> =A101+D101 </td>
    <td> =B101+E101 </td>
    <td> =C101+F101 </td>
    <td> 0.1 </td>
    <td> = (-9.81 + `r k` * B102^2) * D102</td>
    <td> = B102*C102</td>
  </tr>
</table>

Value view:

<table class="sol">
  <tr>
    <th> </th>
    <th>A</th> 
    <th>B</th>
    <th>C</th>
    <th>D</th>
    <th>E</th>
    <th>F</th>
  </tr>
  <tr>
    <td class="fc">1</td>
    <td> t </td>
    <td> v </td>
    <td> h </td>
    <td> dt </td>
    <td> dv </td>
    <td> dh </td>
  </tr>
  <tr>
    <td class="fc">2</td>
    <td> `r t[1]` </td>
    <td> `r v[1]` </td>
    <td> `r h[1]` </td>
    <td> 0.1 </td>
    <td> `r v[2]-v[1]` </td>
    <td> `r h[2]-h[1]`</td>
  </tr>
  <tr>
    <td class="fc">3</td>
    <td> `r t[2]` </td>
    <td> `r v[2]` </td>
    <td> `r h[2]` </td>
    <td> 0.1 </td>
    <td> `r v[3]-v[2]` </td>
    <td> `r h[3]-h[2]`</td>
  </tr>
  <tr>
    <td class="fc">4</td>
    <td> `r t[3]` </td>
    <td> `r v[3]` </td>
    <td> `r h[3]` </td>
    <td> 0.1 </td>
    <td> = `r v[4]-v[3]` </td>
    <td> = `r h[4]-h[3]`</td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
  </tr>
  <tr>
    <td class="fc">101</td>
    <td> `r t[100]` </td>
    <td> `r v[100]` </td>
    <td> `r h[100]` </td>
    <td> 0.1 </td>
    <td> `r v[101]-v[100]` </td>
    <td> `r h[101]-h[100]`</td>
  </tr>
  <tr>
    <td class="fc">102</td>
    <td> `r t[101]` </td>
    <td> `r v[101]` </td>
    <td> `r h[101]` </td>
    <td> 0.1 </td>
    <td> `r v[102]-v[101]` </td>
    <td> `r h[102]-h[101]`</td>
  </tr>
</table>



Meta-information
============
extype: num
exsolution: `r h[101]`
exname: eulers_method_falling
extol: 0.01