```{r,echo=FALSE}
while(T){
  m = round(runif(1,1.2,1.9),1)
  n = round(runif(1,0.1,0.3),1)
  p = round(runif(1,0.1,0.5),1)
  q = round(runif(1,0.3,0.9),1)
  B = sample(5:40,1)
  C = sample(1:4,1)
  t = 0
  dt = 0.1
  stillgood = T
  for(i in 1:101){
    B = c(B,B[i]+(m*B[i]-n*B[i]*C[i])*dt)
    C = c(C,C[i]+(p*B[i]*C[i]-q*C[i])*dt)
    t = c(t,t[i]+dt)
    if(is.nan(B[i+1]) || B[i+1]<1 || C[i+1]<1){
      stillgood=F
      break
    }
  }
  if(stillgood && B[101]<1000 && B[101]>1 && C[101]<1000 && C[101]>0.5 && max(B)>max(C)){break}
}

if(sample(1:2,1)==1){
  ch = "bunnies"
  sy = "b(10)"
  sol = B[101]
} else {
  ch = "coyotes"
  sy = "c(10)"
  sol = C[101]
}

```


Question
========

The [Lotka–Volterra equations](https://en.wikipedia.org/wiki/Lotka%E2%80%93Volterra_equations) are used to simulate population sizes of predators and prey in an area.

Let's say prey are bunnies and the predators are coyotes, and the following rate equations hold.

$$\frac{\Delta b}{\Delta t} = `r m` b-`r n`bc$$
$$\frac{\Delta c}{\Delta t} = `r p`bc-`r q`c$$

* Initial values:
  * $b(0)=`r B[1]`$ thousand bunnies
  * $c(0)=`r C[1]`$ thousand coyotes
* Euler's method step:
  * $\Delta t = `r dt`$ years
  
Use Euler's method to estimate the number of **`r ch`** (in thousands) after 10 years. The tolerance is $\pm 0.01$ thousand `r ch`.



Solution
========

```{r,echo=F,fig.dim=c(6,6)}
plot(t,B,type="l",ylim=c(0,max(c(B,C))),xlab="time (years)",ylab="pop count (thousands)",col="blue")
lines(t,C,col="red")
legend("bottom",c("bunnies","coyotes"),col=c("blue","red"),lty=c(1,1))
```

<style>
table.brd td{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
}
table.brd th{
  border: 2px solid black;
  padding: 5px;
  text-align: center;
}
table.brd {
  border: 3px solid black;
}
</style>

Use a spreadsheet with formulas. It should match these rows shown.

<table class="brd">
  <tr>
    <th>$t$</th>
    <th>$b$</th>
    <th>$c$</th>
    <th>$\Delta t$</th>
    <th>$\Delta b ~=~ (`r m` b-`r n`bc)\Delta t$</th>
    <th>$\Delta c ~=~ (`r p`bc-`r q`c)\Delta t$</th>
  </tr>
  <tr>
    <td>`r t[1]`</td>
    <td>`r B[1]`</td>
    <td>`r C[1]`</td>
    <td>`r t[2]-t[1]`</td>
    <td>`r B[2]-B[1]`</td>
    <td>`r C[2]-C[1]`</td>
  </tr>
  <tr>
    <td>`r t[2]`</td>
    <td>`r B[2]`</td>
    <td>`r C[2]`</td>
    <td>`r t[3]-t[2]`</td>
    <td>`r B[3]-B[2]`</td>
    <td>`r C[3]-C[2]`</td>
  </tr>
  <tr>
    <td>`r t[3]`</td>
    <td>`r B[3]`</td>
    <td>`r C[3]`</td>
    <td>`r t[4]-t[3]`</td>
    <td>`r B[4]-B[3]`</td>
    <td>`r C[4]-C[3]`</td>
  </tr>
  <tr>
    <td>`r t[4]`</td>
    <td>`r B[4]`</td>
    <td>`r C[4]`</td>
    <td>`r t[5]-t[4]`</td>
    <td>`r B[5]-B[4]`</td>
    <td>`r C[5]-C[4]`</td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
  </tr>
  <tr>
    <td>`r t[101]`</td>
    <td>`r B[101]`</td>
    <td>`r C[101]`</td>
    <td>`r t[102]-t[101]`</td>
    <td>`r B[102]-B[101]`</td>
    <td>`r C[102]-C[101]`</td>
  </tr>
</table>

So the answer is `r sol`, because there are `r sol` thousand `r ch` when $t=10$.

Meta-information
============
extype: num
exsolution: `r sol`
exname: eulers_method_pred_prey
extol: 0.01