```{r,echo=FALSE}
options(scipen=99)
isfinite = sample(c(F,T),1)
if(isfinite){
  mult = -1
  sol = "10"
  gl = "<"
  fi = "finite"
} else {
  mult = 1
  sol = "01"
  gl = ">"
  fi = "infinite"
}

NN = sample(2:8,1)
k = floor(100.0/NN)/100+sample(1:4,1)/100*mult
ths = seq(-pi/2+pi/(NN)/2,pi/2-pi/(NN)/2,pi/(NN))
d = ceiling(log(0.001,k))+1
xmin = 0
xmax = 0
ymin = 0 #-1
ymax = 0
x = list(0)
y = list(0)
t = list(pi/2)
l = 1
x1s = numeric() #c(0)
x2s = numeric() #c(0)
y1s = numeric() #c(-1)
y2s = numeric() #c(0)
for(i in 2:d){
  l = l*k
  for(j in 1:length(x[[i-1]])){
    xp = x[[i-1]][j]
    yp = y[[i-1]][j]
    tp = t[[i-1]][j]
    for(th in ths){
      tc = tp+th
      xc = xp+l*cos(tc)
      yc = yp+l*sin(tc)
      x1s = c(x1s,xp)
      x2s = c(x2s,xc)
      y1s = c(y1s,yp)
      y2s = c(y2s,yc)
      if(length(x)<i){
        x[[i]] = xc
        y[[i]] = yc
        t[[i]] = tc
      } else {
        x[[i]] = c(x[[i]],xc)
        y[[i]] = c(y[[i]],yc)
        t[[i]] = c(t[[i]],tc)
      }
      if(xc<xmin){
        xmin = xc
      }
      if(xc>xmax){
        xmax = xc
      }
      if(yc<ymin){
        ymin = yc
      }
      if(yc>ymax){
        ymax = yc
      }
    }
  }
}
xrange = xmax-xmin
yrange = ymax-ymin
xmid = (xmin+xmax)/2
ymid = (ymin+ymax)/2
rad = max(c(xrange,yrange))/2
```

Question
========

```{r,fig.dim=c(6,6),echo=FALSE}
par(mar=c(0,0,0,0))
plot(0,0,type="n",
     xlim=c(xmid-rad,xmid+rad),
     ylim=c(ymid-rad,ymid+rad),ann=F,axes=F)
for(i in 1:length(x1s)){
  lines(c(x1s[i],x2s[i]),c(y1s[i],y2s[i]))
}
```
\

The fractal above is composed of many line segments. The largest `r NN` segments are each 1 unit long. There are then `r NN^2` segments, each with a length of $k = `r k`$. To continue the pattern, there are `r NN^3` segments with length $k^2=`r k^2`$. Then, `r NN^4` segments with length $k^3$ and `r NN^5` with length $k^4$ etc...

Is the sum of the lengths finite or infinite?

Answerlist
--------

* Finite
* Infinite

Solution
========

This summation is a [geometric series](https://en.wikipedia.org/wiki/Geometric_series). In general, if $|r|<1$ then

$$a + ar + ar^2 +ar^3 + ar^4 +\ldots + ar^{\infty} ~=~ \frac{a}{1-r} $$

In our case, $a=`r NN`$ and $r=`r NN*k`$. Notice, to calculate the common ratio $r$, we multiply the [branching number](https://en.wikipedia.org/wiki/Branching_factor) (`r NN`) by the scaling factor ($k=`r k`$).

Because $|r| `r gl` 1$, the sum is `r fi`

Meta-information
============
extype: schoice
exsolution: `r sol`
exname: fractal_lines_finite_inf