---
header-includes:
   - \usepackage{array}
   - \usepackage{color}
output: pdf_document
params:
    rseed: 1
    useseed: false
    showsol: true
    titex: "Practice"
urlcolor: blue
---

```{r,echo=F}
if(params$useseed){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = F)
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## s19 Matrix Exam (`r params$titex` v`r params$rseed`)


```{r}
### Question 1
while(T){
    picks = sample(1:10)
    x1 = picks[1]
    y1 = picks[2]
    x2 = picks[3]
    y2 = picks[4]
    detA = x1*y2-x2*y1
    if(detA>4 && (x1+x2)<=10 && (y1+y2)<=10){break}
}


```

Let the $2\times 4$ matrix $U$ represent four points in the $xy$-plane (so each column represents a point). When those four points are connected as a convex polygon, matrix $U$ represents a unit square. Also, let the $2\times 2$ matrix $L$ represent a linear transformation. 

$$\begin{aligned}
U~&=~\begin{bmatrix}
0 & 1 & 1 & 0\\
0 & 0 & 1 & 1
\end{bmatrix} & ~&~&
L=\begin{bmatrix}
`r x1` & `r x2` \\
`r y1` & `r y2`
\end{bmatrix}
\end{aligned}$$

Let matrix $P=L\cdot U$, so $P$ is found by matrix multiplication of $L$ times $U$. Matrix $P$ also represents 4 points of a polygon. Use the diagram below to calculate the elements of $P$. Then, draw the polygon represented by matrix $P$ on the $xy$-plane below. Notice I have already drawn the unit square represented by matrix $U$.

```{r}
nr = 4
nc = 6
U = matrix(c(0,1,1,0,0,0,1,1),2,byrow = T)
L = matrix(c(x1,x2,y1,y2),2,byrow=T)
P = L %*% U
```

1. Multiply $L\cdot U$ and draw resulting polygon.

```{r,echo=F,fig.dim=c(2.5,4)}
par(mar=c(0,0,0,0))
hi = 2.5/(nc+1)*(nr+1)
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(-4+hi,nr+1),asp=1,axes=F,ann=F)

nf = 2
np = 2
ns = 4

clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
for(i in 1:nf){
    # polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
    #         c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),
    #         col=F, #clrs[i],
    #         border = T)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
}

for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,L[i,j])
    }
}

for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,U[i,j])
    }
}

if(params$showsol){
    for(i in 1:np){
        for(j in 1:ns){
            text(nf+j,np+1-i,P[i,j],col="red")
        }
    }
}


for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(nf+0.5,nf+0.5),c(np,0)+0.5,lwd=3)
lines(c(nf+0.5,nf+ns+0.5),c(np,np)+0.5,lwd=3)
#####

#####

####
```
```{r,fig.dim=c(4,4)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,10),ylim=c(0,10))
for(i in 0:10){
    lines(c(0,10),c(i,i),col="grey")
    lines(c(i,i),c(0,10),col="grey")
}
for(i in c(5,10)){
    lines(c(0,10),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(0,10),col="darkgrey",lwd=1.2)
}
abline(h=0,lwd=1.5)
abline(v=0,lwd=1.5)

for(i in 1:4){
    points(U[1,i],U[2,i],pch=19)
}
polygon(U[1,1:4],U[2,1:4],lwd=2,col=rgb(0,0,0,0.05))
text(10,-0.2,"x")
text(-0.2,10,"y")

if(params$showsol){
    polygon(P[1,1:4],P[2,1:4],lwd=2,border="red",col=rgb(1,0,0,0.2))
    points(P[1,],P[2,],pch=19,col="red")
}

```

2. What is the area of the convex polygon represented by matrix $P$? *Hint: the area equals the absolute value of the determinant of matrix $L$.*

```{r,eval=params$showsol,results='asis'}
cat("\\color{red}\n")
cat(paste0("$$\\mathrm{area}~=~\\det(L)~=~(",x1,"\\cdot",y2,")-(",x2,"\\cdot",y1,")$$\n",collapse=""))
cat(paste0("$$\\mathrm{area}~=~",det(L),"$$\n\n",collapse=""))
cat("\\color{black}")
```



\newpage

```{r}
# Question 3
while(T){
    A = matrix(sample(c(0,5,10),6,T),2)
    ds = sqrt(A[1,]^2+A[2,]^2)
    detter = (A[1,2]-A[1,1])*(A[2,3]-A[2,1])-(A[1,3]-A[1,1])*(A[2,2]-A[2,1])
    if(max(ds)<=15 && abs(detter)>0 && min(ds)>0){break}
}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
thc = atan(3/4)
wt = sample(1:3,1)
if(wt == 1){
    rf = matrix(c(-1,0,0,1),2) #reflect over y axis
    wrds = paste0("reflect over the $y$ axis")
}
if(wt == 2){
    rf = matrix(c(1,0,0,-1),2) #reflect over y axis
    wrds = paste0("reflect over the $x$ axis")
}
if(wt == 3){
    rf = matrix(c(-1,0,0,-1),2) #reflect over y axis
    wrds = paste0("reflect over the $x$ axis, reflect over the $y$ axis,")
}
while(T){
        th = sample(0:3,1)*pi/2+sample(c(atan(3/4),atan(4/3)),1)
        ro = matrix(c(cos(th),sin(th),-sin(th),cos(th)),2)
        R = ro %*% rf
        B = round(R %*% A,4)
        mins = c(min(sign(B[,1])),min(sign(B[,2])),min(sign(B[,3])))
        if(max(mins)<=0){
            break
        }
}
wrds2 = paste0("and then rotate by ",sprintf("%.02f",th/pi*180),"° counterclockwise")
```

The triangle shown below is composed of the three points represented by matrix $A = `r matpr(A)`$. In order to `r wrds` `r wrds2` we can multiply by the transformation matrix $R=`r matpr(R)`$.

3. Calculate the matrix $R\cdot A$.

```{r}
nc = 5
nr = 4
np = 2
nf = 2
ns = 3
```

```{r,eval=F,fig.dim=c(2,2/(nc+1)*(nr+1)),fig.align='center'}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(0,nr+1),asp=1,axes=F,ann=F)
clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2),rgb(0.2,0.3,0.8,0.2))
for(i in 1:nf){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),
            col=F, #clrs[i],
            border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
    # text((xt1+xt2)/2,(yt1+yt2)/2,foods[i],srt=srt,cex=0.8)
}


for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,R[i,j],col="red")
    }
}

for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,sprintf("%d",A[i,j]),col="red")
    }
}


for(i in 1:np){
    for(j in 1:ns){
        text(nf+j,np+1-i,B[i,j],col="red")
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(nf+0.5,nf+0.5),c(np,0)+0.5,lwd=3)
lines(c(nf+0.5,nf+ns+0.5),c(np,np)+0.5,lwd=3)
```

```{r,eval=params$showsol,results='asis'}
cat("\\color{red}\n")
cat(paste0("$$R\\cdot A~=~",matpr(round(R%*%A,2)),"$$"))

cat("\\color{black}\n")
```

\vfill

4. Draw the triangle represented by $R\cdot A$.

```{r,fig.dim=c(5,5),fig.align='center'}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-15,15),ylim=c(-15,15))
for(i in -15:15){
    lines(c(-15,15),c(i,i),col="grey")
    lines(c(i,i),c(-15,15),col="grey")
}
for(i in seq(-15,15,5)){
    lines(c(-15,15),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(-15,15),col="darkgrey",lwd=1.2)
}
abline(h=0,lwd=1.5)
abline(v=0,lwd=1.5)
polygon(A[1,],A[2,],lwd=2,col=rgb(0,0,0,0.1))
points(A[1,],A[2,],pch=19)

if(params$showsol){
    polygon(B[1,],B[2,],lwd=2,col=rgb(1,0,0,0.1),border="red")
    points(B[1,],B[2,],pch=19,col="red")
}

text(15.5,-0.5,"x")
text(-0.5,15.5,"y")

```




