```{r,echo=FALSE}

while(T){
    roots = round(sort(runif(2,10,90)),1)
    wid = (roots[2]-roots[1])/2
    k = -abs(wid)
    h = mean(roots)
    r = roots[1]
    s = roots[2]
    if(abs(diff(roots))>10 && h-2*wid<0 && h%%0.1==0){break}
}


# # y = a*(x-h)^2+k
# # y = ax^2 - 2ahx + ah^2+k
# 
# # y = a(x-r)(x-s)
# # y = a(x^2-(r+s)x+rs)
# # y = ax^2 - a(r+s)x + ars
# 
# # ah^2+k = ars
# # a = -k/(h^2-rs)
# # a = k/(rs-h^2)

a = k/(r*s-h^2)

hposs = (sample(-4:0,1)+0:4)*0.3+h

achx = paste0("$x=",sprintf("%0.1f",hposs),"$")
achy = paste0("$y=",sprintf("%0.1f",hposs),"$")

cch = paste0("$x=",sprintf("%0.1f",h),"$")

ach = as.vector(rbind(achx,achy))
sol = paste0(1*(ach==cch),collapse="")
al = paste0("* ",ach,collapse="\n")


```


Question
========

A [quadratic function](https://en.wikipedia.org/wiki/Quadratic_function) is graphed below. Notice the curve is a [parabola](https://en.wikipedia.org/wiki/Parabola) with a vertical axis of symmetry and roots at $`r sprintf("%.1f",roots[1])`$ and $`r sprintf("%.1f",roots[2])`$ .


```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(1,1,1,1),pty="s")
plot(0,0,"n",xlim=c(h-2*wid,h+2*wid),ylim=c(-2*wid,2*wid),axes=F,ann=F)

abline(h=0,lwd=2,col="darkgrey")
abline(v=0,lwd=2,col="darkgrey")

x = seq(h-2*wid,h+2*wid,wid/100)
y = a*(x-h)^2+k

lines(x,y,col="blue",lwd=3)
points(roots,c(0,0),col="red",pch=19)
text(roots[1],0,paste0("(",sprintf("%0.1f",roots[1]),", 0)"),col="red",adj=c(1.1,1.4),cex=1.3)
text(roots[2],0,paste0("(",sprintf("%0.1f",roots[2]),", 0)"),col="red",adj=c(-0.1,1.4),cex=1.3)

abline(v=h,lty=2,col="purple")
text(h,wid,"Axis of Symmetry",srt=90,col="purple",adj=c(0.5,-0.5))
# text(h,wid,"x = h",srt=90,col="purple",adj=c(0.5,1.5))

points(h,k,col="purple",pch=19)
text(h,k,"(h,k)",adj=c(-0.1,1.4),col="purple",cex=1.3)

```
\

What is the equation for the axis of symmetry?


Answerlist
--------

`r al`


Solution
========

You can simply find the [mean](https://en.wikipedia.org/wiki/Arithmetic_mean) of the two roots.

$$h=\frac{`r sprintf("%0.1f",roots[1])`+`r sprintf("%0.1f",roots[2])`}{2}$$


$$h=`r sprintf("%0.2f",h)`$$

The axis of symmetry is a vertical line, so it is represented by an equation in which $x$ equals a constant.

$$\text{Axis of Symmetry:}~~~x=`r sprintf("%.1f",h)`$$



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: quad_LOS_from_roots_B