```{r,echo=FALSE}
options(scipen=999)

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}


addorsub = function(x){
    if(x<0){
        return(paste0("-",abs(x),collapse=""))
    } else {
        return(paste0("+",abs(x),collapse=""))
    }
}

while(T){
    abc = sample(2:12,3)*sample(c(-1,1),3,T)
    a = abc[1]
    b = abc[2]
    c = abc[3]
    if(b^2-4*a*c>0){
        x1 = -b/2/a-abs(sqrt(b^2-4*a*c)/2/a)
        x2 = -b/2/a+abs(sqrt(b^2-4*a*c)/2/a)
        xm = -b/2/a-sqrt(b^2-4*a*c)/2/a
        xp = -b/2/a+sqrt(b^2-4*a*c)/2/a
        if(abs(x2-x1)>0.4 && abs(x1)>0.01 && abs(x2)>0.01 && abs(x1)<100 && abs(x2)<100 && !(x1%%1==0) && !(x2%%1==0)){break}
    }
}

ach1 = round(x1+(sample(-4:0,1)+0:4)*0.03,2)
ach2 = round(x2+(sample(-4:0,1)+0:4)*0.03,2)

x1r = round(x1,2)
x2r = round(x2,2)

al1 = paste0("* ",sprintf("%0.2f",ach1),collapse="\n")
al2 = paste0("* ",sprintf("%0.2f",ach2),collapse="\n")

sol1 = paste0(1*(ach1==x1r),collapse="")
sol2 = paste0(1*(ach2==x2r),collapse="")

```


Question
========


Consider the quadratic function defined below:

$$f(x)~=~`r pn(abc,2:0)`$$

When we graph $y=f(x)$, we see there are two [roots](https://en.wikipedia.org/wiki/Zero_of_a_function) at $(r,0)$ and $(s,0)$. (The word "roots" means the same thing as "$x$-intercepts" or "zeros".)

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(4,4,1,1))
wid = abs(sqrt(b^2-4*a*c)/2/a)
mid = -b/2/a

k = a*mid^2+b*mid+c

plot(0,0,"n",xlim=c(mid-2*wid,mid+2*wid),ylim=c(-2*abs(k),2*abs(k)),xlab="x",ylab="y")

abline(h=0,lwd=2)
abline(v=0,lwd=2)

xs = seq(mid-2*wid,mid+2*wid,wid/100)
ys = a*xs^2+b*xs+c

lines(xs,ys,col="blue",lwd=3)

points(x1,0,pch=19,col="red")
points(x2,0,pch=19,col="red")

text(x1,0,"(r,0)",adj=c(0.5+0.6,sign(a)+0.5),col="red",cex=1.5)
text(x2,0,"(s,0)",adj=c(0.5-0.6,sign(a)+0.5),col="red",cex=1.5)

```
\

By using the [quadratic formula](https://en.wikipedia.org/wiki/Quadratic_formula), find the roots.

* $r=$ ##ANSWER1##
* $s=$ ##ANSWER2##



Answerlist
--------


`r al1`
`r al2`


Solution
========

Identify the parameters.

* The quadratic coefficient: $a=`r a`$
* The linear coefficient: $b=`r b`$
* The constant: $c=`r c`$

The $x$-intercepts of a function are found by solving for $x$ when $f(x)=0$.

$$`r pn(abc,2:0)`=0$$

Use the quadratic formula to solve the equation.

$$x~=~\frac{-(`r b`)\pm \sqrt{(`r b`)^2-4(`r a`)(`r c`)}}{2(`r a`)}$$

Simplify.



$$x~=~\frac{`r -b`\pm \sqrt{`r b^2` `r addorsub(-4*a*c)`}}{`r 2*a`}$$

Simplify MORE.

$$x~=~\frac{`r -b`\pm \sqrt{`r b^2-4*a*c`}}{`r 2*a`}$$

Now, plug both expressions into a calculator.


$$x~=~\frac{`r -b`- \sqrt{`r b^2-4*a*c`}}{`r 2*a`}~=~`r xm` ~\approx `r sprintf("%0.2f",xm)`$$

OR 

$$x~=~\frac{`r -b`+ \sqrt{`r b^2-4*a*c`}}{`r 2*a`}~=~`r xp` ~\approx  `r sprintf("%0.2f",xp)`$$

So, $r=`r x1`$ and $s=`r x2`$.



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: quad_formula_roots