```{r,echo=FALSE}
options(scipen=999)
gcd2 <- function(a, b) {
    if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

pfix = function(c,d){
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

x = sample(10:40,1)
y = 2*x
tot = 4*x

```


Question
========

Amelia will use `r tot` feet of fence to build a rectangular enclosure for her dog. Amelia will build the enclosure next to a very long barn, so she'll only use the fencing for 3 of the sides of the rectangle.

Let $x$ represent the length of fence perpendicular to the barn, and let $y$ represent the length of fence parallel to the barn.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
polygon(c(0,0.2,0.2,0),c(0,0,1,1),col="red")
polygon(c(1,0.2,0.2,1),c(0,0,1,1),col=rgb(0.2,0.9,0.2))
text(0.1,0.5,"BARN",col=rgb(0.6,0,0),srt=90,cex=2)
lines(c(0.2,0.5,0.5,0.2),c(0.3,0.3,0.7,0.7),lwd=5,col="black")
text(0.35,0.7,"x",adj=c(0.5,-0.2),cex=2)
text(0.35,0.3,"x",adj=c(0.5,1.2),cex=2)
text(0.5,0.5,"y",adj=c(-0.4,0.5),cex=2)

```
\

She wants to give her dog as much area as possible. Find the value of $x$ that maximizes the area.

Solution
========

The total length of fence is `r tot` feet. There are 2 sides with lengths of $x$ and one side with a length of $y$.

$$2x+y~=~`r tot`$$

Solve for $y$.

$$y~=~`r tot`-2x$$

Write an equation for the area. A rectangular area equals the length times the width.

$$A~=~xy$$

Substitute $`r tot`-2x$ in place of $y$ to get area in terms of only $x$.


$$A~=~x(`r tot`-2x)$$

From here, there are a few different approaches. We can further factor to see the zeros, and then recognize the maximum occurs halfway between the zeros (because a parabola is symmetric). Or, we can expand into standard form, and use the formula $h=\frac{-b}{2a}$ to find the vertex.


### Method 1: factor to find zeros

Notice that both `r tot` and 2 are multiples of 2. Factor out a constant of 2.

$$A~=~2x(`r 2*x`-x)$$

Using the zero-product property, we know the area has zeros at $x=0$ and $x=`r 2*x`$. The maximum occurs halfway between the zeros, because the parabola is symmetric, so the maximum area happens when $x=`r x`$.

### Method 2, expand to standard form and use formula

Let's return to the area function in terms of $x$.

$$A~=~x(`r tot`-2x)$$

Expand into standard form.

$$A~=~-2x^2+`r 2*tot`x$$



Meta-information
============
extype: num
exsolution: `r x`
exname: factor_quadratic