---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

Name: \vspace{5pt} \hrule

## p1029: Box multiplication of linear binomials (v`r params$rseed`)

```{r,echo=F}
if(params$rseed !=0){
    set.seed(params$rseed)
}

pn = function(coeffs,pows){
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    return(ex1)
}

```

## Example

Use the box method to multiply $(6x+3)$ and $(2x+4)$.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)

lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,"6x")
text(5,7,3)
text(1,5,"2x")
text(1,3,4)
text(1,7,"*")

text(3,5,TeX("$12x^2$"),col="red")
text(5,5,"6x",col="red")
text(3,3,"24x",col="red")
text(5,3,"12",col="red")

text(7.2,6,TeX("$12x^2+6x+24x+12$"),col="red")

text(7.2,4.6,"Combine",col="red")
text(7.2,4,"like",col="red")
text(7.2,3.4,"terms.",col="red")

text(7.2,2,TeX("$12x^2+30x+12$"),col="red")

tots = c("12x^2+30x+12")

```

ANSWER: \color{red} $12x^2+30x+12$ \color{black}


\vfill

## Question 1

```{r,echo=F}
while(T){
    digits = sample(2:9,4)
    A = digits[1]
    B = digits[2]
    C = digits[3]
    D = digits[4]
    exp1 = pn(c(A,B),1:0)
    exp2 = pn(c(C,D),1:0)
    a = A*C
    b = A*D+B*C
    c = B*D
    exp3 = pn(c(A*C,A*D,B*C,B*D),c(2,1,1,0))
    exp4 = pn(c(A*C,A*D+B*C,B*D),c(2,1,0))
    if(!(exp4%in%tots)){break}
}
tots = c(tots,exp4)

```

Use the box method to multiply $(`r exp1`)$ and $(`r exp2`)$.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)
lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,TeX(paste0("$",pn(A,1),"$")))
text(5,7,TeX(paste0("$",pn(B,0),"$")))
text(1,5,TeX(paste0("$",pn(C,1),"$")))
text(1,3,TeX(paste0("$",pn(D,0),"$")))
# text(1,1,"TOTAL")
# text(7,7,"TOTAL")

text(1,7,"*")

dasol = ""

if(params$showsol){
    text(3,5,TeX(paste0("$",A*C,"x^2$")),col="red")
    text(5,5,TeX(paste0("$",B*C,"x$")),col="red")
    text(3,3,TeX(paste0("$",A*D,"x$")),col="red")
    text(5,3,TeX(paste0("$",B*D,"$")),col="red")
    dasol = paste0("$",exp4,"$")
    
}

```

ANSWER: \color{red} `r dasol` \color{black}

\vfill

\newpage

## Question 2

```{r,echo=F}
while(T){
    digits = sample(2:9,4)*sample(c(-1,1),4,T)
    A = digits[1]
    B = digits[2]
    C = digits[3]
    D = digits[4]
    exp1 = pn(c(A,B),1:0)
    exp2 = pn(c(C,D),1:0)
    a = A*C
    b = A*D+B*C
    c = B*D
    exp3 = pn(c(A*C,A*D,B*C,B*D),c(2,1,1,0))
    exp4 = pn(c(A*C,A*D+B*C,B*D),c(2,1,0))
    if(!(exp4%in%tots) && length(unique(sign(digits)))==2){break}
}
tots = c(tots,exp4)

```

Use the box method to multiply $(`r exp1`)$ and $(`r exp2`)$.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)
lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,TeX(paste0("$",pn(A,1),"$")))
text(5,7,TeX(paste0("$",pn(B,0),"$")))
text(1,5,TeX(paste0("$",pn(C,1),"$")))
text(1,3,TeX(paste0("$",pn(D,0),"$")))
# text(1,1,"TOTAL")
# text(7,7,"TOTAL")

text(1,7,"*")

dasol = ""

if(params$showsol){
    text(3,5,TeX(paste0("$",A*C,"x^2$")),col="red")
    text(5,5,TeX(paste0("$",B*C,"x$")),col="red")
    text(3,3,TeX(paste0("$",A*D,"x$")),col="red")
    text(5,3,TeX(paste0("$",B*D,"$")),col="red")
    dasol = paste0("$",exp4,"$")
    
}

```

ANSWER: \color{red} `r dasol` \color{black}

\vfill

## Question 3

```{r,echo=F}
while(T){
    digits = sample(2:9,4)*sample(c(-1,1),4,T)
    A = digits[1]
    B = digits[2]
    C = digits[3]
    D = digits[4]
    exp1 = pn(c(A,B),1:0)
    exp2 = pn(c(C,D),1:0)
    a = A*C
    b = A*D+B*C
    c = B*D
    exp3 = pn(c(A*C,A*D,B*C,B*D),c(2,1,1,0))
    exp4 = pn(c(A*C,A*D+B*C,B*D),c(2,1,0))
    if(!(exp4%in%tots) && length(unique(sign(digits)))==2){break}
}
tots = c(tots,exp4)

```

Use the box method to multiply $(`r exp1`)$ and $(`r exp2`)$.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)
lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

# text(1,1,"TOTAL")
# text(7,7,"TOTAL")

text(1,7,"*")

dasol = ""

if(params$showsol){
    text(3,7,TeX(paste0("$",pn(A,1),"$")),col="red")
    text(5,7,TeX(paste0("$",pn(B,0),"$")),col="red")
    text(1,5,TeX(paste0("$",pn(C,1),"$")),col="red")
    text(1,3,TeX(paste0("$",pn(D,0),"$")),col="red")
    text(3,5,TeX(paste0("$",A*C,"x^2$")),col="red")
    text(5,5,TeX(paste0("$",B*C,"x$")),col="red")
    text(3,3,TeX(paste0("$",A*D,"x$")),col="red")
    text(5,3,TeX(paste0("$",B*D,"$")),col="red")
    dasol = paste0("$",exp4,"$")
    
}

```

ANSWER: \color{red} `r dasol` \color{black}

\vfill