---
output: slidy_presentation
---

# Sacred Example!

You are given a quadratic expression in factored form:
$$(6x+5)(7x-2)$$

Expand the expression into standard form using the **BOX** method.


# Expand with box method

Given factored form:

$$(6x+5)(7x-2)$$

Use box.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)

lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,"7x")
text(5,7,-2)
text(1,5,"6x")
text(1,3,5)
text(1,7,"*")

text(3,5,TeX("$42x^2$"),col="red")
text(5,5,"-12x",col="red")
text(3,3,"35x",col="red")
text(5,3,"-10",col="red")

text(7.2,6,TeX("$42x^2-12x+35x-10$"),col="red")

text(7.2,4.6,"Combine",col="red")
text(7.2,4,"like",col="red")
text(7.2,3.4,"terms.",col="red")

text(7.2,2,TeX("$42x^2+23x-10$"),col="red")


```

ANSWER: $$42x^2+23x-10$$

# Sacred Example Too!

You are given a quadratic expression in factored form:
$$(8x-3)(5x-2)$$

Expand the expression into standard form using the **FOIL** method.

# Expand with FOIL method

Given factored form:
$$(8x-3)(5x-2)$$

Use FOIL.

```{r,echo=F,fig.dim=c(6,2)}
A = 8
B = -3
C = 5
D = -2

pn = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

exp1 = pn(c(A,B),c(1,0))
exp2 = pn(c(C,D),c(1,0))

library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1,1),ylim=c(0,1),axes=F,ann=F)
simpex1 = paste0(A,"x+",B)
simpex2 = paste0(C,"x+",D)
simpex1 = gsub("+-","-",simpex1,fixed=T)
simpex2 = gsub("+-","-",simpex2,fixed=T)

e1 = gsub("{","",exp1,fixed=T)
e1 = gsub("}","",e1,fixed=T)
e2 = gsub("{","",exp2,fixed=T)
e2 = gsub("}","",e2,fixed=T)

text(0,0.5,TeX(paste0("$(",e1,")(",e2,")$")),cex=1.5)

x1 = -0.23
x2 = 0.1
y1 = 0.6
y2 = 0.8
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1,x2,0.001)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="red")
text(xmid,y2,"Firsts",col="red",adj=c(0.7,-0.2))

x1 = -0.06
x2 = 0.25+(sign(A)-1)*(-0.01)+(sign(C)-1)*(-0.01)
y1 = 0.6
y2 = 0.8
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1+0.0001,x2-0.0001,length.out=100)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="purple")
text(xmid,y2,"Lasts",col="purple",adj=c(0.3,-0.2))

x1 = -0.23
x2 = 0.25+(sign(A)-1)*(-0.01)+(sign(C)-1)*(-0.01)
y1 = 0.4
y2 = 0.1
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1+0.0001,x2-0.0001,length.out=100)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="darkorange")
text(xmid,y2,"Outsides",col="darkorange",adj=c(0.5,1.2))


x1 = -0.06
x2 = 0.1
y1 = 0.4
y2 = 0.3
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1+0.0001,x2-0.0001,length.out=100)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="blue")
text(xmid,y2,"Insides",col="blue",adj=c(0.5,1.2))

text(-0.95,0.8,TeX(paste0("Firsts= $",pn(A*C,2),"$")),col="red",adj=c(0,0.5),cex=1.2)
text(-0.95,0.6,TeX(paste0("Outsides= $",pn(A*D,1),"$")),col="darkorange",adj=c(0,0.5),cex=1.2)
text(-0.95,0.4,TeX(paste0("Insides= $",pn(B*C,1),"$")),col="blue",adj=c(0,0.5),cex=1.2)
text(-0.95,0.2,TeX(paste0("Lasts= $",B*D,"$")),col="purple",adj=c(0,0.5),cex=1.2)

answers = c(pn(c(6,23,20),c(2,1,0)))

```
\

$$`r pn(c(A*C,A*D,B*C,B*D),c(2,1,1,0))`$$

And, after combining like terms, you should get
$$`r pn(c(A*C,A*D+B*C,B*D),c(2,1,0))`$$

# Simpler question... both binomials have linear coefficients of one

You are given a quadratic expression in factored form:
$$(x+6)(x+7)$$

>- What do you get when you expand into standard form?
>- You get $x^2+13x+42$
>- Notice $13$ is the sum of $6$ plus $7$.
>- Notice $42$ is the product of $6$ times $7$.
>- This is not a coincidence...

# Another simple question

You are given a quadratic expression in factored form:
$$(x-5)(x+9)$$

>- What do you get when you expand into standard form?
>- You get $x^2+4x-45$
>- Notice $4$ is the sum of $-5$ plus $9$.
>- Notice $-45$ is the product of $-5$ times $9$.
>- This is not a coincidence...










