```{r data generation, echo = FALSE, results = "hide"}
# (x+a)^3+b   <->   cbrt(x-b)-a
# (x+a)^3+b   <->   cbrt(x+c)+d
ab = sample(2:7,2)*sample(c(-1,1),2,T)
a = ab[1]
b = ab[2]
c = -b
d = -a

ach = -9:9
al = paste0("* ",ach,collapse="\n")
sol1 = paste0(1*(a==ach),collapse="")
sol2 = paste0(1*(b==ach),collapse="")
sol3 = paste0(1*(c==ach),collapse="")
sol4 = paste0(1*(d==ach),collapse="")

ftx = paste0("(x+",a,")^3+",b,collapse="")
ftx = gsub("+-","-",ftx,fixed=T)
itx = paste0("\\sqrt[3]{x+",c,"}+",d,collapse="")
itx = gsub("+-","-",itx,fixed=T)

is1 = paste0("x~=~(y+",a,")^3+",b,collapse="")
is1 = gsub("+-","-",is1,fixed=T)

if(b>0){
    step2 = paste0("Subtract ",b," from both sides.")
} else {
    step2 = paste0("Add ",abs(b)," to both sides.")
}

is2 = paste0("x+",-b,"~=~(y+",a,")^3",collapse="")
is2 = gsub("+-","-",is2,fixed=T)

is3 = paste0("\\sqrt[3]{x+",-b,"}~=~y+",a,collapse="")
is3 = gsub("+-","-",is3,fixed=T)

if(a>0){
    step4 = paste0("Subtract ",a," from both sides.")
} else {
    step4 = paste0("Add ",abs(a)," to both sides.")
}

is4 = paste0("\\sqrt[3]{x+",-b,"}+",-a,"~=~y",collapse="")
is4 = gsub("+-","-",is4,fixed=T)

```



Question
========

Cubing and cube rooting are inverse operations. Thus, for any value of $x$, if we apply both operations, we get back to $x$.

$$\sqrt[3]{x^3} \equiv \left(\sqrt[3]{x}\right)^3 \equiv  x$$

Because cubing and [cube-rooting](https://en.wikipedia.org/wiki/Cube_root) are inverse operations, curves $y=x^3$ and $y=\sqrt[3]{x}$ have reflective symmetry over the $y=x$ line.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.2)
}
arrows(-10.5,0,10.5,0,0.1,10,3,lwd=2)
arrows(0,-10.5,0,10.5,0.1,10,3,lwd=2)
x = seq(-10,10,0.01)
y = x^3

xx = x[abs(y)<=10]
yy = y[abs(y)<=10]

lines(c(-10,10),c(-10,10),lwd=1,lty=3)
lines(xx,yy,lwd=3,col="red")
lines(yy,xx,lwd=3,col="blue")

legend("topleft",legend = c(TeX("$y = x^3$"),"",TeX("$y = \\sqrt[3]{x}$"),"",TeX("$y=x$")),col=c("red","white","blue","white","black"),lwd=c(3,0,3,0,1),lty=c(1,1,1,1,3))

text(10,-0.5,10,cex=0.8)
text(-10,-0.5,-10,cex=0.8)
text(-0.5,10,10,cex=0.8)
text(-0.5,-10,-10,cex=0.8)
text(10,0.5,"x",cex=0.8)
text(0.5,10,"y",cex=0.8)
```
\

Let function $f$ be defined by [translating](https://en.wikipedia.org/wiki/Translation_(geometry)#Translations_of_a_graph) the $y=x^3$ curve. The graph of $y~=~f(x)$ is drawn below.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.2)
}
arrows(-10.5,0,10.5,0,0.1,10,3,lwd=2)
arrows(0,-10.5,0,10.5,0.1,10,3,lwd=2)
x = seq(-10,10,0.001)
y = (x+a)^3+b

xx = x[abs(y)<=10]
yy = y[abs(y)<=10]

lines(xx,yy,col="red",lwd=3)

legend("topleft",legend = TeX("$y=f(x)$"),col="red",lwd=3)

text(10,-0.5,10,cex=0.8)
text(-10,-0.5,-10,cex=0.8)
text(-0.5,10,10,cex=0.8)
text(-0.5,-10,-10,cex=0.8)
text(10,0.5,"x",cex=0.8)
text(0.5,10,"y",cex=0.8)
```
\

Based on the graph above, determine the values of the four parameters ($a$, $b$, $c$, and $d$) to define $f$ and its inverse $f^{-1}$ algebraically.

$$\begin{align}
f(x)~&=~(x+a)^3+b \\ \\
f^{-1}(x)~&=~\sqrt[3]{x+c}+d
\end{align}$$

* $a=$ ##ANSWER1##
* $b=$ ##ANSWER2##
* $c=$ ##ANSWER3##
* $d=$ ##ANSWER4##

Answerlist
--------

`r al`
`r al`
`r al`
`r al`


Solution
========

To find $a$ and $b$, determine the horizontal translation and the vertical translation. The curve $y=f(x)$ has its [inflection point](https://en.wikipedia.org/wiki/Inflection_point) at $(`r -a`, `r b`)$. Thus,

$$f(x)~=~`r ftx`$$

So,
$$a=`r a`$$
$$b=`r b`$$

To find the inverse function, first replace $x$ with $y$ and replace $f(x)$ with $x$.

$$`r is1`$$

`r step2`

$$`r is2`$$

Take the [cube root](https://en.wikipedia.org/wiki/Cube_root) of both sides.

$$`r is3`$$

`r step4`

$$`r is4`$$

Swap sides and replace $y$ with $f^{-1}(x)$.

$$f^{-1}(x)~=~`r itx`$$

So,

$$c=`r c`$$
$$d=`r d`$$


Notice, if you graph both curves, you'll see they have reflectional symmetry over the $y=x$ line.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.2)
}
arrows(-10.5,0,10.5,0,0.1,10,3,lwd=2)
arrows(0,-10.5,0,10.5,0.1,10,3,lwd=2)
x = seq(-10,10,0.001)
y = (x+a)^3+b

xx = x[abs(y)<=10]
yy = y[abs(y)<=10]

lines(c(-10,10),c(-10,10),lty=3)
lines(xx,yy,col="red",lwd=3)
lines(yy,xx,col="blue",lwd=3)

legend("topleft",legend = c(TeX("$y=f(x)$"),TeX("$y=f^{-1}(x)$"),TeX("$y=x$")),col=c("red","blue","black"),lwd=c(3,3,1),lty=c(1,1,3))

text(10,-0.5,10,cex=0.8)
text(-10,-0.5,-10,cex=0.8)
text(-0.5,10,10,cex=0.8)
text(-0.5,-10,-10,cex=0.8)
text(10,0.5,"x",cex=0.8)
text(0.5,10,"y",cex=0.8)
```
\

With some thinking, you might even determine a graph-based shortcut that allows you to skip that algebraic manipulation to find $c$ and $d$.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: inverse_cube_function