```{r data generation, echo = FALSE, results = "hide"}
x=8
```



Question
========

You should feel pretty comfortable with the following:

$$7^2\cdot 7^3 ~=~ 7^5$$

$$(7^2)^3~=~7^6$$

The governing rules can be written as $x^ax^b\equiv x^{a+b}$ and $(x^a)^b\equiv x^{ab}$.

The square root "undoes" squaring of positive numbers.

$$\sqrt{7^2}~=~7$$

But, notice, it fails for negative numbers.

$$\sqrt{(-7)^2} ~\ne~ -7$$

If we ignore that problem for a moment, we could recognize "another" way to undo squaring, based on the rule $(x^a)^b=x^{ab}$:

$$(7^2)^{1/2} ~=~ 7^{2\cdot \frac{1}{2}} ~=~ 7^1 ~=~ 7$$

But, actually, we've just stumbled upon a useful identity: raising to the 1/2 power is equivalent to taking a square root.

$$\sqrt{x} ~\equiv~ x^{1/2}$$

For example, $\sqrt{10}\approx`r sqrt(10)`$ and also $10^{0.5}\approx`r sqrt(10)`$.

To undo cubing, you can take a cube root. Raising to the 1/3 is equivalent to a cube root.

$$\sqrt[3]{5^3}~=~(5^3)^{1/3}~=~5^1~=~5$$

Notice, if we plot $y=x^3$ and $y=\sqrt[3]{x}$, we see the two curves have reflective symmetry over the $y=x$ line.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0))
x = seq(-12,12,0.01)
y1 = x^3
y2 = abs(x)^(1/3)*sign(x)
plot(0,0,type="n",axes=F,ann=F,xlim=c(-5,5),ylim=c(-5,5))
for(i in -10:10){
    abline(h=i,col="lightgrey",lwd=0.7)
    abline(v=i,col="lightgrey",lwd=0.7)
}
for(i in seq(-10,10,5)){
    abline(h=i,col="darkgrey",lwd=1.2)
    abline(v=i,col="darkgrey",lwd=1.2)
}
arrows(-5.2,0,5.2,0,0.1,10,3,lwd=2)
arrows(0,-5.2,0,5.2,0.1,10,3,lwd=2)
text(5,-0.3,5)
text(-5,-0.3,-5)
text(-0.3,5,5)
text(-0.3,-5,-5)
text(5,0.3,"x")
text(0.3,5,"y")

lines(c(-6,6),c(-6,6),lty=3)
lines(x,y1,col="red",lwd=3)
lines(x,y2,col="blue",lwd=3)
legend("bottomright",legend=c(TeX("$y = x^3$"),TeX("$y=\\sqrt[3]{x}$"),"y = x"),col=c("red","blue","black"),lwd=c(3,3,1),lty=c(1,1,3))

```
\

Inverse functions! So, if $f(x)=x^3$ then $f^{-1}(x)=\sqrt[3]{x}$.

Now, let's get back to squaring and square rooting. If we graph $y=x^2$ and $y=\sqrt{x}$, we see something like inverse functions. Unfortunately, $y=x^2$ is **NOT A ONE-TO-ONE FUNCTION**, and so it is impossible to perfectly undo. To move forward, we restrict the domain over which $y=x^2$ is one-to-one for building our best attempt at an inverse.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0))
x = seq(-12,12,0.01)
y1 = x^2
y2 = x^(1/2)
plot(0,0,type="n",axes=F,ann=F,xlim=c(-5,5),ylim=c(-5,5))
for(i in -10:10){
    abline(h=i,col="lightgrey",lwd=0.7)
    abline(v=i,col="lightgrey",lwd=0.7)
}
for(i in seq(-10,10,5)){
    abline(h=i,col="darkgrey",lwd=1.2)
    abline(v=i,col="darkgrey",lwd=1.2)
}
arrows(-5.2,0,5.2,0,0.1,10,3,lwd=2)
arrows(0,-5.2,0,5.2,0.1,10,3,lwd=2)
text(5,-0.3,5)
text(-5,-0.3,-5)
text(-0.3,5,5)
text(-0.3,-5,-5)
text(5,0.3,"x")
text(0.3,5,"y")

xr = seq(0,6,0.1)
yr = xr^2

lines(c(-6,6),c(-6,6),lty=3)
lines(x,y1,col="red",lwd=1)
lines(xr,yr,col="red",lwd=3,lty=3)
lines(x,y2,col="blue",lwd=3)
legend("bottomright",legend=c(TeX("$y = x^2$"),TeX("One-to-one section of $y=x^2$"),TeX("$y=\\sqrt{x}$"),"y = x"),col=c("red","red","blue","black"),lwd=c(1,2,3,1),lty=c(1,3,1,3))

```
\





Solution
========



Meta-information
============
extype: num
exsolution: 
exname: use_odd_prop