```{r data generation, echo = FALSE, results = "hide"}
library(exams)
## DATA GENERATION
images = c("bike","cat","dog","flower","gem","house","jar","kite","lamp","mop",
           "needle","pig","quilt","rug","shovel","tree","vase","wheel")
colors = c("red","orange","yellow","green","blue","indigo","violet","white",
           "black","teal","pink","gray")

nsig = 2

while(T)
{
    ni = sample(3:5,1)
    nc = sample(3:5,1)
    is = sort(sample(images,ni))
    cs = sort(sample(colors,nc),decreasing=TRUE)
    nums = matrix(sample(10:50,ni*nc),ni)
    rownames(nums) = is
    colnames(nums) = cs
    tots = c()
    for(row in 1:ni)
    {
        tots = c(tots,sum(nums[row,]))
    }
    for(col in 1:nc)
    {
        tots = c(tots,sum(nums[,col]))
    }
    if(min(diff(sort(tots)))>6)      #sum(duplicated(tots))==0)
    {
        break
    }
}

tot = sum(nums)

#marginal image
i1 = sample(1:ni,1)
p1 = round(sum(nums[i1,])/tot,nsig)
t1 = paste0("What is the probability a random card is a ",is[i1],"?",sep="")
ex1 = paste0("$\\mathbb{P}[\\text{",is[i1],"}]",sep="")
s1 = paste("$\\mathbb{P}[\\text{",is[i1],"}]=\\frac{",sum(nums[i1,]),"}{",tot,"}=",p1,"$",sep="")


#marginal color
c2 = sample(1:nc,1)
p2 = round(sum(nums[,c2])/tot,nsig)
t2 = paste0("What is the probability a random card is ",cs[c2],"?",sep="")
s2 = paste0("$\\mathbb{P}[\\text{",cs[c2],"}]=\\frac{",sum(nums[,c2]),"}{",tot,"}=",p2,"$",sep="")

#joint
i3 = sample(1:ni,1)
c3 = sample(1:nc,1)
p3 = round(nums[i3,c3]/tot,nsig)
t3 = paste0("What is the probability a random card is both a ",
            is[i3]," and ",cs[c3],"?",sep="")
numer3 = paste(nums[i3,c3])
denom3 = paste(tot)
s3 = paste0("$\\mathbb{P}[\\text{",is[i3]," and ",cs[c3],"}]=\\frac{",nums[i3,c3],"}{",tot,"}=",p3,"$",sep="")

#disjoint
i4 = sample(1:ni,1)
c4 = sample(1:nc,1)
p4 = round((sum(nums[i4,])+sum(nums[,c4])-nums[i4,c4])/tot,nsig)
t4 = paste0("What is the probability a random card is either a "
            ,is[i4]," or ",cs[c4]," (or both)?",sep="")
numer4 = paste(paste(c(nums[i4,],nums[,c4]),collapse="+"),
               nums[i4,c4],sep="-")
denom4 = paste(tot)
s4 = paste0("$\\mathbb{P}[\\text{",is[i4]," or ",cs[c4],"}]=\\frac{",sum(nums[i4,]),"+",sum(nums[,c4]),"-",nums[i4,c4],"}{",tot,"}=",p4,"$",sep="")

#conditioned on image
i5 = sample(1:ni,1)
c5 = sample(1:nc,1)
p5 = round(nums[i5,c5]/sum(nums[i5,]),nsig)
t5 = paste0("What is the probability a random card is ",
            cs[c5]," given it is a ",is[i5],"?",sep="")
s5 = paste0("$\\mathbb{P}[\\text{",cs[c5]," given ",is[i5],"}]=\\frac{",nums[i5,c5],"}{",sum(nums[i5,]),"}=",p5,"$",sep="")

#conditioned on color
i6 = sample(1:ni,1)
c6 = sample(1:nc,1)
p6 = round(nums[i6,c6]/sum(nums[,c6]),nsig)
t6 = paste0("What is the probability a random card is a ",
            is[i6]," given it is ",cs[c6],"?",sep="")
s6 = paste0("$\\mathbb{P}[\\text{",is[i6]," given ",cs[c6],"}]=\\frac{",nums[i6,c6],"}{",sum(nums[,c6]),"}=",p6,"$",sep="")

#compare 2 images for more likely to have color
i7 = sort(sample(1:ni,2))
c7 = sample(1:nc,1)

p7a = signif(nums[i7[1],c7]/sum(nums[i7[1],]),nsig)
p7b = signif(nums[i7[2],c7]/sum(nums[i7[2],]),nsig)

p7 = c(p7a,p7b)

#p7 = signif(nums[i7,c7]/sum(nums[i7,]),3)
if(p7[1]>p7[2]){
    big = is[i7[1]]
    small = is[i7[2]]
    sol7 = "10"
} else {
    big = is[i7[2]]
    small = is[i7[1]]
    sol7 = "01"
}
t7 = paste("Is a ",is[i7[1]]," or a ",is[i7[2]]," more likely to be ",cs[c7],"?",sep="")

t7 = c(paste("A ", is[i7[1]],".", sep=""),
       paste("A ", is[i7[2]],".", sep=""))

s7 = c(paste("$\\mathbb{P}[\\text{",cs[c7]," given ",is[i7[1]],"}] = ",p7[1],"$ and $\\mathbb{P}[\\text{",cs[c7]," given  ",is[i7[2]],"}] = ",p7[2],"$, so a ",big," is more likely to be ",cs[c7]," than a ",small," is.",sep=""),".")

p = c(p1,p2,p3,p4,p5,p6)
cho = list()
ans = character()

for(i in 1:6){
  numund = sample(0:3,1)
  while(T){
    choices = sort(c(p[i],round(runif(3,sqrt(0.01),sqrt(0.8))^2,nsig)))
    choices = sort(c(p[i],
                     round(runif(numund,sqrt(0.01),sqrt(p[i]))^2,nsig),
                     round(runif(3-numund,sqrt(p[i]),sqrt(0.85))^2,nsig)
                     )
                   )
    if(min(diff(choices))>0.02){
      cho[[i]] = choices
      ans = c(ans,paste0((choices==p[i])*1,collapse=""))
      break
      }
  }
}

ts = list(cho[[1]],cho[[2]],cho[[3]],cho[[4]],cho[[5]],cho[[6]],t7)
sss = list(s1,s2,s3,s4,s5,s6,s7)
types = c(rep("schoice",6),"schoice") ###### edit for MC
sols = list(ans[1],ans[2],ans[3],ans[4],ans[5],ans[6],sol7)
ord = 1:7 #sample(1:7)

tt = lapply(ts[ord],function(a){if(typeof(a)=="double"){sprintf("%.2f",a)}else{a}})
ss = sss[ord]
type = types[ord]
sol = sols[ord]

mystr1 = paste0(t1, " ##ANSWER",which(ord==1),"##",collapse="")
mystr2 = paste0(t2, " ##ANSWER",which(ord==2),"##",collapse="")
mystr3 = paste0(t3, " ##ANSWER",which(ord==3),"##",collapse="")
mystr4 = paste0(t4, " ##ANSWER",which(ord==4),"##",collapse="")
mystr5 = paste0(t5, " ##ANSWER",which(ord==5),"##",collapse="")
mystr6 = paste0(t6, " ##ANSWER",which(ord==6),"##",collapse="")
mystr7 = paste0("Between a ",is[i7[1]]," and a ",is[i7[2]],", which is more likely to be a ",cs[c7],"? ##ANSWER",which(ord==7),"##",collapse="")


mystr = c(mystr1,mystr2,mystr3,mystr4,mystr5,mystr6,mystr7)[ord]

nums <- cbind(nums, Total = rowSums(nums))
nums <- rbind(nums, Total = colSums(nums))

s = paste("\\begin{center}\n\\begin{tabular}{|c|",paste(rep("c",nc),collapse=" "),"|c|} \\hline \n")
s = paste(s, " & ",paste(cs, collapse =" & ")," & Total   \\\\ \\hline \n")
for(i in 1:ni){
    s = paste(s, is[i], " & ", paste(nums[i,],collapse=" & "), "\\\\")
    if(i<ni){
        s = paste(s,"\n")
    }
}
s = paste(s, "\\hline \n")
s = paste(s, "Total & ", paste(nums[ni+1,],collapse=" & "), "\\\\ \\hline \n")
s = paste(s,"\\end{tabular}\n\\end{center}")


```

Question
========

In a deck of strange cards, there are `r tot` cards. Each card has an image and a color.

```{r, fig.width=6,fig.height=4,echo=F}
par(mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-0.2,ni+1.5),ylim=c(-0.5,nc+1),axes=F,ann=F)
for(ii in 1:ni){
    text(ii,nc+0.5,is[ii],pos = 3)
    text(ii,0,nums[ii,nc+1])
}
text(ni+1,nc+0.5,"total",pos=3)
for(cc in 1:nc){
    text(0.5,nc-cc+1,cs[nc-cc+1],pos=2)
    text(ni+1,nc-cc+1,nums[ni+1,nc-cc+1])
}

for(i in 1:ni){
    for(j in 1:nc){
        text(i,j,nums[i,j])
    }
}
text(ni+1,0,nums[ni+1,nc+1])
text(0.5,0,"total",pos=2)
abline(h = nc+0.5)
abline(v = 0.5)
abline(h = 0.5)
abline(v = ni+0.5)
```
\

(Answers can be rounded to nearest hundredth.)

a. `r mystr[1]`
b. `r mystr[2]`
c. `r mystr[3]`
d. `r mystr[4]`
e. `r mystr[5]`
f. `r mystr[6]`
g. `r mystr[7]`

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(unlist(tt), markup = "markdown")
```


Solution
========

[video](https://vimeo.com/531915456){target="_blank"}

The key logical terms are "[and](https://en.wikipedia.org/wiki/Logical_conjunction){target="blank"}", "[or](https://en.wikipedia.org/wiki/Logical_disjunction){target="blank"}", and "[given](https://en.wikipedia.org/wiki/Conditional_probability){target="blank"}". Notice that I am using "given" as a shorter version of "under the condition".  



```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(paste(unlist(ss), sep = ""), markup = "markdown")
```

Meta-information
============
extype: cloze
exsolution: `r paste(sol, collapse="|")`
exclozetype: `r paste(type, collapse="|")`
exname: Cards_probabilities
extol: 0.01
exextra[numwidth,logical]: TRUE
