---
output: pdf_document
geometry: margin=1in
urlcolor: blue
---

```{r,echo=F}
dim = 5
```

# Notes: Parent Function Transformations

1. Make an accurate graph of the transformed parent function.

$$y~=~3\sqrt{\frac{x+4}{2}}-5$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```


\newpage

2. Make an accurate graph of the transformed parent function.

$$y~=~\frac{2}{x-1}+3$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```

\newpage

3. Make an accurate graph of the transformed parent function.

$$y~=~3\cdot 2^{4+x/2}-9$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```


\newpage

4. Make an accurate graph of the transformed parent function.

$$y~=~ \frac{1}{2}\cdot \left(\frac{x}{3}+1\right)^2-7$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```


\newpage

5. Make an accurate graph of the transformed parent function.

$$y~=~ 2\cdot (4-x)^3+7$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```


\newpage

6. Make an accurate graph of the transformed parent function.

$$y~=~ -2 \cdot |x+1|+5$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```




\newpage

7. Make an accurate graph of the transformed parent function.

$$y~=~ \frac{\sqrt[3]{2x-3}}{2}+5$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```



\newpage

8. Make an accurate graph of the transformed parent function.

$$y~=~ 2\cdot \log_2{\left(\frac{x}{2}+2\right)}-2$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
lim = 10
plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
text(5,-0.5,"5",col="darkgrey",cex=0.6)
text(10,-0.5,"10",col="darkgrey",cex=0.6)
text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
for(i in c(-10,-5,5,10)){
    polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
    text(i,-0.5,i,col="black",cex=0.6)
    polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
    text(-0.5,i,i,col="black",cex=0.6)
}
```










