```{r data generation, echo = FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE)
options(scipen=100)

while(T){
  n1 = sample(20:40,1)
  n2 = sample(20:40,1)
  sig1 = runif(1,20,50)
  sig2 = sig1
  mu1 = runif(1,300,900)
  mu2 = mu1+sample(c(-1,1),1)*sig1/sqrt(max(c(n1,n2)))*4
  x1 = round(rnorm(n1,mu1,sig1),1)
  x2 = round(rnorm(n2,mu2,sig2),1)
  xbar1 = mean(x1)
  xbar2 = mean(x2)
  s1 = sd(x1)
  s2 = sd(x2)
  SE1 = s1/sqrt(n1)
  SE2 = s2/sqrt(n2)
  LB1 = round(xbar1-2*SE1,1)
  UB1 = round(xbar1+2*SE1,1)
  LB2 = round(xbar2-2*SE2,1)
  UB2 = round(xbar2+2*SE2,1)
  arediff = (UB1<LB2 || UB2<LB1)
  wfs = c(1/4,1/4*sqrt(2),1/2,1/sqrt(2),sqrt(2),2,2*sqrt(2),4)
  wfs1 = sample(wfs,3)
  wfs2 = sample(wfs,3)
  lb1opts = round(sort(c(LB1,xbar1-SE1*wfs1)),1)
  ub1opts = round(sort(c(UB1,xbar1+SE1*wfs1)),1)
  lb2opts = round(sort(c(LB2,xbar2-SE2*wfs2)),1)
  ub2opts = round(sort(c(UB2,xbar2+SE2*wfs2)),1)
  bounds = sort(c(LB1,LB2,UB1,UB2))
  if(min(diff(bounds))>1 && abs(xbar1-xbar2)>1
     && min(diff(lb1opts))>1
     && min(diff(lb2opts))>1
     && min(diff(ub1opts))>1
     && min(diff(ub2opts))>1){break}
}

isrightlb1 = (lb1opts==LB1)
isrightub1 = (ub1opts==UB1)
isrightlb2 = (lb2opts==LB2)
isrightub2 = (ub2opts==UB2)

slb1 = paste0(isrightlb1*1,collapse="")
sub1 = paste0(isrightub1*1,collapse="")
slb2 = paste0(isrightlb2*1,collapse="")
sub2 = paste0(isrightub2*1,collapse="")

x1df = x1
x2df = x2
len = max(c(length(x1df),length(x2df)))
if(length(x1)<length(x2)){
  x1df = c(x1df,rep(NA,len-length(x1df)))
}
if(length(x1)>length(x2)){
  x2df = c(x2df,rep(NA,len-length(x2df)))
}

if(arediff && xbar1<xbar2){
  ss = "100"
  sss = "Island 1 has a significantly lower average weight."
} else if(arediff && xbar1>xbar2){
  ss = "010"  
  sss = "Island 1 has a significantly higher average weight."
} else {
  ss = "001"
  sss = "These data (and methodology) do not show a significant difference."
  }

```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

A biologist investigated two populations of turtles (on two different islands). They weighed turtles from [simple-random samples](https://en.wikipedia.org/wiki/Simple_random_sample){target="_blank"}; those weights are shown below in grams.


```{r tab_data, echo=FALSE, results="asis"}
opts <- options(knitr.kable.NA = "")
mydf = data.frame(x1df,x2df)
colnames(mydf) = c("Island_1","Island_2")
knitr::kable(mydf,format="html", align = "c",row.names=F,table.attr='class="bordered-table"')
```
\


The scientist hopes to construct a 95% [**confidence interval**](https://en.wikipedia.org/wiki/Confidence_interval){target="blank"} for each island's average turtle weight.

The scientist will later consult a statistician for a more precise method, but for now they will use a quick method to estimate the 95% confidence interval:
$$\text{CI boundaries} = \bar{x}\pm \frac{2s}{\sqrt{n}} $$


The confidence interval for Island 1's average weight is [##ANSWER1##, ##ANSWER2##].

The confidence interval for Island 2's average weight is [##ANSWER3##, ##ANSWER4##].

The biologist wonders if there is a significant difference in mean weights.

* If confidence intervals overlap:
  * the difference of means is not significant
  * a more advanced technique or larger sample sizes could show significance.
* If the confidence intervals do **NOT** overlap:
  * the difference of means is significant.
  
What inference is made?

##ANSWER5##


Answerlist
--------
* `r lb1opts[1]`
* `r lb1opts[2]`
* `r lb1opts[3]`
* `r lb1opts[4]`
* `r ub1opts[1]`
* `r ub1opts[2]`
* `r ub1opts[3]`
* `r ub1opts[4]`
* `r lb2opts[1]`
* `r lb2opts[2]`
* `r lb2opts[3]`
* `r lb2opts[4]`
* `r ub2opts[1]`
* `r ub2opts[2]`
* `r ub2opts[3]`
* `r ub2opts[4]`
* Island 1 has a lower average weight.
* Island 1 has a higher average weight.
* These data (and methodology) do not show a significant difference.


Solution
========

The confidence interval for Island 1 is [`r LB1`, `r UB1`].

The confidence interval for Island 2 is [`r LB2`, `r UB2`].

`r sss`


Meta-information
================
extype: cloze
exsolution: `r slb1`|`r sub1`|`r slb2`|`r sub2`|`r ss`
exclozetype: schoice|schoice|schoice|schoice|schoice
exname: CI 2 means MC
