---
output: pdf_document
params:
    rseed: 0
    showsol: true
    useseed: false
urlcolor: blue
---

```{r,echo=F}
if(params$useseed){
    set.seed(params$rseed)
}

while(T){
    ys1 = c(0,sample(-9:9,3))
    ys2 = c(0,sample(-9:9,3))
    ys3 = c(0,sample(-9:9,3))
    ys4 = c(0,sample(-9:9,3))
    sy1 = sign(diff(ys1))
    sy2 = sign(diff(ys2))
    sy3 = sign(diff(ys3))
    sy4 = sign(diff(ys4))
    ss1 = paste0(sy1,collapse="")
    ss2 = paste0(sy2,collapse="")
    ss3 = paste0(sy3,collapse="")
    ss4 = paste0(sy4,collapse="")
    if(length(unique(c(ss1,ss2,ss3,ss4)))==4){break}
}

```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## PCW_0909_draw_even_or_odd (version `r params$rseed`)

A function is even if $f(x)=f(-x)$ for all $x$ in the domain. A function is odd if $f(x)=-f(-x)$ for all $x$ in the domain.

1. I have drawn half of a function. Draw the other half to make it even or odd.

```{r,echo=F,fig.dim=c(7,3.5)}
makem = function(xs,ys){
    par(mar=c(0,0.5,1,0.5),pty="s",mfrow=c(1,2))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    dems = seq(-10,10,0.2)
    NNN = length(dems)
    for(i in -10:10){
        points(rep(i,NNN),dems,pch=19,cex=0.02)
        points(dems,rep(i,NNN),pch=19,cex=0.02)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),lwd=0.8)
        lines(c(i,i),c(-10,10),lwd=0.8)
    }
    abline(h=0,lwd=2)
    abline(v=0,lwd=2)
    text(10,0,"x",adj=c(-0.1,1.1))
    text(0,10,"y",adj=c(1.1,-0.1))
    lines(xs,ys,lwd=3,col="blue")
    points(xs,ys,pch=19,cex=0.8,col="blue")
    mtext("EVEN",3)
    if(params$showsol){
        lines(-xs,ys,lwd=3,col="red")
    }
    
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    dems = seq(-10,10,0.2)
    NNN = length(dems)
    for(i in -10:10){
        points(rep(i,NNN),dems,pch=19,cex=0.02)
        points(dems,rep(i,NNN),pch=19,cex=0.02)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),lwd=0.8)
        lines(c(i,i),c(-10,10),lwd=0.8)
    }
    abline(h=0,lwd=2)
    abline(v=0,lwd=2)
    text(10,0,"x",adj=c(-0.1,1.1))
    text(0,10,"y",adj=c(1.1,-0.1))
    lines(xs,ys,lwd=3,col="blue")
    points(xs,ys,pch=19,cex=0.8,col="blue")
    mtext("ODD",3)
    if(params$showsol){
        lines(-xs,-ys,lwd=3,col="red")
    }
}
xs = sort(c(0,sample(1:9,3)))
ys = ys1
makem(xs,ys)
```

\vfill

2. I have drawn half of a function. Draw the other half to make it even or odd.


```{r,echo=F,fig.dim=c(7,3.5)}
xs = sort(c(0,sample(1:9,3)))
ys = ys2
makem(xs,ys)
```

\vfill

\newpage

A function is even if $f(x)=f(-x)$ for all $x$ in the domain. A function is odd if $f(x)=-f(-x)$ for all $x$ in the domain.


3. I have drawn half of a function. Draw the other half to make it even or odd.

```{r,echo=F,fig.dim=c(7,3.5)}
xs = sort(c(0,sample(1:9,3)))
ys = ys3
makem(xs,ys)
```

\vfill

4. I have drawn half of a function. Draw the other half to make it even or odd.

```{r,echo=F,fig.dim=c(7,3.5)}
xs = sort(c(0,sample(1:9,3)))
ys = ys4
makem(xs,ys)
```

\vfill

