```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

while(T){
    theta = round(runif(1,pi/4,7*pi/4),2)
    radius = sample(20:99,1)/10
    L = theta*radius
    if(round(L,1)==L && length(unique(c(theta,radius,L)))==3){break}
}

```

Question
========

Consider a circle with a radius of length $r=`r radius`$ meters. A [central angle](https://en.wikipedia.org/wiki/Central_angle), in [standard position](https://libraryguides.centennialcollege.ca/c.php?g=716824&p=5112868), subtends an [arc](https://en.wikipedia.org/wiki/Circular_arc) of length $`r L`$ meters.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
th = seq(0,2*pi,pi/300)
lines(cos(th),sin(th),col="grey")
lines(c(1,0,cos(theta)),c(0,0,sin(theta)),col="black")
th2 = seq(0,theta,pi/300)
lines(cos(th2),sin(th2),col="red",lwd=3)
text(1.1*cos(theta/2),1.1*sin(theta/2),paste0(L," m"),srt=atan(sin(theta/2+pi/2)/cos(theta/2+pi/2))/pi*180,col="red")
text(0.5,-0.05,paste0(radius," m",collapse=""))
points(0,0,pch=20)
lines(0.2*cos(th2),0.2*sin(th2),col=rgb(0.6,0,0.6))
text(0.3*cos(theta/2),0.3*sin(theta/2),TeX("$\\theta$"),col=rgb(0.6,0,0.6))

```
\


**Find $\theta$ in radians**.


Solution
========

Remember, the radian measure of an angle is the length of the arc on the **[unit circle](https://en.wikipedia.org/wiki/Unit_circle)** subtended by the angle. The circle shown is not a unit circle (its radius is `r radius`), but we can add a unit circle into the drawing.

(Not drawn to scale.)

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
th = seq(0,2*pi,pi/300)
lines(cos(th),sin(th),col="grey")
lines(0.2*cos(th),0.2*sin(th),col="grey")
lines(c(1,0,cos(theta)),c(0,0,sin(theta)),col="black")
th2 = seq(0,theta,pi/300)
lines(cos(th2),sin(th2),col="red",lwd=3)
text(1.1*cos(theta/2),1.1*sin(theta/2),paste0(L," m"),srt=atan(sin(theta/2+pi/2)/cos(theta/2+pi/2))/pi*180,col="red")
text(0.5,-0.05,paste0(radius," m",collapse=""))
points(0,0,pch=20)
lines(0.2*cos(th2),0.2*sin(th2),col=rgb(0.6,0,0.6),lwd=2)
text(0.3*cos(theta/2),0.3*sin(theta/2),TeX("$\\theta$"),col=rgb(0.6,0,0.6))
text(0.1,-0.05,"1",col="blue")
lines(c(0,0.2),c(0,0),col="blue",lwd=2)
```
\

$$\frac{\theta}{`r L`}~=~\frac{1}{`r radius`}$$

$$\theta~=~\frac{`r L`}{`r radius`}~=~`r theta`$$

If you refer to the [wikipedia article on circular arcs](https://en.wikipedia.org/wiki/Circular_arc), you'll see a formula:
$$L=\theta r$$
where $L$ is an arc length on a circle of radius $r$ and with central angle $\theta$ (pronounced "theta"). In our case, we were given $L=`r L`$ and $r=`r radius`$, so we can rearrange the formula, solving for $\theta$.

$$\theta = \frac{L}{r} = \frac{`r L`}{`r radius`}$$



Meta-information
============
extype: num
exsolution: `r theta`
exname: radians_from_unit_arc