```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
th = runif(1,pi/20,pi/2-pi/20)+sample(c(0,pi/2,pi,3*pi/2),1)
th = signif(th,3)
m = signif(tan(th),3)
x = cos(th)
xr = signif(x,3)
q = th%/%(pi/2)+1
sx = sign(x)
sy = 1-2*(q>2)
x = sqrt(1/(1+m^2))*sx
y = abs(m*x)*sy
yr = signif(y,3)
rmn = c("I","II","III","IV")

```

Question
========

Given:

$$\tan(\theta)~=~`r m`$$
$$\theta~\text{ is in quadrant `r rmn[q]`}$$

Find $\cos(\theta)$. The tolerance is $\pm 0.001$.


Solution
========

Remember, $\tan(\theta)$ represents **the slope** of the segment connecting $(0,0)$ to $(\cos(\theta),\sin(\theta))$. Draw a sketch. We know the point of interest is in quadrant `r rmn[q]`. Draw the unit circle centered at the origin and the line $y=`r m`x$.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
arrows(-1.3,0,1.3,0,0.1,20,3,lwd=2,col="grey")
arrows(0,-1.3,0,1.3,0.1,20,3,lwd=2,col="grey")
thall = seq(0,2*pi,pi/360)
lines(cos(thall),sin(thall),col="black",lty=3)
# abline(v=x,lty=2,col="blue")
# if(abs(x)>0.6){
#     text(x,-1.15*sign(y),paste0("x=",round(x,5),collapse=""),adj=c(0.5,-0.3),srt=90,col="blue")
# } else {
#     text(x,0,paste0("x=",round(x,5),collapse=""),adj=c(0.5,-0.3),srt=90,col="blue")
# }

abline(0,m,col=rgb(0.6,0.6,1),lty=2)
text(0,0,paste0("y=",m,"x"),srt=atan(m)*180/pi,col="blue",adj=c(0.5,-0.2))

thth = seq(0,th,pi/360)
# polygon(c(0,cos(thth)),c(0,sin(thth)),border=F,col=rgb(0.5,0,0.2,0.1))
lines(cos(thth),sin(thth),col="maroon",lwd=3)
# lines(c(0,cos(th)),c(0,sin(th)),col="red")
text(1.05*cos(th/2),1.05*sin(th/2),TeX("$\\theta$"),col="maroon",cex=1.5)

# library(extrafont)
# font_import()
# loadfonts() 
text(1.15,1.15,"I",family="Tahoma",font=1,cex=1.3)
text(-1.15,1.15,"II",family="Tahoma",font=1,cex=1.3)
text(-1.15,-1.15,"III",family="Tahoma",font=1,cex=1.3)
text(1.15,-1.15,"IV",family="Tahoma",font=1,cex=1.3)
points(x,y,pch=20,col="purple",cex=2)
text(x,y,paste0("(x,  y)"),col="purple",adj=c(0.5-0.7*sign(x),0.5-0.7*sign(y)))

points(-x,-y,pch=19,col="black")
text(-x,-y,adj=c(0.5-0.7*sign(x),0.5-0.7*sign(y)),"wrong\nspot")
srt = (th*180/pi+90)%%180-90
# text(0.5*cos(th),0.5*sin(th),"1",col="red",srt=srt,adj=c(0.5,-0.3))

np = c("negative","positive")
npx = np[round(sign(x)/2+1.5)]
npy = np[round(sign(y)/2+1.5)]

```
\

You can draw a right triangle. The standard way to do this is by using a segment along the $x$-axis and a vertical segment from the $x$-axis to the point. In order for the slope to equal $\frac{y}{x}$, we can enforce that $|y|=|`r m`x|$. Notice I am labeling the lengths with positive numbers; I will take care of signs (whether $x$ or $y$ is positive or negative), after using Pythagorean Theorem, by considering the quadrant.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,
     xlim=c(sign(x)*(0.5-sign(x)*0.6),sign(x)*(0.5+sign(x)*0.6)),
     ylim=c(sign(y)*(0.5-sign(y)*0.6),sign(y)*(0.5+sign(y)*0.6)))
arrows(-1.1,0,1.1,0,0.1,20,3,lwd=2,col="grey")
arrows(0,-1.1,0,1.1,0.1,20,3,lwd=2,col="grey")
thall = seq(0,2*pi,pi/360)
bmp = 0.02
bx = bmp*sign(x)
by = bmp*sign(y)
lines(c(x-bx,x-bx,x),c(0,by,by))

lines(cos(thall),sin(thall),col="grey",lty=3)
thth = seq(0,th,pi/360)
# polygon(c(0,cos(thth)),c(0,sin(thth)),border=F,col=rgb(0.5,0,0.2,0.1))
lines(cos(thth),sin(thth),col=rgb(0.8,0,0.6),lwd=1)
lines(c(0,cos(th)),c(0,sin(th)),col="red",lwd=3)
# text(1.05*cos(th/2),1.05*sin(th/2),TeX("$\\theta$"),col="maroon",cex=1.5)

# library(extrafont)
# font_import()
# loadfonts() 
text(1.05,1.05,"I",family="Tahoma",font=1,cex=1.3)
text(-1.05,1.05,"II",family="Tahoma",font=1,cex=1.3)
text(-1.05,-1.05,"III",family="Tahoma",font=1,cex=1.3)
text(1.05,-1.05,"IV",family="Tahoma",font=1,cex=1.3)
# points(x,y,pch=20,col="purple",cex=2)
# text(1.01*x,1.01*y,paste0("(",round(x,4),",  y)"),col="purple",adj=c(0.5-0.7*sign(x),0.5-0.7*sign(y)))

points(x,-y,pch=19,col="black")
text(x,-y,adj=c(0.5-0.7*sign(x),0.5+0.7*sign(y)),"wrong\nspot")
srt = (th*180/pi+90)%%180-90
text(0.5*cos(th),0.5*sin(th),"1",col="red",srt=srt,adj=c(0.5,0.5-0.8*sign(y)))
lines(c(x,x),c(0,y),col="darkorange",lwd=3)
text(x,y/2,TeX(paste0("$|",abs(m),"x|$")),col="darkorange",srt=90,adj=c(0.5,0.5+0.9*sign(x)))
lines(c(0,x),c(0,0),col="darkgreen",lwd=3)
text(x/2,0,TeX("$|x|$"),col="darkgreen",srt=0,adj=c(0.5,0.5+0.9*sign(y)))

np = c("negative","positive")
npx = np[round(sign(x)/2+1.5)]
npy = np[round(sign(y)/2+1.5)]

```
\

Use Pythagorean Theorem.

$$x^2+(`r abs(m)`x)^2~=~1^2$$

Distribute the power of 2 across the two factors in the parentheses. Also, $1^2=1$.

$$x^2+`r abs(m)^2`x^2~=~1$$

Combine like terms. $1x^2+`r abs(m)^2`x^2\equiv (1+`r abs(m)^2`)x^2 \equiv `r 1+abs(m)^2`x^2$


$$`r 1+abs(m)^2`x^2~=~1$$

Divide both sides by `r 1+abs(m)^2`.

$$x^2~=~\frac{1}{`r 1+abs(m)^2`}$$

Square root both sides.

$$|x|~=~ \sqrt{\frac{1}{`r 1+abs(m)^2`}}$$


We know the quadrant is quadrant `r rmn[q]`, so $x$ is `r npx`.

$$x~=~ `r x`$$

So,

$$\cos(\theta)~=~`r x`$$


Meta-information
============
extype: num
exsolution: `r x`
exname: cos_from_tan_and_Q
extol: 0.001