```{r,echo=FALSE}
options(scipen=999)
xy = sample(8:30,2)

x = xy[1]
y = xy[2]

```

Question
========

A large square comprises a yellow square, two congruent blue rectangles, and a red square.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
N = x+y
b = seq(0,1,length.out=N+1)

polygon(c(0,x/N,x/N,0),c(y/N,y/N,1,1),col="yellow")
polygon(c(1,x/N,x/N,1),c(y/N,y/N,1,1),col="lightblue")
polygon(c(0,x/N,x/N,0),c(0,0,y/N,y/N),col="lightblue")
polygon(c(1,x/N,x/N,1),c(0,0,y/N,y/N),col="pink")

for(i in b){
    lines(c(0,1),c(i,i),col="grey")
    lines(c(i,i),c(0,1),col="grey")
}

```
\

The yellow square has an area of `r x^2` little squares. The two blue rectangles have a combined area of `r 2*x*y` little squares.

What is the area, in little squares, of the red square?



Solution
========


Find the edge length of the yellow square by using the square-root operator.

$$x=\sqrt{`r x^2`}$$

$$x=`r x`$$

Find the area of each blue rectangle.

$$B=\frac{`r 2*x*y`}{2}$$
$$B=`r x*y`$$

Each blue rectangle has one length of `r x` and another of length $y$.

$$xy~=~`r x*y`$$
$$`r x`y~=~`r x*y`$$
$$y~=~`r y`$$

The red square has side lengths equal to $y=`r y`$. To find its area, square the side length.

$$R=y^2$$
$$R=`r y`^2$$
$$R=`r y^2`$$

The area of the red square is `r y^2` little squares.


Meta-information
============
extype: num
exsolution: `r y^2`
exname: complete_the_square_A