```{r,echo=FALSE}
options(scipen=999)
hk = sample(1:5,2)*sample(c(-1,1),2,T)
A = sample(c(-1,1),1)
h = hk[1]
k = hk[2]

whichvaries = sample(1:3,1)

chA = c(-1,1)
chh = -10:10
chk = -10:10

wA = which(chA==A)+1
wh = which(chh==h)+1
wk = which(chk==k)+1

if(whichvaries==1){
    wA = 1
} else if(whichvaries==2){
    wh = 1
} else if(whichvaries==3){
    wk = 1
}

solA = paste0(1*(1:(length(chA)+1)==wA),collapse="")
solh = paste0(1*(1:(length(chh)+1)==wh),collapse="")
solk = paste0(1*(1:(length(chk)+1)==wk),collapse="")

```


Question
========

In [Desmos graphing calculator](https://www.desmos.com/calculator), define $f(x)$ with the following parameterized equation, and add sliders for all three parameters ($A$, $h$, and $k$). The sliders should default with boundaries of $-10$ and $10$.

$$f(x)~=~A(x-h)^2+k$$

To make the animation shown below, two of the parameters were set to constants, and the other parameter was animated by pressing the "play" button. That animated parameter varies between $-10$ and $10$ by default.

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(3,3)}
n = 50
xx = seq(-11,11,0.01)
for(i in 1:n){
    Ai = A
    hi = h
    ki = k
    if(i<n/2){
        t = i/(n/2)*20-10
    } else {
        t = 10-(i-n/2)/(n/2)*20
    }
    if(whichvaries==1){
        Ai = t
    }
    if(whichvaries==2){
        hi = t
    }
    if(whichvaries==3){
        ki = t
    }
    par(pty="s",mar=c(0,0,0,0))
    plot(xx,Ai*(xx-hi)^2+ki,"l",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in 1:10){
        if(i%%5==0){
            abline(h=i,col="black")
            abline(h=-i,col="black")
            abline(v=i,col="black")
            abline(v=-i,col="black")
        } else {
            abline(h=i,col="lightgrey")
            abline(h=-i,col="lightgrey")
            abline(v=i,col="lightgrey")
            abline(v=-i,col="lightgrey")
        }
        
    }
    arrows(0,10.5,0,-10.5,0.05,10,3,lwd=2)
    arrows(10.5,0,-10.5,0,0.05,10,3,lwd=2)
    polygon(c(9.5,10.5,10.5,9.5),c(-0.2,-0.2,-0.8,-0.8),col="white",border = "white")
    text(10,-0.5,"10",cex=0.5)
    polygon(c(-0.2,-0.2,-0.8,-0.8),c(9.5,10.5,10.5,9.5),col="white",border = "white")
    text(-0.5,10,"10",cex=0.5)
    polygon(c(-9.5,-10.5,-10.5,-9.5),c(-0.2,-0.2,-0.8,-0.8),col="white",border = "white")
    text(-10,-0.5,"-10",cex=0.5)
    polygon(c(-0.2,-0.2,-0.8,-0.8),c(-9.5,-10.5,-10.5,-9.5),col="white",border = "white")
    text(-0.5,-10,"-10",cex=0.5)
    polygon(c(4.5,5.5,5.5,4.5),c(-0.2,-0.2,-0.8,-0.8),col="white",border = "white")
    text(5,-0.5,"5",cex=0.5)
    polygon(c(-0.2,-0.2,-0.8,-0.8),c(4.5,5.5,5.5,4.5),col="white",border = "white")
    text(-0.5,5,"5",cex=0.5)
    polygon(c(-4.5,-5.5,-5.5,-4.5),c(-0.2,-0.2,-0.8,-0.8),col="white",border = "white")
    text(-5,-0.5,"-5",cex=0.5)
    polygon(c(-0.2,-0.2,-0.8,-0.8),c(-4.5,-5.5,-5.5,-4.5),col="white",border = "white")
    text(-0.5,-5,"-5",cex=0.5)
    lines(xx,Ai*(xx-hi)^2+ki,col="red",lwd=3)
}
```
\

Find the value of each parameter, or if the parameter varies then choose "animated".

* $A~=~$ ##ANSWER1##
* $h~=~$ ##ANSWER2##
* $k~=~$ ##ANSWER3##

Answerlist
--------

```{r,echo=F}
alh = paste0("* ",chh,collapse="\n")
alk = paste0("* ",chk,collapse="\n")
```

* animated
* -1
* 1
* animated
`r alh`
* animated
`r alk`


Solution
========

```{r, echo=F}

numA = A
numh = h
numk = k

if(whichvaries==1){
    numA = "animated"
} else if(whichvaries==2){
    numh = "animated"
} else if(whichvaries==3){
    numk = "animated"
}

```

* $A=$ `r numA`
* $h=$ `r numh`
* $k=$ `r numk`

Try it out in Desmos!


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r solA`|`r solh`|`r solk`
exname: vertex_form_animation