```{r data generation, echo = FALSE, results = "hide"}
n = 6
while(T){
    xs = sort(sample(10:999,n))/10
    ys = signif(sqrt(xs),3)
    x2 = round(ys^2,1)
    if(min(diff(xs))>0.5 && sum(xs==x2)==n){break}
}

ans = c(ys[1],xs[2],ys[3],xs[4],ys[5],xs[6])
dels = c(0.02,0.2,0.02,0.2,0.02,0.2)

als = character()
sols = character()

for(i in 1:length(ans)){
    an = ans[i]
    ach = an+(sample(-5:0,1)+0:5)*dels[i]
    if(i%%2==1){
        al = paste0("* ",format(ach,nsmall = 2),collapse="\n")
    } else {
        al = paste0("* ",format(ach,nsmall = 1),collapse="\n")
    }
    als = c(als,al)
    sols = c(sols,paste0(1*(ach==an),collapse=""))
}
als = paste0(als,collapse="\n")
sols = paste0(sols,collapse="|")

```

Question
========

Consider the $y=\sqrt{x}$ curve shown below (the square root function). There are `r n` points along the curve, find the missing coordinates of those points in the table.

```{r,echo=F,fig.dim=c(6,4)}
library(latex2exp)
x = seq(0,100,0.01)
y = sqrt(x)
plot(x,y,"l",xlim=c(0,100),ylim=c(0,10),lwd=3,col="blue",xlab="x",ylab=TeX("$y=\\sqrt{x}$"))
arrows(-3,0,103,0,0.1,10,2)
arrows(0,-0.3,0,10.3,0.1,10,2)
lines(x,y,lwd=3,col="blue")
points(xs,ys,pch=20,col="black",cex=1.3)
points(xs,ys,pch=20,col="red")
```
\

| $x$ | $y=\sqrt{x}$ |
|:---:|:---:|
| `r xs[1]` | ##ANSWER1## |
| ##ANSWER2## | `r ys[2]` |
| `r xs[3]` | ##ANSWER3## |
| ##ANSWER4## | `r ys[4]` |
| `r xs[5]` | ##ANSWER5## |
| ##ANSWER6## | `r ys[6]` |


Answerlist
--------

`r als`


Solution
========

To find $y$, use square root or raising to the power of $1/2$. To find $x$, square (raise to the power of $2$).

| $x$ | $y=\sqrt{x}$ |
|:---:|:---:|
| `r xs[1]` | $\sqrt{`r xs[1]`}=(`r xs[1]`)^{1/2}\approx`r ys[1]`$ |
| $`r ys[2]`^2=`r xs[2]`$ | `r ys[2]` |
| `r xs[3]` | $\sqrt{`r xs[3]`}=(`r xs[3]`)^{1/2}\approx`r ys[3]`$ |
| $`r ys[4]`^2=`r xs[4]`$ | `r ys[4]` |
| `r xs[5]` | $\sqrt{`r xs[5]`}=(`r xs[5]`)^{1/2}\approx`r ys[5]`$ |
| $`r ys[6]`^2=`r xs[6]`$ | `r ys[6]` |


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n),collapse="|")`
exsolution: `r sols`
exname: points_on_sqrtx