```{r data generation, echo = FALSE, results = "hide"}
sm = 5 #shift max
hk = sample(1:sm,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
eq = paste0("\\sqrt{x+",-h,"}+",k,collapse="")
eq = gsub("+-","-",eq,fixed=T)

abs = c(0,0,1,1,4,2,9,3,16,4,25,5,36,6)
als = character()
sols = character()
for(i in 1:length(abs)){
    ab = abs[i]
    ach = (ab-sm):(ab+sm)
    als = c(als,paste0("* ",ach,collapse="\n"))
    if(i%%2==1){
        sols = c(sols,paste0(1*((-sm:sm)==h),collapse=""))
    } else {
        sols = c(sols,paste0(1*((-sm:sm)==k),collapse=""))
    }
}
al = paste0(als,collapse="\n")

```

Question
========

The function $f(x)~=~\sqrt{x}$ has some integer input-output pairs (see [Diophantine equations](https://en.wikipedia.org/wiki/Diophantine_equation)). The first 7 are listed and graphed below.

| $x$ | $y=f(x)$ |
|:---:|:---:|
| 0 | 0 |
| 1 | 1 |
| 4 | 2 |
| 9 | 3 |
| 16 | 4 |
| 25 | 5 |
| 36 | 6 |

```{r,echo=F,fig.dim=c(8,2)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,40),ylim=c(0,10),axes=F,ann=F)
for(i in 0:40){
    lines(c(i,i),c(0,10),lwd=0.8,col="lightgrey")
}
for(i in 0:10){
    lines(c(0,40),c(i,i),lwd=0.8,col="lightgrey")
}
for(i in seq(0,40,5)){
    lines(c(i,i),c(0,10),lwd=1.2,col="darkgrey")
}
for(i in seq(0,10,5)){
    lines(c(0,40),c(i,i),lwd=1.2,col="darkgrey")
}
arrows(0,0,40,0,0.1,10,2,lwd=2)
arrows(0,0,0,10,0.1,10,2,lwd=2)
x = seq(0,40,0.01)
y = sqrt(x)
lines(x,y,lwd=3,col="red")
xp = c(0,1,4,9,16,25,36)
yp = sqrt(xp)
points(xp,yp,pch=20,cex=1.2)

```
\

A shifted function $g$ is defined as $g(x)=`r eq`$. Find the corresponding points of integer input and integer output on function $g$.

| $x$ | $y=g(x)$ |
|:---:|:---:|
| ##ANSWER1## | ##ANSWER2## |
| ##ANSWER3## | ##ANSWER4## |
| ##ANSWER5## | ##ANSWER6## |
| ##ANSWER7## | ##ANSWER8## |
| ##ANSWER9## | ##ANSWER10## |
| ##ANSWER11## | ##ANSWER12## |
| ##ANSWER13## | ##ANSWER14## |

Answerlist
--------

`r al`


Solution
========

Function $g$ can be thought of a shifted version of $f$, shifted horizontally by `r h` and vertically by `r k`.

### Graph of function $g$

```{r,echo=F,fig.dim=c(10,4)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,45),ylim=c(-5,15),axes=F,ann=F)
for(i in -5:45){
    lines(c(i,i),c(-5,15),lwd=0.8,col="lightgrey")
}
for(i in -5:15){
    lines(c(-5,45),c(i,i),lwd=0.8,col="lightgrey")
}
for(i in seq(-5,45,5)){
    lines(c(i,i),c(-5,15),lwd=1.2,col="darkgrey")
}
for(i in seq(-5,15,5)){
    lines(c(-5,45),c(i,i),lwd=1.2,col="darkgrey")
}
arrows(-5,0,45,0,0.1,10,2,lwd=2)
arrows(0,-5,0,15,0.1,10,2,lwd=2)
x = seq(0,60,0.01)
y = sqrt(x)
x2 = x+h
y2 = y+k
x3 = x2[x2>-5]
y3 = y2[x2>-5]
x4 = x3[x3<45]
y4 = y3[x3<45]
lines(x4,y4,lwd=3,col="blue")
xp = c(0,1,4,9,16,25,36)+h
yp = sqrt(xp-h)+k
for(i in 2:length(xp)){
    lines(c(xp[i-1],xp[i],xp[i]),c(yp[i-1],yp[i-1],yp[i]),col="purple")
    text(mean(xp[(i-1):i]),yp[i-1]-0.5,paste0("+",i*2-3),col="purple")
}
text(h,k+4.5,paste0("(",h,", ",k,")"),col="red",cex=1.4)
arrows(h,k+3.5,h,k+0.5,length=0.1,angle=10,lwd=3,col="red")

points(xp,yp,pch=20,cex=1.2)

```
\

| $x$ | $y=f(x)$ |
|:---:|:---:|
| `r 0+h` | `r 0+k` |
| `r 1+h` | `r 1+k` |
| `r 4+h` | `r 2+k` |
| `r 9+h` | `r 3+k` |
| `r 16+h` | `r 4+k` |
| `r 25+h` | `r 5+k` |
| `r 36+h` | `r 6+k` |




Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",14),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: sqrt_shift_points