```{r data generation, echo = FALSE, results = "hide"}
n = 6
while(T){
    xs = sort(sample(-999:999,n))
    ys = round(sign(xs)*abs(xs)^(1/3),2)
    x2 = round(ys^3)
    print(x2)
    if(min(diff(xs))>40 && sum(xs==x2)==n){break}
}

ans = c(ys[1],xs[2],ys[3],xs[4],ys[5],xs[6])
dels = c(0.02,2,0.02,2,0.02,2)

als = character()
sols = character()

for(i in 1:length(ans)){
    an = ans[i]
    ach = an+(sample(-5:0,1)+0:5)*dels[i]
    if(i%%2==1){
        al = paste0("* ",format(ach,nsmall = 2),collapse="\n")
    } else {
        al = paste0("* ",format(ach,nsmall = 0),collapse="\n")
    }
    als = c(als,al)
    sols = c(sols,paste0(1*(ach==an),collapse=""))
}
als = paste0(als,collapse="\n")
sols = paste0(sols,collapse="|")

```

Question
========

Consider the $y=\sqrt[3]{x}$ curve shown below (the cube root function). There are `r n` points along the curve, find the missing coordinates of those points in the table.

```{r,echo=F,fig.dim=c(6,4)}
library(latex2exp)
x = seq(-1000,1000,0.1)
y = sign(x)*abs(x)^(1/3)
plot(x,y,"l",xlim=c(-1000,1000),ylim=c(-10,10),lwd=3,col="blue",xlab="x",ylab=TeX("$y=\\sqrt[3]{x}$"))
arrows(-1030,0,1030,0,0.1,10,2)
arrows(0,-10.3,0,10.3,0.1,10,2)
lines(x,y,lwd=3,col="blue")
points(xs,ys,pch=20,col="black",cex=1.3)
points(xs,ys,pch=20,col="red")
```
\

| $x$ | $y=\sqrt[3]{x}$ |
|:---:|:---:|
| `r xs[1]` | ##ANSWER1## |
| ##ANSWER2## | `r ys[2]` |
| `r xs[3]` | ##ANSWER3## |
| ##ANSWER4## | `r ys[4]` |
| `r xs[5]` | ##ANSWER5## |
| ##ANSWER6## | `r ys[6]` |


Answerlist
--------

`r als`


Solution
========

To find $y$, use cube root or raising to the power of $1/3$. To find $x$, cube (raise to the power of $3$).

| $x$ | $y=\sqrt[3]{x}$ |
|:---:|:---:|
| `r xs[1]` | $\sqrt[3]{`r xs[1]`}=(`r xs[1]`)^{1/3}\approx`r ys[1]`$ |
| $(`r ys[2]`)^3=`r xs[2]`$ | `r ys[2]` |
| `r xs[3]` | $\sqrt[3]{`r xs[3]`}=(`r xs[3]`)^{1/3}\approx`r ys[3]`$ |
| $(`r ys[4]`)^3=`r xs[4]`$ | `r ys[4]` |
| `r xs[5]` | $\sqrt[3]{`r xs[5]`}=(`r xs[5]`)^{1/3}\approx`r ys[5]`$ |
| $(`r ys[6]`)^3=`r xs[6]`$ | `r ys[6]` |


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n),collapse="|")`
exsolution: `r sols`
exname: points_on_sqrtx