```{r data generation, echo = FALSE, results = "hide"}
n = 4 # make this an even number probably... 6 is good
hk = sample(2:5,2)

cfs = list()
eqs = character()
eeqs = character()
sus = character()

i = 0
while(i<n){
    hki = hk*sample(c(-1,1),2,T)
    h = hki[1]
    k = hki[2]
    ab = sample(c(-1,1),2,T)
    a = ab[1]
    b = ab[2]
    cf = c(ab,hki)
    su = paste0(h,k,a*b,collapse="_")
    if(ab[1]==-1 && ab[2]==-1){
        eq = paste0("-\\sqrt[3]{-(x+",-h,")}+",k,collapse="")
        eq = gsub("+-","-",eq,fixed=T)
        eeq = paste0("(-1)\\sqrt[3]{(-1)(x+(",-h,"))}+(",k,")",collapse="")
        
    }
    if(ab[1]==1 && ab[2]==-1){
        eq = paste0("\\sqrt[3]{-(x+",-h,")}+",k,collapse="")
        eq = gsub("+-","-",eq,fixed=T)
        eeq = paste0("(1)\\sqrt[3]{(-1)(x+(",-h,"))}+(",k,")",collapse="")
    }
    if(ab[1]==-1 && ab[2]==1){
        eq = paste0("-\\sqrt[3]{x+",-h,"}+",k,collapse="")
        eq = gsub("+-","-",eq,fixed=T)
        eeq = paste0("(-1)\\sqrt[3]{(1)(x+(",-h,"))}+(",k,")",collapse="")
    }
    if(ab[1]==1 && ab[2]==1){
        eq = paste0("\\sqrt[3]{x+",-h,"}+",k,collapse="")
        eq = gsub("+-","-",eq,fixed=T)
        eeq = paste0("(1)\\sqrt[3]{(1)(x+(",-h,"))}+(",k,")",collapse="")
    }
    if(!(su%in%sus)){
        i = i+1
        cfs[[i]] = cf
        eqs[[i]] = eq
        eeqs[[i]] = eeq
        sus = c(sus,su)
    }
}

eqord = sample(1:n)

qlis = character()
sols = character()

expls = character()

for(i in 1:n){
    eq = eqs[[eqord[i]]]
    eeq = eeqs[[eqord[i]]]
    qlis = c(qlis, paste0(i,". Equation $y=",eq,"$ matches graph ##ANSWER",i,"##."))
    sols = c(sols,paste0(1*(eqord[i]==1:n),collapse=""))
    cf = cfs[[eqord[i]]]
    a = cf[1]
    b = cf[2]
    h = cf[3]
    k = cf[4]
    if(a>0 && b>0){
        wrd1="NOT"
        wrd2="NOT"
        wrd3="Because there are no reflections, the curve is in the original increasing orientation."
    } else if(a<0 && b>0){
        wrd1=""
        wrd2="NOT"
        wrd3="For the cube-root function, reflecting either horizontally or vertically results in a decreasing orientation."
    } else if(a>0 && b<0){
        wrd1="NOT"
        wrd2=""
        wrd3="For the cube-root function, reflecting either horizontally or vertically results in a decreasing orientation."
    } else if(a<0 && b<0){
        wrd1=""
        wrd2=""
        wrd3="For the cube-root function, reflecting both horizontally and vertically results in a return to the original increasing orientation."
    }
    expl = paste0("### Equation ",i,"\n\n The curve's equation is $y=",eq,"$\n\nRewrite the equation with explicit parameters.\n\n$y=",eeq,"$\n\nSo, we can more easily see the values of the parameters.\n\n$$m=",a,"$$\n$$n=",b,"$$\n$$p=",-h,"$$\n$$q=",k,"$$This tells us the new inflection point is at $(",h,",",k,")$. We also know there is ",wrd1," a vertical reflection (because $m=",a,"$), and there is ",wrd2," a horizontal reflection (because $n=",b,"$). ",wrd3," Thus, the correct graph is graph ",LETTERS[which(eqord[i]==1:n)],".")
    expls = c(expls,expl)
}

ach = LETTERS[1:n]
al = paste0("* ",ach,collapse="\n")
al = paste0(rep(al,n),collapse="\n")

```

Question
========

Consider the $y=\sqrt[3]{x}$ curve (cube-root function) shown below. In the context of transforming functions, a very simple function is often called a "parent" function.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,3,0),
    pty="s")
library(latex2exp)
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
mtext(TeX("$y=\\sqrt[3]{x}$"),3)
for(j in -10:10){
    lines(c(j,j),c(-10,10),col="lightgrey",cex=0.8)
    lines(c(-10,10),c(j,j),col="lightgrey",cex=0.8)
}
for(j in seq(-10,10,5)){
    lines(c(j,j),c(-10,10),col="darkgrey",cex=1.2)
    lines(c(-10,10),c(j,j),col="darkgrey",cex=1.2)
}
arrows(-10.5,0,10.5,0,0.1,10,3,lwd=2)
arrows(0,-10.5,0,10.5,0.1,10,3,lwd=2)
text(10,-0.5,10,cex=0.7)
text(-10,-0.5,-10,cex=0.7)
text(10,0.5,"x",cex=0.7)
text(-0.5,10,10,cex=0.7)
text(-0.5,-10,-10,cex=0.7)
text(0.5,10,"y",cex=0.7)

x = seq(-10,10,0.01)
y = sign(x)*abs(x)^(1/3)
lines(x,y,lwd=3,col="blue")
```
\

The following `r n` graphs are made by translating and reflecting the $y=\sqrt[3]{x}$ curve. So each one is a different daughter function, made by altering the parent function.

```{r,echo=F,fig.dim=c(8,n*4/2)}
par(mar=c(0,0,3,0),
    mfrow=c(ceiling(n/2),2),
    pty="s")

for(i in 1:n){
    cf = cfs[[i]]
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    mtext(LETTERS[i],3)
    for(j in -10:10){
        lines(c(j,j),c(-10,10),col="lightgrey",cex=0.8)
        lines(c(-10,10),c(j,j),col="lightgrey",cex=0.8)
    }
    for(j in seq(-10,10,5)){
        lines(c(j,j),c(-10,10),col="darkgrey",cex=1.2)
        lines(c(-10,10),c(j,j),col="darkgrey",cex=1.2)
    }
    arrows(-10.5,0,10.5,0,0.1,10,3,lwd=2)
    arrows(0,-10.5,0,10.5,0.1,10,3,lwd=2)
    text(10,-0.5,10,cex=0.7)
    text(-10,-0.5,-10,cex=0.7)
    text(10,0.5,"x",cex=0.7)
    text(-0.5,10,10,cex=0.7)
    text(-0.5,-10,-10,cex=0.7)
    text(0.5,10,"y",cex=0.7)
    
    x = seq(-10,10,0.01)
    y = sign(x)*abs(x)^(1/3)
    lines(x,y,lty=3)
    x = seq(-20,20,0.01)
    y = sign(x)*abs(x)^(1/3)
    x = x*sign(cf[2])
    y = y*sign(cf[1])
    x = x+cf[3]
    y = y+cf[4]
    x2 = x[abs(x)<=10]
    y2 = y[abs(x)<=10]
    x3 = x2[abs(y)<=10]
    y3 = y2[abs(y)<=10]
    lines(x3,y3,lwd=3,col="red")
}
```
\

Match the `r n` graphs with the equations.

`r paste0(qlis,collapse="\n")`


Answerlist
--------

`r al`


Solution
========

The origin of the parent cube-root function is called the "inflection point". It is useful to identify where the inflection point gets moved to.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,3,0),
    pty="s")
library(latex2exp)
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
mtext(TeX("$y=\\sqrt[3]{x}$"),3)
for(j in -10:10){
    lines(c(j,j),c(-10,10),col="lightgrey",cex=0.8)
    lines(c(-10,10),c(j,j),col="lightgrey",cex=0.8)
}
for(j in seq(-10,10,5)){
    lines(c(j,j),c(-10,10),col="darkgrey",cex=1.2)
    lines(c(-10,10),c(j,j),col="darkgrey",cex=1.2)
}
arrows(-10.5,0,10.5,0,0.1,10,3,lwd=2)
arrows(0,-10.5,0,10.5,0.1,10,3,lwd=2)
text(10,-0.5,10,cex=0.7)
text(-10,-0.5,-10,cex=0.7)
text(10,0.5,"x",cex=0.7)
text(-0.5,10,10,cex=0.7)
text(-0.5,-10,-10,cex=0.7)
text(0.5,10,"y",cex=0.7)

x = seq(-10,10,0.01)
y = sign(x)*abs(x)^(1/3)
lines(x,y,lwd=3,col="blue")

arrows(-3,3,-0.5,0.5,0.1,10,lwd=4)
points(0,0,pch=20,cex=1.3,col="blue")
text(-3.5,3.5,"inflection point")
```
\

* Operations inside the function (under the radical) change the $x$ values, so they cause horizontal transformations.
* Operations outside the function change the $y$ values, so they cause vertical transformations.
* Addition/subtraction causes a translation (shift). Horizontal shifts are counterintuitive.
* Multiplying by $-1$ causes a reflection.

You can account for all the transformations with 4 parameters ($m$, $n$, $p$, and $q$).

$$y=m\sqrt[3]{n(x+p)}+q$$

* The parameter $m$ is either $-1$ or $1$. If $m=-1$, then the curve is reflected vertically, so the curve goes down from the starting point (instead of up).
* The parameter $n$ is either $-1$ or $1$. If $n=-1$, then the curve is reflected horizontally, so the curve goes left from the starting point (instead of right).
* The parameter $p$ shifts the curve horizontally.
* The parameter $q$ shifts the curve vertically.
* The starting point will be at $(-p,q)$.


`r paste0(expls,collapse="\n\n")`


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: translate_flip_cbrt