```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

while(T){
    xf = sample(1:10,3)*sample(c(-1,1),3,T)
    xi = xf[1]
    xh = xf[2]
    xv = xf[3]
    yh = (xh-xi)/(xh-xv)
    if(yh%%1==0 && abs(yh)>0 && abs(yh)<=10){break}
}

ex1 = paste0("\\frac{",pfix(c(1,-xi-xh,xi*xh),2:0),"}{",pfix(c(1,-xv-xh,xv*xh),2:0),"}",collapse="")
ex1 = gsub("+-","-",ex1,fixed=T)

ratexp = paste0("\\frac{(x-",min(c(xi,xh)),")(x-",max(c(xi,xh)),")}{(x-",min(c(xv,xh)),")(x-",max(c(xv,xh)),")}",collapse="")
ratexp = gsub("--","+",ratexp,fixed=T)

holefac = paste0("x-",xh,collapse="")
holefac = gsub("--","+",holefac,fixed=T)

gx = paste0("\\frac{x-",xi,"}{x-",xv,"}",collapse="")
gx = gsub("--","+",gx,fixed=T)

ach = -10:10
al = paste0("* ",ach,collapse="\n")
sol1 = paste0(1*(ach==xh),collapse="")
sol2 = paste0(1*(ach==yh),collapse="")


```

Question
========

Let rational function $f$ be defined below.

$$f(x)~=~`r ex1`$$

Find the $(x,y)$-coordinates of the hole (removable discontinuity) on the curve $y=f(x)$.

* The hole is at:

(##ANSWER1##, ##ANSWER2##)

Answerlist
--------

`r al`
`r al`



Solution
========

Factor the numerator, and factor the denominator.

$$f(x)~=~`r ratexp`$$

Notice, the factor $(`r holefac`)$ is in both numerator and denominator. So, the hole is at $x=`r xh`$. Create a new function $g$ with a filled in hole by eliminating common factors.

$$g(x)=`r gx`$$

Plug in $x=`r xh`$ into function $g$.

$$g(`r xh`)~=~`r gsub("x",xh,gx,fixed=T)`~=~\frac{`r xh-xi`}{`r xh-xv`}~=~`r yh`$$

Thus, the hole of $y=f(x)$ is at point $(`r xh`,`r yh`)$.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
x = seq(-10,10,0.01)
x = x[x!=xv]
x = x[x!=xh]
y = (x-xi)/(x-xv)

plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.3)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.3)
}
arrows(-10,0,10,0,0.1,10,3,lwd=2)
arrows(0,-10,0,10,0.1,10,3,lwd=2)
text(10,-0.5,"10")
text(-0.5,10,"10")
text(10,0.5,"x")
text(0.5,10,"y")


x1 = x[x<xv]
y1 = y[x<xv]
x2 = x[x>xv]
y2 = y[x>xv]

lines(x1,y1,col="red",lwd=2)
lines(x2,y2,col="red",lwd=2)
abline(v=xv,lty=3,col="red")
points(xh,yh,col="red",pch=20,cex=2)
points(xh,yh,col="white",pch=20,cex=1.2)


if(xv>0){
    place = "topleft"
} else {
    place = "topright"
}

legend(place,"y = f(x)",col="red",lwd=3)

```
\

Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: find_rational_hole