```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

while(T){
    xf = sample(1:10,3)*sample(c(-1,1),3,T)
    xi = xf[1]
    xh = xf[2]
    xv = xf[3]
    yh = (xh-xi)/(xh-xv)
    h = xh
    k = yh
    b = k-h
    if(yh%%1==0 && abs(yh)>0 && abs(yh)<=10 && abs(b)<20 && b!=-xi && b!=-xv && b!=0){break}
}

ex1 = paste0("\\frac{",pfix(c(1,-xi-xh,xi*xh),2:0),"}{",pfix(c(1,-xv-xh,xv*xh),2:0),"}",collapse="")
ex1 = gsub("+-","-",ex1,fixed=T)

ratexp = paste0("\\frac{(x-",min(c(xi,xh)),")(x-",max(c(xi,xh)),")}{(x-",min(c(xv,xh)),")(x-",max(c(xv,xh)),")}",collapse="")
ratexp = gsub("--","+",ratexp,fixed=T)

holefac = paste0("x-",xh,collapse="")
holefac = gsub("--","+",holefac,fixed=T)

gx = paste0("\\frac{x-",xi,"}{x-",xv,"}",collapse="")
gx = gsub("--","+",gx,fixed=T)

ach = -10:10
al = paste0("* ",ach,collapse="\n")
sol1 = paste0(1*(ach==xh),collapse="")
sol2 = paste0(1*(ach==yh),collapse="")


```

Question
========

Let rational function $f$ be defined below.

$$f(x)~=~`r ex1`$$

Let linear function $L$ have a slope of 1 and an unknown parameter ($b$) dictating the $y$-intercept.

$$L(x)~=~x+B$$

Both curves, $y=f(x)$ and $y=L(x)$, are graphed. The hole of function $f$ is at point $(h,k)$, and the point $(h,k)$ lies on the line, so $k=L(h)$. This implies that the equation $f(x)=L(x)$ would have an extraneous solution of $x=h$.

Find the unknown parameter $B$.


Solution
========

Factor the numerator, and factor the denominator.

$$f(x)~=~`r ratexp`$$

Notice, the factor $(`r holefac`)$ is in both numerator and denominator. So, the hole is at $x=`r xh`$. Create a new function $g$ with a filled in hole by eliminating common factors.

$$g(x)=`r gx`$$

Plug in $x=`r xh`$ into function $g$.

$$g(`r xh`)~=~`r gsub("x",xh,gx,fixed=T)`~=~\frac{`r xh-xi`}{`r xh-xv`}~=~`r yh`$$

Thus, the hole of $y=f(x)$ is at point $(`r xh`,`r yh`)$. This tells us that $`r k`=L(`r h`)$.

$$`r k`=`r pfix(c(h,"B"),c(0,0))`$$

Subtract `r h` from both sides.

$$`r b`=B$$
$$B=`r b`$$


Notices this makes the line go through the hole.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
x = seq(-10,10,0.01)
x = x[x!=xv]
x = x[x!=xh]
y = (x-xi)/(x-xv)

plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.3)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.3)
}
arrows(-10,0,10,0,0.1,10,3,lwd=2)
arrows(0,-10,0,10,0.1,10,3,lwd=2)
text(10,-0.5,"10")
text(-0.5,10,"10")
text(10,0.5,"x")
text(0.5,10,"y")


x1 = x[x<xv]
y1 = y[x<xv]
x2 = x[x>xv]
y2 = y[x>xv]

lines(x1,y1,col="red",lwd=2)
lines(x2,y2,col="red",lwd=2)
abline(v=xv,lty=3,col="red")
points(xh,yh,col="red",pch=20,cex=2)
points(xh,yh,col="white",pch=20,cex=1.2)

xx = seq(-10,10,1)
yy = xx+b
xx = xx[abs(yy)<=10]
yy = yy[abs(yy)<=10]
lines(xx,yy,col="blue",lwd=2)


if(xv>0){
    place = "topleft"
} else {
    place = "topright"
}

legend(place,
       c("y = f(x)","y = L(x)"),
       col=c("red","blue"),
       lwd=c(3,3))

```
\


You might find it interesting to use algebraic manipulations to solve $f(x)=L(x)$, in order to see that you'd be led to an extraneous solution.

$$`r ex1`~=~`r pfix(c(1,b),1:0)`$$

Factor the left side.

$$`r ratexp`~=~`r pfix(c(1,b),1:0)`$$

Simplify by eliminating common factors.

$$`r gx`~=~`r pfix(c(1,b),1:0)`$$

```{r,echo=F}
num = paste0("x-",xi,collapse="")
num = gsub("--","+",num,fixed=T)
den = paste0("x-",xv,collapse="")
den = gsub("--","+",den,fixed=T)
```

Multiply both sides by `r den`.

$$`r num`~=~(`r pfix(c(1,b),1:0)`)(`r den`)$$

FOIL.


$$`r num`~=~`r pfix(c(1,-xv+b,-xv*b),2:0)`$$

Subtract $(`r num`)$ from both sides.

$$0~=~`r pfix(c(1,-xv+b-1,-xv*b+xi),2:0)`$$

```{r,echo=F}
aa = 1
bb = -xv+b-1
cc = -xv*b+xi

root1 = (-bb-sqrt(bb^2-4*aa*cc))/(2*aa)
root2 = (-bb+sqrt(bb^2-4*aa*cc))/(2*aa)
```

From there you can use quadratic formula.

$$x~=~\frac{-(`r bb`)\pm\sqrt{(`r bb`)^2-4(`r aa`)(`r cc`)}}{2(`r aa`)}$$

Which provides two solutions, $x=`r root1`$ and $x=`r root2`$. However, we know that $x=`r xh`$ cannot be a solution, because $f(`r xh`)$ is undefined! Thus, we see that if $L(x)=`r pfix(c(1,b),1:0)`$, then we get an extraneous solution to $f(x)=L(x)$.

This reinforces the implications of having $B=`r b`$, which makes the line go through the hole.


Meta-information
============
extype: num
exsolution: `r b`
exname: line_thru_rational_hole