```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
pts = list(c(3, 4, 5),
           c(6, 8, 10),
           c(9, 12, 15),
           c(12, 16, 20),
           c(15, 20, 25),
           c(18, 24, 30),
           c(21, 28, 35),
           c(24, 32, 40),
           c(27, 36, 45),
           c(30, 40, 50),
           c(33, 44, 55),
           c(36, 48, 60),
           c(39, 52, 65),
           c(42, 56, 70),
           c(45, 60, 75),
           c(48, 64, 80),
           c(51, 68, 85),
           c(54, 72, 90),
           c(57, 76, 95),
           c(60, 80, 100),
           c(5, 12, 13),
           c(10, 24, 26),
           c(15, 36, 39),
           c(20, 48, 52),
           c(25, 60, 65),
           c(30, 72, 78),
           c(35, 84, 91),
           c(8, 15, 17),
           c(16, 30, 34),
           c(24, 45, 51),
           c(32, 60, 68),
           c(40, 75, 85),
           c(7, 24, 25),
           c(14, 48, 50),
           c(21, 72, 75),
           c(28, 96, 100),
           c(20, 21, 29),
           c(40, 42, 58),
           c(60, 63, 87),
           c(12, 35, 37),
           c(24, 70, 74),
           c(9, 40, 41),
           c(18, 80, 82),
           c(28, 45, 53),
           c(11, 60, 61),
           c(16, 63, 65),
           c(33, 56, 65),
           c(48, 55, 73),
           c(13, 84, 85),
           c(36, 77, 85),
           c(39, 80, 89),
           c(65, 72, 97))

hk = sample(91:109,2)
h = hk[1]
k = hk[2]

pnts = list()
ds = numeric()
as = numeric()

da = function(a1,a2){
    da1 = abs(a1-a2)
    da2 = abs(a1+2*pi-a2)%%(2*pi)
    da3 = abs(a2+2*pi-a1)%%(2*pi)
    return(min(c(da1,da2,da3)))
}

while(length(pnts)<5){
    pti = sample(1:length(pts),1)
    pt = pts[[pti]]
    dxdy = sample(pt[1:2])*sample(c(-1,1),2,T)
    x = h+dxdy[1]
    y = k+dxdy[2]
    a = (atan2(dxdy[2],dxdy[1])+2*pi)%%(2*pi)
    das = numeric()
    if(length(pnts)>1){
        for(ass in as){
            das = c(das,da(a,ass))
        }
    }
    
    if(x>0 && x<200 && y>0 && y<200 && min(das)>pi/12 && min(diff(sort(c(pt[3],ds))))>3){
        ds = c(ds,pt[3])
        as = c(as,a)
        pnts[[length(pnts)+1]] = c(x,y)
    }
}

als = character()
sols = character()
for(d in ds){
    ach = d-sample(0:5,1)+0:5
    als = c(als,paste0("* ",ach,collapse="\n"))
    sols = c(sols,paste0(1*(ach==d),collapse=""))
}

als = paste0(als,collapse="\n")
sols = paste0(sols,collapse="|")

```

Question
========

The [2D distance formula](https://en.wikipedia.org/wiki/Euclidean_distance#Two_dimensions) is an equivalent equation to the [Pythagorean equation](https://en.wikipedia.org/wiki/Pythagorean_theorem). When finding distance between two points on an $xy$-plane, it can be helpful to imagine a [right triangle](https://en.wikipedia.org/wiki/Right_triangle) with its legs horizontal and vertical, and its hypotenuse connecting the points. The length of the hypotenuse is the square root of the sum of the squares of the legs' lengths. Each leg's length is found by taking an absolute difference corresponding coordinates; for example $|x_2-x_1|$ is the length of the horizontal leg, and $|y_2-y_1|$ is the length of the vertical leg.

A square field is 200 feet by 200 feet. The field is marked with a grid pattern, so the Southwest corner is at point $(0,0)$ and the Northeast corner is at point $(200,200)$. Near the middle, at position $(`r h`, `r k`)$ is a beacon, marked as a large bright-red dot. On the field are 5 players; their positions are listed in the table below. Find how far each player is from the beacon. 

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,200),ylim=c(-10,200),axes=F,ann=F)
for(i in seq(0,200,10)){
    lines(c(0,200),c(i,i),col="lightgrey",lwd=0.8)
    lines(c(i,i),c(0,200),col="lightgrey",lwd=0.8)
}
for(i in seq(0,200,50)){
    lines(c(0,200),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(0,200),col="darkgrey",lwd=1.2)
}
arrows(0,-10,0,200,0.1,10,2,lwd=3)
arrows(-10,0,200,0,0.1,10,2,lwd=3)
text(100,-5,"100")
text(200,-5,"200")
text(-2,100,"100",adj=1)
text(-2,200,"200",adj=1)

for(i in 1:length(pnts)){
    points(pnts[[i]][1],pnts[[i]][2],pch=20,cex=1.4,col=hsv((i-1)/length(pnts),1,0.6))
    lines(c(h,pnts[[i]][1]),c(k,pnts[[i]][2]),col=hsv((i-1)/length(pnts),1,0.6))
}
points(h,k,col="red",cex=1.7,pch=20)

```
\

I would recommend setting this up in Desmos using $d=\sqrt{(x_2-`r h`)^2+(y_2-`r k`)^2}$ and using sliders for $x_2$ and $y_2$.

| Player | Position | Distance to beacon (ft) |
|:---:|:---:|:---:|
| 1 | (`r pnts[[1]][1]`,`r pnts[[1]][2]`) | ##ANSWER1## |
| 2 | (`r pnts[[2]][1]`,`r pnts[[2]][2]`) | ##ANSWER2## |
| 3 | (`r pnts[[3]][1]`,`r pnts[[3]][2]`) | ##ANSWER3## |
| 4 | (`r pnts[[4]][1]`,`r pnts[[4]][2]`) | ##ANSWER4## |
| 5 | (`r pnts[[5]][1]`,`r pnts[[5]][2]`) | ##ANSWER5## | 

Answerlist
--------

`r als`

Solution
========

I would recommend setting this up in Desmos using $d=\sqrt{(x_2-`r h`)^2+(y_2-`r k`)^2}$ and using sliders for $x_2$ and $y_2$.

```{r,echo=F,results='asis'}
for(i in 1:length(pnts)){
    x = pnts[[i]][1]
    y = pnts[[i]][2]
    st1 = paste0("$$\\sqrt{(",x,"-",h,")^2+(",y,"-",k,")^2}~=~",ds[i],"$$",collapse="")
    cat(st1)
    cat("\n\n")
}

```

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r sols`
exname: distance_formula