```{r data generation, echo = FALSE, results = "hide"}
m = sample(c(-1,1),1)
n = sample(c(-1,1),1)
hk = sample(2:9,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]

if(n==-1){
    exp1 = paste0(m,"\\sqrt{",n,"(x+",-h,")}+",k,collapse="")
} else {
    exp1 = paste0(m,"\\sqrt{x+",-h,"}+",k,collapse="")
}

le = "≤"
lt = "<"
ge = "≥"
gt = ">"
ineqs = c(le,lt,ge,gt)

ints = list(c("[",", ∞)"),
            c("(",", ∞)"),
            c("(-∞, ","]"),
            c("(-∞, ",")"))

inf = "∞"

exp1 = gsub("+-","-",exp1,fixed=T)
exp1 = gsub("-1","-",exp1,fixed=T)
exp1 = gsub("1","",exp1,fixed=T)

ach1 = character()
for(i in sort(c(hk,-hk))){
    for(j in ineqs){
        ach1 = c(ach1,paste0("x ",j," ",i))
    }
}
for(i in sort(c(hk,-hk))){
    for(j in ineqs){
        ach1 = c(ach1,paste0("y ",j," ",i))
    }
}
al1 = paste0("* ",ach1,collapse="\n")

ach2 = character()
for(i in sort(c(hk,-hk))){
    for(j in 1:length(ints)){
        int = ints[[j]]
        ach2 = c(ach2,paste0(int[1],i,int[2]))
    }
}
al2 = paste0("* ",ach2,collapse="\n")

if(m==-1){
    if(n==-1){
        domie = paste0("x ",le," ",h,collapse="")
        domin = paste0("(-∞, ",h,"]",collapse="")
        ranie = paste0("y ",le," ",k,collapse="")
        ranin = paste0("(-∞, ",k,"]",collapse="")
        wrd1 = paste0("Because $a=",m,"$ and $b=",n,"$, the parent function is reflected vertically and horizontally, so from the starting point at (",h,", ",k,"), the curve goes down and to the left.")
    } else {
        domie = paste0("x ",ge," ",h,collapse="")
        domin = paste0("[",h,", ∞)",collapse="")
        ranie = paste0("y ",le," ",k,collapse="")
        ranin = paste0("(-∞, ",k,"]",collapse="")
        wrd1 = paste0("Because $a=",m,"$ and $b=",n,"$, the parent function is reflected vertically, so from the starting point at (",h,", ",k,"), the curve goes down and to the right.")
    }
} else {
    if(n==-1){
        domie = paste0("x ",le," ",h,collapse="")
        domin = paste0("(-∞, ",h,"]",collapse="")
        ranie = paste0("y ",ge," ",k,collapse="")
        ranin = paste0("[",k,", ∞)",collapse="")
        wrd1 = paste0("Because $a=",m,"$ and $b=",n,"$, the parent function is reflected horizontally, so from the starting point at (",h,", ",k,"), the curve goes up and to the left.")
    } else {
        domie = paste0("x ",ge," ",h,collapse="")
        domin = paste0("[",h,", ∞)",collapse="")
        ranie = paste0("y ",ge," ",k,collapse="")
        ranin = paste0("[",k,", ∞)",collapse="")
        wrd1 = paste0("Because $a=",m,"$ and $b=",n,"$, the parent function is not reflected, so from the starting point at (",h,", ",k,"), the curve goes up and to the right.")
    }
}

sol1 = paste0(1*(domie==ach1),collapse="")
sol2 = paste0(1*(domin==ach2),collapse="")
sol3 = paste0(1*(ranie==ach1),collapse="")
sol4 = paste0(1*(ranin==ach2),collapse="")

```

Question
========

Consider the radical function $f$ defined below.

$$f(x)~=~`r exp1`$$

We wish to indicate the domain and range of function $f$.

* Domain:
  - As an inequality: ##ANSWER1##
  - In interval notation: ##ANSWER2##
* Range:
  - As an inequality: ##ANSWER3##
  - In interval notation: ##ANSWER4##



Answerlist
--------

`r al1`
`r al2`
`r al1`
`r al2`


Solution
========

A fully parameterized version of the given function could be written as:

$$f(x)~=~a\sqrt{b(x-h)}+k$$

In our case, we were given $f(x)~=~`r exp1`$, so

$$a = `r m`$$
$$b = `r n`$$
$$h = `r h`$$
$$k = `r k`$$


`r wrd1`

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
ll = -20
ul = 20
plot(0,0,"n",xlim=c(ll,ul),ylim=c(ll,ul),axes=F,ann=F)
for(i in ll:ul){
    lines(c(ll,ul),c(i,i),col="lightgrey",lwd=0.8)
    lines(c(i,i),c(ll,ul),col="lightgrey",lwd=0.8)
}
for(i in seq(ll,ul,1)){
    if(i%%5==0){
        lines(c(ll,ul),c(i,i),col="darkgrey",lwd=1.3)
        lines(c(i,i),c(ll,ul),col="darkgrey",lwd=1.3)
    }
}
arrows(ll,0,ul,0,0.1,10,3,lwd=2)
arrows(0,ll,0,ul,0.1,10,3,lwd=2)

x = seq(0,ul,0.01)
y = sqrt(x)
lines(x,y,lty=2)

x = seq(h,ul*sign(n),0.01*sign(n))
y = m*sqrt(n*(x-h))+k
lines(x,y,lwd=3,col="red")
points(h,k,pch=20,col="red")

library(latex2exp)
legend("topleft",legend=c(TeX("$y = f(x)$"),TeX("$y=\\sqrt{x}$")),col=c("red","black"),
       lwd=c(3,1),lty=c(1,2))

arrows(h,0,ul*sign(n),0,0.1,10,2,lwd=3,col="blue")
points(h,0,pch=20,col="blue")
text(mean(c(h,ul*sign(n))),1,"domain",col="blue")

arrows(0,k,0,ul*sign(m),0.1,10,2,lwd=3,col="purple")
points(0,k,pch=20,col="purple")
text(1,mean(c(k,ul*sign(m))),"range",col="purple",srt=-90)

```
\

The starting point is indeed included in the domain and range because,

$$`r k`~=~`r gsub("x",paste0("(",h,")",collapse=""),exp1,fixed=T)`$$

Thus the finite boundaries should be inclusive. This means we use the "or equal" symbols in the inequalities and "[" or "]" in interval notation on the finite boundary. Remember, domain indicates the values of $x$ over which the function exists, and range indicates the values of $y$ over which the function exists.


* Domain:
  - As an inequality: `r domie`
  - In interval notation: `r domin`
* Range:
  - As an inequality: `r ranie`
  - In interval notation: `r ranin`



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: radical_dom_rng