```{r data generation, echo = FALSE, results = "hide"}
options(scipen=99)
mi = 10^runif(1,log10(6),log10(300))
area = signif(mi^2,2)
ans = sqrt(area)
tol = ans/10
```

Question
========

The lake below has an area of $`r area`$ $\mathrm{miles^2}$.

```{r,echo=F,fig.dim=c(5,5)}
cfs = runif(5,0.01,0.3)
offs = runif(5,0,2*pi)
ths = seq(0,2*pi,pi/1000)
rs = 1+cfs[1]*sin(ths+offs[1])+cfs[2]/2*sin(2*ths+offs[2])+cfs[3]/3*sin(3*ths+offs[3])+cfs[4]/4*sin(4*ths+offs[4])+cfs[5]/5*sin(5*ths+offs[5])
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-max(abs(rs)),max(abs(rs))),ylim=c(-max(abs(rs)),max(abs(rs))),axes=F,ann=F)
polygon(rs*cos(ths),rs*sin(ths),col="blue")

```
\

If you approximate the shape as a square, what is the edge length (in miles)? In other words, what is the approximate distance, in miles, across the lake?

Solution
========

First, imagine the lake is a square with side lengths equaling $s$.

The area of the square equals the side length raised to the power of two.

$$A=s^2$$

The inverse operation is the square root.

$$s=\sqrt{A}$$

Plug in the area.

$$s~=~\sqrt{`r area`~\mathrm{mi^2}}~\approx~`r signif(ans,4)`~\mathrm{mi}$$

So it is approximately `r signif(ans,2)` miles across the lake.


Meta-information
============
extype: num
exsolution: `r ans`
exname: sqrt_lake_area
extol: `r tol`