```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
# y = (ax+b)/(cx+d)
# x = (ay+b)/(cy+d)
# cxy+dx = ay+b
# y(cx-a) = -dx+b
# y = (-Dx+B)/(Cx-A)

# make c=1.. rename d to c... ugh gross...

ABD = sample(2:9,3)*sample(c(-1,1))
A = ABD[1]
B = ABD[2]
D = ABD[3]

a = -D
b = B
c = -A

pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

pfiy = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}y^{",dd,"}",collapse="+")
    p = gsub("y^{0}","",p,fixed=T)
    p = gsub("y^{1}","y",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}y","+y",p,fixed=T)
    p = gsub("-{1}y","-y",p,fixed=T)
    p = gsub("{-1}y","-y",p,fixed=T)
    p = gsub("{1}y","y",p,fixed=T)
    return(p)
}

f1 = paste0("\\frac{",pfix(c(A,B),1:0),"}{",pfix(c(1,D),1:0),"}")

ach = -9:9
al = paste0("* ",ach,collapse="\n")
sol1 = paste0(1*(ach==a),collapse = "")
sol2 = paste0(1*(ach==b),collapse = "")
sol3 = paste0(1*(ach==c),collapse = "")

ie1 = paste0("x~=~",gsub("x","y",f1,fixed=T))

```

Question
========

Let function $f$ be defined by the rational expression below.

$$f(x)~=~`r f1`$$

Its inverse function can be expressed in the following form. Please find the values of the three parameters: $a$, $b$, and $c$.

$$f^{-1}(x)~=~\frac{ax+b}{x+c}$$

* $a=$ ##ANSWER1##
* $b=$ ##ANSWER2##
* $c=$ ##ANSWER3##

Answerlist
--------

`r al`
`r al`
`r al`

Solution
========

Start by getting rid of function notation.

$$y~=~`r f1`$$

To find the **inverse**, swap the $x$ and $y$.

$$`r ie1`$$

Our goal is to get $y$ by itself (solve for $y$). Multiply both sides by $`r pfiy(c(1,D),1:0)`$.

```{r,echo=F}
ie2 = paste0("x\\cdot(y+",D,")~=~",A,"y+",B,collapse="")
ie2 = gsub("+-","-",ie2,fixed=T)
```

$$`r ie2`$$

Distribute $x$ to get rid of parentheses.

```{r,echo=F}
ie3 = paste0("xy+",D,"x~=~",A,"y+",B,collapse="")
ie3 = gsub("+-","-",ie3,fixed=T)
```

$$`r ie3`$$

Notice all terms are either linear in $y$ or independent of $y$. This means we can gather all the terms with $y$ onto the left side and all the terms without $y$ onto the right side. We do this by subtracting $`r D`x$ from both sides and subtracting $`r A`y$ from both sides.

```{r,echo=F}
ie4 = paste0("xy+",-A,"y~=~",-D,"x+",B,collapse="")
ie4 = gsub("+-","-",ie4,fixed=T)
```

$$`r ie4`$$

Factor out the $y$ from both terms on the left side of the equation.

```{r,echo=F}
ie5 = paste0("y\\cdot(x+",-A,")~=~",-D,"x+",B,collapse="")
ie5 = gsub("+-","-",ie5,fixed=T)
myfact = paste0("x+",-A,collapse="")
myfact = gsub("+-","-",myfact,fixed=T)
```

$$`r ie5`$$

Divide both sides by $`r myfact`$.

```{r,echo=F}
ie6 = paste0("y~=~\\frac{",-D,"x+",B,"}{x+",-A,"}",collapse="")
ie6 = gsub("+-","-",ie6,fixed=T)
```

$$`r ie6`$$

Return to function notation, using $f^{-1}$ for inverse.

```{r,echo=F}
ie7 = paste0("\\frac{",-D,"x+",B,"}{x+",-A,"}",collapse="")
ie7 = gsub("+-","-",ie7,fixed=T)
```

$$f^{-1}(x)~=~`r ie7`$$

So,

$$a=`r a`$$
$$b=`r b`$$
$$c=`r c`$$



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: inverse_rational