```{r,echo=FALSE}
hl = -sample(2:8,1)
lowy = sample(1:5,1)
lowx = sample((1-2*hl):(20),1)
hiy = lowy*4
```


Question
========

The doubling time of an exponentially growing function is the amount of time it takes for the population to double. 

```{r,echo=FALSE,fig.dim=c(6,6)}
par(pty="s")
plot(0,0,type="n",xlim=c(0,20),ylim=c(0,20),xlab="t (minutes)",ylab="y (billions)")
for(i in 1:20){
  if(i%%5==0){
    abline(h=i,lty=2)
    abline(v=i,lty=2)
  } else {
    abline(h=i,lty=3)
    abline(v=i,lty=3)
  }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
t = seq(-1,21,0.01)
y = hiy*(1/2)^((t-lowx)/hl)
lines(t,y,lwd=3,col="blue")
# points(c(lowx-2*hl,lowx-hl,lowx,lowx+hl,lowx+2*hl),c(hiy*4,hiy*2,hiy,hiy/2,hiy/4),col="blue",pch=19)
# if(round(100*hiy/8)/100==round(hiy/8)){
#   points(lowx+3*hl,hiy/8,col="blue",pch=19)
# }
```
\

What is the doubling time (in minutes) of the exponential function graphed above? (The answer is an integer.)


Solution
========

The doubling time is `r -hl` minutes.

```{r,echo=FALSE,fig.dim=c(6,6)}
par(pty="s")
plot(0,0,type="n",xlim=c(0,20),ylim=c(0,20),xlab="t (minutes)",ylab="y (billions)")
for(i in 1:20){
  if(i%%5==0){
    abline(h=i,lty=2)
    abline(v=i,lty=2)
  } else {
    abline(h=i,lty=3)
    abline(v=i,lty=3)
  }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
t = seq(-1,21,0.01)
y = hiy*(1/2)^((t-lowx)/hl)
lines(t,y,lwd=3,col="blue")
points(c(lowx-2*hl,lowx-hl,lowx,lowx+hl,lowx+2*hl),c(hiy*4,hiy*2,hiy,hiy/2,hiy/4),col="blue",pch=19)
if(round(100*hiy/8)/100==round(hiy/8)){
  points(lowx+3*hl,hiy/8,col="blue",pch=19)
}
lines(c(lowx,lowx),c(hiy,hiy/2),col="red",lwd=2)
text(lowx-0.5,3*hiy/4,hiy/2,col="red")
lines(c(lowx,lowx),c(hiy/2,0),col="red",lwd=1,lty=2)
text(lowx-0.5,hiy/4,hiy/2,col="red")
lines(c(lowx,lowx+hl),c(hiy/2,hiy/2),col="darkgreen",lwd=2)
text(lowx+hl/2,hiy/2-0.5,-hl,col="darkgreen")
lines(c(lowx+hl,lowx+hl),c(hiy/2,hiy/4),col="red",lwd=2)
text(lowx+hl-0.5,3*hiy/8,hiy/4,col="red")
lines(c(lowx+hl,lowx+hl),c(hiy/4,0),col="red",lwd=1,lty=2)
text(lowx+hl-0.5,hiy/8,hiy/4,col="red")
lines(c(lowx+hl,lowx+2*hl),c(hiy/4,hiy/4),col="darkgreen",lwd=2)
text(lowx+3*hl/2,hiy/4-0.5,-hl,col="darkgreen")
```
\

Every `r -hl` minutes, the population doubles again. 


Meta-information
============
extype: num
exsolution: `r -hl`
exname: doubling_time_from_graph
extol: 0.1