```{r,echo=FALSE}
options(scipen=99)

poss = list()

for(a in 2:7){
    for(b in 2:6){
        for(n in 3:6){
            top = a*b^(n-1)
            if(top>30 && top<400 && a!=b){
                poss[[length(poss)+1]] = c(a,b,n)
            }
        }
    }
}

i = sample(1:length(poss),1)
a = poss[[i]][1]
b = poss[[i]][2]
n = poss[[i]][3]
A = a*b^(0:(n-1))

S = sum(A)

```

Question
========

In the forest diagram below, there are `r a` [complete m-ary](https://en.wikipedia.org/wiki/M-ary_tree) trees. Each tree has a [branching factor](https://en.wikipedia.org/wiki/Branching_factor) of `r b` and a maximum [depth](https://en.wikipedia.org/wiki/Tree_(abstract_data_type)#Terminology) of `r n-1` (so there are `r n` different levels).

```{r,echo=F,fig.dim=c(8,6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),ann=F)
ys = seq(1,0,length.out=n+1)
ys = (ys[2:(n+1)]+ys[1:n])/2
for(i in 2:n){
    aa = A[i]
    x1 = seq(0,1,length.out=aa+1)
    x1 = (x1[2:(aa+1)]+x1[1:aa])/2
    bb = A[i-1]
    x2 = seq(0,1,length.out=bb+1)
    x2 = (x2[2:(bb+1)]+x2[1:bb])/2
    for(x in x1){
        axdiffs = abs(x2-x)
        mindiff = min(axdiffs)
        xx = x2[abs(x2-x)==mindiff]
        lines(c(x,xx),c(ys[i],ys[i-1]))
    }
}
for(i in 1:n){
    aa = A[i]
    xs = seq(0,1,length.out=aa+1)
    xs = (xs[2:(aa+1)]+xs[1:aa])/2
    points(xs,rep(ys[i],aa),pch=19,col="red",cex=0.3)
    text(-0.03,ys[i],i-1,adj=0)
}
text(-0.03,ys[1]+0.03,"Depth",adj=0)
```

How many nodes (red dots) are in the forest diagram? In other words, what is the [size](https://en.wikipedia.org/wiki/Tree_(abstract_data_type)#Terminology) of the forest?


Solution
========

We can recognize that the number of nodes can be represented with a [geometric series](https://en.wikipedia.org/wiki/Geometric_series).

$$S~=~`r paste0(a,"(",b,")^",0:(n-1),collapse="+")`$$

The first term is $a=`r a`$. The common ratio is $r=`r b`$. The number of terms is $n=`r n`$. We can use the [partial geometric series formula](https://chadworley.github.io/a2/u17/slides_sum_geometric/sum_geometric.pdf).

$$S~=~\frac{a(1-r^n)}{1-r}$$


$$S~=~\frac{`r a`\left(1-`r b`^{`r n`}\right)}{1-`r b`}$$

$$S~=~`r S`$$


Meta-information
============
extype: num
exsolution: `r S`
exname: size_small_m-ary_tree