```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+{-","-{",exp,fixed=T)
  exp = gsub("{1}x^{0}","1",exp,fixed=T)
  exp = gsub("{1}","{}",exp,fixed=T)
  exp = gsub("x^{0}","{}",exp,fixed=T)
  return(exp)
}

while(T){
  ab = sort(round(sample(5:95,2)/10,1))
  a = ab[1]
  b = ab[2]
  xx = 0.5
  yy = xx^a-xx^b
  ans = 1/(2*a+1)-2/(a+b+1)+1/(2*b+1)
  
  #\frac{1}{`r 2*a+1`}-\frac{2}{`r a+b+1`}+\frac{1}{`r 2*b+1`}
  if(b-a>0.3 && yy>0.3 && b%%1!=0 && a%%1!=0 && ans>0.002){break}
}



```

Question
========

A 3D shape's base is the 2D region enclosed by $y=0$ and $y=f(x)=x^{`r a`}-x^{`r b`}$ on the $xy$ plane. For every plane perpendicular to the $x$ axis, with $0<x<1$, there is a square cross section. 

I have attempted to draw this below.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s")
xs = seq(0,1,0.01)
y1 = xs*0
y2 = xs^a-xs^b
tp = pi/4
r = 0.7
P = matrix(c(1,r*cos(tp),0,
             0,r*sin(tp),1),2,byrow=T)
curve1 = matrix(c(xs,y2,y2),nrow=3,byrow=T)
flat1 = P%*%curve1
curve2 = matrix(c(xs,y2,y1),nrow=3,byrow=T)
flat2 = P%*%curve2
curve3 = matrix(c(xs,y1,y1),nrow=3,byrow=T)
flat3 = P%*%curve3
curve4 = matrix(c(xs,y1,y2),nrow=3,byrow=T)
flat4 = P%*%curve4

X = matrix(c(xs-0.5,rev(xs)-0.5,xs-0.5,rev(xs)-0.5,
             y2,rev(y2),y1,rev(y1),
             y2,rev(y1),y1,rev(y2)),
           nrow=3,byrow=T)

crossx = numeric()
crossy = numeric()
crossz = numeric()
for(x in seq(0.1,0.9,0.1)){
  z = x^a-x^b
  crossx = c(crossx,rep(x,5))
  crossy = c(crossy,0,0,z,z,0)
  crossz = c(crossz,0,z,z,0,0)
}
C = matrix(c(crossx-0.5,crossy,crossz),3,byrow=3)

xx = 0.5
yy = xx^a-xx^b
sq1 = matrix(c(xx,xx,xx,xx,xx,
               0,0,yy,yy,0,
               0,yy,yy,0,0),nrow=3,byrow=T)
flsq1 = P%*%sq1

plot(flat1[1,],flat1[2,],type="l",xlim=c(-0.1,1.2),ylim=c(-0.1,1.2),xlab="x",ylab="z")

for(x in seq(0,1,0.001)){
  y = x^a-x^b
  sq = matrix(c(x,x,x,x,x,
               0,0,y,y,0,
               0,y,y,0,0),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],col="red",border="red",lwd=1)
}
# for(x in seq(0,1,0.01)){
#   y = x^a-x^b
#   sq = matrix(c(x,x,x,x,x,
#                0,0,y,y,0,
#                0,y,y,0,0),nrow=3,byrow=T)
#   flsq = P%*%sq
#   polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=0.5)
# }

lines(flat1[1,],flat1[2,],col=rgb(0,0,0,1))
lines(flat2[1,],flat2[2,],col=rgb(0,0,0,1))
lines(flat3[1,],flat3[2,],col=rgb(0,0,0,1))
lines(flat4[1,],flat4[2,],col=rgb(0,0,0,1))

for(x in seq(0.1,0.9,0.2)){
  y = x^a-x^b
  sq = matrix(c(x,x,x,x,x,
               0,0,y,y,0,
               0,y,y,0,0),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],border="black",lwd=2)
}
```
\

And here is a spinning animation. Does that help?

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(6,6)}
getR = function(u,t){
  ux = u[1]
  uy = u[2]
  uz = u[3]
  f = cos(t)+ux^2*(1-cos(t))
  g = ux*uy*(1-cos(t))-uz*sin(t)
  h = ux*uz*(1-cos(t))+uy*sin(t)
  i = uy*ux*(1-cos(t))+uz*sin(t)
  j = cos(t)+uy^2*(1-cos(t))
  k = uy*uz*(1-cos(t))-ux*sin(t)
  l = uz*ux*(1-cos(t))-uy*sin(t)
  m = uz*uy*(1-cos(t))+ux*sin(t)
  n = cos(t)+uz^2*(1-cos(t))
  R = matrix(c(f,g,h,i,j,k,l,m,n),3,byrow=T)
  return(R)
}
tp = pi/2
r = 0.2
P = matrix(c(1,r*cos(tp),0,
             0,r*sin(tp),1),2,byrow=T)
n = 20
par(pty="s",mar=c(0,0,0,0))
u = c(0,0,1)
t = 2*pi/n
R = getR(u,t)
Xc = X
Cc = C
for(i in 1:n){
  plot(0,0,type="n",axes=F,ann=F,xlim=c(-0.7,0.7),ylim=c(-0.4,1))
  Xc_flat = P%*%Xc
  lines(Xc_flat[1,],Xc_flat[2,])
  Cc_flat = P%*%Cc
  lines(Cc_flat[1,],Cc_flat[2,])
  Xc = R%*%Xc
  Cc = R%*%Cc
}
```
\


Find the volume of the shape; the tolerance is $\pm 0.001$ cubic units. You might find [this video](https://www.khanacademy.org/math/ap-calculus-ab/ab-applications-of-integration-new/ab-8-7/v/volume-with-cross-sections-intro) helpful. The general topic is "[volume from cross sections](https://en.wikibooks.org/wiki/Calculus/Volume)"; you might try a variety of resources by searching this phrase in your favorite search engine.


Solution
========

The volume can be found by accumulating the volumes of many "slabs", where each slab is a square with some infinitesimal thickness.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s",mar=c(0,0,0,0))
tp = pi/6
r = 0.5
P = matrix(c(1,r*cos(tp),0,
             0,r*sin(tp),1),2,byrow=T)
plot(0,0,type="n",xlim=c(0,1.1),ylim=c(0,1.1))
dx = 0.02
xs = seq(0,1,0.01)
for(x in seq(0,1-dx,dx)){
  y = x^a-x^b
  
  sq = matrix(c(x+dx,x+dx,x,x,
               0,y,y,0,
               y,y,y,y),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)
  
  sq = matrix(c(x+dx,x+dx,x,x,
               0,0,0,0,
               0,y,y,0),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)
  
  sq = matrix(c(x+dx,x+dx,x+dx,x+dx,
               0,0,y,y,
               0,y,y,0),nrow=3,byrow=T)
  flsq = P%*%sq
  polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)
}

xs = seq(0,1,0.001)
lines(xs,xs^a-xs^b,lwd=2)

```
\

The volume of each slab depends on $x$. The width and height are each $f(x)$ and the thickness is an [infinitesimal](https://en.wikipedia.org/wiki/Infinitesimal) $dx$.

```{r,echo=F,fig.dim=c(6,6)}
par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(0,1.2),ylim=c(0,1.2))
dx=0.1
x = 0.3
y = 0.9
sq = matrix(c(x+dx,x+dx,x,x,
             0,y,y,0,
             y,y,y,y),nrow=3,byrow=T)
flsq = P%*%sq
polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)

sq = matrix(c(x+dx,x+dx,x,x,
             0,0,0,0,
             0,y,y,0),nrow=3,byrow=T)
flsq = P%*%sq
polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)

sq = matrix(c(x+dx,x+dx,x+dx,x+dx,
             0,0,y,y,
             0,y,y,0),nrow=3,byrow=T)
flsq = P%*%sq
polygon(flsq[1,],flsq[2,],col="red",border="black",lwd=1)
text(0.26,y/2,"f(x)")
text(0.48,y+0.15,"f(x)")
text(0.75,y+0.27,"dx")
```
\

So, we can find the infinitesimal volume as a function of $x$.

$$dV = (f(x))^2 \,dx$$


$$dV = (x^{`r a`}-x^{`r b`})^2 \,dx$$

We need to sum up all the differential volumes from $x=0$ to $x=1$.

$$V = \int_{x=0}^{x=1} dV$$


$$V = \int_{0}^{1} (x^{`r a`}-x^{`r b`})^2 \,dx$$

You can apply the [binomial theorem](https://en.wikipedia.org/wiki/Binomial_theorem).

$$V = \int_{0}^{1} (x^{`r 2*a`}-2x^{`r a+b`}+x^{`r 2*b`}) \,dx$$

Let $g(x)$ be an antiderivative of $(f(x))^2$ such that $g(0)=0$.

$$g(x)~=~\frac{1}{`r 2*a+1`}x^{`r 2*a+1`}-\frac{2}{`r a+b+1`}x^{`r a+b+1`}+\frac{1}{`r 2*b+1`}x^{`r 2*b+1`}$$

We use the antiderivative to find the definite integral.

$$V = g(1)-g(0)$$

$$V = \left(\frac{1}{`r 2*a+1`}(1)^{`r 2*a+1`}-\frac{2}{`r a+b+1`}(1)^{`r a+b+1`}+\frac{1}{`r 2*b+1`}(1)^{`r 2*b+1`}\right) - \left(\frac{1}{`r 2*a+1`}(0)^{`r 2*a+1`}-\frac{2}{`r a+b+1`}(0)^{`r a+b+1`}+\frac{1}{`r 2*b+1`}(0)^{`r 2*b+1`}\right)$$

$$V = \left(\frac{1}{`r 2*a+1`}-\frac{2}{`r a+b+1`}+\frac{1}{`r 2*b+1`}\right) - \left(0-0+0\right)$$


$$V ~=~ \frac{1}{`r 2*a+1`}-\frac{2}{`r a+b+1`}+\frac{1}{`r 2*b+1`}$$
$$V \approx `r ans`$$


Meta-information
============
extype: num
exsolution: `r ans`
exname: volume_by_slabs
extol: 0.001