```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+{-","-{",exp,fixed=T)
  exp = gsub("{1}x^{0}","1",exp,fixed=T)
  exp = gsub("{1}","{}",exp,fixed=T)
  exp = gsub("x^{0}","{}",exp,fixed=T)
  return(exp)
}

while(T){
  m = round(runif(1,0.2,1),2)
  ab = sort(round(runif(2,1,10),2))
  a = ab[1]
  b = ab[2]
  V = 4*pi*m/3*(b^3-a^3)
  if(b-a>3 && V>3 && V<9999 && m!=0.5 && m!=1){break}
}


```

Question
========

An [isosceles trapezoid](https://en.wikipedia.org/wiki/Isosceles_trapezoid) is the region between the following curves:

$$z ~=~ `r m`x$$
$$z ~=~ `r -m`x$$
$$x ~=~ `r a`$$
$$x ~=~ `r b`$$

```{r,echo=F,fig.dim=c(6,6)}
par(pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="z")
for(i in 0:10){
  abline(h=i,col="grey")
  abline(h=-i,col="grey")
  abline(v=i,col="grey")
  abline(v=-i,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.06,code=3)
arrows(0,-10.5,0,10.5,length=0.06,code=3)
polygon(c(a,b,b,a),
        c(m*a,m*b,-m*b,-m*a),
        col=rgb(0,0,1,0.5))
abline(0,m,col="blue",lwd=3)
abline(0,-m,col="blue",lwd=3)
abline(v=a,col="blue",lwd=3)
abline(v=b,col="blue",lwd=3)

```
\

That trapezoid is [revolved](https://en.wikipedia.org/wiki/Solid_of_revolution) around the $z$ axis to produce a [toroid](https://en.wikipedia.org/wiki/Toroid). A wireframe animation of the toroid is shown below.

```{r,animation.hook="gifski",interval=0.3,echo=F,fig.dim=c(5,5)}
X = list()
nth = 12 #number of angles for wireframe
nfr = 8 #number of frames in gif
thp = pi/6 #perspective rotation around x axis
ths = (1:nth)*2*pi/nth
for(i in 1:nth){
  xs = c(a*cos(ths[i]),b*cos(ths[i]),b*cos(ths[i]),a*cos(ths[i]))
  ys = c(a*sin(ths[i]),b*sin(ths[i]),b*sin(ths[i]),a*sin(ths[i]))
  zs = c(m*a,m*b,-m*b,-m*a)
  cl = length(X)
  X[[cl+1]] = matrix(c(xs,ys,zs),nrow=3,byrow=T)
}
ths = seq(pi/100,2*pi,pi/100)
for(r in c(a,b)){
  for(mm in c(m,-m)){
    xs = r*cos(ths)
    ys = r*sin(ths)
    zs = rep(mm*r,length(xs))
    cl = length(X)
    X[[cl+1]] = matrix(c(xs,ys,zs),nrow=3,byrow=T)
  }
}
ths = (1:nfr)*2*pi/nth/nfr
dth = 2*pi/nth/nfr
Rf = matrix(c(cos(dth),-sin(dth),0,
              sin(dth),cos(dth),0,
              0,0,1),nrow=3,byrow=T)
Rp = matrix(c(1,0,0,
              0,cos(thp),-sin(thp),
              0,sin(thp),cos(thp)),nrow=3,byrow=T)
P = matrix(c(1,0,0,
             0,0,1),nrow=2,byrow=T)
maxy = m*b+sin(thp)*m*b
maxy = max(c(b,maxy))
XX = X
for(i in 1:nfr){
  par(mar=c(0,0,0,0),pty="s")
  plot(0,0,type="n",xlim=c(-maxy,maxy),ylim=c(-maxy,maxy),ann=F,axes=F)
  for(j in 1:length(X)){
    XP = P%*%(Rp%*%XX[[j]])
    polygon(XP[1,],XP[2,],col=NA,border="black")
    XX[[j]] = Rf%*%XX[[j]]
  }
}
```
\

Find the volume of the toroid using [shell integration](https://en.wikipedia.org/wiki/Shell_integration). The tolerance is $\pm 1$ cubic unit.


Solution
========

To use shell integration, we split the volume into a bunch of cylindrical shells.

```{r,animation.hook="gifski",interval=0.5,echo=F,fig.dim=c(5,5)}
draw_shell_back = function(z,r1,r2,h,perspective_ratio=0.5,col="red",nn=100){
  t = seq(0,pi,length.out=nn)
  pr = perspective_ratio
  for(i in 1:(nn-1)){
    polygon(c(r1*cos(t[i]),r1*cos(t[i+1]),r1*cos(t[i+1]),r1*cos(t[i])),
            c(z+pr*r1*sin(t[i]),z+pr*r1*sin(t[i+1]),z+h+pr*r1*sin(t[i+1]),z+h+pr*r1*sin(t[i])),
            col=col,border=col)
    polygon(c(r1*cos(t[i]),r1*cos(t[i+1]),r2*cos(t[i+1]),r2*cos(t[i])),
            c(z+h+pr*r1*sin(t[i]),z+h+pr*r1*sin(t[i+1]),z+h+pr*r2*sin(t[i+1]),z+h+pr*r2*sin(t[i])),
            col=col,border=col)
  }
  lines(r1*cos(t),z+pr*r1*sin(t))
  lines(r1*cos(t),z+h+pr*r1*sin(t))
  lines(r2*cos(t),z+h+pr*r2*sin(t))
}
draw_shell_front = function(z,r1,r2,h,perspective_ratio=0.5,col="red",nn=100){
  t = seq(pi,2*pi,length.out=nn)
  pr = perspective_ratio
  for(i in 1:(nn-1)){
    polygon(c(r2*cos(t[i]),r2*cos(t[i+1]),r2*cos(t[i+1]),r2*cos(t[i])),
            c(z+pr*r2*sin(t[i]),z+pr*r2*sin(t[i+1]),z+h+pr*r2*sin(t[i+1]),z+h+pr*r2*sin(t[i])),
            col=col,border=col)
    polygon(c(r1*cos(t[i]),r1*cos(t[i+1]),r2*cos(t[i+1]),r2*cos(t[i])),
            c(z+h+pr*r1*sin(t[i]),z+h+pr*r1*sin(t[i+1]),z+h+pr*r2*sin(t[i+1]),z+h+pr*r2*sin(t[i])),
            col=col,border=col)
  }
  lines(r2*cos(t),z+pr*r2*sin(t))
  lines(r1*cos(t),z+h+pr*r1*sin(t))
  lines(r2*cos(t),z+h+pr*r2*sin(t))
  lines(c(-r2,-r2),c(z,z+h))
  lines(c(r2,r2),c(z,z+h))
}

nn = 12
zs = seq(m*a,m*b,length.out=nn)
r1 = seq(a,b-(b-a)/nn,length.out=nn)
r2 = seq(a+(b-a)/nn,b,length.out=nn)
hs = zs*2
f = 0.5

for(kk in 1:nn){
  par(pty="s",mar=c(0,0,0,0))
  plot(0,0,type="n",xlim=c(-maxy,maxy),ylim=c(-maxy,maxy),ann=F,axes=F)
  for(i in rev(1:kk)){
    draw_shell_back(-zs[i],r1[i],r2[i],hs[i],f,col=hsv(i/length(zs),0.7,0.4+0.2*i%%3))
  }
  for(i in 1:kk){
    draw_shell_front(-zs[i],r1[i],r2[i],hs[i],f,col=hsv(i/length(zs),0.7,0.4+0.2*i%%3))
  }
}
```
\

Each shell has a radius, height, and an infinitesimal thickness.

```{r,echo=F,fig.dim=c(6,6)}
plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),ann=F,axes=F)
draw_shell_back(-0.5,0.5,0.6,1,f,col="white")
draw_shell_front(-0.5,0.5,0.6,1,f,col="white")

lines(c(-0.5,-0.5),c(0.5,-0.5),lty=3)
lines(c(0.5,0.5),c(0.5,-0.5),lty=3)
th = seq(0,2*pi,length.out=360)
lines(0.5*cos(th),0.5*0.5*sin(th)-0.5,lty=3)

lines(c(0,0.5),c(0.5,0.5),lwd=3,col="blue")
text(0.25,0.6,"r",col="blue",cex=1.3)

lines(c(-0.7,-0.7),c(-0.5,0.5),col="red",lwd=2)
text(-0.75,0,"h",col="red",cex=1.3)

lines(c(0.5,0.5,0.6,0.6),c(0.5,0.7,0.7,0.5),col="purple",lwd=2,lty=3)
lines(c(0.5,0.5,0.6,0.6),c(0.65,0.7,0.7,0.65),col="purple",lwd=2)
text(0.55,0.75,"dr",col="purple")
```
\

The infinitesimal volume can be found as the difference of two cylinders' volumes.

$$dV ~=~ \pi(r+dr)^2h-\pi r^2h$$

Apply the [binomial theorem](https://en.wikipedia.org/wiki/Binomial_theorem).

$$dV ~=~ \pi r^2 h + 2\pi r h\,dr + \pi h \, (dr)^2-\pi r^2h$$

Notice two terms eliminate because they are opposites.

$$dV ~=~ 2\pi r h\,dr + \pi h \, (dr)^2$$

Remember, $dr$ is an infinitesimal amount ($dr$ is near 0), so the second term can be ignored. This leaves us with the differential volume formula for a cylindrical shell (people memorize this):

$$dV ~=~ 2\pi r h\,dr$$

We need to get height as a function of $r$. We can get this from a difference of the two lines.

$$h = (`r m` r) - (-`r m`r)$$

$$h = `r 2*m` r$$


Now we are ready for the integral. We need to sum up a bunch of differential volumes as $r$ varies from `r a` to `r b`.

$$V ~=~ \int_{r=`r a`}^{r=`r b`}dV$$

For cylindrical shells, $dV ~=~ 2\pi r h\,dr$, as we proved earlier.


$$V ~=~ \int_{`r a`}^{`r b`}2\pi r h\,dr$$

Write the expression in terms of $r$. So substitute $h = `r 2*m` r$. Also, constant factors (multipliers) can be taken out from an integral.

$$V ~=~ `r 4*m`\pi\int_{`r a`}^{`r b`}r^2\,dr$$

Use an antiderivative to evaluate the integral.

$$V ~=~ `r 4*m`\pi\left[\frac{r^3}{3}\right]_{`r a`}^{`r b`}$$


$$V ~=~ `r 4*m`\pi\left(\frac{`r b`^3}{3}-\frac{`r a`^3}{3}\right)$$

$$V ~=~ `r V`$$


Meta-information
============
extype: num
exsolution: `r V`
exname: vol_by_shells
extol: 1