---
title: "Unit-Circle Trigonometry Cheat Sheet"
output:
  pdf_document: default
  html_document: default
urlcolor: blue
---

\pagenumbering{gobble}

\vspace{-0.4in}

```{r,echo=F,fig.dim=c(1.5,1.5),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.05,1.05),ylim=c(-1.05,1.05))
th = seq(0,2*pi,pi/360)
arrows(-1.05,0,1.05,0,0.05,15,3)
arrows(0,-1.05,0,1.05,0.05,15,3)
lines(cos(th),sin(th),col="grey",lty=2)
x = -0.6
y = 0.8
t = atan2(y,x)
lines(c(0,x),c(0,y),lwd=2,col="blue")
# dd = 0.03
# lines(c(x-dd,x-dd,x),c(0,dd,dd))
text(x/2,y/2,"1",srt=(t*180/pi+90)%%180-90,adj=c(0.5,-0.3),col="blue")
# text(x/2,0,"adj",srt=0,adj=c(0.5,1.3))
# text(x,y/2,"opp",srt=90,adj=c(0.5,1.3))

thth = seq(0,t,pi/360)
n = length(thth)
ar = 0.2
art = 0.34
lines(ar*cos(thth),ar*sin(thth),col="red",lwd=2)
text(art*cos(t/2),art*sin(t/2),TeX("$\\theta$"),col="red")
# arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.1,20,col="red",lwd=3)
arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.05,30,col="red",lwd=2)

points(x,y,pch=19,col="maroon")
text(x,y,"(x,y)",adj=1.2,col="maroon",cex=0.9)
text(1/sqrt(2),1/sqrt(2),TeX("$x^2+y^2=1$"),srt=-45,col="grey",adj=c(0.5,-0.2),cex=0.6)

```

# Definitions

\begin{align*}
\sin(\theta) &= y & \cos(\theta) &= x & \tan(\theta) &= \frac{y}{x}=\frac{\sin(\theta)}{\cos(\theta)}=\text{slope}
\end{align*}

# Pythagorean Identities

\begin{align*}
\sin^2(\theta)+\cos^2(\theta)&=1 & |\sin(\theta)|&=\sqrt{1-\cos^2(\theta)} & |\cos(\theta)|&=\sqrt{1-\sin^2(\theta)}\\\\
\tan^2(\theta)+1&=\frac{1}{\cos^2(\theta)} & |\tan(\theta)|&=\sqrt{\frac{1-\cos^2(\theta)}{\cos^2(\theta)}} &
|\cos(\theta)|&=\sqrt{\frac{1}{\tan^2(\theta)+1}}\\\\
\tan^2(\theta)+1&=\frac{1}{1-\sin^2(\theta)} & |\tan(\theta)|&=\sqrt{\frac{\sin^2(\theta)}{1-\sin^2(\theta)}} &
|\sin(\theta)|&=\sqrt{\frac{\tan^2(\theta)}{\tan^2(\theta)+1}}\\\\
\end{align*}

# Polar Coordinates

```{r,echo=F,fig.dim=c(1.5,1.5),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.05,1.05),ylim=c(-1.05,1.05))
th = seq(0,2*pi,pi/360)
arrows(-1.05,0,1.05,0,0.05,15,3)
arrows(0,-1.05,0,1.05,0.05,15,3)
lines(cos(th),sin(th),col="grey",lty=2)
x = -0.6
y = 0.8
t = atan2(y,x)
lines(c(0,x),c(0,y),lwd=2,col="blue")
# dd = 0.03
# lines(c(x-dd,x-dd,x),c(0,dd,dd))
text(x/2,y/2,"r",srt=(t*180/pi+90)%%180-90,adj=c(0.5,-0.3),col="blue")
# text(x/2,0,"adj",srt=0,adj=c(0.5,1.3))
# text(x,y/2,"opp",srt=90,adj=c(0.5,1.3))

thth = seq(0,t,pi/360)
n = length(thth)
ar = 0.2
art = 0.34
lines(ar*cos(thth),ar*sin(thth),col="red",lwd=2)
text(art*cos(t/2),art*sin(t/2),TeX("$\\theta$"),col="red")
# arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.1,20,col="red",lwd=3)
arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.05,30,col="red",lwd=2)

points(x,y,pch=19,col="maroon")
text(x,y,"(x,y)",adj=1.2,col="maroon",cex=0.9)
text(1/sqrt(2),1/sqrt(2),TeX("$x^2+y^2=r^2$"),srt=-45,col="grey",adj=c(0.5,-0.2),cex=0.6)

```

\begin{align*}
x &= r\cdot\cos(\theta) & r &= \sqrt{x^2+y^2} \\
y &=r\cdot\sin(\theta) & \theta&=\arctan(y,x)
\end{align*}


\newpage

# Special angles

* Draw an isosceles right triangle with a hypotenuse of length 1 and leg length of $x$. Solve $x^2+x^2=1^2$ to prove length ratios of $\frac{\sqrt{2}}{2}:\frac{\sqrt{2}}{2}:1$ for the $45^{\circ}-45^{\circ}-90^{\circ}$ triangle.
* Draw an equilateral triangle, and cut it in half to produce a right triangle with a hypotenuse of length 1, a leg of length 1/2, and another leg of length $x$. Solve $x^2+\left(\frac{1}{2}\right)^2=1^2$ to prove length ratios of $\frac{1}{2}:\frac{\sqrt{3}}{2}:1$ for the $30^{\circ}-60^{\circ}-90^{\circ}$ triangle..
* See the [right-triangle cheat sheet](https://chadworley.github.io/a2/u13/rtt_cheat_sheet/cheat_sheet_rtt_trig.html) for diagrams.
* Use symmetry of the unit circle to determine all coordinates shown below.

```{r,echo=F,fig.dim=c(6,6),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
th = seq(0,2*pi,pi/360)
arrows(-1.05,0,1.05,0,0.05,15,3)
arrows(0,-1.05,0,1.05,0.05,15,3)
polygon(c(0.2,0.2,0.8,0.8),c(-0.1,0.1,0.1,-0.1),border="white",col="white")
polygon(c(-0.3,-0.3,-0.7,-0.7),c(-0.1,0.1,0.1,-0.1),border="white",col="white")
polygon(c(-0.1,0.1,0.1,-0.1),c(0.3,0.3,0.7,0.7),border="white",col="white")
polygon(c(-0.1,0.1,0.1,-0.1),c(-0.3,-0.3,-0.7,-0.7),border="white",col="white")

lines(cos(th),sin(th),col="black",lty=1)
nums_dot = c(1,5,7,11,13,17,19,23)
nums_30 = c(2,4,8,10,14,16,20,22)
nums_45 = c(3,9,15,21)
nums_90 = c(6,12,18,24)

lty = rep(c(1,3,2,1,2,3),4)
col = rep(c("black","grey","maroon","black","maroon","grey"),4)
pac = c("$(1,0)$",
        "",
        "$\\left(\\frac{\\sqrt{3}}{2},\\frac{1}{2}\\right)$",
        "$\\left(\\frac{\\sqrt{2}}{2},\\frac{\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{1}{2},\\frac{\\sqrt{3}}{2}\\right)$",
        "",
        "$(0,1)$",
        "",
        "$\\left(\\frac{-1}{2},\\frac{\\sqrt{3}}{2}\\right)$",
        "$\\left(\\frac{-\\sqrt{2}}{2},\\frac{\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{-\\sqrt{3}}{2},\\frac{1}{2}\\right)$",
        "",
        "$(-1,0)$",
        "",
        "$\\left(\\frac{-\\sqrt{3}}{2},\\frac{-1}{2}\\right)$",
        "$\\left(\\frac{-\\sqrt{2}}{2},\\frac{-\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{-1}{2},\\frac{-\\sqrt{3}}{2}\\right)$",
        "",
        "$(0,-1)$",
        "",
        "$\\left(\\frac{1}{2},\\frac{-\\sqrt{3}}{2}\\right)$",
        "$\\left(\\frac{\\sqrt{2}}{2},\\frac{-\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{\\sqrt{3}}{2},\\frac{-1}{2}\\right)$",
        "")

angs = c("0 or $2\\pi=360$°",
         "","$\\pi/6=30$°","$\\pi/4=45$°","$\\pi/3=60$°","","$\\pi/2=90$°",
         "","$2\\pi/3=120$°","$3\\pi/4=135$°","$5\\pi/6=150$°","","$\\pi=180$°",
         "","$7\\pi/6=210$°","$5\\pi/4=225$°","$4\\pi/3=240$°","","$3\\pi/2=270$°",
         "","$5\\pi/3=300$°","$7\\pi/4=315$°","$11\\pi/6=330$°",""
         )

for(i in 1:24){
    t = (i-1)*pi/12
    lines(c(0,cos(t)),c(0,sin(t)),lty=3,col="lightgrey")
    lines(c(0,0.25*cos(t)),c(0,0.25*sin(t)),lty=lty[i],col=col[i])
    lines(c(0.75*cos(t),cos(t)),c(0.75*sin(t),sin(t)),lty=lty[i],col=col[i])
    text(1.17*cos(t),1.17*sin(t),TeX(pac[i]),col=col[i],cex=0.7)
    if(pac[i]!=""){
        points(cos(t),sin(t),pch=19,col=col[i])
    }
    text(0.5*cos(t),0.5*sin(t),TeX(angs[i]),col=col[i],srt=(t/pi*180+90)%%180-90,cex=1)
}
```

So, for example:

\begin{align*}
\sin\left(\frac{2\pi}{3}\right)&=\frac{\sqrt{3}}{2} &
\cos\left(\frac{2\pi}{3}\right)&=\frac{-1}{2} &
\tan\left(\frac{2\pi}{3}\right)&=\frac{\left(\frac{\sqrt{3}}{2}\right)}{\left(\frac{-1}{2}\right)}=-\sqrt{3}
\end{align*}






