---
title: "Right-triangle trigonometry cheat sheet"
output: 
    pdf_document: default
    html_document: default
---

\pagenumbering{gobble}
\vspace{-0.5in}

```{r,echo=F,fig.dim=c(2,2),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(0,0.9),ylim=c(-0.1,0.8))
th = seq(0,pi/2,pi/360)
# arrows(-0.05,0,1.05,0,0.05,15)
# arrows(0,-0.05,0,1.05,0.05,15)
# lines(cos(th),sin(th),col="grey",lty=2)
x = 0.8
y = 0.6
t = atan(y/x)
polygon(c(0,x,x),c(0,0,y),border=rgb(0.3,0,0.7),lwd=2)
dd = 0.03
lines(c(x-dd,x-dd,x),c(0,dd,dd))
text(x/2,y/2,"hyp",srt=t*180/pi,adj=c(0.5,-0.3))
text(x/2,0,"adj",srt=0,adj=c(0.5,1.3))
text(x,y/2,"opp",srt=90,adj=c(0.5,1.3))

thth = seq(0,t,pi/360)
n = length(thth)
ar = 0.2
art = 0.27
lines(ar*cos(thth),ar*sin(thth),col="red",lwd=2)
text(art*cos(t/2),art*sin(t/2),TeX("$\\theta$"),col="red")
arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.1,20,col="red",lwd=3)
arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.08,10,col="red",lwd=3)
```

## SOHCAHTOA

\begin{align*}
\sin(\theta) ~&=~ \frac{\text{opp}}{\text{hyp}} & \text{opp} ~&=~ \text{hyp}\cdot\sin(\theta) & \text{hyp} ~&=~ \frac{\text{opp}}{\sin(\theta)} & \theta ~=~ \arcsin\left(\frac{\text{opp}}{\text{hyp}}\right)\\\\
\cos(\theta) ~&=~ \frac{\text{adj}}{\text{hyp}} & \text{adj} ~&=~ \text{hyp}\cdot\cos(\theta) & \text{hyp} ~&=~ \frac{\text{adj}}{\cos(\theta)} & \theta ~=~ \arccos\left(\frac{\text{adj}}{\text{hyp}}\right)\\\\
\tan(\theta) ~&=~ \frac{\text{opp}}{\text{adj}} & \text{opp} ~&=~ \text{adj}\cdot\tan(\theta) & \text{adj} ~&=~ \frac{\text{opp}}{\tan(\theta)} & \theta ~=~ \arctan\left(\frac{\text{opp}}{\text{adj}}\right)
\end{align*}

## Tangent Identity

$$\tan(\theta)~=~\frac{\sin(\theta)}{\cos(\theta)}$$

## Pythagorean Identities

\begin{align*}
\mathrm{adj^2+opp^2}&=\mathrm{hyp^2} & \mathrm{hyp}&=\sqrt{\mathrm{adj^2+opp^2}} & \mathrm{adj}&=\sqrt{\mathrm{hyp^2-opp^2}} & \mathrm{opp}&=\sqrt{\mathrm{hyp^2-adj^2}}
\end{align*}

\begin{align*}
\sin^2(\theta)+\cos^2(\theta)&=1 & \sin(\theta)&=\sqrt{1-\cos^2(\theta)} & \cos(\theta)&=\sqrt{1-\sin^2(\theta)}\\\\
\tan^2(\theta)+1&=\frac{1}{\cos^2(\theta)} & \tan(\theta)&=\sqrt{\frac{1-\cos^2(\theta)}{\cos^2(\theta)}} &
\cos(\theta)&=\sqrt{\frac{1}{\tan^2(\theta)+1}}\\\\
\tan^2(\theta)+1&=\frac{1}{1-\sin^2(\theta)} & \tan(\theta)&=\sqrt{\frac{\sin^2(\theta)}{1-\sin^2(\theta)}} &
\sin(\theta)&=\sqrt{\frac{\tan^2(\theta)}{\tan^2(\theta)+1}}\\\\
\end{align*}

\newpage

# Special Right Triangles

## Isosceles Right Triangle

* Both legs are congruent, and both acute angles are congruent.
* Each acute angle has a measure of $45^{\circ}$, which is equivalent to $\frac{\pi}{4}$ radians.

```{r,echo=F,fig.dim=c(2,2),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(0,0.9),ylim=c(-0.1,0.8))
th = seq(0,pi/2,pi/360)
# arrows(-0.05,0,1.05,0,0.05,15)
# arrows(0,-0.05,0,1.05,0.05,15)
# lines(cos(th),sin(th),col="grey",lty=2)
x = 1/sqrt(2)
y = 1/sqrt(2)
t = atan(y/x)
polygon(c(0,x,x),c(0,0,y),border=rgb(0.3,0,0.7),lwd=2)
dd = 0.03
lines(c(x-dd,x-dd,x),c(0,dd,dd))
text(x/2,y/2,"1",srt=t*180/pi,adj=c(0.5,-0.3))
text(x/2,0,"x",srt=0,adj=c(0.5,1.3))
text(x,y/2,"x",srt=90,adj=c(0.5,1.3))

thth = seq(0,t,pi/360)
n = length(thth)
ar = 0.2
art = 0.27
lines(ar*cos(thth),ar*sin(thth),col="red",lwd=2)
text(art*cos(t/2),art*sin(t/2),TeX("$\\frac{\\pi}{4}$"),col="red")
```

Solve $x^2+x^2=1^2$ to get $x=\frac{\sqrt{2}}{2}$. Thus,


\begin{align*}
\sin\left(\frac{\pi}{4}\right)&=\frac{\sqrt{2}}{2} & 
\cos\left(\frac{\pi}{4}\right)&=\frac{\sqrt{2}}{2} &
\tan\left(\frac{\pi}{4}\right)&=\frac{\left(\frac{\sqrt{2}}{2}\right)}{\left(\frac{\sqrt{2}}{2}\right)}=1
\end{align*}

## Half of an equilateral

* After cutting an equilateral triangle in half (through a line of symmetry), we get one leg half as long as the hypotenuse. We also get $30^{\circ}$ and $60^{\circ}$ as the acute angle measures. In radians, the acute angle measures of $\frac{\pi}{6}$ and $\frac{\pi}{3}$.

```{r,echo=F,fig.dim=c(2,2),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(0,1),ylim=c(-0.5,0.5))
th = seq(0,pi/2,pi/360)
# arrows(-0.05,0,1.05,0,0.05,15)
# arrows(0,-0.05,0,1.05,0.05,15)
# lines(cos(th),sin(th),col="grey",lty=2)
x = sqrt(3)/2
y = 1/2
t = atan(y/x)
polygon(c(0,x,x),c(0,-y,y),border=rgb(0.3,0,0.7),lwd=1,lty=2)
polygon(c(0,x,x),c(0,0,y),border=rgb(0.3,0,0.7),lwd=2)
dd = 0.03
lines(c(x-dd,x-dd,x),c(0,dd,dd))
text(x/2,y/2,"1",srt=t*180/pi,adj=c(0.5,-0.3))
text(x/2,0,"x",srt=0,adj=c(0.5,1.3))
text(x,y/2,"1/2",srt=90,adj=c(0.5,1.3))

thth = seq(0,t,pi/360)
n = length(thth)
ar = 0.3
art = 0.4
lines(ar*cos(thth),ar*sin(thth),col="red",lwd=2)
text(art*cos(t/2),art*sin(t/2),TeX("$\\frac{\\pi}{6}$"),col="red",cex=0.9)
ar = 0.15
art = 0.27
thb = seq(7*pi/6,3*pi/2,pi/360)
tb = mean(c(7*pi/6,3*pi/2))
lines(x+ar*cos(thb),y+ar*sin(thb),col="maroon",lwd=2)
text(x+art*cos(tb),y+art*sin(tb),TeX("$\\frac{\\pi}{3}$"),col="maroon",cex=0.9)
```

Solve $x^2+\left(\frac{1}{2}\right)^2=1^2$ to get $x=\frac{\sqrt{3}}{2}$. Thus,

\begin{align*}
\sin\left(\frac{\pi}{6}\right)&=\frac{1}{2} & 
\cos\left(\frac{\pi}{6}\right)&=\frac{\sqrt{3}}{2} &
\tan\left(\frac{\pi}{6}\right)&=\frac{\left(\frac{1}{2}\right)}{\left(\frac{\sqrt{3}}{2}\right)}=\frac{\sqrt{3}}{3} \\\\
\sin\left(\frac{\pi}{3}\right)&=\frac{\sqrt{3}}{2} & 
\cos\left(\frac{\pi}{3}\right)&=\frac{1}{2} &
\tan\left(\frac{\pi}{3}\right)&=\frac{\left(\frac{\sqrt{3}}{2}\right)}{\left(\frac{1}{2}\right)}=\sqrt{3}
\end{align*}

