```{r,echo=FALSE}
library(reticulate)
deg = sample(4:6,1)
a = sample(c(-5:-2,2:5),1)
while(T){
  cf = sample(c(0,sample(c(-7:-1,1:7),deg-1)))
  bots = c(cf[1])
  mids = numeric()
  for(i in 2:deg){
    mids = c(mids,bots[i-1]*a)
    bots = c(bots,cf[i]+mids[i-1])
  }
  if(cf[1]!=0 && max(abs(c(mids,bots)))<100){break}
}
nans = deg*3


pn = paste0("(",cf,")*x^",(deg-1):0,collapse="+")
dn = paste0("x-(",a,")",collapse="")

ansnums = c(cf,a,mids,bots)

al = sort(unique(ansnums))
anli = paste0("* ",al,"\n")
fullanli = paste0(rep(anli,3*deg),collapse="")
schoices = paste0(rep("schoice",3*deg),collapse="|")

ans = character()
for(i in 1:(3*deg)){
  ans = c(ans,paste0(1*(al==ansnums[i]),collapse = ""))
}
theans = paste0(ans,collapse="|")

trs = "<table style='width:50%'><tr><td class='r'></td>"
for(i in 1:deg){
  trs = paste0(trs,"<td>##ANSWER",i,"##</td>")
}
trs = paste0(trs,"</tr><tr><td class='r'>##ANSWER",deg+1,"##</td><td class='b'></td>")
for(i in (deg+2):(2*deg)){
  trs = paste0(trs,"<td class='b'>##ANSWER",i,"##</td>")
}
trs = paste0(trs,"</tr><tr><td class='r'></td>")
for(i in (2*deg+1):(3*deg)){
  trs = paste0(trs,"<td>##ANSWER",i,"##</td>")
}
trs = paste0(trs,"</tr></table>")
```


Question
========

<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
select {
  width: 70px;
}
</style>

```{python, echo=FALSE}
from sympy import *
x = symbols("x")
pn = latex(sympify(r.pn))
dn = latex(sympify(r.dn))
```

Let polynomial $p(x)=`r py$pn`$. 

Use [synthetic division](https://en.wikipedia.org/wiki/Synthetic_division){target="_blank"} to divide $p(x)$ by $`r py$dn`$.


```{r,echo=FALSE,results='asis'}
cat(trs)
```

Answerlist
--------
`r fullanli`


Solution
========

<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
select {
  width: 70px;
}
</style>

Begin by filling the top row with the coefficients of the polynomial. Remember to use 0 whenever a term is missing.

Then, since the denominator is $`r py$dn`$, fill the leftmost element with $`r a`$.

```{r,echo=FALSE,results='asis'}
trs = "<table style='width:50%'><tr><td class='r'></td>"
for(i in 1:deg){
  trs = paste0(trs,"<td>",cf[i],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r'>",a,"</td><td class='b'></td>")
for(i in (deg+2):(2*deg)){
  trs = paste0(trs,"<td class='b'> </td>")
}
trs = paste0(trs,"</tr><tr><td class='r'> </td>")
for(i in (2*deg+1):(3*deg)){
  trs = paste0(trs,"<td></td>")
}
trs = paste0(trs,"</tr></table>")
cat(trs)
```


Drop the leading coefficient to the bottom row. 

```{r,echo=FALSE,results='asis'}
trs = "<table style='width:50%'><tr><td class='r'></td>"
for(i in 1:deg){
  trs = paste0(trs,"<td>",cf[i],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r' style='color:blue;'>",a,"</td><td class='b'></td>")
for(i in (deg+2):(2*deg)){
  trs = paste0(trs,"<td class='b'> </td>")
}
trs = paste0(trs,"</tr><tr><td class='r'></td><td style='color:red;'>",cf[1],"</td>")
for(i in (2*deg+2):(3*deg)){
  trs = paste0(trs,"<td></td>")
}
trs = paste0(trs,"</tr></table>")
cat(trs)
```

Multiply the <span style="color:blue;">`r a`</span> by the <span style="color:red;">`r cf[1]`</span> to get <span style="color:green;">`r a*cf[1]`</span>.

```{r,echo=FALSE,results='asis'}
trs = "<table style='width:50%'><tr><td class='r'></td>"
for(i in 1:deg){
  trs = paste0(trs,"<td>",cf[i],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r' style='color:blue;'>",a,"</td><td class='b'></td><td class='b' style='color:green'>",cf[1]*a,"</td>")
for(i in (deg+3):(2*deg)){
  trs = paste0(trs,"<td class='b'> </td>")
}
trs = paste0(trs,"</tr><tr><td class='r'></td><td style='color:red;'>",cf[1],"</td>")
for(i in (2*deg+2):(3*deg)){
  trs = paste0(trs,"<td></td>")
}
trs = paste0(trs,"</tr></table>")
cat(trs)
```

Add `r cf[2]` and `r a*cf[1]` to get `r cf[2]+a*cf[1]`.

```{r,echo=FALSE,results='asis'}
trs = "<table style='width:50%'><tr><td class='r'></td>"
for(i in 1:deg){
  trs = paste0(trs,"<td>",cf[i],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r' style='color:blue;'>",a,"</td><td class='b'></td><td class='b' style='color:green'>",cf[1]*a,"</td>")
for(i in (deg+3):(2*deg)){
  trs = paste0(trs,"<td class='b'> </td>")
}
trs = paste0(trs,"</tr><tr><td class='r'></td><td style='color:red;'>",cf[1],
             "</td><td>",bots[2],"</td>")
for(i in (2*deg+3):(3*deg)){
  trs = paste0(trs,"<td></td>")
}
trs = paste0(trs,"</tr></table>")
cat(trs)
```

Continue to alternate between multiplication (by `r a`) and addition.

```{r,echo=FALSE,results='asis'}
trs = "<table style='width:50%'><tr><td class='r'></td>"
for(i in 1:deg){
  trs = paste0(trs,"<td>",cf[i],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r'>",a,"</td><td class='b'></td>")
for(i in (deg+2):(2*deg)){
  trs = paste0(trs,"<td class='b'>",mids[i-deg-1],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r'> </td>")
for(i in (2*deg+1):(3*deg)){
  trs = paste0(trs,"<td>",bots[i-2*deg],"</td>")
}
trs = paste0(trs,"</tr></table>")
cat(trs)
```



```{python,echo=FALSE}
ex = (sympify(r.pn))/(sympify(r.dn))
lex = latex(ex)
qex = div(sympify(r.pn), sympify(r.dn), domain ='QQ')
qex1 = latex(qex[0])
qex2 = latex(qex[1])
```

The last number is called the remainder. One way to express the answer is with an [identity](https://en.wikipedia.org/wiki/Identity_(mathematics)){target="_blank"} (an equation that's true for all $x$):

$$`r py$lex` ~=~ `r py$qex1` + \frac{`r py$qex2`}{`r py$dn`}$$

From the [remainder theorem](https://en.wikipedia.org/wiki/Polynomial_remainder_theorem){target="_blank"}, we also know that $p(`r a`) = `r py$qex2`$. This can be seen by multiplying both sides by `r py$dn` and pluggling in $x=`r a`$.

$$p(x) ~=~ `r py$pn` ~=~ (`r py$qex1`)(`r py$dn`) + (`r py$qex2`) $$


```{r,echo=FALSE}
pf = gsub("x",paste0("(",a,")",collapse=""),py$pn)
```

$$p(`r a`) ~=~ `r pf` ~=~ (\ldots)(0) + (`r py$qex2`) $$

$$p(`r a`) ~=~ `r py$qex2`$$


Meta-information
============
extype: cloze
exclozetype: `r schoices`
exsolution: `r theans`
exname: synthetic_division