```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
primes = c(2,3,5,7)
r1 = sample(primes,2)
a1 = r1[1]
b1 = r1[2]*sample(c(-1,1),1)
r1 = -b1/a1
while(T){
  r2 = sample(primes,2)
  a2 = r2[1]
  b2 = r2[2]*sample(c(-1,1),1)
  r2 = -b2/a2
  if(r1!=r2 && r1!=-r2){break}
}
if(r1<r2){
  n1 = -b1
  d1 = a1
  n2 = -b2
  d2 = a2
} else {
  n1 = -b2
  d1 = a2
  n2 = -b1
  d2 = a1
}
a = a1*a2
b = a1*b2+a2*b1
c = b1*b2
eq = paste0(a,"x^2+",b,"x+",c)
eq = gsub("+-","-",eq,fixed=TRUE)
eq = gsub("+1x","+x",eq,fixed=TRUE)
eq = gsub("-1x","-x",eq,fixed=TRUE)

fracs = c(n1/d1,n2/d2,-n1/d1,-n2/d2)
ns = c(n1,n2,-n1,-n2)
ds = c(d1,d2,d1,d2)
while(length(fracs)<8){
  r = sample(primes,2)
  n = r[1]*sample(c(-1,1),1)
  d = r[2]
  r = n/d
  if(sum(r==fracs)==0){
    fracs = c(fracs,r,-r)
    ns = c(ns,n,-n)
    ds = c(ds,d,d)
  }
}
ord = numeric()
for(i in sort(fracs)){
  ord = c(ord,which(fracs==i))
}
sfs = fracs[ord]
sns = ns[ord]
sds = ds[ord]
anli = paste0("* ",sns,"/",sds,"\n",collapse="")
sol = paste0(1*(sfs==fracs[1])+1*(sfs==fracs[2]),collapse="")
```


Question
========

The quadratic formula states:

* If $ax^2+bx+c=0$ then:
$$x = \frac{-b\pm\sqrt{b^2-4ac}}{2a}$$

Use the quadratic formula to solve the quadratic equation:
$$`r eq`=0$$

Answerlist
--------

`r anli`


Solution
========

Plug numbers into the quadratic formula.

$$x = \frac{-(`r b`)\pm\sqrt{(`r b`)^2-4(`r a`)(`r c`)}}{2(`r a`)} $$

Simplify.

$$x = \frac{`r -b` \pm \sqrt{`r b^2-4*a*c`}}{`r 2*a`}$$

$$x = \frac{`r -b` \pm `r sqrt(b^2-4*a*c)`}{`r 2*a`}$$

$$x = \frac{`r -b-sqrt(b^2-4*a*c)`}{`r 2*a`}~~~~~~~~\text{OR}~~~~~~~~\frac{`r -b+sqrt(b^2-4*a*c)`}{`r 2*a`}$$

$$x = \frac{`r n1`}{`r d1`} ~~~~~~\text{OR}~~~~~~~ x=\frac{`r n2`}{`r d2`} $$

### Factoring

I should mention if you are handy with factoring, you might create an equivalent (factored) equation:

```{r,echo=FALSE}
fex = paste0("(",d1,"x-",n1,")(",d2,"x-",n2,") = 0",collapse="")
fex = gsub("--","+",fex,fixed=TRUE)
```

$$`r fex`$$



Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: quadratic_formula