```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
while(T){
  a = sample(c(-9:-1,1:9),1)
  b = sample(c(-9:-1,1:9),1)
  cn = function(a,b){
    cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
    cn = gsub("0+0i","0",cn,fixed=TRUE)
    cn = gsub("1i","i",cn,fixed=TRUE)
    cn = gsub("-1i","-i",cn,fixed=TRUE)
    cn = gsub("+0i","",cn,fixed=TRUE)
    cn = gsub("-0i","",cn,fixed=TRUE)
    if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
    if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
    return(cn)
  }
  cn1 = cn(a,b)
  m = sqrt(a^2+b^2)
  theta = atan2(b,a)
  if(abs(theta)>pi/4){break}
}
```

Question
========

Let $z_1$ be a complex number with integer components. It is graphed on a [complex plane](https://en.wikipedia.org/wiki/Complex_plane) below. The [argument](https://en.wikipedia.org/wiki/Complex_number#Modulus_and_argument) is the standard angle indicated with $\theta$. 


```{r,fig.dim=c(6,6),echo=FALSE,results="asis"}
library(latex2exp)
par(pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),lwd=2,ylab="imaginary component",xlab="real component")
for(j in seq(-10,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(c(0,a),c(0,b),lwd=2,col="red")
points(a,b,pch=20,cex=1.5,col="black")
th = seq(0,theta,length=100)
r = m/3
r2 = m/2
xx = 1*cos(th)
yy = 1*sin(th)
lines(xx,yy,lwd=2,col="blue")
arrows(xx[length(xx)-1],yy[length(xx)-1],xx[length(xx)],yy[length(xx)],col="blue",length = 0.05,lwd=4)
text(2*cos(theta/2),2*sin(theta/2),TeX("$\\theta$"),lwd=2,col="blue",cex=2.2)
```
\

The argument can be found using the [atan2](https://en.wikipedia.org/wiki/Atan2) function. Find the angle (the argument) of $z_1$ in [radians](https://en.wikipedia.org/wiki/Radian) between $-\pi$ and $\pi$. A negative angle indicates a clockwise rotation from East, and a positive angle indicates a counter-clockwise rotation from East.

*The tolerance is $\pm0.01$.*


Solution
========

The horizontal (real) component is `r a`. The vertical (imaginary) component is `r b`. So,
$$z_1 = `r cn1`$$

A spreadsheet can be used to evaluate ``=atan2(`r a`,`r b`)``. It will provide the answer in radians in the interval between $-\pi$ and $\pi$ as requested.


Meta-information
============
extype: num
exsolution: `r theta`
exname: complex_argument
extol: 0.01