```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
deg = sample(4:7,1)
cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("1i","i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(nchar(cn)>1 && substr(cn,1,2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(nchar(cn)>1 && substr(cn,1,2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}
r = sample(-5:5,1)
a1 = sample(-5:5,1)
b1 = sample(1:3,1)
as = c(r,a1,a1)
bs = c(0,b1,-b1)
cns = c(cn(r,0),cn(a1,b1),cn(a1,-b1))
while(length(cns)<deg){
  if(length(cns)==deg-1 || sample(1:2,1,F,c(0.66,0.34))==1){
    a = sample(-5:5,1)
    b = 0
    cn1 = cn(a,b)
    if(sum(cn1==cns)==0){
      as = c(as,a)
      bs = c(bs,b)
      cns = c(cns,cn1)
    }
  } else {
    a = sample(-5:5,1)
    b = sample(1:5,1)
    cn1 = cn(a,b)
    cn2 = cn(a,-b)
    if(sum(cn1==cns)==0){
      as = c(as,a,a)
      bs = c(bs,b,-b)
      cns = c(cns,cn1,cn2)
    }
  }
}
ex = paste0("(x-(",as,"+",bs,"*I))",collapse="*")
ex = gsub("+-","-",ex,fixed=TRUE)

asall = as
bsall = bs
cnall = cns
while(length(cnall)<10){
  if(length(cnall)==9 || sample(1:2,1,F,c(0.66,0.34))==1){
    a = sample(-5:5,1)
    b = 0
    cn1 = cn(a,b)
    if(sum(cn1==cnall)==0){
      asall = c(asall,a)
      bsall = c(bsall,b)
      cnall = c(cnall,cn1)
    }
  } else {
    a = sample(-5:5,1)
    b = sample(1:5,1)
    cn1 = cn(a,b)
    cn2 = cn(a,-b)
    if(sum(cn1==cnall)==0){
      asall = c(asall,a,a)
      bsall = c(bsall,b,-b)
      cnall = c(cnall,cn1,cn2)
    }
  }
}

cnall = sort(cnall)
anli = paste0("* ",cnall,"\n",collapse="")

sol = numeric()
for(z in cnall){
  if(sum(z==cns)>0){
    sol=c(sol,1)
  } else {
    sol=c(sol,0)
  }
}
sol = paste0(sol,collapse="")
```


Question
========

```{python,echo=FALSE}
from sympy import *
x = symbols("x")
ex = sympify(r.ex)
ex2 = expand(ex)
lex = latex(ex2)
pex = str(ex2)
```

Find solutions to the polynomial equation below.
$$`r gsub("x","z",py$lex)`=0$$

```{r,echo=FALSE}
link = gsub("**","%5E",py$pex,fixed=TRUE)
link = gsub("+","%2B",link,fixed=TRUE)
link = gsub(" ","",link,fixed=TRUE)
link = gsub("x","z",link,fixed=TRUE)
```


To find the solutions, I'd recommend using [this website](https://samuelj.li/complex-function-plotter/#`r link`), which uses [domain coloring](https://en.wikipedia.org/wiki/Domain_coloring) to visualize the solutions. By default the solutions will appear as the center of concentric rings.



Answerlist
--------

`r anli`


Solution
========


Notice that the degree is `r deg` and there are `r deg` solutions. This hints at the [fundamental theorem of algebra](https://en.wikipedia.org/wiki/Fundamental_theorem_of_algebra).

The solutions: `r cns`


Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: polynomial_complex