```{r,echo=FALSE}
options(scipen=999)
xy = sample(8:30,2)
x = xy[1]
y = xy[2]
```

Question
========

A large square comprises a yellow square, two congruent blue rectangles, and a red square.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.1,1.1),axes=F,ann=F)
N = x+y
b = seq(0,1,length.out=N+1)

polygon(c(0,x/N,x/N,0),c(y/N,y/N,1,1),col="yellow")
polygon(c(1,x/N,x/N,1),c(y/N,y/N,1,1),col="lightblue")
polygon(c(0,x/N,x/N,0),c(0,0,y/N,y/N),col="lightblue")
polygon(c(1,x/N,x/N,1),c(0,0,y/N,y/N),col="pink")

col1 = color=rgb(0.5,0.5,0)
col2 = color=rgb(0.5,0.2,0.2)

text(x/N/2,1.05,"x",cex=1.3,col=col1)
text(-0.05,(1-x/N/2),"x",cex=1.3,col=col1)
text(1-y/N/2,1.05,"y",cex=1.3,col=col2)
text(-0.05,(y/N/2),"y",cex=1.3,col=col2)

```
\

The yellow square has an area of $x^2$ square units. The two blue rectangles have a combined area of $`r 2*y`x$ square units.

What is the area, in square units, of the red square?



Solution
========



Find the area of each blue rectangle.

$$B=\frac{`r 2*y`x}{2}$$
$$B=`r y`x$$


Each blue rectangle has one length of $x$ and another of length $`r y`$.


```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.1,1.1),axes=F,ann=F)
N = x+y
b = seq(0,1,length.out=N+1)

polygon(c(0,x/N,x/N,0),c(y/N,y/N,1,1),col="yellow")
polygon(c(1,x/N,x/N,1),c(y/N,y/N,1,1),col="lightblue")
polygon(c(0,x/N,x/N,0),c(0,0,y/N,y/N),col="lightblue")
polygon(c(1,x/N,x/N,1),c(0,0,y/N,y/N),col="pink")

col1 = color=rgb(0.5,0.5,0)
col2 = color=rgb(0.5,0.2,0.2)

text(x/N/2,-0.05,"x",cex=1.1,col=col1)
text(1.05,(1-x/N/2),"x",cex=1.1,col=col1)
text(1-y/N/2,1.05,y,cex=1.1,col=col2)
text(-0.05,(y/N/2),y,cex=1.1,col=col2)

```
\


The red square has side lengths equal to $y=`r y`$. To find its area, square the side length.

$$R=y^2$$
$$R=`r y`^2$$
$$R=`r y^2`$$

The area of the red square is `r y^2` square units.


Meta-information
============
extype: num
exsolution: `r y^2`
exname: complete_the_square_B