```{r,echo=FALSE}
options(scipen=999)
digits = sample(2:9,4)
At = digits[1]
Ao = digits[2]
Bt = digits[3]
Bo = digits[4]
A = At*10+Ao
B = Bt*10+Bo

p1 = At*Bt
p2 = Ao*Bt
p3 = At*Bo
p4 = Ao*Bo

ch1 = c(1,10,100,1000)*p1
ch2 = c(1,10,100,1000)*p2
ch3 = c(1,10,100,1000)*p3
ch4 = c(1,10,100,1000)*p4

sol1 = "0010"
sol2 = "0100"
sol3 = "0100"
sol4 = "1000"

al1 = paste0("* ",ch1,collapse="\n")
al2 = paste0("* ",ch2,collapse="\n")
al3 = paste0("* ",ch3,collapse="\n")
al4 = paste0("* ",ch4,collapse="\n")

tot5 = 100*p1+10*p2
tot6 = 10*p3+p4
tot7 = 100*p1+10*p3
tot8 = 10*p2+p4
tot9 = A*B

cht = sort(c(tot5,tot6,tot7,tot8,tot9))
alt = paste0("* ",cht,collapse="\n")
sol5 = paste0(1*(tot5==cht),collapse="")
sol6 = paste0(1*(tot6==cht),collapse="")
sol7 = paste0(1*(tot7==cht),collapse="")
sol8 = paste0(1*(tot8==cht),collapse="")
sol9 = paste0(1*(tot9==cht),collapse="")

```


Question
========

Let's consider an alternative way to multiply `r A` and `r B`.

First, let's break each number into its tens and ones.

$$`r A` ~~=~~ `r At*10`+`r Ao`$$
$$`r B` ~~=~~ `r Bt*10`+`r Bo`$$

Now, find all 4 indicated products. Also, find the totals.

```{css,echo=F}
.boxy td {
    padding: 2em;
    border: 1px solid black;
    text-align: center;
    font-size: 1em;
    color: black;
    background-color: white;
  }
.boxy th {
    background-color: rgb(200, 200, 200);
    color: black;
    padding: 2em;
    font-size: 1em;
    text-align: center;
    border: 1px solid black;
  }
.boxy td:first-child {
    background-color: rgb(200, 200, 200);
    color: black;
    padding: 2em;
    font-size: 1em;
    text-align: center;
    border: 1px solid black;
  }
.boxy select {
    width: 7em;
    margin-bottom: 0.8em;
    margin-top: 0.8em;
    margin-right: 0.8em;
    margin-left: 0.8em;
}
```

<div class="boxy">

|  \* | $`r At*10`$ | $`r Ao`$ | **total** |
|:---:|:---:|:---:|:---:|
|$`r Bt*10`$|##ANSWER1##|##ANSWER2##|##ANSWER5##|
|$`r Bo`$|##ANSWER3##|##ANSWER4##|##ANSWER6##|
| **total** |##ANSWER7## |##ANSWER8##|##ANSWER9##|

</div>






Answerlist
--------

`r al1`
`r al2`
`r al3`
`r al4`
`r alt`
`r alt`
`r alt`
`r alt`
`r alt`




Solution
========

$$`r A`\cdot `r B` = `r A*B`$$


```{css,echo=F}
.boxy td {
    padding: 1em;
    border: 1px solid black;
    text-align: center;
    font-size: 1em;
    color: black;
    background-color: white;
  }
.boxy th {
    background-color: rgb(200, 200, 200);
    color: black;
    padding: 1em;
    font-size: 1em;
    text-align: center;
    border: 1px solid black;
  }
.boxy td:first-child {
    background-color: rgb(200, 200, 200);
    color: black;
    padding: 1em;
    font-size: 1em;
    text-align: center;
    border: 1px solid black;
  }
```

<div class="boxy">

|  \* | $`r At*10`$ | $`r Ao`$ | **total** |
|:---:|:---:|:---:|:---:|
|$`r Bt*10`$|`r At*Bt*100`|`r Ao*Bt*10`|`r tot5`|
|$`r Bo`$|`r At*Bo*10`|`r Ao*Bo`|`r tot6`|
| **total** |`r tot7`|`r tot8`|`r tot9`|

</div>


At some point I learned about the [multiplication by lines](https://www.mathnstuff.com/math/spoken/here/2class/60/bylines.htm) method. You'll notice there are `r At` lines above `r Ao` lines, both with positive slope. There are also `r Bt` lines above `r Bo` lines, both with negative slope. The number of intersections in the four corners are found with multiplication: $`r At`\cdot`r Bt`=`r p1`$ and $`r Ao`\cdot`r Bt`=`r p2`$ and $`r At`\cdot`r Bo`=`r p3`$  and $`r Ao`\cdot`r Bo`=`r p4`$.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)

for(i in 1:Ao){
    abline(-0.6-0.05*Ao/2+0.05*i,1)
}
for(i in 1:At){
    abline(0.6-0.05*At/2+0.05*i,1)
}
for(i in 1:Bo){
    abline(-0.6-0.05*Bo/2+0.05*i,-1)
}
for(i in 1:Bt){
    abline(0.6-0.05*Bt/2+0.05*i,-1)
}

text(0,0.9,paste0(At,"*",Bt," = ",At*Bt,"\n",At*10,"*",Bt*10," = ",At*Bt*100),col="red",cex=1.5)
text(0.6,0.3,paste0(Ao,"*",Bt," = ",Ao*Bt,"\n",Ao,"*",Bt*10," = ",Ao*Bt*10),col="red",cex=1.5)
text(-0.6,0.3,paste0(At,"*",Bo," = ",At*Bo,"\n",At*10,"*",Bo," = ",At*Bo*10),col="red",cex=1.5)
text(0,-0.4,paste0(Ao,"*",Bo," = ",Ao*Bo),col="red",cex=1.5)

```
\

$$`r p1*100` + `r p2*10` + `r p3*10` + `r p4` ~~=~~ `r A*B`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`|`r sol6`|`r sol7`|`r sol8`|`r sol9`
exname: multiply_2digits