---
output: pdf_document
params:
    rseed: 1
    showsol: true
urlcolor: blue
---

```{r,echo=F}
set.seed(params$rseed)
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## Practice finding inverse functions

1. Find the inverse function.
$$f(x)~=~ 3x+5$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}(x)~=~\\frac{x-5}{3}$$\n\n\\color{black}")
```

\vfill

2. Find the inverse function.
$$f(x)~=~ \frac{x-4}{7}$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}(x)~=~7x+4$$\n\n\\color{black}")
```

\vfill

3. Find the inverse function.
$$f(x)~=~ 6(x+1)$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}(x)~=~\\frac{x}{6}-1$$\n\n\\color{black}")
```

\vfill

4. Find the inverse function.
$$f(x)~=~ 8+\frac{x}{3}$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}(x)~=~3(x-8)$$\n\n\\color{black}")
```

\vfill

\newpage

5. Find the inverse function.
$$f(x)~=~ 7x-2$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}~=~\\frac{x+2}{7}$$\n\n\\color{black}")
```

\vfill

6. Find the inverse function.
$$f(x)~=~ \frac{5+x}{9}$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}~=~9x-5$$\n\n\\color{black}")
```

\vfill

7. Find the inverse function.
$$f(x)~=~ (x-8)\cdot 3$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}~=~\\frac{x}{3}+8$$\n\n\\color{black}")
```

\vfill

8. Find the inverse function.
$$f(x)~=~ \frac{x}{5}-2$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$f^{-1}~=~5(x+2)$$\n\n\\color{black}")
```

\vfill
