---
output: pdf_document
params:
    rseed: 1
    showsol: true
urlcolor: blue
---

```{r,echo=F}
set.seed(params$rseed)
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## Practice finding inverse functions

1. Find the inverse function.
$$f(x)~=~ 3x+5$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=3x+5$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=3y+5$$Subtract 5 from both sides.$$x-5=3y$$Divide both sides by 3.$$\\frac{x-5}{3}=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~\\frac{x-5}{3}$$\n\n\\color{black}")
```

\vfill

2. Find the inverse function.
$$f(x)~=~ \frac{x-4}{7}$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=\\frac{x-4}{7}$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=\\frac{y-4}{7}$$ Multiply both sides by 7.$$7x=y-4$$Add 4 to both sides.$$7x+4=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~7x+4$$\n\n\\color{black}")
```

\vfill

\newpage

3. Find the inverse function.
$$f(x)~=~ 6(x+1)$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=6(x+1)$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=6(y+1)$$ Divide both sides by 6.$$\\frac{x}{6}=y+1$$Subtract 1 from both sides.$$\\frac{x}{6}-1=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~\\frac{x}{6}-1$$\n\n\\color{black}")
```

\vfill

4. Find the inverse function.
$$f(x)~=~ 8+\frac{x}{3}$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=8+\\frac{x}{3}$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=8+\\frac{y}{3}$$ Subtract 8 from both sides.$$x-8=\\frac{y}{3}$$Multiply both sides by 3.$$3(x-8)=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~3(x-8)$$\n\n\\color{black}")
```

\vfill

\newpage

5. Find the inverse function.
$$f(x)~=~ 7x-2$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=7x-2$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=7x-2$$ Add 2 to both sides.$$x+2=7y$$Divide both sides by 7.$$\\frac{x+2}{7}=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~\\frac{x+2}{7}$$\n\n\\color{black}")
```

\vfill

6. Find the inverse function.
$$f(x)~=~ \frac{5+x}{9}$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=\\frac{5+x}{9}$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=\\frac{5+y}{9}$$ Multiply both sides by 9.$$9x=5+y$$Subtract 5 from both sides.$$9x-5=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~9x-5$$\n\n\\color{black}")
```

\vfill

\newpage

7. Find the inverse function.
$$f(x)~=~ (x-8)\cdot 3$$

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=(x-8)\\cdot 3$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=(y-8)\\cdot 3$$ Divide both sides by 3.$$\\frac{x}{3}=y-8$$Add 8 to both sides.$$\\frac{x}{3}+8=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~\\frac{x}{3}+8$$\n\n\\color{black}")
```

\vfill

8. Find the inverse function.
$$f(x)~=~ \frac{x}{5}-2$$

\vfill


```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}Remove function notation by replacing $f(x)$ with $y$.$$y=\\frac{x}{5}-2$$Swap $x$ and $y$, so now $y$ represents the inverse function, $f^{-1}(x)$.$$x=\\frac{x}{5}-2$$ Add 2 to both sides.$$x+2=\\frac{x}{5}$$Multiply both sides by 5.$$5(x+2)=y$$ Return to function notation. Remember, after the swap, $y$ represents the inverse function. $$f^{-1}(x)~=~5(x+2)$$\n\n\\color{black}")
```


\vfill
