---
title: "Creating inverse functions"
date: "Thu Aug 28"
author: "Mr. Worley"
output: 
    slidy_presentation:
        incremental: true
---

# Entrance Ticket

Entrance ticket on Canvas: [ET_08_28](https://bart.instructure.com/courses/2110/quizzes/3142)


# Note: fraction bars have implied parentheses.

The fraction bar has implied parentheses.
$$\frac{3+4}{5+6}~~=~~(3+4)\div(5+6)$$

# Find inverse of function defined with algebraic expression

* We begin with simple functions that can be understood as taking an input and then applying a series of elementary additions, subtractions, multiplications, and divisions by integers.
* Find the inverse:
$$f(x)~=~9\cdot\left(\frac{2x+7}{5}-8\right)+3$$
* Start by identifying the sequence of operations applied to $x$. (Describe function $f$.)
    1. Multiply by 2
    2. Add 7
    3. Divide by 5
    4. Subtract 8
    5. Multiply by 9
    6. Add 3
* Replace $f(x)$ with $y$... for... simplicity.
$$y~=~9\cdot\left(\frac{2x+7}{5}-8\right)+3$$
* Swap $x$ and $y$. So, now $y$ represents the inverse function.
$$x~=~9\cdot\left(\frac{2y+7}{5}-8\right)+3$$
* Undo those operations in reverse order to solve for $y$.
    1. Subtract 3. $$x-3~=~9\cdot\left(\frac{2y+7}{5}-8\right)$$
    2. Divide by 9. $$\frac{x-3}{9}~=~\frac{2y+7}{5}-8$$
    3. Add 8. $$\frac{x-3}{9}+8~=~\frac{2y+7}{5}$$
    4. Multiply by 5. $$5\left(\frac{x-3}{9}+8\right)~=~2y+7$$
    5. Subtract 7. $$5\left(\frac{x-3}{9}+8\right)-7~=~2y$$
    6. Divide by 2. $$\frac{5\left(\frac{x-3}{9}+8\right)-7}{2}~=~y$$
* Return to function notation. Remember, after the swap, $y$ is the INVERSE function.
$$\frac{5\left(\frac{x-3}{9}+8\right)-7}{2}~=~f^{-1}(x)$$
* Equality is commutative. We tend to put the function notation on left side.
$$f^{-1}(x)~=~\frac{5\left(\frac{x-3}{9}+8\right)-7}{2}$$


# Simple example

Find the inverse:
$$f(x)~=~ \frac{7+x}{3}$$

* Let's use the standard approach.
* First, get rid of function notation.$$y=\frac{7+x}{3}$$
* Swap $x$ and $y$. $$x=\frac{7+y}{3}$$
* At this point, the $y$ represents the inverse function. Solve for $y$. (Get $y$ by itself.)
* Multiply both sides by 3. $$3x=7+y$$
* Subtract 7 from both sides. $$3x-7=y$$
* Return to function notation. Because we swapped in the beginning, $y$ is the inverse function. $$3x-7=f^{-1}(x)$$
* Use commutative property of equality. We typically put the function notation on the left side.$$f^{-1}(x)~=~3x-7$$


# Simple example 2

Find the inverse:
$$f(x)~=~ 8\left(4+\frac{x}{9}\right)$$


# Inverse function from table


Consider the function $f$ defined by the table below.

```{css,echo=F}
#myContainer table {
        border-collapse: collapse; /* Optional: Collapses borders for a single line */
        border: 2px solid black; /* Border around the entire table */
    }
#myContainer th,
#myContainer td {
        border: 1px solid grey; /* Borders for individual cells */
        padding: 8px; /* Optional: Add padding for better readability */
}
```

<div id="myContainer">

| $x$ | $f(x)$ |
|:---:|:---:|
| 1 | 5 |
| 2 | 3 |
| 3 | 1 |
| 4 | 2 |
| 5 | 4 |

</div>

What values would you use to fill the inverse function's table?

<div id="myContainer">

| $x$ | $f^{-1}(x)$ |
|:---:|:---:|
| 1 |  |
| 2 |  |
| 3 |  |
| 4 |  |
| 5 |  |

</div>


# Inverse function from table


Consider the function $f$ defined by the table below.

```{css,echo=F}
#myContainer table {
        border-collapse: collapse; /* Optional: Collapses borders for a single line */
        border: 2px solid black; /* Border around the entire table */
    }
#myContainer th,
#myContainer td {
        border: 1px solid grey; /* Borders for individual cells */
        padding: 8px; /* Optional: Add padding for better readability */
}
```

<div id="myContainer">

| $x$ | $f(x)$ |
|:---:|:---:|
| 1 | 5 |
| 2 | 3 |
| 3 | 1 |
| 4 | 2 |
| 5 | 4 |

</div>

What values would you use to fill the inverse function's table?

<div id="myContainer">

| $x$ | $f^{-1}(x)$ |
|:---:|:---:|
| 1 | 3 |
| 2 | 4 |
| 3 | 2 |
| 4 | 5 |
| 5 | 1 |

</div>

Notice you swap the two columns, and then sort the first column. We are still "swapping $x$ and $y$".



# Inverse function from table


Consider the function $f$ defined by the table below.

```{css,echo=F}
#myContainer table {
        border-collapse: collapse; /* Optional: Collapses borders for a single line */
        border: 2px solid black; /* Border around the entire table */
    }
#myContainer th,
#myContainer td {
        border: 1px solid grey; /* Borders for individual cells */
        padding: 8px; /* Optional: Add padding for better readability */
}
```

<div id="myContainer">

| $x$ | $f(x)$ |
|:---:|:---:|
| 1 | 4 |
| 2 | 1 |
| 3 | 2 |
| 4 | 5 |
| 5 | 3 |

</div>

What values would you use to fill the inverse function's table?

<div id="myContainer">

| $x$ | $f^{-1}(x)$ |
|:---:|:---:|
| 1 |  |
| 2 |  |
| 3 |  |
| 4 |  |
| 5 |  |

</div>



# Inverse function from curve

Let function $f$ be defined by the (piece-wise linear) curve shown below.

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(mar=c(4,4,0,0))
set.seed(123)
xy = sample(1:9,8)
x = sort(xy[1:4])
y = sort(xy[5:8],decreasing = sample(c(T,F),1))
par(pty="s")
plot(0,0,type="n",xlim=c(0,11),ylim=c(0,11),lwd=2,ylab="y",xlab="x")
for(j in seq(0,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,y,col="blue",lwd=2)
legend("topright","y=f(x)",lwd=2,col="blue")
#abline(0,1,col="black",cex="0.5",lty=2)
```

* How to find the inverse function's curve?
* "SWAP $x$ AND $y$"
* The curve reflects over the $y=x$ line (the 45° line).
* Find the coordinates of the vertices:
$$(`r x[1]`,`r y[1]`)~~~(`r x[2]`,`r y[2]`)~~~(`r x[3]`,`r y[3]`)~~~(`r x[4]`,`r y[4]`)$$
* Swap the coordinates of the vertices:
$$(`r y[1]`,`r x[1]`)~~~(`r y[2]`,`r x[2]`)~~~(`r y[3]`,`r x[3]`)~~~(`r y[4]`,`r x[4]`)$$
* Draw a new curve connecting those new coordinates.


# Inverse function from curve

The original function $f$ and the inverse function $f^{-1}$ are mirror reflections over the $y=x$ line. This is because we "swap $x$ and $y$."

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(mar=c(4,4,0,0))
library(latex2exp)
set.seed(123)
xy = sample(1:9,8)
x = sort(xy[1:4])
y = sort(xy[5:8],decreasing = sample(c(T,F),1))
par(pty="s")
plot(0,0,type="n",xlim=c(0,11),ylim=c(0,11),lwd=2,ylab="y",xlab="x")
for(j in seq(0,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,y,col="blue",lwd=2)
lines(y,x,col="red",lwd=2)
lines(c(0,11),c(0,11),col="black",lwd=0.5,lty=2)
legend("topright",c(TeX("$y=f(x)$"),TeX("$y=f^{-1}(x)$")),
       lwd=c(2,2),col=c("blue","red"),
       lty=c(1,1))

```



