```{r,echo=FALSE}
exab = sample(2:9,2)
while(T){
    ab = sample(8:49,2)*2/10
    a = ab[1]
    b = ab[2]
    if(!(a%%1==0) && !(b%%1==0) && abs(b-a)>1){break}
}

achoice = signif(a+0.2*(sample(-5:0,1)+0:5),2)
bchoice = signif(b+0.2*(sample(-5:0,1)+0:5),2)
p = signif(a*b,2)
pchoice = signif(p+0.2*(sample(-5:0,1)+0:5)*10^floor(log10(p)),2)

sol1 = paste0(1*(achoice==a),collapse="")
sol2 = paste0(1*(bchoice==b),collapse="")
sol3 = paste0(1*(pchoice==p),collapse="")

```


Question
========

Before cheap hand-held calculators, students learned to use [slide rules](https://en.wikipedia.org/wiki/Slide_rule) to multiply numbers. As a simple example, we can see the slide rule below can be used to show that `r sprintf("%.02f",exab[1])` times `r sprintf("%.02f",exab[2])` equals `r sprintf("%.02f",prod(exab))`.

```{r,echo=F,fig.dim=c(3,10)}
par(mar=c(0,0,0,0))
bmp = 0.1
plot(0,0,"n",xlim=c(0,1),ylim=c(0-bmp,2+bmp),axes=F,ann=F)
for(i in seq(1.2,9.8,0.2)){
    for(j in 0:1){
        num = i*10^j
        y = log10(num)
        lines(c(0.3,0.5),c(y,y),col="grey")
    }
}
for(i in seq(1.2,9.8,0.2)){
    num = i
    y2 = log10(num*exab[1])
    lines(c(0.5,0.7),c(y2,y2),col="grey")
}
nums = c(1:9,(1:9)*10,100)
for(num in nums){
    y = log10(num)
    lines(c(0.2,0.5),c(y,y))
    text(0.1,y,num)
}
for(num in 1:10){
    y2 = log10(num*exab[1])
    lines(c(0.5,0.8),c(y2,y2))
    text(0.9,y2,num)
}

polygon(c(0,0.5,0.5,0),c(0-bmp,0-bmp,2+bmp,2+bmp))
polygon(c(1,0.5,0.5,1),c(0-bmp,0-bmp,1+bmp,1+bmp)+log10(exab[1]))

lines(c(0.15,0.85),rep(log10(prod(exab)),2),col="red")
lines(c(0.4,0.6),rep(log10(exab[1]),2),col="blue")

```
\

Below is another slide rule. Based on the second slide's position, and the red cursor's position, the slide rule indicates another product of two factors.

```{r,echo=F,fig.dim=c(3,10)}
par(mar=c(0,0,0,0))
bmp = 0.1
plot(0,0,"n",xlim=c(0,1),ylim=c(0-bmp,2+bmp),axes=F,ann=F)
for(i in seq(1.2,9.8,0.2)){
    for(j in 0:1){
        num = i*10^j
        y = log10(num)
        lines(c(0.3,0.5),c(y,y),col="grey")
    }
}
for(i in seq(1.2,9.8,0.2)){
    num = i
    y2 = log10(num*a)
    lines(c(0.5,0.7),c(y2,y2),col="grey")
}
nums = c(1:9,(1:9)*10,100)
for(num in nums){
    y = log10(num)
    lines(c(0.2,0.5),c(y,y))
    text(0.1,y,num)
}
for(num in 1:10){
    y2 = log10(num*a)
    lines(c(0.5,0.8),c(y2,y2))
    text(0.9,y2,num)
}

polygon(c(0,0.5,0.5,0),c(0-bmp,0-bmp,2+bmp,2+bmp))
polygon(c(1,0.5,0.5,1),c(0-bmp,0-bmp,1+bmp,1+bmp)+log10(a))

lines(c(0.15,0.85),rep(log10(a*b),2),col="red",lwd=0.7)
lines(c(0.4,0.6),rep(log10(a),2),col="blue")
```
\

The current position of the slide rule (and the red cursor) indicates a specific product. If that product is $a \cdot b = p$, find those three quantities.

* $a =$ ##ANSWER1##
* $b =$ ##ANSWER2##
* $p \approx$ ##ANSWER3##


Answerlist
--------

`r paste0("* ",sprintf("%.01f",achoice),collapse="\n")`
`r paste0("* ",sprintf("%.01f",bchoice),collapse="\n")`
`r paste0("* ",pchoice,collapse="\n")`


Solution
========

$$`r a` \cdot `r b` \approx `r p`$$



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: slide_rule