```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

while(T){
    R = sample(2:9,1)
    frac = list(c(2,3),
                c(3,4),
                c(2,5),c(3,5),c(4,5),
                c(5,6),
                c(2,7),c(3,7),c(4,7),c(5,7),c(6,7),
                c(3,8),c(5,8),c(7,8),
                c(2,9),c(4,9),c(5,9),c(7,9),c(8,9))
    fracn = sample(1:length(frac),1)
    frac = frac[[fracn]]
    if(length(unique(c(frac,R)))==3){break}
}


ans = 2*pi*frac[1]/frac[2]

```

Question
========

A circle with radius $r=`r R`$ centimeters is cut into `r frac[2]` congruent sectors. A length of red string is pulled around the circle, and the string is exactly long enough to span the [arc](https://en.wikipedia.org/wiki/Circular_arc) of `r frac[1]` adjacent sectors, as shown in the diagram below.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
th = seq(0,2*pi,pi/300)
lines(cos(th),sin(th),lwd=2)
for(i in seq(0,2*pi,length.out=frac[2]+1)){
    lines(c(0,cos(i)),c(0,sin(i)))
}
th2 = seq(0,2*pi*frac[1]/frac[2],pi/300)
lines(cos(th2),sin(th2),col="red",lwd=4)
text(0.5,0.05,paste0("r = ",R,collapse=""))
```
\

How long, in centimeters, is the red string? Please answer as a decimal approximation accurate within $\pm 0.01$ centimeters.

Solution
========

Find the [diameter](https://en.wikipedia.org/wiki/Diameter).

$$d=2r$$
$$d=2(`r R`)$$
$$d=`r 2*R`$$

Find the [circumference](https://en.wikipedia.org/wiki/Circumference).

$$C = \pi d$$
$$C = \pi (`r 2*R`)$$
$$C~\approx~`r 2*R*pi`$$






Meta-information
============
extype: num
exsolution: `r ans`
exname: arc_length_from_frac
extol: 0.01