```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
while(T){
    R = sample(3:9,1)
    deg = sample(46:330,1)
    frac = c(deg,360)
    ans = 2*pi*R*frac[1]/frac[2]
    ang = deg/180*pi
    if(deg%%15 != 0){break}
}


```

Question
========

A length of red string is pulled around the circle with radius $r=`r R`$. The red string [subtends](https://en.wikipedia.org/wiki/Subtended_angle) a [central angle](https://en.wikipedia.org/wiki/Central_angle) with a degree measure of `r deg`°, as shown in the diagram below.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
th = seq(0,2*pi,pi/300)
lines(cos(th),sin(th),lwd=2)
th2 = seq(0,2*pi*frac[1]/frac[2],pi/300)
lines(c(cos(ang),0,1),c(sin(ang),0,0))
lines(cos(th2),sin(th2),col="red",lwd=4)
lines(0.05*cos(th2),0.05*sin(th2),col=rgb(0.4,0,0.4))
text(0.15*cos(ang/2),0.15*sin(ang/2),paste0(deg,"°"),adj=c(0.5,0.5),col=rgb(0.4,0,0.4))
text(0.5,0.05,paste0("r = ",R,collapse=""))
```
\

How long, in centimeters, is the red string? Please answer as a decimal approximation accurate within $\pm 0.01$ centimeters.

Solution
========

Find the [diameter](https://en.wikipedia.org/wiki/Diameter).

$$d=2r$$
$$d=2\cdot`r R`$$
$$d=`r 2*R`$$

Find the [circumference](https://en.wikipedia.org/wiki/Circumference).

$$C = \pi d$$
$$C = \pi \cdot `r 2*R`$$
$$C~\approx~`r 2*R*pi`$$

Remember, there are $360^{\circ}$ in a full circle. The [string's length](https://en.wikipedia.org/wiki/Circular_arc) is $\frac{`r frac[1]`}{`r frac[2]`}$ of the circumference.

$$L~=~\frac{`r frac[1]`}{`r frac[2]`}C$$
$$L~=~\frac{`r frac[1]`}{`r frac[2]`}d\pi$$
$$L~=~\frac{`r frac[1]`}{`r frac[2]`}2\pi r$$
$$L~\approx~\frac{`r frac[1]`}{`r frac[2]`}(`r 2*pi*R`)$$
$$L~\approx~`r 2*pi*R*frac[1]/frac[2]`$$




Meta-information
============
extype: num
exsolution: `r ans`
exname: arc_length_from_frac
extol: 0.01