```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

R = round(runif(1,3,4.5),2)
deg = sample(45:260,1)
ang = deg/180*pi
L1 = round(2*pi*deg/360,2)
L2 = round(L1*R,2)
L1 = L2/R

```

Question
========

Two concentric circles have radii $r_1=1$ meters and $r_2=`r R`$ meters. A central angle subtends [similar](https://en.wikipedia.org/wiki/Similarity_(geometry)) arcs on both circles: a blue arc on the smaller circle and a red arc on the larger circle. The red arc length is `r L2` meters, as shown in the diagram below.


```{r,echo=F,fig.dim=c(7,7)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
th = seq(0,2*pi,pi/300)
lines(cos(th),sin(th),lwd=2,col="grey")
lines(R*cos(th),R*sin(th),lwd=2,col="grey")
lines(c(0,R),c(0,0))
lines(c(0,R*cos(ang)),c(0,R*sin(ang)))
points(0,0,pch=20)
th2 = seq(0,ang,pi/300)
lines(R*cos(th2),R*sin(th2),col="red",lwd=2)
text((R+0.2)*cos(ang/2),(R+0.2)*sin(ang/2),paste0(L2," m"),col="red",srt=(-pi/2+ang/2)/pi*180)
lines(cos(th2),sin(th2),col="blue",lwd=2)
text(1.2*cos(ang/2),1.2*sin(ang/2),paste0("? m"),col="blue",srt=(-pi/2+ang/2)/pi*180)
# text(0.5,0.05,TeX("$r_1=1$"),adj=c(0.5,0))
# text(R/2,-0.05,TeX(paste0("$r_2=$",R)),adj=c(0.5,1))

# lines(c(0,0),c(0,-1.5),lty=2,col="lightgrey")
# lines(c(1,1),c(0,-1.5),lty=2,col="lightgrey")

lines(c(0,0),c(0,-2.3),lty=2,col="lightgrey")
lines(c(1,1),c(0,-1.3),lty=2,col="lightgrey")
lines(c(R,R),c(0,-2.3),lty=2,col="lightgrey")

lines(c(0,0,0,1,1,1),c(-1.5,-1.3,-1.4,-1.4,-1.3,-1.5))
text(0.5,-1.3,TeX("$r_1=1\\, m$"),adj=c(0.5,0))

lines(c(0,0,0,R,R,R),-0.8+c(-1.5,-1.3,-1.4,-1.4,-1.3,-1.5))
text(R/2,-2.1,TeX(paste0("$r_2=$",R,"\\, m")),adj=c(0.5,0))

```
\

What is the length, in meters, of the blue arc? *The tolerance is set to $\pm0.01$ meters.*

Solution
========

Okay, this might seem absurdly easy if you are comfortable with [similarity](https://en.wikipedia.org/wiki/Similarity_(geometry)).

$$\frac{1}{?} ~=~ \frac{`r R`}{`r L2`}$$

$$?~=~ \frac{`r L2`}{`r R`} ~=~ `r L1`$$

I am trying to introduce the **[radian](https://en.wikipedia.org/wiki/Radian)**, which is the arc length of a unit circle. 

* Massachusetts learning objective F-TF.A.1:
    * Understand radian measure of an angle as the length of the arc on the unit circle subtended by the angle.
    

If you look up [circular arc](https://en.wikipedia.org/wiki/Circular_arc#Length) on wikipedia, you'll see a formula relating the arc length ($L$) to radius ($r$) and the central angle **measured in radians** ($\theta$).
$$L~=~r\theta$$

So, in our case:

$$`r L2`~=~(`r R`)(\theta)$$

$$\theta~=~\frac{`r L2`}{`r R`}~=~ `r L1`$$



Meta-information
============
extype: num
exsolution: `r L1`
exname: radians_from_r_L
extol: 0.01