---
output: pdf_document
params:
    rseed: 0
    showsol: false
---

Name: \vspace{5pt} \hrule

## at1118paper: Complete the Square (v`r params$rseed`)


```{r,echo=F}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}
gcd2 <- function(a, b) {
    if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

```

```{r,echo=F}
n = 8
xy = sort(sample(8:30,2))
x = xy[1]
y = -xy[2]
area = x^2+2*x*y

x1 = sqrt(area+y^2)-y
x2 = -sqrt(area+y^2)-y

x1s = c(x1)
x2s = c(x2)
ys = c(y)
areas = c(area)

for(i in 1:(n-1)){
    while(T){
        xy = sample(3:30,2)
        x = xy[1]*sample(c(-1,1),1)
        y = xy[2]*sample(c(-1,1),1)
        area = x^2+2*x*y
        x1 = sqrt(area+y^2)-y
        x2 = -sqrt(area+y^2)-y
        if(!(area %in% areas) && !(y %in% ys)){
            x1s = c(x1s,x1)
            x2s = c(x2s,x2)
            ys = c(ys,y)
            areas = c(areas,area)
            break
        }
    }
}
i=0
```



## Example

```{r,echo=F}
i = i+1
x1 = x1s[i]
x2 = x2s[i]
y = ys[i]
area = areas[i]
```

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$


```{r,echo=F,results='asis'}
if(T){# if(params$showsol){
    cat("\\color{red}\n\n")
    cat(paste0("Add ${\\left(\\frac{",2*y,"}{2}\\right)}^{2}$, which equals $",y^2,"$, to both sides of the equation."))
    cat("$$",pn(c(1,2*y,y^2),2:0),"~=~",area+y^2,"$$\n")
    cat("Factor the left side.\n")
    cat("$$(",pn(c(1,y),1:0),")^2~=~",area+y^2,"$$\n")
    cat("Undo the squaring. We need to consider both $\\pm\\sqrt{",area+y^2,"}$.\n")
    cat("\\begin{align*}")
    cat(paste0(pn(c(1,y),1:0),"&=",-sqrt(area+y^2),"&\\text{or}&&",pn(c(1,y),1:0),"&=",sqrt(area+y^2),"\\\\ \n"))
    cat(paste0("x&=",-sqrt(area+y^2)-y,"&\\text{or}&&x&=",sqrt(area+y^2)-y,"\n"))
    cat("\\end{align*}")
    cat("\\color{black}")
}
```

## Question `r i`

```{r,echo=F}
i = i+1
x1 = x1s[i]
x2 = x2s[i]
y = ys[i]
area = areas[i]
```

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$


\vfill

```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$",pn(c(1,2*y,y^2),2:0),"~=~",area+y^2,"$$\n")
    cat("$$(",pn(c(1,y),1:0),")^2~=~",area+y^2,"$$\n")
    cat("$$",pn(c(1,y),1:0),"~=~\\pm",sqrt(area+y^2),"$$\n")
    cat("$$x=",x2,"~~~~~~~~\\text{or}~~~~~~~~ x=",x1,"$$\n\n")
    cat("\\color{black}")
}
```

\vfill

## Question `r i`

```{r,echo=F}
i = i+1
x1 = x1s[i]
x2 = x2s[i]
y = ys[i]
area = areas[i]
```

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$


\vfill

```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$",pn(c(1,2*y,y^2),2:0),"~=~",area+y^2,"$$\n")
    cat("$$(",pn(c(1,y),1:0),")^2~=~",area+y^2,"$$\n")
    cat("$$",pn(c(1,y),1:0),"~=~\\pm",sqrt(area+y^2),"$$\n")
    cat("$$x=",x2,"~~~~~~~~\\text{or}~~~~~~~~ x=",x1,"$$\n\n")
    cat("\\color{black}")
}
```

\vfill


\newpage

## Question `r i`

```{r,echo=F}
i = i+1
x1 = x1s[i]
x2 = x2s[i]
y = ys[i]
area = areas[i]
```

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$


\vfill

```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$",pn(c(1,2*y,y^2),2:0),"~=~",area+y^2,"$$\n")
    cat("$$(",pn(c(1,y),1:0),")^2~=~",area+y^2,"$$\n")
    cat("$$",pn(c(1,y),1:0),"~=~\\pm",sqrt(area+y^2),"$$\n")
    cat("$$x=",x2,"~~~~~~~~\\text{or}~~~~~~~~ x=",x1,"$$\n\n")
    cat("\\color{black}")
}
```

\vfill

## Question `r i`

```{r,echo=F}
i = i+1
x1 = x1s[i]
x2 = x2s[i]
y = ys[i]
area = areas[i]
```

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$


\vfill

```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$",pn(c(1,2*y,y^2),2:0),"~=~",area+y^2,"$$\n")
    cat("$$(",pn(c(1,y),1:0),")^2~=~",area+y^2,"$$\n")
    cat("$$",pn(c(1,y),1:0),"~=~\\pm",sqrt(area+y^2),"$$\n")
    cat("$$x=",x2,"~~~~~~~~\\text{or}~~~~~~~~ x=",x1,"$$\n\n")
    cat("\\color{black}")
}
```

\vfill

## Question `r i`

```{r,echo=F}
i = i+1
x1 = x1s[i]
x2 = x2s[i]
y = ys[i]
area = areas[i]
```

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$


\vfill

```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$",pn(c(1,2*y,y^2),2:0),"~=~",area+y^2,"$$\n")
    cat("$$(",pn(c(1,y),1:0),")^2~=~",area+y^2,"$$\n")
    cat("$$",pn(c(1,y),1:0),"~=~\\pm",sqrt(area+y^2),"$$\n")
    cat("$$x=",x2,"~~~~~~~~\\text{or}~~~~~~~~ x=",x1,"$$\n\n")
    cat("\\color{black}")
}
```

\vfill


## Question `r i`

```{r,echo=F}
i = i+1
x1 = x1s[i]
x2 = x2s[i]
y = ys[i]
area = areas[i]
```

By [completing the square](https://en.wikipedia.org/wiki/Completing_the_square), find both solutions to the given equation:

$$`r pn(c(1,2*y),2:1)`~=~`r area`$$


\vfill

```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$",pn(c(1,2*y,y^2),2:0),"~=~",area+y^2,"$$\n")
    cat("$$(",pn(c(1,y),1:0),")^2~=~",area+y^2,"$$\n")
    cat("$$",pn(c(1,y),1:0),"~=~\\pm",sqrt(area+y^2),"$$\n")
    cat("$$x=",x2,"~~~~~~~~\\text{or}~~~~~~~~ x=",x1,"$$\n\n")
    cat("\\color{black}")
}
```

\vfill



