```{r,echo=FALSE}
Ti = round(runif(1,10,30),0)
B = round(runif(1,0.11,0.5),2)
if(B==1){
  B = 1.1
}
C = round(B*Ti+runif(1,2,8),0)
dt = 0.1
Tf = Ti+(-B*Ti+C)*dt

Ts = c(Ti)
ts = c(0)

for(i in 1:101){
  TT = Ts[i]
  tt = ts[i]
  TT2 = (-B*TT+C)*dt+TT
  tt2 = ts[i]+dt
  Ts = c(Ts,TT2)
  ts = c(ts,tt2)
}

```


Question
========

Let's learn how to use [Euler's method](https://en.wikipedia.org/wiki/Euler_method) to simulate the changing temperature of a pot of water that is simultaneously cooled by air and warmed by a heater (and well-stirred). The basic idea of Euler's method is that during a short amount of time, we can assume the **average rate of change is approximately equal to the instantaneous rate of change at the beginning** of the time interval.

Let's say that when $t=0$ min, the water temperature is `r Ti`°C.

$$T(0) = `r Ti` $$
The air-cooling rate is [proportional to the difference](https://en.wikipedia.org/wiki/Newton%27s_law_of_cooling) between the temperatures; let's say the proportionality constant for air cooling is `r B` min$^{-1}$. Remember, this proportionality constant depends on many things, like the size of pot and speed of wind. Let's say the heater warms at a steady rate, so if the pot were insulated the temperature would steadily increase at `r C`°C/min. If we plot temperature versus time, the rate of change is the slope (rise over run), so we know how to calculate the slope $\frac{\Delta T}{\Delta t}$ if we know the temperature $T$.

$$\frac{\Delta T}{\Delta t} ~\approx~ -`r B` T+`r C`$$



Let's use a step size of $\Delta t=`r dt`$ min. We typically work in a table (or a spreadsheet). Here are the first few rounds of calculations. Notice it is important to [maintain as many digits](https://en.wikipedia.org/wiki/Euler_method#Rounding_errors) as possible during the steps.

<style>
table.brd td{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
}
table.brd th{
  border: 2px solid black;
  padding: 5px;
  text-align: center;
}
table.brd {
  border: 3px solid black;
}
</style>

<table class="brd">
  <tr>
    <th>$t$</th> 
    <th>$T$</th>
    <th>$\Delta t$</th>
    <th>$\Delta T ~=~ (-`r B`T+`r C`)\cdot\Delta t$
  </tr>
  <tr>
    <td>0</td>
    <td>`r Ti`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ti+C)*dt`</td>
  </tr>
  <tr>
    <td>`r ts[2]`</td>
    <td>`r Ts[2]`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ts[2]+C)*dt`</td>
  </tr>
  <tr>
    <td>`r ts[3]`</td>
    <td>`r Ts[3]`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ts[3]+C)*dt`</td>
  </tr>
  <tr>
    <td>`r ts[4]`</td>
    <td>`r Ts[4]`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ts[4]+C)*dt`</td>
  </tr>
</table>

Notice, in each row, we add $T$ and $\Delta T$ to get the next $T$. In other words, $T(t+\Delta t) ~=~ T(t)+\Delta T$. For example $T(0.1) = `r Ti`+`r Ts[2]-Ts[1]` = `r Ts[2]`$.

* Continue the table, using Euler's method, to estimate $T(10)$, the temperature after 10 minutes. The tolerance is $\pm 0.01$.



Solution
========

Your spreadsheet should look something like this (in formula-view mode). The vertical dots ($\vdots$) indicate rows that you should calculate, but I felt unnecessary to show. You should be able to drag the formulas down.

<style>
table.sol td{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
}
table.sol td.fc{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
  background-color: #aaaaaa;
}
table.sol th{
  border: 2px solid black;
  padding: 5px;
  text-align: center;
  background-color: #aaaaaa;
}
table.sol {
  border: 3px solid black;
}

</style>

<table class="sol">
  <tr>
    <th> </th>
    <th>A</th> 
    <th>B</th>
    <th>C</th>
    <th>D</th>
  </tr>
  <tr>
    <td class="fc">1</td>
    <td> 0 </td>
    <td> `r Ti` </td>
    <td> `r dt` </td>
    <td> = (-`r B` * B1 + `r C`)*C1 </td>
  </tr>
  <tr>
    <td class="fc">2</td>
    <td> =A1+C1 </td>
    <td> =B1+D1 </td>
    <td> =`r dt` </td>
    <td> = (-`r B` * B2 + `r C`)*C2 </td>
  </tr>
  <tr>
    <td class="fc">3</td>
    <td> =A2+C2 </td>
    <td> =B2+D2 </td>
    <td> =`r dt` </td>
    <td> = (-`r B` * B3 + `r C`)*C3 </td>
  </tr>
  <tr>
    <td class="fc">4</td>
    <td> =A3+C3 </td>
    <td> =B3+D3 </td>
    <td> =`r dt` </td>
    <td> = (-`r B` * B4 + `r C`)*C4 </td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td> $\vdots$ </td>
    <td> $\vdots$ </td>
    <td> $\vdots$ </td>
    <td> $\vdots$ </td>
  </tr>
  <tr>
    <td class="fc">101</td>
    <td> =A100+C100 </td>
    <td> =B100+D100 </td>
    <td> =`r dt` </td>
    <td> = (-`r B` * B100 + `r C`)*C100 </td>
  </tr>
</table>

In the cell-value view:

<table class="sol">
  <tr>
    <th> </th>
    <th>A</th> 
    <th>B</th>
    <th>C</th>
    <th>D</th>
  </tr>
  <tr>
    <td class="fc">1</td>
    <td>0</td>
    <td>`r Ti`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ti+C)*dt`</td>
  </tr>
  <tr>
    <td class="fc">2</td>
    <td>`r ts[2]`</td>
    <td>`r Ts[2]`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ts[2]+C)*dt`</td>
  </tr>
  <tr>
    <td class="fc">3</td>
    <td>`r ts[3]`</td>
    <td>`r Ts[3]`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ts[3]+C)*dt`</td>
  </tr>
  <tr>
    <td class="fc">4</td>
    <td>`r ts[4]`</td>
    <td>`r Ts[4]`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ts[4]+C)*dt`</td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td> $\vdots$ </td>
    <td> $\vdots$ </td>
    <td> $\vdots$ </td>
    <td> $\vdots$ </td>
  </tr>
  <tr>
    <td class="fc">101</td>
    <td>`r ts[101]`</td>
    <td>`r Ts[101]`</td>
    <td>`r dt`</td>
    <td>`r (-B*Ts[101]+C)*dt`</td>
  </tr>
</table>


If you plot the temperatures, you should see a curve that seems to approach a horizontal asymptote. As the temperature difference between the water and air increases, eventually the cooling rate perfectly opposes the heating rate, so the temperature holds steady.

```{r,echo=F,fig.dim=c(6,6)}
plot(ts[0:100],Ts[0:100],type="l",xlab="time (min)",ylab="Temp (Celsius)")
```
\

So, $T(10) \approx `r round(Ts[101],2)`$.


Meta-information
============
extype: num
exsolution: `r Ts[101]`
exname: eulers_method_water
extol: 0.01