```{r,echo=FALSE}
options(scipen=99)
r = round(runif(1,0.01,0.024),3) #per year
K = sample(7:20,1) #billion
x0 = round(runif(1,1,3),1) #billion
dt = 2 #sample(c(0.1,0.5,2,3,5,10),1)

t = c(0)
x = c(x0)

for(i in 1:105){
  t = c(t, t[i]+dt)
  x = c(x, x[i]+r*x[i]*(1-x[i]/K)*dt)
}
```


Question
========

The [competitive Lotka–Volterra equation](https://en.wikipedia.org/wiki/Competitive_Lotka%E2%80%93Volterra_equations) is used to simulate population growth.

$$\frac{\Delta x}{\Delta t} = rx\left(1-\frac{x}{K}\right)$$

where $x$ is population count, $t$ is time in years, $r$ is the growth factor, and $K$ is the [carrying capacity](https://en.wikipedia.org/wiki/Carrying_capacity).

For our simulation, use the following values for the initial values and parameters.

* Parameters:
  * $r=`r r`$ $\mathrm{yr^{-1}}$
  * $K=`r K`$ billion
* Initial values:
  * $x(0) = `r x0`$ billion
* Euler's method step size:
  * $\Delta t = `r dt`$ yr

Using Euler's method, we can produce the first few rounds of the simulation.

<style>
table.brd td{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
}
table.brd th{
  border: 2px solid black;
  padding: 5px;
  text-align: center;
}
table.brd {
  border: 3px solid black;
}
</style>

<table class="brd">
  <tr>
    <th>$t$</th>
    <th>$x$</th>
    <th>$\Delta t$</th>
    <th>$\Delta x ~=~ `r r`\cdot x\cdot (1-x/`r K`)\cdot\Delta t$</th>
  </tr>
  <tr>
    <td>0</td>
    <td>`r x[1]`</td>
    <td>`r dt`</td>
    <td>`r x[2]-x[1]`</td>
  </tr>
  <tr>
    <td>`r t[2]`</td>
    <td>`r x[2]`</td>
    <td>`r dt`</td>
    <td>`r x[3]-x[2]`</td>
  </tr>
  <tr>
    <td>`r t[3]`</td>
    <td>`r x[3]`</td>
    <td>`r dt`</td>
    <td>`r x[4]-x[3]`</td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
  </tr>
</table>

* Continue using Euler's method to estimate the population (in billions) after $t=`r dt*100`$ years. In other words, find $x(`r dt*100`)$. Please answer in billions. For example, enter `9` for 9 billion, not $9\cdot 10^9$ and not $`r 9e9`$. The tolerance is $\pm 0.01$ billion.

Solution
========

Use a spreadsheet. If your formulas produce the first 3 rows correctly, they should continue to work to find $x(`r dt*100`)=`r x[101]`$ billion.

```{r,echo=F,fig.dim=c(6,6)}
plot(t,x,type="l")
```
\

Correct answer: `r x[101]`




Meta-information
============
extype: num
exsolution: `r x[101]`
exname: eulers_method_pop_grow
extol: 0.01