```{r,echo=FALSE}
dubtim = round(runif(1,2,8),1)
k = round(log(2)/dubtim,2)
A0 = round(runif(1,4,19),1)
dbtm = log(2)/k
```


Question
========

At $t=0$ a population is $y(0)=`r A0`$ million. The population changes with the following rate equation (assuming $\Delta t$ is very small):
$$\frac{\Delta y}{\Delta t} \approx -`r k` y$$

where $t$ has units of years, $y$ has units of millions, and $k$ has units of years$^{-1}$. The exact solution (using algebraic calculus instead of Euler's method) is an exponential function.

$$y = `r A0`e^{-`r k`t}$$

What is the half life (in years)? (The tolerance is $\pm 0.2$ years.)


Solution
========

You can graph the function (using either Euler's method or the provided function.) Find where the graph reaches twice the initial value.

```{r,echo=F}
t = seq(-1,10,0.01)
y = A0*exp(-k*t)
plot(t,y,type="l",ylim=c(0,ceiling(A0*1.05)),xlim=c(0,10),col="blue")
abline(h=A0/2,col="red")
abline(h=A0,col="red")
text(9,A0*0.55,paste0("y = ",round(A0/2,4),collapse=""),col="red")
text(9,A0*1.05,paste0("y = ",A0,collapse=""),col="red")
abline(h=0)
abline(v=0)
abline(v=dbtm,col="darkgreen")
text(dbtm+0.7,A0*0.2,paste0("x = ",round(dbtm,2)),col="darkgreen")
```
\

The half life is `r dbtm` years.

You could also use algebra to find $\lambda$ so the following equation is true for all $t$.

$$`r A0`e^{-`r k`t} = `r A0`\left(\frac{1}{2}\right)^{t/\lambda} $$

Meta-information
============
extype: num
exsolution: `r dbtm`
exname: half-life_from_eq
extol: 0.2