```{r,echo=FALSE}
b = round(sample(c(seq(-4.5,-2,0.1),seq(2,4.5,0.1)),1),1)
if(b<0){
  sym = "-"
} else {
  sym = ""
}
B = exp(1/b)
```


Question
========

For [exponential functions](https://en.wikipedia.org/wiki/Exponential_function), a horizontal stretch is equivalent to a change of base. Consider the two functions below, where $g$ is equivalent to stretching $f$ horizontally by a factor $`r b`$:

```{r,echo=FALSE,fig.dim=c(6,6)}
par(pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(0,20),xlab="x",ylab="y")
for(i in -15:22){
  if(i%%5==0){
    abline(h=i,lty=2)
    abline(v=i,lty=2)
  } else {
    abline(h=i,lty=3)
    abline(v=i,lty=3)
  }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-11,11,0.01)
y = exp(x)
lines(x,y,col="blue",lwd=4)
x = seq(-11,11,0.01)
y = exp(x/b)
lines(x,y,col="red",lwd=4)
legend(-10,20,c("y = f(x)","y = g(x)"),lwd=2,col = c("blue","red"))
```
\

$$\begin{align}
f(x) &= e^{x}\\\\
g(x) &= e^{`r sym`x/`r abs(b)`}
\end{align}$$

Instead of using the horizontal stretch transformation, we could have changed the base.

$$g(x) = B^{x}$$

where $B$ represents the new base.

* Find $B$. The tolerance is $\pm 0.01$.



Solution
========

It can be shown that $B = `r B`$. For all $x$:

$$e^{`r sym`x/`r abs(b)`} = B^x $$

Division is multiplication by a reciprocal and $a^{bc}\equiv \left(a^{b}\right)^c$.

$$\left(e^{`r sym`1/`r abs(b)`}\right)^x = B^x $$

Since the equation must hold for all values of $x$,

$$e^{`r sym`1/`r abs(b)`} = B $$

Evaluate.

$$B = `r B`$$



Meta-information
============
extype: num
exsolution: `r B`
exname: exp_base_and_stretch_eq
extol: 0.01