---
header-includes:
   - \usepackage{array}
   - \usepackage{color}
   - \usepackage{tabularx}
output: pdf_document
params:
    rseed: 1
    showsol: false
    titex: "Practice"
urlcolor: blue
---

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## \sc u15ws1: Draw Cosine and Sine Wave Functions

A unit circle diagram shows the $xy$ coordinates of special angles. For point $(x,y)$ at angle $\theta$, we define the trigonometric functions so that $\sin(\theta)=x$ and $\cos(\theta)=y$.

```{r,echo=F,fig.dim=c(5,5),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
th = seq(0,2*pi,pi/360)
arrows(-1.05,0,1.05,0,0.05,15,3)
arrows(0,-1.05,0,1.05,0.05,15,3)
polygon(c(0.2,0.2,0.8,0.8),c(-0.1,0.1,0.1,-0.1),border="white",col="white")
polygon(c(-0.3,-0.3,-0.7,-0.7),c(-0.1,0.1,0.1,-0.1),border="white",col="white")
polygon(c(-0.1,0.1,0.1,-0.1),c(0.3,0.3,0.7,0.7),border="white",col="white")
polygon(c(-0.1,0.1,0.1,-0.1),c(-0.3,-0.3,-0.7,-0.7),border="white",col="white")

lines(cos(th),sin(th),col="black",lty=1)
nums_dot = c(1,5,7,11,13,17,19,23)
nums_30 = c(2,4,8,10,14,16,20,22)
nums_45 = c(3,9,15,21)
nums_90 = c(6,12,18,24)

lty = rep(c(1,1,1,1,1,1),4)
col = rep(c("black","grey","maroon","blue","maroon","grey"),4)
pac = c("$(1,0)$",
        "",
        "$\\left(\\frac{\\sqrt{3}}{2},\\frac{1}{2}\\right)$",
        "$\\left(\\frac{\\sqrt{2}}{2},\\frac{\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{1}{2},\\frac{\\sqrt{3}}{2}\\right)$",
        "",
        "$(0,1)$",
        "",
        "$\\left(\\frac{-1}{2},\\frac{\\sqrt{3}}{2}\\right)$",
        "$\\left(\\frac{-\\sqrt{2}}{2},\\frac{\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{-\\sqrt{3}}{2},\\frac{1}{2}\\right)$",
        "",
        "$(-1,0)$",
        "",
        "$\\left(\\frac{-\\sqrt{3}}{2},\\frac{-1}{2}\\right)$",
        "$\\left(\\frac{-\\sqrt{2}}{2},\\frac{-\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{-1}{2},\\frac{-\\sqrt{3}}{2}\\right)$",
        "",
        "$(0,-1)$",
        "",
        "$\\left(\\frac{1}{2},\\frac{-\\sqrt{3}}{2}\\right)$",
        "$\\left(\\frac{\\sqrt{2}}{2},\\frac{-\\sqrt{2}}{2}\\right)$",
        "$\\left(\\frac{\\sqrt{3}}{2},\\frac{-1}{2}\\right)$",
        "")

angs = c("0 or $2\\pi$",
         "","$\\pi/6$","$\\pi/4$","$\\pi/3$","","$\\pi/2$",
         "","$2\\pi/3$","$3\\pi/4$","$5\\pi/6$","","$\\pi$",
         "","$7\\pi/6$","$5\\pi/4$","$4\\pi/3$","","$3\\pi/2$",
         "","$5\\pi/3$","$7\\pi/4$","$11\\pi/6$",""
         )

for(i in 1:24){
    t = (i-1)*pi/12
    lines(c(0,cos(t)),c(0,sin(t)),lty=lty[i],col=col[i])
    text(1.2*cos(t),1.2*sin(t),TeX(pac[i]),col=col[i],cex=0.7)
    if(pac[i]!=""){
        points(cos(t),sin(t),pch=19,col=col[i])
    }
    if(angs[i]!=""){
        lines(c(0.45,0.75)*cos(t),c(0.45,0.75)*sin(t),col="white",lwd=3)
    }
    text(0.6*cos(t),0.6*sin(t),TeX(angs[i]),col=col[i],srt=(t/pi*180+90)%%180-90,cex=1)
}
```

In order to graph the sinusoidal wave functions, it will help to use the following decimal approximations: $\frac{\sqrt{2}}{2}\approx `r round(sqrt(2)/2,2)`$ and $\frac{\sqrt{3}}{2}\approx `r round(sqrt(3)/2,2)`$.

Please make a table relating the angles to the **decimal** values.

\setlength{\extrarowheight}{9pt}
\begin{tabularx}{\textwidth}{| X || X | X | X | X | X | X | X | X | X |}\hline
$\theta$ & 0 & $\pi/6$ & $\pi/4$ & $\pi/3$ & $\pi/2$ & $2\pi/3$ & $3\pi/4$ & $5\pi/6$ & $\pi$ \\ \hline
$\cos(\theta)$ & $\phantom{\huge\frac{4}{3}}$ &&&&&&&& \\ \hline
$\sin(\theta)$ & $\phantom{\huge\frac{4}{3}}$ &&&&&&&& \\ \hline
\end{tabularx}

\begin{tabularx}{\textwidth}{| X || X | X | X | X | X | X | X | X | X |}\hline
$\theta$ & $\pi$ & $7\pi/6$ & $5\pi/4$ & $4\pi/3$ & $3\pi/2$ & $5\pi/3$ & $7\pi/4$ & $11\pi/6$ & $2\pi$ \\ \hline
$\cos(\theta)$ & $\phantom{\huge\frac{4}{3}}$ &&&&&&&& \\ \hline
$\sin(\theta)$ & $\phantom{\huge\frac{4}{3}}$ &&&&&&&& \\ \hline
\end{tabularx}

\newpage


## \sc{u15ws1}

On a $tz$ plane, plot $z=\cos(t)$. You should use the first and second rows, and all 17 columns, from the first page. Be as accurate as possible. Connect the points with a smooth curve.

\vspace{-20pt}

```{r,echo=F,fig.dim=c(7.5,4)}
par(mar=c(2,2,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-(7-2*pi)/2,2*pi+(7-2*pi)/2),ylim=c(-1,1),asp=1,xlab="t",ylab="y=cos(t)")
mtext("t",1,1.2)
mtext("z = cos(t)",2,1.2)
axis(2,pos=-0.3,at=c(-1,0,1))
axis(1,pos=-1.3,at=c(0,pi/2,pi,3*pi/2,2*pi),labels = c("0",TeX("$\\frac{\\pi}{2}$"),TeX("$\\pi$"),TeX("$\\frac{3\\pi}{2}$"),TeX("$2\\pi$")),padj = 0.5)
for(i in seq(-1,1,0.1)){
    lines(c(0,2*pi),c(i,i),col="grey",lwd=0.8)
}
for(i in seq(-1,1,0.5)){
    lines(c(0,2*pi),c(i,i),col="darkgrey",lwd=1)
}
for(i in seq(-1,1,1)){
    lines(c(0,2*pi),c(i,i),col="black",lwd=1)
}

cols = rep(c("black","grey","maroon","blue","maroon","grey"),9)
ltys = rep(c(1,1,1,1,1,1),9)
for(i in 0:24){
    th = i*pi/12
    col = cols[i+1]
    lty = ltys[i+1]
    lines(c(th,th),c(-1,1),col=col,lty=lty)
}

arrows(0,0,6.5,0,0.1,15,2,lwd=2)
arrows(0,-1.1,0,1.1,0.1,15,3,lwd=2)

```

\vfill
\vfill

On a $tz$ plane, plot $z=\sin(t)$. You should use the first and third rows, and all 17 columns, from the first page. Be as accurate as possible. Connect the points with a smooth curve.

\vspace{-20pt}

```{r,echo=F,fig.dim=c(7.5,4)}
par(mar=c(2,2,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-(7-2*pi)/2,2*pi+(7-2*pi)/2),ylim=c(-1,1),asp=1,xlab="t",ylab="y=sin(t)")
mtext("t",1,1.2)
mtext("z = sin(t)",2,1.2)
axis(2,pos=-0.3,at=c(-1,0,1))
axis(1,pos=-1.3,at=c(0,pi/2,pi,3*pi/2,2*pi),labels = c("0",TeX("$\\frac{\\pi}{2}$"),TeX("$\\pi$"),TeX("$\\frac{3\\pi}{2}$"),TeX("$2\\pi$")),padj = 0.5)
for(i in seq(-1,1,0.1)){
    lines(c(0,2*pi),c(i,i),col="grey",lwd=0.8)
}
for(i in seq(-1,1,0.5)){
    lines(c(0,2*pi),c(i,i),col="darkgrey",lwd=1)
}
for(i in seq(-1,1,1)){
    lines(c(0,2*pi),c(i,i),col="black",lwd=1)
}

cols = rep(c("black","grey","maroon","blue","maroon","grey"),9)
ltys = rep(c(1,1,1,1,1,1),9)
for(i in 0:24){
    th = i*pi/12
    col = cols[i+1]
    lty = ltys[i+1]
    lines(c(th,th),c(-1,1),col=col,lty=lty)
}

arrows(0,0,6.5,0,0.1,15,2,lwd=2)
arrows(0,-1.1,0,1.1,0.1,15,3,lwd=2)

```


\vfill




