```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
foods = c("apple","banana","cherry","durian")
foods2 = c("apples","bananas","cherries","durian")
pricemu = c(1.5,0.9,6,8)
stores = c("Lovely Lunches","More Munchies",
              "Niche Necessities","Overpriced Options",
              "Price Pincher")
people = c("Quintin","Rachel","Sebastian")

nf = length(foods)
ns = length(stores)
np = length(people)
while(T){
  mults = runif(length(foods)*length(stores),0.75,1.25)
  prices = round(rep(pricemu,length(stores))*mults,2)
  amounts = numeric()
  for(i in 1:length(people)){
    amounts = c(amounts,sample(c(1,1,2,2,3,4,5),length(foods)))
  }
  P = matrix(prices,nrow=length(stores),byrow=T)
  Q = matrix(amounts,ncol=length(people))
  
  C = P%*%Q
  if(max(C)<100 && length(unique(c(C)))==length(C) && length(unique(c(P)))==length(P)){break}
}


smm = function(M){
  dastras = character()
  for(i in 1:dim(M)[1]){
    dastras = c(dastras,paste0(M[i,],collapse=","))
  }
  s = paste0("[[",paste0(dastras,collapse="],\n            ["),"]]")
  return(s)
}

smm2 = function(M){
  dastras = character()
  for(i in 1:dim(M)[1]){
    dastras = c(dastras,paste0(sprintf("%.2f",M[i,]),collapse=","))
  }
  s = paste0("[[",paste0(dastras,collapse="],\n            ["),"]]")
  return(s)
}
unki = sample(1:length(foods),1)
unkj = sample(1:length(stores),1)

# solq = Q[1:length(foods),unki]
solp = P[unkj,1:length(foods)]

eqp = paste(solp)
eqp[unki] = "x"

x = P[unkj,unki]

eqq1 = paste(Q[1:length(foods),1])
eqq2 = paste(Q[1:length(foods),2])
eqq3 = paste(Q[1:length(foods),3])

nr = length(people)+length(foods)
nc = length(stores)+length(foods)

```

Question
========

Three people are buying fruit, and there are five grocery stores. Each person has a shopping list dictating how many pounds of each fruit to buy. Each store has different unit costs of fruit.

In order to consider the **total** cost for each person at each store, we can use [matrix multiplication](https://en.wikipedia.org/wiki/Matrix_multiplication). In order to help visualize matrix multiplication, the shopping lists are shown as a matrix on the bottom-left, the unit prices as a matrix on top-right, and the resulting (unfilled) matrix of totals in the bottom-right.

A peculiarity of matrix multiplication requires the **columns** of the first matrix to "match" the **rows** of the second matrix. In this case, notice the various fruits correspond to columns in the first matrix (bottom-left) and rows in the second matrix (top-right). This visualization is an attempt to make this seem more natural.

```{r,echo=F,fig.dim=c(6.5,6.5/(nc+1.6)*(nr+3))}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.6,nc+1),ylim=c(0,nr+3),asp=1)

for(i in 1:length(people)){
    text(0.5,length(people)-i+1,people[i],adj=1.1)
}
for(i in 1:length(stores)){
    text(nc-length(stores)+i,nr+0.5,stores[i],srt=-90,adj=1.1)
}



clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
for(i in 1:length(foods)){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),col=clrs[i],border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
    text((xt1+xt2)/2,(yt1+yt2)/2,foods[i],srt=srt,cex=0.8)
}

for(i in 1:length(people)){
    for(j in 1:length(foods)){
        text(j,length(people)-i+1,Q[j,i])
    }
}

for(i in 1:length(foods)){
    for(j in 1:length(stores)){
        if(i != unki || j!= unkj){
            text(j+length(foods),length(people)+length(foods)-i+1,sprintf("%.02f",P[j,i]))
        } else {
            text(j+length(foods),length(people)+length(foods)-i+1,"?")
        }
    }
}

text(nf/2+0.5,0,"Shopping lists (pounds)")
text(nf+ns+1,np+nf/2+0.5,"Unit costs ($/pound)",srt=-90)
text(nf+ns/2+0.5,0,"Total costs ($)")

for(i in 1:length(people)){
    for(j in 1:length(stores)){
        text(nf+j,np+1-i,sprintf("%.02f",C[j,i]))
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(np+1.5,np+1.5),c(nf,1)-0.5,lwd=3)
lines(c(np+1.5,np+ns+1.5),c(nf,nf)-0.5,lwd=3)


```
\

What is the unit cost of `r foods2[unki]`, in dollars per pound, at `r stores[unkj]`?


Solution
========

You can use any person's shopping trip at `r stores[unkj]`. Use $x$ to represent the unknown unit cost.

* If you use `r people[1]`, solve the following equation:

$$`r paste0("(",eqq1,"\\cdot ",eqp,")",collapse="+")`=`r C[unkj,1]`$$

* If you use `r people[2]`, solve the following equation:

$$`r paste0("(",eqq2,"\\cdot ",eqp,")",collapse="+")`=`r C[unkj,2]`$$

* If you use `r people[3]`, solve the following equation:

$$`r paste0("(",eqq3,"\\cdot ",eqp,")",collapse="+")`=`r C[unkj,3]`$$

Any equation solves to give $x=`r x`$. Thus, the unit price of `r foods2[unki]` at `r stores[unkj]` is \$`r sprintf("%.02f",x)` per pound.


Meta-information
============
extype: num
exsolution: `r x`
exname: groceries_get_uc
extol: 0.005