```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

nf = 4
ns = 5
np = 3

while(T){
    P = matrix(sample(0:6,nf*ns,T),ncol=nf)
    Q = matrix(sample(0:6,nf*np,T),nrow=nf)
    C = P%*%Q
    unki = sample(1:np,1)
    unkj = sample(1:ns,1)
    
    solq = Q[1:nf,unki]
    solp = P[unkj,1:nf]
    
    nr = np+nf
    nc = ns+nf
    if(min(C)>0 && max(C)<100 && length(unique(solq))>2 && length(unique(solp))>2){break}
}


smm = function(M){
  dastras = character()
  for(i in 1:dim(M)[1]){
    dastras = c(dastras,paste0(M[i,],collapse=","))
  }
  s = paste0("[[",paste0(dastras,collapse="],\n            ["),"]]")
  return(s)
}

smm2 = function(M){
  dastras = character()
  for(i in 1:dim(M)[1]){
    dastras = c(dastras,paste0(sprintf("%.2f",M[i,]),collapse=","))
  }
  s = paste0("[[",paste0(dastras,collapse="],\n            ["),"]]")
  return(s)
}

A = t(Q)
B = t(P)
```

Question
========

Let matrices $A$ and $B$ be defined below.

$$A = `r matpr(A)`$$
$$B = `r matpr(B)`$$

A third matrix, $C$, is equal to the [product](https://en.wikipedia.org/wiki/Matrix_multiplication) $AB$. A student set up a diagram to help find the product; they are missing a single element in $C$, element $c_{`r unki`,`r unkj`}$.

```{r,echo=F,fig.dim=c(4.5,4.5/(nc+1)*(nr+1))}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(0,nr+1),asp=1)

clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
for(i in 1:nf){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),col=clrs[i],border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
}

for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,Q[j,i])
    }
}

for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,sprintf("%d",P[j,i]))
    }
}

for(i in 1:np){
    for(j in 1:ns){
        if(i != unki || j!= unkj){
            text(nf+j,np+1-i,sprintf("%d",C[j,i]))
        } else {
            text(nf+j,np+1-i,"?")
        }
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(np+1.5,np+1.5),c(nf,1)-0.5,lwd=3)
lines(c(np+1.5,np+ns+1.5),c(nf,nf)-0.5,lwd=3)


```
\

What is $c_{`r unki`,`r unkj`}$?


Solution
========

To find $c_{`r unki`,`r unkj`}$, you use row `r unki` from matrix $A$ and column `r unkj` from matrix $B$. 

```{r,echo=F,fig.dim=c(4.5,4.5/(nc+1)*(nr+1))}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(0,nr+1),asp=1)

clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
clrs3 = c(rgb(1,0,0,0.1),rgb(1,1,0,0.2),rgb(0.8,0,0.8,0.15),rgb(0.6,0.5,0.2,0.1))
for(i in 1:nf){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),col=clrs3[i],border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
    # text((xt1+xt2)/2,(yt1+yt2)/2,foods[i],srt=srt,cex=0.8)
}

for(jj in 1:nf){
    polygon(c(jj-0.5,jj+0.5,jj+0.5,jj-0.5),np+1-c(unki-0.5,unki-0.5,unki+0.5,unki+0.5),col=clrs[jj],border=F)
    polygon(nf+c(unkj-0.5,unkj-0.5,unkj+0.5,unkj+0.5),np+nf+1-c(jj-0.5,jj+0.5,jj+0.5,jj-0.5),col=clrs[jj],border=F)
}

for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,Q[j,i])
    }
}

for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,sprintf("%d",P[j,i]))
    }
}

# text(nf/2+0.5,0,"Shopping lists (pounds)")
# text(nf+ns+1,np+nf/2+0.5,"Unit costs ($/pound)",srt=-90)
# text(nf+ns/2+0.5,0,"Total costs ($)")

for(i in 1:np){
    for(j in 1:ns){
        if(i != unki || j!= unkj){
            text(nf+j,np+1-i,sprintf("%d",C[j,i]))
        } else {
            text(nf+j,np+1-i,"?")
        }
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(np+1.5,np+1.5),c(nf,1)-0.5,lwd=3)
lines(c(np+1.5,np+ns+1.5),c(nf,nf)-0.5,lwd=3)
```
\


You multiply corresponding elements and sum those products.

$$c_{`r unki`,`r unkj`}~=~`r paste("(",solq,"\\cdot ",solp,")",collapse="+")`$$

$$c_{`r unki`,`r unkj`}~=~`r paste(solq*solp,collapse="+")`$$

$$c_{`r unki`,`r unkj`}~=~`r sum(solq*solp)`$$

Thus,

$$`r matpr(t(Q))` \cdot `r matpr(t(P))` ~=~ `r matpr(t(C))`$$


Meta-information
============
extype: num
exsolution: `r round(sum(solq*solp))`
exname: mult_mats_diagram
extol: 0.001