```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

cord = sample(1:2,1) # C or D
let = c("c","d")[cord]
LET = c("C","D")[cord]

while(T){
    A = matrix(sample(1:9),ncol=3)
    B = matrix(sample(1:9),nrow=3)
    C = A %*% B
    D = B %*% A
    unkij = sample(1:3,2)
    unki = unkij[1]
    unkj = unkij[2]
    cans = C[unki,unkj]
    dans = D[unki,unkj]
    if(length(unique(c(C)))==9 && length(unique(c(D)))==9 && cans!=dans){break}
}

pans = c(cans,dans)
ans = pans[cord]
unk = paste0(let,"_{",unki,",",unkj,"}",collapse="")
op1 = c("A","B")[cord]
op2 = c("B","A")[cord]

if(cord==1){
    mat1 = A
    mat2 = B
} else {
    mat1 = B
    mat2 = A
}


```

Question
========

Let matrices $A$ and $B$ be defined below.

$$A = `r matpr(A)`$$
$$B = `r matpr(B)`$$

Also, let $C=AB$ and $D=BA$.

* Find element $`r unk`$


Solution
========

I'd recommend setting up a diagram on (*gasp*) paper.

When calculating matrix $`r LET`$ with the matrix multiplication $`r LET`=`r op1`\cdot `r op2`$, the fact that matrix $`r op1`$ is before matrix $`r op2`$ matters (because matrix multiplication is **NOT** [commutative](https://en.wikipedia.org/wiki/Commutative_property)). So, in our diagram, matrix $`r op1`$ is in bottom-left position and matrix $`r op2`$ is in top-right position.

```{r,echo=F}
nc = 6
nr = 6
nf = 3
np = 3
ns = 3
```


```{r,echo=F,fig.dim=c(4.5,4.5/(nc+1)*(nr+1))}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(0,nr+1),asp=1)

clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
clrs3 = c(rgb(1,0,0,0.1),rgb(1,1,0,0.2),rgb(0.8,0,0.8,0.15),rgb(0.6,0.5,0.2,0.1))
for(i in 1:nf){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),col=clrs3[i],border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
    # text((xt1+xt2)/2,(yt1+yt2)/2,foods[i],srt=srt,cex=0.8)
}

for(jj in 1:nf){
    polygon(c(jj-0.5,jj+0.5,jj+0.5,jj-0.5),np+1-c(unki-0.5,unki-0.5,unki+0.5,unki+0.5),col=clrs[jj],border=F)
    polygon(nf+c(unkj-0.5,unkj-0.5,unkj+0.5,unkj+0.5),np+nf+1-c(jj-0.5,jj+0.5,jj+0.5,jj-0.5),col=clrs[jj],border=F)
}

polygon(c(-0.5,0.5,0.5,-0.5)+3+unkj,c(-0.5,-0.5,0.5,0.5)+4-unki,col=rgb(0,0,0,0.1))

for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,mat1[i,j])
    }
}

for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,sprintf("%d",mat2[i,j]))
    }
}


for(i in 1:np){
    for(j in 1:ns){
        if(i != unki || j!= unkj){
            text(nf+j,np+1-i,TeX(paste0("$",let,"_{",i,",",j,"}$")))
        } else {
            # text(nf+j,np+1-i,"?")
            text(nf+j,np+1-i,TeX(paste0("$",let,"_{",i,",",j,"}$")))
        }
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(nf+0.5,nf+0.5),c(nf,0)+0.5,lwd=3)
lines(c(nf+0.5,nf+ns+0.5),c(np,np)+0.5,lwd=3)

text(0,2,op1)
text(5,7,op2)

```
\

Notice we use row `r unki` from $`r op1`$ and column `r unkj` from $`r op2`$.

$$`r unk`~~=~~`r paste0(mat1[unki,1:3],"\\cdot ",mat2[1:3,unkj],collapse="~+~")`$$
$$`r unk`~~=~~`r ans`$$


Meta-information
============
extype: num
exsolution: `r ans`
exname: mult_mats_no_dgrm