```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
foods = c("apple","banana","cherry","durian",
          "eggplant","fig","grapefruit","honeydew")
pricemu = c(1.5,0.9,6,8,4,4,3,6)
groceries = c("Lovely Lunches","More Munchies",
              "Nick's Necessities","Overpriced Options",
              "Price Pincher")
people = c("Quintin","Rachel","Sebastian","Trevor","Ursula","Venus")
while(T){
  mults = runif(length(foods)*length(groceries),0.75,1.25)
  prices = round(rep(pricemu,length(groceries))*mults,2)
  amounts = numeric()
  for(i in 1:length(people)){
    amounts = c(amounts,sample(c(0,0,0,0,1,1,1,2,2,2,3,4),length(foods)))
  }
  P = matrix(prices,nrow=length(groceries),byrow=T)
  Q = matrix(amounts,ncol=length(people))
  
  C = P%*%Q
  if(max(C)<100){break}
}


smm = function(M){
  dastras = character()
  for(i in 1:dim(M)[1]){
    dastras = c(dastras,paste0(M[i,],collapse=","))
  }
  s = paste0("[[",paste0(dastras,collapse="],\n            ["),"]]")
  return(s)
}

smm2 = function(M){
  dastras = character()
  for(i in 1:dim(M)[1]){
    dastras = c(dastras,paste0(sprintf("%.2f",M[i,]),collapse=","))
  }
  s = paste0("[[",paste0(dastras,collapse="],\n            ["),"]]")
  return(s)
}

```

Question
========

A few grocery stores' prices (in USD) for some foods are shown.

```{r,echo=F}
dfP = data.frame(P)
rownames(dfP) = groceries
colnames(dfP) = foods
knitr::kable(dfP)
```

Each of the people below plans to go shopping for those foods. Their grocery lists are shown.

```{r,echo=F}
dfQ = data.frame(Q)
rownames(dfQ) = foods
colnames(dfQ) = people
knitr::kable(dfQ)
```

We can create these matrices in [SageMath](https://chadworley.github.io/sage.html) using the following commands:

```
P = matrix(`r smm2(P)`)

Q = matrix(`r smm(Q)`)
```

The product, $A$, of those two matrices can be calculated in SageMath. Notice, in programming languages the `=` symbol is the [assignment operator](https://doc.sagemath.org/html/en/tutorial/tour_assignment.html). This means the expression on the right is evaluated and stored into the variable on the left. 

```
A = P*Q
```

The result can be printed using [`pretty_print` function](https://doc.sagemath.org/html/en/reference/repl/sage/repl/rich_output/pretty_print.html).

```
pretty_print(A)
```

After you run those commands, you should see a matrix filled with all the possible totals spent by various people at various stores. What is the maximum possible cost of a grocery trip?


Solution
========

The maximum cost is `r max(C)` USD. When you run the lines of code, you should get the following matrix:

$$`r matpr(C)`$$
If there are many trailing 0s, you can use the [`n` function](https://doc.sagemath.org/html/en/reference/misc/sage/misc/functional.html#sage.misc.functional.n) to get numerical approximations.

```
P = matrix(`r smm2(P)`)
Q = matrix(`r smm(Q)`)
A = P*Q
B = n(A,digits=4)
pretty_print(B)
```

You can manually identify the maximum cost.

[Getting sagemath to identify the largest element is annoyingly unintuitive.](https://ask.sagemath.org/question/10344/maximum-element-of-a-matrix/)

```
print(max(B.list()))
```


Meta-information
============
extype: num
exsolution: `r max(C)`
exname: groceries
extol: 0.01