```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

while(T){
  n = sample(8:12,1)
  points = matrix(sample(-7:7,n*2,T),2)
  ps = character()
  for(i in 1:n){
    ps = c(ps,paste0(points[1:2,i]))
  }
  theta = round(runif(4,0.1,2*pi-0.1),2)
  R = matrix(c(cos(theta),-sin(theta),sin(theta),cos(theta)),nrow=2,byrow = T)
  if(min(diff(sort(theta)))>0.4 && length(unique(ps))==n){break}
}
whth = sample(1:4,1)
th = theta[whth]
P = points

sol = paste0(1*(1:4==whth),collapse="")

```

Question
========

## Matrix of original points (preimage)

A list of 2D-cartesian points is stored as the preimage matrix. Each column represents one point.

$$P = `r matpr(points)`$$

```
P = matrix(`r matcc(points)`)
```

## Rotation matrix

We want to rotate the points by $\theta=`r th`$ radians counterclockwise. We will do this by [matrix multiplication with the 2D rotation matrix](https://en.wikipedia.org/wiki/Rotation_matrix).

$$R = \begin{bmatrix}\cos(\theta) & -\sin(\theta) \\ \sin(\theta) & \cos(\theta) \end{bmatrix}$$

## Image

We can apply the rotation to the points through matrix multiplication. Remember, matrix multiplication is not commutative. Let $T$ represent a matrix holding the final positions of the image (after the transformation).

$$T = RP$$

After you calculate $T$, you can plot the points in $T$ with the following code (in SageMath):

```
point(T.transpose(),xmin=-10,xmax=10,ymin=-10,ymax=10,size=50)
```

Which is the graph of the points in $T$? (Please excuse minor stylistic differences due to my graphs being made in R, not SageMath.)

```{r,echo=F,fig.dim=c(8,8)}
par(mfrow=c(2,2),pty="s")
for(i in 1:4){
  tht = theta[i]
  R = matrix(c(cos(tht),-sin(tht),sin(tht),cos(tht)),2,byrow = T)
  tm = R%*%P
  plot(0,0,type="n",axes=T,ann=T,main=c("A","B","C","D")[i],
       xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="y")
  abline(h=0)
  abline(v=0)
  points(tm[1,],tm[2,],pch=20,cex=2,col="blue")
}

```
\


Answerlist
--------

* A
* B
* C
* D


Solution
========


```
P = matrix(`r matcc(points)`)
theta = `r th`
R = matrix([[cos(theta),-sin(theta)],
            [sin(theta),cos(theta)]])
T = R*P
point(T.transpose(),xmin=-10,xmax=10,ymin=-10,ymax=10,size=50)
```



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: rotate_2D