```{r,echo=F,warning=F}
n = 10
while(T){
    rs = sqrt(runif(n,0,1))*9+0.9
    ths = runif(n,0,2*pi)
    x1 = round(rs*cos(ths),3)
    y1 = round(rs*sin(ths),3)
    mind = 10
    for(i in 1:(n-1)){
        for(j in (i+1):n){
            d = sqrt((x1[j]-x1[i])^2+(y1[j]-y1[i])^2)
            mind = min(d,mind)
        }
    }
    if(mind>0.5){break}
}
th = round(runif(1,pi/8,3*pi/8),3)

s = matrix(c(x1,y1),n)
R = matrix(c(cos(th),-sin(th),sin(th),cos(th)),2)

x2 = x1*cos(th)-y1*sin(th)
y2 = x1*sin(th)+y1*cos(th)

f = matrix(c(x2,y2),n)
f2 = s%*%R

wunk = sample(1:n,1)
xory = sample(1:2,1)

matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
hues = runif(n,0,1)

```

Question
========

A video-game developer is hoping to rotate a set of points around the origin by `r th` radians counterclockwise by using matrix multiplication.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
abline(h=0)
abline(v=0)
thth = seq(0,th,pi/1200)
n2 = length(thth)
hf = 0.7
for(i in 1:n){
    xx = x1[i]*cos(thth)-y1[i]*sin(thth)
    yy = x1[i]*sin(thth)+y1[i]*cos(thth)
    for(j in 1:n2){
        points(xx[j],yy[j],col=hsv(hues[i],0.1+0.8*j/n2,1),cex=0.03)
    }
}
points(x1,y1,pch=19,col=hsv(hues,0.4,1))
points(x2,y2,pch=19,col=hsv(hues,1,1))
legend("topleft",c("Starting","Final"),col=c(hsv(0,0.4,1),hsv(0,1,1)),pch=c(19,19))
```
\

The starting points are stored as rows in a `r n` $\times$ 2 matrix $S$.

$$S=`r matpr(s)`$$

The 2D-rotation matrix can be found by using $\theta=`r th`$ in the formula below.

$$R~=~\begin{bmatrix}\cos(\theta)&\sin(\theta)\\ -\sin(\theta) & \cos(\theta)\end{bmatrix}$$

The final points (in matrix $F$) are found by multiplying $S\cdot R$.

$$F=S\cdot R$$

That multiplication can be done using the diagram below.

```{r,echo=F}
nc = 4
nr = n+2
```

```{r,echo=F,fig.dim=c(3.5,3.5/(nc+1)*(nr+1))}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(0,nr+1),asp=1)

nf = 2
np = n
ns = 2

clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
for(i in 1:nf){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),col=clrs[i],border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
}

for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,s[i,j])
    }
}

Rstr = matrix(c("$\\cos(\\theta)$","$-\\sin(\\theta)$","$\\sin(\\theta)$","$\\cos(\\theta)$"),2)

for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,TeX(Rstr[i,j]))
    }
}

for(i in 1:np){
    for(j in 1:ns){
        if(i != wunk || j!= xory){
            text(nf+j,np+1-i,sprintf("%.03f",f[i,j]))
        } else {
            text(nf+j,np+1-i,"?")
        }
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(nf+0.5,nf+0.5),c(np,0)+0.5,lwd=3)
lines(c(nf+0.5,nf+ns+0.5),c(np,np)+0.5,lwd=3)


```
\

As denoted by the question mark in the diagram above, when the point $(`r x1[wunk]`,`r y1[wunk]`)$ is rotated by `r th` radians, what is the new $`r c("x","y")[xory]`$ coordinate?


Solution
========

First, you can get decimal approximations for the rotation-matrix elements by using $\theta=`r th`$.

$$R=`r matpr(R)`$$

The initial point $(`r x1[wunk]`,`r y1[wunk]`)$ is in row `r wunk` of $S$. Because we want to find the new $`r c("x","y")[xory]`$ coordinate, use column `r xory` of $R$.

```{r,echo=F}
rx = R[1,xory]
ry = R[2,xory]
```

$$(`r x1[wunk]`)(`r rx`)~+~(`r y1[wunk]`)(`r ry`)$$

So, the new $`r c("x","y")[xory]`$ coordinate is `r f[wunk,xory]`.


Meta-information
============
extype: num
exsolution: `r f[wunk,xory]`
exname: rotate_2D
extol: 0.001