```{r,echo=F,warning=F}
n = 5
while(T){
    x1 = round(runif(n,1,6)*sample(c(-1,1),n,T),3)
    y1 = round(runif(n,1,6)*sample(c(-1,1),n,T),3)
    mind = 10
    for(i in 1:(n-1)){
        for(j in (i+1):n){
            d = sqrt((x1[j]-x1[i])^2+(y1[j]-y1[i])^2)
            mind = min(d,mind)
        }
    }
    if(mind>3 && sum(sign(x1)==1)>1 && sum(sign(x1)==-1)>1
       && sum(sign(y1)==1)>1  && sum(sign(y1)==-1)>1 ){break}
}
k = signif(2^(runif(1,0.4,1)*sample(c(-1,1),1)),3)
t = matrix(c(k,0,0,1/k),2)
tstr = matrix(c("k","0","0","1/k"),2)
xory = sample(1:2,1)

s = matrix(c(x1,y1),n)
f = s%*%t

wunk = sample(1:n,1)

matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
hues = seq(0,1,length.out=n+1)[1:n]

alldem = c(x1,y1,f[,1],f[,2])
mx = max(abs(alldem))
```

Question
========

A video-game developer is hoping to apply a [squeeze map](https://en.wikipedia.org/wiki/Squeeze_mapping) to a set of points by using matrix multiplication. Interestingly, during a squeeze map, the area remains constant.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-mx,mx),ylim=c(-mx,mx),axes=F,ann=F)
abline(h=0)
abline(v=0)
hf = 0.7
polygon(x1,y1,col=rgb(0.5,0.5,0.5,0.1),border="grey")
polygon(f[,1],f[,2],col=rgb(1,0,0,0.3))
ks = seq(1,k,(k-1)/1000)
for(i in 1:n){
    xx = x1[i]*ks
    yy = y1[i]/ks
    for(j in 1:1000){
        points(xx[j],yy[j],col=hsv(hues[i],0.1+0.8*j/1000,0.9),cex=0.03)
    }
}
points(x1,y1,pch=19,col="black",cex=1.1)
points(f[,1],f[,2],pch=19,col="black",cex=1.1)
points(x1,y1,pch=19,col=hsv(hues,0.2,0.9))
points(f[,1],f[,2],pch=19,col=hsv(hues,1,0.9))
legend("topleft",c("Starting","Final"),col=c(hsv(0,0.2,0.9),hsv(0,1,0.9)),pch=c(19,19))
```
\

The starting points are stored as rows in a `r n` $\times$ 2 matrix $S$.

$$S=`r matpr(s)`$$

The squeeze matrix can be found by using $k=`r k`$ in the formula below.

$$T~=~`r matpr(tstr)`$$

The final points (in matrix $F$) are found by multiplying $S\cdot T$.

$$F=S\cdot T$$

That multiplication can be done using the diagram below.

```{r,echo=F}
nc = 4
nr = n+2
```

```{r,echo=F,fig.dim=c(3.5,3.5/(nc+1)*(nr+1))}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(0,nr+1),asp=1)

nf = 2
np = n
ns = 2

clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
for(i in 1:nf){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),col=clrs[i],border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
}

for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,s[i,j])
    }
}

Rstr = matrix(c("$\\cos(\\theta)$","$-\\sin(\\theta)$","$\\sin(\\theta)$","$\\cos(\\theta)$"),2)

for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,TeX(tstr[i,j]))
    }
}

for(i in 1:np){
    for(j in 1:ns){
        if(i != wunk || j!= xory){
            text(nf+j,np+1-i,sprintf("%.03f",f[i,j]))
        } else {
            text(nf+j,np+1-i,"?")
        }
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(nf+0.5,nf+0.5),c(np,0)+0.5,lwd=3)
lines(c(nf+0.5,nf+ns+0.5),c(np,np)+0.5,lwd=3)
```
\

What is the new `r c("x","y")[xory]` coordinate when point $(`r x1[wunk]`, `r y1[wunk]`)$ undergoes the squeeze transformation with $k=`r k`$?

Solution
========

The squeeze transformation matrix:

$$T=`r matpr(t)`$$

We are looking for the new `r c("x","y")[xory]` coordinate after point $(`r x1[wunk]`, `r y1[wunk]`)$ undergoes the squeeze mapping. Use column `r xory` of $T$:


```{r,echo=F}
tx = t[1,xory]
ty = t[2,xory]
```

$$(`r x1[wunk]`)(`r tx`)~+~(`r y1[wunk]`)(`r ty`)$$

The new `r c("x","y")[xory]` coordinate is `r f[wunk,xory]`.

Meta-information
============
extype: num
exsolution: `r f[wunk,xory]`
exname: squeeze_2D
extol: 0.001