```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
getR = function(u,t){
  ux = u[1]
  uy = u[2]
  uz = u[3]
  f = cos(t)+ux^2*(1-cos(t))
  g = ux*uy*(1-cos(t))-uz*sin(t)
  h = ux*uz*(1-cos(t))+uy*sin(t)
  i = uy*ux*(1-cos(t))+uz*sin(t)
  j = cos(t)+uy^2*(1-cos(t))
  k = uy*uz*(1-cos(t))-ux*sin(t)
  l = uz*ux*(1-cos(t))-uy*sin(t)
  m = uz*uy*(1-cos(t))+ux*sin(t)
  n = cos(t)+uz^2*(1-cos(t))
  R = matrix(c(f,g,h,i,j,k,l,m,n),3,byrow=T)
  return(R)
}

s = t(matrix(c(1,-1,-1,
      -1,-1,-1,
      -1,1,-1,
      1,1,-1,
      0,0,1),3))

s2 = t(matrix(c(1,-1,-1,
      -1,-1,-1,
      -1,1,-1,
      1,1,-1,
      1,-1,-1,
      0,0,1,
      1,1,-1,
      -1,1,-1,
      0,0,1,
      -1,-1,-1),3))

# s3 = c(0,0,0,
#       0,0,1,
#       0,1,1,
#       0,1,0,
#       0,0,0,
#       1,0,0,
#       1,1,0,
#       0,1,0,
#       1,1,0,
#       1,1,1,
#       0,1,1,
#       1,1,1,
#       1,0,1,
#       0,0,1,
#       1,0,1,
#       1,0,0)
# s2 = t(matrix(s2,3))
n = 5

for(i in 1:7){
    u = rnorm(3)
    u[2] = abs(u[2])
    u[3] = abs(u[3])
    u = u/sqrt(sum(u^2))
    th = runif(1,0,2*pi)
    R = getR(u,th)
    s = s%*%R
    s2 = s2%*%R
}

s = round(s,4)
s2 = round(s2,4)

r = signif(runif(1,0.2,0.6),4)
th = signif(runif(1,pi/6,pi/3),4)

P = matrix(c(1,0,r*cos(th),0,1,r*sin(th)),3)
Pstr = matrix(c("1","0","r\\cdot\\cos(\\theta)","0","1","r\\cdot\\sin(\\theta)"),3)

wunk = sample(1:5,1)
xory = sample(1:2,1)

f = s%*%P
f2 = s2%*%P


```

Question
========

A video-game developer is hoping to apply an [oblique projection](https://en.wikipedia.org/wiki/Oblique_projection) to show a set of 3D points as a 2D image. The starting points are stored as rows in a `r n` $\times$ 3 matrix $S$.

$$S=`r matpr(s)`$$

The oblique projection matrix $P$ has two key parameters: $\theta$ and $r$. For this problem, use $\theta=`r th`$ and $r=`r r`$.

$$P~=~`r matpr(Pstr)`$$

The final points (in matrix $F$) are found by multiplying $S\cdot P$.

$$F=S\cdot P$$



```{r,echo=F}
nc = 5
nr = n+3
```

```{r,echo=F,fig.dim=c(5,5/(nc+1)*(nr+1))}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nc+1),ylim=c(0,nr+1),asp=1)

nf = 3
np = n
ns = 2

clrs = c("red","yellow","maroon","tan")
clrs = c(rgb(1,0,0,0.2),rgb(1,1,0,0.4),rgb(0.8,0,0.8,0.3),rgb(0.6,0.5,0.2,0.2))
clrs2 = c(rgb(1,0,0),rgb(1,1,0),rgb(0.8,0,0.8),rgb(0.6,0.5,0.2))
for(i in 1:nf){
    polygon(c(i-0.5,i-0.5,nf+0.5,nf+ns+0.5,nf+ns+0.5,nf+0.5,i+0.5,i+0.5),
            c(0.5,np+0.5,np+nf-i+1.5,np+nf-i+1.5,np+nf-i+0.5,np+nf-i+0.5,np+0.5,0.5),col=clrs[i],border = F)
    xt1 = i-0.3
    xt2 = nf+0.5
    yt1 = np+0.5
    yt2 = np+nf-i+1.3
    srt = atan2(yt2-yt1,xt2-xt1)/pi*180
}

for(i in 1:np){
    for(j in 1:nf){
        text(j,np-i+1,s[i,j])
    }
}


for(i in 1:nf){
    for(j in 1:ns){
        text(j+nf,np+nf-i+1,TeX(Pstr[i,j]))
    }
}

for(i in 1:np){
    for(j in 1:ns){
        if(i != wunk || j!= xory){
            text(nf+j,np+1-i,sprintf("%.03f",f[i,j]))
        } else {
            text(nf+j,np+1-i,"?")
        }
    }
}

for(i in 0:np){
    lines(c(0.5,nc+0.5),c(i,i)+0.5)
}
for(i in 0:ns){
    lines(nf+c(i,i)+0.5,c(0.5,np+nf+0.5))
}

lines(c(nf+0.5,nf+0.5),c(np,0)+0.5,lwd=3)
lines(c(nf+0.5,nf+ns+0.5),c(np,np)+0.5,lwd=3)
```
\

What is the new $`r c("x","y")[xory]`$ coordinate when point $(`r s[wunk,1]`, `r s[wunk,2]`, `r s[wunk,3]`)$ is projected using the oblique projection with $\theta=`r th`$ and $r=`r r`$?


Solution
========

Find the projection matrix by pluggin in $\theta=`r th`$ and $r=`r r`$.

$$P=`r matpr(P)`$$

We use row `r wunk` of the points matrix and column `r xory` of the projection matrix.


$$(`r s[wunk,1]`)(`r P[1,xory]`)~+~(`r s[wunk,2]`)(`r P[2,xory]`)~+~(`r s[wunk,3]`)(`r P[3,xory]`)$$

Thus, $`r c("x","y")[xory]`=`r f[wunk,xory]`$.


```{r,echo=F,fig.dim=c(5,5)}
maxx = max(f2[,1])
minx = min(f2[,1])
maxy = max(f2[,2])
miny = min(f2[,2])
midx = mean(c(minx,maxx))
midy = mean(c(miny,maxy))
radx = maxx-midx
rady = maxy-midy
maxrad = max(c(radx,rady))
xlo = midx-maxrad
xhi = midx+maxrad
ylo = midy-maxrad
yhi = midy+maxrad
plot(0,0,"n",xlim=c(xlo,xhi),ylim=c(ylo,yhi),xlab="x",ylab="y",asp=1)
lines(f2[,1],f2[,2])
points(f[wunk,1],f[wunk,2],pch=19,col="red")
```
\



Meta-information
============
extype: num
exsolution: `r f[wunk,xory]`
exname: projection_3D_to_2D
extol: 0.001