```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],\n            [",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

while(T){
  X = matrix(c(0,1,1,0,0,0,1,1),2,byrow=T)
  transformations = sample(1:5,3)
  nums = numeric()
  wrd1 = character()
  mats = list()
  for(i in 1:length(transformations)){
    tr = transformations[i]
    k1 = sample(13:25,1)/10
    k2 = sample(3:15,1)/10
    th = round(runif(1,0.1,2*pi-0.1),2)
    if(tr==1){
      k = k1
      wrd1 = c(wrd1,paste0("horizontal stretch by factor ",k))
      nums = c(nums,k)
      mats[[i]] = matrix(c(k,0,0,1),2,byrow=T)
    }
    if(tr==2){
      k = k1
      wrd1 = c(wrd1,paste0("vertical stretch by factor ",k))
      nums = c(nums,k)
      mats[[i]] = matrix(c(1,0,0,k),2,byrow=T)
    }
    if(tr==3){
      wrd1 = c(wrd1,paste0("rotation by angle ",th))
      nums = c(nums,th)
      mats[[i]] = matrix(round(c(cos(th),-sin(th),sin(th),cos(th)),3),2,byrow=T)
    }
    if(tr==4){
      k = k2
      wrd1 = c(wrd1,paste0("horizontal shear by factor ",k))
      nums = c(nums,k)
      mats[[i]] = matrix(c(1,k,0,1),2,byrow=T)
    }
    if(tr==5){
      k = k2
      wrd1 = c(wrd1,paste0("vertical shear by factor ",k))
      nums = c(nums,k)
      mats[[i]] = matrix(c(1,0,k,1),2,byrow=T)
    }
  }
  
  A = mats[[1]]
  B = mats[[2]]
  C = mats[[3]]
  
  xp1 = C %*% B %*% A %*% X
  xp2 = matrix(c(0,1,-1,0),2,byrow=T) %*% xp1
  xp3 = matrix(c(-1,0,0,-1),2,byrow=T) %*% xp1
  xp4 = matrix(c(0,-1,1,0),2,byrow=T) %*% xp1
  
  XP = list(xp1,xp2,xp3,xp4)
  
  xpn = A %*% B %*% C %*% X
  
  
  ord = sample(1:4)
  sol = paste0(1*(1==ord),collapse="")
  if(sum(3==transformations)==1 && sum(xp1==xpn)<8){break}
}

```

Question
========

Some basic [2D-transformation matrices](https://en.wikipedia.org/wiki/Transformation_matrix) are shown:

* Horizontal stretch by factor $k$ (with reflection if $k<0$). $$\begin{bmatrix}k & 0 \\ 0 & 1\end{bmatrix}$$
* Vertical stretch by factor $k$  (with reflection if $k<0$). $$\begin{bmatrix}1 & 0 \\ 0 & k\end{bmatrix}$$
* Rotation by angle $\theta$ radians. $$\begin{bmatrix}\cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{bmatrix}$$
* Horizontal shearing by factor $k$. $$\begin{bmatrix}1 & 0 \\ k & 1\end{bmatrix}$$
* Vertical shearing by factor $k$. $$\begin{bmatrix}1 & k \\ 0 & 1\end{bmatrix}$$

When multiple transformations are applied, order matters. If $A$ is the first transformation matrix, $B$ is the second, $C$ was the third, and $X$ was a matrix of row vectors, then the result, $X'$, would be found with the following matrix multiplication:
$$X' = XABC$$
Notice, we defined our transformation matrices as right-operands, so the order matches. If we used (the more standard) left-operand transformation matrices, the order would be reverse with $X$ at the end.

## Problem-specific information

We will use [SageMath](https://sagecell.sagemath.org/) to apply 3 transformations of a unit square. Begin with the points of a unit square.

$$X = \begin{bmatrix}0 & 0 \\ 0 & 1 \\ 1 & 1 \\ 1 & 0\end{bmatrix}$$
```
X = matrix([[0,0],[0,1],[1,1],[1,0]])
polygon(X,xmin=-5,xmax=5,ymin=-5,ymax=5,aspect_ratio=1,color="red")
```

Apply the following transformations in the indicated order:

1. A `r wrd1[1]`.
2. A `r wrd1[2]`.
3. A `r wrd1[3]`.

Which graph is generated when polygon $X$ is plotted in red and polygon $X'$ is plotted in blue?

```{r,echo=F,fig.dim=c(8,8)}
par(mfrow=c(2,2),pty="s")
for(i in 1:4){
  plot(0,0,type="n",axes=T,ann=T,main=c("A","B","C","D")[i],
       xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="y")
  abline(h=0)
  abline(v=0)
  polygon(X[1,],X[2,],col=rgb(1,0,0,0.5))
  polygon(XP[[ord[i]]][1,],XP[[ord[i]]][2,],col=rgb(0,0,1,0.5))
}

```
\

Answerlist
--------

* A
* B
* C
* D


Solution
========

The answer is `r c("A","B","C","D")[ord==1]`.

[SageMath](https://sagecell.sagemath.org/):
```
mygraph = Graphics()
X = matrix([[0,0],[0,1],[1,1],[1,0]])
mygraph += polygon(X,color="red",alpha=0.5)
A = matrix(`r matcc(t(A))`)
B = matrix(`r matcc(t(B))`)
C = matrix(`r matcc(t(C))`)
XP = X*A*B*C
mygraph += polygon(XP,color="blue",alpha=0.5)
show(mygraph,xmin=-10,xmax=10,ymin=-10,ymax=10,aspect_ratio=1)
```



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: multiple_transforms