```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

while(T){
    endxy = sample(6:10,2,T)
    xt = endxy[1]
    yt = endxy[2]
    x1 = sample(1:(xt-1),1)
    y1max = floor(yt/xt*x1)
    y1 = sample(1:(y1max-1),1)
    x2 = xt-x1
    y2 = yt-y1
    th1 = atan(y1/x1)
    th2 = atan(y2/x2)
    a = x1*y1/2
    b = x2*y1
    c = x2*y2/2
    d = c
    e = b
    f = a
    g = (x1+x2)*(y1+y2)-a-b-c-d-e-f
    g2 = abs(x1*y2-x2*y1)
    if(y2>0 && y1>0 && (y1/x1)<(y2/x2) & th2-th1>pi/12 && d!=a){break}
}

acha = a-0.5*(sample(0:5,1)-0:5)
if(min(acha)<0){acha = acha+abs(min(acha))+0.5}
achb = b-0.5*(sample(0:5,1)-0:5)
if(min(achb)<0){achb = achb+abs(min(achb))+0.5}
achc = c-0.5*(sample(0:5,1)-0:5)
if(min(achc)<0){achc = achc+abs(min(achc))+0.5}
achd = d-0.5*(sample(0:5,1)-0:5)
if(min(achd)<0){achd = achd+abs(min(achd))+0.5}
ache = e-0.5*(sample(0:5,1)-0:5)
if(min(ache)<0){ache = ache+abs(min(ache))+0.5}
achf = f-0.5*(sample(0:5,1)-0:5)
if(min(achf)<0){achf = achf+abs(min(achf))+0.5}
achg = g-0.5*(sample(0:5,1)-0:5)
if(min(achg)<0){achg = achg+abs(min(achg))+0.5}
sola = paste0(1*(acha==a),collapse = "")
solb = paste0(1*(achb==b),collapse = "")
solc = paste0(1*(achc==c),collapse = "")
sold = paste0(1*(achd==d),collapse = "")
sole = paste0(1*(ache==e),collapse = "")
solf = paste0(1*(achf==f),collapse = "")
solg = paste0(1*(achg==g),collapse = "")

```

Question
========

The figure below shows 7 polygons on a $10\times10$ grid. The grid is composed of 100 squares, each with an area of 1. Each polygon's area is labelled with an uppercase letter from $A$ to $G$. 

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,10),ylim=c(0,10),axes=F,ann=F)
for(i in 0:10){
    lines(c(i,i),c(0,10),col="grey")
    lines(c(0,10),c(i,i),col="grey")
}
cex = 1.4
val = 0.6

hues = seq(0,1,1/8)
polygon(c(0,x1,x1),c(0,0,y1),col=hsv(hues[1],1,1,0.3))
text(x1*2/3,y1/3,"A",col=hsv(hues[1],1,val),cex=cex)
polygon(c(x1,x1,xt,xt),c(0,y1,y1,0),col=hsv(hues[2],1,1,0.3))
text((x1+x2/2),y1/2,"B",col=hsv(hues[2],1,val),cex=cex)
polygon(c(x1,xt,xt),c(y1,y1,yt),col=hsv(hues[3],1,1,0.3))
text((x1+2*x2/3),y1+y2/3,"C",col=hsv(hues[3],1,val),cex=cex)

polygon(c(0,0,x2),c(0,y2,y2),col=hsv(hues[4],1,1,0.3))
text((x2/3),2*y2/3,"D",col=hsv(hues[4],1,val),cex=cex)
polygon(c(0,0,x2,x2),c(y2,yt,yt,y2),col=hsv(hues[5],1,1,0.3))
text((x2/2),y2+y1/2,"E",col=hsv(hues[5],1,val),cex=cex)
polygon(c(x2,x2,xt),c(y2,yt,yt),col=hsv(hues[6],1,1,0.3))
text(x2+x1/3,y2+2*y1/3,"F",col=hsv(hues[6],1,val),cex=cex)

polygon(c(0,x1,xt,x2),c(0,y1,yt,y2),col=hsv(hues[7],1,1,0.3))
text(xt/2,yt/2,"G",col=hsv(hues[7],1,val),cex=cex)

```
\

Find the areas of the triangles, rectangles, and parallelogram.

* $A=$ ##ANSWER1##
* $B=$ ##ANSWER2##
* $C=$ ##ANSWER3##
* $D=$ ##ANSWER4##
* $E=$ ##ANSWER5##
* $F=$ ##ANSWER6##
* $G=$ ##ANSWER7##



Answerlist
--------

`r paste0("* ",acha,collapse="\n")`
`r paste0("* ",achb,collapse="\n")`
`r paste0("* ",achc,collapse="\n")`
`r paste0("* ",achd,collapse="\n")`
`r paste0("* ",ache,collapse="\n")`
`r paste0("* ",achf,collapse="\n")`
`r paste0("* ",achg,collapse="\n")`


Solution
========

* Remember the area of a rectangle is width times height.
* Remember the area of a triangle is half of base times height.
    * For a right triangle, half the product of the legs.
* To find the area of the parallelogram, you can subtract all 6 other areas from the total area of the rectangle containing all 7 pieces.

* $a=`r a`$
* $b=`r b`$
* $c=`r c`$
* $d=`r d`$
* $e=`r e`$
* $f=`r f`$
* $g=`r g`$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r sola`|`r solb`|`r solc`|`r sold`|`r sole`|`r solf`|`r solg`
exname: area_parallelogram