```{r,echo=F,warning=F}
library(latex2exp)
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

while(T){
    endxy = sample(6:10,2,T)
    xt = endxy[1]
    yt = endxy[2]
    x1 = sample(1:(xt-1),1)
    y1max = floor(yt/xt*x1)
    y1 = sample(1:(y1max-1),1)
    x2 = xt-x1
    y2 = yt-y1
    th1 = atan(y1/x1)
    th2 = atan(y2/x2)
    a = x1*y1/2
    b = x2*y1
    c = x2*y2/2
    d = c
    e = b
    f = a
    g = (x1+x2)*(y1+y2)-a-b-c-d-e-f
    g2 = abs(x1*y2-x2*y1)
    if(y2>0 && y1>0 && (y1/x1)<(y2/x2) & th2-th1>pi/12 && d!=a){break}
}
```

Question
========

A $2\times 2$ matrix is often interpreted as two 2D points. We could think of each row (or each column) as representing a point in the $(x,y)$ plane.

$$A~=~\begin{bmatrix}x_1 & y_1 \\ x_2 & y_2\end{bmatrix}$$

The [determinant](https://en.wikipedia.org/wiki/Determinant) is defined as follows:

$$\det(A)~=~x_1 y_2 - x_2y_1$$

Let's practice evaluating the determinant.

$$B=\begin{bmatrix}`r x1` & `r y1` \\ `r x2` & `r y2`\end{bmatrix}$$


Evaluate $\det(B)$.


Solution
========

$$\det(B) ~=~ `r x1`\cdot`r y2` - `r x2`\cdot`r y1`$$
$$\det(B) ~=~ `r g`$$

Notice, this also is the area of the parallelogram shown below:

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,10),ylim=c(0,10),axes=F,ann=F)
for(i in 0:10){
    lines(c(i,i),c(0,10),col="grey")
    lines(c(0,10),c(i,i),col="grey")
}
cex = 1.4
val = 0.6

hues = seq(0,1,1/8)
# polygon(c(0,x1,x1),c(0,0,y1),col=hsv(hues[1],1,1,0.3))
# text(x1*2/3,y1/3,"A",col=hsv(hues[1],1,val),cex=cex)
# polygon(c(x1,x1,xt,xt),c(0,y1,y1,0),col=hsv(hues[2],1,1,0.3))
# text((x1+x2/2),y1/2,"B",col=hsv(hues[2],1,val),cex=cex)
# polygon(c(x1,xt,xt),c(y1,y1,yt),col=hsv(hues[3],1,1,0.3))
# text((x1+2*x2/3),y1+y2/3,"C",col=hsv(hues[3],1,val),cex=cex)
# 
# polygon(c(0,0,x2),c(0,y2,y2),col=hsv(hues[4],1,1,0.3))
# text((x2/3),2*y2/3,"D",col=hsv(hues[4],1,val),cex=cex)
# polygon(c(0,0,x2,x2),c(y2,yt,yt,y2),col=hsv(hues[5],1,1,0.3))
# text((x2/2),y2+y1/2,"E",col=hsv(hues[5],1,val),cex=cex)
# polygon(c(x2,x2,xt),c(y2,yt,yt),col=hsv(hues[6],1,1,0.3))
# text(x2+x1/3,y2+2*y1/3,"F",col=hsv(hues[6],1,val),cex=cex)

abline(h=0)
abline(v=0)

polygon(c(0,x1,xt,x2),c(0,y1,yt,y2),col=hsv(hues[7],1,1,0.3))
text(xt/2,yt/2,"G",col=hsv(hues[7],1,val),cex=cex)
points(x1,y1,pch=19)
points(x2,y2,pch=19)
text(x1,y1,TeX(paste0("$(",x1,",",y1,")$",collapse="")),adj=c(-0.1,1.1))
text(x2,y2,TeX(paste0("$(",x2,",",y2,")$",collapse="")),adj=c(1.1,-0.1))
```
\

$$G=`r g`$$


Meta-information
============
extype: num
exsolution: `r g`
exname: determinant_B