```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

lat = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],\n            [",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

lataug = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:3],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,'\\end{matrix}
  \\;\\middle|\\;
    \\,
    \\begin{matrix}\n')
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,4:6],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

styleblock = '<style>
select.question_input {
width: 5em;
}
tr {height: 3em;}
.mc {
display: inline-block;
padding: 1px;
margin: 1px;
white-space: nowrap;
background: linear-gradient(to right, black, black 10%, transparent 10%,transparent 90%,black 90%,black);
}
.matrix {
    padding: 5px;
    margin: 3px;
    background: white;
}
td.lbtd {
border-left: solid 2px #000;
}
.matrix td {
    padding: 10px;    
    text-align: center;
}
</style>'

while(T){
    abcdef = sample(2:12,6)*sample(c(-1,1),6,T)
    a = abcdef[1]
    b = abcdef[2]
    c = abcdef[3]
    d = abcdef[4]
    e = abcdef[5]
    f = abcdef[6]
    if(sum(sign(c(a,b,c)))<0){
        a = -a
        b = -b
        c = -c
    }
    if(sum(sign(c(d,e,f)))<0){
        d = -d
        e = -e
        f = -f
    }
    ### ax+by=c
    ### dx+ey=f
    detA = a*e-b*d
    detx = c*e-b*f
    dety = a*f-c*d
    x = detx/detA
    y = dety/detA
    xr = round(detx/detA,2)
    yr = round(dety/detA,2)
    if(abs(detA)>0 && abs(detx)>0 && abs(dety)>0 && 
       abs(gcd(c(a,b,c)))==1 && abs(gcd(c(d,e,f)))==1 && xr%%1!=0 && yr%%1!=0 && abs(xr)>0.1 && abs(yr)>0.1 && abs(xr)<100 && abs(yr)<100){break}
}

xch = round(xr-0.01*(sample(0:5,1)-0:5),2)
ych = round(yr-0.01*(sample(0:5,1)-0:5),2)
ach = sort(unique(c(xch,ych)))

sol1 = paste0(1*(xr==ach),collapse="")
sol2 = paste0(1*(yr==ach),collapse="")

```

Question
========

A [linear 2-equation-2-variable system](https://en.wikipedia.org/wiki/System_of_linear_equations) of equations can be expressed generally in standard form, using 6 parameters ($a$ through $f$) and 2 variables ($x$ and $y$).

$$\begin{align}ax+by &= c \\ dx+ey &=f\end{align}$$

Using determinants, we can express [Cramer's rule](https://en.wikipedia.org/wiki/Cramer%27s_rule), which gives us the solutions to the system:

$$x = \frac{\det\left(\begin{bmatrix}c & b\\ f & e\end{bmatrix}\right)}{\det\left(\begin{bmatrix}a & b\\ d & e\end{bmatrix}\right)}~=~\frac{ce-bf}{ae-bd}$$

and

$$y = \frac{\det\left(\begin{bmatrix}a & c\\ d & f\end{bmatrix}\right)}{\det\left(\begin{bmatrix}a & b\\ d & e\end{bmatrix}\right)}~=~\frac{af-cd}{ae-bd}$$

Using Cramer's rule, solve the linear system below:

```{r,echo=F}
soe = paste0("\\begin{align}",a,"x+",b,"y&=",c,"\\\\",d,"x+",e,"y&=",f,"\\end{align}",collapse="")
soe = gsub("+-","-",soe,fixed=T)
```


$$`r soe`$$

Express your answers in decimal form rounded to the hundredths place.

* $x=$ ##ANSWER1##
* $y=$ ##ANSWER2##


Answerlist
--------

`r paste0("* ",sprintf("%.02f",ach),collapse="\n")`
`r paste0("* ",sprintf("%.02f",ach),collapse="\n")`

Solution
========

Use Cramer's rule. Here is the given system:

$$`r soe`$$

Identify the parameters as defined in the general desciption.

$$a=`r a`$$
$$b=`r b`$$
$$c=`r c`$$
$$d=`r d`$$
$$e=`r e`$$
$$f=`r f`$$

Put parameters into the formula for $x$.

$$x = \frac{\det\left(\begin{bmatrix}c & b\\ f & e\end{bmatrix}\right)}{\det\left(\begin{bmatrix}a & b\\ d & e\end{bmatrix}\right)}~=~\frac{\det\left(\begin{bmatrix}`r c` & `r b`\\ `r f` & `r e`\end{bmatrix}\right)}{\det\left(\begin{bmatrix}`r a` & `r b`\\ `r d` & `r e`\end{bmatrix}\right)}$$

Remember how to calculate a [determinant](https://en.wikipedia.org/wiki/Determinant). 

$$\begin{align}x~&=~\frac{(`r c`)(`r e`)-(`r b`)(`r f`)}{(`r a`)(`r e`)-(`r b`)(`r d`)}\\\\
x~&=~ \frac{`r c*e-b*f`}{`r a*e-b*d`} \\\\
x~&\approx~ `r sprintf("%.02f",xr)`
\end{align}$$

Put parameters into the formula for $y$.

$$y = \frac{\det\left(\begin{bmatrix}a & c\\ d & f\end{bmatrix}\right)}{\det\left(\begin{bmatrix}a & b\\ d & e\end{bmatrix}\right)}~=~\frac{\det\left(\begin{bmatrix}`r a` & `r c`\\ `r d` & `r f`\end{bmatrix}\right)}{\det\left(\begin{bmatrix}`r a` & `r b`\\ `r d` & `r e`\end{bmatrix}\right)}$$

$$\begin{align}y~&=~\frac{(`r a`)(`r f`)-(`r c`)(`r d`)}{(`r a`)(`r e`)-(`r b`)(`r d`)}\\\\
y~&=~ \frac{`r a*f-c*d`}{`r a*e-b*d`} \\\\
y~&\approx~ `r sprintf("%.02f",yr)`
\end{align}$$



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: Cramers_rule_2x2