```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

lat = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

lataug = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  nch = nc-1
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:nch],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,'\\end{matrix}
  \\;\\middle|\\;
    \\,
    \\begin{matrix}\n')
  for(i in 1:dim(A)[1]){
    s = paste0(s,A[i,nc]," \\\\\n")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

latmat = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:nc],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

styleblock = '<style>
select.question_input {
width: 5em;
}
tr {height: 3em;}
.mc {
display: inline-block;
padding: 1px;
margin: 1px;
white-space: nowrap;
background: linear-gradient(to right, black, black 10%, transparent 10%,transparent 90%,black 90%,black);
}
.matrix {
    padding: 5px;
    margin: 3px;
    background: white;
}
td.lbtd {
border-left: solid 2px #000;
}
.matrix td {
    padding: 10px;    
    text-align: center;
}
</style>'

strt = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("")
  } else {
    return(as.character(s))
  }
}

md = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("+")
  } else if(s<0){
    return(as.character(s))
  } else {
    return(paste0("+",s,collapse=""))
  }
}

html_input_table = function(){
  s = "<div class='mc'><table class='matrix'>"
  nr = 3
  nc = 4
  nv = nc-1
  for(i in 1:nr){
    rs = paste0("<td>",rep("!!!",nv),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"<td class='lbtd'>!!!</td></tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

html_input_table_33 = function(nr=3,nc=3){
  s = "<div class='mc'><table class='matrix'>"
  for(i in 1:nr){
    rs = paste0("<td>",rep("!!!",nc),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"</tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

prs = function(M,lets=c("x","y","z","q","r","s","t","u","v","w")){
  s = "\\begin{aligned}"
  for(i in 1:dim(M)[1]){
    row = ""
    nc = dim(M)[2]
    ls = lets[1:(nc-1)]
    row = paste0(strt(M[i,1]),ls[1],collapse="")
    for(j in 2:(nc-1)){
      row = paste0(row,md(M[i,j]),ls[j],collapse="")
    }
    row = paste(row,"&=",M[i,nc],"\\\\\n",collapse="")
    row = sub("0x+","",row,fixed=T)
    row = sub("0x-","-",row,fixed=T)
    row = sub("0y+","",row,fixed=T)
    row = sub("0y-","-",row,fixed=T)
    row = sub("+0z","",row,fixed=T)
    row = sub("-0z","",row,fixed=T)
    s = paste0(s,row,collapse="")
  }
  s = paste0(s,"\\end{aligned}",collapse="")
  return(s)
}

########################
########################
########################
########################
########################
########################
########################


A = matrix(sample(-9:9,9,T),3)
I = matrix(c(1,0,0,0,1,0,0,0,1),3)

ac = -9:9


sols = character()
for(aa in c(t(A))){
  sols = c(sols,paste0(1*(aa==ac),collapse=""))
}

al = paste0("* ",ac,collapse="\n")
al = paste0(rep(al,9),collapse="\n")

solstr=""

for(i in 1:3){
  for(j in 1:3){
    solstr = paste0(solstr,"To find the product matrix's value in row ",i," and column ",j,", sum the products of corresponding elements of row ",i," in matrix A and column ",j," in matrix B.\n","$$P_{[",i,",",j,"]}=")
    damath = paste0("(",I[i,],")(",A[,j],")",collapse="+")
    solstr = paste0(solstr,damath,"=",A[i,j],"$$\n\n")
  }
}

```

Question
========

`r styleblock`

Let $I$ be a 3x3 [identity matrix](https://en.wikipedia.org/wiki/Identity_matrix). $$I = `r latmat(I)`$$

and let $A$ be a 3x3 square matrix.

$$A = `r latmat(A)`$$
Let $P$ be the product of $I$ times $A$. 

$$P = I\cdot A$$

$$P = `r latmat(I)` \cdot `r latmat(A)`$$

Determine the values of matrix $P$:

```{r,echo=F,results='asis'}
ans_num=1
hm = html_input_table_33()
for(j in 1:12){
  hm = sub("!!!",paste0("##ANSWER",ans_num,"##",collapse=""),hm,fixed = T)
  ans_num=ans_num+1
}
cat(hm)
```

Answerlist
--------

`r al`

Solution
========

We wish to do matrix multiplication:

$$`r latmat(I)` \cdot `r latmat(A)`$$

`r solstr`

All of that work leads to the answer:

$$P ~=~ IA ~=~ `r latmat(A)`$$




Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",9),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: identity_matrix