```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

lat = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

latmat = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:nc],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

styleblock = '<style>
select.question_input {
width: 5em;
}
tr {height: 3em;}
.mc {
display: inline-block;
padding: 1px;
margin: 1px;
white-space: nowrap;
background: linear-gradient(to right, black, black 10%, transparent 10%,transparent 90%,black 90%,black);
}
.matrix {
    padding: 5px;
    margin: 3px;
    background: white;
}
td.lbtd {
border-left: solid 2px #000;
}
.matrix td {
    padding: 10px;    
    text-align: center;
}
</style>'


html_input_table = function(){
  s = "<div class='mc'><table class='matrix'>"
  nr = 3
  nc = 4
  nv = nc-1
  for(i in 1:nr){
    rs = paste0("<td>",rep("!!!",nv),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"<td class='lbtd'>!!!</td></tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

html_input_table_33 = function(nr=3,nc=3){
  s = "<div class='mc'><table class='matrix'>"
  for(i in 1:nr){
    rs = paste0("<td>",rep("!!!",nc),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"</tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

prs = function(M,lets=c("x","y","z","q","r","s","t","u","v","w")){
  s = "\\begin{aligned}"
  for(i in 1:dim(M)[1]){
    row = ""
    nc = dim(M)[2]
    ls = lets[1:(nc-1)]
    row = paste0(strt(M[i,1]),ls[1],collapse="")
    for(j in 2:(nc-1)){
      row = paste0(row,md(M[i,j]),ls[j],collapse="")
    }
    row = paste(row,"&=",M[i,nc],"\\\\\n",collapse="")
    row = sub("0x+","",row,fixed=T)
    row = sub("0x-","-",row,fixed=T)
    row = sub("0y+","",row,fixed=T)
    row = sub("0y-","-",row,fixed=T)
    row = sub("+0z","",row,fixed=T)
    row = sub("-0z","",row,fixed=T)
    s = paste0(s,row,collapse="")
  }
  s = paste0(s,"\\end{aligned}",collapse="")
  return(s)
}

########################
########################
########################
########################
########################
########################
########################

while(T){
    A = matrix(sample(-10:10,12,T),3)
    B = matrix(sample(-10:10,12,T),3)
    C = A-B
    if(max(abs(C))<=12){break}
}

ac = -12:12

sols = character()
for(aa in c(t(C))){
  sols = c(sols,paste0(1*(aa==ac),collapse=""))
}

al = paste0("* ",ac,collapse="\n")
al = paste0(rep(al,12),collapse="\n")

```

Question
========

`r styleblock`

Let $A$ and $B$ be 3x4 matrices.

$$A = `r latmat(A)`$$

$$B = `r latmat(B)`$$

Let $C$ be the [difference](https://en.wikipedia.org/wiki/Matrix_addition) of $A$ minus $B$. 

$$C ~=~ A - B$$

Determine the values of matrix $C$:

```{r,echo=F,results='asis'}
ans_num=1
hm = html_input_table_33(3,4)
for(j in 1:12){
  hm = sub("!!!",paste0("##ANSWER",ans_num,"##",collapse=""),hm,fixed = T)
  ans_num=ans_num+1
}
cat(hm)
```

Answerlist
--------

`r al`

Solution
========

Simply subtract corresponding elements.

$$C ~=~ `r latmat(C)`$$

You might be wondering why matrix multiplication is not as simple. What you are looking for is called the [Hadamard product](https://en.wikipedia.org/wiki/Hadamard_product_(matrices)).


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",12),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: subtract_matrices