```{r,echo=F,results='hide',message=FALSE, warning=FALSE, include=FALSE}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

lat = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

html_input_table_33 = function(nr=3,nc=3){
  s = "<div class='mc'><table class='matrix'>"
  for(i in 1:nr){
    rs = paste0("<td>",rep("!!!",nc),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"</tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

latmat = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:nc],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

#library
library(igraph,quietly=T)

# Create data
# set.seed(10)
data <- matrix(sample(0:1, 25, replace=TRUE,prob=c(0.6,0.4)), nrow=5)
colnames(data) = rownames(data) = LETTERS[1:5]

for(i in 1:5){
    data[i,i] = 0
}

# build the graph object
network <- graph_from_adjacency_matrix(data)


sols = character()
for(jj in c(t(data))){
    sols = c(sols,paste0(1*(jj==c(0,1)),collapse=""))
}

```

Question
========

A matrix can be used to represent incidence relationships in a network. As a simple example, the [directed graph](https://en.wikipedia.org/wiki/Directed_graph) below

```{r,echo=F,fig.dim=c(3,3)}
par(mar=c(0,0,0,0))
data2 = matrix(c(0,1,1,0,0,1,1,0,0),3,byrow = T)
colnames(data2) = rownames(data2) = LETTERS[24:26]
network2 <- graph_from_adjacency_matrix(data2)
plot(network2)
```

can be represented with the following matrix

$$`r latmat(data2)`$$

because 

* $X$ points to $Y$
* $X$ points to $Z$
* $Y$ points to $Z$
* $Z$ points to $X$

Notice I did assume the rows and columns follow alphabetical order.

## Write matrix from directed graph

Here is another directed graph:

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0))
plot(network)
```

Please write the corresponding matrix. Assume rows and columns represent $a$ through $e$ in alphabetical order. Putting a 1 in the matrix represents the letter of that row points toward the letter of the column.

```{r,echo=F,results='asis'}
ans_num=1
hm = html_input_table_33(5,5)
for(j in 1:25){
  hm = sub("!!!",paste0("##ANSWER",ans_num,"##",collapse=""),hm,fixed = T)
  ans_num=ans_num+1
}
cat(hm)
```


Answerlist
--------

`r paste0(rep("* 0\n* 1",25),collapse="\n")`


Solution
========


$$`r latmat(data)`$$


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",25),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: subtract_matrices