```{r,echo=F,warning=F}

# I STARTED SWITCHING OVER TO 2nd-operand transformation matrices
# But then I decided this whole question is mid...

matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

X = matrix(c(1,-1,-1,
      -1,-1,-1,
      -1,1,-1,
      1,1,-1,
      1,-1,-1,
      0,0,1,
      1,1,-1,
      -1,1,-1,
      0,0,1,
      -1,-1,-1),3)


XS = c(0,0,0,
      0,0,1,
      0,1,1,
      0,1,0,
      0,0,0,
      1,0,0,
      1,1,0,
      0,1,0,
      1,1,0,
      1,1,1,
      0,1,1,
      1,1,1,
      1,0,1,
      0,0,1,
      1,0,1,
      1,0,0)
XS = matrix(XS,3)

tx = round(runif(1,0.1,2*pi-0.1),2)
ty = round(runif(1,0.1,2*pi-0.1),2)
tz = round(runif(1,0.1,2*pi-0.1),2)
tp = round(runif(1,0.1,pi/4),2)
r = round(runif(1,0.05,0.5),2)

pams1 = c(tp,r,tx,ty,tz)

pm = list(pams1)

for(i in 2:4){
  tx2 = round(runif(1,0.1,2*pi-0.1),2)
  ty2 = round(runif(1,0.1,2*pi-0.1),2)
  tz2 = round(runif(1,0.1,2*pi-0.1),2)
  tp2 = round(runif(1,0.1,pi/4),2)
  r2 = round(runif(1,0.05,0.5),2)
  pams2 = c(tp2,r2,tx2,ty2,tz2)
  pm[[i]] = pams2
}

ord = sample(1:4)
sol = paste0(1*(1==ord),collapse="")

```

Question
========

One of the simplest 3D $\to$ 2D projections (to draw by hand) is an [oblique projection](https://en.wikipedia.org/wiki/Oblique_projection). Each type of oblique projection can be parameterized with an angle ($\theta$) and a ratio ($r<1$). Below is an oblique-projection matrix.


$$P = \begin{bmatrix}1 & 0 \\ r\cos(\theta_P) & r\sin(\theta_P) \\ 0 & 1 \end{bmatrix}$$

We can exemplify an oblique projection with $r=0.5$ and $\theta_P=\frac{pi}{6}$ on a unit cube. The cube has lengths 1 unit long.

([SageMath](https://sagecell.sagemath.org/?z=eJxtUF0LgyAUfRf8Dxf2oiEtH7a3fsN6DCLCwuCOpk4N9vPnWrGgecCPq-d47jnBrZ_wOWtw3t71ENEasCPMBiMMc68pqSWU8FDR44s1TSE2yITD3ApKYD-a39PvumGV-UfYXR9pbcsp8clSkV8oiS7tHJ6vlFR7m1L4bLCBRcc_fyRRnwU0y1kuEuOkYrf0VmW1pGRCo9lazKNXJjgbNONCBZdy6bxK2ZSSvwGw2ExO&lang=sage&interacts=eJyLjgUAARUAuQ==))
```
X = matrix(`r matcc(t(XS))`)
r = 0.5
tp = pi/6
P = matrix([[1,0],[r*cos(tp),r*sin(tp)],[0,1]])
flat_X = X*P
line(flat_X,aspect_ratio=1)
```

```{r,echo=F,fig.dim=c(5,5)}
r3 = 0.5
t3 = pi/6
P3 = matrix(c(1,r3*cos(t3),0,0,r3*sin(t3),1),2,byrow=T)
Y3 = P3%*%XS
par(pty="s")
plot(Y3[1,],Y3[2,],type="l",xlim=c(-0.1,1.5),ylim=c(-0.1,1.5),xlab="x",ylab="z")
lines(c(1+r3,1,1+r3*cos(t3)),c(0,0,r3*sin(t3)),col="red",lwd=2)
th = seq(0,2*pi,length.out=300)
lines(1+r3*cos(th),r3*sin(th),col="red",lty=3)
th = seq(0,t3,length.out=100)
lines(1+r3*cos(th),r3*sin(th),col="red",lwd=2)
text(1+0.3*cos(t3/2),0.3*sin(t3/2),"pi/6",col="red")
text(1+r/2,-0.05,r3,col="red")
```
\

In 3D, there are relatively simple rotation matrices for spinning around the $x$, $y$, or $z$ axis.

$$R_x = \begin{bmatrix}1 & 0 & 0 \\ 0 & \cos(\theta_x) & \sin(\theta_x) \\ 0 &-\sin(\theta_x) & \cos(\theta_x) \end{bmatrix}$$

$$R_y = \begin{bmatrix}\cos(\theta_y) & 0 & -\sin(\theta_y) \\ 0 & 1 & 0 \\ \sin(\theta_y) & 0 & \cos(\theta_y) \end{bmatrix}$$

$$R_z = \begin{bmatrix}\cos(\theta_z) & \sin(\theta_z) & 0 \\ -\sin(\theta_z) & \cos(\theta_z) & 0 \\ 0 & 0 & 1\end{bmatrix}$$

## Information specific to this question

Fill in the missing code to generate various rotations of a square pyramid.

* Red: X1 is the original
* Orange: X2 is after a rotation of `r tx` radians around the x-axis
* Green: X3 has another rotation of `r ty` radians around the y-axis
* Blue: X4 has another rotation of `r tz` radians around the z-axis

In order to flatten the 3D points onto a 2D graph, each pyramid will undergo an oblique projection with $r=`r r`$ and $\theta_P=`r tp`$.

```
graph01 = Graphics()
X1 = matrix(`r matcc(X)`)
P = ...
X1_flat = ...
graph01 += line(X1_flat.transpose(),color="red")
Rx = ...
X2 = ...
X2_flat = ...
graph01 += line(X2_flat.transpose(),color="orange")
Ry = ...
X3 = ...
X3_flat = ...
graph01 += ...
Rz = ...
X4 = ...
X4_flat = ...
graph01 += ...
show(graph01,aspect_ratio=1,axes=False)
```

Which graph matches?

```{r,echo=F,fig.dim=c(8,8)}
par(pty="s",mfrow=c(2,2),mar=c(0,0,3,0))
for(i in 1:4){
  pams = pm[[ord[i]]]
  TP = pams[1]
  R = pams[2]
  TX = pams[3]
  TY = pams[4]
  TZ = pams[5]
  rx = matrix(c(1,0,0,
                0,cos(TX),-sin(TX),
                0,sin(TX),cos(TX)),3,byrow = T)
  ry = matrix(c(cos(TY),0,sin(TY),
                0,1,0,
                -sin(TY),0,cos(TY)),3,byrow = T)
  rz = matrix(c(cos(TZ),-sin(TZ),0,
                sin(TZ),cos(TZ),0,
                0,0,1),3,byrow = T)
  pp = matrix(c(1,R*cos(TP),0,
                0,R*sin(TP),1),2,byrow=T)
  x1 = pp %*% X
  x2 = pp %*% rx %*% X
  x3 = pp %*% ry %*% rx %*% X
  x4 = pp %*% rz %*% ry %*% rx %*% X
  plot(0,0,type="n",axes=F,ann=T,xlab="",ylab="",xlim=c(-2,2),ylim=c(-2,2),main=c("A","B","C","D")[i])
  lines(x1[1,],x1[2,],col="red")
  lines(x2[1,],x2[2,],col="orange")
  lines(x3[1,],x3[2,],col="darkgreen")
  lines(x4[1,],x4[2,],col="blue")
}
```
\

Answerlist
--------

* A
* B
* C
* D


Solution
========

The answer is `r c("A","B","C","D")[ord==1]`.

[SageMath](https://sagecell.sagemath.org/)
```
graph01 = Graphics()
X1 = matrix(`r matcc(X)`)
P = matrix([[1,`r r`*cos(`r tp`),0],[0,`r r`*sin(`r tp`),1]])
X1_flat = P*X1
graph01 += line(X1_flat.transpose(),color="red")
tx = `r tx`
Rx = matrix([[1,0,0],
             [0,cos(tx),-sin(tx)],
             [0,sin(tx),cos(tx)]])
X2 = Rx*X1
X2_flat = P*X2
graph01 += line(X2_flat.transpose(),color="orange")
Ry = matrix([[cos(`r ty`),0,sin(`r ty`)],
             [0,1,0],
             [-sin(`r ty`),0,cos(`r ty`)]])
X3 = Ry*X2
X3_flat = P*X3
graph01 += line(X3_flat.transpose(),color="green")
Rz = matrix([[cos(`r tz`),-sin(`r tz`),0],
             [sin(`r tz`),cos(`r tz`),0],
             [0,0,1]])
X4 = Rz*X3
X4_flat = P*X4
graph01 += line(X4_flat.transpose(),color="blue")
show(graph01,aspect_ratio=1,axes=False)
```


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: oblique_projection