```{r,echo=F,warning=F}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

n = 7
r = sqrt(runif(n,0.05,1))
t = runif(n,0,2*pi)
y = runif(n,-1,1)
x = r*cos(t)
z = r*sin(t)

S = round(matrix(c(x,y,z),n),4)

```

Question
========

Some [3D-to-2D projections](https://en.wikipedia.org/wiki/3D_projection) are not done by matrix multiplication. For example, a [one-point perspective](https://en.wikipedia.org/wiki/Perspective_(graphical)) could be achieved with the following (nonlinear, and therefore not done by matrix multiplication) formulas:

$$x'~=~k\frac{x}{z}$$
$$y'~=~k\frac{y}{z}$$

where $x'$ and $y'$ are the coordinates of the 2D image, and $(x,y,z)$ is any point in 3D space, and $k$ is a scaling parameter. More specifically, imagine a camera with a sightline (like a laser) pointing straight ahead: $x$ is the horizontal displacement of any point from that sightline; $y$ is the vertical displacement of any point from that sightline; and $z$ is the distance of the object away from the camera. This assumes $z>0$.

Even when matrix multiplication is not used for projecting the 3D points into 2D images, matrix multiplication remains useful for rotating, shearing, stretching, and reflecting points.

Our goal will be to animate a 3D trace

`r matcc(S)`

```{r,echo=F}

```


Answerlist
--------




Solution
========




Meta-information
============
extype: schoice
exsolution: 
exname: spinning_3D_pnts