```{r data generation, echo = FALSE, results = "hide"}
while(T){
    n = sample(5:8,1)
    x = sort(sample(1:30,n))
    l = sort(round(runif(n-1,0,1),2))
    breaks = c(0,l,1)
    p = round(breaks[2:(n+1)]-breaks[1:n],2)
    mu = sum(p*x)
    sig = sqrt(sum(p*(x-mu)^2))
    # the following requirements add considerable time...
    if(sum(p)==1 & sum(p>0.05)==n & as.integer(mu)==mu){
        break
    }
}

s = ''
for(i in 1:n){
    s = paste(s,'|',x[i],'|',p[i],'|\n')
}

c3 = x*p
c4 = x-mu
c5 = (x-mu)^2
c6 = p*(x-mu)^2

s2 = ''
for(i in 1:n){
    s2 = paste(s2,'|',x[i],'|',p[i],'|',c3[i],'|',c4[i],'|',c5[i],'|',c6[i],'|')
    if(i < n){
        s2 = paste(s2,'\n')
    }
}

exact = sample(1:n,1)
xex = x[exact]
two = sort(sample(1:n,2))
ptwo = sum(p[two])
if(n==3){
  atlm = 2
} else {
  atlm = sample(2:(n-1),size=1)
}
xatlm = x[atlm]
atl = sample(c(T,F),1)
if(atl){
  word = "least"
  patlm = sum(p[atlm:n])
  sym = "\\ge"
} else {
  word = "most"
  patlm = sum(p[1:atlm])
  sym = "\\le"
}

mydf = data.frame(x,p)
colnames(mydf) = c("x","P[x]")
```

Question
========

A spinner was constructed:

```{r echo=F,fig.width=4,fig.height=4}
theta = seq(0,2*pi,length.out=1000)
par(mar=c(0,0,0,0))
plot(sin(theta),cos(theta),type="l",ann=F,axes=F)
for(i in 1:length(p)){
  lines(c(0,sin(breaks[i+1]*2*pi)),c(0,cos(breaks[i+1]*2*pi)))
  thetaText = 2*pi*(breaks[i+1]+breaks[i])/2
  text(0.8*sin(thetaText),0.8*cos(thetaText),x[i])
}
arrows(-0.6,-0.1,0.6,0.1,lwd=3)
for(perc in seq(0,1,0.1)){
  the = perc*2*pi
  lines(c(1,1.05)*sin(the),c(1,1.05)*cos(the))
}
for(perc in seq(0,1,0.01)){
  the = perc*2*pi
  lines(c(1,1.02)*sin(the),c(1,1.02)*cos(the))
}

mydf = data.frame(x,p)
colnames(mydf) = c("$x$","$P[x]$")

r1 = p[exact]
r2 = ptwo
r3 = p[two[1]]*p[two[2]]
r4 = patlm
r5 = mu
r6 = sig
while(T){
  ch1 = sort(c(r1,sample(1:99,3)/100))
  an1 = paste0((ch1==r1)*1,collapse="")
  if(min(diff(ch1))>0.01){break}
}
while(T){
  ch2 = sort(c(r2,sample(1:99,3)/100))
  an2 = paste0((ch2==r2)*1,collapse="")
  if(min(diff(ch2))>0.01){break}
}
bot = sample((-3):0,1)
ch3 = signif(2^(bot:(bot+3))*r3,4)
an3 = paste0((ch3==signif(r3,4))*1,collapse="")
while(T){
  ch4 = sort(c(r4,sample(1:99,3)/100))
  an4 = paste0((ch4==r4)*1,collapse="")
  if(min(diff(ch4))>0.01){break}
}
bot = sample((-3):0,1)
ch5 = r5+(bot:(bot+3))
an5 = paste0((ch5==r5)*1,collapse="")
bot = sample((-3):0,1)
ch6 = r6*1.2^(bot:(bot+3))
an6 = paste0((ch6==r6)*1,collapse="")
```
\

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

The spinner's probability distribution is shown below.

```{r tab1, results="asis", echo=F}
knitr::kable(mydf,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


* What is the probability of spinning `r xex`? In other words, what is $P[X=`r xex`]$? ##ANSWER1##
* What is the probability of spinning `r x[two[1]]` or `r x[two[2]]`? In other words, what is $P[X=`r x[two[1]]` ~\text{ or }~ X=`r x[two[2]]`]$? ##ANSWER2##
* If spinning twice, what is the probability of first spinning `r x[two[1]]` and then spinning `r x[two[2]]`? In other words, what is $P[X_1=`r x[two[1]]` ~\text{ and }~ X_2=`r x[two[2]]`]$? ##ANSWER3##
* What is the probability of spinning at `r word` `r xatlm`? In other words, what is $P[X`r sym` `r xatlm`]$? ##ANSWER4##
* Determine the mean of the probability distribution by using $\mu = \sum x\cdot P[x]$. ##ANSWER5##
* Determine the standard deviation of the probability distribution by using $\sigma = \sqrt{\sum (x-\mu)^2 \cdot P[x]}$. ##ANSWER6##

Answerlist
--------

* `r ch1[1]`
* `r ch1[2]`
* `r ch1[3]`
* `r ch1[4]`
* `r ch2[1]`
* `r ch2[2]`
* `r ch2[3]`
* `r ch2[4]`
* `r ch3[1]`
* `r ch3[2]`
* `r ch3[3]`
* `r ch3[4]`
* `r ch4[1]`
* `r ch4[2]`
* `r ch4[3]`
* `r ch4[4]`
* `r ch5[1]`
* `r ch5[2]`
* `r ch5[3]`
* `r ch5[4]`
* `r ch6[1]`
* `r ch6[2]`
* `r ch6[3]`
* `r ch6[4]`


Solution
========

[video](https://vimeo.com/531915788){target="_blank"}

Make a table (for mean and standard deviation).

```{r table, echo=F}
s3 = '\\begin{center}\n\\begin{tabular}{|c|c|c|c|c|c|} \\hline\n'
s3 = paste(s3, "$x$ & $P[x]$ & $x\\cdot P[x]$ & $x-\\mu$ & $(x-\\mu)^2$ & $(x-\\mu)^2 \\cdot P[x]$ \\\\ \\hline\n")
for(i in 1:n){
    s3 = paste(s3,x[i],'&',p[i],'&',c3[i],'&',c4[i],'&',c5[i],'&',c6[i],'\\\\')
    if(i < n){
        s3 = paste(s3,'\n')
    }
}
s3 = paste(s3, '\\hline\n')
s3 = paste(s3, "& & $\\sum x \\cdot P[x]=",mu,"$& & & $\\sigma^2 =",sum(c6),"$ \\\\ \\hline\n")
s3 = paste(s3, "& & $\\mu=",mu,"$& & & $\\sigma =",sig,"$ \\\\ \\hline\n")
s3 = paste(s3,"\\end{tabular}\n\\end{center}",sep="")

mydf2 = data.frame(x,p,c3,c4,c5,c6)
colnames(mydf2) = c("$x$","$P[x]$","$x\\cdot P[x]$",
                    "$x-\\mu$","$(x-\\mu)^2$","$(x-\\mu)^2 \\cdot P[x]$")
```

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab2, results="asis", echo=F}
mydf2 = type.convert(mydf2, as.is = TRUE)
mydf2 = rbind(mydf2,rep("",6))
mydf2 = rbind(mydf2,c("","",
                      sprintf("$\\sum x \\cdot P[x]=%.2f$",mu),"","",
                      sprintf("$\\sigma^2=%.2f$",sum(c6))))
mydf2 = rbind(mydf2,c("","",
                      sprintf("$\\mu = %.2f$",mu),"","",
                      sprintf("$\\sigma=%.2f$",sig)))
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cccccc",row.names=F)
```


* `r p[exact]`
* $`r p[two[1]]` + `r p[two[2]]`$ = **`r ptwo`**
* $`r p[two[1]]` \times `r p[two[2]]`$ = **`r p[two[1]]*p[two[2]]`**
* `r patlm`
* $\mu = `r mu`$
* $\sigma = `r sig`$


Meta-information
============
extype: cloze
exsolution: `r an1`|`r an2`|`r an3`|`r an4`|`r an5`|`r an6`
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exname: probability_distribution_MC