---
title: "Binomial Distribution"
author: Chad Worley
date: 2023 Sep 19
output: ioslides_presentation
---


## Entrance Ticket

![](pics/ski.svg){width=60%}

How many routes can the skier ski down from the top (A) to the lodge (S), without going through trees?

## Pascal's Triangle

![](pics/pascal.svg){width=80%}

## Anagram Approach

The skier had to head East three times and West twice.

> - EEEWW
> - EEWEW
> - EEWWE
> - EWEEW
> - EWEWE
> - EWWEE
> - WEEEW
> - WEEWE
> - WEWEE
> - WWEEE

## Simple anagrams (no repeats)

How many ways can the letters in "FROG" be rearranged?

> - There are 4 possible spots for the "F".
> - Once the location of "F" is decided, there are 3 spots for the "R".
> - Two spots for the "O".
> - The last remaining spot goes to the "G".


## Arrangements of FROG 

```
FROG RFOG ROFG ROGF
FRGO RFGO RGFO RGOF
FORG OFRG ORFG ORGF
FGRO GFRO GRFO GROF
FOGR OFGR OGFR OGRF
FGOR GFOR GOFR GORF
```

```
1234 2134 3124 4123
1243 2143 3142 4132
1324 2314 3214 4213
1342 2341 3241 4231
1423 2413 3412 4312
1432 2431 3421 4321
```

## Factorial

$$4! = 4\cdot 3\cdot 2\cdot 1 = 24$$

> - $5! =\, ?$
> - $5! = 120$
> - $1! =\, ?$
> - $1! = 1$
> - $0! =\, ?$
> - $0! = 1$
> - In sheets, use `=FACT(5)` to calculate $5!$.

## MYSTICAL

How many ways can the letters in "MYSTICAL" be arranged?

> - There are 8 unique letters.
> - `=FACT(8)` equals 40320

## ROOF

How many ways can the letters in "ROOF" be arranged?

> - There are 4 spots for the "R".
> - There are 3 spots for the "F".
> - The remaining spots are filled with "O"s.
> - $4 \cdot 3 = 12$.

## ABCXXX

How many ways can the letters in "ABCDXXX" be arranged?

> - There are 7 spots for "A", 6 spots for "B", 5 spots for "C", and 4 spots for "D".
> - The remaining spots are filled with "X"s.
> - $7 \cdot 6 \cdot 5 \cdot 4 = 840$.
> - Notice, for each arrangement of "ABCDXXX", there would be $3!=6$ equivalent arrangements of "ABCDXYZ".
> - For example, "ADXXBCX" is equivalent to "ADXYBCZ", "ADXZBCY", "ADYXBCZ", "ADYZBCX", "ADZXBCY", and "ADZYBCX".
> - So, $\frac{7!}{3!} = 840$

## Permutations

In a class of 100 students, an election will select one president, one vice president, and one jester. How many possible election outcomes are there?

> - ${_{100}P_{3}} = \frac{100!}{(100-3)!} = \frac{100!}{97!} = 100\cdot99\cdot98 = 970200$
> - `=PERMUT(100,3)` equals 970200
> - Notice this is equivalent to arrangements of ABCXXX...XXX, with 97 "X"s.
> - ${_{n}P_{r}} = \frac{n!}{(n-r)!}$

## MISSISSIPPI

How many ways can the letters in "MISSISSIPPI" be arranged?

> - There are 11 letters in total.
> - The counts are 1, 4, 4, and 2.
> - $\frac{11!}{1!\cdot 4! \cdot 4! \cdot 2!} = 34650$

## AAAAXXX

How many ways can the letters in "AAAAXXX" be arranged?

> - $\frac{7!}{4! \cdot 3!} = 35$

## Combinations 

In a class of 100 students, an election will select three council members. How many possible election outcomes are there?

> - ${_{100}C_{3}} = \frac{100!}{(100-3)!\cdot 3!} = \frac{100!}{97!\cdot 3!} = \frac{100\cdot99\cdot98}{3\cdot2\cdot1} = 161700$
> - `=COMBIN(100,3)` equals 161700
> - Notice this is equivalent to arrangements of AAAXXX...XXX, with 3 "A"s and 97 "X"s.
> - ${_{n}C_{r}} = {n \choose r} = \frac{n!}{(n-r)!\cdot r!}$

## Pascal's Triangle

![](pics/pascal.svg){width=60%}

* These represent combinations.
* Notice, ${6\choose0} = 1$, ${6\choose1} = 6$, ${6\choose 2} = 15$,  ${6\choose 3} = 20$, ${6\choose 4} = 15$, ${6\choose 5} = 6$, and ${6\choose 6} = 1$.

## Connect the dots

![](pics/dots_7.svg){width=50%}

How many line segments can you draw that connect 2 of the 7 dots?


## Connect the dots

![](pics/dots_7_solution.svg){width=50%}

${7 \choose 2} = \frac{7!}{5! \cdot 2!} = \frac{7\cdot 6}{2} = \frac{7\cdot3}{1} = 21$

> - Note, this is similar to arrangements of "AAXXXXX", where the two As dictate the segment.

## Some probability rules

$$P(A \text{ and } B) = P(A)\cdot P(B \text{ given } A) $$

> - Events $A$ and $B$ are independent if and only if $P(B \text{ given }A) = P(B)$. So, if $A$ and $B$ are independent, then $P(A \text{ and } B) = P(A)\cdot P(B)$.

$$P(A \text{ or } B) = P(A) +  P(B) - P(A \text{ and } B)$$

> - Events $A$ and $B$ are mutually exclusive if and only if $P(A \text{ and }B) = 0$. So, if $A$ and $B$ are mutually exclusive, then $P(A \text{ or } B) = P(A) + P(B)$.

## Free throws

Jason has an 80% chance to hit each free throw. If Jason shoots 10 free throws, what is the probability Jason makes exactly 8?

> - First, what is the probability Jason makes the first 8 and misses the last two? $$P(1111111100)=\,?$$
> - Each shot is **independent**.
> - $0.8\cdot0.8\cdot0.8\cdot0.8\cdot0.8\cdot0.8\cdot0.8\cdot0.8\cdot0.2\cdot0.2$
> - $P(1111111100) = (0.8)^8(0.2)^2$.
> - What is $P(1110111011)$?
> - $0.8\cdot0.8\cdot0.8\cdot0.2\cdot0.8\cdot0.8\cdot0.8\cdot0.2\cdot0.8\cdot0.8$
> - $P(1110111011) = (0.8)^8(0.2)^2$

## Free throws cont.

Jason has an 80% chance to hit each free throw. If Jason shoots 10 free throws, what is the probability Jason makes exactly 8?

> - Each specific arrangement of 8 1s and 2 0s has the same probability.
> - Each of those compound events is **MUTUALLY EXCLUSIVE**.
> - Thus, we just add up all the probabilities of all the possible ways to make 8 out of 10.
> - How many arrangements of `1111111100` are there?
> - `=COMBIN(10,8)` equals 45.
> - Thus, $P(\text{8 out of 10}) = 45 \cdot (0.8)^8\cdot(0.2)^2 = `r dbinom(8,10,0.8)`$
> - `=BINOMDIST(8,10,0.8,FALSE)` equals `r dbinom(8,10,0.8)`


## Binomial Distribution

In $n$ trials, each attempt has a $p$ chance of success. What is $P(x)$, the probability of getting $x$ successes?

$$P(x) = {n \choose x} p^x (1-p)^{n-x} $$

> - `=BINOMDIST()`

## Binomial Distribution

```{r,echo=F}
x=0:10
P=dbinom(x,10,0.8)
mydf = data.frame(x,P)
colnames(mydf) = c("x","P(x)")
```

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab1, results="asis", echo=F}
knitr::kable(mydf,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


## Cumulative Binomial Distribution Problems

Jason has an 80% chance to hit each free throw. If Jason shoots 10 free throws, what is the probability Jason makes at most 8?

> - `=BINOMDIST(8,10,0.8,TRUE)` = `r pbinom(8,10,0.8)`

Jason has an 80% chance to hit each free throw. If Jason shoots 10 free throws, what is the probability Jason makes less than 8?

> - `=BINOMDIST(7,10,0.8,TRUE)` = `r pbinom(7,10,0.8)`

## Cumulative Binomial Distribution Problems cont.

Jason has an 80% chance to hit each free throw. If Jason shoots 10 free throws, what is the probability Jason makes at least 8?

> - `=1-BINOMDIST(7,10,0.8,TRUE)` = `r 1-pbinom(7,10,0.8)`

Jason has an 80% chance to hit each free throw. If Jason shoots 10 free throws, what is the probability Jason makes more than 8?

> - `=1-BINOMDIST(8,10,0.8,TRUE)` = `r 1-pbinom(8,10,0.8)`



