```{r data generation, echo = FALSE, results = "hide"}
library(MASS)
x = c(0,1,2)
y = c(0,2,1)

abposs = sort(c(1/2,2,-1/2,-2))
params = sample(abposs,4,T)
a = params[1]
b = params[2]
h = params[3]
k = params[4]

if(a<0){
  isrv = " and reflected vertically"
} else {
  isrv = ""
}
if(b<0){
  isrh = " and reflected horizontally"
} else {
  isrh = ""
}
if(h<0){
  lr = "left"
  inside = "+"
} else {
  lr = "right"
  inside = "-"
}
if(k<0){
  ud = "down"
  outside = "-"
} else {
  ud = "up"
  outside = "+"
}

ast = fractions(a)
bst = fractions(b)
hst = fractions(h)
kst = fractions(k)

ans1 = paste0(1*(a==abposs),collapse="")
ans2 = paste0(1*(b==abposs),collapse="")
ans3 = paste0(1*(h==abposs),collapse="")
ans4 = paste0(1*(k==abposs),collapse="")

ans5 = paste0(1*(a==abposs),collapse="")
ans6 = paste0(1*(b==abposs),collapse="")
ans7 = paste0(1*(-h==abposs),collapse="")
ans8 = paste0(1*(k==abposs),collapse="")

abposs1 = c("-2","-1/2","1/2","2")
abposs2 = c("-2","-1/2","+1/2","+2")

al = paste0("* ",abposs1,"\n",collapse="")
ahkex = paste0("* ",abposs2,"\n",collapse="")
```

Question
========

A simple piece-wise function $f$ is plotted below.

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s")
plot(0,0,type="n",xlim=c(-6,6),ylim=c(-6,6),ylab="f(x)",xlab="x")
for(j in seq(-10,10,1)){
  abline(v=j,lty=3)
}
for(j in seq(-10,10,1)){
  abline(h=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,y,col = "blue",lwd=4)
```
\

It's general daughter function, having translations, reflections, and stretches, can be expressed with 4 parameters: $a$, $b$, $h$, and $k$.

$$g(x) = a\, f(b(x-h))+k $$

Compared to the parent function, the daughter is stretched vertically by a factor of $a$, stretched horizontally by a factor of $\frac{1}{b}$, and then shifted (translated) right $h$ and shifted up $k$. 

Notice, a left or down shift gives a negative value for $h$ or $k$. Also, a negative stretch factor causes a reflection.

Each of those four parameters is randomly assigned $2$ or $-2$ or $\frac{1}{2}$ or $-\frac{1}{2}$. Determine the four parameters of the daughter by inspecting the daughter's graph:

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s")
plot(0,0,type="n",xlim=c(-6,6),ylim=c(-6,6),ylab="g(x)",xlab="x")
for(j in seq(-10,10,1)){
  abline(v=j,lty=3)
}
for(j in seq(-10,10,1)){
  abline(h=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,y,col = "blue",lwd=2,lty=3)
lines(x/b+h,a*y+k,col = "red",lwd=4)
legend(3,6,legend = c("f(x)","g(x)"),col=c("blue","red"),lty=c(3,1),lwd=c(2,4),cex=0.7)
```
\

* $a =$ ##ANSWER1##
* $b =$ ##ANSWER2##
* $h =$ ##ANSWER3##
* $k =$ ##ANSWER4##

Also, write the equation to define the daughter.

```{css,echo=F}
.mini select {
    width:5em;
    margin-bottom: 0.5em;
    margin-top: 0.5em;
    margin-right: 0em;
    margin-left: 0.5em;
}
```


<div class="mini">

$g(x) =$ ##ANSWER5## $f($ ##ANSWER6## $(x$ ##ANSWER7## $)$ ##ANSWER8##

</div>

Answerlist
--------
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r ahkex`
`r ahkex`

Solution
========

* The daughter is stretched vertically by a factor of `r abs(a)``r isrv`, so $a=`r a`$.
* The daughter is stretched horizontally by a factor of `r abs(1/b)``r isrh`, so $b=`r b`$.
* The parent's origin (free end of long segment), is shifted to (`r h`, `r k`), so $h=`r h`$ and $k=`r k`$.

When we put those parameters into definition of $g$, we get:
$$g(x) = `r a`\,f(`r b`(x`r inside``r abs(h)`))`r outside``r abs(k)` $$

Personally, I find it most interesting that the horizontal transformations occur **REVERSE** PEMDAS. Most people would guess, using order of operations, that the horizontal translation by $h$ would occur before the horizontal stretch by $\frac{1}{b}$, but this would be wrong. You might remember that applying inverse operations in reverse PEMDAS is what we do to solve equations in Algebra.

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`|`r ans5`|`r ans6`|`r ans7`|`r ans8`
exname: translate_and_stretch