```{r,echo=F,results = "hide"}
while(T){
    xy = sample(-9:9,6)
    x = sort(xy[1:3])
    y = xy[4:6]
    
    xx1 = seq(x[1],x[2],1)
    xx2 = seq(x[2],x[3],1)
    yy1 = (y[2]-y[1])/(x[2]-x[1])*(xx1-x[1])+y[1]
    yy2 = (y[3]-y[2])/(x[3]-x[2])*(xx2-x[2])+y[2]
    xx = c(xx1,xx2)
    yy = c(yy1,yy2)
    
    if(abs(sum(sign(y)))==1 && (sign(y[2])==sign(y[1]) || sign(y[2])==sign(y[3])) && sum(yy==0)==1 && (y[2]==max(y) || y[2]==min(y)) && x[3]-x[1]>4){break}
}

if(y[2]==max(y)){
    mami = "maximum"
    lp = "("
    rp = "]"
    incl = x[1]
    incr = x[2]
    decl = x[2]
    decr = x[3]
    col1 = "orange"
    col1t = rgb(0.4,0.2,0)
    tex1 = "increasing"
    col2 = rgb(0,0.6,1)
    col2t = rgb(0,0.1,0.5)
    tex2 = "decreasing"
    yy1 = 9.5
    yy2 = -9.5
}
if(y[2]==min(y)){
    mami = "minimum"
    lp = "["
    rp = ")"
    incl = x[2]
    incr = x[3]
    decl = x[1]
    decr = x[2]
    col2 = "orange"
    col2t = rgb(0.4,0.2,0)
    tex2 = "increasing"
    col1 = rgb(0,0.6,1)
    col1t = rgb(0,0.1,0.5)
    tex1 = "decreasing"
    yy1 = -9.5
    yy2 = 9.5
}

posl = min(xx[yy>=0])
posr = max(xx[yy>=0])
negl = min(xx[yy<=0])
negr = max(xx[yy<=0])

doml = x[1]
domr = x[3]
ranl = min(y)
ranr = max(y)

relx = x[2]
rely = y[2]

ach = -9:9
al = paste0("* ",ach,collapse="\n")

sols = c(posl,posr,
         negl,negr,
         incl,incr,
         decl,decr,
         doml,domr,
         ranl,ranr,
         relx,rely)

fal = paste0(rep(al,length(sols)),collapse="\n")

sol = character()
for(ss in sols){
    sol = c(sol,paste0(1*(ach==ss),collapse=""))
}

fsol = paste0(sol,collapse="|")

```


Question
========

The graph of $y=f(x)$ is shown below.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(xx,yy,"l",xlim=c(-10,10),ylim=c(-10,10))

for(i in -10:10){
    if(i%%5==0){
        abline(h=i,col="darkgrey",lwd=1.2)
        abline(v=i,col="darkgrey",lwd=1.2)
    } else {
        abline(h=i,col="lightgrey",lwd=0.8)
        abline(v=i,col="lightgrey",lwd=0.8)
    }
}
for(i in seq(-10,10,5)){
    abline(h=i,col="darkgrey",lwd=1.2)
    abline(v=i,col="darkgrey",lwd=1.2)
}

arrows(-10.3,0,10.3,0,0.1,10,3,lwd=3)
arrows(0,-10.3,0,10.3,0.1,10,3,lwd=3)
text(10,-0.5,10,cex=0.7)
text(-10,-0.5,-10,cex=0.7)
text(-0.5,10,10,cex=0.7)
text(-0.5,-10,-10,cex=0.7)
text(10,0.5,"x",cex=0.7)
text(0.5,10,"y",cex=0.7)

lines(xx,yy,lwd=4,col="blue")
points(x,y,pch=20,col="blue",cex=1.6)
points(x[c(1,3)],y[c(1,3)],pch=20,col="white",cex=0.9)
# points(x,y,pch=20,col="white")

```
\

```{css,echo=F}
.smallsel select {
    width: 5em;
    margin: 0.5em;
}
```

<div class="smallsel">

Using [interval notation](https://en.wikipedia.org/wiki/Interval_(mathematics)#Notations_for_intervals), indicate the following:

1. For what values of $x$ is the function's output positive? (Where is $f(x)>0$?)
* (##ANSWER1##, ##ANSWER2##)
2. For what values of $x$ is the function's output negative? (Where is $f(x)<0$?)
* (##ANSWER3##, ##ANSWER4##)
3. For what values of $x$ is the function increasing?
* (##ANSWER5##, ##ANSWER6##)
4. For what values of $x$ is the function decreasing?
* (##ANSWER7##, ##ANSWER8##)
5. What is the domain of $f$? (For what values of $x$ does $f$ exist?)
* (##ANSWER9##, ##ANSWER10##)
6. What is the range of $f$? (For what values of $y$ does $f$ exist?)
* `r lp`##ANSWER11##, ##ANSWER12##`r rp`

Now, using a [Cartesian coordinate](https://en.wikipedia.org/wiki/Cartesian_coordinate_system), indicate the location of the local `r mami`.

7. The location of the local `r mami` is (##ANSWER13##, ##ANSWER14##).

</div>

Answerlist
--------

`r fal`


Solution
========

1. Interval where $f$ is positive = (`r posl`, `r posr`)
2. Interval where $f$ is negative = (`r negl`, `r negr`)
3. Interval where $f$ is increasing = (`r incl`, `r incr`)
4. Interval where $f$ is decreasing = (`r decl`, `r decr`)
5. Domain = (`r doml`, `r domr`)
6. Range = `r lp``r ranl`, `r ranr``r rp`
7. Point of relative `r mami` = (`r relx`, `r rely`)


```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(xx,yy,"l",xlim=c(-10,10),ylim=c(-10,10))

polygon(c(min(xx[yy>=0]),xx[yy>=0],max(xx[yy>=0])),c(0,yy[yy>=0],0),lwd=4,col=rgb(0.5,1,0.5),border=NA)
polygon(c(min(xx[yy<=0]),xx[yy<=0],max(xx[yy<=0])),c(0,yy[yy<=0],0),lwd=4,col=rgb(1,0.5,0.7),border=NA)

for(i in -10:10){
    if(i%%5==0){
        abline(h=i,col="darkgrey",lwd=1.2)
        abline(v=i,col="darkgrey",lwd=1.2)
    } else {
        abline(h=i,col="lightgrey",lwd=0.8)
        abline(v=i,col="lightgrey",lwd=0.8)
    }
}
for(i in seq(-10,10,5)){
    abline(h=i,col="darkgrey",lwd=1.2)
    abline(v=i,col="darkgrey",lwd=1.2)
}

arrows(-10.3,0,10.3,0,0.1,10,3,lwd=3)
arrows(0,-10.3,0,10.3,0.1,10,3,lwd=3)
text(10,-0.5,10,cex=0.7)
text(-10,-0.5,-10,cex=0.7)
text(-0.5,10,10,cex=0.7)
text(-0.5,-10,-10,cex=0.7)
text(10,0.5,"x",cex=0.7)
text(0.5,10,"y",cex=0.7)

lines(x[c(1,2)],y[c(1,2)],lwd=6,col="black")
lines(x[c(1,2)],y[c(1,2)],lwd=3,col=col1)
lines(x[c(2,3)],y[c(2,3)],lwd=6,col="black")
lines(x[c(2,3)],y[c(2,3)],lwd=3,col=col2)

lines(c(min(xx[yy>=0]),max(xx[yy>=0])),c(10.5,10.5),lwd=10,col=rgb(0.5,1,0.5),lend=3)
text(mean(c(min(xx[yy>=0]),max(xx[yy>=0]))),10.5,"positive",col=rgb(0,0.5,0))
lines(c(min(xx[yy<=0]),max(xx[yy<=0])),c(-10.5,-10.5),lwd=10,col=rgb(1,0.5,0.7),lend=3)
text(mean(c(min(xx[yy<=0]),max(xx[yy<=0]))),-10.5,"negative",col=rgb(0.5,0,0.2))
lines(x[c(1,2)],c(yy1,yy1),lwd=10,col=col1,lend=3)
text(mean(x[c(1,2)]),yy1,tex1,col=col1t)
lines(x[c(2,3)],c(yy2,yy2),lwd=10,col=col2,lend=3)
text(mean(x[c(2,3)]),yy2,tex2,col=col2t)

points(x,y,pch=20,col="blue",cex=1.6)
points(x[c(1,3)],y[c(1,3)],pch=20,col="white",cex=0.9)
# points(x,y,pch=20,col="white")


text(x,-0.5,x,cex=0.9)

text(xx[yy==0],-0.5,xx[yy==0],cex=0.9)

```
\


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",length(sols)),collapse="|")`
exsolution: `r fsol`
exname: intervals_check