```{r data generation, echo = FALSE}
dafracs = list(c(1,2),c(3,2),c(5,2),c(7,2),c(9,2),
               c(1,3),c(2,3),c(4,3),c(5,3),c(7,3),c(8,3),
               c(1,4),c(3,4),c(5,4),c(7,4),c(9,4),
               c(1,5),c(2,5),c(3,5),c(4,5),c(6,5),c(7,5),c(8,5),c(9,5),
               c(1,6),c(5,6),c(7,6),
               c(1,7),c(2,7),c(3,7),c(4,7),c(5,7),c(6,7),c(8,7),c(9,7),
               c(1,8),c(3,8),c(5,8),c(7,8),c(9,8),
               c(1,9),c(2,9),c(4,9),c(5,9),c(7,9),c(8,9))

fi = sample(1:length(dafracs),3)
mult = sample(2:9,3,T)
sgn = sample(c(-1,1),3,T)
f1 = dafracs[[fi[1]]]
f2 = dafracs[[fi[2]]]
f3 = dafracs[[fi[3]]]
dy1 = f1[1]*mult[1]*sample(c(-1,1),1)
dy2 = f2[1]*mult[2]*sample(c(-1,1),1)
dy3 = f3[1]*mult[3]*sample(c(-1,1),1)
w1 = f1[2]*mult[1]
w2 = f2[2]*mult[2]
w3 = f3[2]*mult[3]

while(T){
    x1l = sample(11:99,1)
    x1r = x1l+w1
    x2l = sample(11:99,1)
    x2r = x2l+w2
    x3l = sample(11:99,1)
    x3r = x3l+w3
    xa = c(x1l,x1r,x2l,x2r,x3l,x3r)
    xs = unique(xa)
    if(max(xs)<100 && length(xs)<6){break}
}

while(T){
    y1l = sample(11:99,1)
    y1r = y1l+dy1
    y2l = sample(11:99,1)
    y2r = y2l+dy2
    y3l = sample(11:99,1)
    y3r = y3l+dy3
    ya = c(y1l,y1r,y2l,y2r,y3l,y3r)
    ys = unique(ya)
    if(max(ys)<100 && min(ys)>0){break}
}

while(length(xs)<10){
    xs = sort(unique(c(xs,sample(11:99,1))))
}

f = sample(11:99,10,T)
g = sample(11:99,10,T)
h = sample(11:99,10,T)

for(i in 1:10){
    x = xs[i]
    if(x==x1l){
        f[i] = y1l
    }
    if(x==x1r){
        f[i] = y1r
    }
    if(x==x2l){
        g[i] = y2l
    }
    if(x==x2r){
        g[i] = y2r
    }
    if(x==x3l){
        h[i] = y3l
    }
    if(x==x3r){
        h[i] = y3r
    }
}

mytab = data.frame(xs,f,g,h)
colnames(mytab) = c("t","f(t)","g(t)","h(t)")

numch = c(-9:-1,1:9)
dench = 1:9

sol1 = paste0(1*(f1[1]*sign(dy1)==numch),collapse="")
sol2 = paste0(1*(f1[2]==dench),collapse="")
sol3 = paste0(1*(f2[1]*sign(dy2)==numch),collapse="")
sol4 = paste0(1*(f2[2]==dench),collapse="")
sol5 = paste0(1*(f3[1]*sign(dy3)==numch),collapse="")
sol6 = paste0(1*(f3[2]==dench),collapse="")

al1 = paste0("* ",numch,collapse="\n")
al2 = paste0("* ",dench,collapse="\n")

```


Question
========

Three functions vary in time as shown in the table below.

```{css,echo=F}
.tabl td {
  border: 1px solid black;
  text-align: center;
  padding: 15px;
  margin: 1em;
}
.tabl th {
  border: 2px solid black;
  border-bottom: 2px solid black;
  text-align: center;
  background-color: #227;
  padding: 15px;
  color: white;
}
```

<div class="tabl">

```{r,echo=F}
kableExtra::kable(mytab)
```

</div>

```{css,echo=F}
.frac table {
    width: 4em;
    background-color: #FFF;
}
.frac td {
  border: 0px;
  text-align: center;
  padding: 0px;
  margin: 0em;
  background-color: #FFF;
}
.frac th {
  border-bottom: 2px solid black;
  text-align: center;
  padding: 0px;
  margin: 0em;
  background-color: #FFF;
}
```

1. Find the average rate of change of function $f$ between $t=`r x1l`$ and $t=`r x1r`$. Express your answer as a fraction in reduced form.

<div class="frac">
| ##ANSWER1## |
|:---:|
| ##ANSWER2## |
</div>


2. Find the average rate of change of function $g$ between $t=`r x2l`$ and $t=`r x2r`$. Express your answer as a fraction in reduced form.

<div class="frac">
| ##ANSWER3## |
|:---:|
| ##ANSWER4## |
</div>


3. Find the average rate of change of function $h$ between $t=`r x3l`$ and $t=`r x3r`$. Express your answer as a fraction in reduced form.

<div class="frac">
| ##ANSWER5## |
|:---:|
| ##ANSWER6## |
</div>

Answerlist
--------

`r al1`
`r al2`
`r al1`
`r al2`
`r al1`
`r al2`


Solution
========

1. The average rate of change of function $f$ between $t=`r x1l`$ and $t=`r x1r`$ =

$$\frac{f(`r x1r`)-f(`r x1l`)}{`r x1r`-`r x1l`}~=~\frac{`r y1r`-`r y1l`}{`r x1r`-`r x1l`} ~=~ \frac{`r y1r-y1l`}{`r x1r-x1l`} ~=~ \frac{`r f1[1]*sign(dy1)`}{`r f1[2]`}$$

2. The average rate of change of function $g$ between $t=`r x2l`$ and $t=`r x2r`$ =

$$\frac{g(`r x2r`)-g(`r x2l`)}{`r x2r`-`r x2l`}~=~\frac{`r y2r`-`r y2l`}{`r x2r`-`r x2l`} ~=~ \frac{`r y2r-y2l`}{`r x2r-x2l`} ~=~ \frac{`r f2[1]*sign(dy2)`}{`r f2[2]`}$$

3. The average rate of change of function $h$ between $t=`r x3l`$ and $t=`r x3r`$ =

$$\frac{h(`r x3r`)-h(`r x3l`)}{`r x3r`-`r x3l`}~=~\frac{`r y3r`-`r y3l`}{`r x3r`-`r x3l`} ~=~ \frac{`r y3r-y3l`}{`r x3r-x3l`} ~=~ \frac{`r f3[1]*sign(dy3)`}{`r f3[2]`}$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`|`r sol6`
exname: aroc_table