```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

while(T){
    degcuts = c(0,sample(seq(5,175,5),2),180)
    degs = diff(sort(degcuts))
    degs = sample(degs)
    Ad = degs[1]
    Bd = degs[2]
    Cd = degs[3]
    A = Ad/180*pi
    B = Bd/180*pi
    C = Cd/180*pi
    pA = c(0,0)
    pB = c(1,0)
    c = 1
    b = c*sin(B)/sin(C)
    a = c*sin(A)/sin(C)
    pC = c(b*cos(A),b*sin(A))
    throt = runif(1,0,2*pi)
    prA = c(cos(throt)*pA[1]-sin(throt)*pA[2],sin(throt)*pA[1]+cos(throt)*pA[2])
    prB = c(cos(throt)*pB[1]-sin(throt)*pB[2],sin(throt)*pB[1]+cos(throt)*pB[2])
    prC = c(cos(throt)*pC[1]-sin(throt)*pC[2],sin(throt)*pC[1]+cos(throt)*pC[2])
    xs = c(prA[1],prB[1],prC[1])
    ys = c(prA[2],prB[2],prC[2])
    xwid = (max(xs)-min(xs))/2
    ywid = (max(ys)-min(ys))/2
    xmid = mean(c(max(xs),min(xs)))
    ymid = mean(c(max(ys),min(ys)))
    wid = max(c(xwid,ywid))
    dt = 0.4*wid
    rtA = dt/A
    rtB = dt/B
    rtC = dt/C/2
    ptA = c(rtA*cos(A/2),rtA*sin(A/2))
    ptB = c(1+rtB*cos(pi-B/2),rtB*sin(pi-B/2))
    th1 = atan2(pA[2]-pC[2],pA[1]-pC[1])
    th2 = atan2(pB[2]-pC[2],pB[1]-pC[1])
    th3 = mean(c(th1,th2))
    ptC = pC+c(rtC*cos(th3),rtC*sin(th3))
    ptA = c(cos(throt)*ptA[1]-sin(throt)*ptA[2],sin(throt)*ptA[1]+cos(throt)*ptA[2])
    ptB = c(cos(throt)*ptB[1]-sin(throt)*ptB[2],sin(throt)*ptB[1]+cos(throt)*ptB[2])
    ptC = c(cos(throt)*ptC[1]-sin(throt)*ptC[2],sin(throt)*ptC[1]+cos(throt)*ptC[2])
    
    Arnum = Ad
    Arden = 180
    gg = gcd(c(Arnum,Arden))
    Arnum = round(Arnum/gg)
    Arden = round(Arden/gg)
    
    Brnum = Bd
    Brden = 180
    gg = gcd(c(Brnum,Brden))
    Brnum = round(Brnum/gg)
    Brden = round(Brden/gg)
    
    Crnum = Cd
    Crden = 180
    gg = gcd(c(Crnum,Crden))
    Crnum = round(Crnum/gg)
    Crden = round(Crden/gg)
    
    texA = paste0("\\frac{",Arnum,"\\pi}{",Arden,"}",collapse="")
    if(Arnum==1){
        texA = paste0("\\frac{\\pi}{",Arden,"}",collapse="")
    }
    texB = paste0("\\frac{",Brnum,"\\pi}{",Brden,"}",collapse="")
    if(Brnum==1){
        texB = paste0("\\frac{\\pi}{",Brden,"}",collapse="")
    }
    texC = paste0("\\frac{",Crnum,"\\pi}{",Crden,"}",collapse="")
    if(Crnum==1){
        texC = paste0("\\frac{\\pi}{",Crden,"}",collapse="")
    }
    if(min(degs)>1 && length(unique(c(a,b,c)))==3 && Arden>1 && Brden>1 && Crden>1 && length(unique(c(Arden,Brden,Crden)))==3){break}
}

ach1 = paste0(1:36,"π")
ach2 = c(2,3,4,6,9,12,18,36)

ach1[1] = "π"

al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")

sol1 = paste0(1*(1:36==Crnum),collapse="")
sol2 = paste0(1*(ach2==Crden),collapse="")

```

Question
========

A triangle is drawn. Two of the interior angle measures are known to be $`r texA`$ and $`r texB`$. Find the third interior angle measure in radians.


* ##ANSWER1## / ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`


Solution
========

The interior angle measures sum to $\pi$ radians (because $\pi$ radians equals 180°). The unknown angle measure can be found by subtracting the other two angles from $\pi$.

$$\pi-`r texA`-`r texB`$$

```{r,echo=F}
gg = gcd(c(Arden,Brden))
lcm = Arden*Brden/gg
mA = lcm/Arden
mB = lcm/Brden

```



Find the least common denominator. The least common multiple of `r Arden` and `r Brden` is `r Arden*Brden/gcd(c(Arden,Brden))`.

$$\frac{`r lcm`\pi}{`r lcm`}-\frac{`r mA*Arnum`\pi}{`r mA*Arden`}-\frac{`r mB*Brnum`\pi}{`r mB*Brden`}$$

With common denominators, we can simply subtract the numerators.


$$\frac{`r lcm`\pi-`r mA*Arnum`\pi-`r mB*Brnum`\pi}{`r lcm`}$$

Subtract.

$$\frac{`r lcm-mA*Arnum-mB*Brnum`\pi}{`r lcm`}$$

Simplify (if necessary)

$$`r texC`$$






Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: triangle_3rd_angle_rad