```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

deg1 = sample(c(seq(15,75,5),seq(18,72,9)),1)
deg2 = 90-deg1

radnum1 = deg1
radden1 = 180
gg = gcd(c(radnum1,radden1))
radnum1 = round(radnum1/gg)
radden1 = round(radden1/gg)
radtex1 = paste0("\\frac{",radnum1,"\\pi}{",radden1,"}")
if(radnum1==1){
    radtex1 = paste0("\\frac{\\pi}{",radden1,"}")
}

radnum2 = deg2
radden2 = 180
gg = gcd(c(radnum2,radden2))
radnum2 = round(radnum2/gg)
radden2 = round(radden2/gg)
radtex2 = paste0("\\frac{",radnum2,"\\pi}{",radden2,"}")
if(radnum2==1){
    radtex2 = paste0("\\frac{\\pi}{",radden2,"}")
}

ach1 = paste0(1:36,"π")
ach2 = 3:36

ach1[1] = "π"

al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")

sol1 = paste0(1*(1:36==radnum2),collapse="")
sol2 = paste0(1*(ach2==radden2),collapse="")

```

Question
========

A right triangle is drawn such that its hypotenuse connects the origin to the edge of the unit circle (which is centered at the origin) in the first quadrant. The acute angle at the origin has a measure of $`r radtex1`$. What is the measure, in radians, of the other acute angle of the right triangle?

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
dd = 1.2
plot(0,0,"n",xlim=c(-dd,dd),ylim=c(-dd,dd),axes=F,ann=F)
for(i in seq(-dd,dd,0.1)){
    lines(c(i,i),c(-dd,dd),col="grey",lwd=0.5)
    lines(c(-dd,dd),c(i,i),col="grey",lwd=0.5)
}
for(i in seq(-1,1,1)){
    lines(c(i,i),c(-dd,dd),col="darkgrey",lwd=1)
    lines(c(-dd,dd),c(i,i),col="darkgrey",lwd=1)
}
arrows(-dd*1.04,0,dd*1.04,0,0.1,10,3,lwd=3,col="darkgrey")
arrows(0,-dd*1.04,0,dd*1.04,0.1,10,3,lwd=3,col="darkgrey")
text(1.02,-0.04,"1")
text(-0.03,1.03,"1")
text(1.17,-0.04,"x")
text(-0.03,1.17,"y")

th = seq(0,2*pi,pi/360)
lines(cos(th),sin(th))

rad1 = deg1*pi/180

polygon(c(0,cos(rad1),cos(rad1)),c(0,sin(rad1),0),border="black",lwd=2)
db = 0.04
lines(c(cos(rad1)-db,cos(rad1)-db,cos(rad1)),
      c(0,db,db))


rl1 = 0.15/rad1
drl = 0.02
th2 = seq(0,rad1,pi/360)
lines((rl1-drl)*cos(th2),(rl1-drl)*sin(th2),col="red",lwd=2)
text(rl1*cos(rad1/2),rl1*sin(rad1/2),TeX(radtex1),col="red",srt=deg1/2,adj=c(0,0.5),cex=0.5)

rad2 = deg2*pi/180
th3 = seq(3*pi/2-rad2,3*pi/2,pi/360)
lines(cos(rad1)+0.1*cos(th3),sin(rad1)+0.1*sin(th3),col="blue",lwd=2)
text(cos(rad1)+0.2*cos(-pi/2-rad2/2),
     sin(rad1)+0.2*sin(-pi/2-rad2/2),"?",col="blue")


```
\

* ##ANSWER1## / ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`




Solution
========

The interior angle measures sum to $\pi$ radians (because $\pi$ radians equals 180°). The unknown angle measure can be found by subtracting the other two angles from $\pi$. The right angle has a measure of $\frac{\pi}{2}$.

$$\pi-`r radtex1`-\frac{\pi}{2}$$

```{r,echo=F}
gg = gcd(c(radden1,2))
lcm = radden1*2/gg
mA = lcm/radden1
mB = lcm/2

```



Find the least common denominator. The least common multiple of `r radden1` and `r 2` is `r lcm`.

$$\frac{`r lcm`\pi}{`r lcm`}-\frac{`r mA*radnum1`\pi}{`r mA*radden1`}-\frac{`r mB`\pi}{`r mB*2`}$$

With common denominators, we can simply subtract the numerators.


$$\frac{`r lcm`\pi-`r mA*radnum1`\pi-`r mB`\pi}{`r lcm`}$$

Subtract.

$$\frac{`r lcm-mA*radnum1-mB`\pi}{`r lcm`}$$

Simplify (if necessary)

$$`r radtex2`$$






Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: right_tri_complems_rad