```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
deg = sample(c(90,180,270),1)+sample(20:70,1)
if(deg>90 && deg<180){
    ref = 180-deg
    deg2 = 180
} else if(deg>180 && deg<270){
    ref = deg-180
    deg2 = 180
} else if(deg>270 && deg<360){
    ref = 360-deg
    deg2 = 360
} else {
    ref = -666
    deg2 = 666
}

rad = deg/180*pi
rad2 = deg2/180*pi

```

Question
========

A unit circle was drawn centered at the origin. An initial ray was drawn from the origin through point (1,0). A terminal ray was drawn `r deg`° counterclockwise from the initial ray.

From the intersection of the circle and the terminal ray, a vertical line segment was drawn. Using the three vertices of intersection between the terminal ray, the vertical line, and the $x$-axis, a right triangle was drawn.

The resulting right triangle has an acute angle at the origin. The measure of this acute angle is called a [reference angle](https://math.libretexts.org/Courses/Cosumnes_River_College/Math_373%3A_Trigonometry_for_Calculus/04%3A_Radian_Measure_and_the_Circular_Functions/4.01%3A_Reference_Angles). Find the measure, **in degrees**, of the reference angle.


```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
arrows(-1.2,0,1.2,0,0.1,20,0,lwd=1)
arrows(0,-1.2,0,1.2,0.1,20,0,lwd=1)
arrows(0,0,1.2,0,0.1,20,lwd=2)
text(1.1,-0.03,"x")
text(-0.03,1.1,"y")
th = seq(0,2*pi,pi/360)
lines(cos(th),sin(th))
arrows(0,0,1.2*cos(rad),1.2*sin(rad),0.1,20,lwd=2)
abline(v=cos(rad),lty=2,lwd=0.5)
polygon(c(0,cos(rad),cos(rad)),c(0,sin(rad),0),lwd=3,border="purple")
th2 = seq(0,rad,pi/360)
n = length(th2)
lines(0.2*cos(th2),0.2*sin(th2),col="red",lwd=2)
arrows(0.2*cos(th2[n-1]),0.2*sin(th2[n-1]),0.2*cos(th2[n]),0.2*sin(th2[n]),0.1,20,col="red",lwd=2)
text(0.3*cos(rad/2),0.3*sin(rad/2),paste0(deg,"°",collapse=""),col="red")

th3 = seq(rad,rad2,sign(rad2-rad)*pi/360)
lines(0.25*cos(th3),0.25*sin(th3),col="blue",lwd=2)
text(0.35*cos(mean(th3)),0.35*sin(mean(th3)),"?",col="blue")

```
\




Solution
========




Meta-information
============
extype: num
exsolution: 
exname: reference_angle_deg