```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

bas = c(0,90,180,270)
while(T){
    q = sample(2:4,1)
    d = bas[q]+sample(20:70,1)
    grn = d # given's radian numerator number
    grd = 180 # given's radian denominator
    gg = gcd(c(grn,grd))
    grn = round(grn/gg)
    grd = round(grd/gg)
    gtex = paste0("\\frac{",grn,"\\pi}{",grd,"}",collapse="")
    gr = grn*pi/grd
    if(q==2){
        rd = 180-d
        a1 = pi
        quad = "II"
    } else if(q==3){
        rd = d-180
        a1 = pi
        quad = "III"
    } else if(q==4){
        rd = 360-d
        a1 = 2*pi
        quad = "IV"
    }
    rrn = rd
    rrd = 180
    gg = gcd(c(rrn,rrd))
    rrn = round(rrn/gg)
    rrd = round(rrd/gg)
    rr = rrn*pi/rrd
    rtex = paste0("\\frac{",rrn,"\\pi}{",rrd,"}",collapse="")
    if(grd<=36 && rrd<=36 && rrn>=2){break}
}

ach1 = paste0(1:18,"π")
ach1[1] = "π"
ach2 = 2:36

al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")

sol1 = paste0(1*(1:18==rrn),collapse="")
sol2 = paste0(1*(ach2==rrd),collapse="")

```

Question
========

Find the reference angle, **in radians**, corresponding to a given angle of $`r gtex`$.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
arrows(-1.2,0,1.2,0,0.1,20,0,lwd=1)
arrows(0,-1.2,0,1.2,0.1,20,0,lwd=1)
arrows(0,0,1.2,0,0.1,20,lwd=2)
text(1.1,-0.03,"x")
text(-0.03,1.1,"y")
th = seq(0,2*pi,pi/360)
lines(cos(th),sin(th))
rad = gr
arrows(0,0,1.2*cos(rad),1.2*sin(rad),0.1,20,lwd=2)
abline(v=cos(rad),lty=2,lwd=0.5)
polygon(c(0,cos(rad),cos(rad)),c(0,sin(rad),0),lwd=3,border="purple")
bm = 0.04
lines(c(cos(rad)-bm*sign(cos(rad)),cos(rad)-bm*sign(cos(rad)),cos(rad)),c(0,bm,bm)*sign(sin(rad)),col="purple")
th2 = seq(0,rad,pi/360)
n = length(th2)
lines(0.2*cos(th2),0.2*sin(th2),col="red",lwd=2)
arrows(0.2*cos(th2[n-1]),0.2*sin(th2[n-1]),0.2*cos(th2[n]),0.2*sin(th2[n]),0.1,20,col="red",lwd=2)
text(0.3*cos(rad/2),0.3*sin(rad/2),TeX(gtex),col="red")
rad2 = a1
th3 = seq(rad,rad2,sign(rad2-rad)*pi/360)
lines(0.25*cos(th3),0.25*sin(th3),col="blue",lwd=2)
text(0.35*cos(mean(th3)),0.35*sin(mean(th3)),"?",col="blue")

```
\

* ##ANSWER1##/##ANSWER2##

Answerlist
--------

`r al1`
`r al2`


Solution
========

The process depends on the quadrant. Let's call the given angle measure "$g$" and the reference angle measure "$r$".

* If the terminal side (terminal ray) is in quadrant I, then $r=g$.
* If the terminal side (terminal ray) is in quadrant II, then $r=\pi-g$.
* If the terminal side (terminal ray) is in quadrant III, then $r=g-\pi$.
* If the terminal side (terminal ray) is in quadrant IV, then $r=2\pi-g$.

The given angle is in quadrant `r quad`.

```{r,echo=F}
if(q==2){
    t1a = "\\pi"
    t2a = gtex
    t1b = paste0("\\frac{",grd,"\\pi}{",grd,"}",collapse="")
    t2b = gtex
}
if(q==3){
    t1a = gtex
    t2a = "\\pi"
    t1b = gtex
    t2b = paste0("\\frac{",grd,"\\pi}{",grd,"}",collapse="")
}
if(q==4){
    t1a = "2\\pi"
    t2a = gtex
    t1b = paste0("\\frac{",2*grd,"\\pi}{",grd,"}",collapse="")
    t2b = gtex
}
eq1 = paste0("r=",t1a,"-",t2a,collapse="")
eq2 = paste0("r=",t1b,"-",t2b,collapse="")
eq3 = paste0("r=",rtex,collapse="")
```

$$`r eq1`$$

Get a common denominator.

$$`r eq2`$$

Subtract the fractions.

$$`r eq3`$$

The reference angle is $`r rtex`$.





Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: reference_angle_rad