```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
options(scipen=99)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

while(T){
    c = sample(2:40,1)
    b = sample(c(1,2,3,5,6,7,10,11,13,14,15,17,19,21,22,23,26,29,30,31,33,34,35,37,38,39),1)
    a = sample(1:20,1)
    gg = gcd(c(a,c))
    a = round(a/gg)
    c = round(c/gg)
    sn = a^2*b
    sd = c^2
    asn = c^2-a^2*b
    lsf = 1
    for(i in 1:49){
        if(asn%%(i^2)==0){
            lsf = i
        }
    }
    aa = lsf
    bb = round(asn/lsf^2)
    cc = c
    if((a^2*b)<(c^2) && max(c(aa,bb,cc))<40 && a>1 && aa>1 && b>1 && bb>1){break}
}

gtex = paste0("\\frac{",a,"\\sqrt{",b,"}}{",c,"}")
if(a == 1){
    gtex = paste0("\\frac{\\sqrt{",b,"}}{",c,"}")
}
if(b == 1){
    gtex = paste0("\\frac{",a,"}{",c,"}")
}
atex = paste0("\\frac{",aa,"\\sqrt{",bb,"}}{",cc,"}")
if(aa == 1){
    atex = paste0("\\frac{\\sqrt{",bb,"}}{",cc,"}")
}
if(bb == 1){
    atex = paste0("\\frac{",aa,"}{",cc,"}")
}

y = a*sqrt(b)/c
x = aa*sqrt(bb)/cc

ach = 1:40
al = paste0("* ",ach,collapse="\n")
sol1 = paste0(1*(ach==aa),collapse="")
sol2 = paste0(1*(ach==bb),collapse="")
sol3 = paste0(1*(ach==cc),collapse="")

primes = c(2, 3, 5, 7, 11, 13, 17, 19, 23, 29, 31, 37, 41, 43, 47, 53, 59, 61, 67, 71, 73, 79, 83, 89, 97)

```

Question
========

A right triangle is drawn with a hypotenuse of length 1 and a leg of length $`r gtex`$. The other leg is of length $x$.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-0.1,1.2),ylim=c(-0.1,1.2))
arrows(-0.1,0,1.2,0,0.1,20,lwd=2)
arrows(0,-0.1,0,1.2,0.1,20,lwd=2)
th = seq(0,2*pi,pi/360)
lines(cos(th),sin(th),col="darkgrey")
polygon(c(0,x,x),c(0,0,y),border="purple",lwd=3)
bmp = 0.03
polygon(c(x-bmp,x-bmp,x,x),c(0,bmp,bmp,0),border="purple")
ang = atan(y/x)
text(x/2,y/2,"1",srt=ang*180/pi,adj=c(0.5,-0.3),cex=2,col="purple")
text(x,y/2,TeX(gtex),adj=c(-0.2),col="purple")
text(x/2,0,"x",adj=c(0.5,1.5),col="purple",cex=2)

```
\


The other leg can be expressed as a fraction of a radical.

$$x~=~\frac{a\sqrt{b}}{c}$$

where $a$, $b$, and $c$ are positive integers. Find the length of the other leg. Express the length exactly by stating the values of $a$, $b$, and $c$.

* $a=$ ##ANSWER1##
* $b=$ ##ANSWER2##
* $c=$ ##ANSWER3##

Answerlist
--------

`r al`
`r al`
`r al`



Solution
========

Use the [Pythagorean Theorem](https://en.wikipedia.org/wiki/Pythagorean_theorem).

$$\left(`r gtex`\right)^2+x^2~=~1^2$$



When a product (or quotient) is raised to a power, the power can be distributed to the factors. If there was addition (or subtraction) in the fraction, then this would be more complicated. Also, $1^2=1$.

$$\frac{`r a`^2\cdot `r b`}{`r c`^2}+x^2~=~1$$

Evaluate the numerator and denominator.


$$\frac{`r a^2*b`}{`r c^2`}+x^2~=~1$$

Subtract $\frac{`r a^2*b`}{`r c^2`}$ from both sides.


$$x^2~=~1-\frac{`r a^2*b`}{`r c^2`}$$

Get a common denominator by recognizing that $1=\frac{`r c^2`}{`r c^2`}$.


$$x^2~=~\frac{`r c^2`}{`r c^2`}-\frac{`r a^2*b`}{`r c^2`}$$

In general, $\frac{m}{d}-\frac{n}{d}\equiv \frac{m-n}{d}$, for any $m,n,d$; that's the reason we got a common denominator in the first place.

$$x^2~=~\frac{`r c^2`-`r a^2*b`}{`r c^2`}$$

Simplify the numerator.


$$x^2~=~\frac{`r c^2-a^2*b`}{`r c^2`}$$

Take the square root of both sides. We are confident that we are looking for a positive value of $x$, so we do not need to consider the negative square root.


$$x~=~\sqrt{\frac{`r c^2-a^2*b`}{`r c^2`}}$$

Since a square-root radical is equivalent to raising to the power of 1/2, we can again distribute this power to the factors of the quotient.

$$x~=~\frac{\sqrt{`r c^2-a^2*b`}}{\sqrt{`r c^2`}}$$

The denominator is easy to simplify, because $\sqrt{`r c^2`}=`r c`$.


$$x~=~\frac{\sqrt{`r c^2-a^2*b`}}{`r c`}$$

The numerator is a bit trickier to simplify. We need to find the largest perfect-square factor of `r c^2-a^2*b`. Personally, I'd do this by making a [factor tree](https://en.wikipedia.org/wiki/Integer_factorization#Prime_decomposition) using an algorithm based on [the simplest primality test](https://en.wikipedia.org/wiki/Primality_test#Simple_methods), which involves using [trial division](https://en.wikipedia.org/wiki/Trial_division). Specifically, in this case, I'd start by trying to divide `r c^2-a^2*b` by all [primes](https://en.wikipedia.org/wiki/Prime_number) less than $\sqrt{`r c^2-a^2*b`}\approx `r sqrt(c^2-a^2*b)`$. So, I'd try to divide `r c^2-a^2*b` by all the numbers in this list: `r primes[primes<sqrt(c^2-a^2*b)]`. 

```{r,echo=F}
fac = 1
cab = c^2-a^2*b
for(pr in primes){
    if(cab%%pr==0){
        fac = pr
        break
    }
}
cab2 = round(cab/fac)
```

After a bit of work, you could find that `r fac` is a factor of `r cab`.


$$x~=~\frac{\sqrt{`r fac`\cdot`r cab2`}}{`r c`}$$

We can now repeat that strategy with the non-prime factor until we have only prime factors.

```{r,echo=F,results='asis'}
cab3 = cab2
facs = c(fac)
done = FALSE
while(!(done)){
    done = TRUE
    for(pr in primes[primes<=sqrt(cab3)]){
        if(cab3%%pr==0){
            facs = c(facs,pr)
            cab3 = round(cab3/pr)
            cat("$$x=\\frac{\\sqrt{",paste0(facs,collapse="\\cdot"),"\\cdot",cab3,"}}{",c,"}$$\n\n")
            done = FALSE
            break
        }
    }
}

ufs = unique(c(facs,cab3))
afs = numeric()
bfs = numeric()
for(uf in ufs){
    n = sum(uf==c(facs,cab3))
    na = n %/% 2
    nb = n %% 2
    afs = c(afs,rep(uf,na))
    bfs = c(bfs,rep(uf,nb))
}

ugh = character()
for(i in afs){
    ugh = c(ugh,paste0("\\sqrt{",paste0(rep(i,2),collapse="\\cdot"),"}"))
}

```

Look for factors that repeat. Again, we can treat a square-root radical like a power, so since $(fg)^k\equiv f^kg^k$, we can split up the square root of a product into a product of square roots.

$$\frac{`r paste0(ugh,collapse="\\cdot")`\cdot\sqrt{`r paste0(bfs,collapse="\\cdot")`}}{`r c`}$$

Simplify.

$$\frac{`r paste0(afs,collapse="\\cdot")`\sqrt{`r paste0(bfs,collapse="\\cdot")`}}{`r c`}$$

```{r,echo=F,results='asis'}
if((length(afs)>1) || (length(bfs)>1)){
    cat("Simplify more.\n\n")
    cat(paste0("$$",atex,"$$"))
}
```


So,

* $a=`r aa`$
* $b=`r bb`$
* $c=`r cc`$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: unit_hyp_pyth_thm