```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

while(T){
    th = runif(1,0,2*pi)
    x = cos(th) #runif(1,0.01,0.99)*sample(c(-1,1),1)
    y = sin(th) #sqrt(1-x^2)*sample(c(-1,1),1)
    m = y/x
    if((x<0 || y<0) && abs(x)>0.01 && abs(y)>0.01 && abs(x)<0.99 && abs(y)<0.99 && abs(m)<10 && abs(m)>0.01){break}
}
rmn = c("I","II","III","IV")

if(x<0 && y>0){
    q = 2
}
if(x<0 && y<0){
    q = 3
}
if(x>0 && y<0){
    q = 4
}

vns = c("x","y")
vvs = c(x,y)
kn = sample(1:2,1)
un = (1:2)[-kn]
kvn = vns[kn]
uvn = vns[un]
kvv = vvs[kn]
uvv = vvs[un]
orients = c("vertical","horizontal")
lo = orients[kn]
pnt = "(x,y)"
pnt = gsub(kvn,kvv,pnt,fixed=T)


```

Question
========

A unit circle (a circle with radius of 1) is centered at the origin of a $xy$-plane. On the circle's edge, a point has a $`r kvn`$ coordinate of `r kvv`, and the point is in [quadrant](https://en.wikipedia.org/wiki/Quadrant_(plane_geometry)) `r rmn[q]`.

Another line connects the origin to the point described above. What is the slope of this line that connects the point to the origin? Please be accurate within $\pm 0.001$.


Solution
========

The equation of a unit circle centered at the origin is based on the distance formula.

$$x^2+y^2=1$$

We wish to solve for $`r uvn`$, so subtract $`r kvn`^2$ from both sides.

$$`r uvn`^2=1-`r kvn`^2$$

Now, to isolate $`r uvn`$, we can square-root both sides. We have to accommodate both the positive and negative square roots as possibilities.

$$`r uvn`=\pm \sqrt{1-`r kvn`^2}$$

Plug in the given value.

$$`r uvn`=\pm \sqrt{1-(`r kvv`)^2}$$

$$`r uvn`\approx\pm \sqrt{1-`r kvv^2`}$$

$$`r uvn`\approx\pm \sqrt{`r 1-kvv^2`}$$

$$`r uvn`\approx\pm `r sqrt(1-kvv^2)`$$

We were told the point is in quadrant `r rmn[q]`. Draw a sketch.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
arrows(-1.2,0,1.2,0,0.1,20,3,lwd=2,col="grey")
arrows(0,-1.2,0,1.2,0.1,20,3,lwd=2,col="grey")
th = seq(0,2*pi,pi/360)
lines(cos(th),sin(th),col="red")
if(kn==1){
    abline(v=x,lty=2,col="blue")
    text(x,-1.05*sign(y),paste0("x=",round(x,5),collapse=""),adj=c(0.5,-0.3),srt=90,col="blue")
} else {
    abline(h=y,lty=2,col="blue")
    text(1.05*sign(-x),y,paste0("y=",round(y,5),collapse=""),adj=c(0.5,1.3),srt=0,col="blue")
}
# library(extrafont)
# font_import()
# loadfonts() 
text(1.15,1.15,"I",family="Tahoma",font=1,cex=1.3)
text(-1.15,1.15,"II",family="Tahoma",font=1,cex=1.3)
text(-1.15,-1.15,"III",family="Tahoma",font=1,cex=1.3)
text(1.15,-1.15,"IV",family="Tahoma",font=1,cex=1.3)
points(x,y,pch=20,col="purple",cex=2)
text(x,y,paste0("(",round(x,4),", ",round(y,4),")"),col="purple",adj=c(0.5+0.6*sign(x),0.5+sign(y)),cex=1.2)

np = c("negative","positive")
npx = np[round(sign(x)/2+1.5)]
npy = np[round(sign(y)/2+1.5)]

```
\

Notice, in quadrant `r rmn[q]`, the $x$ coordinate is `r npx`, and the $y$ coordinate is `r npy`. So, we know that $`r uvn`=`r uvv`$.


```{r,echo=F,fig.dim=c(6,30),results="hide",eval=FALSE}
# library(extrafont)
par(mar=c(0,0,0,0))
fnts = extrafont::fonts()
n = length(fnts)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-n,0))
for(i in 1:n){
    fnt = fnts[i]
    text(0,-i,paste0("IIIV ",fnt),family=fnt)
}

```
\

The slope of the line can be found with the "rise over run" formula.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
arrows(-1.2,0,1.2,0,0.1,20,3,lwd=2,col="grey")
arrows(0,-1.2,0,1.2,0.1,20,3,lwd=2,col="grey")
th = seq(0,2*pi,pi/360)
lines(cos(th),sin(th),col="red")
abline(0,m,col="maroon",lwd=2)

points(x,y,pch=20,col="purple",cex=2)
arrows(0,0,x,y,0.15,20,2,col="maroon",lwd=4)
lines(c(0,x),c(0,0),col="blue",lwd=3)
lines(c(x,x),c(0,y),col="darkgreen",lwd=3)
text(x/2,0,TeX(paste0("$\\Delta x = ",round(x,5),"$")),adj=c(0.5,0.5+1*sign(y)),col="blue")
text(x,y/2,TeX(paste0("$\\Delta y = ",round(y,5),"$")),srt=-90,adj=c(0.5,0.5-1*sign(x)),col="darkgreen")
```
\


$$\text{slope} ~=~ \frac{\text{rise}}{\text{run}}$$


$$\text{slope} ~=~ \frac{\Delta y}{\Delta x}$$


$$\text{slope} ~=~ \frac{y_2-y_1}{x_2-x_1}$$

$$\text{slope} ~=~ \frac{`r y`-0}{`r x`-0}$$

$$\text{slope} ~=~ \frac{`r y`}{`r x`}$$

$$\text{slope} ~\approx~ `r y/x`$$



Meta-information
============
extype: num
exsolution: `r m`
exname: uc_slope_from_x_and_Q
extol: 0.001