```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
m = round(2^runif(1,-3,3),2)
th1 = atan(m)
x = cos(th1)
y = sin(th1)

```

Question
========

In the first quadrant, a point is on the [unit circle](https://en.wikipedia.org/wiki/Unit_circle) (centered at the origin). A line connecting the point to the origin has a slope of `r m`, as enforced by the diagram below:

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-0.2,1.2),ylim=c(-0.2,1.2))
th = seq(0,2*pi,pi/360)
arrows(-1.2,0,1.2,0,0.1,20,3,col="grey")
arrows(0,-1.2,0,1.2,0.1,20,3,col="grey")
lines(cos(th),sin(th))
lines(c(0,cos(th1)),c(0,sin(th1)))
points(cos(th1),sin(th1),pch=19)
bmp = 0.03
lines(c(x-bmp,x-bmp,x),c(0,bmp,bmp))
lines(c(0,cos(th1)),c(0,0),col="red",lwd=2)
text(x/2,0,"x",adj=c(0.5,1.5),col="red")
lines(c(x,x),c(0,y),col="blue",lwd=2)
text(x,y/2,paste(m,"x"),srt=90,adj=c(0.5,1.5),col="blue")
text(x/2,y/2,"1",srt=th1/pi*180,adj=c(0.5,-0.5))
```
\

Find a decimal approximation of $x$ accurate within $\pm 0.01$.


Solution
========

[Pythagorean Theorem](https://en.wikipedia.org/wiki/Pythagorean_theorem)!

$$x^2+(`r m`x)^2=1^2$$

Evaluate the squares.

$$x^2+`r m^2`x^2=1$$

Combine like terms.

$$`r m^2+1`x^2=1$$

Divide both sides by `r m^2+1`.

$$x^2=\frac{1}{`r m^2+1`}$$

Square root both sides. In this case, we are only interested in the positive square root.

$$x=\sqrt{\frac{1}{`r m^2+1`}}$$

Get a decimal approximation.

$$x=`r sqrt(1/(m^2+1))`$$


Meta-information
============
extype: num
exsolution: `r x`
exname: uc_x_from_slope_Q1
extol: 0.001