```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

while(T){
    m = round(2^runif(1,-3,3),2)*sample(c(-1,1),1)
    th1 = atan(m)+sample(0:1,1)*pi
    x = cos(th1)
    y = sin(th1)
    if((x>0) && (y>0)){
        q = 1
    }
    if((x<0) && (y>0)){
        q = 2
    }
    if((x<0) && (y<0)){
        q = 3
    }
    if((x>0) && (y<0)){
        q = 4
    }
    if(q>1 && abs(x)>0.1 && abs(y)>0.1){break}
}
rmn = c("I","II","III","IV")

xa = round(x,3)
ya = round(y,3)

xopts = xa+0.003*(0:5-sample(0:5,1))
yopts = ya+0.003*(0:5-sample(0:5,1))
xopts = sort(c(-xopts,xopts))
yopts = sort(c(-yopts,yopts))

alx = paste0("* ",sprintf("%.3f",xopts),collapse="\n")
aly = paste0("* ",sprintf("%.3f",yopts),collapse="\n")

sol1 = paste0(1*(xopts==xa),collapse="")
sol2 = paste0(1*(yopts==ya),collapse="")

np = c("negative","positive")
xnp = np[sign(x)/2+1.5]
ynp = np[sign(y)/2+1.5]

```

Question
========

A point is on the [unit circle](https://en.wikipedia.org/wiki/Unit_circle) and in quadrant `r rmn[q]`. A line connecting the point to the origin has a slope of `r m`. Find the coordinates, $(x,y)$, of the point.


* $x=$ ##ANSWER1##
* $y=$ ##ANSWER2##

Answerlist
--------

`r alx`
`r aly`


Solution
========

Because the slope is `r m`, we know $y=`r m`x$. Draw a sketch.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
th = seq(0,2*pi,pi/360)
arrows(-1.2,0,1.2,0,0.1,20,3,col="grey")
arrows(0,-1.2,0,1.2,0.1,20,3,col="grey")
lines(cos(th),sin(th))
lines(c(0,cos(th1)),c(0,sin(th1)))
points(cos(th1),sin(th1),pch=19)
bmp = 0.03
lines(c(x-bmp*sign(x),x-bmp*sign(x),x),c(0,bmp,bmp)*sign(y))
lines(c(0,cos(th1)),c(0,0),col="red",lwd=2)
# text(x/2,0,"L",adj=c(0.5,0.5+sign(y)),col="red")
lines(c(x,x),c(0,y),col="blue",lwd=2)
# text(x,y/2,paste(abs(m),"L"),srt=90,adj=c(0.5,0.5+sign(x)),col="blue")
text(x/2,y/2,"1",srt=(th1/pi*180+90)%%180-90,adj=c(0.5,0.5-sign(y)))
text(1.1*x,1.1*y,paste0("(x, ",m,"x)"),srt=(th1/pi*180+180)%%180-90)
```
\

The point is on the unit circle, so we know $x^2+y^2=1$.

$$x^2+(`r m`x)^2=1$$

Distribute the power over the product.

$$x^2+`r m^2`x^2=1$$

Combine like terms.

$$`r m^2+1`x^2=1$$

Divide both sides by `r m^2+1`.

$$x^2=\frac{1}{`r m^2+1`}$$

Square root both sides. We need to consider both the positive and negative possibilities.

$$x=\pm \sqrt{\frac{1}{`r m^2+1`}}$$

Since the point is in quadrant `r rmn[q]`, we know x is `r xnp`. We can get the decimal approximation of $x$.


$$x=`r x`$$

Calculate $y$ using $y=(`r m`)\cdot(`r x`)$.

$$y=`r y`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: uc_x_y_from_slope_and_Q
extol: 0.001