```{r,echo=F}
while(T){
  ang = round(runif(1,pi/7,1.3),2)
  opp = round(runif(1,11,99),0)
  opp2 = opp
  hyp = opp/sin(ang)
  hyp2 = round(hyp,0)
  angt = sprintf("%.2f",ang)
  hypt = sprintf("%.0f",round(hyp2,0))
  oppt = sprintf("%.0f",round(opp,0))
  if(hyp-opp2>2 && hyp2<99 && round(ang*hyp2)!=opp2 && hyp2!=round(opp2/ang)){break}
}
```

Question
========

A right triangle has an angle of `r angt` radians. The opposite leg has a length of `r oppt` meters. How long, in meters, is the hypotenuse?

```{r,fig.dim=c(5,5),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",axes=F,ann=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
th = seq(0,pi/2,length.out=100)
lines(cos(th),sin(th),lty=2,col="grey")
lines(c(0,cos(ang),cos(ang),0),c(0,0,sin(ang),0),lwd=3)
lines(c(cos(ang)-0.02,cos(ang)-0.02,cos(ang)),c(0,0.02,0.02))
th2 = seq(0,ang,length.out=100)
#lines(cos(th2),sin(th2),lty=2,col=rgb(1,0.8,0.8))
#text(1.07*cos(ang/2),1.07*sin(ang/2),paste0(angt,"*",hypt),col=rgb(1,0.8,0.8),cex=0.7)
lines(c(cos(ang),cos(ang)),c(0,sin(ang)),col="purple",lwd=4)
text(cos(ang)+0.05,sin(ang)/2,paste0(oppt," m"),col="purple",cex=0.8)
lines(c(0,cos(ang)),c(0,sin(ang)),col="blue",lwd=4)
text(cos(ang)/2+0.05*cos(ang+pi/2),
     sin(ang)/2+0.05*sin(ang+pi/2),
     paste0("?"," m"),srt=ang/pi*180,col="blue",cex=0.8)
lines(0.1*cos(th2),0.1*sin(th2),col="red")
text(0.16*cos(ang/2),0.16*sin(ang/2),angt,col="red",cex=0.8)
```
\

Please round your answer to the nearest meter.


Solution
========

First, identify the correct trigonometric function. Remember, [SOHCAHTOA](https://en.wikipedia.org/wiki/Mnemonics_in_trigonometry).

$$\sin(\theta)=\frac{\mathrm{opposite}}{\mathrm{hypotenuse}}$$


$$\cos(\theta)=\frac{\mathrm{adjacent}}{\mathrm{hypotenuse}}$$


$$\tan(\theta)=\frac{\mathrm{opposite}}{\mathrm{adjacent}}$$

In this case, we are given the angle and the **opposite**, and we are asked for the **hypotenuse**. The trigonometric ratio that relates these two sides is [sine](https://en.wikipedia.org/wiki/Trigonometric_functions). Let $x$ represent the requested length.

$$\sin(`r angt`) = \frac{`r oppt`}{x}$$
Multiply both sides by $x$ and divide both sides by $\sin(`r angt`)$ to solve for $x$.

$$x = \frac{`r oppt`}{\sin(`r angt`)}$$
To evaluate $x$, type the following into a modern calculator: ``round(`r oppt`/sin(`r angt`))``. Make sure to be in radian mode, not degree mode.

$$x \approx `r hypt`$$


Meta-information
============
extype: num
exsolution: `r hyp2`
exname: sin_get_hyp