```{r,echo=F}
while(T){
    th = runif(1,0.05,pi/2-0.05)
    x = round(cos(th),3)
    y = round(sin(th),3)
    t = round(y/x,3)
    rt = round(x/y,3)
    others = round(20^runif(4,-1,1),3)
    tha = round(atan(t),3)
    thb = round(asin(y),3)
    thc = round(acos(x),3)
    thz = c(tha,thb,thc)
    alls = sort(c(x,y,t,rt,thb,others))
    if(min(diff(alls))>0.02 && (max(thz)-min(thz))<0.005){break}
}
al = paste0("* ",alls,collapse="\n")
sol1 = paste0(1*(alls==y),collapse="")
sol2 = paste0(1*(alls==x),collapse="")
sol3 = paste0(1*(alls==t),collapse="")
sol4 = paste0(1*(alls==thb),collapse="")

```

Question
========

A unit circle is drawn centered at the origin. A ray emanates from the origin at an angle of $\theta$ radians and intersects the unit circle at point $(`r x`, `r y`)$, as shown below.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-0.2,1.2),ylim=c(-0.2,1.2))
arrows(-1.2,0,1.2,0,0.1,20,3,col="grey",lwd=2)
arrows(0,-1.2,0,1.2,0.1,20,3,col="grey",lwd=2)
points(0,0,pch=20)
th1 = seq(0,2*pi,pi/360)
lines(cos(th1),sin(th1),col="grey")
arrows(0,0,1.1*x,1.1*y,0.2,20,2,lwd=3)
th2 = seq(0,th,pi/360)
lines(0.2*cos(th2),0.2*sin(th2),col="red",lwd=3)
text(0.25*cos(th/2),0.25*sin(th/2),TeX("$\\theta$"),col="red",cex=1.3)
points(1,0,pch=19,col="purple")
text(1,0,"(1,0)",col="purple",adj=c(-0.2,1.5))
points(0,1,pch=19,col="purple")
text(0,1,"(0,1)",col="purple",adj=c(-0.2,-0.5))
points(x,y,pch=19,col="red")
text(x,y,paste0("(",x,", ",y,")",collapse=""),adj=c(1.2,-0.5),col="red")

```
\

Evaluate the following trigonometric functions:

* $\sin(\theta)=$ ##ANSWER1##
* $\cos(\theta)=$ ##ANSWER2##
* $\tan(\theta)=$ ##ANSWER3##

Also, find the angle measure, $\theta$, in radians.

* $\theta=$ ##ANSWER4##

Answerlist
--------

`r al`
`r al`
`r al`
`r al`


Solution
========

Notice, you can draw a right triangle with a hypotenuse of length 1.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-0.2,1.2),ylim=c(-0.2,1.2))
arrows(-1.2,0,1.2,0,0.1,20,3,col="grey",lwd=2)
arrows(0,-1.2,0,1.2,0.1,20,3,col="grey",lwd=2)
points(0,0,pch=20)
th1 = seq(0,2*pi,pi/360)
lines(cos(th1),sin(th1),col="grey")
arrows(0,0,1.1*x,1.1*y,0.2,20,2,lwd=1,col="darkgrey")
th2 = seq(0,th,pi/360)
lines(0.2*cos(th2),0.2*sin(th2),col="red",lwd=3)
text(0.25*cos(th/2),0.25*sin(th/2),TeX("$\\theta$"),col="red",cex=1.3)
points(1,0,pch=19,col="purple")
text(1,0,"(1,0)",col="purple",adj=c(-0.2,1.5))
points(0,1,pch=19,col="purple")
text(0,1,"(0,1)",col="purple",adj=c(-0.2,-0.5))
points(x,y,pch=19,col="red")
text(x,y,paste0("(",x,", ",y,")",collapse=""),adj=c(1.2,-0.5),col="red")

lines(c(0,x),c(0,0),col="blue",lwd=5)
text(x/2,0,sprintf("%.3f",x),adj=c(0.5,1.5),col="blue")

lines(c(x,x),c(0,y),col="darkgreen",lwd=5)
text(x,y/2,sprintf("%.3f",y),srt=90,adj=c(0.5,1.5),col="darkgreen")

lines(c(0,x),c(0,y),col="maroon",lwd=5)
text(x/2,y/2,"1",srt=th/pi*180,adj=c(0.5,-0.5),col="maroon")
```
\

Use [SOHCAHTOA](https://en.wikipedia.org/wiki/Mnemonics_in_trigonometry#SOH-CAH-TOA) to find the answers.

$$\sin(\theta) ~=~ \frac{`r y`}{1} ~=~ `r y`$$

$$\cos(\theta) ~=~ \frac{`r x`}{1} ~=~ `r x`$$
$$\tan(\theta) ~=~ \frac{`r y`}{`r x`} ~\approx~ `r t`$$

To find the angle measure, we can use any of the [inverse trig functions](https://en.wikipedia.org/wiki/Inverse_trigonometric_functions).

$$\arcsin(`r y`)~\approx~`r thb`$$
$$\arccos(`r x`)~\approx~`r thc`$$
$$\arctan(`r t`)~\approx~`r tha`$$

So, $\theta\approx`r thc`$.

Notice, on a [unit circle](https://en.wikipedia.org/wiki/Unit_circle), $\sin(\theta)=y$ and $\cos(\theta)=x$ and $\tan(\theta)=\frac{y}{x}$. Also, notice that $\tan(\theta)$ gives the SLOPE of the ray.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: trigs_from_uc_point_Q1