```{r,echo=F}
while(T){
  rs = sample(11:99,2)/10
  r1 = rs[1]
  r2 = rs[2]
  ds = sort(sample(11:79,2))
  d1 = ds[1]
  d2 = ds[2]
  t1 = d1/180*pi
  t2 = d2/180*pi
  a1 = r1*cos(t1)
  b1 = r1*sin(t1)
  a2 = r2*cos(t2)
  b2 = r2*sin(t2)
  a3 = a1+a2
  b3 = b1+b2
  r3 = sqrt(a3^2+b3^2)
  t3 = atan(b3/a3)
  d3 = t3*180/pi
  if(t3-t1>pi/20 && abs(r2-r1)<1/3*min(c(r1,r2)) && abs(r2-r1)>0.4 && r1!=r2 && round(r1)!=r1 && round(r2)!=r2 && b3<a3*1.5){break}
}
ans1 = round(d3)
ans2 = round(r3,1)

nch = 8
which1 = sample(1:nch,1)
which2 = sample(1:nch,1)
st1 = 1
st2 = 0.1

ac1 = round(seq(ans1-(which1-1)*st1,ans1+(nch-which1)*st1,length.out=nch))
ac2 = round(seq(ans2-(which2-1)*st2,ans2+(nch-which2)*st2,length.out=nch),1)

al1 = paste0("* ",ac1,"°\n",collapse="")
al2 = paste0("* ",sprintf("%.1f",ac2)," mi\n",collapse="")

sol1 = paste0(1*(ac1==ans1),collapse="")
sol2 = paste0(1*(ac2==ans2),collapse="")
```

Question
========

A ship sailed `r r1` miles in a direction of `r d1`° North of East. The ship turned and sailed `r r2` miles in a direction `r d2`° North of East.


```{r,echo=F,fig.width=8}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(c(0,a3,a3,0),c(0,b3,0,0),type="l",asp=1,ann=F,axes=F,lwd=1,col="grey")
m = 0.03*a3
lines(c(a3-m,a3-m,a3),c(0,m,m),col="grey")
lines(c(0,a3),c(0,b3),col="grey",lwd=2)
arrows(0,0,a3,b3,angle=10,length=0.2,lwd=3,col="grey")
lines(c(0,a1,a1,0),c(0,0,b1,0),col="red",lwd=1)
lines(c(0,a1),c(0,b1),col="red",lwd=3)
arrows(0,0,a1,b1,angle=10,length=0.15,lwd=3,col="red")
lines(c(a1-m,a1-m,a1),c(0,m,m),col="red")
ths = seq(0,t1,length.out=100)
lines((m+m/t1)*cos(ths),(m+m/t1)*sin(ths),col="red")
text((3*m+m/t1)*cos(t1/2),(3*m+m/t1)*sin(t1/2),
     paste0(d1,"°"),col="red",srt=t1/pi*180/2)
text(a1/2+cos(t1+pi/2)*m,b1/2+sin(t1+pi/2)*m,
     paste0(r1," mi"),srt=t1/pi*180,col="red")
lines(c(a1,a3,a3,a1),c(b1,b1,b3,b1),col="blue",lwd=1)
lines(c(a1,a3),c(b1,b3),col="blue",lwd=3)
lines(c(a3-m,a3-m,a3),c(b1,b1+m,b1+m),col="blue")
arrows(a1,b1,a3,b3,angle=10,length=0.15,lwd=3,col="blue")
phs = seq(0,t2,length.out=100)
lines(a1+(m+m/t2)*cos(phs),b1+(m+m/t2)*sin(phs),col="blue")
text(a1+(3*m+m/t2)*cos(t2/2),b1+(3*m+m/t2)*sin(t2/2),
     paste0(d2,"°"),col="blue",srt=t2/pi*180/2)
text(a1+a2/2+m*cos(pi/2+t2),b1+b2/2+m*sin(pi/2+t2),
     paste0(r2," mi"),col="blue",srt=t2/pi*180)
```
\

The ship's captain suffers a terrible accident. The first officer radios for help and sets anchor, waiting for help while administering first aid.

A helicopter, starting where the ship started, wishes to fly directly to the ship. What direction ($\theta$ rounded to nearest degree) and distance ($r$ rounded to nearest tenth of a mile) should the helicopter fly?


```{r,echo=F,fig.width=8}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(c(0,a3,a3,0),c(0,b3,0,0),type="l",asp=1,ann=F,axes=F,lwd=1,col="grey")
m = 0.03*a3
red2 = rgb(1,0.8,0.8)
blue2 = rgb(0.8,0.8,1)
lines(c(0,a1,a1,0),c(0,0,b1,0),col=red2,lwd=1)
lines(c(0,a1),c(0,b1),col=red2,lwd=3)
arrows(0,0,a1,b1,angle=10,length=0.15,lwd=3,col=red2)
lines(c(a1-m,a1-m,a1),c(0,m,m),col=red2)
lines(c(a1,a3,a3,a1),c(b1,b1,b3,b1),col=blue2,lwd=1)
lines(c(a1,a3),c(b1,b3),col=blue2,lwd=3)
lines(c(a3-m,a3-m,a3),c(b1,b1+m,b1+m),col=blue2)
arrows(a1,b1,a3,b3,angle=10,length=0.15,lwd=3,col=blue2)
lines(c(0,a3,a3,0),c(0,b3,0,0))
lines(c(a3-m,a3-m,a3),c(0,m,m),col="black")
lines(c(0,a3),c(0,b3),col="black",lwd=2)
arrows(0,0,a3,b3,angle=10,length=0.2,lwd=4,col="black")
ws = seq(0,t3,length.out=100)
lines((m+m/t3)*cos(ws),(m+m/t3)*sin(ws),lwd=2,col="black")
text((3*m+m/t3)*cos(t3/2),(3*m+m/t3)*sin(t3/2),
     TeX("$\\theta$"),col="black",srt=t3/pi*180/2,cex=1.2)
text(a3/2+m*cos(pi/2+t3),b3/2+m*sin(pi/2+t3),
     TeX("$r$"),col="black",srt=t3/pi*180,cex=1.2)
```
\


* The direction: $\theta =$ ##ANSWER1##
* The distance: $r =$ ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`

Solution
========

Start by naming some lengths (the legs of the two small triangles).

```{r,echo=F,fig.width=8}
library(latex2exp)
m = 0.03*a3
par(mar=c(0,0,0,0))
plot(c(0,a3,a3,0),c(0,b3,0,0),type="l",asp=1,ann=F,axes=F,lwd=1,col="grey",xlim=c(-2*m,a3+2*m),ylim=c(-2*m,b3+2*m))
lines(c(a3-m,a3-m,a3),c(0,m,m),col="grey")
lines(c(0,a3),c(0,b3),col="grey",lwd=2)
arrows(0,0,a3,b3,angle=10,length=0.2,lwd=3,col="grey")
lines(c(0,a1,a1,0),c(0,0,b1,0),col="red",lwd=1)
lines(c(0,a1),c(0,b1),col="red",lwd=3)
arrows(0,0,a1,b1,angle=10,length=0.15,lwd=3,col="red")
lines(c(a1-m,a1-m,a1),c(0,m,m),col="red")
ths = seq(0,t1,length.out=100)
lines((m+m/t1)*cos(ths),(m+m/t1)*sin(ths),col="red")
text((3*m+m/t1)*cos(t1/2),(3*m+m/t1)*sin(t1/2),
     paste0(d1,"°"),col="red",srt=t1/pi*180/2)
text(a1/2+cos(t1+pi/2)*m,b1/2+sin(t1+pi/2)*m,
     paste0(r1," mi"),srt=t1/pi*180,col="red")
text(a1/2,-m,"a",col="red")
text(a1+m,b1/2,"b",col="red")
lines(c(a1,a3,a3,a1),c(b1,b1,b3,b1),col="blue",lwd=1)
lines(c(a1,a3),c(b1,b3),col="blue",lwd=3)
lines(c(a3-m,a3-m,a3),c(b1,b1+m,b1+m),col="blue")
arrows(a1,b1,a3,b3,angle=10,length=0.15,lwd=3,col="blue")
phs = seq(0,t2,length.out=100)
lines(a1+(m+m/t2)*cos(phs),b1+(m+m/t2)*sin(phs),col="blue")
text(a1+(3*m+m/t2)*cos(t2/2),b1+(3*m+m/t2)*sin(t2/2),
     paste0(d2,"°"),col="blue",srt=t2/pi*180/2)
text(a1+a2/2+m*cos(pi/2+t2),b1+b2/2+m*sin(pi/2+t2),
     paste0(r2," mi"),col="blue",srt=t2/pi*180)
text(a1+a2/2,b1-m,"j",col="blue")
text(a1+a2+m,b1+b2/2,"k",col="blue")
```
\

Evaluate $a$, $b$, $j$, and $k$. Remember to set your calculator to DEGREE MODE.

$$a ~=~ `r r1` \cos(`r d1`^\circ) ~=~ `r a1`$$
$$b ~=~ `r r1` \sin(`r d1`^\circ) ~=~ `r b1`$$
$$j ~=~ `r r2` \cos(`r d2`^\circ) ~=~ `r a2`$$
$$k ~=~ `r r2` \sin(`r d2`^\circ) ~=~ `r b2`$$

Name the lengths of the large triangle.

```{r,echo=F,fig.width=8}
library(latex2exp)
m = 0.03*a3
par(mar=c(0,0,0,0))
plot(c(0,a3,a3,0),c(0,b3,0,0),type="l",asp=1,ann=F,axes=F,lwd=1,col="grey",xlim=c(-2*m,a3+2*m),ylim=c(-2*m,b3+2*m))
red2 = rgb(1,0.8,0.8)
blue2 = rgb(0.8,0.8,1)
lines(c(0,a1,a1,0),c(0,0,b1,0),col=red2,lwd=1)
lines(c(0,a1),c(0,b1),col=red2,lwd=3)
arrows(0,0,a1,b1,angle=10,length=0.15,lwd=3,col=red2)
lines(c(a1-m,a1-m,a1),c(0,m,m),col=red2)
lines(c(a1,a3,a3,a1),c(b1,b1,b3,b1),col=blue2,lwd=1)
lines(c(a1,a3),c(b1,b3),col=blue2,lwd=3)
lines(c(a3-m,a3-m,a3),c(b1,b1+m,b1+m),col=blue2)
arrows(a1,b1,a3,b3,angle=10,length=0.15,lwd=3,col=blue2)
lines(c(0,a3,a3,0),c(0,b3,0,0))
lines(c(a3-m,a3-m,a3),c(0,m,m),col="black")
lines(c(0,a3),c(0,b3),col="black",lwd=2)
arrows(0,0,a3,b3,angle=10,length=0.2,lwd=4,col="black")
ws = seq(0,t3,length.out=100)
lines((m+m/t3)*cos(ws),(m+m/t3)*sin(ws),lwd=2,col="black")
text((3*m+m/t3)*cos(t3/2),(3*m+m/t3)*sin(t3/2),
     TeX("$\\theta$"),col="black",srt=t3/pi*180/2,cex=1.2)
text(a3/2+m*cos(pi/2+t3),b3/2+m*sin(pi/2+t3),
     TeX("$r$"),col="black",srt=t3/pi*180,cex=1.2)
text(a3/2,-m,"x",col="black")
text(a3+m,b3/2,"y",col="black")
```
\

Calculate $x$ and $y$.

$$x~=~`r a1`+`r a2`~=~`r a3`$$
$$y~=~`r b1`+`r b2`~=~`r b3`$$
Calculate $\theta$. Remember to set your calculator to DEGREE MODE.

$$\theta ~=~ \arctan\left(\frac{`r b3`}{`r a3`}\right) ~=~ `r d3`^\circ ~\approx~ `r ans1`^\circ$$

Calculate $r$ by using [Pythagorean Theorem](https://en.wikipedia.org/wiki/Pythagorean_theorem).

$$r ~=~ \sqrt{`r a3`^2+`r b3`^2} ~=~ `r r3` ~\approx~ `r ans2` ~\mathrm{mi}$$

Instead of using Pythagorean Theorem, you could have used trigonometry.

$$r ~=~ \frac{`r a3`}{\cos(`r d3`^\circ)} ~=~ \frac{`r b3`}{\sin(`r d3`^\circ)} ~=~ `r r3` ~\approx~ `r ans2`~\mathrm{mi}$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: polar_vector_add_simple