```{r,echo=F}
## 1 circle
r = sample(2:5,1)
c = sample(2:5,2)*sample(c(-1,1),2,T)
xn = paste0(c[1],"+",r,"\\cos(t)")
yn = paste0(c[2],"+",r,"\\sin(t)")
v = 0
w = 2*pi
vn = "0"
wn = "2\\pi"
t = seq(v,w,length.out=1200)
x = c[1]+r*cos(t)
y = c[2]+r*sin(t)
xns = c(xn)
yns = c(yn)
xs = list(x)
ys = list(y)
vns = c(vn)
wns = c(wn)

## 2 ellipse
r = sample(2:8,2)
xn = paste0(r[1],"\\cos(t)")
yn = paste0(r[2],"\\sin(t)")
v = 0
w = 2*pi
vn = "0"
wn = "2\\pi"
t = seq(v,w,length.out=1200)
x = r[1]*cos(t)
y = r[2]*sin(t)
xns = c(xns,xn)
yns = c(yns,yn)
xs[[2]] = x
ys[[2]] = y
vns = c(vns,vn)
wns = c(wns,wn)

## 3 arithmetic spiral
n = sample(2:8,1)
xn = paste0("t\\cos(",n,"t)")
yn = paste0("t\\sin(",n,"t)")
v = 0
w = 4*pi
vn = "0"
wn = "4\\pi"
t = seq(v,w,length.out=1200)
x = t*cos(n*t)
y = t*sin(n*t)
xns = c(xns,xn)
yns = c(yns,yn)
xs[[3]] = x
ys[[3]] = y
vns = c(vns,vn)
wns = c(wns,wn)

## 4 exponential spiral
n = sample(8:18,1)
xn = paste0("e^t\\cos(",n,"t)")
yn = paste0("e^t\\sin(",n,"t)")
v = -4*pi
w = 4*pi
vn = "-4\\pi"
wn = "4\\pi"
t = seq(v,w,length.out=3600)
x = exp(t)*cos(n*t)
y = exp(t)*sin(n*t)
xns = c(xns,xn)
yns = c(yns,yn)
xs[[4]] = x
ys[[4]] = y
vns = c(vns,vn)
wns = c(wns,wn)

## 5 sine product function
n = sample(2:9,4)
r = sample(5:9,1)
xn = paste0(r,"\\sin(",n[1],"t)\\cdot\\sin(",n[2],"t)")
yn = paste0(r,"\\sin(",n[3],"t)\\cdot\\sin(",n[4],"t)")
v = 0
w = 2*pi
vn = "0"
wn = "2\\pi"
t = seq(v,w,length.out=1200)
x = r*sin(n[1]*t)*sin(n[2]*t)
y = r*sin(n[3]*t)*sin(n[4]*t)
xns = c(xns,xn)
yns = c(yns,yn)
xs[[5]] = x
ys[[5]] = y
vns = c(vns,vn)
wns = c(wns,wn)


## 6 moon trajectory
n = sample(3:9,1)
r = sample(5:8,1)
xn = paste0(r,"\\cos(t)+",10-r,"\\cos(",n,"t)")
yn = paste0(r,"\\sin(t)+",10-r,"\\sin(",n,"t)")
v = 0
w = 2*pi
vn = "0"
wn = "2\\pi"
t = seq(v,w,length.out=1200)
x = r*cos(t)+(10-r)*cos(n*t)
y = r*sin(t)+(10-r)*sin(n*t)
xns = c(xns,xn)
yns = c(yns,yn)
xs[[6]] = x
ys[[6]] = y
vns = c(vns,vn)
wns = c(wns,wn)

## 7 star
r = sample(3:7,1)
n = sample(5:9,1)
xn = paste0("(",r,"+\\sin(",n,"t))\\cos(t)")
yn = paste0("(",r,"+\\sin(",n,"t))\\sin(t)")
v = 0
w = 2*pi
vn = "0"
wn = "2\\pi"
t = seq(v,w,length.out=1200)
x = (r+sin(n*t))*cos(t)
y = (r+sin(n*t))*sin(t)
xns = c(xns,xn)
yns = c(yns,yn)
xs[[7]] = x
ys[[7]] = y
vns = c(vns,vn)
wns = c(wns,wn)

## 8 boring
v = -2*pi
w = 2*pi
vn = "-2\\pi"
wn = "2\\pi"
t = seq(v,w,length.out=1200)
typ = sample(1:4,1)
if(typ == 1){
  xn = "t"
  yn = "\\sin(t)"
  x = t
  y = sin(t)
}
if(typ == 2){
  xn = "t"
  yn = "\\cos(t)"
  x = t
  y = cos(t)
}
if(typ == 3){
  xn = "\\cos(t)"
  yn = "t"
  x = cos(t)
  y = t
}
if(typ == 4){
  xn = "\\sin(t)"
  yn = "t"
  x = sin(t)
  y = t
}
xns = c(xns,xn)
yns = c(yns,yn)
xs[[8]] = x
ys[[8]] = y
vns = c(vns,vn)
wns = c(wns,wn)


ord1 = sample(1:8)
ord2 = sample(1:8)

sol = list()
for(i in 1:8){
  sol[[i]] = paste0(1*(ord1[i]==ord2),collapse="")
}

exps = paste0(1:8,". The following parametric equations match graph ##ANSWER",1:8,"## $$x=",xns[ord1],"$$ $$y=",yns[ord1],"$$ $$",vns[ord1],"\\le t \\le ",wns[ord1],"$$",collapse="\n")

ch = LETTERS[1:8]
al = paste0("* ",ch,"\n",collapse="")

```

Question
========

Match the [parametric equations](https://help.desmos.com/hc/en-us/articles/4406906208397-Parametric-Equations) to their graphs. 

```{r,fig.dim=c(6,12),echo=F}
par(pty="s",mfrow=c(4,2))
for(i in 1:8){
  plot(xs[[ord2[i]]],ys[[ord2[i]]],type="l",xlim=c(-10,10),ylim=c(-10,10),main=LETTERS[i],xlab="x",ylab="y")
}
```
\


`r exps`

Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`


Solution
========

Graph using using Desmos or a similar graphing utility.

In Desmos, to graph parametric equations, use the same notation you'd use for a point, but instead of $(x,y)$, put two expressions with $t$ as the independent variable.

For example, the first one, you'd type:


$${\large(}`r xns[ord1[1]]`,~~`r yns[ord1[1]]`{\large)}$$
And then set the proper domain of $t$.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r sol[1]`|`r sol[2]`|`r sol[3]`|`r sol[4]`|`r sol[5]`|`r sol[6]`|`r sol[7]`|`r sol[8]`
exname: match_parametrics