```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
th = runif(1,pi/20,pi/2-pi/20)+sample(c(0,pi/2,pi,3*pi/2),1)
th = signif(th,3)
y = signif(sin(th),3)
q = th%/%(pi/2)+1
sx = 1-2*(q %in% c(2,3))
x = sx*sqrt(1-y^2)
xr = signif(x,3)
rmn = c("I","II","III","IV")
m = y/x

```

Question
========

Given:

$$\sin(\theta)~=~`r y`$$
$$\theta~\text{ is in quadrant `r rmn[q]`}$$

Find $\tan(\theta)$. The tolerance is $\pm 0.001$.


Solution
========

Remember, $\sin(\theta)$ represents the $y$ value on the unit circle at an angle of $\theta$. Draw a sketch. We know the point of interest is in quadrant `r rmn[q]`.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
arrows(-1.3,0,1.3,0,0.1,20,3,lwd=2,col="grey")
arrows(0,-1.3,0,1.3,0.1,20,3,lwd=2,col="grey")
thall = seq(0,2*pi,pi/360)
lines(cos(thall),sin(thall),col="black",lty=3)
abline(h=y,lty=2,col="blue")
if(abs(y)>0.6){
    text(-1.15*sign(x),y,paste0("y=",round(y,5),collapse=""),adj=c(0.5,-0.3),col="blue")
} else {
    text(0,y,paste0("y=",round(y,5),collapse=""),adj=c(0.5,-0.3),col="blue")
}

thth = seq(0,th,pi/360)
# polygon(c(0,cos(thth)),c(0,sin(thth)),border=F,col=rgb(0.5,0,0.2,0.1))
lines(cos(thth),sin(thth),col="maroon",lwd=3)
lines(c(0,cos(th)),c(0,sin(th)),col="red")
text(1.05*cos(th/2),1.05*sin(th/2),TeX("$\\theta$"),col="maroon",cex=1.5)

# library(extrafont)
# font_import()
# loadfonts() 
text(1.15,1.15,"I",family="Tahoma",font=1,cex=1.3)
text(-1.15,1.15,"II",family="Tahoma",font=1,cex=1.3)
text(-1.15,-1.15,"III",family="Tahoma",font=1,cex=1.3)
text(1.15,-1.15,"IV",family="Tahoma",font=1,cex=1.3)
points(x,y,pch=20,col="purple",cex=2)
text(x,y,paste0("(x, ",round(y,4),")"),col="purple",adj=c(0.5-0.7*sign(x),0.5-0.7*sign(y)))

points(-x,y,pch=19,col="black")
text(-x,y,adj=c(0.5-0.7*sign(x),0.5+0.7*sign(y)),"wrong\nspot")
srt = (th*180/pi+90)%%180-90
text(0.5*cos(th),0.5*sin(th),"1",col="red",srt=srt,adj=c(0.5,-0.3))

np = c("negative","positive")
npx = np[round(sign(x)/2+1.5)]
npy = np[round(sign(y)/2+1.5)]

```
\

You can draw a right triangle. The standard way to do this is by using a segment along the $x$-axis and a vertical segment.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,
     xlim=c(sign(x)*(0.5-sign(x)*0.6),sign(x)*(0.5+sign(x)*0.6)),
     ylim=c(sign(y)*(0.5-sign(y)*0.6),sign(y)*(0.5+sign(y)*0.6)))
arrows(-1.1,0,1.1,0,0.1,20,3,lwd=2,col="grey")
arrows(0,-1.1,0,1.1,0.1,20,3,lwd=2,col="grey")
thall = seq(0,2*pi,pi/360)
bmp = 0.02
bx = bmp*sign(x)
by = bmp*sign(y)
lines(c(x-bx,x-bx,x),c(0,by,by))

lines(cos(thall),sin(thall),col="grey",lty=3)
thth = seq(0,th,pi/360)
# polygon(c(0,cos(thth)),c(0,sin(thth)),border=F,col=rgb(0.5,0,0.2,0.1))
lines(cos(thth),sin(thth),col=rgb(0.8,0,0.6),lwd=1)
lines(c(0,cos(th)),c(0,sin(th)),col="red",lwd=3)
# text(1.05*cos(th/2),1.05*sin(th/2),TeX("$\\theta$"),col="maroon",cex=1.5)

# library(extrafont)
# font_import()
# loadfonts() 
text(1.05,1.05,"I",family="Tahoma",font=1,cex=1.3)
text(-1.05,1.05,"II",family="Tahoma",font=1,cex=1.3)
text(-1.05,-1.05,"III",family="Tahoma",font=1,cex=1.3)
text(1.05,-1.05,"IV",family="Tahoma",font=1,cex=1.3)
# points(x,y,pch=20,col="purple",cex=2)
# text(1.01*x,1.01*y,paste0("(",round(x,4),",  y)"),col="purple",adj=c(0.5-0.7*sign(x),0.5-0.7*sign(y)))

points(x,-y,pch=19,col="black")
text(x,-y,adj=c(0.5-0.7*sign(x),0.5+0.7*sign(y)),"wrong\nspot")
srt = (th*180/pi+90)%%180-90
text(0.5*cos(th),0.5*sin(th),"1",col="red",srt=srt,adj=c(0.5,0.5-0.8*sign(y)))
lines(c(x,x),c(0,y),col="darkorange",lwd=3)
text(x,y/2,abs(y),col="darkorange",srt=90,adj=c(0.5,0.5+0.9*sign(x)))
lines(c(0,x),c(0,0),col="darkgreen",lwd=3)
text(x/2,0,TeX("$|x|=|cos(\\theta)|$"),col="darkgreen",srt=0,adj=c(0.5,0.5+0.9*sign(y)))

np = c("negative","positive")
npx = np[round(sign(x)/2+1.5)]
npy = np[round(sign(y)/2+1.5)]

```
\

Use Pythagorean Theorem.

$$x^2+`r abs(y)`^2~=~1^2$$
$$x^2+`r abs(y)`^2~=~1$$

Subtract $`r abs(y)`^2$ from both sides.

$$x^2~=~1-`r abs(y)`^2$$

Square root both sides.

$$|x|~=~\sqrt{(1-`r abs(y)`^2)}$$

We know the quadrant is quadrant `r rmn[q]`, so $x$ is `r npx`.


$$x~=~`r x`$$

So,

$$\cos(\theta)~=~`r x`$$

Remember, $\tan(\theta)\equiv\frac{\sin(\theta)}{\cos(\theta)}$ for any value of $\theta$. In other words, $\tan(\theta)$ is the slope of the line connecting the point to the origin.

$$\tan(\theta)~=~\frac{`r y`}{`r x`}~=~ `r m`$$



Meta-information
============
extype: num
exsolution: `r m`
exname: tan_from_sin_and_Q
extol: 0.001