```{r data generation, echo = FALSE, results = "hide"}
rands = sample(1:9,8)
x = sort(rands[1:4])
y = rands[5:8]
oc1 = sample(0:1,1)
oc2 = sample(0:1,1)
anli = 0:10
apast = paste0("* ",anli,"\n",collapse="")

dl = min(x)
dh = max(x)
rl = min(y)
rh = max(y)
ans1 = paste0(1*(dl==anli),collapse="")
ans2 = paste0(1*(dh==anli),collapse="")
ans3 = paste0(1*(rl==anli),collapse="")
ans4 = paste0(1*(rh==anli),collapse="")

```



Question
========


A function $f$ is graphed below.

```{r,fig.dim=c(5,5),echo=FALSE}
par(pty="s")
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="f(x)",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(0,length(x)-2),0),border="blue",lwd=4)
points(c(x[1],x[4]),c(y[1],y[4]),pch=20,cex=2,col="blue")
```
\

Determine the [domain](https://en.wikipedia.org/wiki/Domain_of_a_function){target="_blank"} and [range](https://en.wikipedia.org/wiki/Range_of_a_function){target="_blank"}. *Note: wikipedia suggests using "[image](https://en.wikipedia.org/wiki/Image_(mathematics)){target="_blank"}" instead of "range".*

Express your answer using [interval notation](https://en.wikipedia.org/wiki/Interval_(mathematics)#Including_or_excluding_endpoints){target="_blank"}.

```{css, echo=F}
.thinsel select {
    width: 5em;
    margin-bottom: 0.5em;
    margin-top: 0.5em;
    margin-right: 0.5em;
    margin-left: 0.5em;
}
```

<div class="thinsel">

What is the domain? 

* [##ANSWER1##, ##ANSWER2##]

What is the range? 

* [##ANSWER3##, ##ANSWER4##]

</div>

Answerlist
--------

`r apast`
`r apast`
`r apast`
`r apast`


Solution
========

Because the curve is [continuous](https://en.wikipedia.org/wiki/Continuous_function){target="_blank"}, the domain is from the minimum $x$ value to the maximum $x$ value: $[`r min(x)`,\,`r max(x)`]$, and the range is from the minimum $y$ to the maximum $y$: $[`r min(y)`,\,`r max(y)`]$.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`
exname: domain_range