```{r data generation, echo = FALSE, results = "hide"}

f = function(x){
    return(x^3-x)
}

g = function(x,t){
    return(f(x+t))
}
h = function(x,t){
    return(f(x)+t)
}
m = function(x,t){
    return(f(t*x))
}
n = function(x,t){
    return(t*f(x))
}

t = c(seq(-10,10,2),seq(10,-10,-2))
x = seq(-50,50,0.01)
gt = list()
ht = list()
mt = list()
nt = list()
for(i in 1:length(t)){
    gt[[i]] = g(x,t[i])
    ht[[i]] = h(x,t[i])
    mt[[i]] = m(x,t[i])
    nt[[i]] = n(x,t[i])
}

lis = list(gt,ht,mt,nt)

ord = sample(1:4)
sol1 = paste0(1*(1:4==ord[1]),collapse="")
sol2 = paste0(1*(1:4==ord[2]),collapse="")
sol3 = paste0(1*(1:4==ord[3]),collapse="")
sol4 = paste0(1*(1:4==ord[4]),collapse="")

ach = c("g(x) = f(x+t)",
       "h(x) = f(x)+t",
       "m(x) = f(tx)",
       "n(x) = t*f(x)"
       )
al = paste0("* ",ach,collapse="\n")

```

Question
========

In [Desmos](https://www.desmos.com/calculator), define function $f$ with the equation below.
$$f(x)~=~x^3-x$$

Then, define the following four functions, and make a slider for $t$:
$$g(x)=f(x+t)$$
$$h(x)=f(x)+t$$
$$m(x)=f(tx)$$
$$n(x)=t\cdot f(x)$$

When slider $t$ is animated, with domain (-10,10), those four functions will exhibit the four different behaviors shown below. Match the animations below to the four functions.

### Animation 1

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(2,2)}
for(i in 1:length(t)){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    arrows(-10.3,0,10.3,0,0.1,10,3)
    arrows(0,-10.3,0,10.3,0.1,10,3)
    lines(x,lis[[ord[1]]][[i]],col="blue",lwd=2)
}
```
\

* Animation 1 matches ##ANSWER1##

### Animation 2

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(2,2)}
for(i in 1:length(t)){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    arrows(-10.3,0,10.3,0,0.1,10,3)
    arrows(0,-10.3,0,10.3,0.1,10,3)
    lines(x,lis[[ord[2]]][[i]],col="blue",lwd=2)
}
```
\

* Animation 2 matches ##ANSWER2##

### Animation 3

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(2,2)}
for(i in 1:length(t)){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    arrows(-10.3,0,10.3,0,0.1,10,3)
    arrows(0,-10.3,0,10.3,0.1,10,3)
    lines(x,lis[[ord[3]]][[i]],col="blue",lwd=2)
}
```
\

* Animation 3 matches ##ANSWER3##


### Animation 4

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(2,2)}
for(i in 1:length(t)){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    arrows(-10.3,0,10.3,0,0.1,10,3)
    arrows(0,-10.3,0,10.3,0.1,10,3)
    lines(x,lis[[ord[4]]][[i]],col="blue",lwd=2)
}
```
\

* Animation 4 matches ##ANSWER4##



Answerlist
--------

`r al`
`r al`
`r al`
`r al`


Solution
========

I'd recommend actually using Desmos as described. It should show you the answers.

* Animation 1 matches `r ach[ord[1]]`
* Animation 2 matches `r ach[ord[2]]`
* Animation 3 matches `r ach[ord[3]]`
* Animation 4 matches `r ach[ord[4]]`


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: stretch_graph