```{r data generation, echo = FALSE, results = "hide"}
xmin = -100
ymin = -100
xmax = 100
ymax = 100
np = 3
exp_types = sample(5:12,2,T)
et1 = exp_types[1]
et2 = exp_types[2]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]

exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "-M\\left(x-A\\right)",
               "-M x+A",
               "-M\\left(x+A\\right)",
               "-M x-A",
               "\\frac{-x-A}{M}",
               "\\frac{-x}{M}-A",
               "\\frac{A-x}{M}",
               "\\frac{-x}{M}+A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "-M\\cdot\\left(x-A\\right)",
               "-M\\cdot x+A",
               "-M\\cdot\\left(x+A\\right)",
               "-M\\cdot x-A",
               "\\frac{-x-A}{M}",
               "\\frac{-x}{M}-A",
               "\\frac{A-x}{M}",
               "\\frac{-x}{M}+A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

funcs = list(function(x,A,M){M*(x+A)},
             function(x,A,M){M*x+A},
             function(x,A,M){M*(x-A)},
             function(x,A,M){M*x-A},
             function(x,A,M){M*(A-x)},
             function(x,A,M){-M*x+A},
             function(x,A,M){-M*(x+A)},
             function(x,A,M){-M*x-A},
             function(x,A,M){-(x+A)/M},
             function(x,A,M){-x/M-A},
             function(x,A,M){(A-x)/M},
             function(x,A,M){-x/M+A},
             function(x,A,M){(x+A)/M},
             function(x,A,M){x/M+A},
             function(x,A,M){(x-A)/M},
             function(x,A,M){x/M-A}
             )

while(T){
    xold = numeric()
    yold = numeric()
    xnew = numeric()
    ynew = numeric()
    while(length(xold)<np){
        xo = sample(-100:100,1)
        yo = sample(-100:100,1)
        xn = funcs[[17-et1]](xo,a1,m1)
        yn = funcs[[et2]](yo,a2,m2)
        if(xn%%1==0 && yn%%1==0 && !(xo %in% xold) && !(yo %in% yold) && 
           xn>=xmin && xn<=xmax && yn>=ymin && yn<=ymax){
            xold = c(xold,xo)
            yold = c(yold,yo)
            xnew = c(xnew,xn)
            ynew = c(ynew,yn)
            }
    }
    xoldsorted = sort(xold)
    yoldunsorted = yold
    xnewunsorted = xnew
    ynewunsorted = ynew
    for(i in 1:length(xoldsorted)){
        j = which(xold==xoldsorted[i])
        yold[i] = yoldunsorted[j]
        xnew[i] = xnewunsorted[j]
        ynew[i] = ynewunsorted[j]
    }
    xold = xoldsorted
    if(min(xold)<0 && max(xold)>0 &&
       min(yold)<0 && max(yold)>0 &&
       min(xnew)<0 && max(xnew)>0 &&
       min(ynew)<0 && max(ynew)>0){break}
}


exp1 = exp_frames2[et2]
exp1 = gsub("A",a2,exp1,fixed=T)
exp1 = gsub("M",m2,exp1,fixed=T)
exp1 = gsub("x","f{\\left[arg\\right]}",exp1,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exp1,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

exb1 = exp_frames2[et2]
exb1 = gsub("A",a2,exb1,fixed=T)
exb1 = gsub("M",m2,exb1,fixed=T)
exb1 = gsub("x","f{\\left[a\\right]}",exb1,fixed=T)

argex = exp_frames[et1]
argex = gsub("A",a1,argex,fixed=T)
argex = gsub("M",m1,argex,fixed=T)

invarg = exp_frames[17-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

invsub = exp_frames2[17-et1]
invsub = gsub("A",a1,invsub,fixed=T)
invsub = gsub("M",m1,invsub,fixed=T)
invsub = gsub("x",xold[1],invsub,fixed=T)

# argwd = wd[et1]
# argwd = gsub("A",a1,argwd,fixed=T)
# argwd = gsub("M",m1,argwd,fixed=T)
# 
# invwd = wd[17-et1]
# invwd = gsub("A",a1,invwd,fixed=T)
# invwd = gsub("M",m1,invwd,fixed=T)


outex = exp_frames2[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

outex2 = exp_frames2[et2]
outex2 = gsub("A",a2,outex2,fixed=T)
outex2 = gsub("M",m2,outex2,fixed=T)
outex2 = gsub("x",yold[1],outex2,fixed=T)

ach = sort(unique(c(xnew,ynew)))
while(length(ach)<10){
    ach = sort(unique(c(ach,sample(-100:100,1))))
}

sols = character()
for(i in 1:np){
    sols = c(sols,paste0(1*(ach==xnew[i]),collapse=""))
}
for(i in 1:np){
    sols = c(sols,paste0(1*(ach==ynew[i]),collapse=""))
}

al = paste0("* ",ach,collapse="\n")
tal = paste0(rep(al,np*2),collapse="\n")


```

Question
========

Let $f$ be a function with three known input-output pairs, shown as solutions to the equation $b=f[a]$.

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(xold,yold)
colnames(df) = c("$a$","$b$")
kable(df) %>%
    kable_styling("bordered",full_width = F)
```

Find the corresponding solutions to the following equation: $$y~=~`r exp1`$$

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(paste0("##ANSWER",1:np,"##"),paste0("##ANSWER",(np+1):(2*np),"##"))
colnames(df) = c("$x$","$y$")
kable(df) %>%
    kable_styling("bordered",full_width = F)
```

Answerlist
--------

`r tal`


Solution
========

Restate the given equation.

$$y~=~`r exp1`$$

Set $f$'s argument equal to $a$.

$$`r argex`~=~a$$

Solve the equation for $x$. In other words, isolate $x$.

$$x~=~`r invarg`$$

Because we set $`r argex`$ equal to $a$, we can replace $`r argex`$ with $a$ in the main equation.

$$y=`r exb1`$$


We know $f[a]=b$, so replace $f[a]$ with $b$.

$$y~=~`r outex`$$

We now have two formulas: $x=`r invarg`$ and $y=`r outex`$. Use those formulas!

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(xold,yold,xnew,ynew)
colnames(df) = c("$a$","$b$","$x$","$y$")
kable(df) %>%
    kable_styling("bordered",full_width = F)
```

Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",np*2),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: bfa_to_ya_negs