---
output: slidy_presentation
title: "Function Features and Intervals"
author: "Mr. Worley"
date: "Tues Oct 14"
---

# Agenda

* Entrance ticket!
* Slides
* OCW_1014_A
* OCW_1014_B
* PCW_1014

# Function Features

* **Domain**
* **Range**
* **Increasing/decreasing**
* **Positive/negative**
* Extrema (local and global minimums and maximums)
    * We will cover these another day
* Intercepts (with $x$ axis or $y$ axis)
    * These you already know, and we will cover these another day.

# Interval notation

* Standard [interval notation](https://en.wikipedia.org/wiki/Interval_(mathematics)#Notations_for_intervals) looks kind of like the notation we use for [Cartesian coordinates](https://en.wikipedia.org/wiki/Cartesian_coordinate_system).
* Parentheses indicate an exclusive (open) boundary.
* Brackets indicate an inclusive (closed) boundary.
* A union symbol ($\cup$) indicates a [union](https://en.wikipedia.org/wiki/Union_(set_theory)) of multiple intervals.
* Examples:
    * $(3,5)$ means all real numbers between 3 and 5, but NOT including the boundaries. As an inequality, $3<x<5$.
    * $(3,5]$ means all real numbers between 3 and 5, but NOT including 3. As an inequality, $3<x\le 5$.
    * $[3,5)$ means all real numbers between 3 and 5, but NOT including 5. As an inequality, $3\le x < 5$.
    * $[3,5]$ means all real numbers between 3 and 5, including both boundaries. As an inequality, $3\le x \le 5$.
    

Using interval notation, express the real numbers highlighted on the number line below.

```{r,echo=F,fig.dim=c(8,2)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-2,2),axes=F,ann=F)
abline(h=0,lwd=1,col="black")
for(i in -10:10){
    lines(c(i,i),c(-0.5,0.5),col="black")
    text(i,-0.8,i,col="black")
}
x = list(c(-9,-5),c(-3,0),c(1,6),c(7,8))
fill = list(c("red","white"),c("red","red"),c("white","red"),c("white","white"))

for(i in 1:length(x)){
    xp = x[[i]]
    lines(xp,c(0,0),col="red",lwd=4)
    points(xp,c(0,0),pch=19,cex=1,col="red")
    points(xp,c(0,0),pch=19,cex=0.7,col=fill[[i]])
}
```

>* \
$$[-9,-5) ~\cup~ [-3,0] ~\cup~ (1,6] ~\cup~ (7,8)$$

\newpage

# Domain of a function

* The [domain](https://en.wikipedia.org/wiki/Domain_of_a_function) of a function describes the set of possible inputs (the possible $x$ values).
* Using interval notation, express the domain of the function shown below.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid = function(){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),col="grey",lwd=0.8)
        lines(c(i,i),c(-10,10),col="grey",lwd=0.8)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.5)
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.5)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    text(10,-0.5,"10",col="black")
    text(-0.5,10,"10",col="black")
    text(-10,-0.5,"-10",col="black")
    text(-0.5,-10,"-10",col="black")
    text(10.5,0.5,"x")
    text(0.5,10.5,"y")
}
mkgrid()

x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("blue","blue","white"),
          c("white","blue"),
          c("blue","blue","blue"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="blue")
    points(x[[i]],y[[i]],pch=19,col="blue")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}
```

>* Imagine the function flattening onto the $x$ axis.

>* \
```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()
x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("blue","blue","white"),
          c("white","blue"),
          c("blue","blue","blue"))
fc2 = list(c("red","red","white"),
          c("white","red"),
          c("red","red","red"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="blue")
    points(x[[i]],y[[i]],pch=19,col="blue")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
    lines(x[[i]],rep(0,length(x[[i]])),lwd=4,col="red")
    points(x[[i]],rep(0,length(x[[i]])),pch=19,col="red")
    points(x[[i]],rep(0,length(x[[i]])),pch=19,cex=0.7,col=fc2[[i]])
}
```

>* Domain: $$[-9,-4) ~\cup~ (-2,1) ~\cup~ [5,8]$$

\newpage

# Range of a function

* The [range](https://en.wikipedia.org/wiki/Range_of_a_function) of a function describes the set of possible outputs (the possible $y$ values).
* Using interval notation, express the range of the function shown below.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("blue","blue","white"),
          c("white","blue"),
          c("blue","blue","blue"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="blue")
    points(x[[i]],y[[i]],pch=19,col="blue")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}
```

>* Imagine the function flattening onto the $y$ axis.

>* \
```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()
x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("blue","blue","white"),
          c("white","blue"),
          c("blue","blue","blue"))
x2 = list(c(0,0),c(0,0))
y2 = list(c(-8,-4),c(-3,9))
fc2 = list(c("red","red"),c("red","white"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="blue")
    points(x[[i]],y[[i]],pch=19,col="blue")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}
for(i in 1:length(x2)){
    lines(x2[[i]],y2[[i]],lwd=4,col="red")
    points(x2[[i]],y2[[i]],pch=19,col="red")
    points(x2[[i]],y2[[i]],pch=19,cex=0.7,col=fc2[[i]])}

```

>* Range: $$[-8,-4]~\cup~[-3,9)$$

\newpage

# Where is function INCREASING?

* Follow curve left to right (like when reading English).
* I imagine an ant hiking left to right along the mountain ridges.
* If curve is going up, it is increasing.


```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("blue","blue","white"),
          c("white","blue"),
          c("blue","blue","blue"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="blue")
    points(x[[i]],y[[i]],pch=19,col="blue")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}

```

* Using function notation, express where the function is increasing. 
* Notice, on functions, we indicate "where" with the $x$ values.

>* \
```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("grey","grey","white"),
          c("white","grey"),
          c("grey","grey","grey"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="grey")
    points(x[[i]],y[[i]],pch=19,col="grey")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}
x2 = list(c(-9,-7,-4),c(7,8))
y2 = list(c(-3,2,4),c(-8,-4))
fc2 = list(c("red","red","white"),
          c("red","red"))
for(i in 1:length(x2)){
    lines(x2[[i]],y2[[i]],lwd=4,col="red")
    points(x2[[i]],y2[[i]],pch=19,col="red")
    points(x2[[i]],y2[[i]],pch=19,cex=0.7,col=fc2[[i]])
}
fc2 = list(c("purple","purple","white"),
          c("purple","purple"))
for(i in 1:length(x2)){
    lines(x2[[i]],rep(0,length(x2[[i]])),lwd=4,col="purple")
    points(x2[[i]],rep(0,length(x2[[i]])),pch=19,col="purple")
    points(x2[[i]],rep(0,length(x2[[i]])),pch=19,cex=0.7,col=fc2[[i]])
}
```


>* $$[-9,-4)~\cup~[7,8]$$

>* Although, if we want to get into a debate, I'd personally argue it is better to not include endpoints in intervals of increase/decrease. You can read a thorough treatment of this discussion here: [https://www.themathdoctors.org/open-or-closed-intervals-it-depends/](https://www.themathdoctors.org/open-or-closed-intervals-it-depends/)

>* In other words, I'd also accept $$(-9,-4)~\cup~(7,8)$$

\newpage

# Where is function DECREASING?

* Follow curve left to right (like when reading English).
* I imagine an ant hiking left to right along the mountain ridges.
* If curve is going down, it is decreasing.



```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("blue","blue","white"),
          c("white","blue"),
          c("blue","blue","blue"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="blue")
    points(x[[i]],y[[i]],pch=19,col="blue")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}

```




* Using function notation, express where the function is increasing. 
* Notice, on functions, we indicate "where" with the $x$ values.

>* \
```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-7,-4),c(-2,1),c(5,7,8))
y = list(c(-3,2,4),c(9,2),c(-5,-8,-4))
fc = list(c("grey","grey","white"),
          c("white","grey"),
          c("grey","grey","grey"))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col="grey")
    points(x[[i]],y[[i]],pch=19,col="grey")
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}
x2 = list(c(-2,1),c(5,7))
y2 = list(c(9,2),c(-5,-8))
fc2 = list(c("white","red"),
          c("red","red"))
for(i in 1:length(x2)){
    lines(x2[[i]],y2[[i]],lwd=4,col="red")
    points(x2[[i]],y2[[i]],pch=19,col="red")
    points(x2[[i]],y2[[i]],pch=19,cex=0.7,col=fc2[[i]])
}
fc2 = list(c("white","purple"),
          c("purple","purple"))
for(i in 1:length(x2)){
    lines(x2[[i]],rep(0,length(x2[[i]])),lwd=4,col="purple")
    points(x2[[i]],rep(0,length(x2[[i]])),pch=19,col="purple")
    points(x2[[i]],rep(0,length(x2[[i]])),pch=19,cex=0.7,col=fc2[[i]])
}
```


>* $$(-2,1]~\cup~[5,7]$$

>* Again, [we can argue](https://www.themathdoctors.org/open-or-closed-intervals-it-depends/) that the boundaries should not be included. So, I'd also accept $$(-2,1)~\cup~(5,7)$$

\newpage

# Where is function POSITIVE?

* A function is positive where it is above the $x$ axis.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-6,-4,-1),c(3,6,8))
y = list(c(-5,10,1,-2),c(4,-2,-3))
c1 = "white"
c2 = "blue"
fc = list(c(c1,c2,c2,c1),
          c(c2,c2,c2))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col=c2)
    points(x[[i]],y[[i]],pch=19,col=c2)
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}
```

* Using function notation, express where the function is positive. 
* (Remember, we are indicating $x$ values to denote "where" on a function.)

>* \
```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-6,-4,-1),c(3,6,8))
y = list(c(-5,10,1,-2),c(4,-2,-3))
c1 = "white"
c2 = "grey"
fc = list(c(c1,c2,c2,c1),
          c(c2,c2,c2))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col=c2)
    points(x[[i]],y[[i]],pch=19,col=c2)
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}

x = list(c(-8,-6,-4,-3),c(3,5))
y = list(c(0,10,1,-0),c(4,0))

c2 = "red"
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col=c2)
}
points(3,4,col=c2,pch=19)
```

>* The function is positive when $x$ is within the intervals indicated below:
$$(-8,-3)~\cup~[3,5)$$

>* Notice I am not including the $x$ intercepts, because 0 is not positive.

\newpage

# Where is function NEGATIVE?

* A function is negative where it is below the $x$ axis.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-6,-4,-1),c(3,6,8))
y = list(c(-5,10,1,-2),c(4,-2,-3))
c1 = "white"
c2 = "blue"
fc = list(c(c1,c2,c2,c1),
          c(c2,c2,c2))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col=c2)
    points(x[[i]],y[[i]],pch=19,col=c2)
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}
```

* Using function notation, express where the function is negative.

>* \
```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
mkgrid()

x = list(c(-9,-6,-4,-1),c(3,6,8))
y = list(c(-5,10,1,-2),c(4,-2,-3))
c1 = "white"
c2 = "grey"
fc = list(c(c1,c2,c2,c1),
          c(c2,c2,c2))
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col=c2)
    points(x[[i]],y[[i]],pch=19,col=c2)
    points(x[[i]],y[[i]],pch=19,cex=0.7,col=fc[[i]])
}

x = list(c(-9,-8),c(-3,-1),c(5,6,8))
y = list(c(-5,0),c(0,-2),c(0,-2,-3))

c2 = "red"
for(i in 1:length(x)){
    lines(x[[i]],y[[i]],lwd=4,col=c2)
}
points(-9,-5,col=c2,pch=19)
points(-9,-5,col=c1,pch=19,cex=0.6)
points(-1,-2,col=c2,pch=19)
points(-1,-2,col=c1,pch=19,cex=0.6)
points(8,-3,col=c2,pch=19)
```

>* The function is negative when $x$ is contained in the set of real numbers expressed below in interval notation:
$$(-9,-8)~\cup~(-3,-1)~\cup~(5,8]$$

>* Notice I am not including the $x$ intercepts, because 0 is not negative.


