---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

Name: \vspace{5pt} \hrule

## at1117paper: Complete the Square (v`r params$rseed`)


```{r,echo=F}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}
gcd2 <- function(a, b) {
    if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

```

```{r,echo=F}
n = 6
xy = sort(sample(8:30,2))
x = xy[1]
y = xy[2]
area = x^2+2*x*y

xs = c(x)
ys = c(y)
areas = c(area)

for(i in 1:(n-1)){
    while(T){
        xy = sort(sample(6:30,2))
        x = xy[1]
        y = xy[2]
        area = x^2+2*x*y
        if((!(x %in% xs))||(!(y %in% ys))){
            xs = c(xs,x)
            ys = c(ys,y)
            area = c(areas,area)
            break
        }
    }
}

```

### Question 1

```{r,echo=F}
i = 1
x = xs[i]
y = ys[i]
area = areas[i]
```

A wrap-around L-shaped patio will measure $y$ feet along one wall and $z$ feet along another wall. The patio will stick out $x$ feet from the walls, and the total area will be `r x^2+2*x*y` square feet. *Note: you can assume all angles are right angles.*

```{r,echo=F,fig.dim=c(2,2)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.1,1.1),axes=F,ann=F)
N = x+y
b = seq(0,1,length.out=N+1)


polygon(c(0,x/N,x/N,1,1,0),c(0,0,y/N,y/N,1,1),col="grey")
text(2*x/N/3,1-2*x/N/3,paste0(area," sqft"))


# polygon(c(0,x/N,x/N,0),c(y/N,y/N,1,1),col="grey")
# polygon(c(1,x/N,x/N,1),c(y/N,y/N,1,1),col="grey")
# polygon(c(0,x/N,x/N,0),c(0,0,y/N,y/N),col="grey")
# polygon(c(1,x/N,x/N,1),c(0,0,y/N,y/N),col="pink")

col1 = "black" #rgb(0.5,0.5,0)
col2 = "black" #rgb(0.5,0.2,0.2)

text(x/N/2,0,"x ft",cex=1.3,col=col1,adj=c(0.5,1.2))
text(1,(1-x/N/2),"x ft",cex=1.3,col=col1,srt=90,adj=c(0.5,1.2))

text(1-y/N/2,1-x/N,"y ft",cex=1.3,col=col2,adj=c(0.5,1.2))
text(x/N,(y/N/2),"z ft",cex=1.3,col=col2,srt=90,adj=c(0.5,1.2))

```
\

You know that the sum of $y$ and $z$ is `r 2*y`.

$$y+z=`r 2*y`$$

What value of $x$ satisfies the conditions stated above?




