---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

Name: \vspace{5pt} \hrule

## at1117paper: Complete the Square (v`r params$rseed`)


```{r,echo=F}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}
gcd2 <- function(a, b) {
    if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

```

```{r,echo=F}
n = 6
xy = sort(sample(8:30,2))
x = xy[1]
y = xy[2]
area = x^2+2*x*y

xs = c(x)
ys = c(y)
areas = c(area)

for(i in 1:(n-1)){
    while(T){
        xy = sort(sample(6:30,2))
        x = xy[1]
        y = xy[2]
        area = x^2+2*x*y
        if((!(x %in% xs))||(!(y %in% ys))){
            xs = c(xs,x)
            ys = c(ys,y)
            areas = c(areas,area)
            break
        }
    }
}

```

## Example

```{r,echo=F}
i = 1
x = xs[i]
y = ys[i]
area = areas[i]
```


A square's edge length is $x$ feet. A rectangle has a height of $x$ feet and a width of $`r 2*y`$ feet. Their combined area, found by adding the square's area and the rectangle's area, is $`r area`$ square feet. What is the value of $x$?

### Example's Solution

\color{red}
$$x^2+`r 2*y`x=`r area`$$

To complete the square, add $\left(\frac{`r 2*y`}{2}\right)^2=`r y^2`$ to both sides.
$$x^2+`r 2*y`x+`r y^2`=`r area+y^2`$$
Recognize the left side is now a perfect-square trinomial. Factor the left side.
$$(x+`r y`)^2=`r area+y^2`$$
Undo the squaring.
$$x+`r y`=\pm\sqrt{`r area+y^2`}$$
$$x+`r y`=\pm`r sqrt(area+y^2)`$$
Subtract `r y` from both sides.
$$x=-`r y`\pm`r sqrt(area+y^2)`$$
In this geometric example, we are only concerned about the positive solution. So, $$x=`r x`$$

\color{black}


## Question 1

```{r,echo=F}
i = i+1
x = xs[i]
y = ys[i]
area = areas[i]
```

A square's edge length is $x$ feet. A rectangle has a height of $x$ feet and a width of $`r 2*y`$ feet. The total area, of the square and rectangle, is $`r area`$ square feet. What is the value of $x$?


\vfill

```{r,echo=F,results="asis"}
if(params$showsol){
    cat("\\color{red}\n\n")
    eq1 = paste0("$$x^2+",2*y,"x=",area,"$$")
    cat(eq1)
    cat("\n")
    eq2 = paste0("$$x^2+",2*y,"x+",y^2,"=",area+y^2,"$$")
    cat(eq2)
    cat("\n")
    eq3 = paste0("$$(x+",y,")^2=",area+y^2,"$$")
    cat(eq3)
    cat("\n")
    eq4 = paste0("$$x+",y,"=\\pm",sqrt(area+y^2),"$$")
    cat(eq4)
    cat("\n")
    eq5 = paste0("$$x=",x,"$$")
    cat(eq5)
    cat("\n")
    cat("\\color{black}")
}

```

\vfill

\newpage 


## Question 2

```{r,echo=F}
i = i+1
x = xs[i]
y = ys[i]
area = areas[i]
```

A square's edge length is $x$ feet. A rectangle has a height of $x$ feet and a width of $`r 2*y`$ feet. The total area, of the square and rectangle, is $`r area`$ square feet. What is the value of $x$?


\vfill

```{r,echo=F,results="asis"}
if(params$showsol){
    cat("\\color{red}\n\n")
    eq1 = paste0("$$x^2+",2*y,"x=",area,"$$")
    cat(eq1)
    cat("\n")
    eq2 = paste0("$$x^2+",2*y,"x+",y^2,"=",area+y^2,"$$")
    cat(eq2)
    cat("\n")
    eq3 = paste0("$$(x+",y,")^2=",area+y^2,"$$")
    cat(eq3)
    cat("\n")
    eq4 = paste0("$$x+",y,"=\\pm",sqrt(area+y^2),"$$")
    cat(eq4)
    cat("\n")
    eq5 = paste0("$$x=",x,"$$")
    cat(eq5)
    cat("\n")
    cat("\\color{black}")
}

```

\vfill

## Question 3

```{r,echo=F}
i = i+1
x = xs[i]
y = ys[i]
area = areas[i]
```

A square's edge length is $x$ feet. A rectangle has a height of $x$ feet and a width of $`r 2*y`$ feet. The total area, of the square and rectangle, is $`r area`$ square feet. What is the value of $x$?


\vfill

```{r,echo=F,results="asis"}
if(params$showsol){
    cat("\\color{red}\n\n")
    eq1 = paste0("$$x^2+",2*y,"x=",area,"$$")
    cat(eq1)
    cat("\n")
    eq2 = paste0("$$x^2+",2*y,"x+",y^2,"=",area+y^2,"$$")
    cat(eq2)
    cat("\n")
    eq3 = paste0("$$(x+",y,")^2=",area+y^2,"$$")
    cat(eq3)
    cat("\n")
    eq4 = paste0("$$x+",y,"=\\pm",sqrt(area+y^2),"$$")
    cat(eq4)
    cat("\n")
    eq5 = paste0("$$x=",x,"$$")
    cat(eq5)
    cat("\n")
    cat("\\color{black}")
}

```

\vfill