```{r,echo=FALSE}
options(scipen=999)
xy = sort(sample(8:30,2))
x = xy[1]
y = xy[2]

area = x^2+2*x*y
```

Question
========

A wrap-around L-shaped patio will measure $y$ feet along one wall and $z$ feet along another wall. The patio will stick out $x$ feet from the walls, and the total area will be `r x^2+2*x*y` square feet. *Note: you can assume all angles are right angles.*

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.1,1.1),axes=F,ann=F)
N = x+y
b = seq(0,1,length.out=N+1)


polygon(c(0,x/N,x/N,1,1,0),c(0,0,y/N,y/N,1,1),col="grey")
text(2*x/N/3,1-2*x/N/3,paste0(area," sqft"))


# polygon(c(0,x/N,x/N,0),c(y/N,y/N,1,1),col="grey")
# polygon(c(1,x/N,x/N,1),c(y/N,y/N,1,1),col="grey")
# polygon(c(0,x/N,x/N,0),c(0,0,y/N,y/N),col="grey")
# polygon(c(1,x/N,x/N,1),c(0,0,y/N,y/N),col="pink")

col1 = "black" #rgb(0.5,0.5,0)
col2 = "black" #rgb(0.5,0.2,0.2)

text(x/N/2,0,"x ft",cex=1.3,col=col1,adj=c(0.5,1.2))
text(1,(1-x/N/2),"x ft",cex=1.3,col=col1,srt=90,adj=c(0.5,1.2))

text(1-y/N/2,1-x/N,"y ft",cex=1.3,col=col2,adj=c(0.5,1.2))
text(x/N,(y/N/2),"z ft",cex=1.3,col=col2,srt=90,adj=c(0.5,1.2))

```
\

You know that the sum of $y$ and $z$ is `r 2*y`.

$$y+z=`r 2*y`$$

What value of $x$ satisfies the conditions stated above?


Solution
========

It is easiest to just assume $y=z$ in order to make a square. So, divide `r 2*y` by two.

$$\frac{`r 2*y`}{2}~=~`r y`$$

We can write an equation by saying the sum of $x^2$ and $`r y`x$ and $`r y`x$ equals `r x^2+2*x*y`. These expressions represent the areas of a small square and two rectangles.

```{r,echo=F,fig.dim=c(4,4)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.1,1.1),axes=F,ann=F)
N = x+y
b = seq(0,1,length.out=N+1)


# polygon(c(0,x/N,x/N,1,1,0),c(0,0,y/N,y/N,1,1),col="grey")

polygon(c(0,x/N,x/N,0),c(y/N,y/N,1,1),col=rgb(1,1,0,0.7))
polygon(c(1,x/N,x/N,1),c(y/N,y/N,1,1),col=rgb(0,1,0,0.7))
polygon(c(0,x/N,x/N,0),c(0,0,y/N,y/N),col=rgb(0,1,0,0.7))

text(x/N/2,1-x/N/2,TeX(paste0("$x^2$ sqft")),col=rgb(0.5,0.5,0))
text(1-y/N/2,1-x/N/2,paste0(y,"x sqft"),col=rgb(0,0.5,0))
text(x/N/2,y/N/2,paste0(y,"x sqft"),col=rgb(0,0.5,0))

# polygon(c(1,x/N,x/N,1),c(0,0,y/N,y/N),col="pink")

col1 = "black" #rgb(0.5,0.5,0)
col2 = "black" #rgb(0.5,0.2,0.2)

text(x/N/2,-0.05,"x",cex=1.3,col=col1)
text(1.05,(1-x/N/2),"x",cex=1.3,col=col1)

text(1-y/N/2,1-x/N-0.05,y,cex=1.3,col=col2)
text(x/N+0.05,(y/N/2),y,cex=1.3,col=col2)

```
\

$$x^2+`r y`x+`r y`x~=~`r area`$$

Combine like terms.

$$x^2+`r 2*y`x~=~`r area`$$


There is a fun way to solve this. We will "complete the square". In this situation, we imagine adding some extra area to the picture to make a large square. In this case, we need to add a square with edge lengths of `r y`, adding `r y^2` square feet to the area.


```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.1,1.1),axes=F,ann=F)
N = x+y
b = seq(0,1,length.out=N+1)


polygon(c(0,x/N,x/N,1,1,0),c(0,0,y/N,y/N,1,1),col=rgb(0,0,1,0.5))
text(2*x/N/3,1-2*x/N/3,paste0(area," sqft"),col=rgb(0,0,0.8))

polygon(c(x/N,1,1,x/N),c(0,0,1-x/N,1-x/N),col=rgb(1,0,0,0.5))

text(1-y/N/2,y/N/2,paste0(y^2," sqft"),col=rgb(0.8,0,0))

# polygon(c(0,x/N,x/N,0),c(y/N,y/N,1,1),col="grey")
# polygon(c(1,x/N,x/N,1),c(y/N,y/N,1,1),col="grey")
# polygon(c(0,x/N,x/N,0),c(0,0,y/N,y/N),col="grey")
# polygon(c(1,x/N,x/N,1),c(0,0,y/N,y/N),col="pink")

col1 = "black" #rgb(0.5,0.5,0)
col2 = "black" #rgb(0.5,0.2,0.2)

text(x/N/2,-0.05,"x",cex=1.3,col=col1)
text(1.05,(1-x/N/2),"x",cex=1.3,col=col1)

text(1-y/N/2,-0.05,y,cex=1.3,col=col2)
text(1+0.05,(y/N/2),y,cex=1.3,col=col2)

```
\


$$x^2+`r 2*y`x+`r y^2`~=~`r area`+`r y^2`$$


$$x^2+`r 2*y`x+`r y^2`~=~`r area+y^2`$$

But, notice, if you look at the last picture, we have another way to represent the total area. The newly formed large square has side lengths of $x+`r y`$. So we can represent the total area of the large square as $(x+`r y`)^2$.

$$(x+`r y`)^2~=~`r area+y^2`$$

Undo the squaring on both sides. Use a calculator to find that $\sqrt{`r area+y^2`}=`r sqrt(area+y^2)`$.

$$x+`r y`~=~\pm `r sqrt(area+y^2)`$$

And, lastly, subtract `r y` from both sides of the equation.

$$x~=~-`r y` \pm  `r sqrt(area+y^2)`$$

We are only interesting in the positive value.


$$x~=~-`r y` +  `r sqrt(area+y^2)`$$

$$x~=~`r x`$$


Meta-information
============
extype: num
exsolution: `r x`
exname: complete_the_square_C