```{r,echo=FALSE}
options(scipen=999)
xy = sort(sample(8:30,2))
x = xy[1]
y = xy[2]
area = x^2+2*x*y
```

Question
========

The *not-drawn-to-scale* figure below is composed of a blue square and a red rectangle. Each of the square's lengths measures $x$ feet. The rectangle is $x$ feet tall and $`r 2*y`$ feet wide. 

```{r,echo=F,fig.dim=c(3,1)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.2,0.2),axes=F,ann=F)

col1 = rgb(0,0,1,0.5)
col2 = rgb(1,0,0,0.5)
col1t = rgb(0,0,1,0.5)
col2t = rgb(1,0,0,0.5)
polygon(c(0,0.2,0.2,0),c(0.1,0.1,-0.1,-0.1),col=col1)
polygon(c(1,0.3,0.3,1),c(0.1,0.1,-0.1,-0.1),col=col2)
text(0.1,0.1,"x",adj=c(0.5,-0.2))
text(0,0,"x",adj=c(1.2,0.5))
text(mean(c(0.3,1)),0.1,2*y,adj=c(0.5,-0.2))
text(0.3,0,"x",adj=c(1.2,0.5))

```
\

The total combined area, found by adding together the area of the square and the area of the rectangle, is $`r area`$ square feet.

What value of $x$ satisfies the conditions stated above?


Solution
========

Write the sum of areas in algebraic notation.

$$x^2+`r 2*y`x~=~`r area`$$

To visualize "completing the square", cut the rectangle in half, so divide `r 2*y` by two.

$$\frac{`r 2*y`}{2}~=~`r y`$$

Place those two halves to make an L-shaped figure.

```{r,echo=F,fig.dim=c(2,2)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,0.7),ylim=c(0.3,1.1),axes=F,ann=F)

polygon(c(0,0.2,0.2,0),c(0.8,0.8,1,1),col=col1)
polygon(c(0.55,0.2,0.2,0.55),c(0.8,0.8,1,1),col=col2)
polygon(c(0,0.2,0.2,0),c(0.8,0.8,0.45,0.45),col=col2)

text(0.1,1,"x",adj=c(0.5,-0.2))
text(0,0.9,"x",adj=c(1.2,0.5))

text(mean(c(0.2,0.55)),0.8,y,adj=c(0.5,1.2))
text(0.2,mean(c(0.8,0.45)),y,adj=c(0.5,1.2),srt=90)
```
\


Add some extra area to the picture to make a large square. In this case, we need to add a square with edge lengths of `r y`, adding `r y^2` square feet to the area.


```{r,echo=F,fig.dim=c(2,2)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.1,0.7),ylim=c(0.3,1.1),axes=F,ann=F)

col3 = rgb(1,1,0,0.7)

polygon(c(0,0.2,0.2,0),c(0.8,0.8,1,1),col=col1)
polygon(c(0.55,0.2,0.2,0.55),c(0.8,0.8,1,1),col=col2)
polygon(c(0,0.2,0.2,0),c(0.8,0.8,0.45,0.45),col=col2)
polygon(c(0.55,0.2,0.2,0.55),c(0.8,0.8,0.45,0.45),col=col3)

text(0.1,1,"x",adj=c(0.5,-0.2))
text(0,0.9,"x",adj=c(1.2,0.5))

text(mean(c(0.2,0.55)),0.45,y,adj=c(0.5,1.2))
text(0.55,mean(c(0.8,0.45)),y,adj=c(-0.2,0.5))
```
\


$$x^2+`r 2*y`x+`r y^2`~=~`r area`+`r y^2`$$


$$x^2+`r 2*y`x+`r y^2`~=~`r area+y^2`$$

But, notice, if you look at the last picture, we have another way to represent the total area. The newly formed large square has side lengths of $x+`r y`$. So we can represent the total area of the large square as $(x+`r y`)^2$.

$$(x+`r y`)^2~=~`r area+y^2`$$

Undo the squaring on both sides. Use a calculator to find that $\sqrt{`r area+y^2`}=`r sqrt(area+y^2)`$.

$$x+`r y`~=~\pm `r sqrt(area+y^2)`$$

And, lastly, subtract `r y` from both sides of the equation.

$$x~=~-`r y` \pm  `r sqrt(area+y^2)`$$

We are only interesting in the positive value.


$$x~=~-`r y` +  `r sqrt(area+y^2)`$$

$$x~=~`r x`$$


Meta-information
============
extype: num
exsolution: `r x`
exname: complete_the_square_E