```{r data generation, echo = FALSE, results = "hide"}
np = 5
while(T){
    x1 = sort(sample(-5:5,5)*2)
    y1 = sample(-5:5,5)*2
    m = diff(y1)/diff(x1)
    if(min(x1)<0 && min(y1)<0 && max(x1)>0 && max(y1)>0 && min(abs(diff(m)))>0){break}
}


hwo = sample(1:4,1)
vwo = sample(1:4,1)

hmoves = c("shift left by 2","shift right by 2","stretch by factor 2","shrink by factor 2")
hops = list(function(x){x-2},
            function(x){x+2},
            function(x){2*x},
            function(x){x/2})
hexp = c("x+2","x-2","\\frac{x}{2}","2x")
hct = c("a-2","a+2","2a","\\frac{a}{2}")

vmoves = c("shift down by 2","shift up by 2","stretch by factor 2","shrink by factor 2")
vops = list(function(x){x-2},
            function(x){x+2},
            function(x){2*x},
            function(x){x/2})
vexp = c("f{\\left(x\\right)}-2","f{\\left(x\\right)}+2","2\\cdot f{\\left(x\\right)}","\\frac{f{\\left(x\\right)}}{2}")
vct = c("b-2","b+2","2b","\\frac{b}{2}")

ca = paste0("g(x)~=~",gsub("x",hexp[hwo],vexp[vwo],fixed=T),collapse="")
x2 = hops[[hwo]](x1)
y2 = vops[[vwo]](y1)
ct = paste0("(a,b)\\to\\left(",hct[hwo],",",vct[vwo],"\\right)",collapse="")

# ach = character()
# while(length(ach)<6){
#     ach = unique(c(ach,paste0("g(x)~=~",gsub("x",hexp[sample(1:4,1)],vexp[sample(1:4,1)],fixed=T),collapse="")))
# }
# if(!(ca %in% ach)){
#     ach[1] == ca
# }

ach = character()
for(i in 1:4){
    for(j in 1:4){
        ach = c(ach,paste0("g(x)~=~",gsub("x",hexp[i],vexp[j],fixed=T),collapse=""))
    }
}
al = paste0("* $",ach,"$",collapse="\n")
sol = paste0(1*(ach==ca),collapse="")
```

Question
========

The blue curve represents $y=f(x)$. The red curve represents $y=g(x)$.

```{r,echo=F,fig.dim=c(8,4),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
lim = 20
plot(0,0,"n",xlim=c(-lim,lim),ylim=c(-lim,lim),axes=F,ann=F)

for(i in -lim:lim){
    lines(c(-lim,lim),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-lim,lim),col="grey",lwd=0.5)
}
for(i in seq(-lim,lim,5)){
    lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(lim,0,"x",adj=c(-0.3,1.2))
text(0,lim,"y",adj=c(1.2,-0.3))
lines(x1,y1,col="blue",lwd=1.4)
points(x1,y1,col="blue",pch=19,cex=0.5)
lines(x2,y2,col="red",lwd=1.4)
points(x2,y2,col="red",pch=19,cex=0.5)


plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("bottomleft",c(TeX("$y=f(x)$"),TeX("$y=g(x)$")),col=c("blue","red"),lwd=c(1.4,1.4))
```
\

What equation expresses the function transformation?

Answerlist
--------

`r al`


Solution
========

Horizontally, we have a `r hmoves[hwo]`. Vertically, we have a `r vmoves[vwo]`. As a coordinate transformation:
$$`r ct`$$
In the function-transformation equation, the horizontal transformation is indicated in the argument, and it is "backwards". The vertical transformation is indicated outside the function, and it is "normal".

$$`r ca`$$



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: H_left_V_stretch