---
output: 
  pdf_document:
    extra_dependencies: ["fancyhdr"]
fontsize: 12pt
params:
  num: "9999"
  mytitle: "PC 026 NO-CALC Mastery"
geometry: "left=3cm,right=3cm,top=3cm,bottom=3cm"
---

```{r,echo=F}
set.seed(as.numeric(params$num))
```

\setlength{\headheight}{18.0pt}

\fancyhead[L]{\sc{`r params$mytitle` v`r params$num`}}
\fancyhead[R]{\bf \large Name:\hspace{2in}}
\fancyfoot[R]{\sc Page \thepage ~ of 4}
\fancyfoot[C]{}
\pagestyle{fancy}


## Question 1

In terms of $\alpha$ and $\beta$, express all the lengths and other angle measures ($\theta$ and $\phi$).

\vspace{-25pt}

```{r,fig.dim=c(3,3),echo=F,fig.align='center'}
library(latex2exp)
a = pi/8
b = pi/5
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",ann=F,axes=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
yma = sin(a+b)
xma = cos(a)*cos(b)
lines(c(0,xma,xma,0,0),c(0,0,yma,yma,0))
lines(c(0,xma),c(0,sin(a)*cos(b)))
lines(c(0,cos(a+b),xma),c(0,sin(a+b),sin(a)*cos(b)))
lines(c(xma-0.02,xma-0.02,xma),c(0,0.02,0.02))
xc = cos(a)*cos(b)
yc = sin(a)*cos(b)
x1 = xc+0.02*cos(a+pi)
y1 = yc+0.02*sin(a+pi)
x2 = xc+0.02*sqrt(2)*cos(a+3*pi/4)
y2 = yc+0.02*sqrt(2)*sin(a+3*pi/4)
x3 = xc+0.02*cos(a+pi/2)
y3 = yc+0.02*sin(a+pi/2)
lines(c(x1,x2,x3),c(y1,y2,y3))
lines(c(xma,xma-0.02,xma-0.02),c(yma-0.02,yma-0.02,yma))
xmid = cos(a+b)/2
ymid = sin(a+b)/2
text(xmid+0.03*cos(a+b+pi/2),ymid+0.03*sin(a+b+pi/2),"1")
text(0.06/a*cos(a/2),0.06/a*sin(a/2),TeX("$\\alpha$"))
text(0.06/b*cos(a+b/2),0.06/b*sin(a+b/2),TeX("$\\beta$"))
xmid = cos(a)/2
ymid = sin(a)/2
text(xmid+0.03*cos(a+pi/2),ymid+0.03*sin(a+pi/2),"p")

xs = c(xma,cos(a+b))
ys = c(sin(a)*cos(b),yma)
th = atan2(diff(ys),diff(xs))
anngg = (th-pi/2)/2
text(xma+0.03/anngg*cos(anngg+pi/2),
     sin(a)*cos(b)+0.03/anngg*sin(anngg+pi/2),
     TeX("$\\theta$"))
xs = c(0,cos(a+b))
ys = c(0,yma)
th = atan(yma/cos(a+b))
anngg = (th)/2
text(xs[2]+0.03/anngg*cos(anngg+pi),
     ys[2]+0.03/anngg*sin(anngg+pi),
     TeX("$\\phi$"))

get_spot = function(xs,ys,r=0.03){
  xmid = mean(xs)
  ymid = mean(ys)
  th = atan2(diff(ys),diff(ys))
  return(c(xmid+r*cos(th+pi/2),ymid+r*cos(th+pi/2)))
}
xy = get_spot(c(xma,cos(a+b)),c(sin(a)*cos(b),yma))
text(xy[1],xy[2],"q")
text(xma/2,-0.03,"r")
text(xma+0.03,sin(a)*cos(b)/2,"s")
text(xma+0.03,sin(a)*cos(b)+cos(a)*sin(b)/2,"t")
text(xma-sin(a)*sin(b)/2,yma+0.03,"u")
text(cos(a+b)/2,yma+0.03,"v")
text(-0.03,yma/2,"w")
```
\

\vspace{-30pt}

\renewcommand{\arraystretch}{2.3}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Variable & \hfill ~~~~~~~~~~~~~~~~~~~~~Algebraic expression~~~~~~~~~~~~~~~~~~~~~ \hfill\\
\hline \hline
$p ~=$ & \\
\hline
$q ~=$ & \\
\hline
$r ~=$ & \\
\hline
$s ~=$ & \\
\hline
$\theta ~=$ & \\
\hline
$t ~=$ & \\
\hline
$u ~=$ & \\
\hline
$\phi ~=$ & \\
\hline
$v ~=$ & \\
\hline
$w ~=$ & \\
\hline
\end{tabular}
\end{center}

\newpage

## Question 2

The angle-sum and angle-difference identities are listed below:

$$\sin(\alpha\pm\beta) ~=~ \sin(\alpha)\cos(\beta)\pm\cos(\alpha)\sin(\beta)$$
$$\cos(\alpha\pm\beta) ~=~ \cos(\alpha)\cos(\beta)\mp\sin(\alpha)\sin(\beta)$$

```{r,echo=F,}
ai = sample(1:4,1)
a = c("\\frac{\\pi}{4}","\\frac{3\\pi}{4}",
      "\\frac{5\\pi}{4}","\\frac{7\\pi}{4}")[ai]
ad = c(45,135,225,315)[ai]
sina = c("\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{2}}{2}",
         "\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{2}}{2}")[ai]
cosa = c("\\frac{\\sqrt{2}}{2}","\\frac{-\\sqrt{2}}{2}",
         "\\frac{-\\sqrt{2}}{2}","\\frac{\\sqrt{2}}{2}")[ai]
bi = sample(1:8,1)
b = c("\\frac{\\pi}{6}","\\frac{\\pi}{3}",
      "\\frac{2\\pi}{3}","\\frac{5\\pi}{6}",
      "\\frac{7\\pi}{6}","\\frac{4\\pi}{3}",
      "\\frac{5\\pi}{3}","\\frac{11\\pi}{6}")[bi]
bd = c(30,60,120,150,210,240,300,330)[bi]
sinb = c("\\frac{1}{2}","\\frac{\\sqrt{3}}{2}",
         "\\frac{\\sqrt{3}}{2}","\\frac{1}{2}",
         "\\frac{-1}{2}","\\frac{-\\sqrt{3}}{2}",
         "\\frac{-\\sqrt{3}}{2}","\\frac{-1}{2}")[bi]
cosb = c("\\frac{\\sqrt{3}}{2}","\\frac{1}{2}",
         "\\frac{-1}{2}","\\frac{-\\sqrt{3}}{2}",
         "\\frac{-\\sqrt{3}}{2}","\\frac{-1}{2}",
         "\\frac{1}{2}","\\frac{\\sqrt{3}}{2}")[bi]

ord = sample(1:2)
fd = c(ad,bd)[ord[1]]
sd = c(ad,bd)[ord[2]]
wtf = sample(c("sin","cos"),1)
if(sample(1:2,1)==1){
  th = fd-sd
} else {
  th = fd+sd
}

wf = sample(1:2)
ang1 = c(ad,bd)[wf[1]]
sin1 = c(sina,sinb)[wf[1]]
cos1 = c(cosa,cosb)[wf[1]]
ang2 = c(ad,bd)[wf[2]]
sin2 = c(sina,sinb)[wf[2]]
cos2 = c(cosa,cosb)[wf[2]]
```


You know the following:

\begin{align*}
\sin(`r ang1`^{\circ})&=`r sin1` & \sin(`r ang2`^{\circ})&=`r sin2` \\\\
\cos(`r ang1`^{\circ})&=`r cos1` & \cos(`r ang2`^{\circ})&=`r cos2`
\end{align*}

Determine $\`r wtf`(`r th`^{\circ})$ exactly.

\newpage

## Question 3

Prove the (sine) double-angle identity: $\sin(2x) = 2\sin(x)\cos(x)$

*(Hint: start with an angle-sum formula from Question 2.)*

\vfill 

## Question 4

Prove the (cosine) double-angle identity: $\cos(2x) = 2\cos^2(x)-1$

*(Hint: start with an angle-sum formula from Question 2. Also, you will need to use the Pythagorean Identity: $\sin^2(x)+\cos^2(x)=1$)*

\vfill

\newpage

## Question 5

Prove the (cosine) half-angle identity: $\cos\left(\frac{\,y\,}{2}\right) = \pm\sqrt{\frac{1+\cos(y)}{2}}$.

*(Hint: start with the double-angle identity from Question 4.)*

\vfill

## Question 6

```{r,echo=F}
while(T){
  y = round(runif(1,10,85),0)*2
  yo2 = y/2
  cosy = round(cos(y*pi/180),2)
  if(sum(yo2==c(30,45,60,90))==0){break}
}
```

Given $\cos(`r y`^{\circ})\approx`r cosy`$, what is $\cos(`r yo2`^{\circ})$? Please set up an expression, but do **not** try to simplify or evaluate a decimal approximation.

*(Hint: $`r y`/2=`r yo2`$.)*

\vfill



