```{r data generation, echo = FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE)

while(T){

# Radii density: quadratic(roots @ 0 and 1) * exponential decay
parr = function(x,a,xmax=1){
  x = x/xmax
  (exp(-(a*x))*((a-2)*exp(a*x+a)+a^2*exp(a)*x^2+(2*a-a^2)*exp(a)*x+(2-a)*exp(a)))/((a-2)*exp(a)+a+2)*(x>0)*(x<1)+1*(x>=1)
  }
qarr = function(p,a,xmax=1){
  step = 1e-4
  xlist = c(seq(0,1-step,step),1-step/10,1-step/100,1-step/1000,1-step/1e4,1)
  plist = parr(xlist,a)
  if(length(p)==1){
    i = min(which(plist>=p))
  } else {
    i = numeric()
    for(p1 in p){
      i = c(i,min(which(plist>=p1)))
    }
  }
  xlist[i]*xmax
}
rarr = function(n,a,xmax=1){qarr(runif(n),a,xmax)}

makebullseye = function(scale=1,axes=T){
  x = cos(2*seq(0,pi,length.out=1000)*pi)*scale
  y = sin(2*seq(0,pi,length.out=1000)*pi)*scale
  plot(x,y,type="l",lwd=3,xlim=c(-scale,scale)*1.1,ylim=c(-scale,scale)*1.1,ann=F,axes=axes)
  lines(x=c(-1,1,1,-1,-1)*scale*1.1,y=c(1,1,-1,-1,1)*scale*1.1,lwd=4)
  colors = c("yellow","yellow","red","red","blue","blue","grey30","grey30","white","white")
  colors2 = lapply(colors, col2rgb)
  linecolors = c(rep("black",6),"white",rep("black",3))
  textcolors = c(rep("black",6),rep("white",2),rep("black",2))
  for(i in 10:1){
    x2 = x*i/10
    y2 = y*i/10
    polygon(x2[1:(length(x2)-1)],y2[1:(length(x2)-1)],col=colors[i],border=F)
    lines(x2,y2,col=linecolors[i])
  }
  points(0,0,pch=20,cex=0.5)
}

rb = seq(0,1,0.1)

a = runif(1,1.5,4)^2
rmax = runif(1,0.9,1.1)

pb = parr(rb,a,rmax)

probs = pb[2:length(pb)]-pb[1:(length(pb)-1)]
probs = c(probs,1-sum(probs))
points = 10:0
mu = round(sum(probs*points),2)
sigma = round(sqrt( sum((points-mu)^2*probs) ),2)



#sample
n = 12*sample(3:12,1)
r = rarr(n,a,rmax)
t = runif(n,0,2*pi)
pnt = points[ ceiling(r*10) ]
tot = sum(pnt)
xbar = round(tot/n,3)
se = round(sigma/sqrt(n),3)
z = round((xbar-mu)/se,2)
if(is.numeric(z) & z%%0.5>0.03 & z%%0.5<0.47){break}
}

alsol = function(ans,n=5,dx=1,spri=NULL){
    choices = ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx
    al = paste0("* ",choices,collapse="\n")
    if(!is.null(spri)){
        choices = round(ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx,spri)
        al = paste0("* ",sprintf(paste0("%.",spri,"f",collapse=""),choices),collapse="\n")
    }
    sol = paste0(1*(ans==choices),collapse="")
    return(data.frame(al,sol))
}

as1 = alsol(round(mu,2),5,0.01,2)
as2 = alsol(round(se,3),5,0.002,3)
as3 = alsol(round(z,2),5,0.02,2)
as4 = alsol(round(pnorm(z),4),5,0.0003,4)

```

Question
========

This question provides $\mu$, $\sigma$, $n$, and $\bar{x}$. You will characterize the [sampling distribution](https://en.wikipedia.org/wiki/Sampling_distribution) by finding the [standard error](https://en.wikipedia.org/wiki/Standard_error), calculate the [standard score](https://en.wikipedia.org/wiki/Standard_score), determine the [percentile rank](https://en.wikipedia.org/wiki/Percentile_rank) (expressed as a decimal), and translate the score into a rating (see below).

### Population

When Archie practices archery, each arrow has the same probability distribution (see [i.i.d](https://en.wikipedia.org/wiki/Independent_and_identically_distributed_random_variables){target="blank"}). This means her skill is constant, there is no [hot-hand effect](https://en.wikipedia.org/wiki/Hot_hand){target="blank"}, and there is no [maturity of chances](https://en.wikipedia.org/wiki/Gambler%27s_fallacy){target="blank"}.

Over many months, Archie has shot ten thousand arrows (their positions are shown below as dots).

```{r,fig.width=4,fig.height=4}
par(mar=c(0,0,0,0))
makebullseye(1,F)
n2 = 1e4
r2 = rarr(n2,a,rmax)
t2 = runif(n2,0,2*pi)
points(r2*cos(t2),r2*sin(t2),pch=20,cex=0.1,col=rgb(0,0,0,0.5))
```
\

From those many arrows, Archie has determined an accurate probability distribution (of the points scored by an arrow).

```{r fig.width=6,fig.height=4}
barplot(rev(probs),names.arg=rev(points),xlab="Points",ylab="Probability",main="Probability Distribution for Each Arrow")
```
\

Archie has determined her arrows' population mean and population standard deviation.
$$\mu=`r mu`$$
$$\sigma=`r sigma` $$

## Sampling distribution

Each day, Archie shoots `r n` arrows ($n=`r n`$) and determines that day's mean score. A mean of 10 would be a perfect day. We can treat each day's mean as a random variable with its own probability distribution: a [sampling distribution](https://en.wikipedia.org/wiki/Sampling_distribution){target="blank"}. We wish to characterize this sampling distribution. From the [central limit theorem](https://en.wikipedia.org/wiki/Central_limit_theorem){target="blank"}, we know the sampling distribution is approximately normal; however, we need to calculate the parameters: the mean and the standard error.


### Mean of the sampling distribution

The sampling distribution's mean is simply equal to the population mean.
$$\text{expected mean} = \mu $$

* What is the sampling distribution's mean?
* ##ANSWER1##

### Standard error (standard deviation of sampling distribution)

The standard error of a mean is the quotient of the population standard deviation and the square root of the sample size.
$$\text{standard error of mean} = \frac{\sigma}{\sqrt{n}}$$
This standard error is the standard deviation of the sampling distribution.

* What is the standard error of the sampling distribution?
* ##ANSWER2##

### Sample 

Today, Archie's mean score is `r xbar` points ($\bar{x} = `r xbar`$). 

```{r,fig.width=4,fig.height=4}
par(mar=c(0,0,0,0))
makebullseye(1,F)
points(r*cos(t),r*sin(t),pch=20)
```
\

### Standard score

Archie would like to know how well she did today. She wants you to calculate a standard score (a $z$ score). To calculate the standard score of a sample mean, you can use the following formula.
$$z = \frac{\bar x - \mu}{\sigma/\sqrt{n}}$$

* What is the $z$ score?
* ##ANSWER3##

### Cumulative probability (percentile rank)

Archie would like to know the probability that tomorrow she shoots worse than today. To estimate this, report the cumulative probability associated with the $z$-score you calculated. This can be done with a [$z$ table](https://en.wikipedia.org/wiki/Standard_normal_table#Conversion){target="blank"}, `pnorm` function in R, `NORM.DIST` function in a spreadsheet, or with other standard normal tools.

Remember, since we are using a $z$ score, the normal distribution parameters are mean=0 and sd=1.

* What is the probability that Archie shoots worse tomorrow?
* ##ANSWER4##

### Rating

Archie would like a rating for her day's performance. You decide to use the following scale and that if $z$ is on a boundary, Archie will be given the higher rating.

|    $z$ interval      | rating |
|:--------------------:|:---:|
|$-\infty$ to -1.51| F |
| -1.5     to -0.51| D |
| -0.5     to  0.49| C |
|  0.5     to  1.49| B |
|  1.5  to $\infty$ |  A |

```{r,fig.width=5,fig.height=3}
par(mar=c(5,0,0,0))
plot(0,0,type="n",xlim=c(-3,3),ylim=c(0,0.8),axes=F,xlab="z")
axis(1,at=seq(-1.5,1.5,1))
axis(1,at=-3:3)
abline(v=seq(-1.5,1.5,1))
text(c(-2.5,-1,0,1,2.5),rep(0.6,5),c("F","D","C","B","A"),cex=3)
bs = c(-10,-1.5,-0.5,0.5,1.5,10)
grades = c("F","D","C","B","A")
ans1 = rev((bs[1:5]<=z) & (bs[2:6]>z))
ans = paste0(ans1*1, collapse="")
g2 = rev(grades)
zzz = seq(-3,3,0.001)
lines(zzz,dnorm(zzz))
abline(h=0)
```
\

* Determine Archie's rating:  ##ANSWER5##

Answerlist
--------

`r as1$al`
`r as2$al`
`r as3$al`
`r as4$al`
* A
* B
* C
* D
* F

Solution
========

The sampling distribution is approximately normal with mean `r mu` and standard error `r sprintf("%.3f",round(sigma/sqrt(n),3))`.

$$\mathrm{SE} ~=~ \frac{\sigma}{\sqrt{n}} ~=~\frac{`r sigma`}{\sqrt{`r n`}} ~\approx~ `r sprintf("%.3f",round(sigma/sqrt(n),3))`$$

The $z$ score is found with the given formula.

$$z ~=~ \frac{\bar{x}-\mu}{\mathrm{SE}} ~=~ \frac{`r xbar`-`r mu`}{`r round(sigma/sqrt(n),3)`} ~\approx~ `r sprintf("%.2f",z)`$$

The sampling distribution can be visualized, along with today's mean (`r xbar`) highlighted in red. The cumulative probability is the sum of the probabilities of scores less than (or equal) `r xbar`. Thus, the area highlighted in blue represents the cumulative probability.

```{r fig.width=5,fig.height=4,fig.align='center'}
zzz = seq(-3,3,0.01)

minx = floor(mu*n-3*sigma*sqrt(n))
maxx = ceiling(mu*n+3*sigma*sqrt(n))
xb = seq(minx-0.5,maxx+0.5,1)
zb = (xb-mu*n)/(sigma*sqrt(n))
xm = seq(minx,maxx,1)
zm = (xm-mu*n)/(sigma*sqrt(n))
N = length(zb)
probs2 = pnorm(zb[2:N])-pnorm(zb[1:(N-1)])

par(mar=c(7,2,2,2))
plot(zzz,dnorm(zzz),type="l",axes=F,ann=F,col=rgb(0,0,0,0.5))
axis(1,at=-3:3,labels=round((mu+(-3:3)*sigma/sqrt(n)),2))
axis(1,at=-3:3,line=3)
mtext("z",1,5)

for(i in 1:length(xm)){
  lines(c(zb[i],zb[i],zb[i+1],zb[i+1]),
        c(0,probs2[i]*sigma*sqrt(n),probs2[i]*sigma*sqrt(n),0))
}
zbtot1 = (tot-0.5-mu*n)/(sigma*sqrt(n))
zbtot2 = (tot+0.5-mu*n)/(sigma*sqrt(n))

mtext("probability",2)
mtext(sprintf("Archie's sampling distribution (when n=%d)",n))
for(i in 1:sum(zm<z)){
  polygon(c(zb[i],zb[i],zb[i+1],zb[i+1]),
          c(0,dnorm(zm[i]),dnorm(zm[i]),0),
          col=rgb(0,0,1,0.5))
}
polygon(c(zbtot1,zbtot1,zbtot2,zbtot2),
        c(0,dnorm(z),dnorm(z),0),
        col=rgb(1,0,0))
```
\

To find the cumulative probability using a spreadsheet, you can use ``=NORM.DIST(`r z`,0,1,TRUE)``.
$$P(Z\le `r z`) ~=~ `r round(pnorm(z),4)`$$

By comparing the $z$ score to the grade chart, you find the proper rating is `r g2[ans1]`.


exsolution: `r as1$sol`|`r as2$sol`|`r as3$sol`|`r as4$sol`|`r ans`


Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r as1$sol`|`r as2$sol`|`r as3$sol`|`r as4$sol`|`r ans`
exname: Get z from sample mean