```{r data generation, echo = FALSE, results = "hide"}
library(exams)
options(scipen=100)
types = c("A","B","C","D")
fruit = c("apple","orange","banana","mango","plum","grapefruit","kiwi","lemon","papaya","apricot","persimmon","watermelon","pineapple","coconut")
mass = c(180,180,180,250,90,240,80,100,450,50,170,9000,2000,700)
is = sample(1:length(mass),4)
while(T){
  is = sample(1:length(mass),4)
  f = fruit[is]
  fs = paste(f,"s",sep="")
  mus = round(mass[is]*runif(4,0.7,1.3))
  sigs = round(mus/runif(4,6,20))
  ns = sample(5:12,4)^2
  ses = sigs/sqrt(ns)
  ps = runif(4,0.02,0.98)
  zs = round(qnorm(ps),2)
  xbars = signif(mus+zs*ses,4)
  zs = round((xbars-mus)/ses,2)
  ps = round(pnorm(zs),2)
  if(sum(zs>0)>=1 & sum(zs<0)>=1 & length(unique(abs(zs)))==4 & min(c(dist(abs(zs),method = "manhattan"))) > 0.1){
    break
  }
}

scs1 = mchoice2string(zs==max(zs))
scs2 = mchoice2string(zs==min(zs))
scs3 = mchoice2string(abs(zs)==min(abs(zs)))
scs4 = mchoice2string(abs(zs)==max(abs(zs)))
data = data.frame(f,mus,sigs,ns,xbars)
colnames(data) = c("fruit",
                   "mu",
                   "sigma",
                   "n",
                   "xbar")
write.csv(data,"fruit.csv",row.names=F)

tab1 = data.frame(f,mus,sigs)
colnames(tab1) = c("Type of fruit","$\\mu$, population mean mass in grams","$\\sigma$, population standard deviation in grams")
tab2 = data.frame(f,ns,xbars)
colnames(tab2) = c("Type of fruit","$n$, sample size","$\\bar{x}$, sample mean")


alsol = function(ans,n=5,dx=1,spri=NULL){
    choices = ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx
    al = paste0("* ",choices,collapse="\n")
    if(!is.null(spri)){
        choices = round(ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx,spri)
        al = paste0("* ",sprintf(paste0("%.",spri,"f",collapse=""),choices),collapse="\n")
    }
    sol = paste0(1*(ans==choices),collapse="")
    return(data.frame(al,sol))
}

as1 = alsol(zs[1],5,0.02,2)
as2 = alsol(ps[1],5,0.01,2)
as3 = alsol(zs[2],5,0.02,2)
as4 = alsol(ps[2],5,0.01,2)
as5 = alsol(zs[3],5,0.02,2)
as6 = alsol(ps[3],5,0.01,2)
as7 = alsol(zs[4],5,0.02,2)
as8 = alsol(ps[4],5,0.01,2)

```

Question
========

A farm produces 4 types of fruit: `r fs[1]`, `r fs[2]`, `r fs[3]`, and `r fs[4]`. The fruits' masses have population parameters dependent on the type of fruit. (All values are in grams.)

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab1, results="asis",echo=F}
knitr::kable(tab1,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```


A sample of each type is weighed. The results are shown below.

```{r tab2, results="asis",echo=F}
knitr::kable(tab2,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```

<!-- The population parameters and sample statistics can be [downloaded as a csv](fruit.csv){target="blank"}. -->

For each sample, determine the [standard score](https://en.wikipedia.org/wiki/Standard_score) and the [cumulative probability](https://en.wikipedia.org/wiki/Cumulative_distribution_function){target="blank"} by assuming the requirements for the [central limit theorem](https://en.wikipedia.org/wiki/Central_limit_theorem){target="blank"} are met. Then determine which sample mean is most unusually large, most unusually small, most typically sized, and most unusually sized.

The standard score of a sample mean:
$$z = \frac{\bar{x}-\mu}{\sigma/\sqrt{n}}$$

Some people prefer to call this denominator [the standard error](https://en.wikipedia.org/wiki/Standard_error){target="blank"}.
$$\text{standard error of mean} = \text{SE} = \frac{\sigma}{\sqrt{n}} $$
So the standard score ($z$-score) of a sample mean can also be expressed as
$$z = \frac{\bar{x}-\mu}{\text{SE}} $$

a. Calculate a $z$-score for the `r f[1]` sample mean. (Round to the nearest hundredth.)
* ##ANSWER1##
b. What proportion of `r f[1]` samples of size $n=`r ns[1]`$ have a smaller mean than the `r f[1]` sample?
* ##ANSWER2##
c. Calculate a $z$-score for the `r f[2]` sample mean. (Round to the nearest hundredth.)
* ##ANSWER3##
d. What proportion of `r f[2]` samples of size $n=`r ns[2]`$ have a smaller mean than the `r f[2]` sample?
* ##ANSWER4##
e. Calculate a $z$-score for the `r f[3]` sample mean. (Round to the nearest hundredth.)
* ##ANSWER5##
f. What proportion of `r f[3]` samples of size $n=`r ns[3]`$ have a smaller mean than the `r f[3]` sample?
* ##ANSWER6##
g. Calculate a $z$-score for the `r f[4]` sample mean. (Round to the nearest hundredth.)
* ##ANSWER7##
h. What proportion of `r f[4]` samples of size $n=`r ns[4]`$ have a smaller mean than the `r f[4]` sample?
* ##ANSWER8##
i. Which sample mean is most unusually large? 
* ##ANSWER9##
j. Which sample mean is most unusually small? 
* ##ANSWER10##
k. Which sample mean is most typically sized?
* ##ANSWER11##
l. Which sample mean is most unusually sized?
* ##ANSWER12##

Answerlist
--------

`r as1$al`
`r as2$al`
`r as3$al`
`r as4$al`
`r as5$al`
`r as6$al`
`r as7$al`
`r as8$al`
* The `r f[1]` sample mean is most unusually large.
* The `r f[2]` sample mean is most unusually large.
* The `r f[3]` sample mean is most unusually large.
* The `r f[4]` sample mean is most unusually large.
* The `r f[1]` sample mean is most unusually small.
* The `r f[2]` sample mean is most unusually small.
* The `r f[3]` sample mean is most unusually small.
* The `r f[4]` sample mean is most unusually small.
* The `r f[1]` sample mean is most typically sized.
* The `r f[2]` sample mean is most typically sized.
* The `r f[3]` sample mean is most typically sized.
* The `r f[4]` sample mean is most typically sized.
* The `r f[1]` sample mean is most unusually sized.
* The `r f[2]` sample mean is most unusually sized.
* The `r f[3]` sample mean is most unusually sized.
* The `r f[4]` sample mean is most unusually sized.


Solution
========

<!-- [video](https://vimeo.com/531938648){target="_blank"} -->

The formula to determine the $z$-score of a **sample mean** is the ratio shown below.

$$z = \frac{\bar{x}-\mu}{\sigma/\sqrt{n}} $$

The highest $z$-score (furthest right on [number line](https://en.wikipedia.org/wiki/Number_line){target="blank"}) corresponds to the most unusually large sample mean. 

The smallest $z$-score (furthest left on [number line](https://en.wikipedia.org/wiki/Number_line){target="blank"}) corresponds to the most unusually small sample mean.

The smallest [**absolute**](https://en.wikipedia.org/wiki/Absolute_value){target="blank"} $z$-score corresponds to the most usually sized sample mean.

The largest [**absolute**](https://en.wikipedia.org/wiki/Absolute_value){target="blank"} $z$-score corresponds to the most unusually sized sample mean.


### Spreadsheet:

By using the formulas, you should be able to get a spreadsheet like the one displayed here:

```{r fig.width=10,fig.height=5,echo=F}
draw_ss = function(df){
  nrow = length(df[,1])
  ncol = length(df[1,])
  par(mar=c(0,0,0,0))
  plot(0,0,type="n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
  hi = 1:((nrow+2)*2+1)
  vi = 1:((ncol+1)*2+1)
  hpos = seq(1,0,length.out=(nrow+2)*2+1)
  vpos = seq(0,1,length.out=(ncol+1)*2+1)
  hlin = hpos[hi%%2==1]
  ytex = hpos[hi%%2==0]
  vlin = vpos[vi%%2==1]
  xtex = vpos[vi%%2==0]
  abline(h=hlin)
  abline(h=hlin[2],lwd=3)
  abline(v=vlin)
  abline(v=vlin[2],lwd=3)
  for(i in 2:(ncol+1)){
    text(xtex[i],ytex[1],LETTERS[i-1],col=rgb(0.5,0.5,0.5))
    text(xtex[i],ytex[2],colnames(df)[i-1])
  }    
  for(i in 2:(nrow+2)){
    text(xtex[1],ytex[i],i-1,col=rgb(0.5,0.5,0.5))
  }
  for(i in 1:nrow){
    for(j in 1:ncol){
      text(xtex[j+1],ytex[i+2],df[i,j])
    }
  }
}

data2 = data.frame(f,mus,sigs,ns,xbars,signif(ses,4),zs,ps,abs(zs))
colnames(data2) = c("fruit",
                   "mu",
                   "sigma",
                   "n",
                   "xbar",
                   "SE",
                   "z",
                   "P(Z<z)",
                   "abs(z)")

draw_ss(data2)
```
\

<!-- ### To do this in R: -->

<!-- ```{r} -->
<!-- data = read.csv("fruit.csv", as.is=TRUE) -->
<!-- fruit = data$fruit -->
<!-- mu = data$mu -->
<!-- sigma = data$sigma -->
<!-- n = data$n -->
<!-- xbar = data$xbar -->

<!-- SE = sigma/sqrt(n) -->
<!-- z = round( (xbar-mu)/SE ,2) -->
<!-- cum_prob = round( pnorm(z) ,4) -->
<!-- data.frame(data,SE,z,cum_prob,abs(z)) -->

<!-- # Most unusually large -->
<!-- fruit[z==max(z)] -->

<!-- # Most unusually small -->
<!-- fruit[z==min(z)] -->

<!-- # Most typically sized -->
<!-- fruit[abs(z)==min(abs(z))] -->

<!-- # Most unusually sized -->
<!-- fruit[abs(z)==max(abs(z))] -->
<!-- ``` -->


* We use the formula for calculating the `r f[1]` sample-mean $z$ score.
$$z = \frac{`r xbars[1]`-`r mus[1]`}{`r sigs[1]`/\sqrt{`r ns[1]`}} = `r zs[1]` $$
* Use the [$z$ table](https://en.wikipedia.org/wiki/Standard_normal_table#Cumulative_(less_than_Z)) to find the cumulative probability.
$$P(Z<`r zs[1]`) = `r ps[1]` $$
* We use the formula for calculating the `r f[2]` sample-mean $z$ score.
$$z = \frac{`r xbars[2]`-`r mus[2]`}{`r sigs[2]`/\sqrt{`r ns[2]`}} = `r zs[2]` $$
* Use the $z$ table to find the cumulative probability.
$$P(Z<`r zs[2]`) = `r ps[2]` $$
* We use the formula for calculating the `r f[3]` sample-mean $z$ score.
$$z = \frac{`r xbars[3]`-`r mus[3]`}{`r sigs[3]`/\sqrt{`r ns[3]`}} = `r zs[3]` $$
* Use the $z$ table to find the cumulative probability.
$$P(Z<`r zs[3]`) = `r ps[3]` $$
* We use the formula for calculating the `r f[4]` sample-mean $z$ score.
$$z = \frac{`r xbars[4]`-`r mus[4]`}{`r sigs[4]`/\sqrt{`r ns[4]`}} = `r zs[4]` $$
* Use the $z$ table to find the cumulative probability.
$$P(Z<`r zs[4]`) = `r ps[4]` $$
* We determine the maximum $z$ score is $`r max(zs)`$, which belongs to the `r f[zs==max(zs)]`.
* We determine the minimum $z$ score is $`r min(zs)`$, which belongs to the `r f[zs==min(zs)]`.
* We determine the minimum [**absolute**](https://en.wikipedia.org/wiki/Absolute_value){target="blank"} $z$ score is $`r min(abs(zs))`$, which belongs to the `r f[abs(zs)==min(abs(zs))]`. 
* We determine the maximum [**absolute**](https://en.wikipedia.org/wiki/Absolute_value){target="blank"} $z$ score is $`r max(abs(zs))`$, which belongs to the `r f[abs(zs)==max(abs(zs))]`.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r as1$sol`|`r as2$sol`|`r as3$sol`|`r as4$sol`|`r as5$sol`|`r as6$sol`|`r as7$sol`|`r as8$sol`|`r scs1`|`r scs2`|`r scs3`|`r scs4`
exname: compare_zs_means