```{r data generation, echo = FALSE, results = "hide"}
ndec = 3
while(T){
    n = sample(c(20,30,40,50,60,70,100),1)
    p = sample(15:85,1)/100
    mu = p*n
    sig = sqrt(p*(1-p))*sqrt(n)
    bmin = ceiling(mu-2*sig)
    bmax = floor(mu+2*sig)
    
    lbrb = sample(bmin:bmax,2)+c(0.5,-0.5)
    lb = lbrb[1]
    rb = lbrb[2]
    bb = sort(sample(bmin:bmax,2))+c(-0.5,0.5)
    
    el = round(pbinom(lb,n,p),ndec)
    er = round(1-pbinom(rb,n,p),ndec)
    eb = round(pbinom(bb[2],n,p)-pbinom(bb[1],n,p),ndec)
    
    nl = round(pnorm(lb,mu,sig),ndec)
    nr = round(1-pnorm(rb,mu,sig),ndec)
    nb = round(pnorm(bb[2],mu,sig)-pnorm(bb[1],mu,sig),ndec)
    
    choices = sort(c(el,nl,er,nr,eb,nb))
    if(length(unique(choices))==6 && bb[2]-bb[1]>2 && min(choices)>0.01 && max(choices)<0.99 && min(diff(choices))>0.003) {break}
}

sch = sprintf("%.3f",choices)
al = paste0("* ",sch,collapse="\n")

san = sprintf("%.3f",c(el,nl,er,nr,eb,nb))

sol1 = paste0(1*(choices==el),collapse="")
sol2 = paste0(1*(choices==nl),collapse="")
sol3 = paste0(1*(choices==er),collapse="")
sol4 = paste0(1*(choices==nr),collapse="")
sol5 = paste0(1*(choices==eb),collapse="")
sol6 = paste0(1*(choices==nb),collapse="")

```

Question
========

Tyler has a `r p*100`% chance to hit each freethrow (so $p=`r p`$). Each freethrow is [independent](https://en.wikipedia.org/wiki/Independent_and_identically_distributed_random_variables).

Each day, Tyler attempts $n=`r n`$ freethrows. Each success gets 1 point. Each failure gets 0 points.

We can predict the distribution of points per day . We will use 2 strategies:

* An exact [binomial distribution](https://en.wikipedia.org/wiki/Binomial_distribution).
* A normal approximation.

```{r,echo=F,fig.dim=c(8,4)}
plot(0,0,"n",xlim=c(mu-3*sig,mu+3*sig),ylim=c(0,dnorm(mu,mu,sig)),xlab="Points",ylab="Probability",main=paste0("Probability Distribution  n=",n," p=",p,collapse=""))
xx = seq(mu-3*sig,mu+3*sig,sig/100)
yy = dnorm(xx,mu,sig)
lines(xx,yy,col="red")

db = function(llx,lly,w,h,col="blue"){
    lines(c(llx,llx,llx+w,llx+w,llx),c(lly,lly+h,lly+h,lly,lly),col=col)
}

for(i in round(mu-3*sig):round(mu+3*sig)){
    h = dbinom(i,n,p)
    db(i-0.5,0,1,h)
}

legend("topleft",legend=c("Exact binom","Norm approx"),col = c("blue","red"),lty = c(1,1))

```
\

* We can set up the exact binomial in [Desmos](https://www.desmos.com/calculator) using ``binomialdist(`r n`,`r p`)``

To set up the normal approximation, we need to find the mean and the standard deviation.

$$\mu = np$$
$$\sigma = \sqrt{np(1-p)}$$

* Once you get $\mu$ and $\sigma$, you can set up the normal approximation in [Desmos](https://www.desmos.com/calculator) using ``normaldist(``$\mu$``,``$\sigma$``)``


Please find the following probabilities:

1. Using the exact binomial, calculate $P(X<`r lb`)$. ##ANSWER1##
2. Using the normal approximation, calculate $P(X<`r lb`)$. ##ANSWER2##
3. Using the exact binomial, calculate $P(X>`r rb`)$. ##ANSWER3##
4. Using the normal approximation, calculate $P(X>`r rb`)$. ##ANSWER4##
5. Using the exact binomial, calculate $P(`r bb[1]`<X<`r bb[2]`)$. ##ANSWER5##
6. Using the normal approximation, calculate $P(`r bb[1]`<X<`r bb[2]`)$. ##ANSWER6##

*(Notice I already gave [half-integer](https://en.wikipedia.org/wiki/Half-integer) boundaries for the [continuity correction](https://en.wikipedia.org/wiki/Continuity_correction).)*

Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`
`r al`


Solution
========

### Answers

1. Exact: $P(X<`r lb`)=`r san[1]`$
2. Approx: $P(X<`r lb`)\approx`r san[2]`$
3. Exact: $P(X>`r rb`)=`r san[3]`$
4. Approx: $P(X>`r rb`)\approx`r san[4]`$
5. Exact: $P(`r bb[1]`<X<`r bb[2]`)=`r san[5]`$
6. Approx: $P(`r bb[1]`<X<`r bb[2]`)\approx`r san[6]`$

### How to: first find $\mu$ and $\sigma$ for normal approximation

$$\mu ~=~ pn ~=~ (`r p`)(`r n`) ~=~ `r mu`$$


$$\sigma ~=~ \sqrt{np(1-p)} ~=~ \sqrt{(`r n`)(`r p`)(1-`r p`)} ~=~ `r sig`$$

### 1.

In Desmos:

* Type in ``binomialdist(`r n`,`r p`)`` and click the magnifying glass.
* Check the box `Find Cumulative Probability (CDF)`
* Set Min$=-\infty$ and Max$=`r lb`$

### 2.

In Desmos:

* Type in ``normaldist(`r mu`,`r sig`)`` and click the magnifying glass.
* Check the box `Find Cumulative Probability (CDF)`
* Set Min$=-\infty$ and Max$=`r lb`$

### 3.

In Desmos:

* Type in ``binomialdist(`r n`,`r p`)`` and click the magnifying glass.
* Check the box `Find Cumulative Probability (CDF)`
* Set Min$=`r rb`$ and Max$=\infty$

### 4.

In Desmos:

* Type in ``normaldist(`r mu`,`r sig`)`` and click the magnifying glass.
* Check the box `Find Cumulative Probability (CDF)`
* Set Min$=`r rb`$ and Max$=\infty$

### 5.

In Desmos:

* Type in ``binomialdist(`r n`,`r p`)`` and click the magnifying glass.
* Check the box `Find Cumulative Probability (CDF)`
* Set Min$=`r bb[1]`$ and Max$=`r bb[2]`$

### 6.

In Desmos:

* Type in ``normaldist(`r mu`,`r sig`)`` and click the magnifying glass.
* Check the box `Find Cumulative Probability (CDF)`
* Set Min$=`r bb[1]`$ and Max$=`r bb[2]`$



Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`|`r sol6`
exname: binom_exact_and_approx