---
title: "Central Limit Theorem"
author: "Chad Worley"
date: "2024 Sep 20"
output: slidy_presentation
---

# [Central limit theorem](https://en.wikipedia.org/wiki/Central_limit_theorem)

Let $X$ represent a [random variable](https://en.wikipedia.org/wiki/Random_variable) that generates [independent and identically distributed](https://en.wikipedia.org/wiki/Independent_and_identically_distributed_random_variables) numbers. 

* You can visualize $X$ as a spinner.
* We can call $X$ the **population** that we sample from.

That random variable has an expected value (or population mean) and standard deviation.
$$\text{mean of }X=\mu$$
$$\text{SD of }X=\sigma$$

If we will average $n$ spins repeatedly, those averages will be **approximately normal** with the following parameters:
$$\text{mean of normal approx}=\mu$$
$$\text{SD of normal approx}=\frac{\sigma}{\sqrt{n}}$$

*This is true even if $X$ is NOT normally distributed. The approximation gets better with larger $n$.*


# Is the Central Limit Theorem important?

* Yes.
* Understanding the Central Limit Theorem is the most important step to unlocking the logic behind Statistics.
* Even if the population is not normal, averages (and totals) will be approximately normal.
* Remember how the normal (bell) curve kept showing up when we had averages of repetitions or sums of repetitions?

# Example: Dice

* Let random variable $X$ represent a fair 6-sided die. 

```{r,echo=F,fig.dim=c(7,3),fig.align='center'}
xs = 1:6
par(mar=c(2,3,1,1),pty="s",mfrow=c(1,2))
th = seq(0,2*pi,pi/100)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
begs = seq(0,2*pi-2*pi/(6),2*pi/(6))
mids = begs+pi/(6)
for(i in begs){
    lines(c(0,sin(i)),c(0,cos(i)))
}
for(i in 1:length(xs)){
    text(0.8*sin(mids[i]),0.8*cos(mids[i]),xs[i])
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

text(0,0,"X",cex=5)


barplot(rep(1/6,6),1,names.arg=1:6,ylab="probability")


mu = 3.5
sig = sqrt(35/12)

```

$$\mu = \frac{1+2+3+4+5+6}{6} = 3.5$$
$$\sigma = \sqrt{\frac{(-2.5)^2+(-1.5)^2+(-0.5)^2+0.5^2+1.5^2+2.5^2}{6}} = `r round(sig,4)`$$

# Example: Dice... (2d6)/2

* Let random variable $Y$ represent (2d6)/2, the average of 2 dice.
* There are 36 equally likely outcomes.

```{css, echo=F}
td, th {
    border: 1px solid black;
    padding: 10px;
    text-align: center;
}
.invisible {
    border: none;
    background-color:transparent;
}
.leftHeader {
    font-weight: bold;
    background-color:lightgray;
    padding: 10px;
}
th {
    background-color:lightgray;
}
```

<table>
    <thead>
        <tr>
            <th class="invisible"></th>
            <th>1</th>
            <th>2</th>
            <th>3</th>
            <th>4</th>
            <th>5</th>
            <th>6</th>
        </tr>
    </thead>
    <tbody>
        <tr>
            <td class="leftHeader">1</td>
            <td>1</td>
            <td>1.5</td>
            <td>2</td>
            <td>2.5</td>
            <td>3</td>
            <td>3.5</td>
        </tr>
        <tr>
            <td class="leftHeader">2</td>
            <td>1.5</td>
            <td>2</td>
            <td>2.5</td>
            <td>3</td>
            <td>3.5</td>
            <td>4</td>
        </tr>
        <tr>
            <td class="leftHeader">3</td>
            <td>2</td>
            <td>2.5</td>
            <td>3</td>
            <td>3.5</td>
            <td>4</td>
            <td>4.5</td>
        </tr>
        <tr>
            <td class="leftHeader">4</td>
            <td>2.5</td>
            <td>3</td>
            <td>3.5</td>
            <td>4</td>
            <td>4.5</td>
            <td>5</td>
        </tr>
        <tr>
            <td class="leftHeader">5</td>
            <td>3</td>
            <td>3.5</td>
            <td>4</td>
            <td>4.5</td>
            <td>5</td>
            <td>5.5</td>
        </tr>
        <tr>
            <td class="leftHeader">6</td>
            <td>3.5</td>
            <td>4</td>
            <td>4.5</td>
            <td>5</td>
            <td>5.5</td>
            <td>6</td>
        </tr>
    </tbody>
</table>


```{r,echo=F,fig.dim=c(8,4),fig.align='center'}
xs = c(rep(1,1),rep(1.5,2),rep(2,3),rep(2.5,4),rep(3,5),rep(3.5,6),rep(4,5),rep(4.5,4),rep(5,3),rep(5.5,2),rep(6,1))
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
th = seq(0,2*pi,pi/100)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
begs = seq(0,2*pi-2*pi/(36),2*pi/(36))
mids = begs+pi/(36)
for(i in begs){
    lines(c(0,sin(i)),c(0,cos(i)))
}
for(i in 1:length(xs)){
    text(0.8*sin(mids[i]),0.8*cos(mids[i]),xs[i])
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

text(0,0,"Y",cex=5)

x = seq(1,6,0.5)
p = c(1,2,3,4,5,6,5,4,3,2,1)/36
cp = cumsum(p)
acp = c(0,cp)
mids = (acp[2:length(acp)]-acp[1:(length(acp)-1)])/2+acp[1:(length(acp)-1)]

plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
for(cpp in cp){
    lines(c(0,sin(2*pi*cpp)),c(0,cos(2*pi*cpp)))
}
for(i in 1:length(x)){
    text(0.8*sin(2*pi*mids[i]),0.8*cos(2*pi*mids[i]),x[i])
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

text(0,0,"Y",cex=5)

```

```{r,echo=F,fig.dim=c(5,5)}
barplot(p,names.arg = x,ylab="probability",xlab="ave of 2 dice")
```

$$\mu = \frac{1\cdot 1 +1.5\cdot 2 +2\cdot 3 +2.5\cdot 4 +3\cdot 5 +3.5\cdot 6 +4\cdot 5 +4.5\cdot 4 +5\cdot 3 +5.5\cdot 2 +6\cdot 1}{36} = 3.5$$

* You can use the [standard deviation formula](https://en.wikipedia.org/wiki/Standard_deviation#Basic_examples) using all 36 possibilities to find $\sigma$.

$$\sigma = `r round(sig/sqrt(2),4)`$$

* We already learned [a shortcut](https://en.wikipedia.org/wiki/Algebra_of_random_variables#Variance_algebra_for_random_variables) to get $\sigma$ because we know the standard deviation of 1d6.

$$\frac{\sqrt{`r round(sig,4)`^2+`r round(sig,4)`^2}}{2} = \frac{`r round(sig,4)`}{\sqrt{2}} = `r round(sig/sqrt(2),4)`$$


# Example: Dice... (3d6)/3

* What about the average of 3 dice?
* If we have 3 dice, there are $`r 6^3`$ equally likely possibilities:

```{r,echo=F}
posses = numeric()
aves = numeric()
for(i in 1:6){
    for(j in 1:6){
        for(k in 1:6){
            posses = c(posses,100*i+10*j+k)
            aves = c(aves,round((i+j+k)/3,3))
        }
    }
}
pp = paste0(posses, collapse=", ")
ap = paste0(aves, collapse=", ")

mt = table(aves)
aposs = round(seq(1,6,0.33333333333333),2)
acnt = c(1,3,6,10,15,21,25,27,27,25,21,15,10,6,3,1)
aprb = round(acnt/6^3,3)
```

`r pp`

* We can find those averages.

`r ap`

* We can count how many times each average shows up.

| average | count | probability | density |
|:---:|:---:|:---:|:---:|
| 1 | 1 | `r round(1/216,3)` |  `r round(1/216,3)*3` |
| 1.333 | 3 | `r round(3/216,3)` |  `r round(3/216,3)*3` |
| 1.667 | 6 | `r round(6/216,3)` |  `r round(6/216,3)*3` |
| 2 | 10 | `r round(10/216,3)` |  `r round(10/216,3)*3` |
| 2.333 | 15 | `r round(15/216,3)` |  `r round(15/216,3)*3` |
| 2.667 | 21 | `r round(21/216,3)` |  `r round(21/216,3)*3` |
| 3 | 25 | `r round(25/216,3)` |  `r round(25/216,3)*3` |
| 3.333 | 27 | `r round(27/216,3)` |  `r round(27/216,3)*3` |
| 3.667 | 27 | `r round(27/216,3)` |  `r round(27/216,3)*3` |
| 4 | 25 | `r round(25/216,3)` |  `r round(25/216,3)*3` |
| 4.333 | 21 | `r round(21/216,3)` |  `r round(21/216,3)*3` |
| 4.667 | 15 | `r round(15/216,3)` |  `r round(15/216,3)*3` |
| 5 | 10 | `r round(10/216,3)` |  `r round(10/216,3)*3` |
| 5.333 | 6 | `r round(6/216,3)` |  `r round(6/216,3)*3` |
| 5.667 | 3 | `r round(3/216,3)` |  `r round(3/216,3)*3` |
| 6 | 1 | `r round(1/216,3)` |  `r round(1/216,3)*3` |


```{r,echo=F,fig.dim=c(6,6),fig.align='center'}
cp = cumsum(aprb)
x = aposs
acp = c(0,cp)
mids = (acp[2:length(acp)]-acp[1:(length(acp)-1)])/2+acp[1:(length(acp)-1)]

par(mar=c(0,0,0,0),pty="s")
th = seq(0,2*pi,pi/100)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
for(cpp in cp){
    lines(c(0,sin(2*pi*cpp)),c(0,cos(2*pi*cpp)))
}
for(i in 1:length(x)){
    if(aprb[i]>0.02){
        text(0.8*sin(2*pi*mids[i]),0.8*cos(2*pi*mids[i]),x[i])
    }
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

```

```{r,echo=F,fig.dim=c(10,5)}
barplot(aprb,names.arg = round(aposs,2),ylab="probability",xlab="ave of 3 dice",beside = T)
```

$$\mu = 3.5$$
$$\sigma = \frac{`r sig`}{\sqrt{3}} = `r round(sig/sqrt(3),4)`$$

# Example Dice... cumulative average

```{r,echo=F}
set.seed(2)
x = sample(1:6,25,T)
xpas = paste0(x,collapse=", ")
```

* I rolled a die 25 times: `r xpas`

* As I went, I kept recalculating the average.

$$\bar{x}_1 = \frac{`r x[1]`}{1} = `r mean(x[1])`$$
$$\bar{x}_2 = \frac{`r paste0(x[1:2],collapse="+")`}{2} = `r mean(x[1:2])`$$
$$\bar{x}_3 = \frac{`r paste0(x[1:3],collapse="+")`}{3} = `r mean(x[1:3])`$$
$$\bar{x}_4 = \frac{`r paste0(x[1:4],collapse="+")`}{4} = `r mean(x[1:4])`$$
$$\bar{x}_5 = \frac{`r paste0(x[1:5],collapse="+")`}{5} = `r mean(x[1:5])`$$
$$\bar{x}_6 = \frac{`r paste0(x[1:6],collapse="+")`}{6} = `r mean(x[1:6])`$$

* I plotted the average versus sample size. This is called a [cumulative average](https://en.wikipedia.org/wiki/Moving_average#Cumulative_average) curve or a running mean curve.

```{r,echo=F}
library(latex2exp)
set.seed(2)
x = sample(1:6,25,T)
xpas = paste0(x,collapse=", ")
ca = cumsum(x)/(1:length(x))
plot(1:length(x),ca,"l",xlab="n",ylab=TeX("$\\bar{x}_n$"),ylim=c(1,6))
abline(h=3.5,col="red",lty=3)
```

* Notice the cumulative average approaches $\mu=3.5$ as $n$ increases. This is a representation of the [law of large numbers](https://en.wikipedia.org/wiki/Law_of_large_numbers).

# Example Dice... overlapping cumulative-average curves

* This time I rolled 100 dice to make a cumulative-average curve. Then I repeated that process 1000 times. I plotted those 1000 cumulative-average curves.

```{r,echo=F,fig.dim=c(8,5)}
library(latex2exp)
set.seed(1)
x = sample(1:6,100*1000,T)
x = matrix(x,ncol=100)
myfun = function(y){
    return(cumsum(y)/(1:length(y)))
}
cx = list()
for(i in 1:1000){
    cx[[i]] = myfun(x[i,])
}
plot(0,0,"n",xlim=c(0,100),ylim=c(1,6),xlab="n",ylab=TeX("$\\bar{x}_n$"))
for(i in 1:1000){
    lines(1:100,cx[[i]],col=hsv((i/230)%%1,1,1,0.5))
}
abline(h=3.5,col="black",lty=3,lwd=3)

xme = seq(0.1,100,0.1)
ume = 3.5+2*sig/sqrt(xme)
lme = 3.5-2*sig/sqrt(xme)

lines(xme,ume,col="black",lwd=2)
lines(xme,lme,col="black",lwd=2)

text(60,5,TeX("$3.5+\\frac{2\\cdot 1.707}{\\sqrt{n}}$"))
text(60,2,TeX("$3.5-\\frac{2\\cdot 1.707}{\\sqrt{n}}$"))

text(90,5,TeX("$\\mu+\\frac{2 \\sigma}{\\sqrt{n}}$"))
text(90,2,TeX("$\\mu-\\frac{2 \\sigma}{\\sqrt{n}}$"))

text(20,5.5,"Color indicates\nrepetition")
```

* For each value of $n$, we can make a histogram of the 1000 current averages.

```{r,echo=F}
ma = t(simplify2array(cx))
breaks = list()
mids = list()
counts = list()
densities = list()
for(i in 1:100){
    bwm = min(i,20)
    myhist = hist(ma[,i],breaks=seq(1-1/bwm/2,6+1/bwm/2,1/bwm),plot=F)
    breaks[[i]] = myhist$breaks
    counts[[i]] = myhist$counts
    mids[[i]] = myhist$mids
    densities[[i]] = myhist$density
}

plot(0,0,"n",xlim=c(0,7),ylim=c(0,2.5),xlab="ave",ylab="density",main="Histograms as n grows from 1 to 100")
mycurves = list()
xxx = rep(breaks[[1]],each=2)
yyy = c(0,rep(densities[[1]],each=2),0)
lines(xxx,yyy,lwd=3,col="purple")
text(1,0.3,"n=1",col="purple")
for(i in 2:100){
    xxx = rep(breaks[[i]],each=2)
    yyy = c(0,rep(densities[[i]],each=2),0)
    lines(xxx,yyy,col=hsv(i/150,1,1))
}
xxx = rep(breaks[[100]],each=2)
yyy = c(0,rep(densities[[100]],each=2),0)
lines(xxx,yyy,lwd=3)
text(4,2.2,"n=100",adj=0)
text(1,2,"Color indicates n")
xxx = seq(0,7,0.1)
```

* We could have predicted this shape based on probabilities.

```{r,echo=F}
poss = list()
prob = list()
dens = list()

poss[[1]] = c(1,2,3,4,5,6)
prob[[1]] = rep(1/6,6)
dens[[1]] = prob[[1]]/diff(poss[[1]][1:2])

for(i in 2:6){
    oposs = poss[[i-1]]
    oprob = prob[[i-1]]
    nposs = c()
    nprob = c()
    for(j in 1:length(oposs)){
        for(k in 1:6){
            nposs = c(nposs,(oposs[j]*(i-1)+k)/i)
            nprob = c(nprob,oprob[j]/6)
        }
    }
    uposs = sort(unique(nposs))
    uprob = numeric()
    for(uposs1 in uposs){
        uprob = c(uprob,sum(nprob[uposs1==nposs]))
    }
    poss[[i]] = uposs
    prob[[i]] = uprob
    dens[[i]] = prob[[i]]/diff(poss[[i]][1:2])
}

plot(0,0,type="n",xlim=c(0,7),ylim=c(0,0.6),xlab="average",ylab="density")
xxx = seq(0,7,0.01)
lines(xxx,dnorm(xxx,3.5,sqrt(35/12)/sqrt(6)),col="red")
for(i in 1:6){
    lines(poss[[i]],dens[[i]],lwd=2,col=hsv(i/6,1,0.5))
    j = floor((length(poss[[i]])+1)/2)
    text(3.5,dens[[i]][j]-0.03+0.01*(i==3),paste0("n=",i),col=hsv(i/6,1,0.5))
}

text(1,0.5,"Normal approx with",col="red")
text(1,0.42,TeX("$\\mu=3.5$"),col="red")
text(1,0.3,TeX("$\\sigma=\\frac{1.7078}{\\sqrt{6}}$"),col="red")
```

* Notice the normal approximation is quite close. It gets better as $n$ increases.
* This animation might help.

```{r,animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(3,3)}
getR = function(u,t){
  ux = u[1]
  uy = u[2]
  uz = u[3]
  f = cos(t)+ux^2*(1-cos(t))
  g = ux*uy*(1-cos(t))-uz*sin(t)
  h = ux*uz*(1-cos(t))+uy*sin(t)
  i = uy*ux*(1-cos(t))+uz*sin(t)
  j = cos(t)+uy^2*(1-cos(t))
  k = uy*uz*(1-cos(t))-ux*sin(t)
  l = uz*ux*(1-cos(t))-uy*sin(t)
  m = uz*uy*(1-cos(t))+ux*sin(t)
  n = cos(t)+uz^2*(1-cos(t))
  R = matrix(c(f,g,h,i,j,k,l,m,n),3,byrow=T)
  return(R)
}

n = 40
R = getR(c(0,0,1),2*pi/n)
P = matrix(c(1,0,0,0,0,1),2,byrow = T)
par(pty="s",mar=c(0,0,0,0))

XX = list()
for(i in 1:6){
    mynums = numeric()
    for(j in 1:length(poss[[i]])){
        mynums = c(mynums,poss[[i]][j]-3.5,i-3.5,dens[[i]][j])
    }
    XX[[i]] = matrix(mynums,3)
}


XC = XX
for(i in 1:n){
    plot(0,0,type="n",axes=F,ann=F,xlim=c(-4,4),ylim=c(0,1))
    for(j in 1:6){
        Xc = XC[[j]]
        Xc_flat = P%*%Xc
        one = Xc_flat[1,][1]
        nn = length(Xc_flat[1,])
        las = Xc_flat[1,][nn]
        one2 = Xc_flat[2,][1]
        nn2 = length(Xc_flat[2,])
        las2 = Xc_flat[2,][nn]
        polygon(c(one,Xc_flat[1,],las),c(0,Xc_flat[2,],0),col=hsv(j/6,1,0.5,0.2),border=hsv(j/6,1,0.5))
        XC[[j]] = R%*%Xc
    }
}
```
\

# NOT JUST DICE!

* But the central limit theorem is not just about dice. 
* We can start with just about any spinner, and once $n>20$, the averages will be approximately normal.
* You can even see the progression toward a normal (bell-shaped) curve when $n$ is small.

* Fair coin

```{r,echo=F,fig.dim=c(10,5)}
par(mfrow=c(1,2),pty="s")
xs = 0:1
th = seq(0,2*pi,pi/100)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
begs = seq(0,2*pi-2*pi/(2),2*pi/(2))
mids = begs+pi/(2)
for(i in begs){
    lines(c(0,sin(i)),c(0,cos(i)))
}
for(i in 1:length(xs)){
    text(0.8*sin(mids[i]),0.8*cos(mids[i]),xs[i])
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

barplot(rep(1/2,2),1,names.arg=0:1,ylab="density")

```

* Average of two fair coins

```{r,echo=F,fig.dim=c(10,5)}
par(mfrow=c(1,2),pty="s")
xs = c(0,0.5,0.5,1)
th = seq(0,2*pi,pi/100)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
begs = seq(0,2*pi-2*pi/(4),2*pi/(4))
mids = begs+pi/(4)
for(i in begs){
    lines(c(0,sin(i)),c(0,cos(i)))
}
for(i in 1:length(xs)){
    text(0.8*sin(mids[i]),0.8*cos(mids[i]),xs[i])
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

barplot(c(0.25,0.5,0.25),1,names.arg=c(0,0.5,1),ylab="probability")

```

* Average of 3 fair coins (proportion heads after 3 flips)

```{r,echo=F,fig.dim=c(10,5)}
par(mfrow=c(1,2),pty="s")
xs = c(0,0.333,0.333,0.333,0.667,0.667,0.667,1)
nnn = length(xs)
th = seq(0,2*pi,pi/100)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
begs = seq(0,2*pi-2*pi/(nnn),2*pi/(nnn))
mids = begs+pi/(nnn)
for(i in begs){
    lines(c(0,sin(i)),c(0,cos(i)))
}
for(i in 1:length(xs)){
    text(0.8*sin(mids[i]),0.8*cos(mids[i]),xs[i])
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

barplot(c(0.125,0.375,0.375,0.125),1,names.arg=c(0,0.333,0.667,1),ylab="probability")

```

* Average of 4 fair coins (proportion of heads after 4 flips)

```{r,echo=F,fig.dim=c(10,5)}
par(mfrow=c(1,2),pty="s")
xs = c(0,rep(0.25,4),rep(0.5,6),rep(0.75,4),1)
nnn = length(xs)
th = seq(0,2*pi,pi/100)
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
lines(cos(th),sin(th))
begs = seq(0,2*pi-2*pi/(nnn),2*pi/(nnn))
mids = begs+pi/(nnn)
for(i in begs){
    lines(c(0,sin(i)),c(0,cos(i)))
}
for(i in 1:length(xs)){
    text(0.8*sin(mids[i]),0.8*cos(mids[i]),xs[i])
}
polygon(0.1*sin(th),0.1*cos(th),col="red")
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=7)
arrows(-0.6,-0.1,0.6,0.1,length=0.1,angle=25,lwd=5,col="red")
polygon(0.01*sin(th),0.01*cos(th),col="red")

xcv = sort(unique(xs))
ppp = numeric()
for(vcx in xcv){
    ppp=c(ppp,sum(xs==vcx)/length(xs))
}

barplot(ppp,1,names.arg=sort(unique(xs)),ylab="probability")

```


# Not just dice and coins





