```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
maxnum = 8
ezprimes = c(2,3,5)
primes = c(2,3,5,7,11,13)
while(T){
    n = sample(5:maxnum,1)
    p1 = sample(ezprimes,n-1,T,c(10,4,7))
    p2 = sample(primes,1)
    ps = c(p1,p2)
    C = prod(c(ps))
    if(C<1000){break}
}
num1 = sum(ps==2)
num2 = sum(ps==3)
num3 = sum(ps==5)
num4 = sum(ps==7)
num5 = sum(ps==11)
num6 = sum(ps==13)

nums = c(num1,num2,num3,num4,num5,num6)

ch = 0:maxnum

al = paste0("* ",ch,collapse="\n")
fal = paste0(rep(al,6),collapse="\n")

sol1 = paste0(1*(num1==ch),collapse="")
sol2 = paste0(1*(num2==ch),collapse="")
sol3 = paste0(1*(num3==ch),collapse="")
sol4 = paste0(1*(num4==ch),collapse="")
sol5 = paste0(1*(num5==ch),collapse="")
sol6 = paste0(1*(num6==ch),collapse="")

sols = c(sol1,sol2,sol3,sol4,sol5,sol6)
fsol = paste0(sols,collapse="|")

solexp = paste0(primes,"^{",nums,"}",collapse="\\cdot")
solexpshort = paste0(primes[nums!=0],"^{",nums[nums!=0],"}",collapse="\\cdot")

```


Question
========

A composite number was created by multiplying a sample (with repetition) of primes between 2 and 13.

* The composite: `r C`

Please factor the composite number into its [prime factorization](https://en.wikipedia.org/wiki/Fundamental_theorem_of_arithmetic).

```{css,echo=F}
.powerselect select {
    width : 7em;
}
.sml select {
    font-size: 0.8em;
    margin-bottom: 1em;
    margin-top: 0.5em;
    margin-right: 0.5em;
    margin-left: 0em;
}
```

<div class="powerselect">

* The prime factorization: 

$`r C`~=~2$<sup class="sml">##ANSWER1##</sup>$\cdot 3$<sup class="sml">##ANSWER2##</sup>$\cdot 5$<sup class="sml">##ANSWER3##</sup>$\cdot 7$<sup class="sml">##ANSWER4##</sup>$\cdot 11$<sup class="sml">##ANSWER5##</sup>$\cdot 13$<sup class="sml">##ANSWER6##</sup>

</div>

Answerlist
--------

`r fal`


Solution
========

You can make a [factor tree](https://en.wikipedia.org/wiki/Integer_factorization#Prime_decomposition).

```{r,echo=F,fig.dim=c(7,3)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,7),ylim=c(0,3),axes=F,ann=F)
sps = sort(ps)
dx = 6/n
tot = C
for(i in 1:n){
    if(i<n){
        text(1+(i-1)*dx-0.2*dx,1,sps[i],col="red")
        text(1+(i-1)*dx,2,tot,col="black")
        lines(c(1+(i-1)*dx+0.2,1+(i-1)*dx+0.8*dx),c(2,2))
        lines(c(1+(i-1)*dx-0.1,1+(i-1)*dx-0.2),c(1.6,1.3))
    } else {
        text(1+(i-1)*dx,2,tot,col="red")
    }
    tot = round(tot/sps[i])
}
```

We can express `r C` as a product of primes.

$$`r C`~=~ `r paste0(sps,collapse="\\cdot")`$$

Repeated multiplication can be expressed with powers.

$$`r C`~=~ `r solexpshort`$$

For this problem, we want all the exponents for primes between 2 and 13 to be expressed explicitly (so we include some exponents of 0).

$$`r C`~=~ `r solexp`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r fsol`
exname: prime_factorization