```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
poss = -6:6
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
while(T){
  r = sample(poss,3,TRUE)
  if(sum(r==0)<1){break}
}
ex1 = paste0("(x-",r[1],")*(x-",r[2],")*(x-",r[3],")",collapse="")
ex1 = gsub("--","+",ex1,fixed=TRUE)
ex2 = paste0("(x-",r[1],")(x-",r[2],")(x-",r[3],")",collapse="")
ex2 = gsub("--","+",ex2,fixed=TRUE)
ex2 = gsub("-0","",ex2,fixed=TRUE)
anli = paste0("* ",poss,"\n",collapse="")
sol = rep(0,length(poss))
for(rr in r){
  sol[poss==rr] = 1
}
sol = paste0(sol,collapse="")
a = 1
b = -sum(r)
c = r[1]*r[2]+r[2]*r[3]+r[1]*r[3]
d = -r[1]*r[2]*r[3]
```


Question
========

```{python,echo=FALSE}
from sympy import *
x = symbols("x")
qex = sympify(r.ex1)
ex = expand(qex)
qex = latex(ex)
```

Factor the cubic polynomial $`r py$qex`$ to find solutions to the cubic equation:
$$`r py$qex`=0$$

*Hint: all solutions are integers between `r min(poss)` and `r max(poss)`*.

You might find the [rational root theorem](https://en.wikipedia.org/wiki/Rational_root_theorem) helpful. I'd recommend using [synthetic division](https://en.wikipedia.org/wiki/Synthetic_division) to check your guesses until you find one linear factor, then you'll just need to factor the quadratic factor into two linear factors.

Answerlist
-------
`r anli`


Solution
========

<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
</style>

```{r,echo=FALSE,results='asis'}
rrr = sort(unique(r))
for(i in 1:length(rrr)){
  rr = rrr[i]
  cat(paste0("## Possible successful route ",i,"\n\n",collapse=""))
  cat("<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
</style>")
  cf = c(a,b,c,d)
  bots = c(cf[1])
  mids = numeric()
  deg = length(cf)
  for(i in 2:deg){
    mids = c(mids,bots[i-1]*rr)
    bots = c(bots,cf[i]+mids[i-1])
  }
  trs = paste0("* Guess that $(x-",rr,")$ is a factor:\n<table style='width:50%'><tr><td class='r'></td>",collapse="")
  trs = gsub("--","+",trs,fixed=TRUE)
  for(i in 1:deg){
    trs = paste0(trs,"<td>",cf[i],"</td>")
  }
  trs = paste0(trs,"</tr><tr><td class='r'>",rr,"</td><td class='b'></td>")
  for(i in (deg+2):(2*deg)){
    trs = paste0(trs,"<td class='b'>",mids[i-deg-1],"</td>")
  }
  trs = paste0(trs,"</tr><tr><td class='r'> </td>")
  for(i in (2*deg+1):(3*deg)){
    trs = paste0(trs,"<td>",bots[i-2*deg],"</td>")
  }
  trs = paste0(trs,"</tr></table>\n")
  cat(trs)
  so = "Notice, the remainder is 0, so the guess was good! So, we rephrase the original equation into a semi-factored form."
  eq = paste0("$$(",pfix(c(1,-rr),1:0),")(",pfix(c(1,bots[2],bots[3]),2:0),")=0$$",collapse="")
  cat(so)
  cat(eq)
  cat("Then factor the quadratic expression to get the fully factored form of the equation.")
  cat(paste0("$$",ex2,"=0$$"))
  cat(paste0("Thus the solutions are: {",paste0(rrr,collapse=", "),"}"))
  cat("\n\n")
}
```

<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
</style>



Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: cubic_easy