```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
while(T){
  rr = sample(1:6,1)*sample(c(-1,1),1)
  aa = sample(1:9,1)*sample(c(-1,1),1)
  bb = sample(1:9,1)
  a = 1
  b = -(rr+2*aa)
  c = 2*aa*rr+aa^2+bb^2
  d = -rr*(aa^2+bb^2)
  cf = c(a,b,c,d)
  if(max(abs(cf))<100){break}
}
ex1 = paste0("x^3+",b,"x^2+",c,"x+",d,collapse="")
ex1 = gsub("+-","-",ex1,fixed=TRUE)
ex1 = gsub("+1x","+x",ex1,fixed=TRUE)
ex1 = gsub("-1x","-x",ex1,fixed=TRUE)
ex1 = gsub("+0x^2","",ex1,fixed=TRUE)
ex1 = gsub("+0x","",ex1,fixed=TRUE)
ex1 = gsub("+0","",ex1,fixed=TRUE)
sel = -10:10
anli = paste0("* ",sel,"\n",collapse="")
sol1 = paste0(1*(sel==rr),collapse="")
sol2 = paste0(1*(sel==aa),collapse="")
sol3 = paste0(1*(sel==bb),collapse="")
sol4 = paste0(1*(sel==aa),collapse="")
sol5 = paste0(1*(sel==bb),collapse="")
cn1 = gsub("1i","i",paste0(aa,"-",bb,"i"))
cn2 = gsub("1i","i",paste0(aa,"+",bb,"i"))
fff = paste0("(x-(",rr,"))(x-(",cn1,"))(x-(",cn2,"))")
```


Question
========

Solve:

$$`r ex1`=0$$

<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
select {
  width: 70px;
}
</style>

* The real solution: ##ANSWER1##
* The first complex solution: ##ANSWER2##-##ANSWER3##$i$
* The other complex solution: ##ANSWER4##+##ANSWER5##$i$


*Hint: the real solution is an integer between -6 and 6. Also the [rational root theorem](https://en.wikipedia.org/wiki/Rational_root_theorem) places additional constraints on possible real solutions. [Descarte's rule of signs](https://en.wikipedia.org/wiki/Descartes%27_rule_of_signs) can also help eliminate possibilities.*

Answerlist
--------
`r anli`
`r anli`
`r anli`
`r anli`
`r anli`

Solution
========

```{r,echo=FALSE,results='asis'}
cat("<style>
.r {
border-right: 1px solid black;
}
.b {
border-bottom: 1px solid black;
}
td {
height: 13pt;
text-align: center;
}
</style>")
cf = c(a,b,c,d)
bots = c(cf[1])
mids = numeric()
deg = length(cf)
for(i in 2:deg){
  mids = c(mids,bots[i-1]*rr)
  bots = c(bots,cf[i]+mids[i-1])
}
trs = paste0("* Guess that $(x-",rr,")$ is a factor:\n<table style='width:50%'><tr><td class='r'></td>",collapse="")
trs = gsub("--","+",trs,fixed=TRUE)
for(i in 1:deg){
  trs = paste0(trs,"<td>",cf[i],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r'>",rr,"</td><td class='b'></td>")
for(i in (deg+2):(2*deg)){
  trs = paste0(trs,"<td class='b'>",mids[i-deg-1],"</td>")
}
trs = paste0(trs,"</tr><tr><td class='r'> </td>")
for(i in (2*deg+1):(3*deg)){
  trs = paste0(trs,"<td>",bots[i-2*deg],"</td>")
}
trs = paste0(trs,"</tr></table>\n")
cat(trs)
so = "Notice, the remainder is 0, so the guess was good! So, we rephrase the original equation into a semi-factored form."
eq = paste0("$$(",pfix(c(1,-rr),1:0),")(",pfix(c(1,bots[2],bots[3]),2:0),")=0$$",collapse="")
cat(so)
cat(eq)
a = 1
b = bots[2]
c = bots[3]
cat("\nI would recommend using quadratic formula to determine the complex roots.")
cat(paste0("$$a=",a,"$$\n$$b=",b,"$$\n$$c=",c,"$$\n\n"))
```

Plug numbers into the quadratic formula.

$$x = \frac{-(`r b`)\pm\sqrt{(`r b`)^2-4(`r a`)(`r c`)}}{2(`r a`)} $$

Simplify.

$$x = \frac{`r -b` \pm \sqrt{`r b^2-4*a*c`}}{`r 2*a`}$$

$$x = \frac{`r -b` \pm `r sqrt(-b^2+4*a*c)`i}{`r 2*a`}$$

$$x = `r cn2` ~~~~~~~~\text{  OR  }~~~~~~~~ x=`r cn1`$$

We could rewrite the original equation in fully factored form.

$$\Big(x-(`r rr`)\Big)\cdot\Big(x-(`r cn1`)\Big)\cdot\Big(x-(`r cn2`)\Big)~~=~~0$$

The solutions are:
$$x = `r rr`$$
$$x = `r cn1`$$
$$x = `r cn2`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`
exname: cubic_complex