```{r,echo=FALSE}
options(scipen=999)
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
cn = function(re,im){
    com = paste0(re,"+{",im,"}i")
    com = gsub("+{0}i","",com,fixed=T)
    com = gsub("+{1}i","+i",com,fixed=T)
    com = gsub("+{-1}i","-i",com,fixed=T)
    com = gsub("+{-","-{",com,fixed=T)
    com = gsub("0+","",com,fixed=T)
    com = gsub("0-","-",com,fixed=T)
    return(com)
}

# factored form: (x-m)*(x-(n+p*i))*(x-(n-p*i))
#                (x-m)*(x^2-2*n*x+(n^2+p^2))
# x^3  - m*x^2 - 2*n*x^2  + 2*m*n*x + n^2*x + p^2*x  - m*n^2 - m*p^2 

mposs = c(-6:-1,1:6)
nposs = c(-6:-1,1:6)
pposs = 1:6

m = sample(mposs,1)
n = sample(nposs,1)
p = sample(pposs,1)
A = 1
B = -2*n-m
C = n^2+p^2+2*m*n
D = -m*(n^2+p^2)

all1 = numeric()
all2 = numeric()
all3 = numeric()
for(mm in mposs){
    for(nn in nposs){
        for(pp in pposs){
            bbb = -2*nn-mm
            ccc = nn^2+pp^2-2*mm*nn
            ddd = -mm*(nn^2+pp^2)
            all1 = sort(unique(c(all1,bbb)))
            all2 = sort(unique(c(all2,ccc)))
            all3 = sort(unique(c(all3,ddd)))
        }
    }
}

al1 = paste0("* ",all1,collapse="\n")
al2 = paste0("* ",all2,collapse="\n")
al3 = paste0("* ",all3,collapse="\n")

sol1 = paste0(1*(B==all1),collapse="")
sol2 = paste0(1*(C==all2),collapse="")
sol3 = paste0(1*(D==all3),collapse="")

```


Question
========

A cubic polynomial, $f(x)$, is generated by randomly selecting the three **real** parameters, $B$, $C$, and $D$, in the equation below.

$$f(x)~=~x^3+Bx^2+Cx+D$$

You know the graph $y=f(x)$ has one real root at $x=`r m`$. You are told that another (complex) root is $x=`r cn(n,p)`$.

```{r,echo=F,fig.dim=c(8,6)}
# xmi = (-bb+sqrt(bb^2-4*aa*cc))/(2*aa)
# xma = (-bb-sqrt(bb^2-4*aa*cc))/(2*aa)
# ymi = xmi^3+B*xmi^2+C*xmi+D
# yma = xma^3+B*xma^2+C*xma+D
# mama = max(abs(c(ymi,yma)))
# print(xmi)
# print(xma)
# print(ymi)
# print(yma)
# print(mama)

x = seq(-10,10,0.01)
y = x^3+B*x^2+C*x+D
ym = max(abs(y))
plot(x,y,"l",col="blue",lwd=2,xlim=c(-12,12),ylim=c(-ym,ym),
     ylab="f(x)",xlab="x",axes=T,ann=T)
for(i in -10:10){
    lines(c(i,i),c(ym/20,-ym/20))
}
text(-10,-ym/10,"-10")
text(10,-ym/10,"10")
arrows(-11,0,11,0,0.1,15,3)
arrows(0,ym,0,-ym,0.1,15,3)
points(m,0,pch=20,col="red",cex=2)
# text(12,0,"x",cex=1.5)
# text(0,mama*1.2,"y",cex=1.5)

```
\

Find $B$, $C$, and $D$.

* $B=$ ##ANSWER1##
* $C=$ ##ANSWER2##
* $D=$ ##ANSWER3##

Answerlist
--------

`r al1`
`r al2`
`r al3`


Solution
========

We know that complex roots come as pairs of complex conjugates. We are told $x=`r cn(n,p)`$ is a root, so we also know $x=`r cn(n,-p)`$ is another root.

Write the cubic polynomial in factored form (based on the three roots).

$$f(x)~=~(`r pfix(c(1,-m),1:0)`)\cdot\left(x-(`r cn(n,p)`)\right)\cdot\left(x-(`r cn(n,-p)`)\right)$$


```{css,echo=F}
.boxy td {
    border: 1px solid black;
    color: black;
    background-color: white;
  }
.boxy th {
    background-color: rgb(200, 200, 200);
    color: black;
    border: 1px solid black;
  }
.boxy td:first-child {
    background-color: rgb(200, 200, 200);
    color: black;
    border: 1px solid black;
  }
```

```{r,echo=F}
quci = paste0("\\left(x+",cn(-n,-p),"\\right)\\cdot\\left(x+",cn(-n,p),"\\right)",collapse="")
quci = gsub("+-","-",quci,fixed=T)
```

I would expand $\left(x-(`r cn(n,p)`)\right)\cdot\left(x-(`r cn(n,-p)`)\right)$ by first distributing across the internal parentheses to get $`r quci`$ and then using the box method to multiply.

<div class="boxy">

| *        | $x$        | $`r -n`$    | $`r -p`i$     |
|:--------:|:----------:|:-----------:|:-------------:|
| $x$      | $x^2$      | $`r -n`x$   | $`r -p`ix$    |
| $`r -n`$ |$`r -n`x$   | $`r n^2`$   | $`r n*p`i$    |
| $`r p`i$ |$`r p`ix$   | $`r -n*p`i$ | $`r p^2`$     |

</div>

Combine like terms to get:

$$f(x)~=~(`r pfix(c(1,-m),1:0)`)\cdot\left(`r pfix(c(1,-2*n,n^2+p^2),2:0)`\right)$$

Now, we multiply again.


<div class="boxy">

| *        | $x^2$      | $`r -2*n`x$  | $`r n^2+p^2`$ |
|:--------:|:----------:|:-----------:|:-------------:|
| $x$      | $x^3$      | $`r -2*n`x^2$   | $`r n^2+p^2`x$    |
| $`r -m`$ |$`r -m`x^2$   | $`r 2*n*m`x$   | $`r -m*(n^2+p^2)`$ |

</div>


Combine like terms to get:
$$f(x)~~=~~ `r pfix(c(1,B,C,D),3:0)`$$

Thus,

* $B=`r B`$
* $C=`r C`$
* $D=`r D`$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: cubic_from_zeros