```{r,echo=FALSE}
options(scipen=999)
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
degs = numeric()
negs = numeric()
pols = character()
sols = character()
cfs = list()
for(i in 1:8){
    deg = sample(5:8,1)
    cf = c(sample(c(-9:-1,1:9),1),sample(-9:9,deg))
    pol = pfix(cf,deg:0)
    neg = sign(cf[1])
    wh = -neg+2+(deg %% 2)
    degs = c(degs,deg)
    negs = c(negs,neg)
    pols = c(pols,pol)
    sols = c(sols,paste0(1*(1:4==wh),collapse=""))
    cfs[[i]] = cf
}

asol = paste0(sols,collapse="|")

ch = c("up,up","down,up","down,down","up,down")
al = paste0("* ",ch,collapse="\n")

```

Question
========

There are four types of end behavior in polynomials (seen by zooming out on the graph and looking far left or far right):

```{r,echo=F,fig.dim=c(8,8)}
par(mfrow=c(2,2),pty="s",mar=c(0,0,2,0))
x = seq(-1,1,0.001)


plot(0,0,"n",main="up,up",xlim=c(-1,1),ylim=c(-1,1),ylab="",axes=F)
arrows(0,-1,0,1,0.1,15,code=3)
arrows(-1,0,1,0,0.1,15,code=3)
lines(x,(x-0.6)*(x-0.1)*(x+0.1)*(x+0.6),lwd=2,col="blue")
text(-1,0.8,"up",adj=0,col="blue")
text(1,0.8,"up",adj=1,col="blue")

plot(0,0,"n",main="down,up",xlim=c(-1,1),ylim=c(-1,1),ylab="",axes=F)
arrows(0,-1,0,1,0.1,15,code=3)
arrows(-1,0,1,0,0.1,15,code=3)
lines(x,(x-0.6)*(x-0.5)*x*(x+0.5)*(x+0.6),lwd=2,col="blue")
text(-1,-0.8,"down",adj=0,col="blue")
text(1,0.8,"up",adj=1,col="blue")

plot(0,0,"n",main="down,down",xlim=c(-1,1),ylim=c(-1,1),ylab="",axes=F)
arrows(0,-1,0,1,0.1,15,code=3)
arrows(-1,0,1,0,0.1,15,code=3)
lines(x,-(x-0.6)*(x-0.1)*(x+0.1)*(x+0.6),lwd=2,col="blue")
text(-1,-0.8,"down",adj=0,col="blue")
text(1,-0.8,"down",adj=1,col="blue")

plot(0,0,"n",main="up,down",xlim=c(-1,1),ylim=c(-1,1),ylab="",axes=F)
arrows(0,-1,0,1,0.1,15,code=3)
arrows(-1,0,1,0,0.1,15,code=3)
lines(x,-(x-0.6)*(x-0.5)*x*(x+0.5)*(x+0.6),lwd=2,col="blue")
text(-1,0.8,"up",adj=0,col="blue")
text(1,-0.8,"down",adj=1,col="blue")


```


**For each polynomial, state the end behavior.**

1. $f(x)~=~`r pols[1]`$
* End behavior for $f(x)$ is ##ANSWER1##.
2. $g(x)~=~`r pols[2]`$
* End behavior for $g(x)$ is ##ANSWER2##.
3. $h(x)~=~`r pols[3]`$
* End behavior for $h(x)$ is ##ANSWER3##.
4. $i(x)~=~`r pols[4]`$
* End behavior for $i(x)$ is ##ANSWER4##.
5. $j(x)~=~`r pols[5]`$
* End behavior for $j(x)$ is ##ANSWER5##.
6. $k(x)~=~`r pols[6]`$
* End behavior for $k(x)$ is ##ANSWER6##.
7. $l(x)~=~`r pols[7]`$
* End behavior for $l(x)$ is ##ANSWER7##.
8. $m(x)~=~`r pols[8]`$
* End behavior for $m(x)$ is ##ANSWER8##.


Answerlist
-------

`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`

Solution
========

For each polynomial, consider the highest-degree term.

```{css,echo=F}
.boxy td {
    border: 1px solid black;
    color: black;
    background-color: white;
  }
.boxy th {
    background-color: rgb(200, 200, 200);
    color: black;
    border: 1px solid black;
  }
.boxy td:first-child {
    background-color: rgb(200, 200, 200);
    color: black;
    border: 1px solid black;
  }
```

<div class="boxy">

|     | lead degree even | lead degree odd |
|:---:|:---:|:---:|
| lead coefficient positive | up,up | down,up |
| lead coefficient negative | down,down | up,down |

</div>

```{r,echo=F,results='asis'}
lets = c("f","g","h","i","j","k","l","m")
for(i in 1:8){
    deg = degs[i]
    cf = cfs[[i]][1]
    neg = sign(cf)
    wh = -neg+2+(deg %% 2)
    if(neg==-1){
        wrd = "negative"
    } else {
        wrd = "positive"
    }
    if(deg%%2==0){
        wrd2 = "even"
    } else {
        wrd2 = "odd"
    }
    cat(paste0(i,". The highest-degree term of $",lets[i],"(x)$ is $",pfix(cf,deg),"$. The coefficient is ",wrd,". The degree is ",wrd2,". Thus, the end behavior is ",ch[wh],".\n\n"))
}
```


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r asol`
exname: polynomial_ends_B