```{r,echo=FALSE}
options(scipen=999)
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
mfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("+{",cc,"}x^{",dd,"}",collapse="")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
### (x-h)^2+k
hk = sample(2:9,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
## x^2-2hx+(h^2+k)
A = -1
B = 2*h
C = -h^2+k
### -(x-h)^2+k
### -x^2+2hx-h^2+k
A2 = 1
B2 = -2*h
C2 = h^2+k

bl = c(B2,B,-B2,-B)
cl = c(C2,C,-C2,-C)

while(length(bl)<10 || length(cl)<10){
    hki = sample(2:9,2)*sample(c(-1,1),2,T)
    hi = hki[1]
    ki = hki[2]
    B2i = -2*hi
    C2i = hi^2+ki
    Bi = 2*hi
    Ci = -hi^2+ki
    if(length(bl)<10){
        bl = sort(unique(c(bl,B2i,-B2i,Bi,-Bi)))
    }
    if(length(cl)<10){
        cl = sort(unique(c(cl,C2i,-C2i,Ci,-Ci)))
    }
}

sol1 = paste0(1*(B2==bl),collapse="")
sol2 = paste0(1*(C2==cl),collapse="")

al1 = paste0("* ",bl,collapse="\n")
al2 = paste0("* ",cl,collapse="\n")


```

Question
========

A downward-facing [parabola](https://en.wikipedia.org/wiki/Parabola) $f$ is defined below.

$$f(x)~=~`r pfix(c(A,B,C),2:0)`$$

An upwards-facing parabola, $g$, is constructed such that $g$ and $f$ are mirror images with a shared vertex, as shown in the graph below.

```{r,echo=F,fig.dim=c(6,3)}
x = seq(-11,11,0.01)
f = A*x^2+B*x+C
g = A2*x^2+B2*x+C2

par(mar=c(0,0,0,0),mfrow=c(1,2))
plot(x,f,"n",xlim=c(-12,12),ylim=c(-12,12),axes=F,ann=F,col="blue")
arrows(-12,0,12,0,0.1,15,3,lwd=2)
arrows(0,-12,0,12,0.1,15,3,lwd=2)
lines(x,f,col="blue",lwd=3)
lines(x,g,col="red",lwd=3)
text(12,-1,"x")
text(-1,12,"y")
points(h,k,pch=20,col="black",cex=1.2)
points(h,k,pch=20,col="yellow",cex=0.8)
plot(0,0,"n",axes=F,ann=F)
legend("left",legend=c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=c(2,2))

```
\

The second parabola, $g$, can be written in standard form with two parameters ($B$ and $C$).

$$g(x)~=~x^2+Bx+C$$

Find $B$ and $C$.

* $B~=~$##ANSWER1##
* $C~=~$##ANSWER2##


Answerlist
-------

`r al1`
`r al2`



Solution
========

1. Find the vertex by completing the square. *(First factor out the negative to get a quadratic polynomial with a +1 leading coefficient.)*

$$f(x)~=~-\left(`r pfix(c(1,-B,-C),2:0)`\right)$$

$$\left(\frac{`r -B`}{2}\right)^2~=~`r round(B/2)^2`$$

$$f(x)~=~-\left(`r pfix(c(1,-B,round(B/2)^2,-C,-round(B/2)^2),c(2,1,0,0,0))`\right)$$

$$f(x)~=~-\left( (`r pfix(c(1,round(-B/2)),1:0)`)^2`r mfix(-C-round(-B/2)^2,0)` \right)$$


$$f(x)~=~-(`r pfix(c(1,round(-B/2)),1:0)`)^2`r mfix(C+round(-B/2)^2,0)`$$

2. The second parabola has the same vertex $(`r h`,`r k`)$, but it faces upwards. The general vertex form is $A(x-h)^2+k$. If $A$ is positive, the parabola faces upward, and if $A$ is negative, the parabola faces downward. If $|A|>1$, then the parabola gets stretched vertically. If $|A|<1$, then the parabola gets squished vertically. Anyway, in this case, we just need to switch the sign of $A$.

$$g(x)~=~(`r pfix(c(1,round(-B/2)),1:0)`)^2`r mfix(C+round(-B/2)^2,0)`$$

3. Expand to produce standard form.

$$g(x)~=~`r pfix(c(1,2*round(-B/2),round(B/2)^2),2:0)``r mfix(C+round(-B/2)^2,0)`$$

$$g(x)~=~`r pfix(c(1,2*round(-B/2),round(B/2)^2+C+round(-B/2)^2),2:0)`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: flip_parabola