```{r,echo=FALSE}
options(scipen=999)
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
mfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("+{",cc,"}x^{",dd,"}",collapse="")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

while(T){
    h = sample(c(-10:-1,1:10),3)
    nh = -h
    A = 1
    B = sum(nh)
    C = sum(c(prod(nh[1:2]),prod(nh[c(1,3)]),prod(nh[2:3])))
    D = prod(nh)
    
    mb = sample(c(-10:-1,1:10),2)
    m = mb[1]
    b = mb[2]
    cf1 = c(A,B,C+m,D+b)
    cf2 = c(m,b)
    cf3 = c(A,B,C,D)
    if(max(abs(c(cf1,cf2,cf3)))<200){break}
}


ch = c(-10:10)
al = paste0("* ",ch,collapse="\n")
sol = rep(0,length(ch))
for(ii in h){
    sol[ch==ii] = 1
}
sol = paste0(sol,collapse="")

```



Question
========

A cubic polynomial, $p(x)$, and a linear function, $n(x)$, intersect three times. Find the values of $x$ where they intersect. (*The solutions are all integers between $-10$ and $10$.*)

$$p(x)~=~`r pfix(c(A,B,C+m,D+b),3:0)`$$
$$n(x)~=~`r pfix(c(m,b),1:0)`$$

Answerlist
--------

`r al`


Solution
========

The intersections occur at values of $x$ such that $p(x)=n(x)$.

$$`r pfix(c(A,B,C+m,D+b),3:0)`~=~`r pfix(c(m,b),1:0)`$$

Subtract $`r pfix(c(m,b),1:0)`$ from both sides of the equation.

$$`r pfix(c(A,B,C,D),3:0)`~=~0$$

Then, use the strategy from [this previous problem](https://chadworley.github.io/a2/u06/outhtml/05_solve_cubic_easy_integers.html) to get the solutions. Remember, the [rational-root theorem](https://en.wikipedia.org/wiki/Rational_root_theorem) promises we only need to check (positive and negative) factors of `r D`, the constant of the cubic expression equaling 0.

<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
</style>

```{r,echo=FALSE,results='asis'}

ex1 = paste0("(x-",h[1],")*(x-",h[2],")*(x-",h[3],")",collapse="")
ex1 = gsub("--","+",ex1,fixed=TRUE)
ex2 = paste0("(x-",h[1],")(x-",h[2],")(x-",h[3],")",collapse="")
ex2 = gsub("--","+",ex2,fixed=TRUE)
ex2 = gsub("-0","",ex2,fixed=TRUE)

rrr = sort(unique(h))
for(i in 1:length(rrr)){
  rr = rrr[i]
  cat(paste0("## Possible successful route ",i,"\n\n",collapse=""))
  cat("<style>
.r {
  border-right: 1px solid black;
}
.b {
  border-bottom: 1px solid black;
}
td {
  height: 13pt;
  text-align: center;
}
</style>")
  cf = c(A,B,C,D)
  bots = c(cf[1])
  mids = numeric()
  deg = length(cf)
  for(j in 2:deg){
    mids = c(mids,bots[j-1]*rr)
    bots = c(bots,cf[j]+mids[j-1])
  }
  trs = paste0("* Guess that $(x-",rr,")$ is a factor:\n<table style='width:50%'><tr><td class='r'></td>",collapse="")
  trs = gsub("--","+",trs,fixed=TRUE)
  for(j in 1:deg){
    trs = paste0(trs,"<td>",cf[j],"</td>")
  }
  trs = paste0(trs,"</tr><tr><td class='r'>",rr,"</td><td class='b'></td>")
  for(j in (deg+2):(2*deg)){
    trs = paste0(trs,"<td class='b'>",mids[j-deg-1],"</td>")
  }
  trs = paste0(trs,"</tr><tr><td class='r'> </td>")
  for(j in (2*deg+1):(3*deg)){
    trs = paste0(trs,"<td>",bots[j-2*deg],"</td>")
  }
  trs = paste0(trs,"</tr></table>\n")
  cat(trs)
  so = "Notice, the remainder is 0, so the guess was good! So, we rephrase the original equation into a semi-factored form."
  eq = paste0("$$(",pfix(c(1,-rr),1:0),")(",pfix(c(1,bots[2],bots[3]),2:0),")=0$$",collapse="")
  cat(so)
  cat(eq)
  cat(paste0("Then factor the quadratic expression to get the fully factored form of the equation. You can do this by finding two integers that multiply to give ",bots[3]," and add to give ",bots[2],"."))
  cat(paste0("$$(",pfix(c(1,-rr),1:0),")(",pfix(c(1,-rrr[-i][1]),1:0),")(",pfix(c(1,-rrr[-i][2]),1:0),")=0$$"))
  cat(paste0("Thus the solutions are: {",paste0(rrr,collapse=", "),"}"))
  cat("\n\n")
}
```




Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: intersect_cubic_line