```{r,echo=FALSE}
options(scipen=999)
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
mfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("+{",cc,"}x^{",dd,"}",collapse="")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
ffix = function(roots,degs,A=1,x="x"){
    rr = roots[degs!=0]
    dd = degs[degs!=0]
    if(A==1){
        p = paste0("",paste0("(",x,"-",rr,")^{",dd,"}",collapse="\\cdot "))
    } else if(A==-1){
        p = paste0("-",paste0("(",x,"-",rr,")^{",dd,"}",collapse="\\cdot "))
    } else {
        p = paste0(A,paste0("(",x,"-",rr,")^{",dd,"}",collapse="\\cdot "))
    }
    p = gsub("--","+",p,fixed=T)
    p = gsub(paste0("(",x,"-0)",collapse=""),x,p,fixed=T)
    p = gsub("^{1}","",p,fixed=T)
    return(p)
}
pon = function(x){
    wrds = c("\\mathrm{neg}","\\mathrm{zero}","\\mathrm{pos}")
    x = sign(x)+2
    return(wrds[x])
}
sa = function(roots,degs,A=1,x=0){
    rr = roots[degs!=0]
    dd = degs[degs!=0]
    if(A==1){
        p = paste0("",paste0("(",pon(x-rr),")^{",dd,"}",collapse="\\cdot "))
    } else if(A==-1){
        p = paste0("-",paste0("(",pon(x-rr),")^{",dd,"}",collapse="\\cdot "))
    } else {
        p = paste0(A,paste0("(",pon(x-rr),")^{",dd,"}",collapse="\\cdot "))
    }
    p = gsub("^{1}","",p,fixed=T)
    return(p)
}

numroots = sample(2:3,1)
while(T){
    h = sort(sample(-9:9,numroots))
    if(min(diff(h))>2 && length(unique(c(h,-h)))>3){break}
}

degs = sample(c(rep(1,numroots-1),2))
A = sample(c(-1,1),1)

p = function(x,h,d,A){
    return(A*prod((x-h)^d))
}

```



Question
========

A polynomial, $p(x)$, is given in factored form.
$$p(x)~=~`r ffix(h,degs,A)`$$

Which of the following graphs matches $y=p(x)$?

```{r,echo=F,fig.dim=c(6,6)}
par(mfrow=c(2,2),mar=c(3,3,3,3))

multA = c(1,1,-1,-1)
multh = c(1,-1,1,-1)
ord = sample(1:4)

iii = 0
for(i in ord){
    iii = iii+1
    xx = seq(-12,12,0.01)
    yy = numeric()
    for(x in xx){
        yy = c(yy,p(x,h*multh[i],degs,A*multA[i]))
    }
    xx2 = seq(min(h*multh[i]),max(h*multh[i]),0.01)
    yy2 = numeric()
    for(x in xx2){
        yy2 = c(yy2,p(x,h*multh[i],degs,A*multA[i]))
    }
    ama = max(abs(yy2))
    plot(xx,yy,"l",axes=F,ann=F,xlim=c(-12,12),ylim=c(-ama*1.1,ama*1.1))
    mtext(LETTERS[iii],3)
    arrows(-12,0,12,0,0.1,15,3)
    arrows(0,ama*1.1,0,-ama*1.1,0.1,15,3)
    for(j in -10:10){
        if(j %% 10 == 0){
            lines(c(j,j),c(-ama/20,ama/20),lwd=1.3)
        } else if(j %% 5 == 0){
            lines(c(j,j),c(-ama/25,ama/25),lwd=1.3)
        } else {
            lines(c(j,j),c(-ama/30,ama/30),lwd=1)
        }
    }
    lines(xx,yy,col="blue",lwd=2)
    text(12,-ama/10,"x",cex=0.8)
    text(1,ama,"y",cex=0.8)
}

sol = paste0(1*(1==ord),collapse="")

```
\


Solution
========

```{r,echo=F,results='asis'}
if(sum(degs)%%2==0){
    wrd4 = "roots"
    wrd1 = "even"
    if(A<0){
        wrd2= "negative"
        wrd3= "down,down"
        ll = "-\\infty"
        rl = "-\\infty"
    } else {
        wrd2= "positive"
        wrd3= "up,up"
        ll = "\\infty"
        rl = "\\infty"
    }
} else {
    wrd4 = "root"
    wrd1 = "odd"
    if(A<0){
        wrd2= "negative"
        wrd3= "up,down"
        ll = "\\infty"
        rl = "-\\infty"
    } else {
        wrd2= "positive"
        wrd3= "down,up"
        ll = "-\\infty"
        rl = "\\infty"
    }
}

xeq = paste0("$x=",h,"$", collapse=" or ")
cxeq = ""
for(hh in h){
   cxeq = paste0(cxeq,"$$p(",hh,")~=~",ffix(h,degs,A,hh),"~=~0$$\n") 
}

```

First, consider the end behavior. If you expanded the polynomial into standard form, the highest-degree term would be $`r pfix(A,numroots+1)`$. 

$$p(x)~=~`r pfix(A,numroots+1)`+\ldots$$

The highest degree term has a `r wrd2` coefficient and an `r wrd1` degree, so the end behavior is **"`r wrd3`"**. Or, [more formally](https://en.wikipedia.org/wiki/Limit_(mathematics)), $\lim\limits_{x\to-\infty} p(x) ~=~ `r ll`$ and $\lim\limits_{x\to\infty} p(x) ~=~ `r rl`$.

Next, we consider the roots. From the factored form, $p(x)~=~`r ffix(h,degs,A)`$, it is easy to see (see [zero-product property](https://en.wikipedia.org/wiki/Zero-product_property)) that `r xeq` makes the polynomial output 0.

`r cxeq`

We predict that at $x=`r h[degs==2]`$ there is a double root (multiplicity of 2) because the corresponding factor is squared. Graphically, we expect the curve to "bounce" off the $x$ axis at $x=`r h[degs==2]`$. At the other `r wrd4`, we expect the curve to cut through the $x$ axis.

Anyway, based on this analysis, we can produce a [sign](https://en.wikipedia.org/wiki/Sign_function) graph of the polynomial.

```{r,echo=F}
s = paste0("|$(-\\infty,",h[1],")$|$",sa(h,degs,A,-20),"$|$",sign(p(-20,h,degs,A)),"$|\n",collapse="")

for(i in 1:(length(h)-1)){
    h1 = h[i]
    h2 = h[i+1]
    s = paste0(s,"|$",h1,"$|$",sa(h,degs,A,h1),"$|$",sign(p(h1,h,degs,A)),"$|\n",collapse="")
    xxx = mean(c(h1,h2))
    s = paste0(s,"|$(",h1,",",h2,")$|$",sa(h,degs,A,xxx),"$|$",sign(p(xxx,h,degs,A)),"$|\n",collapse="")
}

i = length(h)
h1 = h[i]
h2 = 20
s = paste0(s,"|$",h1,"$|$",sa(h,degs,A,h1),"$|$",sign(p(h1,h,degs,A)),"$|\n",collapse="")
xxx = mean(c(h1,h2))
s = paste0(s,"|$(",h1,",\\infty)$|$",sa(h,degs,A,xxx),"$|$",sign(p(xxx,h,degs,A)),"$|\n",collapse="")

```


| $x$ interval or value | sign analysis of $p(x)~=~`r ffix(h,degs,A)`$ | sign |
|:---:|:---:|:---:|
`r s`



```{r,echo=F,fig.dim=c(4,4)}
xx = seq(-12,12,0.01)
yy = numeric()
for(x in xx){
    yy = c(yy,p(x,h,degs,A))
}
plot(xx,sign(yy),"l",xlim=c(-12,12),ylim=c(-2,2),lwd=2,col="blue",xlab="x",ylab="sign(p(x))")
for(xh in h){
    points(xh,0,pch=20,cex=1.5)
}
arrows(-12,0,12,0,0.1,10,3)
arrows(0,-2,0,2,0.1,10,3)
for(iii in -10:10){
    if(iii%%5==0){
        lines(c(iii,iii),c(-0.13,0.13),lwd=1.5) 
    } else {
        lines(c(iii,iii),c(-0.1,0.1))
    }
    
}
```
\

And only one option matches.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,2,0))
xx = seq(-12,12,0.01)
yy = numeric()
xx2 = seq(min(h),max(h),0.01)
yy2 = numeric()
for(x in xx2){
    yy2 = c(yy2,p(x,h,degs,A))
}
ama = max(abs(yy2))
for(x in xx){
    yy = c(yy,p(x,h,degs,A))
}
plot(xx,yy,"l",xlim=c(-12,12),ylim=c(-ama*1.1,ama*1.1),lwd=2,col="blue",xlab="x",ylab="p(x)",axes=F,ann=F)
for(xh in h){
    points(xh,0,pch=20,cex=1.5)
}
arrows(-12,0,12,0,0.1,10,3)
arrows(0,-ama*1.1,0,ama*1.1,0.1,10,3)
for(iii in -10:10){
    if(iii%%5==0){
        lines(c(iii,iii),c(-ama/20,ama/20),lwd=1.5) 
    } else {
        lines(c(iii,iii),c(-ama/30,ama/30))
    }
}
text(12,-ama/10,"x",cex=0.8)
text(1,ama,"y",cex=0.8)
mtext(LETTERS[which(ord==1)],3)
```
\






Meta-information
============
extype: schoice
exsolution: `r sol`
exname: sketch_factored_poly