---
output: slidy_presentation
---

# Agenda

* Entrance Ticket
* Coordinate Transformations


# Coordinate transformations

* Shift all points 2 units right:
$$(a,b)\to (a+2,b)$$
* Shift all points 3 units left and 5 units up:
$$(a,b)\to (a-3,b+5)$$
* Stretch points horizontally by a factor of 2:
$$(a,b)\to (2a,b)$$


# Problem 1

Let function $g$ be defined as a transformation of function $f$:

$$g[x]~=~ \frac{f[2x+3]}{5}+7$$

We know point $(a,b)$ is on curve $f$. In other words, we know $f[a]=b$.

* What is the corresponding point on curve $g$?

# Solution 1

Restate problem. We are given two equations:

$$g[x]~=~ \frac{f[2x+3]}{5}+7$$
$$f[a]=b$$

We wish to find a coordinate transformation that describes how to find the corresponding point on $g$.


1. Set the argument of $f$ equal to $a$ because we want to use the fact that $f[a]=b$.
$$2x+3=a$$
2. Solve for $x$.
$$2x=a-3$$
$$x=\frac{a-3}{2}$$
3. Substitute $a$ for $2x+3$.

$$g[x]~=~ \frac{f[a]}{5}+7$$

4. Substitute $\frac{a-3}{2}$ for $x$.

$$g{\left[\frac{a-3}{2}\right]}~=~ \frac{f[a]}{5}+7$$

5. Substitute $b$ for $f[a]$.

$$g{\left[\frac{a-3}{2}\right]}~=~ \frac{b}{5}+7$$

And, so we know point $\left(\frac{a-3}{2},\frac{b}{5}+7\right)$ is on the $g$ curve. Thus, the coordinate transformation can be written:

$$(a,b)\to \left(\frac{a-3}{2},\frac{b}{5}+7\right)$$

# Shortcut

We were given:

$$g[x]~=~ \frac{f[2x+3]}{5}+7$$

### Horizontal coordinate

Notice the argument $2x+3$ is composed of two elementary operations:

1. Multiply by 2
2. Add 3

If we consider the INVERSE of the argument:

1. Subtract 3
2. Divide by 2

And that's exactly what we see in the expression $\frac{a-3}{2}$. This is not a coincidence.

### Vertical coordinate

Replace the entire $f$ expression (the $f$, the argument, and the argument's brackets) with $b$. In this case, we get $\frac{b}{5}+7$


### Final answer

$$(a,b)\to \left(\frac{a-3}{2},\frac{b}{5}+7\right)$$



# Problem 2

```{r, echo = FALSE, results = "hide"}
set.seed(1)
et1s = sample(1:8,8)
et2s = sample(1:8,8)
et1 = et1s[1]
et2 = et2s[1]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$",collapse="")

```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


# Solution 2

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


`r ca`


# Problem 3

```{r, echo = FALSE, results = "hide"}
et1 = et1s[2]
et2 = et2s[2]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$",collapse="")

```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


# Solution 3

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


`r ca`


# Problem 4

```{r, echo = FALSE, results = "hide"}
et1 = et1s[3]
et2 = et2s[3]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$",collapse="")

```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


# Solution 4

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


`r ca`


# Problem 5

```{r, echo = FALSE, results = "hide"}
et1 = et1s[4]
et2 = et2s[4]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$",collapse="")

```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


# Solution 5

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. 

Write the coordinate transformation.


`r ca`




