```{r,echo=F}
while(T){
  ang = round(runif(1,pi/7,1.3),2)
  hyp = round(runif(1,12,99),0)
  adj = cos(ang)*hyp
  adj2 = round(adj)
  opp = tan(ang)*adj2
  opp2 = round(opp,0)
  ang2 = round(atan(opp2/adj2),2)
  angt = sprintf("%.2f",ang2)
  adjt = sprintf("%.0f",adj2)
  hypt = sprintf("%.0f",round(hyp,0))
  oppt = sprintf("%.0f",round(opp2,0))
  if(opp2!=adj2 && hyp-opp2>2 && hyp-adj2>2 && opp2>10 && adj>10 && round(ang*adj2)!=opp2 && round(ang*opp2)!=adj2 && ang2!=round(opp2/adj2,2) &&
      ang2!=round(adj2/opp2,2) &&
      ang2!=round(1/tan(opp2/adj2),2) &&
      ang2!=round(1/tan(adj2/opp2),2)){break}
}
```

Question
========

A right triangle has an angle of $\theta$ radians. The adjacent leg has a length of `r adjt` meters, and the opposite leg has a length of `r opp2` meters. What is the angle measure $\theta$ in radians?

```{r,fig.dim=c(5,5),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",axes=F,ann=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
th = seq(0,pi/2,length.out=100)
lines(cos(th),sin(th),lty=2,col="grey")
lines(c(0,cos(ang),cos(ang),0),c(0,0,sin(ang),0),lwd=3)
lines(c(cos(ang)-0.02,cos(ang)-0.02,cos(ang)),c(0,0.02,0.02))
th2 = seq(0,ang,length.out=100)
#lines(cos(th2),sin(th2),lty=2,col=rgb(1,0.8,0.8))
#text(1.07*cos(ang/2),1.07*sin(ang/2),paste0(angt,"*",hypt),col=rgb(1,0.8,0.8),cex=0.7)
lines(c(cos(ang),cos(ang)),c(0,sin(ang)),col="purple",lwd=4)
text(cos(ang)+0.05,sin(ang)/2,paste0(opp2," m"),col="purple",cex=0.8)
lines(c(0,cos(ang)),c(0,0),col="blue",lwd=4)
text(cos(ang)/2,
     -0.05,
     paste0(adj2," m"),col="blue",cex=0.8)
lines(0.1*cos(th2),0.1*sin(th2),col="red")
text(0.16*cos(ang/2),0.16*sin(ang/2),TeX("$\\theta$"),col="red",cex=0.8)
```
\

Please round your answer to the nearest hundredth of a radian.

Solution
========

First, identify the correct trigonometric function. Remember, [SOHCAHTOA](https://en.wikipedia.org/wiki/Mnemonics_in_trigonometry).

$$\sin(\theta)=\frac{\mathrm{opposite}}{\mathrm{hypotenuse}}$$


$$\cos(\theta)=\frac{\mathrm{adjacent}}{\mathrm{hypotenuse}}$$


$$\tan(\theta)=\frac{\mathrm{opposite}}{\mathrm{adjacent}}$$

In this case, we are given the **adjacent** and the **opposite**, and we are asked for the angle measure. The trigonometric ratio that relates these two sides is [tangent](https://en.wikipedia.org/wiki/Trigonometric_functions). Use $\theta$ to represent the requested angle measure.

$$\tan(\theta) = \frac{`r opp2`}{`r adjt`}$$

To evaluate $\theta$, we need to use the [inverse of tangent](https://en.wikipedia.org/wiki/Inverse_trigonometric_functions). This inverse function has a few names: arctan, atan, or $\tan^{-1}$ are the most commonly used.

$$\theta = \arctan\left(\frac{`r opp2`}{`r adj2`}\right)$$
Depending on your calculator, you might type something like ``round(arctan(`r opp2`/`r adj2`),2)``

$$\theta \approx `r ang2`$$

Meta-information
============
extype: num
exsolution: `r ang2`
exname: tan_get_ang