```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
step = 0.01
x = seq(-5,5,step)
n = length(x)
a = sample(3:5,1)
h = sample(-3:4,1)
fun = function(x){round(a*sin(pi/4*(x-h)),8)}
dfun = function(x){round(a*cos(pi/4*(x-h))*pi/4,8)}
ddfun = function(x){round(-a*sin(pi/4*(x-h))*pi^2/4^2,8)}

y = fun(x)
dy = dfun(x)
ddy = ddfun(x)

maxes = c(-14,-6,2,10)+h
mins = c(-10,-2,6,14)+h
znp = c(-8,0,8)+h
zpn = c(-12,-4,4,12)+h
ends = c(-5,5)
crits = sort(unique(c(zpn,znp,mins,maxes)))
crits = crits[abs(crits)<5]

posint = ""
negint = ""
incint = ""
decint = ""

if(y[1]>0){
  posint = "(-5,"
}
if(y[1]<0){
  negint = "(-5,"
}
if(y[1]==0){
  if(dy[1]>0){
    posint = "(-5,"
  }
  if(dy[1]<0){
    negint = "(-5,"
  }
}
if(dy[1]>0){
  incint = "(-5,"
}
if(dy[1]<0){
  decint = "(-5,"
}
if(dy[1]==0){
    if(ddy[1]>0){
    incint = "(-5,"
  }
  if(ddy[1]<0){
    decint = "(-5,"
  }
}

for(xx in crits){
  i = which(x==xx)
  if(xx %in% maxes){
    incint = paste0(incint,xx,")")
    decint = paste0(decint,"(",xx,",")
  }
  if(xx %in% mins){
    decint = paste0(decint,xx,")")
    incint = paste0(incint,"(",xx,",")
  }
  if(xx %in% znp){
    negint = paste0(negint,xx,")")
    posint = paste0(posint,"(",xx,",")
  }
  if(xx %in% zpn){
    posint = paste0(posint,xx,")")
    negint = paste0(negint,"(",xx,",")
  }
}

xe = x[length(y)]
ye = y[length(y)]
dye = dy[length(y)]
ddye = ddy[length(y)]

if(ye>0){
  posint = paste0(posint,xe,")")
}
if(ye<0){
  negint =  paste0(negint,xe,")")
}
if(ye==0){
  if(dye>0){
    negint = paste0(negint,xe,")")
  }
  if(dye<0){
    posint = paste0(posint,xe,")")
  }
}
if(dye>0){
  incint = paste0(incint,xe,")")
}
if(dye<0){
  decint = paste0(decint,xe,")")
}
if(dye==0){
    if(ddye<0){
    incint = paste0(incint,xe,")")
  }
  if(ddye>0){
    decint = paste0(decint,xe,")")
  }
}

posint = gsub("\\)\\(","\\)U\\(",posint)
negint = gsub("\\)\\(","\\)U\\(",negint)
incint = gsub("\\)\\(","\\)U\\(",incint)
decint = gsub("\\)\\(","\\)U\\(",decint)

intervals = sample(c(posint,negint,incint,decint))

al = paste0("* ",intervals,"\n",collapse="")

ans1 = paste0(1*(intervals==posint),collapse="")
ans2 = paste0(1*(intervals==negint),collapse="")
ans3 = paste0(1*(intervals==incint),collapse="")
ans4 = paste0(1*(intervals==decint),collapse="")
```

Question
========

Let function $f$ be defined by the graph below.

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s")
plot(0,0,type="n",xlim=c(-5,5),ylim=c(-5,5),lwd=2,ylab="f(x)",xlab="x")
for(j in seq(-5,5,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,y,col = "blue",lwd=4)
points(x[1],y[1],col="blue",cex=2.5,pch=20)
points(x[1],y[1],col="white",cex=1.5,pch=20)
points(x[n],y[n],col="blue",cex=2.5,pch=20)
points(x[n],y[n],col="white",cex=1.5,pch=20)
```
\

* Over what interval is the function positive? ##ANSWER1##
* Over what interval is the function negative? ##ANSWER2##
* Over what interval is the function increasing? ##ANSWER3##
* Over what interval is the function decreasing? ##ANSWER4##

Answerlist
--------
`r al`
`r al`
`r al`
`r al`

Solution
========

* The function "is positive" when $f(x)>0$. The interval refers to the $x$ values (inputs) that produce a positive output. Determine where the curve is above the $x$ axis. Indicate "where" with the $x$ values at the endpoints: `r posint`
* The function "is negative" when $f(x)<0$. The interval refers to the $x$ values (inputs) that produce a negative output. Determine where the curve is below the $x$ axis. Indicate "where" with the $x$ values at the endpoints: `r negint`
* The function is increasing when an ant going left-to-right is walking up hill: `r incint`
* The function is decreasing when an ant going left-to-right is walking down hill: `r decint`



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`
exname: intervals_sinusoidal