```{r data generation, echo = FALSE, results = "hide"}

x = seq(0,50,0.1)
y = sqrt(48*x)-x

xp = 12
yp = 12

poss = c(-3/2,-4/3,-3/4,-2/3,2/3,3/4,4/3,3/2)
sposs = c("-3/2","-4/3","-3/4","-2/3","2/3","3/4","4/3","3/2")
fposs = c("\\frac{-3}{2}","\\frac{-4}{3}","\\frac{-3}{4}","\\frac{-2}{3}",
          "\\frac{2}{3}","\\frac{3}{4}","\\frac{4}{3}","\\frac{3}{2}")
hposs = c("\\frac{-2}{3}","\\frac{-3}{4}","\\frac{-4}{3}","\\frac{-3}{2}",
          "\\frac{3}{2}","\\frac{4}{3}","\\frac{3}{4}","\\frac{2}{3}")

wa = sample(1:length(poss),1)
wb = sample(1:length(poss),1)

a = poss[wa]
b = poss[wb]

x2 = x/b
y2 = y*a

xp2 = round(xp/b)
yp2 = round(yp*a)

sol1 = paste0(1*(wa==1:length(poss)),collapse="")
sol2 = paste0(1*(wb==1:length(poss)),collapse="")

al = paste0("* ",sposs,collapse="\n")

```

Question
========

Let $f$ be a function defined below for $x\ge 0$:

$$f(x)~=~\sqrt{48\cdot x}\,-\,x$$

Notice $f$ has a [global extremum](https://en.wikipedia.org/wiki/Maximum_and_minimum) at point $(12, 12)$.

A second function, $g$, is created by randomly selecting $a$ and $b$ in the definitional equation below.

$$g(x)~=~a\cdot f(bx)$$

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-20,20),ylim=c(-20,20),axes=F,ann=F)
for(i in -22:22){
    abline(h=i,col="lightgrey",lwd=0.8)
    abline(v=i,col="lightgrey",lwd=0.8)
}
for(i in seq(-20,20,5)){
    abline(h=i,col="darkgrey",lwd=1.2)
    abline(v=i,col="darkgrey",lwd=1.2)
}
for(i in seq(-20,20,10)){
    abline(h=i,col="black",lwd=1.2)
    abline(v=i,col="black",lwd=1.2)
}
arrows(-20.9,0,20.9,0,0.1,10,3,lwd=2.5)
arrows(0,-20.9,0,20.9,0.1,10,3,lwd=2.5)
lines(x,y,col="blue",lwd=3)
points(xp,yp,col="blue",pch=20,cex=1.5)
lines(x2,y2,col="red",lwd=3)
points(xp2,yp2,col="red",pch=20,cex=1.5)
text(10,-0.3,10,adj=c(0.5,1))
text(-10,-0.3,-10,adj=c(0.5,1))
text(-0.3,10,10,adj=c(1,0.5))
text(-0.3,-10,-10,adj=c(1,0.5))
text(21,0.5,"x",cex=0.8)
text(0.5,21,"y",cex=0.8)

xxx = c(x,x2)
yyy = c(y,y2)

adtl = min((xxx+10)^2+(yyy-10)^2)
adtr = min((xxx-10)^2+(yyy-10)^2)
adbl = min((xxx+10)^2+(yyy+10)^2)
adbr = min((xxx-10)^2+(yyy+10)^2)
ads = c(adtl,adtr,adbl,adbr)
iii = min(which(ads==max(ads)))

if(iii==1){
    legend("topleft",c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=c(3,3))
} else if(iii==2){
    legend("topright",c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=c(3,3))
} else if(iii==3){
    legend("bottomleft",c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=c(3,3))
} else if(iii==4){
    legend("bottomright",c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=c(3,3))
}

```
\

We can see that $g$ is a stretched (and possibly reflected) version of $f$. Finish the equality below.

* $g(x)~=~$ ##ANSWER1## $\cdot f($ ##ANSWER2## $\cdot x)$


Answerlist
--------

`r al`
`r al`

Solution
========

Notice the extremum of $g$ is at $(`r xp2`, `r yp2`)$.

* The horizontal scale factor equals $\frac{`r xp2`}{12} ~=~ `r hposs[wb]`$
* The vertical scale factor equals $\frac{`r yp2`}{12} ~=~ `r fposs[wa]`$

The horizontal multiplicative factor ($b$) is the [reciprocal](https://en.wikipedia.org/wiki/Multiplicative_inverse) of the horizontal scale factor.

$$b~=~ \left(`r hposs[wb]`\right)^{-1} ~=~ `r fposs[wb]`$$

The vertical multiplicative factor ($a$) is equal to the vertical scale factor.

$$a~=~`r fposs[wa]`$$

Thus,

$$g(x) ~=~ `r fposs[wa]` \cdot f\left(`r fposs[wb]` \cdot x\right)$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: stretch_graph