```{r,echo=F,warning=F}
# Draw a bunch of alien worms
NNN = 1200
w = rep(0.2,NNN)
h = sort(runif(NNN,0.2,1))
di = runif(NNN,0,2*pi)
hue = (runif(NNN,0,0.15)+runif(1))%%1

num3 = sample(1:NNN)
h3 = h[num3]
di3 = di[num3]
hu3 = hue[num3]

sol = sample(c("01","10"),1)

if(sol=="10"){
  nums = sample(1:NNN,15*5)
  H = h[nums]
  HUE = hue[nums]
  DI = di[nums]
} else {
  nrh = sample(2:3,1)
  howwrong = sample(1:3,1)
  if(howwrong==1){
    nums = sample(c(sample(1:(NNN%/%2),15*5-nrh),sample((3*NNN%/%4):NNN,nrh)))
    H = h[nums]
    HUE = hue[nums]
    DI = di[nums]
  } else if(howwrong==2) {
    nums = sample(c(sample(1:(NNN%/%4),nrh),sample((NNN%/%2):NNN,15*5-nrh)))
    H = h[nums]
    HUE = hue[nums]
    DI = di[nums]
  } else if(howwrong==3){
    nums = sample((2*NNN%/%5):(3*NNN%/%5),15*5)
    H = h[nums]
    HUE = hue[nums]
    DI = di[nums]
  }
}

if(sol=="01"){
  if(howwrong==2){
    txt = "No, the sample is NOT representative. The heights are almost all tall."
  } else if(howwrong==1) {
    txt = "No, the sample is NOT representative. The heights are almost all short."
  } else if(howwrong==3) {
    txt = "No, the sample is NOT representative. The heights are all middling."
  }
} else {
  txt = "Yes, the sample appears to be representative. There are similar proportions of small and tall in that sample as in the population."
}


```

Question
========

On a distant planet, in an alien town, there are 1200 inhabitants with varying heights.

```{r,echo=F,fig.dim=c(6,6)}
par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(0,20),ylim=c(0,20),axes=F,ann=F)
th=seq(0,2*pi,pi/100)
for(i in 1:(NNN/20)){
  for(j in 1:20){
    n = (i-1)*20+j
    polygon(i/3+c(-w[n],-w[n],w[n],w[n])/2-0.5/3,
            j+c(-h3[n],h3[n],h3[n],-h3[n])/2-1+h3[n]/2,
            col=hsv(hu3[n],0.9,1),lwd=0.5)
    polygon(i/3+0.06*cos(th)-0.5/3,
            j+0.06*sin(th)+h3[n]/2-0.09-1+h3[n]/2,
            col="white",lwd=0.3)
    polygon(i/3+0.03*cos(di3[n])+0.03*cos(th)-0.5/3,
            j+0.03*sin(di3[n])+h3[n]/2-0.09+0.03*sin(th)-1+h3[n]/2,
            col="black",lwd=0.3)
  }
}
```
\

A researcher gathers a sample ($n=75$) to estimate the average height and to estimate the variability of height. The sample is shown below.

```{r,echo=F,fig.dim=c(1.5,1.5)}
par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(0,5),ylim=c(0,5),axes=F,ann=F)
th=seq(0,2*pi,pi/100)
for(i in 1:15){
  for(j in 1:5){
    n = (i-1)*5+j
    polygon(i/3+c(-w[n],-w[n],w[n],w[n])/2-0.5/3,
            j+c(-H[n],H[n],H[n],-H[n])/2-1+H[n]/2,
            col=hsv(HUE[n],0.9,1),lwd=0.5)
    polygon(i/3+0.06*cos(th)-0.5/3,
            j+0.06*sin(th)+H[n]/2-0.09-1+H[n]/2,
            col="white",lwd=0.3)
    polygon(i/3+0.03*cos(DI[n])+0.03*cos(th)-0.5/3,
            j+0.03*sin(DI[n])+H[n]/2-0.09+0.03*sin(th)-1+H[n]/2,
            col="black",lwd=0.3)
  }
}
```
\

Does the sample appear to be representative of the population? In other words, does it appear that a simple random sample was taken?

Answerlist
--------

* Yes, the sample is representative of the population.
* No, the sample is NOT representative of the population.

Solution
========

`r txt`


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: is_sample_rprsnttv