```{r,echo=F,warning=F}
typ = 1 #sample(1:5,1)
NNN = 1200
pams = list(c(1,1,0.5),
            c(0.1,0.1,0.5),
            c(10,10,0.5),
            c(0.8,2,0.75),
            c(2,0.8,0.25))
if(typ==1){
  a = 1
  b = 1
  m = 0.5
} else if(typ == 2){
  a = 0.2
  b = 0.2
  m = 0.5
} else if(typ == 3){
  a = 10
  b = 10
  m = 0.5
} else if(typ == 4){
  a = 0.8
  b = 2
  m = 0.75
} else if(typ == 5){
  a = 2
  b = 0.8
  m = 0.25
}

H = sort(rbeta(NNN,a,b)*0.75+0.2)
di = runif(NNN,0,2*pi)
hu = (runif(NNN,0,0.15)+runif(1,0,1))%%1

n = 75
pop = sample(1:NNN)
sam1 = sample(1:NNN,n)
nrh = sample(2:4,1)
sam2 = sample(c(1:(n-nrh),sample((NNN-n):NNN,nrh)))
nrh = sample(2:4,1)
sam3 = sample(c((NNN-n+nrh):(NNN),sample(1:n,nrh)))
nrh = sample(3:6,1)
sam4 = sample(c((NNN*m-n%/%2-2):(NNN*m-n%/%2-2+n-nrh),sample(1:NNN,nrh)))
sam5 = sample(c(1:(n%/%2),sample((NNN-n%/%2):NNN)))

makeit = function(ns=1:NNN,ncol=NNN/20,nrow=20,h=H){
  par(pty="s",mar=c(0,0,0,0))
  plot(0,0,type="n",xlim=c(0,ncol/3),ylim=c(0,nrow),axes=F,ann=F)
  th=seq(0,2*pi,pi/100)
  w = 0.2
  for(i in 1:ncol){
    for(j in 1:nrow){
      n = ns[(i-1)*nrow+j]
      polygon(i/3+c(-w,-w,-0.5*w,0.5*w,w,w,0.5*w,-0.5*w)/2-0.5/3,
              j+c(-h[n]+0.5*w,h[n]-0.5*w,h[n],h[n],h[n]-0.5*w,-h[n]+0.5*w,-h[n],-h[n])/2-1+h[n]/2,
              col=hsv(hu[n],0.9,1),lwd=0.5)
      polygon(i/3+0.06*cos(th)-0.5/3,
              j+0.06*sin(th)+h[n]/2-0.1-1+h[n]/2,
              col="white",lwd=0.3)
      polygon(i/3+0.03*cos(di[n])+0.03*cos(th)-0.5/3,
              j+0.03*sin(di[n])+h[n]/2-0.1+0.03*sin(th)-1+h[n]/2,
              col="black",lwd=0.3)
    }
  }
}

rreepp = sample(1:5)
sol = paste0(1*(1==rreepp),collapse="")

```

Question
========

On a distant planet, in an alien town, there are 1200 inhabitants with varying heights.

```{r,echo=F,fig.dim=c(6,6)}
makeit(pop,NNN/20,20,H)
```
\

A researcher uses five different methods to get a sample (with sample size $n=75$).

```{r,echo=F,fig.dim=c(1.5,1.5),results='asis'}

sams = list(sam1,sam2,sam3,sam4,sam5)
for(i in 1:5){
  makeit(sams[[rreepp[i]]],NNN/20/4,20/4,H)
  text(2.5,2.5,LETTERS[i],cex=3)
}
```
\

Which sample is representative of the population? In other words, which sample appears to be a [simple random sample](https://en.wikipedia.org/wiki/Simple_random_sample)?


Answerlist
--------

* A
* B
* C
* D
* E

Solution
========



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: which_srs