```{r data generation, echo = FALSE, results = "hide"}
while(T){
    x = sort(sample(3:7,4))
    y = sample(3:7,4)
    if(length(unique(c(x,y)))==5){break}
}

hk = sample(2:3,2)
h = 0
k = hk[2]
x2 = x-h
y2 = y+k
f = data.frame(x,y)
colnames(f) = c("$x$","$f(x)$")
g = data.frame(x2,y2)
colnames(g) = c("$x$","$g(x)$")
col1 = paste0("##ANSWER",1:4,"##")
col2 = paste0("##ANSWER",5:8,"##")
adf = data.frame(col1,col2)
colnames(adf) = c("$x$","$g(x)$")
if(h<0){
  inside = paste0("+",h,collapse="")
  hor = "right"
} else {
  inside = paste0("-",-h,collapse="")
  hor = "left"
}
if(k<0){
  outside = paste0("-",-k,collapse="")
  ver = "down"
} else {
  outside = paste0("+",k,collapse="")
  ver = "up"
}
ex = paste0("f(x)+",abs(k),collapse="")
answer_possibilities = 0:10
anslist = paste0("* ",rep(answer_possibilities,8),"\n",collapse="")
ans1 = paste0(1*(x2[1]==answer_possibilities),collapse="")
ans2 = paste0(1*(x2[2]==answer_possibilities),collapse="")
ans3 = paste0(1*(x2[3]==answer_possibilities),collapse="")
ans4 = paste0(1*(x2[4]==answer_possibilities),collapse="")
ans5 = paste0(1*(y2[1]==answer_possibilities),collapse="")
ans6 = paste0(1*(y2[2]==answer_possibilities),collapse="")
ans7 = paste0(1*(y2[3]==answer_possibilities),collapse="")
ans8 = paste0(1*(y2[4]==answer_possibilities),collapse="")
```

Question
========

Let $f(x)$ be defined by the table below:

```{r tabf, results="asis", echo=F,warning=F}
library(kableExtra)
kable_styling(kable(f, align = "cc",row.names=F),bootstrap_options = "bordered",full_width = F)
```

Let $g(x)$ be defined with the equation $g(x)=`r ex`$. What are the 4 corresponding points on $g$? (Use same order.)

```{r tabadf, results="asis", echo=F}
kable_styling(kable(adf, align = "cc",row.names=F),bootstrap_options = "bordered",full_width = F)
```



Answerlist
--------
`r anslist`


Solution
========


```{r tabg, results="asis", echo=F}
kable_styling(kable(g, align = "cc",row.names=F),bootstrap_options = "bordered",full_width = F)
```

* Notice $g(`r x2[1]`)~=~f(`r x2[1]`)+`r k` ~=~`r y[1]`+`r k`~=~`r y2[1]`$
* Notice $g(`r x2[2]`)~=~f(`r x2[2]`)+`r k` ~=~`r y[2]`+`r k`~=~`r y2[2]`$
* Notice $g(`r x2[3]`)~=~f(`r x2[3]`)+`r k` ~=~`r y[3]`+`r k`~=~`r y2[3]`$
* Notice $g(`r x2[4]`)~=~f(`r x2[4]`)+`r k` ~=~`r y[4]`+`r k`~=~`r y2[4]`$

The "shortcut" is to recognize that the definition $g(x)=`r ex`$ implies a vertical shift **up** by `r abs(k)`.

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`|`r ans5`|`r ans6`|`r ans7`|`r ans8`
exname: translate_table
exshuffle: FALSE