```{r,echo=F,warning=F}
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("t^0","",exp,fixed=T)
  exp = gsub("t^1","x",exp,fixed=T)
  return(exp)
}

while(T)
{
  tf = runif(1,5,20)
  Pb = runif(1,30,90)
  pmax = runif(1,400,1200)
  tm = 1/3*tf
  A = -27/4*(Pb - pmax)/tf^3
  
  # P(t) = A*t(t-tf)^2+Pb
  # P(t) = A*t(t^2-2*tf*t+tf^2)+Pb
  # P(t) = At^3 - 2*tf*A*t^2 + tf^2*A*t + Pb
  # E(t) = 1/4*A*t^4 - 2/3*A*t^3*tf + 1/2*A*t^2*tf^2 + Pb*t
  
  a = round(1/4*A,2)
  b = round(-2/3*A*tf,2)
  c = round(1/2*A*tf^2,2)
  d = round(Pb,2)
  
  t = round(runif(1,tf*0.1,tf*0.9),1)
  Et = a*t^4+b*t^3+c*t^2+d*t
  Ept = 4*a*t^3+3*b*t^2+2*c*t+d
  if(a>0.1 && max(c(a,b,c,d))<1000){break}
}

ex1 = fixer(paste0(a,"t^4+",b,"t^3+",c,"t^2+",d,"t",collapse=""))
ex2 = fixer(paste0(4*a,"t^3+",3*b,"t^2+",2*c,"t+",d,collapse=""))
```

Question
========

A human converts [chemical energy](https://en.wikipedia.org/wiki/Chemical_energy) (energy stored as ATP and carbohydrates) into [gravitational potential energy](https://en.wikipedia.org/wiki/Gravitational_energy) by pedaling a bicycle up a hill. During a short burst, the amount of [work](https://en.wikipedia.org/wiki/Work_(physics)) (stored as potential energy), as a function of time, follows the polynomial expression below, where energy ($E$) is in [joules](https://en.wikipedia.org/wiki/Joule) and time ($t$) is in [seconds](https://en.wikipedia.org/wiki/Second).
$$E(t) ~=~ `r ex1`$$

```{r,echo=F,fig.dim=c(6,6)}
tt = seq(0,tf,length.out=100)
EE = (a*tt^4+b*tt^3+c*tt^2+d*tt)
plot(tt,EE,type="l",xlab="time (s)",ylab="energy (J)")
```
\

For your reference, 4184 joules is 1 kilocalorie ([and in the US, in regards to food, we call 1 kilocalorie a "calorie"... just to be as confused as possible](https://en.wikipedia.org/wiki/Calorie#Food_energy)).

[Power](https://en.wikipedia.org/wiki/Power_(physics)) is the rate of energy per time. In this case, we will measure power in [watts](https://en.wikipedia.org/wiki/Watt), where 1 watt equals 1 joule per second. A human burns 100 watts as [basal metabolism](https://en.wikipedia.org/wiki/Basal_metabolic_rate). Walking burns an additional 30 watts. A professional cyclist can maintain 400 watts of output while racing (see [Human Power](https://en.wikipedia.org/wiki/Human_power#Available_power)). A typical college-aged student can output 1000 watts for a few seconds. Usain Bolt's record sprint required a burst of 2500 watts (about 3.5 horsepower) for part of the sprint. Throughout history, a laborer would average about 100 watts above basal metabolism (see [Vaclav Smil](https://vaclavsmil.com/wp-content/uploads/docs/smil-articles-science-energy-ethics-civilization.pdf)).

Anyway, at $t=`r t`$ seconds, what is the power output of the human in watts? The tolerance is $\pm 1$ watt.


Solution
========

Find the derivative.

$$E'(t) ~=~ `r ex2`$$

Plug in $t=`r t`$ seconds.

$$E'(`r t`) ~=~ `r Ept`$$

```{r,echo=F,fig.dim=c(6,6)}
tt = seq(0,tf,length.out=100)
EE = (a*tt^4+b*tt^3+c*tt^2+d*tt)
plot(tt,EE,type="l",xlab="time (s)",ylab="energy (J)",
     main=paste0("At t=",t," seconds\nthe power is ",round(Ept)," J/s.",collapse=""))
tt2 = seq(t-0.5,t+0.5,length.out=10)
lines(tt2,Ept*(tt2-t)+Et,col="red",lwd=3)
points(t,Et,col="purple")
```
\

So, the answer is `r round(Ept)` J/s or `r round(Ept)` watts.


Meta-information
============
extype: num
exsolution: `r Ept`
exname: ddt_energy
extol: 1