```{r,echo=F,warning=F}
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("t^0","",exp,fixed=T)
  exp = gsub("t^1","x",exp,fixed=T)
  return(exp)
}

fracs = c(1,1/2,1/3,1/4,1/5,2/3,2/5,3/4,3/5,4/5,2,3,4,5,3/2,5/2,4/3,5/3,5/4)

nums = c(1,1,1,1,1,2,2,3,3,4,2,3,4,5,3,5,4,5,5)
dens = c(1,2,3,4,5,3,5,4,5,5,1,1,1,1,2,2,3,3,4)

nums = c(nums,-nums)
dens = c(dens,dens)
fracs = c(fracs,-fracs)

while(T){
  a = sample(-5:5,1)
  w = sample(1:length(nums),1)
  m = fracs[w]
  p = runif(1,-2,2)
  q = runif(1,-2,2)
  # f'(x) = m*(1+qx-qa)+p(x-a)^2 = mqx+(m-mqa)+px^2-2apx+pa^2 = 
  # f'(x) = px^2+(mq-2ap)x+(m-mqa+pa^2)
  # f(x) = p/3*x^3+(mq-2pa)/2*x^2+(m-m*q*a+p*a^2)x+D
  A = p/3
  B = (m*q-2*a*p)/2
  C = (m-m*q*a+p*a^2)
  D = -(A*a^3+B*a^2+C*a)+sample(1:3,1)*sample(c(-1,1),1)
  x = seq(-11,11,length.out=1000)
  y = A*x^3+B*x^2+C*x+D
  ya = A*a^3+B*a^2+C*a+D
  if(max(abs(y))<30 && a!=0){break}
}
```

Question
========

The graph of $y=f(x)$ is shown below. Also, at $x=`r a`$, a [tangent line](https://en.wikipedia.org/wiki/Tangent) is drawn.

```{r,echo=F,fig.dim=c(8,8)}
par(pty="s")
plot(x,y,type="l",col="blue",lwd=3,xlim=c(-10,10),ylim=c(-10,10))
arrows(-10,0,10,0,length=0.15,angle=20,code=3,col="black",lwd=2)
arrows(0,-10,0,10,length=0.15,angle=20,code=3,col="black",lwd=2)
for(i in 1:10){
  abline(h=i,col="grey")
  abline(h=-i,col="grey")
  abline(v=i,col="grey")
  abline(v=-i,col="grey")
}
lines(x,y,col="blue",lwd=3)
lines(x,m*(x-a)+ya,col="red",lwd=2)
points(a,ya,col="purple",pch=19)
legend("top",legend=c("y=f(x)","tangent"),col=c("blue","red"),lwd=c(3,2))
```
\

The tangent line can be used to determine the [instantaneous rate of change](https://en.wikipedia.org/wiki/Derivative) of $f(x)$ at $x=`r a`$. 

Please estimate $f'(`r a`)$ within the nearest hundredth. This could also be notated as $\left.\frac{df(x)}{dx}\right|_{x=`r a`}$ or as $\frac{df}{dx}(`r a`)$. For more, see [wikipedia's article on notation for differentiation](https://en.wikipedia.org/wiki/Notation_for_differentiation).


Solution
========

Notice the tangent line intersects $f(x)$ at point $(`r a`,`r ya`)$. From there, follow the red line until you get to another point with integer coordinates.

```{r,echo=F,fig.dim=c(8,8)}
par(pty="s")
plot(x,y,type="l",col="blue",lwd=1,xlim=c(-10,10),ylim=c(-10,10))
arrows(-10,0,10,0,length=0.15,angle=20,code=3,col="darkgrey",lwd=2)
arrows(0,-10,0,10,length=0.15,angle=20,code=3,col="darkgrey",lwd=2)
for(i in 1:10){
  abline(h=i,col="grey")
  abline(h=-i,col="grey")
  abline(v=i,col="grey")
  abline(v=-i,col="grey")
}
lines(x,y,col="blue",lwd=1)
lines(x,m*(x-a)+ya,col="red",lwd=1)
points(a,ya,col="purple",pch=19)
legend("top",legend=c("y=f(x)","tangent"),col=c("blue","red"),lwd=c(1,1))
points(a+dens[w],ya+nums[w],pch=19)
lines(c(a,a+dens[w]),c(ya,ya),col="darkgreen",lwd=2)
lines(c(a+dens[w],a+dens[w]),c(ya,ya+nums[w]),col="darkgreen",lwd=2)
text(a+dens[w]/2,ya-0.5*sign(nums[w]),dens[w],cex=2,col="darkgreen")
text(a+dens[w]+0.5,ya+0.5*nums[w],nums[w],cex=2,col="darkgreen")
```
\

The slope of the tangent line is found with "rise over run".

$$m ~=~ \frac{`r nums[w]`}{`r dens[w]`}$$

$$m ~=~ `r m`$$

So, the equation of the tangent line in point-slope form is $y=`r round(m,3)`(x-(`r a`))+(`r ya`)$. More importantly for this question, the slope of the tangent line equals the instantaneous rate of change of the function, which equals the derivative at $x=`r a`$. In other words,
$$f'(`r a`) ~=~ `r m`$$


$$\left.\frac{df(x)}{dx}\right|_{x=`r a`} ~=~ `r m`$$


$$\frac{df}{dx}(`r a`) ~=~ `r m`$$


Meta-information
============
extype: num
exsolution: `r m`
exname: ddt_energy
extol: 0.01