```{r,echo=F}
trips = list(c(3,4,5),
             c(5, 12, 13),
             c(8, 15, 17),
             c(7, 24, 25),
             c(20, 21, 29),
             c(12, 35, 37),
             c(9, 40, 41),
             c(28, 45, 53),
             c(11, 60, 61),
             c(16, 63, 65),
             c(33, 56, 65),
             c(48, 55, 73),
             c(13, 84, 85),
             c(36, 77, 85),
             c(39, 80, 89),
             c(65, 72, 97))
trp = trips[[sample(1:length(trips),1)]]
a = trp[1]
b = trp[2]
c = trp[3]
sols = c(a,c,b,c,a,b,c,a,c,b,b,a,
         b,c,a,c,b,a,c,b,c,a,a,b)

sols2 = character()
for(i in 1:length(sols)){
  sols2 = c(sols2,paste0(1*(c(a,b,c)==sols[i]),collapse=""))
}

al = paste0("* ",rep(list(a,b,c),24),"\n",collapse="")
```

Question
========

Consider the right triangle with lengths `r trp` and acute angles $\phi$ and $\theta$, where $\theta<\phi$. Find all the [trigonometric ratios](https://en.wikipedia.org/wiki/Trigonometric_functions#Right-angled_triangle_definitions). 

```{r, echo=F, fig.dim=c(5,5)}
library(latex2exp)
par(pty="s",mar=c(0,0,0,0))
a = trp[1]
b = trp[2]
c = trp[3]
theta = atan(a/b)
phi = atan(b/a)
y1 = 0.5-a/b/2
y2 = 0.5+a/b/2
plot(c(0,1,1,0),c(y1,y1,y2,y1),type="l",lwd=2,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
lines(c(0.95,0.95,1),c(y1,y1+0.05,y1+0.05))
text(0.5,y1-0.05,b)
text(1.05,0.5,a)
text(0.06/theta*cos(theta/2),y1+0.06/theta*sin(theta/2),TeX("$\\theta$"))
text(1+0.06/phi*cos(3*pi/2-phi/2),y2+0.06/phi*sin(3*pi/2-phi/2),TeX("$\\phi$"))
text(c/b/2*cos(theta)+0.05*cos(theta+pi/2),
     y1+c/b/2*sin(theta)+0.05*sin(theta+pi/2),
     c,
     srt=theta/pi*180)


```
\



* $\sin(\theta)$ = ##ANSWER1##/##ANSWER2##
* $\cos(\theta)$ = ##ANSWER3##/##ANSWER4##
* $\tan(\theta)$ = ##ANSWER5##/##ANSWER6##
* $\csc(\theta)$ = ##ANSWER7##/##ANSWER8##
* $\sec(\theta)$ = ##ANSWER9##/##ANSWER10##
* $\cot(\theta)$ = ##ANSWER11##/##ANSWER12##
* $\sin(\phi)$ = ##ANSWER13##/##ANSWER14##
* $\cos(\phi)$ = ##ANSWER15##/##ANSWER16##
* $\tan(\phi)$ = ##ANSWER17##/##ANSWER18##
* $\csc(\phi)$ = ##ANSWER19##/##ANSWER20##
* $\sec(\phi)$ = ##ANSWER21##/##ANSWER22##
* $\cot(\phi)$ = ##ANSWER23##/##ANSWER24##

Answerlist
--------

`r al`


Solution
========

This is definitional. It is also exhaustive and tediuous. Sorry?

* $\sin(\theta) = \frac{`r a`}{`r c`}$
* $\cos(\theta) = \frac{`r b`}{`r c`}$
* $\tan(\theta) = \frac{`r a`}{`r b`}$
* $\csc(\theta) = \frac{`r c`}{`r a`}$
* $\sec(\theta) = \frac{`r c`}{`r b`}$
* $\cot(\theta) = \frac{`r b`}{`r a`}$
* $\sin(\phi) = \frac{`r b`}{`r c`}$
* $\cos(\phi) = \frac{`r a`}{`r c`}$
* $\tan(\phi) = \frac{`r b`}{`r a`}$
* $\csc(\phi) = \frac{`r c`}{`r b`}$
* $\sec(\phi) = \frac{`r c`}{`r a`}$
* $\cot(\phi) = \frac{`r a`}{`r b`}$

Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",24),collapse="|")`
exsolution: `r paste0(sols2,collapse="|")`
exname: trig_ratios_from_sides