```{r,echo=F}
while(T){
  t = runif(1,2*pi,6*pi)*sample(c(-1,1),1)
  x = round(cos(t),3)
  y = round(sin(t),3)
  ta = round(y/x,3)
  cs = round(1/y,3)
  se = round(1/x,3)
  co = round(x/y,3)
  al = sort(c(x,y,ta,cs,se,co))
  anli = paste0("* ",al,collapse="\n")
  a1 = paste0(1*(y==al),collapse="")
  a2 = paste0(1*(x==al),collapse="")
  a3 = paste0(1*(ta==al),collapse="")
  a4 = paste0(1*(cs==al),collapse="")
  a5 = paste0(1*(se==al),collapse="")
  a6 = paste0(1*(co==al),collapse="")
  if(abs(abs(x)-abs(y))>0.01 && abs(x)>0.01 && abs(y)>0.01 && length(unique(al))==6 && min(diff(sort(abs(al))))>0.01 && 
     sum(y==al)==1 &&
     sum(x==al)==1 &&
     sum(ta==al)==1 &&
     sum(cs==al)==1 &&
     sum(se==al)==1 &&
     sum(co==al)==1){break}
}

```

Question
========

An angle, $\theta$, is shown below in standard position as a blue spiraling arrow. A radius (of length 1) is drawn at that angle. Where the radius connects to the circumference of the unit circle has Cartesian coordinates $(`r x`, `r y`)$.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",ann=F,axes=F,asp=1,xlim=c(-1.4,1.4),ylim=c(-1.4,1.4))
for(i in seq(-1.5,1.5,0.1)){
  abline(h=i,col="grey",lty=3)
  abline(v=i,col="grey",lty=3)
}
arrows(-1.1,0,1.1,0,length=0.1,angle=10,code=3,lwd=2)
arrows(0,-1.1,0,1.1,length=0.1,angle=10,code=3,lwd=2)
th = seq(0,2*pi,length.out=360)
lines(cos(th),sin(th),lwd=2)
lo = round(abs(t*30))
th = seq(0,t,length.out=lo)
lines(0.1*(3+abs(th)/2/pi)*cos(th),0.1*(3+abs(th)/2/pi)*sin(th),col="blue")
arrows(0.1*(3+abs(th[lo-1])/2/pi)*cos(th[lo-1]),0.1*(3+abs(th[lo-1])/2/pi)*sin(th[lo-1]),
       0.1*(3+abs(th[lo])/2/pi)*cos(th[lo]),0.1*(3+abs(th[lo])/2/pi)*sin(th[lo]),col="blue",length=0.2,angle=30)
lines(c(0,cos(t)),c(0,sin(t)),col=rgb(1,0.7,0.7))
points(cos(t),sin(t),col="red",pch=20)
text(1.3*cos(t),1.3*sin(t),paste0("(",sprintf("%.3f",x),", ",sprintf("%.3f",y),")"),col="red")
text(0.7*cos(t)+0.05*cos(t+pi/2*sign(t)),0.7*sin(t)+0.05*sin(t+pi/2*sign(t)),"1",col="red")
```
\

Calculate the trigonometric ratios of $\theta$.

* The sine: $\sin(\theta) =$ ##ANSWER1## 
* The cosine: $\cos(\theta)=$ ##ANSWER2##
* The tangent: $\tan(\theta)=$ ##ANSWER3##
* The cosecant: $\csc(\theta)=$ ##ANSWER4##
* The secant: $\sec(\theta)=$ ##ANSWER5##
* The cotangent: $\cot(\theta)=$ ##ANSWER6##

Answerlist
--------

`r anli`
`r anli`
`r anli`
`r anli`
`r anli`
`r anli`

Solution
========

| function | expression | number | 
|:---:|:---:|:---:|
| sine | $y$ | `r y` |
| cosine | $x$ | `r x` |
| tangent | $\frac{y}{x}$ | `r ta` |
| cosecant | $\frac{1}{y}$ | `r cs` |
| secant | $\frac{1}{x}$ | `r se` |
| cotangent | $\frac{x}{y}$ | `r co` |


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r a1`|`r a2`|`r a3`|`r a4`|`r a5`|`r a6`
exname: unit_circle_float