```{r data generation, echo = FALSE, results = "hide"}
## This version does not have the composition element of inverse functions... just table

x = 1:7
while(T){
  f = sample(x)
  canpass = T
  for(i in x){
    if(which(f==i)==f[i]){
      canpass = F
    }
  }
  if(sum(f==x)==0 && canpass){break}
}

fi = numeric()
for(i in x){
  fi = c(fi,which(f==i))
}
al = paste0("* ",x,"\n",collapse="")
al2 = paste0(rep(al,length(x)),collapse="")
ans = character()
for(i in x){
  ans = c(ans,paste0(1*(x==fi[i]),collapse=""))
}

rx = sample(x,4)
ff = f[f[rx[1]]]
fg = f[fi[rx[2]]]
gf = fi[f[rx[3]]]
gg = fi[fi[rx[4]]]

p2nums = c(ff,fg,gf,gg)
p2nams = c(paste0("f(f(",rx[1],"))"),
           paste0("f(f^{-1}(",rx[2],"))"),
           paste0("f^{-1}(f(",rx[3],"))"),
           paste0("f^{-1}(f^{-1}(",rx[4],"))")
)

p2exp = c(paste0("f(f(",rx[1],")) = f(",f[rx[1]],") = ",f[f[rx[1]]]),
          paste0("f(f^{-1}(",rx[2],")) = f(",fi[rx[2]],") = ",f[fi[rx[2]]]),
          paste0("f^{-1}(f(",rx[3],")) = f^{-1}(",f[rx[3]],") = ",fi[f[rx[3]]]),
          paste0("f^{-1}(f^{-1}(",rx[4],")) = f^{-1}(",fi[rx[4]],") = ",fi[fi[rx[4]]])
          )

p2ord = sample(1:4)
p2ans1 = paste0(1*(p2nums[1]==x),collapse="")
p2ans2 = paste0(1*(p2nums[2]==x),collapse="")
p2ans3 = paste0(1*(p2nums[3]==x),collapse="")
p2ans4 = paste0(1*(p2nums[4]==x),collapse="")
n = length(x)

p2ans = c(p2ans1,p2ans2,p2ans3,p2ans4)

p2q = paste0("* Calculate $",p2nams[p2ord],"$ = ##ANSWER",(n+1):(n+length(p2ord)),"##\n",collapse="")

p2al = paste0("* ",x,"\n",collapse="")
p2al2 = paste0(rep(p2al,length(p2ord)),collapse="")

p2es = paste0("* Use tables: $",p2exp[p2ord],"$\n",collapse="")
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

Let a [one-to-one function](https://en.wikipedia.org/wiki/Injective_function), $f$, be defined by the table below.

```{r tab2, results="asis", echo=F}
mydf2 = data.frame(x,f)
colnames(mydf2) = c("$x$","$f(x)$")
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


Create the [inverse function's](https://en.wikipedia.org/wiki/Inverse_function){target="_blank"} table.

```{r tab4, results="asis", echo=F}
allans = paste0("##ANSWER",x,"##")
mydf4 = data.frame(x,allans)
colnames(mydf4) = c("$x$","$f^{-1}(x)$")
knitr::kable(mydf4,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


Answerlist
--------
`r al2`


Solution
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

The inverse function $f^{-1}$ is defined by the table below.

```{r tab3, results="asis", echo=F}
mydf3 = data.frame(x,fi)
colnames(mydf3) = c("$x$","$f^{-1}(x)$")
knitr::kable(mydf3,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

Notice, you just switch the columns of the given $f$ table and then sort by the first column.


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",length(x)),collapse="|")`
exsolution: `r paste0(ans,collapse="|")`
exname: inverse_table