---
title: "Create Inverse Function"
date: "Wed Aug 27"
output: 
    slidy_presentation:
        incremental: true
        css: style.css
---

# An inverse function UNDOES operations in REVERSE order

To put on footwear:

1. Put on socks.
2. Put on shoes.
3. Tie shoes.

To invert...

1. Untie shoes
2. Remove shoes
3. Remove socks


# PEMDAS: order of operations

Review, evaluate the expression:

$$10-2\cdot 3$$

* The multiplication occurs before the subtraction.
* $10-6~=~ 4$


# Many functions are a sequence of operations.


Consider the function shown below:

$$f(x)~=~\frac{2x-7}{5}$$

What are the operations applied to the input?

1. Multiply by 2.
2. Subtract 7.
3. Divide by 5.

* How would you undo those operations in reverse order?

1. Multiply by 5.
2. Add 7.
3. Divide by 2.

* Indeed, $f^{-1}(x)~=~\frac{5x+7}{2}$


# A function and its inverse undo each other

Consider the algebraic definitions of a function and its inverse:

$$f(x)~=~\frac{2x-7}{5}$$

$$f^{-1}(x)~=~\frac{5x+7}{2}$$

Evaluate $f(11)$

# A function and its inverse undo each other

Consider the algebraic definitions of a function and its inverse:

$$f(x)~=~\frac{2x-7}{5}$$

$$f^{-1}(x)~=~\frac{5x+7}{2}$$

Evaluate $f(11)$

$$f(11)~=~\frac{2(11)-7}{5}$$


$$f(11)~=~\frac{22-7}{5}$$


$$f(11)~=~\frac{15}{5}$$


$$f(11)~=~3$$

# A function and its inverse undo each other

Consider the algebraic definitions of a function and its inverse:

$$f(x)~=~\frac{2x-7}{5}$$

$$f^{-1}(x)~=~\frac{5x+7}{2}$$

Evaluate $f^{-1}(3)$


# A function and its inverse undo each other

Consider the algebraic definitions of a function and its inverse:

$$f(x)~=~\frac{2x-7}{5}$$

$$f^{-1}(x)~=~\frac{5x+7}{2}$$

Evaluate $f^{-1}(3)$

$$f^{-1}(3)~=~\frac{5(3)+7}{2}$$

$$f^{-1}(3)~=~\frac{15+7}{2}$$

$$f^{-1}(3)~=~\frac{22}{2}$$

$$f^{-1}(3)~=~11$$

# A function and its inverse undo each other

Consider the algebraic definitions of a function and its inverse:

$$f(x)~=~\frac{2x-7}{5}$$

$$f^{-1}(x)~=~\frac{5x+7}{2}$$

Notice $f(11)=3$ and $f^{-1}(3)=11$.


# To get an inverse function, "swap $x$ and $y$"

A one-to-one function, $g$, is defined with the table below.

```{r,echo=F,warning=F}
library(kableExtra)
set.seed(123)
x = 1:6
g = sample(1:6)
df = data.frame(x,g)
colnames(df) = c("$x$","$g(x)$")
df %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

Can you identify the values to put in the inverse function's table?

```{r,echo=F,warning=F}
x = 1:6
gi = rep(" ",6)
df2 = data.frame(x,gi)
colnames(df2) = c("$x$","$g^{-1}(x)$")
df2 %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

# To get an inverse function, "swap $x$ and $y$"

A one-to-one function, $g$, is defined with the table below.

```{r,echo=F,warning=F}
library(kableExtra)
set.seed(123)
x = 1:6
g = sample(1:6)
df = data.frame(x,g)
colnames(df) = c("$x$","$g(x)$")
df %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

Can you identify the values to put in the inverse function's table?

```{r,echo=F,warning=F}
x = 1:6
gi = c("6",rep(" ",5))
df2 = data.frame(x,gi)
colnames(df2) = c("$x$","$g^{-1}(x)$")
df2 %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```


# To get an inverse function, "swap $x$ and $y$"

A one-to-one function, $g$, is defined with the table below.

```{r,echo=F,warning=F}
library(kableExtra)
set.seed(123)
x = 1:6
g = sample(1:6)
df = data.frame(x,g)
colnames(df) = c("$x$","$g(x)$")
df %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

Can you identify the values to put in the inverse function's table?

```{r,echo=F,warning=F}
x = 1:6
gi = c("6","3",rep(" ",4))
df2 = data.frame(x,gi)
colnames(df2) = c("$x$","$g^{-1}(x)$")
df2 %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```


# To get an inverse function, "swap $x$ and $y$"

A one-to-one function, $g$, is defined with the table below.

```{r,echo=F,warning=F}
library(kableExtra)
set.seed(123)
x = 1:6
g = sample(1:6)
df = data.frame(x,g)
colnames(df) = c("$x$","$g(x)$")
df %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

Can you identify the values to put in the inverse function's table?

```{r,echo=F,warning=F}
x = 1:6
gi = c("6","3","1",rep(" ",3))
df2 = data.frame(x,gi)
colnames(df2) = c("$x$","$g^{-1}(x)$")
df2 %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

# To get an inverse function, "swap $x$ and $y$"

A one-to-one function, $g$, is defined with the table below.

```{r,echo=F,warning=F}
library(kableExtra)
set.seed(123)
x = 1:6
g = sample(1:6)
df = data.frame(x,g)
colnames(df) = c("$x$","$g(x)$")
df %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

Can you identify the values to put in the inverse function's table?

```{r,echo=F,warning=F}
x = 1:6
gi = c("6","3","1","4",rep(" ",2))
df2 = data.frame(x,gi)
colnames(df2) = c("$x$","$g^{-1}(x)$")
df2 %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

# To get an inverse function, "swap $x$ and $y$"

A one-to-one function, $g$, is defined with the table below.

```{r,echo=F,warning=F}
library(kableExtra)
set.seed(123)
x = 1:6
g = sample(1:6)
df = data.frame(x,g)
colnames(df) = c("$x$","$g(x)$")
df %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

Can you identify the values to put in the inverse function's table?

```{r,echo=F,warning=F}
x = 1:6
gi = c("6","3","1","4","5"," ")
df2 = data.frame(x,gi)
colnames(df2) = c("$x$","$g^{-1}(x)$")
df2 %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

# To get an inverse function, "swap $x$ and $y$"

A one-to-one function, $g$, is defined with the table below.

```{r,echo=F,warning=F}
library(kableExtra)
set.seed(123)
x = 1:6
g = sample(1:6)
df = data.frame(x,g)
colnames(df) = c("$x$","$g(x)$")
df %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```

Can you identify the values to put in the inverse function's table?

```{r,echo=F,warning=F}
x = 1:6
gi = c("6","3","1","4","5","2")
df2 = data.frame(x,gi)
colnames(df2) = c("$x$","$g^{-1}(x)$")
df2 %>%
kable() %>%
kable_styling(bootstrap_options = c("bordered","striped","condensed"),full_width = F)
```




