---
title: "Evaluate Function and Evaluate Inverse Function"
date: "Wed Aug 27"
output: 
    slidy_presentation:
        incremental: true
        css: style.css
---

# Entrance ticket

Complete the entrance ticket on Canvas.

[Entrance_Ticket_Aug_27](https://bart.instructure.com/courses/2110/quizzes/3139)


# Function evaluation from table

The table below defines 3 one-to-one functions: $f$, $g$, and $h$.

```{r,echo=F,warning=FALSE}
library(kableExtra)
x = 1:6
f = 11:16
g = 16:11
h = c(11,16,12,15,13,14)

df = data.frame(x,f,g,h)
colnames(df) = c("x","f(x)","g(x)","h(x)")

df %>%
kable() %>%
kable_styling(bootstrap_options=c("striped", "hover","bordered","condensed"))
```

* Examples of function notation:
    * $f(2)~=~12$
    * $g(2)~=~15$
    * $h(5)~=~?$
    
    
# Inverse function evaluation from table

The table below defines 3 one-to-one functions: $f$, $g$, and $h$.

```{r,echo=F,warning=FALSE}
library(kableExtra)
x = 1:6
f = 11:16
g = 16:11
h = c(11,16,12,15,13,14)

df = data.frame(x,f,g,h)
colnames(df) = c("x","f(x)","g(x)","h(x)")

df %>%
kable() %>%
kable_styling(bootstrap_options=c("striped", "hover","bordered","condensed"))
```

* Examples of inverse function notation:
    * $f^{-1}(12)~=~2$
    * $g^{-1}(14)~=~3$
    * $h^{-1}(14)~=~?$


# Evaluate function from algebraic definition

Let a function, $f$, be defined with the following algebraic expression:

$$f(x)~=~2x+3$$

* Evaluate:
    * $f(4)~=~ ?$ 
    * $f(4) ~=~ 2\cdot 4 + 3$
    * $f(4) ~=~ 11$
    * $f(10) ~=~ ?$
    * $f(10) ~=~ 23$
    * $f(100) ~=~ ?$
    * $f(100) ~=~ 203$

# Evaluate function from curve

```{r,echo=F}
set.seed(55)
rands = sample(1:9,8)
xbase = rands[1:3]
x = sort(c(0,rands[1:3],10))
y = rands[4:8]
x1 = sample(xbase,1)
y1 = y[x==x1]
```

```{r,fig.dim=c(4,4),echo=FALSE}
par(pty="s",mar=c(4,4,0,0))
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="y",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
legend("topright","y = f(x)",lwd=4,col="blue")
```
\

Evaluate $f(`r x1`)$

# Evaluate function from curve

```{r,echo=F}
set.seed(55)
rands = sample(1:9,8)
xbase = rands[1:3]
x = sort(c(0,rands[1:3],10))
y = rands[4:8]
x1 = sample(xbase,1)
y1 = y[x==x1]
```

```{r,fig.dim=c(4,4),echo=FALSE}
par(pty="s",mar=c(4,4,0,0))
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="y",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
legend("topright","y = f(x)",lwd=4,col="blue")

points(x1,y1,cex=1.3,pch=19,col="black")
points(x1,y1,pch=19,col="red")
```
\

$$f(`r x1`)~=~`r y1`$$

# Evaluate function from curve

```{r,echo=F}
set.seed(55)
rands = sample(1:9,8)
xbase = rands[1:3]
x = sort(c(0,rands[1:3],10))
y = rands[4:8]
x1 = sample(xbase,1)
y1 = y[x==x1]
```

```{r,fig.dim=c(4,4),echo=FALSE}
par(pty="s",mar=c(4,4,0,0))
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="y",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
legend("topright","y = f(x)",lwd=4,col="blue")

```
\

Evaluate $f(5)$.
$$f(5)~=~?$$

* $f(5)~=~2$


# Evaluate inverse from one-to-one function curve

```{r,echo=F}
set.seed(45)
while(T){
  rands = sample(1:9,8)
  xbase = rands[1:3]
  x = sort(c(0,rands[1:3],10))
  isdown=sample(c(T,F),1)
  y = sort(rands[4:8],decreasing = isdown)
  x1 = sample(xbase,1)
  y1 = y[x==x1]
  if(length(unique(diff(y)/diff(x)))>2){break}
}
```

```{r,fig.dim=c(4,4),echo=FALSE}
par(pty="s",mar=c(4,4,0,0))
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="y",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
legend("topright","y = f(x)",lwd=4,col="blue")
```
\

Evaluate $f^{-1}(`r y1`)$

# Evaluate inverse from one-to-one function curve

```{r,echo=F}
set.seed(45)
while(T){
  rands = sample(1:9,8)
  xbase = rands[1:3]
  x = sort(c(0,rands[1:3],10))
  isdown=sample(c(T,F),1)
  y = sort(rands[4:8],decreasing = isdown)
  x1 = sample(xbase,1)
  y1 = y[x==x1]
  if(length(unique(diff(y)/diff(x)))>2){break}
}
```

```{r,fig.dim=c(4,4),echo=FALSE}
par(pty="s",mar=c(4,4,0,0))
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="y",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
legend("topright","y = f(x)",lwd=4,col="blue")

points(x1,y1,cex=1.3,pch=19,col="black")
points(x1,y1,pch=19,col="red")
```
\

$$f^{-1}(`r y1`)~=~`r x1`$$

# Evaluate inverse from one-to-one function curve

```{r,echo=F}
set.seed(45)
while(T){
  rands = sample(1:9,8)
  xbase = rands[1:3]
  x = sort(c(0,rands[1:3],10))
  isdown=sample(c(T,F),1)
  y = sort(rands[4:8],decreasing = isdown)
  x1 = sample(xbase,1)
  y1 = y[x==x1]
  if(length(unique(diff(y)/diff(x)))>2){break}
}
```

```{r,fig.dim=c(4,4),echo=FALSE}
par(pty="s",mar=c(4,4,0,0))
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="y",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
legend("topright","y = f(x)",lwd=4,col="blue")
```
\

Evaluate $f^{-1}(2)$.
$$f^{-1}(2)~=~?$$

* $f^{-1}(2)~=~10$