---
output: pdf_document
---

# Lindenmayer Systems and Turtle Graphics


```{r,echo=F}

getstr = function(start="A",
                  rules=list("A"="A[+A][-A]b","b"="[+C][-C]","C"="CC"),
                  n=10){
    st = start
    for(jj in 1:n){
        st2 = ""
        for(i in 1:nchar(st)){
            ch = substr(st,i,i)
            # cn = as.integer(charToRaw(ch))
            if(!is.null(rules[[ch]])){
                st2 = paste0(st2,rules[[ch]],collapse="")
            } else {
                st2 = paste0(st2,ch,collapse="")
            }
        }
        st = st2
    }
    return(st)
}

getxyc = function(string="AA+AA+AA+A+A",angle=pi/2,angle_initial=pi/2,col="blue"){
    switch = 1
    d = angle_initial
    x = 0
    y = 0
    xl = c(x)
    yl = c(y)
    cols = numeric()
    dsave = numeric()
    xsave = numeric()
    ysave = numeric()
    for(i in 1:nchar(string)){
        ch = substr(string,i,i)
        cn = as.integer(charToRaw(ch))
        if(cn>=as.integer(charToRaw("A")) && cn<=as.integer(charToRaw("L"))){
            cols = c(cols,col)
            x = x+cos(d)
            y = y+sin(d)
            xl = c(xl,x)
            yl = c(yl,y)
        }
        if(cn>=as.integer(charToRaw("M")) && cn<=as.integer(charToRaw("Z"))){
            cols = c(cols,"NA")
            x = x+cos(d)
            y = y+sin(d)
            xl = c(xl,x)
            yl = c(yl,y)
        }
        if(cn==as.integer(charToRaw("["))){
            dsave = c(dsave,d)
            xsave = c(xsave,x)
            ysave = c(ysave,y)
        }
        if(cn==as.integer(charToRaw("]"))){
            cols = c(cols,"NA")
            x = xsave[length(xsave)]
            y = ysave[length(ysave)]
            d = dsave[length(dsave)]
            if(length(xsave)>1){
                xsave = xsave[1:(length(xsave)-1)]
                ysave = ysave[1:(length(ysave)-1)]
                dsave = dsave[1:(length(dsave)-1)]
            } else {
                xsave = numeric()
                ysave = numeric()
                dsave = numeric()
            }
            xl = c(xl,x)
            yl = c(yl,y)
        }
        if(cn==as.integer(charToRaw("-"))){
            d = d-angle
        }
        if(cn==as.integer(charToRaw("+"))){
            d = d+angle
        }
        if(cn==as.integer(charToRaw("."))){
            switch = switch*(-1)
        }
    }
    
    xwid = max(xl)-min(xl)
    ywid = max(yl)-min(yl)
    xmid = (max(xl)+min(xl))/2
    ymid = (max(yl)+min(yl))/2
    wid = max(c(xwid,ywid))
    x2 = (xl-xmid)/wid*2
    y2 = (yl-ymid)/wid*2
    return(list(x2,y2,cols))
}

makeplot = function(xyc,lwd=1){
    x = xyc[[1]]
    y = xyc[[2]]
    c = xyc[[3]]
    plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
    # lines(x2,y2)
    for(i in 2:length(x)){
        lines(c(x[i-1],x[i]),c(y[i-1],y[i]),col=c[i-1])
    }
}
```


```{r,echo=F,fig.dim=c(6,1)}
minus = 2
par(mfrow=c(1,6),mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")

start = c("A")
rules = list("A"="B-C-B-C-",
             "B"="B+B-",
             "C"="B")
s = getstr(start,rules,10-minus)
xyc = getxyc(s,pi/2,angle_initial=3*pi/4,col="red")
makeplot(xyc,lwd=0.3)

start = c("A")
rules = list("A"="AA[+A][-A]")
s = getstr(start,rules,n=6-minus)
xyc = getxyc(s,pi/3,angle_initial=pi/2,col="orange")
makeplot(xyc,lwd=0.3)

start = c("-x")
rules = list("x"="F+[[x]-x]-F[-Fx]+x",
             "F"="FF")
s = getstr(start,rules,n=6-minus)
xyc = getxyc(s,25/180*pi,angle_initial=pi/2,col="darkgreen")
makeplot(xyc,lwd=0.3)

start = c("A")
rules = list("A"="B-A-B",
             "B"="A+B+A")
s = getstr(start,rules,n=6-minus)
xyc = getxyc(s,pi/3,angle_initial=pi/2,col="blue")
makeplot(xyc,lwd=0.3)

start = c("F")
rules = list("F"="F+G",
             "G"="F-G")
s = getstr(start,rules,n=10-minus)
xyc = getxyc(s,pi/2,angle_initial=pi/2,col="purple")
makeplot(xyc,lwd=0.3)

start = c("A")
rules = list("A"="AB",
             "B"="[-A][+A]")
s = getstr(start,rules,n=13-minus)
xyc = getxyc(s,pi/12,angle_initial=pi/2,col="black")
makeplot(xyc,lwd=0.3)
```


A [Lindenmayer system](https://en.wikipedia.org/wiki/L-system) (or L-system) is a set of rewrite rules. When these rules are repeatedly applied to a starting string ("word"), we can get complex results from simple rules. For example:

```
Start:
    x
Rules:
    A > AA
    x > xAx
The start string and first 4 recursions:
    0. x
    1. xAx
    2. xAxAAxAx
    3. xAxAAxAxAAAAxAxAAxAx
    4. xAxAAxAxAAAAxAxAAxAxAAAAAAAAxAxAAxAxAAAAxAxAAxAx
```


# Practice

* Start
    * A
* Rules
    A $\to$ BA
    B $\to$ AB
* Write the first 5 iterations of this L-system:





\newpage  
   

When these letters correspond to drawing commands (like move forward, turn 15°, or go back to last saved spot), we can get fractals.

