---
output: pdf_document
---


```{r,echo=F}
start = c("A")
rules = list("A"="+B-A-B+",
             "B"="-A+B+A-")
n = 6
sts = start
st = start
for(jj in 1:n){
    st2 = ""
    for(i in 1:nchar(st)){
        ch = substr(st,i,i)
        # cn = as.integer(charToRaw(ch))
        st2 = paste0(st2,rules[[ch]])
    } 
    sts = c(sts,st2)
    st = st2
}
```


```{r,echo=F,fig.dim=c(2,2)}
string = sts[7]
angle = pi/4
switch = 1
d = 0
x = 0
y = 0
xl = c(x)
yl = c(y)
cols = numeric()
dsave = numeric()
xsave = numeric()
ysave = numeric()
for(i in 1:nchar(string)){
    ch = substr(string,i,i)
    cn = as.integer(charToRaw(ch))
    if(cn>=as.integer(charToRaw("A")) && cn<=as.integer(charToRaw("L"))){
        cols = c(cols,"blue")
        x = x+cos(d)
        y = y+sin(d)
        xl = c(xl,x)
        yl = c(yl,y)
    }
    if(cn>=as.integer(charToRaw("M")) && cn<=as.integer(charToRaw("Z"))){
        cols = c(cols,"NA")
        x = x+cos(d)
        y = y+sin(d)
        xl = c(xl,x)
        yl = c(yl,y)
    }
    if(cn==as.integer(charToRaw("["))){
        dsave = c(dsave,d)
        xsave = c(xsave,d)
        ysave = c(ysave,d)
    }
    if(cn==as.integer(charToRaw("["))){
        cols = c(cols,"NA")
        x = xsave[length(xsave)]
        y = ysave[length(ysave)]
        d = dsave[length(dsave)]
        if(length(xsave)>1){
            xsave = xsave[1:(length(xsave)-1)]
            ysave = ysave[1:(length(xsave)-1)]
            dsave = dsave[1:(length(xsave)-1)]
        } else {
            xsave = numeric()
            ysave = numeric()
            dsave = numeric()
        }
        xl = c(xl,x)
        yl = c(yl,y)
    }
    if(cn==as.integer(charToRaw("-"))){
        d = d-angle*switch
    }
    if(cn==as.integer(charToRaw("+"))){
        d = d+angle*switch
    }
    if(cn==as.integer(charToRaw("."))){
        switch = switch*(-1)
    }
}
xwid = max(xl)-min(xl)
ywid = max(yl)-min(yl)
xmid = (max(xl)+min(xl))/2
ymid = (max(yl)+min(yl))/2
wid = max(c(xwid,ywid))
x2 = (xl-xmid)/wid*2
y2 = (yl-ymid)/wid*2

par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
lines(x2,y2)
# for(i in 2:length(xl)){
#     lines(c(x2[i-1],x2[i]),c(y2[i-1],y2[i]),col="blue")
# }
polygon(c(-1,-1,1,1),c(-1,1,1,-1))
print(x2)
print(y2)
print(cols)
```


A [Lindenmayer system](https://en.wikipedia.org/wiki/L-system) (or L-system) is a set of rewrite rules. When these rules are iterated multiple times, we can get complex results from rather simple rules. For example:

* Start
    * A
* Rules
    * A $\to$ AB
    * B $\to$ A
* Iterations:
    1. A
    2. AB
    3. ABA
    4. ABAAB
    5. ABAABABA
    6. ABAABABAABAAB
    
It might help to see this spaced out...

```
5. A  B  A  A  B  A  B  A
6. AB A  AB AB A  AB A  AB
```

# Practice

* Start
    * A
* Rules
    * A $\to$ BA
    * B $\to$ AB
* Write the first 5 iterations of this L-system:

\vspace{3in}
    
    
<!-- 1. A -->
<!-- 2. BA -->
<!-- 3. ABBA -->
<!-- 4. BAABABBA -->
<!-- 5. ABBABAABBAABABBA -->

When these letters correspond to drawing commands (like move forward, turn 15°, or go back to last saved spot), we can get fractals.

