---
output: slidy_presentation
title: "Lindenmayer Systems and Turtle Graphics"
author: "Mr. Worley"
date: "2025 Sep 29"
---

```{r,echo=F}
subtrahend = 2
```


```{r,echo=F,cache=T}
getstr = function(start="A",
                  rules=list("A"="A[+A][-A]b","b"="[+C][-C]","C"="CC"),
                  n=10){
    st = start
    for(jj in 1:n){
        ss = strsplit(st,"")[[1]]
        s2 = ss
        for(i in names(rules)){
            s2[ss==i] = rules[[i]]
        }
        st = paste0(s2,collapse="")
    }
    return(st)
}

getxyc = function(string="AA+AA+AA+A+A",angle=pi/2,angle_initial=pi/2){
    switch = 1
    d = angle_initial
    x = 0
    y = 0
    dsave = numeric()
    xsave = numeric()
    ysave = numeric()
    chs = strsplit(string,"")[[1]]
    xl = numeric(sum(chs %in% LETTERS)+sum(chs=="]")+1)
    yl = numeric(sum(chs %in% LETTERS)+sum(chs=="]")+1)
    draw = numeric(sum(chs %in% LETTERS)+sum(chs=="]")+1)
    j = 0
    for(i in 1:nchar(string)){
        ch = chs[i]
        cn = as.integer(charToRaw(ch))
        if(cn>=as.integer(charToRaw("A")) && cn<=as.integer(charToRaw("L"))){
            j = j+1
            draw[j+1] = 1
            x = x+cos(d)
            y = y+sin(d)
            xl[j+1] = x
            yl[j+1] = y
        }
        if(cn>=as.integer(charToRaw("M")) && cn<=as.integer(charToRaw("Z"))){
            j = j+1
            draw[j+1] = 0
            x = x+cos(d)
            y = y+sin(d)
            xl[j+1] = x
            yl[j+1] = y
        }
        if(cn==as.integer(charToRaw("["))){
            dsave = c(dsave,d)
            xsave = c(xsave,x)
            ysave = c(ysave,y)
        }
        if(cn==as.integer(charToRaw("]"))){
            j = j+1
            draw[j+1] = 0
            x = xsave[length(xsave)]
            y = ysave[length(ysave)]
            d = dsave[length(dsave)]
            if(length(xsave)>1){
                xsave = xsave[1:(length(xsave)-1)]
                ysave = ysave[1:(length(ysave)-1)]
                dsave = dsave[1:(length(dsave)-1)]
            } else {
                xsave = numeric()
                ysave = numeric()
                dsave = numeric()
            }
            xl[j+1] = x
            yl[j+1] = y
        }
        if(cn==as.integer(charToRaw("-"))){
            d = d-angle*switch
        }
        if(cn==as.integer(charToRaw("+"))){
            d = d+angle*switch
        }
        if(cn==as.integer(charToRaw("."))){
            switch = switch*(-1)
        }
    }
    
    xwid = max(xl)-min(xl)
    ywid = max(yl)-min(yl)
    xmid = (max(xl)+min(xl))/2
    ymid = (max(yl)+min(yl))/2
    wid = max(c(xwid,ywid))
    x2 = (xl-xmid)/wid*2
    y2 = (yl-ymid)/wid*2
    return(list(x2,y2,draw))
}

makeplot = function(xyd,lwd=1,col="blue"){
    x = xyd[[1]]
    y = xyd[[2]]
    d = xyd[[3]]
    plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
    starts = numeric()
    if(d[1]){
        starts = c(1)
    }
    starts = c(starts,which(diff(d)==1))
    ends = which(diff(d)==-1)
    if(d[length(d)]==1){
        ends = c(ends,length(d))
    }
    for(i in 1:length(starts)){
        lines(x[starts[i]:ends[i]],y[starts[i]:ends[i]],lwd=lwd,col=col)
    }
}

catinfo = function(angle,start,rules,N){
    cat(paste0("Angle = ",angle,"°\n"))
    cat(paste0("Start = ",start))
    cat("\n")
    cat("Rules:")
    cat("\n")
    cat(paste0("  ",names(rules)," > ",rules,collapse="\n"))
    cat(paste0("\nNumber of recursions = ",N))
}
```

# Examples

## Example 1

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
angle = 30
N = 7
start_angle = 90
start = "A"
rules = list("A"="A[+A][-A]B",
             "B"="[--B]A")
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
# print(xyc[[3]])
makeplot(xyc,lwd=0.6,col="darkgreen")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 2

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
angle = 60
N = 7
start_angle = 0
start = "A"
rules = list("A"="B+B+B+B+B+B+",
             "B"="B[--CCC-a][-CCC-a]B",
             "C"="CC",
             "a"="B+B+B+B+B+B+")
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=0.6,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 3

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="[----AAB][--AAB][++AAB]AAB",
             "B"="[-C][+C][--C][++C][---C][+++C]",
             "C"="CAB")
angle = 45
start_angle = 0
N = 6
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=0.6,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 4

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="[-AAB][--AAB][+AAB][++AAB]AAB",
             "B"="[-C][+C][--C][++C]CA",
             "C"="CC")
angle = 72
start_angle = 72/4
N = 5
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=0.6,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 5

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "a"
rules = list("a"="B+B+B+B+B+B",
             "B"="BB[---CCa]",
             "C"="CC")
angle = 60
start_angle = 0
N = 9
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 6

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="B+B+B+B+B",
             "B"="[-CCA]BB",
             "C"="CC")
angle = 72
start_angle = 0
N = 9
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 7

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="+A-B-B[B]",
             "B"="-B+A+A[A]")
angle = 45
start_angle = 0
N = 8
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```


## Example 8

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="AA[-A][+A]")
angle = 90
start_angle = 0
N = 8
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 9

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="AcbcA",
             "b"="[+A][-A][++A][--A][+++A][---A][++++A][----A][+++++A][-----A]",
             "c"="bAb")
angle = 30
start_angle = 0
N = 6
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 10

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "AB"
rules = list("A"="B--B",
             "B"="AA+++AA")
angle = 30
start_angle = 0
N = 12
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 11

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "x"
rules = list("x"="FFF[+FFF+FFF+FF+FF+F+Fx][-FFF-FFF-FF-FF-F-Fx]Fx",
             "F"="FFx")
angle = 30
start_angle = 90
N = 6
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=0.3,col="black")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 12

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="AB",
             "B"="A[++C][--C]",
             "C"="C[+C][-C]A")
angle = 45
start_angle = 90
N = 10
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col="maroon")
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 13

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "-x"
rules = list("x"="F+[[x]-x]-F[-Fx]+x",
             "F"="FF")
angle = 25
start_angle = 90
N = 7
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col=rgb(0.5,0,0.5))
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 14

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "b"
rules = list("A"="AA",
             "b"="AbA+AbA+AbA")
angle = 90
start_angle = 90
N = 9
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col=rgb(0,0,0.5))
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 15

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="A+A-A")
angle = 115
start_angle = 90
N = 11
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col=rgb(0,0,0))
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 16

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "A"
rules = list("A"="A[+AA][-AA]B",
             "B"="ABA")
angle = 90
start_angle = -90
N = 7
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col=rgb(0,0,0))
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

## Example 17

```{r,echo=F,fig.dim=c(5,5),cache=T}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
start = "x"
rules = list("x"="FFF[+FF+FF+FF+F+Fx][-FF-FF-FF-F-Fx]FFFFFFFFFFFFFFx",
             "F"="FF")
angle = 6
start_angle = 90
N = 8
s = getstr(start,rules,N)
xyc = getxyc(s,angle/180*pi,angle_initial=start_angle/180*pi)
makeplot(xyc,lwd=1,col=rgb(0,0,0))
```

```
```{r,echo=F,results='asis'}
catinfo(angle,start,rules,N)
```
```

# What is a Lindenmayer System?

* Begin with a string of characters (a "word").
    * For example, let's start with "A".
* Define replacement rules.
    * Example:
        * Replace "A" with "BO"
        * Replace "B" with "BA"
        * Replace "O" with "BA"
    * First few recursions:
        
        >0. "A"
        >1. "BO"
        >2. "BABA"
        >3. "BABOBABO"
        >4. "BABOBABABABOBABA"
        >5. "BABOBABABABOBABOBABOBABABABOBABO"

# Recursive Replacement of Letters

* Start:
    * `A`
* Rules:
    * `A` $\to$ `ART-`
    * `R` $\to$ `RAT-`
    * `T` $\to$ `TAR-`
    * `-` $\to$ `-`
* Notice, "-" is constant. We usually don't include constants in the rules. If a character does not have a replacement rule, we assume it is a constant.
* Find the recursions (the iterations):

    >0. `A`
    >1. `ART-`
    >2. `ART-RAT-TAR-`
    >3. `ART-RAT-TAR--RAT-ART-TAR--TAR-ART-RAT--`
    >3. `ART-RAT-TAR--RAT-ART-TAR--TAR-ART-RAT---RAT-ART-TAR--ART-RAT-TAR--TAR-ART-RAT---TAR-ART-RAT--ART-RAT-TAR--RAT-ART-TAR---`

# Recursive Replacement of Letters

* Start:
    * "CAT"
* Rules:
    * "C" $\to$ "TTT"
    * "A" $\to$ "AA"
    * "T" $\to$ "C"
* Find the recursions (the iterations):

    >0. "CAT"
    >1. "TTTAAC"
    >2. "CCCAAAATTT"
    >3. "TTTTTTTTTAAAAAAAACCC"
    >4. "CCCCCCCCCAAAAAAAAAAAAAAAATTTTTTTTT"

>- Notice there were 9 Cs, 16 As, 9 Ts

# Okay, but what about those pictures?

* Turtle Graphics! A turtle drags a pen and follows commands.
    * "F" = Forward one step
    * "+" = Turn right by 90°
    * "-" = Turn left by 90°
    * "[" = Record current position, top of a list
    * "]" = Teleport to top-of-list position, and remove position from list


```{r,echo=F}
xyd = function(string="AA+AA+AA+A+A",angle=pi/2,angle_initial=pi/2){
    switch = 1
    d = angle_initial
    x = 0
    y = 0
    xl = c(x)
    yl = c(y)
    dsave = numeric()
    xsave = numeric()
    ysave = numeric()
    chs = strsplit(string,"")[[1]]
    xl = numeric(sum(chs %in% LETTERS)+sum(chs=="]")+1)
    yl = numeric(sum(chs %in% LETTERS)+sum(chs=="]")+1)
    draw = numeric(sum(chs %in% LETTERS)+sum(chs=="]")+1)
    draw[1]=1
    j = 1
    for(i in 1:nchar(string)){
        ch = chs[i]
        cn = as.integer(charToRaw(ch))
        if(cn>=as.integer(charToRaw("A")) && cn<=as.integer(charToRaw("L"))){
            j = j+1
            draw[j] = 1
            x = x+cos(d)
            y = y+sin(d)
            xl[j] = x
            yl[j] = y
        }
        if(cn>=as.integer(charToRaw("M")) && cn<=as.integer(charToRaw("Z"))){
            j = j+1
            draw[j] = 0
            x = x+cos(d)
            y = y+sin(d)
            xl[j] = x
            yl[j] = y
        }
        if(cn==as.integer(charToRaw("["))){
            dsave = c(dsave,d)
            xsave = c(xsave,x)
            ysave = c(ysave,y)
        }
        if(cn==as.integer(charToRaw("]"))){
            j = j+1
            draw[j] = 0
            x = xsave[length(xsave)]
            y = ysave[length(ysave)]
            d = dsave[length(dsave)]
            if(length(xsave)>1){
                xsave = xsave[1:(length(xsave)-1)]
                ysave = ysave[1:(length(ysave)-1)]
                dsave = dsave[1:(length(dsave)-1)]
            } else {
                xsave = numeric()
                ysave = numeric()
                dsave = numeric()
            }
            xl[j] = x
            yl[j] = y
        }
        if(cn==as.integer(charToRaw("-"))){
            d = d+angle*switch
        }
        if(cn==as.integer(charToRaw("+"))){
            d = d-angle*switch
        }
        if(cn==as.integer(charToRaw("."))){
            switch = switch*(-1)
        }
    }
    return(list(xl,yl,draw,x,y,d,xsave,ysave,dsave))
}

plotit = function(xyd,lwd=1,col="blue"){
    x = xyd[[1]]
    y = xyd[[2]]
    d = xyd[[3]]
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    starts = numeric()
    if(d[1]){
        starts = c(1)
    }
    starts = c(starts,which(diff(d)==1))
    ends = which(diff(d)==-1)
    if(d[length(d)]==1){
        ends = c(ends,length(d))
    }
    for(i in 1:length(starts)){
        lines(x[starts[i]:ends[i]],y[starts[i]:ends[i]],lwd=lwd,col=col)
    }
}
```

```{r,echo=F,animation.hook='gifski',interval=1,fig.dim=c(5,5),cache=T}
s = "FFFF[+FFF[+FF+F][-FF-F]F][-FFF[-FF-F][+FF+F]F]F[+F][-F]F"
# ss = strsplit(s,"")[[1]]
x = 0
y = 0
d = pi/2
for(i in 1:nchar(s)){
    par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
    ss = substr(s,1,i)
    xyd1 = xyd(ss,pi/2,angle_initial=pi/2)
    plotit(xyd1,lwd=3,col=rgb(0,0,0))
    text(-9,9,s,adj=c(0,0.5),col="grey")
    text(-9,9,ss,adj=c(0,0.5))
    x = xyd1[[4]]
    y = xyd1[[5]]
    d = xyd1[[6]]
    xsave = round(xyd1[[7]],1)
    ysave = round(xyd1[[8]],1)
    dsave = xyd1[[9]]
    arrows(x-cos(d)/4,y-sin(d)/4,x+cos(d)/4,y+sin(d)/4,0.1,15,2,col="darkgreen",lwd=5)
    if(length(xsave)>0){
        text(-5,-9,paste0(rev(xsave),collapse="\n"),adj=c(0.5,0),col="red")
        text(0,-9,paste0(rev(ysave),collapse="\n"),adj=c(0.5,0),col="red")
        text(5,-9,paste0(rev(round(dsave/pi*180)),"°",collapse="\n"),adj=c(0.5,0),col="red")
        for(i in 1:length(xsave)){
            xs = xsave[i]
            ys = ysave[i]
            ds = dsave[i]
            arrows(xs-cos(ds)/5,ys-sin(ds)/5,xs+cos(ds)/5,ys+sin(ds)/5,0.1,15,2,col="red",lwd=2)
        }
    }
    
}

```

# You try!

* "F" = Forward one step
* "+" = Turn right by 90°
* "-" = Turn left by 90°
* "[" = Record current position, top of a list
* "]" = Teleport to top-of-list position, and remove position from list


Draw the following string:

$$\mathtt{FFF[+FFF+FFF+FF+FF+F+F][-FFF-FFF-FF-FF-F-F]F}$$

# Correct answer

```{r,echo=F,animation.hook='gifski',interval=0.3,fig.dim=c(5,5),cache=T}
s = "FFF[+FFF+FFF+FF+FF+F+F][-FFF-FFF-FF-FF-F-F]F"
x = 0
y = 0
d = pi/2
for(i in 1:nchar(s)){
    par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
    ss = substr(s,1,i)
    xyd1 = xyd(ss,pi/2,angle_initial=pi/2)
    plotit(xyd1,lwd=3,col=rgb(0,0,0))
    text(-9,9,s,adj=c(0,0.5),col="grey")
    text(-9,9,ss,adj=c(0,0.5))
    x = xyd1[[4]]
    y = xyd1[[5]]
    d = xyd1[[6]]
    xsave = round(xyd1[[7]],1)
    ysave = round(xyd1[[8]],1)
    dsave = xyd1[[9]]
    arrows(x-cos(d)/4,y-sin(d)/4,x+cos(d)/4,y+sin(d)/4,0.1,15,2,col="darkgreen",lwd=5)
    if(length(xsave)>0){
        text(-5,-9,paste0(rev(xsave),collapse="\n"),adj=c(0.5,0),col="red")
        text(0,-9,paste0(rev(ysave),collapse="\n"),adj=c(0.5,0),col="red")
        text(5,-9,paste0(rev(round(dsave/pi*180)),"°",collapse="\n"),adj=c(0.5,0),col="red")
        for(i in 1:length(xsave)){
            xs = xsave[i]
            ys = ysave[i]
            ds = dsave[i]
            arrows(xs-cos(ds)/5,ys-sin(ds)/5,xs+cos(ds)/5,ys+sin(ds)/5,0.1,15,2,col="red",lwd=2)
        }
    }
}
```



# Okay




