```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

lat = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

lataug = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  nch = nc-1
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:nch],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,'\\end{matrix}
  \\;\\middle|\\;
    \\,
    \\begin{matrix}\n')
  for(i in 1:dim(A)[1]){
    s = paste0(s,A[i,nc]," \\\\\n")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

styleblock = '<style>
select.question_input {
width: 5em;
}
tr {height: 3em;}
.matrix-container {
display: inline-block;
padding: 1px;
margin: 1px;
white-space: nowrap;
background: linear-gradient(to right, black, black 10%, transparent 10%,transparent 90%,black 90%,black);
}
.matrix {
    padding: 5px;
    margin: 3px;
    background: white;
}
td.lbtd {
border-left: solid 2px #000;
}
.matrix td {
    padding: 10px;    
    text-align: center;
}
</style>'

rowops = character()

strt = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("")
  } else {
    return(as.character(s))
  }
}

md = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("+")
  } else if(s<0){
    return(as.character(s))
  } else {
    return(paste0("+",s,collapse=""))
  }
}

while(T)
{
  ac = -9:9
  rowops = character()
  eqops = character()
  A1 = matrix(c(1,sample(1:9,8,T))*c(1,sample(c(-1,1),8,T)),3)
  X = matrix(sample(-9:9,3),3)
  B1 = A1%*%X
  M1 = cbind(A1,B1)
  ms = list(M1)
  M = M1
  rowop = paste0(strt(-M[2,1]),"R_1",md(M[1,1]),"R_2\\rightarrow R_2",collapse="")
  rowops = c(rowops,rowop)
  eqop = paste0("Combine ",-M[2,1]," times eq1 and ",M[1,1]," times eq2 to get the new eq2.",collapse="")
  eqops = c(eqops,eqop)
  M[2,] = M[1,1]*M[2,]-M[2,1]*M[1,]
  ms[[2]] = M
  nums = unique(M[2,])
  l = length(nums)
  if(l>1){
    g = gcd(rev(nums[2:l]))
  } else {
    next
  }
  if(is.null(g)){next}
  ind = 3
  if(abs(g)>1){
    rowop = paste0("R_2/(",g,")\\rightarrow R_2",collapse="")
    rowops = c(rowops,rowop)
    eqop = paste0("Divide eq2 by ",g," to get the new eq2.",collapse="")
    eqops = c(eqops,eqop)
    M[2,] = M[2,]/g
    ms[[ind]] = M
    ind = ind+1
  }
  rowop = paste0(strt(-M[3,1]),"R_1",md(M[1,1]),"R_3\\rightarrow R_3",collapse="")
  rowops = c(rowops,rowop)
  eqop = paste0("Combine ",-M[3,1]," times eq1 and ",M[1,1]," times eq3 to get the new eq3.",collapse="")
  eqops = c(eqops,eqop)
  M[3,] = M[1,1]*M[3,]-M[3,1]*M[1,]
  ms[[ind]] = M
  ind = ind+1
  nums = unique(M[3,])
  l = length(nums)
  if(l>1){
    g = gcd(rev(nums[2:l]))
  } else {
    next
  }
  if(is.null(g)){next}
  if(abs(g)>1){
    rowop = paste0("R_3/",abs(g),"\\rightarrow R_3",collapse="")
    rowops = c(rowops,rowop)
    eqop = paste0("Divide eq3 by ",abs(g)," to get the new eq3.",collapse="")
    eqops = c(eqops,eqop)
    M[3,] = M[3,]/abs(g)
    ms[[ind]] = M
    ind = ind+1
  }
  rowop = paste0(strt(-M[3,2]),"R_2",md(M[2,2]),"R_3\\rightarrow R_3",collapse="")
  rowops = c(rowops,rowop)
  eqop = paste0("Combine ",-M[3,2]," times eq2 and ",M[2,2]," times eq3 to get the new eq3.",collapse="")
  eqops = c(eqops,eqop)
  M[3,] = M[2,2]*M[3,]-M[3,2]*M[2,]
  ms[[ind]] = M
  ind = ind+1
  nums = unique(M[3,])
  l = length(nums)
  if(l>1){
    g = gcd(rev(nums[2:l]))
  } else {
    next
  }
  if(is.null(g)){next}
  if(abs(g)>1){
    rowop = paste0("R_3/(",abs(g),")\\rightarrow R_3",collapse="")
    rowops = c(rowops,rowop)
    eqop = paste0("Divide eq3 by ",abs(g)," to get the new eq3.",collapse="")
    eqops = c(eqops,eqop)
    M[3,] = M[3,]/g
    ms[[ind]] = M
    ind = ind+1
  }
  if(M[2,3]!=0){
    rowop = paste0("R_2",md(-M[2,3]),"R_3\\rightarrow R_2",collapse="")
    rowops = c(rowops,rowop)
  eqop = paste0("Combine eq2 and ",-M[2,3]," times eq3 to get the new eq2.",collapse="")
  eqops = c(eqops,eqop)
    M[2,] = M[2,]-M[2,3]*M[3,]
    ms[[ind]] = M
    ind = ind+1
  }
  if(M[1,3]!=0){
    rowop = paste0("R_1",md(-M[1,3]),"R_3\\rightarrow R_1",collapse="")
    rowops = c(rowops,rowop)
  eqop = paste0("Combine eq1 and ",-M[1,3]," times eq3 to get the new eq1.",collapse="")
  eqops = c(eqops,eqop)
    M[1,] = M[1,]-M[1,3]*M[3,]
    ms[[ind]] = M
    ind = ind+1
  }
  if(M[1,2]!=0){
    rowop = paste0("R_1",md(-M[1,2]),"R_2\\rightarrow R_1",collapse="")
    rowops = c(rowops,rowop)
  eqop = paste0("Combine eq1 and ",-M[1,2]," times eq2 to get the new eq1.",collapse="")
  eqops = c(eqops,eqop)
    M[1,] = M[1,]-M[1,2]*M[2,]
    ms[[ind]] = M
    ind = ind+1
  }
  for(i in 1:(ind-1)){
    ac = sort(unique(c(ac,unique(ms[[i]]))))
  }
  if(det(A1)!=0 && max(abs(M))<100 && M[2,2]==1 && M[3,3]!=0 && max(abs(ac))<100 && ms[[2]][2,3]!=0){break}
}

prs = function(M,lets=c("x","y","z","q","r","s","t","u","v","w")){
  s = "\\begin{align*}"
  for(i in 1:dim(M)[1]){
    row = ""
    nc = dim(M)[2]
    ls = lets[1:(nc-1)]
    row = paste0(strt(M[i,1]),ls[1],collapse="")
    for(j in 2:(nc-1)){
      row = paste0(row,md(M[i,j]),ls[j],collapse="")
    }
    row = paste(row,"&=",M[i,nc],"\\\\\n",collapse="")
    row = sub("0x+","",row,fixed=T)
    row = sub("0x-","-",row,fixed=T)
    row = sub("0y+","",row,fixed=T)
    row = sub("0y-","-",row,fixed=T)
    row = sub("+0z","",row,fixed=T)
    row = sub("-0z","",row,fixed=T)
    s = paste0(s,row,collapse="")
  }
  s = paste0(s,"\\end{align*}",collapse="")
  return(s)
}


html_input_table = function(){
  s = "<div class='matrix-container'><table class='matrix'>"
  nr = 3
  nc = 4
  nv = nc-1
  for(i in 1:nr){
    rs = paste0("<td>",rep("!!!",nv),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"<td class='lbtd'>!!!</td></tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

acs = list()
sols = character()
nm = ind-1
tac = character()
for(i in 2:nm){
  M = ms[[i]]
  aaa = c(t(M))
  for(aa in aaa){
    while(T){
      aacc = unique(c(aa,sample(ac,3)))
      if(length(aacc)==4){break}
    }
    tac = c(tac,aacc)
    sols=c(sols,paste0(1*(aa==aacc),collapse=""))
  }
}
al = paste0("* ",tac,collapse="\n")

```

Question
========

`r styleblock`

In [Gauss–Jordan elimination](https://en.wikipedia.org/wiki/Gaussian_elimination#Gauss%E2%80%93Jordan_elimination), elementary row operations are used to convert an augmented matrix into [reduced row echelon form](https://en.wikipedia.org/wiki/Row_echelon_form#Reduced_row_echelon_form). We will see this is equivalent to solving the 3x3 linear system via an elimination method.

We begin with a 3x3 system of equations:

$$`r prs(M1)`$$

We put that system into augmented-matrix form.

$$`r lataug(ms[[1]])`$$

By using row operations, we will convert the 3x3 coefficient matrix (left of the vertical line) into a [3x3 identity matrix](https://en.wikipedia.org/wiki/Identity_matrix). If you remember solving 3x3 systems of equations, we began by eliminating the same variable from two pairs of equations to produce a 2x2 system, then solve the 2x2 system by eliminating another variable. Once one variable was known, the other variables were relatively easy to determine.

In Jordan-Gauss elimination, we begin by getting 0s in the bottom left corner and 1s along the diagonal. We create these 0s with linear combinations of rows (and possibly simplifying to get 1s on diagonal). We then get 0s above the main diagonal to get the solution. In the problem below, **follow the indicated row operations to solve the system.**

```{r,echo=F,results='asis'}
#cat(paste0("$$",lataug(ms[[1]]),"$$\n"))
ans_num = 1
for(i in 2:(ind-1)){
  cat(paste0("Row operation: $",rowops[i-1],"$\n\n"))
  #cat(paste0("$$",lataug(ms[[i]]),"$$\n"))
  mm = ms[[i]]
  hm = html_input_table()
  for(j in 1:12){
    hm = sub("!!!",paste0("##ANSWER",ans_num,"##",collapse=""),hm,fixed = T)
    ans_num=ans_num+1
  }
  cat(hm)
  cat('\n\n')
}
```

Answerlist
--------

`r al`


Solution
========

`r styleblock`

```{r,echo=F,results='asis'}
cat(paste0("$$",lataug(ms[[1]]),"~~~~",prs(ms[[1]]),"$$\n"))
for(i in 2:(ind-1)){
  cat(paste0("Row operation: $",rowops[i-1],"$\n\n"))
  cat(paste0("Equation operation: ",eqops[i-1],"\n"))
  cat(paste0("$$",lataug(ms[[i]]),"~~~~",prs(ms[[i]]),"$$\n"))
}
```


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",length(sols)),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: row_ops_to_rref