---
output: pdf_document
params:
    rseed: 1
    showsol: true
urlcolor: blue
---

```{r,echo=F}
# set.seed(params$rseed)
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

There are 7 frieze-pattern groups (https://en.wikipedia.org/wiki/Frieze_group). To generate the patterns, we will need to use translation, reflection, rotation (by 180°), and glide reflection (a combination of a reflection and translation). Please continue the frieze patterns shown below.

## Hop (p1, translation only)

```{r,echo=F,fig.dim=c(6,1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))
# n = 6
# x = sample(0:9,n)/10
# y = sample(0:9,n)/10

x = c(0:9,0,1,2,3,4,5,5,5,4,3)/10
y = c(round(((0:9)/10)^2*10/1.5),6,7,8,9,9,8,7,6,5,6)/10
n = length(x)

# x = c(1,1,2,2,2,3,3,3,4,4,4,4,4,4,4,5,5,5,5,5,6,6,6,7,7,8,8,8)
# y = c(7,8,3,6,9,2,5,9,0,1,2,3,4,6,9,1,4,6,7,9,2,4,9,5,9,6,7,8)
# n = length(x)
# x = x/10
# y = y/10

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.3)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.3)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i))
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1))
}
for(i in 1:n){
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(1,1,1,1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(2,2,2,2),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    # polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(3,3,3,3),
    #         c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
}
```

## Step (p11g, glide reflections)

```{r,echo=F,fig.dim=c(6,1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))
# n = 6
# x = sample(0:9,n)/10
# y = sample(0:9,n)/10

x = c(0,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,4,4,5,5,5,5,6,6,6,6,7,8,9)
y = c(4,4,3,2,1,5,3,2,1,0,6,2,1,0,7,3,2,1,0,7,1,2,3,7,2,3,4,7,6,6)
x = x/10
y = y/10
n = length(x)

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.3)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.3)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i))
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1))
}
for(i in 1:n){
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(1,1,1,1),
            1-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(2,2,2,2),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    # polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(3,3,3,3),
    #         1-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
}
```

## Sidle (p1m1, reflections)

```{r,echo=F,fig.dim=c(6,1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))
# n = 6
# x = sample(0:9,n)/10
# y = sample(0:9,n)/10

x = c(1,1,1,2,2,2,2,2,2,3,3,4,5,6,7,7,8,8,8,9)
y = c(3,4,5,1,2,3,5,6,7,0,8,9,5,6,2,6,1,5,6,1)
x = x/10
y = y/10
n = length(x)

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.3)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.3)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i))
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1))
}
for(i in 1:n){
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(2,2,2,2)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(2,2,2,2),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    # polygon(c(4,4,4,4)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
    #         c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
}
```


## Spinning hop (p2, 180° rotations)

```{r,echo=F,fig.dim=c(6,1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))
x = c(0,0,1,2,3:9,     8,7,6,6,6,7,8,9)/10
y = c(4,3,2,1,rep(0,7),3,3,4,5,6,7,8,9)/10
n = length(x)

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.3)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.3)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i))
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1))
}
for(i in 1:n){
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(2,2,2,2)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            1-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(2,2,2,2),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    # polygon(c(4,4,4,4)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
    #         1-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
}
```

## Spinning sidle (p2mg, reflections and 180° rotations)

```{r,echo=F,fig.dim=c(6,1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))
# n = 6
# x = sample(0:9,n)/10
# y = sample(0:9,n)/10

x = c(1,1,1,1,1,1,1,2,2,2,3,3,4,4,4,4,4,5,5,5,5,6,6,6,6,6,7,7,7,7,8,8,9,9)
y = c(1,2,3,4,5,6,7,0,7,8,8,9,2,3,6,7,9,1,3,8,9,1,2,3,7,8,1,3,6,7,2,6,0,6)
n = length(x)
x = x/10
y = y/10

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.3)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.3)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i))
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1))
}
for(i in 1:n){
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(2,2,2,2)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1)+c(2,2,2,2),
            1-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    # polygon(c(4,4,4,4)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
    #         1-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
}
```


## Jump (p11m, reflection over horizontal axis, translation)

```{r,echo=F,fig.dim=c(6,1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))
# n = 4
# x = sample(0:9,n)/10
# y = sample(5:9,n)/10

# x = c(0,0,1,2,3,4,5,6,7,7,8,8)
# y = c(4,3,2,2,2,2,1,0,1,4,2,3)
x = c(0,0,0,1,1,2,2,2,3,4,5,6,7,8,8,8,9,9,9)
y = c(0,2,3,0,3,1,2,3,3,3,3,2,1,0,3,4,0,2,3)
n = length(x)
x = x/10
y = y/10

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.3)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.3)
}
for(i in seq(0,1,0.5)){
    lines(c(0,6),c(i,i))
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1))
}
for(i in 1:n){
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(1,1,1,1)-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    
    polygon(c(1,1,1,1)+c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(1,1,1,1)+c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(1,1,1,1)-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    
    polygon(c(2,2,2,2)+c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(2,2,2,2)+c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(1,1,1,1)-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
}
```

## Spinning jump (p2mm, reflections over horizontal axis and vertical axes)

```{r,echo=F,fig.dim=c(6,1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))
# n = 4
# x = sample(0:9,n)/10
# y = sample(5:9,n)/10

x = c(0,0,1,1,2,2,3,4,5,6,7,8,8,9,9,9)
y = c(0,3,0,4,1,2,3,4,3,2,2,1,4,1,3,4)
n = length(x)
x = x/10
y = y/10

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.3)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.3)
}
for(i in seq(0,1,0.5)){
    lines(c(0,6),c(i,i))
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1))
}
for(i in 1:n){
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(1,1,1,1)-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    
    polygon(c(2,2,2,2)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(2,2,2,2)-c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(1,1,1,1)-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    
    polygon(c(2,2,2,2)+c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
    polygon(c(2,2,2,2)+c(x[i],x[i],x[i]+0.1,x[i]+0.1),
            c(1,1,1,1)-c(y[i],y[i]+0.1,y[i]+0.1,y[i]),col="black",border = F)
}
```

Now, make your own! Choose 3 (different) frieze groups, and make a pattern. You might try this tool: https://chadworley.github.io/frieze/frieze.html

Keep in mind, you do not need to actually fill the "pixels". You can draw smooth curves; you might find the grid helpful when enforcing the symmetry.

PLEASE SPECIFY WHICH FRIEZE GROUP YOU ARE USING!

\vfill

**Frieze Group:** 

```{r,echo=F,fig.dim=c(7.5,7.5/6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.2)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.2)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i),lwd=0.4)
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1),lwd=0.4)
}
```

\vfill

**Frieze Group:** 

```{r,echo=F,fig.dim=c(7.5,7.5/6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.2)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.2)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i),lwd=0.4)
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1),lwd=0.4)
}
```

\vfill

**Frieze Group:** 

```{r,echo=F,fig.dim=c(7.5,7.5/6)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,6),ylim=c(0,1))

for(i in seq(0,1,0.1)){
    lines(c(0,6),c(i,i),lwd=0.2)
}
for(i in seq(0,6,0.1)){
    lines(c(i,i),c(0,1),lwd=0.2)
}
for(i in seq(0,1,1)){
    lines(c(0,6),c(i,i),lwd=0.4)
}
for(i in seq(0,6,1)){
    lines(c(i,i),c(0,1),lwd=0.4)
}
```
