---
title: "Translation, Reflection, Rotation, and Glide Reflection"
output: slidy_presentation
---

# Frieze Groups

* https://eschermath.org/wiki/Frieze_Patterns.html
* https://maths.nuigalway.ie/~rquinlan/groups/exhibition/burke_hasanik_mcmahon_sweetman.pdf
* https://www.onlinemath4all.com/frieze-patterns-geometry.html
* https://lindagreen.web.unc.edu/wp-content/uploads/sites/5262/2020/12/Section15_ClassifyingFriezePatterns.pdf
* https://www.youtube.com/watch?v=0mXz-NP-raY


# Transformations

```{r,echo=F}
set.seed(1)
myorder = sample(1:4)
wrds = c("translation","rotation","glide","mirror")
mywrds = wrds[myorder]

al = paste0("* ",wrds,collapse="\n")
sol1 = paste0(1*(myorder[1]==1:4),collapse="")
sol2 = paste0(1*(myorder[2]==1:4),collapse="")
sol3 = paste0(1*(myorder[3]==1:4),collapse="")
sol4 = paste0(1*(myorder[4]==1:4),collapse="")

getbasedots = function(fg=1,n=4){
    if(fg<6){
        x = runif(2*n)
        y = runif(2*n)-0.5
        h = runif(2*n)
        p = sample(1:20,2*n)
    } else {
        x = runif(n)
        y = runif(n)-0.5
        h = runif(n)
        p = sample(1:20,n)
        x = c(x,x)
        y = c(y,-y)
        h = c(h,h)
        p = c(p,p) 
    }
    dots = data.frame(x,y,h,p)
    return(dots)
}

translate = function(dots,dx=1){
    tdots = data.frame(dots)
    tdots$x = dots$x+dx
    return(tdots)
}
rotate = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    tdots$y = -tdots$y
    return(tdots)
}
glide = function(dots,dx){
    tdots = data.frame(dots)
    tdots$x = tdots$x+dx
    tdots$y = -tdots$y
    return(tdots)
}
mirror = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    return(tdots)
}

```



There are 4 basic transformations in Frieze groups:

* Translation
* Rotation (by 180$^\circ$)
* Glide reflection (reflect vertically then translate horizontally)
* Mirror (reflect horizontally)

I have depicted those four transformations here:

```{r,echo=F,fig.dim=c(3,6)}

lwd=3
col="blue"

par(mar=c(0,0,0,0),mfrow=c(4,1))
mydots = data.frame(x=c(0.8,0.8,0.2,0.8),y=c(-0.4,0,0,0.4))
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(mydots$x,mydots$y,lwd=lwd,col=col)
d2 = translate(mydots,1)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=1,lty=2)
text(0.1,0.4,"translation",adj=0)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))

plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(mydots$x,mydots$y,lwd=lwd,col=col)
d2 = rotate(mydots,1)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
points(1,0)
text(0.1,0.4,"rotation",adj=0)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))

plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(mydots$x,mydots$y,lwd=lwd,col=col)
d2 = glide(mydots,1)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
text(0.1,0.4,"glide",adj=0)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))

plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(mydots$x,mydots$y,lwd=lwd,col=col)
d2 = mirror(mydots,1)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
text(0.1,0.4,"mirror",adj=0)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))

```
\


Label the four visual representations below:

## Transformation 1

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
dots = getbasedots(1,6)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[1]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(dots$x,dots$y,lwd=lwd,col=col)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
```
\

* What type of transformation?


## Transformation 2

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
dots = getbasedots(1,6)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[2]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(dots$x,dots$y,lwd=lwd,col=col)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
```
\

* What type of transformation?


## Transformation 3

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
dots = getbasedots(1,6)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[3]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(dots$x,dots$y,lwd=lwd,col=col)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
```
\

* What type of transformation?

## Transformation 4

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
dots = getbasedots(1,6)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[4]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
lines(dots$x,dots$y,lwd=lwd,col=col)
lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
```
\

* What type of transformation?

