```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

lat = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],\n            [",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

lataug = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:3],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,'\\end{matrix}
  \\;\\middle|\\;
    \\,
    \\begin{matrix}\n')
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,4:6],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

styleblock = '<style>
select.question_input {
width: 5em;
}
tr {height: 3em;}
.mc {
display: inline-block;
padding: 3px;
margin: 3px;
white-space: nowrap;
background: linear-gradient(to right, black, black 10%, transparent 10%,transparent 90%,black 90%,black);
}
.matrix {
    padding: 5px;
    margin: 3px;
    background: white;
}
td.lbtd {
border-left: solid 2px #000;
}
.matrix td {
    padding: 10px;    
    text-align: center;
}
</style>'

strt = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("")
  } else {
    return(as.character(s))
  }
}

md = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("+")
  } else if(s<0){
    return(as.character(s))
  } else {
    return(paste0("+",s,collapse=""))
  }
}

html_input_table = function(){
  s = "<div class='mc'><table class='matrix'>"
  for(i in 1:3){
    rs = paste0("<td>",rep("!!!",3),"</td>",collapse="")
    rs2 = paste0("<td>",rep("!!!",2),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"<td class='lbtd'>!!!</td>",rs2,"</tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

html_input_table_33 = function(){
  s = "<div class='mc'><table class='matrix'>"
  for(i in 1:3){
    rs = paste0("<td>",rep("!!!",3),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"</tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

while(T){
  A = matrix(sample(1:10,9,T)*sample(c(-1,1),9,T),3)
  if(abs(det(A))!=1){next}
  Ainv = round(solve(A),3)
  if(max(abs(Ainv))>10){next}
  I = matrix(c(1,0,0,0,1,0,0,0,1),3)
  rowops = character()
  i = 1
  M = cbind(A,I)
  m = list(M)
  ## step 1: Combine 1,2->2
  if(M[2,1]==0){next}
  if(M[2,1]!=0){
    g = gcd(M[1,1],M[2,1])
    a = M[2,1]/g
    b = -M[1,1]/g
    e22a = a*M[1,2]+b*M[2,2]
    if(e22a==0 || a*M[1,3]+b*M[2,3]==0){
      next
    }
    if(e22a<0){
      a = -a
      b = -b
    }
    rowop = paste0(strt(a),"R_1",md(b),"R_2\\to R_2")
    rowops = c(rowops,rowop)
    M[2,] = a*M[1,]+b*M[2,]
    i = i+1
    m[[i]] = M
  }
  ## step 2: Combine 1,3->3
  if(M[3,1]==0){next}
  if(M[3,1]!=0){
    g = gcd(M[1,1],M[3,1])
    a = M[3,1]/g
    b = -M[1,1]/g
    e32a = a*M[1,2]+b*M[3,2]
    if(e32a==0){next}
    if(e32a<0){
      a = -a
      b = -b
    }
    rowop = paste0(strt(a),"R_1",md(b),"R_3\\to R_3")
    rowops = c(rowops,rowop)
    M[3,] = a*M[1,]+b*M[3,]
    i = i+1
    m[[i]] = M
  }
  ## step 3: Combine 2,3->3
  if(M[3,2]==0){next}
  if(M[3,2]!=0){
    g = gcd(M[2,2],M[3,2])
    a = M[3,2]/g
    b = -M[2,2]/g
    e33a = a*M[2,3]+b*M[3,3]
    if(e33a==0){next}
    if(e33a<0){
      a = -a
      b = -b
    }
    rowop = paste0(strt(a),"R_2",md(b),"R_3\\to R_3")
    rowops = c(rowops,rowop)
    M[3,] = a*M[2,]+b*M[3,]
    i = i+1
    m[[i]] = M
  }
  ## step 4: Simplify 3
  if(M[3,3]!=1){
    rowop = paste0("R_3/(",M[3,3],")\\to R_3")
    rowops = c(rowops,rowop)
    M[3,] = M[3,]/M[3,3]
    i = i+1
    m[[i]] = M
  }
  ## step 5: C23,2
  if(M[2,3]!=0){
    g = gcd(M[2,3],M[3,3])
    a = M[3,3]/g
    b = -M[2,3]/g
    e33a = a*M[2,2]+b*M[3,2]
    if(e33a==0){next}
    if(e33a<0){
      a = -a
      b = -b
    }
    rowop = paste0(strt(a),"R_2",md(b),"R_3\\to R_2")
    rowops = c(rowops,rowop)
    M[2,] = a*M[2,]+b*M[3,]
    i = i+1
    m[[i]] = M
  }
  ## step 6: Simplify 2
  if(M[2,2]!=1){
    rowop = paste0("R_2/(",M[2,2],")\\to R_2")
    rowops = c(rowops,rowop)
    M[2,] = M[2,]/M[2,2]
    i = i+1
    m[[i]] = M
  }
  ## step 7: C13,1
  if(M[1,3]!=0){
    g = gcd(M[1,3],M[3,3])
    a = M[3,3]/g
    b = -M[1,3]/g
    e33a = a*M[1,1]+b*M[3,1]
    if(e33a==0){next}
    if(e33a<0){
      a = -a
      b = -b
    }
    rowop = paste0(strt(a),"R_1",md(b),"R_3\\to R_1")
    rowops = c(rowops,rowop)
    M[1,] = a*M[1,]+b*M[3,]
    i = i+1
    m[[i]] = M
  }
  ## step 8: C12,1
  if(M[1,2]!=0){
    g = gcd(M[1,2],M[2,2])
    a = M[2,2]/g
    b = -M[1,2]/g
    e33a = a*M[1,1]+b*M[2,1]
    if(e33a==0){next}
    if(e33a<0){
      a = -a
      b = -b
    }
    rowop = paste0(strt(a),"R_1",md(b),"R_2\\to R_1")
    rowops = c(rowops,rowop)
    M[1,] = a*M[1,]+b*M[2,]
    i = i+1
    m[[i]] = M
  }
  ## step 9: Simp1
  if(M[1,1]!=1){
    rowop = paste0("R_1/(",M[1,1],")\\to R_1")
    rowops = c(rowops,rowop)
    M[1,] = M[1,]/M[1,1]
    i = i+1
    m[[i]] = M
  }
  if(abs(det(A))==1 && i<10){break}
}

ac = numeric()
for(i in 1:length(m)){
  ac = sort(unique(c(ac,unique(m[[i]]))))
}

acs = list()
sols = character()
nm = length(m)
tac = character()
for(i in 2:nm){
  M = m[[i]]
  aaa = c(t(M[,4:6]))
  for(aa in aaa){
    while(T){
      aacc = sort(unique(c(aa,sample(ac,1))))
      if(length(aacc)==2){break}
    }
    tac = c(tac,aacc)
    sols=c(sols,paste0(1*(aa==aacc),collapse=""))
  }
}

# M = m[[length(m)]]
# aaa = c(t(M[,4:6]))
# for(aa in aaa){
#   tac = c(tac,-10:10)
#   sols = c(sols,paste0(1*(-10:10==aa),collapse=""))
# }

al = paste0("* ",tac,collapse="\n")

```

Question
========

`r styleblock`

Let $A$ be the 3x3 matrix below.

$$A=`r lat(A)`$$

To find the inverse of $A$, we can set up an augmented matrix with $A$ augmented with an identity matrix. We then use row operations to get to reduced row echelon form. (I'll dictate the row operations, and I'll take care of the first 3 columns.) The resulting 3x3 matrix (on the right of the augment) is the inverse of $A$.

$$`r lataug(m[[1]])`$$

```{r,echo=F,results='asis'}
ans_num = 1
for(i in 2:(length(m))){
  cat(paste0("Row operation: $",rowops[i-1],"$\n\n"))
  #cat(paste0("$$",lataug(ms[[i]]),"$$\n"))
  mm = m[[i]]
  hm = html_input_table()
  for(j in 0:17){
    if(j%%6<3){
      rn = j%/%6+1
      cn = j%%6+1
      hm = sub("!!!",paste0(mm[rn,cn]),hm,fixed = T)
    } else {
      hm = sub("!!!",paste0("##ANSWER",ans_num,"##",collapse=""),hm,fixed = T)
      ans_num=ans_num+1
    }
  }
  cat(hm)
  cat('\n\n')
}
# 
# mm = m[[length(m)]]
# hm = html_input_table_33()
# for(j in 1:9){
#   hm = sub("!!!",paste0("##ANSWER",ans_num,"##",collapse=""),hm,fixed = T)
#   ans_num=ans_num+1
# }

```


Answerlist
--------

`r al`


Solution
========



So, the inverse of $A$, which is denoted as $A^{-1}$, has been found.

$$A^{-1} = `r lat(Ainv)`$$

Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",length(sols)),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: row_ops_get_inverse