```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

lat = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}

matcc = function(A){
  s = "[["
  for(i in 1:(dim(A)[1])){
    s2 = paste0(A[i,],collapse=",")
    s = paste0(s,s2,collapse="")
    if(i<dim(A)[1]){
      s = paste0(s,"],[",collapse="")
    }
  }
  s = paste0(s,"]]",collapse="")
  return(s)
}

lataug = function(A){
  s = '\\left[
  \\begin{matrix}\n'
  nc = dim(A)[2]
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,1:3],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,'\\end{matrix}
  \\;\\middle|\\;
    \\,
    \\begin{matrix}\n')
  for(i in 1:dim(A)[1]){
    s2 = paste0(A[i,4:6],collapse=" & ")
    s = paste0(s,s2,"\\\\\n",collapse="")
  }
  s = paste0(s,"\\end{matrix}
\\right]")
  return(s)
}

styleblock = '<style>
select.question_input {
width: 5em;
}
tr {height: 3em;}
.mc {
display: inline-block;
padding: 1px;
margin: 1px;
white-space: nowrap;
background: linear-gradient(to right, black, black 10%, transparent 10%,transparent 90%,black 90%,black);
}
.matrix {
    padding: 5px;
    margin: 3px;
    background: white;
}
td.lbtd {
border-left: solid 2px #000;
}
.matrix td {
    padding: 10px;    
    text-align: center;
}
</style>'

strt = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("")
  } else {
    return(as.character(s))
  }
}

md = function(s){
  if(s==-1){
    return("-")
  } else if(s==1){
    return("+")
  } else if(s<0){
    return(as.character(s))
  } else {
    return(paste0("+",s,collapse=""))
  }
}

html_input_table = function(){
  s = "<div class='mc'><table class='matrix'>"
  for(i in 1:3){
    rs = paste0("<td>",rep("!!!",3),"</td>",collapse="")
    rs2 = paste0("<td>",rep("!!!",2),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"<td class='lbtd'>!!!</td>",rs2,"</tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

html_input_table_33 = function(){
  s = "<div class='mc'><table class='matrix'>"
  for(i in 1:3){
    rs = paste0("<td>",rep("!!!",3),"</td>",collapse="")
    s = paste0(s,'<tr>',rs,"</tr>")
  }
  s = paste0(s,'</table></div>')
  return(s)
}

prs = function(M,lets=c("x","y","z","q","r","s","t","u","v","w")){
  s = "\\begin{align*}"
  for(i in 1:dim(M)[1]){
    row = ""
    nc = dim(M)[2]
    ls = lets[1:(nc-1)]
    row = paste0(strt(M[i,1]),ls[1],collapse="")
    for(j in 2:(nc-1)){
      row = paste0(row,md(M[i,j]),ls[j],collapse="")
    }
    row = paste(row,"&=",M[i,nc],"\\\\\n",collapse="")
    row = sub("0x+","",row,fixed=T)
    row = sub("0x-","-",row,fixed=T)
    row = sub("0y+","",row,fixed=T)
    row = sub("0y-","-",row,fixed=T)
    row = sub("+0z","",row,fixed=T)
    row = sub("-0z","",row,fixed=T)
    s = paste0(s,row,collapse="")
  }
  s = paste0(s,"\\end{align*}",collapse="")
  return(s)
}

while(T){
  A = matrix(sample(-15:15,9,T),3)
  if(abs(det(A))!=1){next}
  Ainv = round(solve(A),3)
  if(max(abs(Ainv))>100){next}
  break
}
I = matrix(c(1,0,0,0,1,0,0,0,1),3)



m1 = cbind(A,I)

X = matrix(sample(-10:10,3),3)

B = A%*%X

tac = numeric()
sols = character()
aaa = c(t(X))
for(aa in aaa){
  tac = c(tac,-10:10)
  sols = c(sols,paste0(1*(-10:10==aa),collapse=""))
}
al = paste0("* ",tac,collapse="\n")

xxx = matrix(c("x","y","z"),3)

```

Question
========

`r styleblock`

Let $A$ be the 3x3 matrix below.

$$A=`r lat(A)`$$
```
A = matrix(`r matcc(A)`)
```


Its inverse is shown below.

$$A^{-1}= `r lat(Ainv)`$$

```
Ainv = matrix(`r matcc(Ainv)`)
```

Use that information to solve the system below.

```{r,echo=F,results='asis'}
M = cbind(A,B)
cat(prs(M))
```


* $x=$ ##ANSWER1##
* $y=$ ##ANSWER2##
* $z=$ ##ANSWER3##


Answerlist
--------

`r al`


Solution
========

Write the system in matrix form $A\cdot X = B$.

$$`r lat(A)`\cdot`r lat(xxx)` = `r lat(B)`$$

You can left-multiply both sides by the inverse.
$$A^{-1}AX = A^{-1}B$$
$$`r lat(Ainv)`\cdot `r lat(A)` \cdot `r lat(xxx)` = `r lat(Ainv)`\cdot `r lat(B)`$$

We know that $A^{-1}\cdot A = I$, where $I$ is the identity matrix.

$$`r lat(I)` \cdot `r lat(xxx)` = `r lat(Ainv)`\cdot `r lat(B)`$$

We know $I\cdot X = X$, because multiplication by an identity matrix returns an unchanged matrix.

$$`r lat(xxx)` = `r lat(Ainv)`\cdot `r lat(B)`$$

So, in short, we just need to evaluate $A^{-1}\cdot B$.


Use [sagemath](https://sagecell.sagemath.org/).

```
Ainv = matrix(`r matcc(Ainv)`)
B = matrix(`r matcc(t(B))`).transpose()
XYZ = Ainv*B
pretty_print(XYZ)
```

$$X = `r lat(X)`$$

So, 

$$`r prs(cbind(I,X))`$$


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",length(sols)),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: get_inverse_rref