```{r,echo=F}

while(T){
    hw = sample(2:8,4,T)
    h1 = hw[1]
    w1 = hw[2]
    h2 = hw[3]
    w2 = hw[4]
    x1 = sample(0:(10-w1),1)
    y1 = sample(0:(10-h1),1)
    x2 = sample(0:(10-w2),1)
    y2 = sample(0:(10-h2),1)
    mA = matrix(rep(0,100),10)
    mB = matrix(rep(0,100),10)
    mI = matrix(rep(0,100),10)
    mU = matrix(rep(0,100),10)
    moA = matrix(rep(0,100),10)
    moB = matrix(rep(0,100),10)
    for(i in 1:10){
        for(j in 1:10){
            if(i>x1 && i<=(x1+w1) && j>y1 && j<=(y1+h1)){
                mA[j,i] = 1
            }
            if(i>x2 && i<=(x2+w2) && j>y2 && j<=(y2+h2)){
                mB[j,i] = 1
            }
            if(mA[j,i]==1 && mB[j,i]==1){mI[j,i]=1}
            if(mA[j,i]==1 || mB[j,i]==1){mU[j,i]=1}
            if(mA[j,i]==1 && mB[j,i]==0){moA[j,i]=1}
            if(mA[j,i]==0 && mB[j,i]==1){moB[j,i]=1}
        }
    }
    A = sum(mA)
    B = sum(mB)
    I = sum(mI)
    U = sum(mU)
    oA = sum(moA)
    oB = sum(moB)
    nC = 100-U
    aaa = c(oA,oB,I,U,A,B,nC)
    if(length(unique(aaa))==7 && min(aaa)>1 && !(x1+w1/2==x2+w2/2 && y1+h1/2==y2+h2/2)){break}
}

a = sort(aaa)
al = paste0("* ",a,"\n",collapse="")
s1 = paste0(1*(a==A),collapse="")
s2 = paste0(1*(a==B),collapse="")
s3 = paste0(1*(a==I),collapse="")
s4 = paste0(1*(a==U),collapse="")
s5 = paste0(1*(a==oA),collapse="")
s6 = paste0(1*(a==oB),collapse="")
s7 = paste0(1*(a==nC),collapse="")

```


Question
========

Jason drew two overlapping rectangles on a 10x10 grid.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(0,10),ylim=c(0,10))
for(i in 0:10){
    lines(c(0,10),c(i,i),col="grey")
    lines(c(i,i),c(0,10),col="grey")
}
polygon(c(x1,x1,x1+w1,x1+w1),c(y1,y1+h1,y1+h1,y1),col=rgb(1,0,0,0.2))
polygon(c(x2,x2,x2+w2,x2+w2),c(y2,y2+h2,y2+h2,y2),col=rgb(0,0,1,0.2))
text(x1+w1/2,y1+h1/2,"A",col="red",cex=2)
text(x2+w2/2,y2+h2/2,"B",col="blue",cex=2)

```
\

Let's call the red rectangle A and the blue rectangle B. Find the following areas:

* Area covered by A = ##ANSWER1## squares
* Area covered by B = ##ANSWER2## squares
* Area covered by the intersection of A and B = ##ANSWER3## squares
* Area covered by the union of A and B = ##ANSWER4## squares
* Area covered by ONLY A (and not B) = ##ANSWER5## squares
* Area covered by ONLY B (and not A) = ##ANSWER6## squares
* Area not covered (neither A nor B) = ##ANSWER7## squares

Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`


Solution
========

* Area covered by A = `r A`
* Area covered by B = `r B`
* Area covered by the intersection of A and B = `r I`
* Area covered by the union of A and B = `r U`
* Area covered by ONLY A (and not B) = `r oA`
* Area covered by ONLY B (and not A) = `r oB`
* Area not covered (neither A nor B) = `r nC`


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r s1`|`r s2`|`r s3`|`r s4`|`r s5`|`r s6`|`r s7`
exname: venn_rects