```{r,echo=F}

# set oA, oB, i, nAB
# u = oA+oB-i
# A = oA+i
# B = oB+i
# tot = u+nAB
# oA, oB, i, u, A, B, nAB   

while(T){
    da4 = sample(10:40,3)
    oA = round(da4[1]/100,2)
    oB = round(da4[2]/100,2)
    I = round(da4[3]/100,2)
    U = round(oA+oB+I,2)
    A = round(oA+I,2)
    B = round(oB+I,2)
    nAB = round(1-U,2)
    nA = round(1-A,2)
    nB = round(1-B,2)
    a = c(oA,oB,I,U,A,B,nAB,nA,nB)
    nnn = length(a)
    whichgive = sample(1:6,3)
    gottem = 1*(1:nnn==whichgive[1])+1*(1:nnn==whichgive[2])+1*(1:nnn==whichgive[3])
    eqs = list(c(1,3,5),c(2,3,6),c(1,2,3,4),c(4,7),c(5,8),c(6,9))
    wa = numeric()
    for(i in 1:10){
        for(eq in eqs){
            if(sum(gottem[eq])+1==length(eq)){
                for(j in eq){
                    if(gottem[j]==0){
                        gottem[j] = 1
                        wa = c(wa,j)
                    }
                }
            }
        }
    }
    if(length(unique(a))==length(a) && min(a)>=0.04 && sum(gottem)==length(a)){break}
}
states = c(paste0("$P(A\\cap \\neg B)=",oA,"$",collapse=""),
           paste0("$P(\\neg A\\cap B)=",oB,"$",collapse=""),
           paste0("$P(A\\cap B)=",I,"$",collapse=""),
           paste0("$P(A\\cup B)=",U,"$",collapse=""),
           paste0("$P(A)=",A,"$",collapse=""),
           paste0("$P(B)=",B,"$",collapse=""),
           paste0("$P(\\neg A \\cap \\neg B)=",nAB,"$",collapse=""),
           paste0("$P(\\neg A)=",nA,"$",collapse=""),
           paste0("$P(\\neg B)=",nB,"$",collapse="")
           )

quests = c("$P(A\\cap \\neg B)=$",
           "$P(\\neg A\\cap B)=$",
           "$P(A\\cap B)=$",
           "$P(A\\cup B)=$",
           "$P(A)=$",
           "$P(B)=$",
           "$P(\\neg A\\cap \\neg B)=$",
           "$P(\\neg A)$",
           "$P(\\neg B)$"
           )

alsol = function(ans,n=5,dx=1,spri=NULL){
    choices = ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx
    al = paste0("* ",choices,collapse="\n")
    if(!is.null(spri)){
        choices = round(ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx,spri)
        al = paste0("* ",sprintf(paste0("%.",spri,"f",collapse=""),choices),collapse="\n")
    }
    sol = paste0(1*(ans==choices),collapse="")
    return(data.frame(al,sol))
}

asses = list()
altot = ""
soltot = ""
statot = ""
quetot = ""
sols = character()

for(i in 1:length(wa)){
    asses[[i]] = alsol(a[wa[1]],5,0.02,2)
    altot = paste0(altot,"\n",asses[[i]]$al,collapse="")
    sols = c(sols,asses[[i]]$sol)
    statot = paste0(statot,"* ",states[wa[i]],"\n",collapse="")
    quetot = paste0(quetot,"* ",quests[wa[i]]," ##ANSWER",i,"## students\n",collapse="")
}

soltot = paste0(sols,collapse="|")
schtot = paste0(rep("schoice",length(wa)),collapse="|")


```


Question
========

In symbolic logic, we often use the following symbols for [NOT](https://en.wikipedia.org/wiki/Negation), [AND](https://en.wikipedia.org/wiki/Logical_conjunction), and [OR](https://en.wikipedia.org/wiki/Logical_disjunction):

$$\neg ~=~ \text{not}$$
$$\cap ~=~ \text{and} ~=~ \text{intersection}$$
$$\cup ~=~ \text{or} ~=~ \text{union}$$

In this case (and almost always), [unary operators](https://en.wikipedia.org/wiki/Unary_operation) (like $\neg$) have higher [precedence](https://en.wikipedia.org/wiki/Order_of_operations) than [binary operators](https://en.wikipedia.org/wiki/Arity) (like $\cup$ and $\cap$). 


You are given the following probabilities (regarding events $A$ and $B$).

* `r states[whichgive[1]]`
* `r states[whichgive[2]]`
* `r states[whichgive[3]]`

Calculate the following:

`r quetot`

## Optional metaphorical context

Imagine getting blindfolded and throwing darts at a board far away on a gusty day. On that board are two overlapping circles: circle A and circle B. If you miss the board completely, the throw does not count, and you try again. If you hit circle A, that counts as event $A$. If you miss circle A (but hit the board), that counts as $\neg A$. The probability that you hit circle A will depend on the proportion of the board's area taken up by circle A.

$$P(A) ~=~ \frac{\text{area of circle A}}{\text{area of board}}$$
$$P(\neg A) ~=~ \frac{\text{area of board} ~~-~~ \text{area of circle A}}{\text{area of board}}$$


Answerlist
--------

`r altot`

Solution
========

`r statot`


You might find it helpful to draw a Venn diagram.

* NOTE: These areas are not drawn to scale.

```{r,echo=F,fig.dim=c(10/2,10/2)}
circ = function(x0,y0,r,col=rgb(0,0,0,0)){
    th = seq(0,2*pi,pi/100)
    polygon(x0+r*cos(th),y0+r*sin(th),col=col)
}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1,9),ylim=c(-1,7.5),axes=F,ann=F)
circ(2.5,3,2.2,col=rgb(1,0,0,0.2))
circ(5.5,3,2.2,col=rgb(0,0,1,0.2))
circ(2.5,3,2.2)
circ(5.5,3,2.2)
text(2,3,oA,cex=1.2)
text(6,3,oB,cex=1.2)
text(4,3,I,cex=1.2)
lines(c(0.3,0.3,4.7,4.7),c(0.5,0.4,0.4,0.5))
text(2.5,0.2,A)
lines(c(3.3,3.3,7.7,7.7),c(0.3,0.2,0.2,0.3))
text(5.5,0,B)
lines(c(0.3,0.3,7.7,7.7),c(5.2,5.3,5.3,5.2))
text(4,5.5,U)
lines(c(-1,-1,9,9,-1),c(-1,7,7,-1,-1))
text(-0.5,7.2,"1")
text(0,6.5,nAB,cex=1.2)
```
\


```{r,echo=F,fig.dim=c(10/2,10/2)}
library(latex2exp)
circ = function(x0,y0,r,col=rgb(0,0,0,0)){
    th = seq(0,2*pi,pi/100)
    polygon(x0+r*cos(th),y0+r*sin(th),col=col)
}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1,9),ylim=c(-1,7.5),axes=F,ann=F)
polygon(c(-1,-1,9,9,-1),c(-1,7,7,-1,-1),col=rgb(0.7,1,0.7))
circ(2.5,3,2.2,col=rgb(0.9,0.4,0.4))
circ(2.5,3,2.2)
circ(5.5,3,2.2)
text(2.5,3,TeX(paste0("$P(A)=",A,"$",collapse="")),col=rgb(0.5,0,0),cex=1.1)
text(6,6,TeX(paste0("$P(\\neg A)=",nA,"$",collapse="")),col=rgb(0.2,0.6,0.2),cex=1.5)
```
\

```{r,echo=F,fig.dim=c(10/2,10/2)}
library(latex2exp)
circ = function(x0,y0,r,col=rgb(0,0,0,0)){
    th = seq(0,2*pi,pi/100)
    polygon(x0+r*cos(th),y0+r*sin(th),col=col)
}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1,9),ylim=c(-1,7.5),axes=F,ann=F)
polygon(c(-1,-1,9,9,-1),c(-1,7,7,-1,-1),col="yellow")
circ(2.5,3,2.2,col="yellow")
circ(5.5,3,2.2,col=rgb(0.5,0.5,1))
text(5.5,3,TeX(paste0("$P(B)=",B,"$",collapse="")),col=rgb(0,0,0.5),cex=1.1)
circ(2.5,3,2.2)
circ(5.5,3,2.2)
text(3,6,TeX(paste0("$P(\\neg B)=",nB,"$",collapse="")),col=rgb(0.6,0.6,0.3),cex=1.5)
```
\





Meta-information
============
extype: cloze
exclozetype: `r schtot`
exsolution: `r soltot`
exname: probs
