```{r data generation, echo = FALSE, results = "hide"}
library(exams)

while(T){
  p1 = round(runif(1,0.2,0.8),2)
  p2 = round(runif(1,0.2,0.8),2)
  if(abs(p1-p2)>0.2) {break}
}
an1 = round(p1*p2,4)
an2 = round((1-p1)*(1-p2),4)
an3 = round(p1*(1-p2)+(1-p1)*p2,4)

p = c(an1,an2,an3)
cho = list()
ans = character()

for(i in 1:3){
  numund = sample(0:3,1)
  while(T){
    choices = sort(c(p[i],
                     round(runif(numund,0.02,p[i]),4),
                     round(runif(3-numund,p[i],0.8),4)
                     )
                   )
    if(min(diff(choices))>0.002){
      cho[[i]] = choices
      ans = c(ans,paste0((choices==p[i])*1,collapse=""))
      break
      }
  }
}

cho = lapply(cho,function(a){if(typeof(a)=="double"){sprintf("%.4f",a)}else{a}})
```

Question
========
Cindy has two games today. Each game she will either win or lose. She has a `r p1` chance of winning the first game and a `r p2` chance of winning the second game.

a. What is the chance Cindy wins both games? ##ANSWER1##
b. What is the chance Cindy loses both games? ##ANSWER2##
c. What is the chance Cindy wins once and loses once (in either order)? ##ANSWER3##


```{r questionlist, echo = FALSE, results = "asis"}
answerlist(unlist(cho), markup = "markdown")
```


Solution
========


[video](https://vimeo.com/531918967){target="_blank"}

$$P(WW) = `r p1` \times `r p2` = `r p1*p2` $$
$$P(LL) = `r (1-p1)` \times `r (1-p2)` = `r (1-p1)*(1-p2)` $$
$$P(WL) = `r p1`\times `r 1-p2` = `r p1*(1-p2)` $$
$$P(LW) = `r (1-p1)`\times `r p2` = `r (1-p1)*p2`$$

* P(WW) =  `r p1` * `r p2` =  **`r p1*p2`**
* P(LL) =  (1-`r p1`) * (1-`r p2`) =  **`r (1-p1)*(1-p2)`**
* P(WL or LW) = 1-`r p1*p2`-`r (1-p1)*(1-p2)` = **`r 1-p1*p2-(1-p1)*(1-p2)`**


Meta-information
============
extype: cloze
exsolution: `r ans[1]`|`r ans[2]`|`r ans[3]`
exclozetype: schoice|schoice|schoice
exname: winlose