```{r data generation, echo = FALSE, results = "hide"}
p1 = round(runif(1,0.2,0.8),2)
p2 = round(runif(1,0.4,0.9),2)
p3 = round(runif(1,0.1,p2-0.1),2)

pwh = p1*p2
plh = (1-p1)*p3
ph = pwh+plh
pwgh = pwh/ph
```

Question
========

Bob has a `r p1` chance of winning a game. If Bob wins, he has a `r p2` chance of being happy after the game. If Bob loses, he has a `r p3` chance of being happy after the game. 

After the game, you notice Bob is happy. What is the chance that Bob won his game?


Solution
========

(ANS=`r pwgh`)

[video](https://vimeo.com/531918707){target="_blank"}

Use the definition of [conditional probability](https://en.wikipedia.org/wiki/Conditional_probability){target="blank"}.
$$P(\text{win given happy}) = \frac{P(\text{win and happy})}{P(\text{happy})}$$
We can first determine all the joint probabilities.
$$P(A\text{ and }B) = P(A)\cdot P(B\text{ given } A) $$
$$\begin{aligned}
P(\text{win and happy}) &= `r p1`\times`r p2` = `r p1*p2`\\
P(\text{win and sad}) &= `r p1`\times(1-`r p2`) = `r p1*(1-p2)`\\
P(\text{lose and happy}) &= (1-`r p1`)\times`r p3` = `r (1-p1)*p3`\\
P(\text{lose and sad}) &= (1-`r p1`)\times(1-`r p3`) = `r (1-p1)*(1-p3)`\\
\end{aligned}$$

Notice there are two [mutually exclusive](https://en.wikipedia.org/wiki/Mutual_exclusivity) ways Bob could be happy.
$$\begin{aligned}
P(\text{happy}) &= P\left(\text{[win and happy] OR [lose and happy]}\right) \\
&= P(\text{win and happy}) + P(\text{lose and happy}) \\
&= `r pwh`+`r plh` \\
&= `r ph`
\end{aligned}$$
So, back to the conditional probability.
$$P(\text{win given happy}) = \frac{`r pwh`}{`r ph`} = `r signif(pwgh,3)`$$


You might find the following [tree diagram](https://en.wikipedia.org/wiki/Tree_diagram_(probability_theory)) helpful.

```{r,echo=F,fig.dim=c(6,4)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-0.5,3.5),ylim=c(-3,3),axes=F,ann=F)
lines(c(0,1,2),c(0,1.5,2))
lines(c(0,1,2),c(0,1.5,1))
lines(c(0,1,2),c(0,-1.5,-1))
lines(c(0,1,2),c(0,-1.5,-2))
text(0,2.5,"Game 1")
text(1,2.5,"Game 2")
text(0.5,1,"W")
text(0.5,0.5,p1)
text(0.5,-1,"L")
text(0.5,-0.5,1-p1)
text(1.6,2,"H")
text(1.7,1.7,p2)
text(1.6,1,"S")
text(1.7,1.3,1-p2)
text(1.6,-1,"H")
text(1.7,-1.3,p3)
text(1.6,-2,"S")
text(1.7,-1.7,1-p3)
text(2.5,2,p1*p2)
text(2.5,1,p1*(1-p2))
text(2.5,-2,(1-p1)*(1-p3))
text(2.5,-1,(1-p1)*p3)
```
\


Meta-information
============
extype: num
exsolution: `r pwgh`
exname: bobHappy
extol: 0.01
