```{r data generation, echo = FALSE, results = "hide"}

while(T){
    n = sample(4:6,1)
    x = c(0,sort(sample(1:99,n-1)))
    l = sort(round(runif(n-1,0,1),2))
    breaks = c(0,l,1)
    p = sort(round(breaks[2:(n+1)]-breaks[1:n],2),decreasing = T)
    mu = sum(p*x)
    sig = sqrt(sum(p*(x-mu)^2))
    # the following requirements add considerable time...
    if(sum(p)==1 & sum(p>0.05)==n & as.integer(mu*10)==mu*10){
        break
    }
}

mydf = data.frame(x,p)
colnames(mydf) = c("payout ($)","probability")
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

A scratch-off lottery ticket has the following payout probabilities:

```{r tab1, results="asis", echo=F}
knitr::kable(mydf,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

What is the value, in dollars, of the unscratched ticket (to a [risk-neutral](https://en.wikipedia.org/wiki/Risk_neutral_preferences) individual)?



Solution
========

The [expected value](https://en.wikipedia.org/wiki/Expected_value) is the weighted average of the payouts weighted by their probabilities. The expected value is the sum of the products of each payout times its probability.

$$\mu ~=~ \sum x\cdot P(x)$$


$$\mu ~=~ `r paste0("(",x,"\\cdot",p,")",collapse="+")`$$

$$\mu ~=~ `r paste0(x*p,collapse="+")`$$

$$\mu ~=~ `r mu`$$

A risk-neutral person would value an unscratched ticket at $`r sprintf("%.2f",mu)`.


Meta-information
============
extype: num
exsolution: `r mu`
exname: scratchoff_value
extol: 0.01