```{r data generation, echo = FALSE, results = "hide"}
x = 6*(1:4)
y = 6*sample(5:10,4)
abposs = c(2,3,1/2,1/3)
ab = sample(2:3)^sample(c(-1,1))
a = ab[1]
b = ab[2]

library(MASS)

x2 = round(x/b)
y2 = round(y*a)
f = data.frame(x,y)
colnames(f) = c("$x$","$f(x)$")
g = data.frame(x2,y2)
colnames(g) = c("$x$","$g(x)$")
col1 = paste0("##ANSWER",1:4,"##")
col2 = paste0("##ANSWER",5:8,"##")
adf = data.frame(col1,col2)
colnames(adf) = c("$x$","$g(x)$")
if(a==2){
  ex = paste0("2\\, f(\\frac{1}{3}x)")
}
if(a==1/2){
  ex = paste0("\\frac{1}{2}\\,f(3x)")
}
if(a==3){
  ex = paste0("3\\, f(\\frac{1}{2}x)")
}
if(a==1/3){
  ex = paste0("\\frac{1}{3}\\,f(2x)")
}

x_answer_possibilities = numeric()
y_answer_possibilities = numeric()

for(j in abposs){
  x_answer_possibilities = sort(unique(c(x_answer_possibilities,j*x)))
  y_answer_possibilities = sort(unique(c(y_answer_possibilities,j*y)))
}

anslist = paste0("* ",c(rep(x_answer_possibilities,4),
                        rep(y_answer_possibilities,4)),"\n",collapse="")
ans1 = paste0(1*(x2[1]==x_answer_possibilities),collapse="")
ans2 = paste0(1*(x2[2]==x_answer_possibilities),collapse="")
ans3 = paste0(1*(x2[3]==x_answer_possibilities),collapse="")
ans4 = paste0(1*(x2[4]==x_answer_possibilities),collapse="")
ans5 = paste0(1*(y2[1]==y_answer_possibilities),collapse="")
ans6 = paste0(1*(y2[2]==y_answer_possibilities),collapse="")
ans7 = paste0(1*(y2[3]==y_answer_possibilities),collapse="")
ans8 = paste0(1*(y2[4]==y_answer_possibilities),collapse="")
```

Question
========

Let $f(x)$ be defined by the table below:

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tabf, results="asis", echo=F}
knitr::kable(f,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


Let $g(x)$ be defined with the equation $g(x)=`r ex`$. What are the 4 corresponding points on $g$? (Use same order.)

```{r tabadf, results="asis", echo=F}
knitr::kable(adf,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```




Answerlist
--------

`r anslist`


Solution
========

```{r tabg, results="asis", echo=F}
knitr::kable(g,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

* Notice $g(`r x2[1]`)~=~`r a`\cdot f(`r b`\cdot `r x2[1]`)~=~`r a`\cdot f(`r b*x2[1]`)~=~`r a`\cdot `r y[1]`~=~ `r y2[1]`$
* Notice $g(`r x2[2]`)~=~`r a`\cdot f(`r b`\cdot `r x2[2]`)~=~`r a`\cdot f(`r b*x2[2]`)~=~`r a`\cdot `r y[2]`~=~ `r y2[2]`$
* Notice $g(`r x2[3]`)~=~`r a`\cdot f(`r b`\cdot `r x2[3]`)~=~`r a`\cdot f(`r b*x2[3]`)~=~`r a`\cdot `r y[3]`~=~ `r y2[3]`$
* Notice $g(`r x2[4]`)~=~`r a`\cdot f(`r b`\cdot `r x2[4]`)~=~`r a`\cdot f(`r b*x2[4]`)~=~`r a`\cdot `r y[4]`~=~ `r y2[4]`$

The "shortcut" is to recognize that the definition $g(x)=`r ex`$ implies a horizontal stretch of `r 1/b` and a vertical stretch of `r a`. The horizontal stretch is an multiplicative/divisive change to the inputs. The vertical stretch is an multiplicative/divisive change to the outputs.

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`|`r ans5`|`r ans6`|`r ans7`|`r ans8`
exname: translate_table
exshuffle: FALSE