---
output: pdf_document
params:
    rseed: 0
    showsol: false
    useseed: false
---

```{r,echo=F,eval=params$useseed}
set.seed(params$rseed)
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## Grid Countdown Spirals

Follow the teacher! Use a ruler!

1. Start at the star.
2. Go down 4 units.
3. Go right 3 units.
4. Go up 2 units.
5. Go left 1 unit.
6. Repeat steps 2 through 5... Notice a 90° turn counterclockwise after each segment. 

```{r,echo=F,fig.dim=c(6,6)}
pch = 8
par(mar=c(0,0,0,0),pty="s")
turn = pi/2
a1 = -pi/2
lengths = 4:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr,midx+rr),ylim=c(midy-rr,midy+rr))
xlow = floor(midx-rr)-1
xhi = ceiling(midx+rr)+1
ylow = floor(midy-rr)-1
yhi = ceiling(midy+rr)+1
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.2)
    }
}
points(0,0,pch=pch,cex=0.6)
if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:


\newpage

This time, count down from 5.

1. Start at the star, heading down.
2. Move 5 and then turn 90° counterclockwise.
3. Move 4 and then turn 90° counterclockwise.
4. Move 3 and then turn 90° counterclockwise.
5. Move 2 and then turn 90° counterclockwise.
6. Move 1 and then turn 90° counterclockwise.
7. Repeat steps 2 through 6.


```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
turn = pi/2
a1 = -pi/2
lengths = 5:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.4)
    }
}
points(0,0,pch=pch,cex=0.8)
if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:


\newpage

This time, count down from 6.

1. Start at the star, heading down.
2. Move 6 and then turn 90° counterclockwise.
3. Move 5 and then turn 90° counterclockwise.
4. Move 4 and then turn 90° counterclockwise.
5. Move 3 and then turn 90° counterclockwise.
6. Move 2 and then turn 90° counterclockwise.
7. Move 1 and then turn 90° counterclockwise.
8. Repeat steps 2 through 7.


```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
turn = pi/2
a1 = -pi/2
lengths = 6:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.4)
    }
}
points(0,0,pch=pch,cex=0.8)

if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:

\newpage

This time, count down from 9. (And still start at star heading down.)

```{r,echo=F,fig.dim=c(7,7)}
par(mar=c(0,0,0,0),pty="s")
turn = pi/2
a1 = -pi/2
lengths = 9:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.4)
    }
}
points(0,0,pch=pch,cex=0.8)

if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:



\newpage


This time, count down from 10. (And still start at star heading down.)

```{r,echo=F,fig.dim=c(7,7)}
par(mar=c(0,0,0,0),pty="s")
turn = pi/2
a1 = -pi/2
lengths = 10:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.4)
    }
}
points(0,0,pch=pch,cex=0.8)

if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:



\newpage


This time, turn 120° counterclockwise after each segment. And count down from 10. (And still start at star heading down.) This time I've started the pattern for you.

```{r,echo=F,fig.dim=c(7,7)}
par(mar=c(0,0,0,0),pty="s")
turn = 2*pi/3
a1 = -pi/2
lengths = 10:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
ndl = ceiling(-xlow/cos(pi/3))
ndr = ceiling(xhi/cos(pi/3))
ndd = ceiling(-ylow/sin(pi/3))
ndu = ceiling(yhi/sin(pi/3))

for(i in -ndl:ndr){
    for(j in -ndd:ndu){
        points(i*cos(pi/6),j+0.5*(i%%2),pch=19,cex=0.3)
    }
}
points(0,0,pch=pch,cex=0.8)
lines(xs[1:5],ys[1:5],col="black")

if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:


\newpage

This time, turn 60° counterclockwise after each segment. And count down from 10. (And still start at star heading down.) This time I've started the pattern for you.

```{r,echo=F,fig.dim=c(7,7)}
par(mar=c(0,0,0,0),pty="s")
turn = pi/3
a1 = -pi/2
lengths = 10:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
ndl = ceiling(-xlow/cos(pi/3))
ndr = ceiling(xhi/cos(pi/3))
ndd = ceiling(-ylow/sin(pi/3))
ndu = ceiling(yhi/sin(pi/3))

for(i in -ndl:ndr){
    for(j in -ndd:ndu){
        points(i*cos(pi/6),j+0.5*(i%%2),pch=19,cex=0.3)
    }
}
points(0,0,pch=pch,cex=0.8)
lines(xs[1:5],ys[1:5],col="black")

if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:



\newpage

This time, turn 60° counterclockwise after each segment. And count down from 7. (And still start at star heading down.) This time I've started the pattern for you.

```{r,echo=F,fig.dim=c(7,7)}
par(mar=c(0,0,0,0),pty="s")
turn = pi/3
a1 = -pi/2
lengths = 7:1
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
ndl = ceiling(-xlow/cos(pi/3))
ndr = ceiling(xhi/cos(pi/3))
ndd = ceiling(-ylow/sin(pi/3))
ndu = ceiling(yhi/sin(pi/3))

for(i in -ndl:ndr){
    for(j in -ndd:ndu){
        points(i*cos(pi/6),j+0.5*(i%%2),pch=19,cex=0.3)
    }
}
points(0,0,pch=pch,cex=0.8)
lines(xs[1:5],ys[1:5],col="black")

if(params$showsol){
    lines(xs,ys,col="red")
}

```

* Describe the result:

\newpage

Design your own variations of the patterns shown above. Explain the algorithm used to generate the images!

```{r,echo=F,fig.dim=c(7.09,7.09)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(0,18),ylim=c(0,18),axes=F,ann=F,xaxs="i",yaxs="i")
for(i in 0:(2*18)){
    for(j in 0:(2*18)){
        points(i/2,j/2,pch=19,cex=0.4)
    }
}
```

Explain your algorithm:


\newpage


Design your own variations of the patterns shown above. Explain the algorithm used to generate the images!

```{r,echo=F,fig.dim=c(7.09,7.09)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(0,18),ylim=c(0,18),axes=F,ann=F,xaxs="i",yaxs="i")
ndr = ceiling(18/cos(pi/3))*2
for(i in 0:ndr){
    for(j in -3:50){
        points(i*cos(pi/6)/2,(j+0.5*(i%%2))/2,pch=19,cex=0.3)
    }
}
```

Explain your algorithm:

