---
title: "grid spirals"
author: "Mr. Worley"
# output: slidy_presentation
output: html_document
---


# Turn 90°, lengths: 4, 3, 2, 1

Dr. Huston suggested to draw a pattern on grid paper by:

1. Start on a gridpoint.
2. Draw a line straight down of length 4.
3. Turn 90° counterclockwise.
4. Draw a line with length 3.
5. Turn 90° counterclockwise.
6. Draw a line with length 2.
7. Turn 90° counterclockwise.
8. Draw a line with length 1.
7. Turn 90° counterclockwise.
8. Draw a line with length 4.
9. Keep going with this pattern. Lengths are 4, then 3, then 2, then 1. Each time turn 90°.



```{r,echo=F}
turn = pi/2
a1 = -pi/2
lengths = 4:1
n = 100
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
par(pty="s",mar=c(0,0,0,0))
plot(xs,ys,"l",axes=F,ann=F)
for(xi in min(xs-1):max(xs+1)){
    lines(c(xi,xi),c(min(ys)-1,max(ys)+1),col="grey",lwd=0.6)
}
for(yi in min(ys-1):max(ys+1)){
    lines(c(min(xs)-1,max(xs)+1),c(yi,yi),col="grey",lwd=0.6)
}
lines(xs,ys,lwd=1.2)
points(0,0,pch=19,cex=0.8)
```

# Turn 90°, lengths: 5, 4, 3, 2, 1

If we count down from 5 instead of 4, we get a closed-loop pattern.

```{r,echo=F}
turn = pi/2
a1 = -pi/2
lengths = 5:1
n = 100
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
par(pty="s",mar=c(0,0,0,0))
plot(xs,ys,"l",axes=F,ann=F)
for(xi in min(xs-1):max(xs+1)){
    lines(c(xi,xi),c(min(ys)-1,max(ys)+1),col="grey",lwd=0.6)
}
for(yi in min(ys-1):max(ys+1)){
    lines(c(min(xs)-1,max(xs)+1),c(yi,yi),col="grey",lwd=0.6)
}
lines(xs,ys,lwd=1.2)
points(0,0,pch=19,cex=0.8)
```

# Turn 90°, lengths: [6 .. 1]

If we count down from 6, we get another closed-loop pattern.

```{r,echo=F}
getxsys = function(turn,a1,lengths,n){
    a = a1
    x = 0
    y = 0
    xs = c(x)
    ys = c(y)
    for(i in 0:n){
        l = lengths[(i %% length(lengths)) +1]
        x2 = x+l*cos(a)
        y2 = y+l*sin(a)
        xs = c(xs,x2)
        ys = c(ys,y2)
        x = x2
        y = y2
        a = a+turn
    }
    return(list(xs,ys))
}
plotpattern = function(xsys){
    par(pty="s",mar=c(0,0,0,0))
    xs = xsys[[1]]
    ys = xsys[[2]]
    plot(xs,ys,"l",axes=F,ann=F)
    for(xi in min(xs-1):max(xs+1)){
        lines(c(xi,xi),c(min(ys)-1,max(ys)+1),col="grey",lwd=0.6)
    }
    for(yi in min(ys-1):max(ys+1)){
        lines(c(min(xs)-1,max(xs)+1),c(yi,yi),col="grey",lwd=0.6)
    }
    lines(xs,ys,lwd=1.2)
    points(0,0,pch=19,cex=0.8)
}
turn = pi/2
a1 = -pi/2
lengths = 6:1
n = 100
xsys = getxsys(turn,a1,lengths,n)
plotpattern(xsys)
```

# Turn 90°, lengths: [7 .. 1]

If we count down from 7, we get another closed-loop pattern.

```{r,echo=F}
getxsys = function(turn,a1,lengths,n){
    a = a1
    x = 0
    y = 0
    xs = c(x)
    ys = c(y)
    for(i in 0:n){
        l = lengths[(i %% length(lengths)) +1]
        x2 = x+l*cos(a)
        y2 = y+l*sin(a)
        xs = c(xs,x2)
        ys = c(ys,y2)
        x = x2
        y = y2
        a = a+turn
    }
    return(list(xs,ys))
}
plotpattern = function(xsys){
    par(pty="s",mar=c(0,0,0,0))
    xs = xsys[[1]]
    ys = xsys[[2]]
    plot(xs,ys,"l",axes=F,ann=F)
    for(xi in min(xs-1):max(xs+1)){
        lines(c(xi,xi),c(min(ys)-1,max(ys)+1),col="grey",lwd=0.6)
    }
    for(yi in min(ys-1):max(ys+1)){
        lines(c(min(xs)-1,max(xs)+1),c(yi,yi),col="grey",lwd=0.6)
    }
    lines(xs,ys,lwd=1.2)
    points(0,0,pch=19,cex=0.8)
}
turn = pi/2
a1 = -pi/2
lengths = 7:1
n = 100
xsys = getxsys(turn,a1,lengths,n)
plotpattern(xsys)
```





# Turn 90°, lengths: [11 .. 1]

If we count down from 11, we get another closed-loop pattern.

```{r,echo=F}
turn = pi/2
a1 = -pi/2
lengths = 11:1
n = 100
xsys = getxsys(turn,a1,lengths,n)
plotpattern(xsys)
```

# Turn 120°, lengths: [7 .. 1]

If we count down from 7, and turn by 120°, we get another closed-loop pattern.

```{r,echo=F}
plotpattern2 = function(xsys){
    par(pty="s",mar=c(0,0,0,0))
    xs = xsys[[1]]
    ys = xsys[[2]]
    plot(xs,ys,"l",axes=F,ann=F)
    for(i in -20:20){
        abline(v=i*cos(pi/6),col="grey",lwd=0.6)
        abline(a=sin(pi/6)*i*2,b=tan(pi/6),col="grey",lwd=0.6)
        abline(a=sin(pi/6)*i*2,b=tan(-pi/6),col="grey",lwd=0.6)
    }
    lines(xs,ys,lwd=1.2)
    points(0,0,pch=19,cex=0.8)
}
turn = 2*pi/3
a1 = -pi/2
lengths = 7:1
n = 100
xsys = getxsys(turn,a1,lengths,n)
plotpattern2(xsys)

```


# Turn 60°, lengths: [5 .. 1]

If we count down from 5, and turn by 60°, we get another closed-loop pattern.

```{r,echo=F}
plotpattern2 = function(xsys){
    par(pty="s",mar=c(0,0,0,0))
    xs = xsys[[1]]
    ys = xsys[[2]]
    plot(xs,ys,"l",axes=F,ann=F)
    for(i in -100:100){
        abline(v=i*cos(pi/6),col="grey",lwd=0.6)
        abline(a=sin(pi/6)*i*2,b=tan(pi/6),col="grey",lwd=0.6)
        abline(a=sin(pi/6)*i*2,b=tan(-pi/6),col="grey",lwd=0.6)
    }
    lines(xs,ys,lwd=1.2)
    points(0,0,pch=19,cex=0.8)
}
turn = pi/3
a1 = -pi/2
lengths = 5:1
n = 100
xsys = getxsys(turn,a1,lengths,n)
plotpattern2(xsys)

```

