```{r data generation, echo = FALSE, results = "hide"}
x = sort(sample(2:8,4))
y = sample(2:8,4)
hk = sample(1:5,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
x2 = x+h
y2 = y+k
f = data.frame(x,y)
colnames(f) = c("$x$","$f(x)$")
g = data.frame(x2,y2)
colnames(g) = c("$x$","$g(x)$")
col1 = paste0("##ANSWER",1:4,"##")
col2 = paste0("##ANSWER",5:8,"##")
adf = data.frame(col1,col2)
colnames(adf) = c("$x$","$g(x)$")
if(h<0){
  inside = paste0("+",-h,collapse="")
  hor = "left"
} else {
  inside = paste0("-",h,collapse="")
  hor = "right"
}
if(k<0){
  outside = paste0("-",-k,collapse="")
  ver = "down"
} else {
  outside = paste0("+",k,collapse="")
  ver = "up"
}
ex = paste0("f(x",inside,")",outside)
answer_possibilities = -5:15
anslist = paste0("* ",rep(answer_possibilities,8),"\n",collapse="")
ans1 = paste0(1*(x2[1]==answer_possibilities),collapse="")
ans2 = paste0(1*(x2[2]==answer_possibilities),collapse="")
ans3 = paste0(1*(x2[3]==answer_possibilities),collapse="")
ans4 = paste0(1*(x2[4]==answer_possibilities),collapse="")
ans5 = paste0(1*(y2[1]==answer_possibilities),collapse="")
ans6 = paste0(1*(y2[2]==answer_possibilities),collapse="")
ans7 = paste0(1*(y2[3]==answer_possibilities),collapse="")
ans8 = paste0(1*(y2[4]==answer_possibilities),collapse="")
```

Question
========

Let $f(x)$ be defined by the table below:

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tabf, results="asis", echo=F}
knitr::kable(f,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

So, for example, $f(`r x[1]`)=`r y[1]`$.


Let $g(x)$ be defined with the equation $g(x)=`r ex`$. What are the 4 corresponding points on $g$? (Use same order.)

```{r tabadf, results="asis", echo=F}
knitr::kable(adf,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```




Answerlist
--------
`r anslist`


Solution
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tabg, results="asis", echo=F}
knitr::kable(g,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

* Notice $g(`r x2[1]`)~=~f(`r x2[1]` `r inside`)`r outside`~=~f(`r x2[1]-h`)`r outside`~=~`r y[1]` `r outside` ~=~ `r y2[1]`$
* Notice $g(`r x2[2]`)~=~f(`r x2[2]` `r inside`)`r outside`~=~f(`r x2[2]-h`)`r outside`~=~`r y[2]` `r outside` ~=~ `r y2[2]`$
* Notice $g(`r x2[3]`)~=~f(`r x2[3]` `r inside`)`r outside`~=~f(`r x2[3]-h`)`r outside`~=~`r y[3]` `r outside` ~=~ `r y2[3]`$
* Notice $g(`r x2[4]`)~=~f(`r x2[4]` `r inside`)`r outside`~=~f(`r x2[4]-h`)`r outside`~=~`r y[4]` `r outside` ~=~ `r y2[4]`$

The "shortcut" is to recognize that the definition $g(x)=`r ex`$ implies a horizontal shift of `r hor` by `r abs(h)` and a vertical shift of `r ver` by `r abs(k)`. The horizontal shift is an additive/subtractive change to the inputs. The vertical shift is an additive/subtractive change to the outputs.

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`|`r ans5`|`r ans6`|`r ans7`|`r ans8`
exname: translate_table
exshuffle: FALSE