```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
pa = 1:9
while(T){
  x1 = sort(c(1,sample(2:8,3),9))
  f = sample(pa,5)
  a = sample(x1,1)
  x2 = sort(c(1,sample(2:8,3),9))
  g = sample(pa,5)
  b = sample(x2,1)
  an1 = g[which(x2==f[which(x1==a)])]
  an2 = f[which(x1==g[which(x2==b)])]
  if(f[which(x1==a)] %in% x2 &&
     g[which(x2==b)] %in% x1 &&
     abs(f[5]-g[5]) > 2 &&
     an1 != an2 &&
     a != an1 &&
     b != an2 &&
     a != an2 &&
     b != an1 &&
     a != f[which(x1==a)] &&
     b != g[which(x2==b)] &&
     an1 != g[which(x2==b)] &&
     an2 != f[which(x1==a)]
     ){break}
}

al = paste0("* ",pa,"\n",collapse="")

ans1 = paste0(1*(pa==an1),collapse="")
ans2 = paste0(1*(pa==an2),collapse="")
```

Question
========

Let functions $f$ and $g$ be defined by the graph below.

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s")
plot(0,0,type="n",xlim=c(0,10),ylim=c(0,10),lwd=2,ylab="y",xlab="x")
for(j in seq(0,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xspline(x1,f,shape=c(0,rep(-0.2,length(x1)-2),0),border = "blue",lwd=4)
xspline(x2,g,shape=c(0,rep(-0.2,length(x1)-2),0),border = "red",lwd=4)
text(x1[length(x1)]+0.4,f[length(x1)],"f",col="blue",cex=2)
text(x2[length(x2)]+0.4,g[length(x2)],"g",col="red",cex=2)
```
\


Evaluate the following:

* $g(f(`r a`)) =$ ##ANSWER1##
* $f(g(`r b`)) =$ ##ANSWER2##

Answerlist
--------

`r al`
`r al`

Solution
========

* $g(f(`r a`))=g(`r f[which(x1==a)]`)=`r an1`$
* $f(g(`r b`))=f(`r g[which(x2==b)]`)=`r an2`$


### For the first one:
1. Notice, on the blue curve is point (`r a`,`r f[which(x1==a)]`), so $f(`r a`)=`r f[which(x1==a)]`$.
2. Notice, on the red curve is point (`r f[which(x1==a)]`,`r an1`), so $g(`r f[which(x1==a)]`)=`r an1`$.

### For the second one:
1. Notice, on the red curve is point (`r b`,`r f[which(x2==b)]`), so $f(`r b`)=`r f[which(x2==b)]`$.
2. Notice, on the blue curve is point (`r f[which(x2==b)]`,`r an2`), so $g(`r f[which(x2==b)]`)=`r an2`$.





Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r ans1`|`r ans2`
exname: compose_graphs