```{r data generation, echo = FALSE, results = "hide"}

f = function(x){
    return((x^3-3*x^2+2)/2)
}
ht = function(x,k){
    return(f(x+k))
}
vt = function(x,k){
    return(f(x)+k)
}
hd = function(x,k){
    return(f(k*x))
}
vd = function(x,k){
    return(k*f(x))
}

gposs = c(ht,vt,hd,vd)
kposs = c(-2,-1/2,1/2,2)

k = sample(kposs,1)
wt = sample(1:4,1)
x = seq(-10,10,0.01)
ys = list(ht(x,k),
          vt(x,k),
          hd(x,k),
          vd(x,k))
y = ys[[wt]]

sol1 = paste0(1*(wt==1:4),collapse="")
sol2 = paste0(1*(kposs==k),collapse="")

gtp = c("g(x) = f(x+k)",
        "g(x) = f(x)+k",
        "g(x) = f(k*x)",
        "g(x) = k*f(x)"
        )
gtex = c("g(x)~=~f(x+k)",
        "g(x)~=~f(x)+k",
        "g(x)~=~f(k\\cdot x)",
        "g(x) = k \\cdot f(x)"
        )

ans = gtex[wt]
ans2 = gsub("k",k,ans,fixed=T)
ans2 = gsub("+-","-",ans2,fixed=T)

```

Question
========

Let $f(x)=\frac{x^3-3x^2+2}{2}$. Function $g$ is made with a simple transformation (horizontal or vertical shift or stretch with possible reflection). Both functions are graphed below.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-6,6),ylim=c(-6,6),ann=F,axes=F)
for(i in -10:10){
    abline(h=i,col="lightgrey",lwd=0.8)
    abline(v=i,col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    abline(h=i,col="darkgrey")
    abline(v=i,col="darkgrey")
}
arrows(-6.3,0,6.3,0,0.1,10,3,lwd=2)
arrows(0,-6.3,0,6.3,0.1,10,3,lwd=2)
text(5,-0.5,"5")
text(-5,-0.5,"-5")
text(-0.5,5,"5")
text(-0.5,-5,"-5")
text(5.5,0.5,"x")
text(0.5,5.5,"y")

lines(x,f(x),lwd=2,col="red",lty=2)
lines(x,y,lwd=3,col="blue")

legend("topright",legend=c("y = f(x)","y = g(x)"),col=c("red","blue"),lty=c(2,1),lwd=c(2,3))

```
\

1. Which equation was used to generate $g$?
* ##ANSWER1##
2. What is the value of $k$?
* ##ANSWER2##


Answerlist
--------

* g(x) = f(x+k)
* g(x) = f(x)+k
* g(x) = f(k*x)
* g(x) = k*f(x)
* k = -2
* k = -1/2
* k = 1/2
* k = 2


Solution
========

If you open [Desmos](https://www.desmos.com/calculator) and type $f(x)=\frac{x^3-3x^2+2}{2}$ and then type

$$`r ans2`$$

You'll get a picture that looks like the given graph.

So, the equation was $`r ans`$, and the parameter was $k=`r k`$.

To arrive at this answer, I would use Desmos. I would start by typing $f(x)=\frac{x^3-3x^2+2}{2}$. Then I would try $g(x)=f(x+k)$, add a slider for $k$, and check if you can get the second curve to look like the given. If not, try $g(x)=f(x)+k$ or $g(x)=f(kx)$ or $g(x)=k\cdot f(x)$. Remember, there are only 4 possible values for $k$.



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: identify_transformation