```{r data generation, echo = FALSE, results = "hide"}

D = list(c("energy","N\\cdot m","distance","m","force","N"),
         c("energy","J","time","s","power","J/s"),
         c("energy","kW\\cdot hr","time","hr","power","kW"),
         c("distance","m","time","s","velocity","m/s"),
         c("velocity","m/s","time","s","acceleration","m/s^2"),
         c("acceleration","m/s^2","time","s","jerk","m/s^3"),
         c("impulse","N\\cdot s","time","s","force","N"),
         c("charge","C","time","s","current","C/s")
         )

uc = c("s","hr","m","m/s","m/s^2","m/s^3","N","N\\cdot s","N\\cdot m","J","J/s",
          "kW","kW\\cdot hr","C","C/s")

units = c("s","hr","m","m/s","m/s²","m/s³","N","N*s","N*m","J","J/s",
          "kW","kW*hr","C","C/s")

quants = sort(c("time","distance","force","energy","power","velocity","acceleration","jerk","impulse","charge","current"))

while(T){
    whi = sample(1:length(D),1)
    u = D[[whi]]
    x = seq(0,1,0.001)
    while(T){
        cf = runif(6,-1,1)
        ss = runif(1,-0.2,0.2)
        ph = runif(1,0,2*pi)
        ff = runif(1,1,3)
        y = (cf[6]*x^5+cf[5]*x^4+
                 cf[4]*x^3+cf[3]*x^2+cf[2]*x+cf[1])+ss*sin(x*2*pi*ff+ph)
        if(min(y)>0 && max(y)<1 && max(y)-min(y)>0.4){break}
    }
    x = x*100
    ymult = sample(c(1,10,100,1000),1)
    y = y*ymult
    
    while(T){
        ii = sort(sample(2:(length(x)-1),2))
        x1 = x[ii[1]]
        x2 = x[ii[2]]
        y1 = round(y[ii[1]]/ymult*1000)*ymult/1000
        y2 = round(y[ii[2]]/ymult*1000)*ymult/1000
        if(x2-x1>5){break}
    }
    
    ii3 = round(mean(ii))
    m = (y2-y1)/(x2-x1)
    ylin = m*(x-x1)+y1
    
    mr = signif(m,3)
    sfs = (sqrt(10))^((-4:0+sample(0:4,1)))
    ach = sort(c(-signif(m*sfs,3),signif(m*sfs,3)))
    sol1 = paste0(1*(mr==ach),collapse="")
    sol2 = paste0(1*(uc==u[6]),collapse="")
    sol3 = paste0(1*(quants==u[5]),collapse="")
    if(sum(mr==ach)==1  && mr>0.01){break}
}

al1 = paste0("* ",ach,collapse="\n")
al2 = paste0("* ",units,collapse="\n")
al3 = paste0("* ",quants,collapse="\n")


```



Question
========

In the table below, various physical quantities and some common units of measure are presented:

```{css, echo=F}
td {
    border: 2px solid black;
    padding: 0.5em;
}
tr {
    border: 2px solid black;
    padding: 0.5em;
}
th {
    border: 2px solid black;
    border-bottom: 5px solid black;
    background: #CCC;
    padding: 0.5em;
}
```

<div class="taby">
| quantity | units of measure |
|:---:|:---:|
| time | seconds ($\mathrm{s}$) |
| distance | meters ($\mathrm{m}$) |
| velocity | meters per second ($\mathrm{m/s}$) |
| acceleration | meters per squared second ($\mathrm{m/s^2}$) |
| jerk | meters per cubed second ($\mathrm{m/s^3}$) |
| force | Newtons ($\mathrm{N}$) |
| impulse (momentum) | Newton-seconds ($\mathrm{N\cdot s}$) |
| energy | Newton-meters ($\mathrm{N\cdot m}$)|
| energy | Joules ($\mathrm{J}$) |
| energy | kilowatt-hours ($\mathrm{kW\cdot hr}$) |
| power | Newton-meters per second ($\mathrm{\frac{N\cdot m}{s}}$) |
| power | Joules per second ($\mathrm{J/s}$) = Watts ($\mathrm{W}$) |
| power | kilowatt ($\mathrm{kW}$) |
| electrical charge | Coulombs ($\mathrm{C}$) |
| electrical current | Coulombs/second ($\mathrm{C/s}$) = amperes ($\mathrm{A}$) |
</div>

A device measures `r u[1]` (in $\mathrm{`r u[2]`}$) as a function of `r u[3]` (in $\mathrm{`r u[4]`}$). Those measurements are graphed below.

```{r,echo=F,fig.dim=c(8,5)}
library(latex2exp)

par(mar=c(4,5,2,2))

plot(x,y,"l",col="blue",lwd=2,xlim=c(0,100),ylim=c(0,ymult),xlab=TeX(paste0(u[3]," ($",u[4],"$)",collapse="")),ylab=TeX(paste0(u[1]," ($",u[2],"$)",collapse="")))

lines(x,ylin,col="red")
points(x1,y1,pch=20,col="red",cex=1.3)
points(x2,y2,pch=20,col="red",cex=1.3)

```
\

The two marked points are at coordinates (`r x1`, `r y1`) and (`r x2`, `r y2`). Determine the average rate of change of the `r u[1]` over the given interval of `r u[3]` marked by the two points.

AROC = ##ANSWER1## ##ANSWER2##

This average rate of change is a quantity of ##ANSWER3##.


Answerlist
--------

`r al1`
`r al2`
`r al3`

Solution
========

$$\mathrm{AROC}~=~\frac{(`r y2`-`r y1`)(\mathrm{`r u[2]`})}{(`r x2`-`r x1`)(\mathrm{`r u[4]`})}$$

$$\mathrm{AROC}~=~\frac{`r y2-y1`}{`r x2-x1`}\,\frac{\mathrm{`r u[2]`}}{\mathrm{`r u[4]`}}$$

$$\mathrm{AROC}~=~`r mr`\,\mathrm{`r u[6]`}$$

Thus when we find the average rate of change of `r u[1]` over an interval of `r u[3]`, the result is a quantity of `r u[5]`.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: AROC_dimensions