```{r,echo=FALSE}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

while(T){
    abc = sample(2:12,3)*sample(c(-1,1),3,T)
    a = abc[1]
    b = abc[2]
    c = abc[3]
    h = -b/2/a
    D = b^2-4*a*c
    if(D>0){
        wid = sqrt(D)/2/abs(a)
        r = h-wid
        s = h+wid
        k = a*r*s-a*h^2
        if(!(h%%1==0)){break}
    }
}
# # y = a*(x-h)^2+k
# # y = ax^2 - 2ahx + ah^2+k
# 
# # y = a(x-r)(x-s)
# # y = a(x^2-(r+s)x+rs)
# # y = ax^2 - a(r+s)x + ars
# 
# # ah^2+k = ars
# # a = -k/(h^2-rs)
# # a = k/(rs-h^2)

```


Question
========


Consider the [quadratic function](https://en.wikipedia.org/wiki/Quadratic_function) defined below. 

$$f(x)~=~`r pn(abc,2:0)`$$

Below, I've graphed $y=f(x)$, and I've included the axis of symmetry as a dashed purple line and the vertex as a filled red dot.

```{r,echo=F}
par(mar=c(5,5,1,1))
plot(0,0,"n",xlim=c(h-2*wid,h+2*wid),ylim=c(-2*abs(k),2*abs(k)),xlab="x",ylab="y")
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(h-2*wid,h+2*wid,wid/100)
y = a*x^2+b*x+c
lines(x,y,lwd=3,col="blue")

abline(v=h,col="purple",lty=2)

points(h,k,pch=19,col="red")
text(h,k,"(h,k)",adj=c(1.2,0.5+sign(a)),col="red")

```
\

Using [the geometric significance of the quadratic formula](https://en.wikipedia.org/wiki/Quadratic_formula#Geometric_significance), calculate $h$, the horizontal coordinate of the vertex. *The tolerance is $\pm 0.01$.*


Solution
========

Look at the quadratic formula, which tells us if our quadratic function is in standard form, like $y=ax^2+bx+c$, then:

$$\text{roots of quadratic function} ~=~ \frac{-b}{2a}\pm\frac{\sqrt{b^2-4ac}}{2a}$$

We were given a quadratic function in standard form. Identify the parameters.

* The quadratic coefficient: $a=`r a`$
* The linear coefficient: $b=`r b`$
* The constant: $c=`r c`$

The [the geometric significance of the quadratic formula](https://en.wikipedia.org/wiki/Quadratic_formula#Geometric_significance) tells us that $h=\frac{-b}{2a}$ and the distance of the roots to the axis of symmetry is $\frac{\sqrt{b^2-4ac}}{2a}$. Use the formula to calculate $h$.

$$\begin{align}
h &= \frac{-b}{2a} \\\\ 
 &= \frac{-(`r b`)}{2(`r a`)} \\\\
 &= `r h`
\end{align}$$

* The axis of symmetry is line $x=`r h`$.
* The vertex is point $(`r h`,\,`r k`)$


Meta-information
============
extype: num
exsolution: `r h`
exname: quad_AOS_from_standard
extol: 0.01