```{r,echo=FALSE}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}

gcd <- function(...) Reduce(gcd2, c(...))

while(T){
    abc = sample(2:12,3)*sample(c(-1,1),3,T)
    a = abc[1]
    b = abc[2]
    c = abc[3]
    h = -b/2/a
    D = b^2-4*a*c
    if(D>0){
        r = sqrt(D)/2/abs(a)
        m = h-r
        n = h+r
        k = a*m*n-a*h^2
        if(!(h%%1==0)){break}
    }
}

hn1 = -b
hd1 = 2*a

hn2 = round(hn1/gcd(hn1,hd1))
hd2 = round(hd1/gcd(hn1,hd1))

hfrac = paste0("\\frac{",sign(h)*abs(hn2),"}{",abs(hd2),"}")

kn1 = b^2-4*a*c
kd1 = -4*a

kn2 = round(kn1/gcd(kn1,kd1))
kd2 = round(kd1/gcd(kn1,kd1))

kfrac = paste0("\\frac{",sign(k)*abs(kn2),"}{",abs(kd2),"}")

```


Question
========


Consider the [quadratic function](https://en.wikipedia.org/wiki/Quadratic_function) defined below. 

$$f(x)~=~`r pn(abc,2:0)`$$

Below, I've graphed $y=f(x)$, and I've included the axis of symmetry as a dashed purple line and I've marked the distance from the axis of symmetry to one of the roots with a red line segment labelled $w$.

```{r,echo=F}
par(mar=c(5,5,1,1))
plot(0,0,"n",xlim=c(h-2*r,h+2*r),ylim=c(-2*abs(k),2*abs(k)),xlab="x",ylab="y")
abline(h=0,lwd=2,col="darkgrey")
abline(v=0,lwd=2,col="darkgrey")
x = seq(h-2*r,h+2*r,r/100)
y = a*x^2+b*x+c
lines(x,y,lwd=3,col="blue")

abline(v=h,col="purple",lty=2)

# points(h,k,pch=19,col="red")
# text(h,k,"(h,k)",adj=c(1.2,0.5+sign(a)),col="red")


points(h,0,pch=19,col="black")
points(n,0,pch=19,col="black")

lines(c(h,n),c(0,0),lwd=3,col="red")
text(mean(c(h,n)),0,"w",adj=c(0.5,0.5-sign(a)),col="red",cex=2)

```
\

Using [the geometric significance of the quadratic formula](https://en.wikipedia.org/wiki/Quadratic_formula#Geometric_significance), calculate $w$, the distance between the axis of symmetry and one of the roots. *The tolerance is $\pm 0.01$.*


Solution
========

Look at the quadratic formula, which tells us if our quadratic function is in standard form, like $y=ax^2+bx+c$, then:

$$\text{roots of quadratic function} ~=~ \frac{-b}{2a}\pm\frac{\sqrt{b^2-4ac}}{2a}$$

We were given a quadratic function in standard form. Identify the parameters.

* The quadratic coefficient: $a=`r a`$
* The linear coefficient: $b=`r b`$
* The constant: $c=`r c`$

The [the geometric significance of the quadratic formula](https://en.wikipedia.org/wiki/Quadratic_formula#Geometric_significance) tells us that $h=\frac{-b}{2a}$ and the distance of the roots to the axis of symmetry is $w=\frac{\sqrt{b^2-4ac}}{|2a|}$. Use the formula to calculate $w$.

$$w~=~\frac{\sqrt{(`r b`)^2-4(`r a`)(`r c`)}}{|2(`r a`)|}$$

Simplify.

$$w~=~\frac{\sqrt{`r pn(c(b^2,-4*a*c),c(0,0))`}}{|`r 2*a`|}$$


Simplify.


$$w~=~\frac{\sqrt{`r b^2-4*a*c`}}{`r abs(2*a)`}$$

Use a calculator.

$$w~=~`r r`$$



Meta-information
============
extype: num
exsolution: `r r`
exname: quad_k_from_standard
extol: 0.01