```{r data generation, echo = FALSE, results = "hide"}
# S-IC.A.2: Decide if a specified model is consistent with results from a given data-generating process, e.g., using simulation.

while(T){
  n = 6 #sample(8:15,1)
  countwrds = c("one","two","three","four","five","six","seven","eight","nine","ten")
  cn = countwrds[n]
  d = 4 #sample(c(4,6,8,10,12,20),1)
  sig = sqrt((d^2-1)/12)
  ME = 1.96*sig*sqrt(n)
  EV = (d+1)/2*n
  B1 = round(EV-ME)
  B2 = round(EV+ME)
  if(n!=d && !(n==10 && d==6)){break}
}

```

Question
========

*S-IC.A.2: Decide if a specified model is consistent with results from a given data-generating process, e.g., using simulation.*

In [table-top role-playing games](https://en.wikipedia.org/wiki/Tabletop_role-playing_game), it is common to use [dice notation](https://en.wikipedia.org/wiki/Dice_notation). As an example, if a spell deals `r n`d`r d` damage, the player will roll `r cn` `r d`-sided dice (where each die follows a [discrete uniform distribution](https://en.wikipedia.org/wiki/Discrete_uniform_distribution) between 1 and `r d`) and add all the [pips](https://en.wikipedia.org/wiki/Pip_(counting)).

Please use a spreadsheet to simulate 1000 repetitions of `r n`d`r d`. From the simulation, determine an interval of typical totals (the boundaries of the middle 95%) and a margin of error (half the width of the interval). You might find [this guide](https://chadworley.github.io/a2/u01/p07_dice_sim.html) helpful.





```{r}
lowb1 = 20
hib1 = 1
for(i in 1:1000){
  x = sample(1:4,6*1000,T)
  x = matrix(x,ncol=6)
  tots = sort(apply(x,1,sum))
  b1 = tots[26]
  b2 = tots[975]
  if(b1<lowb1){lowb1=b1}
  if(b1>hib1){hib1=b1}
}

print(lowb1)
print(B1)
print(hib1)
```

Solution
========




Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: 
exname: basic_data_analysis