```{r data generation, echo = FALSE, results = "hide"}
# S-IC.A.2: Decide if a specified model is consistent with results from a given data-generating process, e.g., using simulation.

n = sample(6:12,1)
p = sample(seq(20,50,5),1)/100
t = sample(seq(0.5,5,0.5),1)

mutt = sample(c(10,15,20,25,30,45),1)
sigtt = round(runif(1,1,2),1)

et = n*(1-p)*t/2

mes = numeric()

for(i in 1:1000){
    x = (p<runif(n*1000))*t*runif(n*1000)
    x = matrix(x,ncol=n)
    sums = apply(x,1,sum)
    sums = sums+rnorm(1000,mutt,sigtt)
    ss = sort(sums)
    lo = ss[25]
    hi = ss[975]
    mid = (hi+lo)/2
    me = (hi-lo)/2
    mes = c(mes,me)
}
tol = ceiling((max(mes)-min(mes))/2*100)/100
ME = round((max(mes)+min(mes))/2,2)

```

Question
========

*S-IC.A.2: Decide if a specified model is consistent with results from a given data-generating process, e.g., using simulation.*

You wish to simulate how long your morning commute takes. You break the commute into two parts.

* Moving time
    * Approximately normal with $\mu=`r mutt`$ minutes and $\sigma=`r sigtt`$ minutes.
    * In a spreadsheet, this is simulated with ``=norminv(rand(),`r mutt`,`r sigtt`)``
* Waiting time at `r n` intersections.
    * Each intersection has a `r p` chance to be green. If the light is not green, you will wait up to `r t` minutes (following a uniform distribution).
    * In a spreadsheet, **each** intersection is simulated with ``=if(rand()<`r p`, 0, rand()*`r t`)``

Simulate 1000 repetitions. In each repetition, get the **total** time (moving and waiting). Find the 2.5th percentile and the 97.5th percentile to find the boundaries of the middle 95% of totals. Divide this interval's width by 2 to get the margin of error.

What is your simulated **margin of error**?

Solution
========

You should get a margin of error near `r ME` minutes. The tolerance should take anything from `r ME-tol` and `r ME+tol` minutes.

I've shown a histogram of my simulation below.

```{r,echo=F,fig.dim=c(8,8)}
myplot = hist(ss,xlab="time (minutes)",main="Stop-light sim, 1000 repetitions")
cnts = myplot$counts
ydraw = max(cnts)/2
lines(c(mid,mid,mid,hi,hi,hi),ydraw*c(0.95,1.05,1,1,1.05,0.95),col="red",lwd=3)
mex = mean(c(mid,hi))
text(mex,1.05*ydraw,round(me,3),col="red")
```
\


Meta-information
================
extype: num
exsolution: `r ME`
exname: stoplight_sim
extol: `r tol`