```{r,data,generation,echo=FALSE,results="hide"}
# S-ID.A: Summarize, represent, and interpret data on a single count or measurement variable. Use calculators, spreadsheets, and other technology as appropriate.

types = c("Bell","Uniform","Bimodal","Positive-skew","Negative-skew")

n = 200
beta1 = c(3,1,0.6,1.2,4)
beta2 = c(3,1,0.6,4,1.2)

bell = round(rbeta(n,beta1[1],beta2[1])*10,2)
uniform = round(rbeta(n,beta1[2],beta2[2])*10,2)
bimodal = round(sample(1:9,n,TRUE,c(0.3,0.1,0.05,0.04,0.02,0.04,0.05,0.1,0.3))+runif(n,-1,1),2)
right_skew = round(rbeta(n,beta1[4],beta2[4])*10,2)
left_skew = round(rbeta(n,beta1[5],beta2[5])*10,2)

data = data.frame(bell,uniform,bimodal,right_skew,left_skew)

ord = sample(1:5)
type = sample(1:5,1)

i = 1:n
x = data[,type]

ans1 = paste0((type==ord)*1,collapse="")
ans2 = paste0((1:5==type)*1,collapse="")

y = lapply(x, function(xx) sprintf("%5.2f",xx))
```


Question
========

*S-ID.A: Summarize, represent, and interpret data on a single count or measurement variable. Use calculators, spreadsheets, and other technology as appropriate.*

A sample of size $n=`r n`$ was taken from an unknown population. The sample is shown below:

`r paste0(y,collapse=",")`

Use those data to draw a histogram. 

**Identify the correct histogram below and describe the shape.** Note, the bucket size is 1.

```{r echo=F,fig.width=8,fig.height=5}
par(mfrow=c(2,3))
for(j in 1:5){
  par(mar=c(2,1,3,1))
  i = ord[j]
  hist(data[,i],axes=F,xlim=c(0,10),breaks=0:10,main=paste0("histogram ",j),col=rgb(0.9,0.7,0.7))
  box("figure")
}
```
\


* Which histogram is appropriate? \#\#ANSWER1\#\#
* Which shape description is appropriate?  \#\#ANSWER2\#\#


Answerlist
--------
* histogram 1
* histogram 2
* histogram 3
* histogram 4
* histogram 5
* Bell
* Uniform
* Bimodal
* Positive-skew
* Negative-skew


Solution
========

You should make a histogram using a spreadsheet. Copy data into spreadsheet. Highlight data. Click `Insert`. Click `Chart`. Choose Histogram.

* Under `Customize`, select `Histogram`. Set bucket size to 1.
* Under `Customize`, select `Horizontal axis`. Set min to 0.

The correct histogram is number `r (1:5)[type==ord]`.

The correct description is `r types[type]`.

* **References**
  * [Skewness](https://en.wikipedia.org/wiki/Skewness).
  * [Bimodal](https://en.wikipedia.org/wiki/Multimodal_distribution)
  * [Uniform](https://en.wikipedia.org/wiki/Continuous_uniform_distribution)
  * [Bell shaped](https://en.wikipedia.org/wiki/Bell-shaped_function)



Meta-information
================
extype: cloze
exclozetype: schoice|schoice
exsolution: `r ans1`|`r ans2`
exname: identify_histogram
extol: 0
exextra[numwidth]: 999.999
