```{r data generation, echo = FALSE, results = "hide"}
# S-ID.A: Summarize, represent, and interpret data on a single count or measurement variable. Use calculators, spreadsheets, and other technology as appropriate.


```

Question
========

*S-ID.A: Summarize, represent, and interpret data on a single count or measurement variable. Use calculators, spreadsheets, and other technology as appropriate.*

A spinner was made to model a [continuous triangular distribution](https://en.wikipedia.org/wiki/Triangular_distribution). It was spun 50 times; those locations are marked.

```{r,fig.dim=c(6,6),echo=F}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
t = seq(0,2*pi,pi/100)
polygon(sin(t),cos(t))

for(i in seq(a,b,bw)){
  p = cdf(i,a,b,c)
  ang = p*pi
  lines(c(0.92,1)*sin(ang),c(0.92,1)*cos(ang),lwd=2)
  lines(c(0.92,1)*sin(-ang),c(0.92,1)*cos(-ang),lwd=2)
  if(abs(ang)>pi/20 && abs(ang)<19*pi/20){
    text(0.87*sin(ang),0.87*cos(ang),i,cex=0.7)
    text(0.87*sin(-ang),0.87*cos(-ang),i,cex=0.7)
  }
  if(ang==0){
    text(0.87*sin(ang),0.87*cos(ang),i,cex=0.8,col="red")
  }
  if(ang==pi){
    text(0.87*sin(ang),0.87*cos(ang),i,cex=0.8,col="blue")
  }
}

for(i in a:b){
  p = cdf(i,a,b,c)
  ang = p*pi
  lines(c(0.95,1)*sin(ang),c(0.95,1)*cos(ang))
  lines(c(0.95,1)*sin(-ang),c(0.95,1)*cos(-ang))
}

for(i in seq(a,b,0.1)){
  p = cdf(i,a,b,c)
  ang = p*pi
  lines(c(0.98,1)*sin(ang),c(0.98,1)*cos(ang),lwd=0.5)
  lines(c(0.98,1)*sin(-ang),c(0.98,1)*cos(-ang),lwd=0.5)
}

i = 1
for(u in uu){
  ang = sample(c(-1,1),1)*pi*u
  points(sin(ang)*1.02,cos(ang)*1.02,pch=19,cex=0.5,col=cols[i])
  i = i+1
}

polygon(sin(t)*0.05,cos(t)*0.05,border="black",col="red")
arrows(-0.7,-0.2,0.7,0.2,lwd=8,length=0.1,angle=25,col="black")
arrows(-0.7,-0.2,0.7,0.2,lwd=6,length=0.1,angle=25,col="red")
polygon(sin(t)*0.01,cos(t)*0.01,border="black",col="red")
```
\

The name "triangular distribution" comes from the probability density curve.


```{r,echo=F,fig.dim=c(6,4)}
h = 1/wid*2
plot(c(a,c,b),c(0,1/wid*2,0),"l",xlab="spin result",ylab="probability density",lwd=2,main="Triangular Density")
for(x in seq(a,b,length.out=21)){
  abline(v=x,col="grey")
}
for(y in seq(0,h,length.out=11)){
  abline(h=y,col="grey")
}
polygon(c(a,c,b),c(0,1/wid*2,0),border=F,col=rgb(0,0,0,0.3))
lines(c(a,c,b),c(0,1/wid*2,0),lwd=3)

i = 1
for(x in xx){
  points(x,0,pch=19,cex=0.5,col=cols[i])
  i = i+1
}

```
\

Notice that because the spinner is continuous, it generates data like `r qua(runif(1,0.1,0.9))` and `r qua(runif(1,0.1,0.9))`. Of course, a human would probably round to the nearest tenth or so.

### Actual question

The 50 spins were used to generate a histogram.

```{r,echo=F}
hist(xx,breaks=seq(a,b,bw),labels=T,ylim=c(0,max(cnts)*1.1),main="Histogram of 50 spins",xlab="spin result",xaxt = "n",xlim=c(a-1,b+1))

bcs = rep(0,nb)
for(i in 1:length(xx)){
  x = xx[i]
  col = cols[i]
  j = ceiling((x-a)/bw)
  bcs[j] = bcs[j]+1
  points((j-0.5)*bw+a,bcs[j]-0.5,pch=19,cex=0.5,col=col)
  lines(c((j-1)*bw+a,j*bw+a),c(bcs[j],bcs[j]),lwd=0.5,col=rgb(0,0,0,0.2))
}

axis(1,at=seq(a,b,bw))
```
\

* How many spins were less than `r bp1`?
  * $\#(x<`r bp1`) =$ ##ANSWER1##
* What proportion of spins were less than `r bp1`?
  * $\mathrm{proportion}(x<`r bp1`) =$ ##ANSWER2##
* How many spins were more than `r bp2`?
  * $\#(x>`r bp2`) =$ ##ANSWER3##
* What proportion of spins were more than `r bp2`?
  * $\mathrm{proportion}(x>`r bp2`) =$ ##ANSWER4##
* How many spins were between `r bp3` and `r bp4`?
  * $\#(`r bp3`<x<`r bp4`) =$ ##ANSWER5##
* What proportion of spins were between `r bp3` and `r bp4`?
  * $\mathrm{proportion}(`r bp3`<x<`r bp4`) =$ ##ANSWER6##

Answerlist
--------

`r c1al`
`r p1al`
`r c2al`
`r p2al`
`r c3al`
`r p3al`


Solution
========

* $\#(x<`r bp1`) =$ `r c1`
* $\mathrm{proportion}(x<`r bp1`) = \frac{`r c1`}{50} =$ `r c1/50`
* $\#(x>`r bp2`) =$ `r c2`
* $\mathrm{proportion}(x>`r bp2`) = \frac{`r c2`}{50} =$ `r c2/50`
* $\#(`r bp3`<x<`r bp4`) =$ `r c3`
* $\mathrm{proportion}(`r bp3`<x<`r bp4`) = \frac{`r c3`}{50} =$ `r c3/50`

You might find the following visualizations helpful.

```{r,echo=F}
p1 <- hist(xx,breaks=seq(a,b,bw),plot=F)                    
p2 <- hist(xx[xx<bp1],breaks=seq(a,b,bw),plot=F)
g = max(cnts)*0.05
plot(p1, col=rgb(0,0,0,1/8), xlim=c(a-1,b+1),ylim=c(0,max(cnts)*1.1),main=paste0("Spins less than ",bp1," are highlighted"),xlab="spin result",xaxt = "n")
plot(p2, col=rgb(1,0,0,1/2), add=T)
cnts1 = numeric()
for(i in 1:length(cnts)){
  x = bw*(i-0.5)+a
  if(x<bp1){
    text(x,cnts[i]+g,cnts[i],cex=1.1,col="red")
    cnts1 = c(cnts1,cnts[i])
  } else {
    text(x,cnts[i]+g,cnts[i],cex=0.9,col="grey")
  }
}
axis(1,at=seq(a,b,bw))
```
\

$$`r paste0(cnts1,collapse="+")`=`r c1`$$

```{r,echo=F}
p1 <- hist(xx,breaks=seq(a,b,bw),plot=F)                    
p2 <- hist(xx[xx>bp2],breaks=seq(a,b,bw),plot=F)
g = max(cnts)*0.05
plot(p1, col=rgb(0,0,0,1/8), xlim=c(a-1,b+1),ylim=c(0,max(cnts)*1.1),main=paste0("Spins more than ",bp2," are highlighted"),xlab="spin result",xaxt = "n")
plot(p2, col=rgb(1,0,0,1/2), add=T)
cnts2 = numeric()
for(i in 1:length(cnts)){
  x = bw*(i-0.5)+a
  if(x>bp2){
    text(x,cnts[i]+g,cnts[i],cex=1.1,col="red")
    cnts2 = c(cnts2,cnts[i])
  } else {
    text(x,cnts[i]+g,cnts[i],cex=0.9,col="grey")
  }
}
axis(1,at=seq(a,b,bw))
```
\

$$`r paste0(cnts2,collapse="+")`=`r c2`$$

```{r,echo=F}
p1 <- hist(xx,breaks=seq(a,b,bw),plot=F)                    
p2 <- hist(xx[abs(xx-mean(bs[3:4]))<(diff(bs[3:4])/2)],breaks=seq(a,b,bw),plot=F)
g = max(cnts)*0.05
plot(p1, col=rgb(0,0,0,1/8), xlim=c(a-1,b+1),ylim=c(0,max(cnts)*1.1),main=paste0("Spins between ",bp3," and ",bp4," are highlighted"),xlab="spin result",xaxt = "n")
plot(p2, col=rgb(1,0,0,1/2), add=T)
cnts3 = numeric()
for(i in 1:length(cnts)){
  x = bw*(i-0.5)+a
  if(bp3<x && x<bp4){
    text(x,cnts[i]+g,cnts[i],cex=1.1,col="red")
    cnts3 = c(cnts3,cnts[i])
  } else {
    text(x,cnts[i]+g,cnts[i],cex=0.9,col="grey")
  }
}
axis(1,at=seq(a,b,bw))
```
\

$$`r paste0(cnts3,collapse="+")`=`r c3`$$



Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r c1sol`|`r p1sol`|`r c2sol`|`r p2sol`|`r c3sol`|`r p3sol`
exname: read_hist