```{r,data,generation,echo=FALSE,results="hide"}
types = c("Bell","Uniform","Bimodal","Positive-skew","Negative-skew")

n = 2000
beta1 = c(3,1,0.5,0.7,1.4)
beta2 = c(3,1,0.5,1.4,0.7)

bell = rbeta(n,beta1[1],beta2[1])
uniform = rbeta(n,beta1[2],beta2[2])
bimodal = rbeta(n,beta1[3],beta2[3])
right_skew = rbeta(n,beta1[4],beta2[4])
left_skew = rbeta(n,beta1[5],beta2[5])

data = data.frame(bell,uniform,bimodal,right_skew,left_skew)

ord = sample(1:5)
ord2 = sample(1:5)

sol1 = paste0(1*(ord==ord2[1]),collapse="")
sol2 = paste0(1*(ord==ord2[2]),collapse="")
sol3 = paste0(1*(ord==ord2[3]),collapse="")
sol4 = paste0(1*(ord==ord2[4]),collapse="")
sol5 = paste0(1*(ord==ord2[5]),collapse="")

al = paste0("* distribution ",1:5,collapse="\n")

```


Question
========

Match the five histograms with their appropriate description.

```{r echo=F,fig.width=8,fig.height=5}
par(mfrow=c(2,3))
for(j in 1:5){
  par(mar=c(2,1,3,1))
  i = ord[j]
  hist(data[,i],axes=F,xlim=c(0,1),main=paste0("distribution ",j),col=rgb(0.9,0.7,0.7))
  box("figure")
}
```
\


* `r types[ord2[1]]`: ##ANSWER1##
* `r types[ord2[2]]`: ##ANSWER2##
* `r types[ord2[3]]`: ##ANSWER3##
* `r types[ord2[4]]`: ##ANSWER4##
* `r types[ord2[5]]`: ##ANSWER5##

Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`



Solution
========

This is definitional.


* `r types[ord2[1]]`: distribution `r which(ord==ord2[1])`
* `r types[ord2[2]]`: distribution `r which(ord==ord2[2])`
* `r types[ord2[3]]`: distribution `r which(ord==ord2[3])`
* `r types[ord2[4]]`: distribution `r which(ord==ord2[4])`
* `r types[ord2[5]]`: distribution `r which(ord==ord2[5])`


I also will say "left-skewed" for negatively skewed and "right-skewed" for positively skewed.


Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`
exname: identify_shapes