```{r data generation, echo = FALSE, results = "hide"}
# S-IC.A.2: Decide if a specified model is consistent with results from a given data-generating process, e.g., using simulation.

prop_scens <- rbind(
  c("students who pass a standardized test", "educational testing service", 0.75, "students", 
    "a student who passes the standardized test", "a student who fails the standardized test"),
  c("teachers who incorporate technology in their lessons", "education research group", 0.65, "teachers", 
    "a teacher who uses technology in the classroom", "a teacher who avoids technology"),
  c("dogs that are trained as service animals", "animal assistance organization", 0.80, "dogs", 
    "a dog that is a service animal", "a dog that is not a service animal"),
  c("cats that prefer wet food over dry food", "pet food survey", 0.70, "cats", 
    "a cat that prefers wet food", "a cat that prefers dry food"),
  c("drivers who use seat belts", "traffic safety organization", 0.90, "drivers", 
    "a driver who always uses a seat belt", "a driver who never uses a seat belt"),
  c("people who own at least one pet", "pet association", 0.60, "people", 
    "a person who owns a pet", "a person who does not own a pet"),
  c("hikers who prefer mountain trails", "outdoor recreation association", 0.55, "hikers", 
    "a hiker who prefers mountain trails", "a hiker who prefers flat trails"),
  c("people who visit national parks annually", "national parks service", 0.45, "people", 
    "a person who visits national parks annually", "a person who never visits national parks"),
  c("homeowners who have a garden", "gardening club", 0.40, "homeowners", 
    "a homeowner who has a garden", "a homeowner who does not have a garden"),
  c("cats that enjoy catnip", "veterinary research", 0.75, "cats", 
    "a cat that enjoys catnip", "a cat that does not enjoy catnip"),
  c("students who participate in science fairs", "educational committee", 0.65, "students", 
    "a student who participates in science fairs", "a student who does not participate"),
  c("dogs that are adopted from shelters", "animal rescue organizations", 0.45, "dogs", 
    "a dog that is adopted from a shelter", "a dog that is not adopted from a shelter"),
  c("people who believe in animal rights", "animal advocacy group", 0.70, "people", 
    "a person who believes in animal rights", "a person who does not believe in animal rights"),
  c("teachers who provide after-school tutoring", "school district", 0.50, "teachers", 
    "a teacher who provides after-school tutoring", "a teacher who does not provide tutoring"),
  c("volunteers who work at animal shelters", "community organization", 0.55, "volunteers", 
    "a volunteer who works at an animal shelter", "a volunteer who does not work at an animal shelter"),
  c("drivers who prefer electric vehicles", "transportation study", 0.25, "drivers", 
    "a driver who prefers electric vehicles", "a driver who prefers gas vehicles"),
  c("people who regularly attend yoga classes", "fitness research group", 0.60, "people", 
    "a person who attends yoga classes", "a person who does not attend yoga classes"),
  c("frogs that thrive in urban environments", "wildlife preservation society", 0.30, "frogs", 
    "a frog that thrives in urban environments", "a frog that does not thrive in urban environments"),
  c("people who enjoy pet therapy", "mental health professionals", 0.65, "people", 
    "a person who enjoys pet therapy", "a person who does not enjoy pet therapy"),
  c("students who choose online learning", "educational researchers", 0.40, "students", 
    "a student who chooses online learning", "a student who prefers in-person learning"),
  c("animals in zoos that are bred successfully", "zoological association", 0.80, "animals in zoos", 
    "an animal in a zoo that is bred successfully", "an animal in a zoo that is not bred successfully"),
  c("people who own reptiles as pets", "reptile enthusiasts club", 0.20, "people", 
    "a person who owns a reptile as a pet", "a person who does not own a reptile"),
  c("students who participate in sports teams", "school athletics department", 0.75, "students", 
    "a student who participates in sports teams", "a student who does not participate in sports"),
  c("people who cook healthy meals at home", "nutrition association", 0.70, "people", 
    "a person who cooks healthy meals", "a person who does not cook healthy meals"),
  c("cats that are indoor only", "pet owner survey", 0.65, "cats", 
    "a cat that is indoor only", "a cat that is allowed outdoors"),
  c("drivers using rideshare apps", "transportation research firm", 0.55, "drivers", 
    "a driver who uses rideshare apps", "a driver who does not use rideshare apps"),
  c("dogs that enjoy swimming", "pet behavior study", 0.60, "dogs", 
    "a dog that enjoys swimming", "a dog that does not enjoy swimming"),
  c("hikers who prefer solo hikes", "hiking club", 0.50, "hikers", 
    "a hiker who prefers solo hikes", "a hiker who prefers group hikes"),
  c("homeowners who have energy-efficient appliances", "energy star program", 0.75, "homeowners", 
    "a homeowner with energy-efficient appliances", "a homeowner without energy-efficient appliances"),
  c("animals that benefit from wildlife corridors", "environmental protection agency", 0.65, "animals", 
    "an animal that benefits from wildlife corridors", "an animal that does not benefit from wildlife corridors"),
  c("people who follow a gluten-free diet", "health survey", 0.30, "people", 
    "a person who follows a gluten-free diet", "a person who does not follow a gluten-free diet"),
  c("cats that are shy around strangers", "animal behavior study", 0.55, "cats", 
    "a cat that is shy around strangers", "a cat that is outgoing around strangers"),
  c("students who study abroad", "university administration", 0.40, "students", 
    "a student who studies abroad", "a student who does not study abroad"),
  c("people who regularly donate to wildlife charities", "charity organization", 0.60, "people", 
    "a person who regularly donates to wildlife charities", "a person who does not donate to wildlife charities"),
  c("drivers who use public transportation", "urban planning department", 0.45, "drivers", 
    "a driver who uses public transportation", "a driver who does not use public transportation"),
  c("dogs that are trained for competitive sports", "dog trainers association", 0.50, "dogs", 
    "a dog that is trained for competitive sports", "a dog that is not trained for competitive sports"),
  c("frogs that are part of conservation programs", "frog conservation project", 0.35, "frogs", 
    "a frog in a conservation program", "a frog not in a conservation program"),
  c("people who understand the importance of biodiversity", "ecological organization", 0.80, "people", 
    "a person who understands the importance of biodiversity", "a person who does not understand it"),
  c("students who are enrolled in art classes", "art school survey", 0.65, "students", 
    "a student enrolled in art classes", "a student not enrolled in art classes"),
  c("animals in sanctuaries that receive proper care", "animal sanctuary organization", 0.90, "animals in sanctuaries", 
    "an animal in a sanctuary that receives proper care", "an animal in a sanctuary that does not receive proper care"),
  c("homeowners who engage in community cleanup days", "local council", 0.55, "homeowners", 
    "a homeowner who engages in community cleanup", "a homeowner who does not engage in cleanup"),
  c("people who adopt rescue animals", "animal welfare organization", 0.75, "people", 
    "a person who adopts a rescue animal", "a person who does not adopt rescue animals"),
  c("drivers who participate in carpooling", "environmental group", 0.60, "drivers", 
    "a driver who participates in carpooling", "a driver who does not carpool"),
  c("cats that interact well with other pets", "pet behavior research", 0.70, "cats", 
    "a cat that interacts well with other pets", "a cat that does not interact well"),
  c("students who are members of student government", "educational association", 0.40, "students", 
    "a student who is a member of student government", "a student who is not a member"),
  c("drivers who participate in eco-driving courses", "transportation organization", 0.65, "drivers", 
    "a driver who participates in eco-driving", "a driver who does not participate"),
  c("people who are aware of endangered species", "wildlife awareness group", 0.70, "people", 
    "a person who is aware of endangered species", "a person who is unaware of endangered species"),
  c("frogs that are part of educational programs", "environmental education group", 0.50, "frogs", 
    "a frog in an educational program", "a frog not in an educational program"),
  c("animals in zoos that receive proper care", "zoological society", 0.90, "animals in zoos", 
    "an animal in a zoo that receives proper care", "an animal in a zoo that does not receive proper care"),
  c("homeowners who utilize rainwater harvesting", "sustainability group", 0.30, "homeowners", 
    "a homeowner who utilizes rainwater harvesting", "a homeowner who does not utilize it"),
  c("people who grow their own herbs", "culinary gardening group", 0.75, "people", 
    "a person who grows their own herbs", "a person who does not grow their own herbs")
)

prop_scens <- data.frame(prop_scens, stringsAsFactors = FALSE)
names(prop_scens) <- c("scenario", "authority", "proportion", "subject", "affirmative_example", "negative_example")

while(T){
  n = sample(c(10,12,14,15,16,18,20,22,24),1)
  i = sample(1:dim(prop_scens)[1],1)
  scn = prop_scens[i,]
  thing = scn[[1]]
  auth = scn[[2]]
  p = max(min(as.numeric(scn[[3]])+0.01*sample(-10:10,1),0.9),0.1)
  subj = scn[[4]]
  aff = scn[[5]]
  neg = scn[[6]]
  ev = p*n
  me = 2*sqrt(p*(1-p))*sqrt(n)
  lo = floor(ev-me)
  hi = ceiling(ev+me)
  if((hi-lo)>4 && (lo>2 || n-hi>2)){break}
}

N = 10000
xxx = sort(rbinom(N,n,p))
lb = xxx[round(N*0.025+1)]
ub = xxx[round(N*0.975)]

while(T){
  lbopts = lb-sample(0:3,1)*3+(0:3)*3
  if(lbopts[1]>=0){break}
}
while(T){
  ubopts = ub-sample(0:3,1)*3+(0:3)*3
  if(ubopts[4]<=n){break}
}

lbal = paste0("* ",lbopts,collapse="\n")
ubal = paste0("* ",ubopts,collapse="\n")
lbsol = paste0(1*(lbopts==lb),collapse="")
ubsol = paste0(1*(ubopts==ub),collapse="")

me = round((ub-lb)/2,1)
while(T){
  meopts = me-sample(0:3,1)*3+(0:3)*3
  if(meopts[1]>=0){break}
}
meal = paste0("* ",meopts,collapse="\n")
mesol = paste0(1*(meopts==me),collapse="")

isin = sample(c(T,F),1)

if(isin){
  ns = sample(c(lb+2,lb+3,ub-3,ub-2),1)
  sigsol = "01"
  sigwrd = "did not find significant difference"
  w2 = ""
} else {
  ons = c(lb-2:5,ub+2:5)
  ons = ons[ons>0]
  ons = ons[ons<n]
  ns = sample(ons,1)
  sigsol = "10"
  sigwrd = "found significant difference"
  w2 = "NOT"
}

data = sample(c(rep(1,ns),rep(0,n-ns)))

```

Question
========

*S-IC.A.2: Decide if a specified model is consistent with results from a given data-generating process, e.g., using simulation.*

You have heard from a good authority (`r auth`) that a few years ago a survey showed that in Berkshire County the proportion of `r thing` is $p=`r p`$. You think that maybe the population proportion has changed with the times. You decide to test your hunch by getting a [simple random sample](https://en.wikipedia.org/wiki/Simple_random_sample) of the `r subj` in Berkshire County.

But, you don't just start gathering data. You need to have a clear test in mind before gathering any data; otherwise you might change the test in response to the data (see [post hoc analysis](https://en.wikipedia.org/wiki/Post_hoc_analysis)). 

## Decide on test

First, you decide on a sample size. You carefully balance your expectations of time, cost, and enthusiasm to decide on a sample size of $n=`r n`$.

For your test, you decide on a [significance level](https://en.wikipedia.org/wiki/Statistical_significance) of 5%. You will use a simulation (with $p=`r p`$) to find an interval of the middle 95% of outcomes. Then,

* If the observed result is **outside** the interval, you will conclude the current proportion is not equal $`r p`$.
  * You will say that you "**found a significant difference**" between the old proportion and the new proportion.
* Otherwise, if the observed result is **inside** the interval, you will conclude that there remain two possibilities:
  * The current proportion still equals `r p`.
  * You need more data to detect the difference.
  * In this case, you can just say you "**did not find a significant difference**". 

### Simulation

With the sample size $n=`r n`$ in mind you are able to run a (repeated) simulation while assuming $p=`r p`$. To do that in a [spreadsheet](https://sheets.new), each cell will use ``=IF(RAND()<`r p`,1,0)``, which uses `1` for affirmative and `0` for negative.

* The simulation shows `1` for `r aff`
* The simulation shows `0` for `r neg`
* To simulate checking `r n` `r subj`, use ``=IF(RAND()<`r p`,1,0)`` in all cells in range A1:`r LETTERS[n]`1.
* To count how many of the `r n` `r subj` are `r aff`, in cell `r LETTERS[n+2]`1, use ``=sum(A1:`r LETTERS[n]`1)``
* Repeat the simulation in rows 1 to 1000. Highlight A1:`r LETTERS[n]`1, `ctrl+shift+down`, and `ctrl+enter`.
* To get result of each row, highlight `r LETTERS[n+2]`1, `ctrl+shift+down`, and `ctrl+enter`.
* Freeze the simulation with `ctrl+a`, `ctrl+c`, and `ctrl+shift+v`.
* To sort, highlight column `r LETTERS[n+2]`. Click `Data`, ``Sort Sheet by column `r LETTERS[n+2]```.
* Because you have 1000 repetitions, and $0.025\cdot1000=25$, drop the lowest 25 and the highest 25 results. In other words, get the numbers in `r LETTERS[n+2]`26 and `r LETTERS[n+2]`975. Those two numbers indicate the interval of typical results.

Based on your simulation, what are the most reasonable boundaries of the interval of typical (middle 95%) results?

* Lower boundary = ##ANSWER1##
* Upper boundary = ##ANSWER2##

Let's also get a margin of error by halving the difference of those boundaries.

* Margin of error = ##ANSWER3##

## Collect data

Phew! You've set your study design and you've simulated a model. Now you go collect data to see if it behaves like the model. Here are your raw data:

```{r,echo=F,results='asis'}
cat(paste0(data,collapse=", "))
```

What do you conclude?

* Conclusion = ##ANSWER4##


Answerlist
--------

`r lbal`
`r ubal`
`r meal`
* Found significant difference!
* Did not find significant difference.


Solution
========

Remember, your simulation may have given slightly different numbers. Pick the closest.

* Lower boundary of middle 95% of simulated results = `r lb`
* Upper boundary of middle 95% of simulated results = `r ub`
* Margin of error $= \frac{`r ub`-`r lb`}{2} = `r me`$
* Because your survey had `r ns` affirmatives, and `r ns` is `r w2` between `r lb` and `r ub`, conclusion = `r sigwrd`

Here is a visualization of a simulation like yours. The red dots represent those that are considered unusual enough to be excluded from the interval of typical results. Remember, we keep the middle 95% and get rid of the lowest 2.5% and the highest 2.5%. This is how we do a two-tail significance test with a significance level of 5% (and in this class we will stick to these percentages).

```{r,fig.dim=c(6,10),echo=F}
while(T){
  tots = sort(rbinom(1000,n,p))
  b1 = tots[26]
  b2 = tots[975]
  if(b1==lb && b2==ub){break}
}
stripchart(tots,method="stack",offset=0.7,pch=19,cex=0.2,xlim=c(min(tots),max(tots)),ylim=c(0.9,3),col="black")
stripchart(tots[1:25],method="stack",offset=0.7,pch=19,cex=0.2,ylim=c(1,1.4),col="red",add=T)
stripchart(tots[976:1000],method="stack",offset=0.7,pch=19,cex=0.2,ylim=c(1,1.4),col="red",add=T)
text(tots[26],0.92,tots[26],col="blue")
lines(c(tots[26],tots[26]),c(0.94,1),col="blue")
text(tots[975],0.92,tots[975],col="blue")
lines(c(tots[975],tots[975]),c(0.94,1),col="blue")
x1 = mean(c(b1,b2))

lines(c(x1,x1,x1,b2,b2,b2),c(-0.01,0.01,0,0,0.01,-0.01)+0.98,lwd=3,col="purple")
# text(mean(c(x1,b2)),0.96,"ME",col="purple")
text(mean(c(x1,b2)),0.92,(b2-b1)/2,col="purple")
```
\

It might also help to see all the results of my simulation.

```{r,echo=F,fig.dim=c(8,8)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,21),ylim=c(0,51))
for(j in 1:50){
  for(i in 1:20){
    k = (j-1)*20+i
    text(i,51-j,tots[k],cex=0.5,col="black")
    if(k<26 || k>975){
      lines(c(i-0.3,i+0.3),51-c(j+0.5,j-0.5),col="red")
    }
    if(k==26 || k==975){
      polygon(c(i-0.3,i-0.3,i+0.3,i+0.3),51-c(j+0.5,j-0.5,j-0.5,j+0.5),border="blue")
    }
  }
}
```
\



Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r lbsol`|`r ubsol`|`r mesol`|`r sigsol`
exname: prop_test_sim