```{r data generation, echo = FALSE, results = "hide"}
n = sample(5:7,1)
tens = sample(3:8,1)
while(T){
  ones = sample(0:19,n,T)
  x = sort(tens*10+ones)
  mu = mean(x)
  devs = round(x-mu,1)
  sqd = round((x-mu)^2,2)
  v = mean(sqd)
  sig = sqrt(v)
  if(100*sig==round(100*sig) && sig>0 && round(10*mu)==10*mu && length(unique(sqd))>1){break}
}
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

A lottery machine (population) will produce random numbers with replacement. It has `r n` balls, with the following numbers:

```{r tab_data, echo=FALSE, results="asis"}
X = c(paste(x))
ct = data.frame(X)
colnames(ct) = c("$x_i$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```
\


Please calculate the population standard deviation. To do this, first calculate the population mean.

$$\mu = \frac{\sum\limits_{i=1}^n x_i}{n}$$

Calculate the population variance by averaging the squared deviations.
$$\text{variance} = \sigma^2 = \frac{\sum\limits_{i=1}^n (x_i-\mu)^2}{n} $$

Determine the population standard deviation by taking the square root of the population variance.
$$\sigma = \sqrt{\sigma^2} $$


Solution
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

Find the mean.
$$\mu = \frac{`r paste0(x,collapse="+")`}{`r n`} = `r mu` $$

Find the variance.

```{r, echo=FALSE}
s = paste0("(",x,"-",mu,")^2")
s = paste0("(",devs,")^2",collapse="+")
s2 = paste0("(",x,"-",mu,")^2")
s2 = paste0(s2,collapse="+")
```

$$\sigma^2 = \frac{`r s2`}{`r n`} $$

$$\sigma^2 = \frac{`r s`}{`r n`}$$

$$\sigma^2 = \frac{`r paste0(sqd,collapse="+")`}{`r n`}$$

$$\sigma^2 = `r v`$$
Calculate the standard deviation by taking the square root of the variance.
$$\sigma = \sqrt{`r v`} = `r sig` $$


You might find it helpful to organize your work in a table.

```{r tab1, echo=FALSE, results="asis"}
X = c(paste(x),"","$\\sum\\limits_{i=1}^{n} x_i$",paste(sum(x)),"","$\\mu$",paste(mean(x)),"","","")
deviations = c(paste(devs),"","","","","","","","","")
squared_devs = c(paste(sqd),"","$\\sum\\limits_{i=1}^{n} (x_i-\\mu)^2$",paste(sum(sqd)),"","$\\sigma^2$",paste(mean(sqd)),"","$\\sigma$",paste(sig))
ct = data.frame(X,deviations,squared_devs)
colnames(ct) = c("$x_i$","$(x_i-\\mu)$","$(x_i-\\mu)^2$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```
\

Meta-information
================
extype: num
exsolution: `r sig`
exname: sd_pop
extol: 0