```{r data generation, echo = FALSE, results = "hide"}
n = sample(4:6,1)
tens = sample(3:8,1)
while(T){
  ones = sample(0:19,n,T)
  x = tens*10+ones
  xbar = mean(x)
  devs = (x-xbar)
  sqd = (x-xbar)^2
  v = sum(sqd)/(n-1)
  sig = sqrt(v)
  if(10*sig==round(10*sig) && sig>0 && round(xbar)==xbar && length(unique(sqd))>1){break}
}
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

A small sample was gathered. The measurements are below.

```{r tab_data, echo=FALSE, results="asis"}
X = c(paste(x))
ct = data.frame(X)
colnames(ct) = c("$x_i$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```


Please calculate the sample standard deviation. To do this, first calculate the sample mean.

$$\bar{x} = \frac{\sum\limits_{i=1}^n x_i}{n}$$

Calculate the sample variance by dividing the sum of the squared deviations by $n-1$. This subtlety (of replacing the denominator with $n-1$ instead of $n$) is called [Bessel's correction](https://en.wikipedia.org/wiki/Bessel%27s_correction){target="_blank"}. This provides an unbiased estimation of the population's variance when the population's mean is also unknown.
$$\text{sample variance (with Bessel correction)} = s^2 = \frac{\sum\limits_{i=1}^n (x_i-\bar{x})^2}{n-1} $$

Determine the sample standard deviation by taking the square root of the sample variance.
$$s = \sqrt{s^2} $$


Solution
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

Find the sample mean.
$$\bar{x} = \frac{`r paste0(x,collapse="+")`}{`r n`} = `r xbar` $$

Find the variance.

```{r, echo=FALSE}
s = paste0("(",x,"-",xbar,")^2")
s = paste0("(",devs,")^2",collapse="+")
s2 = paste0("(",x,"-",xbar,")^2")
s2 = paste0(s2,collapse="+")
```

$$s^2 = \frac{`r s2`}{`r n-1`} $$

$$s^2 = \frac{`r s`}{`r n-1`}$$

$$s^2 = \frac{`r paste0(sqd,collapse="+")`}{`r n-1`}$$

$$s^2 = `r v` $$
Calculate the standard deviation.
$$s = \sqrt{`r v`} = `r sig` $$


You might find it helpful to organize your work in a table.

```{r tab1, echo=FALSE, results="asis"}
X = c(paste(x),"","$n$",paste(sum(n)),"","$\\sum\\limits_{i=1}^{n} x_i$",paste(sum(x)),"","$\\bar{x}$",paste(mean(x)))
deviations = c(paste(x-sig),"","","","","","","","","")
squared_devs = c(paste(sqd),"","$\\sum\\limits_{i=1}^{n} (x_i-\\bar{x})^2$",paste(sum(sqd)),"","$s^2=\\frac{1}{n-1}\\sum\\limits_{i=1}^{n} (x_i-\\bar{x})^2$",paste(sum(sqd)/(n-1)),"","$s$",paste(sig))
ct = data.frame(X,deviations,squared_devs)
colnames(ct) = c("$x_i$","$(x_i-\\bar{x})$","$(x_i-\\bar{x})^2$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```
\

Meta-information
================
extype: num
exsolution: `r sig`
exname: sig_pop_int
extol: 0
