---
title: "Introduction to Google Sheets"
subtitle: "*S-ID.A: Summarize, represent, and interpret data on a single count or measurement variable. Use calculators, spreadsheets, and other technology as appropriate.*"
output:
  revealjs::revealjs_presentation:
    theme: simple
    transition: slide
    center: true
    slideNumber: true
---

## Welcome to Google Sheets!


* Today, we'll explore the power of Google Sheets for analyzing data.
* We'll learn how to use cell references, basic functions, and explore data insights.

## Cell References

* Each cell in a spreadsheet has a unique address: **[Column Letter][Row Number]**
* **Example:** Cell A1 is at the intersection of column A and row 1.
* To refer to a cell's value, simply type its address: `=A1`

## Cell-reference Example

* **Challenge:** Try entering `=A1+B2` in an empty cell to see the result!

```{r,echo=F}
xxx = sample(10:40,12)
xxx = matrix(xxx,ncol=3)
data = data.frame(xxx)
```

```{r fig.width=5,fig.height=5,echo=F}
draw_ss = function(df,widths=rep(1,length(df[1,])+1)){
  xline = c(0,cumsum(widths)/sum(widths))
  nrow = length(df[,1])
  ncol = length(df[1,])
  xtex = (xline[2:(ncol+3)]+xline[1:(ncol+2)])/2
  par(mar=c(0,0,0,0))
  plot(0,0,type="n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
  hi = 1:((nrow+2)*2+1)
  vi = 1:((ncol+1)*2+1)
  hpos = seq(1,0,length.out=(nrow+2)*2+1)
  vpos = seq(0,1,length.out=(ncol+1)*2+1)
  hlin = hpos[hi%%2==1]
  ytex = hpos[hi%%2==0]
  vlin = vpos[vi%%2==1]
  #xtex = vpos[vi%%2==0]
  abline(h=hlin)
  abline(h=hlin[2],lwd=3)
  abline(v=xline)
  abline(v=xline[2],lwd=3)
  for(i in 2:(ncol+2)){
    text(xtex[i],ytex[1],LETTERS[i-1],col=rgb(0.5,0.5,0.5))
    #text(xtex[i],ytex[2],colnames(df)[i-1])
  }    
  for(i in 2:(nrow+2)){
    text(xtex[1],ytex[i],i-1,col=rgb(0.5,0.5,0.5))
  }
  for(i in 1:nrow){
    for(j in 1:ncol){
      text(xtex[j+1],ytex[i+1],df[i,j])
    }
  }
}
draw_ss(data)
```
\


## COUNT Function

* **Syntax:** `=COUNT(range)`
* **Purpose:**  Counts the number of cells in a range that contain numbers.
* **Example:** `=COUNT(A1:A10)` counts the numbers in cells A1 through A10.

## COUNT example

What would be the result of putting `=COUNT(A1:B3)` in an empty cell?

```{r fig.width=5,fig.height=5,echo=F}
draw_ss(data)
```
\

## SUM Function

* **Syntax:** `=SUM(range)`
* **Purpose:** Adds the values of all cells in a range.
* **Example:** `=SUM(B2:B10)` sums the values in cells B2 through B10.

## SUM example

What would be the result of putting `=SUM(A1:B2)` in an empty cell?

```{r fig.width=5,fig.height=5,echo=F}
draw_ss(data)
```
\

## AVERAGE Function

* **Syntax:** `=AVERAGE(range)`
* **Purpose:** Calculates the average (mean) of values in a range.
* **Example:** `=AVERAGE(C1:C5)` calculates the average of values in cells C1 through C5.

## MEDIAN Function

* **Syntax:** `=MEDIAN(range)`
* **Purpose:** Finds the middle value in a sorted range.
* **Example:** `=MEDIAN(D1:D8)` finds the median value in cells D1 through D8.

## COUNTIF Function

* **Syntax:** `=COUNTIF(range, criteria)`
* **Purpose:** Counts the number of cells in a range that meet a specific condition.
* **Example:** `=COUNTIF(A1:A10, ">10")` counts cells in A1:A10 with values greater than 10.

## COUNTIF Example

```{r,echo=F}
xl = sort(c(xxx))
bb = xl[5]
```

What would be the result of putting ``=COUNTIF(A1:C3,"<=`r bb`")`` in an empty cell?

```{r fig.width=5,fig.height=5,echo=F}
draw_ss(data)
```
\


## Sorting Your Data

* **Need to organize your data in a specific order?**
* **Google Sheets' Sort tool makes it easy!**
* **To sort:**
    * Select the range of data you want to sort.
    * Go to **Data > Sort Range**.
    * Choose the column you want to sort by and the sorting order (ascending or descending). 
    * Click **Sort**. 
* **Example:** Sort a list of student names alphabetically, or a column of test scores from highest to lowest.


## Conclusion

* You've learned to use basic functions in Google Sheets!
* These tools empower you to analyze data effectively.
* Explore further with more functions and features!

## Practice Time

* [https://chadworley.github.io/a2/u01/u01_shared1.html#Q5v1](https://chadworley.github.io/a2/u01/u01_shared1.html#Q5v1)