---
title: "Parent-Night Information"
author: "Chad Worley"
output: slidy_presentation
---

# BART rules

::: columns

:::: {.column width=80%}
* No personal electronics
* No food or drinks (other than water) outside cafeteria
* No hoods, hats, or bulky coats
* No drugs
* Lateness/absence:
    * BART is focused on bringing up the attendance rate.
    * "Accumulating 3 or more absences in a quarter can lead to disciplinary action, a formal attendance plan, and loss of privileges. If you accumulate 10 or more absences in a semester-long course, or 20 or more absences in a full-year course, you may lose credit for the course."
* SmartPass is used whenever a student leaves the classroom during a class.
::::

:::: {.column width=20%}
```{r,fig.width=2,echo=F,fig.align='center'}
library(qrcode)
code <- qr_code("https://chadworley.github.io/parent_night/parent_night.html")
par(mar=c(0,0,0,0))
plot(code)
```
::::

:::


# Algebra 2

::: columns

:::: {.column width=80%}
* Topics ([Mass Standards](https://chadworley.github.io/a2/MassStandsAlg2.pdf)):
    * Statistics
    * Rational Expressions
    * Trigonometric Functions
    * Exponential/Logarithmic Functions
* [Daily agenda](https://chadworley.github.io/a2/weekly_a2.html)
* [Canvas page](https://bart.instructure.com/courses/1314)
* [Link parent to student in Canvas](https://chadworley.github.io/parent_night/Link_Student_Parent_Canvas.pdf)
* [Syllabus](https://chadworley.github.io/a2/syllabus_a2.html)
* Best way to contact me: [ParentSquare](https://www.parentsquare.com/schools/30932)
::::

:::: {.column width=20%}
```{r,fig.width=2,echo=F,fig.align='center'}
library(qrcode)
code <- qr_code("https://chadworley.github.io/parent_night/parent_night.html")
par(mar=c(0,0,0,0))
plot(code)
```
::::

:::



# Math Literacy

::: columns

:::: {.column width=80%}
* Math Literacy is a project-based math class. We reinforce fundamental math fluency by completing projects that involve mathematics.
* [Daily agenda](https://chadworley.github.io/ml/weekly_ml.html)
* [Canvas page](https://bart.instructure.com/courses/1282)
* [Link parent to student in Canvas](https://chadworley.github.io/parent_night/Link_Student_Parent_Canvas.pdf)
* [Syllabus](https://chadworley.github.io/ml/syllabus_ml.html)
* Best way to contact me: [ParentSquare](https://www.parentsquare.com/schools/30932)
::::

:::: {.column width=20%}
```{r,fig.width=2,echo=F,fig.align='center'}
library(qrcode)
code <- qr_code("https://chadworley.github.io/parent_night/parent_night.html")
par(mar=c(0,0,0,0))
plot(code)
```
::::

:::












