```{r,echo=F,warning=F}
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("x^0","",exp,fixed=T)
  exp = gsub("x^1","x",exp,fixed=T)
  return(exp)
}

while(T){
  tf = runif(1,1,10) #sample(5:60,1)/10
  V0 = round(runif(1,2,20),1)  #sample(20:80,1)/10
  # V0(1-t/tf)^2
  # V0(1-2t/tf+t^2/tf^2)
  # V0/tf^2*t^2 - 2V0/tf*t + V0
  a = round(V0/tf^2,1)
  b = round(-2*V0/tf,1)
  c = round(V0,1)
  t = round(runif(1,tf*0.1,tf*0.9),2)
  dVdt = 2*a*t+b
  if(a>0.5 && abs(dVdt)>0.1){break}
}

ex1 = fixer(paste0(a,"t^2+",b,"t+",c,collapse=""))
ex2 = fixer(paste0(2*a,"t+",b,collapse=""))
```

Question
========

A bucket initially holds `r V0` liters of water. A hole is punched into the bottom of the bucket, so water leaks out following [Torricelli's law](https://en.wikipedia.org/wiki/Torricelli%27s_law). Below, volume is shown as a function of time, where $t$ in in minutes.

$$V(t)~=~`r ex1`$$

How fast (in liters per minute) is water leaving the bucket at $t=`r t`$ minutes? (Tolerance is $\pm 0.01$ liters per minute.) The volume in the bucket is decreasing, so the derivative will be negative, but the question is asking about the rate of water leaving, so your answer should be positive.

Solution
========

We were given the volume as a function of time.

$$V(t) ~=~ `r ex1`$$

Find the derivative of the volume function (with respect to time). Use the [differentiation rules](https://en.wikipedia.org/wiki/Differentiation_rules#The_polynomial_or_elementary_power_rule).

$$V'(t) ~=~ (`r a`\cdot 2)t^{2-1}+(`r b`\cdot 1)t^{1-1}$$

$$V'(t) ~=~ `r ex2`$$

Plug the specified time $t=`r t`$ into the function.

$$V'(`r t`) ~=~ `r dVdt`$$

So, when $t=`r t`$, water is leaving at a rate of `r abs(dVdt)` liters per minute.

```{r,echo=F,fig.dim=c(6,6)}
tt = seq(0,tf,length.out=100)
VV = a*tt^2+b*tt+c
Vt = a*t^2+b*t+c
tt2 = seq(t*0.6,t*1.4,length.out=10)
plot(tt,VV,type="l",col="blue",xlab="time (min)",ylab="volume (L)",main=paste0("At (",t,",",round(Vt,2),")\nslope is ",round(dVdt,2)," L/min.",collapse=""))
lines(tt2,dVdt*(tt2-t)+Vt,col="red")
points(t,Vt,pch=19,col="purple")
```
\

Meta-information
============
extype: num
exsolution: `r abs(dVdt)`
exname: ddt_of_volume
extol: 0.01