```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("t^0","",exp,fixed=T)
  exp = gsub("t^1","x",exp,fixed=T)
  return(exp)
}

while(T){
  a = round(10^runif(1,log(0.1,10),1),2)
  x = round(runif(1,2,7),2)
  gx = a^x
  gpx = a^x*log(a)
  if(abs(gpx)>0.2 && abs(gpx)<5 && gx<8){break}
}

```

Question
========

In Calculus you will prove various [differentiation rules](https://en.wikipedia.org/wiki/Differentiation_rules). We already "proved" the [power rule](https://en.wikipedia.org/wiki/Power_rule). From here on, we will just practice using the rules (and not first prove them).

The [rule to find the derivative of an exponential function](https://en.wikipedia.org/wiki/Differentiation_rules#Derivatives_of_exponential_and_logarithmic_functions) is shown below, where $a$ is a constant, and $\ln(a)$ is the [natural logarithm](https://en.wikipedia.org/wiki/Natural_logarithm) of $a$.

$$f(x) ~=~ a^x$$

$$f'(x) ~=~ a^x\cdot\ln(a)$$

Let $g(x)=`r a`^x$. Calculate $g'(`r x`)$. The tolerance is $\pm 0.01$.


Solution
========

We were given $g(x)=`r a`^x$. We were told the rule to find the derivative of an exponential function.

$$g'(x) = `r a`^x \cdot \ln(`r a`)$$

Plug in $x=`r x`$.

$$g'(`r x`) = `r a`^{`r x`} \cdot \ln(`r a`)$$


$$g'(`r x`) = `r a^x*log(a)`$$

```{r,echo=F,fig.dim=c(8,8)}
par(pty="s")
xx = seq(0,20,0.01)
plot(xx,a^xx,type="l",xlab="x",ylab="g(x)",xlim=c(0,10),ylim=c(0,10))
arrows(0,0,10.3,0,lwd=2,length=0.2)
arrows(0,0,0,10.3,lwd=2,length=0.2)
for(i in 1:20){
  abline(h=i,col="grey")
  abline(v=i,col="grey")
}
for(i in seq(5,20,5)){
  abline(h=i,col="darkgrey",lwd=2)
  abline(v=i,col="darkgrey",lwd=2)
}
lines(xx,a^xx,lwd=3,col="blue")
lines(xx,gpx*(xx-x)+gx,lwd=2,col="red")
points(x,gx,col="purple",pch=19)
text(x,gx,paste0("(",x,", ",round(gx,2),")",collapse=""),
     col="purple",adj=c(1.1,-0.2))
theta = atan(gpx)
text(x+0.5*cos(pi+theta),gx+0.5*sin(pi+theta),paste0("slope=",round(gpx,2),collapse=""),srt=atan(gpx)/pi*180,adj=c(1,1.2),col="red")
text(x+0.5*cos(theta),gx+0.5*sin(theta),paste0("y=",round(gpx,2),"*(x-",x,")+",round(gx,2),collapse=""),srt=atan(gpx)/pi*180,adj=c(0,1.2),col="red")
```
\


Meta-information
============
extype: num
exsolution: 1
exname: ddx_exp
extol: 0.01