```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("t^0","",exp,fixed=T)
  exp = gsub("t^1","x",exp,fixed=T)
  return(exp)
}

while(T){
  FC = 10^runif(1,3,7)  # Fixed cost of equipment
  U = 10^runif(1,0,4)
  ndoubcost = 10^runif(1,3,6)
  A = FC/ndoubcost^3
  B = U*runif(1,1,1000)
  nrev0 = ndoubcost*runif(1,0.01,100)
  C = B/nrev0^2
  FC = signif(FC,2)
  U = signif(U,2)
  A = signif(A,2)
  B = signif(B,2)
  C = signif(C,2)
  nrev0 = sqrt(B/C)
  n2 = (FC/2/A)^(1/3)
  cpu1 = A+U+FC
  cpu2 = A*n2^2+U+FC/n2
  cpu3 = A*nrev0^2+U+FC/nrev0
  nstar = sqrt((B-U)/(3*A+3*C))
  Pstar = -A*nstar^3-C*nstar^3+(B-U)*nstar-FC
  if(A>0.00001 && B>0.001 && C>0.00001 && nstar>100 && nstar<100000 && Pstar>1000 && nstar<nrev0 && n2<nrev0 &&
    n2>nrev0/10 && n2<nrev0/2){break}
}

```

Question
========

A new business plans to produce and sell widgets.

The long-run cost to produce each widget is dependent on the scale (size) of the operation. See [economies of scale](https://en.wikipedia.org/wiki/Economies_of_scale). The business models the total cost of the business with a polynomial, where $n$ is the number of widgets made and sold.
$$C(n) ~=~ `r A`n^3+`r U`n+`r FC`$$

```{r,echo=F,fig.dim=c(8,4)}
par(pty="s",mfrow=c(1,2))
nn = seq(100,nrev0,length.out=1000)
plot(nn,A*nn^2+U+FC/nn,type="l",xlab="n",ylab="Cost per widget",xlim=c(0,nrev0))
plot(nn,A*nn^3+U*nn+FC,type="l",xlab="n",ylab="Total cost",xlim=c(0,nrev0))
```
\

The revenue from selling each widget is relatively constant until the scale of the operation is large enough to flood the market. The business models the revenue with another polynomial.

$$R(n) ~=~ `r B`n-`r C`n^3$$

```{r,echo=F,fig.dim=c(8,4)}
par(pty="s",mfrow=c(1,2))
nn = seq(10,nrev0,length.out=1000)
plot(nn,B-C*nn^2,type="l",xlab="n",ylab="Revenue per widget",xlim=c(0,nrev0))
plot(nn,B*nn-C*nn^3,type="l",xlab="n",ylab="Total revenue",xlim=c(0,nrev0))
```
\

By subtracting cost from revenue, we get a profit function.

$$P(n) ~=~ R(n)-C(n)$$

$$P(n) ~=~ -`r A+C`n^3+`r B-U`n-`r FC`$$

How many widgets should the business plan to make and sell in order to maximize profit? You can solve this by finding the special number, $n^\star$, such that $P'(n^\star)=0$.

The tolerance is $\pm 10$ widgets.


Solution
========

This is called an [optimization problem](https://en.wikipedia.org/wiki/Mathematical_optimization), where we hope to find a [maximum](https://en.wikipedia.org/wiki/Maximum_and_minimum). Since the profit function is a [differentiable function](https://en.wikipedia.org/wiki/Differentiable_function), we can simply find where the derivative equals 0.

Take a derivative of the profit function.

$$P(n) ~=~ -`r A+C`n^3+`r B-U`n-`r FC`$$

$$P'(n) ~=~ -`r 3*A+3*C`n^2+`r B-U`$$

Find $n^\star$ such that $P'(n^\star)=0.$ 

$$-`r 3*A+3*C`(n^\star)^2+`r B-U`=0$$ 
$$-`r 3*A+3*C`\cdot (n^\star)^2 = -`r B-U`$$
$$(n^\star)^2 = \frac{`r B-U`}{`r 3*A+3*C`}$$
$$n^\star = \sqrt{\frac{`r B-U`}{`r 3*A+3*C`}}$$

$$n^\star=`r nstar`$$

```{r,echo=F,fig.dim=c(8,8)}
nn = seq(10,nrev0,length.out=1000)
plot(nn,-A*nn^3-C*nn^3+(B-U)*nn-FC,type="l",xlim=c(0,nrev0),ylim=c(0,Pstar*1.3),xlab="n",ylab="P(n)")
lines(c(nstar*0.1,nstar*1.9),c(Pstar,Pstar),col="purple")
points(nstar,Pstar,pch=19,col="red")
text(nstar,Pstar,paste0("(",round(nstar),", ",signif(Pstar,3),")",collapse=""),col="red",adj=c(0.5,-0.5))
text(nstar*1.8,Pstar,paste0("slope=0"),col="purple",adj=c(1,-0.5))
```
\

Meta-information
============
extype: num
exsolution: `r round(nstar)`
exname: optimize_profit
extol: 10