```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("t^0","",exp,fixed=T)
  exp = gsub("t^1","x",exp,fixed=T)
  return(exp)
}


xx = seq(-10,10,length.out=1000)
getcurves = function(){
  while(T){
    coefs = runif(6,-2.5,2.5)/factorial(rev(1:6))
    f = function(x){return(coefs[1]*x^5+coefs[2]*x^4+coefs[3]*x^3+coefs[4]*x^2+coefs[5]*x+coefs[6])}
    fp = function(x){return(5*coefs[1]*x^4+4*coefs[2]*x^3+3*coefs[3]*x^2+2*coefs[4]*x+coefs[5])}
    #fpp = function(x){return(5*4*coefs[1]*x^3+4*3*coefs[2]*x^2+3*2*coefs[3]*x+2*coefs[4])}
    xx = seq(-10,10,length.out=1000)
    yy1 = f(xx)
    yy2 = fp(xx)
    #yy3 = fpp(xx)
    if(max(abs(yy1))<10 && 
       max(abs(yy2))<10 && 
       max(abs(yy1))>2 && 
       max(abs(yy2))>2 &&
       length(unique(sign(yy1)))>1 && length(unique(sign(yy2)))>1){break}
  }
  return(list(yy1,yy2))
}

while(T){
  l1 = getcurves()
  l2 = getcurves()
  l3 = getcurves()
  l4 = getcurves()
  L1 = l1
  L2 = list(l2[[1]],l3[[2]])
  L3 = list(l3[[1]],l4[[2]])
  L4 = list(l4[[1]],l2[[2]])
  z1 = xx[diff(sign(L1[[2]]))!=0]
  z2 = xx[diff(sign(L2[[2]]))!=0]
  z3 = xx[diff(sign(L3[[2]]))!=0]
  z4 = xx[diff(sign(L4[[2]]))!=0]
  zs = list(z1,z2,z3,z4)
  cangoon = T
  for(i in 1:3){
    for(j in (i+1):4){
      maxmin = 0
      for(h in 1:length(zs[[i]])){
        mymin = 1000
        for(k in 1:length(zs[[j]])){
          mymin = min(c(mymin,abs(zs[[i]][h]-zs[[j]][k])))
        }
        maxmin = max(c(maxmin,mymin))
      }
      if(maxmin<1){
        cangoon = F
        break
        }
    }
  }
  if(cangoon){break}
}



Ls = list(L1,L2,L3,L4)

ord = sample(1:4)
sol = paste0(1*(1==ord),collapse="")

```

Question
========

Which graph shows a correct pair of <font color="blue">$f(x)$</font> as a blue curve and <font color="red">$f'(x)$</font> as a red curve? Remember the output ($y$) of the red [derivative function](https://en.wikipedia.org/wiki/Derivative) should match the instantaneous slope of the blue curve for all values of $x$.

```{r,echo=F,fig.dim=c(8,8)}
par(mfrow=c(2,2),pty="s")

for(j in 1:4){
  i = ord[j]
  yy1 = Ls[[i]][[1]]
  yy2 = Ls[[i]][[2]]
  plot(xx,yy1,col="blue",type="l",lwd=2,xlim=c(-10,10),ylim=c(-10,10),main=LETTERS[j],xlab="x",ylab="y")
  for(i in seq(0,10,1)){
    abline(h=i,col="grey")
    abline(v=i,col="grey")
    abline(h=-i,col="grey")
    abline(v=-i,col="grey")
  }
  arrows(-10.5,0,10.5,0,code=3,length=0.1,angle=20,lwd=2)
  lines(xx,yy1,col="blue",lwd=2)
  lines(xx,yy2,col="red",lwd=2)
}
```
\

Solution
========

The correct answer is `r LETTERS[1:4][1==ord]`. Notice that when blue has positive slope, red has positive $y$. When blue has negative slop, red has negative $y$.

Probably the easiest characteristic to check first is where blue has a peak or valley (so slope equals 0), the red curve should have an $x$ intercept.





Meta-information
============
extype: schoice
exsolution: `r sol`
exname: visualize_der_func