```{r,echo=F,warning=F}
options(scipen=999)
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("t^0","",exp,fixed=T)
  exp = gsub("t^1","x",exp,fixed=T)
  return(exp)
}

dt = 0.01
while(T){
  t = sample(1:9,1)
  w = round(runif(1,2,sqrt(99)),2)
  h = round(runif(1,2,sqrt(99)),2)
  A = w*h
  hdw = runif(1,0.1,2)
  wdh = runif(1,0.1,2)
  dw = round(hdw/h,2)
  dh = round(wdh/w,2)
  dA1 = h*dw+w*dh
  dA2 = dA1+dw*dh
  if(dw*dh<0.005 && abs(diff(c(h,w)))>0.5 && abs(log(w/h))<log(1.6) && abs(diff(c(dw,dh)))>0.02 && abs(log(dw/dh))<log(3)){break}
}

At = w*h
hdw = hdw
wdh = wdh
dwdh = dw*dh
dA = hdw+wdh+dwdh
edA = hdw+wdh
A2 = (w+dw)*(h+dh)
eA2 = At+hdw+wdh
dwdt = dw/dt
dhdt = dh/dt
dAdt = dA/dt
edAdt = edA/dt

vals = c(At,hdw,wdh,dwdh,dA,edA,A2,eA2,dwdt,dhdt,dAdt,edAdt)
suv = sort(unique(vals))

sols = character()
for(i in 1:length(vals)){
  sols = c(sols,paste0(1*(vals[i]==suv),collapse=""))
}

al = paste0("* ",rep(suv,12),collapse="\n")
```

Question
========

The area of a rectangle is the product of its width and height. A rectangle is growing both horizontally and vertically, so that both width and height are functions of time.

$$A(t) ~=~ w(t)\cdot h(t)$$

At $t=`r t`$ seconds, the width is `r w` meters, and the height is `r h` meters.

$$w(`r t`)=`r w`$$
$$h(`r t`)=`r h`$$

Over a small interval of time ($\Delta t = 0.01$) the rectangle's width grows by $\Delta w=`r dw`$ meters and the height grows by $\Delta h =`r dh`$ meters, so $w(`r t+0.01`)=`r w+dw`$ and $h(`r t+0.01`)=`r h+dh`$. This is depicted below (not drawn to scale).


```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
bump = 0.1
plot(0,0,type="n",xlim=c(0-bump,1),ylim=c(0,1+bump),axes=F,ann=F)
ratio1 = w/h
ratio2 = dw/dh

ds = c(dw,dh)
mind = min(ds)
dpl = ds/mind*0.2

ws = c(w,h)
wpl = ws/min(ws)*0.8

tots = ws+ds
totpl = tots/max(tots)

rs = wpl/(wpl+dpl)

x = rs[1]*totpl[1]
y = rs[2]*totpl[2]
x2 = totpl[1]
y2 = totpl[2]
x3 = mean(c(x,x2))
y3 = mean(c(y,y2))

polygon(c(0,0,x,x),1-c(0,y,y,0),col=rgb(0.2,0.1,0.6,0.5),border=rgb(0.2,0.1,0.6))
polygon(c(0,0,x2,x2),1-c(0,y2,y2,0),col=rgb(0.2,0.1,0.6,0.2),border=rgb(0.2,0.1,0.6))
lines(c(0,0,x,x),1-c(y,y2,y2,y),col="red")
lines(c(x,x2,x2,x),1-c(y,y,0,0),col="blue")
lines(c(x,x2,x2),1-c(y2,y2,y))
text(x/2,1.05,paste0("w(",t,")",collapse=""))
text(-0.05,1-y/2,paste0("h(",t,")",collapse=""),srt=90)
text(x3,1.05,TeX("$\\Delta w$"))
text(-0.05,1-y3,TeX("$\\Delta h$"),srt=90)
arrows(0.1,1-y,0.1,1-y2,length=0.08,angle=15,lwd=2,col="red")
arrows(x,1-0.1,x2,1-0.1,length=0.08,angle=15,lwd=2,col="blue")
text(x/2,1-y/2,TeX(paste0("$A(",t,")$",collapse="")))
text(x/2,1-y3,TeX(paste0("$w(",t,") \\cdot \\Delta h$",collapse="")))
text(x3,1-y/2,TeX(paste0("$h(",t,") \\cdot \\Delta w$",collapse="")))
text(x3,1-y3,TeX("$\\Delta w \\cdot \\Delta h$"))
```
\

By calculating various values, we will explore the fact that if $\Delta w$ and $\Delta h$ are quite small compared to $w$ and $h$, then the area $\Delta w\cdot \Delta h$ is so small that we can ignore it for many purposes. In the process, we will "prove" the [product rule](https://en.wikipedia.org/wiki/Differentiation_rules#The_product_rule).

Find the area of the rectangle at $t=`r t`$.

* $A(`r t`)=$ ##ANSWER1## $\mathrm{m^2}$

Find the other areas in the diagram.

* $h(`r t`) \Delta w=$ ##ANSWER2## $\mathrm{m^2}$
* $w(`r t`) \Delta h=$ ##ANSWER3## $\mathrm{m^2}$
* $\Delta w \Delta h=$ ##ANSWER4## $\mathrm{m^2}$

How much did the area grow by?

* $\Delta A ~=~ A(`r t+0.01`)-A(`r t`) ~=~$ ##ANSWER5## $\mathrm{m^2}$

What would be the estimated growth of area if we ignored the smallest area?

* $h(`r t`)\Delta w + w(`r t`)\Delta h=$ ##ANSWER6## $\mathrm{m^2}$

Find the final area of the rectangle.

* $A(`r t+0.01`)=$ ##ANSWER7## $\mathrm{m^2}$

What would be the estimated final area of the rectangle if you ignored the smallest area?

* $A(`r t`)+h(`r t`)\Delta w + w(`r t`)\Delta h=$ ##ANSWER8## $\mathrm{m^2}$

How fast (on average) are the width and height growing between $t=`r t`$ and $t=`r t+0.01`$?

* $\frac{\Delta w}{\Delta t} =$ ##ANSWER9## $\mathrm{\frac{m}{s}}$
* $\frac{\Delta h}{\Delta t} =$ ##ANSWER10## $\mathrm{\frac{m}{s}}$

What is the average rate of growth of the rectangle's area between $t=`r t`$ and $t=`r t+0.01`$?

* $\frac{\Delta A}{\Delta t}=$ ##ANSWER11## $\mathrm{\frac{m^2}{s}}$

What would be the estimated rate of growth if we ignored the smallest area?

* $h\cdot \frac{\Delta w}{\Delta t}~+~w\cdot \frac{\Delta h}{\Delta t}=$ ##ANSWER12## $\mathrm{\frac{m^2}{s}}$


Answerlist
--------

`r al`


Solution
========

* $A(`r t`)=$ `r At` $\mathrm{m^2}$
* $h(`r t`) \Delta w=$ `r hdw` $\mathrm{m^2}$
* $w(`r t`) \Delta h=$ `r wdh` $\mathrm{m^2}$
* $\Delta w \Delta h=$ `r dwdh` $\mathrm{m^2}$
* $\Delta A =$ `r dA` $\mathrm{m^2}$
* $h(`r t`)\Delta w + w(`r t`)\Delta h=$ `r edA` $\mathrm{m^2}$
* $A(`r t+0.01`)=$ `r A2` $\mathrm{m^2}$
* $A(`r t`)+h(`r t`)\Delta w + w(`r t`)\Delta h=$ `r eA2` $\mathrm{m^2}$
* $\frac{\Delta w}{\Delta t} =$ `r dwdt` $\mathrm{\frac{m}{s}}$
* $\frac{\Delta h}{\Delta t} =$ `r dhdt` $\mathrm{\frac{m}{s}}$
* $\frac{\Delta A}{\Delta t}=$ `r dAdt` $\mathrm{\frac{m^2}{s}}$
* $h\cdot \frac{\Delta w}{\Delta t}~+~w\cdot \frac{\Delta h}{\Delta t}=$ `r edAdt` $\mathrm{\frac{m^2}{s}}$

Notice, this suggests that in the limit as $\Delta t \to 0$, then we get the product rule:

$$A'(t) ~=~ w'(t)h(t)+w(t)h'(t)$$


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",12),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: prod_rule_rect_area