```{r,echo=F,warning=F}
fixer = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("-1x","-x",exp,fixed=T)
  exp = gsub("+1x","+x",exp,fixed=T)
  exp = gsub(" 1x^3","x^3",exp,fixed=T)
  exp = gsub(" ","",exp,fixed=T)
  return(exp)
}
fixer2 = function(exp){
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("-1x","-x",exp,fixed=T)
  exp = gsub("+1x","+x",exp,fixed=T)
  exp = gsub(" 1x^2","x^2",exp,fixed=T)
  exp = gsub(" ","",exp,fixed=T)
  return(exp)
}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

fracs = c(1,1/2,1/3,1/4,1/5,2/3,2/5,3/4,3/5,4/5,2,3,4,5,3/2,5/2,4/3,5/3,5/4)

nums = c(1,1,1,1,1,2,2,3,3,4,2,3,4,5,3,5,4,5,5)
dens = c(1,2,3,4,5,3,5,4,5,5,1,1,1,1,2,2,3,3,4)

nums = c(nums,-nums)
dens = c(dens,dens)
fracs = c(fracs,-fracs)

while(T){
  h = sample(2:7,1)*sample(c(-1,1),1)
  a = 3*sample(1:6,1)
  b = 2*sample(1:10,1)*sample(c(-1,1),1)
  c = -(a*h^2+b*h)+sample(1:15,1)*sample(c(-1,1),1)
  m = a*h^2+b*h+c
  A = round(a/3)
  B = round(b/2)
  C = round(c)
  D = -(A*h^3+B*h^2+C*h)+sample(1:15,1)*sample(c(-1,1),1)
  k = A*h^3+B*h^2+C*h+D
  ntr = k-m*h
  if(abs(m)>0 && abs(m)<11 && abs(C)<30 && abs(D)<50 && abs(ntr)<11){break}
}

# $$adh^2+bdh+cd = n$$
# $$Ah^3+Bh^2+Ch+D$$

exp1 = fixer(paste0(" ",A,"x^3+",B,"x^2+",C,"x+",D))
exp2 = fixer2(paste0(" ",a,"x^2+",b,"x+",c))

ac = -10:10

sol1 = paste0(1*(ac==m),collapse="")
sol2 = paste0(1*(ac==ntr),collapse="")

al = paste0("* ",ac,collapse="\n")


```

Question
========

Let $f(x)=`r exp1`$. A tangent line is drawn through $(`r h`, `r k`)$. Find the equation of the tangent line in slope-intercept form ($y=mx+b$).

* $m=$ ##ANSWER1##
* $b=$ ##ANSWER2##

Answerlist
--------

`r al`


Solution
========

We were given $f(x)=`r exp1`$. Differentiate to find the derivative.

$$f'(x)=`r exp2`$$

Find the instantaneous rate of change at $x=`r h`$.

$$f'(`r h`) = `r m`$$
The derivative of $f(x)$ at $x=`r h`$ equals the slope of the tangent line.
$$m=`r m`$$

```{r,echo=F}
sif = fixer(paste0("y=",m,"x+",ntr))
sifb = fixer(paste0("y=",m,"x+b"))
psf = fixer(paste0("y=",m,"(x+",-h,")+",k))
psf2 = fixer(paste0("y=",m,"x+",-m*h,"+",k))
```

At this stage there are two good options. We either substitute into $y=mx+b$ with $y=`r k`$, $m=`r m`$, and $x=`r h`$ to find $b$ or simplify the point-slope ($y=m(x-x_0)+y_0$) form into slope-intercept form.

### Option 1: plug point $(`r h`, `r k`)$ into $`r sifb`$ to get $b$

We already know the slope.
$$`r sifb`$$
We know the line must go through point $(`r h`, `r k`)$.
$$`r k`=(`r m`)(`r h`)+b$$

$$`r k`=`r m*h`+b$$

$$`r k-m*h`=b$$

So the tangent line is expressed with the equation $`r sif`$

### Option 2: simplify point-slope form

We already know a point (`r h`,`r k`) and the slope, $m=`r m`$, of the line. Plug into $y=m(x-x_0)+y_0$.

$$`r psf`$$

Distribute.
$$`r psf2`$$
Combine the constants.
$$`r sif`$$

### Answer

$$m=`r m`$$
$$b=`r b`$$

So, the equation of the tangent line is known:

$$`r sif`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: get_tangent_slope_int
extol: 0.01