```{r data generation, echo = FALSE, results = "hide"}
hk = sample(1:6,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]

lr = c("left","right")[(sign(h)+1)/2+1]
du = c("down","up")[(sign(k)+1)/2+1]

x1 = seq(-30,30,0.1)
y1 = sign(x1)*(abs(x1))^(1/3)
x2 = x1+h
y2 = y1+k

px1 = (-5:5)^3
py1 = sign(px1)*abs(px1)^(1/3)
px2 = px1+h
py2 = py1+k

cch = paste0("\\sqrt[3]{x+",-h,"}+",k,collapse="")
cch = gsub("+-","-",cch,fixed=T)
ach = character()
for(i in c(-1,1)){
    for(j in c(-1,1)){
        ch = paste0("\\sqrt[3]{x+",-h*i,"}+",k*j,collapse="")
        ch = gsub("+-","-",ch,fixed=T)
        ach = c(ach,ch)
        ch = paste0("\\sqrt[3]{x+",k*i,"}+",h*j,collapse="")
        ch = gsub("+-","-",ch,fixed=T)
        ach = c(ach,ch)
    }
}
ach = sort(ach)
al = paste0("* $y=",ach,"$",collapse="\n")
sol = paste0(1*(ach==cch),collapse="")


```

Question
========

From a [cube-root](https://en.wikipedia.org/wiki/Cube_root) parent function $y=\sqrt[3]{x}$, a translation is plotted below:

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),lwd=0.4)
    lines(c(-10,10),c(i,i),lwd=0.4)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),lwd=0.8)
    lines(c(-10,10),c(i,i),lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

text(10.5,-0.5,"x")
text(-0.5,10.5,"y")
text(5,-0.5,"5")
text(-0.5,5,"5")

lines(x2,y2,col="blue",lwd=3)
points(px2,py2,pch=19,col="blue",cex=0.8)
```
\

Which equation represents the plotted curve?


Answerlist
--------

`r al`


Solution
========

The correct option is:

$$y=`r cch`$$

Notice, the parent function $y=x^3$ has an inflection point at $(0,0)$. The shifts are `r abs(h)` units `r lr` and `r abs(k)` units `r du`. When $x=`r h`$, the argument of the function is 0. This line of reasoning explains why the horizontal shift is "backwards".


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: shift_cube