---
output: slidy_presentation
---

# Agenda

* Entrance Ticket: [ET_0929](https://bart.instructure.com/courses/2110/quizzes/3203)
    * Review of function translations
* A [new parent-function reference](https://chadworley.github.io/algtwo2026/u02/09_29/parent_functions.pdf)
* [PCW_09_29_graph_parent_translations](https://bart.instructure.com/courses/2110/assignments/28864)
    * Graph 8 shifted parent functions on paper
    * Due today!

# Shifts

* Adding/subtracting in the argument shifts function horizontally. The direction is "backwards".
* Adding/subtracting outside the function shifts function vertically. The direction is "normal".
* Examples:
    * If we compare $y=f(x)$ and $y=f(x+2)+3$, the second curve is congruent to the first, but the second curve is shifted 2 units **left** and 3 units **up**.
    * If we compare $y=f(x)$ and $y=f(x-2)+3$, the second curve is congruent to the first, but the second curve is shifted 2 units **right** and 3 units **up**.
    * If we compare $y=f(x)$ and $y=f(x+2)-3$, the second curve is congruent to the first, but the second curve is shifted 2 units **left** and 3 units **down**.
    * If we compare $y=f(x)$ and $y=f(x-2)-3$, the second curve is congruent to the first, but the second curve is shifted 2 units **right** and 3 units **down**.


# Parent functions

* A [pdf of important parent functions](https://chadworley.github.io/algtwo2026/u02/09_29/parent_functions.pdf).


```{r,echo=F}
fdim = 3
```

### Absolute-value function

$$y=|x|$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit = function(){
    par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
        lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    text(5,-0.5,"5",cex=0.7)
    text(-0.5,5,"5",cex=0.7)
    text(10,-0.5,"x",cex=0.7)
    text(-0.5,10,"y",cex=0.7)
}
startit()
x = seq(-10,10,0.1)
y = abs(x)
lines(x,y,lwd=3,col="blue")
xp = 0
yp = 0
points(yp,xp,pch=19,col="blue",cex=0.8)
```

\vfill

### Reciprocal function

$$y=\frac{1}{x}~~~~\text{or}~~~~y=x^{-1}$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x1 = seq(-10,-1/10,0.01)
y1 = 1/x1
lines(x1,y1,lwd=3,col="blue")
x2 = seq(1/10,10,0.01)
y2 = 1/x2
lines(x2,y2,lwd=3,col="blue")
xp = c(-1,1)
yp = 1/xp
points(yp,xp,pch=19,col="blue",cex=0.8)
```

\vfill

\newpage

### Squaring function (Quadratic)

$$y=x^2$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-sqrt(10),sqrt(10),0.01)
y = x^2
lines(x,y,lwd=3,col="blue")
xp = -3:3
yp = xp^2
points(xp,yp,pch=19,col="blue",cex=0.8)
```

\vfill


### Square-root function

$$y=\sqrt{x}~~~~\text{or}~~~~y=x^{1/2}$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(0,sqrt(10),0.01)
y = x^2
lines(y,x,lwd=3,col="blue")
xp = 0:3
yp = xp^2
points(yp,xp,pch=19,col="blue",cex=0.8)
```

\vfill


\newpage


### Cubing function (Cubic)

$$y=x^3$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-10^(1/3),10^(1/3),0.01)
y = x^3
lines(x,y,lwd=3,col="blue")
xp = -2:2
yp = xp^3
points(xp,yp,pch=19,col="blue",cex=0.8)
```

\vfill

### Cube-root function

$$y=\sqrt[3]{x}~~~~\text{or}~~~~y=x^{1/3}$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-10,10,0.01)
y = sign(x)*abs(x)^(1/3)
lines(x,y,lwd=3,col="blue")
xp = c(-8,-1,0,1,8)
yp = sign(xp)*abs(xp)^(1/3)
points(xp,yp,pch=19,col="blue",cex=0.8)
```

\vfill

\newpage

### Exponential (base 2) function

$$y=2^x$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-10,log(10)/log(2),0.001)
y = 2^x
lines(x,y,lwd=3,col="blue")
xp = c(0,1,2,3)
yp = 2^xp
points(xp,yp,pch=19,col="blue",cex=0.8)
```

\vfill

### Logarithmic (base 2) function

$$y=\log_2(x)$$

```{r,echo=F,fig.dim=c(fdim,fdim),fig.align='center'}
startit()
x = seq(-10,log(10)/log(2),0.001)
y = 2^x
lines(y,x,lwd=3,col="blue")
xp = c(0,1,2,3)
yp = 2^xp
points(yp,xp,pch=19,col="blue",cex=0.8)
```

\vfill



