```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
l1 = c(-9:-1,1:9) #possible values for a
l2 = c(-9:-1,1:9) #possible values for b
a = sample(l1,1)
b = sample(l2,1)
s = a+b
p = a*b
allsums = unique(apply(expand.grid(l1,l2),1,prod))
sall = unique(c(s,a-b,b-a,-a-b))
while(length(sall)<4){
  sall = unique(c(sall,sample(allsums,1)))
}
allprods = unique(apply(expand.grid(l1,l2),1,prod))
pw = sample(allprods,1)
pall = unique(c(p,-p,pw,-pw))
while(length(pall)<4){
  pw = sample(allprods,1)
  pall = unique(c(p,-p,pw,-pw))
}
sall = sort(sall)
pall = sort(pall)
allposs = unique(c(allsums,allprods))
qall = unique(c(sall,pall))
while(length(qall)<8){
  qall = unique(c(qall,sample(allposs,1)))
}
qall = sort(qall)
qst = character()
for(i in qall){
  if(i>0){
    qst = c(qst,paste0("+",i,collapse=""))
  } else {
    qst = c(qst,paste0(i))
  }
}
ans1 = paste0((qall==s)*1,collapse="")
ans2 = paste0((qall==p)*1,collapse="")
```

Question
========

```{python, echo=FALSE}
from sympy import *
x = symbols("x")
exp1 = x**2+r.s*x+r.p
lexp1 = latex(exp1)
exp2 = (x+r.a)*(x+r.b)
lexp2 = latex(exp2)
```

Expand the following polynomial.

$$`r py$lexp2`$$

Answer:
$x^2$ ##ANSWER1##  ##ANSWER2##


Answerlist
--------

* `r qst[1]`x
* `r qst[2]`x
* `r qst[3]`x
* `r qst[4]`x
* `r qst[5]`x
* `r qst[6]`x
* `r qst[7]`x
* `r qst[8]`x
* `r qst[1]`
* `r qst[2]`
* `r qst[3]`
* `r qst[4]`
* `r qst[5]`
* `r qst[6]`
* `r qst[7]`
* `r qst[8]`

Solution
========

The answer is $`r py$lexp1`$.


```{python,echo=F}
f1 = latex((x+r.a))
f2 = latex((x+r.b))
```

There are multiple methods for expanding a product of two binomials. We begin by rewriting the product.
$$(`r py$f1`)(`r py$f2`)$$

### Method 1: Distribution

The distributive property promises us that for all $a$, $b$, and $c$:
$$a(b+c) ~\equiv~ ab+ac$$

Since we are expanding $(`r py$f1`)(`r py$f2`)$, we can say $a=(`r py$f1`)$ and $b=x$ and $c=`r b`$, leading us to
$$(`r py$f1`)(x)~+~(`r py$f1`)(`r b`)$$
Multiplication is commutative, meaning the order does not matter. It promises that $de \equiv ed$ for all $d$ and $e$. We can rearrange the products in order to reuse the distributive property.

$$(x)(`r py$f1`)~+~(`r b`)(`r py$f1`)$$

For each term, $(x)(`r py$f1`)$ and $(`r b`)(`r py$f1`)$, reuse the distributive property.

$$x^2 ~+~ (`r a`)x ~+~ (`r b`)x ~+~ (`r p`) $$
Notice the two like terms: $`r a`x$ and $`r b`x$. Combine the like terms to get the final answer.

$$`r py$lexp1`$$

### Method 2: FOIL

The acronym FOIL stands for products of Firsts, Outsides, Insides, Lasts. For any $(a+b)(c+d)$:

* Firsts: $ac$
* Outsides: $ad$
* Insides: $bc$
* Lasts: $bd$

In our example, $(`r py$f1`)(`r py$f2`)$, we find the products:

* Firsts: $x^2$
* Outsides: $`r b`x$
* Insides: $`r a`x$
* Lasts: $`r p`$

When we add together those products, we get:

$$x^2 ~+~ (`r b`)x ~+~ (`r a`)x ~+~ (`r p`) $$
Notice the two like terms: $`r a`x$ and $`r b`x$. Combine the like terms to get the final answer.

$$`r py$lexp1`$$

### Method 3: Box

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

The factored form has two factors: $(`r py$f1`)$ and $(`r py$f2`)$. The two terms in the first factor are $x$ and $`r a`$. The two terms in the second factor are $x$ and $`r b`$. We put all four terms on the outside of the box. Then we find the products.

```{r,echo=F}
col1 = c("","$x$",paste0("$",a,"$",collapse=""))
col2 = c("","","")
col3 = c("","$x^2$",paste0("$",a,"x$"))
col4 = c("",paste0("$",b,"x$"),paste0("$",a*b,"$"))
mydf = data.frame(col1,col2,col3,col4)
colnames(mydf) = c("","","$x$",paste0("$",b,"$",collapse=""))
knitr::kable(mydf,format="html",table.attr='class="bordered-table"', align = "cccccc",row.names=F)
```

We write a sum of those 4 products.

$$x^2 ~+~ (`r b`)x ~+~ (`r a`)x ~+~ (`r p`) $$
Notice the two like terms: $`r a`x$ and $`r b`x$. Combine the like terms to get the final answer.

$$`r py$lexp1`$$

### Method 4: sum and product

Notice, we started with factored form: $$`r py$lexp2`$$

The sum of `r a` and `r b` is `r a+b`.
$$(`r a`)+(`r b`)=`r a+b`$$
The product of `r a` and `r b` is `r a*b`.
$$(`r a`)(`r b`) = `r a*b`$$

The sum and product show up consistently in the expanded form:

$$`r py$lexp1`$$



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r ans1`|`r ans2`
exname: expand_MC