```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
xs = seq(-3*pi,3*pi,pi/1080)
y1 = sin(xs)
y2 = cos(xs)
y3 = -sin(xs)
y4 = -cos(xs)
ys = list(y1,y2,y3,y4)
ord = sample(1:4)

ach = c("sin","cos","-sin","-cos")
al1 = paste0("* f(x) = ",ach,"(x)",collapse="\n")
al2 = paste0("* g(x) = ",ach,"(x)",collapse="\n")
al3 = paste0("* h(x) = ",ach,"(x)",collapse="\n")
al4 = paste0("* j(x) = ",ach,"(x)",collapse="\n")

sol1 = paste0(1*(ord[1]==1:4),collapse="")
sol2 = paste0(1*(ord[2]==1:4),collapse="")
sol3 = paste0(1*(ord[3]==1:4),collapse="")
sol4 = paste0(1*(ord[4]==1:4),collapse="")
```

Question
========

Match the graphs to their trigonometric functions.

```{r,echo=F,fig.dim=c(8,4)}
plot(0,0,"n",xlim=c(-7,7),ylim=c(-2,2),asp=1,xlab="x",ylab="y=f(x)")
arrows(-7,0,7,0,0.1,15,3)
arrows(0,2,0,-2,0.1,15,3)
lines(xs,ys[[ord[4]]])
```
\

* ##ANSWER1##


```{r,echo=F,fig.dim=c(8,4)}
plot(0,0,"n",xlim=c(-7,7),ylim=c(-2,2),asp=1,xlab="x",ylab="y=g(x)")
arrows(-7,0,7,0,0.1,15,3)
arrows(0,2,0,-2,0.1,15,3)
lines(xs,ys[[ord[4]]])
```
\

* ##ANSWER2##


```{r,echo=F,fig.dim=c(8,4)}
plot(0,0,"n",xlim=c(-7,7),ylim=c(-2,2),asp=1,xlab="x",ylab="y=h(x)")
arrows(-7,0,7,0,0.1,15,3)
arrows(0,2,0,-2,0.1,15,3)
lines(xs,ys[[ord[4]]])
```
\

* ##ANSWER3##

```{r,echo=F,fig.dim=c(8,4)}
plot(0,0,"n",xlim=c(-7,7),ylim=c(-2,2),asp=1,xlab="x",ylab="y=j(x)")
arrows(-7,0,7,0,0.1,15,3)
arrows(0,2,0,-2,0.1,15,3)
lines(xs,ys[[ord[4]]])
```
\

* ##ANSWER4##

Answerlist
--------

`r al1`
`r al2`
`r al3`
`r al4`

Solution
========

* You already know $y=\sin(t)$. It goes through the origin with a positive slope.
* You already know $y=\cos(t)$. Its initial value is 1; it goes through $(0,1)$.
* If you multiply the output of the function by $-1$, it causes a vertical reflection over the $x$-axis.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: wave_vert_reflect