```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
P = round(runif(1,0.2,1.4),1)*4

```

Question
========

Below, on the $ty$ plane, is a graph of $y=\sin\left(\frac{2\pi}{P}t\right)$ with a random parameter $P$.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
mm = 5
x = seq(-mm,mm,pi/360)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-mm,mm),ylim=c(-mm,mm),axes=F,ann=F)
for(i in seq(-mm,mm,0.1)){
    lines(c(-mm,mm),c(i,i),lwd=0.8,col="lightgrey")
    lines(c(i,i),c(-mm,mm),lwd=0.8,col="lightgrey")
}
for(i in seq(-mm,mm,0.5)){
    lines(c(-mm,mm),c(i,i),lwd=1,col="grey")
    lines(c(i,i),c(-mm,mm),lwd=1,col="grey")
}
for(i in seq(-mm,mm,1)){
    lines(c(-mm,mm),c(i,i),lwd=1.2,col="darkgrey")
    lines(c(i,i),c(-mm,mm),lwd=1.2,col="darkgrey")
}
for(i in seq(-mm,mm,5)){
    lines(c(-mm,mm),c(i,i),lwd=1.4,col="black")
    lines(c(i,i),c(-mm,mm),lwd=1.4,col="black")
}
for(i in -mm:mm){
    if(i!=0){
        text(0,i,i,adj=c(1.1,0.5))
        text(i,0,i,adj=c(0.5,1.1))
    }
}
text(mm*1.05,0,"t",adj=c(0.5,-0.5))
text(0,mm*1.05,"y",adj=c(-0.5,0.5))

arrows(-mm*1.05,0,mm*1.05,0,0.1,20,3,lwd=2)
arrows(0,-mm*1.05,0,mm*1.05,0.1,20,3,lwd=2)
lines(x,sin(2*pi/P*x),lwd=2,col="blue")

```
\

What is the value of $P$?


Solution
========

When we multiply the input of a function, the graphical result is a [horizontal compression](https://mathbitsnotebook.com/Algebra1/FunctionGraphs/FNGFunctionHorizontalStretchCompress.html).

For temporal waves, this horizontal stretching will alter the period and the frequency. If the period (time between repeats) increases, then the frequency decreases.

The parameter $P$, when in $y=\sin\left(\frac{2\pi}{P}t\right)$, is the period. To find the period, find the **time difference between peaks** (or troughs).

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
mm = 5
x = seq(-mm,mm,pi/360)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-mm,mm),ylim=c(-mm,mm),axes=F,ann=F)
for(i in seq(-mm,mm,0.1)){
    lines(c(-mm,mm),c(i,i),lwd=0.8,col="lightgrey")
    lines(c(i,i),c(-mm,mm),lwd=0.8,col="lightgrey")
}
for(i in seq(-mm,mm,0.5)){
    lines(c(-mm,mm),c(i,i),lwd=1,col="grey")
    lines(c(i,i),c(-mm,mm),lwd=1,col="grey")
}
for(i in seq(-mm,mm,1)){
    lines(c(-mm,mm),c(i,i),lwd=1.2,col="darkgrey")
    lines(c(i,i),c(-mm,mm),lwd=1.2,col="darkgrey")
}
for(i in seq(-mm,mm,5)){
    lines(c(-mm,mm),c(i,i),lwd=1.4,col="black")
    lines(c(i,i),c(-mm,mm),lwd=1.4,col="black")
}
for(i in -mm:mm){
    if(i!=0){
        text(0,i,i,adj=c(1.1,0.5))
        text(i,0,i,adj=c(0.5,1.1))
    }
}
text(mm*1.05,0,"t",adj=c(0.5,-0.5))
text(0,mm*1.05,"y",adj=c(-0.5,0.5))

arrows(-mm*1.05,0,mm*1.05,0,0.1,20,3,lwd=2)
arrows(0,-mm*1.05,0,mm*1.05,0.1,20,3,lwd=2)
lines(x,sin(2*pi/P*x),lwd=2,col="blue")

bmp = 0.2
yl = 1.5
lines(c(rep(-3/4*P,3),rep(1/4*P,3)),c(yl-bmp,yl+bmp,yl,yl,yl+bmp,yl-bmp),lwd=1.5,col="red")
text(-1/4*P,yl,P,col="red",adj=c(0.5,-0.2))

points(-3/4*P,1,pch=20,col="red")
points(1/4*P,1,pch=20,col="red")
text(-3/4*P,1,paste0("(",round(-3/4*P,1),",1)"),col="red",adj=c(1.1,-0.4))
text(1/4*P,1,paste0("(",round(1/4*P,1),",1)"),col="red",adj=c(-0.1,-0.4))

```
\

$$P ~=~ `r round(P/4,1)`-(`r round(-3/4*P,1)`) ~=~ `r P`$$

If the wave was spatial, the space difference between peaks is called the wavelength ($\lambda$). A spatiotemporal wave has both a period and a wavelength, and they are related by the wave's speed ($v$): $v=\frac{\lambda}{P}$.



Meta-information
============
extype: num
exsolution: `r P`
exname: sin_period
extol: 0.1