```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
while(T){
    A = round(runif(1,1.1,4),1)
    P = round(runif(1,0.2,1.4),1)*4
    D = round(runif(1,0.4,4),1)*sample(c(-1,1),1)
    if(A+abs(D)<4.7 && length(unique(abs(c(A,P,D))))==3){break}
}

aposs = round(seq(0.5,4,0.1),1)
pposs = round(seq(0.4,1.4*4,0.4),1)
dposs = round(seq(-4,4,0.1),1)

al1 = paste0("* ",aposs,collapse="\n")
al2 = paste0("* ",pposs,collapse="\n")
al3 = paste0("* ",dposs,collapse="\n")

sol1 = paste0(1*(aposs==A),collapse="")
sol2 = paste0(1*(pposs==P),collapse="")
sol3 = paste0(1*(dposs==D),collapse="")

```

Question
========

Below, on the $ty$ plane, is a graph of $y=A\sin\left(\frac{2\pi}{P}t\right)+D$ with random parameters $A$, $P$, and $D$.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
mm = 5
x = seq(-mm,mm,pi/360)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-mm,mm),ylim=c(-mm,mm),axes=F,ann=F)
for(i in seq(-mm,mm,0.1)){
    lines(c(-mm,mm),c(i,i),lwd=0.8,col="lightgrey")
    lines(c(i,i),c(-mm,mm),lwd=0.8,col="lightgrey")
}
for(i in seq(-mm,mm,0.5)){
    lines(c(-mm,mm),c(i,i),lwd=1,col="grey")
    lines(c(i,i),c(-mm,mm),lwd=1,col="grey")
}
for(i in seq(-mm,mm,1)){
    lines(c(-mm,mm),c(i,i),lwd=1.2,col="darkgrey")
    lines(c(i,i),c(-mm,mm),lwd=1.2,col="darkgrey")
}
for(i in seq(-mm,mm,5)){
    lines(c(-mm,mm),c(i,i),lwd=1.4,col="black")
    lines(c(i,i),c(-mm,mm),lwd=1.4,col="black")
}
for(i in -mm:mm){
    if(i!=0){
        text(0,i,i,adj=c(1.1,0.5))
        text(i,0,i,adj=c(0.5,1.1))
    }
}
text(mm*1.05,0,"t",adj=c(0.5,-0.5))
text(0,mm*1.05,"y",adj=c(-0.5,0.5))

arrows(-mm*1.05,0,mm*1.05,0,0.1,20,3,lwd=2)
arrows(0,-mm*1.05,0,mm*1.05,0.1,20,3,lwd=2)
lines(x,A*sin(2*pi/P*x)+D,lwd=2,col="blue")
```
\

What are the values of the parameters?

* $A=$ ##ANSWER1##
* $P=$ ##ANSWER2##
* $D=$ ##ANSWER3##

Answerlist
--------

`r al1`
`r al2`
`r al3`


Solution
========

Combine the techniques for finding amplitude, period, and midline.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
mm = 5
x = seq(-mm,mm,pi/360)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-mm,mm),ylim=c(-mm,mm),axes=F,ann=F)
for(i in seq(-mm,mm,0.1)){
    lines(c(-mm,mm),c(i,i),lwd=0.8,col="lightgrey")
    lines(c(i,i),c(-mm,mm),lwd=0.8,col="lightgrey")
}
for(i in seq(-mm,mm,0.5)){
    lines(c(-mm,mm),c(i,i),lwd=1,col="lightgrey")
    lines(c(i,i),c(-mm,mm),lwd=1,col="lightgrey")
}
for(i in seq(-mm,mm,1)){
    lines(c(-mm,mm),c(i,i),lwd=1.2,col="grey")
    lines(c(i,i),c(-mm,mm),lwd=1.2,col="grey")
}
for(i in seq(-mm,mm,5)){
    lines(c(-mm,mm),c(i,i),lwd=1.4,col="darkgrey")
    lines(c(i,i),c(-mm,mm),lwd=1.4,col="darkgrey")
}
for(i in -mm:mm){
    if(i!=0){
        text(0,i,i,adj=c(1.1,0.5),col="darkgrey")
        text(i,0,i,adj=c(0.5,1.1),col="darkgrey")
    }
}
text(mm*1.05,0,"t",adj=c(0.5,-0.5))
text(0,mm*1.05,"y",adj=c(-0.5,0.5))

arrows(-mm*1.05,0,mm*1.05,0,0.1,20,3,lwd=2,col="darkgrey")
arrows(0,-mm*1.05,0,mm*1.05,0.1,20,3,lwd=2,col="darkgrey")
lines(x,A*sin(2*pi/P*x)+D,lwd=2,col="lightblue")

bmp = 0
yl = A+D

abline(h=D+A,lwd=1,lty=2,col="brown")
text(4,A+D,paste0("y=",A+D),col="brown",adj=c(0.5,-0.3),cex=1)
abline(h=D-A,lwd=1,lty=2,col="brown")
text(4,D-A,paste0("y=",D-A),col="brown",adj=c(0.5,-0.3),cex=1)

abline(v=1/4*P,lwd=1,lty=2,col="brown")
text(1/4*P,-4*sign(D),paste0("t=",round(P/4,1)),col="brown",adj=c(0.5,-0.3),cex=1,srt=90)
abline(v=-3/4*P,lwd=1,lty=2,col="brown")
text(-3/4*P,-4*sign(D),paste0("t=",round(-3*P/4,1)),col="brown",adj=c(0.5,-0.3),cex=1,srt=90)

lines(c(rep(-3/4*P,3),rep(1/4*P,3)),c(yl-bmp,yl+bmp,yl,yl,yl+bmp,yl-bmp),lwd=3,col="red")
text(-1/4*P,A+D,P,col="red",adj=c(0.5,-0.3),cex=1.5)

abline(h=D,col="maroon",lwd=3)
text(4,D,paste0("y=",D),col="maroon",adj=c(0.5,-0.3),cex=1.5)

x1 = 1/4*P
lines(c(x1-bmp,x1+bmp,x1,x1,x1-bmp,x1+bmp),c(D,D,D,D+A,D+A,D+A),col="darkorange",lwd=3)
text(x1,D+A/2,round(A,1),adj=c(-0.3,0.5),col="darkorange",cex=1.5)


```
\

Identify the maximum and minimum.

$$\mathrm{max}~=~`r D+A`$$
$$\mathrm{min}~=~`r D-A`$$

The amplitude is half the difference of max and min.

$$A~=~\frac{(`r D+A`)-(`r D-A`)}{2}~=~`r A`$$

The midline is at the average of the max and min.

$$D~=~\frac{(`r D+A`)+(`r D-A`)}{2}~=~`r D`$$

To get the period, find the $t$ coordinates of two peaks.

$$t_\mathrm{peak_1}=`r round(-3*P/4,1)`$$
$$t_\mathrm{peak_2}=`r round(P/4,1)`$$

The period is the difference of those times.

$$P ~=~ `r round(P/4,1)`-(`r round(-3/4*P,1)`) ~=~ `r P`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: sin_amp_per_mid