```{r,echo=F,warning=F}
A = round(runif(1,0.7,4),1)
P = round(runif(1,2,6.6)/4,1)*4
B = 2*pi/P
D = round(runif(1,0.1,4.9-A),1)*sample(c(-1,1),1)
h = round(runif(1,0.1,P),1)
C = h*B
```

Question
========

A sinusoidal wave is graphed below.

```{r,fig.dim=c(9,9),echo=F}
par(mar=c(4,4,4,4),pty="s")
plot(0,0,type="n",xlim=c(-5,5),ylim=c(-5,5),xlab="t",ylab="y")
axis(3)
axis(4)
mtext("t",3,3)
mtext("y",4,3)
for(i in seq(-6,6,0.1)){
  if(i%%1==0){
    abline(h=i,col="darkgrey",lwd=1.4)
    abline(v=i,col="darkgrey",lwd=1.4)
  } else if(abs(i%%1)==0.5) {
    abline(h=i,col="darkgrey",lwd=0.8)
    abline(v=i,col="darkgrey",lwd=0.8)
  } else {
    abline(h=i,col="grey",lwd=0.5)
    abline(v=i,col="grey",lwd=0.5)
  }
}

arrows(0,-5,0,5,length=0.1,angle=10,code=3,lwd=1.5)
arrows(-5,0,5,0,length=0.1,angle=10,code=3,lwd=1.5)

t = seq(-6,6,0.01)
lines(t,A*sin(B*t+C)+D,lwd=3,col="blue")
```
\

Estimate the **period** of the [sinusoidal](https://www.khanacademy.org/math/algebra2/x2ec2f6f830c9fb89:trig/x2ec2f6f830c9fb89:amp-mid-period/a/midline-amplitude-and-period-review) function graphed above.


Solution
========

Find the time difference between corresponding points in sequential repetitions.

```{r,fig.dim=c(9,9),echo=F}
par(mar=c(4,4,4,4),pty="s")
plot(0,0,type="n",xlim=c(-5,5),ylim=c(-5,5),xlab="t",ylab="y")
axis(3)
axis(4)
mtext("t",3,3)
mtext("y",4,3)
for(i in seq(-6,6,0.1)){
  if(i%%1==0){
    abline(h=i,col="darkgrey",lwd=1.4)
    abline(v=i,col="darkgrey",lwd=1.4)
  } else if(abs(i%%1)==0.5) {
    abline(h=i,col="darkgrey",lwd=0.8)
    abline(v=i,col="darkgrey",lwd=0.8)
  } else {
    abline(h=i,col="grey",lwd=0.5)
    abline(v=i,col="grey",lwd=0.5)
  }
}

arrows(0,-5.2,0,5.2,length=0.1,angle=10,code=3,lwd=1.5)
arrows(-5.2,0,5.2,0,length=0.1,angle=10,code=3,lwd=1.5)

t = seq(-6,6,0.01)
lines(t,A*sin(2*pi/P*(t+h))+D,lwd=3,col="blue")

xmas = -h+P/4+P*(-2:2)
xmis = -h+3*P/4+P*(-2:2)
xmas = xmas[abs(xmas)<5]
xmis = xmis[abs(xmis)<5]
if(length(xmas)>1){
  xs = round(xmas,2)
  ys = round(rep(A+D,length(xs)),2)
  for(j in 1:length(xs)){
    text(xs[j]+0.6,ys[j]+0.2,paste0("(",xs[j],", ",ys[j],")"),col="purple",cex=1)
    text(xs[j]-0.2,-4.5,
         paste0("t = ",xs[j],collapse=""),srt=90,cex=2,col="purple")
  }
} else {
  xs = round(xmis,2)
  ys = round(rep(-A+D,length(xs)),2)
  for(j in 1:length(xs)){
    text(xs[j]+0.6,ys[j]-0.2,paste0("(",xs[j],", ",ys[j],")"),col="purple",cex=1)
    text(xs[j]-0.2,-4.5,
         paste0("t = ",xs[j],collapse=""),srt=90,cex=2,col="purple")
  }
}
points(xs,ys,pch=19,col="purple",cex=2)
abline(v=xs,col="purple",lty=2,lwd=3)

arrows(xs[1],-3,xs[2],-3,0.1,10,3,col="red",lwd=4)
text(mean(xs[1:2]),-2.5,paste0("P = ",P,collapse=""),col="red",cex=2)

```
\

$$P~=~ (`r xs[2]`)-(`r xs[1]`)$$
$$P = `r P`$$


This exact function could be plotted with the following algebraic definition:
$$y(t) = `r A` \sin\left(\frac{2\pi}{`r P`}(t+`r h`)\right)+(`r D`)$$

The amplitude is `r A`; the period is `r P`; the horizontal shift is left by `r h`; and the midline is $y=`r D`$.



Meta-information
============
extype: num
exsolution: `r P`
exname: estimate_period
extol: 0.1