```{r,echo=F,warning=F}
A = round(runif(1,0.7,4),1)
P = round(runif(1,2,8)/4,1)*4
B = 2*pi/P
D = round(runif(1,0.1,4.9-A),1)*sample(c(-1,1),1)
h = round(runif(1,0,P),1)
C = h*B
```

Question
========


A sinusoidal wave is graphed below.

```{r,fig.dim=c(9,9),echo=F}
par(mar=c(4,4,4,4),pty="s")
plot(0,0,type="n",xlim=c(-5,5),ylim=c(-5,5),xlab="t",ylab="y")
axis(3)
axis(4)
mtext("t",3,3)
mtext("y",4,3)
for(i in seq(-6,6,0.1)){
  if(i%%1==0){
    abline(h=i,col="darkgrey",lwd=1.4)
    abline(v=i,col="darkgrey",lwd=1.4)
  } else if(abs(i%%1)==0.5) {
    abline(h=i,col="darkgrey",lwd=0.8)
    abline(v=i,col="darkgrey",lwd=0.8)
  } else {
    abline(h=i,col="grey",lwd=0.5)
    abline(v=i,col="grey",lwd=0.5)
  }
}

arrows(0,-5,0,5,length=0.1,angle=10,code=3,lwd=1.5)
arrows(-5,0,5,0,length=0.1,angle=10,code=3,lwd=1.5)

t = seq(-6,6,0.01)
lines(t,A*sin(B*t+C)+D,lwd=3,col="blue")
```
\

The midline is at $y=D$. Find $D$.

Solution
========

The vertical offset can be found by subtracting the amplitude from the maximum.

The amplitude of a [sinusoidal function](https://en.wikipedia.org/wiki/Sine_wave) is half the difference between the maximum $y$ and the minimum $y$. 

```{r,fig.dim=c(9,9),echo=F}
par(mar=c(4,4,4,4),pty="s")
plot(0,0,type="n",xlim=c(-5,5),ylim=c(-5,5),xlab="t",ylab="y")
axis(3)
axis(4)
mtext("t",3,3)
mtext("y",4,3)
for(i in seq(-6,6,0.1)){
  if(i%%1==0){
    abline(h=i,col="darkgrey",lwd=1.4)
    abline(v=i,col="darkgrey",lwd=1.4)
  } else if(abs(i%%1)==0.5) {
    abline(h=i,col="darkgrey",lwd=0.8)
    abline(v=i,col="darkgrey",lwd=0.8)
  } else {
    abline(h=i,col="grey",lwd=0.5)
    abline(v=i,col="grey",lwd=0.5)
  }
}

arrows(0,-5.2,0,5.2,length=0.1,angle=10,code=3,lwd=1.5)
arrows(-5.2,0,5.2,0,length=0.1,angle=10,code=3,lwd=1.5)

t = seq(-6,6,0.01)
lines(t,A*sin(B*t+C)+D,lwd=2,col="blue")

abline(h=A+D,col="red",lwd=2,lty=2)
text(-4,A+D+0.2,paste0("y = ",sprintf("%.2f",A+D)),col="red")
abline(h=-A+D,col="red",lwd=2,lty=2)
text(-4,-A+D-0.2,paste0("y = ",sprintf("%.2f",-A+D)),col="red")

abline(h=D,col=rgb(0.1,0.1,0.1),lwd=2,lty=2)
text(-4.5,D+0.25*sign(D),paste0("y = ",D),col=rgb(0.1,0.1,0.1),cex=2)
arrows(-3,-A+D,-3,A+D,0.1,10,3,col="red",lwd=4)
text(-2.5,D,2*A,col="red",cex=3)

arrows(3,D,3,A+D,0.1,10,3,col="purple",lwd=4)
text(3.5,D+A/2,A,col="purple",cex=3)


```
\

$$A~=~\frac{(`r A+D`)-(`r -A+D`)}{2} ~=~ \frac{`r 2*A`}{2} ~=~ `r A`$$

The amplitude is `r A`. Subtract `r A` from `r A+D` (the maximum).

$$D ~=~ `r A+D`-`r A`$$
$$D ~=~ `r D`$$


This exact function could be plotted with the following algebraic definition:
$$y(t) = `r A` \sin\left(\frac{2\pi}{`r P`}(t+`r h`)\right)+(`r D`)$$

The amplitude is `r A`; the period is `r P`; the horizontal shift is left by `r h`; and the midline is $y=`r D`$.


Meta-information
============
extype: num
exsolution: `r D`
exname: estimate_midline
extol: 0.1