```{r,echo=F,warning=F}
dt = 0.1
tf = 5
H = 4 #height of room
miny = runif(1,0.4,1)
A = runif(1,0.4,1.2)
maxy = miny+2*A
P = runif(1,1,3)
B = 2*pi/P
D = mean(c(miny,maxy))
C = 0 #runif(1,0,2*pi)
tdata = seq(0,tf,dt)
ydata = round(A*cos(B*tdata+C)+D+runif(length(tdata),-0.04,0.04),2)

data = data.frame(tdata,ydata)
mod <- ydata ~ a1*sin(b1*tdata+c1)+d1
start_vals <- list(a1=A, b1=B, c1=C+pi/2, d1=D)
fit <- nls(mod, data = data, start = start_vals)
cf = summary(fit)$coefficients

Pfit = 2*pi/cf[2]

```

Question
========

The canonical example of [simple harmonic motion](https://en.wikipedia.org/wiki/Simple_harmonic_motion) is a mass-spring system. A lightweight spring is attached to a ceiling, and a moderately heavy mass is attached to the dangling end. If the mass is pulled away from its resting elevation, and released, the weight will bounce up and down, approximately following a sinusoidal function in time. By placing the mass-spring system close to a marked wall, and by using a camera with a long [focal length](https://en.wikipedia.org/wiki/Focal_length#In_photography), the position (in meters above floor) of the mass was tracked over time (in seconds).

Of course, in order to exactly follow a sinusoidal path through time, a few unrealistic assumptions need to be true. There should be no friction (no air resistance nor internal resistance of the bending spring). Also, the spring should exactly follow [Hooke's law](https://en.wikipedia.org/wiki/Hooke%27s_law).

```{r,echo=F,fig.dim=c(3,3),animation.hook='gifski',interval=dt}
nloop = round((H-D)/0.1)
boxr = 0.2
yspr = seq(0,1,1/(nloop*12))
xspr = H/2+boxr/2*sin(yspr*nloop*2*pi)
allpoints = list()
allexts = c()
for(i in seq(0,tf,dt)){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(0,H),ylim=c(0,H),axes=F,ann=F)
    y = A*cos(B*i+C)+D
    ybt = y+boxr
    lines(xspr,yspr*(H-ybt)+ybt,col="grey")
    polygon(H/2+boxr*c(-1,-1,1,1),y+boxr*c(1,-1,-1,1),col="blue")
    polygon(c(-1,-1,5,5),c(H*2,H,H,H*2),col="darkgrey")
    polygon(c(-1,-1,5,5),c(-H,0,0,-H),col="darkgrey")
    text(0,0,paste0("t = ",sprintf("%.01f s",i)),adj=c(-0.3,-0.3))
    for(yy in seq(0.1,H-0.1,0.1)){
        lines(c(H/2-boxr*3,H/2-2*boxr),c(yy,yy),col="lightgrey",lwd=0.7)
    }
    for(yy in seq(0,H,0.5)){
        if(yy>0 && yy<H){
            lines(c(H/2-boxr*3.5,H/2-1.5*boxr),c(yy,yy),col="grey",lwd=0.9)
        }
    }
    for(yy in seq(0,H,1)){
        if(yy>0 && yy<H){
            lines(c(H/2-boxr*4,H/2-1*boxr),c(yy,yy),col="darkgrey",lwd=1.1)
            text(H/2-boxr*4,yy,paste0(round(yy)," m"),adj=c(1.3,0.5),col="darkgrey")}
    }
    extent = i/tf
    allpoints[[length(allpoints)+1]] = c(H/2-boxr*2.5,y)
    allexts = c(allexts,extent)
    for(j in 1:length(allexts)){
        points(allpoints[[j]][1],allpoints[[j]][2],pch=19,cex=1.4)
        points(allpoints[[j]][1],allpoints[[j]][2],pch=19,cex=1,col=hsv(allexts[j],1,0.9))
    }
    points(H/2,y,pch=19,cex=1.4)
    points(H/2,y,pch=19,col=hsv(extent,1,0.9))
}
```
\

After capturing the video, elevation measurements were recorded every 0.1 seconds over an interval of 5 seconds.

| $t$ (time in seconds) | $y$ (height in meters) |
|:---:|:---:|
`r paste0("| ",sprintf("%.01f",tdata)," | ",sprintf("%.02f",ydata)," |",collapse="\n")`

1. Run a sinusoidal regression on the data.
2. The regression will have the form $y = A\sin(Bt+C)+D$, where the parameters are $A$, $B$, $C$, and $D$, which are the amplitude, [angular frequency](https://en.wikipedia.org/wiki/Angular_frequency), phase shift, and vertical offset (or midline constant).
3. Using the angular frequency, calculate the [period](https://en.wikipedia.org/wiki/Periodic_function) ($P$) using $P=\frac{2\pi}{B}$.

Using the process outlined above, report the period of the best-fit curve. The tolerance is $\pm 0.001$ seconds.


Solution
========

1. Copy and paste data into a [Desmos](https://www.desmos.com/calculator) expression.
2. Click the `Add Regression` icon.
3. Choose `Sinusoidal Regression`.
4. The best-fit curve has four parameters:
$$y~=~`r round(cf[1],5)`\cdot \sin(`r round(cf[2],5)`t+`r round(cf[3],5)`)+`r round(cf[4],5)`$$
5. Recognize that the angular frequency is the multiplier inside the argument.
$$B=`r round(cf[2],5)`$$
6. Use the formula to calculate the period from the angular frequency. (This formula is always the same.)
$$P~=~\frac{2\pi}{B}$$
$$P~=~\frac{2\pi}{`r round(cf[2],5)`}$$
$$P~=~`r signif(Pfit,5)`$$




Meta-information
============
extype: num
exsolution: `r Pfit`
exname: mass_spring_period
extol: 0.001