```{r,echo=F,warning=F}
par(scipen=99)
A = round(runif(1,20,125),1) #m, radius of ferris wheel
v = runif(1,0.5,4) #m/s
B = v/A #radians/s
f = B/2/pi #turns/s
P = round(1/f,0)
while(T){
    t = round(P*runif(1,2,3),0)
    x = A*sin(B*t)
    if(abs(x)>5 && abs(abs(x)-A)>3){break}
}
B = signif(2*pi/P,6)
tfin = t
xfin = x
axfin = abs(x)

```

Question
========

A Ferris wheel has a radius of `r A` meters, and (while spinning) one rotation takes `r P` seconds.

Samuel gets into a carriage at the bottom of the Ferris wheel. At $t=0$, the wheel starts spinning, and it spins continuously for `r t` seconds until an abrupt stop. At that moment, Samuel drops his keys, which fall directly down to the ground.

```{r,echo=F,fig.dim=c(4,4),animation.hook='gifski',interval=0.15}
drawstills = function(){
    polygon(c(-2,2,2,-2),c(-2,-2,2,2),col="skyblue")
    polygon(c(-2,2,2,-2),c(-1,-1,-2,-2),col="darkgreen")
    thcirc = seq(0,2*pi,pi/360)
    for(tthh in seq(0,2*pi,pi/30)){
        lines(c(0,cos(tthh+thcur)),c(0.05,0.05+sin(tthh+thcur)),lwd=0.5,col="grey")
    }
    lines(c(-1.05,0,1.05),c(-1,0.05,-1),col="black",lwd=3)
    lines(c(-1.05,0,1.05),c(-1,0.05,-1),col="white",lwd=2)
    lines(cos(thcirc),sin(thcirc)+0.05,col="black",lwd=3)
    lines(cos(thcirc),sin(thcirc)+0.05,col="white",lwd=2)
}
drawcar = function(x,y){
    wid = 0.025
    polygon(c(x,x-wid,x-wid,x+wid,x+wid),c(y+0.005,y-wid,y-2*wid,y-2*wid,y-wid),
            lwd=1,col="white",border="black")
}
drawsam = function(x,y){
    wid = 0.025
    swid = wid/2
    lines(c(x-swid,x,x,x-swid,x,x+swid,x,x,x+swid),
          c(y-1.2*wid,y-1.2*wid,y-wid*1.5,y-2*wid,y-wid*1.5,y-2*wid,y-1.5*wid,
            y-1.2*wid,y-1.2*wid),col="black")
    points(x,y-0.7*wid,pch=19,cex=0.3)
}

nframes = 40
nrots = t/P
drad = nrots*2*pi/nframes
totrad = nrots*2*pi
rads = seq(0,totrad,drad)

for(thcur in rads){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
    drawstills()
    thadd = seq(0,2*pi,2*pi/12)
    for(thc in thadd){
        drawcar(cos(thc+thcur),0.05+sin(thc+thcur))
    }
    drawsam(sin(thcur),0.05-cos(thcur))
}
ystop = 0.05-cos(totrad)
xstop = sin(totrad)

ykey = seq(ystop,-1,length.out=10)

for(i in 1:10){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
    drawstills()
    thadd = seq(0,2*pi,2*pi/12)
    for(thc in thadd){
        drawcar(cos(thc+totrad),0.05+sin(thc+totrad))
    }
    drawsam(sin(totrad),0.05-cos(totrad))
    points(xstop,ykey[i],pch=8,col="gold")
}

for(i in 1:30){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))
    drawstills()
    thadd = seq(0,2*pi,2*pi/12)
    for(thc in thadd){
        drawcar(cos(thc+totrad),0.05+sin(thc+totrad))
    }
    drawsam(sin(totrad),0.05-cos(totrad))
    points(xstop,-1,pch=8,col="gold")
    bmp = 0.02
    lines(c(0,0),c(0.05,-1),col="red",lty=2)
    lines(c(0,0,0,xstop,xstop,xstop),c(-1-bmp,-1+bmp,-1,-1,-1-bmp,-1+bmp),lwd=3,col="red")
    text(xstop/2,-1+rnorm(1,0,0.005),"?",col="red",adj=c(0.5,-0.4),cex=2)
}

par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1),ylim=c(-1,1))

```
\

How far, in meters, are the keys from where Samuel entered the carriage? The tolerance is $\pm 0.1$ meters.

Solution
========

Since Samuel got on at the bottom of the wheel, he begins at the midline (horizontally). Thus, we can use a stretched, but unshifted, sine wave to model Samuel's horizontal position over time.

$$x~=~A\cdot\sin(Bt)$$

The amplitude will match the radius of the wheel.

$$A=`r A`$$

To get $B$, the angular frequency, we divide $2\pi$ by the period (which was given to us).

$$B~=~\frac{2\pi}{P}$$

$$B~=~\frac{2\pi}{`r P`}$$

$$B~\approx~`r B`$$

Notice,

$$x~=~`r A`\cdot\sin(`r B`\cdot `r t`)$$

$$x~=~`r xfin`$$

We only care about the absolute value of $x$.

$$|x| ~=~ `r axfin`$$



Meta-information
============
extype: num
exsolution: `r axfin`
exname: ferris_wheel_key_drop
extol: 0.1