```{r,echo=F,warning=F}
# F-TF.B.5. Choose trigonometric functions to model periodic phenomena with specified amplitude, frequency, and midline.
P = sample(c(4,6,8,10),1)
A = sample(c(2,3,4),1)*sample(c(-1,1),1)
D = sample(c(-2,-1,1,2),1)
gch = c("sin","cos")
cs = sample(c("cos","sin"))
x = seq(-10,10,0.05)
if(cs[1]=="cos"){
    y = A*cos(2*pi/P*x)+D
    st = paste0("y=",A,"\\cos\\left(\\frac{\\pi}{",round(P/2),"}t\\right)+",D)
    st = gsub("+-","-",st,fixed=T)
}
if(cs[1]=="sin"){
    y = A*sin(2*pi/P*x)+D
    st = paste0("y=",A,"\\sin\\left(\\frac{\\pi}{",round(P/2),"}t\\right)+",D)
    st = gsub("+-","-",st,fixed=T)
}
B = 2*pi/P
f = 1/P
g = cs[1]

achA = c(-4,-3,-2,-1,0,1,2,3,4)
alA = paste0("* ",achA,collapse="\n")
solA = paste0(1*(achA==A),collapse="")

achg = gch
alg = paste0("* ",achg,collapse="\n")
solg = paste0(1*(achg==g),collapse="")

achP = 2:12
alP = paste0("* ",achP,collapse="\n")
solP = paste0(1*(achP==P),collapse="")

achD = c(-3,-2,-1,0,1,2,3)
alD = paste0("* ",achD,collapse="\n")
solD = paste0(1*(achD==D),collapse="")

statements = c(paste0("The amplitude is ",abs(A)," meters."),
               paste0("The period is ",P," seconds."),
               paste0("The midline is at ",D," meters."))

x = seq(-10,10,0.05)
if(g=="sin" && A>0){
    s4 = "At $t=0$, the mass is at the midline with an upwards velocity."
    y = A*sin(2*pi*f*x)+D
}
if(g=="sin" && A<0){
    s4 = "At $t=0$, the mass is at the midline with an downwards velocity."
    y = A*sin(2*pi*f*x)+D
}
if(g=="cos" && A>0){
    s4 = "At $t=0$, the mass is at the maximum height."
    y = A*cos(2*pi*f*x)+D
}
if(g=="cos" && A<0){
    s4 = "At $t=0$, the mass is at the minimum height."
    y = A*cos(2*pi*f*x)+D
}

st = sample(statements)
st = paste0(1:3,". ",st,collapse="\n")


Dstr = paste0("+",D)
if(D<0){
    Dstr = paste0(D)
}


```

Question
========

A [mass-spring system](https://en.wikipedia.org/wiki/Simple_harmonic_motion#Examples) oscillates over time. The position (in meters) of the mass is plotted as a function of time (in seconds).

```{r,echo=F,fig.dim=c(7,3.5)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-10,10),ylim=c(-6,6),asp=1)
for(xx in seq(-10,10,1)){
    lines(c(xx,xx),c(-6,6),col="grey",lwd=0.8)    
}
for(yy in seq(-6,6,1)){
    lines(c(-10,10),c(yy,yy),col="grey",lwd=0.8)    
}
for(xx in seq(-10,10,5)){
    lines(c(xx,xx),c(-6,6),col="darkgrey",lwd=1.2)    
}
for(yy in seq(-5,5,5)){
    lines(c(-10,10),c(yy,yy),col="darkgrey",lwd=1.2)    
}
arrows(-10.5,0,10.5,0,0.1,15,3,lwd=1.5)
arrows(0,-6.5,0,6.5,0.1,15,3,lwd=1.5)
text(10.5,0,"t",adj=c(0.5,1.3))
text(10,0,"10",adj=c(0.5,-0.3))
text(-10,0,"-10",adj=c(0.5,-0.3))
text(0,6.3,"y",adj=c(1.3,0.5))
text(0,5,"5",adj=c(-0.3,0.5))
text(0,-5,"-5",adj=c(-0.3,0.5))

lines(x,y,col="blue",lwd=2)
```
\

Choose a trigonometric function ($g$), and the parameters ($A$, $P$, and $D$), to model this oscillatory motion.

$$y~=~A\cdot g\left(\frac{2\pi}{P}t\right)+D$$

* $g=$ ##ANSWER1##
* $A=$ ##ANSWER2##
* $P=$ ##ANSWER3##
* $D=$ ##ANSWER4##


Answerlist
--------

`r alg`
`r alA`
`r alP`
`r alD`

Solution
========

`r paste0("* ",statements,collapse="\n")`

The amplitude is the absolute value of $A$.
$$|A|~=~`r abs(A)`$$

1. If when $t=0$ (at $y$-axis) the wave is at midline and is increasing, then $A>0$ and $g=\sin$.
2. If when $t=0$ (at $y$-axis) the wave is at midline and is decreasing, then $A<0$ and $g=\sin$.
3. If when $t=0$ (at $y$-axis) the wave is at maximum, then $A>0$ and $g=\cos$.
4. If when $t=0$ (at $y$-axis) the wave is at minimum, then $A<0$ and $g=\cos$.

$$A=`r A`$$
$$g=\`r g`$$


The vertical shift is determined by the midline at $y=`r D`$.

$$D=`r D`$$

So,

$$y ~=~ `r signif(A,2)`\cdot\`r g`\left(\frac{2\pi}{`r P`}t\right)`r Dstr`$$

* $g=\`r g`$ 
* $A=`r A`$
* $P=`r P`$
* $D=`r D`$

### Extra stuff

Of course, we would typically simplify the fraction.


$$y ~=~ `r signif(A,2)`\cdot\`r g`\left(\frac{\pi}{`r round(P/2)`}t\right)`r Dstr`$$

The value $\frac{\pi}{`r round(P/2)`}\approx`r B`$ is called the angular frequency, which we've been representing with $B$.

$$B=\frac{2\pi}{P}$$
$$P=\frac{2\pi}{B}$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r solg`|`r solA`|`r solP`|`r solD`
exname: pick_wave_pams3