```{r,echo=F,warning=F}
n = 60
height = runif(1,0.1,4) #meters
wavelength = 24.635*height^0.799073 #meters
period = 0.981497*sqrt(wavelength) #seconds
velocity = wavelength/period #m/s
windspeed = velocity*1.73065 #m/s
interval = period/n

L = signif(wavelength,3)
v = signif(velocity,3)
P = L/v
h = signif(height,3)

str1 = paste0("The wave height equals ",h," meters.")
str2 = paste0("The wavelength equals ",L," meters.")
str3 = paste0("The wave speed equals ",v," meters/second.")
strs = sample(c(str1,str2,str3))

```

Question
========

A mallard floats in a large ocean (in deep water far from shore). The mallard is not moving in [cardinal directions](https://en.wikipedia.org/wiki/Cardinal_direction), but the mallard is bobbing up and down as the [wind waves](https://en.wikipedia.org/wiki/Wind_wave) pass.

In deep water, with a large fetch, when wind is consistently blowing at `r signif(windspeed,3)` meters per second, the waves will have the following (approximate) characteristics:

* `r strs[1]`
* `r strs[2]`
* `r strs[3]`

I've animated this below... somewhat to scale.

```{r,echo=F,fig.dim=c(4,3),animation.hook='gifski',interval=interval}

drawduck = function(x,y,s=0.3,rot=0){
    th = seq(0,2*pi,pi/360)
    x1 = cos(th)*s
    y1 = sin(th)*s/3+s/3
    x1r = x1*cos(rot)-y1*sin(rot)
    y1r = x1*sin(rot)+y1*cos(rot)
    polygon(x1r+x,y1r+y,col="brown",lwd=0.7)
    x2 = cos(pi/4)*s*5/4+cos(th)*s/4
    y2 = sin(pi/4)*s/3*5/4+s/3+sin(th)*s/4
    x2r = x2*cos(rot)-y2*sin(rot)
    y2r = x2*sin(rot)+y2*cos(rot)
    polygon(x2r+x,y2r+y,col="darkgreen",lwd=0.7)
    x3 = cos(pi/4)*s*5/4+s/4+c(0,0,s/4)
    y3 = sin(pi/4)*s/3*5/4+s/3+c(-s/8,s/12,-s/12)
    x3r = x3*cos(rot)-y3*sin(rot)
    y3r = x3*sin(rot)+y3*cos(rot)
    polygon(x3r+x,y3r+y,col="yellow",lwd=0.7)
    
}
for(t in seq(0,period,length.out=n)){
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-1,7),ylim=c(-3,3),asp=1,axes=F,ann=F)
    A = height/2
    B1 = 2*pi/wavelength
    B2 = 2*pi/period
    xx = seq(-1,7,0.01)
    polygon(c(-1,xx,7),c(-3,A*sin(B1*xx+B2*t),-3),col="blue",lwd=0.7)
    rotang = atan(A*B1*cos(B2*t))
    drawduck(0,A*sin(B2*t),0.2,rotang) 
}

```
\

What is the period (in seconds) of these waves? In other words, how much time does it take for the mallard to complete a cycle? The tolerance is $\pm 0.01$ seconds.


Solution
========


When you have the wavelength ($\lambda$) and the wave speed ($v$), it is easy to calculate the period ($P$).

$$P~=~\frac{\lambda}{v}$$

Notice, that [dimensional analysis](https://en.wikipedia.org/wiki/Dimensional_analysis) can help confirm the relationship.

$$\mathrm{(second)}~=~\frac{\mathrm{(meter)}}{\left(\mathrm{\frac{meter}{second}}\right)}$$

You should get approximately $P=`r sprintf("%.02f",P)`$ seconds.


Meta-information
============
extype: num
exsolution: `r P`
exname: bobbing_duck
extol: 0.01