```{r,echo=F,warning=F}
## This uses gifski
## install.packages('gifski', repos = c('https://r-rust.r-universe.dev', 'https://cloud.r-project.org'))
## https://r-rust.r-universe.dev/gifski

n = 8
ts = seq(0,2*pi-2*pi/n,length.out=n)

fs = c("y=\\sin(x)\\cdot \\cos(t)",
       "y=\\frac{\\sin(x-t)+\\sin(x+t)}{2}",
       "y=\\sin(x+t)",
       "y=\\sin(x)\\cos(t)+\\cos(x)\\sin(t)",
       "y=\\sin(x)+\\cos(t)",
       "y=\\sin(x\\cdot t)")

ans = c(1,1,2,2,3,4)

mkf = function(typ,ttl){
  x = seq(-2*pi,2*pi,length.out=1000)
  for (t in ts){
    par(mar=c(5,5,2,2))
    if(typ==1){
      plot(x,sin(x)*cos(t),type="l",xlim=c(-6,6),ylim=c(-3,3),xlab="x",ylab="y",main=ttl)
    }
    if(typ==2){
      plot(x,sin(x+t),type="l",xlim=c(-6,6),ylim=c(-3,3),xlab="x",ylab="y",main=ttl)
    }
    if(typ==3){
      plot(x,sin(x)+cos(t),type="l",xlim=c(-6,6),ylim=c(-3,3),xlab="x",ylab="y",main=ttl)
    }
    if(typ==4){
      plot(x,sin(x*t),type="l",xlim=c(-6,6),ylim=c(-3,3),xlab="x",ylab="y",main=ttl)
    }
    
  }
}

ord = sample(1:4)
ord2 = sample(1:length(fs))

sol1 = paste0(1*(ans[ord2[1]]==ord),collapse="")
sol2 = paste0(1*(ans[ord2[2]]==ord),collapse="")
sol3 = paste0(1*(ans[ord2[3]]==ord),collapse="")
sol4 = paste0(1*(ans[ord2[4]]==ord),collapse="")
sol5 = paste0(1*(ans[ord2[5]]==ord),collapse="")
sol6 = paste0(1*(ans[ord2[6]]==ord),collapse="")

```

Question
========

Match the animations to the equations.

```{r, animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(6,3)}
mkf(ord[1],"A")
```
\

```{r, animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(6,3)}
mkf(ord[2],"B")
```
\


```{r, animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(6,3)}
mkf(ord[3],"C")
```
\

```{r, animation.hook="gifski",interval=0.2,echo=F,fig.dim=c(6,3)}
mkf(ord[4],"D")
```
\

Match each equation to its animation. In the animations, $t$ goes from 0 to $2\pi$.

* $`r fs[ord2[1]]`~\to$  ##ANSWER1##
* $`r fs[ord2[2]]`~\to$  ##ANSWER2##
* $`r fs[ord2[3]]`~\to$  ##ANSWER3##
* $`r fs[ord2[4]]`~\to$  ##ANSWER4##
* $`r fs[ord2[5]]`~\to$  ##ANSWER5##
* $`r fs[ord2[6]]`~\to$  ##ANSWER6##

Answerlist
--------

* A
* B
* C
* D
* A
* B
* C
* D
* A
* B
* C
* D
* A
* B
* C
* D
* A
* B
* C
* D
* A
* B
* C
* D


Solution
========

Use Desmos to make each animation. Set $t$ to a slider with boundaries of 0 and $2\pi$. Press play.

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`|`r sol6`
exname: match_animations