```{r,echo=F}
pn = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

while(T){
    abcd = sample(1:9,4,T)*sample(c(-1,1),4,T)
    A = abcd[1]
    B = abcd[2]
    C = abcd[3]
    D = abcd[4]
    a = A*C
    b = A*D+B*C
    c = B*D
    if(min(abs(c(a,b,c)))>0){break}
}


exp1 = pn(c(A,B),c(1,0))
exp2 = pn(c(C,D),c(1,0))
```




Question
========

Consider the following product of linear binomials:

$$(`r exp1`)(`r exp2`)$$

When the expression is expanded and like terms are combined, an equivalent expression can be expressed in standard form:

$$ax^2+bx+c$$

where $a$, $b$, and $c$ are integers. 

* What is the value of $b$?


Solution
========

You could use the box method.

```{r,echo=F,fig.dim=c(2,2)}
library(latex2exp)

par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,6),ylim=c(0,6),axes=F,ann=F)
abline(h=0)
abline(h=2)
abline(h=4,lwd=3)
abline(v=2,lwd=3)
abline(v=4)
abline(v=6)

text(3,5,TeX(paste0("$",pn(C,1),"$")))
text(5,5,TeX(paste0("$",pn(D,0),"$")))

text(1,3,TeX(paste0("$",pn(A,1),"$")))
text(1,1,TeX(paste0("$",pn(B,0),"$")))

text(3,3,TeX(paste0("$",pn(A*C,2),"$")),col="red")
text(5,3,TeX(paste0("$",pn(A*D,1),"$")),col="red")
text(3,1,TeX(paste0("$",pn(B*C,1),"$")),col="red")
text(5,1,TeX(paste0("$",pn(B*D,0),"$")),col="red")

```
\

Or, you can FOIL...

```{r,echo=F,fig.dim=c(6,2)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1,1),ylim=c(0,1),axes=F,ann=F)
simpex1 = paste0(A,"x+",B)
simpex2 = paste0(C,"x+",D)
simpex1 = gsub("+-","-",simpex1,fixed=T)
simpex2 = gsub("+-","-",simpex2,fixed=T)

e1 = gsub("{","",exp1,fixed=T)
e1 = gsub("}","",e1,fixed=T)
e2 = gsub("{","",exp2,fixed=T)
e2 = gsub("}","",e2,fixed=T)

text(0,0.5,TeX(paste0("$(",e1,")(",e2,")$")),cex=1.5)

x1 = -0.23
x2 = 0.1
y1 = 0.6
y2 = 0.8
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1,x2,0.001)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="red")
text(xmid,y2,"Firsts",col="red",adj=c(0.7,-0.2))

x1 = -0.06
x2 = 0.25+(sign(A)-1)*(-0.01)+(sign(C)-1)*(-0.01)
y1 = 0.6
y2 = 0.8
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1+0.0001,x2-0.0001,length.out=100)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="purple")
text(xmid,y2,"Lasts",col="purple",adj=c(0.3,-0.2))

x1 = -0.23
x2 = 0.25+(sign(A)-1)*(-0.01)+(sign(C)-1)*(-0.01)
y1 = 0.4
y2 = 0.1
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1+0.0001,x2-0.0001,length.out=100)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="orange")
text(xmid,y2,"Outsides",col="orange",adj=c(0.5,1.2))


x1 = -0.06
x2 = 0.1
y1 = 0.4
y2 = 0.3
xmid = mean(c(x1,x2))
xr = abs(x2-xmid)
x = seq(x1+0.0001,x2-0.0001,length.out=100)
y = (y2-y1)*sqrt(((xr)^2-(x-xmid)^2)/xr^2)+y1
lines(x,y,lwd=3,col="blue")
text(xmid,y2,"Insides",col="blue",adj=c(0.5,1.2))

text(-0.95,0.8,TeX(paste0("Firsts= $",pn(A*C,2),"$")),col="red",adj=c(0,0.5),cex=1.2)
text(-0.95,0.6,TeX(paste0("Outsides= $",pn(A*D,1),"$")),col="orange",adj=c(0,0.5),cex=1.2)
text(-0.95,0.4,TeX(paste0("Insides= $",pn(B*C,1),"$")),col="blue",adj=c(0,0.5),cex=1.2)
text(-0.95,0.2,TeX(paste0("Lasts= $",B*D,"$")),col="purple",adj=c(0,0.5),cex=1.2)

answers = c(pn(c(6,23,20),c(2,1,0)))

```
\

Either way, you should first get
$$`r pn(c(A*C,A*D,B*C,B*D),c(2,1,1,0))`$$

And, after combining like terms, you should get
$$`r pn(c(A*C,A*D+B*C,B*D),c(2,1,0))`$$

Thus, $a=`r A*C`$ and $b=`r A*D+B*C`$ and $c=`r B*D`$. This question specifically asked for the value of $b$, so the answer is $`r A*D+B*C`$.


Meta-information
============
extype: num
exsolution: `r A*D+B*C`
exname: foil_get_b
