```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
while(T){
    hks = sample(10:90,4)
    h1 = hks[1]
    k1 = hks[2]
    h2 = hks[3]
    k2 = hks[4]
    d = sqrt((h1-h2)^2+(k1-k2)^2)
    rat = runif(1,0.2,0.8)
    midx = (1-rat)*h1+rat*h2
    midy = (1-rat)*k1+rat*k2
    r1 = round(sqrt((h1-midx)^2+(k1-midy)^2)+runif(1,1,5))
    r2 = round(sqrt((h2-midx)^2+(k2-midy)^2)+runif(1,1,5))
    xp = round(midx+sample(-9:9,10))
    yp = round(midy+sample(-9:9,10))
    isin1 = sqrt((xp-h1)^2+(yp-k1)^2)<=r1
    isin2 = sqrt((xp-h2)^2+(yp-k2)^2)<=r2
    isin = (isin1*isin2)
    xmin = min(c(h1-r1,h2-r2))-1
    xmax = max(c(h1+r1,h2+r2))+1
    ymin = min(c(k1-r1,k2-r2))-1
    ymax = max(c(k1+r1,k2+r2))+1
    if(sum(isin)>2 && sum(isin)<8 && 
       min(xp)>0 && max(xp)<100 &&
       min(yp)>0 && max(yp)<100 &&
       xmin>0 && xmax<100 && ymin>0 && ymax<100){break}
}


pts = paste0("(",xp,",",yp,")")
al = paste0("* ",pts,collapse="\n")
sol = paste0(1*isin,collapse="")

ineq1 = paste0("(x-",h1,")^2+(y-",k1,")^2~\\le~",r1,"^2",collapse="")
ineq1 = gsub("--","+",ineq1,fixed=T)

ineq2 = paste0("(x-",h2,")^2+(y-",k2,")^2~\\le~",r2,"^2",collapse="")
ineq2 = gsub("--","+",ineq2,fixed=T)

ts = c("is NOT in","is in")
sols = paste0("* point ",pts," ",ts[isin+rep(1,10)],collapse = "\n")


```

Question
========

Consider the points listed below:

* `r pts`

Please determine which points satisfy both criteria below:

1. Closer than `r r1` units from point (`r h1`, `r k1`), and
2. Closer than `r r2` units from point (`r h2`, `r k2`).



Answerlist
--------

`r al`


Solution
========

1. Open [Desmos](https://www.desmos.com/calculator).
2. As the first item, use the standard form of a circle to visualize the first criterion.
$$`r ineq1`$$
3. As the second item, use the standard form of a circle to visualize the second criterion.
$$`r ineq2`$$
4. As the third item, copy/paste the list of points. Click the "Label" checkbox.
5. Read which points are in the overlapping region.

```{r,echo=F,fig.dim=c(7,7)}
xmin = min(c(h1-r1,h2-r2))-1
xmax = max(c(h1+r1,h2+r2))+1
ymin = min(c(k1-r1,k2-r2))-1
ymax = max(c(k1+r1,k2+r2))+1
xwid = xmax-xmin
ywid = ymax-ymin
wid = max(c(xwid,ywid))
xm = mean(c(xmin,xmax))
ym = mean(c(ymin,ymax))
xlo = floor(xm-wid/2)
xhi = ceiling(xm+wid/2)
ylo = floor(ym-wid/2)
yhi = ceiling(ym+wid/2)

par(pty="s")
plot(0,0,"n",xlim=c(xlo,xhi),ylim=c(ylo,yhi),xlab="x",ylab="y")

for(x in xlo:xhi){
    lines(c(x,x),c(ylo,yhi),col="lightgrey",lwd=0.7)
}
for(y in ylo:yhi){
    lines(c(xlo,xhi),c(y,y),col="lightgrey",lwd=0.7)
}
for(x in xlo:xhi){
    if(x%%5==0){
        lines(c(x,x),c(ylo,yhi),col="darkgrey",lwd=1.2)
    }
}
for(y in ylo:yhi){
    if(y%%5==0){
        lines(c(xlo,xhi),c(y,y),col="darkgrey",lwd=1.2)
    }
}

th = seq(0,2*pi,pi/200)
polygon(cos(th)*r1+h1,sin(th)*r1+k1,border="red",lwd=2,col=rgb(1,0,0,0.4))
polygon(cos(th)*r2+h2,sin(th)*r2+k2,border="blue",lwd=2,col=rgb(0,0,1,0.4))
points(xp,yp,pch=isin*6+rep(13,10))
# points(h,k,col="red",pch=19)
# text(h+r/20,k+r/20,paste0("(",h,",",k,")",collapse=""),adj=c(0,0),col="red")


```
\

`r sols`

Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: points_in_overlap