```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
maxval = 20

while(T){
    xsys = sample(1:(maxval-1),6)
    xs = xsys[1:3]
    ys = xsys[4:6]
    xdiff = diff(c(xs,xs[1]))
    ydiff = diff(c(ys,ys[1]))
    lens = sqrt(xdiff^2+ydiff^2)
    A = lens[c(1,2,3)]
    B = lens[c(2,3,1)]
    C = lens[c(3,1,2)]
    th = acos((A^2+B^2-C^2)/(2*A*B))
    if(min(th)>pi/12 && min(lens)>5 && min(abs(xdiff))>1 && min(abs(ydiff))>1 &&
       length(unique(lens))==3){break}
}

pnts = paste0("(",xs,", ",ys,")")
pl = paste("* ",pnts,collapse="\n")
per = sum(lens)

```

Question
========

Consider the triangle with vertices at the following coordinates:

`r pl`

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s")
plot(0,0,"n",xlim=c(0,maxval),ylim=c(0,maxval),xlab="x",ylab="y")
for(i in 1:maxval){
    lines(c(0,maxval),c(i,i),col="lightgrey",lwd=0.5)
    lines(c(i,i),c(0,maxval),col="lightgrey",lwd=0.5)
}
for(i in seq(5,maxval,5)){
    lines(c(0,maxval),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(0,maxval),col="darkgrey",lwd=0.8)
}
for(i in seq(10,maxval,10)){
    lines(c(0,maxval),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(0,maxval),col="darkgrey",lwd=1.2)
}
arrows(0,0,0,maxval*1.03,0.1,10,lwd=2)
arrows(0,0,maxval*1.03,0,0.1,10,lwd=2)
polygon(xs,ys,border="blue",col=rgb(0,0,1,0.1),lwd=2)
points(xs,ys,pch=20,col="blue")

```
\

Calculate the [perimeter](https://en.wikipedia.org/wiki/Perimeter). Please be accurate to within 0.01 units.


Solution
========

We want to use the [Pythagorean theorem](https://en.wikipedia.org/wiki/Pythagorean_theorem), which tells us the hypotenuse's length, $c$, can be calculated from the two legs' lengths ($a$ and $b$) by using $c=\sqrt{a^2+b^2}$. It is easy to draw right triangles by using vertical and horizontal legs. The leg lengths can be found by taken differences of corresponding coordinates or by counting on the graph. See the diagram below.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s")
plot(0,0,"n",xlim=c(0,maxval),ylim=c(0,maxval),xlab="x",ylab="y")
for(i in 1:maxval){
    lines(c(0,maxval),c(i,i),col="lightgrey",lwd=0.5)
    lines(c(i,i),c(0,maxval),col="lightgrey",lwd=0.5)
}
for(i in seq(5,maxval,5)){
    lines(c(0,maxval),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(0,maxval),col="darkgrey",lwd=0.8)
}
for(i in seq(10,maxval,10)){
    lines(c(0,maxval),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(0,maxval),col="darkgrey",lwd=1.2)
}
arrows(0,0,0,maxval*1.03,0.1,10,lwd=2)
arrows(0,0,maxval*1.03,0,0.1,10,lwd=2)
polygon(xs,ys,border="blue",lwd=2)
points(xs,ys,pch=20,col="blue")

x = c(xs,xs)
y = c(ys,ys)

cols = c(rgb(1,0,0,1),rgb(0.8,0,0.2,1),rgb(0.6,0,0.4,1))
colfill = c(rgb(1,0,0,0.3),rgb(0.8,0,0.2,0.3),rgb(0.6,0,0.4,0.3))
for(i in 1:3){
    x1 = x[i]
    y1 = y[i]
    x2 = x[i+1]
    y2 = y[i+1]
    x3 = x[i+2]
    y3 = y[i+2]
    vx1 = x2-x1
    vx2 = x3-x2
    vy1 = y2-y1
    vy2 = y3-y2
    cp = vx1*vy2-vx2*vy1
    midx = x1
    midy = y2
    vx1 = x2-x1
    vx2 = midx-x2
    vy1 = y2-y1
    vy2 = midy-y2
    cp2 = vx1*vy2-vx2*vy1
    if(sign(cp)==sign(cp2)){
        midx = x2
        midy = y1
    }
    polygon(c(x1,midx,x2),c(y1,midy,y2),col=colfill[i],border=cols[i],lwd=2)
    htx = mean(c(x1,x2))
    vty = mean(c(y1,y2))
    if(midx==max(c(x1,x2))){
        vtx = midx+0.1
        adjv = c(0,0.5)
    } else {
        vtx = midx-0.1
        adjv = c(1,0.5)
    }
    if(midy==max(c(y1,y2))){
        hty = midy+0.1
        adjh = c(0.5,0)
    } else {
        hty = midy-0.1
        adjh = c(0.5,1)
    }
    text(htx,hty,abs(x2-x1),col=cols[i],adj=adjh)
    text(vtx,vty,abs(y2-y1),col=cols[i],adj=adjv)
}


```
\

Calculate the hypotenuses' lengths.

$$\sqrt{`r abs(xdiff[1])`^2+`r abs(ydiff[1])`^2}~=~ `r lens[1]`$$

$$\sqrt{`r abs(xdiff[2])`^2+`r abs(ydiff[2])`^2}~=~ `r lens[2]`$$

$$\sqrt{`r abs(xdiff[3])`^2+`r abs(ydiff[3])`^2}~=~ `r lens[3]`$$


```{r,echo=F,fig.dim=c(5,5)}
par(pty="s")
plot(0,0,"n",xlim=c(0,maxval),ylim=c(0,maxval),xlab="x",ylab="y")
for(i in 1:maxval){
    lines(c(0,maxval),c(i,i),col="lightgrey",lwd=0.5)
    lines(c(i,i),c(0,maxval),col="lightgrey",lwd=0.5)
}
for(i in seq(5,maxval,5)){
    lines(c(0,maxval),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(0,maxval),col="darkgrey",lwd=0.8)
}
for(i in seq(10,maxval,10)){
    lines(c(0,maxval),c(i,i),col="darkgrey",lwd=1.2)
    lines(c(i,i),c(0,maxval),col="darkgrey",lwd=1.2)
}
arrows(0,0,0,maxval*1.03,0.1,10,lwd=2)
arrows(0,0,maxval*1.03,0,0.1,10,lwd=2)
polygon(xs,ys,border="blue",col=rgb(0,0,1,0.3),lwd=2)
points(xs,ys,pch=20,col="blue")

x = c(xs,xs)
y = c(ys,ys)

for(i in 1:3){
    x1 = x[i]
    y1 = y[i]
    x2 = x[i+1]
    y2 = y[i+1]
    x3 = x[i+2]
    y3 = y[i+2]
    vx1 = x2-x1
    vx2 = x3-x2
    vy1 = y2-y1
    vy2 = y3-y2
    cp = vx1*vy2-vx2*vy1
    ang = atan((y2-y1)/(x2-x1))
    midx = mean(c(x1,x2))+cos(ang+pi/2)*0.7
    midy = mean(c(y1,y2))+sin(ang+pi/2)*0.7
    vx2 = midx-x2
    vy2 = midy-y2
    cp2 = vx1*vy2-vx2*vy1
    if(sign(cp)==sign(cp2)){
        midx = mean(c(x1,x2))+cos(ang-pi/2)*0.7
        midy = mean(c(y1,y2))+sin(ang-pi/2)*0.7
    }
    text(midx,midy,round(lens[i],4),srt=ang/pi*180,col=cols[i])
}

```
\

To find the perimeter, add up the three lengths.

$$P~=~`r lens[1]`+`r lens[2]`+`r lens[3]`$$

$$P~=~`r sum(lens)`$$

Meta-information
============
extype: num
exsolution: `r per`
exname: triangle_perimeter
extol: 0.01