```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
xyz = sample(5:20,3)
x = xyz[1]
y = xyz[2]
z = xyz[3]

D = sqrt(x^2+y^2+z^2)

p = c(0,0,0, #1
      0,0,z, #2
      0,y,0, #3
      x,0,0, #4
      0,y,z, #5
      x,0,z, #6
      x,y,0, #7
      x,y,z) #8
p = matrix(p,ncol=3,byrow=T)

X = numeric()
Y = numeric()
for(i in 1:dim(p)[1]){
    px = p[i,1]
    py = p[i,2]
    pz = p[i,3]
    X = c(X,0.7*px-0.7*py)
    Y = c(Y,0.2*px+0.2*py+pz)
}

l = c(1,2,
      1,3,
      1,4,
      2,5,
      2,6,
      3,5,
      3,7,
      4,6,
      4,7,
      5,8,
      6,8,
      7,8)
l  = matrix(l,ncol=2,byrow=T)

XLO = min(X)
XHI = max(X)
YLO = min(Y)
YHI = max(Y)
widX = XHI-XLO
widY = YHI-YLO
maxwid = max(c(widX,widY))
xmid = mean(c(XHI,XLO))
ymid = mean(c(YHI,YLO))

```

Question
========

A [right rectangular prism](https://en.m.wikipedia.org/wiki/Rectangular_cuboid) is `r x` inches wide, `r y` inches deep, and `r z` inches tall.

What is the distance between opposite corners?

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")

plot(0,0,"n",axes=F,ann=F,
     xlim=c(xmid-maxwid/2,xmid+maxwid/2),
     ylim=c(ymid-maxwid/2,ymid+maxwid/2),
     )

for(i in 1:dim(l)[1]){
    # p1 = paste0(p[l[i,1],],collapse=",")
    # p2 = paste0(p[l[i,2],],collapse=",")
    # print(paste(p1," -> ",p2,collapse=""))
    p1 = l[i,1]
    p2 = l[i,2]
    lines(c(X[p1],X[p2]),c(Y[p1],Y[p2]),col="darkgrey")
}
lines(c(X[3],X[6]),c(Y[3],Y[6]),col=rgb(1,0.6,0.6),lwd=2)

dtx = mean(X[c(1,3)])
dty = mean(Y[c(1,3)])
text(dtx,dty,y,col="blue")

htx = mean(X[c(4,6)])
hty = mean(Y[c(4,6)])
text(htx,hty,z,col="blue")

ltx = mean(X[c(1,4)])
lty = mean(Y[c(1,4)])
text(ltx,lty,x,col="blue")

Dtx = mean(X[c(3,6)])
Dty = mean(Y[c(3,6)])
text(Dtx,Dty,"?",col="red",cex=1.3)

```
\

Please be accurate within $\pm$ 0.01 of the exact answer.

Solution
========

Let's use Pythagorean Theorem. This is possible because all angles are 90 degrees. To do this, we can first find the length of a diagonal across the bottom. Let's call it $B$.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,
     xlim=c(xmid-maxwid/2,xmid+maxwid/2),
     ylim=c(ymid-maxwid/2,ymid+maxwid/2),
     )

for(i in 1:dim(l)[1]){
    # p1 = paste0(p[l[i,1],],collapse=",")
    # p2 = paste0(p[l[i,2],],collapse=",")
    # print(paste(p1," -> ",p2,collapse=""))
    p1 = l[i,1]
    p2 = l[i,2]
    lines(c(X[p1],X[p2]),c(Y[p1],Y[p2]),col="darkgrey")
}
lines(c(X[3],X[6]),c(Y[3],Y[6]),col=rgb(1,0.6,0.6,0.2),lwd=2)

dtx = mean(X[c(1,3)])
dty = mean(Y[c(1,3)])
text(dtx,dty,y,col="blue")

# htx = mean(X[c(1,2)])
# hty = mean(Y[c(1,2)])
# text(htx,hty,z,col="blue")

ltx = mean(X[c(1,4)])
lty = mean(Y[c(1,4)])
text(ltx,lty,x,col="blue")

Dtx = mean(X[c(3,6)])
Dty = mean(Y[c(3,6)])
text(Dtx,Dty,"?",col=rgb(1,0,0,0.2),cex=1.3)

polygon(X[c(1,3,4)],Y[c(1,3,4)],col=rgb(0.8,0.8,0,0.2),border=NA)
lines(c(X[3],X[4]),c(Y[3],Y[4]),col=rgb(0.6,0.6,0,0.4),lwd=2)
btx = mean(X[c(3,4)])
bty = mean(Y[c(3,4)])
text(btx,bty,"B",col=rgb(0.1,0.1,0))

px1 = c(0,1,1)/2
py1 = c(1,1,0)/2
pz1 = c(0,0,0)/2
X1 = 0.7*px1-0.7*py1
Y1 = 0.2*px1+0.2*py1+pz1

lines(X1,Y1)
```
\

$$B~=~\sqrt{`r x`^2+`r y`^2}~=~\sqrt{`r x^2+y^2`} ~\approx~`r sqrt(x^2+y^2)`$$

Now we can form another **right triangle**, using $B$, the height, and the desired length, which we can call $D$.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,
     xlim=c(xmid-maxwid/2,xmid+maxwid/2),
     ylim=c(ymid-maxwid/2,ymid+maxwid/2),
     )

for(i in 1:dim(l)[1]){
    # p1 = paste0(p[l[i,1],],collapse=",")
    # p2 = paste0(p[l[i,2],],collapse=",")
    # print(paste(p1," -> ",p2,collapse=""))
    p1 = l[i,1]
    p2 = l[i,2]
    lines(c(X[p1],X[p2]),c(Y[p1],Y[p2]),col="darkgrey")
}
polygon(X[c(3,4,6)],Y[c(3,4,6)],col=rgb(1,0,0,0.2),border=NA)

lines(c(X[3],X[6]),c(Y[3],Y[6]),col=rgb(1,0,0,0.4),lwd=2)

# dtx = mean(X[c(1,3)])
# dty = mean(Y[c(1,3)])
# text(dtx,dty,y,col="blue")

htx = mean(X[c(4,6)])
hty = mean(Y[c(4,6)])
text(htx,hty,z,col="blue")

# ltx = mean(X[c(1,4)])
# lty = mean(Y[c(1,4)])
# text(ltx,lty,x,col="blue")

Dtx = mean(X[c(3,6)])
Dty = mean(Y[c(3,6)])
text(Dtx,Dty,"D",col=rgb(1,0,0),cex=1.3)

lines(c(X[3],X[4]),c(Y[3],Y[4]),col=rgb(0.6,0.6,0,0.4),lwd=2)
btx = mean(X[c(3,4)])
bty = mean(Y[c(3,4)])
text(btx,bty,TeX(paste0("$\\sqrt{",x^2+y^2,"}$")),col=rgb(0.4,0.4,0))

vb = p[4,]-p[3,]
lb = sqrt(sum(vb^2))
ub = vb/lb

px1 = c(p[4,1]-ub[1]/2,p[4,1]-ub[1]/2,p[4,1])
py1 = c(p[4,2]-ub[2]/2,p[4,2]-ub[2]/2,p[4,2])
pz1 = c(0,1,1)/2
X1 = 0.7*px1-0.7*py1
Y1 = 0.2*px1+0.2*py1+pz1
lines(X1,Y1)


```
\

$$D ~=~ \sqrt{`r z`^2+\left(\sqrt{`r x^2+y^2`}\right)^2}$$
$$D ~=~ \sqrt{`r z^2`+`r x^2+y^2`}$$
$$D ~=~ \sqrt{`r z^2+x^2+y^2`}$$
$$D ~\approx~ `r D`$$

If you were super observant, you might have picked up on a shortcut. Basically, in 3D, [the distance](https://en.wikipedia.org/wiki/Distance#Straight-line_or_Euclidean_distance) between 2 points is:

$$D~=~\sqrt{(\Delta x)^2+(\Delta y)^2+(\Delta z)^2}$$

where $\Delta x=x_2-x_1$ and $\Delta y=y_2-y_1$ and $\Delta z=z_2-z_1$.


Meta-information
============
extype: num
exsolution: `r D`
exname: three_dim_dist
extol: 0.01