```{r data generation, echo = FALSE, results = "hide"}
n = 5
xmax = 30
m = round(runif(1,0.5,3),2)
b = round(runif(1,0.5,10),2)
while(T){
    lem = sample(c(-1,1),n,T)
    x = round(runif(n,2,xmax),1)
    y = round(m*x+b+lem*(runif(n,(m*x+b)/8,(m*x+b)/3)),2)
    if(length(unique(x))==n && length(unique(y))==n && length(unique(lem))==2 &&
       min(diff(sort(x)))>2){break}
}

mp = sprintf("%.2f",m)
bp = sprintf("%.2f",b)
yp = sprintf("%.2f",y)


names = c("Arnold","Betty","Chester","Denali","Edward")
isin = lem==1
addstr = c(" NOT "," ")[isin+1]
ynstr = c("No, ","Yes, ")[isin+1]
solstr = paste0("* ",ynstr,names," can",addstr," afford to go ",x," miles with \\$",yp," in pocket.",collapse="\n")

sols = c("01","10")

al = "* yes\n* no"
al = paste0(rep(al,n),collapse="\n")

sol = paste0(sols[isin+1],collapse="|")

```


Question
========

A taxi service charges a fixed base cost of \$`r sprintf("%.2f",b)` and then a mileage cost of \$`r sprintf("%.2f",m)` per mile. The following people wonder whether they can travel a specified distance with the amount of cash they are carrying.

* Can Arnold go `r x[1]` miles with \$`r yp[1]`?
    * ##ANSWER1##
* Can Betty go `r x[2]` miles with \$`r yp[2]`?
    * ##ANSWER2##
* Can Chester go `r x[3]` miles with \$`r yp[3]`?
    * ##ANSWER3##
* Can Denali go `r x[4]` miles with \$`r yp[4]`?
    * ##ANSWER4##
* Can Edward go `r x[5]` miles with \$`r yp[5]`?
    * ##ANSWER5##
    
Answerlist
--------

`r al`

Solution
========

I'd recommend doing this with [Desmos](https://www.desmos.com/calculator). Start by creating the equation describing the linear equation between distance ($x$, miles) and total cost ($y$, dollars).

$$y~=~`r bp`+`r mp`x$$

A passenger needs to have **at least** the total in cash to afford the ride. If the passenger has more than enough money, they can still afford the ride. So, if we redefine $y$ to be any possible amount of pocket money, we can say $y$ must be as much **or more** than the cost of the ride.

$$y~\ge~`r bp`+`r mp`x$$

So, type that inequality into Desmos. Then type in the following points:

```{r,echo=F}
pnts = paste0("(",x,",",y,")",collapse="\n\n")
```

`r pnts`

For each point, if it falls in [the feasible region](https://en.wikipedia.org/wiki/Inequality_(mathematics)), then it is a solution to the inequality.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(4,4,0,0))
ymax = max(c(m*xmax+b,y))
xx = c(0,xmax*1.2)
yy = m*xx+b
plot(xx,yy,"l",xlim=c(0,xmax),ylim=c(0,ymax*1.2),xlab="distance (miles)",ylab="money ($)")
polygon(c(xx,xmax,0),c(yy,ymax*1.5,ymax*1.5),col=rgb(0.4,0,0.8,0.3),border=NA)
lines(xx,yy,col=rgb(0.4,0,0.8),lwd=2)

text(30,m*60+b,"feasible\nregion",col=rgb(0.4,0,0.8))

arrows(0,0,0,m*xmax+b,0.1,10,lwd=2)
arrows(0,0,xmax,0,0.1,10,lwd=2)

points(x,y,pch=16+lem*3)
text(x,y,LETTERS[1:n],adj=c(0.5,-0.9),cex=0.8)

legend("topleft",c("feasible region","boundary","solution","not solution"),fill=c(rgb(0.4,0,0.8,0.3),NA,NA,NA),lwd=c(2,2,NA,NA),pch=c(NA,NA,19,13),
       col=c(NA,rgb(0.4,0,0.8),"black","black"),border=c(rgb(0.4,0,0.8),NA,NA,NA))

```
\

`r solstr`



Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n),collapse="|")`
exsolution: `r sol`
exname: check_sols_ineq