```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
solty = sample(1:3,1,FALSE,c(0.15,0.7,0.15))

while(T){
  ints = sample(c(1:20),4)
  xi1 = ints[1]
  xi2 = ints[2]
  yi1 = ints[3]
  yi2 = ints[4]
  vx = round(runif(1,1,10),2)
  vy = round(runif(1,1,10),2)
  c = abs(xi1*yi1)
  f = abs(xi2*yi2)
  a = c/xi1
  b = c/yi1
  d = f/xi2
  e = f/yi2
  x = (c*e-b*f)/(a*e-b*d)
  y = (c*d-a*f)/(b*d-a*e)
  prof1 = sum(c(0,min(yi1,yi2))*c(vx,vy))
  prof2 = sum(c(x,y)*c(vx,vy))
  prof3 = sum(c(min(xi1,xi2),0)*c(vx,vy))
  if(length(unique(c(prof1,prof2,prof3)))==3 &&
     min(abs(diff(c(prof1,prof2,prof3,prof1)))) > 1 &&
     c(prof1,prof2,prof3)[solty]==max(c(prof1,prof2,prof3)) &&
     round(x)==x && 
     round(y)==y && 
     x<20 && 
     y<20 && 
     x>0 && 
     y>0 && x!=y){break}
}
x = round(x)
y = round(y)
al = 0:20
als = paste0("* ",al,"\n",collapse="")

ans = max(c(prof1,prof2,prof3))
```


Question
========

```{python,echo=FALSE}
from sympy import *
x,y = symbols("x y")
gcd1 = gcd(int(r.a), int(r.b))
gcd2 = gcd(int(r.d), int(r.e))
lex1 = latex(int(r.a/gcd1)*x+int(r.b/gcd1)*y)
lex2 = latex(int(r.d/gcd2)*x+int(r.e/gcd2)*y)
cc = int(int(r.c)/gcd1)
ff = int(int(r.f)/gcd2)

a = int(r.a/gcd1)
b = int(r.b/gcd1)
c = cc
d = int(r.d/gcd2)
e = int(r.e/gcd2)
f = ff

a2 = r.a #int(r.a/gcd1)
b2 = r.b #int(r.b/gcd1)
c2 = r.c #cc
d2 = r.d #int(r.d/gcd2)
e2 = r.e #int(r.e/gcd2)
f2 = r.f #ff



LCM = lcm(b,e)
mult1 = int(LCM/b)
mult2 = int(-LCM/e)
```

```{r,echo=F}
a = py$a
b = py$b
c = py$c
d = py$d
e = py$e
f = py$f

a2 = py$a2
b2 = py$b2
c2 = py$c2
d2 = py$d2
e2 = py$e2
f2 = py$f2

LCM1 = py$LCM
mult1 = py$mult1
mult2 = py$mult2

ae = a*mult1
be = b*mult1
ce = c*mult1
de = d*mult2
ee = e*mult2
fe = f*mult2
```

A thief is stealing xots and yivs. Each xot has a mass of `r a2` kilograms and a volume of `r d2` liters. Each yiv has a mass of `r b2` kilograms and a volume of `r e2` liters. The thief can carry a maximum mass of `r c2` kilograms and a maximum volume of `r f2` liters. The profit from each xot is \$`r vx` and the profit from each yiv is \$`r vy`.

For your convenience, those numbers are organized in the table below.

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab2, results="asis", echo=F}
attribute = c("mass (kg)","volume (L)","profit ($)")
xot = c(paste(a2),paste(d2),sprintf("%.2f",vx))
yiv = c(paste(b2),paste(e2),sprintf("%.2f",vy))
capacity = c(paste(c2),paste(f2),"$\\infty$")
mydf2 = data.frame(attribute,xot,yiv,capacity)
#colnames(mydf2) = c("$x$","$f(x)$")
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```

What is the maximum profit the thief can produce? *(In dollars.)*

Solution
========

This is an example of [linear programming](https://en.wikipedia.org/wiki/Linear_programming){target="_blank"}. 

Define $x$ as number of xots and $y$ as number of yivs. Write the constraints as inequalities.

* Mass constraint: $`r a2`x+`r b2`y \le `r c2`$
* Volume constraint: $`r d2`x+`r e2`y \le `r f2`$

We can assume that optimal profit will occur at a boundary, so we can just consider the equations.
$$`r a2`x+`r b2`y = `r c2`$$
$$`r d2`x+`r e2`y = `r f2`$$

If either equation has coefficients that all share a common factor, we can simplify by dividing both sides by the greatest common factor:

$$`r a`x+`r b`y = `r c`$$
$$`r d`x+`r e`y = `r f`$$

We need to find the $x$ intercepts and the $y$ intercepts.

To find the $x$-intercepts, set $y$ to 0.

* The $x$-intercept of the mass constraint:
$$`r a`x_{\text{int}1}+(`r b`)(0) = `r c` $$
$$`r a`x_{\text{int}1} = `r c` $$
$$x_{\text{int}1} = \frac{`r c`}{`r a`} = `r round(c/a)` $$

* The $x$-intercept of the volume constraint:

$$`r d`x_{\text{int}2}+(`r e`)(0) = `r f` $$
$$`r d`x_{\text{int}2} = `r f` $$
$$x_{\text{int}2} = \frac{`r f`}{`r d`} = `r round(f/d)` $$

To find the $y$-intercepts, set $x$ to 0.

* The $y$-intercept of the mass constraint:
$$(`r a`)(0)+(`r b`)(y_{\text{int1}}) = `r c` $$
$$`r b`y_{\text{int}1} = `r c` $$
$$y_{\text{int}1} = \frac{`r c`}{`r b`} = `r round(c/b)` $$


* The $y$-intercept of the volume constraint:

$$(`r d`)(0)+(`r e`)y_{\text{int2}} = `r f` $$
$$`r e`y_{\text{int}2} = `r f` $$
$$y_{\text{int}2} = \frac{`r f`}{`r e`} = `r round(f/e)` $$

To find the intersection of the constraints, I would recommend elimination. Multiply the equations to have matching coefficients for $y$ terms. 

$$`r ae`x + `r be`y = `r ce`$$
$$`r -de`x + `r -ee`y = `r -fe`$$
Subtract equations.

$$`r abs(ae+de)`x + (0)y = `r abs(ce+fe)`$$

Simplify.

$$`r abs(ae+de)`x = `r abs(ce+fe)`$$

Divide by `r abs(ae+de)`.

$$x = `r abs(ce+fe)/abs(ae+de)`$$

Plug $x = `r x`$ into the first equation. Solve for $y$.

$$(`r a`)(`r x`)+`r b`y = `r c`$$
$$`r a*x`+`r b`y = `r c`$$
$$`r b`y = `r c-a*x`$$
$$y = `r (c-a*x)/b`$$

So, the intersection occurs at $(`r x`,\,`r y`)$.

You can plot the boundaries and shade the [feasible region](https://en.wikipedia.org/wiki/Feasible_region){target="_blank"}.

```{r,fig.dim=c(6,6),echo=FALSE,results="asis"}
library(latex2exp)
par(pty="s")
plot(0,0,type="n",xlim=c(0,20),ylim=c(0,20),lwd=2,ylab=TeX("$y$"),xlab=TeX("$x$"))
for(j in seq(0,20,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xx = seq(-1,21,1)
y1 = (-a/b)*xx+c/b
y2 = (-d/e)*xx+f/e
polygon(c(0,0,x,min(xi1,xi2)),c(0,min(yi1,yi2),y,0),col=rgb(1,1,0,0.5))
lines(xx,y1,col="blue",lwd=3)
lines(xx,y2,col="red",lwd=3)
points(c(0,x,min(xi1,xi2)),c(min(yi1,yi2),y,0))

legend("topright",c("mass constraint","volume constraint","feasible region","possible optimum"),col=c("blue","red",rgb(1,1,0,0.5),"black"),lwd=c(3,3,10,NA),pch=c(NA,NA,NA,1))

```
\


The maximum profit could occur at $(0,`r min(yi1,yi2)`)$ or $(`r x`,`r y`)$ or $(`r min(xi1,xi2)`,0)$.

Find those profits, using $P(x,y)=`r vx`x+`r vy`y$.

$$P(0,`r min(yi1,yi2)`)=(`r vx`)(0)+(`r vy`)(`r min(yi1,yi2)`) = `r prof1`$$
$$P(`r x`,`r y`)=(`r vx`)(`r x`)+(`r vy`)(`r y`) = `r prof2`$$
$$P(`r min(xi1,xi2)`,0)=(`r vx`)(`r min(xi1,xi2)`)+(`r vy`)(0) = `r prof3`$$

So, the maximum profit is $`r sprintf("%.2f",max(c(prof1,prof2,prof3)))`.


It might help to visualize this in 3D, with xots, yivs, and profit on the 3 axes. Sorry, I was not able to make a 3D plot show up here. But, we can add a third "dimension" by using a color ramp for profit. You can see that since our profit function is linear in $x$ and linear in $y$, the profit grows linearly as either xots or yivs are added. Another useful concept is an [isoprofit line](https://www.youtube.com/watch?v=QkIrNqiJZw4), which shows all the possible combinations of xots and yivs that would generate the same profit (see [contour lines](https://en.wikipedia.org/wiki/Contour_line)). Since profit is linear in both $x$ and $y$, we see the isoprofit lines are all parallel. Also, in this case, the isoprofit lines are not parallel to either constraint, so there will be only a single optimal choice.


```{r,fig.dim=c(6,6),echo=FALSE,results="asis"}
library(latex2exp)
par(pty="s")

hihi = 20-5*(min(xi1,xi2)<15 && min(yi1,yi2)<15)-5*(min(xi1,xi2)<10 && min(yi1,yi2)<10)-5*(min(xi1,xi2)<5 && min(yi1,yi2)<5)

plot(0,0,type="n",xlim=c(0,hihi),ylim=c(0,hihi),lwd=2,ylab=TeX("$y$"),xlab=TeX("$x$"))

maxpro = ans
mpdigs = ceiling(log(maxpro)/log(10))
ld = floor(maxpro/10^(mpdigs-1))
pfs = seq(10^(mpdigs-1),maxpro,10^(mpdigs-1))
if(length(pfs)<5){
    pfs = seq(10^(mpdigs-1)/2,maxpro,10^(mpdigs-1)/2)
}
if(length(pfs)<5){
    pfs = seq(10^(mpdigs-1)/5,maxpro,10^(mpdigs-1)/5)
}
if(length(pfs)<5){
    pfs = seq(10^(mpdigs-1)/10,maxpro,10^(mpdigs-1)/10)
}
for(i in seq(0,maxpro,maxpro/1000)){
    xi00 = i/vx
    yi00 = i/vy
    lines(c(xi00,0),c(0,yi00),col=hsv(1/2-i/maxpro/2,1,1,0.2),lwd=0.2)
}
for(i in pfs){
    xi00 = i/vx
    yi00 = i/vy
    lines(c(xi00,0),c(0,yi00),col=hsv((1/2-i/maxpro/2)%%1,1,0.8,1),lwd=1)
}

polygon(c(0,x,min(xi1,xi2),25,25,0),c(min(yi1,yi2),y,0,0,25,25),border=NA,col="white")

for(j in seq(0,20,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xx = seq(-1,21,1)
y1 = (-a/b)*xx+c/b
y2 = (-d/e)*xx+f/e


lines(xx,y1,col="grey",lwd=1)
lines(xx,y2,col="grey",lwd=1)

prfs = c(prof1,prof2,prof3)
points(c(0,x,min(xi1,xi2)),c(min(yi1,yi2),y,0),pch=20,col=hsv((1/2-prfs/maxpro/2)%%1,1,0.6))
text(0,min(yi1,yi2),paste0("$",prof1,collapse=""),adj=c(-0.2,-0.2),col=hsv((1/2-prof1/maxpro/2)%%1,1,0.6))
text(x,y,paste0("$",prof2,collapse=""),adj=c(-0.2,-0.2),col=hsv((1/2-prof2/maxpro/2)%%1,1,0.6))
text(min(xi1,xi2),0,paste0("$",prof3,collapse=""),adj=c(-0.2,-0.2),col=hsv((1/2-prof3/maxpro/2)%%1,1,0.6))


legend("topright",paste0("$",pfs),lwd=rep(1,length(pfs)),col=hsv((1/2-pfs/maxpro/2)%%1,1,0.8,1))


```
\



Meta-information
============
extype: num
exsolution: `r ans`
extol: 0.01
exname: opt_thief