```{r data generation, echo = FALSE, results = "hide"}

numres = 100 #sample(c(4,5),1)

while(T){
    p1p2 = sort(sample(seq(2*numres,9*numres,1),2)/numres)
    p1 = p1p2[1]
    p2 = p1p2[2]
    n1n2 = sample(5:50,2)
    n1 = n1n2[1]
    n2 = n1n2[2]
    n = n1+n2
    p = n1*p1+n2*p2
    pp = sprintf("%.2f",p)
    pp1 = sprintf("%.2f",p1)
    pp2 = sprintf("%.2f",p2)
    if(diff(p1p2)>2 && abs(diff(n1n2))>2 && p<1000){break}
}

qt = sample(1:2,1)
qps = c("How many child tickets were sold?",
        "How many adult tickets were sold?")[qt]

sol = c(n1,n2)[qt]

```


Question
========

An event has two types of tickets: each adult ticket costs \$`r pp2` and each child ticket costs \$`r pp1`. The event sold `r n` tickets for a revenue of \$`r pp`.

* `r qps`


Solution
========

Let's use $x$ to represent the number of adult tickets and $y$ to represent the number of child tickets. We know the total number of tickets sold is `r n`.
$$x+y~=~`r n`$$
The revenue from adults equals the product of \$`r pp2` and $x$. The revenue from children equals the product of \$`r pp1` and $y$. The total revenue is the sum of the two types of revenue, and it equals \$`r pp`.

$$`r pp2`x+`r pp1`y~=~`r pp`$$

```{r,echo=F}
var1 = c("x","y")[qt]
var2 = c("y","x")[qt]
wrd1 = c("the number of adult tickets","the number of child tickets")[qt]
wrd2 = c("the number of child tickets","the number of adult tickets")[qt]
```


We have a system of two equations and two unknowns. We want to solve for $`r var2`$, which is `r wrd2`. To do this, I'd start by isolating $`r var1`$ in the first equation (the equation from the number of tickets).

$$`r var1`~=~`r n`-`r var2`$$

We can now substitute $`r n`-`r var2`$ for $`r var1`$ in the second equation (the equation from the total revenue).

```{r,echo=F}
eq1a = paste0(pp2,"x+",pp1,"\\cdot(",n,"-x)=",pp,collapse="")
eq1b = paste0(pp2,"\\cdot(",n,"-y)+",pp1,"y=",pp,collapse="")
eq1 = c(eq1b,eq1a)[qt]
```

$$`r eq1`$$

Distribute.

```{r,echo=F}
eq1a = paste0(pp2,"x+",p1*n,"-",pp1,"x=",pp,collapse="")
eq1b = paste0(p2*n,"-",pp2,"y+",pp1,"y=",pp,collapse="")
eq1 = c(eq1b,eq1a)[qt]

sub1 = c(p2*n,p1*n)[qt]
```

$$`r eq1`$$

Subtract `r sub1` from both sides.

```{r,echo=F}
eq1a = paste0(pp2,"x-",pp1,"x=",p-p1*n,collapse="")
eq1b = paste0("-",pp2,"y+",pp1,"y=",p-p2*n,collapse="")
eq1 = c(eq1b,eq1a)[qt]
```

$$`r eq1`$$

Combine the linear terms.

```{r,echo=F}
eq1a = paste0(p2-p1,"x=",p-p1*n,collapse="")
eq1b = paste0(p1-p2,"y=",p-p2*n,collapse="")
eq1 = c(eq1b,eq1a)[qt]

div1 = c(p1-p2,p2-p1)[qt]
```

$$`r eq1`$$

Divide both sides by `r div1`.

```{r,echo=F}
eq1a = paste0("x=",(p-p1*n)/(p2-p1),collapse="")
eq1b = paste0("y=",(p-p2*n)/(p1-p2),collapse="")
eq1 = c(eq1b,eq1a)[qt]

```

$$`r eq1`$$


Meta-information
============
extype: num
exsolution: `r sol`
exname: ticket_prices