```{r,echo=F}
while(T){
  dims = sort(sample(12:40,2))
  w = dims[2]
  h = dims[1]
  RF = w/h
  x = runif(1,h/3,h/1.2)
  r = round(1+(w-h)/x,2)
  x = (w-h)/(r-1)
  b = (h-x)/2
  bs = b/w
  if(RF>1.2 && RF<3 && bs>0.05){break}
}
ws = 1
hs = h/w
xs = x/w
xrs = r*x/w

ifbnoty = sample(c(T,F),1)
if(ifbnoty){
  let = "b"
  sol = b
  wrds = "the width of the mat in inches"
} else {
  let = "y"
  sol = x
  wrds = "the height of the image in inches"
}

```

Question
========

The inner dimensions of a frame are `r w` inches by `r h` inches. An artist hopes to print an image with an aspect ratio of `r r` such that a uniformly wide  [mat](https://en.wikipedia.org/wiki/Mat_(picture_framing)) fits around the image. 

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
huecent = runif(1)
color = hsv(0,0,0.1)
tcol = hsv(0,0,1)
plot(0,0,type="n",ann=F,axes=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
polygon(c(-0.1,-0.1,1.1,1.1),c(0.5+h/w/2,0.5+h/w/2+0.1,0.5+h/w/2+0.1,0.5+h/w/2),
        col=color,border=NA)
polygon(c(-0.1,-0.1,1.1,1.1),c(0.5-h/w/2,0.5-h/w/2-0.1,0.5-h/w/2-0.1,0.5-h/w/2),
        col=color,border=NA)
polygon(c(-0.1,-0.1,0,0),c(0.5-h/w/2-0.1,0.5+h/w/2+0.1,0.5+h/w/2+0.1,0.5-h/w/2-0.1),
        col=color,border=NA)
polygon(c(1,1,1.1,1.1),c(0.5-h/w/2-0.1,0.5+h/w/2+0.1,0.5+h/w/2+0.1,0.5-h/w/2-0.1),
        col=color,border=NA)
lines(c(0,0,1,1,0),c(0.5-h/w/2,0.5+h/w/2,0.5+h/w/2,0.5-h/w/2,0.5-h/w/2))
lines(c(-0.1,-0.1,1.1,1.1,-0.1),c(0.5-h/w/2-0.1,0.5+h/w/2+0.1,0.5+h/w/2+0.1,0.5-h/w/2-0.1,0.5-h/w/2-0.1))
lines(c(-0.04,-0.02,-0.03,-0.03),c(0.5+h/w/2,0.5+h/w/2,0.5+h/w/2,0.5+0.07),lwd=1,
      col=tcol)
lines(c(-0.04,-0.02,-0.03,-0.03),c(0.5-h/w/2,0.5-h/w/2,0.5-h/w/2,0.5-0.07),lwd=1,
      col=tcol)
text(-0.03,0.5,paste0(h," in"),srt=90,col=tcol)
lines(c(0,0,0,0.5-0.07),c(0.5+h/w/2+0.04,0.5+h/w/2+0.02,0.5+h/w/2+0.03,0.5+h/w/2+0.03),lwd=1,
      col=tcol)
lines(c(1,1,1,0.5+0.07),c(0.5+h/w/2+0.04,0.5+h/w/2+0.02,0.5+h/w/2+0.03,0.5+h/w/2+0.03),lwd=1,
      col=tcol)
text(0.5,0.5+h/w/2+0.03,paste0(w," in"),col=tcol)

dd = runif(1,20,60)
angle1 = runif(1,0,90)

polygon(c(0.5-r*x/2/w,0.5-r*x/2/w,0.5+r*x/2/w,0.5+r*x/2/w),
        c(0.5-x/2/w,0.5+x/2/w,0.5+x/2/w,0.5-x/2/w),density=50,lwd=3,angle=angle1)
polygon(c(0.5-r*x/2/w,0.5-r*x/2/w,0.5+r*x/2/w,0.5+r*x/2/w),
        c(0.5-x/2/w,0.5+x/2/w,0.5+x/2/w,0.5-x/2/w),
        col=hsv((huecent+0.5-0.05)%%1,runif(1,0.7,1),runif(1,0.7,1)),
        density=dd,angle=angle1-1)
polygon(c(0.5-r*x/2/w,0.5-r*x/2/w,0.5+r*x/2/w,0.5+r*x/2/w),
        c(0.5-x/2/w,0.5+x/2/w,0.5+x/2/w,0.5-x/2/w),
        col=hsv((huecent+0.5+0.05)%%1,runif(1,0.7,1),runif(1,0.7,1)),
        density=dd-2,angle=angle1+1)
polygon(c(0.5-r*x/2/w,0.5-r*x/2/w,0.5+r*x/2/w,0.5+r*x/2/w),
        c(0.5-x/2/w,0.5+x/2/w,0.5+x/2/w,0.5-x/2/w),
        col=hsv((huecent+0.5)%%1,runif(1,0.7,1),runif(1,0.7,1)),
        density=dd-1,angle=angle1)


circ = function(cx,cy,r,col="red"){
  th = seq(0,2*pi,pi/100)
  polygon(cos(th)*r+cx,sin(th)*r+cy,col=col,border=NA)
}

xl = 0.5-r*x/2/w
xr = 0.5+r*x/2/w
yb = 0.5-x/2/w
yt = 0.5+x/2/w

for(i in 1:4){
  rad = runif(1,xs/20,xs/10)
  cx = c(xl+rad,xl+rad,xr-rad,xr-rad)[i]
  cy = c(yb+rad,yt-rad,yt-rad,yb+rad)[i]
  red = (huecent+runif(1,-0.05,0.05))%%1
  green = runif(1,0.7,1)
  blue = runif(1,0.5,1)
  alph = runif(1,0.8,1)
  circ(cx,cy,rad,hsv(red,green,blue,alph))
}
imax = 100
for(i in 1:imax){
  rad = min(xs/128*2^rexp(1,0.9),xs/2.5)
  cx = runif(1,0.5-x*r/2/w+rad,0.5+x*r/2/w-rad)
  cy = runif(1,0.5-x/2/w+rad,0.5+x/2/w-rad)
  red = (huecent+runif(1,-0.05,0.05))%%1
  green = runif(1)
  blue = runif(1)
  alph = 1 #runif(1,0.7,1)
  circ(cx,cy,rad,hsv(red,green,blue,alph))
}



polygon(c(0.5-r*x/2/w,0.5-r*x/2/w,0.5+r*x/2/w,0.5+r*x/2/w),
        c(0.5-x/2/w,0.5+x/2/w,0.5+x/2/w,0.5-x/2/w),lwd=1)


lines(c(xl,xl,xl,0.5-0.07),c(yt+0.04,yt+0.02,yt+0.03,yt+0.03),lwd=2,col="blue")
lines(c(xr,xr,xr,0.5+0.07),c(yt+0.04,yt+0.02,yt+0.03,yt+0.03),lwd=2,col="blue")
text(0.5,yt+0.03,paste0(r,"y",collapse=""),col="blue")
lines(c(xl-0.04,xl-0.02,xl-0.03,xl-0.03),c(yt,yt,yt,0.5+0.04),lwd=2,col="darkgreen")
lines(c(xl-0.04,xl-0.02,xl-0.03,xl-0.03),c(yb,yb,yb,0.5-0.04),lwd=2,col="darkgreen")
text(0.5-x*r/2/w-0.03,0.5,"y",srt=90,col="darkgreen")

arrows(0.5+x*r/2/w,0.5,1,0.5,length=0.1,angle=45,code=3,col="red",lwd=2)
text((0.5+x*r/2/w+1)/2,0.46,"b",col="red")
arrows(0.5,0.5-x/2/w,0.5,0.5-h/2/w,length=0.1,angle=45,code=3,col="red",lwd=2)
text(0.53,(1-x/2/w-h/2/w)/2,"b",col="red")

```
\

Find $`r let`$, `r wrds`. The tolerance is $\pm 0.01$ inches.

Solution
========

A system of equations can be written from the frame's width and height:

$$`r w` = `r r`y+2b$$
$$`r h` = y+2b$$
Subtract the two equations.

$$`r w-h` = `r r-1`y$$

Divide both sides by `r r-1`.

$$`r (w-h)/(r-1)` = y$$

To find $b$, you can rearrange the second equation from the system, and plug in the value of $y$.
$$b ~=~ \frac{`r h`-y}{2} ~=~ \frac{`r h`-`r x`}{2} ~=~ `r (h-x)/2`$$


Meta-information
============
extype: num
exsolution: `r sol`
exname: resize_image_even_border
extol: 0.01