```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
while(T){
    hkr = sample(2:15,3)*c(sample(c(-1,1),2,T),1)
    h = hkr[1]
    k = hkr[2]
    r = abs(hkr[3])
    extrms = c(h-r,k-r,h+r,k+r)
    if(max(abs(extrms))<15){break}
}


ach = -15:15

sol1 = paste0(1*(ach==h),collapse="")
sol2 = paste0(1*(ach==k),collapse="")
sol3 = paste0(1*(ach==r),collapse="")

al = paste0("* ",ach,collapse="\n")

```

Question
========

A circle is the collection of points equally distant from a center. If the circle has a center $(h,k)$ and a radius $r$, then we can represent that circle in the $xy$-plane using the following standard form of a circle:

$$(x-h)^2+(y-k)^2 = r^2$$

Notice that this equation looks like the Pythagorean Equation (from the Pythagorean Theorem): $a^2+b^2=c^2$. It also looks like the distance formula, were $r$ is the distance, $x-h$ is the horizontal displacement, and $y-k$ is the vertical displacement.

Consider the circle graphed below. Some of the points on the circle are $(`r h+r`,`r k`)$, $(`r h`,`r k+r`)$, $(`r h-r`,`r k`)$, and $(`r h`,`r k-r`)$.

```{r,echo=F,fig.dim=c(7,7)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-15,15),ylim=c(-15,15))
for(i in -15:15){
    lines(c(-15,15),c(i,i),col="lightgrey",lwd=0.5)
    lines(c(i,i),c(-15,15),col="lightgrey",lwd=0.5)
}
for(i in seq(-15,15,5)){
    lines(c(-15,15),c(i,i),col="darkgrey",lwd=1)
    lines(c(i,i),c(-15,15),col="darkgrey",lwd=1)
}
arrows(-15.5,0,15.5,0,0.1,10,3,lwd=2)
arrows(0,-15.5,0,15.5,0.1,10,3,lwd=2)
text(15,-0.5,"15")
text(15,0.5,"x")
text(-0.5,15,"15")
text(0.5,15,"y")

th = seq(0,2*pi,pi/300)
lines(h+r*cos(th),k+r*sin(th),lwd=3,col="blue")


```
\

Find the values of the parameters $h$, $k$, and $r$.

* $h=$ ##ANSWER1##
* $k=$ ##ANSWER2##
* $r=$ ##ANSWER3##


Answerlist
--------

`r al`
`r al`
`r al`


Solution
========

The center of the circle is at $(`r h`, `r k`)$, so $h=`r h`$ and $k=`r k`$. The radius of the circle is the distance from the center to the edge. The radius is `r r`, so $r=`r r`$.

```{r,echo=F}
eq = paste0("(x-",h,")^2+(y-",k,")^2=",r,"^2",collapse="")
eq = gsub("--","+",eq,fixed=T)
```

The standard equation of the circle is shown:

$$`r eq`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: circ_params_from_graph