```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

hkr = sample(3:12,3)*c(sample(c(-1,1),2),1)
h = hkr[1]
k = hkr[2]
r = abs(hkr[3])
extrms = c(h-r,k-r,h+r,k+r)

ach = -15:15

sol1 = paste0(1*(ach==h),collapse="")
sol2 = paste0(1*(ach==k),collapse="")
sol3 = paste0(1*(ach==r),collapse="")

al = paste0("* ",ach,collapse="\n")

```

Question
========

```{r,echo=F}
eq = paste0("(x-",h,")^2+(y-",k,")^2=",r^2,collapse="")
eq = gsub("--","+",eq,fixed=T)
```

The following equation produces a circle.

$$`r eq`$$

That circle has a center point, $(h,k)$, and radius, $r$.


Find the values of the parameters $h$, $k$, and $r$.

* $h=$ ##ANSWER1##
* $k=$ ##ANSWER2##
* $r=$ ##ANSWER3##


Answerlist
--------

`r al`
`r al`
`r al`


Solution
========

The standard form of a circle at center $(h,k)$ with radius $r$ is:

$$(x-h)^2+(y-k)^2=r^2$$

The given equation:

```{r,echo=F}
eq = paste0("(x-",h,")^2+(y-",k,")^2=",r^2,collapse="")
eq = gsub("--","+",eq,fixed=T)
```

$$`r eq`$$

With a bit of rearrangement:

```{r,echo=F}
eq = paste0("\\left(x-(",h,")\\right)^2+\\left(y-(",k,")\\right)^2=",r,"^2",collapse="")
```

$$`r eq`$$

* $h=`r h`$
* $k=`r k`$
* $r=`r r`$

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: circ_params_from_graph