```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
while(T){
    horv = sample(1:2,1)
    desc = c("horizontal","vertical")[horv]
    hork = round(sample(10:90,2)/100,2)
    usfl = hork[1]
    rdhr = hork[2]
    pnt = c(paste0("(",rdhr,",",usfl,")",collapse=""),paste0("(",usfl,",",rdhr,")",collapse=""))[horv]
    qdnt = c("II","IV")[horv]
    unkn = c("x","y")[horv]
    lv = c("y","x")[horv]
    ans = sqrt(1-usfl^2)
    xy = list(c(ans,usfl),
              c(usfl,ans))[[horv]]
    x = xy[1]
    y = xy[2]
    if(min(diff(sort(c(hork,ans))))>0.05){break}
}


```

Question
========

A circle is centered at the origin with a radius equal to 1. This circle is called [the unit circle](https://en.wikipedia.org/wiki/Unit_circle), where "unit" refers to 1. 

A **`r desc`** line passes through point $`r pnt`$.

That `r desc` line intersects the circle at two points: one in Quadrant I and another in Quadrant `r qdnt`. 

Determine the $`r unkn`$-coordinate of the intersection between the line and the circle in Quadrant I.

Please be accurate within $\pm 0.001$.


Solution
========

The general form of a circle:

$$(x-h)^2+(y-k)^2~=~r^2$$

We were told the center is $(0,0)$ and radius is 1. So, the equation of the unit circle:

$$(x-0)^2+(y-0)^2=1^2$$

$$x^2+y^2=1$$

The general form of a `r desc` line:

$$`r lv`=c$$

In our case, because the line hits point $`r pnt`$ we know the `r desc` line should include every point where $`r lv`$ equals `r usfl`.
$$`r lv`=`r usfl`$$

So, to find the other coordinate of the intersection, replace `r lv` with `r usfl` in the unit-circle equation. Solve for `r unkn`.

```{r, echo=F}
if(horv==1){
    eq1 = paste0("x^2+",usfl,"^2=1",collapse="")
    eq2 = paste0("x^2=1-",usfl,"^2",collapse="")
    eq3 = paste0("x=\\sqrt{1-",usfl,"^2}",collapse="")
} else {
    eq1 = paste0(usfl,"^2+y^2=1",collapse="")
    eq2 = paste0("y^2=1-",usfl,"^2",collapse="")
    eq3 = paste0("y=\\sqrt{1-",usfl,"^2}",collapse="")
}
```

$$`r eq1`$$
$$`r eq2`$$
$$`r eq3`$$
$$`r unkn`~\approx~`r ans`$$

Let's graph the circle, both points, and line.

```{r,echo=F}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1.2,1.2),ylim=c(-1.2,1.2),axes=F,ann=F)
for(i in seq(-1,1,0.1)){
    lines(c(i,i),c(-1,1),col="lightgrey",lwd=0.6)
    lines(c(-1,1),c(i,i),col="lightgrey",lwd=0.6)
}
for(i in seq(-1,1,0.5)){
    lines(c(i,i),c(-1,1),col="darkgrey",lwd=1.0)
    lines(c(-1,1),c(i,i),col="darkgrey",lwd=1.0)
}
arrows(-1.1,0,1.1,0,.1,10,3,lwd=2)
arrows(0,-1.1,0,1.1,.1,10,3,lwd=2)
th = seq(0,2*pi,pi/300)
lines(cos(th),sin(th),lwd=2.5,col="blue")
if(horv==1){
    lines(c(-1.05,1.05),c(usfl,usfl),col="purple",lwd=2.5)
    points(rdhr,usfl,col="red",pch=19)
    eq1 = paste0("x^2+",usfl,"^2=1",collapse="")
    eq2 = paste0("x^2=1-",usfl,"^2",collapse="")
    eq3 = paste0("x=\\sqrt{1-",usfl,"^2}",collapse="")
} else {
    lines(c(usfl,usfl),c(-1.05,1.05),col="purple",lwd=2.5)
    points(usfl,rdhr,col="red",pch=19)
    eq1 = paste0(usfl,"^2+y^2=1",collapse="")
    eq2 = paste0("y^2=1-",usfl,"^2",collapse="")
    eq3 = paste0("y=\\sqrt{1-",usfl,"^2}",collapse="")
}
points(x,y,col="black",pch=19)
library(latex2exp)
legend("topleft",
       legend=c(TeX("$x^2+y^2=1$"),
                TeX(pnt),
                TeX(paste0("$",lv,"=",usfl,"$",collapse="")),
                TeX(paste0("$(",round(x,3),",",round(y,3),")$",collapse=""))),
       col=c("blue","red","purple","black"),
       lwd=c(2.5,NA,2.5,NA),
       pch=c(NA,20,NA,20)
       )
text(1.02,-0.05,"1")
text(0.5,-0.05,"0.5")
text(-1.02,-0.05,"-1")
text(-0.5,-0.05,"-0.5")
text(1.02,0.05,"x")
text(-0.05,1.02,"1")
text(-0.07,0.5,"0.5")
text(-0.05,-1.02,"-1")
text(-0.07,-0.5,"-0.5")
text(0.05,1.02,"y")
```
\




Meta-information
============
extype: num
exsolution: `r ans`
exname: circ_2nd_coordinate
extol: 0.001