```{r,echo=F}
hd = sample(10:30,1)*10
vd = sample(1:6,1)*10
ls = round(runif(1,2,4),1)
ss = round(runif(1,0.8,1.9),1)

xx = seq(0,hd,0.01)
tt = xx/ls+sqrt((hd-xx)^2+vd^2)/ss

tmin = min(tt)
xmin = xx[tt==tmin]
```

Question
========

A lifeguard wants to save a struggling swimmer as soon as possible. The lifeguard can run along the beach at `r ls` m/s and swim at `r ss` m/s. The lifeguard will run $x$ meters and swim $\sqrt{(`r hd`-x)^2+`r vd`^2}$ meters.

```{r,echo=F}
par(mar=c(0,0,0,0))
plot(0,0,type="n",axes=F,ann=F,xlim=c(0,1),ylim=c(0,1))
t = seq(0,1,0.01)
polygon(c(0,0,t,1,1),c(0,0.2,sin(10*pi*t)/150+0.2,0.2,0),col=rgb(0.9,0.9,0.3),border = NA)
polygon(c(0,0,t,1,1),c(1,0.2,sin(10*pi*t)/150+0.2,0.2,1),col=rgb(0.7,0.7,1),border= NA)
lines(c(0.1,0.6,0.9),c(0.19,0.19,0.7),col="red",lwd=4)
lines(c(0.6,0.9,0.9),c(0.19,0.19,0.7),lty=3,col="red",lwd=3)
points(0.1,0.19,cex=2,pch=21,col="black",bg="red")
points(0.9,0.7,cex=2,pch=21,col="black",bg="purple")
lines(c(0.1,0.1,0.9,0.9),c(0.13,0.1,0.1,0.13))
text(0.5,0.05,paste(hd," m",collapse=""))
text(0.35,0.25,"x",col="red",cex=1.5)
lines(c(0.93,0.95,0.95,0.93),c(0.19,0.19,0.7,0.7))
text(0.97,0.45,paste(vd," m",collapse=""),srt=90)
text(0.1,0.25,"lifeguard",col="red")
text(0.9,0.75,"swimmer",col="purple")
```
\

Thus, the time is a function of $x$. Find the value of $x$ (in meters) that minimizes the amount of time. The tolerance is $\pm 0.1$ meters.

Solution
========

Use a graphing utility to find the minimum.

```{r,echo=F}
xx = seq(0,hd,0.1)
tt = xx/ls+sqrt((hd-xx)^2+vd^2)/ss
plot(xx,tt,type="l",ylim=c(0,max(tt)),xlab="x (meters)",ylab="t (seconds)")
points(xmin,tmin,pch=20,col="red")
text(xmin-10,tmin*0.8,paste0("(",xmin,", ",round(tmin,2),")",collapse=""),col="red")
```
\

So the optimal value of $x$ equals `r xmin` in order to get to the struggling swimmer as quickly as possible.


Meta-information
============
extype: num
exsolution: `r xmin`
exname: which_has_complex_sol
extol: 0.1