---
output: slidy_presentation
---

# Agenda

* Entrance Ticket: [ET_0924](https://bart.instructure.com/courses/2110/quizzes/3196)
* Shifting $y=\sqrt{x}$
    * [slides_0924](https://chadworley.github.io/algtwo2026/u02/09_24/slides_0924.html)
    * [OCW_0924_A_shift_square_root](https://bart.instructure.com/courses/2110/quizzes/3199)
* Shifting $y=|x|$ and $y=x^2$ and $y=x^3$ and $y=\sqrt[3]{x}$
    * [OCW_0924_B_shift_parents](https://bart.instructure.com/courses/2110/quizzes/3200)

# The square-root function

* The [square-root](https://en.wikipedia.org/wiki/Square_root) function is typically indicated with a [radical symbol](https://en.wikipedia.org/wiki/Radical_symbol).
$$\text{square-root}(x) ~=~ \sqrt{x}$$
* Notice the [overline](https://en.wikipedia.org/wiki/Overline) indicates the [argument](https://en.wikipedia.org/wiki/Argument_of_a_function) of the function.
$$\sqrt{\mathrm{argument}}$$
* The square-root function is an imperfect **[inverse](https://en.wikipedia.org/wiki/Inverse_function)** of the [squaring function](https://en.wikipedia.org/wiki/Square_(algebra)#square_function). For example...
$$\sqrt{3^2}=3$$
$$\sqrt{4^2}=4$$
$$\sqrt{(-4)^2}\ne -4$$
* Here are some key input-output pairs:
$$\sqrt{0}=0$$
$$\sqrt{1}=1$$
$$\sqrt{4}=2$$
$$\sqrt{9}=3$$
$$\sqrt{16}=4$$
$$\sqrt{25}=5$$

* Practice: evaluate the expression.
$$2\cdot \sqrt{\frac{10}{2}+11}+4$$

# The graph of $y=\sqrt{x}$

```{r,echo=F,fig.dim=c(9,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,25),ylim=c(-5,5),axes=F,ann=F)
for(i in -5:25){
    lines(c(i,i),c(-5,5),lwd=0.4)
}
for(i in -5:5){
    lines(c(-5,25),c(i,i),lwd=0.4)
}
for(i in seq(-5,25,5)){
    lines(c(i,i),c(-5,5),lwd=1)
    if(i!=0){
        text(i,-0.5,i)
    }
}
for(i in seq(-5,5,5)){
    lines(c(-5,25),c(i,i),lwd=1)
    if(i!=0){
        text(-0.5,i,i)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl,yl,lwd=3,col="blue")
points(xp,yp,pch=19,col="blue")
text(25.5,0,"x",adj=c(0.5,1.3))
text(0.25,5.1,"y")

```


```{r,echo=F,warning=FALSE}
library(kableExtra)
df = data.frame(xp,yp)
colnames(df) = c("$x$","$y$")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```

# Add a constant in the argument

Some solutions to $b=\sqrt{a}$ are shown below.

```{r,echo=F,warning=FALSE}
eqs = paste0("$\\sqrt{",(0:5)^2,"}=",0:5,"$")
df = data.frame(xp,yp,eqs)
colnames(df) = c("$a$","$b$","equation")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```


Find the corresponding solutions to $y=\sqrt{x+2}$.

```{r,echo=F,warning=FALSE}
blanks = rep("$\\phantom{\\cfrac{999}{999}}$",length(xp))
df = data.frame(blanks,blanks)
colnames(df) = c("$x$","$y$")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```

# Graph of $y=\sqrt{x+2}$


```{r,echo=F,fig.dim=c(9,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,25),ylim=c(-5,5),axes=F,ann=F)
for(i in -5:25){
    lines(c(i,i),c(-5,5),lwd=0.4)
}
for(i in -5:5){
    lines(c(-5,25),c(i,i),lwd=0.4)
}
for(i in seq(-5,25,5)){
    lines(c(i,i),c(-5,5),lwd=1)
    if(i!=0){
        text(i,-0.5,i)
    }
}
for(i in seq(-5,5,5)){
    lines(c(-5,25),c(i,i),lwd=1)
    if(i!=0){
        text(-0.5,i,i)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(25.5,0,"x",adj=c(0.5,1.3))
text(0.25,5.1,"y")

yp = 0:5
xp = yp^2-2
xl = seq(-2,25,0.1)
yl = sqrt(xl+2)
lines(xl,yl,lwd=3,col="blue")
points(xp,yp,pch=19,col="blue")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl,yl,lwd=3,col="grey")
points(xp,yp,pch=19,col="grey")

library(latex2exp)
legend("topleft",c(TeX("$y=\\sqrt{x+2}$"),TeX("$y=\\sqrt{x}$")),col=c("blue","grey"),lwd=c(3,3))

```

Adding 2 inside the argument shifted (translated) the curve 2 units to the **LEFT**.


# Add constant outside of function

Some solutions to $b=\sqrt{a}$ are shown below.

```{r,echo=F,warning=FALSE}
eqs = paste0("$\\sqrt{",(0:5)^2,"}=",0:5,"$")
df = data.frame(xp,yp,eqs)
colnames(df) = c("$a$","$b$","equation")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```

Find the corresponding solutions to $y=\sqrt{x}+2$.

```{r,echo=F,warning=FALSE}
blanks = rep("$\\phantom{\\cfrac{999}{999}}$",length(xp))
df = data.frame(blanks,blanks)
colnames(df) = c("$x$","$y$")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```

# Graph of $y=\sqrt{x}+2$

```{r,echo=F,fig.dim=c(9,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,25),ylim=c(-5,5),axes=F,ann=F)
for(i in -5:25){
    lines(c(i,i),c(-5,5),lwd=0.4)
}
for(i in -5:5){
    lines(c(-5,25),c(i,i),lwd=0.4)
}
for(i in seq(-5,25,5)){
    lines(c(i,i),c(-5,5),lwd=1)
    if(i!=0){
        text(i,-0.5,i)
    }
}
for(i in seq(-5,5,5)){
    lines(c(-5,25),c(i,i),lwd=1)
    if(i!=0){
        text(-0.5,i,i)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(25.5,0,"x",adj=c(0.5,1.3))
text(0.25,5.1,"y")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)+2
lines(xl,yl,lwd=3,col="blue")
points(xp,yp+2,pch=19,col="blue")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl,yl,lwd=3,col="grey")
points(xp,yp,pch=19,col="grey")

library(latex2exp)
legend("topleft",c(TeX("$y=\\sqrt{x}+2$"),TeX("$y=\\sqrt{x}$")),col=c("blue","grey"),lwd=c(3,3))

```

Adding 2 outside the argument shifted (translated) the curve 2 units **UP**.

# Subtract constant inside of function

Some solutions to $b=\sqrt{a}$ are shown below.

```{r,echo=F,warning=FALSE}
eqs = paste0("$\\sqrt{",(0:5)^2,"}=",0:5,"$")
df = data.frame(xp,yp,eqs)
colnames(df) = c("$a$","$b$","equation")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```

Find the corresponding solutions to $y=\sqrt{x-2}$.

```{r,echo=F,warning=FALSE}
blanks = rep("$\\phantom{\\cfrac{999}{999}}$",length(xp))
df = data.frame(blanks,blanks)
colnames(df) = c("$x$","$y$")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```

# Graph of $y=\sqrt{x-2}$

```{r,echo=F,fig.dim=c(9,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,25),ylim=c(-5,5),axes=F,ann=F)
for(i in -5:25){
    lines(c(i,i),c(-5,5),lwd=0.4)
}
for(i in -5:5){
    lines(c(-5,25),c(i,i),lwd=0.4)
}
for(i in seq(-5,25,5)){
    lines(c(i,i),c(-5,5),lwd=1)
    if(i!=0){
        text(i,-0.5,i)
    }
}
for(i in seq(-5,5,5)){
    lines(c(-5,25),c(i,i),lwd=1)
    if(i!=0){
        text(-0.5,i,i)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(25.5,0,"x",adj=c(0.5,1.3))
text(0.25,5.1,"y")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl+2,yl,lwd=3,col="blue")
points(xp+2,yp,pch=19,col="blue")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl,yl,lwd=3,col="grey")
points(xp,yp,pch=19,col="grey")

library(latex2exp)
legend("topleft",c(TeX("$y=\\sqrt{x-2}$"),TeX("$y=\\sqrt{x}$")),col=c("blue","grey"),lwd=c(3,3))

```

**Subtracting** 2 inside the argument shifted (translated) the curve 2 units **RIGHT**.

$$(a,b)~\to~(a+2,b)$$

The horizontal coordinate transformations are from the INVERSE of the argument.

Remember, we can set the argument equal to $a$.

$$a=x-2$$

And solve for $x$.

$$x=a+2$$

# Subtracting a constant outside the function

Some solutions to $b=\sqrt{a}$ are shown below.

```{r,echo=F,warning=FALSE}
eqs = paste0("$\\sqrt{",(0:5)^2,"}=",0:5,"$")
df = data.frame(xp,yp,eqs)
colnames(df) = c("$a$","$b$","equation")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```

Find the corresponding solutions to $y=\sqrt{x}-2$.

```{r,echo=F,warning=FALSE}
blanks = rep("$\\phantom{\\cfrac{999}{999}}$",length(xp))
df = data.frame(blanks,blanks)
colnames(df) = c("$x$","$y$")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```


# Graph of $y=\sqrt{x}-2$


```{r,echo=F,fig.dim=c(9,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,25),ylim=c(-5,5),axes=F,ann=F)
for(i in -5:25){
    lines(c(i,i),c(-5,5),lwd=0.4)
}
for(i in -5:5){
    lines(c(-5,25),c(i,i),lwd=0.4)
}
for(i in seq(-5,25,5)){
    lines(c(i,i),c(-5,5),lwd=1)
    if(i!=0){
        text(i,-0.5,i)
    }
}
for(i in seq(-5,5,5)){
    lines(c(-5,25),c(i,i),lwd=1)
    if(i!=0){
        text(-0.5,i,i)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(25.5,0,"x",adj=c(0.5,1.3))
text(0.25,5.1,"y")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl,yl-2,lwd=3,col="blue")
points(xp,yp-2,pch=19,col="blue")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl,yl,lwd=3,col="grey")
points(xp,yp,pch=19,col="grey")

library(latex2exp)
legend("topleft",c(TeX("$y=\\sqrt{x}-2$"),TeX("$y=\\sqrt{x}$")),col=c("blue","grey"),lwd=c(3,3))

```


Subtracting 2 outside the function resulted is a shift **DOWN** by 2 units.

$$(a,b)~\to~(a,b-2)$$

Notice, we just replace the whole square-root function (and its argument) with $b$.


# Adding or Subtracting Inside and Out

Use these facts:
$$\sqrt{0}=0$$
$$\sqrt{1}=1$$
$$\sqrt{4}=2$$
$$\sqrt{9}=3$$
$$\sqrt{16}=4$$
$$\sqrt{25}=5$$

To find corresponding solutions to the equation below:
$$y=\sqrt{x-6}-4$$


# Some solutions to $y=\sqrt{x-6}-4$

```{r,echo=F,warning=FALSE}
eqs = paste0("$\\sqrt{",(0:5)^2,"}=",0:5,"$")
xx = c(0,1,4,9,16,25)+6
yy = (0:5)-4
exps = paste0("$\\sqrt{",xx,"-6}-4$")
x2 = paste0("$",xx,"$")
y2 = paste0("$",yy,"$")
df = data.frame(eqs,x2,exps,y2)
colnames(df) = c("square-root fact","$~~~x~~~$","$\\sqrt{x-6}-4$","$~~~y~~~$")
kable(df,align = "c") %>%
    kable_styling("bordered",full_width = F)
```



```{r,echo=F,fig.dim=c(9,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,25),ylim=c(-5,5),axes=F,ann=F)
for(i in -5:25){
    lines(c(i,i),c(-5,5),lwd=0.4)
}
for(i in -5:5){
    lines(c(-5,25),c(i,i),lwd=0.4)
}
for(i in seq(-5,25,5)){
    lines(c(i,i),c(-5,5),lwd=1)
    if(i!=0){
        text(i,-0.5,i)
    }
}
for(i in seq(-5,5,5)){
    lines(c(-5,25),c(i,i),lwd=1)
    if(i!=0){
        text(-0.5,i,i)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(25.5,0,"x",adj=c(0.5,1.3))
text(0.25,5.1,"y")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl+6,yl-4,lwd=3,col="blue")
points(xp+6,yp-4,pch=19,col="blue")

yp = 0:5
xp = yp^2
xl = seq(0,25,0.1)
yl = sqrt(xl)
lines(xl,yl,lwd=3,col="grey")
points(xp,yp,pch=19,col="grey")

library(latex2exp)
legend("topleft",c(TeX("$y=\\sqrt{x-6}-4$"),TeX("$y=\\sqrt{x}$")),col=c("blue","grey"),lwd=c(3,3))

```

The curve shifted 6 units right and 4 units down.


# Other examples of shifted parent functions


```{r,echo=F,fig.dim=c(5,5)}
hk = sample(1:6,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
lr = c("left","right")[(sign(h)+1)/2+1]
du = c("down","up")[(sign(k)+1)/2+1]
x1 = seq(-30,30,0.1)
y1 = abs(x1)
x2 = x1+h
y2 = y1+k
cch = paste0("|x+",-h,"|+",k,collapse="")
cch = gsub("+-","-",cch,fixed=T)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),lwd=0.4)
    lines(c(-10,10),c(i,i),lwd=0.4)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),lwd=0.8)
    lines(c(-10,10),c(i,i),lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

text(10.5,-0.5,"x")
text(-0.5,10.5,"y")
text(5,-0.5,"5")
text(-0.5,5,"5")

lines(x2,y2,col="blue",lwd=3)
```
\

$$y=`r cch`$$

# Other examples of shifted parent functions


```{r,echo=F,fig.dim=c(5,5)}
hk = sample(1:6,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
lr = c("left","right")[(sign(h)+1)/2+1]
du = c("down","up")[(sign(k)+1)/2+1]
x1 = seq(-30,30,0.1)
y1 = (x1)^2
x2 = x1+h
y2 = y1+k
cch = paste0("(x+",-h,")^2+",k,collapse="")
cch = gsub("+-","-",cch,fixed=T)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),lwd=0.4)
    lines(c(-10,10),c(i,i),lwd=0.4)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),lwd=0.8)
    lines(c(-10,10),c(i,i),lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

text(10.5,-0.5,"x")
text(-0.5,10.5,"y")
text(5,-0.5,"5")
text(-0.5,5,"5")

lines(x2,y2,col="blue",lwd=3)
```
\

$$y=`r cch`$$


# Other examples of shifted parent functions

```{r,echo=F,fig.dim=c(5,5)}
hk = sample(1:6,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
lr = c("left","right")[(sign(h)+1)/2+1]
du = c("down","up")[(sign(k)+1)/2+1]
x1 = seq(-30,30,0.1)
y1 = (x1)^3
x2 = x1+h
y2 = y1+k
cch = paste0("(x+",-h,")^3+",k,collapse="")
cch = gsub("+-","-",cch,fixed=T)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),lwd=0.4)
    lines(c(-10,10),c(i,i),lwd=0.4)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),lwd=0.8)
    lines(c(-10,10),c(i,i),lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

text(10.5,-0.5,"x")
text(-0.5,10.5,"y")
text(5,-0.5,"5")
text(-0.5,5,"5")

lines(x2,y2,col="blue",lwd=3)
```
\

$$y=`r cch`$$



# Other examples of shifted parent functions

```{r,echo=F,fig.dim=c(5,5)}
hk = sample(1:6,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
lr = c("left","right")[(sign(h)+1)/2+1]
du = c("down","up")[(sign(k)+1)/2+1]
x1 = seq(-30,30,0.1)
y1 = sign(x1)*abs(x1)^(1/3)
x2 = x1+h
y2 = y1+k
cch = paste0("\\sqrt[3]{x+",-h,"}+",k,collapse="")
cch = gsub("+-","-",cch,fixed=T)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),lwd=0.4)
    lines(c(-10,10),c(i,i),lwd=0.4)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),lwd=0.8)
    lines(c(-10,10),c(i,i),lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

text(10.5,-0.5,"x")
text(-0.5,10.5,"y")
text(5,-0.5,"5")
text(-0.5,5,"5")

lines(x2,y2,col="blue",lwd=3)
```
\

$$y=`r cch`$$


