```{r,echo=F}
while(T){
  phi = round(runif(1,pi/8,pi/2-pi/8),2)*sample(c(-1,1),1)
  m = tan(phi)
  b = runif(1,-4,4)
  x0 = -b/m
  if(round(phi,1)!=phi && abs(x0)<5){break}
}
```

Question
========

A line forms an angle of inclination of $\theta=`r phi`$ radians with the horizontal axis. What is the slope of the line?

```{r,fig.dim=c(6,6),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
for(i in 1:10){
  p = seq(-10,10,0.2)
  points(rep(i,length(p)),p,col="grey",pch=19,cex=0.2)
  points(rep(-i,length(p)),p,col="grey",pch=19,cex=0.2)
  points(p,rep(i,length(p)),col="grey",pch=19,cex=0.2)
  points(p,rep(-i,length(p)),col="grey",pch=19,cex=0.2)
}
arrows(0,-10.5,0,10.5,length=0.1,angle=10,code=3,lwd=2)
arrows(-10.5,0,10.5,0,length=0.1,angle=10,code=3,lwd=2)
abline(b,m,col="blue",lwd=2)
ts = seq(0,phi,length.out=100)
lines(x0+cos(ts),sin(ts),col="red",lwd=4)
text(x0+2*cos(phi/2),2*sin(phi/2),TeX("$\\theta$"),srt=phi/2/pi*180,cex=2,col="red")
```
\

In other words, the line could be represented with a linear equation, $y=mx+b$, and your goal is to determine $m$.

The tolerance is $\pm 0.01$.

Solution
========

Draw a right triangle.

```{r,fig.dim=c(6,6),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
for(i in 1:10){
  p = seq(-10,10,0.2)
  points(rep(i,length(p)),p,col="grey",pch=19,cex=0.2)
  points(rep(-i,length(p)),p,col="grey",pch=19,cex=0.2)
  points(p,rep(i,length(p)),col="grey",pch=19,cex=0.2)
  points(p,rep(-i,length(p)),col="grey",pch=19,cex=0.2)
}
arrows(0,-10.5,0,10.5,length=0.1,angle=10,code=3,lwd=2)
arrows(-10.5,0,10.5,0,length=0.1,angle=10,code=3,lwd=2)
abline(b,m,col=rgb(0.8,0.8,1),lwd=2)
ts = seq(0,phi,length.out=100)
lines(x0+cos(ts),sin(ts),col=rgb(1,0.3,0.3),lwd=2)
text(x0+1.3*cos(phi/2),1.3*sin(phi/2),TeX("$\\phi$"),srt=phi/2/pi*180,cex=1,col=rgb(1,0.3,0.3))
lines(c(x0,x0+4,x0+4,x0),c(0,0,4*m,0),col="purple",lwd=3)
lines(c(x0+3.5,x0+3.5,x0+4),c(0,0.5*sign(m),0.5*sign(m)),col="purple",lwd=1)
text(x0+2,-0.5*sign(m),TeX("$\\Delta x$"),col="purple",cex=1.5)
text(x0+4.5,2*m,TeX("$\\Delta y$"),col="purple",cex=1.5)
```
\

Remember that the slope is equivalent to rise over run.

$$m = \frac{\Delta y}{\Delta x}$$

Recognize that the tangent (trigonometric) function also represents this ratio.

$$\tan(\phi) = \frac{\Delta y}{\Delta x}$$

Use the [transitive property of equality](https://simple.wikipedia.org/wiki/Equality_(mathematics)#:~:text=An%20equality%20is%20also%20a,the%20third%20object%20as%20well.).

$$m ~=~ \tan(`r phi`) ~=~ `r m`$$


Meta-information
============
extype: num
exsolution: `r m`
exname: slope
extol: 0.01