```{r,echo=F}
while(T){
  grad = round(runif(1,7,45),1)
  if(grad != round(grad)){break}
}
rad = atan(grad/100)
deg = rad/pi*180
```

Question
========

On steep streets, you may see signs that indicate the [grade](https://en.wikipedia.org/wiki/Grade_(slope)), which is usually shown as a percentage. The grade is equivalent to [slope](https://en.wikipedia.org/wiki/Slope), written as a percentage.

The highest grade of the Ashuwillticook Rail Trail is 2.5%. The Mohawk Trail (Route 2), near the hairpin turn, has sections of 8% grade. Notch Road, heading up Mount Greylock, has grades as high as 12%. Circuit Road, below Berry Pond in Pittsfield State Forest, has a section of 16% grade. Thunderbolt Ski Trail's steepest section has 35% grade.

```{r,fig.dim=c(6,6),echo=F}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
yel1 = rgb(1,0.9,0)
th1 = seq(3*pi/4,5*pi/4,length.out=50)
th2 = seq(5*pi/4,7*pi/4,length.out=50)
th3 = seq(-pi/4,pi/4,length.out=50)
th4 = seq(pi/4,3*pi/4,length.out=50)
lr = 0.02
polygon(c(-1+lr*cos(th1),
          lr*cos(th2),
          1+lr*cos(th3),
          lr*cos(th4)),
        c(lr*sin(th1),
          -1+lr*sin(th2),
          lr*sin(th3),
          1+lr*sin(th4)),
        col=yel1,border=F)
rr = 0.96
polygon(rr*c(-1+lr*cos(th1),
          lr*cos(th2),
          1+lr*cos(th3),
          lr*cos(th4)),
        rr*c(lr*sin(th1),
          -1+lr*sin(th2),
          lr*sin(th3),
          1+lr*sin(th4)),col=yel1,lwd=3)
dx = 1
dy = 0.5
m = dy/dx
b = -0.05
t = atan(m)
polygon(c(-0.5,0.5,0.5),c(-0.3,-0.3,0.2),col="black",border=NA)
wr = 0.05
th = seq(0,2*pi,length.out=100)
x1 = -0.4
y1 = m*x1+b
x1c = x1+wr*cos(pi/2+t)
y1c = y1+wr*sin(pi/2+t)
polygon(x1c+wr*cos(th),y1c+wr*sin(th),col="black",border=NA)
x1 = -0.1
y1 = m*x1+b
x1c = x1+wr*cos(pi/2+t)
y1c = y1+wr*sin(pi/2+t)
polygon(x1c+wr*cos(th),y1c+wr*sin(th),col="black",border=NA)
x1 = 0.4
y1 = m*x1+b
x1c = x1+wr*cos(pi/2+t)
y1c = y1+wr*sin(pi/2+t)
polygon(x1c+wr*cos(th),y1c+wr*sin(th),col="black",border=NA)
x1 = -0.2
y1 = m*x1+b
x2 = 0.5
y2 = m*x2+b
h1 = 1.6
h2 = 9
x1c = x1+h1*wr*cos(pi/2+t)
y1c = y1+h1*wr*sin(pi/2+t)
x1d = x1+h2*wr*cos(pi/2+t)
y1d = y1+h2*wr*sin(pi/2+t)
x2c = x2+h1*wr*cos(pi/2+t)
y2c = y2+h1*wr*sin(pi/2+t)
x2d = x2+h2*wr*cos(pi/2+t)
y2d = y2+h2*wr*sin(pi/2+t)
polygon(c(x1c,x1d,x2d,x2c),c(y1c,y1d,y2d,y2c),
        border=NA,col="black")

xas = c(-0.5,-0.49,-0.47,-0.4,-0.32,-0.23,-0.23,-0.1,-0.1,-0.23,-0.23)
has = c(1.2,3.6,4.1,4.1,6,6,1.9,1.9,1.6,1.6,1.2)
yas = m*xas+b
xa = xas+has*wr*cos(pi/2+t)
ya = yas+has*wr*sin(pi/2+t)
polygon(xa,ya,col="black",border=NA)
text(0,-0.55,paste0(grad,"%"),cex=3)
```
\

A grade of `r grad`% implies that for every 100 feet of horizontal travel (as seen on a map), the elevation changes by `r grad` feet. We wish to determine the angle of inclination (in degrees) of a `r grad`% grade.

```{r,echo=F,fig.width=7}
library(latex2exp)
par(mar=c(0,0,0,0))
plot(c(0,100,100,0),c(0,0,grad,0),type="l",asp=1,ann=F,axes=F,lwd=2)
lines(c(96,96,100),c(0,4,4))
text(50,2,"100")
text(95,grad/2,grad)
th = seq(0,rad,length.out=30)
polygon(c(0,20*cos(th)),c(0,20*sin(th)),col=rgb(1,0.8,0.8),border=NA)
lines(20*cos(th),20*sin(th),col="red",lwd=3)
text(25*cos(rad/2),25*sin(rad/2),col="red",TeX("$\\theta^{\\circ}$"))
```
\

Find $\theta$, the angle of inclination in degrees. The tolerance is $\pm0.1^\circ$.


Solution
========

Remember to use DEGREE mode.

$$\theta = \arctan\left(\frac{`r grad`}{100}\right)$$

$$\theta \approx `r round(deg,1)`^\circ$$

Humans tend to think terrain is much steeper than it truly is. It is tempting to think a hill is going up at a 45$^\circ$ angle, but this would be a 100% grade, much steeper than any public street in the world. The steepest public roads have angles of inclination under $`r round(atan(0.4)*180/pi)`^\circ$ (under 40% grade). Some examples: [Canton Avenue](https://en.wikipedia.org/wiki/Canton_Avenue) in Pennsylvania, [Baldwin Street](https://en.wikipedia.org/wiki/Baldwin_Street) in New Zealand, and [Ffordd_Pen_Llech](https://en.wikipedia.org/wiki/Ffordd_Pen_Llech) in North Wales.


Meta-information
============
extype: num
exsolution: `r deg`
exname: deg_from_grad
extol: 0.1