```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  rdn = sample(5:15,1)
  rnf = sample((rdn%/%2+1):(rdn*2-1),1)
  ttx = paste0("\\frac{",rnf,"\\pi}{",rdn,"}",collapse = "")
  t = rnf*pi/rdn
  r = sample(310:750,1)/100
  x = r*cos(t)
  y = r*sin(t)
  xa = round(x,2)
  ya = round(y,2)
  n = 8
  d = 0.05
  r = round(sqrt(xa^2+ya^2),2)
  t = round((atan2(ya,xa)+2*pi)%%(2*pi),2)
  ru = sqrt(xa^2+ya^2)
  tu = (atan2(ya,xa)+2*pi)%%(2*pi)
  which1 = sample(1:n,1)
  ac1 = round(seq(r-d*(which1-1),r+d*(n-which1),length.out=n),2)
  which2 = sample(1:n,1)
  ac2 = round(seq(t-d*(which2-1),t+d*(n-which2),length.out=n),2)
  al1 = paste0("* ",ac1,collapse="\n")
  al2 = paste0("* ",ac2,collapse="\n")
  sol1 = paste0(1*(ac1==r),collapse="")
  sol2 = paste0(1*(ac2==t),collapse="")
  if(gcd2(rdn,rnf)==1 && abs(x)>1.2 && abs(y)>1.2 &&
     abs(x)<4.5 && abs(y)<4.5 && round(r,1)!=r && sum(ac1==r)==1 && sum(ac2==t)==1){break}
}

```

Question
========

A point on a Cartesian plane is denoted in [rectangular coordinates](https://en.wikipedia.org/wiki/Cartesian_coordinate_system):
$$x = `r xa`$$
$$y=`r ya`$$

```{r,echo=F,fig.width=8}
library(latex2exp)
par(pty="s")
plot(x,y,xlim=c(-5,5),ylim=c(-5,5))
arrows(-5,0,5,0,length=0.1,angle=8,code=3,lwd=1)
arrows(0,-5,0,5,length=0.1,angle=8,code=3,lwd=1)
lines(c(0,x,x,0),c(0,0,y,0),lwd=2,col="purple")
lines(c(0,x),c(0,y),lwd=3,col="red")
text(x/2+0.5*cos(t+pi/2*sign(x*y)),
     y/2+0.5*sin(t+pi/2*sign(x*y)),"r",col="red",cex=1.5)
th = seq(0,t,length.out=100)
lines(cos(th),sin(th),col="blue")
arrows(cos(th[99]),sin(th[99]),cos(th[100]),sin(th[100]),col="blue",length=0.05,angle=20,lwd=2)
text(1.4*cos(t/2),1.4*sin(t/2),TeX("$\\theta$"),col="blue",cex=1.5)
points(x,y,pch=19,col="purple",cex=1.3)
text(x,y+sign(y)/2,"(x,y)",col="purple")
```


Please determine the polar coordinates ($r$ and $\theta$), enforcing $0\le\theta<2\pi$.

* The radius: $r=$ ##ANSWER1##
* The angle: $\theta=$ ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`



Solution
========

First, get the radius, using Pythagorean Theorem.

$$r = \sqrt{(`r abs(xa)`)^2+(`r abs(ya)`)^2}$$

$$r \approx `r r`$$


```{r,echo=FALSE}
if(t<3*pi/2){
  refinit = "\\pi"
  refnmr = abs(rnf-rdn)
} else {
  refinit = "2\\pi"
  refnmr = abs(rnf-2*rdn)
}
refnmrt = paste0(refnmr)
if(refnmrt=="1"){refnmrt=""}
```

We can use right-triangle trigonometry. Start by finding the [reference angle](https://courses.lumenlearning.com/csn-precalculus/chapter/reference-angles/) by using the arctan function with the quotient of the absolute values of the rectangular coordinates.

$$\phi ~=~ \arctan\left(\frac{`r abs(ya)`}{`r abs(xa)`}\right)$$

$$\phi ~=~ `r atan(abs(ya)/abs(xa))`$$

```{r,echo=F,fig.width=8}
library(latex2exp)
par(pty="s")
plot(x,y,xlim=c(-5,5),ylim=c(-5,5))
arrows(-5,0,5,0,length=0.1,angle=8,code=3,lwd=1)
arrows(0,-5,0,5,length=0.1,angle=8,code=3,lwd=1)
lines(c(0,x,x,0),c(0,0,y,0),lwd=2,col="purple")
lines(c(0,x),c(0,y),lwd=3,col="red")
text(x/2+0.5*cos(t+pi/2*sign(x*y)),
     y/2+0.5*sin(t+pi/2*sign(x*y)),"r",col="red",cex=1.5)
if(t<3*pi/2){t2=pi}else{t2=2*pi}
th = seq(t2,t,length.out=100)
lines(cos(th),sin(th),col="blue")
text(1.4*cos(th[50]),1.4*sin(th[50]),TeX("$\\phi$"),col="blue",cex=1)
points(x,y,pch=19,col="purple",cex=1.3)
text(x,y+sign(y)/2,"(x,y)",col="purple")
```


Remember, $r=`r r`$. Use trigonometry to calculate the lengths of the right triangle.

$$|x| ~=~ `r r`\cos\left(\frac{`r refnmrt`\pi}{`r rdn`}\right) ~=~ `r r*cos(abs(t-t2))`$$

$$|y| ~=~ `r r`\sin\left(\frac{`r refnmrt`\pi}{`r rdn`}\right) ~=~ `r r*sin(abs(t-t2))`$$

```{r,echo=FALSE}
qn = t%/%(pi/2)+1
```

Since we are in quadrant `r qn`, we know the signs of $x$ and $y$.

$$x = `r x`$$

$$y = `r y`$$

If you round to the hundredths place:

$$x = `r xa`$$
$$y = `r ya`$$

### Another approach

It turns out that the trigonometric functions are defined for all angles (not just acute angles). The way they are defined actually makes this problem trivial. There is no need to find an acute reference angle.

$$x = r \cos(\theta)$$

$$y = r \sin(\theta)$$

Using these above formulas will work directly. 


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: polar_to_rect