```{r,echo=F}
ts = c("0","\\frac{\\pi}{6}","\\frac{\\pi}{4}","\\frac{\\pi}{3}",
       "\\frac{\\pi}{2}","\\frac{2\\pi}{3}","\\frac{3\\pi}{4}",
       "\\frac{5\\pi}{6}","\\pi","\\frac{7\\pi}{6}","\\frac{5\\pi}{4}",
       "\\frac{4\\pi}{3}","\\frac{3\\pi}{2}","\\frac{5\\pi}{3}",
       "\\frac{7\\pi}{4}","\\frac{11\\pi}{6}","2\\pi")

xs = c("1","\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}","0",
       "\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}","-1",
       "\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}","0",
       "\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}","1")

ys = c("0","\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}","1",
       "\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}","0",
       "\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}","-1",
       "\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}","0")

choices = c("-1","\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}","0","\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}","1")

while(T){
  wi = sample(2:(length(ts)-1),1)
  cs = sample(1:2,1)
  
  if(cs==1){
    get = paste0("\\cos\\left(\\theta\\right)")
    stx = paste0("\\cos\\left(",ts[wi],"\\right)",collapse="")
    ans = paste0(xs[wi])
  }
  if(cs==2){
    get = paste0("\\sin\\left(\\theta\\right)")
    stx = paste0("\\sin\\left(",ts[wi],"\\right)",collapse="")
    ans = paste0(ys[wi])
  }
  al = paste0("* $",choices,"$",collapse="\n")
  sol = paste0(1*(ans==choices),collapse="")
  if(sum(ans==choices)==1){break}
}
```

Question
========

The [unit circle](https://en.wikipedia.org/wiki/Unit_circle) below has a radius of length 1. The coordinates of special angles are shown.

```{r,fig.dim=c(8,8),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-1.3,1.3),ylim=c(-1.3,1.3),axes=F,ann=F)
arrows(-1.05,0,1.05,0,0.08,12,3)
arrows(0,-1.05,0,1.05,0.08,12,3)
th = seq(0,2*pi,length.out=120)
lines(cos(th),sin(th))
th12 = seq(0,2*pi,length.out=25)
for(t in th12){
  lines(c(0,cos(t)),c(0,sin(t)),lty=3,col="grey")
}
thsp = c(0,pi/6,pi/4,pi/3,pi/2,2*pi/3,3*pi/4,5*pi/6,pi,
         7*pi/6,5*pi/4,4*pi/3,3*pi/2,5*pi/3,7*pi/4,11*pi/6,2*pi)

for(i in 1:length(thsp)){
  t = thsp[i]
  lines(c(0,cos(t)),c(0,sin(t)),col="red")
  points(cos(t),sin(t),pch=20,col="red")
  text(1.2*cos(t),1.2*sin(t),TeX(paste0("$\\left(",xs[i],",",ys[i],"\\right)$",collapse="")),cex=0.8)
}

ttt = seq(0,thsp[wi],length.out=100)
lines(0.3*cos(ttt),0.3*sin(ttt),col="blue",lwd=2)
text(0.4*cos(thsp[wi]/2),0.4*sin(thsp[wi]/2),TeX("$\\theta$"),cex=2,col="blue")
arrows(0.3*cos(ttt[99]),0.3*sin(ttt[99]),
       0.3*cos(ttt[100]),0.3*sin(ttt[100]),lwd=2,col="blue")

```
\

Determine $`r get`$.


Answerlist
--------

`r al`


Solution
========

Each point is $(\cos(\theta),\sin(\theta))$. So, the horizontal coordinate is the cosine of the angle and the vertical coordinate is the sine of the angle.

In this case, $\theta=`r ts[wi]`$.

```{r,fig.dim=c(8,8),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-1.3,1.3),ylim=c(-1.3,1.3),axes=F,ann=F)
arrows(-1.05,0,1.05,0,0.08,12,3)
arrows(0,-1.05,0,1.05,0.08,12,3)
th = seq(0,2*pi,length.out=120)
lines(cos(th),sin(th))
th12 = seq(0,2*pi,length.out=25)
for(t in th12){
  lines(c(0,cos(t)),c(0,sin(t)),lty=3,col="grey")
}
thsp = c(0,pi/6,pi/4,pi/3,pi/2,2*pi/3,3*pi/4,5*pi/6,pi,
         7*pi/6,5*pi/4,4*pi/3,3*pi/2,5*pi/3,7*pi/4,11*pi/6,2*pi)

for(i in 1:length(thsp)){
  t = thsp[i]
  lines(c(0,cos(t)),c(0,sin(t)),col="grey")
  points(cos(t),sin(t),pch=20,col="grey")
  text(1.2*cos(t),1.2*sin(t),TeX(paste0("$\\left(",xs[i],",",ys[i],"\\right)$",collapse="")),cex=0.8,col="grey")
}

i = wi
t = thsp[i]
lines(c(0,cos(t)),c(0,sin(t)),col="red")
points(cos(t),sin(t),pch=20,col="red")
text(1.2*cos(t),1.2*sin(t),TeX(paste0("$\\left(",xs[i],",",ys[i],"\\right)$",collapse="")),cex=0.8,col="black")

ttt = seq(0,thsp[wi],length.out=100)
lines(0.3*cos(ttt),0.3*sin(ttt),col="blue",lwd=2)
text(0.4*cos(thsp[wi]/2),0.4*sin(thsp[wi]/2),TeX(paste0("$",ts[wi],"$")),cex=1,col="blue")
arrows(0.3*cos(ttt[99]),0.3*sin(ttt[99]),
       0.3*cos(ttt[100]),0.3*sin(ttt[100]),lwd=2,col="blue")
```
\

$$\cos\left(`r ts[wi]`\right) = `r xs[wi]`$$
$$\sin\left(`r ts[wi]`\right) = `r ys[wi]`$$

So,

$$`r stx` = `r ans`$$



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: unit_circle_intro