```{r,echo=F}
while(T){
  xs = runif(3,-2,2)
  ys = runif(3,-2,2)
  r = runif(1,5,8)
  t = runif(1,0,2*pi)
  xs = round(r*cos(t)+xs,2)
  ys = round(r*sin(t)+ys,2)
  xc = c(xs,xs[1])
  yc = c(ys,ys[1])
  dc = sqrt(diff(xc)^2+diff(yc)^2)
  a = dc[1]
  b = dc[2]
  c = dc[3]
  t1 = acos((a^2+b^2-c^2)/2/a/b)
  t2 = acos((a^2-b^2+c^2)/2/a/c)
  t3 = acos((-a^2+b^2+c^2)/2/c/b)
  th = round(runif(1,pi/2,3*pi/2)*sample(c(-1,1),1),2)
  cwccw = c("clockwise","counterclockwise")[round((sign(th)+1)/2)+1]
  wp = sample(1:3,1)
  wc = sample(1:2,1)
  X1 = xs[wp]
  Y1 = ys[wp]
  radius = sqrt(X1^2+Y1^2)
  theta = atan2(Y1,X1)
  X2 = radius*cos(theta+th)
  Y2 = radius*sin(theta+th)
  if(min(c(t1,t2,t3))>pi/12 && max(c(t1,t2,t3))<3*pi/2 && min(dc)>1 && abs(X1)>0.02 && abs(Y1)>0.02 && abs(X2)>0.02 && abs(Y2)>0.02){break}
}


anpo = c(X2,Y2)
sol = anpo[wc]
qor = c("A","B","C")[wp]
qpo = c("A'","B'","C'")[wp]
qco = c("x","y")[wc]
```

Question
========

A red triangle has coordinates $A(`r xs[1]`, `r ys[1]`)$, $B(`r xs[2]`, `r ys[2]`)$, and $C(`r xs[3]`, `r ys[3]`)$. The triangle is rotated `r abs(th)` radians `r cwccw` around the origin to produce a blue triangle $A'B'C'$.

```{r,echo=F,fig.dim=c(8,8)}
par(pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="y")
for(i in seq(-10,10,1)){
  abline(h=i,col="grey",lty=2)
  abline(v=i,col="grey",lty=2)
}
arrows(-10.5,0,10.5,0,length=0.1,angle=10,code=3,col=rgb(0.3,0.3,0.3))
arrows(0,-10.5,0,10.5,length=0.1,angle=10,code=3,col=rgb(0.3,0.3,0.3))
rs = sqrt(xs^2+ys^2)
ths = atan2(ys,xs)
ttt = min(c(floor(abs(th)/max(abs(diff(c(ths,ths[1]))))),8))
n = max(c(ttt,4)) #round(abs(th*1.5)+1)
for(i in seq(0,th,length.out=n)[2:(n-1)]){
  x2s = rs*cos(ths+i)
  y2s = rs*sin(ths+i)
  polygon(x2s,y2s,col=rgb(0.2,0.2,0.2,0.2),border=rgb(0.2,0.2,0.2,0.5))
}

labtri = function(xs,ys,col,lets=c("A","B","C")){
  for(i in 1:3){
    xa = xs[i]
    xb = xs[c(1,2,3)[-i][1]]
    xc = xs[c(1,2,3)[-i][2]]
    ya = ys[i]
    yb = ys[c(1,2,3)[-i][1]]
    yc = ys[c(1,2,3)[-i][2]]
    t1 = atan2((yb-ya),(xb-xa))
    t2 = atan2((yc-ya),(xc-xa))
    tave = (t1+t2)/2
    if(abs(t2-t1)>pi){adder=pi}else{adder=0}
    let = lets[i]
    text(xa+0.5*cos(tave+pi+adder),ya+0.5*sin(tave+pi+adder),let,col=col)
  }
}

polygon(xs,ys,col=rgb(1,0.2,0.2,0.5))
points(xs,ys,col=rgb(1,0.2,0.2,0.5))
labtri(xs,ys,"red")

x2s = rs*cos(ths+th)
y2s = rs*sin(ths+th)
polygon(x2s,y2s,col=rgb(0.2,0.2,1,0.5))
points(x2s,y2s,col=rgb(0.2,0.2,1,0.5))
labtri(x2s,y2s,"blue",lets=c("A'","B'","C'"))
```
\

Find the $`r qco`$ coordinate of point `r qpo`. The tolerance is $\pm0.01$.


Solution
========

Determine the [polar coordinates](https://en.wikipedia.org/wiki/Polar_coordinate_system) of the original point $`r qor`(`r xs[wp]`, `r ys[wp]`)$.


$$r_{`r qor`} = \sqrt{(`r X1`)^2+(`r Y1`)^2}$$

$$r_{`r qor`} = `r radius`$$

```{r,echo=F}
qd = ((atan2(ys[wp],xs[wp])+2*pi)%%(2*pi))%/%(pi/2)+1
quad = c("I","II","III","IV")[qd]

if(qd==2 || qd==3){
  xp = "+\\pi"
  thclc = atan(ys[wp]/xs[wp])+pi
} else {
  xp = ""
  thclc = atan(ys[wp]/xs[wp])
}

excalct2 = gsub("+-","-",paste0("\\theta_{",qor,"}+",th),fixed=T)
```


Point $`r qor`$ is in [quadrant](https://en.wikipedia.org/wiki/Quadrant_(plane_geometry)) $\mathrm{`r quad`}$. In quadrant $\mathrm{I}$ or $\mathrm{IV}$, the arctan function will provide a correct angle. For quadrant $\mathrm{II}$ or $\mathrm{III}$, add $\pi$ to get a correct angle.

$$\theta_{`r qor`} = \arctan\left(\frac{`r ys[wp]`}{`r xs[wp]`}\right)`r xp`$$

$$\theta_{`r qor`} = `r thclc`$$

The new point, $`r qpo`$, will have the same distance from the origin, but its angle will be changed by `r c("subtracting","adding")[round((sign(th)+1)/2+1)]` `r abs(th)` radians.

$$r_{`r qpo`} = `r radius`$$

$$\theta_{`r qpo`} ~=~ `r excalct2` ~=~ `r thclc+th`$$

Calculate the Cartesian (rectangular) coordinates of point `r qpo`.

$$x_{`r qpo`} ~=~ `r radius` \cdot \cos(`r thclc+th`) ~=~ `r X2`$$
$$y_{`r qpo`} ~=~ `r radius` \cdot \sin(`r thclc+th`) ~=~ `r Y2`$$

The answer, rounded to the nearest hundredth, is `r round(sol,2)`.

### Simpler method

There is a [simpler formula](https://en.wikipedia.org/wiki/Rotation_(mathematics)#Two_dimensions). However, we do not yet have [the background to prove it](https://en.wikipedia.org/wiki/List_of_trigonometric_identities#Angle_sum_and_difference_identities).


Meta-information
============
extype: num
exsolution: `r sol`
exname: rotate_point
extol: 0.01