---
header-includes:
   - \usepackage{array}
output: html_document
geometry: margin=1in
urlcolor: blue
---

```{r,echo=F}
dim = 3.9
```

Name: \hrule

# PCW_1015: Parent Transformations and Feature Locations

1. Make an accurate graph, and describe locations of the features (using interval notation, line equations, and Cartesian coordinates).

$$y~=~2\cdot \sqrt{5-x}-4$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
mkgrid = function(){
    par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
    lim = 10
    plot(0,0,"n",xlim=c(-lim*1.15,lim*1.15),ylim=c(-lim*1.2,lim*1.2),axes=F,ann=F)
    for(i in -lim:lim){
        lines(c(-lim,lim),c(i,i),col="grey",lwd=0.3)
        lines(c(i,i),c(-lim,lim),col="grey",lwd=0.3)
    }
    for(i in seq(-lim,lim,5)){
        lines(c(-lim,lim),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-lim,lim),col="darkgrey",lwd=0.8)
    }
    arrows(-lim*1.1,0,lim*1.1,0,0.1,15,3,lwd=1.5)
    arrows(0,-lim*1.1,0,lim*1.1,0.1,15,3,lwd=1.5)
    text(5,-0.5,"5",col="darkgrey",cex=0.6)
    text(10,-0.5,"10",col="darkgrey",cex=0.6)
    text(-5,-0.5,"-5",col="darkgrey",cex=0.6)
    text(-10,-0.5,"-10",col="darkgrey",cex=0.6)
    for(i in c(-10,-5,5,10)){
        polygon(c(i-0.4,i-0.4,i+0.4,i+0.4),c(-0.1,-0.9,-0.9,-0.1),col="white",border = NA)
        text(i,-0.5,i,col="black",cex=0.6)
        polygon(c(-0.1,-0.95,-0.95,-0.1),c(i-0.4,i-0.4,i+0.4,i+0.4),col="white",border = NA)
        text(-0.5,i,i,col="black",cex=0.6)
    }
}
mkgrid()
```

```{r,echo=F,results='asis'}
mktab = function(){
    cat("\\begin{tabular}{|m{2in}|m{4in}|}\\hline
Feature & Where \\\\ \\hline \\hline
Domain ($x$ interval) &  \\\\ [1.7em]  \\hline
Range ($y$ interval) &  \\\\ [1.7em]  \\hline
Positive ($x$ interval) &  \\\\  [1.7em]  \\hline
Negative ($x$ interval) &   \\\\ [1.7em]  \\hline
Increasing ($x$ interval) & \\\\ [1.7em]  \\hline
Decreasing ($x$ interval) &  \\\\ [1.7em]  \\hline
Asymptote(s) (line equations)&  \\\\ [1.7em]  \\hline
Intercept(s) (coordinates)&  \\\\ [1.7em]  \\hline
\\end{tabular}")
}
mktab()
```

\newpage

2. Make an accurate graph, and describe locations of the features (using interval notation, line equations, and Cartesian coordinates).

$$y~=~- \sqrt{x+4}+1$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
mkgrid()
```

```{r,echo=F,results='asis'}
mktab()
```

\newpage

3. Make an accurate graph, and describe locations of the features (using interval notation, line equations, and Cartesian coordinates).

$$y~=~- \left(\frac{x}{3}+1\right)^2+4$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
mkgrid()
```

```{r,echo=F,results='asis'}
mktab()
```

\newpage

4. Make an accurate graph, and describe locations of the features (using interval notation, line equations, and Cartesian coordinates).

$$y~=~3\cdot 2^{-x}-6$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
mkgrid()
```

```{r,echo=F,results='asis'}
mktab()
```

\newpage

5. Make an accurate graph, and describe locations of the features (using interval notation, line equations, and Cartesian coordinates).

$$y~=~\frac{(x+4)^3}{8}-1$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
mkgrid()
```

```{r,echo=F,results='asis'}
mktab()
```

\newpage

6. Make an accurate graph, and describe locations of the features (using interval notation, line equations, and Cartesian coordinates).

$$y~=~\frac{1}{3-x}-1$$

\vfill

```{r,echo=F,fig.dim=c(dim,dim)}
mkgrid()
```

```{r,echo=F,results='asis'}
mktab()
```






