```{r,echo=F}
while(T){
  xsol = sample(-7:7,3)
  a = sample(c(-1,1),1)
  r = xsol[1]
  s = xsol[2]
  xint = sample(-4:4,1)
  yint = xint*sample(c(-1,1),1)
  rand = sample(c(-1,1),1)
  linex = paste0(rand*sign(xint),"x+",rand*sign(yint),"y=",rand*abs(xint))
  linex = gsub("1x","x",linex)
  linex = gsub("1y","y",linex)
  linex = gsub("+-","-",linex,fixed=T)
  m = round(-yint/xint)
  b = yint
  xv = (r+s+m)/2
  yv1 = a*(xv-r)*(xv-s)+xv*m+b
  yi1 = r*m+b
  yi2 = s*m+b
  x1 = r
  y1 = r*m+b
  y2 = s
  x2 = s*m+b
  x3 = (r+s+m)/2
  y3 = a*(x3-r)*(x3-s)+x3*m+b
  x4 = xsol[3]
  y4 = x4*m+b
  p1 = paste0("(",x1,", ",y1,")",collapse="")
  p2 = paste0("(",x2,", ",y2,")",collapse="")
  p3 = paste0("(",x3,", ",y3,")",collapse="")
  p4 = paste0("(",x4,", ",y4,")",collapse="")
  pbad = paste0("(",y2,", ",x2,")",collapse="")
  ps = sample(c(p1,p2,p3,p4))
  sol = paste0(1*(ps==p1),collapse="")
  if(!is.nan(yv1) && y2!=x2 && x3!=x1 && abs(yv1)<8 && abs(yi1)<8 && abs(yi2)<8 && sign(a)==sign(-yv1) && y3!=0 && y1!=0 && x3%%1==0 && abs(diff(c(x4,x3)))<5 && abs(diff(c(x4,x3)))>0 && length(unique(ps))==4 && sum(ps==pbad)==0){break}
}

```

Question
========

The graph of a quadratic function is shown below.

```{r,echo=F}
par(mar=c(3,3,0,0),pty="s")
x = seq(-10,10,0.1)
plot(x,a*(x-xsol[1])*(x-xsol[2])+m*x+b,xlim=c(-10,10),ylim=c(-10,10),type="l",lwd=2,col="blue",xlab="x",ylab="y")
for(i in 1:10){
  if(i%%5==0){
    abline(h=i,lty=2)
    abline(h=-i,lty=2)
    abline(v=i,lty=2)
    abline(v=-i,lty=2)
  } else {
    abline(h=i,lty=3)
    abline(h=-i,lty=3)
    abline(v=i,lty=3)
    abline(v=-i,lty=3)
  }
  
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,a*(x-xsol[1])*(x-xsol[2])+m*x+b,lwd=3,col="blue")
```
\

When the graph of $`r linex`$ is drawn on the same axes, one solution to this system is

Answerlist
--------

* `r ps[1]`
* `r ps[2]`
* `r ps[3]`
* `r ps[4]`

Solution
========

When a linear equation is given in standard form, I typically graph by finding the intercepts: $(`r xint`, 0)$ and $(0, `r yint`)$. Notice,

```{r, echo=F}
lex1 = gsub("x",paste0("(",xint,")",collapse=""),linex,fixed=T)
lex1 = gsub("y",paste0("(0)",collapse=""),lex1,fixed=T)
lex2 = gsub("y",paste0("(",yint,")",collapse=""),linex,fixed=T)
lex2 = gsub("x",paste0("(0)",collapse=""),lex2,fixed=T)
```

$$`r lex1`$$

$$`r lex2`$$

To connect the two points on the line, we recognize it has a slope of `r m`. We draw the line, and look at the two points of intersection. The correct answer is `r p1`. The other intersection point is (`r y2`, `r x2`), but that was not an option.

```{r,echo=F}
par(mar=c(3,3,0,0),pty="s")
x = seq(-10,10,0.1)
plot(x,a*(x-xsol[1])*(x-xsol[2])+m*x+b,xlim=c(-10,10),ylim=c(-10,10),type="l",lwd=2,col="blue",xlab="x",ylab="y")
for(i in 1:10){
  if(i%%5==0){
    abline(h=i,lty=2)
    abline(h=-i,lty=2)
    abline(v=i,lty=2)
    abline(v=-i,lty=2)
  } else {
    abline(h=i,lty=3)
    abline(h=-i,lty=3)
    abline(v=i,lty=3)
    abline(v=-i,lty=3)
  }
  
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,a*(x-xsol[1])*(x-xsol[2])+m*x+b,lwd=3,col="blue")
lines(x,m*x+b,lwd=3,col="red")
```
\



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: parabola_line_intersect