```{r,echo=FALSE}
options(scipen=999)
maxopt = 10
gcd2 <- function(a, b) {
    if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

pfix = function(c,d){
    d = d[c!=0]
    c = c[c!=0]
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

while(T){
    PQRS = sample(2:9,4,T)
    P = PQRS[1]
    Q = PQRS[2]*sample(c(-1,1),1)
    R = PQRS[3]
    S = PQRS[4]*sample(c(-1,1),1)
    pr = prod(c(P,Q,R,S))
    su = P*S+Q*R
    a = P*R
    b = su
    c = Q*S
    addend1 = P*S
    addend2 = Q*R
    ads = c(addend1,addend2)
    ch1 = pfix(c(P,Q),1:0)
    ch2 = pfix(c(R,S),1:0)
    if(abs(pr)<200 && min(abs(ads))<11 && abs(gcd(P,Q))==1 && abs(gcd(R,S))==1 && ch1!=ch2){break}
}
ch1 = pfix(c(P,Q),1:0)
ch2 = pfix(c(R,S),1:0)

chs = c(ch1,ch2)

while(length(chs)<20){
    PQRS2 = sample(2:9,4,T)
    P2 = PQRS2[1]
    Q2 = PQRS2[2]*sample(c(-1,1),1)
    R2 = PQRS2[3]
    S2 = PQRS2[4]*sample(c(-1,1),1)
    pr2 = prod(c(P2,Q2,R2,S2))
    su2 = P2*S2+Q2*R2
    a2 = P2*R2
    b2 = su2
    c2 = Q2*S2
    addend12 = P2*S2
    addend22 = Q2*R2
    ads2 = c(addend12,addend22)
    if(abs(pr2)<200 && min(abs(ads2))<11 && abs(gcd(P2,Q2))==1 && abs(gcd(R2,S2))==1 &&
       sum(c(P,Q,R,S)==c(P2,Q2,R2,S2))){
        chs = unique(c(chs,pfix(c(P2,Q2),1:0),pfix(c(R2,S2),1:0)))
    }
}

ex1 = pfix(c(a,addend1,addend2,c),c(2,1,1,0))

ach = sort(chs)
al = paste0("* $",ach,"$",collapse="\n")

sol1 = ach==ch1
sol2 = ach==ch2

sol = sol1+sol2

sol = paste0(1*(sol!=0),collapse="")


```


Question
========

Please review [this article](https://www.khanacademy.org/math/algebra/x2f8bb11595b61c86:quadratics-multiplying-factoring/x2f8bb11595b61c86:factor-quadratics-grouping/a/factoring-by-grouping) on factoring by grouping.

Consider the expression:

$$`r ex1`$$

Notice that the product of the quadratic coefficient and the constant is `r a*c`.

$$(`r a`)(`r c`)=`r a*c`$$ 

Also the product of both linear coefficients is `r a*c`. $$(`r addend1`)(`r addend2`)=`r a*c`$$

Since both of those products match, we are set up for factoring by grouping. 

When the expression is factored into factored form, what are the two factors?


Answerlist
--------

`r al`

Solution
========

$$`r ex1`$$

The first two terms are $`r a`x^2$ and $`r addend1`x$. The greatest common factor of those two terms is $`r pfix(P,1)`$. Factor out $`r pfix(P,1)`$ from the first two terms.

```{r,echo=F}
ex2 = paste0(pfix(P,1),"(",pfix(c(R,S),1:0),")+",pfix(c(Q*R,Q*S),1:0),collapse="")
ex2 = gsub("+-","-",ex2,fixed=T)
ex2 = gsub("+{-","-{",ex2,fixed=T)
```

$$`r ex2`$$

The last two terms are $`r addend2`x$ and $`r c`$. The greatest common factor of those two terms is $`r Q`$. Notice, I am picking the sign (positive or negative) so that both expressions in parentheses will match. Factor out $`r Q`$ from the last two terms.

```{r,echo=F}
ex3 = paste0(pfix(P,1),"(",pfix(c(R,S),1:0),")+",Q,"(",pfix(c(R,S),1:0),")",collapse="")
ex3 = gsub("+{-","-{",ex3,fixed=T)
ex3 = gsub("+-","-",ex3,fixed=T)
```


$$`r ex3`$$

```{r,echo=F}
term1 = paste0(pfix(P,1),"(",pfix(c(R,S),1:0),")",collapse="")
term2 = paste0(Q,"(",pfix(c(R,S),1:0),")",collapse="")
```

We now have two terms: $`r term1`$ and $`r term2`$. Notice, both terms share a factor of $`r pfix(c(R,S),1:0)`$, so we can now get the expression in fully factored form. (By using distributive property... backwards...)

$$(`r pfix(c(P,Q),1:0)`)(`r pfix(c(R,S),1:0)`)$$

If that was confusing, I recommend checking out [the article](https://www.khanacademy.org/math/algebra/x2f8bb11595b61c86:quadratics-multiplying-factoring/x2f8bb11595b61c86:factor-quadratics-grouping/a/factoring-by-grouping).


Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: factor_by_grouping