```{r data generation, echo = FALSE, results = "hide"}
x = -4:4
f = sample(x)
nf = -f
fn = f[length(x):1]
nfn = -fn

# fi = numeric()
# for(i in x){
#   fi = c(fi,x[which(f==i)])
# }

ach = x

sols = character()

anf = paste0("##ANSWER",seq(1,length(x)*3-2,3),"##")
afn = paste0("##ANSWER",seq(2,length(x)*3-1,3),"##")
anfn = paste0("##ANSWER",seq(3,length(x)*3,3),"##")

for(i in 1:length(x)){
    sols = c(sols,paste0(1*(nf[i]==ach),collapse=""))
    sols = c(sols,paste0(1*(fn[i]==ach),collapse=""))
    sols = c(sols,paste0(1*(nfn[i]==ach),collapse=""))
}

al = paste0("* ",ach,collapse="\n")
al2 = paste0(rep(al,length(x)*3),collapse="\n")

```

Question
========


A function, $f$, maps a domain of all integers from $`r min(x)`$ to $`r max(x)`$ onto a range of all integers from $`r min(x)`$ to $`r max(x)`$, as shown in the table below. Finish the table below to complete the columns of $-f(x)$ and $f(-x)$ and $-f(-x)$.

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(x,f,anf,afn,anfn)
colnames(df) = c("$x$","$f(x)$","$-f(x)$","$f(-x)$","$-f(-x)$")
kable(df) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```



Answerlist
--------

`r al2`

Solution
========

See [the slides](https://chadworley.github.io/algtwo2026/daily_materials/day005/slides_09_02_function_reflections.html).

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(x,f,nf,fn,nfn)
colnames(df) = c("$x$","$f(x)$","$-f(x)$","$f(-x)$","$-f(-x)$")
kable(df) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",length(sols)),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: inverse_table