---
output: html_document
---

```{r,echo=F}
dd = 3
```

# Vertical reflection: $y=-f(x)$

* Vertical reflection (reflection over the $x$ axis)
* Let corresponding points $(x_1,y_1)$ and $(x_2,y_2)$ exist such that $y_1=f(x_1)$ if and only if $y_2=-f(x_2)$.
    * Then we know $x_2=x_1$ and $y_2=-y_1$. (Negate the $y$ values.)
    * In other words: $(a,b) \to (a,-b)$ for any point $(a,b)$ on curve $y=f(x)$.
    * For example, $(3,1)$ is on $y=f(x)$ if and only if $(3,-1)$ is on $y=-f(x)$

```{r,echo=F,fig.dim=c(2*dd,dd)}
library(latex2exp)
x = seq(-3,5,0.01)
y = sqrt(x+3)-1
yp = -1:5
xp = (yp+1)^2-3
par(pty="s",mar=c(4,4,0,0),mfrow=c(1,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),xlab="x",ylab="y")
abline(h=0)
abline(v=0)
lines(x,y,col="blue")
lines(x,-y,col="red")
points(xp,yp,pch=19,cex=0.7,col="blue")
points(xp,-yp,pch=19,cex=0.7,col="red")
plot(0,0,"n",axes=F,ann=F)
legend("topleft",c(TeX("$y=f(x)$"),TeX("$y=-f(x)$")),col=c("blue","red"),lwd=c(1,1))
```

# Horizontal reflection: $y=f(-x)$

* Horizontal reflection (reflection over the $y$ axis)
* Let corresponding points $(x_1,y_1)$ and $(x_2,y_2)$ exist such that $y_1=f(x_1)$ if and only if $y_2=f(-x_2)$.
    * Then we know $x_2=-x_1$ and $y_2=y_1$. (Negate the $x$ values.)
    * In other words: $(a,b) \to (-a,b)$ for any point $(a,b)$ on curve $y=f(x)$.
    * For example, $(3,1)$ is on $y=f(x)$ if and only if $(-3,1)$ is on $y=f(-x)$

```{r,echo=F,fig.dim=c(2*dd,dd)}
library(latex2exp)
x = seq(-3,5,0.01)
y = sqrt(x+3)-1
yp = -1:5
xp = (yp+1)^2-3
par(pty="s",mar=c(4,4,0,0),mfrow=c(1,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),xlab="x",ylab="y")
abline(h=0)
abline(v=0)
lines(x,y,col="blue")
lines(-x,y,col="red")
points(xp,yp,pch=19,cex=0.7,col="blue")
points(-xp,yp,pch=19,cex=0.7,col="red")
plot(0,0,"n",axes=F,ann=F)
legend("topleft",c(TeX("$y=f(x)$"),TeX("$y=f(-x)$")),col=c("blue","red"),lwd=c(1,1))
```

# Inverse function: $y=f^{-1}(x)$

* Reflection over the $y=x$ line.
* Let $f$ represent a one-to-one function.
* Let corresponding points $(x_1,y_1)$ and $(x_2,y_2)$ exist such that $y_1=f(x_1)$ if and only if $y_2=f^{-1}(x_2)$.
    * Then we know $x_2=y_1$ and $y_2=x_1$. (Swap the $x$ and $y$.)
    * In other words: $(a,b) \to (b,a)$ for any point $(a,b)$ on curve $y=f(x)$.
    * For example, $(3,1)$ is on $y=f(x)$ if and only if $(1,3)$ is on $y=f^{-1}(x)$

```{r,echo=F,fig.dim=c(2*dd,dd)}
library(latex2exp)
x = seq(-3,5,0.01)
y = sqrt(x+3)-1
yp = -1:5
xp = (yp+1)^2-3
par(pty="s",mar=c(4,4,0,0),mfrow=c(1,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),xlab="x",ylab="y")
abline(h=0)
abline(v=0)
lines(x,y,col="blue")
lines(y,x,col="red")
points(xp,yp,pch=19,cex=0.7,col="blue")
points(yp,xp,pch=19,cex=0.7,col="red")
plot(0,0,"n",axes=F,ann=F)
legend("topleft",c(TeX("$y=f(x)$"),TeX("$y=f^{-1}(x)$")),col=c("blue","red"),lwd=c(1,1))
```


# Double reflection: $y=-f(-x)$

* Double reflection over $x$ axis and then $y$ axis (or 180° rotation around origin).
* Let corresponding points $(x_1,y_1)$ and $(x_2,y_2)$ exist such that $y_1=f(x_1)$ if and only if $y_2=-f(-x_2)$.
    * Then we know $x_2=-x_1$ and $y_2=-y_1$.  (Negate the $x$ and $y$ values.)
    * In other words: $(a,b) \to (-a,-b)$ for any point $(a,b)$ on curve $y=f(x)$.
    * For example, $(3,1)$ is on $y=f(x)$ if and only if $(-3,-1)$ is on $y=-f(-x)$

```{r,echo=F,fig.dim=c(2*dd,dd)}
library(latex2exp)
x = seq(-3,5,0.01)
y = sqrt(x+3)-1
yp = -1:5
xp = (yp+1)^2-3
par(pty="s",mar=c(4,4,0,0),mfrow=c(1,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),xlab="x",ylab="y")
abline(h=0)
abline(v=0)
lines(x,y,col="blue")
lines(-x,-y,col="red")
points(xp,yp,pch=19,cex=0.7,col="blue")
points(-xp,-yp,pch=19,cex=0.7,col="red")
plot(0,0,"n",axes=F,ann=F)
legend("topleft",c(TeX("$y=f(x)$"),TeX("$y=-f(-x)$")),col=c("blue","red"),lwd=c(1,1))
```

