---
title: "Function Reflections"
author: "Mr. Worley"
date: "2025 Sep 4"
# output: html_document
output:
    slidy_presentation:
        incremental: true
---

# Puzzle 1

Let function $f$ be defined by the table below.

```{r, echo = FALSE, results = "hide"}
set.seed(123)
x = -3:3
n = length(x)
f = sample(10:(10+n-1),n)*sample(c(-1,1),n,T)
a = sample(1:3,1)*sample(c(-1,1),1)
fn = rev(f)
fna = fn[x==a]
```

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(x,f)
colnames(df) = c("$x$","$f(x)$")
kable_styling(kable(df),bootstrap_options = "bordered",full_width = F)
```

Let $a=`r a`$. Evaluate $f(-a)$.

* Solution
* Since $a=`r a`$, we know $-a=`r -a`$. So we evaluate $f(`r -a`)$.
$$f(`r -a`) = `r fna`$$
Thus, $f(-(`r a`))=`r fna`$ and $$f(-a)=`r fna`$$

# Puzzle 2

Let function $f$ be defined by the table below.

```{r, echo = FALSE, results = "hide"}
x = -3:3
n = length(x)
f = sample(10:(10+n-1),n)*sample(c(-1,1),n,T)
a = sample(1:3,1)*sample(c(-1,1),1)
fn = rev(f)
fna = fn[x==a]
nf = -f
nfa = nf[x==a]
nfn = -fn
nfna = nfn[x==a]
```

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(x,f)
colnames(df) = c("$x$","$f(x)$")
kable_styling(kable(df),bootstrap_options = "bordered",full_width = F)
```

Let $a=`r a`$. Evaluate $-f(a)$.

* Solution
* First, evaluate $f(`r a`)$.
$$f(`r a`)=`r f[x==a]`$$
* So, we can just multiply both sides of the equation by $-1$.
$$-f(`r a`) = `r nfa`$$
* Thus, $$-f(a)=`r nfa`$$
(because $a=`r a`$)

# Puzzle 3

Let function $f$ be defined by the table below.

```{r, echo = FALSE, results = "hide"}
x = -3:3
n = length(x)
f = sample(10:(10+n-1),n)*sample(c(-1,1),n,T)
a = sample(1:3,1)*sample(c(-1,1),1)
fn = rev(f)
fna = fn[x==a]
nf = -f
nfa = nf[x==a]
nfn = -fn
nfna = nfn[x==a]
```

```{r,echo=F,warning=F}
library(kableExtra)
df = data.frame(x,f)
colnames(df) = c("$x$","$f(x)$")
kable_styling(kable(df),bootstrap_options = "bordered",full_width = F)
```

Let $a=`r a`$. Evaluate $-f(-a)$.

* Solution
* Since $a=`r a`$, we know $-a=`r -a`$. So we evaluate $-f(`r -a`)$. In order to do this, first evaluate $f(`r -a`)$. 
$$f(`r -a`)=`r fna`$$
* Multiply both sides by $-1$.
$$-f(`r -a`)=`r -fna`$$
* And thus, if $a=`r a`$, then we know $-f(-a)=`r nfna`$.

# Classwork break 1

Please complete [OCW_eval_func_w_negs](https://bart.instructure.com/courses/2110/quizzes/3150)

# Generate $f(-x)$ from $f(x)$ table

Let's define a function with a table.

```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
df1 = data.frame(x,f)
colnames(df1) = c("$x$","$f(x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```

Our first goal is to make another column for $f(-x)$.

* We must distinguish between two things that were previously equivalent:
    1. The value of $x$
    2. The input into the function (the argument)
* For example, if $x=2$, then the argument of $f(-x)$ is $-2$, because $-x=-2$.
* In our example, we know $f(-2)=-1$.
```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
fn = c(" "," "," "," "," ","-1"," ")
df1 = data.frame(x,f,fn)
colnames(df1) = c("$x$","$f(x)$","$f(-x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```
* Can you fill the rest of the table?
* Basically, the $f(-x)$ column is just the reverse of the $f(x)$ column. 
\
```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
fn = f[length(x):1]
df1 = data.frame(x,f,fn)
colnames(df1) = c("$x$","$f(x)$","$f(-x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```
* Can you predict what geometric transformation relates the graphs of $y=f(x)$ and $y=f(-x)$?
* The graphs (connected with line segments for visual clarity) are reflections of each other over the $y$ axis.
* 
```{r,echo=F,fig.dim=c(8,4)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,f,col="blue",lwd=4)
lines(x,fn,col="red",lwd=4)

plot(0,0,"n",axes=F,ann=F)
legend("left",
       c(TeX("$y=f(x)$"),TeX("$y=f(-x)$")),
       col=c("blue","red"),
       lwd=c(4,4))
```



# Generate $-f(x)$ from $f(x)$ table

Let's reuse the example function:

```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
df1 = data.frame(x,f)
colnames(df1) = c("$x$","$f(x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```

Our goal is to make another column for $-f(x)$. 

* Notice the value of $-f(x)$ is simply to opposite of the value of $f(x)$.
* For example, if $f(x)=3$ then $-f(x)=-3$. In our example, this means that since $f(-1)=3$ we know $-f(-1)=-3$.
```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
nf = c(" "," ","-3"," "," "," "," ")
df1 = data.frame(x,f,nf)
colnames(df1) = c("$x$","$f(x)$","$-f(x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```
* Can you predict the rest of the table?
* To produce this new column, we just use the negatives of the values in the $f(x)$ column.
```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
nf = -f
df1 = data.frame(x,f,nf)
colnames(df1) = c("$x$","$f(x)$","$-f(x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```
* Can you predict the geometric transformation that relates the graphs of $y=f(x)$ and $y=-f(x)$?
* The graphs are mirror reflections across the $x$ axis. I've connected the points for visual clarity (even though the function was only defined for integers).
* 
```{r,echo=F,fig.dim=c(8,4)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,f,col="blue",lwd=3)
lines(x,nf,col="purple",lwd=4)

plot(0,0,"n",axes=F,ann=F)
legend("left",
       c(TeX("$y=f(x)$"),TeX("$y=-f(x)$")),
       col=c("blue","purple"),
       lwd=c(3,4))
```


# Generate $-f(-x)$ from $f(x)$ table


Again, let's reuse the example function:

```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
df1 = data.frame(x,f)
colnames(df1) = c("$x$","$f(x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```

Our goal is to make another column for $-f(-x)$. Based on the two previous examples, you might be able to predict how to fill the $-f(-x)$ column.

* Pick a value of $x$. Let's start with $x=-3$. Our goal is to evaluate $-f(-(-3))$.
* Simplify the expression inside the argument. We know $-(-3)=3$.
* So, we need to evaluate $-f(3)$.
* Okay, we can find $f(3)$ and then negate it.
* Thus, since $f(3)=1$, we know that $-f(-(-3))=-1$.
```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
nfn = c("-1"," "," "," "," "," "," ")
df1 = data.frame(x,f,nfn)
colnames(df1) = c("$x$","$f(x)$","$-f(-x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```
* Can you predict how to fill the rest of the table?
* Basically, you can reverse the order of the second column and then negate each element.
```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
nfn = -fn
df1 = data.frame(x,f,nfn)
colnames(df1) = c("$x$","$f(x)$","$-f(-x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```
* Can you predict the geometric transformation that relates the graphs of $y=f(x)$ and $y=-f(-x)$?
* The two graphs are related by a 180° rotation around the origin. 
* This is equivalent to combining two reflections, one over the $y$ axis and one over the $x$ axis (in either order).
* 
```{r,echo=F,fig.dim=c(8,4)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,f,col="blue",lwd=3)
lines(x,nfn,col="darkgreen",lwd=4)

plot(0,0,"n",axes=F,ann=F)
legend("left",
       c(TeX("$y=f(x)$"),TeX("$y=-f(-x)$")),
       col=c("blue","darkgreen"),
       lwd=c(3,4))
```

# All of them: $f(x)$ and $-f(x)$ and $f(-x)$ and $-f(-x)$

All four in a table:

```{r,echo=F,warning=F}
library(kableExtra)
x = -3:3
f = c(2,-1,3,-3,-2,0,1)
df1 = data.frame(x,f,nf,fn,nfn)
colnames(df1) = c("$x$","$f(x)$","$-f(x)$","$f(-x)$","$-f(-x)$")
kable(df1) %>%
    kable_styling(bootstrap_options = "bordered",full_width = F)
```


All four graphed:

```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s",mfrow=c(2,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,f,col="blue",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=f(x)$"),col="blue",lwd=2)

plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,fn,col="red",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=f(-x)$"),col="red",lwd=2)

plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,nf,col="purple",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=-f(x)$"),col="purple",lwd=2)

plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,nfn,col="darkgreen",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=-f(-x)$"),col="darkgreen",lwd=2)

```


# Summary

* Graphs of $y=f(x)$ and $y=f(-x)$ are reflections over the $y$-axis. (So the corresponding $x$ values are opposites.)
    * For example if point $(3,1)$ is on $y=f(x)$ then point $(-3,1)$ is on $y=f(-x)$.
* Graphs of $y=f(x)$ and $y=-f(x)$ are reflections over the $x$-axis. (So the corresponding $y$ values are opposites.)
    * For example if point $(3,1)$ is on $y=f(x)$ then point $(3,-1)$ is on $y=-f(x)$.
* Graphs of $y=f(x)$ and $y=-f(-x)$ are reflections over both axes. In other words, they are 180° rotations around the origin. (So the corresponding $x$ values are opposites, and the corresponding $y$ values are opposites.)
    * For example if point $(3,1)$ is on $y=f(x)$ then point $(-3,-1)$ is on $y=-f(-x)$.
* 
```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s",mfrow=c(2,2))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,f,col="blue",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=f(x)$"),col="blue",lwd=2)
points(3,1,pch=19,col="blue")

plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,fn,col="red",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=f(-x)$"),col="red",lwd=2)
points(-3,1,pch=19,col="red")

plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,nf,col="purple",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=-f(x)$"),col="purple",lwd=2)
points(3,-1,pch=19,col="purple")

plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,5),axes=F,ann=F)
for(i in seq(-5,5,1)){
    lines(c(i,i),c(-5,5),col="grey")
    lines(c(-5,5),c(i,i),col="grey")
    text(i,0,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
    text(0,i,i,cex=0.8,adj=c(1.2,1.2),col="darkgrey")
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(5.3,0,"x",adj=c(1.2,1.2))
text(0,5.5,"y",adj=c(1.2,1.2))
lines(x,nfn,col="darkgreen",lwd=2)
legend(0,4,xjust = 0.5,yjust = 0.5,TeX("$y=-f(-x)$"),col="darkgreen",lwd=2)
points(-3,-1,pch=19,col="darkgreen")

```





