```{r,echo=F,warning=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  ab = round(runif(2,2,9),1)
  a = ab[1]
  b = ab[2]
  thd = sample(5:30,1)
  thn = sample(2:(thd-1),1)
  g = gcd2(thd,thn)
  thd = thd/g
  thn = thn/g
  C = thn*pi/thd
  c = sqrt(a^2+b^2-2*a*b*cos(C))
  A = acos((c^2+b^2-a^2)/2/c/b)
  B = acos((a^2+c^2-b^2)/2/a/c)
  if(thn>1 && A>pi/12 && A<11*pi/12 && B>pi/12 && B<11*pi/12 && C>pi/12 && C<11*pi/12 && abs(A-pi/2)>pi/12 && abs(B-pi/2)>pi/12 && abs(C-pi/2)>pi/12){break}
}
pC = c(0,0)
pB = c(a,0)
pA = c(cos(C)*b,sin(C)*b)
phi = runif(1,0,2*pi)
ps = matrix(c(pA,pB,pC),nrow=2,byrow=F)
shx = 2/3*mean(c(a,cos(C)*b))
shy = 2/3*mean(c(0,sin(C)*b))
ps = ps-matrix(c(shx,shx,shx,shy,shy,shy),nrow=2,byrow=T)
rotM = matrix(c(cos(phi),
                -sin(phi),
                sin(phi),
                cos(phi)),ncol=2,byrow=T)
p = rotM%*%ps
t1 = phi
t2 = C+phi
bump = max(c(a,b,c))/20
texa = c(a/2,-bump)
texb = c(cos(C)*b/2+bump*cos(C+pi/2),
         sin(C)*b/2+bump*sin(C+pi/2))
texC = c(1.5*bump/C*cos(C/2),1.5*bump/C*sin(C/2))
texx = matrix(c(texa,texb,texC),nrow=2,byrow=F)
texx = texx-matrix(c(shx,shx,shx,shy,shy,shy),nrow=2,byrow=T)
texx = rotM%*%texx
switchem = sample(c(T,F),1)
area = a*b*sin(C)/2
```

Question
========

The area of a triangle equals half the product of base times height.
$$A_{\triangle}=\frac{bh}{2}$$

The diagram below shows how this makes sense by making a rectangle with equivalent area with the same base but half the height of the triangle.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(pty="s",mar=c(0,0,0,0))
plot(c(0,5,2,0),c(0,0,6,0),type="l",xlim=c(-1,6),ylim=c(-0.5,6.5))
for(i in (-2):7){
  abline(h=i,col="darkgrey")
  abline(v=i,col="darkgrey")
}
#polygon(c(0,5,5,0),c(0,0,6,6),col=rgb(0.8,0.8,1,0.5))
lines(c(1,3.5),c(3,3),lty=2,lwd=2)
lines(c(3.5,5,5),c(3,3,0),lty=2,lwd=1)
lines(c(1,0,0),c(3,3,0),lty=2,lwd=1)
polygon(c(0,5,2,0),c(0,0,6,0),col=rgb(1,0.8,0.8,0.5))
lines(c(0,5),c(0,0),lwd=3,col="blue")
text(2.5,-0.3,TeX("$b$"),col="blue",cex=2)
lines(c(2,2.3,2.3),c(0.3,0.3,0),col="red")
lines(c(2,2),c(0,6),lty=2,lwd=3,col="red")
text(2.3,2.7,TeX("$h$"),col="red",cex=2)
polygon(c(5,5,3.5),c(0,3,3),border=F,col=rgb(0,0,0,0.1))
polygon(c(0,0,1),c(0,3,3),border=F,col=rgb(0,0,0,0.1))
text(-0.5,1.5,TeX("$\\frac{h}{2}$"))
r = 1
cx = 3.5
cy = 3
t1 = atan2(2,-1)+atan2(2,1)/2
t2 = atan2(-2,1)+atan2(2,1)/2
n = 100
ts = seq(t1,t2,length.out=n)
lines(cx+r*cos(ts),cy+r*sin(ts),col="purple",lwd=3)
arrows(cx+r*cos(ts[n-1]),cy+r*sin(ts[n-1]),cx+r*cos(ts[n]),cy+r*sin(ts[n]),0.1,20,lwd=4,col="purple")
r = 0.7
cx = 1
cy = 3
t1 = atan2(3,1)-atan2(3,1)/2
t2 = atan2(-3,-1)-atan2(3,1)/2+2*pi
n = 100
ts = seq(t1,t2,length.out=n)
lines(cx+r*cos(ts),cy+r*sin(ts),col="purple",lwd=3)
arrows(cx+r*cos(ts[n-1]),cy+r*sin(ts[n-1]),cx+r*cos(ts[n]),cy+r*sin(ts[n]),0.1,20,lwd=4,col="purple")
```
/


This still works with obtuse triangles.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-1,6),ylim=c(-0.5,6.5))
for(i in (-2):7){
  abline(h=i,col="darkgrey")
  abline(v=i,col="darkgrey")
}
polygon(c(2.5,5,0),c(0,0,6),col=rgb(0.8,0.8,1,0.6))
polygon(c(5,3.75,2.5),c(0,3,3),col=rgb(0,0,0,0.05),border=F)
polygon(c(5,3.75,5),c(0,3,3),col=rgb(0,0,0,0.1),border=F)
lines(c(2.5,2.5,1.25),c(0,3,3),lty=2)
lines(c(5,5,3.75,5),c(0,3,3,0),lty=2)
lines(c(2.5,3.75),c(3,3),lty=2)
lines(c(0,0),c(0,6),lty=2,lwd=3,col="red")
text(0.3,2.7,"h",cex=2,col="red")
lines(c(2.5,5),c(0,0),lwd=3,col="purple")
text(mean(c(2.5,5)),-0.3,"b",col="purple",cex=2)
arrows(2,2.5,4.5,2.5,lwd=2,length=0.1,col="darkgrey")
th = seq(11*pi/12,-pi/12,length.out=100)
r = 0.9
lines(2.5+r*cos(th),3+r*sin(th),lwd=2,col="darkgrey")
arrows(2.5+r*cos(th[99]),3+r*sin(th[99]),
       2.5+r*cos(th[100]),3+r*sin(th[100]),
       lwd=2,length=0.1,col="darkgrey")
lines(c(5,5),c(0,3),lwd=3,col="blue")
text(5.3,1.5,TeX("$\\frac{h}{2}$"),col="blue",cex=1.5)
if(switchem){
  aaa = b
  bbb = a
} else {
  aaa = a
  bbb = b
}
```
\

Based on the formula above, and by using some trigonometry, **find the area** (in cm$^2$) of the triangle below, where $a=`r aaa`$ cm and $b=`r bbb`$ cm and $\gamma=\frac{`r thn`\pi}{`r thd`}$ radians.


```{r,fig.dim=c(5,5),echo=F}
mxmx = ceiling(max(abs(p)))
par(pty="s",mar=c(0,0,0,0))
plot(c(p[1,],texx[1,]),c(p[2,],texx[2,]),type="n",axes=F,ann=F,
     xlim=c(-mxmx,mxmx),ylim=c(-mxmx,mxmx))
for(i in (-mxmx):mxmx){
  abline(h=i,col="grey")
  abline(v=i,col="grey")
}
polygon(p[1,],p[2,],col=rgb(1,0.8,0.8,0.5))
if(switchem){
  text(texx[1,2],texx[2,2],TeX("$a$"))
  text(texx[1,1],texx[2,1],TeX("$b$"))
} else {
  text(texx[1,1],texx[2,1],TeX("$a$"))
  text(texx[1,2],texx[2,2],TeX("$b$"))
}
text(texx[1,3],texx[2,3],TeX("$\\gamma$"))
```
\

The tolerance is $\pm0.1$ cm$^2$.

Solution
========

We are given two lengths of a triangle and the angle measure between those lengths. We can draw a generic diagram for this scenario:

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(pty="s",mar=c(0,0,0,0))
plot(c(0,5,2,0),c(0,0,6,0),type="l",xlim=c(-1,6),ylim=c(-0.5,6.5))
for(i in (-2):7){
  abline(h=i,col="darkgrey")
  abline(v=i,col="darkgrey")
}
polygon(c(0,5,2,0),c(0,0,6,0),col=rgb(1,0.8,0.8,0.5))
lines(c(0,5),c(0,0),lwd=3,col="blue")
text(2.5,-0.3,TeX("$b$"),col="blue",cex=2)
lines(c(2,2.3,2.3),c(0.3,0.3,0),col="red")
lines(c(2,2),c(0,6),lty=2,lwd=3,col="red")
text(2.3,2.7,TeX("$h$"),col="red",cex=2)
lines(c(0,2),c(0,6),col="purple",lwd=3)
text(0.8,3.3,"a",col="purple",cex=2)
r=0.6
tt = atan(3)
text(r*cos(tt/2),r*sin(tt/2),TeX("$\\gamma$"),cex=2)
```
\

We notice that we can write a trigonometric equation:
$$\sin(\gamma) = \frac{h}{a}$$
We can solve for $h$.
$$h = a \sin(\gamma)$$
Substitute for $h$ in the area formula.
$$A_{\triangle} = \frac{ab \sin(\gamma)}{2}$$
That formula will work even if $\gamma$ is obtuse.

$$A_{\triangle} = \frac{`r aaa`\cdot `r bbb` \sin\left(\frac{`r thn`\pi}{`r thd`}\right)}{2}$$


$$A_{\triangle} = `r area` ~\mathrm{cm^2}$$

$$A_{\triangle} \approx `r round(area,1)` ~\mathrm{cm^2}$$


Meta-information
============
extype: num
exsolution: `r area`
exname: area_of_triangle
extol: 0.1