```{r,echo=F,warning=F}
while(T){
  while(T){
    alpha_den = sample(c(11,13,17,19,23,29,31,37,41,43,47,53,59,61,67,71,73,79,83,89,97),1)
    alpha_num = sample(2:(alpha_den%/%2-2),1)
    alpha = alpha_num*pi/alpha_den
    c = round(runif(1,3,9),1)
    h = sin(alpha)*c
    if(c-h>0.4 && alpha>pi/8){break}
  }
  a = round(runif(1,h+0.1,c-0.1),1)
  gamma1 = asin(c*sin(alpha)/a)
  gamma2 = pi-gamma1
  beta1 = pi-alpha-gamma1
  beta2 = pi-alpha-gamma2
  b1 = a*sin(beta1)/sin(alpha)
  b2 = a*sin(beta2)/sin(alpha)
  if(beta2>pi/12){break}
}
hm = 5
ans1 = round(gamma1,2)
ans2 = round(gamma2,2)
wa1 = sample(1:hm,1)
ac1 = ans1+0.05*(1:5-wa1)
al1 = paste0("* ",ac1,collapse="\n")
sol1 = paste0(1*(1:5==wa1),collapse="")
wa2 = hm+1-wa1
ac2 = ans2+0.05*(1:5-wa2)
al2 = paste0("* ",ac2,collapse="\n")
sol2 = paste0(1*(1:5==wa2),collapse="")
```


Question
========

This question is about the [ambiguous case](https://en.wikipedia.org/wiki/Law_of_sines#The_ambiguous_case_of_triangle_solution) encountered when using law of sines to find angles of triangles.

Consider the triangle(s) with $\alpha=\frac{`r alpha_num`\pi}{`r alpha_den`}$ and $a=`r a`$ and $c=`r c`$. Notice there are two possible triangles with these attributes.

```{r,echo=F,fig.dim=c(8,4)}
library(latex2exp)
par(mar=c(1,1,1,1),pty="s",mfrow=c(1,2))
di = ceiling(max(c(h,b1)))
bmp = di/30
plot(0,0,type="n",axes=F,ann=F,xlim=c(0,di),ylim=c(h/2-di/2,h/2+di/2))
for(i in (-di):(2*di)){
  abline(h=i,lwd=1,col="grey")
  abline(v=i,lwd=1,col="grey")
}
lines(c(0,b1,cos(alpha)*c,0),c(0,0,h,0),lwd=2,col="blue")
text(2*bmp/alpha*cos(alpha/2),2*bmp/alpha*sin(alpha/2),TeX("$\\alpha$"))
text(c/2*cos(alpha)+bmp*cos(alpha+pi/2),
     c/2*sin(alpha)+bmp*sin(alpha+pi/2),
     "c")
text(b1+a/2*cos(pi-gamma1)+bmp*cos(pi/2-gamma1),
     a/2*sin(pi-gamma1)+bmp*sin(pi/2-gamma1),TeX("$a$"))
text(b1-3*bmp/gamma1*cos(gamma1/2),
     3*bmp/gamma1*sin(gamma1/2),TeX("$\\gamma_1$"))

plot(0,0,type="n",axes=F,ann=F,xlim=c(0,di),ylim=c(h/2-di/2,h/2+di/2))
for(i in (-di):(2*di)){
  abline(h=i,lwd=1,col="grey")
  abline(v=i,lwd=1,col="grey")
}
lines(c(0,b2,cos(alpha)*c,0),c(0,0,h,0),lwd=2,col="blue")
text(2*bmp/alpha*cos(alpha/2),2*bmp/alpha*sin(alpha/2),TeX("$\\alpha$"))
text(c/2*cos(alpha)+bmp*cos(alpha+pi/2),
     c/2*sin(alpha)+bmp*sin(alpha+pi/2),
     "c")
text(b2+a/2*cos(pi-gamma2)+bmp*cos(pi/2-gamma2),
     a/2*sin(pi-gamma2)+bmp*sin(pi/2-gamma2),TeX("$a$"))
text(b2-3*bmp/gamma2*cos(gamma2/2),
     3*bmp/gamma2*sin(gamma2/2),TeX("$\\gamma_2$"))
```
\

The law of sines promises:

$$\frac{\sin(\alpha)}{a} = \frac{\sin(\gamma_1)}{c}$$

and

$$\frac{\sin(\alpha)}{a} = \frac{\sin(\gamma_2)}{c}$$

Find $\gamma_1$ and $\gamma_2$.

* $\gamma_1 =$ ##ANSWER1##
* $\gamma_2 =$ ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`



Solution
========

Remember, the arcsin function only returns acute angles (between $\frac{-\pi}{2}$ and $\frac{\pi}{2}$). We use arcsin to solve the first equation.

$$\sin(\gamma_1) = \frac{c\sin(\alpha)}{a}$$

$$\gamma_1 = \arcsin\left(\frac{c\sin(\alpha)}{a}\right)$$

which will work because $\gamma_1$ is acute.

$$\gamma_1 = \arcsin\left(\frac{`r c`\sin\left(\frac{`r alpha_num`\pi}{`r alpha_den`}\right)}{`r a`}\right)$$

$$\gamma_1 = `r gamma1`$$

$$\gamma_1 ~\approx~ `r ans1`$$

However, to find $\gamma_2$, it helps to draw a diagram.

```{r,echo=F,fig.dim=c(4,4)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
di = ceiling(max(c(h,b1)))
bmp = di/30
plot(0,0,type="n",axes=F,ann=F,xlim=c(0,di),ylim=c(h/2-di/2,h/2+di/2))
for(i in (-di):(2*di)){
  abline(h=i,lwd=1,col="grey")
  abline(v=i,lwd=1,col="grey")
}
lines(c(0,b1,cos(alpha)*c,0),c(0,0,h,0),lwd=2,col="blue")
text(2*bmp/alpha*cos(alpha/2),2*bmp/alpha*sin(alpha/2),TeX("$\\alpha$"))
text(c/2*cos(alpha)+bmp*cos(alpha+pi/2),
     c/2*sin(alpha)+bmp*sin(alpha+pi/2),
     "c")
text(b1+a/2*cos(pi-gamma1)+bmp*cos(pi/2-gamma1),
     a/2*sin(pi-gamma1)+bmp*sin(pi/2-gamma1),"a")
text(b1-3*bmp/gamma1*cos(gamma1/2),
     3*bmp/gamma1*sin(gamma1/2),TeX("$\\gamma_1$"))

lines(c(0,b2,cos(alpha)*c,0),c(0,0,h,0),lwd=2,col="blue")
text(2*bmp/alpha*cos(alpha/2),2*bmp/alpha*sin(alpha/2),TeX("$\\alpha$"))
text(c/2*cos(alpha)+bmp*cos(alpha+pi/2),
     c/2*sin(alpha)+bmp*sin(alpha+pi/2),
     "c")
text(b2+a/2*cos(pi-gamma2)+bmp*cos(pi/2-gamma2),
     a/2*sin(pi-gamma2)+bmp*sin(pi/2-gamma2),"a")
text(b2-3*bmp/gamma2*cos(gamma2/2),
     3*bmp/gamma2*sin(gamma2/2),TeX("$\\gamma_2$"))

# lines(c(c*cos(alpha),c*cos(alpha)),c(0,h),lty=2,col="purple")
# text(c*cos(alpha)+bmp,h/2,"h",col="purple")
```
\

Notice the [isosceles triangle](https://en.wikipedia.org/wiki/Isosceles_triangle). This implies that $\gamma_2 = \pi-\gamma_1$.

$$\gamma_2 \approx 3.14-`r ans1`$$
$$\gamma_2 \approx `r ans2`$$



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: LOS_ambig_case