```{r,echo=F,warning=F}
while(T){
  ad = sample(c(11,13,17,19,23,29,
                31,37,41,43,47,53,
                59,61,67,71,73,79,
                83,89,97),1)
  an = sort(sample(0:ad,3))
  th = 2*an*pi/ad
  an2 = c(an,an[1]+ad)
  th2 = 2*an2*pi/ad
  m = (diff(th2)/2)[c(2,3,1)]
  alpha = m[1]
  beta = m[2]
  gamma = m[3]
  mn = diff(an2)[c(2,3,1)]
  gf = runif(1,1,5)
  a = 2*sin(alpha)*gf
  b = 2*sin(beta)*gf
  c = 2*sin(gamma)*gf
  l = c(a,b,c)
  lr = round(l,1)
  if(min(diff(th2))>pi/3 && min(diff(an))>1 && length(unique(mn))==3 && length(unique(lr))==3){break}
}
km = sample(1:3,1)
kl = (1:3)[-km]
x = cos(th)
y = sin(th)
xx = c(x,x[1])
yy = c(y,y[1])
xm = (x[c(2,3,1)]+x[c(3,1,2)])/2
ym = (y[c(2,3,1)]+y[c(3,1,2)])/2
s = numeric()
for(i in c(2,3,1)){
  s = c(s,atan2(yy[i+1]-yy[i],xx[i+1]-xx[i]))
}

aa = round(l[kl[1]],2)
bb = round(l[kl[2]],2)
gam = m[km]

cc = sqrt(aa^2+bb^2-2*aa*bb*cos(gam))

```

Question
========

The [law of cosines](https://en.wikipedia.org/wiki/Law_of_cosines) is a correction to [Pythagorean Theorem](https://en.wikipedia.org/wiki/Pythagorean_theorem) that is accurate for ALL triangles (not just right triangles).

$$a^2 = b^2+c^2-2bc\cos(\alpha)$$
$$b^2 = a^2+c^2-2ac\cos(\beta)$$
$$c^2 = a^2+b^2-2ab\cos(\gamma)$$

where angles with measures $\alpha$, $\beta$, and $\gamma$ are opposing sides with lengths $a$, $b$, and $c$ respectively.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-1.1,1.1),ylim=c(-1.1,1.1),axes=F,ann=F)
for(i in seq(-20/gf,20/gf,1/gf)){
  abline(h=i,col="grey")
  abline(v=i,col="grey")
}
tthh = seq(0,2*pi,length.out=1000)
lines(cos(tthh),sin(tthh),lty=3,col="darkgrey")
polygon(cos(th),sin(th),col=rgb(1,0.8,0.8,0.6))
incenter = c(sum(l*cos(th))/(sum(l)),sum(l*sin(th))/(sum(l)))
text(0.7*cos(th[km])+0.3*incenter[1],
     0.7*sin(th[km])+0.3*incenter[2],
     TeX(paste0("$\\frac{",mn[km],"\\pi}{",ad,"}$"))
     )
# for(i in 1:3){
#   text(0.7*cos(th[i])+0.3*incenter[1],
#      0.7*sin(th[i])+0.3*incenter[2],
#      TeX(paste0("$\\frac{",mn[i],"\\pi}{",ad,"}$"))
#      )
# }
for(i in kl){
  text(xm[i]+0.1*cos(s[i]-pi/2),ym[i]+0.1*sin(s[i]-pi/2),round(l[i],2))
}
text(xm[km]+0.1*cos(s[km]-pi/2),ym[km]+0.1*sin(s[km]-pi/2),"?")
```
\

In a triangle, two sides have lengths `r round(l[kl[1]],2)` and `r round(l[kl[2]],2)` with an included angle with measure $\frac{`r mn[km]`\pi}{`r ad`}$ radians.

**Find the length** labelled "?". The tolerance is $\pm 0.01$.


Solution
========

Use the law of cosines.

$$\sqrt{`r aa`^2+`r bb`^2-2\cdot `r aa`\cdot `r bb` \cos\left(\frac{`r mn[km]`\pi}{`r ad`}\right)} ~\approx~ `r round(cc,2)`$$



Meta-information
============
extype: num
exsolution: `r cc`
exname: LOC_get_side
extol: 0.01