```{r,echo=F,warning=F}
fixer = function(exp){
  exp = gsub("--","+",exp,fixed=T)
  return(exp)
}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

while(T){
  hkab = sample(2:8,4)
  h = hkab[1]*sample(c(-1,1),1)
  k = hkab[2]*sample(c(-1,1),1)
  a = hkab[3]
  b = hkab[4]
  c = sqrt(a^2+b^2)
  if(abs(h)+c<10 && abs(k)+b<10 && b/a<3 && b/a>1/3){break}
}

ac1 = -10:10
al1 = paste0("* ",ac1,collapse="\n")
sol1 = paste0(1*(h==ac1),collapse="")
sol2 = paste0(1*(k==ac1),collapse="")
ac2 = 1:10
al2 = paste0("* ",ac2,collapse="\n")
sol3 = paste0(1*(a==ac2),collapse="")
sol4 = paste0(1*(b==ac2),collapse="")

exes = c(fixer(paste0("\\frac{(x-",h,")^2}{",a^2,"}-\\frac{(y-",k,")^2}{",b^2,"}=1")))

nopts = 5
while(length(exes)<nopts){
  hk = sample(c(h,k),2)*sample(c(-1,1),2,T)
  ab = sample(c(a,b))
  hh = hk[1]
  kk = hk[2]
  aa = ab[1]
  bb = ab[2]
  ex = fixer(paste0("\\frac{(x-",hh,")^2}{",aa^2,"}-\\frac{(y-",kk,")^2}{",bb^2,"}=1"))
  exes = unique(c(exes,ex))
}

rexes = sample(exes)
al5 = paste0("* ",LETTERS[1:nopts],collapse="\n")
disp = paste0(LETTERS[1:nopts],":\n\n$$",rexes,"$$",collapse="\n\n")
sol5 = paste0(1*(rexes==exes[1]),collapse="")
```

Question
========

A horizontal [hyperbola](https://openstax.org/books/precalculus-2e/pages/10-2-the-hyperbola) (opening west and east) centered at $(h,k)$ with transverse-axis length $2a$ and conjugate-axis length $2b$ is the set of $x,y$ coordinates that satisfy the equation below.

$$\frac{(x-h)^2}{a^2}-\frac{(y-k)^2}{b^2}=1$$

The four parameters ($h$, $k$, $a$, and $b$) are randomly set to integers. The resulting hyperbola is graphed below, along with the central rectangle and asymptotes.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
polygon(c(h-a,h-a,h+a,h+a),c(k+b,k-b,k-b,k+b),lty=3,border="darkcyan",lwd=2)
th = seq(-pi/2,pi/2,length.out=1000)
x = h+a/cos(th)
y = k+b*tan(th)
lines(x,y,col="blue",lwd=2)
th = seq(pi/2+0.000001,3*pi/2-0.00001,length.out=1000)
x = h+a/cos(th)
y = k+b*tan(th)
lines(x,y,col="blue",lwd=2)
points(c(h-c,h+c),c(k,k),pch=19,col="red")

xx = c(-11,11)
yy = b/a*(xx-h)+k
lines(xx,yy,col="darkorange",lwd=2,lty=3)
xx = c(-11,11)
yy = -b/a*(xx-h)+k
lines(xx,yy,col="darkorange",lwd=2,lty=3)
```
\

* $h=$ ##ANSWER1##
* $k=$ ##ANSWER2##
* $a=$ ##ANSWER3##
* $b=$ ##ANSWER4##

Which of the equations below matches the graph above?

`r disp`

* Equation ##ANSWER5##


Answerlist
--------

`r al1`
`r al1`
`r al2`
`r al2`
`r al5`

Solution
========

Find the center and the dimensions of the central rectangle.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
polygon(c(h-a,h-a,h+a,h+a),c(k+b,k-b,k-b,k+b),lty=3,border="darkcyan",lwd=2)
th = seq(-pi/2,pi/2,length.out=1000)
x = h+a/cos(th)
y = k+b*tan(th)
lines(x,y,col="blue",lwd=2)
th = seq(pi/2+0.000001,3*pi/2-0.00001,length.out=1000)
x = h+a/cos(th)
y = k+b*tan(th)
lines(x,y,col="blue",lwd=2)
points(c(h-c,h+c),c(k,k),pch=19,col="red")

xx = c(-11,11)
yy = b/a*(xx-h)+k
lines(xx,yy,col="darkorange",lwd=2,lty=3)
xx = c(-11,11)
yy = -b/a*(xx-h)+k
lines(xx,yy,col="darkorange",lwd=2,lty=3)

lines(c(h,h+a),c(k,k),lwd=3,col="purple")
text(h+a/2,k+0.1,a,adj=c(0.5,0),col="purple")
lines(c(h,h),c(k,k+b),lwd=3,col="darkgreen")
text(h-0.1,k+b/2,b,adj=c(1,0.5),col="darkgreen")
points(h,k,pch=19,cex=1.3)
text(h-0.1,k-0.1,paste0("(",h,", ",k,")",collapse=""),adj=c(1,1))
```
\

$$h=`r h`$$
$$k=`r k`$$
$$a=`r a`$$
$$b=`r b`$$

Put those into the equation and simplify.

$$`r exes[1]`$$

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`
exname: hyp_get_params