```{r,echo=F,warning=F}
fixer = function(exp){
  exp = gsub("--","+",exp,fixed=T)
  return(exp)
}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

numq = 6
hkabs = list()
for(i in 1:numq){
  while(T){
    hkab = sample(2:8,4)
    h = hkab[1]*sample(c(-1,1),1)
    k = hkab[2]*sample(c(-1,1),1)
    a = hkab[3]
    b = hkab[4]
    c = sqrt(a^2+b^2)
    if(abs(h)+c<10 && abs(k)+b<10 && b/a<3 && b/a>1/3){break}
  }
  hkabs[[i]] = c(h,k,a,b)
}

figshows = character()
eqs = character()
eqshows = character()
ishors = numeric()
x1s = list()
x2s = list()
y1s = list()
y2s = list()
xfs = list()
yfs = list()
sols = character()

for(i in 1:numq){
  h = hkabs[[i]][1]
  k = hkabs[[i]][2]
  a = hkabs[[i]][3]
  b = hkabs[[i]][4]
  figshow = sample(c(T,F),1)
  if(figshow){
    figshows=c(figshows,'asis')
  } else {
    figshows=c(figshows,'hide') 
  }
  ishor = sample(c(T,F),1)
  ishors = c(ishors,1*ishor)
  ord = sample(c(1,2),1)
  if(ishor && ord==1){
    eq = fixer(paste0("\\frac{(x-",h,")^2}{",a^2,"}-\\frac{(y-",k,")^2}{",b^2,"}=1"))
  } else if(ishor && ord==2){
    eq = fixer(paste0("-\\frac{(y-",k,")^2}{",b^2,"}+\\frac{(x-",h,")^2}{",a^2,"}=1"))
  } else if(!ishor && ord==1){
    eq = fixer(paste0("\\frac{(y-",h,")^2}{",a^2,"}-\\frac{(x-",k,")^2}{",b^2,"}=1"))
  } else if(!ishor && ord==2){
    eq = fixer(paste0("-\\frac{(x-",k,")^2}{",b^2,"}+\\frac{(y-",h,")^2}{",a^2,"}=1"))
  }
  eqs = c(eqs,eq)
  if(figshow){
    eqshows= c(eqshows,"")
  } else {
    eqshows = c(eqshows,paste0("$$",eq,"$$",collapse=""))
  }
  if(ishor){
    th = seq(-pi/2,pi/2,length.out=1000)
    x = h+a/cos(th)
    y = k+b*tan(th)
    x1s[[i]] = x
    y1s[[i]] = y
    th = seq(pi/2+0.000001,3*pi/2-0.00001,length.out=1000)
    x = h+a/cos(th)
    y = k+b*tan(th)
    x2s[[i]] = x
    y2s[[i]] = y
    c = sqrt(a^2+b^2)
    xfs[[i]] = c(h-c,h+c)
    yfs[[i]] = c(k,k)
    sols = c(sols,"10")
  } else {
    th = seq(-pi/2,pi/2,length.out=1000)
    x = k+b*tan(th)
    y = h+a/cos(th)
    x1s[[i]] = x
    y1s[[i]] = y
    th = seq(pi/2+0.000001,3*pi/2-0.00001,length.out=1000)
    x = k+b*tan(th)
    y = h+a/cos(th)
    x2s[[i]] = x
    y2s[[i]] = y
    c = sqrt(a^2+b^2)
    yfs[[i]] = c(h-c,h+c)
    xfs[[i]] = c(k,k)
    sols = c(sols,"01")
  }
}

al = paste0("* ",c("horizontal","vertical"),collapse="\n")
al = paste0(rep(al,numq),collapse="\n")
```

Question
========


A **horizontal hyperbola** has two curves facing East and West (like  `)(`  ). There is a center $(h,k)$, transverse semi-axis $a$, and conjugate semi-axis $b$. A horizontal hyperbola is the set of points satisfying the equation below.


$$\frac{(x-h)^2}{a^2}-\frac{(y-k)^2}{b^2}=1$$

A **vertical hyperbola** has two curves facing North and South (like  $\asymp$  ). There is a center $(h,k)$, transverse semi-axis $a$, and conjugate semi-axis $b$. A vertical hyperbola is the set of points satisfying the equation below.


$$\frac{(y-k)^2}{a^2}-\frac{(x-h)^2}{b^2}=1$$


Determine whether the following are horizontal or vertical.

## A

Is the hyperbola represented below horizontal or vertical?

```{r,echo=FALSE,fig.dim=c(5,5),fig.show=figshows[1]}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
lines(x1s[[1]],y1s[[1]],col="blue",lwd=2)
lines(x2s[[1]],y2s[[1]],col="blue",lwd=2)
points(xfs[[1]],yfs[[1]],col="red",pch=19)
```
\

`r eqshows[1]`

The hyperbola represented above is ##ANSWER1##

## B

Is the hyperbola represented below horizontal or vertical?

```{r,echo=FALSE,fig.dim=c(5,5),fig.show=figshows[2]}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
lines(x1s[[2]],y1s[[2]],col="blue",lwd=2)
lines(x2s[[2]],y2s[[2]],col="blue",lwd=2)
points(xfs[[2]],yfs[[2]],col="red",pch=19)
```
\

`r eqshows[2]`

The hyperbola represented above is ##ANSWER2##

## C

Is the hyperbola represented below horizontal or vertical?

```{r,echo=FALSE,fig.dim=c(5,5),fig.show=figshows[3]}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
lines(x1s[[3]],y1s[[3]],col="blue",lwd=2)
lines(x2s[[3]],y2s[[3]],col="blue",lwd=2)
points(xfs[[3]],yfs[[3]],col="red",pch=19)
```
\

`r eqshows[3]`

The hyperbola represented above is ##ANSWER3##

## D

Is the hyperbola represented below horizontal or vertical?

```{r,echo=FALSE,fig.dim=c(5,5),fig.show=figshows[4]}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
lines(x1s[[4]],y1s[[4]],col="blue",lwd=2)
lines(x2s[[4]],y2s[[4]],col="blue",lwd=2)
points(xfs[[4]],yfs[[4]],col="red",pch=19)
```
\

`r eqshows[4]`

The hyperbola represented above is ##ANSWER4##

## E

Is the hyperbola represented below horizontal or vertical?

```{r,echo=FALSE,fig.dim=c(5,5),fig.show=figshows[5]}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
lines(x1s[[5]],y1s[[5]],col="blue",lwd=2)
lines(x2s[[5]],y2s[[5]],col="blue",lwd=2)
points(xfs[[5]],yfs[[5]],col="red",pch=19)
```
\

`r eqshows[5]`

The hyperbola represented above is ##ANSWER5##

## F

Is the hyperbola represented below horizontal or vertical?

```{r,echo=FALSE,fig.dim=c(5,5),fig.show=figshows[6]}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
lines(x1s[[6]],y1s[[6]],col="blue",lwd=2)
lines(x2s[[6]],y2s[[6]],col="blue",lwd=2)
points(xfs[[6]],yfs[[6]],col="red",pch=19)
```
\

`r eqshows[6]`

The hyperbola represented above is ##ANSWER6##

Answerlist
--------

`r al`


Solution
========

The graphs should be pretty easy. `)(` is horizontal and $\asymp$ is vertical.

The equations can be a bit tricky, because the order of the fractions is randomized. **Pay attention to which fraction (containing $x$ or $y$) has the negative sign.**

Personally, I think about $x$ and $y$ values that make the numerators 0. Then I think if there could be any solutions. The key idea is that there are no real $n$ and $d$ such that $-\frac{n^2}{d^2}=1$. If there are $x$ values that have no solution (no corresponding $y$ to make the equation true), then there are vertical lines that do not hit the hyperbola, meaning the hyperbola must be horizontal. If there are $y$ values that have no solution, then there are horizontal lines that do not hit the hyperbola, meaning the hyperbola must be vertical. I know that is convoluted, but I've yet to find a more robust way to store this in my long-term memory.



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r paste0(sols,collapse="|")`
exname: hyp_hor_or_ver