```{r,echo=FALSE}
dt = 0.02
n = 500
sigma = 10 #round(10+runif(1,-0.5,0.5),2)
rho = 28 #round(28 + runif(1,-3,3),2)
beta = 8/3 #round(8/3+runif(1,-0.2,0.2),2)
x0 = round(runif(1,-15,15),1)
y0 = round(runif(1,-10,10),1)
z0 = round(runif(1,15,40),1)
t0 = 0
x0s = c(x0,x0+sample(c(-0.02,-0.01,0.01,0.02)))
y0s = c(y0,y0+sample(c(-0.02,-0.01,0.01,0.02)))
z0s = c(z0,z0+sample(c(-0.02,-0.01,0.01,0.02)))
t = seq(0,dt*n,dt)
x = list()
y = list()
z = list()
for(i in 1:length(x0s)){
  xx = c(x0s[i])
  yy = c(y0s[i])
  zz = c(z0s[i])
  for(j in 1:length(t)){
    dx = (sigma*(yy[j]-xx[j]))*dt
    dy = (xx[j]*(rho-zz[j])-yy[j])*dt
    dz = (xx[j]*yy[j]-beta*zz[j])*dt
    xx = c(xx,xx[j]+dx)
    yy = c(yy,yy[j]+dy)
    zz = c(zz,zz[j]+dz)
  }
  x[[i]] = xx
  y[[i]] = yy
  z[[i]] = zz
}
ord = sample(1:5)
lets = c("A","B","C","D","E")
sol = paste0(1*(1==ord),collapse="")
alet = lets[sum((1:5)[1==ord])]
```


Question
========

By simulating the [Lorenz system](https://en.wikipedia.org/wiki/Lorenz_system), Lorenz made an important contribution to the development of [chaos theory](https://en.wikipedia.org/wiki/Chaos_theory). Below are the rate equations with his original parameters.

$$\begin{align}
\frac{\Delta x}{\Delta t} ~&=~ `r sigma`(y-x)\\\\
\frac{\Delta y}{\Delta t} ~&=~ x(`r rho`-z)-y\\\\
\frac{\Delta z}{\Delta t} ~&=~ xy-\frac{8}{3}z
\end{align}$$

Use Euler's method with $\Delta t=`r dt`$ for time $t=0$ to $t=`r dt*n`$. Use the initial conditions below.

$$x_0 = `r x0`$$
$$y_0 = `r y0`$$
$$z_0 = `r z0`$$
Plot $z$ versus $x$. (Put $z$ on the vertical axis and $x$ on the horizontal axis.) Determine which graph best matches your graph.

```{r,echo=F,fig.dim=c(8,12)}
par(mfrow=c(3,2),mar=c(7,5,1,0))
lets = c("A","B","C","D","E")
for(i in 1:5){
  x2 = x[[ord[i]]]
  y2 = y[[ord[i]]]
  z2 = z[[ord[i]]]
  plot(x2[1:length(t)],z2[1:length(t)],type="l",
       main=lets[i],xlab="x",ylab="z")
}
```
\

Answerlist
--------

* A
* B
* C
* D
* E

Solution
========

The best graph is **`r alet`**. 

```{r,echo=F}
ans = sum((1:5)[ord==1])
x2 = x[[1]]
y2 = y[[1]]
z2 = z[[1]]
plot(x2[1:length(t)],z2[1:length(t)],type="l",col="blue",
     main=lets[ans],xlab="x",ylab="z")
```
\

If two graphs looked almost identical to the correct answer, please screen shot the correct answer along with the options and send those screenshots to me.

Meta-information
============
extype: schoice
exsolution: `r sol`
exname: lorenz_system