```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
deg_opts = c(0,30,45,60,90,120,135,150,180,210,225,240,270,300,315,330,360)
dos = paste0(deg_opts,"ยบ")
ras = c("0","\\pi/6","\\pi/4","\\pi/3","\\pi/2","2\\pi/3","3\\pi/4","5\\pi/6","\\pi","7\\pi/6","5\\pi/4","4\\pi/3","3\\pi/2","5\\pi/3","7\\pi/4","11\\pi/6","2\\pi")
ras2 = c("0","\\frac{\\pi}{6}","\\frac{\\pi}{4}","\\frac{\\pi}{3}","\\frac{\\pi}{2}","\\frac{2\\pi}{3}","\\frac{3\\pi}{4}","\\frac{5\\pi}{6}","\\pi","\\frac{7\\pi}{6}","\\frac{5\\pi}{4}","\\frac{4\\pi}{3}","\\frac{3\\pi}{2}","\\frac{5\\pi}{3}","\\frac{7\\pi}{4}","\\frac{11\\pi}{6}","2\\pi")

angi = sample(c(2:4,6:8,10:12,14:16),1)
deg = deg_opts[angi]
dtex = dos[angi]
rtex = ras2[angi]
rad = deg/180*pi
theta = rad

```

Question
========

Consider the unit circle (radius equals 1) with a central angle subtending an arc with a length of $`r rtex`$.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
th = seq(0,2*pi,pi/300)
plot(cos(th),sin(th),"l",axes=F,ann=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
lines(c(cos(theta),0),c(sin(theta),0),col="black")
lines(c(0,1),c(0,0),col="purple",lwd=3)
points(0,0,pch=20,col="purple")
text(0.5,-0.07,TeX(paste0("$",1,"$")),col="purple")
th2 = seq(0,theta,pi/300)
lines(0.2*cos(th2),0.2*sin(th2),col="blue",lwd=3)
n = length(th2)
arrows(0.2*cos(th2[n-1]),0.2*sin(th2[n-1]),0.2*cos(th2[n]),0.2*sin(th2[n]),0.07,30,2,"blue",lwd=3)
text(0.4*cos(theta/2),0.4*sin(theta/2),TeX(paste0("$x^{\\circ}$")),col="blue",cex=2)
lines(cos(th2),sin(th2),col="red",lwd=3)
text(1.2*cos(theta/2),1.2*sin(theta/2),TeX(paste0("$",rtex,"$")),col="red")
```
\

The central angle measure is $x$ **degrees**. Find $x$.


Solution
========

* You should understand radian measure of an angle as the length of the arc on the unit circle subtended by the angle.

Thus, this question is equivalent to converting $`r rtex`$ radians to degrees.


Meta-information
============
extype: num
exsolution: `r deg`
exname: unit_circle_deg_from_L