```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
library(latex2exp)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

tdens = c(18,20,24)

rnums = numeric()
rdens = numeric()
rdecs = numeric()
rpris = character()

makepr = function(rnum,rden){
    if(rden==1){
        s = paste0("{",rnum,"}\\pi")    
    } else {
        s = paste0("\\frac{{",rnum,"}\\pi}{",rden,"}")
    }
    s = gsub("{1}","",s,fixed=T)
    return(s)
}

for(tden in tdens){
    for(tnum in 1:tden){
        rnum = tnum*2
        rden = tden
        gg = gcd(rnum,rden)
        rnum = round(rnum/gg)
        rden = round(rden/gg)
        rdec = round(pi*rnum/rden,5)
        if(rnum>1 && rden>1 && !(rdec%in%rdecs)){
            rnums = c(rnums,rnum)
            rdens = c(rdens,rden)
            rdecs = c(rdecs,rdec)
            rpris = c(rpris,makepr(rnum,rden))
            }
    }
}

myord = order(rdecs) #I thought it'd be multiple choice, but actually... dec approx answer better?
rdecs = rdecs[myord]
rnums = rnums[myord]
rdens = rdens[myord]
rpris = rpris[myord]

angi = sample(1:length(rdecs),1)
rdec = rdecs[angi]
rnum = rnums[angi]
rden = rdens[angi]
rpri = rpris[angi]
theta = rdec
```

Question
========

Consider the unit circle (radius equals 1) with a central angle subtending an arc with a length of $`r rpri`$.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
th = seq(0,2*pi,pi/300)
plot(cos(th),sin(th),"l",axes=F,ann=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
lines(c(cos(theta),0),c(sin(theta),0),col="black")
lines(c(0,1),c(0,0),col="purple",lwd=3)
points(0,0,pch=20,col="purple")
text(0.5,-0.07,TeX(paste0("$",1,"$")),col="purple")
th2 = seq(0,theta,pi/300)
lines(0.2*cos(th2),0.2*sin(th2),col="blue",lwd=3)
n = length(th2)
arrows(0.2*cos(th2[n-1]),0.2*sin(th2[n-1]),0.2*cos(th2[n]),0.2*sin(th2[n]),0.07,30,2,"blue",lwd=3)
text(0.4*cos(theta/2),0.4*sin(theta/2),TeX(paste0("$\\theta$")),col="blue",cex=2)
lines(cos(th2),sin(th2),col="red",lwd=3)
text(1.2*cos(theta/2),1.2*sin(theta/2),TeX(paste0("$",rpri,"$")),col="red")
```
\

The central angle measure is $\theta$ **radians**. Find a decimal approximation of the central angle measure, $\theta$, in radians. The tolerance is $\pm 0.01$.


Solution
========

* You should understand radian measure of an angle as the length of the arc on the unit circle subtended by the angle.

Thus, this question is equivalent to converting $`r rpri`$ radians to its decimal approximation. You can do that by typing $`r rpri`$ into a calculator.


Meta-information
============
extype: num
exsolution: `r rdec`
exname: unit_circle_rad_from_L
extol: 0.01