```{r,echo=F}
while(T){
  ang = runif(1,0.1,0.9)*2*pi*sample(c(-1,1),1)
  deg = round(ang/pi*180)
  if(abs(deg%%90)>5){break}
}

correct = c(0,ang)
wrong1 = c(0,-ang)
wrong2 = c(pi/2,pi/2+ang)
wrong3 = c(pi/2,pi/2-ang)
wrong4 = c(pi,pi+ang)
wrong5 = c(pi,pi-ang)
wrong6 = c(3*pi/2,3*pi/2+ang)
wrong7 = c(3*pi/2,3*pi/2-ang)
allchoices = list(correct,wrong1,wrong2,wrong3,wrong4,wrong5,wrong6,wrong7)
shuch = sample(allchoices)
sol = ""
for(i in 1:length(shuch)){
  if(shuch[[i]][1]==correct[1] && shuch[[i]][2]==correct[2]){
    sol = paste0(sol,"1",collapse="")
    sollet = LETTERS[i]
  } else {
    sol = paste0(sol,"0",collapse="")
  }
}
if(ang>0){
  wrd1 = "positive"
  wrd2 = "counterclockwise"
} else {
  wrd1 = "negative"
  wrd2 = "clockwise"
}
```

Question
========

Which graph shows a `r deg`$^\circ$ angle in standard position?

```{r,echo=F,fig.dim=c(6,12)}
par(mfrow = c(4, 2))
for(i in 1:length(shuch)){
  par(mar=c(0,3,3,3),pty="s")
  plot(0,0,type="n",axes=F,xlim=c(-1,1),ylim=c(-1,1),main=LETTERS[i])
  abline(h=0)
  abline(v=0)
  a1 = shuch[[i]][1]
  a2 = shuch[[i]][2]
  lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
  lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
  len = 100
  th = seq(a1,a2,sign(a2-a1)*pi/100)
  len = length(th)-1
  r = 0.7
  lines(r*cos(th),r*sin(th),lwd=2,col="blue")
  arrows(r*cos(th[len]),r*sin(th[len]),r*cos(th[len+1]),r*sin(th[len+1]),lwd=2,col="blue")
}

```
\

Answerlist
--------

* A
* B
* C
* D
* E
* F
* G
* H



Solution
========

The standard position of an angle puts the initial side pointing East (horizontally to the right). A positive angle opens COUNTERCLOCKWISE, and a negative angle opens clockwise. The terminal side of the angle is placed at the end of the angle's arc.


In this case the angle is `r wrd1`, so the angle rotates `r wrd2`. Thus, the correct answer is `r sollet`.


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: plot_angle_standard_position