```{r,echo=F}
## Editorial note: it would be nice to show remainder with long division

while(T){
  ang = runif(1,1.1,3.9)*2*pi*sample(c(-1,1),1)
  deg = round(ang/pi*180)
  if(abs(deg%%90)>10 && abs(deg%%90)<80){break}
}
correct = c(0,ang)
wrong1 = c(0,-ang)
wrong2 = c(0,pi/2*sample(c(-1,1),1)+ang)
wrong3 = c(0,pi/2*sample(c(-1,1),1)-ang)
wrong4 = c(0,pi*sample(c(-1,1),1)+ang)
wrong5 = c(0,pi*sample(c(-1,1),1)-ang)
wrong6 = c(0,3*pi/2*sample(c(-1,1),1)+ang)
wrong7 = c(0,3*pi/2*sample(c(-1,1),1)-ang)
allchoices = list(correct,wrong1,wrong2,wrong3,wrong4,wrong5,wrong6,wrong7)
shuch = sample(allchoices)
sol = ""
for(i in 1:length(shuch)){
  if(shuch[[i]][1]==correct[1] && shuch[[i]][2]==correct[2]){
    sol = paste0(sol,"1",collapse="")
    sollet = LETTERS[i]
  } else {
    sol = paste0(sol,"0",collapse="")
  }
}

div = floor(abs(deg)/360)
rem = abs(deg)%%360

qts = rem%/%90
lq = qts*90
uq = (qts+1)*90

if(ang>0){
  wrd1 = "positive"
  wrd2 = "counterclockwise"
  q = qts+1
} else {
  wrd1 = "negative"
  wrd2 = "clockwise"
  q = 4-qts
}

qls = c("I","II","III","IV")

```

Question
========

Which graph shows a `r deg`$^\circ$ angle in standard position?

```{r,echo=F,fig.dim=c(6,12)}
par(mfrow = c(4, 2))
for(i in 1:length(shuch)){
  par(mar=c(0,3,3,3),pty="s")
  plot(0,0,type="n",axes=F,xlim=c(-1,1),ylim=c(-1,1),main=LETTERS[i])
  abline(h=0)
  abline(v=0)
  a1 = shuch[[i]][1]
  a2 = shuch[[i]][2]
  lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
  lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
  len = 500
  th = seq(a1,a2,sign(a2-a1)*pi/100)
  len = length(th)-1
  r = seq(0.4,0.8,0.4/len)
  lines(r*cos(th),r*sin(th),lwd=2,col="red")
  arrows(0.8*cos(th[len]),0.8*sin(th[len]),0.8*cos(th[len+1]),0.8*sin(th[len+1]),lwd=2,col="red",length=0.1)
}

```
\

Answerlist
--------

* A
* B
* C
* D
* E
* F
* G
* H



Solution
========

The given angle is `r deg`$^\circ$. The angle is `r wrd1`, so the angle rotates **`r wrd2`**.

Notice if we divide `r abs(deg)` by 360 we get `r div` with a remainder of `r rem`. So, rotate `r div` full times and then also rotate by `r rem`$^\circ$. 

Notice that `r rem`$^\circ$ is between `r lq`$^\circ$ and `r uq`$^\circ$, so it'll need between `r qts` and `r qts+1` quarter turns after the `r div` full turns (all `r wrd2`). That puts the terminal side in quadrant `r q` (quadrant `r qls[q]`).

```{r,echo=F,fig.dim=c(6,6)}

par(mar=c(0,3,3,3),pty="s")
plot(0,0,type="n",axes=F,xlim=c(-1,1),ylim=c(-1,1))
abline(h=0)
abline(v=0)
a1 = correct[1]
a2 = correct[2]
lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
len = 500
mi = 0.4
ma = 0.8
th = seq(a1,a2,(a2-a1)/len)
r = seq(mi,ma,(ma-mi)/len)
len = length(th)-1
lines(r*cos(th),r*sin(th),lwd=2,col="red")
arrows(0.8*cos(th[len]),0.8*sin(th[len]),0.8*cos(th[len+1]),0.8*sin(th[len+1]),lwd=2,col="red",length=0.2)

for(i in 0:div){
  text(i/(abs(deg)/360)*(ma-mi)+mi-0.03,0.04,i)
}

```
\



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: plot_angle_standard_position