```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  den = sample(c(5,10,7,14,9,18,11,12,22,24),1)
  num = sample(1:den,1)
  div = gcd(den,num)
  num = round(num/div)
  den = round(den/div)
  radnum = num*2
  radden = den
  raddiv = gcd(radnum,radden)
  radnum = round(radnum/raddiv)
  radden = round(radden/raddiv)
  deg = den*360/num
  ang = radnum*pi/radden
  ref = ang%%(pi/2)
  ref = min(ref,pi/2-ref)
  if(radden>2 && radden<9 && radden!=4 && abs(pi/4-ref)>pi/17){break}
}

offby = sample(c(-3,-2,-1,1,2,3),1)
ang = ang+offby*2*pi
deg = ang*180/pi

correct = c(0,ang)
wrong1 = c(0,-ang)
wrong2 = c(0,pi/2*sample(c(-1,1),1)+ang)
wrong3 = c(0,pi/2*sample(c(-1,1),1)-ang)
wrong4 = c(0,pi*sample(c(-1,1),1)+ang)
wrong5 = c(0,pi*sample(c(-1,1),1)-ang)
wrong6 = c(0,3*pi/2*sample(c(-1,1),1)+ang)
wrong7 = c(0,3*pi/2*sample(c(-1,1),1)-ang)
allchoices = list(correct,wrong1,wrong2,wrong3,wrong4,wrong5,wrong6,wrong7)
shuch = sample(allchoices)
sol = ""
for(i in 1:length(shuch)){
  if(shuch[[i]][1]==correct[1] && shuch[[i]][2]==correct[2]){
    sol = paste0(sol,"1",collapse="")
    sollet = LETTERS[i]
  } else {
    sol = paste0(sol,"0",collapse="")
  }
}

if(ang>0){
  wrd1 = "positive"
  wrd2 = "counterclockwise"
} else {
  wrd1 = "negative"
  wrd2 = "clockwise"
}

qls = c("I","II","III","IV")

rn = paste0(radnum)
if(radnum==1){rn=""}


rn3 = radnum+offby*2*radden
rn2 = radnum+offby*2*radden
if(rn2 == -1){rn2="-"} else {rn2=paste0(rn2)}


```

Question
========

Which graph shows a $\frac{`r rn2`\pi}{`r radden`}$ angle in standard position?

```{r,echo=F,fig.dim=c(6,12)}
par(mfrow = c(4, 2))
for(i in 1:length(shuch)){
  par(mar=c(0,3,3,3),pty="s")
  plot(0,0,type="n",axes=F,xlim=c(-1,1),ylim=c(-1,1),main=LETTERS[i])
  abline(h=0)
  abline(v=0)
  a1 = shuch[[i]][1]
  a2 = shuch[[i]][2]
  lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
  lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
  th = seq(a1,a2,sign(a2-a1)*pi/100)
  len = length(th)
  if(abs(a2)<2*pi){
    r = 0.8
  } else {
    r = seq(0.4,0.8,length.out=length(th))
  }
  lines(r*cos(th),r*sin(th),lwd=2,col="red")
  arrows(0.8*cos(th[len-1]),0.8*sin(th[len-1]),0.8*cos(th[len]),0.8*sin(th[len]),lwd=2,col="red",length=0.1)
}

```
\

Answerlist
--------

* A
* B
* C
* D
* E
* F
* G
* H



Solution
========

The given angle is $\frac{`r rn2`\pi}{`r radden`}$. The angle is `r wrd1`, so the angle rotates **`r wrd2`**.

Each wedge shown below corresponds to an angle of $\frac{\pi}{`r radden`}$. So, we just need to turn across `r abs(rn3)` wedges `r wrd2`.

```{r,echo=F,fig.dim=c(6,6)}
library(latex2exp)
par(mar=c(0,3,3,3),pty="s")
plot(0,0,type="n",axes=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
abline(h=0,col=rgb(0,0,0,0.2))
abline(v=0,col=rgb(0,0,0,0.2))
a1 = correct[1]
a2 = correct[2]
lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=3)
lines(c(0,cos(a2)),c(0,sin(a2)),col="blue",lwd=3)
len = 500
th = seq(a1,a2,length.out = len+1)
if(abs(a2)<2*pi){
  r = 0.8
} else {
  r = seq(0.4,0.8,length.out = len+1)
}
lines(r*cos(th),r*sin(th),lwd=2,col="red")
arrows(0.8*cos(th[len]),0.8*sin(th[len]),0.8*cos(th[len+1]),0.8*sin(th[len+1]),lwd=2,col="red",length=0.2)

for(i in 1:(2*radden-1)){
  chi = i*pi/radden
  ni = i
  if(i==1){
    ni = ""
  }
  lines(c(1.1*cos(chi),0),c(1.1*sin(chi),0),col="purple",lwd=1,lty=2)
  # text(1.25*cos(chi),1.25*sin(chi),TeX(paste0("$\\frac{",i,"\\pi}{",radden,"}$")))
}

```
\



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: plot_angle_standard_position