```{r data generation, echo = FALSE, results = "hide"}
x = 1:9
f = sample(1:9)
g = sample(1:9)
h = sample(1:9)

funs = list(f,g,h)

al = paste0("* ",1:9,collapse="\n")

while(T){
    fun12 = sample(1:3,2)
    fun1 = fun12[1]
    fun2 = fun12[2]
    num1 = sample(1:9,1)
    num2 = sample(1:9,1)
    ans1 = funs[[fun1]][num1]
    ans2 = x[num2==funs[[fun2]]]
    if(length(unique(c(num1,num2,ans1,ans2)))==4){break}
}

lets = c("f","g","h")
let1 = lets[fun1]
let2 = lets[fun2]

sol1 = paste0(1*(ans1==1:9),collapse="")
sol2 = paste0(1*(ans2==1:9),collapse="")

```

Question
========

Consider the functions $f$, $g$, and $h$ defined by the table below.

```{r,echo=F,warning=FALSE}
library(kableExtra)
data <- data.frame(
  x,
  f,
  g,
  h
)
colnames(data) = c("x","f(x)","g(x)","h(x)")
kable(data, "html") %>%
  kable_styling(bootstrap_options = "bordered",full_width=F)
```
\

Evaluate the expressions:

* $`r let1`(`r num1`)~=$ ##ANSWER1##
* $`r let2`^{-1}(`r num2`)~=$ ##ANSWER2##


Answerlist
--------

`r al`
`r al`


Solution
========

To evaluate $`r let1`(`r num1`)$, you start in the $x$ column, go down to where $x=`r num1`$, then go across to the `r let1` column, and read the number.

$$`r let1`(`r num1`)~=~`r ans1`$$

To evaluate $`r let2`^{-1}(`r num2`)$, you start in the $`r let2`$ column, go down to where $`r let2`(x)=`r num2`$, then go across to the $x$ column, and read the number.


$$`r let2`^{-1}(`r num2`)~=~`r ans2`$$



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: eval_fun_n_inv_table