```{r data generation, echo = FALSE, results = "hide"}
rands = sample(1:9,8)
xbase = rands[1:3]
x = sort(c(0,rands[1:3],10))
y = sort(rands[4:8],decreasing = sample(c(T,F),1))

xs = sample(xbase,2)
x1 = xs[1]
x2 = xs[2]
y1 = y[x==x1]
y2 = y[x==x2]

ach = 1:9

sol1 = paste0(1*(y1==ach),collapse="")
sol2 = paste0(1*(x2==ach),collapse="")

al = paste0("* ",ach,collapse="\n")

```



Question
========


Function $f$ is graphed below.

```{r,fig.dim=c(5,5),echo=FALSE}
par(pty="s")
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="f(x)",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
```
\

Evaluate the expressions:

* $f(`r x1`)~=~$ ##ANSWER1##
* $f^{-1}(`r y2`)~=~$ ##ANSWER2## 

Answerlist
--------

`r al`
`r al`


Solution
========

Find the correct points on the graph where $x=`r x1`$ and where $f(x)=`r y2`$.

```{r,fig.dim=c(5,5),echo=FALSE}
par(pty="s")
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="f(x)",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
dify=0
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
points(x1,y1,pch=20,cex=2.5,col="black")
points(x1,y1,pch=20,cex=2,col="red")
points(x2,y2,pch=20,cex=2.5,col="black")
points(x2,y2,pch=20,cex=2,col="green")
```
\

First, the red dot tells us that $f(`r x1`)=`r y1`$.

And then, the green dot tells us that $f(`r x2`)=`r y2`$, and thus $f^{-1}(`r y2`)=`r x2`$.



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: eval_func_n_inv_from_graph