```{r buildQM,echo=F}
# S-IC.A.1: Understand statistics as a process for making inferences to be made about population parameters based on a random sample from that population.

# The Question Matrix is built in this block of code. One scenario will be chosen randomly.

# Scenario 1
Scenario = "A baker wants to know the average number of chocolate chips in all the cookies in their bakery. They take $10$ cookies at random and count the chocolate chips in each cookie. They find an average of $15$ chocolate chips per cookie in their sample."

Sample = "The $10$ cookies that the baker selected"
Statistic = "The average of $15$ chocolate chips per cookie found in the sample"
Population = "All the cookies in the bakery"
Parameter = "The average number of chocolate chips in all the cookies in the bakery"

QM = data.frame(Scenario,Sample,Statistic,Population,Parameter)

# Scenario 2
Scenario = "A teacher has $100$ students this year and wants to know what percentage of their students like to read. They ask $15$ students if they enjoy reading, and $10$ of those students say they do."

Sample = "The $15$ students the teacher asked"
Statistic = "$66.7\\%$ ($10$ out of $15$) of the students in the sample enjoy reading"
Population = "The $100$ students in the teacher's classes"
Parameter = "The percentage of all students in the class who enjoy reading"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 3
Scenario = "A scientist wants to know the average height of all trees in a forest. They measure the height of $20$ randomly selected trees in the forest. The average height of the trees in their sample is $12$ feet."

Sample = "The $20$ trees that the scientist measured"
Statistic = "The average height of $12$ feet found in the sample of trees"
Population = "All the trees in the forest"
Parameter = "The average height of all the trees in the forest"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 4
Scenario = "A pet store owner wants to know the average weight of all the goldfish in their tanks. They weigh $10$ goldfish at random and find an average weight of $0.5$ ounces."

Sample = "The $10$ goldfish that the owner weighed"
Statistic = "The average weight of $0.5$ ounces found in the sample of goldfish"
Population = "All the goldfish in the store's tanks"
Parameter = "The average weight of all the goldfish in the store's tanks"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 5
Scenario = "A farmer wants to estimate the average number of apples on each tree in their orchard. They randomly select $5$ trees and count the total number of apples on each tree. They find an average of $36$ apples per tree."

Sample = "The $5$ trees the farmer selected"
Statistic = "The average of $36$ apples per tree found in the sample"
Population = "All the trees in the orchard"
Parameter = "The average number of apples on each tree in the orchard"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 6
Scenario = "A librarian wants to know what percentage of the available books in the library are checked out today. They randomly choose $50$ books from the shelves and note whether each book is checked out today. $15$ of the $50$ books are checked out."

Sample = "The $50$ books the librarian selected"
Statistic = "$30\\%$ of the books in the sample are checked out"
Population = "All the books in the library"
Parameter = "The percentage of books in the library that are checked out today"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 7
Scenario = "A company wants to know what percentage of their customers are satisfied with their product. They send out a survey to $500$ customers and find that $425$ are satisfied."

Sample = "The $500$ customers who received the survey"
Statistic = "$85\\%$ of the customers in the sample are satisfied"
Population = "All the company's customers"
Parameter = "The percentage of all customers who are satisfied"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 8
Scenario = "A scientist wants to know the average wingspan of all butterflies in a meadow. They catch and measure the wingspan of $15$ butterflies. They find an average wingspan of $3$ inches."

Sample = "The $15$ butterflies that the scientist measured"
Statistic = "The average wingspan of $3$ inches found in the sample of butterflies"
Population = "All the butterflies in the meadow"
Parameter = "The average wingspan of all the butterflies in the meadow"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 9
Scenario = "A teacher has $80$ students and wants to know the average number of words their students can read per minute. They have $20$ randomly selected students read a passage and count the number of words read in one minute. The average words read per minute in the sample is $100$ words."

Sample = "The $20$ students who participated in the reading test"
Statistic = "The average of $100$ words per minute found in the sample of students"
Population = "The $80$ students the teacher has in their classes"
Parameter = "The average number of words per minute that all students in the class can read"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 10
Scenario = "A restaurant owner wants to know the average time customers spend waiting for their food. They record the wait time of $25$ customers at random. The average wait time in the sample is $15$ minutes."

Sample = "The $25$ customers whose wait times were recorded"
Statistic = "The average wait time of $15$ minutes found in the sample of customers"
Population = "All the customers who visit the restaurant"
Parameter = "The average wait time for all customers in the restaurant"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 11
Scenario = "A gardener wants to know what percentage of their tomatoes plants have ripe tomatoes. They check $20$ tomato plants and find that $10$ of them have ripe tomatoes."

Sample = "The $20$ tomato plants that the gardener checked"
Statistic = "$50\\%$ of the tomato plants in the sample have ripe tomatoes"
Population = "All the tomato plants in the garden"
Parameter = "The percentage of tomato plants in the garden with ripe tomatoes"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 12
Scenario = "A doctor wants to know the average blood pressure of all their patients. They measure the blood pressure of $50$ patients at random. They find an average blood pressure of $120/80$."

Sample = "The $50$ patients whose blood pressure was measured"
Statistic = "The average blood pressure of $120/80$ found in the sample of patients"
Population = "All the doctor's patients"
Parameter = "The average blood pressure of all the doctor's patients"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 13
Scenario = "A store manager wants to know the average price of all the items in their store. They randomly select $50$ items and find an average price of $\\$10$."

Sample = "The $50$ items that the manager selected"
Statistic = "The average price of $\\$10$ found in the sample of items"
Population = "All the items in the store"
Parameter = "The average price of all the items in the store"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 14
Scenario = "A school has $350$ students. A teacher wants to estimate the percentage of the students have at least one pet. They ask $25$ random students and find that $15$ of them have at least one pet."

Sample = "The $25$ students that the teacher asked"
Statistic = "$60\\%$ of the students in the sample have at least one pet"
Population = "All the students in the school"
Parameter = "The percentage of all the students in the school who have at least one pet"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 15
Scenario = "A zookeeper wants to know the average weight of all $35$ of the tigers in the tiger zoo. They weigh $8$ random tigers and find an average weight of $400$ pounds."

Sample = "The $8$ tigers that the zookeeper weighed"
Statistic = "The average weight of $400$ pounds found in the sample of tigers"
Population = "All the tigers in the zoo"
Parameter = "The average weight of all the tigers in the zoo"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 16
Scenario = "A researcher wants to know the average number of words on each page in a novel. They randomly select $10$ pages and count the words on each page. They find an average of $250$ words per page."

Sample = "The $10$ pages that the researcher selected"
Statistic = "The average of $250$ words per page found in the sample of pages"
Population = "All the pages in the novel"
Parameter = "The average number of words on each page in the novel"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 17
Scenario = "A fruit stand owner wants to know what percentage of their apples are ripe. They randomly select $20$ apples and find that $15$ are ripe."

Sample = "The $20$ apples that the owner selected"
Statistic = "$75\\%$ of the apples in the sample are ripe"
Population = "All the apples at the fruit stand"
Parameter = "The percentage of all apples at the fruit stand that are ripe"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 18
Scenario = "A factory manager wants to know how many of their light bulbs are defective. They test $100$ randomly selected light bulbs and find that $5$ are defective." 

Sample = "The $100$ light bulbs that the manager tested"
Statistic = "$5\\%$ of the light bulbs in the sample are defective"
Population = "All the light bulbs produced in the factory"
Parameter = "The percentage of all light bulbs produced in the factory that are defective"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 19
Scenario = "A teacher wants to know how many of their students are absent on a typical day. They check the attendance records for a week and find that 3 out of 25 students were absent on average per day."

Sample = "The attendance records for the week"
Statistic = "$12\\%$ of the students were absent on average per day that week"
Population = "All the days that the teacher has students"
Parameter = "The percentage of all the students in the class who are absent on a typical day"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 20
Scenario = "A park ranger wants to know the average age of all the trees in a national park. They randomly select $30$ trees and find an average age of $75$ years."

Sample = "The $30$ trees that the ranger selected"
Statistic = "The average age of $75$ years found in the sample of trees"
Population = "All the trees in the national park"
Parameter = "The average age of all the trees in the park"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 21
Scenario = "A researcher wants to know the average number of hours people spend watching TV each day. They ask $100$ people about their TV viewing habits and find an average of $2$ hours per day."

Sample = "The $100$ people who participated in the survey"
Statistic = "The average of $2$ hours per day found in the sample of people"
Population = "All the people in the country"
Parameter = "The average number of hours per day that all people in the country spend watching TV"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 22
Scenario = "A  restaurant owner wants to know the average amount of money customers spend per meal. They check the receipts of $50$ customers and find an average spending of $\\$20$."

Sample = "The $50$ customers whose receipts were checked"
Statistic = "The average spending of $\\$20$ found in the sample of customers"
Population = "All the customers who eat at the restaurant"
Parameter = "The average amount of money that all customers spend per meal at the restaurant"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 23
Scenario = "A teacher wants to know the average number of siblings their students have. They ask $20$ students and find an average of $2$ siblings per student."

Sample = "The $20$ students that the teacher asked"
Statistic = "The average of $2$ siblings per student found in the sample"
Population = "All the students in the teacher's class"
Parameter = "The average number of siblings that all students in the class have"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 24
Scenario = "A store owner wants to know the average price of all the shoes in their store. They randomly select $25$ pairs of shoes and find an average price of $\\$150$."

Sample = "The $25$ pairs of shoes that the owner selected"
Statistic = "The average price of $\\$150$ found in the sample of shoes"
Population = "All the shoes in the store"
Parameter = "The average price of all the shoes in the store"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 25
Scenario = "A scientist wants to know the average lifespan of a type of insect. They observe $100$ insects and record their lifespans. They find an average lifespan of $30$ days."

Sample = "The $100$ insects that the scientist observed"
Statistic = "The average lifespan of $30$ days found in the sample of insects"
Population = "All the insects of that type"
Parameter = "The average lifespan of all insects of that type"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 26
Scenario = "A survey is conducted to estimate the percentage of people in a country who prefer a particular brand of coffee. They ask $1000$ people and find that $600$ prefer the brand."

Sample = "The $1000$ people who were surveyed"
Statistic = "$60\\%$ of the people in the sample prefer the brand"
Population = "All the people in the country"
Parameter = "The percentage of all people in the country who prefer the brand"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 27
Scenario = "A gambler wants to investigate a coin's chance to land heads. They flip the coin $1000$ times and get $520$ heads."

Sample = "The $1000$ coin flips"
Statistic = "$52\\%$ of the coin flips in the sample landed heads"
Population = "All possible flips of the coin"
Parameter = "The probability of getting heads on any given flip of the coin" 

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 28
Scenario = "A farmer wants to know the average yield of their cornfield. They randomly select $10$ rows of corn and measure the yield of each row. They find an average yield of $150$ bushels per acre."

Sample = "The $10$ rows of corn that the farmer selected"
Statistic = "The average yield of $150$ bushels per acre found in the sample of rows"
Population = "All the rows of corn in the field"
Parameter = "The average yield of all the rows of corn in the field"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 29
Scenario = "A company wants to know the average number of hours their employees work per week. They take a sample of $50$ employees and find an average work week of $40$ hours."

Sample = "The $50$ employees whose work hours were measured"
Statistic = "The average work week of $40$ hours found in the sample of employees"
Population = "All the employees in the company"
Parameter = "The average number of hours per week that all employees in the company work"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 30
Scenario = "A  researcher wants to estimate the average age of people in a certain city. They take a random sample of $200$ residents and find an average age of $35$ years."

Sample = "The $200$ residents who were sampled"
Statistic = "The average age of $35$ years found in the sample of residents"
Population = "All the residents in the city"
Parameter = "The average age of all residents in the city"

# Scenario 31
Scenario = "A clothing store owner wants to know what percentage of their shirts are sold each day. They randomly select $50$ shirts from their inventory and find that $10$ of them have been sold."

Sample = "The $50$ shirts that the owner selected"
Statistic = "The $20\\%$ of shirts in the sample that have been sold"
Population = "All the shirts in the store"
Parameter = "The percentage of shirts in the store that are sold each day"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 32
Scenario = "A school wants to know the average number of books read by each student in their library. They record the number of books read by $25$ randomly selected students. The average number of books read in the sample is $10$ books."

Sample = "The $25$ students whose book reading records were checked"
Statistic = "The average of $10$ books per student found in the sample"
Population = "All the students in the school"
Parameter = "The average number of books read by each student in the library"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 33
Scenario = "A  researcher wants to investigate the percentage of cars that are red on a certain highway. They count the color of $100$ cars and find $15$ of them are red."

Sample = "The $100$ cars that the researcher observed"
Statistic = "The $15\\%$ of the cars in the sample that are red"
Population = "All the cars on the highway"
Parameter = "The percentage of all cars on the highway that are red"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 34
Scenario = "A musician wants to know the average number of songs their fans listen to each day. They ask $30$ fans how many songs they listen to daily and find an average of $25$ songs."

Sample = "The $30$ fans who responded to the musician's question"
Statistic = "The average of $25$ songs per day found in the sample of fans"
Population = "All the musician's fans"
Parameter = "The average number of songs the musician's fans listen to each day"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 35
Scenario = "A bakery wants to know what percentage of their customers order cupcakes. They keep track of the orders for one week and find that $30$ out of $100$ customers ordered cupcakes."

Sample = "The $100$ customers who placed orders that week"
Statistic = "The $30\\%$ of customers in the sample who ordered cupcakes"
Population = "All the customers who visit the bakery"
Parameter = "The percentage of all bakery customers who order cupcakes"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 36
Scenario = "A  researcher wants to know the average number of hours students spend studying each day. They survey $50$ students and find an average of $3$ hours per day."

Sample = "The $50$ students who participated in the survey"
Statistic = "The average of $3$ hours per day found in the sample of students"
Population = "All the students in the school"
Parameter = "The average number of hours per day that all students in the school spend studying"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 37
Scenario = "A  teacher wants to know the average height of all the students in their class. They measure the height of $10$ randomly selected students. The average height of the students in their sample is $5$ feet $5$ inches."

Sample = "The $10$ students that the teacher measured"
Statistic = "The average height of $5$ feet $5$ inches found in the sample of students"
Population = "All the students in the teacher's class"
Parameter = "The average height of all the students in the teacher's class"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 38
Scenario = "A company wants to estimate the percentage of their employees who use public transportation to get to work. They survey $100$ randomly selected employees and find that $40$ of them use public transportation."

Sample = "The $100$ employees who participated in the survey"
Statistic = "The $40\\%$ of employees in the sample who use public transportation"
Population = "All the employees in the company"
Parameter = "The percentage of all employees in the company who use public transportation"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 39
Scenario = "A farmer wants to know the average weight of their watermelons. They randomly select $10$ watermelons from their field and weigh them. They find an average weight of $20$ pounds."

Sample = "The $10$ watermelons that the farmer weighed"
Statistic = "The average weight of $20$ pounds found in the sample of watermelons"
Population = "All the watermelons in the farmer's field"
Parameter = "The average weight of all the watermelons in the farmer's field"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 40
Scenario = "A researcher wants to know the average number of books people read per year. They survey $500$ people and find an average of $12$ books per year."

Sample = "The $500$ people who participated in the survey"
Statistic = "The average of $12$ books per year found in the sample of people"
Population = "All the people in the country"
Parameter = "The average number of books that all people in the country read per year"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 41
Scenario = "A zookeeper is trying to determine how many of the zoo's $150$ flamingos have a pink feather. They catch $12$ of them and find $9$ have pink feathers."

Sample = "The $12$ flamingos that the zookeeper caught"
Statistic = "$75\\%$ of the flamingos in the sample have a pink feather"
Population = "All the flamingos in the zoo"
Parameter = "The percentage of flamingos in the zoo that have a pink feather"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 42
Scenario = "A  restaurant owner wants to know how many customers order pizza on Friday nights. They randomly select $25$ receipts from Friday nights and find $10$ of them are for pizzas."

Sample = "The $25$ receipts that the owner selected"
Statistic = "The $40\\%$ of receipts in the sample were for pizzas"
Population = "All the receipts from Friday nights"
Parameter = "The percentage of receipts from Friday nights that are for pizzas"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 43
Scenario = "A teacher is curious about how many students in their $40$ student class can solve a Rubik's Cube.  They randomly choose $10$ students and find that $3$ can solve a Rubik's Cube."

Sample = "The $10$ students the teacher chose"
Statistic = "The $30\\%$ of students in the sample can solve a Rubik's Cube"
Population = "All the students in the teacher's class"
Parameter = "The percentage of all the students in the teacher's class who can solve a Rubik's Cube"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 44
Scenario = "A scientist is studying the average lifespan of a particular species of snail. They collect $50$ snails and find the average lifespan to be $3$ years."

Sample = "The $50$ snails the scientist collected"
Statistic = "The average lifespan of $3$ years found in the sample of snails"
Population = "All the snails of that species"
Parameter = "The average lifespan of all the snails of that species"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 45
Scenario = "A baker wants to know how many of the $100$ chocolate chip cookies they baked have at least $20$ chocolate chips in them. They take $10$ cookies at random and count the chocolate chips in each cookie. They find that $5$ of the $10$ cookies have at least $20$ chocolate chips."

Sample = "The $10$ cookies that the baker selected"
Statistic = "The $50\\%$ of cookies in the sample have at least $20$ chocolate chips"
Population = "All the cookies that the baker made"
Parameter = "The percentage of cookies baked that have at least $20$ chocolate chips"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 46
Scenario = "A musician wants to know the average number of times people listen to their song per week. They ask $50$ people and find that they listen to their song an average of $3$ times per week."

Sample = "The $50$ people that the musician asked"
Statistic = "The average of $3$ listens per week found in the sample of people"
Population = "All the people who have listened to the musician's song"
Parameter = "The average number of times people listen to the musician's song per week"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 47
Scenario = "A pet store owner wants to know the average number of fish per tank in their store. They randomly select $10$ tanks and count the fish in each tank. They find an average of $12$ fish per tank."

Sample = "The $10$ tanks the owner selected"
Statistic = "The average of $12$ fish per tank found in the sample"
Population = "All the fish tanks in the store"
Parameter = "The average number of fish per tank in the store"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 48
Scenario = "A company wants to know what percentage of their employees are late to work. They randomly select $20$ employees and find that $2$ of them were late to work on a given day."

Sample = "The $20$ employees that the company selected"
Statistic = "The $10\\%$ of employees in the sample were late to work"
Population = "All the employees in the company"
Parameter = "The percentage of all employees in the company that are late to work"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 49
Scenario = "A gardener wants to know the average number of flowers on each sunflower in their garden. They randomly select $15$ sunflowers and count the number of flowers on each sunflower. They find an average of $35$ flowers per sunflower."

Sample = "The $15$ sunflowers that the gardener selected"
Statistic = "The average of $35$ flowers per sunflower found in the sample"
Population = "All the sunflowers in the garden"
Parameter = "The average number of flowers on each sunflower in the garden"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 50
Scenario = "A librarian wants to know the percentage of books in their library that are fiction. They randomly choose $100$ books from the shelves and note whether each book is fiction or nonfiction. They find that $60$ of the $100$ books are fiction."

Sample = "The $100$ books that the librarian selected"
Statistic = "The $60\\%$ of the books in the sample are fiction"
Population = "All the books in the library"
Parameter = "The percentage of books in the library that are fiction"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 51
Scenario = "A teacher wants to know what percentage of their students like math. They ask $25$ students if they like math, and $10$ of those students say they do."

Sample = "The $25$ students the teacher asked"
Statistic = "$40\\%$ ($10$ out of $25$) of the students in the sample like math"
Population = "All the students in the teacher's class"
Parameter = "The percentage of all students in the class who like math"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 52
Scenario = "A scientist wants to know the average size of all the leaves on a tree. They collect $30$ leaves from the tree and measure their area. The average area of the leaves in their sample is $10$ square centimeters."

Sample = "The $30$ leaves that the scientist collected"
Statistic = "The average area of $10$ square centimeters found in the sample of leaves"
Population = "All the leaves on the tree"
Parameter = "The average size of all the leaves on the tree"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 53
Scenario = "A pet store owner wants to know the average weight of all the hamsters in their store. They weigh $15$ hamsters at random and find an average weight of $0.2$ pounds."

Sample = "The $15$ hamsters that the owner weighed"
Statistic = "The average weight of $0.2$ pounds found in the sample of hamsters"
Population = "All the hamsters in the store"
Parameter = "The average weight of all the hamsters in the store"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 54
Scenario = "A farmer wants to estimate the average number of tomatoes on each plant in their greenhouse. They randomly select $10$ plants and count the tomatoes on each plant. They find an average of $28$ tomatoes per plant."

Sample = "The $10$ plants the farmer selected"
Statistic = "The average of $28$ tomatoes per plant found in the sample"
Population = "All the tomato plants in the greenhouse"
Parameter = "The average number of tomatoes on each plant in the greenhouse"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 55
Scenario = "A librarian wants to know what percentage of the available books in the library are overdue. They randomly choose $50$ books from the shelves and note whether each book is overdue. $10$ of the $50$ books are overdue."

Sample = "The $50$ books the librarian selected"
Statistic = "$20\\%$ of the books in the sample are overdue"
Population = "All the books in the library"
Parameter = "The percentage of books in the library that are overdue"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 56
Scenario = "A company wants to know what percentage of their customers use a particular app. They send out a survey to $1000$ customers and find that $650$ use the app."

Sample = "The $1000$ customers who received the survey"
Statistic = "$65\\%$ of the customers in the sample use the app"
Population = "All the company's customers"
Parameter = "The percentage of all customers who use the app"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 57
Scenario = "A scientist wants to know the average wingspan of all butterflies in a specific region. They catch and measure the wingspan of $25$ butterflies. They find an average wingspan of $2.5$ inches."

Sample = "The $25$ butterflies that the scientist measured"
Statistic = "The average wingspan of $2.5$ inches found in the sample of butterflies"
Population = "All the butterflies in the region"
Parameter = "The average wingspan of all the butterflies in the region"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 58
Scenario = "A teacher has $60$ students and wants to know the average number of times their students can jump rope in a minute. They have $15$ randomly selected students jump rope for a minute and count the number of jumps. The average jumps per minute in the sample is $75$ jumps."

Sample = "The $15$ students who participated in the jump rope test"
Statistic = "The average of $75$ jumps per minute found in the sample of students"
Population = "The $60$ students the teacher has in their classes"
Parameter = "The average number of jumps per minute that all students in the class can jump rope"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 59
Scenario = "A restaurant owner wants to know the average time customers spend eating their meal. They record the time $30$ customers spend eating at random. The average time in the sample is $45$ minutes."

Sample = "The $30$ customers whose eating times were recorded"
Statistic = "The average eating time of $45$ minutes found in the sample of customers"
Population = "All the customers who visit the restaurant"
Parameter = "The average time for all customers in the restaurant to eat their meal"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 60
Scenario = "A gardener wants to know what percentage of their rose bushes have at least one bloom. They check $10$ rose bushes and find that $6$ of them have at least one bloom."

Sample = "The $10$ rose bushes that the gardener checked"
Statistic = "$60\\%$ of the rose bushes in the sample have at least one bloom"
Population = "All the rose bushes in the garden"
Parameter = "The percentage of rose bushes in the garden with at least one bloom"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 61
Scenario = "A doctor wants to know the average height of all their patients. They measure the height of $40$ patients at random. They find an average height of $5$ feet $8$ inches."

Sample = "The $40$ patients whose height was measured"
Statistic = "The average height of $5$ feet $8$ inches found in the sample of patients"
Population = "All the doctor's patients"
Parameter = "The average height of all the doctor's patients"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 62
Scenario = "A store manager wants to know the average price of all the hats in their store. They randomly select $30$ hats and find an average price of $\\$25$."

Sample = "The $30$ hats that the manager selected"
Statistic = "The average price of $\\$25$ found in the sample of hats"
Population = "All the hats in the store"
Parameter = "The average price of all the hats in the store"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 63
Scenario = "A school has $400$ students. A teacher wants to estimate the percentage of the students have a driver's license. They ask $30$ random students and find that $18$ of them have a driver's license."

Sample = "The $30$ students that the teacher asked"
Statistic = "$60\\%$ of the students in the sample have a driver's license"
Population = "All the students in the school"
Parameter = "The percentage of all the students in the school who have a driver's license"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 64
Scenario = "A zookeeper wants to know the average weight of all $20$ of the giraffes in the giraffe enclosure. They weigh $5$ random giraffes and find an average weight of $1800$ pounds."

Sample = "The $5$ giraffes that the zookeeper weighed"
Statistic = "The average weight of $1800$ pounds found in the sample of giraffes"
Population = "All the giraffes in the enclosure"
Parameter = "The average weight of all the giraffes in the enclosure"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 65
Scenario = "A researcher wants to know the average number of pages in each book in a library. They randomly select $20$ books and count the pages in each book. They find an average of $300$ pages per book."

Sample = "The $20$ books that the researcher selected"
Statistic = "The average of $300$ pages per book found in the sample of books"
Population = "All the books in the library"
Parameter = "The average number of pages in each book in the library"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 66
Scenario = "A fruit stand owner wants to know what percentage of their bananas are bruised. They randomly select $30$ bananas and find that $5$ are bruised."

Sample = "The $30$ bananas that the owner selected"
Statistic = "$16.7\\%$ of the bananas in the sample are bruised"
Population = "All the bananas at the fruit stand"
Parameter = "The percentage of all bananas at the fruit stand that are bruised"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 67
Scenario = "A factory manager wants to know how many of their light bulbs have a lifespan longer than $1000$ hours. They test $50$ randomly selected light bulbs and find that $40$ have a lifespan longer than $1000$ hours." 

Sample = "The $50$ light bulbs that the manager tested"
Statistic = "$80\\%$ of the light bulbs in the sample have a lifespan longer than $1000$ hours"
Population = "All the light bulbs produced in the factory"
Parameter = "The percentage of all light bulbs produced in the factory that have a lifespan longer than $1000$ hours"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 68
Scenario = "A teacher wants to know how many of their students are left-handed. They check the class roster and find that $3$ out of $20$ students are left-handed."

Sample = "The class roster"
Statistic = "$15\\%$ of the students in the sample are left-handed"
Population = "All the students in the teacher's class"
Parameter = "The percentage of all the students in the class who are left-handed"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 69
Scenario = "A park ranger wants to know the average age of all the oak trees in a forest. They randomly select $20$ oak trees and find an average age of $100$ years."

Sample = "The $20$ oak trees that the ranger selected"
Statistic = "The average age of $100$ years found in the sample of oak trees"
Population = "All the oak trees in the forest"
Parameter = "The average age of all the oak trees in the forest"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 70
Scenario = "A researcher wants to know the average number of hours people spend exercising each day. They ask $150$ people about their exercise habits and find an average of $1$ hour per day."

Sample = "The $150$ people who participated in the survey"
Statistic = "The average of $1$ hour per day found in the sample of people"
Population = "All the people in the country"
Parameter = "The average number of hours per day that all people in the country spend exercising"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 71
Scenario = "A  restaurant owner wants to know the average amount of money customers spend on desserts. They check the receipts of $75$ customers and find an average spending of $\\$5$."

Sample = "The $75$ customers whose receipts were checked"
Statistic = "The average spending of $\\$5$ found in the sample of customers"
Population = "All the customers who eat at the restaurant"
Parameter = "The average amount of money that all customers spend on desserts at the restaurant"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 72
Scenario = "A teacher wants to know the average number of books read by each student over the summer. They ask $30$ students and find an average of $5$ books per student."

Sample = "The $30$ students the teacher asked"
Statistic = "The average of $5$ books per student found in the sample"
Population = "All the students in the teacher's class"
Parameter = "The average number of books read by each student in the teacher's class over the summer"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 73
Scenario = "A scientist randomly selected $18$ butterflies from her collection in order to estimate the average number of spots on the wings of butterflies in her collection. In this sample, she found an average of $12.5$ spots per butterfly."

Sample = "The $18$ butterflies that the scientist selected"
Statistic = "The average of $12.5$ spots per butterfly found in the sample"
Population = "All the butterflies in the scientist's collection"
Parameter = "The average number of spots on the wings of butterflies in the scientist's collection"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 74
Scenario = "A scientist randomly selected $18$ butterflies from her collection and found they had an average of $12.5$ spots per butterfly. Her goal was to estimate the average number of spots per butterfly in her collection."

Sample = "The $18$ butterflies that the scientist selected"
Statistic = "The average of $12.5$ spots per butterfly found in the sample"
Population = "All the butterflies in the scientist's collection"
Parameter = "The average number of spots on the wings of butterflies in the scientist's collection"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 75
Scenario = "A chef randomly selected $15$ recipes from a cookbook and found that $8$ of them included garlic. The chef wanted to estimate the proportion of all recipes in the cookbook that include garlic." 

Sample = "The $15$ recipes that the chef selected"
Statistic = "The $53.3\\%$ of recipes in the sample that include garlic"
Population = "All the recipes in the cookbook"
Parameter = "The proportion of all recipes in the cookbook that include garlic"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 76
Scenario = "A baker randomly selected $12$ cupcakes from their bakery and found that $5$ of them were lemon-flavored. Their goal was to estimate the percentage of all cupcakes in their bakery that are lemon-flavored."

Sample = "The $12$ cupcakes the baker selected"
Statistic = "The $41.7\\%$ of cupcakes in the sample that are lemon-flavored"
Population = "All the cupcakes in the bakery"
Parameter = "The percentage of all cupcakes in the bakery that are lemon-flavored"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 77
Scenario = "A dog groomer randomly selected $20$ dogs from their appointment schedule and found that $12$ of them were golden retrievers. They wanted to estimate the percentage of all dogs that come to their grooming salon who are golden retrievers."

Sample = "The $20$ dogs that the groomer selected"
Statistic = "The $60\\%$ of dogs in the sample that are golden retrievers"
Population = "All the dogs that come to the groomer's salon"
Parameter = "The percentage of all dogs that come to the groomer's salon who are golden retrievers"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 78
Scenario = "A librarian randomly selected $40$ books from the library's collection and found that $15$ of them were biographies. They wanted to estimate the proportion of all books in the library that are biographies." 

Sample = "The $40$ books that the librarian selected"
Statistic = "The $37.5\\%$ of books in the sample that are biographies"
Population = "All the books in the library"
Parameter = "The proportion of all books in the library that are biographies"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 79
Scenario = "A scientist randomly selected $50$ plants from a garden and found that $30$ of them had more than $5$ flowers. They wanted to estimate the proportion of all plants in the garden with more than $5$ flowers."

Sample = "The $50$ plants that the scientist selected"
Statistic = "The $60\\%$ of plants in the sample that have more than $5$ flowers"
Population = "All the plants in the garden"
Parameter = "The proportion of all plants in the garden that have more than $5$ flowers"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 80
Scenario = "A teacher randomly selected $25$ students from their class and found that $10$ of them had been to Disneyland. They wanted to estimate the percentage of all students in their class who have been to Disneyland."

Sample = "The $25$ students that the teacher selected"
Statistic = "The $40\\%$ of students in the sample who have been to Disneyland"
Population = "All the students in the teacher's class"
Parameter = "The percentage of all students in the teacher's class who have been to Disneyland"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 81
Scenario = "A  restaurant owner is interested in the average number of people in each party that visits their restaurant on a Friday night. They keep track of $20$ parties that come in on a Friday night and find an average of $3.2$ people per party."

Sample = "The $20$ parties that the owner observed"
Statistic = "The average of $3.2$ people per party found in the sample"
Population = "All the parties that visit the restaurant on a Friday night"
Parameter = "The average number of people in each party that visits the restaurant on a Friday night"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 82
Scenario = "A gardener is curious about the average height of all the tomato plants in their garden. They measure the height of $10$ randomly selected tomato plants and find an average height of $2$ feet."

Sample = "The $10$ tomato plants that the gardener measured"
Statistic = "The average height of $2$ feet found in the sample of tomato plants"
Population = "All the tomato plants in the garden"
Parameter = "The average height of all the tomato plants in the garden"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 83
Scenario = "A scientist wants to know what percentage of the seeds in a batch of $1000$ seeds are viable. They take $50$ of those seeds at random and plant them. They find that $45$ of those seeds germinate. " 

Sample = "The $50$ seeds that the scientist planted"
Statistic = "The $90\\%$ of seeds in the sample that germinated"
Population = "The $1000$ seeds in the batch"
Parameter = "The percentage of seeds in the batch that are viable"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 84
Scenario = "An artist wants to know what percentage of their paintings have sold in the last year.  They randomly select $10$ of the paintings they made in the last year and find that $4$ of them have been sold." 

Sample = "The $10$ paintings that the artist selected"
Statistic = "The $40\\%$ of paintings in the sample that have been sold"
Population = "All the paintings that the artist made in the last year"
Parameter = "The percentage of paintings made in the last year that have been sold"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 85
Scenario = "A musician wants to know the average number of hours that people spend listening to their music each day. They ask $50$ people how much time they spend listening to their music each day and find an average of $1.5$ hours."

Sample = "The $50$ people that the musician asked"
Statistic = "The average of $1.5$ hours per day found in the sample"
Population = "All the people who listen to the musician's music"
Parameter = "The average number of hours per day that all people spend listening to the musician's music"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 86
Scenario = "A baker is interested in the average number of cookies that people buy from their bakery each week. They keep track of $20$ customers over one week and find an average of $1.8$ cookies purchased per customer." 

Sample = "The $20$ customers that the baker observed"
Statistic = "The average of $1.8$ cookies per customer found in the sample"
Population = "All the customers of the bakery"
Parameter = "The average number of cookies that all customers buy from the bakery each week"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 87
Scenario = "A teacher wants to know what percentage of their students have visited a foreign country. They ask $10$ random students whether they have visited a foreign country and find that $7$ have." 

Sample = "The $10$ students that the teacher asked"
Statistic = "The $70\\%$ of students in the sample who have visited a foreign country"
Population = "All the students in the teacher's class"
Parameter = "The percentage of all students in the teacher's class who have visited a foreign country"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 88
Scenario = "A librarian is interested in the average number of pages in all the books in the library's children's section. They randomly select $15$ books from the children's section and find an average of $80$ pages per book." 

Sample = "The $15$ books that the librarian selected"
Statistic = "The average of $80$ pages per book found in the sample"
Population = "All the books in the library's children's section"
Parameter = "The average number of pages in all the books in the library's children's section"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 89
Scenario = "A scientist wants to know what percentage of the seeds in a batch of $100$ seeds will sprout. They plant $20$ of the seeds at random and find that $15$ of them sprout." 

Sample = "The $20$ seeds that the scientist planted"
Statistic = "The $75\\%$ of seeds in the sample that sprouted"
Population = "The $100$ seeds in the batch"
Parameter = "The percentage of seeds in the batch that will sprout"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 90
Scenario = "A gardener wants to know how many of their $50$ tomato plants have produced at least one ripe tomato. They randomly select $10$ tomato plants and find that $6$ of them have at least one ripe tomato."

Sample = "The $10$ tomato plants that the gardener selected"
Statistic = "The $60\\%$ of tomato plants in the sample that have produced at least one ripe tomato"
Population = "The $50$ tomato plants in the garden"
Parameter = "The percentage of tomato plants in the garden that have produced at least one ripe tomato"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 91
Scenario = "A scientist randomly selected $10$ trees from a forest and found that $3$ of them had signs of disease. The scientist wanted to estimate the percentage of all trees in the forest that had signs of disease." 

Sample = "The $10$ trees that the scientist selected"
Statistic = "The $30\\%$ of trees in the sample that had signs of disease"
Population = "All the trees in the forest"
Parameter = "The percentage of all trees in the forest that have signs of disease"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 92
Scenario = "A restaurant owner wants to know the average number of times people visit their restaurant each month. They track $50$ customers and find an average of $2.5$ visits per customer each month." 

Sample = "The $50$ customers that the owner tracked"
Statistic = "The average of $2.5$ visits per customer found in the sample"
Population = "All the customers who visit the restaurant"
Parameter = "The average number of times people visit the restaurant each month"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 93
Scenario = "A teacher wants to know what percentage of their students have seen a particular movie. They ask $20$ students if they have seen the movie, and $12$ of those students say they have."

Sample = "The $20$ students the teacher asked"
Statistic = "$60\\%$ of the students in the sample have seen the movie"
Population = "All the students in the teacher's class"
Parameter = "The percentage of all students in the class who have seen the movie"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 94
Scenario = "A scientist randomly selected $30$ fish from a lake and found that $10$ of them were trout. The scientist wanted to estimate the proportion of all fish in the lake that were trout."

Sample = "The $30$ fish that the scientist selected"
Statistic = "The $33.3\\%$ of fish in the sample that were trout"
Population = "All the fish in the lake"
Parameter = "The proportion of all fish in the lake that are trout"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 95
Scenario = "A restaurant owner wants to know the average number of minutes people spend waiting for a table. They record the wait times of $40$ customers and find an average wait time of $10$ minutes."

Sample = "The $40$ customers whose wait times were recorded"
Statistic = "The average wait time of $10$ minutes found in the sample of customers"
Population = "All the customers who visit the restaurant"
Parameter = "The average wait time for all customers in the restaurant"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 96
Scenario = "A baker is interested in the average number of chocolate chips in a cookie they bake. They take a sample of $5$ cookies and find an average of $18$ chocolate chips per cookie." 

Sample = "The $5$ cookies that the baker selected"
Statistic = "The average of $18$ chocolate chips per cookie found in the sample"
Population = "All the chocolate chip cookies the baker bakes"
Parameter = "The average number of chocolate chips in a cookie"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 97
Scenario = "A teacher wants to know what percentage of students in a school prefer to learn in a group setting. They ask $30$ random students if they prefer group work or individual work and find that $15$ prefer group work."

Sample = "The $30$ students the teacher asked"
Statistic = "$50\\%$ of the students in the sample prefer group work"
Population = "All the students in the school"
Parameter = "The percentage of all students in the school who prefer to learn in a group setting"

QM = rbind(QM, c(Scenario, Sample, Statistic,Population,Parameter))

# Scenario 98
Scenario = "A scientist wants to know the average number of seeds in an apple from Jaeschke's Orchard. They randomly select $12$ apples and count the seeds in each apple. They find an average of $8$ seeds per apple."

Sample = "The $12$ apples that the scientist selected"
Statistic = "The average of $8$ seeds per apple found in the sample"
Population = "All the apples at Jaeschke's Orchard"
Parameter = "The average number of seeds in an apple from Jaeschke's Orchard"
```

```{r selection,echo=F}
nopts = dim(QM)[1]
n = sample(1:nopts,1)
qq = QM[n,]
Scenario = qq[[1]]
po = sample(1:4) #print order of sample statistic population and parameter

sol1 = paste0(1*(1==po),collapse="")
sol2 = paste0(1*(2==po),collapse="")
sol3 = paste0(1*(3==po),collapse="")
sol4 = paste0(1*(4==po),collapse="")
```

Question
========

*S-IC.A.1: Understand statistics as a process for making inferences to be made about population parameters based on a random sample from that population.*

Below are some important definitions:

* Sample: A smaller group taken from the population.
* Sample Statistic: A number that describes the sample.
* Population: The entire group of interest.
* Population Parameter: A number that describes the entire population.

In Statistics, we learn a process for making inferences about population parameters based
on a random sample from that population. For a simple parameter, like an average or proportion, the sample statistic will be a best-guess estimate for the corresponding population parameter (for estimating the population's [standard deviation](https://en.wikipedia.org/wiki/Standard_deviation), we will use [Bessel's correction](https://en.wikipedia.org/wiki/Bessel%27s_correction) to find a best-guess estimate from the sample). Later, we will also learn how to express the amount of uncertainty in the estimation. (See [confidence interval](https://en.wikipedia.org/wiki/Confidence_interval) and [margin of error](https://en.wikipedia.org/wiki/Margin_of_error) to preview how we express uncertainty about the population parameter.)

For now, let's practice identifying the sample, statistic, population, and parameter.

### Scenario

`r Scenario`

The four concepts are described in random order below.

a. `r qq[[po[1]+1]]`
b. `r qq[[po[2]+1]]`
c. `r qq[[po[3]+1]]`
d. `r qq[[po[4]+1]]`

Match the concept to the description.

1. Sample = ##ANSWER1##
2. Statistic = ##ANSWER2##
3. Population = ##ANSWER3##
4. Parameter = ##ANSWER4##

Answerlist
--------

* a
* b
* c
* d
* a
* b
* c
* d
* a
* b
* c
* d
* a
* b
* c
* d


Solution
========

* Sample = `r letters[1:4][po==1]` = `r qq[[2]]`
* Sample Statistic = `r letters[1:4][po==2]` = `r qq[[3]]`
* Population = `r letters[1:4][po==3]` = `r qq[[4]]`
* Population Parameter = `r letters[1:4][po==4]` = `r qq[[5]]`


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: sam_stat_pop_prop