```{r,echo=F}
while(T){
  ang = round(runif(1,pi/7,1.3),2)
  hyp = round(runif(1,12,99),0)
  adj = cos(ang)*hyp
  adj2 = round(adj,0)
  ang2 = round(acos(adj/hyp),2)
  angt = sprintf("%.2f",ang2)
  hypt = sprintf("%.0f",round(hyp,0))
  adjt = sprintf("%.0f",round(adj2,0))
  if(hyp-adj2>2 && adj2>10 && round((pi/2-ang)*hyp)!=adj2 && hyp!=round(adj2*ang) && round(adj2/hyp)!=ang2 && ang2 != round(1/cos(adj2/hyp),2)){break}
}
```

Question
========

A right triangle has an angle measure $\theta$. The adjacent leg's length is `r adj2` meters, and the hypotenuse's length is `r hypt` meters. What is the angle measure $\theta$ in radians?

```{r,fig.dim=c(5,5),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",axes=F,ann=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
th = seq(0,pi/2,length.out=100)
lines(cos(th),sin(th),lty=2,col="grey")
lines(c(0,cos(ang),cos(ang),0),c(0,0,sin(ang),0),lwd=3)
lines(c(cos(ang)-0.02,cos(ang)-0.02,cos(ang)),c(0,0.02,0.02))
th2 = seq(0,ang,length.out=100)
#lines(cos(th2),sin(th2),lty=2,col=rgb(1,0.8,0.8))
#text(1.07*cos(ang/2),1.07*sin(ang/2),paste0(angt,"*",hypt),col=rgb(1,0.8,0.8),cex=0.7)
lines(c(0,cos(ang)),c(0,0),col="purple",lwd=4)
text(cos(ang)/2,-0.05,paste0(adj2," m"),col="purple",cex=0.8)
lines(c(0,cos(ang)),c(0,sin(ang)),col="blue",lwd=4)
text(cos(ang)/2+0.05*cos(ang+pi/2),
     sin(ang)/2+0.05*sin(ang+pi/2),
     paste0(hypt," m"),srt=ang/pi*180,col="blue",cex=0.8)
lines(0.1*cos(th2),0.1*sin(th2),col="red")
text(0.16*cos(ang/2),0.16*sin(ang/2),TeX("$\\theta$"),col="red",cex=0.8)
```
\

Please round your answer to the nearest hundredth of a radian.


Solution
========

First, identify the correct trigonometric function. Remember, [SOHCAHTOA](https://en.wikipedia.org/wiki/Mnemonics_in_trigonometry).

$$\sin(\theta)=\frac{\mathrm{opposite}}{\mathrm{hypotenuse}}$$


$$\cos(\theta)=\frac{\mathrm{adjacent}}{\mathrm{hypotenuse}}$$


$$\tan(\theta)=\frac{\mathrm{opposite}}{\mathrm{adjacent}}$$

In this case, we are given the **adjacent** and the **hypotenuse**, and we are asked for the angle measure. The trigonometric ratio that relates these two sides is [cosine](https://en.wikipedia.org/wiki/Trigonometric_functions). Use $\theta$ to represent the requested angle measure.

$$\cos(\theta) = \frac{`r adj2`}{`r hypt`}$$

To evaluate $\theta$, we need to use the [inverse of cosine](https://en.wikipedia.org/wiki/Inverse_trigonometric_functions). This inverse function has a few names: arccos, acos, or $\cos^{-1}$ are the most commonly used.

$$\theta = \arccos\left(\frac{`r adj2`}{`r hypt`}\right)$$

$$\theta = \cos^{-1}\left(\frac{`r adj2`}{`r hypt`}\right)$$

Depending on your calculator, you might type something like ``round(arccos(`r adj2`/`r hypt`),2)``

$$\theta \approx `r ang2`$$

Meta-information
============
extype: num
exsolution: `r ang2`
exname: cos_get_ang