---
output: 
  pdf_document:
    extra_dependencies: ["fancyhdr","multicol"]
fontsize: 12pt
params:
  num: "1234"
  mytitle: "PC 029 NO-CALC Mastery"
  showsol: True
geometry: "left=3cm,right=3cm,top=3cm,bottom=3cm"
---

```{r,echo=F}
library(latex2exp)

set.seed(as.numeric(params$num))
showsol = params$showsol

fixer = function(exp){
  exp = gsub("--","+",exp,fixed=T)
  return(exp)
}

makegrid = function(){
  plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
  for(i in c(-5,5)){
    lines(c(i,i),c(-10,10),col="darkgrey")
    lines(c(-10,10),c(i,i),col="darkgrey")
  }
  for(i in -10:10){
    for(j in seq(-9.9,9.9,0.1)){
      if(j%%1!=0 && i!=0 && abs(i)!=5){
        points(i,j,col="grey",pch=19,cex=0.01)
        points(j,i,col="grey",pch=19,cex=0.01)
      }
      if(j%%1<0.05 && i!=0){
        points(i,j,col="black",pch=19,cex=0.01)
        points(j,i,col="black",pch=19,cex=0.01)
      }
    }
    
  }
  arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
  arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
}

aa = numeric()
bb = numeric()
hh = numeric()
kk = numeric()
eh = numeric()
hv = numeric()
eqs = character()
x1s = list()
y1s = list()
x2s = list()
y2s = list()
th = seq(0,2*pi,length.out=1000)
eps = 0.00001
th1 = seq(-pi/2+eps,pi/2-eps,length.out=1000)
th2 = seq(pi/2+eps,3*pi/2-eps,length.out=1000)
th3 = seq(eps,pi-eps,length.out=1000)
th4 = seq(pi+eps,2*pi-eps,length.out=1000)

while(T){
  hkab = sample(1:8,4)
  h = hkab[1]*sample(c(-1,1),1)
  k = hkab[2]*sample(c(-1,1),1)
  a = hkab[3]
  b = hkab[4]
  if(abs(h)+a<10 && abs(k)+b<10 && a>1 && b>1){break}
}
aa = c(aa,a)
bb = c(bb,b)
hh = c(hh,h)
kk = c(kk,k)
eh = c(eh,1)
hv = c(hv,0)
eqs = c(eqs,fixer(paste0("\\frac{(x-",h,")^2}{",a^2,"}+\\frac{(y-",k,")^2}{",b^2,"}=1",collapse="")))
x1s[[1]] = h+a*cos(th)
y1s[[1]] = k+b*sin(th)
x2s[[1]] = numeric()
y2s[[1]] = numeric()

while(T){
  hkab = sample(1:8,4)
  h = hkab[1]*sample(c(-1,1),1)
  k = hkab[2]*sample(c(-1,1),1)
  a = hkab[3]
  b = hkab[4]
  c = sqrt(a^2+b^2)
  ishor = sample(c(T,F),1)
  if(ishor){
    maxx = abs(h)+c
    maxy = abs(k)+b
    hvhv = 1
  } else {
    maxx = abs(h)+a
    maxy = abs(k)+c
    hvhv = 2
  }
  if(maxx<10 && maxy<10 && a>1 && b>1){break}
}
aa = c(aa,a)
bb = c(bb,b)
hh = c(hh,h)
kk = c(kk,k)
eh = c(eh,2)
hv = c(hv,hvhv)
if(hvhv==1){
  eqs = c(eqs,fixer(paste0("\\frac{(x-",h,")^2}{",a^2,"}-\\frac{(y-",k,")^2}{",b^2,"}=1",collapse="")))
  x1s[[2]] = h+a/cos(th1)
  y1s[[2]] = k+b*tan(th1)
  x2s[[2]] = h+a/cos(th2)
  y2s[[2]] = k+b*tan(th2)
} else {
  eqs = c(eqs,fixer(paste0("-\\frac{(x-",h,")^2}{",a^2,"}+\\frac{(y-",k,")^2}{",b^2,"}=1",collapse="")))
  x1s[[2]] = h+a*tan(th1)
  y1s[[2]] = k+b/cos(th1)
  x2s[[2]] = h+a*tan(th2)
  y2s[[2]] = k+b/cos(th2)
}


while(T){
  hkab = sample(1:8,4)
  h = hkab[1]*sample(c(-1,1),1)
  k = hkab[2]*sample(c(-1,1),1)
  a = hkab[3]
  b = hkab[4]
  if(abs(h)+a<10 && abs(k)+b<10 && a>1 && b>1){break}
}
aa = c(aa,a)
bb = c(bb,b)
hh = c(hh,h)
kk = c(kk,k)
eh = c(eh,1)
hv = c(hv,0)
eqs = c(eqs,fixer(paste0("\\frac{(x-",h,")^2}{",a^2,"}+\\frac{(y-",k,")^2}{",b^2,"}=1",collapse="")))
x1s[[3]] = h+a*cos(th)
y1s[[3]] = k+b*sin(th)
x2s[[3]] = numeric()
y2s[[3]] = numeric()

while(T){
  hkab = sample(1:8,4)
  h = hkab[1]*sample(c(-1,1),1)
  k = hkab[2]*sample(c(-1,1),1)
  a = hkab[3]
  b = hkab[4]
  c = sqrt(a^2+b^2)
  ishor = sample(c(T,F),1)
  if(ishor){
    maxx = abs(h)+c
    maxy = abs(k)+b
    hvhv = 1
  } else {
    maxx = abs(h)+a
    maxy = abs(k)+c
    hvhv = 2
  }
  if(maxx<10 && maxy<10 && a>1 && b>1){break}
}
aa = c(aa,a)
bb = c(bb,b)
hh = c(hh,h)
kk = c(kk,k)
eh = c(eh,2)
hv = c(hv,hvhv)
if(hvhv==1){
  eqs = c(eqs,fixer(paste0("\\frac{(x-",h,")^2}{",a^2,"}-\\frac{(y-",k,")^2}{",b^2,"}=1",collapse="")))
  x1s[[4]] = h+a/cos(th1)
  y1s[[4]] = k+b*tan(th1)
  x2s[[4]] = h+a/cos(th2)
  y2s[[4]] = k+b*tan(th2)
} else {
  eqs = c(eqs,fixer(paste0("-\\frac{(x-",h,")^2}{",a^2,"}+\\frac{(y-",k,")^2}{",b^2,"}=1",collapse="")))
  x1s[[4]] = h+a*tan(th1)
  y1s[[4]] = k+b/cos(th1)
  x2s[[4]] = h+a*tan(th2)
  y2s[[4]] = k+b/cos(th2)
}

ord = c(sample(c(1,2)),sample(c(3,4)))

if(showsol){
  soltxt = "SOL"
} else {
  soltxt = ""
}

```

\setlength{\headheight}{18.0pt}
\fancyhead[L]{\sc{`r params$mytitle` v`r params$num` `r soltxt`}}
\fancyhead[R]{\bf \large Name:\hspace{2in}}
\fancyfoot[R]{\sc Page \thepage ~ of 2}
\fancyfoot[C]{}
\pagestyle{fancy}


## Question 1

Please write the equation of the conic section graphed below. You can assume all vertices and co-vertices are on integer gridpoints.

```{r,echo=F,fig.dim=c(7,3.5)}
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
makegrid()
w = ord[1]
a = aa[w]
b = bb[w]
h = hh[w]
k = kk[w]
if(eh[w]==2){
  lines(c(h-a,h-a,h+a,h+a,h-a),c(k-b,k+b,k+b,k-b,k-b),col="darkgreen",lty=1)
  m = b/a
  xxx = c(-11,11)
  yyy = m*(xxx-h)+k
  lines(xxx,yyy,col="red",lty=1,lwd=1)
  m = -b/a
  xxx = c(-11,11)
  yyy = m*(xxx-h)+k
  lines(xxx,yyy,col="red",lty=1,lwd=1)
}
x = x1s[[w]]
y = y1s[[w]]
lines(x,y,lwd=2,col="blue")
x = x2s[[w]]
y = y2s[[w]]
lines(x,y,lwd=2,col="blue")
plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
if(showsol){
  text(0,0,TeX(paste0("$",eqs[w],"$",collapse="")))
}
```
\


## Question 2

Please write the equation of the conic section graphed below. You can assume all vertices and co-vertices are on integer gridpoints.

```{r,echo=F,fig.dim=c(7,3.5)}
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
makegrid()
w = ord[2]
a = aa[w]
b = bb[w]
h = hh[w]
k = kk[w]
if(eh[w]==2){
  lines(c(h-a,h-a,h+a,h+a,h-a),c(k-b,k+b,k+b,k-b,k-b),col="darkgreen",lty=1)
  m = b/a
  xxx = c(-11,11)
  yyy = m*(xxx-h)+k
  lines(xxx,yyy,col="red",lty=1,lwd=1)
  m = -b/a
  xxx = c(-11,11)
  yyy = m*(xxx-h)+k
  lines(xxx,yyy,col="red",lty=1,lwd=1)
}
x = x1s[[w]]
y = y1s[[w]]
lines(x,y,lwd=2,col="blue")
x = x2s[[w]]
y = y2s[[w]]
lines(x,y,lwd=2,col="blue")

plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
if(showsol){
  text(0,0,TeX(paste0("$",eqs[w],"$",collapse="")))
}
```
\

\newpage

## Question 3

Graph the conic section represented by the equation. For a hyperbola, please include the central rectangle and the asymptotes.

```{r,echo=F,fig.dim=c(7,3.5)}
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
makegrid()
w = ord[3]
if(showsol){
  th = seq(0,2*pi,length.out=1000)
  a = aa[w]
  b = bb[w]
  h = hh[w]
  k = kk[w]
  if(eh[w]==2){
    lines(c(h-a,h-a,h+a,h+a,h-a),c(k-b,k+b,k+b,k-b,k-b),col="darkgreen",lty=1)
    m = b/a
    xxx = c(-11,11)
    yyy = m*(xxx-h)+k
    lines(xxx,yyy,col="red",lty=1,lwd=1)
    m = -b/a
    xxx = c(-11,11)
    yyy = m*(xxx-h)+k
    lines(xxx,yyy,col="red",lty=1,lwd=1)
  }
  x = x1s[[w]]
  y = y1s[[w]]
  lines(x,y,lwd=2,col="blue")
  x = x2s[[w]]
  y = y2s[[w]]
  lines(x,y,lwd=2,col="blue")
  
}

plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
text(0,0,TeX(paste0("$",eqs[w],"$",collapse="")))
```
\


## Question 4

Graph the conic section represented by the equation. For a hyperbola, please include the central rectangle and the asymptotes.

```{r,echo=F,fig.dim=c(7,3.5)}
par(mar=c(0,0,0,0),pty="s",mfrow=c(1,2))
makegrid()
w = ord[4]
if(showsol){
  th = seq(0,2*pi,length.out=1000)
  a = aa[w]
  b = bb[w]
  h = hh[w]
  k = kk[w]
  if(eh[w]==2){
    lines(c(h-a,h-a,h+a,h+a,h-a),c(k-b,k+b,k+b,k-b,k-b),col="darkgreen",lty=1)
    m = b/a
    xxx = c(-11,11)
    yyy = m*(xxx-h)+k
    lines(xxx,yyy,col="red",lty=1,lwd=1)
    m = -b/a
    xxx = c(-11,11)
    yyy = m*(xxx-h)+k
    lines(xxx,yyy,col="red",lty=1,lwd=1)
  }
  x = x1s[[w]]
  y = y1s[[w]]
  lines(x,y,lwd=2,col="blue")
  x = x2s[[w]]
  y = y2s[[w]]
  lines(x,y,lwd=2,col="blue")
  
}

plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
text(0,0,TeX(paste0("$",eqs[w],"$",collapse="")))
```
\

