---
title: "Instantaneous Slope Writeup"
author: "Due 2023 Oct 11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Slope of a secant line

A secant line connects two points along a function. The slope is called the average rate of change. A function $f$ over an interval $[x_a,x_b]$ has an average rate of change equal to the quotient of rise over run.
$$\text{averate rate of change} = \frac{f(x_b)-f(x_a)}{x_b-x_a}$$

Let's say a ball's height $h$ in meters is a function of time $t$ in seconds. It is dropped from a tower 100 meters tall, so it's position is approximately quadratic in time during the free fall.

$$h(t) = 100-10t^2$$

1. Find the average rate of change between $t_a=1$ and $t_b=2$. *Please give appropriate units and explain its meaning in context.*

\vfill


## "Instantaneous" rate of change

Another way to write the average-rate-of-change formula uses $\Delta x = x_b - x_a$.

$$\text{AROC} = \frac{f(x_a+\Delta x)~-~f(x_a)}{\Delta x} $$

2. Going back to the falling ball, with $h(t)=100-10t^2$, find the average rate of change when $t_a=2$ and $\Delta t = 0.01$. *Please give appropriate units and explain its meaning in context.*

\vfill



\newpage

## Desmos

On Desmos graphing calculator, enter the following expressions.

$$h(t) = 100-10t^2$$

$$t_a = 2$$

$$D=0.01$$

$$m=\frac{h(t_a+D)-h(t_a)}{D}$$

$$y=m\cdot(t-t_a)+h(t_a)$$

Fill out the table:

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

\huge
```{r tabf, results="asis", echo=F}
a = seq(0,3,0.5)
b = rep("            ",length(a))
f = data.frame(a,b)
colnames(f) = c("$t_a$","$m$ (an instantaneous rate of change)")
knitr::kable(f, align = "cc",row.names=F)
```

\normalsize

3. Summarize the results. *Please give appropriate units and explain the results in context.*



