```{r,echo=F}
while(T){
    x1 = round(runif(8,0,1),2)
    y1 = round(runif(8,0,1),2)
    hs = runif(8)
    x = c(-x1,-x1,x1,x1)
    y = c(-y1,y1,-y1,y1)
    h = c(hs,hs,hs,hs)
    r = round(runif(1,2,3),1)
    th1 = round(sample(0:3,1)*pi/2+runif(1,pi/12,pi/2-pi/12),2)
    th2 = th1+pi/2
    
    rn = sample(1:length(x),1)
    x0 = x[rn]
    y0 = y[rn]
    Dx = round(r*cos(th1),2)
    Dy = round(r*sin(th1),2)
    x1 = round(x0+Dx,2)
    y1 = round(y0+Dy,2)
    hrn = h[rn]
    
    alsol = function(ans,n=5,dx=1){
        choices = ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx
        al = paste0("* ",choices,collapse="\n")
        sol = paste0(1*(ans==choices),collapse="")
        blah = 1*(ans==choices)
        return(data.frame(al,sol))
    }
    
    fx = alsol(x1,4,0.03)
    fy = alsol(y1,4,0.03)
    if(Dx>0.05 && Dy>0.05){break}
}



```

Question
========

A p1 wallpaper was made by using repeated translations. I have depicted the translation of point $(`r x0`, `r y0`)$ in the direction $\theta=`r th1`$ (radians) by a distance of $r=`r r`$. 

```{r,echo=F,fig.dim=c(8,8)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",axes=F,ann=F,xlim=c(-4,4),ylim=c(-4,4))
for(i in -8:8){
    for(j in -8:8){
        dx = i*r*cos(th1)+j*r*cos(th2)
        dy = i*r*sin(th1)+j*r*sin(th2)
        points(x+dx,y+dy,col=hsv(h,0.7,1,0.2),pch=19)
    }
}
points(x,y,col=hsv(h,0.7,1,1),pch=19)

points(x1,y1,col=hsv(hrn,0.7,1,1),pch=19)
arrows(x0,y0,x1,y1)
```
\


What are the coordinates of the point at the end of the arrow (the result of the translation)?

* The horizontal coordinate, $x'=$ ##ANSWER1##
* The vertical coordinate, $y'=$ ##ANSWER2##

Answerlist
--------

`r fx$al`
`r fy$al`

Solution
--------

To find the changes of translation, we can use trigonometry.

$$\Delta x = r\cdot \cos(\theta)$$
$$\Delta y = r\cdot \sin(\theta)$$

Let's evaluate those changes.

$$\Delta x ~=~ (`r r`)\cos(`r th1`) ~=~ `r round(Dx,2)`$$
$$\Delta y ~=~ (`r r`)\sin(`r th1`) ~=~ `r round(Dy,2)`$$

We can then add these changes to the original point.

```{r,echo=F}
if(Dx<0){
    st1 = paste0(x0,"-",abs(Dx),collapse="") 
} else {
    st1 = paste0(x0,"+",abs(Dx),collapse="") 
}
if(Dy<0){
    st2 = paste0(y0,"-",abs(Dy),collapse="") 
} else {
    st2 = paste0(y0,"+",abs(Dy),collapse="") 
}

```

$$x' ~=~ `r st1` ~=~ `r x1`$$
$$y' ~=~ `r st2` ~=~ `r y1`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r fx$sol`|`r fy$sol`
exname: translate_point