```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
a = sample(c(-1,1),1)
picks = sample(1:6,2)
h = picks[1]*sample(c(-1,1),1)
k = picks[2]*sample(c(-1,1),1)
poses = list(c(1,1,1),
             c(1,1,-1),
             c(1,-1,1),
             c(1,-1,-1),
             c(-1,1,1),
             c(-1,1,-1),
             c(-1,-1,1),
             c(-1,-1,-1))
sels = sample(c(1,sample(2:length(poses),3)))
ans = paste0((sels==c(1,1,1))*1,collapse="")

if(h<0){hor="left"}else{hor="right"}
if(k<0){ver="down"}else{ver="up"}
if(a<0){
  coef="points down"
  symb="<"
}else{
  coef="points up"
  symb=">"
}

cn = gregexpr(pattern ='1',ans)
```

Question
========

```{python, echo=FALSE}
from sympy import *
x, y = symbols("x y")
eq1 = int(r.a)*abs(x-int(r.h))+int(r.k)
leq1 = latex(eq1)
```

Which plot matches the function:

$$y = `r py$leq1`$$

```{r,fig.dim = c(8, 8),echo=FALSE}
par(mfrow = c(2, 2),pty="s")
x = seq(-11,11,0.1)
for(i in 1:length(sels)){
  ind = sels[i]
  a2 = a*poses[[ind]][1]
  h2 = h*poses[[ind]][2]
  k2 = k*poses[[ind]][3]
  plot(x,a2*abs(x-h2)+k2,ylim=c(-10,10),xlim=c(-10,10),lwd=3,type="l",
       asp=1,ylab="y",xlab="x",main=paste0("Plot ",i,collapse=""))
  abline(h=0)
  abline(v=0)
  for(i in -10:10){
    for(j in seq(-10,10,0.2)){
      points(i,j,cex=0.03,pch=20)
      points(j,i,cex=0.03,pch=20)
    }
  }
}
```
\

Answerlist
--------

* Plot 1
* Plot 2
* Plot 3
* Plot 4

Solution
========

The parent function is $y=|x|$, which has a vertex at the origin.

The general parameterization is $y=a\left|x-h\right|+k$. The vertex shifts to $(h,k)$. The multiplicative factor, $a$, causes a vertical stretch and/or a vertical flip. 

In this example, $a=`r a`$ and $h=`r h`$ and $k=`r k`$.

To get the correct daughter graph, translate the parent `r abs(h)` units `r hor` and `r abs(k)` units `r ver`. Since $a`r symb`0$, the daughter `r coef`. 

The correct plot is Plot `r cn`.


```{r,fig.dim = c(5, 5),echo=FALSE}
par(pty="s")
x = seq(-11,11,0.1)
for(i in cn){
  ind = sels[i]
  a2 = a*poses[[ind]][1]
  h2 = h*poses[[ind]][2]
  k2 = k*poses[[ind]][3]
  plot(x,a2*abs(x-h2)+k2,ylim=c(-10,10),xlim=c(-10,10),lwd=3,type="l",
       asp=1,ylab="y",xlab="x",main=paste0("Plot ",i,collapse=""))
  abline(h=0)
  abline(v=0)
  for(i in -10:10){
    for(j in seq(-10,10,0.2)){
      points(i,j,cex=0.03,pch=20)
      points(j,i,cex=0.03,pch=20)
    }
  }
}
```
\

$$y = `r py$leq1`$$


Meta-information
============
extype: schoice
exsolution: `r ans`
exname: graph_translations_and_reflections_abs_function