```{r data generation, echo = FALSE, results = "hide"}
xc = sample(2:8,1)
ys = sample(2:8,5)
al = 0:10
ans1 = paste0(1*(al==ys[3]),collapse="")
ans2 = paste0(1*(al==ys[2]),collapse="")
ans3 = paste0(1*(al==ys[4]),collapse="")
altex = paste0("* ",al,"\n",collapse="")
```

Question
========

This question asks you to find [one-sided limits](https://en.wikipedia.org/wiki/One-sided_limit){target="_blank"}.


```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
library(latex2exp)
par(pty="s")
plot(0,0,type="n",xlim=c(0,10),ylim=c(0,10),ylab=TeX("$f(x)$"),xlab=TeX("$x$"))
for(j in seq(0,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
big = 1.3
sma = 1
lines(c(0,xc),ys[1:2],lwd=4,col="blue")
points(xc,ys[2],pch=19,col="blue",cex=big)
points(xc,ys[2],pch=19,col="white",cex=sma)
points(xc,ys[3],pch=19,col="blue",cex=big)
lines(c(xc,10),ys[4:5],lwd=4,col="blue")
points(xc,ys[4],pch=19,col="blue",cex=big)
points(xc,ys[4],pch=19,col="white",cex=sma)
```
\

* Find $f(`r xc`)$: ##ANSWER1##
* Find $\lim\limits_{x\to`r xc`^{-}}f(x)$: ##ANSWER2##
* Find $\lim\limits_{x\to`r xc`^{+}}f(x)$: ##ANSWER3##

Answerlist
--------
`r altex`
`r altex`
`r altex`


Solution
========

To find $f(`r xc`)$, you put your pencil at the origin, then move right until $x=`r xc`$. Then, you go up until you hit the function (the solid dot in this case). Find the vertical coordinate of that spot. $f(`r xc`)=`r ys[3]`$.

To find the limit as $x$ approaches $`r xc`$ from the left, imagine walking along the curve from left to right. Just before $x=`r xc`$, it seems the path is heading to a vertical coordinate of `r ys[2]`. So, $\lim\limits_{x\to`r xc`^{-}}f(x) = `r ys[2]`$. 

To find the limit as $x$ approaches $`r xc`$ from the right, imagine walking along the curve from right to left Just before $x=`r xc`$, it seems the path is heading to a vertical coordinate of `r ys[4]`. So, $\lim\limits_{x\to`r xc`^{+}}f(x) = `r ys[4]`$. 

(Just FYI:) Since the limit from the left does not equal the limit from the right, the overall limit does not exist.

$$\lim\limits_{x\to`r xc`^{-}}f(x) \ne \lim\limits_{x\to`r xc`^{+}}f(x) ~~~~ \to ~~~~ \lim\limits_{x\to`r xc`}f(x)=\text{DNE}$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`
exname: graph_limits