```{r data generation, echo = FALSE, results = "hide"}
rands = sample(1:9,8)
x = sort(c(0,rands[1:3],10))
y = rands[4:8]
xs = sort(sample(x,2))
x1 = xs[1]
x2 = xs[2]
y1 = y[x==x1]
y2 = y[x==x2]
m = (y2-y1)/(x2-x1)
```



Question
========

This question is about [average rate of change](https://en.wikipedia.org/wiki/Rate_(mathematics)#Of_change){target="_blank"}. For function $f(x)$, its average rate of change between $x=a$ and $x=b$ equals a quotient of differences:
$$\text{ave rate of change} = \frac{f(b)-f(a)}{b-a} $$

A function $f$ is graphed below.

```{r,fig.dim=c(5,5),echo=FALSE}
par(pty="s")
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="f(x)",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
```
\

* Find the average rate of change between $x=`r x1`$ and $x=`r x2`$.

*You can round to the nearest hundredth.*

Solution
========

```{r,fig.dim=c(5,5),echo=FALSE}
par(pty="s")
plot(x,y,type="n",xlim=c(0,10),ylim=c(0,10),xlab="x",ylab="f(x)",asp=1,pch=20,cex=2)
for(i in 0:10){
  abline(h=i,lty=3)
  abline(v=i,lty=3)
}
dify=0
xspline(x,y,shape=c(0,rep(-0.3,length(x)-2),0),border="blue",lwd=4)
points(x1,y1,pch=20,cex=2,col="black")
points(x2,y2,pch=20,cex=2,col="black")
xx = 0:10
lines(xx,m*(xx-x1)+y1,lwd=2,col="red")
lines(c(x1,x2),c(y1,y1),lwd=2,col="violet")
lines(c(x2,x2),c(y1,y2),lwd=2,col="orange")
```
\


$$f(`r x1`)=`r y1`$$

$$f(`r x2`)=`r y2`$$

$$\text{ave rate of change} = \frac{f(`r x2`)-f(`r x1`)}{`r x2`-`r x1`} = \frac{`r y2`-`r y1`}{`r x2`-`r x1`} = \frac{`r y2-y1`}{`r x2-x1`} = `r round(m,2)` $$

Notice the orange segment has length of `r abs(y2-y1)` and the violet segment has length of `r abs(x2-x1)`. The formula for average rate of change is "rise over run".

Meta-information
============
extype: num
exsolution: `r m`
exname: ave_rate_of_change_from_graph
extol: 0.01