```{r data generation, echo = FALSE, results = "hide"}

hk = sample(1:6,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]

f = paste0("\\log_2(x+",-h,")+",k,collapse="")
f = gsub("+-","-",f,fixed=T)

a1 = "No."
a2 = paste0("Yes, at x=",h,".",collapse="")

ach = character()
for(i in c("x","y")){
    for(j in sort(c(-h,-k,h,k))){
        ach = c(ach,paste0("Yes, at ",i,"=",j,".",collapse=""))
    }
}
ach = c(ach,"No.")
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==a1),collapse="")
sol2 = paste0(1*(ach==a2),collapse="")

```

Question
========

Consider the curve represented by the equation below:

$$y~=~`r f`$$

Does the curve $y=`r f`$ have a horizontal [asymptote](https://en.wikipedia.org/wiki/Asymptote)?

##ANSWER1##

Does the curve $y=`r f`$ have a vertical [asymptote](https://en.wikipedia.org/wiki/Asymptote)?

##ANSWER2##

Answerlist
--------

`r al`
`r al`

Solution
========

The vertical asymptote is shown below as a red dashed line. The blue curve represents $y=`r f`$.

```{r,echo=F,fig.dim=c(5,5),warning=F}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

x = seq(-10,10,0.00001)
y = log(x-h)/log(2)+k
x2 = x[!is.na(y)]
y2 = y[!is.na(y)]
x = x2[abs(y2)<=10]
y = y2[abs(y2)<=10]
breaks = c(0,which(abs(diff(y))>10),length(x))
for(j in 1:(length(breaks)-1)){
    suppressWarnings(lines(x[(breaks[j]+1):(breaks[j+1]-1)],y[(breaks[j]+1):(breaks[j+1]-1)],type="l",lwd=4,col="blue"))
}

abline(v=h,col="red",lty=2,lwd=2)

```
\

Notice, the parent function, $y=\log_2(x)$, has a vertical asymptote at $x=0$. When we shift the points left or right, the vertical asymptote also shifts left or right.

Also, kind of strange, but a vertical line is indicated by $x$ equaling a constant.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: asymp_log