---
output: slidy_presentation
---


# Agenda

* Entrance ticket: [ET_0930](https://bart.instructure.com/courses/2110/quizzes/3204)
* Slides: Asymptotes in parent functions and shifts
* [OCW_0930_asymptote_shift](https://bart.instructure.com/courses/2110/quizzes/3205)
* [PCW_0930](PCW_0930: EQs from shifts)



# Asymptotes in parent functions

* An [asymptote](https://en.wikipedia.org/wiki/Asymptote) of a curve is a straight line such that the distance between the curve and the line approaches zero as one or both of the $x$ or $y$ coordinates tends to infinity.
* Examples:
    * Exponential parent function, $y=2^x$, has a horizontal asymptote $y=0$, which is approached as $x\to -\infty$.\
```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-10,10,0.1)
y = 2^x
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(x2,y2,lwd=5,col="blue")
abline(h=0,col="red",lty=2,lwd=4)
text(10,-0.5,"x")
text(-0.5,10,"y")
```
\
* Logarithmic parent function, $y=\log_2(x)$, has a vertical asymptote $x=0$, which is approached as $y\to -\infty$.\
```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-10,10,0.1)
y = 2^x
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(y2,x2,lwd=5,col="blue")
abline(v=0,col="red",lty=2,lwd=4)
text(10,-0.5,"x")
text(-0.5,10,"y")
```
\
* Reciprocal parent function, $y=\frac{1}{x}$, has two asymptotes at $y=0$ and $x=0$.\
```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-10,-0.001,0.001)
y = 1/x
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(x2,y2,lwd=5,col="blue")
x = seq(0.001,10,0.001)
y = 1/x
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(x2,y2,lwd=5,col="blue")
abline(v=0,col="red",lty=2,lwd=4)
abline(h=0,col="red",lty=2,lwd=4)
text(10,-0.5,"x")
text(-0.5,10,"y")
```
\
* Tangent parent function, $y=\tan(x)$, has vertical asymptotes at $x=\pi/2+n\pi$ for any integer $n$.\
```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-10,10,0.001)
y = tan(x)
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]

breaks = c(0,which(abs(diff(y2))>=5),length(x2))
for(i in 1:(length(breaks)-1)){
    lines(x2[(breaks[i]+1):(breaks[i+1])],y2[(breaks[i]+1):(breaks[i+1])],lwd=5,col="blue")
}
abline(v=pi/2,col="red",lty=2,lwd=4)
abline(v=pi/2+pi,col="red",lty=2,lwd=4)
abline(v=pi/2+2*pi,col="red",lty=2,lwd=4)
abline(v=pi/2-pi,col="red",lty=2,lwd=4)
abline(v=pi/2-2*pi,col="red",lty=2,lwd=4)
abline(v=pi/2-3*pi,col="red",lty=2,lwd=4)
text(10,-0.5,"x")
text(-0.5,10,"y")
```
\

# Shifting with asymptotes

Asymptotes shift when the function shifts.

* Consider $y=2^{x-3}+4$. Notice the horizontal asymptote shifts up to $y=4$.\
```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-10,10,0.1)
y = 2^(x-3)+4
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(x2,y2,lwd=5,col="blue")
abline(h=+4,col="red",lty=2,lwd=4)
text(10,-0.5,"x")
text(-0.5,10,"y")
```
\
* Consider $y=\log_2(x-3)+4$. Notice the vertical asymptote shifts right to $x=3$.\
```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-10,10,0.1)
y = 2^(x-4)+3
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(y2,x2,lwd=5,col="blue")
abline(v=3,col="red",lty=2,lwd=4)
text(10,-0.5,"x")
text(-0.5,10,"y")
```
\
* Consider $y=\frac{1}{x-3}+4$.\
```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-10,3-0.001,0.001)
y = 1/(x-3)+4
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(x2,y2,lwd=5,col="blue")
x = seq(3+0.001,10,0.001)
y = 1/(x-3)+4
x2 = x[abs(y)<=10]
y2 = y[abs(y)<=10]
lines(x2,y2,lwd=5,col="blue")
abline(v=3,col="red",lty=2,lwd=4)
abline(h=4,col="red",lty=2,lwd=4)
text(10,-0.5,"x")
text(-0.5,10,"y")
```
\


