```{r,echo=F}
ts = c("0","\\frac{\\pi}{6}","\\frac{\\pi}{4}","\\frac{\\pi}{3}","\\frac{\\pi}{2}","\\frac{2\\pi}{3}","\\frac{3\\pi}{4}","\\frac{5\\pi}{6}","\\pi","\\frac{7\\pi}{6}","\\frac{5\\pi}{4}","\\frac{4\\pi}{3}","\\frac{3\\pi}{2}","\\frac{5\\pi}{3}","\\frac{7\\pi}{4}","\\frac{11\\pi}{6}","2\\pi")

tns = c(0,pi/6,pi/4,pi/3,pi/2,2*pi/3,3*pi/4,5*pi/6,pi,7*pi/6,5*pi/4,4*pi/3,3*pi/2,5*pi/3,7*pi/4,11*pi/6,2*pi)
xns = cos(tns)
yns = sin(tns)
tanns = yns/xns

xs = c("1","\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}","0","\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}","-1","\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}","0","\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}","1")

ys = c("0","\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}","1","\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}","0","\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}","-1","\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}","0")

tans = c("0","\\frac{\\sqrt{3}}{3}","1","\\sqrt{3}","\\pm\\infty","-\\sqrt{3}","-1","\\frac{-\\sqrt{3}}{3}","0","\\frac{\\sqrt{3}}{3}","1","\\sqrt{3}","\\pm\\infty","-\\sqrt{3}","-1","\\frac{-\\sqrt{3}}{3}","0")

cscs = c("\\pm\\infty","2","\\sqrt{2}","\\frac{2\\sqrt{3}}{3}","1","\\frac{2\\sqrt{3}}{3}","\\sqrt{2}","2","\\pm\\infty","-2","-\\sqrt{2}","\\frac{-2\\sqrt{3}}{3}","-1","\\frac{-2\\sqrt{3}}{3}","-\\sqrt{2}","-2","\\pm\\infty")

secs = c("1","\\frac{2\\sqrt{3}}{3}","\\sqrt{2}","2","\\pm\\infty","-2","-\\sqrt{2}","-\\frac{2\\sqrt{3}}{3}","-1","\\frac{-2\\sqrt{3}}{3}","-\\sqrt{2}","-2","\\pm\\infty","2","\\sqrt{2}","\\frac{2\\sqrt{3}}{3}","1")

cots = c("\\pm\\infty","\\sqrt{3}","1","\\frac{\\sqrt{3}}{3}","0","\\frac{-\\sqrt{3}}{3}","-1","-\\sqrt{3}","\\pm\\infty","\\sqrt{3}","1","\\frac{\\sqrt{3}}{3}","0","\\frac{-\\sqrt{3}}{3}","-1","-\\sqrt{3}","\\pm\\infty")

chall = c(-2,-sqrt(3),-sqrt(2),-2/3*sqrt(3),-1,-1/2*sqrt(3),-1/2*sqrt(2),-1/3*sqrt(3),-1/2,0,1/2,1/3*sqrt(3),1/2*sqrt(2),1/2*sqrt(3),1,2/3*sqrt(3),sqrt(2),sqrt(3),2,Inf)

choices = c("-2","-\\sqrt{3}","-\\sqrt{2}","\\frac{-2\\sqrt{3}}{3}","-1","\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{3}","\\frac{-1}{2}","0","\\frac{1}{2}","\\frac{\\sqrt{3}}{3}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}","1","\\frac{2\\sqrt{3}}{3}","\\sqrt{2}","\\sqrt{3}","2","\\pm\\infty")

wi = sample(c(6,7,8,10,11,12,14,15,16),1)
cs = sample(3:6,1)
fun = c("sin","cos","tan","csc","sec","cot")[cs]

get = paste0("\\",fun,"\\left(\\theta\\right)",collapse="")
stx = paste0("\\",fun,"\\left(",ts[wi],"\\right)",collapse="")
outs = list(ys,xs,tans,cscs,secs,cots)
ans = outs[[cs]][wi]
step1 = c("y","x","\\frac{y}{x}",
          "\\frac{1}{y}","\\frac{1}{x}","\\frac{x}{y}")[cs]
step2 = gsub("y",ys[wi],gsub("x",xs[wi],step1,fixed=T),fixed=T)

al = paste0("* $",choices,"$",collapse="\n")
sol = paste0(1*(ans==choices),collapse="")
```

Question
========

To evaluate the trigonometric functions by using the unit circle, it can be helpful to know the following:

| function | value |
|:---:|:---:|
| sine | $y$ |
| cosine | $x$ |
| tangent | $\frac{y}{x}$ |
| cosecant | $\frac{1}{y}$ |
| secant | $\frac{1}{x}$ |
| cotangent | $\frac{x}{y}$ |

The [unit circle](https://en.wikipedia.org/wiki/Unit_circle) below has a radius of length 1. The coordinates of special angles are shown.

```{r,fig.dim=c(8,8),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-1.3,1.3),ylim=c(-1.3,1.3),axes=F,ann=F)
arrows(-1.05,0,1.05,0,0.08,12,3)
arrows(0,-1.05,0,1.05,0.08,12,3)
th = seq(0,2*pi,length.out=120)
lines(cos(th),sin(th))
th12 = seq(0,2*pi,length.out=25)
for(t in th12){
  lines(c(0,cos(t)),c(0,sin(t)),lty=3,col="grey")
}
thsp = c(0,pi/6,pi/4,pi/3,pi/2,2*pi/3,3*pi/4,5*pi/6,pi,
         7*pi/6,5*pi/4,4*pi/3,3*pi/2,5*pi/3,7*pi/4,11*pi/6,2*pi)

for(i in 1:length(thsp)){
  t = thsp[i]
  lines(c(0,cos(t)),c(0,sin(t)),col="red")
  points(cos(t),sin(t),pch=20,col="red")
  text(1.2*cos(t),1.2*sin(t),TeX(paste0("$\\left(",xs[i],",",ys[i],"\\right)$",collapse="")),cex=0.8)
}

ttt = seq(0,thsp[wi],length.out=100)
lines(0.3*cos(ttt),0.3*sin(ttt),col="blue",lwd=2)
text(0.4*cos(thsp[wi]/2),0.4*sin(thsp[wi]/2),TeX("$\\theta$"),cex=2,col="blue")
arrows(0.3*cos(ttt[99]),0.3*sin(ttt[99]),
       0.3*cos(ttt[100]),0.3*sin(ttt[100]),lwd=2,col="blue")

```
\

Determine $`r get`$. You might need to rationalize a denominator and/or simplify a fraction.

Answerlist
--------

`r al`

Solution
========

We know that $`r get`=`r step1`$. In this case, $\theta=`r ts[wi]`$ and $x=`r xs[wi]`$ and $y=`r ys[wi]`$. So

$$`r stx` = `r step2`$$

Simplify the fraction. You might need to rationalize a denominator.

$$`r stx` =  `r ans`$$

It should be mentioned that the fact that $\theta=`r ts[wi]`$ is not necessary to answer this question.


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: unit_circle_special