```{r,echo=FALSE}
deg = sample(4:6,1)
a = sample(c(-9:-1,1:9),1)
cf = c(a,sample(c(0,1,sample(c(-9:-1,1:9),deg-2))))

scf = cf[cf!=0]
sdg = (deg:0)[cf!=0]

P = paste0("{",scf,"}x^{",sdg,"}",collapse="+")
P = gsub("x^{0}","",P,fixed=T)
P = gsub("{1}x","x",P,fixed = T)
P = gsub("+{-1}x","-x",P,fixed = T)
P = gsub("+{-","-{",P,fixed = T)
P = gsub("x^{1}","x",P,fixed=T)
P = gsub("{-1}x","-x",P,fixed = T)

degwrd = c("constant","linear","quadratic","cubic","quartic","quintic","sextic")

chs = -10:10
al = paste0("* ",chs,"\n",collapse="")
fal = paste0(rep(al,deg+1),collapse="\n")
sols = character()
for(i in 1:(deg+1)){
    sols = c(sols,paste0(1*(cf[i]==chs),collapse=""))
}
fsol = paste0(sols,collapse="|")
fct = paste0(rep("schoice",deg+1),collapse="|")

```


Question
========

Below is a [polynomial](https://en.wikipedia.org/wiki/Polynomial) of a single variable, $x$, written in [standard form](https://flexbooks.ck12.org/cbook/ck-12-interactive-algebra-1-for-ccss/section/2.2/related/lesson/polynomials-in-standard-form-bsc-alg/).

$$P(x)=`r P`$$

A polynomial is composed by adding (and subtracting) together multiple terms. Each term has the form $ax^b$, where $a$ is the coefficient and $b$ is the degree, which must be a nonnegative integer. Some special cases are simplified. If $a=1$ or $a=-1$, then the 1 will not be explicitly shown. If $a=0$, then the whole term will not be shown. Similarly, $x^1$ simplifies to $x$ and $x^0$ simplifies to 1. (Technically $0^0$ is undefined, but let's ignore that for now.)


Please identify the coefficients of the terms.

```{css,echo=F}
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
```

```{r,echo=F}
degree = deg:0
coefficient = cf
coefq = paste0("##ANSWER",1:(deg+1),"##")
mydf = data.frame(degwrd[(deg+1):1],degree,coefq)
colnames(mydf) = c("Term","Degree","Coefficient")
knitr::kable(mydf,format="html",label = NA, align = "c",row.names=F,table.attr='class="bordered-table"')
```
\

Answerlist
--------

`r fal`

Solution
========

```{r,echo=F}
P2 = paste0("(",cf,")x^{",deg:0,"}",collapse="+")
```

It might help to see the polynomial in unsimplified form.

$$`r P2`$$


```{css,echo=F}
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
```

```{r,echo=F}
degree = deg:0
coefficient = cf
coefq = paste0("##ANSWER",1:(deg+1),"##")
mydf = data.frame(degwrd[(deg+1):1],degree,coefficient)
colnames(mydf) = c("Term","Degree","Coefficient")
knitr::kable(mydf,format="html",label = NA, align = "c",row.names=F,table.attr='class="bordered-table"')
```
\


Meta-information
============
extype: cloze
exclozetype: `r fct`
exsolution: `r fsol`
exname: polynomial_terminology