```{r,echo=FALSE}
options(scipen=999)
deg1 = sample(4:6,1)
deg2 = sample(4:6,1)
md = max(c(deg1,deg2))
mind = min(c(deg1,deg2))
while(T){
    cfs1 = c(sample(c(0,1,sample(-9:9,deg1-2,T))),sample(1:9,1)*sample(c(-1,1),1))
    cfs2 = c(sample(c(0,1,sample(-9:9,deg2-2,T))),sample(1:9,1)*sample(c(-1,1),1))
    degspe = sample(1:(mind-1),2)
    cfs1[degspe[1]] = cfs2[degspe[1]]
    cfs2[degspe[2]] = cfs1[degspe[2]]+sample(c(-1,1),1)
    if(deg1<deg2){
        cf1 = c(cfs1,rep(0,deg2-deg1))
        cf2 = cfs2
    } else if(deg2<deg1){
        cf2 = c(cfs2,rep(0,deg1-deg2))
        cf1 = cfs1
    } else {
        cf1 = cfs1
        cf2 = cfs2
    }
    cf3 = cf1-cf2
    if(cf3[md]!=0){break}
}
rc1 = rev(cf1)
rc2 = rev(cf2)
rc3 = rev(cf3)

e1 = (md:0)[rc1!=0]
c1 = rc1[rc1!=0]
e2 = (md:0)[rc2!=0]
c2 = rc2[rc2!=0]
e3 = (md:0)[rc3!=0]
c3 = rc3[rc3!=0]

p = function(e,c){
    s = paste0("{",c,"}x^{",e,"}",collapse="+")
    s = gsub("x^{0}","",s,fixed=T)
    s = gsub("+{-1}x","-x",s,fixed=T)
    s = gsub("+{1}x","+x",s,fixed=T)
    s = gsub("+{-","-{",s,fixed=T)
    s = gsub("x^{1}","x",s,fixed=T)
    s = gsub("{-1}x","-x",s,fixed=T)
    s = gsub("{1}x","x",s,fixed=T)
    return(s)
}

p1 = p(e1,c1)
p2 = p(e2,c2)
p3 = p(e3,c3)

rstr = p(md:0,LETTERS[1:(md+1)])

wrds = c("constant","linear","quadratic","cubic","quartic","quintic","sextic")

qs = paste0("* The ",wrds[(md+1):1]," coefficient, $",LETTERS[1:(md+1)],"=$ ##ANSWER",1:(md+1),"##",collapse="\n")

ch = (-20):20

al = paste0("* ",ch,collapse="\n")
fal = paste0(rep(al,md+1),collapse="\n")

sols = character()
for(i in rc3){
    sols = c(sols,paste0(1*(ch==i),collapse=""))
}
sols = paste0(sols,collapse="|")

schs = paste0(rep("schoice",md+1),collapse="|")

ans = paste0("* The ",wrds[(md+1):1]," coefficient, $",LETTERS[1:(md+1)],"=",rc3,"$",collapse="\n")


```


Question
========

Consider the two polynomial functions below:

$$p(x) ~=~ `r p1`$$
$$q(x) ~=~ `r p2`$$

Let polynomial $r(x)$ equal the difference of polynomials $p(x)$ and $q(x)$:

$$r(x) = p(x)-q(x)$$

The resulting polynomial can be expressed using `r paste0("$",LETTERS[1:(md)],"$",collapse=", ")`, and $`r LETTERS[md+1]`$ to represent the coefficients.

$$r(x) ~=~ `r rstr`$$

**Find the value of each coefficient. Notice they might be negative or 0.**

`r qs`

Answerlist
--------

`r fal`


Solution
========

You might find it helpful to put $p$ and $q$ in unsimplified form.

```{r,echo=F}
pun = paste0("(",rc1,")x^{",(md):0,"}",collapse="+")
qun = paste0("(",rc2,")x^{",(md):0,"}",collapse="+")
run = paste0("(",rc3,")x^{",(md):0,"}",collapse="+")
```

$$p(x)=`r pun`$$
$$q(x)=`r qun`$$

Subtract the coefficients of the [like terms](https://en.wikipedia.org/wiki/Like_terms#Simplifying_an_expression). Remember, order matters in subtraction.
$$r(x)=`r run`$$

Thus, we get our answers:

`r ans`

Most people would simplify the result.

$$r(x)=`r p3`$$


Meta-information
============
extype: cloze
exclozetype: `r schs`
exsolution: `r sols`
exname: subtract_poly