```{r,echo=F}
hwl = sample(22:88,3)/10
s = sample(12:31,1)/10
h = hwl[1]
w = hwl[2]
l = hwl[3]
H = h*s
w = w*s
l = l*s

p1 = 4*h+4*w+4*l
a1 = 2*w*h+2*w*l+2*l*h
v1 = h*w*l

p2 = p1*s
a2 = a1*s*s
v2 = v1*s*s*s

alsol = function(ans,n=5,dx=1,spri=NULL){
    choices = ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx
    al = paste0("* ",choices,collapse="\n")
    if(!is.null(spri)){
        choices = round(ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx,spri)
        al = paste0("* ",sprintf(paste0("%.",spri,"f",collapse=""),choices),collapse="\n")
    }
    sol = paste0(1*(ans==choices),collapse="")
    return(data.frame(al,sol))
}

as1 = alsol(round(p1),5,2,0)
as2 = alsol(round(a1),5,2,0)
as3 = alsol(round(v1),5,2,0)
as4 = alsol(round(p2),5,2,0)
as5 = alsol(round(a2),5,2,0)
as6 = alsol(round(v2),5,2,0)

```


Question
========

A rectangular prism is constructed with the following dimensions:

* Length = $`r l`$ meters
* Width = $`r w`$ meters
* Height = $`r h`$ meters

First, its frame is built using 12 lengths of wood.

```{r,echo=F,fig.dim=c(3,3)}
d = l
yr = 0.1

draw_box = function(x,y,z,lwd=2){
    lines(c(0,x,x+yr*y,yr*y,0),c(0,0,yr*y,yr*y,0),lwd=lwd)
    lines(c(0,x,x+yr*y,yr*y,0),c(z,z,z+yr*y,z+yr*y,z),lwd=lwd)
    lines(c(0,0),c(0,z),lwd=lwd)
    lines(c(x,x),c(0,z),lwd=lwd)
    lines(c(y*yr,y*yr),c(y*yr,z+y*yr),lwd=lwd)
    lines(c(x+y*yr,x+y*yr),c(y*yr,z+y*yr),lwd=lwd)
}

par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,max(c(w,d,h))*(1+yr)),ylim=c(-1,max(c(w,d,h))*(1+yr)))
draw_box(w,d,h,lwd=4)
```
\

* Ignoring the overlap in the corners, what total length of wood is needed to build the frame?
* ##ANSWER1## meters

Next, plywood is placed around the frame on all 6 sides.

* What is the area of the plywood?
* ##ANSWER2## square meters

Lastly, the box is filled with cement.

* What is the volume of cement?
* ##ANSWER3## cubic meters


Another builder wants to build a similar box, but they want the box to be scaled by a factor of `r s`. (Each length is scaled by multiplying by `r s`.)

* Ignoring the overlap in the corners, what total length of wood is needed to build the larger frame?
* ##ANSWER4## meters

* What is the area of the plywood for the larger box?
* ##ANSWER5## square meters

* What is the volume of cement for the larger box?
* ##ANSWER6## cubic meters

Answerlist
--------

`r as1$al`
`r as2$al`
`r as3$al`
`r as4$al`
`r as5$al`
`r as6$al`


Solution
========

* `r p1` meters
* `r a1` square meters
* `r v1` cubic meters
* `r p2` meters
* `r a2` square meters
* `r v2` cubic meters



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r as1$sol`|`r as2$sol`|`r as3$sol`|`r as4$sol`|`r as5$sol`|`r as6$sol`
exname: scale_rectangular_prism

