```{r,echo=F}

# set oA, oB, i, nAB
# u = oA+oB+i
# A = oA+i
# B = oB+i
# tot = u+nAB
# oA, oB, i, u, A, B, nAB, tot   

while(T){
    da4 = sample(2:30,3)
    oA = da4[1]
    oB = da4[2]
    I = da4[3]
    U = oA+oB+I
    A = oA+I
    B = oB+I
    a = c(oA,oB,I,U,A,B)
    n = length(a)
    whichgive = sample(1:n,3)
    wa = numeric()
    gottem = 1*(1:n==whichgive[1])+1*(1:n==whichgive[2])+1*(1:n==whichgive[3])
    eqs = list(c(1,3,5),c(2,3,6),c(1,2,3,4))
    for(i in 1:10){
        for(eq in eqs){
            if(sum(gottem[eq])+1==length(eq)){
                for(j in eq){
                    if(gottem[j]==0){
                        gottem[j] = 1
                        wa = c(wa,j)
                    }
                }
            }
        }
    }
    if(length(unique(a))==n && min(a)>=0 && sum(gottem)==n){break}
}
states = c(paste0("The volume remaining when object B is subtracted from object A is ",oA," cubic meters.",collapse=""),
           paste0("The volume remaining when object A is subtracted from object B is ",oB," cubic meters.",collapse=""),
           paste0("The volume of the intersection is ",I," cubic meters.",collapse=""),
           paste0("The volume of the union is ",U," cubic meters.",collapse=""),
           paste0("The volume of object A is ",A," cubic meters.",collapse=""),
           paste0("The volume of object B is ",B," cubic meters.",collapse="")
           )

quests = c("What is the volume remaining when object B is subtracted from object A?",
           "What is the volume remaining when object A is subtracted from object B?",
           "What is the volume of the intersection?",
           "What is the volume of the union?",
           "What is the volume of object A?",
           "What is the volume of object B?"
           )

# whichask = sample((1:n)[!(1:n %in% whichgive)]) ## use wa instead

alsol = function(ans,n=5,dx=1,spri=NULL){
    choices = ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx
    al = paste0("* ",choices,collapse="\n")
    if(!is.null(spri)){
        choices = round(ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx,spri)
        al = paste0("* ",sprintf(paste0("%.",spri,"f",collapse=""),choices),collapse="\n")
    }
    sol = paste0(1*(ans==choices),collapse="")
    return(data.frame(al,sol))
}

as1 = alsol(a[wa[1]])
as2 = alsol(a[wa[2]])
as3 = alsol(a[wa[3]])


```


Question
========

In SketchUp, someone created two overlapping objects. Call them object A and object B. 

* `r states[whichgive[1]]`
* `r states[whichgive[2]]`
* `r states[whichgive[3]]`

Calculate the following volumes:

* `r quests[wa[1]]` ##ANSWER1## $\mathrm{m^3}$
* `r quests[wa[2]]` ##ANSWER2## $\mathrm{m^3}$
* `r quests[wa[3]]` ##ANSWER3## $\mathrm{m^3}$

Answerlist
--------

`r as1$al`
`r as2$al`
`r as3$al`


Solution
========

* `r states[wa[1]]`
* `r states[wa[2]]`
* `r states[wa[3]]`


```{r,echo=F,fig.dim=c(4,3)}
circ = function(x0,y0,r,col=rgb(0,0,0,0)){
    th = seq(0,2*pi,pi/100)
    polygon(x0+r*cos(th),y0+r*sin(th),col=col)
}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(0,6),axes=F,ann=F)
circ(2.5,3,2.2,col=rgb(1,0,0,0.2))
circ(5.5,3,2.2,col=rgb(0,0,1,0.2))
circ(2.5,3,2.2)
circ(5.5,3,2.2)
text(2,3,oA)
text(6,3,oB)
text(4,3,I)
lines(c(0.3,0.3,4.7,4.7),c(0.5,0.4,0.4,0.5))
text(2.5,0.2,A)
lines(c(3.3,3.3,7.7,7.7),c(0.3,0.2,0.2,0.3))
text(5.5,0,B)
lines(c(0.3,0.3,7.7,7.7),c(5.2,5.3,5.3,5.2))
text(4,5.5,U)
```
\



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r as1$sol`|`r as2$sol`|`r as3$sol`
exname: venn_vol
