```{r,echo=F}

# set oA, oB, i, nAB
# u = oA+oB-i
# A = oA+i
# B = oB+i
# tot = u+nAB
# oA, oB, i, u, A, B, nAB, tot   

while(T){
    da4 = sample(2:30,4)
    oA = da4[1]
    oB = da4[2]
    I = da4[3]
    nAB = da4[4]
    U = oA+oB+I
    A = oA+I
    B = oB+I
    tot = U+nAB
    a = c(oA,oB,I,U,A,B,nAB,tot)
    whichgive = sample(1:8,4)
    gottem = 1*(1:8==whichgive[1])+1*(1:8==whichgive[2])+1*(1:8==whichgive[3])+1*(1:8==whichgive[4])
    eqs = list(c(1,3,5),c(2,3,6),c(4,7,8),c(1,2,3,4))
    wa = numeric()
    for(i in 1:10){
        for(eq in eqs){
            if(sum(gottem[eq])+1==length(eq)){
                for(j in eq){
                    if(gottem[j]==0){
                        gottem[j] = 1
                        wa = c(wa,j)
                    }
                }
            }
        }
    }
    if(length(unique(a))==8 && min(a)>=0 && sum(gottem)==8){break}
}
states = c(paste0("The number of students in only club A (and not club B) is ",oA,".",collapse=""),
           paste0("The number of students in only club B (and not club A) is ",oB,".",collapse=""),
           paste0("The number of students in both clubs (in A and B) is ",I,".",collapse=""),
           paste0("The number of students in at least one club is ",U,".",collapse=""),
           paste0("The number of students in club A is ",A,".",collapse=""),
           paste0("The number of students in club B is ",B,".",collapse=""),
           paste0("The number of students in neither club is ",nAB,".",collapse=""),
           paste0("The total number of students in the school is ",tot,".",collapse="")
           )

quests = c("How many students are only in club A (and not club B)?",
           "How many students are only in club B (and not club A)?",
           "How many students are only in BOTH clubs?",
           "How many students are in at least one club?",
           "How many students are in club A?",
           "How many students are in club B?",
           "How many students are in neither club?",
           "How many students are in the school?"
           )

alsol = function(ans,n=5,dx=1,spri=NULL){
    choices = ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx
    al = paste0("* ",choices,collapse="\n")
    if(!is.null(spri)){
        choices = round(ans-sample(0:(n-1),1)*dx+(0:(n-1))*dx,spri)
        al = paste0("* ",sprintf(paste0("%.",spri,"f",collapse=""),choices),collapse="\n")
    }
    sol = paste0(1*(ans==choices),collapse="")
    return(data.frame(al,sol))
}

as1 = alsol(a[wa[1]])
as2 = alsol(a[wa[2]])
as3 = alsol(a[wa[3]])
as4 = alsol(a[wa[4]])


```


Question
========

In a school, there are two clubs: club A and club B. Students can join one club, both clubs, or neither club.

* `r states[whichgive[1]]`
* `r states[whichgive[2]]`
* `r states[whichgive[3]]`
* `r states[whichgive[4]]`

Calculate the following:

* `r quests[wa[1]]` ##ANSWER1## students
* `r quests[wa[2]]` ##ANSWER2## students
* `r quests[wa[3]]` ##ANSWER3## students
* `r quests[wa[4]]` ##ANSWER4## students

Answerlist
--------

`r as1$al`
`r as2$al`
`r as3$al`
`r as4$al`


Solution
========

* `r states[wa[1]]`
* `r states[wa[2]]`
* `r states[wa[3]]`
* `r states[wa[4]]`


```{r,echo=F,fig.dim=c(8.5/2,10/2)}
circ = function(x0,y0,r,col=rgb(0,0,0,0)){
    th = seq(0,2*pi,pi/100)
    polygon(x0+r*cos(th),y0+r*sin(th),col=col)
}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1,9),ylim=c(-1,7.5),axes=F,ann=F)
circ(2.5,3,2.2,col=rgb(1,0,0,0.2))
circ(5.5,3,2.2,col=rgb(0,0,1,0.2))
circ(2.5,3,2.2)
circ(5.5,3,2.2)
text(2,3,oA,cex=1.2)
text(6,3,oB,cex=1.2)
text(4,3,I,cex=1.2)
lines(c(0.3,0.3,4.7,4.7),c(0.5,0.4,0.4,0.5))
text(2.5,0.2,A)
lines(c(3.3,3.3,7.7,7.7),c(0.3,0.2,0.2,0.3))
text(5.5,0,B)
lines(c(0.3,0.3,7.7,7.7),c(5.2,5.3,5.3,5.2))
text(4,5.5,U)
lines(c(-1,-1,9,9,-1),c(-1,7,7,-1,-1))
text(-0.5,7.2,tot)
text(0,6.5,nAB,cex=1.2)

```
\



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r as1$sol`|`r as2$sol`|`r as3$sol`|`r as4$sol`
exname: venn_clubs
