```{r data generation, echo = FALSE, results = "hide"}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
## (px+s)(qx+t) = pq x^2  +  (pt+qs) x  +  st
while(T){
    psqt = sample(2:10,4)
    p = psqt[1]*sample(c(-1,1),1)
    s = psqt[2]*sample(c(-1,1),1)
    q = psqt[3]*sample(c(-1,1),1)
    t = psqt[4]*sample(c(-1,1),1)
    a = p*q
    b = (p*t+q*s)
    c = s*t
    if(abs(gcd2(p,s))==1 && abs(gcd2(q,t))==1 && abs(b)>1 && length(unique(sign(c(a,b,c))))==2){break}
}
B = sample(2:9,1)
cf = c(a,b,c)
istop = cf>0
isbot = cf<0
exps = c(paste0(a,"x^2",collapse=""),paste0(b,"x",collapse=""),paste0(c,collapse=""))
aexps = c(paste0(abs(a),"x^2",collapse=""),paste0(abs(b),"x",collapse=""),paste0(abs(c),collapse=""))

tops = paste0(B,"^{",exps[istop],"}",collapse="\\cdot ")
bots = paste0(B,"^{",aexps[isbot],"}",collapse="\\cdot ")
frac1 = paste0("\\frac{",tops,"}{",bots,"}")
stan = paste0(exps,collapse="+")
stan = gsub("+-","-",stan,fixed=T)

i = 0
alnums = list()
fracs = character()
al = character()
for(denom in 2:10){
    for(numer in c(-10:-2,2:10)){
        if(!(list(c(numer,denom)) %in% alnums) && abs(gcd2(denom,numer))==1){
            i = i+1
            alnums[[i]] = c(numer,denom)
            fracs = c(fracs,paste0(numer,"/",denom,collapse=""))
            al = c(al,paste0(numer,"/",denom,collapse=""))
        }
    } 
}
al = paste0("* ",al,collapse="\n")
ans1 = paste0(-s*sign(p),"/",abs(p),collapse="")
ans2 = paste0(-t*sign(q),"/",abs(q),collapse="")
ans = c(ans1,ans2)
sols = paste0(1*(fracs %in% ans),collapse="")

```

Question
========

Find all solutions to the equation:
$$`r frac1`~=~ 1$$

Answerlist
--------

`r al`


Solution
========

Use the rules of exponents to rewrite the equation.

$$`r B`^{`r stan`}~=~`r B`^{0}$$

Each side has a single exponential expression with a common base, so the exponents are equivalent.

$$`r stan`~=~0$$

```{r,echo=F,results='asis'}
if(a<0){
    cat("The leading coefficient is negative. Multiply both sides by $=-1$ to get a positive quadratic coefficient.\n\n")
    a = -a
    b = -b
    c = -c
    exps = c(paste0(a,"x^2",collapse=""),paste0(b,"x",collapse=""),paste0(c,collapse=""))
    stan = paste0(exps,collapse="+")
    stan = gsub("+-","-",stan,fixed=T)
    cat(paste0("$$",stan,"=0$$"))
}
```

You could, with enough guess-and-check, factor this expression. However, since this quadratic has a composite (non-prime) leading coefficient and composite constant, I'd recommend using the [quadratic formula](https://en.wikipedia.org/wiki/Quadratic_formula). Start by identifying the parameters.

$$a~=~`r a`$$
$$b~=~`r b`$$
$$c~=~`r c`$$

Next, type the quadratic formula into Desmos. I'd recommend doing it with parameters and sliders. Desmos does not have a $\pm$ symbol, so just write it twice. Desmos will also simplify fractions for you (if you click on the fraction button).

$$x~=~\frac{-(`r b`)\pm \sqrt{(`r b`)^2-4(`r a`)(`r c`)}}{2(`r a`)}$$


$$x~=~\frac{`r -b` \pm \sqrt{`r b^2`-(`r 4*a*c`)}}{`r 2*a`}$$


$$x~=~\frac{`r -b` \pm \sqrt{`r b^2-4*a*c`}}{`r 2*a`}$$


$$x~=~\frac{`r -b` \pm `r round(sqrt(b^2-4*a*c))`}{`r 2*a`}$$


Split the $\pm$ into $-$ and $+$.

$$\begin{aligned}
x~&=~\frac{`r round(-b-sqrt(b^2-4*a*c))`}{`r 2*a`} & \text{or}&& x~&=~\frac{`r round(-b+sqrt(b^2-4*a*c))`}{`r 2*a`}
\end{aligned}$$

Simplify the fractions.

```{r,echo=F}
top1 = round(-b-sqrt(b^2-4*a*c))
bot1 = 2*a
top2 = round(-b+sqrt(b^2-4*a*c))
bot2 = 2*a
gg1 = gcd2(top1,bot1)
top1 = round(top1/gg1)
bot1 = round(bot1/gg1)
gg2 = gcd2(top2,bot2)
top2 = round(top2/gg2)
bot2 = round(bot2/gg2)

factored = paste0("(",bot1,"x+",-top1,")(",bot2,"x+",-top2,")",collapse="")
factored = gsub("+-","-",factored,fixed=T)
```

$$\begin{aligned}
x~&=~\frac{`r top1`}{`r bot1`} & \text{or}&& x~&=~\frac{`r top2`}{`r bot2`}
\end{aligned}$$


I'll point out that if you had guess-and-checked the factored form, you'd get:

$$`r stan`~\equiv~`r factored`$$

Because $(`r bot1`)(`r bot2`)=`r bot1*bot2`$ and $(`r bot1`)(`r -top2`)+(`r bot2`)(`r -top1`)=`r -bot1*top2-bot2*top1`$ and $(`r -top1`)(`r -top2`)=`r top1*top2`$. Notice it is easy to find the solutions from this factored form equation.

$$`r factored`~=~0$$

$$\begin{aligned}
x~&=~\frac{`r top1`}{`r bot1`} & \text{or}&& x~&=~\frac{`r top2`}{`r bot2`}
\end{aligned}$$


Meta-information
============
extype: mchoice
exsolution: `r sols`
exname: common_base_quad_rats