```{r data generation, echo = FALSE, results = "hide"}
options(scipen=99)
xs = seq(-3,3,0.1)
ys = numeric()
for(jj in -3:2){
    for(ii in 1:9){
        ys = c(ys,ii*10^jj)
    }
}
# while(T){
#     B = runif(1,3,30)
#     x = runif(1,0.5,3)*sample(c(-1,1),1)
#     y = B^x
#     xq = signif(x,1)
#     if(min(abs(x-xs))<0.01 && min(abs(y-ys))/abs(y)<0.1 && xq%%1!=0){break}
# }

while(T){
    xp = sample(seq(-2.9,2.9,0.1),1)
    yp = sample(2:9,1)*10^sample(-3:2,1)
    B = yp^(1/xp)
    if(B>2 && B<50 && xp%%1!=0 && abs(xp)>0.4){break}
}
x = xp
y = yp

powy = floor(log(y,10))
tol = 10^(powy-1)*5
```



Question
========

An exponential growth curve, $y=B^x$ with base $B>1$, is graphed below using a [semi-log plot](https://en.wikipedia.org/wiki/Semi-log_plot).

```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
plot(0,0,"n",axes=F,xlim=c(-3,3),ylim=c(-3,3),xlab="x",ylab="y")
# axis(2,at=-3:3,labels=TeX(paste0("$10^{",-3:3,"}$")))
axis(2,at=-3:3,labels=paste0(10^(-3:3)))
axis(1,at=-3:3)
# abline(h=-30:30/10,lty=1,lwd=0.2,col="lightgrey")
for(ii in 1:9){
    for(jj in -4:4){
        abline(h=log(ii*10^jj,10),lwd=0.2,col="lightgrey")
    }
}
abline(v=-30:30/10,lty=1,lwd=0.5,col="lightgrey")
abline(h=-3:3,lty=1,lwd=0.8,col="grey")
abline(v=-3:3,lty=1,lwd=0.8,col="grey")
abline(h=0)
abline(v=0)
# abline(0,1,col="blue",lwd=2)
legend("topleft",TeX("$y=B^x$"),col="blue",lwd=1)
yp = log10(B^c(-3,3))
lines(c(-3,3),yp,col="blue",lwd=1)
```
\

Estimate $\log_B(`r signif(y,2)`)$.



Solution
========

Logarithms are inverses of exponential functions. So, if $f(x)=B^x$ then $f^{-1}(x)=\log_B(x)$. In this case, that means we know the $y$ coordinate is `r signif(y,1)`, and we are looking for the $x$ coordinate.


It might help to see more labels on a small section of the $y$ (logarithmic) axis.

```{r,echo=F,fig.dim=c(1,7)}
library(latex2exp)
par(mar=c(0,3,0,0))
plot(0,0,"n",axes=F,xlim=c(0,1),ylim=c(-1,2),ann=F)
# axis(2,at=-3:3,labels=TeX(paste0("$10^{",-3:3,"}$")))
yl = numeric()
for(jj in -1:1){
    for(ii in 1:9){
        yl = c(yl,ii*10^jj)
    }
}
yl = c(yl,100)

axis(2,at=-1:2,labels=paste0(10^(-1:2)))
# axis(1,at=-3:3)
# abline(h=-30:30/10,lty=1,lwd=0.2,col="lightgrey")
for(ii in 1:9){
    for(jj in -1:2){
        abline(h=log(ii*10^jj,10),lwd=0.2,col="lightgrey")
    }
}
# abline(v=-30:30/10,lty=1,lwd=0.5,col="lightgrey")
abline(h=-1:2,lty=1,lwd=0.8,col="grey")
# abline(v=-3:3,lty=1,lwd=0.8,col="grey")
abline(h=0)
# abline(v=0)
# abline(0,1,col="blue",lwd=2)
# legend("topleft",TeX("$y=f(x)$"),col="blue",lwd=1)
# yp = log10(B^c(-3,3))
# lines(c(-3,3),yp,col="blue",lwd=1)
text(0.5,log10(yl),paste0(yl),cex=0.5)
```
\


With that in mind, you just need to locate the correct spot on the graph.

```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
plot(0,0,"n",axes=F,xlim=c(-3,3),ylim=c(-3,3),xlab="x",ylab="y")
# axis(2,at=-3:3,labels=TeX(paste0("$10^{",-3:3,"}$")))
axis(2,at=-3:3,labels=paste0(10^(-3:3)))
axis(1,at=-3:3)
# abline(h=-30:30/10,lty=1,lwd=0.2,col="lightgrey")
for(ii in 1:9){
    for(jj in -4:4){
        abline(h=log(ii*10^jj,10),lwd=0.2,col="lightgrey")
    }
}
abline(v=-30:30/10,lty=1,lwd=0.5,col="lightgrey")
abline(h=-3:3,lty=1,lwd=0.8,col="grey")
abline(v=-3:3,lty=1,lwd=0.8,col="grey")
abline(h=0)
abline(v=0)
# abline(0,1,col="blue",lwd=2)
legend("topleft",TeX("$y=f(x)$"),col="blue",lwd=1)
yp = log10(B^c(-3,3))
lines(c(-3,3),yp,col="blue",lwd=1)
points(x,log10(y),pch=19,col="red",cex=0.5)
text(x,log10(y),paste0("(",signif(x,2),", ",signif(y,2),")"),adj=0.5+0.7*sign(x),col="red",cex=1.5)

```
\

So, $$\log_B(`r signif(y,2)`)~=~`r signif(x,2)`$$


Meta-information
============
extype: num
exsolution: `r signif(x,2)`
exname: log_graph_get_exp
extol: 0.05