```{r,echo=FALSE}
options(scipen=99)
N = sample(5:40,1)
kf = floor(N*log(1.5,2))
kc = ceiling(N*log(1.5,2))
a = round(N*log(1.5,2),0)
R = 2^(a/N)
Iex = 1200*log2(1.5)
Ix = 1200*log2(R)
cents = 1200*log2(R/1.5)
```

Question
========

When the ratio between two [fundamental frequencies](https://en.wikipedia.org/wiki/Fundamental_frequency) is near 3:2, musicians call the [interval](https://en.wikipedia.org/wiki/Interval_(music)) a "[fifth](https://en.wikipedia.org/wiki/Perfect_fifth)", named from playing the first and fifth notes in a classical [diatonic scale](https://en.wikipedia.org/wiki/Diatonic_scale). Somewhat annoyingly, [equal temperament](https://en.wikipedia.org/wiki/Equal_temperament) does not allow for a ratio of exactly 3:2. Some equal temperaments get closer than others. Let's investigate how close [`r N` EDO](https://en.wikipedia.org/wiki/Equal_temperament#Various_equal_temperaments) can get to an [exact 3:2 ratio of frequencies](https://en.wikipedia.org/wiki/Just_intonation). We will report the "distance" in [cents](https://en.wikipedia.org/wiki/Cent_(music)).

```{r,echo=FALSE,fig.dim=c(5*8/5,1*8/5)}
par(mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(0,1),ylim=c(-0.1,0.1),axes=FALSE,ann=FALSE)
text(0.25,0.095,paste0("Frets positioned for ",N," EDO"))
lines(c(1/3,1/3),c(-0.05,0.055),col="red")
text(1/3,0.07,"3:2",col="red")
lines(c(1/2,1/2),c(-0.05,0.055),col="blue")
text(1/2,0.07,"2:1",col="blue")
text(1/2,0.09,"octave",col="blue")
lines(c(0,0),c(-0.05,0.055),col="green")
text(0,0.07,"1",col="green")
theta=seq(0,2*pi,pi/100)
r = 2+cos(2*theta)+0.3*cos(theta)
xx = 1/8*r*cos(theta)+0.9
yy = 1/8*r*sin(theta)
polygon(xx,yy,col="tan")
polygon(c(0,0,0.8,0.8),c(-0.03,0.03,0.03,-0.03),col="white")
polygon(c(0.99,0.99,1.01,1.01),c(-0.03,0.03,0.03,-0.03),col="white")
polygon(0.06*cos(theta)+0.8,0.06*sin(theta),col="grey")
lines(c(0,1),c(0.008,0.008))
lines(c(0,1),c(-0.008,-0.008))
lines(c(0,1),c(0.024,0.024))
lines(c(0,1),c(-0.024,-0.024))
polygon(c(0,0,-0.1,-0.1),c(0.03,-0.03,-0.05,0.05),col="tan")
polygon(0.01*cos(theta)-0.03,0.01*sin(theta)+0.02,col="grey")
polygon(0.01*cos(theta)-0.08,0.01*sin(theta)+0.02,col="grey")
polygon(0.01*cos(theta)-0.03,0.01*sin(theta)-0.02,col="grey")
polygon(0.01*cos(theta)-0.08,0.01*sin(theta)-0.02,col="grey")
for(i in 1:N){
  fr = 1-(1/2)^(i/N)
  lines(c(fr,fr),c(-0.03,0.03))
}
y0 = -0.06
lines(c(0,1),c(y0,y0))
for(i in 0:100){
  if(i%%10==0){
    lines(c(i/100,i/100),c(y0-0.005,y0+0.005))
  } else if(i%%5==0){
    lines(c(i/100,i/100),c(y0-0.003,y0+0.003))
  } else {
    lines(c(i/100,i/100),c(y0-0.001,y0+0.001))
  }
}
lines(c(1,1,0.5,0.5),c(-0.07,-0.08,-0.08,-0.07),col="blue")
lines(c(0,0,0.5,0.5),c(-0.07,-0.08,-0.08,-0.07),col="blue")
lines(c(0,0,1/3,1/3),c(-0.085,-0.095,-0.095,-0.085),col="red")
lines(c(1/3,1/3,2/3,2/3),c(-0.085,-0.095,-0.095,-0.085),col="red")
lines(c(2/3,2/3,1,1),c(-0.085,-0.095,-0.095,-0.085),col="red")
```
\

First, determine the interval (in [cents](https://en.wikipedia.org/wiki/Cent_(music))) of an exact 3:2 ratio.

$$I_\text{exact} ~=~ 1200\cdot\log_2\left(\frac{3}{2}\right) ~=~ `r 1200*log(1.5,2)`$$

Determine the best [fret](https://en.wikipedia.org/wiki/Fret) on the `r N`-EDO guitar to approximate a 3:2 ratio (after playing an open string) by [rounding](https://en.wikipedia.org/wiki/Rounding#Rounding_to_the_nearest_integer) a logarithmic function.

$$x ~=~ \text{round} \left(`r N`\cdot \log_2\left(\frac{3}{2}\right) \right)$$
Then, determine the ratio of frequencies between an open string and the $x$th fret on the `r N`-EDO guitar. The ratio should be near 1.5, but a bit off.

$$r = 2^{x/`r N`}$$

Calculate the cents of the interval between the open string and the $x$th fret.

$$I_{\text{fret}} = 1200 \cdot \log_2(r) $$


Finally, determine the absolute difference.

$$\text{answer} = \left|I_{\text{fret}} - I_{\text{exact}}\right|$$

Your answer can be rounded to the nearest cent.

Solution
========

Use the formulas. First find the fret.

$$x ~=~ \text{round} \left(`r N`\cdot \log_2(1.5) \right) ~=~ `r a`$$

To approximate a 3:2 ratio, the musician could play a string open and then the same string on fret number `r a`. Find the ratio of frequencies.

$$r ~=~ 2^{`r a`/`r N`} ~=~ `r R`$$
When the musician plays a string open and then on fret number `r a`, the ratio of frequencies is `r R`. Get the interval between open and fret in cents.

$$I_{\text{fret}} ~=~ 1200 \cdot \log_2(`r R`) ~=~ `r Ix`$$

It should be pointed out that due to [logarithmic identities](https://en.wikipedia.org/wiki/List_of_logarithmic_identities#Cancelling_exponentials), we could calculate $I_{\text{fret}}$ in a more straightforward manner.

$$I_{\text{fret}} ~=~ 1200 \cdot \frac{`r a`}{`r N`} ~=~ `r Ix`$$

A ratio of `r R` is equivalent to `r Ix` cents. We can get the final answer by taking the absolute difference of the two intervals.

$$\Big|`r Iex` - `r Ix`\Big| = `r abs(cents)`$$




Meta-information
============
extype: num
exsolution: `r abs(cents)`
extol: 1
exname: fifth_error