```{r data generation, echo = FALSE, results = "hide"}
options(scipen=99)
xposs = -4:10
yposs = 2^xposs
aposs = sort(unique(c(xposs,yposs)))
x = sort(sample(xposs,5))
f = 2^x
al = paste0("* ",aposs,collapse="\n")
answers = c(f,x)
sols = character()
for(answer in answers){
    sols = c(sols,paste0(1*(aposs==answer),collapse=""))
}
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

I've located 5 points on the $y=2^x$ curve.

```{r tab2, results="asis", echo=F}
mydf2 = data.frame(paste0(x),paste0(f))
colnames(mydf2) = c("$x$","$y=2^x$")
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


If a parent function is $f(x)=2^x$ then the [inverse function](https://en.wikipedia.org/wiki/Inverse_function) is $f^{-1}(y)=\log_{2}(y)$. Use the 5 points given above to fill out the table below (with corresponding points in increasing order).

```{r tab4, results="asis", echo=F}
mydf4 = data.frame(paste0("##ANSWER",1:5,"##"),paste0("##ANSWER",6:10,"##"))
colnames(mydf4) = c("$y$","$x=\\log_{2}(y)$")
knitr::kable(mydf4,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`
`r al`


Solution
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

The inverse function $f^{-1}(z)=\log_{2}(z)$ is defined by the table below.

```{r tab3, results="asis", echo=F}
mydf3 = data.frame(paste0(f),paste0(x))
colnames(mydf3) = c("$y$","$x=\\log_{2}(y)$")
knitr::kable(mydf3,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

Notice, you just switch the columns of the given $y=2^x$ table.

Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",10),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: log10_inverse_table