```{r data generation, echo = FALSE, results = "hide"}
options(scipen=99)
xs = seq(-3,3,0.1)
ys = numeric()
for(jj in -3:2){
    for(ii in 1:9){
        ys = c(ys,ii*10^jj)
    }
}
# while(T){
#     B = runif(1,3,30)
#     x = runif(1,0.5,3)*sample(c(-1,1),1)
#     y = B^x
#     xq = signif(x,1)
#     if(min(abs(x-xs))<0.01 && min(abs(y-ys))/abs(y)<0.1 && xq%%1!=0){break}
# }

while(T){
    xp = sample(seq(-2.9,2.9,0.1),1)
    yp = sample(2:9,1)*10^sample(-3:2,1)
    B = yp^(1/xp)
    if(B>2 && B<50 && xp%%1!=0 && abs(xp)>0.4){break}
}
x = xp
y = yp

powy = floor(log(B,10))
tol = 10^(powy-2)*5
```



Question
========

An exponential growth curve, $y=B^x$ with base $B>1$, is graphed below using a [semi-log plot](https://en.wikipedia.org/wiki/Semi-log_plot).

```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
plot(0,0,"n",axes=F,xlim=c(-3,3),ylim=c(-3,3),xlab="x",ylab="y")
# axis(2,at=-3:3,labels=TeX(paste0("$10^{",-3:3,"}$")))
axis(2,at=-3:3,labels=paste0(10^(-3:3)))
axis(1,at=-3:3)
# abline(h=-30:30/10,lty=1,lwd=0.2,col="lightgrey")
for(ii in 1:9){
    for(jj in -4:4){
        abline(h=log(ii*10^jj,10),lwd=0.2,col="lightgrey")
    }
}
abline(v=-30:30/10,lty=1,lwd=0.5,col="lightgrey")
abline(h=-3:3,lty=1,lwd=0.8,col="grey")
abline(v=-3:3,lty=1,lwd=0.8,col="grey")
abline(h=0)
abline(v=0)
# abline(0,1,col="blue",lwd=2)
legend("topleft",TeX("$y=B^x$"),col="blue",lwd=1)
yp = log10(B^c(-3,3))
lines(c(-3,3),yp,col="blue",lwd=1)
points(x,log10(y),pch=19,col="red",cex=0.5)
```
\

Based on the red point, estimate the base $B$. 



Solution
========


Determine the coordinates of the point on the graph.

```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
plot(0,0,"n",axes=F,xlim=c(-3,3),ylim=c(-3,3),xlab="x",ylab="y")
# axis(2,at=-3:3,labels=TeX(paste0("$10^{",-3:3,"}$")))
axis(2,at=-3:3,labels=paste0(10^(-3:3)))
axis(1,at=-3:3)
# abline(h=-30:30/10,lty=1,lwd=0.2,col="lightgrey")
for(ii in 1:9){
    for(jj in -4:4){
        abline(h=log(ii*10^jj,10),lwd=0.2,col="lightgrey")
    }
}
abline(v=-30:30/10,lty=1,lwd=0.5,col="lightgrey")
abline(h=-3:3,lty=1,lwd=0.8,col="grey")
abline(v=-3:3,lty=1,lwd=0.8,col="grey")
abline(h=0)
abline(v=0)
# abline(0,1,col="blue",lwd=2)
legend("topleft",TeX("$y=f(x)$"),col="blue",lwd=1)
yp = log10(B^c(-3,3))
lines(c(-3,3),yp,col="blue",lwd=1)
points(x,log10(y),pch=19,col="red",cex=0.5)
text(x,log10(y),paste0("(",signif(x,2),", ",signif(y,2),")"),adj=0.5+0.7*sign(x),col="red",cex=1.5)

```
\

We know that $B^{`r signif(x,2)`}=`r signif(y,1)`$. To solve for $B$, raise both sides of the equation to the power of $\frac{1}{`r signif(x,2)`}$.

$$\left(B^{`r signif(x,2)`}\right)^{\frac{1}{`r signif(x,2)`}}=\left(`r signif(y,1)`\right)^{\frac{1}{`r signif(x,2)`}}$$

We know [from our exponent rules](https://chadworley.github.io/a2/u18/Exponent_rules.html) that $(a^x)^y\equiv a^{xy}$. We also know that $c\cdot \frac{1}{c}=1$ for any $c\ne 0$. Those two rules allow us to simplify the left side.

$$B~=~\left(`r signif(y,1)`\right)^{\frac{1}{`r signif(x,2)`}}$$

Use a calculator.


$$B~\approx~`r B`$$


Meta-information
============
extype: num
exsolution: `r B`
exname: log_graph_get_exp
extol: `r tol`