```{r,echo=FALSE}

x1 = seq(-10,10,0.01)
ya = exp(x1)
yb = exp(x1+2)
yc = exp(x1)+2
yd = exp(x1-2)
ye = exp(x1)-2
y2 = seq(-10,10,0.01)
xf = exp(y2)  # y = ln(x)
xg = exp(y2+2) # y = ln(x)-2
xh = exp(y2)+2 # y = ln(x-2)
xi = exp(y2-2) # y = ln(x)+2
xj = exp(y2)-2 # y = ln(x+2)
asympts = list(list(c(-7,7),c(0,0)),
               list(c(-7,7),c(0,0)),
               list(c(-7,7),c(2,2)),
               list(c(-7,7),c(0,0)),
               list(c(-7,7),c(-2,-2)),
               list(c(0,0),c(-7,7)),
               list(c(0,0),c(-7,7)),
               list(c(2,2),c(-7,7)),
               list(c(0,0),c(-7,7)),
               list(c(-2,-2),c(-7,7)),
               list(c(0,0),c(-7,7)))
graphs = list(list(x1,ya),
              list(x1,yb),
              list(x1,yc),
              list(x1,yd),
              list(x1,ye),
              list(xf,y2),
              list(xg,y2),
              list(xh,y2),
              list(xi,y2),
              list(xj,y2))
eqs = c("y=e^{x}",
        "y=e^{x+2}",
        "y=e^{x}+2",
        "y=e^{x-2}",
        "y=e^{x}-2",
        "y=\\ln(x)",
        "y=\\ln(x)-2",
        "y=\\ln(x-2)",
        "y=\\ln(x)+2",
        "y=\\ln(x+2)")
ordgraphs = sample(1:10) 
ordeqs = sample(1:10)

ach = LETTERS[1:10]

sols = character()
for(i in ordeqs){
    sol = paste0(1*(ordgraphs==i),collapse="")
    sols = c(sols,sol)
}


```


Question
========

Match the following graphs to their equations. I've shown the asymptotes as dotted red lines.

```{r,echo=F,fig.dim=c(6,15)}
par(mfrow=c(5,2))
for(i in 1:10){
    x = graphs[[ordgraphs[i]]][[1]]
    y = graphs[[ordgraphs[i]]][[2]]
    plot(x,y,"l",xlim=c(-5,5),ylim=c(-5,5),main=LETTERS[i],asp=1)
    abline(h=0,col="grey")
    abline(v=0,col="grey")
    asx = asympts[[ordgraphs[i]]][[1]]
    asy = asympts[[ordgraphs[i]]][[2]]
    lines(asx,asy,col="red",lty=2)
    lines(x,y,col="blue",lwd=2)
}

```

1. $`r eqs[ordeqs[1]]`$ ##ANSWER1##
2. $`r eqs[ordeqs[2]]`$ ##ANSWER2##
3. $`r eqs[ordeqs[3]]`$ ##ANSWER3##
4. $`r eqs[ordeqs[4]]`$ ##ANSWER4##
5. $`r eqs[ordeqs[5]]`$ ##ANSWER5##
6. $`r eqs[ordeqs[6]]`$ ##ANSWER6##
7. $`r eqs[ordeqs[7]]`$ ##ANSWER7##
8. $`r eqs[ordeqs[8]]`$ ##ANSWER8##
9. $`r eqs[ordeqs[9]]`$ ##ANSWER9##
10. $`r eqs[ordeqs[10]]`$ ##ANSWER10##


Answerlist
--------

`r paste0("* ",rep(ach,10),collapse="\n")`


Solution
========

1. $`r eqs[ordeqs[1]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[1])]`
2. $`r eqs[ordeqs[2]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[2])]`
3. $`r eqs[ordeqs[3]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[3])]`
4. $`r eqs[ordeqs[4]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[4])]`
5. $`r eqs[ordeqs[5]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[5])]`
6. $`r eqs[ordeqs[6]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[6])]`
7. $`r eqs[ordeqs[7]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[7])]`
8. $`r eqs[ordeqs[8]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[8])]`
9. $`r eqs[ordeqs[9]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[9])]`
10. $`r eqs[ordeqs[10]]`$ is graph `r LETTERS[which(ordgraphs==ordeqs[10])]`






Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",10),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: shifted_exp_log