```{r,echo=FALSE}
options(scipen=99)
## B^(x-h)+k
## log_B(x-h)+k
B = signif(2^(runif(1,1.1,3)*sample(c(-1,1),1)),3)
hk = sample(2:8,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]
ex1 = paste0(B,"^{x+",-h,"}+",k)
ex1 = gsub("+-","-",ex1,fixed=T)

ach1 = c("horizontal asymptote","vertical asymptote")
ach2 = c(paste0("x=",-9:9),paste0("y=",-9:9))

sol1 = "10"
ans2 = paste0("y=",k,collapse="")
sol2 = paste0(1*(ans2==ach2),collapse="")

if(B<1){
    sym1 = ""
} else {
    sym1 = "-"
}

```


Question
========

Consider the exponential function:

$$f(x)~=~`r ex1`$$

Describe the function's [asymptote](https://en.wikipedia.org/wiki/Asymptote). The function $f$ has a ##ANSWER1## at ##ANSWER2##.

Answerlist
--------

`r paste0("* ",ach1,collapse="\n")`
`r paste0("* ",ach2,collapse="\n")`


Solution
========

Graph the function as $y=f(x)$. Notice that as $x\to`r sym1`\infty$, we see $y\to `r k`$. Thus, there is a horizontal asymptote at $y=`r k`$. Notice this means the [range](https://en.wikipedia.org/wiki/Range_of_a_function) is $(`r k`,\infty)$, so the possible outputs include all real numbers greater than `r k`.

```{r,echo=F,fig.dim=c(5,5)}
xs = seq(-10,10,0.1)
ys = B^(xs-h)+k
plot(xs,ys,"l",col="blue",xlab="x",ylab="y",xlim=c(-10,10),ylim=c(-10,10))
abline(h=k,col="red",lty=2)

```
\

You might think it looks like there is also a vertical asymptote, but you'd be wrong. The curve has a [domain](https://en.wikipedia.org/wiki/Domain_of_a_function) of $(-\infty,\infty)$.



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: exponential_asymptote