```{r,echo=FALSE}
neg = 1 #sample(c(-1,1),1)
base = round(runif(1,1.2,1.9)^neg,2)
A = sample(3:6,1)
h = log(A,base)
```


Question
========

For [exponential functions](https://en.wikipedia.org/wiki/Exponential_function), a horizontal shift is equivalent to a vertical stretch. Consider the two functions below, where $g$ is equivalent to $f$ stretched vertically by a factor $`r A`$:

```{r,echo=FALSE,fig.dim=c(6,6)}
par(pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(0,20),xlab="x",ylab="y")
for(i in -15:22){
  if(i%%5==0){
    abline(h=i,lty=2)
    abline(v=i,lty=2)
  } else {
    abline(h=i,lty=3)
    abline(v=i,lty=3)
  }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-11,11,0.01)
y = base^x
lines(x,y,col="blue",lwd=4)
x = seq(-11,11,0.01)
y = A*base^(x)
lines(x,y,col="red",lwd=4)
legend(-10*neg,20,c("y = f(x)","y = g(x)"),lwd=2,col = c("blue","red"))
points(c(0,0),c(1,A),col=c("blue","red"),pch=19)
farx = log(20,base)
garx = floor(abs(farx-h))*neg
points(c(garx,garx),c(base^garx,A*base^garx),col=c("blue","red"),pch=19)
lines(c(garx,garx),c(0,A*base^garx),col="purple",lwd=3)
for(i in 0:A){
  lines(c(garx-0.2,garx+0.2),c(i*base^garx,i*base^garx),lwd=3,col="purple")
}
lines(c(0,0),c(0,A),col="orange",lwd=3)
for(i in 0:A){
  lines(c(-0.2,0.2),c(i,i),lwd=3,col="orange")
}
```
\

$$\begin{align}
f(x) &= `r base`^{x}\\\\
g(x) &= `r A`\cdot `r base`^{x}
\end{align}$$

Instead of using the vertical stretch transformation, we could have used a horizontal shift. Notice the $g$ curve is congruent to the $f$ curve, just shifted to the left. Thus, we can express $g$ as a horizontally shifted version of $f$.

$$g(x) = f(x+h)$$

Or,

$$g(x) = `r base`^{x+h}$$

where $h$ represents the distance of the horizontal shift.

* Find $h$. The tolerance is $\pm 0.01$.



Solution
========

It can be shown that $h = `r h`$.

```{r,echo=FALSE,fig.dim=c(6,6)}
par(pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-5,15),xlab="x",ylab="y")
for(i in -15:20){
  if(i%%5==0){
    abline(h=i,lty=2)
    abline(v=i,lty=2)
  } else {
    abline(h=i,lty=3)
    abline(v=i,lty=3)
  }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
x = seq(-11,11,0.01)
y = base^x
lines(x,y,col="blue",lwd=3)
x = seq(-11,11,0.01)
y = A*base^(x)
lines(x,y,col="red",lwd=3)
legend(-9,10,c("f(x)","g(x)"),lwd=2,col = c("blue","red"))
lines(c(-h,0),c(1,1),col="darkgreen")
text(-h/2,1.5,round(h,2),col="darkgreen")
lines(c(0,h),c(A,A),col="darkgreen")
text(h/2,A+0.5,round(h,2),col="darkgreen")
lines(c(log(2*A,base),log(2*A,base)-h),c(2*A,2*A),col="darkgreen")
text(log(2*A,base)-h/2,2*A+0.5,round(h,2),col="darkgreen")
points(c(-h,0,0,h,log(2*A,base),log(2*A,base)-h),c(1,1,A,A,2*A,2*A),col="darkgreen",pch=19)
```
\

To solve for $h$ algebraically, first identify that both definitions of $g$ must work, so for all $x$:

$$`r A`\cdot `r base`^{x} = `r base`^{x+h}$$

Use the identity $a^{b+c}\equiv a^ba^c$.
$$`r A`\cdot `r base`^{x} = `r base`^{x}\cdot`r base`^{h}$$

Divide both sides by $`r base`^x$.
$$`r A` = `r base`^{h}$$
Solve this equation using logarithms.

$$h=`r h`$$



Meta-information
============
extype: num
exsolution: `r h`
exname: exp_stretch_shift_equiv
extol: 0.01