```{r data generation, echo = FALSE, results = "hide"}
# S-IC.B.4: Use data from a sample survey to estimate a population mean or proportion; develop a margin of error through the use of simulation models for random sampling.

while(T){
  n = sample(8:12,1)
  mu = runif(1,400,600)
  sig = runif(1,mu/50,mu/10)
  x = round(rnorm(n,mu,sig),0)
  xbar = round(mean(x))
  lbs = numeric()
  ubs = numeric()
  for(i in 1:1000){
    xx = matrix(sample(x,n*1000,T),nrow=1000)
    avs = sort(apply(xx,1,mean))
    lb = avs[25]
    lbs = c(lbs,lb)
    ub = avs[975]
    ubs = c(ubs,ub)
  }
  
  lbs = sort(lbs)
  ubs = sort(ubs)
  
  lb = round(lbs[500],0)
  ub = round(ubs[500],0)
  me = round((ub-lb)/2,0)
  
  dlb = max(lbs)-min(lbs)
  dub = max(ubs)-min(ubs)
  del = ceiling(max(dlb,dub))+1
  
  xbopts = round(xbar+(-sample(0:4,1)+0:4)*2)
  xbal = paste0("* ",xbopts,collapse="\n")
  xbsol = paste0(1*(xbar==xbopts),collapse="")
  
  lbopts = round(lb+(-sample(0:4,1)+0:4)*del)
  ubopts = round(ub+(-sample(0:4,1)+0:4)*del)
  meopts = round(me+(-sample(0:4,1)+0:4)*del)
  lbal = paste0("* ",lbopts,collapse="\n")
  ubal = paste0("* ",ubopts,collapse="\n")
  meal = paste0("* ",meopts,collapse="\n")
  lbsol = paste0(1*(lb==lbopts),collapse="")
  ubsol = paste0(1*(ub==ubopts),collapse="")
  mesol = paste0(1*(me==meopts),collapse="")
  if(del>1 && min(meopts)>0){break}
}



```

Question
========

*S-IC.B.4: Use data from a sample survey to estimate a population mean or proportion; develop a margin of error through the use of simulation models for random sampling.*

A scientist wants to estimate the average mass of adult lab rats under certain conditions. She randomly selects a sample of $n=`r n`$ mice from the population, and finds their masses in grams, to the nearest gram.

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab_data, echo=FALSE, results="asis"}
opts <- options(knitr.kable.NA = "")
mydf = data.frame(matrix(x,nrow = 1))
colnames(mydf) = rep(" ",n)
knitr::kable(mydf,format="html",col.names = NULL,label = NA, align = "c",row.names=F,table.attr='class="bordered-table"')
```
\

Your goals are:

* Decide a best estimate for the population mean. (Hint: the sample mean.)
* Find a 95% [confidence interval](https://en.wikipedia.org/wiki/Confidence_interval) by [resampling](https://en.wikipedia.org/wiki/Resampling_(statistics)#Bootstrap) 1000 times.
* Find the margin of error (by dividing the interval width by 2).

Your answers (pick closest to your answer):

* What is the best estimate for the population mean? ##ANSWER1## grams.
* Lower boundary of confidence interval = ##ANSWER2## grams.
* Upper boundary of confidence interval = ##ANSWER3## grams.
* Margin of error = ##ANSWER4##


Answerlist
--------

`r xbal`
`r lbal`
`r ubal`
`r meal`



Solution
========

* The best guess for the population mean is the sample mean. $\bar{x}=`r xbar`$.
* The lower boundary = `r lb`
* The upper boundary = `r ub`
* The margin of error $= \frac{`r ub`-`r lb`}{2} = `r me`$

Use a [new spreadsheet](https://sheets.new).

```{r,echo=F}
LETS = c(LETTERS)
for(i in LETTERS){
  LETS = c(LETS,paste0(i,LETTERS))
}

l1 = LETS[n]
l2 = LETS[n+4]
l3 = LETS[2*n+4]
l4 = LETS[n+2]

if(2*n+3>26){
  txt = "(You may need to add columns.)"
} else {
  txt = ""
}
```

* Paste data into A1:`r l1`1.
* To find sample mean, in cell C3, type ``=AVERAGE(A1:`r l1`1)``.
* The key formula for resampling will be ``=INDEX($A$1:$`r l1`$1,1,RANDBETWEEN(1,`r n`))``.
* In all cells from `r l2`1 to `r l3`1, put the formula. `r txt`
* Notice there are `r n` values, just like the original sample. However there will be more repetition, because these `r n` values are made by resampling [with replacement](https://en.wikipedia.org/wiki/Sampling_(statistics)#Replacement_of_selected_units).
* To repeat 1000 times, select range `r l2`1:`r l3`1 and use `ctrl+shift+down` and `ctrl+enter`.
* Now, we want an average for each row. In `r l4`1 write `=AVERAGE(`r l2`1:`r l3`1)`.
* Copy the average formula down for all rows. You now have 1000 averages from resampling.
* Freeze the page with `ctrl+a` to select everything, `ctrl+c` to copy, and `ctrl+shift+v` to paste values only.
* Sort column `r l4`.
* In an empty cell, type ``=`r l4`25``. In another empty cell, type ``=`r l4`975``. These are the boundaries of the 95%  confidence interval.

To find the margin of error, find half the difference of the boundaries.


Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r xbsol`|`r lbsol`|`r ubsol`|`r mesol`
exname: resample_mean_ME