```{r data generation, echo = FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE)
options(scipen=100)

posright = sample(1:4,1)

while(T){
  shape1 = runif(1,0.3,5)
  shape2 = runif(1,0.3,5)
  mubasic = shape1/(shape1+shape2)
  offset = runif(1,10,80)
  multer = runif(1,2,20)
  n = sample(25:49,1)
  x = round(rbeta(n,shape1,shape2)*multer+offset,1)
  
  xbar = mean(x)
  s = sd(x)
  LB = round(xbar-2*s/sqrt(n),1)
  UB = round(xbar+2*s/sqrt(n),1)
  
  lba = round(xbar-2*s/n,1)
  uba = round(xbar+2*s/n,1)
  lbb = round(xbar-s/sqrt(n),1) 
  ubb = round(xbar+s/sqrt(n),1)
  lbc = round(xbar-2*s,1)
  ubc = round(xbar+2*s,1)
  lbd = round(xbar-s,1)
  ubd = round(xbar+s,1)
  lbe = round(xbar-4*s/sqrt(n),1)
  ube = round(xbar+4*s/sqrt(n),1)
  lbf = round(xbar-s/sqrt(n)/2,1)
  ubf = round(xbar+s/sqrt(n)/2,1)
  lbh = round(xbar-s/sqrt(n)/4,1)
  ubh = round(xbar+s/sqrt(n)/4,1)
  
  tightlb = c(lba,lbb,lbf,lbh)
  tightub = c(uba,ubb,ubf,ubh)
  widelb = c(lbc,lbd,lbe)
  wideub = c(ubc,ubd,ube)
  
  
  tightpicks = sample(1:length(tightlb),posright-1)
  widepicks = sample(1:length(widelb),4-posright)
  
  ansli1 = sort(c(tightlb[tightpicks],LB,widelb[widepicks]))
  ansli2 = sort(c(tightub[tightpicks],UB,wideub[widepicks]))
  
  s1 = paste0((ansli1==LB)*1,collapse="")
  s2 = paste0((ansli2==UB)*1,collapse="")
  if(length(unique(ansli1))==4 && min(diff(ansli1))>0.2){break}
}
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

A scientist measured weights of a [simple-random sample](https://en.wikipedia.org/wiki/Simple_random_sample){target="_blank"} of a newly discovered organism. Those weights are given below (in grams):

```{r tab_data, echo=FALSE, results="asis"}
opts <- options(knitr.kable.NA = "")
knitr::kable(data.frame(x),format="html", align = "c",row.names=F,table.attr='class="bordered-table"')
```
\


The scientist hopes to construct a 95% [**confidence interval**](https://en.wikipedia.org/wiki/Confidence_interval){target="blank"} of the organism's [*population mean*](https://en.wikipedia.org/wiki/Statistical_population#Mean){target="_blank"} weight ($\mu$).

The scientist will later consult a statistician for a more precise method, but for now they will use a quick method to estimate the 95% confidence interval:
$$\text{CI boundaries} = \bar{x}\pm \frac{2s}{\sqrt{n}} $$


In [interval notation](https://en.wikipedia.org/wiki/Interval_(mathematics)#Notations_for_intervals){target="_blank"}, the confidence interval is  [##ANSWER1##, ##ANSWER2##].


Answerlist
--------
* `r ansli1[1]`
* `r ansli1[2]`
* `r ansli1[3]`
* `r ansli1[4]`
* `r ansli2[1]`
* `r ansli2[2]`
* `r ansli2[3]`
* `r ansli2[4]`


Solution
========

Find the sample mean (use `=average()` in spreadsheet.)
$$\bar{x}=`r xbar`$$
Find the sample standard deviation (use `=stdev()` in spreadsheet.)
$$s = `r s`$$
Find the sample size (use `=count()` in spreadsheet.)
$$n = `r n`$$

Plug the numbers into the expressions.

* Lower bound = $`r xbar`-2(`r s`)/\sqrt{`r n`} ~=~ `r LB`$
* Upper bound = $`r xbar`+2(`r s`)/\sqrt{`r n`} ~=~ `r UB`$

Using [interval notation](https://en.wikipedia.org/wiki/Interval_(mathematics)#Notations_for_intervals){target="_blank"}, the 95% confidence interval is [`r LB`, `r UB`].


Meta-information
================
extype: cloze
exsolution: `r s1`|`r s2`
exclozetype: schoice|schoice
exname: confidence interval simple MC
