```{r data generation, echo = FALSE, results = "hide"}
# S-IC.B.5: Use data from a randomized experiment to compare two treatments; use simulations to decide if differences between parameters are significant.

names_vector <- c(
  "Aria",   # A
  "Bodhi",  # B
  "Celia",  # C
  "Dante",  # D
  "Elara",  # E
  "Fabian", # F
  "Ginevra",# G
  "Hugo",   # H
  "Ilaria", # I
  "Jovan",  # J
  "Kaia",   # K
  "Luca",   # L
  "Mila",   # M
  "Niko",   # N
  "Orla",   # O
  "Piero",  # P
  "Quinn",  # Q
  "Rhea",   # R
  "Soren",  # S
  "Talia",  # T
  "Ulises", # U
  "Veda",   # V
  "Wendell",# W
  "Xena",   # X
  "Yara",   # Y
  "Zara"    # Z
)

names = sort(sample(names_vector,2))
p1 = names[1]
p2 = names[2]

is_diff_signif = sample(c(T,F),1)

if(is_diff_signif){
    bnds = c(960,999)
    bt = c(950,1000)
    bi = 5
    q7sol = "10"
    q8sol = "10"
    sym = "<"
    sigwrd = ""
} else {
    bi = sample(1:4,1)
    bnds = list(c(605,695),c(705,795),c(805,895),c(902,948))[[bi]]
    bt = list(c(600,700),c(700,800),c(800,900),c(900,950))[[bi]]
    q7sol = "01"
    q8sol = "01"
    sym = "\\ge"
    sigwrd = "NOT"
}

posses = list(c(600,700),c(700,800),c(800,900),c(900,950),c(950,1000))
solbnd = posses[[bi]]

q4al = c("* (600,700)\n* (700,800)\n* (800,900)\n* (900,950)\n* (950,1000)")
q5al = c("* (0,50)\n* (50,100)\n* (100,200)\n* (200,300)\n* (300,400)")
q6al = c("* (0,0.05)\n* (0.05,0.1)\n* (0.1,0.2)\n* (0.2,0.3)\n* (0.3,0.4)")
q7al = c("* Yes. The observed difference is significant.\n* No. The observed difference is not significant.")
q8al = c("* Yes.\n* No.")

q4sol = paste0(1*(1:5==bi),collapse="")
q5sol = paste0(1*(1:5==(6-bi)),collapse="")
q6sol = paste0(1*(1:5==(6-bi)),collapse="")



while(T){
    mu = 220
    siga = sample(8:30,1)
    sigb = siga*2^runif(1,-1,1)
    sig = sample(c(siga,sigb))
    ns = sample(6:12,2)
    app_mes = sig*2/sqrt(ns)
    app_me_diff = sqrt(sum(app_mes^2))*sample(c(-1,1),1)
    mu1 = mu-app_me_diff/2
    mu2 = mu+app_me_diff/2
    n1 = ns[1]
    n2 = ns[2]
    sig1 = sig[1]
    sig2 = sig[2]
    sam1 = round(rnorm(n1,mu1,sig1))
    sam2 = round(rnorm(n2,mu2,sig2))
    xbd = abs(mean(sam2)-mean(sam1))
    rsd = numeric()
    howmany = numeric()
    for(i in 1:100){
        for(i in 1:1000){
            shuff = sample(c(sam1,sam2))
            rs1 = shuff[1:n1]
            rs2 = shuff[(n1+1):(n1+n2)]
            rsd = c(rsd,abs(mean(rs2)-mean(rs1)))
        }
        howmany = c(howmany,sum(rsd<xbd))
        rsd = numeric()
        if(min(howmany)<bnds[1]+1 || max(howmany)>bnds[2]-1 || xbd<1){
            break
        }
    }
    if(length(howmany)==100){break}
}

xbar1 = round(mean(sam1),3)
xbar2 = round(mean(sam2),3)
obs_adm = abs(xbar2-xbar1)

opts_al_sol = function(value,del,nchoice){
    bbb = nchoice-1
    opts = value-sample(0:bbb,1)*del+(0:bbb)*del
    al = paste0("* ",opts,collapse="\n")
    sol = paste0(1*(value==opts),collapse="")
    return(list(opts,al,sol))
}

xbar1oas = opts_al_sol(xbar1,1,4)
xbar2oas = opts_al_sol(xbar2,1,4) 
odoas = opts_al_sol(abs(xbar2-xbar1),1,4)

ALs = character()
SOLs = character()

for(i in 1:5){
    b1b2 = posses[[i]]
}



if(xbar1>xbar2){
    better = p1
    worse = p2
} else {
    better = p2
    worse = p1
}

if(is_diff_signif){
    q8sent = paste0("Because the difference is significant, and we know ",better," scored higher, we can say ",better," is a more skilled archer than ",worse,".")
} else {
    q8sent = paste0("Because the difference is NOT significant, we are left with two possibilities: either they are equally skilled archers or need more data to detect the difference in skill.")
}

```

Question
========

*S-IC.B.5: Use data from a randomized experiment to compare two treatments; use simulations to decide if differences between parameters are significant.*

`r p1` and `r p2` wonder if they are equally skilled at archery. They decide to compare this year's scores using a two-tail [approximate permutation test](https://en.wikipedia.org/wiki/Permutation_test), using a significance level of 5%.

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>


```{r tab_data, echo=FALSE, results="asis"}
opts <- options(knitr.kable.NA = "")
ml = max(length(sam1),length(sam2))
sa1 = c(sam1,rep(NA,ml-length(sam1)+1))
sa2 = c(sam2,rep(NA,ml-length(sam2)+1))
mydf = data.frame(sa1,sa2)
colnames(mydf) = c(p1,p2)
knitr::kable(mydf,format="html", align = "c",row.names=F,table.attr='class="bordered-table"')
```
\

```{r,echo=F}
sampool = c(sam1,sam2)
lo = floor(min(sampool)/10)*10
hi = ceiling(max(sampool)/10)*10
plot1 <- hist(sam1,breaks=seq(lo,hi,10),plot=F)                    
plot2 <- hist(sam2,breaks=seq(lo,hi,10),plot=F)
dens1 = (plot1$counts)/n1
dens2 = (plot2$counts)/n2
mxden = max(c(dens1,dens2))
plot(plot1, col=rgb(0,0,1,1/4), xlim=c(lo,hi), ylim=c(0,max(c(plot1$counts,plot2$counts))*1.1),
     main=paste0(""),
     xlab="score",xaxt = "n")
plot(plot2, col=rgb(1,0,0,1/4), add=T)
cnts1 = numeric()
axis(1,at=seq(lo,hi,10))
legend("topleft",legend=c(p1,p2),fill=c(rgb(0,0,1,1/4),rgb(1,0,0,1/4)),)
```
\

To run the test, first calculate the observed absolute difference of sample means.

* `r p1`'s sample mean = $\bar{x}_1 =$ ##ANSWER1##
* `r p2`'s sample mean = $\bar{x}_2 =$ ##ANSWER2##
* The absolute difference = $|\bar{x}_2 - \bar{x}_1| =$ ##ANSWER3##

## Permutation Test

1. Reshuffle those two samples 1000 times. I'd recommend [this tool](https://chadworley.github.io/a2/tools/two_list_reshuffler.html), which wants comma-separated data, so here are the samples in that format:

    `r paste0(sam1,collapse=", ")`

    `r paste0(sam2,collapse=", ")`

    Notice this reshuffling is equivalent to putting all the scores on cards, shuffling them all together, and then dealing into two piles (repeated 1000 times). Notice, `r p1` had `r n1` scores, so one pile always gets `r n1` numbers, and the other pile gets `r n2` numbers. We are simulating the hypothesis that maybe both people's sample came from equivalent populations with a difference of sample means from natural variation, not unequal skill. We will then see if the observed difference is copacetic with the simulated differences.

2. Paste the 1000 rows into a spreadsheet.
3. For each row, find the absolute difference of the means. Remember, spreadsheets have `=ABS()` for absolute value and `=AVERAGE()` to find a mean.
4. How many times was the simulation's absolute difference of means smaller than the observed absolute difference of means. (Choose an interval.)

* ##ANSWER4##

5. How many times was the simulation's difference as big or bigger than the observation's difference? (Choose an interval.)

* ##ANSWER5##

6. What **proportion** of the time was the simulation as big or bigger? (In statistics this is called the $p$-value.) (Choose an interval.)

* ##ANSWER6##

7. If the $p$-value is less than 0.05, then the difference is significant. Otherwise, the difference is not significant. Is the difference significant?

* ##ANSWER7##

8. So, then, can we conclude that `r better` is significantly better than `r worse` at archery?

* ##ANSWER8##

Answerlist
--------

`r xbar1oas[2]`
`r xbar2oas[2]`
`r odoas[2]`
`r q4al`
`r q5al`
`r q6al`
`r q7al`
`r q8al`



Solution
========

* $\bar{x}_1= `r xbar1`$
* $\bar{x}_2= `r xbar2`$
* $|\bar{x}_2-\bar{x}_1| = `r obs_adm`$
* Your number of sim diffs less than the obs diff "should" be between `r min(howmany)` and `r max(howmany)`. So you would pick interval $(`r solbnd[1]`,`r solbnd[2]`)$.
* Your number of sim diffs greater than or equal to the obs diff "should" be between `r min(1000-howmany)` and `r max(1000-howmany)`. So you would pick interval $(`r 1000-solbnd[2]`,`r 1000-solbnd[1]`)$.
* Your $p$-value should be between `r min(1000-howmany)/1000` and `r max(1000-howmany)/1000`. So, you would pick interval $(`r round((1000-solbnd[2])/1000,4)`,`r round((1000-solbnd[1])/1000,4)`)$
* `r if(is_diff_signif){"Yes. The difference is significant."}else{"No. The difference is not significant."}`
* `r if(is_diff_signif){paste0("Yes. There is a detectible difference, and ",better," scored higher on average",collapse="")}else{"No. They either have equal population means or need more data to detect the difference."}`

### Sample means (Questions 1 and 2)

$$\bar{x}_1=\frac{`r paste0(sam1,collapse="+")`}{`r n1`} = `r xbar1`$$

$$\bar{x}_2=\frac{`r paste0(sam2,collapse="+")`}{`r n2`} = `r xbar2`$$

### Observed absolute difference of means (Question 3)

$$|\bar{x}_2-\bar{x}_1| ~=~ |`r xbar2`-`r xbar1`| ~=~ `r obs_adm`$$

### Simulation  (Question 4)

1. Use the [two-list reshuffler](https://chadworley.github.io/a2/tools/two_list_reshuffler.html) with 1000 rows. You'll notice that `r p1` had `r n1` scores and `r p2` had `r n2` scores. You should picture each score written on a card in a deck of `r n1+n2` cards. You then shuffle the cards and deal them back into two piles with `r n1` cards and `r n2` cards.

```{r,echo=F}
LETS = c(LETTERS)
for(i in LETTERS){
  LETS = c(LETS,paste0(i,LETTERS))
}
g1r = LETS[n1]
g2l = LETS[n1+2]
g2r = LETS[n1+n2+2]
col_adm = LETS[n1+n2+4]
col_test = LETS[n1+n2+5]
col_work = LETS[n1+n2+6]
```

2. Copy all the data into a [new spreadsheet](https://sheets.new). Click on A1 and paste (`ctrl+v`) to use A2:`r g2r`1001 to hold the data. (The first row with be a header with labels.)

3. With each repetition (row) you should find an absolute difference of means. You might need to add some more columns to the right of the data to follow these instructions. 
    * *An easy way to add a bunch of columns: press `ctrl+a`, maybe twice, to highlight all rows and columns; click `Insert>Columns>Columns to the right`.*

    In cell `r col_adm`2, calculate the absolute difference of means with ``=ABS(AVERAGE(A2:`r g1r`2)-AVERAGE(`r g2l`2:`r g2r`2))``. Hit Enter. Select `r col_adm`2. Hit `ctrl+shift+down` and `ctrl+enter` to copy the formula down the whole column. You now have the 1000 simulated differences.

4. Personally, I would now sort the sheet by column `r col_adm`.

5. Now, we want to compare each (absolute) difference to the observed difference of `r obs_adm`. To do that, in cell `r col_test`2 write ``=IF(`r col_adm`2 < `r obs_adm`, 1, 0)``. Hit `Enter`. Click back on cell `r col_test`2; type `ctrl+shift+down` and `ctrl+enter` to copy the formula down. 

6. Count how many 1s (trues) there are. In cell `r col_work`2, write ``=SUM(`r col_test`:`r col_test`)`` to count up the ones.
    * I should mention that you could have just used ``=COUNTIF(`r col_adm`:`r col_adm`,"<`r obs_adm`")``.
    
    You have your answer to question 4. I've made a visualization of my simulation. Your simulated data will be different but similar.
    
    ```{r,fig.dim=c(6,6),echo=F}
while(T){
    rsd = numeric()
    for(i in 1:1000){
        shuff = sample(c(sam1,sam2))
        rs1 = shuff[1:n1]
        rs2 = shuff[(n1+1):(n1+n2)]
        rsd = c(rsd,abs(mean(rs2)-mean(rs1)))
    }
    plt1 = hist(rsd,plot = F,breaks=100)
    num = sum(plt1$counts[plt1$mids<obs_adm])
    num2 = num
    if(bnds[1]<num && num<bnds[2]){
        break
    }
}

plot(0,0,"n",
    xlim=c(0,max(c(plt1$breaks,rsd))),
    ylim=c(-max(plt1$counts)/10,max(plt1$counts)*1.1),
    main="1000 shuffles vs. observation",
    xlab="absolute difference of means",
    ylab="frequency")
for(i in 1:length(plt1$mids)){
    for(j in 1:plt1$counts[i]){
        if(plt1$mids[i]<obs_adm){
            col = rgb(0,0,1,0.5)
        } else {
            col = rgb(1,0,0,0.5)
        }
        if(plt1$counts[i]>0){
            points(plt1$mids[i],j,pch=19,cex=0.2,col=col)
        }
    }
}
bbb = max(plt1$counts)/10
bb2 = bbb*10
abline(h=0)
polygon(c(0,0,obs_adm,obs_adm),c(0,bb2*1.05,bb2*1.05,0),border="blue")
text(obs_adm/2,bb2*1.075,num2,col="blue")
polygon(c(obs_adm,obs_adm,max(c(plt1$breaks,rsd)),max(c(plt1$breaks,rsd))),c(0,bb2*1.05,bb2*1.05,0),border="red")
text((obs_adm+max(rsd))/2,bb2*1.075,1000-num2,col="red")
lines(c(obs_adm,obs_adm),c(bb2*1.05,-bbb/2),col="purple")
text(obs_adm,-3*bbb/4,sprintf("%.3f",obs_adm),col="purple")  
    ```
    \

    For these instructions, we will say the answer to question 4 is `r num2`.
    
## Question 5    
    
To get the answer to question 5, give the absolute difference between your answer to question 4 and 1000. So, for my simulation: $1000-`r num2`=`r 1000-num2`$.

## Question 6

Divide your answer to question 5 by 1000. So, for my simulation:
$$p\mathrm{-value} = `r (1000-num2)/1000`$$

## Question 7

Because $p-\mathrm{value} `r sym` 0.05$, we say the difference is `r sigwrd` significant.

## Question 8

`r q8sent`


Meta-information
================
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r xbar1oas[3]`|`r xbar2oas[3]`|`r odoas[3]`|`r q4sol`|`r q5sol`|`r q6sol`|`r q7sol`|`r q8sol`
exname: reshuffle_two_mean_test