```{r data generation, echo = FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE)
options(scipen=100)

while(T){
  n = sample(16:25,2)
  n1 = n[1]
  n2 = n[2]
  sigma1 = runif(1,10,50)
  sigma2 = sigma1*runif(1,0.6,1/0.6)
  se = sqrt(sigma1^2/n[1]+sigma2^2/n[2])
  me = 2*se
  mu1 = runif(1,200,600)
  mu2 = mu1+sample(c(-1,1),1)*me
  x1 = round(rnorm(n1,mu1,sigma1),1)
  x2 = round(rnorm(n2,mu2,sigma2),1)
  xbar1 = mean(x1)
  xbar2 = mean(x2)
  xbar1r = round(xbar1,1)
  xbar2r = round(xbar2,1)
  s1 = sd(x1)
  s2 = sd(x2)
  s1r = round(s1,1)
  s2r = round(s2,1)
  df = (s1^2/n1+s2^2/n2)^2/(s1^4/n1^2/(n1-1)+s2^4/n2^2/(n2-1))
  t = abs(xbar1-xbar2)/sqrt(s1^2/n1+s2^2/n2)
  cump = pt(t,df)
  pval = 2*(1-cump)
  if(pval<0.2 & pval>0.005 & abs(pval-0.05)>0.01){break}
}

x1rep = x1
x2rep = x2

if(pval<0.05){
  ans2="10"
  s2="The $p$-value is less than 0.05, so the result is significant."
} else {
  ans2="01"
  s2="The $p$-value is more than 0.05, so the result is NOT significant."
}

default_source_hook <- knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(xx, options) {
  xx <- gsub('x1rep',paste(x1,collapse=","),xx)
  xx <- gsub('x2rep',paste(x2,collapse=","),xx)
  default_source_hook(xx, options)
})

```

Question
========

A doctor runs a [controlled experiment](https://en.wikipedia.org/wiki/Randomized_controlled_trial){target="blank"}. The participants are randomly assigned to two groups: control and treatment. The participants in the control group are given a [placebo](https://en.wikipedia.org/wiki/Placebo-controlled_study){target="blank"}. The participants in the treatment group are given a drug. After several months, each participant's triglyceride level is measured (in mg/dL). 

```{r}
len = max(n1,n2)
if(n1>n2){
  x1d = x1
  x2d = c(x2,rep(NA,n1-n2))
  x1s = sprintf(x1, fmt = '%#.2f')
  x2s = c(sprintf(x2, fmt = '%#.2f'),rep("      ",n1-n2))
} else {
  x2d = x2
  x1d = c(x1,rep(NA,n2-n1))
  x2s = sprintf(x2, fmt = '%#.2f')
  x1s = c(sprintf(x1, fmt = '%#.2f'),rep("      ",n2-n1))
}
data = data.frame(x1d,x2d)
colnames(data) = c("x1","x2")
```

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab_data, echo=FALSE, results="asis"}
opts <- options(knitr.kable.NA = "")
knitr::kable(data,format="html", align = "cccc",row.names=F,table.attr='class="bordered-table"')
```
\


You are asked to perform a two-tail [two-sample Welch's $t$ test](https://en.wikipedia.org/wiki/Welch%27s_t-test){target="blank"} to determine whether there is a significant difference of means in the two samples.


* Determine the $p$-value. Answers within a tolerance of 0.005 will be accepted.

Remember, if $p$-value$<0.05$, the difference is significant. Otherwise, the difference is not significant.


Solution
========

Use a spreadsheet. Copy the data over to a [new sheet](https://sheets.new).

```{r}
spacer=rep("",length(x1d))
eq = c("","=T.TEST(A:A,B:B,2,3)",rep("",length(x1d)-2))
sol = data.frame(x1d,x2d,spacer,eq)
colnames(sol)=c("x1","x2","","")
```

You just need to use `T.TEST` with the proper settings. 

```{r fig.height=5,fig.width=6}
draw_ss = function(df,widths=rep(1,length(df[1,])+1)){
  xline = c(0,cumsum(widths)/sum(widths))
  nrow = length(df[,1])
  ncol = length(df[1,])
  xtex = (xline[2:(ncol+2)]+xline[1:(ncol+1)])/2
  par(mar=c(0,0,0,0))
  plot(0,0,type="n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
  hi = 1:((nrow+2)*2+1)
  vi = 1:((ncol+1)*2+1)
  hpos = seq(1,0,length.out=(nrow+2)*2+1)
  vpos = seq(0,1,length.out=(ncol+1)*2+1)
  hlin = hpos[hi%%2==1]
  ytex = hpos[hi%%2==0]
  vlin = vpos[vi%%2==1]
  #xtex = vpos[vi%%2==0]
  abline(h=hlin)
  abline(h=hlin[2],lwd=3)
  abline(v=xline)
  abline(v=xline[2],lwd=3)
  for(i in 2:(ncol+1)){
    text(xtex[i],ytex[1],LETTERS[i-1],col=rgb(0.5,0.5,0.5))
    text(xtex[i],ytex[2],colnames(df)[i-1])
  }    
  for(i in 2:(nrow+2)){
    text(xtex[1],ytex[i],i-1,col=rgb(0.5,0.5,0.5))
  }
  for(i in 1:nrow){
    for(j in 1:ncol){
      text(xtex[j+1],ytex[i+2],df[i,j])
    }
  }
}
draw_ss(sol[1:9,],c(0.4,1,1,0.5,3))
```
\

The $p-\mathrm{value}$ equals `r round(pval,4)`. 

`r s2`


Meta-information
================
extype: num
exsolution: `r pval`
exname: hypothesis test 2 means
extol: 0.005
