---
title: "Bootstrapping Confidence Intervals"
output: slidy_presentation
---

# Learning Objective

* S-IC.B.4: Use data from a sample survey to estimate a population mean or proportion; develop a margin of error through the use of simulation models for random sampling.

# Confidence Interval

* A [confidence interval](https://en.wikipedia.org/wiki/Confidence_interval) is used to express uncertainty about a population mean (or proportion).
* Imagine repeating the process of:
    * Gathering a simple random sample,
    * calculating the sample mean ($\bar{x}$) and sample standard deviation ($s$),
    * calculating a confidence interval (lower boundary and upper boundary) using:
        * [bootstrapping](https://en.wikipedia.org/wiki/Bootstrapping_(statistics)) (if $n$ is small and distribution is maybe not bell shaped) or 
        * $\bar{x}\pm\frac{2s}{\sqrt{n}}$ if $n$ is sufficiently large or we know the population is bell shaped.
* The true population mean ($\mu$) will be in the confidence interval 95% of the time.
* [Misinterpretations are common](https://en.wikipedia.org/wiki/Confidence_interval#Common_misunderstandings), even among professionals.


# Bootstrapping

* The most robust approach to calculating confidence intervals is with repeated [resampling](https://en.wikipedia.org/wiki/Resampling_(statistics)).
* The steps are *very* similar to how we got intervals of typical means. The key new step is that we resample, with replacement, from the actual sample.
* In a spreadsheet, we will resample with replacement by using the [`=INDEX()` function](https://support.google.com/docs/answer/3098242?hl=en) mixed with a `RANDBETWEEN()`.
* Process:
    * Get a sample of data.
    * Resample with replacement 1000 times.
    * For each resample, calculate a mean.
    * Find the 2.5th percentile and the 97.5th percentile. These are the boundaries of the 95% confidence interval.
    * Calculate the half-width (radius) of the interval. This is your margin of error.
* Let's look at an example of resampling on the next two slides.

# Example of resampling

```{r,echo=F}
set.seed(1)
xxx = sample(430:450,5,F)
xxx = c(xxx,sample(xxx,5*6,T))
xxx = matrix(xxx,ncol=5,byrow = T)
xxx[2,] = rep("",5)
data = data.frame(xxx)
```

```{r fig.width=5,fig.height=5,echo=F}
draw_ss = function(df,widths=rep(1,length(df[1,])+1)){
  xline = c(0,cumsum(widths)/sum(widths))
  nrow = length(df[,1])
  ncol = length(df[1,])
  xtex = (xline[2:(ncol+3)]+xline[1:(ncol+2)])/2
  par(mar=c(0,0,0,0))
  plot(0,0,type="n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
  hi = 1:((nrow+2)*2+1)
  vi = 1:((ncol+1)*2+1)
  hpos = seq(1,0,length.out=(nrow+2)*2+1)
  vpos = seq(0,1,length.out=(ncol+1)*2+1)
  hlin = hpos[hi%%2==1]
  ytex = hpos[hi%%2==0]
  vlin = vpos[vi%%2==1]
  #xtex = vpos[vi%%2==0]
  abline(h=hlin)
  abline(h=hlin[2],lwd=3)
  abline(v=xline)
  abline(v=xline[2],lwd=3)
  for(i in 2:(ncol+2)){
    text(xtex[i],ytex[1],LETTERS[i-1],col=rgb(0.5,0.5,0.5))
    #text(xtex[i],ytex[2],colnames(df)[i-1])
  }    
  for(i in 2:(nrow+2)){
    text(xtex[1],ytex[i],i-1,col=rgb(0.5,0.5,0.5))
  }
  for(i in 1:nrow){
    for(j in 1:ncol){
      text(xtex[j+1],ytex[i+1],df[i,j])
    }
  }
}
draw_ss(data)
```
\

* The first row is our original sample.
* The other rows are generated by sampling from the first row, **with replacement**.
* Notice that even though the first row has no repeats, the other rows do!


# Example of resampling

```{r,echo=F}
set.seed(1)
xxx = sample(430:450,5,F)
xxx = c(xxx,sample(xxx,5*6,T))
xxx = matrix(xxx,ncol=5,byrow = T)
xxx[2,] = rep("",5)
xxx[3,] = rep("=INDEX($A$1:$E$1,1,RANDBETWEEN(1,5))",5)
xxx[4,] = rep("=INDEX($A$1:$E$1,1,RANDBETWEEN(1,5))",5)
xxx[5,] = rep("=INDEX($A$1:$E$1,1,RANDBETWEEN(1,5))",5)
xxx[6,] = rep("=INDEX($A$1:$E$1,1,RANDBETWEEN(1,5))",5)
xxx[7,] = rep("=INDEX($A$1:$E$1,1,RANDBETWEEN(1,5))",5)

data = data.frame(xxx)
```

```{r fig.width=30,fig.height=5,echo=F}
draw_ss = function(df,widths=rep(1,length(df[1,])+1)){
  xline = c(0,cumsum(widths)/sum(widths))
  nrow = length(df[,1])
  ncol = length(df[1,])
  xtex = (xline[2:(ncol+3)]+xline[1:(ncol+2)])/2
  par(mar=c(0,0,0,0))
  plot(0,0,type="n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
  hi = 1:((nrow+2)*2+1)
  vi = 1:((ncol+1)*2+1)
  hpos = seq(1,0,length.out=(nrow+2)*2+1)
  vpos = seq(0,1,length.out=(ncol+1)*2+1)
  hlin = hpos[hi%%2==1]
  ytex = hpos[hi%%2==0]
  vlin = vpos[vi%%2==1]
  #xtex = vpos[vi%%2==0]
  abline(h=hlin)
  abline(h=hlin[2],lwd=3)
  abline(v=xline)
  abline(v=xline[2],lwd=3)
  for(i in 2:(ncol+2)){
    text(xtex[i],ytex[1],LETTERS[i-1],col=rgb(0.5,0.5,0.5))
    #text(xtex[i],ytex[2],colnames(df)[i-1])
  }    
  for(i in 2:(nrow+2)){
    text(xtex[1],ytex[i],i-1,col=rgb(0.5,0.5,0.5))
  }
  for(i in 1:nrow){
    for(j in 1:ncol){
      text(xtex[j+1],ytex[i+1],df[i,j])
    }
  }
}
draw_ss(data,c(1,10,10,10,10,10))
```
\

# Practice bootstrapping

[https://chadworley.github.io/a2/u02/outhtml/05_resample_mean_ME.html](https://chadworley.github.io/a2/u02/outhtml/05_resample_mean_ME.html)
