```{r data generation, echo = FALSE, results = "hide"}

## FIX THE LATER ROWS WITH ROUNDING!!

while(T){
    r = sort(signif(runif(4,1,10),3))
    if(min(diff(r))>1){break}
}
d = signif(r*2,3)
c = signif(2*pi*r,3)
a = signif(pi*r^2,3)

as = c(d[1],c[1],a[1],
        r[2],c[2],a[2],
        r[3],d[3],a[3],
        r[4],d[4],c[4])

als = character()
sols = character()
for(aa in as){
    ac = signif(aa*1.05^(sample(-4:0,1)+0:4),3)
    sols = c(sols,paste0(1*(ac==aa),collapse=""))
    als = c(als,paste0("* ",ac,collapse="\n"))
}
al = paste0(als,collapse="\n")

```



Question
========

A 2D circle is the collection of points that are equally far from its center point. That distance from the center to the edge is called the radius ($r$). The distance across the circle, through the center, is called the diameter ($d$). The distance going all the way around the edge is called the circumference ($c$). Lastly, the area ($A$) can be calculated from the radius.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1.2,1.2),ylim=c(-1.2,1.2),axes=F,ann=F)
th = seq(0,2*pi,pi/100)
polygon(cos(th),sin(th),col=rgb(1,1,0.8))
lines(cos(th),sin(th),col="blue",lwd=2)
lines(c(0,cos(pi/3)),c(0,sin(pi/3)),col="red",lwd=2)
lines(c(-1,1),c(0,0),col="purple",lwd=2)
text(0.3,0.4,"r",col="red")
text(0,-0.1,"d",col="purple")
text(-0.8,0.8,"c",col="blue")
text(-0.4,0.4,"A",col=rgb(0.7,0.7,0.3),cex=2)

```
\

Here are the formulas people memorize:

$$d = 2r$$
$$c = \pi d$$

$$A=\pi r^2$$

Fill out the table below.

|          |    $r$      |     $d$     |     $c$     |     $A$     |
|:--------:|:-----------:|:-----------:|:-----------:|:-----------:|
| circle 1 | `r r[1]`    | ##ANSWER1## | ##ANSWER2## | ##ANSWER3## |
| circle 2 | ##ANSWER4## |   `r d[2]`  | ##ANSWER5## | ##ANSWER6## |
| circle 3 | ##ANSWER7## | ##ANSWER8## |   `r c[3]`  | ##ANSWER9## |
| circle 4 | ##ANSWER10## | ##ANSWER11## | ##ANSWER12## | `r a[4]` |



Answerlist
--------

`r al`


Solution
========

Here is the solution:

|          |    $r$      |     $d$     |     $c$     |     $A$     |
|:--------:|:-----------:|:-----------:|:-----------:|:-----------:|
| circle 1 | `r r[1]`    | `r d[1]`    | `r c[1]`    | `r a[1]`    |
| circle 2 | `r r[2]`    |   `r d[2]`  | `r c[2]`    | `r a[2]`    |
| circle 3 | `r r[3]`    |   `r d[3]`  | `r c[3]`    | `r a[3]`    |
| circle 4 | `r r[4]`    |   `r d[4]`  | `r c[4]`    | `r a[4]`    |

Use the formulas. You might need to do a tiny bit of algebra. For example, in the last row, to get the radius from the area of `r a[4]`, use $A=\pi r^2$...

$$`r a[4]`~=~\pi r^2$$

Divide both sides by $\pi$.

$$\frac{`r a[4]`}{\pi}~=~r^2$$

Take the square root of both sides.

$$\sqrt{\frac{`r a[4]`}{\pi}}~=~r$$

Evaluate. $r\approx`r r[4]`$


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",12),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: circle_measures