```{r data generation, echo = FALSE, results = "hide"}
options(scipen=99)
h = sample(8:20,1)
r1 = sample(6:15,1)
rstep = sample(4:10,1)
r2 = r1+rstep
r3 = r2+rstep

v1 = signif(pi*r1^2*h,5)
v2 = signif(pi*r2^2*h,5)
v3 = signif(pi*r3^2*h,5)
V = signif(sum(c(v1,v2,v3)),3)

atop = pi*r1^2
la1 = h*2*pi*r1
la2 = h*2*pi*r2
la3 = h*2*pi*r3
A = sum(c(atop,la1,la2,la3))

rho = round(runif(1,0.3,0.9),2)

mass = V*rho

extol = mass/100

```



Question
========

A three-tiered cake is constructed with three cylinders. Each cylinder has a height of `r h` centimeters. The radii are `r r1` centimeters, `r r2` centimeters, and `r r3` centimeters.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1.4),ylim=c(-1.2,1.2))
th = seq(0,2*pi,pi/100)
lines(cos(th),0.1*sin(th)-0.9)
lines(cos(th),0.1*sin(th)-0.3)
lines(c(-1,-1),c(-0.9,-0.3))
lines(c(1,1),c(-0.9,-0.3))
lines(c(0,1),c(-0.9,-0.9),col="red")
text(0.5,-0.95,paste0(r3," cm"),col="red")

lines(0.8*cos(th),0.8*0.1*sin(th)-0.3)
lines(0.8*cos(th),0.8*0.1*sin(th)+0.3)
lines(c(-0.8,-0.8),c(-0.3,0.3))
lines(c(0.8,0.8),c(-0.3,0.3))
lines(c(0,0.8),c(-0.3,-0.3),col="red")
text(0.4,-0.35,paste0(r2," cm"),col="red")

lines(0.6*cos(th),0.6*0.1*sin(th)+0.3)
lines(0.6*cos(th),0.6*0.1*sin(th)+0.9)
lines(c(-0.6,-0.6),c(0.3,0.9))
lines(c(0.6,0.6),c(0.3,0.9))
lines(c(0,0.6),c(0.3,0.3),col="red")
text(0.3,0.25,paste0(r1," cm"),col="red")

lines(c(1.05,1.1,1.1,1.05)-0.2,c(0.3,0.3,0.9,0.9))
text(1.05,0.6,paste0(h," cm"))

lines(c(1.05,1.1,1.1,1.05),c(-0.3,-0.3,0.3,0.3))
text(1.05+0.2,0,paste0(h," cm"))

lines(c(1.05,1.1,1.1,1.05)+0.1,c(-0.3,-0.3,-0.9,-0.9))
text(1.05+0.3,-0.6,paste0(h," cm"))
```
\

The volume ($V$) of each cylinder can be calulated with the following formula, where $r$ is radius and $h$ is height.

$$V~=~\pi r^2 h$$

You can get the total volume by adding up the volumes of all three cylinders.

After baked, the density of the cake is `r rho` grams per cubic centimeter (this is without the frosting). You can get the total mass by multiplying the volume by the density.

What is the mass of the cake (in grams)?


Solution
========

Get the volume of each cylinder.

$$V_1 ~=~ \pi (`r r1`)^2 (`r h`) ~=~ `r v1` ~\mathrm{cm^3}$$
$$V_2 ~=~ \pi (`r r2`)^2 (`r h`) ~=~ `r v2` ~\mathrm{cm^3}$$
$$V_3 ~=~ \pi (`r r3`)^2 (`r h`) ~=~ `r v3` ~\mathrm{cm^3}$$

Get the total volume.

$$V ~=~ `r v1`+`r v2`+`r v3` ~=~ `r V` ~\mathrm{cm^3}$$

Multiply the volume by the density to get the mass.

$$`r V` ~\mathrm{cm^3} \cdot \frac{`r rho`~\mathrm{g}}{1~\mathrm{cm^3}} ~=~ `r mass` ~\mathrm{g}$$





Meta-information
============
extype: num
exsolution: `r mass`
exname: cake_mass
extol: `r extol`