```{r data generation, echo = FALSE, results = "hide"}
options(scipen=99)
h = sample(8:20,1)
r1 = sample(6:15,1)
rstep = sample(4:10,1)
r2 = r1+rstep
r3 = r2+rstep

v1 = signif(pi*r1^2*h,5)
v2 = signif(pi*r2^2*h,5)
v3 = signif(pi*r3^2*h,5)
V = signif(sum(c(v1,v2,v3)),3)

atop = signif(pi*r3^2,4)
la1 = signif(h*2*pi*r1,4)
la2 = signif(h*2*pi*r2,4)
la3 = signif(h*2*pi*r3,4)
A = signif(sum(c(atop,la1,la2,la3)),3)

rho = round(runif(1,0.3,0.9),2)

mass = V*rho

extol = A/100

```



Question
========

A three-tiered cake is constructed with three cylinders. Each cylinder has a height of `r h` centimeters. The radii are `r r1` centimeters, `r r2` centimeters, and `r r3` centimeters.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-1,1.4),ylim=c(-1.2,1.2))
th = seq(0,2*pi,pi/100)
lines(cos(th),0.1*sin(th)-0.9)
lines(cos(th),0.1*sin(th)-0.3)
lines(c(-1,-1),c(-0.9,-0.3))
lines(c(1,1),c(-0.9,-0.3))
lines(c(0,1),c(-0.9,-0.9),col="red")
text(0.5,-0.95,paste0(r3," cm"),col="red")

lines(0.8*cos(th),0.8*0.1*sin(th)-0.3)
lines(0.8*cos(th),0.8*0.1*sin(th)+0.3)
lines(c(-0.8,-0.8),c(-0.3,0.3))
lines(c(0.8,0.8),c(-0.3,0.3))
lines(c(0,0.8),c(-0.3,-0.3),col="red")
text(0.4,-0.35,paste0(r2," cm"),col="red")

lines(0.6*cos(th),0.6*0.1*sin(th)+0.3)
lines(0.6*cos(th),0.6*0.1*sin(th)+0.9)
lines(c(-0.6,-0.6),c(0.3,0.9))
lines(c(0.6,0.6),c(0.3,0.9))
lines(c(0,0.6),c(0.3,0.3),col="red")
text(0.3,0.25,paste0(r1," cm"),col="red")

lines(c(1.05,1.1,1.1,1.05)-0.2,c(0.3,0.3,0.9,0.9))
text(1.05,0.6,paste0(h," cm"))

lines(c(1.05,1.1,1.1,1.05),c(-0.3,-0.3,0.3,0.3))
text(1.05+0.2,0,paste0(h," cm"))

lines(c(1.05,1.1,1.1,1.05)+0.1,c(-0.3,-0.3,-0.9,-0.9))
text(1.05+0.3,-0.6,paste0(h," cm"))
```
\

We wish to calculate the area covered by frosting.

Each cylinder's sides are covered. The area of a cylinder's sides can be found using the following formula where $r$ is the radius and $h$ is the height.

$$A_{\mathrm{side}} ~=~ 2\pi r h$$

The tops are also frosted. You might think you would need to find the areas of all three, but actually, you can just find the area of the top of the largest cylinder. The top of the cylinder is a circle.

$$A_{\mathrm{top}}~=~ 2\pi r^2$$

How much area is frosted?


Solution
========

Get the side area of each cylinder.

$$A_1 ~=~ 2 \pi (`r r1`) (`r h`) ~=~ `r la1` ~\mathrm{cm^2}$$
$$A_2 ~=~ 2\pi (`r r2`)(`r h`) ~=~ `r la2` ~\mathrm{cm^2}$$
$$A_3 ~=~ 2\pi (`r r3`)(`r h`) ~=~ `r la3` ~\mathrm{cm^2}$$

Get the area of the tops.

$$A_{\mathrm{top}} ~=~ \pi (`r r3`)^2 ~=~ `r atop` ~\mathrm{cm^2}$$

Get the total area.

$$A ~=~ `r la1`+`r la2`+`r la3`+`r atop` ~=~ `r A`~\mathrm{cm^2}$$




Meta-information
============
extype: num
exsolution: `r A`
exname: cake_mass
extol: `r extol`