```{r data generation, echo = FALSE, results = "hide"}
area = sample(15:50,1)
while(T){
    squares = list(c(0,0))
    for(i in 1:(area-1)){
        cango = F
        while(length(squares)<=i){
            sqn = sample(1:length(squares),1)
            sq = squares[[sqn]]
            delta = sample(c(-1,1),1)
            delsq = sample(c(delta,0))
            newsq = sq+delsq
            if(!(list(newsq) %in% squares) && max(abs(newsq))<=5){
                squares[[i+1]] = newsq
            }
        }
    }
    net = list()
    for(i in -6:6){
        j = length(net)
        net[[j+1]] = c(i,6)
    }
    for(i in 5:-5){
        j = length(net)
        net[[j+1]] = c(6,i)
    }
    for(i in 6:-6){
        j = length(net)
        net[[j+1]] = c(i,-6)
    }
    for(i in -5:5){
        j = length(net)
        net[[j+1]] = c(-6,i)
    }
    
    move = T
    dels = list(c(-1,0),c(1,0),c(0,-1),c(0,1))
    while(move){
        move = F
        newnet = list()
        for(i in 1:length(net)){
            nspot = net[[i]]
            for(j in 1:length(dels)){
                del = dels[[j]]
                newspot = nspot+del
                if(!(list(newspot)%in%squares) && !(list(newspot)%in%net) && max(abs(newspot))<=6){
                    move=T
                    net[[length(net)+1]] = newspot
                }
            }
        }
    }
    if(length(net)+length(squares)==13^2){break}
}


alledges = list()
for(i in 1:length(squares)){
    sq = squares[[i]]
    dels = list(c(-0.5,0),c(0.5,0),c(0,-0.5),c(0,0.5))
    for(j in 1:length(dels)){
        ed = sq+dels[[j]]
        alledges[[length(alledges)+1]] = ed
    }
}
lones = list()
for(i in 1:length(alledges)){
    ed = alledges[[i]]
    cnt = 0
    for(j in 1:length(alledges)){
        ed2 = alledges[[j]]
        if(sum(ed==ed2)==2){
            cnt = cnt+1
        }
    }
    if(cnt==1){
        lones[[length(lones)+1]] = ed
    }
}

maxy = -6
minx = 6
orlo = list()
for(i in 1:length(lones)){
    pt = lones[[i]]
    yy = pt[2]
    if(yy>maxy){
        maxy=yy
    }
}
cont = T
for(i in -6:6){
    for(j in 1:length(lones)){
        if(sum(c(i,maxy)==lones[[j]])==2 && cont){
            orlo[[1]] = lones[[j]]
            cont = F
        }
    }
}

while(length(orlo)<length(lones)){
    cl = length(orlo)
    p = orlo[[cl]]
    if(p[1]%%1==0){
        pa = c(p[1]-0.5,p[2])
        pb = c(p[1]+0.5,p[2])
    } else {
        pa = c(p[1],p[2]-0.5)
        pb = c(p[1],p[2]+0.5)
    }
    for(i in 1:length(lones)){
        p2 = lones[[i]]
        if(p2[1]%%1==0){
            pc = c(p2[1]-0.5,p2[2])
            pd = c(p2[1]+0.5,p2[2])
        } else {
            pc = c(p2[1],p2[2]-0.5)
            pd = c(p2[1],p2[2]+0.5)
        }
        if((sum(pd==pb)==2 || sum(pc==pb)==2) && !(list(p2)%in%orlo)){
            orlo[[cl+1]] = p2
        } else if((sum(pd==pa)==2 || sum(pc==pa)==2) && !(list(p2)%in%orlo)){
            orlo[[cl+1]] = p2
        }
    }
}


perimeter = length(lones)

ach1 = perimeter-sample(0:7,1)+0:7
ach2 = area-sample(0:7,1)+0:7
al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
sol1 = paste0(1*(ach1==perimeter),collapse="")
sol2 = paste0(1*(ach2==area),collapse="")
```



Question
========

A polygon is drawn below. Find its perimeter and area. Assume the grid is composed of squares with each length equal to 1 centimeter. Thus, the area of each grid square is 1 $\mathrm{cm^2}$.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-6,6),ylim=c(-6,6),axes=F,ann=F)
for(i in seq(-5.5,5.5,1)){
    lines(c(-6,6),c(i,i))
    lines(c(i,i),c(-6,6))
}
for(i in 1:length(squares)){
    sq = squares[[i]]
    x = sq[1]
    y = sq[2]
    polygon(x+c(-0.5,-0.5,0.5,0.5),y+c(-0.5,0.5,0.5,-0.5),col=rgb(1,0.6,0.6),border="black")
}
# for(i in 1:length(net)){
#     sq = net[[i]]
#     x = sq[1]
#     y = sq[2]
#     polygon(x+c(-0.5,-0.5,0.5,0.5),y+c(-0.5,0.5,0.5,-0.5),col="blue",border="black")
# }
for(i in 1:length(lones)){
    p = lones[[i]]
    # points(p[1],p[2])
    if(p[1]%%1==0){
        lines(c(p[1]-0.5,p[1]+0.5),c(p[2],p[2]),lwd=3)
    } else {
        lines(c(p[1],p[1]),c(p[2]-0.5,p[2]+0.5),lwd=3)
    }
}
```
\

* Perimeter = ##ANSWER1## $\mathrm{cm}$
* Area = ##ANSWER2## $\mathrm{cm^2}$


Answerlist
--------

`r al1`
`r al2`


Solution
========

Count the perimeter.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-6,6),ylim=c(-6,6),axes=F,ann=F)
for(i in seq(-5.5,5.5,1)){
    lines(c(-6,6),c(i,i))
    lines(c(i,i),c(-6,6))
}
for(i in 1:length(squares)){
    sq = squares[[i]]
    x = sq[1]
    y = sq[2]
    polygon(x+c(-0.5,-0.5,0.5,0.5),y+c(-0.5,0.5,0.5,-0.5),col=rgb(1,0.6,0.6),border="black")
}
# for(i in 1:length(net)){
#     sq = net[[i]]
#     x = sq[1]
#     y = sq[2]
#     polygon(x+c(-0.5,-0.5,0.5,0.5),y+c(-0.5,0.5,0.5,-0.5),col="blue",border="black")
# }
for(i in 1:length(lones)){
    p = lones[[i]]
    if(p[1]%%1==0){
        lines(c(p[1]-0.5,p[1]+0.5),c(p[2],p[2]),lwd=2,col="grey")
    } else {
        lines(c(p[1],p[1]),c(p[2]-0.5,p[2]+0.5),lwd=2,col="grey")
    }
    #points(p[1],p[2],cex=1.3)
}

for(i in 1:length(orlo)){
    p = orlo[[i]]
    text(p[1],p[2],i,cex=1)
}

```
\

The perimeter is $`r perimeter` ~\mathrm{cm}$.

Now, count the area.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-6,6),ylim=c(-6,6),axes=F,ann=F)
for(i in seq(-5.5,5.5,1)){
    lines(c(-6,6),c(i,i))
    lines(c(i,i),c(-6,6))
}
for(i in 1:length(squares)){
    sq = squares[[i]]
    x = sq[1]
    y = sq[2]
    polygon(x+c(-0.5,-0.5,0.5,0.5),y+c(-0.5,0.5,0.5,-0.5),col=rgb(1,0.6,0.6),border="black")
}
# for(i in 1:length(net)){
#     sq = net[[i]]
#     x = sq[1]
#     y = sq[2]
#     polygon(x+c(-0.5,-0.5,0.5,0.5),y+c(-0.5,0.5,0.5,-0.5),col="blue",border="black")
# }
for(i in 1:length(lones)){
    p = lones[[i]]
    if(p[1]%%1==0){
        lines(c(p[1]-0.5,p[1]+0.5),c(p[2],p[2]),lwd=2)
    } else {
        lines(c(p[1],p[1]),c(p[2]-0.5,p[2]+0.5),lwd=2)
    }
}

cnt = 1
for(i in 6:-6){
    for(j in -6:6){
        pnt = c(j,i)
        for(k in 1:length(squares)){
            if(sum(pnt==squares[[k]])==2){
                text(j,i,cnt)
                cnt = cnt+1
            }
        }
    }
}

```
\

So the area is $`r area` ~\mathrm{cm^2}$.





Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: area_perimeter_counting