```{r,echo=F,warning=F}
while(T){
  a = round(runif(1,pi/10,pi/4-0.1),3)
  b = round(runif(1,pi/10,pi/4-0.1),3)
  if(abs(diff(c(a,b)))>0.1){break}
}
p = round(cos(b),3)
q = round(sin(b),3)
r = round(cos(a)*cos(b),3)
s = round(sin(a)*cos(b),3)
t = round(cos(a)*sin(b),3)
u = round(sin(a)*sin(b),3)
v = round(cos(a+b),3)
w = round(sin(a+b),3)
ans = c(p,q,r,s,t,u,v,w)
al = numeric()
sol = c()
for(i in 1:length(ans)){
  wc = sample(1:5,1)
  al = c(al,ans[i]+0.003*(1:5-wc))
  sol = c(sol,paste0(1*(wc==1:5),collapse=""))
}
newal = sort(c(a,b,a+b,a-b,b-a))
al = c(al,newal)
sol = c(sol,paste0(1*(newal==a),collapse=""))
newal = sort(c(a,b,a+b,a-b,b-a))
al = c(al,newal)
sol = c(sol,paste0(1*(newal==a+b),collapse=""))

al = paste0("* ",al,collapse="\n")
ect = paste0(rep("schoice",length(al)),collapse="|")
exsol = paste0(sol,collapse="|")
```

Question
========

In the diagram below, let $\alpha=`r a`$ radians and $\beta=`r b`$ radians. Find all the lengths (to the nearest thousandth) and angle measures $\theta$ and $\phi$. Use unrounded values for all intermediate calculations.

```{r,fig.dim=c(7,7),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",ann=F,axes=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
yma = sin(a+b)
xma = cos(a)*cos(b)
lines(c(0,xma,xma,0,0),c(0,0,yma,yma,0))
lines(c(0,xma),c(0,sin(a)*cos(b)))
lines(c(0,cos(a+b),xma),c(0,sin(a+b),sin(a)*cos(b)))
lines(c(xma-0.02,xma-0.02,xma),c(0,0.02,0.02))
xc = cos(a)*cos(b)
yc = sin(a)*cos(b)
x1 = xc+0.02*cos(a+pi)
y1 = yc+0.02*sin(a+pi)
x2 = xc+0.02*sqrt(2)*cos(a+3*pi/4)
y2 = yc+0.02*sqrt(2)*sin(a+3*pi/4)
x3 = xc+0.02*cos(a+pi/2)
y3 = yc+0.02*sin(a+pi/2)
lines(c(x1,x2,x3),c(y1,y2,y3))
lines(c(xma,xma-0.02,xma-0.02),c(yma-0.02,yma-0.02,yma))
xmid = cos(a+b)/2
ymid = sin(a+b)/2
text(xmid+0.03*cos(a+b+pi/2),ymid+0.03*sin(a+b+pi/2),"1")
text(0.05/a*cos(a/2),0.05/a*sin(a/2),TeX("$\\alpha$"))
text(0.05/b*cos(a+b/2),0.05/b*sin(a+b/2),TeX("$\\beta$"))
xmid = cos(a)/2
ymid = sin(a)/2
text(xmid+0.03*cos(a+pi/2),ymid+0.03*sin(a+pi/2),"p")

xs = c(xma,cos(a+b))
ys = c(sin(a)*cos(b),yma)
th = atan2(diff(ys),diff(xs))
anngg = (th-pi/2)/2
text(xma+0.03/anngg*cos(anngg+pi/2),
     sin(a)*cos(b)+0.03/anngg*sin(anngg+pi/2),
     TeX("$\\theta$"))
xs = c(0,cos(a+b))
ys = c(0,yma)
th = atan(yma/cos(a+b))
anngg = (th)/2
text(xs[2]+0.03/anngg*cos(anngg+pi),
     ys[2]+0.03/anngg*sin(anngg+pi),
     TeX("$\\phi$"))

get_spot = function(xs,ys,r=0.03){
  xmid = mean(xs)
  ymid = mean(ys)
  th = atan2(diff(ys),diff(ys))
  return(c(xmid+r*cos(th+pi/2),ymid+r*cos(th+pi/2)))
}
xy = get_spot(c(xma,cos(a+b)),c(sin(a)*cos(b),yma))
text(xy[1],xy[2],"q")
text(xma/2,-0.03,"r")
text(xma+0.03,sin(a)*cos(b)/2,"s")
text(xma+0.03,sin(a)*cos(b)+cos(a)*sin(b)/2,"t")
text(xma-sin(a)*sin(b)/2,yma+0.03,"u")
text(cos(a+b)/2,yma+0.03,"v")
text(-0.03,yma/2,"w")
```
\

* $p=$ ##ANSWER1##
* $q=$ ##ANSWER2##
* $r=$ ##ANSWER3##
* $s=$ ##ANSWER4##
* $\theta=$ ##ANSWER9##
* $t=$ ##ANSWER5##
* $u=$ ##ANSWER6##
* $\phi=$ ##ANSWER10##
* $v=$ ##ANSWER7##
* $w=$ ##ANSWER8##


Answerlist
--------

`r al`


Solution
========

The correct values are shown below.

* $p=`r p`$
* $q=`r q`$
* $r=`r r`$
* $s=`r s`$
* $\theta=`r a`$
* $t=`r t`$
* $u=`r u`$
* $\phi=`r a+b`$
* $v=`r v`$
* $w=`r w`$

You might find [this](https://en.wikipedia.org/wiki/List_of_trigonometric_identities#/media/File:AngleAdditionDiagramSine.svg) helpful.


Meta-information
============
extype: cloze
exclozetype: `r ect`
exsolution: `r exsol`
exname: angle_sum_proof