---
header-includes:
   - \usepackage{array}
   - \usepackage{color}
   - \usepackage{tabularx}
output: pdf_document
params:
    rseed: 1
    showsol: true
    titex: "Practice"
urlcolor: blue
---

```{r,echo=F}
# set.seed(params$rseed)
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## Trig Final (`r params$titex` v`r params$rseed`)

* You should have a calculator (like [Desmos](https://www.desmos.com/calculator)) and a  [unit-circle](https://chadworley.github.io/a2/u16/trig_final/Unit_Circle_no_degs.pdf) reference sheet.

### Question 1

```{r,echo=F}
r = 2^runif(1,1,7)
th = runif(1,pi/4,7*pi/4)
L = r*th
wu = sample(1:3,1)
if(wu==1){
    r = signif(r,2)
    th = signif(th,2)
    L = r*th
    marks = c(paste0(r," m"),paste0(th),"$L$")
    geqs = c(paste0("The radius is ",signif(r,2)," meters.",collapse=""),
             paste0("The angle measure is ",signif(th,2)," radians.",collapse=""))
    ask = c("How long is the arc in meters?")
    sol = paste0("$L=",signif(L,4),"$ meters.")
}
if(wu==2){
    r = signif(r,2)
    L = signif(L,2)
    th = L/r
    marks = c(paste0(r, " m"),"$\\theta$",paste0(L," m"))
    geqs = c(paste0("The radius is ",r," meters.",collapse=""),
             paste0("The arc length is ",L," meters.",collapse=""))
    ask = c("What is the angle measure in radians?")
    sol = paste0("$\\theta=",signif(th,4),"$ radians.")
}
if(wu==3){
    L = signif(L,2)
    th = signif(th,2)
    r = L/th
    marks = c("$r$",paste0(th),paste0(L," m"))
    geqs = c(paste0("The angle measure is ",signif(th,2)," radians.",collapse=""),
             paste0("The arc length is ",L," meters.",collapse=""))
    ask = c("How long is the radius in meters?")
    sol = paste0("$r = ",signif(r,4),"$ meters.")
}
geqs = sample(geqs)
```

In the figure below, we see a circle and a central angle that subtends an arc. `r geqs[1]` `r geqs[2]` `r ask`

```{r,echo=F,fig.dim=c(2,2)}
library(latex2exp)
cex=0.8
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.2,1.2),ylim=c(-1.2,1.2))
thetas = seq(0,2*pi,pi/1000)
lines(cos(thetas),sin(thetas),lty=2)
lines(c(1,0,cos(th)),c(0,0,sin(th)))
lines(c(0,1),c(0,0),lwd=2,col="black")
text(0.6,0,TeX(marks[1]),adj=c(0.5,1.3),col="black",cex=cex)
th2 = seq(0,th,pi/360)
lines(0.2*cos(th2),0.2*sin(th2),col="blue",lwd=1.2)
n = length(th2)
arrows(0.2*cos(th2[n-1]),0.2*sin(th2[n-1]),0.2*cos(th2[n]),0.2*sin(th2[n]),0.03,30,col="blue")
rotang = (th/2/pi*180+90)%%180-90
if(wu!=2){
    if(rotang>0){
        text(0.2*cos(th/2),0.2*sin(th/2),TeX(marks[2]),col="blue",adj=c(-0.2,0.5),srt=rotang,cex=cex)
    } else {
        text(0.2*cos(th/2),0.2*sin(th/2),TeX(marks[2]),col="blue",adj=c(1.2,0.5),srt=rotang,cex=cex)
    }
} else {
    text(0.35*cos(th/2),0.35*sin(th/2),TeX(marks[2]),col="blue",adj=c(0.5,0.5),cex=cex)
}

rotangL = (th/2/pi*180)%%180-90
lines(cos(th2),sin(th2),col="maroon",lwd=1.2)
if(wu!=1){
    if(rotang>0){
        text(cos(th/2),sin(th/2),TeX(marks[3]),col="maroon",adj=c(0.5,-0.2),srt=rotangL,cex=cex)
    } else {
        text(cos(th/2),sin(th/2),TeX(marks[3]),col="maroon",adj=c(0.5,-0.2),srt=rotangL,cex=cex)
    }
} else {
    text(1.15*cos(th/2),1.15*sin(th/2),TeX(marks[3]),col="maroon",adj=c(0.5,0.5),cex=cex)
}
# text(1.2*cos(th/2),1.2*sin(th/2),TeX(marks[3]),col="maroon")
```

```{r,echo=F,results='asis'}
if(params$showsol){
    cat(paste0("\\color{red} \n\n $$\\begin{aligned}\\theta &= \\frac{L}{r}&&& r&=\\frac{L}{\\theta} &&& L&=r\\theta \\end{aligned}$$ \n\n",sol," \\color{black}"))
}
```

\vfill

### Question 2

```{r,echo=F}
# pick an angle greater than 2pi, and a negative angle
# draw angles in standard position on a unit circle
# find sin or cos of the angles

d4i = c(2,5,8,11)

while(T){
    ii = sample(1:12,2)
    i1 = ii[1]
    i2 = ii[2]
    i1in = (i1 %in% d4i)
    i2in = (i2 %in% d4i)
    if(i1 != 13-i2 && sum(c(i1in,i2in))==1){break}
}

sc = sample(c("s","c"))
np = sample(c("n","p"))

ang1poss = c("\\frac{13\\pi}{6}","\\frac{9\\pi}{4}","\\frac{7\\pi}{3}",
             "\\frac{8\\pi}{3}","\\frac{11\\pi}{4}","\\frac{17\\pi}{6}",
             "\\frac{19\\pi}{6}","\\frac{13\\pi}{4}","\\frac{10\\pi}{3}",
             "\\frac{11\\pi}{3}","\\frac{15\\pi}{4}","\\frac{23\\pi}{6}")
ang2poss = c("\\frac{-13\\pi}{6}","\\frac{-9\\pi}{4}","\\frac{-7\\pi}{3}",
             "\\frac{-8\\pi}{3}","\\frac{-11\\pi}{4}","\\frac{-17\\pi}{6}",
             "\\frac{-19\\pi}{6}","\\frac{-13\\pi}{4}","\\frac{-10\\pi}{3}",
             "\\frac{-11\\pi}{3}","\\frac{-15\\pi}{4}","\\frac{-23\\pi}{6}")


A1poss = c("13\\pi/6","9\\pi/4","7\\pi/3",
           "8\\pi/3","11\\pi/4","17\\pi/6",
           "19\\pi/6","13\\pi/4","10\\pi/3",
           "11\\pi/3","15\\pi/4","23\\pi/6")
A2poss = c("-13\\pi/6","-9\\pi/4","-7\\pi/3",
           "-8\\pi/3","-11\\pi/4","-17\\pi/6",
           "-19\\pi/6","-13\\pi/4","-10\\pi/3",
           "-11\\pi/3","-15\\pi/4","-23\\pi/6")

a1p = c(13*pi/6,9*pi/4,7*pi/3,8*pi/3,11*pi/4,17*pi/6,19*pi/6,13*pi/4,10*pi/3,11*pi/3,15*pi/4,23*pi/6)
a2p = -a1p
ca1 = c("\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}",
        "\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}",
        "\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}",
        "\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}")
sa1 = c("\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}",
        "\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}",
        "\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}",
        "\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}")
ca2 = c("\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}",
        "\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}",
        "\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}",
        "\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}")
sa2 = c("\\frac{-1}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-\\sqrt{3}}{2}",
        "\\frac{-\\sqrt{3}}{2}","\\frac{-\\sqrt{2}}{2}","\\frac{-1}{2}",
        "\\frac{1}{2}","\\frac{\\sqrt{2}}{2}","\\frac{\\sqrt{3}}{2}",
        "\\frac{\\sqrt{3}}{2}","\\frac{\\sqrt{2}}{2}","\\frac{1}{2}")

Ca1 = c("\\sqrt{3}/2","\\sqrt{2}/2","1/2",
        "-1/2","-\\sqrt{2}/2","-\\sqrt{3}/2",
        "-\\sqrt{3}/2","-\\sqrt{2}/2","-1/2",
        "1/2","\\sqrt{2}/2","\\sqrt{3}/2")
Sa1 = c("1/2","\\sqrt{2}/2","\\sqrt{3}/2",
        "\\sqrt{3}/2","\\sqrt{2}/2","1/2",
        "-1/2","-\\sqrt{2}/2","-\\sqrt{3}/2",
        "-\\sqrt{3}/2","-\\sqrt{2}/2","-1/2")
Ca2 = Ca1
Sa2 = c("-1/2","-\\sqrt{2}/2","-\\sqrt{3}/2",
        "-\\sqrt{3}/2","-\\sqrt{2}/2","-1/2",
        "1/2","\\sqrt{2}/2","\\sqrt{3}/2",
        "\\sqrt{3}/2","\\sqrt{2}/2","1/2")

if(sc[1]=="s"){
    if(np[1]=="n"){
        a1 = ang2poss[i1]
        a2 = ang1poss[i2]
        A1 = A2poss[i1]
        A2 = A1poss[i2]
        t1 = sa2[i1]
        t2 = ca1[i2]
        p1 = paste0("$\\sin\\left(",a1,"\\right)$")
        p2 = paste0("$\\cos\\left(",a2,"\\right)$")
        q1 = paste0("$\\sin(",A1,")$")
        q2 = paste0("$\\cos(",A2,")$")
        th1 = a2p[i1]
        th2 = a1p[i2]
    } else {
        a1 = ang1poss[i1]
        a2 = ang2poss[i2]
        A1 = A1poss[i1]
        A2 = A2poss[i2]
        t1 = sa1[i1]
        t2 = ca2[i2]
        p1 = paste0("$\\sin\\left(",a1,"\\right)$")
        p2 = paste0("$\\cos\\left(",a2,"\\right)$")
        q1 = paste0("$\\sin(",A1,")$")
        q2 = paste0("$\\cos(",A2,")$")
        th1 = a1p[i1]
        th2 = a2p[i2]
    }
} else {
    if(np[1]=="n"){
        a1 = ang2poss[i1]
        a2 = ang1poss[i2]
        A1 = A2poss[i1]
        A2 = A1poss[i2]
        t1 = ca2[i1]
        t2 = sa1[i2]
        p1 = paste0("$\\cos\\left(",a1,"\\right)$")
        p2 = paste0("$\\sin\\left(",a2,"\\right)$")
        q1 = paste0("$\\cos(",A1,")$")
        q2 = paste0("$\\sin(",A2,")$")
        th1 = a2p[i1]
        th2 = a1p[i2]
    } else {
        a1 = ang1poss[i1]
        a2 = ang2poss[i2]
        A1 = A1poss[i1]
        A2 = A2poss[i2]
        t1 = ca1[i1]
        t2 = sa2[i2]
        p1 = paste0("$\\cos\\left(",a1,"\\right)$")
        p2 = paste0("$\\sin\\left(",a2,"\\right)$")
        q1 = paste0("$\\cos(",A1,")$")
        q2 = paste0("$\\sin(",A2,")$")
        th1 = a1p[i1]
        th2 = a2p[i2]
    }
}

```

Consider angles $`r a1`$ and $`r a2`$. For each angle, use a spiral with an arrow head to **mark** the angle on a circle below in standard position. Then, find **exact** expressions for `r p1` and `r p2` by using a unit circle (provided separately).

```{r,echo=F,fig.dim=c(8,3)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,8),ylim=c(0,3),asp=1)
thetas = seq(0,2*pi,pi/360)
lines(cos(thetas)+2,sin(thetas)+1.5)
lines(cos(thetas)+6,sin(thetas)+1.5)
th3 = seq(0,2*pi,pi/12)
for(i in th3){
    lines(c(0,cos(i))+2,c(0,sin(i))+1.5,lty=3,lwd=0.8)
    lines(c(0,cos(i))+6,c(0,sin(i))+1.5,lty=3,lwd=0.8)
}
th4 = seq(0,2*pi,pi/6)
for(i in th4){
    lines(c(0,cos(i))+2,c(0,sin(i))+1.5,lty=2,lwd=0.8)
    lines(c(0,cos(i))+6,c(0,sin(i))+1.5,lty=2,lwd=0.8)
}
th4 = seq(0,2*pi,pi/4)
for(i in th4){
    lines(c(0,cos(i))+2,c(0,sin(i))+1.5,lty=1,lwd=0.8)
    lines(c(0,cos(i))+6,c(0,sin(i))+1.5,lty=1,lwd=0.8)
}
points(c(2,6),c(1.5,1.5),pch=20)
text(2,2.8,TeX(paste0("Mark $",a1,"$")),cex=cex)
text(6,2.8,TeX(paste0("Mark $",a2,"$")),cex=cex)

text(2,0.2,TeX(paste0("Find ",q1)),cex=cex)
text(6,0.2,TeX(paste0("Find ",q2)),cex=cex)
if(params$showsol){
    thth = seq(0,th1,pi/360*sign(th1))
    xs = 2+(0.4+abs(thth)/10/pi)*cos(thth)
    ys = 1.5+(0.4+abs(thth)/10/pi)*sin(thth)
    n = length(xs)
    lines(xs,ys,col="red")
    arrows(xs[n-1],ys[n-1],xs[n],ys[n],0.1,20,col="red")
    thth = seq(0,th2,pi/360*sign(th2))
    xs = 6+(0.4+abs(thth)/10/pi)*cos(thth)
    ys = 1.5+(0.4+abs(thth)/10/pi)*sin(thth)
    lines(xs,ys,col="red")
    n = length(xs)
    arrows(xs[n-1],ys[n-1],xs[n],ys[n],0.1,20,col="red")
}

```


\vfill

```{r,echo=F,results='asis'}
if(params$showsol){
    cat(paste0("\\color{red} \\hspace{1in} ",q1,"$=",t1,"$ \\hspace{2in} ",q2,"$=",t2,"$ \\color{black}\n\n\\vfill"))
}
```

\vfill

\newpage


### Question 3

```{r,echo=F}
pts = list(c(5, 12, 13),c(8, 15, 17),c(7, 24, 25),c(20, 21, 29),c(12, 35, 37),c(9, 40, 41),c(28, 45, 53),c(11, 60, 61),c(16, 63, 65),c(33, 56, 65),c(48, 55, 73),c(36, 77, 85),c(39, 80, 89),c(65, 72, 97))
i = sample(1:length(pts),1)
pt = pts[[i]]
A = pt[1]
B = pt[2]
C = pt[3]
Q = sample(2:4,1)
if(Q==1){
    signs = c(1,1,1)
}
if(Q==2){
    signs = c(1,-1,-1)
}
if(Q==3){
    signs = c(-1,-1,1)
}
if(Q==4){
    signs = c(-1,1,-1)
}
st = c(signs[1]*B,C)
ct = c(signs[2]*A,C)
tt = c(signs[3]*B,A)
rmn = c("I","II","III","IV")
qt = sample(1:6,1)

if(qt==1){
    giv = paste0("\\sin(\\theta)=\\frac{",st[1],"}{",st[2],"}",collapse="")
    At = "A"
    Bt = paste0(B)
    Ct = paste0(C)
    ask = paste0("\\cos(\\theta)")
    ans = paste0("\\cos(\\theta)=\\frac{",ct[1],"}{",ct[2],"}",collapse="")
    stp = paste0("$$A=\\sqrt{",C,"^2-",B,"^2}$$")
    stp2 = paste0("$$A=",A,"$$")
}
if(qt==2){
    At = "A"
    Bt = paste0(B)
    Ct = paste0(C)
    giv = paste0("\\sin(\\theta)=\\frac{",st[1],"}{",st[2],"}",collapse="")
    ask = paste0("\\tan(\\theta)")
    ans = paste0("\\tan(\\theta)=\\frac{~\\frac{",st[1],"}{",st[2],"}~}{~\\frac{",ct[1],"}{",ct[2],"}~}=\\frac{",tt[1],"}{",tt[2],"}",collapse="")
    stp = paste0("$$A=\\sqrt{",C,"^2-",B,"^2}$$")
    stp2 = paste0("$$A=",A,"$$")
}
if(qt==3){
    At = paste0(A)
    Bt = "B"
    Ct = paste0(C)
    giv = paste0("\\cos(\\theta)=\\frac{",ct[1],"}{",ct[2],"}",collapse="")
    ask = paste0("\\sin(\\theta)")
    ans = paste0("\\sin(\\theta)=\\frac{",st[1],"}{",st[2],"}",collapse="")
    stp = paste0("$$B=\\sqrt{",C,"^2-",A,"^2}$$")
    stp2 = paste0("$$B=",B,"$$")
}
if(qt==4){
    At = paste0(A)
    Bt = "B"
    Ct = paste0(C)
    giv = paste0("\\cos(\\theta)=\\frac{",ct[1],"}{",ct[2],"}",collapse="")
    ask = paste0("\\tan(\\theta)")
    ans = paste0("\\tan(\\theta)=\\frac{~\\frac{",st[1],"}{",st[2],"}~}{~\\frac{",ct[1],"}{",ct[2],"}~}=\\frac{",tt[1],"}{",tt[2],"}",collapse="")
    stp = paste0("$$B=\\sqrt{",C,"^2-",A,"^2}$$")
    stp2 = paste0("$$B=",B,"$$")
}
if(qt==5){
    At = paste0(A)
    Bt = paste0(B)
    Ct = "C"
    giv = paste0("\\tan(\\theta)=\\frac{",tt[1],"}{",tt[2],"}",collapse="")
    ask = paste0("\\sin(\\theta)")
    ans = paste0("\\sin(\\theta)=\\frac{",st[1],"}{",st[2],"}",collapse="")
    stp = paste0("$$C=\\sqrt{",A,"^2+",B,"^2}$$")
    stp2 = paste0("$$C=",C,"$$")
}
if(qt==6){
    At = paste0(A)
    Bt = paste0(B)
    Ct = "C"
    giv = paste0("\\tan(\\theta)=\\frac{",tt[1],"}{",tt[2],"}",collapse="")
    ask = paste0("\\cos(\\theta)")
    ans = paste0("\\cos(\\theta)=\\frac{",ct[1],"}{",ct[2],"}",collapse="")
    stp = paste0("$$C=\\sqrt{",A,"^2+",B,"^2}$$")
    stp2 = paste0("$$C=",C,"$$")
}

```

If $`r giv`$, and $\theta$ is in quadrant $\text{`r rmn[Q]`}$, determine an exact value for $`r ask`$.

```{r,echo=F,eval=params$showsol,fig.dim=c(1.5,1.5),results='asis'}
library(latex2exp)
cat("\\color{red}")
cat("Ignore any negatives and the quadrant, and draw a right triangle (based on SOHCAHTOA) in standard (quadrant I) orientation.\n\n")
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,C*1.1),ylim=c(-C*0.1,C),axes=F,ann=F)
polygon(c(0,A,A),c(0,0,B),border = "red")
text(A/2,0,At,adj=c(0.5,1.2),col="red")
text(A,B/2,Bt,adj=c(-0.2,0.5),col="red")
text(A/2,B/2,Ct,srt=atan(B/A)/pi*180,adj=c(0.5,-0.2),col="red")
thh = seq(0,atan(B/A),pi/1000)
polygon(c(0,cos(thh)*C/20),c(0,sin(thh)*C/20),col="red",border="red")
thq1 = atan(B/A)
lines(c(-C/20,-C/20,0)+A,c(0,C/20,C/20),col="red")
cat("\n\nSolve the Pythagorean Equation\n\n")
cat(paste0("$$",At,"^2+",Bt,"^2=",Ct,"^2$$\n"))
cat(stp)
cat("\n")
cat(stp2)
cat("\n")
cat(paste0("Rescale the triangle so the hypotenuse is 1. Reflect the triangle into Quadrant ",rmn[Q]," in a unit circle."))
cat("\\color{black}\n\n")
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1.1,1.1),ylim=c(-1.1,1.1),axes=F,ann=F)
ths = seq(0,2*pi,pi/360)
col1 = rgb(1,0.9,0.9)
lines(cos(ths),sin(ths),col=col1)
abline(h=0,col=col1)
abline(v=0,col=col1)
xx = ct[1]/ct[2]
yy = st[1]/st[2]
dath = (atan2(st[1],ct[1])+4*pi)%%(2*pi)
ttthhh = seq(0,dath,pi/360)
lines(cos(ttthhh),sin(ttthhh),col="maroon")
text(1.1*cos(dath/2),1.1*sin(dath/2),TeX("$\\theta$"),col="maroon",cex=0.6)
polygon(c(0,xx,xx),c(0,0,yy),border="red")
lines(xx-c(0.05,0.05,0)*sign(xx),c(0,0.05,0.05)*sign(yy),col="red")
text(xx/2,0,TeX(paste0("$\\frac{",ct[1],"}{",ct[2],"}$")),adj=c(0.5,0.5+0.7*sign(yy)),col="red",cex=0.4)
text(xx,yy/2,TeX(paste0("$\\frac{",st[1],"}{",st[2],"}$")),adj=c(0.5-0.8*sign(xx),0.5),col="red",cex=0.4)
text(xx/2,yy/2,"1",srt=(dath/pi*180+90)%%180-90,col="red",cex=0.4,adj=c(0.5,0.5-0.8*sign(yy)))

```


```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat(paste0("$$",ans,"$$\n\n"))
    cat("\\color{black}")
}
```

\vfill

\vfill


### Question 4

```{r,echo=F}
qt = sample(1:4,1)
while(T){
  AfD = round(runif(3,2,9),2)
  if(min(diff(sort(AfD)))>1){break}
}
A = AfD[1]
f = AfD[2]
D = AfD[3]*sample(c(-1,1),1)
if(qt==1){
    g = "sin"
    ic = "midline and moving up"
}
if(qt==2){
    g = "sin"
    ic = "midline and moving down"
    A = -A
}
if(qt==3){
    g = "cos"
    ic = "maximum height"
}
if(qt==4){
    g = "cos"
    ic = "minimum height"
    A = -A
}
states = c(paste0("an amplitude of ",abs(A)," meters",collapse=""),
           paste0("a frequency of ",f," Hz",collapse=""),
           paste0("a midline at $y=",D,"$ meters",collapse=""))
states = sample(states)
pD = paste0("+",D)
pD = gsub("+-","-",pD,fixed=T)
```

A mass-spring system oscillates vertically with `r states[1]`, `r states[2]`, and `r states[3]`. At $t=0$, the mass is at the `r ic`. Write an equation to model the height ($y$ in meters) as a function of time ($t$ in seconds).

```{r,echo=F,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\nAny of these equations would get full credit.")
    cat(paste0("$$y=",A,"\\",g,"(2\\pi",f,"t)",pD,"$$ or $$y=",A,"\\",g,"(",2*f,"\\pi t)",pD,"$$ or $$y=",A,"\\",g,"(",signif(2*f*pi,4)," t)",pD))
    cat("$$\\color{black}")
}
```



\vfill





