---
output: pdf_document
---

Name: \hspace{4in} Date: \hfill \hrule

# Multiply fractions with prime factorization

## Example 1

Using prime factorization, evaluate the product of two fractions shown below. Give your answer as a [reduced fraction](https://en.wikipedia.org/wiki/Irreducible_fraction) (not a [mixed number](https://en.wikipedia.org/wiki/Fraction#Mixed_numbers)).

$$\frac{10}{21}\cdot \frac{28}{25}$$

### Solution to example 1

First, use factor trees to determine the prime factorization of each number.

```{r,echo=F,fig.dim=c(6,1.5)}
par(mar=c(0,0,0,0),mfrow=c(1,4))
plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
text(0.5,0.9,10)
text(0.2,0.1,2)
text(0.8,0.1,5)
lines(c(0.2,0.5,0.8),c(0.2,0.8,0.2))

plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
text(0.5,0.9,21)
text(0.2,0.1,3)
text(0.8,0.1,7)
lines(c(0.2,0.5,0.8),c(0.2,0.8,0.2))

plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
text(0.5,0.9,28)
text(0.2,0.5,4)
text(0.8,0.5,7)
text(0.1,0.1,2)
text(0.3,0.1,2)
lines(c(0.2,0.5,0.8),c(0.6,0.8,0.6))
lines(c(0.1,0.2,0.3),c(0.2,0.4,0.2))

plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
text(0.5,0.9,25)
text(0.2,0.1,5)
text(0.8,0.1,5)
lines(c(0.2,0.5,0.8),c(0.2,0.8,0.2))


# gettree = function(x){
#     facts = list()
#     for(i in 1:20){
#         if(x %/% 2 == 0){
#             facts[[i]] = c(2,round(x/2))
#             x = round(x/2)
#         } else if(x %/% 3 == 0) {
#             facts[[i]] = c(3,round(x/3))
#             x = round(x/3)
#         } else if(x %/% 5 == 0) {
#             facts[[i]] = c(5,round(x/5))
#             x = round(x/5)
#         } else if(x %/% 7 == 0) {
#             facts[[i]] = c(7,round(x/7))
#             x = round(x/7)
#         } else if(x %/% 11 == 0) {
#             facts[[i]] = c(11,round(x/11))
#             x = round(x/11)
#         } else if(x %/% 13 == 0) {
#             facts[[i]] = c(13,round(x/13))
#             x = round(x/13)
#         } else if(x %/% 17 == 0) {
#             facts[[i]] = c(17,round(x/17))
#             x = round(x/17)
#         } else {break}
#     }
#     return(facts)
# }
# plottree = function(x,facts){
#     par(mar=c(0,0,0,0))
#     plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
#     n = length(facts)
#     hsps = 3+n-1
#     vsps = n+1
#     hbs = seq(0,1,length.out=hsps+1)
#     vbs = seq(1,0,length.out=vsps+1)
#     hmids = (hbs[2:(hsps+1)]+hbs[1:hsps])/2
#     vmids = (vbs[2:(vsps+1)]+vbs[1:vsps])/2
# }

```


$$10=2^1 \cdot 5^1$$
$$21=3^1 \cdot 7^1$$
$$28=2^2 \cdot 7^1$$
$$25=5^2$$

Rewrite the fraction using prime factors. Also, remember $\frac{a}{b}\cdot\frac{c}{d}\equiv \frac{ac}{bd}$.

$$\frac{2\cdot 5 \cdot 2 \cdot 2 \cdot 7}{3\cdot 7\cdot 5\cdot 5}$$

Eliminate common factors.

$$\frac{2\cdot \not{5} \cdot 2 \cdot 2 \cdot \not{7}}{3\cdot \not{7}\cdot \not{5}\cdot 5}$$

$$\frac{2 \cdot 2 \cdot 2}{3\cdot 5}$$

Multiply the factors in the numerator, and multiply the factors in the denominator.

$$\frac{8}{15}$$

\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
primes = c(2,3,5,7,11,13)
ep = c(2,3,5)
while(T){
    na = sample(2:5,1)
    A = prod(c(sample(ep,na-1,T),sample(primes,1)))
    nb = sample(2:5,1)
    B = prod(c(sample(ep,nb-1,T),sample(primes,1)))
    nc = sample(2:5,1)
    C = prod(c(sample(ep,nc-1,T),sample(primes,1)))
    nd = sample(2:5,1)
    D = prod(c(sample(ep,nd-1,T),sample(primes,1)))
    ansnum = A*C/gcd(c(A*C,B*D))
    ansden = B*D/gcd(c(A*C,B*D))
    if(length(unique(c(A,B,C,D)))==4 && (A*C)!=(B*D) && gcd(c(A,B))==1 && gcd(c(C,D))==1 && gcd(A,D)>1 && gcd(B,C)>1 && max(c(A,B,C,D))<200 && ansnum<50 && ansden<50){break}
}
```

# Practice 1

* Consider the product of fractions shown below.

$$\frac{`r A`}{`r B`}\cdot \frac{`r C`}{`r D`}$$

* Make factor trees for `r A`, `r B`, `r C`, and `r D`.

\vfill

* Rewrite the problem using prime factors and a single fraction.

\vfill

* Simplify by eliminating common factors.

\vfill


\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
primes = c(2,3,5,7,11,13)
ep = c(2,3,5)
while(T){
    na = sample(2:5,1)
    A = prod(c(sample(ep,na-1,T),sample(primes,1)))
    nb = sample(2:5,1)
    B = prod(c(sample(ep,nb-1,T),sample(primes,1)))
    nc = sample(2:5,1)
    C = prod(c(sample(ep,nc-1,T),sample(primes,1)))
    nd = sample(2:5,1)
    D = prod(c(sample(ep,nd-1,T),sample(primes,1)))
    ansnum = A*C/gcd(c(A*C,B*D))
    ansden = B*D/gcd(c(A*C,B*D))
    if(length(unique(c(A,B,C,D)))==4 && (A*C)!=(B*D) && gcd(c(A,B))==1 && gcd(c(C,D))==1 && gcd(A,D)>1 && gcd(B,C)>1 && max(c(A,B,C,D))<200 && ansnum<50 && ansden<50){break}
}
```

# Practice 2

* Consider the product of fractions shown below.

$$\frac{`r A`}{`r B`}\cdot \frac{`r C`}{`r D`}$$

* Make factor trees for `r A`, `r B`, `r C`, and `r D`.

\vfill

* Rewrite the problem using prime factors and a single fraction.

\vfill

* Simplify by eliminating common factors.

\vfill


\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
primes = c(2,3,5,7,11,13)
ep = c(2,3,5)
while(T){
    na = sample(2:5,1)
    A = prod(c(sample(ep,na-1,T),sample(primes,1)))
    nb = sample(2:5,1)
    B = prod(c(sample(ep,nb-1,T),sample(primes,1)))
    nc = sample(2:5,1)
    C = prod(c(sample(ep,nc-1,T),sample(primes,1)))
    nd = sample(2:5,1)
    D = prod(c(sample(ep,nd-1,T),sample(primes,1)))
    ansnum = A*C/gcd(c(A*C,B*D))
    ansden = B*D/gcd(c(A*C,B*D))
    if(length(unique(c(A,B,C,D)))==4 && (A*C)!=(B*D) && gcd(c(A,B))==1 && gcd(c(C,D))==1 && gcd(A,D)>1 && gcd(B,C)>1 && max(c(A,B,C,D))<200 && ansnum<50 && ansden<50){break}
}
```

# Practice 3

* Consider the product of fractions shown below.

$$\frac{`r A`}{`r B`}\cdot \frac{`r C`}{`r D`}$$

* Make factor trees for `r A`, `r B`, `r C`, and `r D`.

\vfill

* Rewrite the problem using prime factors and a single fraction.

\vfill

* Simplify by eliminating common factors.

\vfill



\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
primes = c(2,3,5,7,11,13)
ep = c(2,3,5)
while(T){
    na = sample(2:5,1)
    A = prod(c(sample(ep,na-1,T),sample(primes,1)))
    nb = sample(2:5,1)
    B = prod(c(sample(ep,nb-1,T),sample(primes,1)))
    nc = sample(2:5,1)
    C = prod(c(sample(ep,nc-1,T),sample(primes,1)))
    nd = sample(2:5,1)
    D = prod(c(sample(ep,nd-1,T),sample(primes,1)))
    ansnum = A*C/gcd(c(A*C,B*D))
    ansden = B*D/gcd(c(A*C,B*D))
    if(length(unique(c(A,B,C,D)))==4 && (A*C)!=(B*D) && gcd(c(A,B))==1 && gcd(c(C,D))==1 && gcd(A,D)>1 && gcd(B,C)>1 && max(c(A,B,C,D))<200 && ansnum<50 && ansden<50){break}
}
```

# Practice 4

* Consider the product of fractions shown below.

$$\frac{`r A`}{`r B`}\cdot \frac{`r C`}{`r D`}$$

* Make factor trees for `r A`, `r B`, `r C`, and `r D`.

\vfill

* Rewrite the problem using prime factors and a single fraction.

\vfill

* Simplify by eliminating common factors.

\vfill


\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
primes = c(2,3,5,7,11,13)
ep = c(2,3,5)
while(T){
    na = sample(2:5,1)
    A = prod(c(sample(ep,na-1,T),sample(primes,1)))
    nb = sample(2:5,1)
    B = prod(c(sample(ep,nb-1,T),sample(primes,1)))
    nc = sample(2:5,1)
    C = prod(c(sample(ep,nc-1,T),sample(primes,1)))
    nd = sample(2:5,1)
    D = prod(c(sample(ep,nd-1,T),sample(primes,1)))
    ansnum = A*C/gcd(c(A*C,B*D))
    ansden = B*D/gcd(c(A*C,B*D))
    if(length(unique(c(A,B,C,D)))==4 && (A*C)!=(B*D) && gcd(c(A,B))==1 && gcd(c(C,D))==1 && gcd(A,D)>1 && gcd(B,C)>1 && max(c(A,B,C,D))<200 && ansnum<50 && ansden<50){break}
}
```

# Practice 5

* Consider the product of fractions shown below.

$$\frac{`r A`}{`r B`}\cdot \frac{`r C`}{`r D`}$$

* Make factor trees for `r A`, `r B`, `r C`, and `r D`.

\vfill

* Rewrite the problem using prime factors and a single fraction.

\vfill

* Simplify by eliminating common factors.

\vfill

\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
primes = c(2,3,5,7,11,13)
ep = c(2,3,5)
while(T){
    na = sample(2:5,1)
    A = prod(c(sample(ep,na-1,T),sample(primes,1)))
    nb = sample(2:5,1)
    B = prod(c(sample(ep,nb-1,T),sample(primes,1)))
    nc = sample(2:5,1)
    C = prod(c(sample(ep,nc-1,T),sample(primes,1)))
    nd = sample(2:5,1)
    D = prod(c(sample(ep,nd-1,T),sample(primes,1)))
    ansnum = A*C/gcd(c(A*C,B*D))
    ansden = B*D/gcd(c(A*C,B*D))
    if(length(unique(c(A,B,C,D)))==4 && (A*C)!=(B*D) && gcd(c(A,B))==1 && gcd(c(C,D))==1 && gcd(A,D)>1 && gcd(B,C)>1 && max(c(A,B,C,D))<200 && ansnum<50 && ansden<50){break}
}
```

# Practice 6

* Consider the product of fractions shown below.

$$\frac{`r A`}{`r B`}\cdot \frac{`r C`}{`r D`}$$

* Make factor trees for `r A`, `r B`, `r C`, and `r D`.

\vfill

* Rewrite the problem using prime factors and a single fraction.

\vfill

* Simplify by eliminating common factors.

\vfill

\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
primes = c(2,3,5,7,11,13)
ep = c(2,3,5)
while(T){
    na = sample(2:5,1)
    A = prod(c(sample(ep,na-1,T),sample(primes,1)))
    nb = sample(2:5,1)
    B = prod(c(sample(ep,nb-1,T),sample(primes,1)))
    nc = sample(2:5,1)
    C = prod(c(sample(ep,nc-1,T),sample(primes,1)))
    nd = sample(2:5,1)
    D = prod(c(sample(ep,nd-1,T),sample(primes,1)))
    ansnum = A*C/gcd(c(A*C,B*D))
    ansden = B*D/gcd(c(A*C,B*D))
    if(length(unique(c(A,B,C,D)))==4 && (A*C)!=(B*D) && gcd(c(A,B))==1 && gcd(c(C,D))==1 && gcd(A,D)>1 && gcd(B,C)>1 && max(c(A,B,C,D))<200 && ansnum<50 && ansden<50){break}
}
```

# Practice 7

* Consider the product of fractions shown below.

$$\frac{`r A`}{`r B`}\cdot \frac{`r C`}{`r D`}$$

* Make factor trees for `r A`, `r B`, `r C`, and `r D`.

\vfill

* Rewrite the problem using prime factors and a single fraction.

\vfill

* Simplify by eliminating common factors.

\vfill





