---
output: pdf_document
---

Name: \hspace{4in} Date: \hfill \hrule

# Prime factorization

```{r,echo=F}
set.seed(1)
```

## Use prime factorization to find greatest common factor (GCF) and least common multiple (LCM)

### Example 1: Find GCF and LCM of 250 and 280.

* First make prime-factor trees

```{r,echo=F,fig.dim=c(4,1.5),fig.align='center'}
vs = -0.05
ys = c(0.78,0.92,0.78)+vs
par(mar=c(0,0,0,0),mfrow=c(1,2))
plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
text(0.5,1+vs,250)
lines(c(0.25,0.5,0.75),ys)
text(0.25,0.7+vs,25)
text(0.75,0.7+vs,10)
lines(c(0.10,0.25,0.40),ys-0.3)
text(0.1,0.4+vs,5)
text(0.4,0.4+vs,5)
lines(c(0.10,0.25,0.40)+0.5,ys-0.3)
text(0.6,0.4+vs,2)
text(0.9,0.4+vs,5)


plot(0,0,"n",xlim=c(0,1),ylim=c(0,1),axes=F,ann=F)
text(0.5,1+vs,280)
lines(c(0.25,0.5,0.75),ys)
text(0.25,0.7+vs,28)
text(0.75,0.7+vs,10)
lines(c(0.10,0.25,0.40),ys-0.3)
text(0.1,0.4+vs,7)
text(0.4,0.4+vs,4)
lines(c(0.10,0.25,0.40)+0.5,ys-0.3)
text(0.6,0.4+vs,2)
text(0.9,0.4+vs,5)
lines(c(0.3,0.4,0.5),ys-0.6)
text(0.3,0.1+vs,2)
text(0.5,0.1+vs,2)

```

* Write each as number in prime-exponent form.
$$250 = 2^1 \cdot 5^3$$
$$280 = 2^3 \cdot 5^1 \cdot 7^1$$
Notice, you could also write $250 = 2^1 \cdot 5^3\cdot 7^0$

* Make a Venn diagram showing the shared factors.

```{r,echo=F,fig.dim=c(3,1.5),fig.align='center'}
par(mar=c(0,0,0,0))
plot(0,0,type="n",axes=F,ann=F,xlim=c(0,2),ylim=c(0,1))
th = seq(0,2*pi,pi/100)
lines(0.5*cos(th)+0.7,0.5*sin(th)+0.5)
lines(0.5*cos(th)+1.3,0.5*sin(th)+0.5)
text(0.5,0.6,"5")
text(0.5,0.4,"5")
text(1,0.6,"2")
text(1,0.4,"5")
text(1.5,0.65,"2")
text(1.5,0.5,"2")
text(1.5,0.35,"7")
text(0.2,0.95,"250")
text(1.8,0.95,"280")
```

* The greatest common factor of 250 and 280 is the product of the factors in the **intersection**.

$$\text{GCF} ~=~ 2^1\cdot 5^1 ~=~ 10$$

* The least common multiple of 250 and 280 is the product of the factors in the **union**.

$$\text{GCF} ~=~ 2^3\cdot 5^3\cdot 7^1 ~=~ 7000$$


\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
    primes = c(2,3,5,7,11)
    n1 = sample(2:6,1)
    n2 = sample(2:6,1)
    c1 = prod(sample(primes,n1,T,c(8,4,6,1,1)))
    c2 = prod(sample(primes,n2,T,c(8,4,6,1,1)))
    gcf = gcd2(c1,c2)
    lcm = c1*c2/gcf
    if(gcf>1 && sum(c1==7)<2 && sum(c1==11)<2 && sum(c2==7)<2 && sum(c2==11)<2 && c1<200 && c2<200 && lcm>max(c(c1,c2))){break}
}
```

1. Find the GCF and LCM of `r c1` and `r c2`.

* Factor trees 

\vfill

* Prime-exponential notation

\vfill

* Venn diagram

\vfill

* GCF

\vfill

* LCM

\vfill

\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
    primes = c(2,3,5,7,11)
    n1 = sample(2:6,1)
    n2 = sample(2:6,1)
    c1 = prod(sample(primes,n1,T,c(8,4,6,1,1)))
    c2 = prod(sample(primes,n2,T,c(8,4,6,1,1)))
    gcf = gcd2(c1,c2)
    lcm = c1*c2/gcf
    if(gcf>1 && sum(c1==7)<2 && sum(c1==11)<2 && sum(c2==7)<2 && sum(c2==11)<2 && c1<200 && c2<200 && lcm>max(c(c1,c2))){break}
}
```

2. Find the GCF and LCM of `r c1` and `r c2`.

* Factor trees 

\vfill

* Prime-exponential notation

\vfill

* Venn diagram

\vfill

* GCF

\vfill

* LCM

\vfill

\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
    primes = c(2,3,5,7,11)
    n1 = sample(2:6,1)
    n2 = sample(2:6,1)
    c1 = prod(sample(primes,n1,T,c(8,4,6,1,1)))
    c2 = prod(sample(primes,n2,T,c(8,4,6,1,1)))
    gcf = gcd2(c1,c2)
    lcm = c1*c2/gcf
    if(gcf>1 && sum(c1==7)<2 && sum(c1==11)<2 && sum(c2==7)<2 && sum(c2==11)<2 && c1<200 && c2<200 && lcm>max(c(c1,c2))){break}
}
```

3. Find the GCF and LCM of `r c1` and `r c2`.

* Factor trees 

\vfill

* Prime-exponential notation

\vfill

* Venn diagram

\vfill

* GCF

\vfill

* LCM

\vfill

\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
    primes = c(2,3,5,7,11)
    n1 = sample(2:6,1)
    n2 = sample(2:6,1)
    c1 = prod(sample(primes,n1,T,c(8,4,6,1,1)))
    c2 = prod(sample(primes,n2,T,c(8,4,6,1,1)))
    gcf = gcd2(c1,c2)
    lcm = c1*c2/gcf
    if(gcf>1 && sum(c1==7)<2 && sum(c1==11)<2 && sum(c2==7)<2 && sum(c2==11)<2 && c1<200 && c2<200 && lcm>max(c(c1,c2))){break}
}
```

4. Find the GCF and LCM of `r c1` and `r c2`.

* Factor trees 

\vfill

* Prime-exponential notation

\vfill

* Venn diagram

\vfill

* GCF

\vfill

* LCM

\vfill

\newpage

```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
    primes = c(2,3,5,7,11)
    n1 = sample(2:6,1)
    n2 = sample(2:6,1)
    c1 = prod(sample(primes,n1,T,c(8,4,6,1,1)))
    c2 = prod(sample(primes,n2,T,c(8,4,6,1,1)))
    gcf = gcd2(c1,c2)
    lcm = c1*c2/gcf
    if(gcf>1 && sum(c1==7)<2 && sum(c1==11)<2 && sum(c2==7)<2 && sum(c2==11)<2 && c1<200 && c2<200 && lcm>max(c(c1,c2))){break}
}
```

5. Find the GCF and LCM of `r c1` and `r c2`.

* Factor trees 

\vfill

* Prime-exponential notation

\vfill

* Venn diagram

\vfill

* GCF

\vfill

* LCM

\vfill

