```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
pa = 1:10
x = pa
f = sample(pa)
g = sample(pa)
mydf2 = data.frame(x,f,g)
colnames(mydf2) = c("$x$","$f(x)$","$g(x)$")
a = sample(pa,1)
b = sample(pa,1)
c = sample(pa,1)
d = sample(pa,1)
e = sample(pa,1)

an1 = f[g[a]]
an2 = g[f[b]]
an3 = f[f[c]]
an4 = g[g[d]]
an5 = f[g[g[e]]]

al = paste0("* ",pa,"\n",collapse="")

ans1 = paste0(1*(pa==an1),collapse="")
ans2 = paste0(1*(pa==an2),collapse="")
ans3 = paste0(1*(pa==an3),collapse="")
ans4 = paste0(1*(pa==an4),collapse="")
ans5 = paste0(1*(pa==an5),collapse="")

```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

Let functions $f$ and $g$ be defined by the table below.

```{r tab2, results="asis", echo=F}
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


Evaluate the following:

* $f(g(`r a`)) =$ ##ANSWER1##
* $g(f(`r b`)) =$ ##ANSWER2##
* $f(f(`r c`)) =$ ##ANSWER3##
* $g(g(`r d`)) =$ ##ANSWER4##
* $f(g(g(`r e`))) =$ ##ANSWER5##

Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`

Solution
========

* $f(g(`r a`))=f(`r g[a]`)=`r an1`$
* $g(f(`r b`))=g(`r f[b]`)=`r an2`$
* $f(f(`r c`))=f(`r f[c]`)=`r an3`$
* $g(g(`r d`))=g(`r g[d]`)=`r an4`$
* $f(g(g(`r e`)))=f(g(`r g[e]`))=f(`r g[g[e]]`)=`r an5`$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`|`r ans5`
exname: compose_table