```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
while(T){
  x = 1:10
  f = sample(1:10)
  g = sample(1:10)
  mydf2 = data.frame(x,f,g)
  colnames(mydf2) = c("$x$","$f(x)$","$g(x)$")
  a = sample(1:10,1)
  if(a != f[a] && a != g[a] && f[a] != g[a] && 
     f[g[a]] != g[f[a]] &&
     f[g[a]] != g[g[a]] &&
     g[f[a]] != f[f[a]]
     ){break}
}
isfg = sample(c(T,F),1)
if(isfg){
  ans = f[g[a]]
  qstr = paste0("f(g(",a,"))",collapse="")
  fir =  paste0("g(",a,")=",g[a],collapse="")
  sec = paste0("f(g(",a,"))=f(",g[a],")=",ans,collapse="")
} else {
  ans = g[f[a]]
  qstr = paste0("g(f(",a,"))",collapse="")
  fir =  paste0("f(",a,")=",f[a],collapse="")
  sec = paste0("g(f(",a,"))=g(",f[a],")=",ans,collapse="")
}
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

Let functions $f$ and $g$ be defined by the table below.

```{r tab2, results="asis", echo=F}
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```


Use those definition to find $`r qstr`$.



Solution
========

Start with the inner function: $$`r fir`$$

Then, evaluate the outer function: $$`r sec`$$

Meta-information
============
extype: num
exsolution: `r ans`
exname: graph_translations_and_reflections_abs_function