```{r data generation, echo = FALSE, results = "hide"}
xn = seq(0,2*pi,pi/2)
x = c("$0$","$\\frac{\\pi}{2}$","$\\pi$","$\\frac{3\\pi}{2}$","$2\\pi$")
y = sin(xn)
f = data.frame(x,y)
# y = a*sin(b(x-h))+k
ap = sample(c(1/2,1,2),4,T)*sample(c(-1,1),4,T)
a = ap[1]
b = ap[2]
h = ap[3]
k = ap[4]
al = sort(c(-4,-2,-1/2,-1/4,1/4,1/2,2,4))
```

Question
========

The sine function, and some of its points are tabled and plotted below.

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>


```{r tabadf, results="asis", echo=F}
knitr::kable(f,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s")
plot(0,0,type="n",xlim=c(0,2*pi),ylim=c(-pi,pi),lwd=2,ylab="sin(x)",xlab="x")
for(j in seq(0,7,0.5)){
  abline(v=j,lty=3)
}
for(j in seq(-4,4,0.5)){
  abline(h=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xx = seq(-1,2*pi+1,pi/50)
lines(xx,sin(xx),col = "blue",lwd=4)
points(xn,y)
points(xn[1],y[1],pch=20)
```
\

The generalized sinusoidal function contains 4 transformation parameters, $a$, $b$, $h$, and $k$:
$$g(x) = a\sin(b(x-h))+k$$

Compared to the parent sine function, the generalized sinusoidal function is stretched vertically by factor $a$, stretched horizontally by factor $\frac{1}{b}$, shifted right by $h$, and shifted up by $k$. The new amplitude equals $a$. The new period equals $\frac{2\pi}{b}$. The parent's origin point is translated to $(h,k)$.

Determine the equation of the sinusoidal function plotted below:

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(pty="s")

xvals = xn/b+h
yvals = y*a+k
xrad = (max(xvals)-min(xvals))/2
xmid = (max(xvals)+min(xvals))/2
yrad = (max(yvals)-min(yvals))/2
ymid = (max(yvals)+min(yvals))/2
maxrad = max(c(xrad,yrad))
xlo = xmid-maxrad
xhi = xmid+maxrad
ylo = ymid-maxrad
yhi = ymid+maxrad

plot(0,0,type="n",
     xlim=c(xlo,xhi),
     ylim=c(ylo,yhi),
     lwd=2,ylab="sin(x)",xlab="x")

for(j in seq(floor(xlo),ceiling(xhi),1)){
  abline(v=j,lty=3)
}
for(j in seq(floor(ylo),ceiling(yhi),1)){
  abline(h=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xx = seq(xlo-1,xhi+1,0.01)
lines(xx,a*sin(b*(xx-h))+k,col = "red",lwd=4)
points(xn/b+h,y*a+k)
points(xn[1]/b+h,y[1]*a+k,pch=20)
```
\


Answerlist
--------



Solution
========



Meta-information
============
extype: cloze
exclozetype: 
exsolution: 
exname: translate_table
exshuffle: FALSE