---
output: pdf_document
params:
    rseed: 0
    showsol: true
    useseed: false
    titex: "null"
urlcolor: blue
---

```{r,echo=F}
if(params$useseed){
    set.seed(params$rseed)
}
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

# PCW_09_22 Coordinate transformations v`r params$rseed`

### Question 1

```{r, echo = FALSE, results = "hide"}
et1s = sample(1:8,8)
et2s = sample(1:8,8)
et1 = et1s[1]
et2 = et2s[1]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("\\color{red}$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$\\color{black}",collapse="")

if(params$showsol){
    sol = ca
} else {
    sol = " "
}
```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. Write the coordinate transformation.

\vfill

`r sol`

\vfill


### Question 2

```{r, echo = FALSE, results = "hide"}
et1 = et1s[2]
et2 = et2s[2]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("\\color{red}$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$\\color{black}",collapse="")

if(params$showsol){
    sol = ca
} else {
    sol = ""
}
```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. Write the coordinate transformation.


\vfill

`r sol`

\vfill

### Question 3

```{r, echo = FALSE, results = "hide"}
et1 = et1s[3]
et2 = et2s[3]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("\\color{red}$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$\\color{black}",collapse="")

if(params$showsol){
    sol = ca
} else {
    sol = ""
}
```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. Write the coordinate transformation.


\vfill

`r sol`

\vfill

\newpage

# PCW_09_22 Coordinate transformations v`r params$rseed`

### Question 4

```{r, echo = FALSE, results = "hide"}
et1 = et1s[4]
et2 = et2s[4]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("\\color{red}$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$\\color{black}",collapse="")

if(params$showsol){
    sol = ca
} else {
    sol = ""
}
```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. Write the coordinate transformation.

\vfill

`r sol`

\vfill


### Question 5

```{r, echo = FALSE, results = "hide"}
et1 = et1s[5]
et2 = et2s[5]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("\\color{red}$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$\\color{black}",collapse="")

if(params$showsol){
    sol = ca
} else {
    sol = ""
}
```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. Write the coordinate transformation.


\vfill

`r sol`

\vfill

### Question 6

```{r, echo = FALSE, results = "hide"}
et1 = et1s[6]
et2 = et2s[6]
mas = sample(2:9,4)
m1 = mas[1]
m2 = mas[2]
a1 = mas[3]
a2 = mas[4]
exp_frames = c("M\\left(x+A\\right)",
               "M x+A",
               "M\\left(x-A\\right)",
               "M x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")
exp_frames2 = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

exp2 = exp_frames2[et2]
exp2 = gsub("A",a2,exp2,fixed=T)
exp2 = gsub("M",m2,exp2,fixed=T)
exp3 = gsub("x","f{\\left[a\\right]}",exp2,fixed=T)
exp4 = gsub("x","b",exp2,fixed=T)
exptemp = gsub("x","f{\\left[arg\\right]}",exp2,fixed=T)
exp1 = gsub("arg",exp_frames[et1],exptemp,fixed=T)
exp1 = gsub("A",a1,exp1,fixed=T)
exp1 = gsub("M",m1,exp1,fixed=T)

invarg = exp_frames[9-et1]
invarg = gsub("A",a1,invarg,fixed=T)
invarg = gsub("M",m1,invarg,fixed=T)
invarg = gsub("x","a",invarg,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",a2,outex,fixed=T)
outex = gsub("M",m2,outex,fixed=T)
outex = gsub("x","b",outex,fixed=T)

ca = paste0("\\color{red}$$(a,b)\\to \\left(",invarg,"~,~",outex,"\\right)$$\\color{black}",collapse="")

if(params$showsol){
    sol = ca
} else {
    sol = ""
}
```

Consider the two functions $f$ and $g$, where $g$ is defined as a transformation of $f$:

$$g[x]~=~`r exp1`$$

For point $(a,b)$ on curve $f$ there is a corresponding point on the curve $g$. Write the coordinate transformation.


\vfill

`r sol`

\vfill


