```{r,echo=FALSE}
ords = list(c(1,2,3),
            c(1,3,2),
            c(2,1,3),
            c(2,3,1),
            c(3,1,2),
            c(3,2,1))
ord = sample(1:6)
ord2 = ords[ord]
xx = list()
yy = list()
zz = list()
tt = list()
col = list()
dt = 0.1
while(T){
  allgood = T
  x0s = sample(seq(-3,3,0.1),3)
  indy = 0
  for(o in ord){
    indy = indy+1
    x0 = x0s[ords[[o]][1]]
    y0 = x0s[ords[[o]][2]]
    z0 = x0s[ords[[o]][3]]
    x = c(x0)
    y = c(y0)
    z = c(z0)
    t = c(0)
    for(i in 1:101){
      dx = y[i]*dt
      dy = (-x[i]+y[i]*z[i])*dt
      dz = (1-y[i]^2)*dt
      x = c(x,x[i]+dx)
      y = c(y,y[i]+dy)
      z = c(z,z[i]+dz)
      t = c(t,t[i]+dt)
      if(abs(x[i+1])>20 || abs(y[i+1])>20 || abs(z[i+1])>20){
        allgood = F
        break
      }
    }
    if(allgood){
      xx[[indy]] = x
      yy[[indy]] = y
      zz[[indy]] = z
      tt[[indy]] = t
      col[[indy]] = c("","","")
      col[[indy]][x0s[1] == c(x0,y0,z0)] = "blue"
      col[[indy]][x0s[2] == c(x0,y0,z0)] = "red"
      col[[indy]][x0s[3] == c(x0,y0,z0)] = "orange"
    } else {
      break
    }
  }
  if(allgood){break}
}
x0 = x0s[1]
y0 = x0s[2]
z0 = x0s[3]
sol = paste0(1*(ord==1),collapse="")
best = c("A","B","C","D","E","F")[ord==1]
```


Question
========

In the book "Chaos and Time-Series Analysis" by Julien Clinton Sprott, a simple system of differential equations is given. Research into this system was published by Nosé (1991) and Hoover (1995).

$$\begin{align}
\frac{\Delta x}{\Delta t} &= y \\\\
\frac{\Delta y}{\Delta t} &= -x+yz \\\\
\frac{\Delta z}{\Delta t} &= 1-y^2
\end{align}$$

Use these initial conditions:
$$t_0 = 0$$
$$x_0 = `r x0`$$
$$y_0 = `r y0`$$
$$z_0 = `r z0`$$

Use Euler's method with a step size of $\Delta t = `r dt`$ to simulate until $t=`r dt*100`$. Plot $x$, $y$, and $z$ as functions of time, using blue, red, and orange respectively. Determine which plot matches your simulation.

```{r,echo=F,fig.dim=c(6,10)}
par(mfrow=c(4,2),mar=c(3,3,1,0))
plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
legend(-1,1,c("x(t)","y(t)","z(t)"),col=c("blue","red","orange"),lwd=c(1,1,1),cex=3)
plot(0,0,type="n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
lets = c("A","B","C","D","E","F")
for(i in 1:6){
  x = xx[[i]]
  y = yy[[i]]
  z = zz[[i]]
  t = tt[[i]]
  minmin = min(c(x,y,z))
  maxmax = max(c(x,y,z))
  plot(t,x,type="l",ylim=c(minmin,maxmax),col=col[[i]][1],main=lets[i])
  lines(t,y,col=col[[i]][2])
  lines(t,z,col=col[[i]][3])
}
```
\

Answerlist
--------

* A
* B
* C
* D
* E
* F



Solution
========

The correct graph is **`r best`**.

```{r,echo=F,fig.dim=c(6,6)}
theone = sum((1:6)[1==ord])
x = xx[[theone]]
y = yy[[theone]]
z = zz[[theone]]
t = tt[[theone]]
minmin = min(c(x,y,z))
maxmax = max(c(x,y,z))
plot(t,x,type="l",col="blue",ylim=c(minmin,maxmax),ylab=c("x, y, z"))
lines(t,y,type="l",col="red")
lines(t,z,type="l",col="orange")
```
\

In each round, to calculate the deltas:

$$\begin{align}
\Delta x &= y \cdot \Delta t \\\\
\Delta y &= (-x+yz)\cdot \Delta t \\\\
\Delta z &= (1-y^2)\cdot \Delta t
\end{align}$$

Your spreadsheet should give these values:

<style>
table.brd td{
  border: 1px solid black;
  padding: 5px;
  text-align: center;
}
table.brd th{
  border: 2px solid black;
  padding: 5px;
  text-align: center;
}
table.brd {
  border: 3px solid black;
}
</style>

<table class="brd">
  <tr>
    <th>$t$</th> 
    <th>$x$</th> 
    <th>$y$</th> 
    <th>$z$</th>
    <th>$\Delta t$</th>
    <th>$\Delta x$</th>
    <th>$\Delta y$</th>
    <th>$\Delta z$</th>
  </tr>
  <tr>
    <td>0</td>
    <td>`r x[1]`</td>
    <td>`r y[1]`</td>
    <td>`r z[1]`</td>
    <td> `r dt` </td>
    <td>`r x[2]-x[1]`</td>
    <td>`r y[2]-y[1]`</td>
    <td>`r z[2]-z[1]`</td>
  </tr>
  <tr>
    <td>`r t[2]`</td>
    <td>`r x[2]`</td>
    <td>`r y[2]`</td>
    <td>`r z[2]`</td>
    <td> `r dt` </td>
    <td>`r x[3]-x[2]`</td>
    <td>`r y[3]-y[2]`</td>
    <td>`r z[3]-z[2]`</td>
  </tr>
  <tr>
    <td>`r t[3]`</td>
    <td>`r x[3]`</td>
    <td>`r y[3]`</td>
    <td>`r z[3]`</td>
    <td> `r dt` </td>
    <td>`r x[4]-x[3]`</td>
    <td>`r y[4]-y[3]`</td>
    <td>`r z[4]-z[3]`</td>
  </tr>
  <tr>
    <td>`r t[4]`</td>
    <td>`r x[4]`</td>
    <td>`r y[4]`</td>
    <td>`r z[4]`</td>
    <td> `r dt` </td>
    <td>`r x[5]-x[4]`</td>
    <td>`r y[5]-y[4]`</td>
    <td>`r z[5]-z[4]`</td>
  </tr>
  <tr>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
    <td>$\vdots$</td>
  </tr>
  <tr>
    <td>`r t[100]`</td>
    <td>`r x[100]`</td>
    <td>`r y[100]`</td>
    <td>`r z[100]`</td>
    <td> `r dt` </td>
    <td>`r x[101]-x[100]`</td>
    <td>`r y[101]-y[100]`</td>
    <td>`r z[101]-z[100]`</td>
  </tr>
  <tr>
    <td>`r t[101]`</td>
    <td>`r x[101]`</td>
    <td>`r y[101]`</td>
    <td>`r z[101]`</td>
    <td> `r dt` </td>
    <td>`r x[102]-x[101]`</td>
    <td>`r y[102]-y[101]`</td>
    <td>`r z[102]-z[101]`</td>
  </tr>
</table>

In a Google spreadsheet, highlight the columns of $t$, $x$, $y$, and $z$. Then `Insert` a `Chart`. Make sure to choose a `Line Chart` for the chart type. Also, make sure to use the first column (with $t$ values) as labels. Google spreadsheets should default to using blue, red, and orange for the lines by default.



Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: Nose_Hoover
extol: 0.01