```{r,echo=F,warning=F}
A = round(runif(1,0.7,4),1)
P = round(runif(1,2,6.6)/4,1)*4
B = 2*pi/P
D = round(runif(1,0.1,4.9-A),1)*sample(c(-1,1),1)
h = round(runif(1,0.1,P),1)
C = h*B
```

Question
========

Some quantity ($y$) is varying in time ($t$), following a temporal [sinusoidal function](https://en.wikipedia.org/wiki/Sine_wave) parameterized with 4 parameters:

$$y(t) ~=~ A\sin\left(\frac{2\pi}{P}(t+L)\right)+D$$

* Amplitude $A$, where $A>0$
  * Amplitude is the "vertical stretch" factor. It is **half the difference of the max and min** (of the $y$ values),
  * A negative $A$ would cause a vertical reflection. However, an equivalent transformation would be caused by shifting "horizontally" (in time) by half a period, so there is no loss of generality by forcing $A$ to be positive.
  * The amplitude might indicate changes in pressure, position, temperature, or many other types of quantities.
  * The [wikipedia article on amplitude](https://en.wikipedia.org/wiki/Amplitude#Semi-amplitude) refers to $A$ as the semi-amplitude.
* Period $P$, where $P>0$
  * Period is a "horizontal stretch" factor.
  * It is the **difference in time between neighboring peaks**.
  * Another symbol, $T$, is often used for period.
  * Period has units of time, typically seconds.
  * The [frequency](https://en.wikipedia.org/wiki/Frequency) is the reciprocal of $P$, so $f=\frac{1}{P}$. Frequency has units of [hertz](https://en.wikipedia.org/wiki/Hertz).
  * The [angular frequency](https://en.wikipedia.org/wiki/Angular_frequency) $\omega$ is in radians per second: $\omega~=~\frac{2\pi}{P}~=~2\pi f$
  * If the independent variable is spatial rather than temporal, the analogous term to "period" is "[wavelength](https://en.wikipedia.org/wiki/Wavelength)"; often $\lambda$ is used for wavelength.
  * Most physical waves (like sound and light) vary in space and time, so they have both wavelength and period, which are related by the speed ($v$) of the wave: $v=\frac{\lambda}{P}$
* Leftward shift $L$, where $0\le L<P$. All points along the sine function are shifted backwards (in time) by $L$.
  * When $t=0$, it is kind of like $L$ time has already passed (compared to the parent sine function).
  * Like $A$, the parameter $L$ does not need to be constrained (between 0 and $P$), but any sinusoidal wave can be generated with this constraint.
  * This parameter, $L$, has units of time.
  * Many textbooks will incorrectly/confusingly refer to this as the "phase shift".
  * The [phase](https://en.wikipedia.org/wiki/Phase_(waves)) shift, $\phi$, has units of radians: $\phi=\frac{2\pi L}{P}$.
* [Vertical shift](https://manual.audacityteam.org/man/dc_offset.html) $D$
  * The vertical shift is **half the sum of the max and min**, which is the average of the max and min.
  * This vertical shift is called [DC offset or DC bias](https://en.wikipedia.org/wiki/DC_bias) in sound recording.
  * The midline at $y=D$ is halfway between the [crests and troughs](https://en.wikipedia.org/wiki/Crest_and_trough).



Those four parameters were randomly assigned values, producing the graph below.

```{r,fig.dim=c(10,10),echo=F}
par(mar=c(5,5,0,0),pty="s")
plot(0,0,type="n",xlim=c(-5,5),ylim=c(-5,5),xlab="t",ylab="y")

for(i in seq(-6,6,0.1)){
  if(i%%1==0){
    abline(h=i,col="darkgrey",lwd=1)
    abline(v=i,col="darkgrey",lwd=1)
  } else {
    abline(h=i,col="grey",lwd=0.5)
    abline(v=i,col="grey",lwd=0.5)
  }
}

arrows(0,-5,0,5,length=0.1,angle=10,code=3,lwd=1.5)
arrows(-5,0,5,0,length=0.1,angle=10,code=3,lwd=1.5)

t = seq(-6,6,0.01)
lines(t,A*sin(B*t+C)+D,lwd=3,col="blue")
```
\

Estimate the **period** of the [sinusoidal](https://www.khanacademy.org/math/algebra2/x2ec2f6f830c9fb89:trig/x2ec2f6f830c9fb89:amp-mid-period/a/midline-amplitude-and-period-review) function graphed above.


Solution
========

Find the time difference between corresponding points in sequential repetitions.

```{r,fig.dim=c(10,10),echo=F}
par(mar=c(5,5,0,0),pty="s")
plot(0,0,type="n",xlim=c(-5,5),ylim=c(-5,5),xlab="t",ylab="y")

for(i in seq(-6,6,0.1)){
  if(i%%1==0){
    abline(h=i,col="darkgrey",lwd=1)
    abline(v=i,col="darkgrey",lwd=1)
  } else {
    abline(h=i,col="grey",lwd=0.5)
    abline(v=i,col="grey",lwd=0.5)
  }
}

arrows(0,-5.2,0,5.2,length=0.1,angle=10,code=3,lwd=1.5)
arrows(-5.2,0,5.2,0,length=0.1,angle=10,code=3,lwd=1.5)

t = seq(-6,6,0.01)
lines(t,A*sin(2*pi/P*(t+h))+D,lwd=3,col="blue")

xmas = -h+P/4+P*(-2:2)
xmis = -h+3*P/4+P*(-2:2)
xmas = xmas[abs(xmas)<5]
xmis = xmis[abs(xmis)<5]
if(length(xmas)>1){
  xs = round(xmas,2)
  ys = round(rep(A+D,length(xs)),2)
  for(j in 1:length(xs)){
    text(xs[j]+0.6,ys[j]+0.2,paste0("(",xs[j],", ",ys[j],")"),col="purple",cex=1)
    text(xs[j]-0.2,-4.5,
         paste0("t = ",xs[j],collapse=""),srt=90,cex=2,col="purple")
  }
} else {
  xs = round(xmis,2)
  ys = round(rep(-A+D,length(xs)),2)
  for(j in 1:length(xs)){
    text(xs[j]+0.6,ys[j]-0.2,paste0("(",xs[j],", ",ys[j],")"),col="purple",cex=1)
    text(xs[j]-0.2,-4.5,
         paste0("t = ",xs[j],collapse=""),srt=90,cex=2,col="purple")
  }
}
points(xs,ys,pch=19,col="purple",cex=2)
abline(v=xs,col="purple",lty=2,lwd=3)

arrows(xs[1],-3,xs[2],-3,0.1,10,3,col="red",lwd=4)
text(mean(xs[1:2]),-2.5,paste0("P = ",P,collapse=""),col="red",cex=2)

```
\

$$P~=~ (`r xs[2]`)-(`r xs[1]`)$$
$$P = `r P`$$


This exact function could be plotted with the following algebraic definition:
$$y(t) = `r A` \sin\left(\frac{2\pi}{`r P`}(t+`r h`)\right)+(`r D`)$$

The amplitude is `r A`; the period is `r P`; the horizontal shift is left by `r h`; and the midline is $y=`r D`$.



Meta-information
============
extype: num
exsolution: `r P`
exname: estimate_period
extol: 0.1