```{r,echo=F}
while(T){
  ang = round(runif(1,pi/7,1.3),2)
  hyp = round(runif(1,12,99),0)
  opp = sin(ang)*hyp
  opp2 = round(opp,0)
  ang2 = round(asin(opp2/hyp),2)
  angt = sprintf("%.2f",ang2)
  angd = sprintf("%.1f",asin(opp2/hyp)*180/pi)
  hypt = sprintf("%.0f",round(hyp,0))
  oppt = sprintf("%.0f",round(opp2,0))
  if(hyp-opp2>2 && opp2>10 && ang2!=round(opp2/hyp,2)  &&
     ang2 != round(1/sin(opp2/hyp),2)){break}
}
angans = round(asin(opp2/hyp)*180/pi,1)
```

Question
========

A right triangle has an angle measure $\theta$. The opposite leg's length is `r opp2` meters, and the hypotenuse's length is `r hypt` meters. What is the angle measure $\theta$ in degrees?

```{r,fig.dim=c(5,5),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",axes=F,ann=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
th = seq(0,pi/2,length.out=100)
lines(cos(th),sin(th),lty=2,col="grey")
lines(c(0,cos(ang),cos(ang),0),c(0,0,sin(ang),0),lwd=3)
lines(c(cos(ang)-0.02,cos(ang)-0.02,cos(ang)),c(0,0.02,0.02))
th2 = seq(0,ang,length.out=100)
#lines(cos(th2),sin(th2),lty=2,col=rgb(1,0.8,0.8))
#text(1.07*cos(ang/2),1.07*sin(ang/2),paste0(angt,"*",hypt),col=rgb(1,0.8,0.8),cex=0.7)
lines(c(cos(ang),cos(ang)),c(0,sin(ang)),col="purple",lwd=4)
text(cos(ang)+0.05,sin(ang)/2,paste0(opp2," m"),col="purple",cex=0.8)
lines(c(0,cos(ang)),c(0,sin(ang)),col="blue",lwd=4)
text(cos(ang)/2+0.05*cos(ang+pi/2),
     sin(ang)/2+0.05*sin(ang+pi/2),
     paste0(hypt," m"),srt=ang/pi*180,col="blue",cex=0.8)
lines(0.1*cos(th2),0.1*sin(th2),col="red")
text(0.16*cos(ang/2),0.16*sin(ang/2),TeX("$\\theta$"),col="red",cex=0.8)
```
\

Please round your answer to the tenth of a degree.


Solution
========

First, identify the correct trigonometric function. Remember, [SOHCAHTOA](https://en.wikipedia.org/wiki/Mnemonics_in_trigonometry).

$$\sin(\theta)=\frac{\mathrm{opposite}}{\mathrm{hypotenuse}}$$


$$\cos(\theta)=\frac{\mathrm{adjacent}}{\mathrm{hypotenuse}}$$


$$\tan(\theta)=\frac{\mathrm{opposite}}{\mathrm{adjacent}}$$

In this case, we are given the **opposite** and the **hypotenuse**, and we are asked for the angle measure. The trigonometric ratio that relates these two sides is [sine](https://en.wikipedia.org/wiki/Trigonometric_functions). Use $\theta$ to represent the requested angle measure.

$$\sin(\theta) = \frac{`r opp2`}{`r hypt`}$$

To evaluate $\theta$, we need to use the [inverse of sine](https://en.wikipedia.org/wiki/Inverse_trigonometric_functions). This inverse function has a few names: arcsin, asin, or $\sin^{-1}$ are the most commonly used.

$$\theta = \arcsin\left(\frac{`r opp2`}{`r hypt`}\right)$$

$$\theta = \sin^{-1}\left(\frac{`r opp2`}{`r hypt`}\right)$$

Depending on your calculator, you might type something like ``round(arcsin(`r opp2`/`r hypt`),2)``.  Make sure you are in degree mode, not radian mode.

$$\theta \approx `r angd`$$


Meta-information
============
extype: num
exsolution: `r angans`
exname: sin_get_ang
extol: 0.1