```{r,echo=F}
while(T){
  ang = round(runif(1,pi/7,1.3),2)
  hyp = round(runif(1,12,99),0)
  adj = cos(ang)*hyp
  adj2 = round(adj,0)
  angt = sprintf("%.2f",ang)
  angd = sprintf("%.1f",ang*180/pi)
  hypt = sprintf("%.0f",round(hyp,0))
  adjt = sprintf("%.0f",round(adj2,0))
  if(hyp-adj2>2 && adj2>10 && round((pi/2-ang)*hyp)!=adj2 && hyp!=round(adj2*ang)){break}
}
```

Question
========

A right triangle has an angle of `r angd` degrees. The hypotenuse has a length of `r hypt` meters. How long, in meters, is the leg adjacent the angle?

```{r,fig.dim=c(5,5),echo=F}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",axes=F,ann=F,xlim=c(-0.1,1.1),ylim=c(-0.1,1.1))
th = seq(0,pi/2,length.out=100)
lines(cos(th),sin(th),lty=2,col="grey")
lines(c(0,cos(ang),cos(ang),0),c(0,0,sin(ang),0),lwd=3)
lines(c(cos(ang)-0.02,cos(ang)-0.02,cos(ang)),c(0,0.02,0.02))
th2 = seq(0,ang,length.out=100)
#lines(cos(th2),sin(th2),lty=2,col=rgb(1,0.8,0.8))
#text(1.07*cos(ang/2),1.07*sin(ang/2),paste0(angt,"*",hypt),col=rgb(1,0.8,0.8),cex=0.7)
lines(c(0,cos(ang)),c(0,0),col="purple",lwd=4)
text(cos(ang)/2,-0.05,"? m",col="purple",cex=0.8)
lines(c(0,cos(ang)),c(0,sin(ang)),col="blue",lwd=4)
text(cos(ang)/2+0.05*cos(ang+pi/2),
     sin(ang)/2+0.05*sin(ang+pi/2),
     paste0(hypt," m"),srt=ang/pi*180,col="blue",cex=0.8)
lines(0.1*cos(th2),0.1*sin(th2),col="red")
text(0.16*cos(ang/2),0.16*sin(ang/2),TeX(paste0("$",angd,"^\\circ$")),col="red",cex=0.8)
```
\

Please round your answer to the nearest meter.


Solution
========

First, identify the correct trigonometric function. Remember, [SOHCAHTOA](https://en.wikipedia.org/wiki/Mnemonics_in_trigonometry).

$$\sin(\theta)=\frac{\mathrm{opposite}}{\mathrm{hypotenuse}}$$


$$\cos(\theta)=\frac{\mathrm{adjacent}}{\mathrm{hypotenuse}}$$


$$\tan(\theta)=\frac{\mathrm{opposite}}{\mathrm{adjacent}}$$

In this case, we are given the angle and the **hypotenuse**, and we are asked for the **adjacent** leg. The trigonometric ratio that relates these two sides is [cosine](https://en.wikipedia.org/wiki/Trigonometric_functions). Let $x$ represent the requested length.

$$\cos(`r angd`) = \frac{x}{`r hypt`}$$
Multiply both sides by `r hypt` to solve for $x$.

$$`r hypt` \cdot \cos(`r angd`) = x$$
To evaluate $x$, type the following into a modern calculator: ``round(`r hypt`*cos(`r angd`))``. Make sure to be in radian mode, not degree mode.

$$x \approx `r adjt`$$

Meta-information
============
extype: num
exsolution: `r adj2`
exname: cos_get_adj
extol: 1