```{r,echo=F}
# 360 = 36*10 = 6*6*2*5 = 2^3*3^2*5
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  deg = sample(30:350,1)
  div = gcd(deg,360)
  num = round(deg/div)
  den = round(360/div)
  radnum = num*2
  radden = den
  raddiv = gcd(radnum,radden)
  radnum = round(radnum/raddiv)
  radden = round(radden/raddiv)
  r = sample(2:8,1)
  shuch = list(c(0,deg/180*pi))
  sol = r*2*pi*deg/360
  anum = num*2*r
  aden = den
  div2 = gcd(anum,aden)
  anum = round(anum/div2)
  aden = round(aden/div2)
  if(den>4 && den<20 && deg%%90 != 0 && aden!=1){break}
}
if(radnum==1){
  rn = ""
} else {
  rn = paste0(radnum)
}
```

Question
========

An arc is drawn along the circumference of a circle with a radius of `r r` meters. The arc's angle is $\frac{`r radnum`\pi}{`r radden`}$ radians. What is the arc's length in meters?

```{r,echo=F,fig.dim=c(4,4)}
library(latex2exp)
par(pty="s")
for(i in 1:length(shuch)){
  par(mar=c(1,1,1,1),pty="s")
  plot(0,0,type="n",ann=F,axes=F,xlim=c(-1,1),ylim=c(-1,1))
  th = seq(0,2*pi,pi/100)
  lines(cos(th),sin(th))
  a1 = shuch[[i]][1]
  a2 = shuch[[i]][2]
  lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=2)
  text(0.5,-0.05,paste0(r," m"),col="blue")
  lines(c(0,cos(a2)),c(0,sin(a2)))
  len = 100
  th = seq(a1,a2,(a2-a1)/len)
  len = length(th)-1
  lines(cos(th),sin(th),col="purple",lwd=2)
  ra = 0.4-0.2*deg/360
  lines(cos(th)*ra,sin(th)*ra,col="red",lwd=2)
  arrows(ra*cos(th[len]),ra*sin(th[len]),
         ra*cos(th[len+1]),ra*sin(th[len+1]),length=0.1,
         col="red",lwd=2)
  text((ra+0.2)*cos(th[len%/%2]),(ra+0.2)*sin(th[len%/%2]),
       TeX(paste0("\\frac{",rn,"\\pi}{",radden,"}")),col="red")
  text(0.9*cos(th[len%/%2]),0.9*sin(th[len%/%2]),TeX("$x$"),col="purple")
}
```
\

The tolerance is $\pm0.01$ meters.

Solution
========

This problem shows a useful property of radians. To find the arc length, just multiply the angle measure (in radians) by the radius.

$$x = \frac{`r radnum`\pi}{`r radden`}\cdot `r r`$$

$$x = \frac{`r anum`\pi}{`r aden`}$$

Evaluate the decimal approximation.

$$x \approx `r sol`$$

So the arc length is approximately `r sol` meters.

Meta-information
============
extype: num
exsolution: `r sol`
exname: arc_length_rads
extol: 0.01