```{r,echo=F}
# 360 = 36*10 = 6*6*2*5 = 2^3*3^2*5
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

r = sample(4:8,1)
theta = round(runif(1,1,5.5),2)
L = r*theta
sa = r*L/2
```

Question
========

An arc is drawn along the circumference of a circle with a radius of $r=`r r`$ meters. The arc's length is $L=`r L`$ meters. What is the corresponding [sector's area](https://en.wikipedia.org/wiki/Circular_sector) (labelled $A$) in square meters?

```{r,echo=F,fig.dim=c(4,4)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",ann=F,axes=F,xlim=c(-1.3,1.3),ylim=c(-1.3,1.3))
th = seq(0,2*pi,pi/100)
lines(cos(th),sin(th))
a1 = 0
a2 = theta
len = 100
th = seq(a1,a2,length.out=len+1)
polygon(c(0,cos(th)),c(0,sin(th)),col=rgb(0.8,0.8,0.1,0.2))
lines(c(0,cos(a1)),c(0,sin(a1)),col="blue",lwd=2)
text(0.5,-0.07,paste0("r = ",r," m"),col="blue")
lines(c(0,cos(a2)),c(0,sin(a2)))
lines(cos(th),sin(th),col="purple",lwd=2)
ra = 1/r
lines(cos(th)*ra,sin(th)*ra,col="red",lwd=2)
arrows(ra*cos(th[len]),ra*sin(th[len]),
       ra*cos(th[len+1]),ra*sin(th[len+1]),length=0.05,
       col="red",lwd=2)
text((ra+0.1)*cos(th[len%/%2]),(ra+0.1)*sin(th[len%/%2]),
     TeX("$\\theta$"),col="red")
text(0.75*cos(th[len%/%2]),0.75*sin(th[len%/%2]),
     "A",col=rgb(0.4,0.4,0.05,1))
text(1.23*cos(th[len%/%2]),1.23*sin(th[len%/%2]),
     TeX(paste0(L," m",collapse="")),col="purple")
```
\

Please give an exact answer (in $\mathrm{m^2}$).

Solution
========

Divide the arc length by the radius to get the angle measure (in radians).

$$\theta = \frac{`r L`}{`r r`}$$

$$\theta = `r theta`$$

Find the area of the entire circle. Then multiply that area by the fraction of the circle.


$$A = \pi r^2 \cdot \frac{\theta}{2\pi}$$

$$A = \pi (`r r`)^2 \cdot \frac{`r theta`}{2\pi}$$

$$A = `r sa`$$

If you are feeling clever, you might derive a simpler formula.

$$\theta = \frac{L}{r}$$
$$A ~=~ \pi r^2 \cdot \frac{L}{2\pi r} ~=~ \frac{rL}{2}$$

So, the area of the sector is `r sa` $\mathrm{m^2}$.

Meta-information
============
extype: num
exsolution: `r sa`
exname: sector_area