---
header-includes:
   - \usepackage{array}
output: pdf_document
params:
    rseed: 1
    showsol: false
    titex: "Practice"
    useseed: false
urlcolor: blue
---


```{r,echo=F}
# In the future, you should make it so the domain is never the same as the range!
if(params$useseed){
    set.seed(params$rseed)
}
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## Intervals, Transformations, and Slope  `r params$titex` (version `r params$rseed`)


```{r,echo=F}
while(T){
    xp = sort(sample(-10:10,5))
    while(T){
        yp = sample(1:10,5,T)*c(1,-1,1,-1,-1)*sample(c(-1,1),1)
        if(abs(yp[5])<abs(yp[4])){break}
    }
    
    if(sample(1:2,1)==1){
        yp = rev(yp)
    }
    xa = min(xp):max(xp)
    ya = rep(0,length(xa))
    for(i in 1:length(xa)){
        x = xa[i]
        xl = max(xp[xp<=x])
        xr = min(c(xp[xp>x],xp[length(xp)]))
        yl = yp[xp==xl]
        yr = yp[xp==xr]
        rat = (x-xl)/(xr-xl)
        if(x>xl){
            ya[i] = yl*(1-rat)+yr*rat
        } else {
            ya[i] = yl
        }
        
    }
    if(sum(ya==0)==3 && !(min(ya)==min(xa) && max(ya)==max(xa))){break}
}

xpn = c(xa[1],xa[ya==0],xa[length(xa)])
ipos = character()
ineg = character()
for(i in 1:(length(xpn)-1)){
    xl = xpn[i]
    xr = xpn[i+1]
    xt = xl+1
    yl = ya[xa==xl]
    yt = ya[xa==xt]
    ymid = mean(c(yl,yt))
    if(ymid>0){
        ipos = c(ipos,paste0("(",xl,", ",xr,")",collapse=""))
    } else {
        ineg = c(ineg,paste0("(",xl,", ",xr,")",collapse=""))
    }
}
iinc = character()
idec = character()
for(i in 1:(length(xp)-1)){
    xl = xp[i]
    xr = xp[i+1]
    xt = xl+1
    yl = ya[xa==xl]
    yt = ya[xa==xt]
    if(yt>yl){
        iinc = c(iinc,paste0("(",xl,", ",xr,")",collapse=""))
    } else {
        idec = c(idec,paste0("(",xl,", ",xr,")",collapse=""))
    }
}


if(params$showsol){
    posint = paste0("$",paste0(ipos,collapse=" \\cup "),"$",collapse="")
    negint = paste0("$",paste0(ineg,collapse=" \\cup "),"$",collapse="")
    incint = paste0("$",paste0(iinc,collapse=" \\cup "),"$",collapse="")
    decint = paste0("$",paste0(idec,collapse=" \\cup "),"$",collapse="")
    domint = paste0("$(",min(xp),", ",max(xp),")$")
    ranint = paste0("$(",min(yp),", ",max(yp),")$")
} else {
    posint = ""
    negint = ""
    incint = ""
    decint = ""
    domint = ""
    ranint = ""
}


```

1. The function $f$ is graphed below.

```{r,echo=F,fig.dim=c(5,4)}
layout(matrix(c(1,1,1,1,2),nrow=1))
par(mar=c(0,0,0,0),pty="s")
plot(xa,ya,"l",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    abline(h=i,col="lightgrey",lwd=0.5)
    abline(v=i,col="lightgrey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    abline(h=i,col="darkgrey",lwd=1)
    abline(v=i,col="darkgrey",lwd=1)
}
arrows(-10.3,0,10.3,0,0.1,10,3,lwd=2)
arrows(0,-10.3,0,10.3,0.1,10,3,lwd=2)
lines(xa,ya,col="blue",lwd=3)
points(xp,yp,pch=20,col="blue",cex=1.6)
points(xa[1],ya[1],pch=20,col="white",cex=0.8)
points(xa[length(xa)],ya[length(xa)],pch=20,col="white",cex=0.8)

text(10,-0.5,"10",cex=0.8)
text(-10,-0.5,"-10",cex=0.8)
text(-0.5,10,"10",cex=0.8)
text(-0.5,-10,"-10",cex=0.8)
text(10,0.5,"x",cex=0.8)
text(0.5,10,"y",cex=0.8)

plot(0,0,"n",axes=F,ann=F)
legend("center",legend="y = f(x)",col="blue",lwd=3)



```
\

Indicate the following intervals using interval notation. Remember, you can use $\cup$ between two intervals to indicate the union. Except for range, all intervals will indicate $x$ values; this is standard.

\begin{tabular}{|m{1in}|m{5in}|}\hline
Feature & Where \\ \hline \hline
Positive & `r posint` \\  [2.5em]  \hline
Negative & `r negint` \\  [2.5em]  \hline
Increasing & `r incint` \\ [2.5em]  \hline
Decreasing & `r decint` \\ [2.5em]  \hline
Domain & `r domint` \\ [2.5em]  \hline
Range & `r ranint` \\ [2.5em]  \hline
\end{tabular}

\newpage

## Intervals, Transformations, and Slope  `r params$titex` (version `r params$rseed`)

```{r prob2,echo=F}
while(T){
    xs = sort(sample(c(-6,-4,-2,0,2,4,6),3))
    ys = sample(-5:5,3)
    m1 = (ys[2]-ys[1])/(xs[2]-xs[1])
    m2 = (ys[3]-ys[2])/(xs[3]-xs[2])
    if(abs(m1)!=abs(m2) && max(xs)-min(xs)>4 && sign(m1)!=sign(m2)){break}
}
h = sample(c(-2,2),1)
xa = xs+h
ya = ys
ea = gsub("--","+",paste0("$y=f(x-",h,")$",collapse=""),fixed=T)

k = sample(c(-2,2),1)
xb = xs
yb = ys+k
eb = gsub("+-","-",paste0("$y=f(x)+",k,"$",collapse=""),fixed=T)

a = sample(c(-2,2),1)
xc = xs
yc = a*ys
ec = paste0("$y=",a,"\\cdot f(x)$",collapse="")

b = sample(c(-2,2),1)
xd = xs/b
yd = ys
ed = paste0("$y=f(",b,"\\cdot x)$",collapse="")

xl = list(xa,xb,xc,xd)
yl = list(ya,yb,yc,yd)
el = c(ea,eb,ec,ed)

daord = sample(1:4)

```

2. In the four graphs below, $y=f(x)$ is graphed as a dotted line. With a solid line, please graph the transformations indicated by the equations below.

```{r,echo=F,fig.dim=c(6,5)}
par(mfrow=c(2,2),pty="s",mar=c(0,0,2,0))
library(latex2exp)
for(j in 1:4){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    mtext(TeX(el[daord[j]]),3,0)
    for(i in -10:10){
        lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.5)
        lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.5)
    }
    for(i in seq(-10,10,5)){
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
    }
    arrows(-10.5,0,10.5,0,0.1,10,3,lwd=2)
    arrows(0,-10.5,0,10.5,0.1,10,3,lwd=2)
    lines(xs,ys,col="red",lty=2,lwd=1)
    points(xs,ys,col="red",pch=20,cex=0.5)
    if(params$showsol){
        lines(xl[[daord[j]]],yl[[daord[j]]],col="blue",lwd=3)
        points(xl[[daord[j]]],yl[[daord[j]]],col="blue",pch=20,cex=1)
    }
}
```
\


```{r prob3, echo=F}
dafracs = list(c(1,2),c(3,2),c(5,2),c(7,2),c(9,2),
               c(1,3),c(2,3),c(4,3),c(5,3),c(7,3),c(8,3),
               c(1,4),c(3,4),c(5,4),c(7,4),c(9,4),
               c(1,5),c(2,5),c(3,5),c(4,5),c(6,5),c(7,5),c(8,5),c(9,5),
               c(1,6),c(5,6),c(7,6),
               c(1,7),c(2,7),c(3,7),c(4,7),c(5,7),c(6,7),c(8,7),c(9,7),
               c(1,8),c(3,8),c(5,8),c(7,8),c(9,8),
               c(1,9),c(2,9),c(4,9),c(5,9),c(7,9),c(8,9))

fi = sample(1:length(dafracs),3)
mult = sample(2:9,3,T)
sgn = sample(c(-1,1),3,T)
f = dafracs[[fi[1]]]
dy = f[1]*mult[1]*sample(c(-1,1),1)
w = f[2]*mult[1]

while(T){
    xl = sample(11:99,1)
    xr = xl+w
    x = c(xl,xr)
    if(max(x)<100){break}
}
while(T){
    yl = sample(11:99,1)
    yr = yl+dy
    y = c(yl,yr)
    dps = sort(unique(c(x,y)))
    if(max(y)<100 && min(y)>0 && length(dps)==4){break}
}
allpairs = list()
for(i in 1:4){
    if(dps[i]==xl){
        allpairs[[i]] = c(xl,yl)
    } else if(dps[i]==xr){
        allpairs[[i]] = c(xr,yr)
    } else if(dps[i]==yl){
        allpairs[[i]] = c(yl,xr)
    } else if(dps[i]==yr){
        allpairs[[i]] = c(yr,xl)
    }
}

solst = ""

if(params$showsol){
    s1 = paste0("$\\frac{g(",xr,")-g(",xl,")}{",xr,"-",xl,"}=\\frac{",yr,"-",yl,"}{",xr,"-",xl,"}=\\frac{",yr-yl,"}{",xr-xl,"}$\n\n",collapse="")
    s4 = paste0("The greatest common factor of ",yr-yl," and ",xr-xl," is ",mult[1],". Divide numerator and denominator by the greatest common factor.",collapse="")
    s5 = paste0("$$\\mathrm{AROC}=\\frac{",sign(dy)*f[1],"}{",f[2],"}$$",collapse="")
    solst = paste0(c(s1,s4,s5),collapse="\n")
}
```

3. Let function $g$ be defined by the table below. Use the formula $\frac{g(x_2)-g(x_1)}{x_2-x_1}$ to find the average rate of change between $x_1=`r xl`$ and $x_2=`r xr`$. Express your answer as a reduced fraction.

| $x$ | $g(x)$ |
|:---:|:---:|
| `r allpairs[[1]][1]` | `r allpairs[[1]][2]` |
| `r allpairs[[2]][1]` | `r allpairs[[2]][2]` |
| `r allpairs[[3]][1]` | `r allpairs[[3]][2]` |
| `r allpairs[[4]][1]` | `r allpairs[[4]][2]` |

`r solst`









