---
title: "Pythagorean Identity"
output: slidy_presentation
---

# Pythagorean Identity

```{r,echo=F,fig.dim=c(3,3),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.05,1.05),ylim=c(-1.05,1.05))
th = seq(0,2*pi,pi/360)
arrows(-1.05,0,1.05,0,0.05,15,3)
arrows(0,-1.05,0,1.05,0.05,15,3)
lines(cos(th),sin(th),col="darkgrey",lty=2)
x = -0.6
y = 0.8
t = atan2(y,x)
lines(c(0,x),c(0,y),lwd=2,col="blue")
# dd = 0.03
# lines(c(x-dd,x-dd,x),c(0,dd,dd))
text(x/2,y/2,"1",srt=(t*180/pi+90)%%180-90,adj=c(0.5,-0.3),col="blue")
# text(x/2,0,"adj",srt=0,adj=c(0.5,1.3))
# text(x,y/2,"opp",srt=90,adj=c(0.5,1.3))

thth = seq(0,t,pi/360)
n = length(thth)
ar = 0.2
art = 0.34
lines(ar*cos(thth),ar*sin(thth),col="red",lwd=2)
text(art*cos(t/2),art*sin(t/2),TeX("$\\theta$"),col="red")
# arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.1,20,col="red",lwd=3)
arrows(ar*cos(thth[n-1]),ar*sin(thth[n-1]),ar*cos(thth[n]),ar*sin(thth[n]),0.05,30,col="red",lwd=2)

points(x,y,pch=19,col="maroon")
text(x,y,"(x,y)",adj=1.2,col="maroon")
text(1/sqrt(2),1/sqrt(2),TeX("$x^2+y^2=1$"),srt=-45,col="darkgrey",adj=c(0.5,-0.2))

```

* Every point on the unit circle is a distance of $1$ unit away from the origin.
* For any point $(x,y)$ on the unit circle, $x^2+y^2=1$ (distance formula).
* We define $\sin(\theta)$ to be the $y$ coordinate on the unit circle at angle $\theta$.
* We define $\cos(\theta)$ to be the $x$ coordinate on the unit circle at angle $\theta$.
* We define $\tan(\theta)$ to be $y/x$, or the slope of the segment connecting $(0,0)$ to $(x,y)$.
* So,

$$\sin^2(\theta)+\cos^2(\theta)=1$$

* Notice, this new notation (putting an exponent between the trig function and its argument) is weird/bad but standard. To write this in a more familiar way, we could write $(\sin(\theta))^2+(\cos(\theta))^2=1$; however, you'll almost always see the Pythagorean identity, and trig functions raised to any power, written as they are shown in $\sin^2(\theta)+\cos^2(\theta)=1$.

# Example 1

1. If $\sin(\theta)=`r round(sin(0.7),3)`$, then what is $\cos(\theta)$?

```{r,echo=F}
y = round(sin(0.7),3)
x = sqrt(1-y^2)
```

We can use the Pythagorean identity.

$$(`r y`)^2+\cos^2(\theta)=1$$

Subtract $(`r y`)^2$ from both sides.

$$\cos^2(\theta)=1-(`r y`)^2$$

Square root both sides.

$$|\cos(\theta)|=\sqrt{1-(`r y`)^2}$$

Get a decimal approximation.


$$|\cos(\theta)|=`r sqrt(1-y^2)`$$


Notice there are two possibilities: $\cos(\theta)=`r sqrt(1-y^2)`$ or $\cos(\theta)=`r -sqrt(1-y^2)`$. We can visualize this by drawing a unit circle and a horizontal line $y=`r y`$.


```{r,echo=F,fig.dim=c(3,3),fig.align='center'}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",axes=F,ann=F,xlim=c(-1.05,1.05),ylim=c(-1.05,1.05))
th = seq(0,2*pi,pi/360)
arrows(-1.05,0,1.05,0,0.05,15,3)
arrows(0,-1.05,0,1.05,0.05,15,3)
lines(cos(th),sin(th),col="darkgrey",lty=2)
t = atan2(y,x)
# lines(c(0,x),c(0,y),lwd=2,col="blue")
# dd = 0.03
# lines(c(x-dd,x-dd,x),c(0,dd,dd))
# text(x/2,y/2,"1",srt=(t*180/pi+90)%%180-90,adj=c(0.5,-0.3),col="blue")
# text(x/2,0,"adj",srt=0,adj=c(0.5,1.3))
# text(x,y/2,"opp",srt=90,adj=c(0.5,1.3))

thth = seq(0,t,pi/360)
n = length(thth)

text(1/sqrt(2),-1/sqrt(2),TeX("$x^2+y^2=1$"),srt=45,col="darkgrey",adj=c(0.5,-0.2))
abline(h=y)

points(x,y,pch=19)
points(-x,y,pch=19)
```
\

Notice, there are two points of intersection. The two points share a common $y$ coordinate, but their $x$ coordinates are opposites. The question would need to specify a quadrant for you to give a single answer!

# "But, but, woe is me. I can't do all that algebra!"

Never fear. I've done the algebra and stored the results in formulae! (These can be found on the [cheat sheet](https://chadworley.github.io/a2/u13/rtt_cheat_sheet/cheat_sheet_uc_trig.pdf).)

\begin{align*}
\sin^2(\theta)+\cos^2(\theta)&=1 & |\sin(\theta)|&=\sqrt{1-\cos^2(\theta)} & |\cos(\theta)|&=\sqrt{1-\sin^2(\theta)}\\\\
\tan^2(\theta)+1&=\frac{1}{\cos^2(\theta)} & |\tan(\theta)|&=\sqrt{\frac{1-\cos^2(\theta)}{\cos^2(\theta)}} &
|\cos(\theta)|&=\sqrt{\frac{1}{\tan^2(\theta)+1}}\\\\
\tan^2(\theta)+1&=\frac{1}{1-\sin^2(\theta)} & |\tan(\theta)|&=\sqrt{\frac{\sin^2(\theta)}{1-\sin^2(\theta)}} &
|\sin(\theta)|&=\sqrt{\frac{\tan^2(\theta)}{\tan^2(\theta)+1}}\\\\
\end{align*}

# Example 2

* Given:
    * $\sin(\theta)=0.5$
    * $\theta$ is in quadrant II
* Find $\tan(\theta)$.

Find the formula that gets $\tan(\theta)$ from $\sin(\theta)$.

$$|\tan(\theta)|=\sqrt{\frac{\sin^2(\theta)}{1-\sin^2(\theta)}}$$

Substitute the given.

$$|\tan(\theta)|=\sqrt{\frac{(0.5)^2}{1-(0.5)^2}}$$

Evaluate a decimal approximation.


$$|\tan(\theta)|=`r sqrt(0.5^2/(1-0.5^2))`$$

In quadrant II, the slope will be **negative** for a line connecting a point on the circle to the origin. Thus,


$$\tan(\theta)=`r -sqrt(0.5^2/(1-0.5^2))`$$

# "That still seems difficult. Is there an easier way?"

* In Desmos, you can graph a unit circle with $x^2+y^2=1$.
* If you are given a value for $\sin(\theta)$, graph a horizontal line $y=\sin(\theta)$.
* If you are given a value for $\cos(\theta)$, graph a vertical line $x=\cos(\theta)$.
* If you are given a value for $\tan(\theta)$, graph a line $y=\tan(\theta)\cdot x$.
* If you want $\sin(\theta)$, find the $y$ coordinate of intersection in given quadrant.
* If you want $\cos(\theta)$, find the $x$ coordinate of intersection in given quadrant.
* If you want $\tan(\theta)$, find $y/x$ of intersection in given quadrant.

* Here, we can argue that because we used $x^2+y^2=1$, we are "using the Pythagorean Identity", since $x=\cos(\theta)$ and $y=\sin(\theta)$...

# "That still seems difficult. Is there an EVEN EASIER way?"

* You can use an arctrig function to first find the angle, and then put that angle into the desired trig function.
* Unfortunately, trig functions are NOT one-to-one, so this can't work perfectly.
* If you are given $\sin(\theta)$ and want $\tan(\theta)$, you could use $\tan(\arcsin(\sin(\theta)))$, and then fix the sign based on the quadrant.
* I will say this strategy is not really "using the Pythagorean Identity", so it is not matching up with the learning objective.
* It is interesting that $\arcsin$ does not perfectly undo $\sin$, just like square root does not perfectly undo squaring (for example $\sqrt{(-5)^2}\ne-5$). This is because non-one-to-one functions cannot be perfectly undone.




