```{r,echo=F,warning=F}
fixer = function(exp){
  exp = gsub("--","+",exp,fixed=T)
  exp = gsub("+-","-",exp,fixed=T)
  exp = gsub("(x-0)","x",exp,fixed=T)
  exp = gsub("(y-0)","y",exp,fixed=T)
  return(exp)
}

# hk = sample(-6:6,2)
# h = hk[1]
# k = hk[2]
# ab = sample(2:(10-max(abs(hk))),2)
# r1 = ab[1]
# r2 = ab[2]

while(T){
  alldem = sample(2:9,4)
  h = alldem[1]*sample(c(-1,1),1)
  k = alldem[2]*sample(c(-1,1),1)
  r1 = alldem[3]
  r2 = alldem[4]
  maxx = abs(h)+r1
  maxy = abs(k)+r2
  if(maxx<11 && maxy<11){break}
}


#anssimp = paste0("\\frac{(x-",h,")^2}{",r1^2,"}+\\frac{(y-",k,")^2}{",r2^2,"}=1",collapse="")
anssimp = paste0("$$x=",h,"+",r1,"\\cos(t)$$ $$y=",k,"+",r2,"\\sin(t)$$",collapse="")
anssimp = gsub("--","+",anssimp,fixed=T)
anssimp = gsub("(x-0)","x",anssimp,fixed=T)
anssimp = gsub("(y-0)","y",anssimp,fixed=T)

ansdes = paste0("(",h,"+",r1,"\\cos(t),~",k,"+",r2,"\\sin(t))",collapse="")

achk = -10:10
acrs = 1:10

solh = paste0(1*(achk==h),collapse="")
solk = paste0(1*(achk==k),collapse="")
solr1 = paste0(1*(acrs==r1),collapse="")
solr2 = paste0(1*(acrs==r2),collapse="")

hkl = min(abs(c(h,k)))
hkb = max(abs(c(h,k)))
rl = min(c(r1,r2))
rb = max(c(r1,r2))

hs = c(-hkl,-hkl,hkl,hkl,
       -hkb,-hkb,hkb,hkb,
       -hkl,-hkl,hkl,hkl,
       -hkb,-hkb,hkb,hkb)
ks = c(-hkb,hkb,-hkb,hkb,
       -hkl,hkl,-hkl,hkl,
       -hkb,hkb,-hkb,hkb,
       -hkl,hkl,-hkl,hkl)
r1s = c(rep(rl,8),rep(rb,8))
r2s = c(rep(rb,8),rep(rl,8))
ord = 1:16

EE = character()
for(i in 1:length(ord)){
  j = ord[i]
  hz = hs[j]
  kz = ks[j]
  r1z = r1s[j]
  r2z = r2s[j]
  exp1 = paste0("$$x=",hz,"+",r1z,"\\cos(t)$$ $$y=",kz,"+",r2z,"\\sin(t)$$",collapse="")
  exp1 = fixer(exp1)
  EE = c(EE,exp1)
}
ace = LETTERS[1:16]
solex = paste0(1*(EE==anssimp),collapse="")
```

Question
========

It can be helpful to represent an ellipse in parametric form:

$$\begin{align}
x &= h+r_1 \cos(t)\\
y &= k+r_2 \sin(t)
\end{align}$$

where the center is $(h,k)$, the horizontal radius is $r_1$, and the vertical radius is $r_2$.

Determine the parameters of the ellipse in the graph below. You can assume all parameters are integers.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2)
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2)
th = seq(0,2*pi,length.out=1000)
x = h+r1*cos(th)
y = k+r2*sin(th)
polygon(x,y,border="blue",lwd=2)
```
\

* $h=$ ##ANSWER1##
* $k=$ ##ANSWER2##
* $r_1=$ ##ANSWER3##
* $r_2=$ ##ANSWER4##

Which of the following parametric systems, for $0\le t<2\pi$, would give the graph above?

A:

`r EE[1]`

B:

`r EE[2]`

C:

`r EE[3]`

D:

`r EE[4]`

E:

`r EE[5]`

F:

`r EE[6]`

G:

`r EE[7]`

H:

`r EE[8]`

I:

`r EE[9]`

J:

`r EE[10]`

K:

`r EE[11]`

L:

`r EE[12]`

M:

`r EE[13]`

N:

`r EE[14]`

O:

`r EE[15]`

P:

`r EE[16]`


Parametric system ##ANSWER5##

Answerlist
--------

`r paste0("* ",achk,collapse="\n")`
`r paste0("* ",achk,collapse="\n")`
`r paste0("* ",acrs,collapse="\n")`
`r paste0("* ",acrs,collapse="\n")`
`r paste0("* ",ace,collapse="\n")`


Solution
========

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in 1:10){
  abline(h=i,lty=2,col="grey")
  abline(h=-i,lty=2,col="grey")
  abline(v=i,lty=2,col="grey")
  abline(v=-i,lty=2,col="grey")
}
arrows(-10.5,0,10.5,0,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
arrows(0,-10.5,0,10.5,length=0.1,angle=15,code=3,lwd=2,col="darkgrey")
th = seq(0,2*pi,length.out=1000)
x = h+r1*cos(th)
y = k+r2*sin(th)
polygon(x,y,border="blue")
lines(c(h,h+r1),c(k,k),col="purple",lwd=2)
text(h+r1/2,k-0.4,r1,col="purple",cex=1.2)
lines(c(h,h),c(k,k+r2),col="darkgreen",lwd=2)
text(h-0.4,k+r2/2,r2,col="darkgreen",cex=1.2)
points(h,k,col="red",pch=19)
text(h-0.1,k-0.2,paste0("(",h,",",k,")"),adj=c(1,1),col="red",cex=1.2)

```
\

So:
$$\begin{align}
h &= `r h`\\\\
k &= `r k`\\\\
r_1 &= `r r1`\\\\
r_2 &= `r r2`
\end{align}$$

Substitute those numbers into the parametric system:

`r anssimp`

In [Desmos](https://www.desmos.com/calculator), you'd graph this by typing:

$$`r ansdes`$$

and setting bounding $t$ so that $0\le t< 2\pi$.



Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r solh`|`r solk`|`r solr1`|`r solr2`|`r solex`
exname: ellipse_get_pams