```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
options(scipen=99)
intv = 0.05
th = signif(runif(1,pi/10,pi/2-pi/10),3) #radians
v = signif(runif(1,2000,5000),3) #m/s
nf = min(c(ceiling((10000/(cos(th)*v))/intv)+3,
           ceiling((10000/(sin(th)*v))/intv)+3)
         )
vx = v*cos(th)
vy = v*sin(th)


```

Question
========

At noon, on an [equinox](https://en.wikipedia.org/wiki/Equinox), at the equator, the sun is directly overhead. Over land with minimal elevation change, we can approximate the local ground as flat.

A rocket is launched at an [angle of elevation](https://en.wikipedia.org/wiki/Elevation_(ballistics)) of `r th` radians above the horizon at a speed of `r v` meters per second.

```{r,echo=F,fig.dim=c(3,3),animation.hook="gifski",interval=intv}
for(i in 1:nf){
    par(mar=c(0,0,0,0),pty="s")
    plot(0,0,"n",xlim=c(0,10000),ylim=c(0,10000),axes=F,ann=F)
    polygon(c(-1000,11000,11000,-1000),c(-1000,-1000,0,0),col="lightgrey")
    polygon(c(-1000,11000,11000,-1000),c(99999,99999,0,0),col="skyblue")
    t = intv*i
    xs = cos(th)*v*t+cos(th)*c(0,300)
    ys = sin(th)*v*t+sin(th)*c(0,300)
    lines(xs,ys-20,pch=19,col="black",lwd=6)
    lines(xs,ys,pch=19,col="red",lwd=6)
    lines(xs,c(-200,-200),pch=19,col="black",lwd=6)
}
```
\

How fast, in meters per second, is the shadow moving across the flat ground? The tolerance is $\pm 10$ m/s.


Solution
========

We recognize that velocity is a [vector](https://en.wikipedia.org/wiki/Euclidean_vector). In this scenario, we can think of the vector as a 2D vector given in [polar form](https://en.wikipedia.org/wiki/Polar_coordinate_system).

Using basic right-triangle trigonometry, you can find the horizontal component of the velocity.

Draw a vector with [magnitude (length)](https://en.wikipedia.org/wiki/Magnitude_(mathematics)#Euclidean_vector_space) of `r v` m/s and angle of `r th` radians. We can indicate the magnitude with double vertical lines on either side of the vector's name. We can also indicate magnitude by leaving off the arrow.

$$||\vec{v}||~=~ v ~=~`r v`~\mathrm{\frac{m}{s}}$$

We want to decompose the vector into its horizontal component ($\vec{v}_x$) and its vertical component ($\vec{v}_y$). The horizontal component's magnitude (denoted as $||\vec{v}_x||$, or more simply as $v_x$) is the speed of the shadow.

```{r,echo=F,fig.dim=c(5,5)}
library(latex2exp)
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-0.1,1.1),ylim=c(-0.1,1.1),axes=F,ann=F)
x = cos(th)
y = sin(th)
arrows(0,0,x,y,0.09,10,col="red",lwd=2)
arrows(0,0,x,0,0.09,10,col="black",lwd=2)
arrows(x,0,x,y,0.09,10,col="blue",lwd=2)
angr = 0.1
ths = seq(0,th,pi/360)
lines(angr*cos(ths),angr*sin(ths),col="darkgreen")
angrt = 0.11
text(angrt*cos(th/2),angrt*sin(th/2),th,srt=th/2/pi*180,col="darkgreen",adj=c(-0.1,0.5))
text(x/2,y/2,v,srt=th/pi*180,adj=c(0.5,-0.2),col="red")
text(x/2,0,TeX("$v_x$"),adj=c(0.5,1.2))
text(x,y/2,TeX("$v_y$"),adj=c(-0.1,0.5),col="blue")

```
\

We can set up the cosine equation.

$$\cos(`r th`)~=~\frac{v_x}{`r v`}$$

Solve for $v_x$.

$$v_x~=~`r v`\cdot\cos(`r th`)$$

Evaluate with a calculator. Remember, we are in RADIAN MODE!

$$v_x~=~`r vx`$$
$$v_x~\approx~`r signif(vx,3)`$$


Meta-information
============
extype: num
exsolution: `r vx`
exname: shadow_speed
extol: 10