```{r,echo=F}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
while(T){
  rdn = sample(5:15,1)
  rnf = sample((rdn%/%2+1):(rdn*2-1),1)
  ttx = paste0("\\frac{",rnf,"\\pi}{",rdn,"}",collapse = "")
  t = rnf*pi/rdn
  r = sample(310:750,1)/100
  x = r*cos(t)
  y = r*sin(t)
  xa = round(x,2)
  ya = round(y,2)
  n = 8
  d = 0.05
  r = round(sqrt(xa^2+ya^2),2)
  t = round((atan2(ya,xa)+2*pi)%%(2*pi),2)
  ru = sqrt(xa^2+ya^2)
  tu = (atan2(ya,xa)+2*pi)%%(2*pi)
  which1 = sample(1:n,1)
  ac1 = round(seq(r-d*(which1-1),r+d*(n-which1),length.out=n),2)
  which2 = sample(1:n,1)
  ac2 = round(seq(t-d*(which2-1),t+d*(n-which2),length.out=n),2)
  al1 = paste0("* ",ac1,collapse="\n")
  al2 = paste0("* ",ac2,collapse="\n")
  sol1 = paste0(1*(ac1==r),collapse="")
  sol2 = paste0(1*(ac2==t),collapse="")
  if(gcd2(rdn,rnf)==1 && abs(x)>1.2 && abs(y)>1.2 &&
     abs(x)<4.5 && abs(y)<4.5 && round(r,1)!=r && sum(ac1==r)==1 && sum(ac2==t)==1){break}
}
```

Question
========

A point on a Cartesian plane is given in [rectangular coordinates](https://en.wikipedia.org/wiki/Cartesian_coordinate_system):
$$x = `r xa`$$
$$y=`r ya`$$

```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
par(pty="s")
plot(x,y,xlim=c(-5,5),ylim=c(-5,5))
arrows(-5,0,5,0,length=0.1,angle=8,code=3,lwd=1)
arrows(0,-5,0,5,length=0.1,angle=8,code=3,lwd=1)
lines(c(0,x,x,0),c(0,0,y,0),lwd=2,col="purple")
lines(c(0,x),c(0,y),lwd=3,col="red")
text(x/2+0.5*cos(t+pi/2*sign(x*y)),
     y/2+0.5*sin(t+pi/2*sign(x*y)),"r",col="red",cex=1.5)
th = seq(0,t,length.out=100)
lines(cos(th),sin(th),col="blue")
arrows(cos(th[99]),sin(th[99]),cos(th[100]),sin(th[100]),col="blue",length=0.05,angle=20,lwd=2)
text(1.4*cos(t/2),1.4*sin(t/2),TeX("$\\theta$"),col="blue",cex=1.5)
points(x,y,pch=19,col="purple",cex=1.3)
text(x,y+sign(y)/2,"(x,y)",col="purple")
```
\


Please determine the polar coordinates ($r$ and $\theta$), enforcing $0\le\theta<2\pi$.

* The radius: $r=$ ##ANSWER1##
* The angle: $\theta=$ ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`



Solution
========

First, get the radius, using [Pythagorean Theorem](https://en.wikipedia.org/wiki/Pythagorean_theorem).

$$r = \sqrt{(`r abs(xa)`)^2+(`r abs(ya)`)^2}$$

$$r \approx `r r`$$


```{r,echo=FALSE}
if(t<3*pi/2){
  refinit = "\\pi"
  refnmr = abs(rnf-rdn)
} else {
  refinit = "2\\pi"
  refnmr = abs(rnf-2*rdn)
}
refnmrt = paste0(refnmr)
if(refnmrt=="1"){refnmrt=""}
```

Find the [reference angle](https://courses.lumenlearning.com/csn-precalculus/chapter/reference-angles/) by using the arctan function with the quotient of the absolute values of the rectangular coordinates.

$$\phi ~=~ \arctan\left(\frac{`r abs(ya)`}{`r abs(xa)`}\right)$$

$$\phi ~=~ `r atan(abs(ya)/abs(xa))`$$

```{r,echo=F,fig.dim=c(8,8)}
library(latex2exp)
par(pty="s")
plot(x,y,xlim=c(-5,5),ylim=c(-5,5))
arrows(-5,0,5,0,length=0.1,angle=8,code=3,lwd=1)
arrows(0,-5,0,5,length=0.1,angle=8,code=3,lwd=1)
lines(c(0,x,x,0),c(0,0,y,0),lwd=2,col="purple")
lines(c(0,x),c(0,y),lwd=3,col="red")
text(x/2+0.5*cos(t+pi/2*sign(x*y)),
     y/2+0.5*sin(t+pi/2*sign(x*y)),"r",col="red",cex=1.5)
if(t<3*pi/2){t2=pi}else{t2=2*pi}
th = seq(t2,t,length.out=100)
lines(cos(th),sin(th),col="blue")
text(1.4*cos(th[50]),1.4*sin(th[50]),TeX("$\\phi$"),col="blue",cex=1)
points(x,y,pch=19,col="purple",cex=1.3)
text(x,y+sign(y)/2,"(x,y)",col="purple")
```
\

```{r,echo=FALSE}
qn = t%/%(pi/2)+1
qstr = c("I","II","III","IV")[qn]
if(qn==2){
  addstr = "find the difference of $\\pi$ minus $\\phi$"
  mathop = "\\theta = \\pi-\\phi"
}
if(qn==3){
  addstr = "add $\\pi$ and $\\phi$"
  mathop = "\\theta = \\pi+\\phi"
}
if(qn==4){
  addstr = "find the difference of $2\\pi$ minus $\\phi$"
  mathop = "\\theta = 2\\pi-\\phi"
}
```

**Because the point is in quadrant `r qstr`**, we `r addstr` to get $\theta$.
$$`r mathop`$$

$$\theta\approx`r t`$$

Unfortunately, you cannot simply use $\arctan\left(\frac{`r ya`}{`r xa`}\right)$ to get the angle $\theta$. This is because tangent is not a one-to-one function.

Now, Desmos (and many other calculators) allow you to feed $y$ and $x$ as two seperate arguments into the arctangent function: $\arctan(`r ya`,`r xa`)$. This will give you a correct angle, between $-\pi$ and $\pi$. If you get a negative angle, you can just add $2\pi$ to get a coterminal angle between $0$ and $2\pi$, as the prompt asks for.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: rect_to_polar