```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
xy = sample(2:9,2)*sample(c(-1,1),2,T)
x = xy[1]
y = xy[2]
th = atan2(y,x)
thpr = sprintf("%.03f",abs(th))
deg = th/pi*180
degpr = sprintf("%.01f",abs(deg))
ans1 = abs(round(th,3))
ach1 = ans1+(0:5-sample(0:5,1))*0.003
al1 = paste0("* ",sprintf("%.03f",ach1),collapse="\n")
sol1 = paste0(1*(ach1==ans1),collapse="")

ach2 = c("clockwise","counterclockwise")
ans2 = ach2[round(sign(deg)/2+1.5)]
sol2 = paste0(1*(ach2==ans2),collapse="")
al2 = paste0("* ",ach2,collapse="\n")

```

Question
========

In the video game [Asteroids](https://en.wikipedia.org/wiki/Asteroids_(video_game)), a player rotates a space ship to aim projectiles at asteroids.

If the ship is located at $(0,0)$ and currently points towards $(1,0)$, how many **radians**, and in which direction, should the ship rotate to aim at $(`r x`, `r y`)$ with as little turning as possible?

* ##ANSWER1## ##ANSWER2##


Answerlist
--------

`r al1`
`r al2`


Solution
========

This is a perfect setup for using [two-argument arctangent](https://en.wikipedia.org/wiki/Atan2).

In Desmos, this can be done by typing ``arctan(`r y`,`r x`)``. Notice, the two-argument arctangent takes the $y$ coordinate first and the $x$ coordinate second. You can blame the writers of Fortran in 1961.

Make sure you are in RADIAN MODE.

A positive angle indicates counterclockwise turning. A negative angle indicates clockwise turning.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.2)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.2)
}


points(x,y,pch=20,cex=2,col="red")

ths = seq(0,th,pi/180*sign(th))
n = length(ths)

xs = 2*cos(ths)
ys = 2*sin(ths)
polygon(c(0,xs),c(0,ys),col=rgb(0,0,1,0.4),border="blue",lwd=0.4)
lines(xs,ys,col="blue",lwd=2)
text(2*cos(th/2),2*sin(th/2),thpr,col="blue",srt=(deg/2+90)%%180-90,
     adj=c(0.5-0.7*sign(cos(th/2)),0.5))

lines(c(0,x),c(0,y),col="red",lty=2)
arrows(xs[n-1],ys[n-1],xs[n],ys[n],0.06,20,col="blue",lwd=2)

polygon(c(0.4,-0.3,-0.1,-0.3),c(0,0.2,0,-0.2),col=rgb(1,0.4,1),border="black",lwd=1.5)
```
\


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: turn_atan2_rads