```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

wo = sample(1:3,1,F,c(2,3,3))

while(T){
    xy = sample(2:9,4)*sample(c(-1,1),4,T)
    x1 = xy[1]
    x2 = xy[2]
    y1 = xy[3]
    y2 = xy[4]
    deg1 = atan2(y1,x1)/pi*180
    deg2 = atan2(y2,x2)/pi*180
    th1 = atan2(y1,x1)
    th2 = atan2(y2,x2)
    
    poss1 = (deg2-deg1)
    poss2 = (360-abs(poss1))*(-sign(deg2-deg1))
    
    dir = c("clockwise","counterclockwise")
    
    alphae = deg2-deg1
    betae = deg2+360-deg1
    gammae = deg2-(deg1+360)
    
    
    alr = th2-th1
    ber = th2-th1+2*pi
    gar = th2-th1-2*pi
    
    if(abs(poss1)<abs(poss2)){
        wd = dir[round(sign(poss1)/2+1.5)]
        dt = poss1
    } else {
        wd = dir[round(sign(poss2)/2+1.5)]
        dt = poss2
    }
    adt = abs(dt)
    possr = c(alr,ber,gar)
    apossr = abs(possr)
    adr = min(apossr)
    isadr = (adr==apossr)
    dr = possr[isadr]
    
    alpha = round(deg2-deg1,1)
    beta = round(deg2+360-deg1,1)
    gamma = round(deg2-(deg1+360),1)
    
    
    ans1 = round(adt,1)
    ach1 = unique(sort(c(abs(alpha)+(0:3-sample(0:3,1))*0.3,
                  abs(beta)+(0:3-sample(0:3,1))*0.3,
                  abs(gamma)+(0:3-sample(0:3,1))*0.3,
                  180-round(adt,1)+(0:3-sample(0:3,1))*0.3,
                  round(runif(1,0.1,179),1)+(0:3-sample(0:3,1))*0.3,
                  round(runif(1,0.1,179),1)+(0:3-sample(0:3,1))*0.3,
                  round(runif(1,0.1,179),1)+(0:3-sample(0:3,1))*0.3)))
    al1 = paste0("* ",sprintf("%.01f",ach1),collapse="\n")
    sol1 = paste0(1*(ans1==ach1),collapse="")
    
    al2 = paste0("* ",dir,collapse="\n")
    sol2 = paste0(1*(dir==wd),collapse="")
    
    if(adt>15 && adt<175 && abs(c(alphae,betae,gammae))[wo]==adt && min(diff(ach1))>0.2){break}
}







```

Question
========

In the video game [Asteroids](https://en.wikipedia.org/wiki/Asteroids_(video_game)), a player rotates a space ship to aim projectiles at asteroids.

If the ship is located at $(0,0)$ and currently points towards $(`r x1`, `r y1`)$, how many **degrees**, and in which direction, should the ship rotate to aim at $(`r x2`, `r y2`)$ with as little turning as possible?

* ##ANSWER1## ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`


Solution
========

I would first use [two-argument arctangent](https://en.wikipedia.org/wiki/Atan2) to find a standard angle (rotating from positive $x$ axis) for each given point. In Desmos, you can just use ``arctan(`r y1`,`r x1`)`` and ``arctan(`r y2`,`r x2`)``. Remember, DEGREE MODE.

$$\theta_1 ~=~ \arctan(`r y1`,`r x1`)~=~`r round(deg1,2)`°$$

$$\theta_2 ~=~ \arctan(`r y2`,`r x2`)~=~`r round(deg2,2)`°$$

Now... unfortunately... we cannot simply assume $\theta_2-\theta_1$ will give the desired turning angle. It would definitely accomplish the task of turning from point 1 to point 2, but $\theta_2-\theta_1$ might not be the smallest turn. To make sure we get the smallest turning angle, we can consider 3 coterminal turning angles.

$$\alpha ~=~ \theta_2-\theta_1$$
$$\beta ~=~ \alpha+360°$$
$$\gamma ~=~ \alpha-360°$$

Using the formulae above, calculate the three possible turning angles that would turn from the first point to the second point.

$$\alpha ~=~ `r round(alpha,2)`°$$
$$\beta ~=~ `r round(beta,2)`°$$
$$\gamma ~=~ `r round(gamma,2)`°$$

Find the option with the least ABSOLUTE value. Also, remember, in math, positive angles correspond to counterclockwise rotations, and negative angles correspond to clockwise rotations. (This is reversed in [navigation with bearings](https://en.wikipedia.org/wiki/Bearing_(navigation)).)


```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.2)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.2)
}


points(x1,y1,pch=20,cex=2,col="red")
points(x2,y2,pch=20,cex=2,col="red")

xship = c(0.4,-0.3,-0.1,-0.3)*1.5
yship = c(0,0.2,0,-0.2)*1.5

xship2 = cos(th1)*xship-sin(th1)*yship
yship2 = sin(th1)*xship+cos(th1)*yship

ths = seq(th1,th1+dr,pi/180*sign(dr))
n = length(ths)
xs = 2*cos(ths)
ys = 2*sin(ths)

th = th1+dr/2
deg = th/pi*180

polygon(c(0,xs),c(0,ys),col=rgb(0,0,1,0.4),border="blue",lwd=0.4)
lines(xs,ys,col="blue",lwd=2)
text(2*cos(th),2*sin(th),paste0(sprintf("%.01f",adt),"°"),col="blue",srt=(deg+90)%%180-90,
     adj=c(0.5-0.7*sign(cos(th)),0.5))

lines(c(0,x1),c(0,y1),col="red",lty=2)
lines(c(0,x2),c(0,y2),col="red",lty=2)
arrows(xs[n-1],ys[n-1],xs[n],ys[n],0.06,20,col="blue",lwd=2)

polygon(xship2,yship2,col=rgb(1,0.4,1),border="black",lwd=1.5)

```
\

The ship should turn `r round(adt,1)`° `r wd`.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: short_turn_degs