```{r data generation, echo = FALSE, results = "hide",warning=FALSE}

while(T){
    xy = round(runif(2,2,9)*sample(c(-1,1),2,T),1)
    x = xy[1]
    y = xy[2]
    rA = sqrt(x^2+y^2)
    thA = atan2(y,x)
    degA = atan2(y,x)/pi*180
    deg = round(runif(1,20,160),1)*sample(c(-1,1),1)
    th = round(deg/180*pi,3)
    deg = th/pi*180
    thB = thA+th
    
    dirs = c("clockwise","counterclockwise")
    dir = dirs[round(sign(deg)/2+1.5)]
    nps = c("negative","positive")
    np = nps[round(sign(deg)/2+1.5)]
    
    degB = degA+deg
    rB = rA
    
    xB = rB*cos(degB/180*pi)
    yB = rB*sin(degB/180*pi)
    
    
    degD = degA-deg
    xD = rB*cos(degD/180*pi)
    yD = rB*sin(degD/180*pi)
    
    xans = round(xB,1)
    yans = round(yB,1)
    
    xbad = round(xD,1)
    ybad = round(yD,1)
    
    achx = xans+(0:5-sample(0:5,1))*0.3
    achy = yans+(0:5-sample(0:5,1))*0.3
    bachx = xbad+(0:5-sample(0:5,1))*0.3
    bachy = ybad+(0:5-sample(0:5,1))*0.3
    ach = sort(unique(c(achx,achy,-achx,-achy,xbad,ybad,-xbad,-ybad)))
    
    if(abs(diff(abs(xy)))>1 && rA<10 && rA>3 && min(diff(ach))>0.1 && abs(xB)>0.5 && abs(yB)>0.5){break}
}

al = paste0("* ",sprintf("%.01f",ach),collapse="\n")
sol1 = paste0(1*(xans==ach),collapse="")
sol2 = paste0(1*(yans==ach),collapse="")

```

Question
========

In an $xy$-plane, point $A$ has coordinates $(`r sprintf("%.01f",x)`,`r sprintf("%.01f",y)`)$. That point is rotated `r sprintf("%.03f",abs(th))` radians `r dir` around the origin, producing point $B$. Find the ([Cartesian](https://en.wikipedia.org/wiki/Cartesian_coordinate_system)) coordinates of $B$.

* (##ANSWER1##,##ANSWER2##)

Answerlist
--------

`r al`
`r al`

Solution
========

Since we are turning `r dir`, the turning angle is `r np`.

$$\theta_T = `r th`$$

Find [polar coordinates](https://en.wikipedia.org/wiki/Polar_coordinate_system) of point $A$. Use distance formula (Pythagorean theorem) to get the radius, and use the [two-argument arctangent](https://en.wikipedia.org/wiki/Atan2) to get the angle.

$$r_A~=~\sqrt{(`r x`)^2+(`r y`)^2}~=~`r rA`$$
$$\theta_A~=~\arctan(`r y`,`r x`)~=~`r thA`$$

When we rotate around the origin, the radius stays the same.

$$r_B~=~r_A$$
$$r_B~=~`r rA`$$

We add the turning angle to the original angle to find the terminal angle.

$$\theta_B~=~\theta_A+\theta_T$$
$$\theta_B~=~(`r thA`)+(`r th`)$$
$$\theta_B~=~`r thB`$$

Convert the polar coordinates of point $B$ back into Cartesian coordinates.

$$x_B ~=~ r_B \cdot \cos(\theta_B) ~\approx~ `r sprintf("%.01f",xB)`$$
$$y_B ~=~ r_B \cdot \sin(\theta_B) ~\approx~ `r sprintf("%.01f",yB)`$$

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
    lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1.2)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1.2)
}

arrows(-10.5,0,10.5,0,0.05,20,3)
arrows(0,-10.5,0,10.5,0.05,20,3)

thetas = seq(0,2*pi,pi/180)
lines(rA*cos(thetas),rA*sin(thetas),lty=2)
thetas2 = seq(thA,thB,pi/180*sign(th))
rmark = 1
polygon(c(0,rmark*cos(thetas2)),c(0,rmark*sin(thetas2)),col=rgb(0.6,0,0.6,0.3),border=NA)
lines(rmark*cos(thetas2),rmark*sin(thetas2),col=rgb(0.6,0,0.6),lwd=2)
n = length(thetas2)
arrows(rmark*cos(thetas2[n-1]),rmark*sin(thetas2[n-1]),rmark*cos(thetas2[n]),rmark*sin(thetas2[n]),0.05,30,col=rgb(0.6,0,0.6),lwd=2)
ttt = thA+th/2
text(rmark*cos(ttt),rmark*sin(ttt),sprintf("%.03f",th),srt=(ttt*180/pi+90)%%180-90,
     col=rgb(0.6,0,0.6),adj=c(0.5-0.6*sign(cos(ttt)),0.5))

lines(c(0,x),c(0,y),lty=2,col="red")
points(x,y,pch=20,cex=2,col="red")
text(x+cos(thA),y+sin(thA),"A",col="red")
lines(c(0,xB),c(0,yB),lty=2,col="blue")
points(xB,yB,pch=20,cex=2,col="blue")
text(xB+cos(thB),yB+sin(thB),"B",col="blue")
points(0,0,pch=19)

```
\

I should also mention that there are [other ways](https://en.wikipedia.org/wiki/Rotation_matrix#In_two_dimensions) to determine the result of a rotation.

Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: rotate_point_rads