```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
while(T){
    vr = round(runif(1,1.0,3.5),1)
    vc = round(runif(1,1.0,3.5),1)
    th = runif(1,pi/6,5*pi/6)
    deg = round(th/pi*180)
    th = deg/180*pi
    if(abs(diff(c(vr,vc)))>0.2 && abs(deg-90)>2){break}
}

```

Question
========

A canoe can travel `r sprintf("%.01f",vc)` m/s relative to the water. A river, heading east, is flowing at `r sprintf("%.01f",vr)` m/s. The canoe points at a direction `r sprintf("%d",deg)`° counterclockwise from east.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
polygon(c(-1,-1,1,1),c(-1,1,1,-1),col="darkgreen")
polygon(c(-1,-1,1,1),c(-0.8,0.8,0.8,-0.8),col="lightblue")
vm = max(c(vr,vc))
vrp = vr/vm
vcp = vc/vm

ths = seq(0,th,pi/360)
polygon(-0.1+c(0,0.15*cos(ths)),-0.5+c(0,0.15*sin(ths)),col=rgb(1,0,0,0.4),border=NA)
lines(-0.1+0.15*cos(ths),-0.5+0.15*sin(ths),col=rgb(1,0,0),lwd=2)
text(-0.1+0.15*cos(th/2),-0.5+0.15*sin(th/2),paste0(sprintf("%d",deg),"°"),srt=(deg/2+90)%%180-90,adj=c(0.5-0.7*sign(cos(th/2)),0.5),col="red")

arrows(-0.1,-0.5,-0.1+vrp,-0.5,0.1,20,2,"blue",1,2)
arrows(-0.1,-0.5,-0.1+vcp*cos(th),-0.5+vcp*sin(th),0.1,20,2,"brown",1,2)
text(-0.1+vrp/2,-0.5,paste0(sprintf("%.01f",vr),"m/s"),col="blue",adj=c(0.5,1.2))
text(-0.1+vcp*cos(th)/2,-0.5+vcp*sin(th)/2,paste0(sprintf("%.01f",vc),"m/s"),srt=(deg+90)%%180-90,col="brown",adj=c(0.5,0.5-0.7*sign(cos(th))))


```
\


Find the canoe's speed, in m/s, and direction of travel, as degrees counterclockwise from east.

* Speed = ##ANSWER1##
* Direction = ##ANSWER2##


Solution
========






Meta-information
============
extype: cloze
exclozetype: 
exsolution: 
exname: rotate_point_rads