```{r data generation, echo = FALSE, results = "hide",warning=FALSE}
while(T){
    vr = round(runif(1,1.0,3.5),1)
    vc = round(runif(1,1.0,3.5),1)
    th = round(runif(1,pi/6,5*pi/6),2)
    deg = th/pi*180 #round(th/pi*180)
    # th = deg/180*pi
    xc = vc*cos(th)
    yc = vc*sin(th)
    
    xt = xc+vr
    yt = yc
    
    rt = sqrt(xt^2+yt^2)
    tht = atan2(yt,xt)
    degt = tht*180/pi
    if(abs(diff(c(vr,vc)))>0.2 && abs(deg-90)>5 && abs(degt-deg)>2 && abs(rt-max(c(vr,vc)))>0.1){break}
}

ans1 = round(rt,1)
ans2 = round(tht,3)
ach1 = ans1+(0:5-sample(0:5,1))*0.1
ach2 = ans2+(0:5-sample(0:5,1))*0.01
sol1 = paste0(1*(ach1==ans1),collapse="")
sol2 = paste0(1*(ach2==ans2),collapse="")
al1 = paste0("* ",sprintf("%.01f",ach1),collapse="\n")
al2 = paste0("* ",sprintf("%.02f",ach2),collapse="\n")

```

Question
========

A canoe travels `r sprintf("%.01f",vc)` m/s **relative to the water**. A river, heading east, flows at `r sprintf("%.01f",vr)` m/s. The canoe points at a direction `r sprintf("%.02f",th)` radians counterclockwise from east.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
polygon(c(-1,-1,1,1),c(-1,1,1,-1),col="darkgreen")
polygon(c(-1,-1,1,1),c(-0.8,0.8,0.8,-0.8),col="lightblue")
vm = max(c(vr,vc))
vrp = vr/vm
vcp = vc/vm

ths = seq(0,th,pi/360)
polygon(-0.1+c(0,0.15*cos(ths)),-0.5+c(0,0.15*sin(ths)),col=rgb(1,0,0,0.4),border=NA)
lines(-0.1+0.15*cos(ths),-0.5+0.15*sin(ths),col=rgb(1,0,0),lwd=2)
text(-0.1+0.15*cos(th/2),-0.5+0.15*sin(th/2),sprintf("%.02f",th),srt=(deg/2+90)%%180-90,adj=c(0.5-0.7*sign(cos(th/2)),0.5),col="red")

arrows(-0.1,-0.5,-0.1+vrp,-0.5,0.1,20,2,"blue",1,2)
arrows(-0.1,-0.5,-0.1+vcp*cos(th),-0.5+vcp*sin(th),0.1,20,2,"brown",1,2)
text(-0.1+vrp/2,-0.5,paste0(sprintf("%.01f",vr)," m/s"),col="blue",adj=c(0.5,1.2))
text(-0.1+vcp*cos(th)/2,-0.5+vcp*sin(th)/2,paste0(sprintf("%.01f",vc)," m/s"),srt=(deg+90)%%180-90,col="brown",adj=c(0.5,0.5-0.7*sign(cos(th))))

angcan = pi/6
thcan = seq(pi/2-angcan,pi/2+angcan,pi/360)
cany = sin(thcan)-sin(pi/2-angcan)
canx = cos(thcan)

canx = c(canx,rev(canx))
cany = c(cany,-rev(cany))

rcx = canx*cos(th)-cany*sin(th)
rcy = canx*sin(th)+cany*cos(th)

polygon(rcx/10-0.1,rcy/10-0.5,col="brown")

```
\


Find the canoe's total speed, in m/s, and direction of travel, as radians counterclockwise from east.

* Speed = ##ANSWER1##
* Direction = ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`


Solution
========

First, find the [rectangular coordinates](https://en.wikipedia.org/wiki/Vector_notation#Rectangular_coordinates) of each velocity vector. The two formulas:

$$x~=~r\cdot\cos(\theta)$$
$$y~=~r\cdot\sin(\theta)$$

We will use $\vec{v}_1$ for the canoe's velocity **relative to water**. It is shown below with approximate rectangular coordinates (found from formulas above, using $r=`r vc`$ and $\theta=`r sprintf("%.02f",th)`$).

$$\vec{v}_1 = (`r sprintf("%.03f",xc)`,`r sprintf("%.03f",yc)`)$$

We will use $\vec{v}_2$ for the river's velocity vector. Since the river flows directly east, all of its speed is in the positive horizontal direction.


$$\vec{v}_2 = (`r sprintf("%.03f",vr)`,`r sprintf("%.03f",0)`)$$

Now, add the corresponding components to find $\vec{v}_3$, the velocity of the canoe **relative to the ground**.

$$\vec{v}_3 = (`r sprintf("%.03f",xc+vr)`,`r sprintf("%.03f",yc)`)$$

Lastly, we need to find the [polar coordinates](https://en.wikipedia.org/wiki/Vector_notation#Polar_coordinates). The formulas are given below. Notice, I am using the [two-argument arctangent](https://en.wikipedia.org/wiki/Atan2) function.

$$r~=~\sqrt{x^2+y^2}$$
$$\theta~=~\arctan(y,x)$$

So,

$$r=\sqrt{(`r sprintf("%.03f",xt)`)^2+(`r sprintf("%.03f",yt)`)^2}~=~`r rt`$$

$$\theta=\arctan(`r sprintf("%.03f",yt)`,`r sprintf("%.03f",xt)`)~=~`r tht`$$

This can be visualized.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
polygon(c(-1,-1,1,1),c(-1,1,1,-1),col="darkgreen")
polygon(c(-1,-1,1,1),c(-0.8,0.8,0.8,-0.8),col="lightblue")
vm = max(c(vr,vc))
vrp = vr/vm/2
vcp = vc/vm/2

# ths = seq(0,th,pi/360)
# polygon(-0.1+c(0,0.15*cos(ths)),-0.5+c(0,0.15*sin(ths)),col=rgb(1,0,0,0.4),border=NA)
# lines(-0.1+0.15*cos(ths),-0.5+0.15*sin(ths),col=rgb(1,0,0),lwd=2)
# text(-0.1+0.15*cos(th/2),-0.5+0.15*sin(th/2),paste0(sprintf("%d",round(deg)),"°"),srt=(deg/2+90)%%180-90,adj=c(0.5-0.7*sign(cos(th/2)),0.5),col="red")

arrows(-0.1,-0.5,-0.1+vrp,-0.5,0.05,10,2,"blue",1,1)
arrows(-0.1,-0.5,-0.1+vcp*cos(th),-0.5+vcp*sin(th),0.05,10,2,"brown",1,1)
arrows(-0.1+vcp*cos(th),-0.5+vcp*sin(th),-0.1+vrp+vcp*cos(th),-0.5+vcp*sin(th),0.05,10,2,"blue",1,1)
arrows(-0.1+vrp,-0.5,-0.1+vcp*cos(th)+vrp,-0.5+vcp*sin(th),0.05,10,2,"brown",1,1)
arrows(-0.1,-0.5,-0.1+vcp*cos(th)+vrp,-0.5+vcp*sin(th),0.1,10,2,"black",1,lwd=2)

# text(-0.1+vrp/2,-0.5,paste0(sprintf("%.01f",vr)," m/s"),col="blue",adj=c(0.5,1.2))
# text(-0.1+vcp*cos(th)/2,-0.5+vcp*sin(th)/2,paste0(sprintf("%.01f",vc)," m/s"),srt=(deg+90)%%180-90,col="brown",adj=c(0.5,0.5-0.7*sign(cos(th))))

angcan = pi/6
thcan = seq(pi/2-angcan,pi/2+angcan,pi/360)
cany = sin(thcan)-sin(pi/2-angcan)
canx = cos(thcan)
canx = c(canx,rev(canx))
cany = c(cany,-rev(cany))
rcx = canx*cos(th)-cany*sin(th)
rcy = canx*sin(th)+cany*cos(th)

fracs = c(0,0.25,0.5,0.75,1)

for(i in fracs){
    polygon(rcx/10-0.1+i*rt*cos(tht)/vm/2,rcy/10-0.5+i*rt*sin(tht)/vm/2,col=rgb(0.5,0.2,0.2,0.5),border=rgb(0,0,0,0.5))
}
```
\

```{r,echo=F,fig.dim=c(5,5),animation.hook="gifski",interval=0.1}
par(mar=c(0,0,0,0),pty="s")

scatx = runif(50,-2,1)
scaty = runif(50,-0.75,0.75)

squigx = seq(-0.1,0.1,0.001)
squigy = 0.01*sin(squigx/0.1*2*pi)

for(i in seq(0,1,0.02)){
    plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)
    polygon(c(-1.2,-1.2,1.2,1.2),c(-1.2,1.2,1.2,-1.2),col="darkgreen")
    polygon(c(-1.2,-1.2,1.2,1.2),c(-0.8,0.8,0.8,-0.8),col="lightblue")
    vm = max(c(vr,vc))
    vrp = vr/vm/2
    vcp = vc/vm/2
    rtp = rt/vm/2
    
    angcan = pi/6
    thcan = seq(pi/2-angcan,pi/2+angcan,pi/360)
    cany = sin(thcan)-sin(pi/2-angcan)
    canx = cos(thcan)
    canx = c(canx,rev(canx))
    cany = c(cany,-rev(cany))
    rcx = canx*cos(th)-cany*sin(th)
    rcy = canx*sin(th)+cany*cos(th)
    # points(scatx+i*vr/vm/2,scaty,pch=19,col="white")
    for(j in 1:length(scatx)){
        lines(scatx[j]+i*vr/vm/2+squigx,scaty[j]+squigy,pch=19,col="white")
    }
    lines(-0.1+i*rt*cos(tht)/vm/2+vcp*c(0,cos(th)),-0.5+i*rt*sin(tht)/vm/2+vcp*c(0,sin(th)),col="brown",lty=2)
    lines(-0.1+2*rtp*c(0,cos(tht)),-0.5+2*rtp*c(0,sin(tht)),col="grey",lty=2)
    lines(-0.1+i*rt*cos(tht)/vm/2+rtp*c(0,cos(tht)),-0.5+i*rt*sin(tht)/vm/2+rtp*c(0,sin(tht)),col="black",lty=2)
    lines(-0.1+i*rt*cos(tht)/vm/2+vrp*c(0,1),-0.5+i*rt*sin(tht)/vm/2+0*c(0,1),col="blue",lty=2)
    polygon(rcx/10-0.1+i*rt*cos(tht)/vm/2,rcy/10-0.5+i*rt*sin(tht)/vm/2,col=rgb(0.5,0.2,0.2),border=rgb(0,0,0))
    
}
```
\


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: canoe_river_degs