---
header-includes:
   - \usepackage{array}
   - \usepackage{color}
output: pdf_document
params:
    rseed: 1
    showsol: true
    titex: "Practice"
urlcolor: blue
---


```{r,echo=F}
# In the future, you should make it so the domain is never the same as the range!
# set.seed(params$rseed)
if(params$showsol){
    solstart = ""
    solend = "\\vfill"
    hidesolstart = "<!---"
    hidesolend = "-->"
} else {
    solstart = "<!---"
    solend = "-->"
    hidesolstart = ""
    hidesolend = ""
}
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

## u10 Radicals, Rationals, and Extraneous Solutions  `r params$titex` (version `r params$rseed`)


```{r,echo=F}
# a*sqrt(b*(x-h))+k
# a,b in {-1,1}
# h,k in {-5:-1,1:5}

while(T){
    a = sample(c(-1,1),1)
    b = sample(c(-1,1),1)
    hk = sample(2:5,2)*sample(c(-1,1),2)
    h = hk[1]
    k = hk[2]
    
    if(a==-1){
        if(b==-1){
            exp1 = paste0("-\\sqrt{-(x+",-h,")}+",k)
            dom1 = paste0("x\\le",h,collapse="")
            dom2 = paste0("\\left(-\\infty, ",h,"\\right]",collapse="")
            ran1 = paste0("y\\le",k,collapse="")
            ran2 = paste0("\\left(-\\infty, ",k,"\\right]",collapse="")
        } else {
            exp1 = paste0("-\\sqrt{x+",-h,"}+",k)
            dom1 = paste0("x\\ge",h,collapse="")
            dom2 = paste0("\\left[",h,",\\infty\\right)",collapse="")
            ran1 = paste0("y\\le",k,collapse="")
            ran2 = paste0("\\left(-\\infty, ",k,"\\right]",collapse="")
        }
    } else {
        if(b==-1){
            exp1 = paste0("\\sqrt{-(x+",-h,")}+",k)
            dom1 = paste0("x\\le",h,collapse="")
            dom2 = paste0("\\left(-\\infty, ",h,"\\right]",collapse="")
            ran1 = paste0("y\\ge",k,collapse="")
            ran2 = paste0("\\left[",k,",\\infty\\right)",collapse="")
        } else {
            exp1 = paste0("\\sqrt{x+",-h,"}+",k)
            dom1 = paste0("x\\ge",h,collapse="")
            dom2 = paste0("\\left[",h,",\\infty\\right)",collapse="")
            ran1 = paste0("y\\ge",k,collapse="")
            ran2 = paste0("\\left[",k,",\\infty\\right)",collapse="")
        }
    }
    exp1 = gsub("+-","-",exp1,fixed=T)
    
    
    basels = list(c(1,-2),
                  c(1,-6),
                  c(-1,2),
                  c(-1,6),
                  c(-1,0))
    baseacts = c(4,9,1,4,0)
    baseexts = c(1,4,4,9,1)
    wo = sample(1:5,1)
    basel = basels[[wo]]
    if(b<0){
        basel[1] = basel[1]*(-1)
    }
    if(a<0){
        basel[1] = basel[1]*(-1)
        basel[2] = basel[2]*(-1)
    }
    basel[2] = basel[2]-h*basel[1]+k
    MB = basel
    xact = baseacts[wo]*sign(b)+h
    xext = baseexts[wo]*sign(b)+h
    lineex = paste0(MB[1],"x+",MB[2],collapse="")
    lineex = gsub("+-","-",lineex,fixed=T)
    lineex = gsub("1x","x",lineex,fixed=T)
    lineex = gsub("+0","",lineex,fixed=T)
    M = MB[1]
    B = MB[2]
    if(B!=0 && B-k!=0 && xact!=0 && xext!=0 && max(abs(c(xact,xext)))<=11){break}
}




```


1. Below I've graphed with a dotted curve $y=\sqrt{x}$ with some key points marked with dots. Please draw a graph for $f(x)=`r exp1`$, paying close attention to the corresponding key points.

```{=latex}
\begin{minipage}[t]{0.65\textwidth} \vspace{0pt}
```
```{r gah,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0))
ml = 15
plot(0,0,"n",axes=F,ann=F,xlim=c(-ml,ml),ylim=c(-ml,ml))
for(i in -ml:ml){
    lines(c(i,i),c(-ml,ml),col="lightgrey",lwd=0.8)
    lines(c(-ml,ml),c(i,i),col="lightgrey",lwd=0.8)
}
for(i in seq(-ml,ml,5)){
    lines(c(i,i),c(-ml,ml),col="darkgrey",lwd=1.2)
    lines(c(-ml,ml),c(i,i),col="darkgrey",lwd=1.2)
}
arrows(-ml*1.05,0,ml*1.05,0,0.1,10,3,lwd=2)
arrows(0,-ml*1.05,0,ml*1.05,0.1,10,3,lwd=2)
text(ml,-1,paste0(ml),cex=0.8)
text(ml,0.5,"x",cex=0.8)
text(-1,ml,paste0(ml),cex=0.8)
text(0.5,ml,"y",cex=0.8)

x = seq(0,ml,0.01)
y = sqrt(x)
xs = c(0,1,4,9)
ys = sqrt(xs)
lines(x,y,lty=2)
points(xs,ys,pch=20)

if(params$showsol){
    xx = seq(h,ml*sign(b),0.01*sign(b))
    yy = a*sqrt(b*(xx-h))+k
    lines(xx,yy,lwd=2.5,col="red")
    for(y in k:((k+3*sign(a)))){
        x = ((y-k)/a)^2/b+h
        if(max(abs(c(x,y)))<=10){
            points(x,y,col="red",cex=1.3,pch=20)
        }
    }
}
```
```{=latex}
\end{minipage} \begin{minipage}[t]{0.35\textwidth} \vspace{0pt}
```
```{r,echo=F,results='asis'}
cat(paste0("\\vspace{12pt}\\noindent 2. State the domain of $y=f(x)$"))
if(params$showsol){
    cat(paste0("\n\n\\color{red} You can use $",dom1,"$ or $",dom2,"$ to state the domain."))
} else {
    cat(paste0("\n\n\\vspace{32pt}"))
}
cat(paste0("\n\n\\vspace{1in}\n\n\\color{black}"))
cat(paste0("\\noindent 3. State the range of $y=f(x)$"))
if(params$showsol){
    cat(paste0("\n\n\\color{red} You can use $",ran1,"$ or $",ran2,"$ to state the range."))
} else {
    cat(paste0("\n\n\\vspace{32pt}"))
}
cat(paste0("\n\n\\vspace{1in}\n\n"))
```
```{=latex}
\end{minipage}
```


4. Find all **extraneous** solutions and **actual** solutions to $`r exp1`=`r lineex`$

```{=latex}
\begin{minipage}[t]{0.5\textwidth} \vspace{0pt}
```
```{r,echo=F,results='asis'}
eq2 = paste0("{",a,"}\\sqrt{{",b,"}x+",-b*h,"}={",M,"}x+",B-k,collapse="")
eq2 = gsub("+-","-",eq2,fixed=T)
eq2 = gsub("{1}","",eq2,fixed=T)
eq2 = gsub("{-1}","-",eq2,fixed=T)
eq2 = gsub("+0","",eq2,fixed=T)
if(params$showsol){
    cat(paste0("\\color{red} $$",exp1,"=",lineex,"$$\n"))
    cat(paste0("\\color{red} $$",eq2,"$$"))
    if(a<0){
        eq2a = paste0("\\sqrt{{",b,"}x+",-b*h,"}={",M*a,"}x+",(B-k)*a,collapse="")
        eq2a = gsub("+-","-",eq2a,fixed=T)
        eq2a = gsub("{1}","",eq2a,fixed=T)
        eq2a = gsub("{-1}","-",eq2a,fixed=T)
        eq2a = gsub("+0","",eq2a,fixed=T)
        cat(paste0("\n\\color{red} $$",eq2a,"$$"))
    }
    eq3 = paste0("{",b,"}x+",-b*h,"={",M^2*a^2,"}x^2+",2*M*(B-k),"x+",((B-k)*a)^2,collapse="")
    eq3 = gsub("+-","-",eq3,fixed=T)
    eq3 = gsub("{1}","",eq3,fixed=T)
    eq3 = gsub("{-1}","-",eq3,fixed=T)
    eq3 = gsub("+0","",eq3,fixed=T)
    cat(paste0("\n\\color{red} $$",eq3,"$$"))
    
    eq4 = paste0("0={",M^2*a^2,"}x^2+",2*M*(B-k)-b,"x+",((B-k)*a)^2+b*h,collapse="")
    eq4 = gsub("+-","-",eq4,fixed=T)
    eq4 = gsub("{1}","",eq4,fixed=T)
    eq4 = gsub("{-1}","-",eq4,fixed=T)
    eq4 = gsub("+0","",eq4,fixed=T)
    cat(paste0("\n\\color{red} $$",eq4,"$$"))
    
    eq5 = paste0("0=(x+",-xext,")(x+",-xact,")",collapse="")
    eq5 = gsub("+-","-",eq5,fixed=T)
    eq5 = gsub("{1}","",eq5,fixed=T)
    eq5 = gsub("{-1}","-",eq5,fixed=T)
    eq5 = gsub("+0","",eq5,fixed=T)
    cat(paste0("\n\\color{red} $$",eq5,"$$"))
    
    cat(paste0("\n\nSo, the possible solutions are $x=",xext,"$ and $x=",xact,"$.\n\nPlug each possible solution into the original equation to check."))
}


```
```{=latex}
\end{minipage} \begin{minipage}[t]{0.05\textwidth} \vspace{0pt}

\vspace{2pt}
\phantom{"hi"}

\end{minipage} \begin{minipage}[t]{0.45\textwidth} \vspace{0pt}
```

```{r,echo=F,results='asis'}
eq1 = paste0(exp1,"=",lineex,collapse="")
if(params$showsol){
    cat(paste0("\n\\color{red} Check whether $x=",xext,"$ makes equation true.\n\n"))
    ch1 = gsub("x",paste0("(",xext,")",collapse=""),eq1,fixed=T)
    ch1 = gsub("=","\\stackrel{?}{=}",ch1,fixed=T)
    cat(paste0("\n\\color{red} $$",ch1,"$$"))
    ch1b = paste0("$$",a*sqrt(b*(xext-h))+k,"\\ne ",M*xext+B,"$$",collapse="")
    cat(paste0("\n\\color{red} ",ch1b,"\n"))
    
    cat(paste0("\n\\color{red} Check whether $x=",xact,"$ makes equation true.\n\n"))
    ch1 = gsub("x",paste0("(",xact,")",collapse=""),eq1,fixed=T)
    ch1 = gsub("=","\\stackrel{?}{=}",ch1,fixed=T)
    cat(paste0("\n\\color{red} $$",ch1,"$$"))
    ch1b = paste0("$$",a*sqrt(b*(xact-h))+k,"= ",M*xact+B,"$$",collapse="")
    cat(paste0("\n\\color{red} ",ch1b,"\n"))
    
    cat(paste0("\n\n* Actual solution: $x=",xact,"$\n* Extraneous solution: $x=",xext,"$\n\nI should say that there is also a graphical approach possible for this problem. If you use it, please explain. "))
}


```
```{=latex}
\end{minipage}
```

\newpage

## u10 Radicals, Rationals, and Extraneous Solutions  `r params$titex` (version `r params$rseed`)

5. 






