---
output: pdf_document
params:
    rseed: 0
    showsol: false
    useseed: false
    titex: "PCW_09_29: Graph Parent Translations"
urlcolor: blue
---


```{r,echo=F}
if(params$useseed){
    set.seed(params$rseed)
}
fun2 = list(c("| x |","absolute value",function(x){abs(x)}),
            c("(x)^2","quadratic",function(x){x^2}),
            c("(x)^3","cubic",function(x){x^3}),
            c("\\frac{1}{x}","reciprocal",function(x){1/x}),
            c("\\sqrt{x}","square root",function(x){x^(1/2)}),
            c("\\sqrt[3]{x}","cube root",function(x){abs(x)^(1/3)*sign(x)}),
            c("2^{x}","exponential",function(x){2^x}),
            c("\\log_{2}(x)","logarithmic",function(x){log(x)/log(2)})
            )

ord = sample(1:8)
hks = list()
ft = list()
for(i in 1:8){
    hk = sample(1:5,2)*sample(c(-1,1),2,T)
    hks[[i]] = hk
    ff = fun2[[ord[i]]][[1]]
    ff = gsub("x",paste0("x+",hk[1],collapse=""),ff,fixed=T)
    ff = paste0(ff,"+",hk[2],collapse="")
    ff = gsub("+-","-",ff,fixed=T)
    ft[[i]] = ff
}

mkplot = function(){
    plot(0,0,"n",axes=F,ann=F,xlim=c(-10,10),ylim=c(-10,10))
    j = seq(-10,10,0.2)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),lwd=0.3)
        lines(c(i,i),c(-10,10),lwd=0.3)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),lwd=0.8)
        lines(c(i,i),c(-10,10),lwd=0.8)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
}

setpar = function(){
    par(mar=c(0,1.5,3,1.5),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
}

prsol = function(ff,h,k){
    x = seq(-10,10,0.0001)
    y = ff(x-h)+k
    x2 = x[!is.na(y)]
    y2 = y[!is.na(y)]
    x = x2[abs(y2)<=10]
    y = y2[abs(y2)<=10]
    breaks = c(0,which(abs(diff(y))>10),length(x))
    for(j in 1:(length(breaks)-1)){
        suppressWarnings(lines(x[(breaks[j]+1):(breaks[j+1]-1)],y[(breaks[j]+1):(breaks[j+1]-1)],type="l",lwd=4,col="red"))
    }
    xp = -10:10
    yp = ff(xp-h)+k
    xp2 = xp[!is.na(yp)]
    yp2 = yp[!is.na(yp)]
    xp = xp2[abs(yp2)<=10]
    yp = yp2[abs(yp2)<=10]
    if(length(yp)>0){
        for(i in 1:length(xp)){
            if(yp[i]%%1==0){points(xp[i],yp[i],pch=19,cex=0.8,col="red")}
        }
    }
}


figdim = c(7,3.5)

```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

# `r params$titex` (version `r params$rseed`)

Graph each equation. Let the $y$ axis be vertical and the $x$ axis be horizontal. Also, let both axes be at unit scale, so each goes from $-10$ to $10$.

Clearly mark every solution where $x$ and $y$ are both integers with a small dot along the curve.


\vfill

```{r,echo=F,fig.dim=figdim,warning=F}
library(latex2exp)
setpar()

n = 1
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}

n = 2
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}
```

\vfill

```{r,echo=F,fig.dim=figdim,warning=F}
setpar()

n = 3
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}

n = 4
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}
```

\vfill

\newpage


# `r params$titex` (version `r params$rseed`)

\vfill

```{r,echo=F,fig.dim=figdim,warning=F}
setpar()

n = 5
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}

n = 6
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}
```

\vfill

```{r,echo=F,fig.dim=figdim,warning=F}
setpar()

n = 7
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}

n = 8
mkplot()
mtext(TeX(paste0("$y=",ft[[n]],"$")))
if(params$showsol){
    prsol(fun2[[ord[n]]][[3]],-hks[[n]][1],hks[[n]][2])
}
```

\vfill




