```{r data generation, echo = FALSE, results = "hide"}
while(T){
  d = sample(2:6,1)
  a1 = sample(2:20,1)
  n = sample(15:40,1)
  an = a1+(n-1)*d
  i = 1:n
  a = a1+(i-1)*d
  ave = (a1+an)/2
  S = sum(a)
  S2 = (a1+an)/2*n
  if(round(ave)==ave){break}
}
```


Question
========

Let $a_{i}$ represent the $i$th term of an [arithmetic series](https://en.wikipedia.org/wiki/Arithmetic_progression#Sum){target="_blank"}, and
$$a_1=`r a1`$$
$$a_2=`r a[2]`$$

Find the sum of the first `r n` terms. In other words, 
$$\sum_{i=1}^{`r n`}a_i = \,?$$


Solution
========

The sum of an arithmetic series is found by averaging the first and last terms and multiplying by the number of terms.

$$\sum_{i=p}^q a_i ~~=~~ \frac{a_p+a_q}{2} \cdot (q-p+1)$$

Determine the common difference.

$$d ~=~ (`r a[2]`)-(`r a1`) ~=~ `r d`$$

Find the value of $a_{`r n`}$ using the explicit arithmetic formula.

$$a_{n} = a_1+(n-1)d $$
$$a_{`r n`} = `r a1`+(`r n`-1)(`r d`)$$
$$a_{`r n`} = `r a[n]`$$

So,

$$\sum_{i=1}^{`r n`} a_i ~=~ \frac{(`r a1`)+(`r an`)}{2} \cdot (`r n`)$$

Evaluate.
$$\sum_{i=1}^{`r n`} a_i ~=~ `r S`$$

I think of an arithmetic series as representing stacks of coins in a stair pattern. Our goal is to count the coins.

```{r,echo=FALSE,fig.dim=c(6,6)}
library(latex2exp)
par(pty="s",mar=c(4,0.1,0.1,0.1))
plot(0,0,type="n",xlim=c(0,n+1),ylim=c(0,round(max(a)+10,-1)),ylab="value",xlab="index")
for(i in 1:n){
  lines(c(i-0.5,i+0.5),c(0,0))
  for(j in 1:a[i]){
    lines(c(i-0.5,i-0.5,i+0.5,i+0.5),c(j-1,j,j,j-1))
  }
}
abline(h=ave,lty=2,col="red")
text(n/8,ave+an/25,paste0("average = ",ave,collapse=""),col="red")
text(1,a1+an/10,TeX(paste0("$a_1=",a1,"$")),col="red")
arrows(1,a1+an/15,1,a1+an/25,col="red",length=0.03)
text(n-0.6,an+an/20,TeX(paste0("$a_{",n,"}=",an,"$")),col="red")
# lines(c(n,n),c(an+an/25,an+an/15),col="red")
```
\

Because of the regularity of the step size, the average stack height is simply the average of the first and last stacks.

If we redistribute the wealth, then all the stacks have the average height.

```{r,echo=FALSE,fig.dim=c(6,6)}
library(latex2exp)
par(pty="s",mar=c(4,0.1,0.1,0.1))
plot(0,0,type="n",xlim=c(0,n+1),ylim=c(0,round(max(a)+10,-1)),ylab="value",xlab="index")
for(i in 1:n){
  lines(c(i-0.5,i+0.5),c(0,0))
  for(j in 1:round(ave)){
    if(j>a[i]){
      lines(c(i-0.5,i-0.5,i+0.5,i+0.5),c(j-1,j,j,j-1),col="grey")
    } else {
      lines(c(i-0.5,i-0.5,i+0.5,i+0.5),c(j-1,j,j,j-1),col="black")
    }
  }
}
abline(h=ave,lty=2,col="red")
text(n/8,ave+an/25,paste0("average = ",ave,collapse=""),col="red")
text(n/2,an-5,TeX(paste0("$",ave,"\\cdot ",n,"=",S,"$")),col="red",cex = 3)
```
\

Thus, we just need to multiply the number of stacks by the average height. And the average height is simply the average of the first and last stack. $`r ave`\cdot`r n` = `r S`$.


Meta-information
============
extype: num
exsolution: `r S`
exname: arith_seq_find_sum