```{r data generation, echo = FALSE, results = "hide"}
while(T){
  X = sort(sample(0:9,4)*c(1,1,1,-1))
  P = sample(1:4)/10
  mu = sum(X*P)
  sig = sqrt(sum(P*(X-mu)^2))

  if(mu < 0 && mu > -5 && abs(mu)>0.02 && round(sig*10)==sig*10){
    break
  }
}
mu = round(10*mu)/10
sig = round(10*sig)/10
prods = X*P
diffs = (X-mu)
sqd = (X-mu)^2
vprods = P*(X-mu)^2
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

A lottery has the [discrete probability distribution](https://en.wikipedia.org/wiki/Probability_mass_function){target="_blank"} below.

```{r tab_data, echo=FALSE, results="asis"}
ct = data.frame(X,P)
colnames(ct) = c("$x_i$","$p_i$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```

Find the population standard deviation. To do this first calculate the population mean.

$$\mu = \sum\limits_{i=1}^{n}p_ix_i$$

Calculate the variance.

$$\sigma^2 = \sum\limits_{i=1}^{n}p_i(x_i-\mu)^2$$

Finally, take the square root of the variance to get the standard deviation.

$$\sigma = \sqrt{\sigma^2}$$


Solution
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>


Calculate the mean.

$$\mu = `r paste0("(",X,")(",P,")",collapse="+")` $$
$$\mu = `r paste0(prods,collapse="+")` $$
$$\mu = `r mu` $$

Next, calculate the variance.

$$\sigma^2 = `r paste0("(",P,")(",X,"-(",mu,"))^2",collapse="+")` $$

$$\sigma^2 = `r paste0("(",P,")(",diffs,")^2",collapse="+")` $$

$$\sigma^2 = `r paste0("(",P,")(",sqd,")",collapse="+")` $$

$$\sigma^2 = `r paste0(vprods,collapse="+")` $$

$$\sigma^2 = `r sum(vprods)`$$
Get the standard deviation by taking the square root of the variance.

$$\sigma = `r sqrt(sum(vprods))`$$

It is probably better to use a table.

```{r tab_data2, echo=FALSE, results="asis"}
X2 = c(paste(X),"","","")
P2 = c(paste(P),"","","")
prod2 = c(paste(X*P),"","$\\mu$",paste(sum(X*P)))
diff2 = c(paste(X-mu),"","","")
sqd2 = c(paste((X-mu)^2),"","","")
vp2 = c(paste(P*(X-mu)^2),"","$\\sigma^2$",paste(sum(P*(X-mu)^2)))
ct = data.frame(X2,P2,prod2,diff2,sqd2,vp2)
colnames(ct) = c("$x_i$","$p_i$","$(x_i)(p_i)$","$x_i-\\mu$","$(x_i-\\mu)^2$","$p_i(x_i-\\mu)^2$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```

$$\sigma = \sqrt{`r sum(P*(X-mu)^2)`} = `r sig` $$

Realistically, it is best to use a spreadsheet to do the arithmetic for you. It would look something like:

|     |     |    A     |   B      |     C      |    D      |      E        | F |
|:---:|:---:|:--------:|:--------:|:----------:|:---------:|:-------------:|:---:|
|  1  |     | $x_i$    | $p_i$    | $x_ip_i$   | $x_i-\mu$ | $(x_i-\mu)^2$ | $p_i(x_i-\mu)^2$ |
|  2  |     | `r X[1]` | `r P[1]` |   =A2*B2   |  =A2-C$8  |   =D2^2       | =B2*F2  |
|  3  |     | `r X[2]` | `r P[2]` |   =A3*B3   |  =A3-C$8  |   =D3^2       | =B3*F3  |
|  4  |     | `r X[3]` | `r P[3]` |   =A4*B4   |  =A4-C$8  |   =D4^2       | =B4*F4  |
|  5  |     | `r X[4]` | `r P[4]` |   =A5*B5   |  =A5-C$8  |   =D5^2       | =B5*F5  |
|  6  |     |          |          |            |           |               |         |
|  7  |     |          |          |  mu        |           |               | variance|
|  8  |     |          |          | =sum(C2:C5)|           |               | =sum(F2:F5) |
|  9  |     |          |          |            |           |               |         |
|  10 |     |          |          |            |           |               | st dev  |
|  11 |     |          |          |            |           |               | =sqrt(F8) |





Meta-information
================
extype: num
exsolution: `r sig`
exname: sig_pop_int
extol: 0.1
