```{r data generation, echo = FALSE, results = "hide"}
while(T){
  X1 = sort(sample(0:9,4)*c(1,1,1,-1))
  P1 = sample(1:4)/10
  mu = sum(X1*P1)
  sig = sqrt(sum(P1*(X1-mu)^2))

  if(mu < 0 && mu > -5 && abs(mu)>0.02 && round(sig*10)==sig*10){
    break
  }
}
mu1 = round(10*mu)/10
sig1 = round(10*sig)/10

while(T){
  X2 = sort(sample(0:9,4)*c(1,1,1,-1))
  P2 = sample(1:4)/10
  mu = sum(X2*P2)
  sig = sqrt(sum(P2*(X2-mu)^2))

  if(mu < 0 && mu > -5 && abs(mu)>0.02 && round(sig*10)==sig*10){
    break
  }
}
mu2 = round(10*mu)/10
sig2 = round(10*sig)/10

sig3 = sqrt(sig1^2+sig2^2)
```

Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

Joe will play two lotteries, with the following profit distributions, mean, and standard deviations.

### Lottery 1
```{r tab_data, echo=FALSE, results="asis"}
ct = data.frame(X1,P1)
colnames(ct) = c("$x_i$","$p_i$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```

$$\mu_1 = `r mu1`$$
$$\sigma_1 = `r sig1`$$

### Lottery 2
```{r tab_data2, echo=FALSE, results="asis"}
ct = data.frame(X2,P2)
colnames(ct) = c("$x_i$","$p_i$")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```

$$\mu_2 = `r mu2`$$
$$\sigma_2 = `r sig2`$$

## Total of both lotteries

There are many possible outcomes for the total of both lotteries. Each pairing of outcomes is a possibility, giving a profit (from the sum of the two profits) and a chance (from the product of the two chances).

```{r,echo=F}
poss = numeric()
prob = numeric()
for(i in 1:4){
  for(j in 1:4){
    xx = X1[i]+X2[j]
    pp = P1[i]*P2[j]
    poss = c(poss,xx)
    prob = c(prob,pp)
  }
}
```

```{r tab_data3, echo=FALSE, results="asis"}
ct = data.frame(poss,prob)
colnames(ct) = c("profit","chance")
knitr::kable(ct,format="html",table.attr='class="bordered-table"', align = "cccc",row.names=F)
```

Notice, some possible profits show up more than once; these could be collapsed by adding their probabilities. It would still be a pain to analyze by hand. Luckily, there are some very nice properties when considering the sum of  [random variables](https://en.wikipedia.org/wiki/Random_variable){target="_blank"}.

$$\mu = \mu_1 + \mu_2$$

$$\sigma^2 = (\sigma_1)^2+(\sigma_2)^2$$

$$\sigma = \sqrt{(\sigma_1)^2+(\sigma_2)^2} $$

Find the [population standard deviation](https://en.wikipedia.org/wiki/Standard_deviation#Discrete_random_variable){target="_blank"} of the profit distribution when Joe plays both lotteries, arriving at a combined profit by adding the two random [independent](https://en.wikipedia.org/wiki/Independence_(probability_theory)){target="_blank"} profits.

Solution
========

This looks much worse than it is. 
$$\sigma = \sqrt{(`r sig1`)^2+(`r sig2`)^2} = `r sig3` $$

Notice, there is no simple formula like this for the [average absolute deviation](https://en.wikipedia.org/wiki/Average_absolute_deviation) of a sum of random variables. This is the **key** reason to use standard deviation (and variance) as our measure of spread. 



Meta-information
================
extype: num
exsolution: `r sig3`
exname: sig_pop_int
extol: 0.1
