---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

Name: \vspace{5pt} \hrule

## p1028a: Box multiplication for two-digit integers (v`r params$rseed`)

```{r,echo=F}
if(params$rseed !=0){
    set.seed(params$rseed)
}

```

## Example

Without a calculator, use the box method to multiply 63 and 24.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)

lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,60)
text(5,7,3)
text(1,5,20)
text(1,3,4)
text(1,7,"*")

text(3,5,"1200",col="red")
text(5,5,"60",col="red")
text(3,3,"240",col="red")
text(5,3,"12",col="red")

text(7.5,7,"1200",adj=1,col="red")
text(7.5,6,"60",adj=1,col="red")
text(7.5,5,"240",adj=1,col="red")
text(7.5,4,"+    12",adj=1,col="red")

lines(c(6.5,8),c(3.5,3.5),col="red")

text(7.5,3,63*24,adj=1,col="red")

tots = c(63*24)

```

\vfill

## Question 1

```{r,echo=F}
while(T){
    digits = sample(2:9,4)
    At = digits[1]
    Ao = digits[2]
    Bt = digits[3]
    Bo = digits[4]
    A = At*10+Ao
    B = Bt*10+Bo
    p1 = At*Bt
    p2 = Ao*Bt
    p3 = At*Bo
    p4 = Ao*Bo
    if(!(A*B%in%tots)){break}
}
tots = c(tots,A*B)

```

Without a calculator, use the box method to multiply `r A` and `r B`.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)
lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)

text(3,7,At*10)
text(5,7,Ao)
text(1,5,Bt*10)
text(1,3,Bo)
# text(1,1,"TOTAL")
# text(7,7,"TOTAL")

text(1,7,"*")

if(params$showsol){
    text(3,5,At*Bt*100,col="red")
    text(5,5,Ao*Bt*10,col="red")
    text(3,3,At*Bo*10,col="red")
    text(5,3,Ao*Bo,col="red")
    
    text(7.5,7,At*Bt*100,adj=1,col="red")
    text(7.5,6,Ao*Bt*10,adj=1,col="red")
    text(7.5,5,At*Bo*10,adj=1,col="red")
    text(7.5,4,paste0("+    ",Ao*Bo),adj=1,col="red")
    
    lines(c(6.5,8),c(3.5,3.5),col="red")
    
    text(7.5,3,A*B,adj=1,col="red")
}

```


\vfill

\newpage


## Question 2

```{r,echo=F}
while(T){
    digits = sample(2:9,4)
    At = digits[1]
    Ao = digits[2]
    Bt = digits[3]
    Bo = digits[4]
    A = At*10+Ao
    B = Bt*10+Bo
    p1 = At*Bt
    p2 = Ao*Bt
    p3 = At*Bo
    p4 = Ao*Bo
    if(!(A*B%in%tots)){break}
}
tots = c(tots,A*B)
```

Without a calculator, use the box method to multiply `r A` and `r B`.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)
lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)


# text(1,1,"TOTAL")
# text(7,7,"TOTAL")

text(1,7,"*")

if(params$showsol){
    text(3,7,At*10,col="red")
    text(5,7,Ao,col="red")
    text(1,5,Bt*10,col="red")
    text(1,3,Bo,col="red")
    text(3,5,At*Bt*100,col="red")
    text(5,5,Ao*Bt*10,col="red")
    text(3,3,At*Bo*10,col="red")
    text(5,3,Ao*Bo,col="red")
    
    text(7.5,7,At*Bt*100,adj=1,col="red")
    text(7.5,6,Ao*Bt*10,adj=1,col="red")
    text(7.5,5,At*Bo*10,adj=1,col="red")
    text(7.5,4,paste0("+    ",Ao*Bo),adj=1,col="red")
    
    lines(c(6.5,8),c(3.5,3.5),col="red")
    
    text(7.5,3,A*B,adj=1,col="red")
}

```

\vfill

## Question 3

```{r,echo=F}
while(T){
    digits = sample(2:9,4)
    At = digits[1]
    Ao = digits[2]
    Bt = digits[3]
    Bo = digits[4]
    A = At*10+Ao
    B = Bt*10+Bo
    p1 = At*Bt
    p2 = Ao*Bt
    p3 = At*Bo
    p4 = Ao*Bo
    if(!(A*B%in%tots)){break}
}
tots = c(tots,A*B)
```

Without a calculator, use the box method to multiply `r A` and `r B`.

```{r,echo=F,fig.dim=c(6,2.5)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,8),ylim=c(2,8),axes=F,ann=F)
lines(c(0,6),c(2,2),lwd=3)
lines(c(0,6),c(4,4),lwd=1)
lines(c(0,6),c(6,6),lwd=3)

lines(c(2,2),c(2,8),lwd=3)
lines(c(4,4),c(2,8),lwd=1)
lines(c(6,6),c(2,8),lwd=3)


# text(1,1,"TOTAL")
# text(7,7,"TOTAL")

text(1,7,"*")

if(params$showsol){
    text(3,7,At*10,col="red")
    text(5,7,Ao,col="red")
    text(1,5,Bt*10,col="red")
    text(1,3,Bo,col="red")
    
    text(3,5,At*Bt*100,col="red")
    text(5,5,Ao*Bt*10,col="red")
    text(3,3,At*Bo*10,col="red")
    text(5,3,Ao*Bo,col="red")
    
    text(7.5,7,At*Bt*100,adj=1,col="red")
    text(7.5,6,Ao*Bt*10,adj=1,col="red")
    text(7.5,5,At*Bo*10,adj=1,col="red")
    text(7.5,4,paste0("+    ",Ao*Bo),adj=1,col="red")
    
    lines(c(6.5,8),c(3.5,3.5),col="red")
    
    text(7.5,3,A*B,adj=1,col="red")
}

```

\vfill
