---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

Name: \vspace{5pt} \hrule

## p1028b: Combine Like Terms (v`r params$rseed`)

```{r,echo=F}

if(params$rseed !=0){
    set.seed(params$rseed)
}

pn = function(coeffs,pows){
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    return(ex1)
}

```


## Example


```{r,echo=F}
while(T){
    coeffs = sample(c(-9:-1,1:9),10)
    pows = c(sample(rep(0:2,3)),sample(0:2,1))
    cnts = c()
    lins = c()
    quas = c()
    for(i in 1:length(pows)){
        if(pows[i]==0){
            cnts = c(cnts,coeffs[i])
        }
        if(pows[i]==1){
            lins = c(lins,coeffs[i])
        }
        if(pows[i]==2){
            quas = c(quas,coeffs[i])
        }
    }
    A = sum(quas)
    B = sum(lins)
    C = sum(cnts)
    if(abs(A)>0 && abs(B)>0 && abs(C)>0){break}
}

ex1 = pn(coeffs,pows)
```

Combine like terms.
$$`r ex1`$$

\color{red}
### Answer
Combine the quadratic terms.

$$`r pn(quas,c(2,2,2))`~\equiv~ `r A`x^2$$

Combine the linear terms.

$$`r pn(lins,c(1,1,1))`~\equiv~ `r B`x$$


Combine the constant terms.

$$`r pn(cnts,c(0,0,0))`~\equiv~ `r C`$$

The final result:

$$`r pn(c(A,B,C),c(2,1,0))`$$
\color{black}

\hrule

## Question 1


```{r,echo=F}
while(T){
    coeffs = sample(c(-9:-1,1:9),10)
    pows = c(sample(rep(0:2,3)),sample(0:2,1))
    cnts = c()
    lins = c()
    quas = c()
    for(i in 1:length(pows)){
        if(pows[i]==0){
            cnts = c(cnts,coeffs[i])
        }
        if(pows[i]==1){
            lins = c(lins,coeffs[i])
        }
        if(pows[i]==2){
            quas = c(quas,coeffs[i])
        }
    }
    A = sum(quas)
    B = sum(lins)
    C = sum(cnts)
    if(abs(A)>0 && abs(B)>0 && abs(C)>0){break}
}

ex1 = pn(coeffs,pows)
if(params$showsol){
    ans = paste0("$$",pn(c(A,B,C),2:0),"$$")
} else {
    ans = ""
}

```


Combine like terms.
$$`r ex1`$$

\vfill

\color{red}
`r ans`
\color{black}

\vfill

\newpage


## Question 2

```{r,echo=F}
while(T){
    coeffs = sample(c(-9:-1,1:9),10)
    pows = c(sample(rep(0:2,3)),sample(0:2,1))
    cnts = c()
    lins = c()
    quas = c()
    for(i in 1:length(pows)){
        if(pows[i]==0){
            cnts = c(cnts,coeffs[i])
        }
        if(pows[i]==1){
            lins = c(lins,coeffs[i])
        }
        if(pows[i]==2){
            quas = c(quas,coeffs[i])
        }
    }
    A = sum(quas)
    B = sum(lins)
    C = sum(cnts)
    if(abs(A)>0 && abs(B)>0 && abs(C)>0){break}
}

ex1 = pn(coeffs,pows)
if(params$showsol){
    ans = paste0("$$",pn(c(A,B,C),2:0),"$$")
} else {
    ans = ""
}

```



Combine like terms.
$$`r ex1`$$

\vfill

\color{red}
`r ans`
\color{black}

\vfill


## Question 3


```{r,echo=F}
while(T){
    coeffs = sample(c(-9:-1,1:9),10)
    pows = c(sample(rep(0:2,3)),sample(0:2,1))
    cnts = c()
    lins = c()
    quas = c()
    for(i in 1:length(pows)){
        if(pows[i]==0){
            cnts = c(cnts,coeffs[i])
        }
        if(pows[i]==1){
            lins = c(lins,coeffs[i])
        }
        if(pows[i]==2){
            quas = c(quas,coeffs[i])
        }
    }
    A = sum(quas)
    B = sum(lins)
    C = sum(cnts)
    if(abs(A)>0 && abs(B)>0 && abs(C)>0){break}
}

ex1 = pn(coeffs,pows)
if(params$showsol){
    ans = paste0("$$",pn(c(A,B,C),2:0),"$$")
} else {
    ans = ""
}

```


Combine like terms.
$$`r ex1`$$

\vfill

\color{red}
`r ans`
\color{black}

\vfill



## Question 4

```{r,echo=F}
while(T){
    coeffs = sample(c(-9:-1,1:9),10)
    pows = c(sample(rep(0:2,3)),sample(0:2,1))
    cnts = c()
    lins = c()
    quas = c()
    for(i in 1:length(pows)){
        if(pows[i]==0){
            cnts = c(cnts,coeffs[i])
        }
        if(pows[i]==1){
            lins = c(lins,coeffs[i])
        }
        if(pows[i]==2){
            quas = c(quas,coeffs[i])
        }
    }
    A = sum(quas)
    B = sum(lins)
    C = sum(cnts)
    if(abs(A)>0 && abs(B)>0 && abs(C)>0){break}
}

ex1 = pn(coeffs,pows)
if(params$showsol){
    ans = paste0("$$",pn(c(A,B,C),2:0),"$$")
} else {
    ans = ""
}

```


Combine like terms.
$$`r ex1`$$

\vfill

\color{red}
`r ans`
\color{black}

\vfill


