---
output: slidy_presentation
---


# Box method for multiplying two two-digit numbers

Consider the product $52\cdot 43$. 

* We will evaluate with the box method.

>- First, break each factor into its tens and ones.
$$52~=~ 50+2$$
$$43~=~ 40+3$$
- We can make a 2x2 box, putting the first factor's terms as column labels and the second factor's terms as row labels.\
```{r,echo=F,fig.dim=c(3,3)}
library(latex2exp)
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,6),ylim=c(0,6),axes=F,ann=F)
abline(h=0)
abline(h=2)
abline(h=4,lwd=3)
abline(v=2,lwd=3)
abline(v=4)
abline(v=6)

text(3,5,"50")
text(5,5,"2")
text(1,3,"40")
text(1,1,"3")

text(1,5,"*")

```
- Fill each cell with the product of its column label and its row label.\
```{r,echo=F,fig.dim=c(3,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,6),ylim=c(0,6),axes=F,ann=F)
abline(h=0)
abline(h=2)
abline(h=4,lwd=3)
abline(v=2,lwd=3)
abline(v=4)
abline(v=6)

text(3,5,"50")
text(5,5,"2")
text(1,3,"40")
text(1,1,"3")

text(3,3,"2000",col="red")
text(5,3,"150",col="red")
text(3,1,"80",col="red")
text(5,1,"6",col="red")

text(1,5,"*")
```
>- Add up the results.
$$2000+150+80+6$$
$$2150+86$$
$$`r 52*43`$$

# Multiply two two-digit numbers with box method... Example 1

Use the box method to multiply.
$$73 \cdot 48$$


# Combining like terms

>- "Terms" are expressions that are added (or subtracted) to something.
>- "Factors" are expressions that are multiplied (or divided) by something.
>- Terms can be composed of factors (and vice versa).

>- We will start with 3 types of terms:\
    * Quadratic terms (a number times $x^2$)
    * Linear terms (a number times $x$)
    * Constant terms (just a number)

>- A common step when simplifying expressions is to **combine like terms**. For example... imagine we are simplifying the following expression.$$4x+5+8x^2+7+9x-3x^2$$

>- We identify the quadratic terms are $8x^2$ and $-3x^2$.
>- We identify the linear terms are $4x$ and $9x$.
>- We identify the constants are $5$ and $7$. 
>- Thus, when we combine like terms we get... (and put in standard order of quadratic, linear, and then constant)...
>- We get $$5x^2+13x+12$$
>- Notice "combine" means add the coefficients... and "coefficient" is the numerical part of the term.


# Combine-like-terms example 1

Consider the function below.

$$f(x)~=~ 6x^2 +8x+4+3x^2-x-2$$

When simplified, that function can be written in standard form:

$$f(x)~=~ ax^2+bx+c$$

where $a$, $b$, and $c$ are integers. Find $a$, $b$, and $c$.

>- Combine the quadratic terms.$$6x^2+3x^2~\equiv~ 9x^2$$
>- Combine the linear terms. Notice $-x$ is equivalent to $-1x$, but we do not write coefficients of 1 or -1. $$8x-x~\equiv~ 7x$$
>- Combine the constant terms.$$4-2~\equiv~ 2$$
>- Write the function.
$$f(x)~=~ 9x^2+7x+2$$
>- Identify the parameters.$$a=9$$ $$b=7$$ $$c=2$$



# Combine-like-terms example 2

Consider the function below.

$$f(x)~=~ 2+8+4x-5x-3+9x^2-x-8x^2+6x$$

When simplified, that function can be written in standard form:

$$f(x)~=~ ax^2+bx+c$$

where $a$, $b$, and $c$ are integers. Find $a$, $b$, and $c$.

>- Combine the quadratic terms.$$9x^2-8x^2+6x^2~\equiv~ 7x^2$$
>- Combine the linear terms. $$4x-5x-x~\equiv~ -2x$$
>- Combine the constant terms.$$2+8-3~\equiv~ 7$$
>- Write the function.
$$f(x)~=~ 7x^2-2x+7$$
>- Identify the parameters.$$a=7$$ $$b=-2$$ $$c=7$$







# Some simple examples of equivalent expressions

>- Simplify $3x+4x$
>- $7x$
>- Simplify $x+4x$
>- $5x$
>- Simplify $3x^2+4x^2$
>- $7x^2$
>- Simplify $3x^2+4x$
>- $3x^2+4x$ Notice we can only combine [like terms](https://en.wikipedia.org/wiki/Like_terms#Example).
>- Simplify $(2)\cdot (x)$
>- $2x$
>- Simplify $(x)\cdot(x)$
>- $x^2$
>- Simplify $(3x)\cdot (5x)$
>- $15x^2$
>- Distribute $2\cdot (3x+5)$
>- $6x+10$
>- Distribute $x\cdot (3x+5)$
>- $3x^2+5x$



# Distributing a sum times a sum


>- What do I get when I distribute $(x+2)\cdot (3x+5)$?
>- First, distribute $(x+2)$ to each term in $(3x+5)$.\
$$(x+2)\cdot 3x ~~~+~~~ (x+2)\cdot 5$$
>- Distribute $3x$ to each term in its $(x+2)$ multiplier.\
$$3x^2+6x ~~~+~~~ (x+2)\cdot 5$$
>- Distribute $5$ to each term in its $(x+2)$ multiplier.\
$$3x^2+6x ~~~+~~~ 5x+10$$
>- Notice we have two [like terms](https://en.wikipedia.org/wiki/Like_terms#Example).
>- Combine the like terms.
>- You get:
$$3x^2+11x+10$$
>- When we get rid of parentheses and combine like terms, we call the process "expansion". You can be asked to "expand the expression".


# Multiply linear binomials with box method

Expand the expression shown below.

$$(2x+3)\cdot (4x+5)$$

>- We can make a 2x2 box, putting the first factor's terms as row labels and the second factor's terms as column labels.\
```{r,echo=F,fig.dim=c(3,3)}
par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,6),ylim=c(0,6),axes=F,ann=F)
abline(h=0)
abline(h=2)
abline(h=4,lwd=3)
abline(v=2,lwd=3)
abline(v=4)
abline(v=6)

text(3,5,"4x")
text(5,5,"5")
text(1,3,"2x")
text(1,1,"3")

```

>- In each cell, write the product of the column label and row label\
```{r,echo=F,fig.dim=c(3,3)}
library(latex2exp)

par(mar=c(0,0,0,0),oma=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,6),ylim=c(0,6),axes=F,ann=F)
abline(h=0)
abline(h=2)
abline(h=4,lwd=3)
abline(v=2,lwd=3)
abline(v=4)
abline(v=6)

text(3,5,"4x")
text(5,5,"5")

text(1,3,"2x")
text(1,1,"3")

text(3,3,TeX("$8x^2$"),col="red")
text(5,3,TeX("$10x$"),col="red")
text(3,1,TeX("$12x$"),col="red")
text(5,1,TeX("$15$"),col="red")

```

>- Write the terms. $$8x^2+10x+12x+15$$
>- Combine the two linear terms to get the answer: $$8x^2+22x+15$$
>- Notice, this is the same result we would get by following the method on the previous slide of repeatedly distributing.








