---
output: pdf_document
params:
    rseed: 1
    showsol: true
    useseed: false
    titex: "practice"
urlcolor: blue
---


```{r,echo=F}
# # Topics:
# * Is a relation a function? Is function one-to-one?
# * Function notation
#     * Evaluate a function at x=a
# * Inverse functions
#     * Tables/graphs/expressions (2 step functions)
# * Function reflections
# * Even/odd functions
if(params$useseed){
    set.seed(params$rseed)
}
if(params$showsol){
    solstart = "\n\n\\color{red}\n\n"
    solend = "\n\n\\color{black}\n\n"
    hidesolstart = "<!---"
    hidesolend = "-->"
} else {
    solstart = "<!---"
    solend = "-->"
    hidesolstart = ""
    hidesolend = ""
}
```

Name: \hspace{4in} Date: \hfill \vspace{3pt} \hrule

# Exam: Function Reflections (`r params$titex` version `r params$rseed`)


```{r, echo = FALSE}

while(T){
    x = 1:9
    f = sample(1:9)
    g = sample(1:9)
    h = sample(1:9)
    pairs = c(paste0(x,f),paste0(x,g),paste0(x,h),paste0(f,x),paste0(g,x),paste0(h,x))
    pairs = unique(pairs)
    funs = list(f,g,h)
    fun12 = sample(1:3,2)
    fun1 = fun12[1]
    fun2 = fun12[2]
    num1 = sample(1:9,1)
    num2 = sample(1:9,1)
    ans1 = funs[[fun1]][num1]
    ans2 = x[num2==funs[[fun2]]]
    p2 = c(paste0(x[num1],f[num1]),paste0(x[num1],g[num1]),paste0(x[num1],h[num1]),
           paste0(f[num1],x[num1]),paste0(g[num1],x[num1]),paste0(h[num1],x[num1]),
           paste0(x[ans2],f[ans2]),paste0(x[ans2],g[ans2]),paste0(x[ans2],h[ans2]),
           paste0(f[ans2],x[ans2]),paste0(g[ans2],x[ans2]),paste0(h[ans2],x[ans2]))
    p2 = unique(p2)
    if(length(unique(c(num1,num2,ans1,ans2)))==4 && length(pairs)>(length(x)*6-7) && length(p2)==12){break}
}

lets = c("f","g","h")
let1 = lets[fun1]
let2 = lets[fun2]

while(T){
    fun34 = sample(1:3,2)
    x34 = sample(1:9,2)
    if(length(unique(c(fun12,fun34)))==3 && length(unique(c(x34,num1,num2,ans1,ans2)))==6){break}
}
eo = sample(1:2,2)
wrds = c("even","odd")
mult = c(1,-1)
x3 = x34[1]
x4 = x34[2]
y3 = funs[[fun34[1]]][x3]*mult[eo[1]]
y4 = funs[[fun34[2]]][x4]*mult[eo[2]]
let3 = lets[fun34[1]]
let4 = lets[fun34[2]]

```

For all questions on this page, the functions $f$, $g$, and $h$ defined by the table below. 

```{r,echo=F,}
data <- data.frame(
  x,
  f,
  g,
  h
)
colnames(data) = c("$x$","$f(x)$","$g(x)$","$h(x)$")
knitr::kable(data,format = "latex",escape = FALSE,align = 'c')
```

**Q1.** Evaluate $`r let1`(`r num1`)$.

\vfill
`r solstart`
$$`r let1`(`r num1`)=`r ans1`$$
`r solend`
\vfill

**Q2.** Evaluate $`r let2`^{-1}(`r num2`)$.

\vfill
`r solstart`
$$`r let2`^{-1}(`r num2`)=`r ans2`$$
`r solend`
\vfill

**Q3.** By filling more rows of the table, it is possible to make function $`r let3`$ **`r wrds[eo[1]]`**. If that were done, what would be the value of $`r let3`(-`r x3`)$?

\vfill
`r solstart`
If function `r let3` is `r wrds[eo[1]]`, then
$$`r let3`(-`r x3`)=`r y3`$$
`r solend`
\vfill

**Q4.** By filling more rows of the table, it is possible to make function $`r let4`$ **`r wrds[eo[2]]`**. If that were done, what would be the value of $`r let4`(-`r x4`)$?

\vfill
`r solstart`
If function `r let4` is `r wrds[eo[2]]`, then
$$`r let4`(-`r x4`)=`r y4`$$
`r solend`
\vfill


\newpage



