```{r data generation, echo = FALSE, results = "hide"}

n = sample(6:9,1)
xl = runif(1,10,80)
xh = runif(1,5,20)+xl
x = round(runif(n,xl,xh),1)
m = sample(c(2:10),1)
b = runif(1,-30,30)
bump = (xh-xl)*abs(m)/5
y = round(m*x+b+runif(n,-bump,bump),1)
mod1 = lm(y~x)
cf = mod1$coefficients
x0 = round(runif(1,xl-10,xh+10))
y0 = cf[1]+cf[2]*x0
y0r = round(cf[1])+round(cf[2],1)*x0
tol = ceiling((max(abs(y0r-y0),1)))
```


Question
========

<style type="text/css" rel="stylesheet">
.bordered-table {
    border-collapse: collapse;
    border-spacing: 0;
    border:2px solid #000000;
}
.bordered-table th {
    border:2px solid #000000;
    padding: 4px;
}
.bordered-table td{
    border:2px solid #000000;
    padding: 4px;
}
</style>

```{r tab2, results="asis", echo=F}
mydf2 = data.frame(x,y)
knitr::kable(mydf2,format="html",table.attr='class="bordered-table"', align = "cc",row.names=F)
```

Find the trendline using a [simple linear regression](https://en.wikipedia.org/wiki/Simple_linear_regression){target="_blank"}. Do **not** assume the $y$-intercept is 0.

Using the linear model, predict $y$ when $x=`r x0`$.


Solution
========

* Copy the $x$ and $y$ values into a spreadsheet.
* Highlight the data. Insert chart $\to$ scatterplot.
* Under Setup, click `Use column A as labels`
* Under Customize $\to$ Series, click `Trendline`
* Change the Label to `Use Equation`

The chart+trendline provide a nice visual, and an approximate linear model. To get more exact values for the slope and y-intercept, use the `=linest()` function. The first argument is the y values, and the second argument is the x values. For the third argument (calculate_b), use `true`. For the fourth argument (verbose), use `false`.

```{r tab3, results="asis", echo=F,fig.dim=c(6,6)}
A = c("x",paste(x))
B = c("y",paste(y))
C = c("",paste0("=linest(B2:B",n+1,", A2:A",n+1,", TRUE, FALSE)"),rep("",n-1))
mydf3 = data.frame(A,B,C)
knitr::kable(mydf3,format="html",table.attr='class="bordered-table"', align = "cc",row.names=T)
```
\

That `linest` will provide two numbers: the slope `r cf[2]` and the intercept `r cf[1]`.

So, our linear model is:
$$y = (`r cf[2]`)x + (`r cf[1]`) $$

Plug in the given value of $x=`r x0`$ for prediction.

$$y ~=~ (`r cf[2]`)(`r x0`) + (`r cf[1]`) ~=~ `r y0`$$

```{r,echo=FALSE}
plot(x,y,xlim=c(floor(xl)-10,ceiling(xh)+10),
     ylim=c(cf[2]*(xl-10)+cf[1], cf[2]*(xh+10)+cf[1]))
abline(mod1,col="red")
points(x0,y0,col="red",pch=3)
points(x0,y0,col="red",pch=4)
points(x0,y0,col="red",pch=1)
```
\



Meta-information
============
extype: num
exsolution: `r y0`
extol: `r tol`
exname: predict_with_trendline