```{r data generation, echo = FALSE, results = "hide"}
library(reticulate)
while(T){
  mn = sample(c(-9:-1,1:9),2)
  md = sample(1:5,2)
  b = sample(c(-8:-1,1:8),2)
  m1 = mn[1]/md[1]
  m2 = mn[2]/md[2]
  b1 = b[1]
  b2 = b[2]
  x = (b2-b1)/(m1-m2)
  y = m1*x+b1
  if(round(x)==x && 
     round(y)==y && 
     abs(x)<11 && 
     abs(y)<11 && 
     abs(x)>0 && 
     abs(y)>0 && x!=y){break}
}
x = round(x)
y = round(y)
al = -10:10
als = paste0("* ",al,"\n",collapse="")

ans1 = paste0(1*(x==al),collapse="")
ans2 = paste0(1*(y==al),collapse="")
```


Question
========

```{python,echo=FALSE}
from sympy import *
x = symbols("x")
lex1 = latex(r.mn[0]*x/r.md[0]+r.b1)
lex2 = latex(r.mn[1]*x/r.md[1]+r.b2)
lex3 = latex(r.mn[0]*x/r.md[0]-r.mn[1]*x/r.md[1]+r.b1-r.b2)
lex4 = latex(r.mn[0]*x/r.md[0]-r.mn[1]*x/r.md[1])
```

Solve the system:
$$y = `r py$lex1`$$
$$y = `r py$lex2`$$

Your answers:

* $x=$ ##ANSWER1##
* $y=$ ##ANSWER2##

Answerlist
--------
`r als`
`r als`


Solution
========

Eliminate $y$ by subtrating the second equation from the first.
$$0 = `r py$lex3`$$

Subtract `r b1-b2` from both sides.

$$`r b2-b1` = `r py$lex4`$$

Multiply/divide to solve for $x$.

$$x = `r x`$$

Plug in `r x` for $x$ in either original equation.

$$y = `r gsub("x",paste0("(",x,")",collapse=""),py$lex1)`$$

$$y = `r y`$$

You can also solve this by graphing!

```{r,fig.dim=c(6,6),echo=FALSE,results="asis"}
library(latex2exp)
par(pty="s")
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),lwd=2,ylab=TeX("$y$"),xlab=TeX("$x$"))
for(j in seq(-10,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xx = seq(-10,10,1)
y1 = m1*xx+b1
y2 = m2*xx+b2
lines(xx,y1,col="blue",lwd=4)
lines(xx,y2,col="red",lwd=4)
```
\


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r ans1`|`r ans2`
exname: solve_lin_sys