---
output:  pdf_document
params:
    showsol: false
---

```{r,echo=F}
set.seed(123)

```

# Practice: solving equations with functions


```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

1. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```

\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

2. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)


\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```

\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

3. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```


\vfill

\newpage



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

4. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)


\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```

\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

5. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```


\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

6. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```

\vfill

\newpage



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

7. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```


\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

8. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```


\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

9. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```


\vfill

\newpage



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

10. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```


\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

11. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)


\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```

\vfill



```{r, echo = FALSE, results = "hide"}
am = "B\\cdot\\left(X+A\\right)"
ad = "\\frac{X+A}{B}"
sm = "B\\cdot\\left(X-A\\right)"
sd = "\\frac{X-A}{B}"
ma = "A\\cdot X+B"
da = "\\frac{X}{A}+B"
ms = "A\\cdot X-B"
ds = "\\frac{X}{A}-B"
qs = c(am,ad,sm,sd,ma,da,ms,ds) #For outer expression

am2 = "B\\left(X+A\\right)"
ad2 = "\\frac{X+A}{B}"
sm2 = "B\\left(X-A\\right)"
sd2 = "\\frac{X-A}{B}"
ma2 = "A X+B"
da2 = "\\frac{X}{A}+B"
ms2 = "A X-B"
ds2 = "\\frac{X}{A}-B"
qs2 = c(am2,ad2,sm2,sd2,ma2,da2,ms2,ds2) #For argument expression


ops = list(c("Add","Multiply by"),
           c("Add","Divide by"),
           c("Subtract","Multiply by"),
           c("Subtract","Divide by"),
           c("Multiply by","Add"),
           c("Divide by","Add"),
           c("Multiply by","Subtract"),
           c("Divide by","Subtract"))

fam = function(X,A,B){B*(X+A)}
fad = function(X,A,B){(X+A)/B}
fsm = function(X,A,B){B*(X-A)}
fsd = function(X,A,B){(X-A)/B}
fma = function(X,A,B){A*X+B}
fda = function(X,A,B){X/A+B}
fms = function(X,A,B){A*X-B}
fds = function(X,A,B){X/A-B}
fs = list(fam,fad,fsm,fsd,fma,fda,fms,fds)

t1 = sample(1:8,1) #arg exp
t2 = sample(1:8,1) #out exp
while(T){
    ns = sample(2:99,4)
    x1 = sample(2:99,1)
    y1 = fs[[t1]](x1,ns[3],ns[4])
    x2 = sample(2:99,1)
    y2 = fs[[t2]](x2,ns[1],ns[2])
    if(y1%%1==0 && y2%%1==0 && y1>1 && y2>1 && y1<100 && y2<100 && length(unique(c(ns,x1,y1,x2,y2)))==8){break}
}
outexp = gsub("A",ns[1],qs[t2],fixed=T)
outexp = gsub("B",ns[2],outexp,fixed=T)
exp1 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp1 = gsub("arg",qs2[t1],exp1,fixed=T)
exp1 = gsub("X","x",exp1,fixed=T)
exp1 = gsub("A",ns[3],exp1,fixed=T)
exp1 = gsub("B",ns[4],exp1,fixed=T)

arg1 = qs2[t1]
arg1 = gsub("X","x",arg1,fixed=T)
arg1 = gsub("A",ns[3],arg1,fixed=T)
arg1 = gsub("B",ns[4],arg1,fixed=T)

am3 = "X+A"
ad3 = "X+A"
sm3 = "X-A"
sd3 = "X-A"
ma3 = "A X"
da3 = "\\frac{X}{A}"
ms3 = "A X"
ds3 = "\\frac{X}{A}"
qs3 = c(am3,ad3,sm3,sd3,ma3,da3,ms3,ds3) #For argument expression
arg3 = qs3[t1]
arg3 = gsub("X","x",arg3,fixed=T)
arg3 = gsub("A",ns[3],arg3,fixed=T)

exp4 = gsub("x",paste0("(",x1,")",collapse=""),exp1,fixed=T)

exp5 = gsub("X","f{\\left[arg\\right]}",outexp,fixed=T)
exp5 = gsub("arg",y1,exp5,fixed=T)

exp6 = gsub("X",x2,outexp,fixed=T)

fam3 = function(X,A){X+A}
fad3 = function(X,A){X+A}
fsm3 = function(X,A){X-A}
fsd3 = function(X,A){X-A}
fma3 = function(X,A){A*X}
fda3 = function(X,A){X/A}
fms3 = function(X,A){A*X}
fds3 = function(X,A){X/A}
fs3 = list(fam3,fad3,fsm3,fsd3,fma3,fda3,fms3,fds3)

ach = numeric()
for(i in 1:8){
    ach = c(ach,fs[[i]](x1,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x2,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x2,ns[3],ns[4]))
    ach = c(ach,fs[[i]](x1,ns[1],ns[2]))
    ach = c(ach,fs[[i]](x1,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x2,ns[2],ns[1]))
    ach = c(ach,fs[[i]](x2,ns[4],ns[3]))
    ach = c(ach,fs[[i]](x1,ns[2],ns[1]))
}
ach = unique(ach)
ach = ach[ach%%1==0]
ach = ach[ach>1]
ach = ach[ach<100]
while(length(ach)<10){
    ach = unique(c(ach,sample(1:99,1)))
}
ach = sample(ach)
if(length(ach)>10){
    ach = ach[1:10]
}
if(!(x1 %in% ach)){
    ach[1] = x1
}
if(!(y2 %in% ach)){
    ach[2] = y2
}
ach = sort(ach)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==x1),collapse="")
sol2 = paste0(1*(ach==y2),collapse="")

```

12. If $f[`r y1`]=`r x2`$, then there exists a knowable solution to the equation below.
$$y=`r exp1`$$
Find the solution. (The solution is the ordered pair $(x,y)$ that makes the equation true.)

\vfill

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n$$x=")
cat(x1)
cat("$$\n\n$$y=")
cat(y2)
cat("$$\n\n\\color{black}\n\n")
```

\vfill