---
title: "Wed Sep 17"
output: slidy_presentation
---

# Agenda

* Entrance Ticket
    * [ET_09_17](https://bart.instructure.com/courses/2110/quizzes/3178)
* Discuss exam scores
* Find a solution to a transformed function when given a corresponding point on $y=f(x)$.
    * [Practice Problems](https://chadworley.github.io/algtwo2026/u02/09_17/outhtml/01_use_fsol_find_gsol.html)
    * [Paper Practice](https://chadworley.github.io/algtwo2026/u02/09_17/practice_solve_eq_w_func.pdf)
    * [OCW_09_17_solve_eq_with_func](https://bart.instructure.com/courses/2110/quizzes/3179)

# Exam scores

```{r,echo=F}
x = c(90,92,81,78,84,58,82,69,71,100,65,94,70,83,70,87,35,47,19,98,59,65,74,68,86)
hist(x,xlab="raw score",main="Histogram of exam scores",breaks = seq(0,100,10))
```

* The test was difficult, and people did quite well.
* I feel a "curve" is warranted.
* Really, it is more of a "50 is the floor" system. If $x$ is the raw score (what is written on your test), you can calculate your mastery score ($y$) using the formula below:
$$y=50+\frac{x}{2}$$

```{r,echo=F}
y = 50+x/2
hist(y,xlab="mastery score",main="Histogram of mastery scores",breaks = seq(0,100,5))
```


# Upcoming topics for Q1

* Function translations
* Function stretches
* Parent functions
* Combining reflections, translations, and stretches with parent functions
* Function descriptions
    * Domain/range
    * Intervals of increase/descrease
    * Intervals of positivity/negativity
    * End behavior
    * Intercepts
    * Extrema (minima and maxima)


# Problem 1

If $f(8)=10$ then we can find a solution to the equation below:

$$y=\frac{f(3x-7)}{5}+4$$

Find the knowable solution.

* $x=$ ?
* $y=$ ?

### Solution

1. Set the argument equal to 8.
$$3x-7=8$$
$$3x=15$$
$$x=5$$

2. Substitute 5 for $x$.
$$y=\frac{f(3\cdot5-7)}{5}+4$$
3. Simplify the argument.
$$y=\frac{f(15-7)}{5}+4$$
$$y=\frac{f(8)}{5}+4$$
4. Substitute 10 for $f(8)$.
$$y=\frac{10}{5}+4$$
$$y=2+4$$
$$y=6$$

So the solution is $(5,6)$, which can be written as two equations: $x=5$ and $y=6$.


# Problem 2

If $f[9]=6$ then we can find a solution to the equation below:

$$y= 4\cdot f{\left[\frac{x+5}{2}\right]}-1$$

Find the knowable solution.

* $x=$ ?
* $y=$ ?

### Solution

1. Set the argument equal to 9.
$$\frac{x+5}{2}=9$$
$$x+5=18$$
$$x=13$$

2. Substitute 13 for $x$.
$$y= 4\cdot f{\left[\frac{13+5}{2}\right]}-1$$
3. Simplify the argument.
$$y= 4\cdot f{\left[\frac{18}{2}\right]}-1$$
$$y= 4\cdot f{\left[9\right]}-1$$
4. Substitute 6 for $f[9]$.
$$y= 4\cdot 6-1$$
$$y=24-1$$
$$y=23$$

So the solution is $(13,23)$, which can be written as two equations: $x=13$ and $y=23$.



# Problem 3

If $f[8]=36$ then we can find a solution to the equation below:

$$y= \frac{1}{4} \cdot f{\left[\frac{x}{2}+5\right]}+22$$

Find the knowable solution.

* $x=$ ?
* $y=$ ?


### Solution

1. Set the argument equal to 8.
$$\frac{x}{2}+5=8$$
$$\frac{x}{2}=3$$
$$x=6$$

2. Substitute 6 for $x$.
$$y= \frac{1}{4} \cdot f{\left[\frac{6}{2}+5\right]}+22$$
3. Simplify the argument.
$$y= \frac{1}{4} \cdot f{\left[3+5\right]}+22$$
$$y= \frac{1}{4} \cdot f{\left[8\right]}+22$$
4. Substitute 36 for $f[8]$.
$$y= \frac{1}{4} \cdot 36+22$$
$$y=9+22$$
$$y=31$$

So the solution is $(6,31)$, which can be written as two equations: $x=6$ and $y=31$.






