```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
maxopt = 10
pfix = function(c,d){
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}
while(T){
    pq = sample(1:maxopt,2)*sample(c(-1,1),2,T)
    p = pq[1]
    q = pq[2]
    A = 1
    B = p+q
    C = p*q
    PE = pfix(c(A,B,C),2:0)
    if(abs(B)>0){break}
}

ch = c((-maxopt):-1,1:maxopt)
fal = character()
for(i in ch){
    ns = pfix(c(1,i),1:0)
    fal = c(fal,ns)
}
fal = paste0("* $",fal,"$",collapse="\n")

sol1 = ch==p
sol2 = ch==q
sol = sol1+sol2
sol = paste0(1*(sol),collapse="")

soltxt1 = pfix(c(1,p,q,p*q),c(2,1,1,0))
solp = pfix(c(1,p),c(1,0))
solq = pfix(c(1,q),c(1,0))

```


Question
========

Consider the quadratic expression shown in standard form:

$$`r PE`$$

In factored form, the expression can be represented as the product of two factors. What are those factors?

Answerlist
--------

`r fal`



Solution
========

You want two numbers that have a sum of `r B` and a product of `r C`.

You can get this by guessing and checking. Eventually you might guess the following factored form:

$$(`r solp`)\cdot(`r solq`)$$

You can check by using polynomial multiplication (in this case you can use the [FOIL method](https://en.wikipedia.org/wiki/FOIL_method)).

```{css,echo=F}
.boxy td {
    border: 1px solid black;
    color: black;
    background-color: white;
  }
.boxy th {
    background-color: rgb(200, 200, 200);
    color: black;
    border: 1px solid black;
  }
.boxy td:first-child {
    background-color: rgb(200, 200, 200);
    color: black;
    border: 1px solid black;
  }
```

<div class="boxy">

| * | $x$ | $`r p`$ |
|:---:|:---:|:---:|
| $x$ | $x^2$ | $`r pfix(p,1)`$ |
| $`r q`$ | $`r pfix(q,1)`$ | $`r p*q`$ |

</div>

$$p(x) ~=~ `r soltxt1`$$

$$p(x) ~=~ `r PE`$$

To spell it out in more detail, you want two numbers that have a sum of `r B` and a product of `r C`. So, you start thinking of factor pairs of `r C` until you find a pair that sums to `r B`. You will see that below I've listed all factor pairs of `r C`, along with the corresponding polynomials in factored and expanded forms.

```{r,echo=F}
flo = numeric()
fhi = numeric()
for(i in 1:floor(sqrt(abs(C)))){
    if(C %% i == 0){
        flo = c(flo,i)
        fhi = c(fhi,round(C/i))
        flo = c(flo,-i)
        fhi = c(fhi,round(-C/i))
    }
}
tlins = character()
for(j in 1:length(flo)){
    pp = flo[j]
    qq = fhi[j]
    lp = pfix(c(1,pp),1:0)
    lq = pfix(c(1,qq),1:0)
    fp = paste0("(",lp,")\\cdot (",lq,")")
    ep = pfix(c(1,pp+qq,pp*qq),2:0)
    tlin = paste0("|",flo[j]," and ",fhi[j],"|$",fp,"$|$",ep,"$|")
    tlins = c(tlins,tlin)
}
tabrows = paste0(tlins,collapse="\n")
```

| Factor pairs of `r C` | Factored polynomial | Expanded polynomial |
|:---:|:---:|:---:|
`r tabrows`

And, so, $`r PE`$ is an [equivalent expression](https://en.wikipedia.org/wiki/Identity_(mathematics)) to $(`r solp`)\cdot(`r solq`)$, which is also equivalent to $(`r solq`)\cdot(`r solp`)$.



Meta-information
============
extype: mchoice
exsolution: `r sol`
exname: factor_quadratic