```{r,echo=F,warning=F}
names = c("sin(x)","cos(x)","tan(x)","csc(x)","sec(x)","cot(x)",
          "arcsin(x)","arccos(x)","arctan(x)",
          "arccsc(x)","arcsec(x)","arccot(x)")
dx = 14/(1001-1)
xs = seq(-7,7,length.out=10000)
ys = list(sin(xs),cos(xs),tan(xs),1/sin(xs),1/cos(xs),1/tan(xs),
          asin(xs),acos(xs),atan(xs),asin(1/xs),acos(1/xs),atan(1/xs)+abs(sign(xs)-1)/2*pi)

ord1 = sample(1:12)

ys2 = ys[ord1]

al = paste0("* y = ",names,"\n",collapse="")

tal = paste0(rep(al,12),collapse="\n")

sols = character()
for(i in 1:12){
  sols = c(sols,paste0(1*(ord1[i]==1:12),collapse=""))
}
tsols = paste0(sols,collapse="|")
ttyps = paste0(rep("schoice",12),collapse="|")
```

Question
========

Match each plot with its function. Different sources define `arccot` with different ranges. I've followed the `arccot` defined by Desmos and [wikipedia](https://en.wikipedia.org/wiki/Inverse_trigonometric_functions#Relationships_among_the_inverse_trigonometric_functions), with a range of $\left[0,\pi\right]$, not $\left[\frac{-\pi}{2},\,\frac{\pi}{2}\right]$. This choice gives a continuous function, but means that when $m<0$, $\arctan(\frac{1}{m})\ne \mathrm{arccot}(m)$. The other possible definition (not used here) is seen on [Wolfram Alpha](https://www.wolframalpha.com/input/?i=arccot+x).


```{r,echo=F,fig.dim=c(5,5),results='asis'}
for(i in 1:length(names)){
  par(pty="s")
  cat(paste0("## Plot ",i,"\n",collapse=""))
  plot(0,0,type="n",xlim=c(-7,7),ylim=c(-7,7),
       xlab="x",ylab="y")
  arrows(-7.5,0,7.5,0,length=0.1,angle=20,code=3)
  arrows(0,-7.5,0,7.5,length=0.1,angle=20,code=3)
  x = xs
  y = ys2[[i]]
  spots = !is.nan(y)
  x = x[spots]
  y = y[spots]
  spots = abs(y)<10
  x = x[spots]
  y = y[spots]
  beg1 = c(1,which(diff(x)>1.1*dx),length(x))
  if(length(beg1)<2){
    lines(x,y)
  } else {
    for(j in 1:(length(beg1)-1)){
      lines(x[(beg1[j]+1):(beg1[j+1]-1)],
            y[(beg1[j]+1):(beg1[j+1]-1)],col="blue",lwd=2)
    }
  }
  
  
  cat(paste0("##ANSWER",i,"##\n\n",collapse=""))
}
```
\

Answerlist
--------

`r tal`



Solution
========

I'd recommend using a graphing utility, like [Desmos](https://www.desmos.com/calculator).

<!-- Here are the solutions: -->

<!-- ```{r,echo=F,fig.dim=c(5,5),results='asis'} -->
<!-- for(i in 1:length(names)){ -->
<!--   par(pty="s") -->
<!--   cat(paste0("### Plot ",i,"\n",collapse="")) -->
<!--   plot(0,0,type="n",xlim=c(-7,7),ylim=c(-7,7), -->
<!--        xlab="x",ylab="y") -->
<!--   arrows(-7.5,0,7.5,0,length=0.1,angle=20,code=3) -->
<!--   arrows(0,-7.5,0,7.5,length=0.1,angle=20,code=3) -->
<!--   x = xs -->
<!--   y = ys2[[i]] -->
<!--   spots = !is.nan(y) -->
<!--   x = x[spots] -->
<!--   y = y[spots] -->
<!--   spots = abs(y)<10 -->
<!--   x = x[spots] -->
<!--   y = y[spots] -->
<!--   beg1 = c(1,which(diff(x)>1.1*dx),length(x)) -->
<!--   if(length(beg1)<2){ -->
<!--     lines(x,y) -->
<!--   } else { -->
<!--     for(j in 1:(length(beg1)-1)){ -->
<!--       lines(x[(beg1[j]+1):(beg1[j+1]-1)], -->
<!--             y[(beg1[j]+1):(beg1[j+1]-1)],col="blue",lwd=2) -->
<!--     } -->
<!--   } -->

<!--   cat("\n") -->
<!--   cat("y = ") -->
<!--   cat(names[ord1[i]]) -->
<!--   cat("\n\n") -->
<!-- } -->
<!-- ``` -->
<!-- \ -->




Meta-information
============
extype: cloze
exclozetype: `r ttyps`
exsolution: `r tsols`
exname: identify_functions