```{r,echo=F,warning=F}
nfull = sample(3:9,1)
pfull = 1/nfull
xn = round(runif(1,1-pfull+0.02,1-0.02),2)
P = xn/nfull
t = seq(-1,2,length.out=3000)
y = cos(2*pi/P*t)
f = 1/P
```


Question
========

A sinusoidal [pure tone](https://en.wikipedia.org/wiki/Pure_tone) is generated by randomly choosing a frequency ($F$) in the following equation:
$$y(t) ~=~ \cos(2\pi F t)$$

```{r,echo=F,fig.dim=c(8,4)}
plot(t,y,xlim=c(0,1),ylim=c(-1,1),type="l",xlab="t (time in seconds)",ylab="y")
arrows(0,-1.1,0,1.1,0.05,20,3,lwd=2)
arrows(-0.03,0,1.03,0,0.05,20,3,lwd=2)
lines(t,y,lwd=2,col="blue")
points(c(0,xn),c(1,1),pch=19,col="red")
text(0.01,0.95,"(0,1)",col="red",adj=0)
text(xn-0.01,0.95,paste0("(",sprintf("%.2f",xn),",1)"),col="red",adj=1)
```
\

As shown above, the curve has maximums at both $t=0$ and $t=`r xn`$. What is the frequency in [Hz](https://en.wikipedia.org/wiki/Hertz)? The tolerance is $\pm 0.01$ Hz.

Solution
========

Count how many periods occur between $t=0$ and $t=`r xn`$.

```{r,echo=F,fig.dim=c(8,4)}
plot(t,y,xlim=c(0,1),ylim=c(-1,1),type="l",xlab="t (time in seconds)",ylab="y")
arrows(0,-1.1,0,1.1,0.05,20,3,lwd=2)
arrows(-0.03,0,1.03,0,0.05,20,3,lwd=2)
lines(t,y,lwd=2,col="blue")
points(c(0,xn),c(1,1),pch=19,col="red")
text(0.01,0.95,"(0,1)",col="red",adj=0)
text(xn-0.01,0.95,paste0("(",sprintf("%.2f",xn),",1)"),col="red",adj=1)
for(i in 1:nfull){
  text(P*i,0.5,i,cex=1.2)
}
```
\

Find the period.

$$P = \frac{`r xn` ~\mathrm{seconds}}{`r nfull`~\mathrm{cycles}}$$

The frequency is the reciprocal of the period.

$$F ~=~ \frac{1}{P} ~=~ \frac{`r nfull`~\mathrm{cycles}}{`r xn` ~\mathrm{seconds}}$$

$$F ~\approx~ `r round(f,2)` ~\mathrm{Hz}$$

Meta-information
============
extype: num
exsolution: `r f`
exname: get_frequency
extol: 0.01