---
output: slidy_presentation
---


# Agenda

* Entrance Ticket: [ET_09_18](https://bart.instructure.com/courses/2110/quizzes/3180)
* Slides: stretching and shifting curves
* [OCW_09_17_solve_eq_with_func](https://bart.instructure.com/courses/2110/quizzes/3179)
* [PCW_09_18](https://bart.instructure.com/courses/2110/assignments/28737)


# Problem 1

Curve $y=f[x]$ hits points $(2,0)$ and $(5,6)$ and $(8,4)$.

```{r,echo=F,fig.dim=c(4,4)}
x = c(2,5,8)
y = c(0,6,4)
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),lwd=0.7,col="grey")
    lines(c(i,i),c(-10,10),lwd=0.7,col="grey")
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey")
    lines(c(i,i),c(-10,10),col="darkgrey")
}
# abline(h=0)
# abline(v=0)
arrows(-10.3,0,10.3,0,0.05,45,3,lwd=2)
arrows(0,-10.3,0,10.3,0.05,45,3,lwd=2)
text(10,0,"x",adj=c(-0.2,1.1))
text(0,10,"y",adj=c(1.1,-0.4))
text(5,0,"5",adj=c(0.5,1.1),col="darkgrey")
text(0,5,"5",adj=c(1.1,0.5),col="darkgrey")


lines(x,y,lwd=2,col="blue")
points(x,y,pch=19,col="blue",cex=0.8)
legend("topleft","y = f[x]",col="blue",lwd=2)

```


Find the corresponding points of the equation below:

$$y~=~\frac{f[3x-7]}{2}+6$$

# Solution 1

Given equation:

$$y~=~\frac{f[3x-7]}{2}+6$$

We were told three input/output pairs of the function.

$$f[2]=0$$
$$f[5]=6$$
$$f[8]=4$$

Let's start by using $f[2]=0$, so let's make the argument equal to $2$.
$$3x-7=2$$
$$3x=9$$
$$x=3$$
$$y=\frac{f[3\cdot 3-7]}{2}+6$$
$$y=\frac{f[9-7]}{2}+6$$
$$y=\frac{f[2]}{2}+6$$
$$y=\frac{0}{2}+6$$
$$y=0+6$$
$$y=6$$
So, the first point on the new curve is $(3,6)$. Now, we can repeat the process using 
$f[5]=6$.
$$3x-7=5$$
$$3x=12$$
$$x=4$$
$$y=\frac{f[3\cdot 4-7]}{2}+6$$
$$y=\frac{f[12-7]}{2}+6$$
$$y=\frac{f[5]}{2}+6$$
$$y=\frac{6}{2}+6$$
$$y=3+6$$
$$y=9$$
The second point on the new curve is $(4,9)$. Now, we can repeat the process using 
$f[8]=4$.

$$3x-7=8$$
$$3x=15$$
$$x=5$$
$$y=\frac{f[3\cdot 5-7]}{2}+6$$
$$y=\frac{f[15-7]}{2}+6$$
$$y=\frac{f[8]}{2}+6$$
$$y=\frac{4}{2}+6$$
$$y=2+6$$
$$y=8$$
And, so our last point is at $(5,8)$.

Let's make a table of the corresponding points:

```{css,echo=F}
#myBorderedDiv table {
  border: 2px solid black; /* Border for the entire table */
  width: 70%; /* Optional: Make the table take full width of its container */
}
#myBorderedDiv th,
#myBorderedDiv td {
  border: 1px solid gray; /* Borders for table headers and data cells */
  padding: 8px; /* Optional: Add some padding inside cells */
  text-align: center; /* Optional: Align text within cells */
}
```


<div id="myBorderedDiv">

| point on $y=f(x)$ | point on $y~=~\frac{f[3x-7]}{2}+6$ |
|:---:|:---:|
| $(2,0)$ | $(3,6)$ |
| $(5,6)$ | $(4,9)$ |
| $(8,4)$ | $(5,8)$ |

</div>


* Questions to ponder
    * What formula produces the new $x$ values from the old $x$ values?
    * What formula produces the new $y$ values from the old $y$ values?

Let's also graph this new curve.

```{r,echo=F,fig.dim=c(4,4)}
x = c(2,5,8)
y = c(0,6,4)
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),lwd=0.7,col="grey")
    lines(c(i,i),c(-10,10),lwd=0.7,col="grey")
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey")
    lines(c(i,i),c(-10,10),col="darkgrey")
}
# abline(h=0)
# abline(v=0)
arrows(-10.3,0,10.3,0,0.05,45,3,lwd=2)
arrows(0,-10.3,0,10.3,0.05,45,3,lwd=2)
text(10,0,"x",adj=c(-0.2,1.1))
text(0,10,"y",adj=c(1.1,-0.4))
text(5,0,"5",adj=c(0.5,1.1),col="darkgrey")
text(0,5,"5",adj=c(1.1,0.5),col="darkgrey")

library(latex2exp)

lines(x,y,lwd=2,col="blue")
points(x,y,pch=19,col="blue",cex=0.8)
legend("topleft",c(TeX("$y = f(x)$"),TeX("y = \\frac{f[3x-7]}{2}+6"),""),col=c("blue","red",NA),lwd=c(2,2,NA))

x2 = c(3,4,5)
y2 = c(6,9,8)

lines(x2,y2,lwd=2,col="red")
points(x2,y2,pch=19,col="red",cex=0.8)


```


Notice the new curve is half as tall and one third as wide. Also, the new curve has shifted.





# Problem 2

Curve $y=f[x]$ hits points $(-3,5)$ and $(0,0)$ and $(2,4)$.

```{r,echo=F,fig.dim=c(4,4)}
x = c(-3,0,2)
y = c(5,0,4)
par(mar=c(0,0,0,0),oma=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
    lines(c(-10,10),c(i,i),lwd=0.7,col="grey")
    lines(c(i,i),c(-10,10),lwd=0.7,col="grey")
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey")
    lines(c(i,i),c(-10,10),col="darkgrey")
}
# abline(h=0)
# abline(v=0)
arrows(-10.3,0,10.3,0,0.05,45,3,lwd=2)
arrows(0,-10.3,0,10.3,0.05,45,3,lwd=2)
text(10,0,"x",adj=c(-0.2,1.1))
text(0,10,"y",adj=c(1.1,-0.4))
text(5,0,"5",adj=c(0.5,1.1),col="darkgrey")
text(0,5,"5",adj=c(1.1,0.5),col="darkgrey")


lines(x,y,lwd=2,col="blue")
points(x,y,pch=19,col="blue",cex=0.8)
legend("topleft","y = f[x]",col="blue",lwd=2)

```


Find the corresponding points of the equation below:

$$y~=~2\cdot f{\left[\frac{x}{3}-1\right]}-6$$

\vspace{10in}


