```{r data generation, echo = FALSE, results = "hide"}
exp_types = sample(1:8,2)
et1 = exp_types[1]
et2 = exp_types[2]
exp_frames = c("M\\cdot\\left(x+A\\right)",
               "M\\cdot x+A",
               "M\\cdot\\left(x-A\\right)",
               "M\\cdot x-A",
               "\\frac{x+A}{M}",
               "\\frac{x}{M}+A",
               "\\frac{x-A}{M}",
               "\\frac{x}{M}-A")

funcs = list(function(x,A,M){M*(x+A)},
             function(x,A,M){M*x+A},
             function(x,A,M){M*(x-A)},
             function(x,A,M){M*x-A},
             function(x,A,M){(x+A)/M},
             function(x,A,M){x/M+A},
             function(x,A,M){(x-A)/M},
             function(x,A,M){x/M-A}
             )
while(T){
    mults = sample(c(2:3),2)
    Mx = mults[1]
    My = mults[2]
    xspace1 = sample(1:3,1)
    yspace1 = sample(1:3,1)
    xspace2 = xspace1*mults[1]
    yspace2 = yspace1*mults[2]
    xbig = sort(sample(0:floor(20/xspace2),3))*xspace2
    ybig = sample(0:floor(20/yspace2),3)*yspace2
    shifts = sample(1:6,2)
    Ax = shifts[1]
    Ay = shifts[2]
    if(et1<5){
        xsmall = funcs[[9-et1]](xbig,Ax,Mx)
        x1 = xbig
        x2 = xsmall
    } else {
        xsmall = funcs[[et1]](xbig,Ax,Mx)
        x1 = xsmall
        x2 = xbig
    }
    if(et2<5){
        ysmall = funcs[[9-et2]](ybig,Ay,My)
        y1 = ysmall
        y2 = ybig
    } else {
        ysmall = funcs[[et2]](ybig,Ay,My)
        y1 = ybig
        y2 = ysmall
    }
    alldem = c(x1,x2,y1,y2)
    m11 = (y1[2]-y1[1])/(x1[2]-x1[1])
    m12 = (y1[3]-y1[2])/(x1[3]-x1[2])
    if(min(alldem)>=0 && max(alldem)<=20 && sum(alldem%%1==0)==12 && m11 != m12){break}
}


exp1 = exp_frames[et2]
exp1 = gsub("x","f{\\left[X\\right]}",exp1,fixed=T)
exp1 = gsub("A",Ay,exp1,fixed=T)
exp1 = gsub("M",My,exp1,fixed=T)
exp1 = gsub("X",exp_frames[et1],exp1,fixed=T)
exp1 = gsub("A",Ax,exp1,fixed=T)
exp1 = gsub("M",Mx,exp1,fixed=T)


answers = c(x2,y2)

ach = sort(answers)
while(length(ach)<10){
    ach=unique(sort(c(ach,sample(0:20,1))))
}

al = paste0("* ",ach,collapse="\n")

answers = c(x2,y2)
sols = character()
for(i in 1:6){
    sols = c(sols,paste0(1*(ach==answers[i]),collapse=""))
}
solstr = paste0(sols,collapse="|")


```

Question
========

Curve $y=f[x]$ contains points $(`r x1[1]`,`r y1[1]`)$ and $(`r x1[2]`,`r y1[2]`)$ and $(`r x1[3]`,`r y1[3]`)$, as shown on the $x$-$y$ plane below.

```{r,echo=F,fig.dim=c(7,3.5)}
par(mar=c(3,3,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
plot(0,0,"n",xlim=c(0,20),ylim=c(0,20),axes=F,ann=F)
for(i in 1:20){
    lines(c(i,i),c(0,20),lwd=0.7)
    lines(c(0,20),c(i,i),lwd=0.7)
}
for(i in seq(0,20,5)){
    lines(c(i,i),c(0,20),lwd=1.2)
    lines(c(0,20),c(i,i),lwd=1.2)
}
axis(1,line=0)
axis(2,line=0)
mtext("x",1,line=2)
mtext("y",2,line=2)
lines(x1,y1,col="blue",lwd=3)
points(x1,y1,col="blue",pch=19,cex=0.8)

# if(params$showsol==T){
#     lines(x2,y2,col="red",lwd=3)
#     points(x2,y2,col="red",pch=19,cex=0.8)
# }

plot(0,0,"n",axes=F,ann=F)
legend("left","y = f[x]",col="blue",lwd=3)
```
\

In other words:
$$f[`r x1[1]`]=`r y1[1]`$$
$$f[`r x1[2]`]=`r y1[2]`$$
$$f[`r x1[3]`]=`r y1[3]`$$

Let function $g$ be a transformation of function $f$, as defined by the equation below:

$$g[x]~=~`r exp1`$$

Find the three corresponding points of curve $y=g[x]$.

```{r,echo=F,warning=F}
library(kableExtra)
x = paste0("##ANSWER",1:3,"##")
gx = paste0("##ANSWER",4:6,"##")
df = data.frame(x,gx)
colnames(df)=c("$x$","$g[x]$")
kable(df)
```

Answerlist
--------

`r al`
`r al`
`r al`
`r al`
`r al`
`r al`


Solution
========

```{r,echo=F,warning=F}
library(kableExtra)
x = paste0(x2)
gx = paste0(y2)
df = data.frame(x,gx)
colnames(df)=c("$x$","$g[x]$")
kable(df)
```


```{r,echo=F}
exp2 = exp_frames[et1]
exp2 = gsub("A",Ax,exp2,fixed=T)
exp2 = gsub("M",Mx,exp2,fixed=T)

```


**How to get the answers...**

Rewrite the given information:
$$f[`r x1[1]`]=`r y1[1]`$$
$$f[`r x1[2]`]=`r y1[2]`$$
$$f[`r x1[3]`]=`r y1[3]`$$
$$g[x]=`r exp1`$$

```{r,echo=F}
exp3 = gsub("x",x2[1],exp1,fixed=T)
exp4 = exp_frames[et2]
exp4 = gsub("x","f{\\left[X\\right]}",exp4,fixed=T)
exp4 = gsub("X",x1[1],exp4,fixed=T)
exp4 = gsub("A",Ay,exp4,fixed=T)
exp4 = gsub("M",My,exp4,fixed=T)
exp5 = exp_frames[et2]
exp5 = gsub("x",y1[1],exp5,fixed=T)
exp5 = gsub("A",Ay,exp5,fixed=T)
exp5 = gsub("M",My,exp5,fixed=T)
```

1. Use $f[`r x1[1]`]=`r y1[1]`$.
    * Set the argument of $f$ equal to `r x1[1]`.
    $$`r exp2`=`r x1[1]`$$
    Solve the two-step equation.
    $$x=`r x2[1]`$$
    Substitute `r x2[1]` for $x$ in the main equation.
    $$g[`r x2[1]`]=`r exp3`$$
    Simplify the argument.
    $$g[`r x2[1]`]=`r exp4`$$
    Substitute `r y1[1]` for $f[`r x1[1]`]$ because $f[`r x1[1]`]=`r y1[1]`$.
    $$g[`r x2[1]`]=`r exp5`$$
    Use arithmetic to evaluate the numerical expression.
    $$g[`r x2[1]`]=`r y2[1]`$$
    So our first new point on $y=g(x)$ is point $(`r x2[1]`,`r y2[1]`)$.
```{r,echo=F}
exp3 = gsub("x",x2[2],exp1,fixed=T)
exp4 = exp_frames[et2]
exp4 = gsub("x","f{\\left[X\\right]}",exp4,fixed=T)
exp4 = gsub("X",x1[2],exp4,fixed=T)
exp4 = gsub("A",Ay,exp4,fixed=T)
exp4 = gsub("M",My,exp4,fixed=T)
exp5 = exp_frames[et2]
exp5 = gsub("x",y1[2],exp5,fixed=T)
exp5 = gsub("A",Ay,exp5,fixed=T)
exp5 = gsub("M",My,exp5,fixed=T)
```
2. Use old point = $(`r x1[2]`,`r y1[2]`)$. So, use $f[`r x1[2]`]=`r y1[2]`$.
    * Set the argument of $f$ equal to `r x1[2]`.
    $$`r exp2`=`r x1[2]`$$
    Solve the two-step equation.
    $$x=`r x2[2]`$$
    Substitute `r x2[2]` for $x$ in the main equation.
    $$g[`r x2[2]`]=`r exp3`$$
    Simplify the argument.
    $$g[`r x2[2]`]=`r exp4`$$
    Substitute `r y1[2]` for $f[`r x1[2]`]$ because $f[`r x1[2]`]=`r y1[2]`$.
    $$g[`r x2[2]`]=`r exp5`$$
    Use arithmetic to evaluate the numerical expression.
    $$g[`r x2[2]`]=`r y2[2]`$$
    So our second new point on $y=g(x)$ is point $(`r x2[2]`,`r y2[2]`)$.
```{r,echo=F}
exp3 = gsub("x",x2[3],exp1,fixed=T)
exp4 = exp_frames[et2]
exp4 = gsub("x","f{\\left[X\\right]}",exp4,fixed=T)
exp4 = gsub("X",x1[3],exp4,fixed=T)
exp4 = gsub("A",Ay,exp4,fixed=T)
exp4 = gsub("M",My,exp4,fixed=T)
exp5 = exp_frames[et2]
exp5 = gsub("x",y1[3],exp5,fixed=T)
exp5 = gsub("A",Ay,exp5,fixed=T)
exp5 = gsub("M",My,exp5,fixed=T)
```
3. Use old point = $(`r x1[3]`,`r y1[3]`)$.  So, use $f[`r x1[3]`]=`r y1[3]`$.
    * Set the argument of $f$ equal to `r x1[3]`.
    $$`r exp2`=`r x1[3]`$$
    Solve the two-step equation.
    $$x=`r x2[3]`$$
    Substitute `r x2[3]` for $x$ in the main equation.
    $$g[`r x2[3]`]=`r exp3`$$
    Simplify the argument.
    $$g[`r x2[3]`]=`r exp4`$$
    Substitute `r y1[3]` for $f[`r x1[3]`]$ because $f[`r x1[3]`]=`r y1[3]`$.
    $$g[`r x2[3]`]=`r exp5`$$
    Use arithmetic to evaluate the numerical expression.
    $$g[`r x2[3]`]=`r y2[3]`$$
    So our third new point on $y=g(x)$ is point $(`r x2[3]`,`r y2[3]`)$.

```{r,echo=F,fig.dim=c(7,3.5)}
par(mar=c(3,3,0,0),oma=c(0,0,0,0),pty="s",mfrow=c(1,2))
plot(0,0,"n",xlim=c(0,20),ylim=c(0,20),axes=F,ann=F)
for(i in 1:20){
    lines(c(i,i),c(0,20),lwd=0.7)
    lines(c(0,20),c(i,i),lwd=0.7)
}
for(i in seq(0,20,5)){
    lines(c(i,i),c(0,20),lwd=1.2)
    lines(c(0,20),c(i,i),lwd=1.2)
}
axis(1,line=0)
axis(2,line=0)
mtext("x",1,line=2)
mtext("y",2,line=2)
lines(x1,y1,col="blue",lwd=3)
points(x1,y1,col="blue",pch=19,cex=0.8)

lines(x2,y2,col="red",lwd=3)
points(x2,y2,col="red",pch=19,cex=0.8)

plot(0,0,"n",axes=F,ann=F)
legend("left",c("y = f[x]","y = g[x]"),col=c("blue","red"),lwd=c(3,3))
```
\

**Shortcut...**

You can save a lot of time by recognizing the following:

```{r,echo=F}
inveq = exp_frames[9-et1]
inveq = gsub("A",Ax,inveq,fixed=T)
inveq = gsub("M",Mx,inveq,fixed=T)
inveq = gsub("x","x_{\\text{old}}",inveq,fixed=T)

yeq = exp_frames[et2]
yeq = gsub("A",Ay,yeq,fixed=T)
yeq = gsub("M",My,yeq,fixed=T)
yeq = gsub("x","y_{\\text{old}}",yeq,fixed=T)

argex = exp_frames[et1]
argex = gsub("A",Ax,argex,fixed=T)
argex = gsub("M",Mx,argex,fixed=T)

outex = exp_frames[et2]
outex = gsub("A",Ay,outex,fixed=T)
outex = gsub("M",My,outex,fixed=T)
outex = gsub("x","f[\\text{arg}]",outex,fixed=T)
```


* The new $x$ values are found using the INVERSE of the argument expression. Remember, the expression in the argument was $`r argex`$, so:
    * $$x_{\text{new}}~=~`r inveq`$$
* The new $y$ values are found using the operations outside the function. It might help to see the original expression with an abbreviated argument: $`r outex`$
    * $$y_{\text{new}}~=~`r yeq`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice|schoice
exsolution: `r solstr`
exname: stretch_and_shift