```{r data generation, echo = FALSE, results = "hide"}
peqs = c("$b = |a|$",
         "$b = \\sqrt{a}$",
         "$b = a^2$",
         "$b = \\sqrt[3]{a}$",
         "$b = a^3$",
         "$b = 2^a$",
         "$b = \\log_{2}(a)$",
         "$b = \\frac{1}{a}$",
         "$b = 3^a$",
         "$b = \\log_3(a)$")

peq2 = c("$y = |x|$",
         "$y = \\sqrt{x}$",
         "$y = x^2$",
         "$y = \\sqrt[3]{x}$",
         "$y = x^3$",
         "$y = 2^x$",
         "$y = \\log_{2}(x)$",
         "$y = \\frac{1}{x}$",
         "$y = 3^x$",
         "$y = \\log_3(x)$")

pas = list(c(-3,-2,-1,0,1,2,3),
           c(0,1,4,9,16,25,36),
           c(-3,-2,-1,0,1,2,3),
           c(-27,-8,-1,0,1,8,27),
           c(-3,-2,-1,0,1,2,3),
           c(-3,-2,-1,0,1,2,3),
           c("\\frac{1}{8}","\\frac{1}{4}","\\frac{1}{2}",1,2,4,8),
           c(-2,-1,"\\frac{-1}{2}","\\frac{1}{2}",1,2),
           c(-3,-2,-1,0,1,2,3),
           c("\\frac{1}{27}","\\frac{1}{9}","\\frac{1}{3}",1,3,9,27))

pbs = list(c(3,2,1,0,1,2,3),
           c(0,1,2,3,4,5,6),
           c(9,4,1,0,1,4,9),
           c(-3,-2,-1,0,1,2,3),
           c(-27,-8,-1,0,1,8,27),
           c("\\frac{1}{8}","\\frac{1}{4}","\\frac{1}{2}",1,2,4,8),
           c(-3,-2,-1,0,1,2,3),
           c("\\frac{-1}{2}",-1,-2,2,1,"\\frac{1}{2}"),
           c("\\frac{1}{27}","\\frac{1}{9}","\\frac{1}{3}",1,3,9,27),
           c(-3,-2,-1,0,1,2,3)
           )

ord1 = sample(1:10)
ord2 = sample(1:10)

ach = peqs[ord2]
al = paste0("* ",ach,collapse="\n")

sols = character()
for(i in 1:10){
    sols = c(sols,paste0(1*(1:10==which(ord2==ord1[i])),collapse=""))
}

```

Question
========

What parent function matches the table?

```{r,echo=F,results='asis',warning=F}
library(kableExtra)
a = pas[[ord1[1]]]
b = pbs[[ord1[1]]]
df = data.frame(paste0("$",a,"$"),paste0("$",b,"$"))
names(df) = c("$a$","$b$")
kable(df) %>%
    kable_styling("bordered",full_width = F)

```


Answerlist
--------

`r al`



Solution
========

The correct answer:

$`r peqs[ord2[which(ord2==ord1[1])]]`$

If you go to [Desmos](https://www.desmos.com/calculator) and graph `r peq2[ord2[which(ord2==ord1[1])]]`, you can see that it indeed goes through the points shown in the table.

You might wonder why I am using $a$ and $b$ in the problem. I am hoping this will help us when we transform the parent functions.


Meta-information
============
extype: schoice
exsolution: `r sols[1]`
exname: parent_tables