```{r data generation, echo = FALSE, results = "hide"}
while(T){
    ylims = sample(2*(0:5),5)
    ylims2 = ylims+sample(c(-1,1),5,T)
    ypnts = c(ylims[1])
    oypnts = numeric()
    for(i in 2:5){
        vv = sample(1:2,2)
        ww = c(ylims[i],ylims2[i-1])
        ypnts = c(ypnts,ww[vv[1]])
        oypnts = c(oypnts,ww[vv[2]])
    }
    ypnts = c(ypnts,ylims2[5])
    xposs = c(2,4,6,8)
    yposs = ypnts[2:5]
    picks = sample(1:4,2)
    x1 = xposs[picks[1]]
    y1 = yposs[picks[1]]
    x2 = xposs[picks[2]]
    y2 = yposs[picks[2]]
    if(min(ylims2)>0 && max(ylims2)<10 &&
       length(unique(ypnts))==6 && 
       y2 %in% oypnts &&
       length(unique(c(x1,y1,x2,y2)))==4){break}
}


ach = 0:10

sol1 = paste0(1*(y1==ach),collapse="")
sol2 = paste0(1*(x2==ach),collapse="")

al = paste0("* ",ach,collapse="\n")
```



Question
========

The graph of $y=f(x)$ is shown below.

```{r,fig.dim=c(10,5),echo=FALSE}
par(pty="s",mar=c(3,3,0,0),mfrow=c(1,2))
plot(0,0,type="n",xlim=c(0,10),ylim=c(0,10),asp=1,ann=F,axes=F)
for(i in 0:10){
  lines(c(0,10),c(i,i),col="grey")
  lines(c(i,i),c(0,10),col="grey")
}
abline(h=0)
abline(v=0)

axis(1,0:10,tick = F,pos = 0)
axis(2,0:10,tick = F,pos = 0)

mtext("x",1,1.2,at=10)
mtext("y",2,1.2,at=10)

for(i in 1:5){
    lines(c(2*i-2,2*i),c(ylims[i],ylims2[i]),col="blue",lwd=3)
}
points(2*(0:5),ypnts,pch=19,col="blue")
points(2*(1:4),oypnts,pch=19,col="blue")
points(2*(1:4),oypnts,pch=19,col="white",cex=0.7)

plot(0,0,type="n",xlim=c(0,10),ylim=c(0,10),asp=1,ann=F,axes=F)
legend("left","y=f(x)",col="blue",lwd=3)
```
\

* $f(`r x1`)=$ ##ANSWER1##
* $f^{-1}(`r y2`)=$ ##ANSWER2##



Answerlist
--------

`r al`
`r al`

Solution
========


To evaluate $f(`r x1`)$, start by finding $x=`r x1`$ on the horizontal axis. Move up until you hit the curve (or a filled dot... NOT an empty dot...). This is marked with a red circle below. Then read off the $y$ coordinate of the point.

$$f(`r x1`)~=~`r y1`$$

To evaluate $f^{-1}(`r y2`)$, start by finding $y=`r y2`$ on the vertical axis. Move sideways until you hit the curve (or a filled dot... NOT an empty dot...). This is marked with a purple circle. Then read off the $x$ coordinate of the point.

$$f^{-1}(`r y2`)~=~`r x2`$$


```{r,fig.dim=c(10,5),echo=FALSE}
par(pty="s",mar=c(3,3,0,0),mfrow=c(1,2))
plot(0,0,type="n",xlim=c(0,10),ylim=c(0,10),asp=1,ann=F,axes=F)
for(i in 0:10){
  lines(c(0,10),c(i,i),col="grey")
  lines(c(i,i),c(0,10),col="grey")
}
abline(h=0)
abline(v=0)

axis(1,0:10,tick = F,pos = 0)
axis(2,0:10,tick = F,pos = 0)

mtext("x",1,1.2,at=10)
mtext("y",2,1.2,at=10)

for(i in 1:5){
    lines(c(2*i-2,2*i),c(ylims[i],ylims2[i]),col="blue",lwd=3)
}
points(2*(0:5),ypnts,pch=19,col="blue")
points(2*(1:4),oypnts,pch=19,col="blue")
points(2*(1:4),oypnts,pch=19,col="white",cex=0.7)


# points(x1,y1,pch=1,cex=1,col="black")
points(x1,y1,pch=1,cex=2,col="red",lwd=2)
# points(x2,y2,pch=1,cex=1,col="black")
points(x2,y2,pch=1,cex=2,col="purple",lwd=2)




plot(0,0,type="n",xlim=c(0,10),ylim=c(0,10),asp=1,ann=F,axes=F)
legend("left","y=f(x)",col="blue",lwd=3)
```
\




Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: eval_func_n_inv_from_graph