---
title: "Creating inverse functions (tables and graphs)"
date: "Fri Aug 29"
author: "Mr. Worley"
output: 
    slidy_presentation:
        incremental: true
---

# Entrance Ticket

Entrance ticket on Canvas: [ET_08_29](https://bart.instructure.com/courses/2110/quizzes/3144)


# Inverse function from table


Consider the function $f$ defined by the table below.

```{css,echo=F}
#myContainer table {
        border-collapse: collapse; /* Optional: Collapses borders for a single line */
        border: 2px solid black; /* Border around the entire table */
    }
#myContainer th,
#myContainer td {
        border: 1px solid grey; /* Borders for individual cells */
        padding: 8px; /* Optional: Add padding for better readability */
}
```

<div id="myContainer">

| $x$ | $f(x)$ |
|:---:|:---:|
| 1 | 5 |
| 2 | 3 |
| 3 | 1 |
| 4 | 2 |
| 5 | 4 |

</div>

What values would you use to fill the inverse function's table?

<div id="myContainer">

| $x$ | $f^{-1}(x)$ |
|:---:|:---:|
| 1 |  |
| 2 |  |
| 3 |  |
| 4 |  |
| 5 |  |

</div>


# Inverse function from table


Consider the function $f$ defined by the table below.

```{css,echo=F}
#myContainer table {
        border-collapse: collapse; /* Optional: Collapses borders for a single line */
        border: 2px solid black; /* Border around the entire table */
    }
#myContainer th,
#myContainer td {
        border: 1px solid grey; /* Borders for individual cells */
        padding: 8px; /* Optional: Add padding for better readability */
}
```

<div id="myContainer">

| $x$ | $f(x)$ |
|:---:|:---:|
| 1 | 5 |
| 2 | 3 |
| 3 | 1 |
| 4 | 2 |
| 5 | 4 |

</div>

What values would you use to fill the inverse function's table?

<div id="myContainer">

| $x$ | $f^{-1}(x)$ |
|:---:|:---:|
| 1 | 3 |
| 2 | 4 |
| 3 | 2 |
| 4 | 5 |
| 5 | 1 |

</div>

Notice you swap the two columns, and then sort the first column. We are still "swapping $x$ and $y$".



# Inverse function from table


Consider the function $f$ defined by the table below.

```{css,echo=F}
#myContainer table {
        border-collapse: collapse; /* Optional: Collapses borders for a single line */
        border: 2px solid black; /* Border around the entire table */
    }
#myContainer th,
#myContainer td {
        border: 1px solid grey; /* Borders for individual cells */
        padding: 8px; /* Optional: Add padding for better readability */
}
```

<div id="myContainer">

| $x$ | $f(x)$ |
|:---:|:---:|
| 1 | 4 |
| 2 | 1 |
| 3 | 2 |
| 4 | 5 |
| 5 | 3 |

</div>

What values would you use to fill the inverse function's table?

<div id="myContainer">

| $x$ | $f^{-1}(x)$ |
|:---:|:---:|
| 1 |  |
| 2 |  |
| 3 |  |
| 4 |  |
| 5 |  |

</div>



# Inverse function from curve

Let function $f$ be defined by the (piece-wise linear) curve shown below.

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(mar=c(4,4,0,0))
set.seed(123)
xy = sample(1:9,8)
x = sort(xy[1:4])
y = sort(xy[5:8],decreasing = sample(c(T,F),1))
par(pty="s")
plot(0,0,type="n",xlim=c(0,11),ylim=c(0,11),lwd=2,ylab="y",xlab="x")
for(j in seq(0,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,y,col="blue",lwd=2)
legend("topright","y=f(x)",lwd=2,col="blue")
#abline(0,1,col="black",cex="0.5",lty=2)
```

* How to find the inverse function's curve?
* "SWAP $x$ AND $y$"
* The curve reflects over the $y=x$ line (the 45° line).
* Find the coordinates of the vertices:
$$(`r x[1]`,`r y[1]`)~~~(`r x[2]`,`r y[2]`)~~~(`r x[3]`,`r y[3]`)~~~(`r x[4]`,`r y[4]`)$$
* Swap the coordinates of the vertices:
$$(`r y[1]`,`r x[1]`)~~~(`r y[2]`,`r x[2]`)~~~(`r y[3]`,`r x[3]`)~~~(`r y[4]`,`r x[4]`)$$
* Draw a new curve connecting those new coordinates.


# Inverse function from curve

The original function $f$ and the inverse function $f^{-1}$ are mirror reflections over the $y=x$ line. This is because we "swap $x$ and $y$."

```{r,fig.dim=c(5,5),echo=FALSE,results="asis"}
par(mar=c(4,4,0,0))
library(latex2exp)
set.seed(123)
xy = sample(1:9,8)
x = sort(xy[1:4])
y = sort(xy[5:8],decreasing = sample(c(T,F),1))
par(pty="s")
plot(0,0,type="n",xlim=c(0,11),ylim=c(0,11),lwd=2,ylab="y",xlab="x")
for(j in seq(0,10,1)){
  abline(h=j,lty=3)
  abline(v=j,lty=3)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(x,y,col="blue",lwd=2)
lines(y,x,col="red",lwd=2)
lines(c(0,11),c(0,11),col="black",lwd=0.5,lty=2)
legend("topright",c(TeX("$y=f(x)$"),TeX("$y=f^{-1}(x)$")),
       lwd=c(2,2),col=c("blue","red"),
       lty=c(1,1))

```



